
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. {\it Bollerslev T.} Generalized autoregressive conditional
heteroskedasticity // Journal of Econometrics. 1986. Vol.~31. N~3.
P.~307--327.

2. {\it Francq C., Zakoian J.-M.} GARCH models: structure,
statistical inference and financial applications. New York: John
Wiley \& Sons, 2010. 504 p.

3. {\it Айвазян С. А., Фантаццини Д.} Эконометрика-2: продвинутый
курс с~приложениями в~финансах. М.: Магистр; Инфра-М, 2014. 944 с.

4. {\it Nelson D.} Conditional heteroskedasticity in asset
returns: a new approach // Econometrica. 1991. Vol.~59. N~2.
P.~347--370.

5. {\it Incl\'{a}n C., Tiao G.} Use of cumulative sums of squares
for retrospective detection of changes of variance // Journal of
the American Statistical Association. 1994. Vol.~89. N~427.
P.~913--923.

6. {\it Kokoszka P., Leipus R.} Testing for parameter changes in
ARCH models // Lithuanian Mathematical Journal. 1999. Vol.~39.
N~2. P.~182--195.

7. {\it Lee S., Tokutsu Y., Maekawa K.} The CUSUM test for
parameter change in regression models with ARCH errors // Journal
of the Japanese Statistical Society. 2004. Vol.~34. N~2.
P.~173--188.

8. {\it Bracker K., Smith K. L.} Detecting and modeling changing
volatility in the copper futures market // Journal of Futures
Markets: Futures, Options, and Other Derivative Products. 1999.
Vol.~19. N~1. P.~79--100.

9. {\it Miralles Marcelo J. L., Miralles Quir\'{o}s J. L.,
Miralles Quir\'{o}s M. M.} Sudden shifts in variance in the
Spanish market: persistence and spillover effects // Applied
Financial Economics. 2008. Vol.~18. N~2. P.~115--124.

10. {\it Malik F.} Estimating the impact of good news on stock
market volatility // Applied Financial Economics. 2011. Vol.~21.
N~8. P.~545--554.

11. {\it Alfreedi A. A., Isa Z., Hassan A.} Regime shifts in
asymmetric GARCH models assuming heavy-tailed distribution:
evidence from GCC stock markets // Journal of Statistical and
Econometric Methods. 2012. Vol.~1. N~1. P.~43--76.

12. {\it Erragragui E., Hassan M., Peillex J., Khan A.} Does
ethics improve stock market resilience in times of instability? //
Economic Systems. 2018. Vol.~42. N~3. P.~450--469.




\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 29 октября 2019~г.

Cтатья принята к~печати 13 февраля 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Борзых Дмитрий Александрович} --- %
%канд. физ.-мат. наук;
borzykh.dmitriy@gmail.com

\vskip2mm \textit{Языков Артем Анатольевич} --- аспирант; %
%канд. физ.-мат. наук;
ayazikov@hse.ru

}
