
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. {\itshape Bertoni\,G., Daemen\,J., Peeters\,M., Assche\,G.\,V.} Sponge functions. Barcelona: Ecrypt Hash Work-\linebreak shop, 2007. 22~p. URL: http://keccak.team/files/SpongeFunctions.pdf (дата обращения: 15.11.2020).
 
\indent2. {\itshape Bertoni G., Daemen J., Peeters M., Van Assche G.} Cryptographic sponge functions. Version 0.1. January 14, 2011.  URL: http://keccak.team/files/CSF-0.1.pdf (дата обращения: 15.11.2020).

3. {\itshape Bertoni G., Daemen J., Peeters M., Van Assche G.} The Keccak reference. SHA-3 competition (round 3), 2011. URL: http://keccak.team/sponge$\_$duplex.html (дата обращения: 15.11.2020).

4. {\itshape Arnault F., Berger T. P., Lauradoux C., Minier M., Pousse B.} A new approach for FCSRs // Cryptology ePrint Archive. Report 2009/167. 2009. URL: http://eprint.iacr.org/2009/167 (дата обращения: 15.11.2020).

5. {\itshape Nizam Chew L. C., Ismail E. S.} $S$-box construction based on linear fractional transformation and permutation function // Symmetry. 2020. Vol.~12. Art. N~826. https://doi.org/10.3390/sym12050826

6. {\itshape Zahid A. H., Arshad M. J.} An innovative design of substitution-boxes using cubic polynomial mapping // Symmetry. 2019. Vol.~11. Art. N~437. https://doi.org/10.3390/sym11030437
	
7. {\itshape Altaleb A., Saeed M. S., Hussain I., Aslam M.} An algorithm for the construction of substitution box for block ciphers based on projective general linear group // AIP Advances. 2017. Vol.~7. Art. N~035116. https://doi.org/10.1063/1.4978264

8. {\itshape Hussain S., Jamal S. S., Shah T., Hussain I.} A power associative loop structure for the construction of non-linear components of block cipher // IEEE Access. 2020. Vol.~8. P.~123492--123506.

9. {\itshape Gao W., Idrees B., Zafar S., Rashid T.} Construction of nonlinear component of block cipher by action of modular group $PSL(2, Z)$ on projective line $PL(GF(2^8))$ // IEEE Access. 2020. Vol.~8. P.~136736--136749.

10. {\itshape Казимиров А.В.} Методы и средства генерации нелинейных узлов замены для симметричных криптоалгоритмов: дисс. канд. техн. наук. Харьков:  Харьк. нац. ун-т радиоэлектроники, 2013. 190~с.

11. {\itshape Rodinko M., Oliynykov R., Gorbenko Y.} Optimization of the high nonlinear $S$-boxes generation method. Bratislava: Tatra Mountains Mathematical Publ., Mathematical Institute, Slovak Academy of Sciences, 2017. Vol.~70. Iss.~1. P.~93--105.

12. {\itshape Ivanov G., Nikolov N., Nikova S.} Cryptographically strong $S$-boxes generated by modified immune algorithm //  Cryptography and Information Security in the Balkans (BalkanCryptSec 2015). Eds by E.~Pasalic, L.~Knudsen. Cham: Springer, 2016. P.~31--42. (Lecture Notes in Computer Science. Vol.~9540.)

13. {\itshape Gorbenko I., Kuznetsov A., Gorbenko Y., Pushkar’ov A., Kotukh Y., Kuznetsova K.} Random\linebreak $S$-boxes generation methods for symmetric cryptography // 2019 IEEE 2nd Ukraine Conference on Electrical and Computer Engineering (UKRCON). Lviv, Ukraine, 2019. P.~947--950.

14. {\itshape Easttom C.} A generalized methodology for designing non-linear elements in symmetric cryp\-to\-grap\-hic primitives // 2018 IEEE 8th Annual Computing and Communication Workshop and Con\-fe\-ren\-ce (CCWC). Las Vegas: NV, 2018. P.~444--449.


%\pagebreak
\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 8 января 2021~г.

Cтатья принята к~печати 4 июня 2021~г.

\vskip5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Оспанов Руслан Маратович} --- ст. науч. сотр.; ospanovrm@gmail.com

\vskip2 mm \textit{Сейткулов Ержан Нураханович} --- канд. физ.-мат. наук, доц.; yerzhan.seitkulov@gmail.com

\vskip2 mm \textit{Сисенов Нурбек Маханбетович} --- докторант, науч. сотр.; nurbek9291@mail.ru

\vskip2 mm \textit{Ергалиева Бану Бакытжановна} --- науч. сотр.; ergalieva\_banu@mail.ru


}
