
{\normalsize

\vskip 4.5%6
mm
%\newpage

\noindent{\bf Photocatalytic fatigue of the polymer nanocomposites %$^{*}$
 }

}

\vskip 2%3
mm

{\small

\noindent{\it A. V. Orekhov, Yu. M. Artem'ev, G. V. Pavilaynen %
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St~Petersburg State University, 7--9, Universitetskaya nab., St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Orekhov A. V., Artem'ev Yu. M., Pavilaynen G. V. Photocatalytic fatigue of the polymer nanocomposites. {\it Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p8}--\pageref{p8e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent We discuss the change in mechanical properties of polymeric nanocomposites with photoactive components caused by solar range lighting. Given degradation photoassisted processes are related with the semiconductor nature of component photoactive particles as photo\-ca\-ta\-lysts. Semiconductor particles can be transferred into electron-exited states due to light quanta absorption. One possible way out from these states is through redox electrochemical reactions with neighbor molecules. The redox reactions can produce transformations of polymer structure and composition, decreasing its mechanical strength. The term ``photo\-ca\-ta\-ly\-tic fatigue'' denotes a special case of the photo-degradation of polymers resulted only in a change in the strength value of the material. We review not numerous published data on investigations of changes in mechanical properties of polymeric nanocomposite, and mainly in the strength value, arisen from solar range light irradiation. We compare the degradation processes of polymeric nanocomposites containing photoactive  components and of the high-cycle fatigue in metals. Likewise, we propose the use of equations of metal high-cycle fatigue curves as a possible approach to mathematical modeling of the processes of polymeric nanocomposites photodegradation. In this, the number of cycles is substitution with exposure time. Especially, the high-cycle fatigue curve equation for the samples with stress  concentrations is considered. The experimental parameters of the ``photocatalytic fatigue'' equation for polymer nanocomposites containing photoactive components are calculated \mbox{using} the  Monte Carlo method.
\\[1mm]
\textit{Keywords}: photocatalysis, polymer nanocomposites,  polypropylene, cyclic fatigue, titanium dioxide,  Wohler curve, stress concentration, Monte Carlo method.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1.\; {Fishman G.\,S.} \emph{Monte Carlo: concepts, algorithms and applications}. New York, USA, Springer Publ., 1996, 698~p.

2.\; {Asmussen S., Glynn P.\,W.} \emph{Stochastic simulation: algorithms and analysis}. New York, USA, Springer Publ., 2007, 476~p.

3.\; {Kroese D.\,P., Taimre T., Botev Z.\,I.} \emph{Handbook of Monte Carlo methods}. New York, USA, John Wiley \& Sons Publ., 2011, 772~p.

4.\; Ermakov S.\,M. \emph{Metod Monte Karlo i smezhnyye voprosy} [\emph{Monte-Carlo method and related issues}]. Moscow, Nauka Publ., 1975, 472~p. (In Russian)

5.\; Ermakov S.\,M., Zhiglyavsky A.\,A. \emph{Matematicheskaya teoriya optimal'nogo eksperimenta} [\emph{Ma\-the\-ma\-ti\-cal theory of optimal experiment}]. Moscow, Nauka Publ., 1987, 320~p. (In Russian)

6.\; Zhiglyavsky A.\,A. \emph{Matematicheskaya teoriya global'nogo sluchaynogo poiska} [\emph{Mathematical theory of global random search}]. Leningrad, Publishing House of Leningrad State University, 1985, 296~p. (In Russian)

7.\; {Nocedal J., Wright S.} \emph{Numerical optimization}. New York, USA, Springer Publ., 2006, 664~p.

8.\; Vasiliev F.\,P. \emph{Metody optimizatsii} [\emph{Optimization methods}]. Moscow, Publishing House of the Moscow Center for Continuous Mathematical Education, 2011, 434~p. (In Russian)

9.\; Malozemov V.\,N., Tamasyan G.\,Sh. O napravlenii naiskoreyshego spuska [On the direction of the steepest descent]. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Cont\-rol Processes}, 2019, vol.~15, iss.~4, pp.~489--501. %\\
https://doi.org/10.21638/11702/spbu10.2019.406 (In Russian)

10.\; {Hanemann T., Szabo D.\,V.} Polymer-nanoparticle composites: From synthesis to modern applications. \emph{Materials}, 2010, vol.~3, pp.~3468--3517. %\\
https://doi.org/10.3390/ma3063468

11.\; {Oladele I.\,O., Omotosho T.\,F., Adediran A.\,A.} Polymer-based composites: An indispensable material for present and future applications. \emph{Intern. Journal of Polymer Science}, 2020, Article ID 8834518, 12~p. %\\
https://doi.org/10.1155/2020/8834518

12.\; {Zepeng M., Zhangbin Y., Jun Zh.} SrTiO$_3$ as a new solar reflective pigment on the cooling property of PMMA-ceramic composites. \emph{Ceramics International}, 2019, vol.~45, iss.~13, pp.~16078--16087. \\
 https://doi.org/10.1016/j.ceramint.2019.05.124

13.\; {Shuang Shi, Dongya Sh., Tao Xu, Yuqing Zh.} Thermal, optical, interfacial and mechanical properties of titanium dioxide/shape memory polyurethane nanocomposites. \emph{Composites Science and Technology}, 2018, vol.~164, no.~18, pp.~17--23. %\\
https://doi.org/10.1016/j.compscitech.2018.05.022

\pagebreak

14.\; Pleskov Yu.\,V., Gurevich Yu.\,Ya. \emph{Semiconductor photoelectrochemistry}. Consultants Bureau, trans. ed. P.~N.~Bartlett. New York, Springer Publ., 1986, XXV + 422~p. (Rus. ed.: Gurevich Yu.\,Ya., Pleskov Yu.\,V. {\it Fotoelektrokhimiia poluprovodnikov}. Moscow, Nauka Publ., 1983, 312~p.)

15.\; Ranby B.\,J., Rabek J.\,F. \emph{Photodegradation, photo-oxidation, and photostabilization of polymers}. London, UK, Wiley Publ., 1975, 652~p. (Rus. ed.: Ranby B.\,J., Rabek J.\,F. {\it Fotodestruktsiia, fotookislenie, fotostabilizatsiia polimerov}. Moscow, Mir Publ., 1978, 676~p.)

16.\; {Klemchuk P. P.} Influence of pigments on the light stability of polymers: A critical review. \emph{Polymer Photochemistry}, 1983, vol.~3, iss.~1, pp.~1--27. %\\
 https://doi.org/10.1016/0144-2880(83)90042-8

17.\; Emanue'l N. M., Buchachenko A. L. \emph{Khimicheskaya fisika molekulyarnogo razrusheniyu i stabilizatsii polimerov} [\emph{The chemical physics of the molecular decomposition and stabilization of polymers}]. Moscow, Nauka Publ., 1988, 388~p. (In Russian)

18.\; {Egerton G.\,S.} Photosensitizing properties of dyes and white pigments. \emph{Nature}, 1964, vol.~204, pp.~1153--1155. %\\
https://doi.org/10.1038/2041153a0

19.\; {Egerton G.\,S., Shah K.\,M.} The effect of temperature on the photochemical degradation of textile materials. Pt I. Degradation sensitized by titanium dioxide. \emph{Textile Research Journal}, 1968, vol.~38, iss.~2, pp.~130--135. %\\
 https://doi.org/10.1177/004051756803800204

20.\; {Kamrannejad M.\,M., Hasanzadeha A., Nosoudi N., Mai L., Babaluo A.\,A.} Photocatalytic degradation of polypropylene/TiO$_2$ nano-composites materials. \emph{Research-Ibero-American Journal of Materials}, 2014, vol.~17, iss.~4, pp.~1039--1046. %\\
 http://dx.doi.org/10.1590/1516-1439.267214

21.\; {Mavric Z., Tomsic B., Simoncic B.} Recent advances in the ultraviolet protection finishing of textiles. \emph{Tekstilec}, 2018, vol.~61(3), pp.~201--220. %\\
 https://doi.org/10.14502/Tekstilec2018.61.201-220

22.\; {Wiener J., Chladova A., Shahidi Sh., Peterova L.} Effect of UV irradiation on mechanical and morphological properties of natural and synthetic fabric before and after nano-TiO$_2$ padding.  \emph{Autex Research Journal}, 2017, vol.~17(4), pp.~370--378. %\\
 http://dx.doi.org/10.1515/aut-2017-0002

23.\; {Chang H. T., Wu N. M., Zhu F.} A kinetic model for photocatalytic degradation of organic contaminants in a thin film TiO$_2$ catalyst. \emph{Water Research}, 2000, vol.~34(2), pp.~407--416. \\
 https://doi.org/10.1016/S0043-1354(99)00247-X

24.\; {Sanongraj W., Chen Y., Crittenden J.\,C., Destaillats H., Hand D.\,W., Perram D.\,L., Taylor R.} Mathematical model for photocatalytic destruction of organic contaminants in air. \emph{Journal of the Air $\&$ Waste Management Association}, 2007, vol.~57, iss.~9, pp.~1112--1122. Publ. online: February 24, 2012. \\
 https://doi.org/10.3155/1047-3289.57.9.1112

25.\; {Lee Q.\,Y., Li H.} Photocatalytic degradation of plastic waste: A mini review. \emph{Micromachines}, 2021, vol.~12, p.~907. %\\
 https://doi.org/10.3390/mi12080907

26.\; {W\"{o}hler A.} \"{U}ber die festigkeitsversuche mit eisen \"{u}nd stahl. \emph{Zeitschrift f\"{u}r Bauwesen}, 1870, vol.~20, pp.~73--106.

27.\; {Rozumek D.} The development of fatigue cracks in metals. \emph{Materials Research Proceedings}, 2019, vol.~12, pp.~124--130. %\\
https://doi.org/10.21741/9781644900215-18

28.\; {Schijve J.} \emph{Fatigue of structures and materials}. Berlin, Heidelberg, Germany, Springer Publ., 2009, 622~p.

29.\; {Kim H.\,S.} \emph{Mechanics of solids and fracture}. 3rd ed. London, UK, Bookboon Publ, 2018. 223~p.

30.\; Stepnov M.\,N., Naumkin A.\,C. Raschetno-eksperimental'nyi metod postroyeniia krivykh mno\-go\-tsik\-lo\-voi ustalosti dlia elementov konstruktsii s kontsentratsiei napryazhenii [A computational and experimental method for plotting multicycle fatigue curves for structural].  \emph{Journal of machinery manufacture and reliability}, 2012, vol.~41(1), pp.~34--38. (In Russian)

31.\; {Kulawinski~D., Nagel K., Henkel S., Hubnerb P., Fischer H., Kuna M., Biermann~H.}  Characterization of stress-strain behavior of a cast TRIP steel under different biaxial planar load ratios. \emph{Engineering Fracture Mechanics}, 2011, vol.~78, iss.~8, pp.~1684--1695. \\
 https://doi.org/10.1016/j.engfracmech.2011.02.021


\vskip1.5mm Received:  February 20, 2021.

Accepted: June 21, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Andrey V. Orekhov} --- Senior Lecturer; a\_v\_orehov@mail.ru \par
%
\vskip2mm \textit{Yurii M. Artem'ev} --- PhD in Chemistry, Associate Professor; yuriim54@yandex.ru \par
%
\vskip2mm \textit{Galina V. Pavilaynen} --- PhD in Physics and Mathematics, Associate Professor;\\ g\_v\_pavilaynen@mail.ru \par
%
%
}
