
{\small

\vskip4%6
mm \noindent \textbf{Литература}

}

\vskip1.8%3
mm

{\footnotesize

1.  \emph{\it  Полякова Л. Н., Буре В. М., Карелин В. В.} Максиминный
подход к оценке объема заказа товара в условиях падения спроса~// Вестник Санкт-Петербургского университета.  Прикладная математика. Информатика. Процессы управления.
 2018. Т.~14. Вып.~4. C.~252--260.\\
https://doi.org/10.21638/11701/spbu10.2018.408

2. \emph{\it Aggarwal S. P., Jaggi C. K.}
 Ordering policies of deteriorating items under permissible delay in payments~//
  J. Oper. Res. Soc.  1995. Vol.~46. N~5. P.~658--662.

3. \emph{\it 	Буре В. М., Карелин В. В., Буре А. В.}
Оценка объема заказа товара при возможном падении спроса~// Вестник Санкт-Петербургского университета.  Прикладная математика. Информатика. Процессы управления,
 2018. Т.~14. Вып.~3. C.~252--260.\\
 https://doi.org/10.21638/11701/spbu10.2018.306

4.  \emph{\it Bure	V. M., Karelin V. V., Polyakova  L. N.}
 Probabilistic model of terminal services~// Appl. Math. Sci. 2016. Vol.~10(39). P.~1945--1952. %\\
https://doi.org/10.12988/ams.2016.63131

5.  \emph{\it  Буре В. М., Карелин В. В., Полякова Л. Н., Ягольник И. В.}
 Моделирование процесса заказа для кусочно-линейного спроса с насыщением~// Вестник Санкт-Петербургского университета.  Прикладная математика. Информатика. Процессы управления.
    2017. Т.~13. Вып.~2. С.~138--146.

6.  \emph{\it Bure V. M., Karelin V. V., Myshkov S. K., Polyakova L. N. }
 Determination of order quantity with piecewise-linear demand function with saturation~//  Intern. Journal of Applied Engineering Research.
    2017. Vol.~12, N~18. P.~7857--7862.

7. \emph{\it 	Chen S. C., Teng J. T., Skouri K. }
 Economic production quantity models for deteriorating items
 with up-stream full trade credit and down-stream partial trade credit~// Intern. Journal Prod. Econ.  2013. Vol.~155.  P.~302--309.

8.  \emph{\it 	Dave U. }
Letters and viewpoints on  economic order quantity under conditions
of permissible delay in payments~// J. Oper. Res. Soc. 1985. Vol.~46.  N~5. P.~1069--1070.


9.  \emph{\it 	Giri B. C., Sharma S.}
 An integrated inventory model for a deteriorating item with allowable
  shortages and credit linked wholesale price~//
  Optim. Lett. 2015. Vol.~37. P.~624--637.\\
  https://doi.org/10.1007/s11590-014-0810-2

10.  \emph{\it Giri B. C., Sharma S.}
Optimal ordering policy for an inventory system with linearly
increasing demand and alowable shortages under two levels trade credit financing~// Oper. Res. Intern. Journal. 2016. Vol.~16.  P.~25--50.

11.  \emph{\it 	Goyal S.  K. }
 Economic order quantity under conditions of permissible delay in payments~//
  J. Oper. Res. Soc. 1985. Vol.~36(4). P.~335--338.

12.  \emph{\it 	Huang Y. F. }
Optimal retailer’s ordering policies in the EOQ model under trade credit financing~// J. Oper. Res. Soc. 2003. Vol.~54(9). P.~1011--1015.

13.  \emph{\it Huang Y. F., Hsu K. H.}
 An EOQ model under retailer partial trade credit policy in supply chain~// Intern. Journal  Prod. Econ. 2008. Vol.~112(2). P.~655--664.

14.  \emph{\it 	Jamal A. M. M., Sarker B. R., Wang S. }
 An ordering policy for deteriorating items with allowable shortages
  and permissible delay in payment~// J. Oper. Res. Soc. 1997. Vol.~48(8). P.~826--833.

15.  \emph{\it 	Khanra S., Ghosh S. K., Chaudhuri K. S.} An EOQ model for a deteriorating item with time dependent quadratic demand under permissible delay in payment // Appl. Math. Comput. 2011. Vol.~218(1). P.~1--9.

16.  \emph{\it 	Khanra S., Mandal B., Sarkar B.} An inventory model with time  dependent demand and shortages under trade credit policy //
  Econ. Model. 2013. Vol.~35. P.~349--355.

17.  \emph{\it 	Maihami R., Abadi I. N. K. } Joint control of inventory and its pricing for non-instantaneously deteriorating items under permissible delay in payments and partial backlogging // Math. Comp. Model. 2012. Vol.~55(5--6). P.~1722--1733.

18.  \emph{\it  Васильев Ф. П. } Методы оптимизации. Кн.~1. М.: Изд-во 	Моск. центра непрерывного матем. образования, 2011. 624~с.

 19. \emph{\it Поляк Б. Т.} Введение в оптимизацию. М.: Наука, 1983. 384~с.

20.  \emph{\it  Сухарев А. Г., Тимохов А. В., Федоров  В. В.}
Курс методов оптимизации.  М.: Наука, 1986.  325~с.

21. \emph{\it   Федоров В. В.} О методе штрафных функций в задаче определения максимина~// Журн. вычисл. матем. и матем. физ.  1972.  №~2. С.~321--333.

 22.  \emph{\it   Полякова Л. Н.} О методе точных штрафных квазидифференцируемых функций~//  Журн. вычисл. матем. и матем. физ.
2001. Т.~41.   №~2. С.~225--238.


%\pagebreak
\vskip 1.2mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 февраля 2021~г.

Cтатья принята к~печати 13 октября 2021~г.

\vskip4%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:


\vskip1.5 mm \textit{Буре Владимир Мансурович} --- д-р техн. наук, проф.;
vlb310154@gmail.com\par%


\vskip1.5 mm \textit{Карелин Владимир Витальевич} --- канд. физ.-мат. наук, доц.; vlkarelin@mail.ru \par%


\vskip1.5 mm \textit{Полякова Людмила Николаевна} --- д-р  физ.-мат. наук, проф.; lnpol07@mail.ru \par%
%
}
