


\zageng{519.6}{S. Kotsios, I. Kostarakos}{CONTROLLING NATIONAL
INCOME\\ AND PUBLIC DEBT VIA FISCAL POLICY.\\ A MODEL MATCHING
ALGORITHMIC APPROACH}{



\vspace{-3mm}\parindent=7mm



%%%%%%%%%%%%%%%%%%%%%%%%%{\copyright} А.~В.~Буре, 2014

%\textit{Новоселов Виктор Сергеевич} --- доктор
%физико-математических наук, профессор,
% главный науч\-ный сотрудник; v.novoselov@spbu.ru


%\textit{Новоселов Виктор Сергеевич} --- доктор
%физико-математических наук, профессор,
% главный науч\-ный сотрудник; v.novoselov@spbu.ru



%\vskip 2.5mm

\emph{Kotsios Stelios} --- doctor of philosophical sciences,
professor; :skotsios@econ.uoa.gr

\emph{Kostarakos Ilias} --- master; hkostarak@econ.uoa.gr


\vskip 2.5mm

\textit{Котсиос Стелеос} --- доктор философских наук, профессор;
:skotsios@econ.uoa.gr


\textit{Костаракос Илиас} --- магистр; hkostarak@econ.uoa.gr


{\copyright} Санкт-Петербургский государственный университет, 2016
}

%$^{*)}$ Работа выполнена при финансовой поддержке
%Санкт-Петербургского государственного университета (грант
%№~6.0.24.2010).}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp08 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\emph{\doivyp/spbu10.\issueyear.\issuenum08 } }\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp08 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp/spbu10.\issueyear.\issuenum08}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize



\noindent National and Kapodistrian University of Athens,\\ 30,
ul.~Panepistimiu, Athens, 10559, Greece




\vskip2.0mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item Our aim in this paper is to present an application of the exact model
matching approach to a~linear, discrete macroeconomic model with
delays. The solution is based on algebraic methods and the
development, in computer algebra software, of appropriate symbolic
algorithms that produce a class of feedback laws as a solution.
These feedback laws constitute a class of potential policies that
the policymaker can implement on the system and modify its
dynamics so that predetermined, desired targets are met. In order
to see the effects of different policies, we implement two
feedback laws on the system at hand. Refs 9. Table 1.

{\it Keywords}: algebraic methods, linear discrete systems, model
matching, symbolic algorithms.

\end{list}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Русский ?


\vskip2.0mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it С. Котсиос, И. Костаракос}

\vskip2mm \noindent{\bf УПРАВЛЕНИЕ НАЦИОНАЛЬНЫМ ДОХОДОМ\\ И
ГОСУДАРСТВЕННЫМ ДОЛГОМ\\ ПОСРЕДСТВОМ ФИСКАЛЬНОЙ ПОЛИТИКИ.\\
МОДЕЛЬ, ПОДСТРАИВАЮЩАЯ АЛГОРИТМ}

\vskip2.0mm


{\footnotesize

\noindent Афинский национальный университет имени Каподистрии,\\
Греция, 10559, Афины, ул. Панепистимиу, 30


\vskip2.5mm


\item Целью в данной работе является применение модели, подстраивающейся к линейной,
дискретной макроэкономической модели с задержками. Решение
основано на алгебраических методах и на развитии алгебраического
программного обеспечения соответствующих символьных алгоритмов,
которые создают класс законов обратной связи. Эти законы обратной
связи представляют собой класс потенциальных стратегий, которые
политик может реализовать, управляя системой и изменением ее
динамики так, чтобы достигались заранее заданные цели. Для того
чтобы продемонстрировать эффект использования различных стратегий,
мы реализуем два закона обратной связи в рассматриваемой системе.
Библиогр.~9 назв. Табл.~1.

\textit{Ключевые слова}: алгебраическиу методы, линейные
дискретные системы, модель, подстраивающая алгоритм.


}

\end{list}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Русский ?

\vskip4mm

The scope of this paper is to examine the problem of shaping the
time path of a linear, discrete macroeconomic model with delays,
using appropriate feedback controllers so that its outputs exactly
follow a predetermined trajectory of desired values. This is,
essentially, a tracking problem that can be tackled utilizing the
(exact) model matching approach under which we want to modify the
nominal plant in such a way that it matches a desired system. In
particular, it amounts to calculating appropriate linear, causal
feedback laws such that the resulting closed-loop system is
identical to a desired one that produces the requested output
values. Although the linear model matching approach has been
extensively studied and is well documented in the control
literature (see, among others [1--4]), it has not, to the extent
of our knowledge, been used in the economic policy literature (for
some exceptions, see [5, 6]) and for a nonlinear application, (see
[7, 8]) in spite of its advantages. The main advantage of this
approach is that it relies only on the use of algebraic tools.
Moreover, the algorithmic nature of the solution allows for the
calculation of a class of feedback laws appropriate for solving
the model matching problem. From an economic policy point of view,
this implies that the policymaker has at his disposal a set of
policy rules available that can be used, depending on the
particular problem at hand.
%\\

\textbf{The macroeconomic model.}\label{model} We consider a
linear deterministic macroeconomical model, described by the
following difference equations:
%
\begin{equation}\label{Y}
Y(t)=C(t)+I(t)+\lambda_0G(t)+\lambda_1G(t-1)+\lambda_2G(t-2),
\end{equation}
\begin{equation}\label{C}
C(t)=(1-s)Y^d(t-1)+sY^d(t-2),
\end{equation}
\begin{equation}\label{Yd}
Y^d(t)=Y(t)-T(t),
\end{equation}
\begin{equation}\label{T}
T(t)=\tau Y(t-1)+E(t),
\end{equation}
\begin{equation}\label{I}
I(t)=\nu(Y(t-1)-Y(t-2)),
\end{equation}
\begin{equation}\label{B}
B(t)=(1+r)B(t-1)+G(t)-T(t),
\end{equation}
%
where $Y(t)$ denotes the national income (GDP); $C(t)$ is
consumption; $I(t)$ is investment; $B(t)$  is the stock of public
debt; $G(t)$ stands for government expenditures; $Y^d(t)$ is the
disposal income; $T(t)$ the tax receipts and $E(t)$ is a distinct
form of taxation, assumed to represent extra tax on wealth. The
$\lambda_i$  parameters indicate that the decision regarding
government expenditures in period $t$ affects the level of GDP in
period $t+i$; that is, there is a delay in the realization of the
effects of changes in government expenditures on GDP levels.
Equations (1)--(5) constitute a variant of the standard
multiplier-accelerator model introduced in [9] whereas equation
(6) is the government budget constraint. Regarding the parameters
of the system, $s\in (0,1)$  is the marginal propensity to save,
$\tau\in (0,1)$ is the (constant) tax rate, $\nu >0$  is the
accelerator and $r\in (0,1)$  is the constant interest on
previously issued public debt. Apart from the $\lambda_i$
parameters, delays are also introduced into the model through
equations (\ref{C}) and (\ref{I}), since it is assumed that the
current levels of  $C(t),I(t)$,   depend upon changes in lagged
values of $Y(t)$.

After all the necessary substitutions and some algebra we end up
with the discrete system
%\begin{multline}
\begin{equation*}
Y(t)-a_1Y(t-1)-a_2Y(t-2)+a_3Y(t-3)=\lambda_0G(t)+\lambda_1G(t-1)~+%\\
\end{equation*}
\begin{equation*}
+\lambda_2G(t-2)-a_4E(t-1)-a_5E(t-2), %\\
\end{equation*}
\begin{equation*} %\\
B(t)-(1+r)B(t-1)-\tau Y(t-1)=G(t)-E(t),
\end{equation*}
%\end{multline}
here $a_1=1+\nu-s$, $a_2=s-\nu-\tau(1-s)$, $a_3=s\tau$, $a_4=1-s$,
$a_5=s$. This is a discrete input--output control system, with
$G(t)$ and $E(t)$ being the inputs, and $Y(t)$ and $B(t)$ the
outputs. Certain initial conditions are assigned to the system,
thus permitting the calculation of all future values of the
outputs for any given input sequences.

Using the notion of the $q$-operator, that is, a lag operator
defined as: $q^mf(t)=f(t-m)$, for any sequence $f(t)$,
$t=0,1,2,\ldots$, the system can be expressed in the following
so-called algebraic form: \small
\[\left[\begin{array}{cc}
1-a_1q-a_2q^2-a_3q^3 & 0 \\
-\tau q  & 1-(1+r)q \end{array} \right]\left[\begin{array}{c}
Y(t) \\
B(t) \end{array} \right]\\=\left[\begin{array}{cc}
\lambda_0+\lambda_1q+\lambda_2q^2 & a_4q+a_5q^2 \\
1                 &     -1
\end{array}
\right]\left[\begin{array}{c}
G(t) \\
E(t) \end{array} \right]\] \normalsize
\begin{equation}\label{alg}
\Longleftrightarrow \qquad {\cal D}(q)\mathbf{z}(t)={\cal
K}(q)\mathbf{u}(t),
\end{equation}\newpage
\noindent where $\mathbf{z}(t)=(Y(t),B(t))^T$,
$\mathbf{u}(t)=(G(t),E(t))^T$ ($T$ denotes transpose ) and ${\cal
D,K}$ are the corresponding $q$-polynomial matrices.
%\\

\textbf{The model matching problem for the macroeconomic model.}
The economic policy problem that we aim to solve is that of
designing appropriate linear, causal feedback laws such that the
resulting closed-loop system exactly tracks the desired sequence
of outputs. In order to solve the problem at hand we follow the
exact model matching approach, which describe in brief. First, the
desired values of the outputs, the so-called reference sequences
(say, $Y^*(t)$ and $B^*(t)$ respectively) are determined by the
policymaker. Then, a linear system is constructed, that produces
as outputs these reference sequences.  Such a linear system can be
represented as
\begin{equation}\label{desired}
{\cal D}^d(q)\mathbf{z}^*(t)={\cal K}^d(q)\mathbf{u}_c(t),
\end{equation}
here $\mathbf{z}^*(t)=(Y(t)^*,B(t)^*)^T$ and ${\cal D}^d(q),{\cal
K}^d(q)$, are appropriate  $q$-polynomial matrices and
$\mathbf{u}_c(t)$ is the command input. System (\ref{desired}) is
known as the desired system. Now, the problem upon discussion is
that of finding linear, causal feedback laws of the form
\begin{equation}\label{feedback}
{\cal R}(q)\mathbf{u}(t)={\cal T}(q)\mathbf{u}_c(t)-{ \cal
S}(q)\mathbf{z}(t),
\end{equation}
where  ${\cal R}(q),{ \cal T}(q),{\cal S}(q)$,
are  $q$-polynomial matrices to be determined, such that the
resulting closed-loop system will be identical (i.~e. matched) to the desired system (\ref{desired}). The following theorems describe the solution method and characterize the solution set.%\\

\textbf{Theorem 1.}\label{eks} {\it Let us suppose that a feedback
law of the form $(\ref{feedback})$ is connected to the nominal
plant $(\ref{alg})$. The obtained closed-loop system will give the
same output with that of the desired system $(\ref{desired})$
under the same initial conditions and the same input, if and only
if the next relations hold}:
    \begin{equation}\label{ena}
    {\cal R}(q){\cal D}(q)+{\cal K}(q){ \cal S}(q)={\cal D}^d(q),
    \end{equation}
    \begin{equation}\label{deytero}
    {\cal K}(q){ \cal T}(q)={\cal K}^d(q),
    \end{equation}
    \begin{equation}\label{trito}
    {\cal R}(q){\cal K}(q)={\cal K}(q){ \cal R}(q),
    \end{equation}
    \begin{equation}\label{tetarto}
    {\cal R}=I+\overline{{\cal R}}, \quad  \quad {\cal D}=I+\overline{{\cal D}}
    \end{equation}
    ($I$ {\it is the identity matrix}).

\so{Proof}. For the sake of presentation we drop the $q$ symbol.
Let us suppose now, that $\mathbf{z}(t)=\mathbf{z}^*(t)$,
$t=0,1,...,m-1$, where $m$ is the largest delay, appeared in the
equations of the system. In other words, we have identical initial
conditions. We shall prove that
$\mathbf{z}(m)=\mathbf{z}^*(m)$.%\\

For $t=m$ we have: ${\cal D}\mathbf{z}(m)={\cal K}\mathbf{u}(m)$
$\Rightarrow$ $(I+\overline{{\cal D}})\mathbf{z}(m)={\cal
K}\mathbf{u}(m)$ $\Rightarrow$ $\mathbf{z}(m)= {\cal
K}\mathbf{u}(m)-\overline{{\cal D}}\mathbf{z}(m)$. But ${\cal
R}\mathbf{u}(t)={\cal T}\mathbf{u}_c(t)-{\cal S}\mathbf{z}(t)$ and
${\cal R}=I+\overline{{\cal R}}$ $\Rightarrow$
$\mathbf{u}(t)={\cal T}\mathbf{u}_c(t)-{\cal
S}\mathbf{z}(t)-\overline{{\cal R}}\mathbf{u}(t)$. By setting
$t=m$ and substitution we get
\begin{equation}\label{basiko}
\mathbf{z}(m)={\cal K}{\cal T}\mathbf{u}_c(m)-{\cal K}{\cal
S}\mathbf{z}(m)-{\cal K}\overline{{\cal
R}}\mathbf{u}(m)-\overline{{\cal D}}\mathbf{z}(m).
\end{equation}
All the quantities at the right hand side of (\ref{basiko}) are
delays of the sequences and thus we can substitute the sequence
$\mathbf{z}(t)$ with $\mathbf{z}^*(t)$ , since
$\mathbf{z}(t)=\mathbf{z}^*(t)$, for $ t=0,1,2,...,m-1$. From
equations (\ref{trito}) and (\ref{tetarto}) we get
$(I+\overline{{\cal R}}){\cal K}={\cal K}(I+\overline{{\cal R}})$
which implies: $\overline{{\cal R}}{\cal K}={\cal
K}\overline{{\cal R}}$. From equations (\ref{ena}) and
(\ref{tetarto}) we get $(I+\overline{{\cal R}})(I+\overline{{\cal
D}})+{\cal K}{\cal S}={\cal D}^d$ or ${\cal K}{\cal S}={\cal
D}^d-I-\overline{{\cal R}}-\overline{{\cal D}}-\overline{{\cal
R}}\overline{{\cal D}}$. Substituting all the above into
(\ref{basiko}) we have\newpage
%
%\begin{multline*}
\begin{equation*}
\mathbf{z}(m)={\cal K}{\cal T}\mathbf{u}_c(m)-{\cal D}^d\mathbf{z}^*(m) +\mathbf{z}^*(m)+\overline{{\cal R}}\mathbf{z}^*(m)~+%\\
\end{equation*}\begin{equation*}
+~\overline{{\cal D}}\mathbf{z}^*(m)+\overline{{\cal
R}}\overline{{\cal D}}\mathbf{z}^*(m)-{\cal K}\overline{{\cal
R}}\mathbf{u}(m)-\overline{{\cal D}}\mathbf{z}^*(m).
%\end{multline*}
\end{equation*}

\noindent Using the facts that $  {\cal K}{ \cal T}={\cal K}^d$,
${\cal D}^d\mathbf{z}^*(m)={\cal K}^d\mathbf{u}_c(m)$,
$\overline{{\cal R}} {\cal D} \mathbf{z}^*(m)=$ $\overline{{\cal
R}}(I+ \overline{{\cal D}})\mathbf{z}^*(m)$ $= \overline{{\cal R}}
{\cal K}\mathbf{u}(m)$ $={\cal K}\overline{{\cal R}}\mathbf{u}(m)$
the latter becomes $\mathbf{z}(m)=\mathbf{z}^*(m)$ as requested.
By induction we get the final result
$\mathbf{z}(t)=\mathbf{z}^*(t)$, for any $t$, and the theorem has
been proved.
%\\

\textbf{Theorem 2.} {\it Let us suppose that the polynomial
matrices ${\cal R}_0$, ${\cal S}_0$, ${\cal T}$, solve the system
{\rm\eqref{ena}}--{\rm\eqref{trito}}, then the polynomial matrices
${\cal R}={\cal R}_0+{\cal Q}{\cal K}$, ${\cal S}={\cal S}_0-{\cal
Q}{\cal D}$, ${\cal T}$ are solutions too, for any arbitrary
polynomial matrix ${\cal Q}$ such that ${\cal Q}{\cal K}={\cal
K}{\cal Q}$}

\so{Proof}.  Substituting in (\ref{ena}), we get $({\cal
R}_0+{\cal Q}{\cal K}){\cal D}+{\cal K}({\cal S}_0-{\cal Q}{\cal
D})$ $={\cal R}_0{\cal D}+{\cal Q}{\cal K}{\cal D}~+$ ${\cal
K}{\cal S}_0-{\cal K}{\cal Q}{\cal D}$. Using the facts that
${\cal R}_0$ and ${\cal S}_0$ are solutions of the system and
that\linebreak ${\cal Q}{\cal K}={\cal K}{\cal Q}$, we conclude
that the above quantity is equal to ${\cal D}^d$. Furthermore, we
have $({\cal R}_0+{\cal Q}{\cal K}){\cal K}$ $={\cal K}({\cal
R}_0+{\cal Q}{\cal K})$ $\Leftrightarrow$ ${\cal R}_0{\cal
K}+{\cal Q}{\cal K}{\cal K}$ $={\cal K}{\cal R}_0+{\cal K}{\cal
Q}{\cal K}$. Using again the facts that  ${\cal Q}{\cal K}={\cal
K}{\cal Q}$ and ${\cal R}_0{\cal K}={\cal K}{\cal R}_0$ we
conclude  that the above relation is valid. From all the above we
get that the new matrices are solutions of the system.
%\\

\textbf{The algorithmic solution.} Now, in order to solve the
problem of designing appropriate polynomial matrices ${\cal R},
{\cal S}$  and ${\cal T}$  we developed two symbolic algorithmic
procedures, the ``Desired System'' algorithm and the ``Income and
Debt Matching'' algorithm. The ``Desired System'' algorithm is
used for the calculation of the polynomial matrices ${\cal D}^d$,
${\cal K}^d$, while the ``Income and Debt Matching'' algorithm
produces the polynomial matrices ${\cal R}, {\cal S}$  and ${\cal
T}$  of the requested feedback law.

\vskip 7 pt {\bf The ``Desired System'' algorithm}
\par \noindent
{\bf Input:} The degrees $n$ and $m$ of the output and input
polynomials.   The desired sequences: $y^*(t),\mathbf{u}^*(t)$,
$t=0,\ldots,k$.
\par \noindent
{\bf Output:} The numbers $a_i$, $i=0,\ldots,n$,~ $b_j$,
$j=0,\ldots,m$.
\\
\par
    \noindent

\begin{list}{}{\leftmargin=7mm} %\rightmargin=7mm \listparindent=5mm}

    {\bf Step 1.} We construct the system of algebraic equations for $t=0, 1, \ldots, k$:
    \[ a_0y^*(t)+a_1y^*(t-1)+\cdots+a_ny^*(t-n)=b_0 \mathbf{u}^*(t)+\cdots +b_m \mathbf{u}^*(t-m).\]

    \par
    \noindent
    {\bf Step 2.} We solve the above system with respect to the unknown coefficients $a_i$, $i=0,\ldots,n$, $b_j$, $j=0,\ldots,m$.
    \vskip 6 pt
    \noindent

\end{list}


\vskip 10 pt {\bf The ``Income and Debt Matching'' algorithm}
\par \noindent
{\bf Input:} The parameters $\nu,s,\tau,r$ and
$\lambda_0,\lambda_1,\lambda_2$. The initial conditions:
$Y(0),B(0),G(0),$ $E(0),Y(3),B(3),G(3),E(3)$. The input:
$\mathbf{u}_c(t)$. The reference sequences: $Y^*(t)$, $B^*(t)$.
\par
\noindent {\bf Output:} The polynomial matrices: ${\cal
R}({\thetabf}^*)$, ${\cal S}(\thetabf^*)$, ${\cal T}(\thetabf^*)$.
%
\\
    \par
    \noindent

\begin{list}{}{\leftmargin=7mm} %\rightmargin=7mm \listparindent=5mm}

    {\bf Step 1.} Form the polynomial matrices ${\cal D}$ and ${\cal
    K}$.\\
    \par

    \noindent
    {\bf Step 2.} Using the ``Desired System'' algorithm, construct a family of desired polynomial matrices ${\cal D}^d(\thetabf)$, ${\cal K}^d(\thetabf)$  such that the output of the system: ${\cal D}^d(\thetabf)\mathbf{z}^*(t)={\cal K}^d(\thetabf)\mathbf{u}_c(t)$  is exactly equal to the reference sequences. \underline{Note}: the vector of the parameters $\thetabf$ consists of the parameters $a_i$, $b_j$ used in the construction of the desired system.
    \\
    \par

    \noindent
    {\bf Step 3.} Construct the system of polynomial equations of Theorem 1. \ref{eks}
    \\
    \par

    \noindent
    {\bf Step 4.} Construct the coefficient matrix of the above system ${\cal A}$ and the corresponding augmented matrix ${\cal A^{\text{aug}}(\thetabf)}$.
    \\
    \par

    \noindent
    {\bf Step 5.} Find a parameter $\thetabf^*$ such that ${\rm rank}(\cal{A})$ $=$ ${\rm rank}(\cal{A^{\text{aug}}(\thetabf^*)})$ and
    $R_{\thetabf^*}=I+\overline{R}_{\thetabf^*}$.
    \\
    \par

    \noindent
    {\bf Step 6.} Solve the system of equations of Theorem 1, with respect to the quantities ${\cal R}(\thetabf^*)$, ${\cal S}(\thetabf^*)$,
    ${\cal T}(\thetabf^*)$, for this particular $\thetabf^*$
    value.%\\
%
%\par
%
%
\end{list}
%
\noindent It is a straightforward result of Theorem 2, that the
output of the ``Income and Debt Matching'' Algorithm, solves the
national income-debt tracking problem upon discussion.
\\

\textbf{An application of the algorithm.} In order to obtain a
better understanding of the effects of the proposed methodology on
the macroeconomic system under consideration, we run some
simulations for a model economy. In particular, let us suppose
that $s=0.2$, $\tau=0.4$, $\nu=1$, $r=5\%$, $\lambda_0=0.4$,
$\lambda_1=0.3$, $\lambda_2=0.3$, so that the open-loop system
becomes:
%\begin{multline*}
\begin{equation*}
Y(t) = 1.8Y(t-1)-1.12Y(t-2)-0.08Y(t-3)+0.4G(t)
~+%\\
\end{equation*}\begin{equation*}
+~0.3G(t-1) + 0.3G(t-2)-0.8E(t-1)-0.8E(t-2),   %\\
\end{equation*}\begin{equation*}
B(t) = 1.05B(t-1) - 0.4Y(t-1) + G(t) - E(t)
\end{equation*}%\end{multline*}
\noindent and the initial conditions are $Y(3)=100, B(3)=215$. For
the purposes of our simulations, we assume that the policymaker
aims for 1\% growth in the levels of $Y$ and 1\% decrease in the
levels of $B$, per period. Then, by applying the ``Desired
System'' algorithm and the ``Income and Debt Matching'' algorithm
we obtain a class of linear, causal feedback laws as a solution.
We present the time paths for the inputs, resulting from two of
the (infinitely many) feedback laws (see Table):


\vskip 2mm
\begin{center}
{\small {\bf Values of the control variables \\ under two feedback
laws}

}

\vskip 1mm

{\footnotesize

\begin{longtable}{|c|c|c|c|c|}
%    \caption{Values of the Control Variables under two Feedback Laws} \label{table}\\
%        \hline
%    $t$ & 4 & 5 & 6 & 7  \\
%    \hline
%    $G_1(t)$ &  31.54  & 30.54  & 32.92  & 33.19    \\
%    $E_1(t)$ &  4.44 & 2.91 & 4.76   & 4.49   \\
%    $G_2(t)$ &  35.5  & 40.3    & 49.5   & 50.4    \\
%    $E_2(t)$ &  8.45  & 12.68   & 21.3   & 58.7    \\
%    \hline
%
        \hline
   $t$ & $G_1(t)$ & $E_1(t)$  & $G_2(t)$ & $E_2(t)$  \\
    \hline
    4 &  31.54 & 4.44 & 35.5   & 8.45   \\
    5 &  30.54  & 2.91    & 40.3   & 12.68    \\
    6 &  32.92  & 4.76   & 49.5   & 21.3    \\
    7 &  33.19  & 4.49   & 50.4   & 58.7    \\
    \hline



\end{longtable}
}

\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



} \noindent The $G_1(t), E_1(t)$ values correspond to the
following feedback law:
%\begin{multline}
\begin{equation*}
G_1(t)=1.44G1(t-1) - 0.366G1(t-2) + 1.36Y(t-1) - 2.48Y(t-2)~- %\\
\end{equation*}\begin{equation*}
-~ 0.645Y(t-3) + 2.27B(t-1) - 1.66B(t-2) + 0.234B(t-3), %\\ %\\
\end{equation*}\begin{equation*}
E_1(t)=1.44E1(t-1) - 0.366E1(t-2) + 1.07Y(t-1) - 1.707Y(t-2)~- %\\
\end{equation*}\begin{equation}
-~1.113Y(t-3) + 4.049B(t-1) - 3.53B(t-2) + 0.35B(t-3),
%\end{multline}
\end{equation}

\noindent whereas the $G_2(t), E_2(t)$ values correspond to the
following feedback law:
%\begin{multline}
\begin{equation*}
G_2(t)=1.44G2(t-1) - 0.366G2(t-2) + 1.33Y(t-1) - 2.45Y(t-2)~- %\\
\end{equation*}\begin{equation*}
-~0.642Y(t-3) + 2.26B(t-1)- 1.63B(t-2) + 0.236B(t-3), %\\
\end{equation*}\begin{equation*}
E_2(t)=1.44E2(t-1) - 0.366E2(t-2) + 1.05Y(t-1) - 1.68Y(t-2)~- %\\
\end{equation*}\begin{equation}
-~1.11Y(t-3) + 4.046B(t-1)- 3.51B(t-2) + 0.354B(t-3).
\end{equation}
%\end{multline}

As we can see from the table, under feedback law (16) the values
of the inputs necessary for simultaneously reaching the reference
sequences are much higher compared to the values under feedback
law (15). This implies that, since the size of the policy
interventions under feedback law (15) are essentially politically
infeasible, the policymaker should choose the feedback law
provides a smoother transition path for the inputs.
%\\

\textbf{Concluding remark.} Our aim in this paper was to present
an application of the model matching approach for the design of
economic policy, i.~e. for the purpose of shaping the time path of
a macroeconomic model. From a control theory perspective, the
advantages of this approach are that it is based on algebraic
tools and that is provides a general class of feedback laws as a
solution. The algorithmic nature of the solution ensures that this
approach can readily be extended to macroeconomic models with more
delays than those considered in this paper.



%%\input{08/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{08/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize




%\thispagestyle{empty}

\vskip 3mm

%\thispagestyle{empty}


\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\it{Вестник~СПбГУ.~Сер.~10.~Прикладная~математика.~Информатика...~\issueyear.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\it{Вестник~СПбГУ.~Сер.~10.~Прикладная~математика.~Информатика...~\issueyear.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.

\vskip 1mm

\noindent Статья поступила в~редакцию 22 июля 2016~г.

\vskip 1mm

\noindent Статья принята к~печати 29 сентября  2016~г.

}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vskip 5mm


%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak

%\vskip 3mm

%\textit{Буре Артем Владимирович}~--- аспирант; e-mail:
%bure.artem@gmail.com

%\vskip 2mm

%\emph{Bure Artem Vladimirovich}~--- post-graduate student; e-mail:
%bure.artem@gmail.com

%}
