


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm

1.     Astrom K. J., Wittenmark B. \textit{Computer-Controlled
Systems: Theory and Design}. 3rd~ed., New York, Dover Publ., 2011,
576~p.

2.  Goodwin G., Sin K.S. \textit{Adaptive filtering prediction and
control}. New York, Dover Publ., 2009, 560~p.

3. Kucera V. Exact model matching, polynomial equation approach.
\textit{Intern. Journal of systems science}, 1981, vol.~12,
no.~12, pp.~1477--1484.

4.  Kucera V., Sebek M. Exact model matching of discrete linear
systems. \textit{Systems and Control Letters}, 1982, vol.~1,
no.~5, pp.~321--325.

5.  Kostarakos I., Kotsios S. Fiscal policy design in Greece in
the aftermath of the crisis: an algorithmic approach.
\emph{Computation Economics}, 2016 (unpublished).

6.  Kostarakos I., Kotsios S. Feedback policy rules for goverment
spending: an algorithmic approach. \emph{Of Economic structures},
2016 (unpublished).

7.  Kotsios S., Leventidis J. A feedback policy for a modified
Samuelson--Hicks model. \textit{Intern. Journal of systems
science}, 2004, vol.~35, no.~6, pp.~331--341.

8.  Prasolov A. V. \textit{Some quantitative methods and models in
economic theory}. New York, Nova Science Publ., 2016, 301~p.

9.   Samuelson P. Interactions between the multiplier analysis and
the principle of acceleration. \textit{Review of Economics and
Statistics}, 1939, vol.~21, no.~2, pp.~75--78.



\vskip 1mm

{\bf For citation:} Kotsios S., Kostarakos I. Controlling national
income and public debt via fiscal policy. A model matching
algorithmic approach. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
