
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Erickson G. M. {\it Dynamic models of advertising competition}.
2 ed. Norwell, Kluwer, Academic Publ., 2004, 122~p.

2. Sorger G. Competitive dynamic advertising: A modification of
the Case game. {\it Journal of Economic Dynamics and Control},
1989, vol.~13, no.~1, pp.~55--80.

3. Jorgensen S., Zaccour G. {\it Differential games in marketing}.
Boston, Kluwer, Academic Publ., 2004, 159~p.

4. Prasad A., Sethi S. P. Competitive advertising under
uncertainty: A stochastic differential game approach. {\it Journal
of Optimization Theory and Applications}, 2004, vol.~123, no.~1,
pp.~163--185.

5. Prasad A., Sethi S. P., Naik P. A. Optimal control of an
oligopoly model of advertising. {\it Proceedings of the 13th IFAC
Symposium on Information Control Problems in Manufacturing, INCOM
2009}. Moscow, 2009, vol.~42, no.~4, pp.~91--96.

6. Naik P. A., Prasad A., Sethi S. P. Building brand awareness in
dynamic oligopoly markets. {\it Management Science}, 2008,
vol.~54, no.~1, pp.~129--138.

%%\bibitem{ref13} Prasad A., Sethi S. P. Competitive advertising under uncertainty: A stochastic differential game approach. {\it Journal of Optimization Theory and Applications}, 2004, vol. 123, no. 1, pp. 163--185.

7. Yeung D. W. K., Petrosian O. L. Infinite horizon dynamic games: %
A new approach via information updating. {\it International Game %
Theory Review}, 2017, vol.~19, no.~4, pp.~1--26.

8. Gromova E. V., Petrosian O. L. Control of information horizon
for cooperative differential game of pollution control. {\it 2016
Intern. conference Stability and Oscillations of Nonlinear Control
Systems}, 2016, pp.~1--4.

9. Petrosian O. L., Gromova E. V. Cooperative differential games
with dynamic updating. {\it IFAC-PapersOnLine}, 2018, vol.~51,
no.~32, pp.~413--417.

10. Petrosian O. L. Looking Forward Approach in cooperative
differential games. {\it International Game Theory Review}, 2016,
vol.~18, no.~2, pp.~1--14.

11. Petrosian O. L., Nastych M. A., Volf D. A. Differential game
of oil market with moving informational horizon and
non-transferable utility. {\it 2017 Constructive Nonsmooth
Analysis and Related Topics}, 2017, pp.~1--4.

12. Petrosian O. L., Nastych M. A., Volf D. A. Non-cooperative
differential game model of oil market with Looking Forward
Approach. {\it Frontiers of Dynamic Games, Game Theory and
Management}, Saint Petersburg, 2017. Eds by L.~A.~Petrosyan,
V.~V.~Mazalov, N.~Zenkevich. Birkhauser, Basel, Springer Publ.,
2018, pp.~189--202.

13. Petrosian O. L., Barabanov A. Looking Forward Approach in
cooperative differential games with uncertain stochastic dynamics.
{\it Journal of Optimization Theory and Applications}, 2017,
vol.~172, no.~2, pp.~328--347.

14. Petrosian O. L. Looking Forward Approach in cooperative
differential games. Saint Petersburg, Saint Petersburg State
University Publ., 2017. Available at:
http://disser.spbu.ru/files/disser2/disser/ Wvm58zpgrB.pdf
(accessed: 02.04.2019).

15. Novikov D. A., Smirnov I. M., Shokhin T. E. {\it Control
mechanisms for dynamic active systems}. Moscow, IPU RAN Publ.,
2002, 124~p.

16. Goodwin G. C., Seron M. M., De Dona J. A. {\it Constrained
control and estimation} --- {\it an optimization perspective}.
London, Springer Publ., 2005, 411~p.

17. Kwon W. H., Han S. H. {\it Receding horizon control: Model
predictive control for state models}. New York, Springer Publ.,
2005, 380~p.

18. Wang C., Ong C. J., Sim M. Convergence properties of
constrained linear system under MPC control law using affine
disturbance feedback. {\it Automatica}, 2009, vol.~45, no.~1,
pp.~1715--1720.

19. Yeung D. W. K., Petrosyan L. A. {\it Subgame--consistent
economic optimization}. New York, Springer Publ., 2012, 395~p.

20. Bellman R. {\it Dynamic programming}. Princeton, Princeton
University Press, 1957, 365~p.

21. Chander P., Tulkens H. A core-theoretic solution for the
design of cooperative agreements on trans-frontier pollution. {\it
Public goods, environmental externalities and fiscal competition}.
New York, Springer Publ., 2006, pp.~176--193.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent
Received:  March 01, 2019.

Accepted: March 15, 2019.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm\textit{Lihong Shi} --- Master; shilihongru@gmail.com

\vskip1.5mm\textit{Ovanes L. Petrosian} --- assistant;
petrosian.ovanes@yandex.ru

\vskip1.5mm\textit{Alina V. Boiko} --- Master; alina.boyko@mail.ru

}
