
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

1. \textit{Camacho~E.~F., Bordons~C.} Model predictive control.
London: Springer-Verlag, 2007. 405~p.

2. \textit{Maciejowski~J.~M.} Predictive control with constraints.
London: Prentice Hall, 2002. 331~p.

3. \textit{Qin~S.~J., Badgwell~T.~A.} A survey of industrial model
predictive control technology~// Control Engineering Practice.
2003. Vol.~11(7). P.~733--764.

4. \textit{Richalet~J., Rault~A., Testud~J.~L., Papon~J.} Model
predictive heuristic control: applications to industrial processes
// Automatica. 1978. Vol.~14(5). P.~413--428.

5. \textit{Веремей~Е.~И., Сотникова~М.~В.} Стабилизация плазмы
на~базе прогноза с~устойчивым линейным приближением~// Вестн.
С.-Петерб. ун-та. Сер.~10. Прикладная математика. Информатика.
Процессы управления. 2011. Вып.~1. С.~116--133.

6. \textit{Sotnikova~M.} Ship dynamics control using predictive
models~// Proceedings of the 9th~IFAC conference on Manoeuvring
and Control of Marine Craft (MCMC 2012). Arenzano, Italy.
September 19--21, 2012. P.~250--255.

7. \textit{Сотникова~М.~В.} Вопросы устойчивости движений
в~системах управления с~прогнозирующими моделями~// Вестн.
Воронеж. гос. техн. ун-та. 2012. T.~8, №~1. С.~72--79.

8. \textit{Chen~W.-H., Ballance~D.~J., O’Reilly~J.} Model
predictive control of nonlinear systems: Computational burden and
stability~// IEE Proc.-Control Theory Appl. 2000. Vol.~147(4).
P.~387--394. %\pubdata

9. \textit{Баранов~О.~В., Попков~А.~С., Смирнов~Н.~В.} Оптимальная
стабилизация квадрокоптера в~режиме реального времени~//
Устойчивость и~процессы управления: материалы III Междунар.
конференции, посвященной памяти В.~И.~Зубова. СПб.: Издат. Дом
Г.~В.~Федоровой, 2015. С.~115--116.

10. \textit{Wang~Y., Boyd~S.} Fast model predictive control using
online optimization~// IEEE Trans. Control Sys. Tech. 2010.
Vol.~18(2). P.~267--278.

11. \textit{Scokaert~P.~O.~M., Mayne~D.~Q., Rawlings~J.~B.}
Suboptimal model predictive control (feasibility implies
stability)~// IEEE Trans. Autom. Control. 1999. Vol.~44(3).
P.~648--654.

12. \textit{Bemporad~A., Oliveri~A., Poggi~T., Storace~M.}
Ultra-fast stabilizing model predictive control via canonical
piecewise affine approximations~// IEEE Trans. Autom. Control.
2011. Vol.~56(12). P.~2883--2897.

13. \textit{Johansen~T.~A., Grancharova~A.} Approximate explicit
constrained linear model predictive control via orthogonal search
tree~// IEEE Trans. Autom. Control. 2003. Vol.~48(5). P.~810--815.

14. \textit{Johansen~T.~A.} Approximate explicit receding horizon
control of constrained nonlinear systems~// Automatica. 2004.
Vol.~40(2). P.~293--300.

15. \textit{Пономарев~А.~А.} Аппроксимация управления в~регуляторе
\MPC~// Устойчивость и~процессы управления: материалы III
Междунар. конференции, посвященной памяти В.~И.~Зубова. СПб.:
Издат. Дом Г.~В.~Федоровой, 2015. С.~329--330.

16. \textit{Пономарев~А.~А.} Построение субоптимального управления
в регуляторе \MPC~// Вестн. С.-Петерб. ун-та. Сер. 10. Прикладная
математика. Информатика. Процессы управления. 2014. Вып.~3.
С.~141--153.

17. \textit{Bellman~R.} The theory of dynamic programming~//
Bulletin of the American Mathematical Society. 1954. Vol.~60(6).
P.~503--516.

18. \textit{Cignoni~P., Montani~C., Scopigno~R.} A comparison of
mesh simplification algorithms~// Computers \& Graphics. 1998.
Vol.~22(1). P.~37--54.




\vskip 2mm

{\bf Для цитирования:} {\it Пономарев А.~А.} Аппроксимация
обратной связи в~регуляторе <<предиктор---корректор>> явной
функцией~// Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06



}
