

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1. Camacho~E.~F., Bordons~C. \textit{Model predictive control.}
London, Springer-Verlag Publ., 2007, 405~p.

2. Maciejowski~J.~M. \textit{Predictive control with constraints.}
London, Prentice Hall Publ., 2002, 331~p.

3. Qin~S.~J., Badgwell~T.~A. A survey of industrial model
predictive control technology. \textit{Control Engineering
Practice}, 2003, vol.~11(7), pp.~733--764.

4. Richalet~J., Rault~A., Testud~J.~L., Papon~J. Model predictive
heuristic control: applications to industrial processes.
\textit{Automatica}, 1978, vol.~14(5), pp.~413--428.

5. Veremey~E.~I., Sotnikova~M.~V. Stabilizatsiya plazmy na baze
prognoza s ustoichivym lineinym priblizheniem [Plasma
stabilization on the base of model predictive control with the
linear closed-loop system stability]. \textit{Vestnik of Saint
Petersburg State University. Series 10. Applied Mathematics.
Computer Sciences. Control Processes}, 2011, iss.~1, pp.~116--133.
(In Russian)

6. Sotnikova~M. Ship dynamics control using predictive models.
\textit{Proceedings of the 9th~IFAC conference on Manoeuvring and
Control of Marine Craft $($MCMC 2012$)$}. Arenzano, Italy,
September 19--21, 2012, pp.~250--255.

7. Sotnikova~M.~V. Voprosy ustoichivosti dvizhenii v sistemah
upravleniya s prognoziruiyshchimi modelyami [The problem of
stability in model predictive control]. \textit{Vestnik of
Voronezh State Technical University}, 2012, vol. 8(1), pp.~72--79.
(In Russian)

8. Chen~W.-H., Ballance~D.~J., O’Reilly~J. Model predictive
control of nonlinear systems: Computational burden and stability.
\textit{IEE Proc.-Control Theory Appl.}, 2000, vol.~147(4),
pp.~387--394.

9. Baranov~O.~V., Popkov~A.~S., Smirnov~N.~V. Optimal'naia
stabilizatsia kvadrokoptera v rezhime real'nogo vremeni [Real-time
quadrocopter optimal stabilization]. \textit{Intern. conference
``Stability and Control Processes'' in memory of V.~I.~Zubov
$($SCP$)$}. Saint Petersburg, Izdat. House of G.~V.~Fedorova
Publ., 2015, pp.~123--125. (In Russian)

10. Wang~Y., Boyd~S. Fast model predictive control using online
optimization. \textit{IEEE Trans. Control Sys. Tech.}, 2010,
vol.~18(2), pp.~267--278.

11. Scokaert~P.~O.~M., Mayne~D.~Q., Rawlings~J.~B. Suboptimal
model predictive control (feasibility implies stability).
\textit{IEEE Trans. Autom. Control}, 1999, vol.~44(3),
pp.~648--654.

12. Bemporad~A., Oliveri~A., Poggi~T., Storace~M. Ultra-fast
stabilizing model predictive control via canonical piecewise
affine approximations. \textit{IEEE Trans. Autom. Control}, 2011,
vol. 56(12), pp.~2883--2897.

13. Johansen~T.~A., Grancharova~A. Approximate explicit
constrained linear model predictive control via orthogonal search
tree. \textit{IEEE Trans. Autom. Control}, 2003, vol.~48(5),
pp.~810--815.

14. Johansen~T.~A. Approximate explicit receding horizon control
of constrained nonlinear systems. \textit{Automatica}, 2004,
vol.~40(2), pp.~293--300.

15. Ponomarev~A.~A. Approksimatsia upravlenia v reguliatore
``prediktor---korrektor'' [Feedback approximation in model
predictive control]. \textit{Intern. conference ``Stability and
Control Processes'' in memory of V.~I.~Zubov $($SCP}). Saint
Petersburg, Izdat. House of G.~V.~Fedorova Publ., 2015,
pp.~342--344. (In Russian)

16. Ponomarev~A.~A. Postroenie suboptimalnogo upravleniya v
regulyatore ``prediktor---korrektor'' [Suboptimal control
construction for the model predictive controller]. \textit{Vestnik
of Saint Petersburg State University. Series 10. Applied
Mathematics. Computer Sciences. Control Processes}, 2014, iss.~3,
pp.~141--153. (In Russian)

17. Bellman~R. The theory of dynamic programming. \textit{Bulletin
of the American Mathematical Society}, 1954, vol.~60(6),
pp.~503--516.

18. Cignoni~P., Montani~C., Scopigno~R. A comparison of mesh
simplification algorithms. \textit{Computers} \&
\textit{Graphics}, 1998, vol.~22(1), pp.~37--54.





\vskip 2mm

{\bf For citation:}  Ponomarev A.~A. Suboptimal control
construction for the model predictive controller. {\it Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06


}
