{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Bakhvalov~Y., Bocharov~V., Vinokurov~V., Nagorsky~V. {\it
Transport s magnitnym podvesom} [{\em Vehicles with magnetic
suspension}]. Moscow, Mashinostroenie Publ., 1991, 320~p. (In
Russian)

2. Dzenzersky~V., Omelyanenko~V., Vasiliev~S., Matin~V.,
Sergeev~S. {\it Vysokoskorostnoj magnitnyj transport s
jelektrodinamicheskoj levitaciej} [{\em High-speed levitating
transport with electrodynamic suspension}]. Kiev, Naukova dumka
Publ., 2001, 482~p. (In Russian)

3. Kim~K. {\it Sistemy jelektrodvizhenija s ispol'zovaniem
magnitnogo podvesa i sverhprovodimosti} [{\em Transportation
systems employing magnetic suspension and superconducting magnet
technology}]. Moscow, Educational and Methodological Centre for
Rail Transport Technology Publ.,  2007, 360~p. (In Russian)

4. Zaitzev~A., Talashkin~G., Sokolova~Yu. {\it Transport na
magnitnom podvese} [{\em Maglev transportation}]. Saint
Petersburg, Petersburg State Transport University Publ., 2010,
160~p. (In Russian)

5 Amoskov~V.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F.,
Filatov~O.~G., Gapionok~E.~I., Garkusha~D.~B., Kokotkov~V.~V.,
Kukhtin~V.~P., Lamzin~E.~A., Sychevsky~S.~E. Programmnyj kompleks
dlja chislennogo modelirovanija kvazistacionarnyh vihrevyh tokov v
tonkih provodjashhih prostranstvennyh obolochechnyh konstrukcijah
slozhnoj geometricheskoj formy [TYPHOON 2.0: computer code for 3D
simulation of electromagnetic transients using the thin shell
approach]. {\em Computer Program Register}, Registration
Certificate 2003612496 of Nov.~12, 2003. Moscow, Rospatent
 Publ., 2003. (In Russian)

6. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V.,
Belyakov~V.~A., Belyakova~T.~F., Firsov~A.~A., Gapionok~E.~I.,
Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S.,
Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N.,
Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Yu., Shatil~N.~A.,
Sychevsky~S.~E., Vasiliev~V.~N., Zaitzev~A.~A. Chislennoe
modelirovanie jelektrodinamicheskih podvesov levitacionnyh
transportnyh sistem. I. Vichislitel'naja tehnologija
modelirovanija jelektromagnitnyh protsessov v
jelektrodinamicheskih podvesah magnito-levitacionnyh transportnyh
sistem [Simulation of electrodynamic suspension systems for
levitating vehicles. I. Modelling of electromagnetic behaviour of
maglev vehicles with electrodynamic suspension]. {\em Vestnik of
Saint Petersburg University. Series~10. Applied mathematics.
Computer science. Control processes}, 2014, issue~4, pp.~5--15.
(In Russian)

7. Amoskov V.~M., Arslanova D.~N., Bazarov A.~M., Belov A.~V.,
Belyakov V.~A., Belyako-\linebreak va T.~F., Vasiliev V.~N.,
Gapionok E.~I., Zaitzev A.~A., Kaparkova M.~V., Kukhtin V.~P.,
Lam-\linebreak zin E.~A., Larionov M.~S., Maximenkova  N.~A.,
Mikhailov V.~M., Nezhentzev A.~N., Ovsyannikov D.~A., Ovsyannikov
A.~D., Rodin I.~Yu., Sychevsky S.~E., Firsov A.~A., Shatil N.~A.
Chislennoe modelirovanie jelektrodinamicheskih podvesov
levitacionnyh transportnyh sistem. II. Verifikacija
vychislitel'nyh modelej [Simulation of electrodynamic suspension
systems for levitating vehicles. I. Validation of computational
models]. {\em Vestnik of Saint Petersburg University. Series~10.
Applied mathematics. Computer science. Control processes}, 2015,
issue~2, pp.~18--32. (In Russian)

8. Amoskov V.~M., Arslanova D.~N., Bazarov A.~M., Belov A.~V.,
Belyakov V.~A., Belyako-\linebreak va T.~F., Gapionok E.~I.,
Zaitzev A.~A., Kaparkova M.~V., Kukhtin V.~P., Lamzin E.~A.,
Larionov~M.~S., Maximenkova N.~A., Mikhailov V.~M., Nezhentzev
A.~N., Ovsyannikov D.~A., Ovsyannikov A.~D., Rodin I.~Yu., Shatil
N.~A., Sychevsky S.~E., Firsov A.~A., Vasiliev V.~N. Chislennoe
modelirovanie jelektrodinamicheskih podvesov levitacionnyh
transportnyh sistem. III. JeDP s nepreryvnoj putevoj strukturoj
[Simulation of electrodynamic suspension systems for levitating
vehicles. III. Continuous track systems]. {\em Vestnik of Saint
Petersburg University. Series~10. Applied mathematics. Computer
science. Control processes}, 2015, issue~3, pp.~4--21. (In
Russian)

9. Amoskov V.~M., Arslanova D.~N., Bazarov A.~M., Baranov G.~A.,
Belov A.~V., Belyakov V.~A., Belyakova T.~F., Vasiliev V.~N.,
Gapionok E.~I., Zaitzev A.~A., Kaparkova M.~V., Kukhtin V.~P.,
Labusov A.~N., Lamzin E.~A., Larionov M.~S., Maximenkova N.~A.,
Mikhailov V.~M., Nezhentzev A.~N., Rodin I.~Yu., Sychevsky S.~E.,
Firsov A.~A., Khokhlov M.~V., Shatil N.~A. Adaptacija
vychislitel'noj tehnologii modelirovanija ustanovok termojadernogo
sinteza dlja analiza i optimizacii magnitnyh podvesov
levitacionnyh transportnyh sistem [Adaptation computation
technology of modeling of thermonuclear syntesis machines for
analysis and optimization of magnetic suspension of levitating
vehicle]. {\em VANT. Series ``Thermonuclear syntesis''}, 2014,
vol.~37, pp.~84--95. (In Russian)

10. Amoskov V.~M., Arslanova D.~N., Bazarov A.~M., Belov A.~V.,
Belyakov V.~A., Vasiliev V.~N.,  Gapionok E.~I., Zaitzev A.~A.,
Kukhtin V.~P., Lamzin E.~A., Larionov M.~S., Maximenkova N.~A.,
Sychevsky S.~E., Filatov O.~G., Firsov A.~A., Shatil N.~A.
Osobennosti chislennogo modelirovanija sistem
jelektrodinamicheskogo podvesa magnito-levitacionnogo transporta s
ispol'zovaniem mnogoprocessornyh JeVM [Simulation of EDS Maglev
transport systems with the use of multiprocessing]. {\em Proc. of
XV Intern. Conf. on Supercomputing and Matematical Modelling}.
Sarov, FGUP ``RFIYAC-VNIIEF'' Publ., 2015, pp.~33--41. (In
Russian)

11. Amoskov~V.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F.,
Gapionok E.~I., Glukhih~M.~I., Kukhtin V.~P., Lamzin E.~A.,
Maximenkova N.~A., Mingalev~B.~S., Sychevsky~S.~E., Filatov~O.~G.
Programmnyj kompleks dlja rascheta magnitnyh sistem, soderzhashhih
magnitotverdye, magnitomjagkie i tokonesushhie jelementy
konstrukcii slozhnoj geometricheskoj formy (KLONDIKE 1.0)
[KLONDIKE 1.0: computer code for 3D simulation of magnet systems
of complex geometry with retentive and non-retentive materials and
current carrying components]. {\em Computer Program Register},
Registration Certificate 2003612487 of Nov.~12, 2003. Moscow,
Rospatent, 2003. (In Russian)

12. Weh~H. {\em Elektrodynamisches Trag und Fuhrungs system.}
German patent 2412221, issued 14.03.74.

13. Danby G. T., Powell J. R. Design approaches and parameters for
magnetically levitated transport systems. {\em Superconductivity
and Its applications} / eds H.~S.~Kwok, D.~F.~Shaw. London,
Elsevier Publ., 1988, pp.~318--342.

14. Hoddeson~L., Kolb A.~W., Westfall~C. {\em Fermilab$:$ Physics,
The Frontier and Megascience.} Chicago, The University of Chicago
Press, 2008, 477~p.

\vskip 2mm

{\bf For citation:} Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M.,
Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N.,
Gapionok~E.~I., Zaitzev~A.~A., Zenkevich~M.~Yu., Kaparkova~M.~V.,
Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A.,
Mikhailov~V.~M., Nezhentzev~A.~N., Ovsyannikov~D.~A.,
Ovsyannikov~A.~D., Rodin~I.~Yu., Sychevsky~S.~E., Firsov~A.~A.,
Shatil~N.~A. Simulation of electrodynamic suspension systems for
levitating vehicles. IV. Discrete track systems. {\it Vestnik of
Saint Petersburg University. Series~10. Applied mathematics.
Computer science. Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
