
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm


1. \textit{Plank J.} A Tutorial on Reed---Solomon coding for
fault-tolerance in RAID-like systems // Software-Practice \&
Experience. 1997. Vol.~27(9). P.~995--1012.

2. \textit{Plank J., Xu L.} Optimizing cauchy Reed---Solomon codes
for fault-tolerant network storage applications //  The 5th IEEE
Intern. symposium on network computing and applications. 2006.
P.~173--180.

3. \textit{Plank J., Blaum M., Hafner J.} SD codes: erasure codes
designed for how storage systems really fail // FAST-2013: 11th
USENIX conference on file and storage technologies.  2013.
P.~95--104.

4. \textit{Papailiopoulos D., Luo J., Dimakis A., Huang C., Li J.}
Simple regenerating codes: network coding for cloud storage //
INFOCOM. Proceedings IEEE. 2012. P.~2801--2805.

5. \textit{Huang C., Simitci H., Xu Y., Ogus A., Calder B.,
Gopalan P., Li J., Yekhanin~S.} Erasure coding in windows azure
storage // USENIX annual technical conference. 2012. URL:
https://www.usenix.org/system/files/conference/atc12/atc12-final181\_0.pdf
(дата обращения: 11.07. 2016).

6. \textit{Huang C., Chen M., Li J.} Pyramid Codes: flexible
schemes to trade space for access efficiency in reliable data
storage systems // NCA--2007: IEEE Intern. symposium on network
computing and applications. 2007. P.~79--86.

7. \emph{Peterson W., Weldon E.} Error-correcting codes.
Cambridge: MIT Press, 1972. 572~p.

8. \emph{Berlekamp E.} Algebraic coding theory. Singapore: World
scientific Publishing Co, 2015. 501~p.


9. \emph{Lidl R., Niederreiter H.} Finite fields. Vol.~1. 2nd~ed.
Cambridge: Cambridge University Press, 1997. 755~p.


10. \textit{Plank J., Greenan K., Miller E.} Screaming fast galois
field arithmetic using Intel SIMD instructions // FAST--2013: 11th
USENIX conference on file and storage technologies. 2013.
P.~299--306.

11. \textit{Plank J.} XOR's lower bounds and MDS codes for storage
// IEEE Information theory workshop. 2011. P.~529--551.


12. \textit{Trifonov P.} Low-complexity implementation of RAID
based on Reed--Solomon codes //  ACM transactions on storage.
2015. URL: http://dl.acm.org/citation.cfm?id=2700308 (дата
обращения: 26.10.2016).

13. \emph{Knuth D.} The art of computer  programming. Vol.~1.
3rd~ed. Reading (Massachusetts): Addison-Wesley Press, 1997.
672~p.

14. \textit{Утешев А. Ю., Калинина Е. А.} Лекции по~высшей
алгебре. Ч.~II: учеб. пособие. СПб.: Соло, 2007. 279~c.

15. \textit{Хорн Р., Джонсон Ч.} Матричный анализ / пер. с~англ.
Х.~Д.~Икрамова и~др.; под ред. Х.~Д.~Икрамова. М: Мир, 1989.
655~с. (\emph{Horn R. A., Johnson Ch. R.} Matrix analysis.)

16. Intel Intelligent Storage Acceleration Library // URL:
https://01.org/intel\%C2\%AE-storage-acceleration-library-open-source-version
(дата обращения: 11.07.2016).

17. Jerasure: Erasure Coding Library // URL: http://jerasure.org/
(дата обращения: 11.07.2016).

\vskip 2mm

{\bf Для цитирования:} Маров А.~В.,~Утешев А.~Ю. Матричный
формализм кодов Рида---Соломо\-на~// Вестник Санкт-Петербургского
университета. Сер.~10. Прикладная математика. Информатика.
Процессы управления. \issueyear. Вып.~\issuenum.
С.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01




}
