{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Plank J. A Tutorial on Reed--Solomon coding for fault-tolerance
in RAID-like systems. \emph{Software--practice \& Experience},
1997, vol.~27(9), pp.~995--1012.

2. Plank J., Xu L. Optimizing cauchy Reed--Solomon codes for
fault-tolerant network storage applications. \emph{The 5th IEEE
Intern. symposium on network computing and applications}, 2006,
pp.~173--180.

3. Plank J., Blaum M., Hafner J. SD codes: erasure codes designed
for how storage systems really fail.  \emph{FAST-2013: 11th USENIX
Conference on File and Storage Technologies}, 2013, pp.~95--104.

4. Papailiopoulos D., Luo J., Dimakis A., Huang C., Li J. Simple
regenerating codes: network coding for cloud storage.
\emph{INFOCOM, Proceedings IEEE}, 2012, pp.~2801--2805.

5. Huang C., Simitci H., Xu Y., Ogus A., Calder B., Gopalan P., Li
J., Yekhanin~S. Erasure coding in windows azure storage.
\emph{USENIX annual technical conference}, 2012. URL:
https://www.usenix.org/system/files/conference/atc12/atc12-final181\_0.pdf
(accessed: 11.07.2016).

6. Huang C., Chen M., Li J. Pyramid codes: flexible schemes to
trade space for access efficiency in reliable data storage
systems. \emph{NCA--2007: IEEE Intern. symposium on network
computing and applications}, 2007, pp.~79--86.

7. Peterson W., Weldon E.  \emph{Error-Correcting Codes.}
Cambridge, MIT Press, 1972, 572~p.

8. Berlekamp E. \emph{Algebraic coding theory.} Singapore, World
scientific Publishing Co, 2015, 501~p.

9. Lidl R., Niederreiter H. \emph{Finite Fields.} Vol.~1. 2nd~ed.
Cambridge, Cambridge University Press, 1997, 755~p.

10. Plank J., Greenan K., Miller E. Screaming fast galois field
arithmetic using Intel SIMD instructions. \emph{FAST--2013: 11th
USENIX Conference on file and storage technologies}, 2013,
pp.~299--306.

11. Plank J. XOR's lower bounds and MDS codes for storage.
\emph{IEEE Information Theory Workshop}, 2011, pp.~529--551.


12. Trifonov P. Low-complexity implementation of RAID based on
Reed--Solomon codes.  \emph{ACM Transactions on Storage}, 2015.
URL: http://dl.acm.org/citation.cfm?id=2700308 (accessed:
26.10.2016).

13. Knuth D. \emph{The art of computer  programming.} Vol.~1. 3rd
ed. Reading (Massachusetts), Addison-Wesley Press, 1997, 672~p.


14. Uteshev A., Kalinina E. \emph{Lekcii po algebre}
[\emph{Lectures in algebra}]. Pt~II.  Saint Petersburg, Solo
Press, 2007,  279~p. (In Russian).

15. Horn R. A., Johnson C. R. \emph{Matrix analysis}. Cambridge,
Cambridge University Press, 1986, 612~p. (Russ ed.: Horn R. A.,
Johnson C. R. {\it Matricnij analiz}. Moscow, Mir Publ., 1989,
655~p.)

16. \emph{Intel intelligent storage acceleration library.} URL:
https://01.org/intel\%C2\%AE-storage-acceleration-library-open-source-version
(accessed: 11.07.2016).

17. \emph{Jerasure: Erasure coding library.} URL:
http://jerasure.org/ (accessed: 11.07.2016).

\vskip 2mm

{\bf For citation:} Marov A.~V., Uteshev A.~Yu. Matrix formalism
of the Reed---Solomon codes. {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathematics. Computer science.
Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
