
{\small

\vskip6mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. \textit{Sokolov S. V., Sokolova A. L.} HIV incidence in Russia: SIR epidemic model-based analysis // Вестник Санкт-Петербургского
университета. Прикладная математика. Информатика. Процессы управления. 2019. Т.~15. Вып.~4. С.~616--623. %\\
 https://doi.org/10.21638/11702/spbu10.2019.416
	
2. \textit{Smith D. L., Battle K. E., Hay S. I., Barker C. M., Scott T. W., McKenzie F. E.} Ross, Macdonald, and a theory for the dynamics and control of mosquito-transmitted pathogens // PLoS Pathog. 2012. Vol.~8. N~4. Art.~N~e1002588.

3. \textit{MacDonald G.} Epidemiological basis of malaria control // Bull. World Health Organ. 1956. Vol.~15. N~3--5. P.~613--626.

4. \textit{Захаров В. В., Балыкина Ю. Е.} Прогнозирование динамики эпидемии
коронавируса (COVID-19) на основе метода прецедентов // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~3. С.~249--259. \\ https://doi.org/10.21638/11701/spbu10.2020.303
		
5. \textit{Feng Z., Hernandez V.} Competitive exclusion in a vector-host model for the dengue fever // Math. Biol. 1997. P. 523--544.
	
6. \textit{Qiu Z.} Dynamical behavior of a vector-host epidemic model with demographic structure // Computers $\&$ Mathematics with Applications.  2008. Vol.~56. N~12. P.~3118--3129.
	
7. \textit{Sirbu A., Lorento V., Servedio V., Tria~F.} Opinion dynamics: models, extensions and external effects // Physics and Society. 2016. Vol.~5. P.~363--401.
	
8. \textit{Bushman M., Antia R., Udhayakumar~V., de~Roode~J.~C.} Within-host competition can de\-lay evolution of drug resistance in malaria // PLoS Biol. 2018. Vol.~16. N~8. Art.~N~e2005712. \\ \url{https://doi.org/10.1371/journal.pbio.2005712}
		
9. \textit{Turner A., Jung C., Tan P., Gotika~S.,  Mago~V.} A comprehensive model of spread of malaria in humans and mosquitos // SoutheastCon. 2015. P.~1--6. %\\
https://doi.org/10.1109/SECON.2015.7132968	
	
10. \textit{Hong H., Wang N., Yang J.} Implications of stochastic transmission rates for managing pandemic risks // Rev. Financ. Stud. 2021. Feb.~9. N~hhaa132. %\\
https://doi.org/10.1093/rfs/hhaa132
	
11. \textit{G\'omez-Hern\'andez E. A., Ibarg\"uen-Mondrag\'on E.} A two patch model for the popula\-tion dynamics of mosquito-borne diseases // J.~Phys.: Conference Series. 2019. Vol.~1408. N~1. Art.~N~012002.
	
12. \textit{Kamgang J. C., Thron C. P.} Analysis of malaria control measures’ effectiveness using multistage vector model // Bull. Math. Biol. 2019.  Vol.~81. P.~4366--4411.
	
13. \textit{Александров А. Ю.} Условия перманентности моделей динамики популяций с переключениями и запаздыванием // Вестник Санкт-Петербургского университета.
Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~2. С.~88--99. \\ https://doi.org/10.21638/11701/spbu10.2020.201
		
14. \textit{Chang S. L., Piraveenan M., Pattison P., Prokopenko M.} Game theoretic modelling of infectious disease dynamics and intervention methods: a review // Journal of Biological
Dynamics. 2020. Vol.~14~(1). P.~57--89.
	
15. \textit{Cai L., Tuncer N., Martcheva M.} How does within-host dynamics affect population-level dynamics? Insights from an immuno-epidemiological model of malaria // Mathematical Methods in the Applied Sciences. 2017. Vol.~40. N~18. P.~6424--6450.
   	
16. \textit{Maliki O., Romanus N.,  Onyemegbulem B.}  A mathematical modelling of the effect of treatment in the control of malaria in a population with infected immigrants // Applied Mathematics. 2018. Vol.~9. P.~1238--1257.
	
17.  \textit{Baygents G., Bani-Yaghoub M.} A mathematical model to analyze spread of hemorrha\-gic disease in white-tailed deer population // Journal of Applied Mathematics and Physics. 2017. Vol.~5. N~11. P.~2262--2282.

18.  \textit{Wiwanitkit V.} Unusual mode of transmission of dengue // Journal of Infect. Dev. Ctries. 2009. Vol.~4. P.~051--054.

19. \textit{Ндиайе С. М., Парилина Е. М.} Эпидемическая модель малярии без вакцинации и при ее наличии. Ч. 1. Модель малярии без вакцинации // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы уп\-рав\-ления. 2022. Т.~18. Вып.~2. С.~263--277.  \\ https://doi.org/10.21638/11701/spbu10.2022.207

20. \textit{Ndiaye S. M.} Mod\'elisation d\'un syst$\grave {\rm e}$me de p$\hat {\rm e}$cherie avec maladie // Bachelor Thesis. Supervis\'e par  M. Lam, F. Mansal. Dakar: Universit\'e Cheikh Anta Diop de Dakar, 2017. P.~3--10.

21.	\textit{Aldila D., Seno H. A.} Population dynamics model of mosquito-borne disease trans\-mis\-sion, focusing on mosquitoes’ biased distribution and mosquito repellent use // Bull. Math. Biol. 2019. Vol.~81. P.~4977--5008.

22. \textit{Lipsitch M., Cohen T., Cooper B., Robins J. M., Ma S., James L.,  Gopalakrishna G., Chew~S.~K., Tan C. C.,  Samore M. H., Fisman D., Murray M.} Transmission dynamics and control of se\-ve\-re acute respiratory syndrome // Science. 2003. Vol.~300. P.~1966--1970.

23.  \textit{Britton T.} Stochastic epidemic models: A survey // Mathematical Biosciences. 2010. Vol.~225. Iss.~1. P.~24--35.

24. \textit{Diekmann O., Heesterbeek A. P., Roberts M. G.} The construction of next-generation matrices for compartmental epidemic models // J.~R.~Soc. Interface.  2010. Vol.~7. P.~873--885.

25. \textit{Van den Driessche P.} Reproduction numbers of infectious disease models // Infect. Dis. Model.  2017. Vol.~2. P.~288--303.

26. \textit{Jones J. H.} Notes on R0 //  Department of Anthropological Sciences.  Stanford, CA, USA. 2007. Vol.~323. P.~1--19.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 15 августа 2022~г.

Cтатья принята к~печати 1 сентября 2022~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Ндиайе Серинь Моду} --- аспирант; mamounepourtoi@gmail.com


\vskip2mm \textit{Парилина Елена Михайловна} --- д-р физ.-мат. наук, проф.; e.parilina@spbu.ru


}
