
{\normalsize

\vskip 5%6
mm
%\newpage

\noindent{\bf An epidemic model of malaria without and with vaccination. Pt 2. A model\\ of malaria with vaccination %$^{*}$
 }

}

\vskip 2.5%3
mm

{\small

\noindent{\it S. M. Ndiaye, E. M. Parilina %
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2.5%3
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St~Petersburg State University, 7--9, Universitetskaya nab., St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2.5%3
mm


\noindent \textbf{For citation:}  Ndiaye S. M., Parilina E. M. An epidemic model of malaria without and with vaccination. Pt 2. A model of malaria with vaccination. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p10}--\pageref{p10e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum10 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent The article proposes a mathematical model of a malaria epidemic with vaccination in a population of people (hosts), where the disease is transmitted by a mosquito (carrier). The malaria transmission model is defined by a system of ordinary differential equations, which takes into account the level of vaccination in the population. The host population at any given time is divided into four subgroups: susceptible, vector-bitten, infected, and recovered. Sufficient conditions for the stability of a disease-free equilibrium and endemic equilibrium are obtained using the theory of Lyapunov functions. Numerical modeling repre\-sents the influence of parameters (including the vaccination level of the population) on the disease spread.
\\[1mm]
\textit{Keywords}: epidemic model, malaria, vaccination, SEIR model, endemic equilibrium.\par}

\vskip4.5%6
mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 1.5%2.0
mm

{\footnotesize

1. Sokolov S. V., Sokolova A. L. HIV incidence in Russia: SIR epidemic model-based
analysis. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~4, pp.~616--623. %\\
https://doi.org/10.21638/11702/spbu10.2019.416

2. Smith D. L, Battle K. E., Hay S. I., Barker C. M., Scott T. W., McKenzie F. E. Ross, Macdonald, and a theory for the dynamics and control of mosquito-transmitted pathogens. \textit{PLoS Pathog}.,  2012, vol.~8, no.~4, Art.~no.~e1002588. %\\
https://doi.org/10.1371/journal.ppat.1002588

3. MacDonald G. Epidemiological basis of malaria control. \textit{Bull. World Health Organ.}, 1956,  vol.~15, no.~3--5, pp.~613--626.

4. Zakharov V. V., Balykina Yu. E. Prognozirovanie dinamiki epidemii koronavirusa (COVID-19) na osnove metoda precedentov [Predicting the dynamics of the coronavirus
(COVID-19) epidemic based on the case-based reasoning approach]. \textit{Vestnik of Saint Peters\-burg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~3, pp.~249--259. \\ https://doi.org/10.21638/11701/spbu10.2020.303 (In Russian)

5. Feng Z., Hernandez V. Competitive exclusion in a vector-host model for the dengue fever. \textit{Math. Biol.}, 1997, pp.~523--544.

6. Qiu Z. Dynamical behavior of a vector-host epidemic model with demographic structure. \textit{Computers $\&$ Mathematics with Applications},  2008, vol.~56, no.~12, pp.~3118--3129.

7. Sirbu A., Lorento V., Servedio V., Tria F. Opinion dynamics: models, extensions and external effects. \textit{Physics and Society}, 2016, vol.~5, pp.~363--401.

8. Bushman M., Antia R., Udhayakumar V., de Roode J. C. Within-host competition can delay evolution of drug resistance in malaria. \textit{PLoS Biol}., 2018, vol.~16, no.~8, Art.~no.~e2005712. \\ https://doi.org/10.1371/journal.pbio.2005712

9. Turner A., Jung C., Tan P., Gotika S.,  Mago V. A comprehensive model of spread of malaria in humans and mosquitos. \textit{SoutheastCon}, 2015, pp.~1--6. https://doi.org/10.1109/SECON.2015.7132968

10. Hong H., Wang N., Yang J. Implications of stochastic transmission rates for managing pandemic risks. \textit{Rev. Financ. Stud.}, 2021, Feb.~9, no.~hhaa132. https://doi.org/10.1093/rfs/hhaa132

11. G\'omez-Hern\'andez E. A., Ibarg\"uen-Mondrag\'on E. A two patch model for the popula\-tion dynamics of mosquito-borne diseases. \textit{J. Phys.: Conference Series,} 2019, vol.~1408, no.~1, Art.~no.~012002.

12. Kamgang J. C., Thron C. P. Analysis of malaria control measures’ effectiveness using multistage vector model. \textit{Bull. Math. Biol.},  2019, vol.~81, pp.~4366--4411.

13. Aleksandrov A. Yu. Usloviya permanentnosti modelej dinamiki populyacij s pereklyu\-cheniyami i zapazdyvaniem [Permanence conditions for models of population dynamics
with switches and delay]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer
	Science. Control Processes}, 2020, vol.~16, iss.~2, pp.~88--99. %\\
https://doi.org/10.21638/11701/spbu10.2020.201  (In Russian)
	
14. Chang S. L., Piraveenan M., Pattison P., Prokopenko M. Game theoretic modelling of infectious disease dynamics and intervention methods: a~review. \textit{Journal of Biological Dynamics}, 2020, vol.~14~(1), pp.~57--89.
	
15. Cai L., Tuncer N., Martcheva M. How does within-host dynamics affect population-level dynamics? Insights from an immuno-epidemiological model of malaria. \textit{Mathematical Methods in the Applied Sciences}, 2017, vol.~40, no.~18, pp.~6424--6450.

16. Maliki O., Romanus N.,  Onyemegbulem B.  A mathematical modelling of the effect of treatment in the control of malaria in a population with infected immigrants. \textit{Applied Mathematics}, 2018, vol.~9, pp.~1238--1257.

17.  Baygents G., Bani-Yaghoub M. A mathematical model to analyze spread of hemor\-rhagic disease in white-tailed deer population. \textit{Journal of Applied Mathematics and Physics}, 2017, vol.~5, no.~11, pp.~2262--2282.

18.  Wiwanitkit V. Unusual mode of transmission of dengue. \textit{Journal of Infect. Dev. Ctries}, 2009, vol.~4, pp.~051--054.

19. Ndiaye S. M., Parilina E. M. Epidemicheskaja model' maljarii bez vakcinacii i pri ee nalichii. Ch. 1 Model' maliarii bez vaktsinatsii [An epidemic model of malaria without and with vaccination. Pt 1. A model of malaria without vaccination]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2022, vol.~18, iss.~2, pp.~263--277.\\ https://doi.org/10.21638/11701/spbu10.2022.207 (In Russian)

20. Ndiaye S. M. Mod\'elisation d\'un syst$\grave {\rm e}$me de p$\hat {\rm e}$cherie avec maladie [Modeling a fishery system with disease]. \textit{Bachelor Thesis}, supervis\'e par M.~Lam, F.~Mansal. Dakar, Universit\'e Cheikh Anta Diop de Dakar Press, 2017, pp.~3--10.

21.	Aldila D., Seno H. A. Population dynamics model of mosquito-borne disease trans\-mis\-sion, focusing on mosquitoes’ biased distribution and mosquito repellent use. \textit{Bull. Math. Biol.}, 2019, vol.~81, pp.~4977--5008.

22. Lipsitch M., Cohen T., Cooper B., Robins J. M., Ma S., James L.,  Gopalakrish\-na G., Chew~S.~K., Tan C. C.,  Samore M. H., Fisman D., Murray M. Transmission dynamics and control of se\-ve\-re acute respiratory syndrome. \textit{Science}, 2003, vol.~300, pp.~1966--1970.

23.  Britton T. Stochastic epidemic models: A survey. \textit{Mathematical Biosciences}, 2010, vol. 225, iss.~1, pp.~24--35.


24. Diekmann O., Heesterbeek A. P., Roberts M. G. The construction of next-generation matrices for compartmental epidemic models. \textit{J. R. Soc. Interface},  2010,  vol.~7, pp.~873--885.

25. Van den Driessche P. Reproduction numbers of infectious disease models. \textit{Infect. Dis. Model.},    2017, vol.~2, pp.~288--303.

26. Jones J. H. Notes on R0.  \textit{Department of Anthropological Sciences}. Stanford, CA, USA, 2007, vol.~323, pp.~1--19.


\vskip1.5mm Received:  August 15, 2022.

Accepted: September 01, 2022.

\vskip4.5%6
mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%

\vskip1.5%2
mm \textit{Serigne M. Ndiaye} --- Postgraduate Student; mamounepourtoi@gmail.com

\vskip1.5%2
mm \textit{Elena M. Parilina} --- Dr. Sci. in Physics and Mathematics, Professor;
 e.parilina@spbu.ru \par
%
%
}
