{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm


1.    Ivchenko~G.\:I., Kashtanov~V.\:A., Kovalenko~I.\:N. {\it
Teoriya massovogo obsluzhivaniya $[$Queuing theory$]$}. Moskow,
Vishaya shkola Publ., 1982, 256~p. (In Russian)

2. Gazis~D. {\it Traffic theory}. Kluwer, MA, Kluwer Academic
Publ., 2002, 259~p.


3.   Haddad~J., De~Schutter~B., Mahalel~V. et al.    Optimal
steady-state control for isolated traffic intersections.  {\it
IEEE Transactions on Automatic Control.}, 2010, vol.~55~(11),
pp.~2612--2617.

4.    Haddad~J., Mahalel~D., Ioslovich~I., Gutman~P.-O.
Constrained optimal steady-state control for isolated traffic
intersections. {\it  Control Theory Tech.}, 2014, vol.~12~(1),
pp.~84--94.

5.   Elfimov A.\:N.  O zadache upravleniya sistemoy massovogo
obsluzhivaniya s dvumya ocheredyami [Control problem of service
system with two queuing]. {\it  Control Processes and Stability},
2015, iss.~2, no.~1, pp.~605--611. (In Russian)

6.     Bure~V.\:M., Karelin~V.\:V., Elfimov~A.\:N.  O odnoy
zadache upravleniya determinirovannoy sistemoy upravleniya [On one
control problem of a deterministic service system]. {\it  Vestnik
of Saint Peterburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes,} 2015, iss.~4, pp.~100--112.
(In Russian)

7.   Karelin~V. V., Bure~V. M., Polyakova~L. N., Elfimov~A. N.
Control problem of a deterministic queueing system. {\it  Applied
Mathematical Sciences}, 2016, vol.~10~(21), pp.~1023--1030.

8.   Karelin~V., Bure~V., Elfimov~A. Deterministic queuing system.
{\it Proceedings VIII Moscow International Conference on
Operations Research}, 2016,  vol.~1, pp.~93--96.

9.   Elfimov A.\:N., Bure~V.\:M. O sychestvovanii stacionarnyh
ciclov v determinirovannoy sisteme obsluzhivaniya pri ogranichenii
na dliny cicla [On the existence of stationary cycles in a
deterministic service system with a constraint on the length of a
cycle]. {\it  Control Processes and Stability}, 2016, vol.~3,
no.~1, pp.~633--637. (In Russian)

10.    Polyakova~L.\:N., Karelin~V.\:V., Bure~V.\:M.,
Chitrov~G.\:M.  Tochnye shtrafnye funkcii v zadache upravleniya
odnoy sistemoy massovogo obsluzhivaniya  [Exact penalty functions
in the control problem of one queuing system]. {\it  Vestnik of
Saint Peterburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes}, 2015, iss.~1, pp.~73--81.
(In Russian)


11.   Yakushev V.~P., Karelin V.~V., Bure V.~M., Parilina E.~M.
 Soil acidity adaptive control problem.
{\it Stochastic Enviromental Research and Risk Assessment}, 2015,
vol.~29, no.~6,  pp.~1671--1677.

12.    Chernikov~S.\:N. {\it Lineynye neravenstva $[$Linear
inequalities$]$}. Moskow, Nauka Publ., 1968, 488~p. (In Russian)




\vskip 2mm

{\bf For citation:} Bure V. M., Elfimov  A. N., Karelin V. V.
Stationary cycles in a deterministic service system. {\it Vestnik
of Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
