

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Computers and Structures Inc. \textit{Integrated analysis, design and drafting of building systems}. Available at: https://www.csiamerica.com/ (accessed: May 13, 2022).

2. Autodesk Inc. \textit{Robot structural analysis}. Available at:\\ https://www.autodesk.com
/products/robot-structural-analysis/overview/ (accessed: May 13, 2022).

3. Bentley Systems Inc. \textit{STAAD 3D structural analysis and design software}. Available at:\\ https://www.bentley.com/en/products/brands/staad/ (accessed: April 02, 2022).

4. Ibraheem A. Elastic-plastic analysis of reinforced concrete frame buildings: Developing a new software package. \textit{Journal of Physics. Conference Series}, 2021, vol.~1959, iss.~1, no.~012023. Available at: http://www.scopus.com/inward/record.url?scp=85111954811\&partnerID=8YFLogxK (accessed:\,April\,02,\linebreak 2022).

5. Ibraheem A., Pronina Y. Accounting for shallow foundation settlement in the analysis and design of multi-storey frame buildings: Development of a new software package. \textit{Procedia Structural Integrity}, 2021, vol.~33, pp.~942--953. Available at:\\ http://www.scopus.com/inward/record.url?scp=85120681412\&partnerID=8YFLogxK (accessed:\,April\,02,\linebreak 2022).

6. Computers and Structures Inc. \textit{Concrete frame design manual ACI 318-14 for ETABS® 2016}. California, Walnut Creek, Computers and Structures Inc. Publ., 2016, 82~p.

7. American concrete institute committee 318. \textit{Building code requirements for structural concrete (ACI 318-14) and commentary (ACI 318R-14)}. Michigan, Farmington Hills, American Concrete Institute Publ., 2014, 524~p.

8. Furlong W., Hsu T., Mirza S. Analysis and design of concrete columns for biaxial bending --- Overview. \textit{ACI Structural Journal}, 2004, pp.~413--423.

9. Bresler B. Design criteria for reinforced columns under axial load and biaxial bending. \textit{ACI Journal}, 1960, vol.~57, pp.~481--490.

10. Monti G., Alessandri S. Assessment of RC columns under combined biaxial bending and axial load. \textit{International Concrete Federation Proceedings of the Second International Congress Naples}. Italy, 2006, vol.~2, pp.~1--12.

11. Abakarov~A., Pronina~Y., Kachanov~M. Symmetric arrangements of cracks with perturbed symmetry: extremal properties of perturbed configurations. \textit{International Journal of Engineering Science}, 2022, vol.~171(4), no.~103617. %\\
http://doi.org/10.1016/j.ijengsci.2021.103617

12. Abakarov~A. M., Pronina~Yu. G. On the effective elastic properties of a material with mutually perpendicular systems of parallel cracks. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2022, vol.~18, iss.~1, pp.~111--119.\\ https://doi.org/10.21638/11701/spbu10.2022.09

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  April 07, 2022.

Accepted: May 05, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Anas Akram Ibraheem}~--- Postgraduate Student; st072637@student.spbu.ru \par

\vskip 2mm \textit{Yulia G. Pronina }~---  Dr. Sci. in Physics and Mathematics, Professor; y.pronina@spbu.ru \par
%
}
