
{\footnotesize


\vskip4mm \noindent {\small \textbf{Литература} }

\vskip3mm


1. {\it Sankoff D., Kruskal J.} Time warps, string edits, and
macromolecules: the theory and practice of sequence comparison.
Ontario: Addison Wesley Publ. Company, 1983. 382 p.

2. {\it Berndt~D. J., Clifford~J.} Using dynamic time warping to
find patterns in time series // KDD workshop on knowledge
discovery in databases. 1994. P.~359--370.

3. {\it Oates~T., Firoiu~L., Cohen P. R.} Clustering time series
with hidden Markov models and dynamic time warping // Proc. of the
IJCAI-99 workshop on neural, symbolic and reinforcement learning
methods for sequence learning. 1999. P.~17--21.

4. {\it Maharaj E. A.} A significance test for classifying arma
models // Journal of Statistical Computation and Simulation. 1996.
Vol.~54, N~4. P.~305--331.

5. {\it Corduas M., Piccolo D.} Time series clustering and
classification by the autoregressive metric // Computational
Statistics \& Data Analysis. 2008. Vol.~52, N~4. P.~1860--1872.

6. {\it Fu T. C.} A Review on time series data mining //
Engineering Applications of Artificial Intelligence. 2011.
Vol.~24, N~1. P.~164--181.

7. {\it Montero P. M., Vilar J. A.} Time series clustering
utilities. Feb. 2015. URL: https://\linebreak
cran.r-project.org/web/packages/TSclust/TSclust.pdf (дата
обращения: 01.11.2016).

8. {\it Fan J., Zhang W.} Generalised likelihood ratio tests for
spectral density // Biometrika. 2004. Vol.~91, N~1. P.~195--209.

9. {\it Cilibrasi R., Vit{\`a}nyi P. M.} Clustering by compression
// IEEE Transactions on Information Theory. 2005. Vol.~51, N~4.
P.~1523--1545.

10. {\it Alcock R. J., Manolopoulos Y.} Time-series similarity
queries employing a feature-based approach // 7th Hellenic
Conference on Informatics. 1999. P.~27--29.

11. {\it Сивоголовко Е. В.} Методы оценки качества четкой
кластеризации // Компьютерные инструменты в образовании. 2011.
№\:4.  С.~14--31.

12. {\it Montero~P., Vilar~J.} TSclust: An R package for time
series clustering // Journal of Statistical Software. 2015.
N~62.1. P.~1--43.




\vskip 2mm

{\bf Для цитирования:} Староверова К.~Ю.,~Буре В.~М. Мера различия
временных рядов, основанная на их характеристиках
// Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p5}--\pageref{p5e}. \doivyp/
spbu10.\issueyear.\issuenum05



}
