{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm


1. Sankoff D., Kruskal J. {\it Time warps, string edits, and
macromolecules: the theory and practice of sequence comparison.}
Ontario, Addison Wesley Publ. Company, 1983, 382~p.

2. Berndt~D. J., Clifford~J. Using dynamic time warping to find
patterns in time series. {\it KDD workshop on knowledge discovery
in databases}, 1994, pp.~359--370.

3. Oates~T., Firoiu~L., Cohen P. R. Clustering time series with
hidden Markov models and dynamic time warping. {\it Processing of
the IJCAI-99 workshop on neural, symbolic and reinforcement
learning methods for sequence learning,} 1999, pp.~17--21.

4. Maharaj E. A. A significance test for classifying arma models.
{\it Journal of Statistical Computation and Simulation,} 1996,
vol.~54, no.~4, pp.~305--331.

5. Corduas M., Piccolo D. Time series clustering and
classification by the autoregressive metric. {\it Computational
Statistics $\&$ Data Analysis,} 2008, vol.~52, no.~4,
pp.~1860--1872.

6. Fu T. C. A Review on time series data mining. {\it Engineering
Applications of Artificial Intelligence,} 2011, vol.~24, no.~1,
pp.~164--181.

7. Montero P. M., Vilar J. A. Time series clustering utilities.
Feb. 2015. Available at: https://\linebreak
cran.r-project.org/web/packages/TSclust/TSclust.pdf (accessed
01.11.2016).

8. Fan J., Zhang W. Generalised likelihood ratio tests for
spectral density. {\it Biometrika,} 2004, vol.~91, no.~1,
pp.~195--209.

9. Cilibrasi R., Vit{\`a}nyi P. M. Clustering by compression. {\it
IEEE Transactions on Information Theory},  2005, vol.~51, no.~4,
pp.~1523--1545.

10. Alcock R. J., Manolopoulos Y. Time-series similarity queries
employing a feature-based approach. {\it 7th Hellenic Conference
on Informatics},  1999, pp.~27--29.

11. Sivogolovko E. V. Metodi ocenki kachestva chetkoi
klasterizacii [Methods of estimation of smooth clustering
quality]. {\it Komp'yuternye instrumenty v obrazovanii} [{\it
Computer tools in education}], 2011, issue~4, pp.~14--31. (In
Russian)

12. Montero~P., Vilar~J. TSclust: An R package for time series
clustering. {\it Journal of Statistical Software,} 2015, no. 62.1,
pp.~1--43.



\vskip 2mm

{\bf For citation:} Staroverova K.~Yu.,~Bure V.~M. Characteristics
based dissimilarity measure for time series. {\it Vestnik of Saint
Petersburg University. Applied mathematics. Computer science.
Control processes}, \issueyear, volume~13, issue~\issuenum,
pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
