
{\normalsize

\vskip 6mm

\noindent{\bf Stability analysis of mechanical systems with
distributed delay\\ via decomposition$^{*}$ }

}

\vskip 3mm

{\small

\noindent{\it A. Yu. Aleksandrov, A. A. Tikhonov %$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent\indent~$^{*}$ This work was  supported by the
Russian Foundation for Basic Research (grant N 19-01-00146-a).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Aleksandrov A. Yu., Tikhonov A. A.
Stability analysis of mechanical systems with distributed delay via decomposition. {\it Vest\-nik of Saint Petersburg
University. Applied Mathe\-ma\-tics. Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~17, iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The article analyzes a linear mechanical system with a large parameter at the vector of velocity forces and a distributed delay in positional forces. With the aid of the decomposition method, conditions are obtained under which the problem of stability analysis of the original system of the second-order differential equations can be reduced to studying the stability of two auxiliary first-order subsystems. It should be noted that one of the auxiliary subsystems does not contain a delay, whereas for the second subsystem containing a distributed delay, the stability conditions are formulated in terms of the feasibility of systems of linear matrix inequalities. To substantiate this decomposition, the Lyapunov direct method is used. Special constructions of Lyapunov---Krasovskii functionals are proposed. The developed approach is applied to the problem of monoaxial stabilization of a rigid body. The results of a numerical simulation are presented confirming the conclusions obtained analytically.
\\[1mm]
\textit{Keywords}: mechanical system, stability, distributed delay, decomposition, rigid body, Lyapunov---Krasovskii functionals.\par}

%\vskip6mm
\pagebreak

\noindent \textbf{References} }

\vskip 3mm

{\footnotesize

1. Matrosov V. M. {\it Metod vektornyh funkcij Ljapunova: analiz
dinamicheskih svojstv nelinejnyh sistem}
[{\it Vector Lyapunov function method: analysis of dynamical properties of nonlinear systems}].
Moscow, Fizmatlit Publ., 2001, 384~p.  (In Russian)


2. Chernous'ko F. L.,  Anan'evskii I. M.,  Reshmin S. A.
 {\it Metody upravlenija nelinejnymi mehanicheskimi sistemami}
[{\it Methods of control of nonlinear mechanical systems}]. Moscow,
Fizmatlit Publ., 2006, 328~p.  (In Russian)


3.  Siljak D. D.  {\it
Decentralized control of complex systems}.
New York,  Academic Press Publ.,  1991, 525~p.


4. Zubov V. I.  {\it Analiticheskaja dinamika giroskopicheskih sistem}
[{\it Analytical dynamics of gyroscopic systems}].
Leningrad, Sudostroenie Publ., 1970,  320~p. (In Russian)






5. Pyatnitskii E. S.
Princip dekompozicii v upravlenii mehanicheskimi sistemami  [The principle of decomposit ion in the control
of mechanical systems].
{\it Doklady Akademii Nauk SSSR} [{\it Proceedings of Academy Sciences USSR}], 1988, vol.~300, no.~2, pp.~300--303. (In Russian)



6. Aleksandrov A. Yu., Platonov A. V.
On stability and dissipativity of some classes of complex systems.
{\it Automation and Remote Control}, 2009, vol.~70, no.~8, pp. 1265--1280.




7.  Tkhai V. N. Model with coupled subsystems.
{\it Automation and Remote Control}, 2013, vol.~74, no.~6, pp.~919--931.







8. Podval'nyi S. L., Provotorov V. V.  Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe
[Start control of a parabolic system with distributed parameters on a graph]. {\it Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes},  2015, iss.~3, pp.~126--142. (In Russian)


9. Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A. Unique
weak solvability of a non-li\-near initial boundary value problem
with distributed parameters in a netlike domain. {\it Vestnik of
Saint Pe\-ters\-burg University. Applied Mathematics. Computer
Science. Control Processes},
 2017, vol.~13, iss.~3, pp.~264--277.
%DOI:  10.21638/11701/spbu10.2017.304



10. Klimina L. A. Method for forming autorotations in controllable
mechanical system with two degrees of freedom. {\it Journal of
Computer and Systems Sciences International},  2020,  vol.~59,
no.~6,  pp.~817--827.


11. Kuptsov S. Yu.  Ob odnom metode issledovanija na ustojchivost'
semejstv linejnyh sistem differencial'nyh uravnenij [On a method for stability investigation of linear differential systems families]. {\it Trudy Srednevolzhskogo matematicheskogo obshchestva} [{\it Proceedings of the Middle Volga Mathematical Society}],  2006,  vol.~8, no.~1, pp.~224--235. (In Russian)


12. {Kosov A. A.}
Issledovanie ustojchivosti singuljarnyh sistem metodom
vektor-funkcij Ljapunova [Stability investigation of singular systems
via vector Lyapunov functions method].
{\it Vestnik of Saint Petersburg University. Series 10.
Applied Mathematics. Computer Science. Control Processes},
 2005, iss.~4, pp.~123--129. (In Russian)


13. {Aleksandrov A. Yu., Chen Y., Kosov A. A., Zhang L.}
 Stability of hybrid mechanical
systems with switching linear force fields. {\it Non-linear Dynamics and Systems
Theory}, 2011, vol.~11, no.~1, pp.~53--64.

14. {Aleksandrov A. Yu., Kosov A. A., Chen Y.}
Stability and stabilization of mechanical
systems with switching. {\it Automation and Remote Control},
2011, vol.~72, no.~6, pp.~1143--1154.



15. {Aleksandrov A. Yu., Aleksandrova E. B., Zhabko A. P.}
 Asymptotic stability conditions
for certain classes of mechanical systems with time delay.
{\it WSEAS Transactions on Systems
and Control}, 2014, vol.~9, pp.~388--397.


16.  {Aleksandrov A. Y.,  Aleksandrova E. B.}
Asymptotic stability conditions for a class of
hybrid mechanical systems with switched non-linear positional forces.
{\it Non-linear Dynamics}, 2016, vol.~83, no.~4, pp.~2427--2434.



17. {Su Y. X., Zheng C. H.}  PID control for global finite-time regulation
of robotic manipulators. {\it Intertnational Journal of Systems Sciences},
2017, vol.~48, pp.~547--558.





18.
Anan'evskii I. M.,  Kolmanovskii V. B.
On stabilization of some control systems with an
after-effect. {\it  Automation and Remote Control}, 1989, no.~9,
pp.~1174--1181.





19. Zhang X., Chen X., Zhu G., Su C.-Y. Output feedback adaptive motion
control and its experimental verification for time-delay non-linear systems
with asymmetric hysteresis.
{\it IEEE Transactions on Industrial Electronics}, 2020, vol.~67, no.~8, pp.~6824--6834.


20.  Pavlikov S. V., Isavnin A. G.   O stabilizacii upravljaemoj mehanicheskoj sistemy s zapazdyvajushhej obratnoj svjaz'ju     [On stabilization of a controlled mechanical system with delayed feedback].
{\it Vestnik of Voronezh State University.  Series Physics. Mathematics},
   2014, no.~1, pp.~139--146. (In Russian)




21. Pavlikov S. V. O stabilizacii dvizhenij upravljaemyh
mehanicheskih sistem s zapazdyvajushhim reguljatorom  [On the
stabilization of movements of controlled mechanical systems with a
retarded % \linebreak
 controller]. {\it Doklady
Rossiiskoi Akademii Nauk} [{\it Proceedings of Academy Sciences of
Russia}],
 2007, vol.~412, no.~2, pp.~176--178.       (In Russian)











22. Fridman E. Tutorial on Lyapunov-based methods for time-delay systems.
{\it European Journal of Control},
2014, vol.~20, pp.~271--283.



23.  Hale J. K.,  Verduyn Lunel S. M. {\it Introduction to functional
differential   equations}. New York, Springer-Verlag Publ., 1993, 458~p.




24.  Zubov V. I. {\it Dinamika upravljaemyh sistem} [{\it Dynamics
of control systems}]. Saint Petersburg,  Saint Petersburg
University Press,
 2004,    380~p.    (In Russian)



25. Aleksandrov A., Mason O. Diagonal Riccati stability and applications.
{\it Linear
Algebra Appl.}, 2016, vol.~492, pp.~38--51.



26.   Samsonov V. A., Dosaev M. Z., Selyutskiy Y. D. Methods of qualitative
analysis in the problem of rigid body motion in medium. {\it International
Journal of Bifurcation and Chaos in Applied Sciences and Engineering},
2011, vol.~21, no.~10, pp.~2955--2961.


27.  Sedighi H. M., Daneshmand F.
    Non-linear transversely vibrating beams by the homotopy
perturbation method with an auxiliary term.  {\it
Journal of Applied and Computational Mechanics},  2015, vol.~1, no.~1, pp.~1--9.



28. Park Y., Lee C. Dynamic investigation of non-linear behavior of hydraulic
cylinder in mold oscillator
using PID control process.  {\it Journal of Applied and Computational
Mechanics}, 2021, vol.~7, no.~1, pp.~270--276.




29. Tikhonov A. A. Rezonansnye javlenija v kolebanijah
gravitacionno-orientirovannogo tverdogo tela. Ch. 4. Mnogochastotnye rezonansy
[Resonance phenomena in oscillations of a gravity-oriented
rigid body. Pt 4. Multifrequency resonances].
{\it Vestnik of Saint Petersburg University. Series 1. Mathematics. Mechanics.
Astronomy}, 2000, iss.~1, pp.~131--137.      (In Russian)

30. Kosjakov E. A., Tikhonov A. A. Differential equations for librational
motion of gravity-oriented rigid body.
{\it International Journal of Non-linear Mechanics}, 2015,
vol.~73, pp.~51--57.



\vskip1.5mm Received:  December 24, 2020.

Accepted: January 15, 2021.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Alexander Yu. Aleksandrov} --- Dr. Sci. in
Physics and Mathematics, Professor;\\  a.u.aleksandrov@spbu.ru

\vskip2mm \textit{Alexey A. Tikhonov} --- Dr. Sci. in Physics and
Mathematics,
Professor;  a.tikhonov@spbu.ru\par
%
%
}
