{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Alsevich V.~V. Mininizatsiya negladkih functsiy na mnozhestve
conechnih sosotoyaniy dinamicheskoy sistemy [Minimization of the
non-smooth functions on the terminal set of positions of a dynamic
system]. \textit{Differential Equations}, 1974, vol. 10, no. 2,
pp. 349--350. (In Russian)

2. Ananyina T.~F. Zadacha upravleniya po nepolnim dannym [The
problem of control with uncertain data]. \textit{Differential
Equations}, 1976, vol. 12, no. 4, pp. 612--620. (In Russian)

3. Bondarev B.~I., Durkin A.~P., Ovsyannikov A.~D. New
mathematical optimization models for RFQ structures.
\textit{Proceedings of the 18th Particle Accelerator Conference}.
New York, USA, 1999, pp.~2808--2810.

4. Demyanov V.~F., Vinogradova T.~K. On the minimax principle in
optimal control problems. \textit{Papers of Russian Academy of
Sciences}, 1973, vol. 213, no. 3, p. 512.

5. Kurzhanski A.~B. {\it Upravlenie i nabludenie v usloviyah
neopredelennosti $[$Control and observation in case of
uncertainty$]$.} Moscow, Fizmatlit Publ., 1977, 392, p. (In
Russian)

6. Ovsyannikov D.~A. Modeling and optimization problems of charged
particle beam dynamics. \textit{Proceedings of the 4th European
Control Conference.} Brussels, Belgium, 1997, pp. 1463--1467.

7. Ovsyannikov D.~A. {\it Modelirovanie i optimizatsiya dinamiki
puchkov zaryazhennih chastits $[$Modeling and optimization of
charged particle beam dynamics$]$.} Leningrad, Leningrad State
University Publ., 1990, 312~p. (In Russian)

8. Ovsyannikov D.~A. Mathematical modeling and optimization of
beam dynamics in accelerators. \textit{Proceedings of the 23rd
Russian Particle Accelerator Conference $($RuPAC 2012$)$}. Saint
Petersburg, Russia, 2012, pp.~68--72.

9. Ovsyannikov A.~D., Ovsyannikov D.~A., Altsybeev V.~V., Durkin
A.~P., Papkovich V.~G. Application of optimization techniques for
RFQ design. \textit{Problems of Atomic Science and Technology},
2014, vol. 3, pp.~116--119.

10. Mizintseva M., Ovsyannikov D. On the problem of simultaneous
optimization of program and disturbed motions. \textit{Proceedings
of SCP 2015 Conference.}  Saint Petersburg, Russia, 2015, pp.
195--196.

11. Mizintseva M., Ovsyannikov D. On the minimax problem of beam
dynamics optimization. \textit{Proceedings of the 27th Russian
Particle Accelerator Conference $($RuPAC 2016$)$.} Saint
Petersburg, Russia, 2016, pp. 360--362.

12. Kapchinsky I.~M. {\it Teoriya Lineynih resonansnih uskoriteley
$[$Theory of resonance linear accelerators$]$.} Moscow,
Energoizdat Publ., 1982, 398 p. (In Russian)

13. Ovsyannikov D.~A., Ovsyannikov A.~D., Vorogushin M.~F.,
Svistunov Yu.~A., Durkin A.~P. Beam dynamics optimization: models,
methods and applications. \textit{Nuclear Instruments and Methods
in Physics Research, Section A558}, 2006, pp. 11--18.

14. Ovsyannikov A.~D., Ovsyannikov D.~A., Balabanov M.~Yu., Chung
S.-L. On the beam dynamics optimization problem. \textit{Intern.
Journal of Modern Physics A}, 2009, vol. 24, no. 5, pp. 941--951.

15. Ovsyannikov A.~D. Upravlenie programmnim i vozmuschennimi
dvizheniyami [Control of program and disturbed motions]. \textit
{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Informatics. Control Processes}, 2006, iss. 2, pp.
111--124.





\vskip 2mm

{\bf For citation:}  Balabanov M.~Yu., Mizintseva M.~A.,
Ovsyannikov D.~A. Beam dynamics optimization in a linear
accelerator. {\it Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, \issueyear,
vol.~14, iss.~\issuenum, pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
