
{\normalsize

\vskip 6mm

\noindent{\bf Periodic modes in an automatic control system \\ with a three-position hysteresis relay%$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it V.~V.~Yevstafyeva, A.~M.~Kamachkin, D.~K.~Potapov %

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by Russian %
%Foundation for Basic Research (project N 20-07-00531 A).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^3$~%
St~Petersburg State University, 7--9, Universitetskaya nab.,
St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation




}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Yevstafyeva V.~V., Kamachkin A.~M., Potapov D.~K. Periodic modes in an automatic control system with a three-position hysteresis relay. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p13}--\pageref{p13e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum13 (In Russian)

\begin{hyphenrules}{english}

\vskip2mm

{\leftskip=7mm\noindent We consider an automatic control system with a three-position hysteresis relay and a continuous periodic external perturbation. The existence theorem is estab\-lished that provide domains in the space of system parameters, including the parameters of the relay
and perturbation, to which periodic modes having a pass to saturation zones with given periods and a specified configuration of phase
trajectories correspond.\\[1mm]
\textit{Keywords}: automatic control system, three-position hysteresis relay, periodic external perturbation,
periodic mode, phase trajectory. \par}

\vskip6mm%5

\end{hyphenrules}

%\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Tsypkin Ya.~Z. {\it Relejnye avtomaticheskie sistemy} [{\it Relay control systems}]. Moscow, Nauka Publ., 1974, 575~p. (In Russian)

2. El-Geldawi F. Stabilization of a relay system containing three-position
element and dead time. {\it Intern. Journal of Control}, 1970, vol.~11, no.~2, pp.~267--275.

3. El-Geldawi F. Exact analysis of a nonlinear time-delay control system
containing a three-position relay with hysteresis. {\it Journal of Engineering and Applied Sciences}, 1981, vol.~1, no.~4, pp.~327--337.

4. Morzhov A.~V., Faldin N.~V. Linearizatsiya po poleznomu signalu relejnykh sistem upravleniya s trekhpozitsionnym relejnym elementom
i nelinejnym ob''ektom upravleniya [Linearization of relay controlling systems with three-position relay block and nonlinear
controlled plant with respect to the actual signal]. {\it Izvestiya RAN. Teoriya i sistemy upravle\-niya}
[{\it Journal of Computer and Systems Sciences International}], 2008, no.~4, pp.~5--14. (In Russian)

5. Kamachkin A.~M., Shamberov V.~N. The decomposition method of research into
the nonlinear dynamical systems' space of parameters. {\it Applied Mathematical Sciences}, 2015, vol.~9, no.~81, pp.~4009--4018.

6. Macki J.~W., Nistri P., Zecca P. Mathematical models for hysteresis. {\it SIAM Review}, 1993, vol.~35, no.~1, pp.~94--123.

7. Mayergoyz I.~D. {\it Mathematical models of hysteresis and their applications}. Amsterdam, Elsevier Publ., 2003, 472~p.

8. Visintin A. Ten issues about hysteresis. {\it Acta Applicandae Mathematicae}, 2014, vol.~132, no.~1, pp.~635--647.

9. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Metod preobrazovaniya slozhnykh sistem avtomaticheskogo upravleniya k
integriruemoj forme [Method for the transformation of complex automatic control systems to integrable form].
{\it Vestnik of Saint Peter\-sburg University. Applied Mathematics. Computer Science. Control Processes},
2021, vol.~17, iss.~2, pp.~196--212. \\ https://doi.org/10.21638/11701/spbu10.2021.209 (In Russian)

10. Burns R.~S. {\it Advanced control engineering}. Oxford, Butterworth-Heinemann Publ., 2001, 464~p.

11. Paraskevopoulos P.~N. {\it Modern control engineering}. New York, Marcel Dekker Inc. Publ., 2002, 736~p.

12. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of periodic
solutions to automatic control system with relay nonlinearity and sinusoidal
external influence. {\it Intern. Journal of Robust and Nonlinear Control}, 2017, vol.~27, no.~2, pp.~204--211.

13. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of subharmonic
solutions to a hysteresis system with sinusoidal external influence.
{\it Electronic Journal of Differential Equations}, 2017, no.~140, pp.~1--10.

14. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. On uniqueness and
properties of periodic solution of second-order nonautonomous system with
discontinuous nonlinearity. {\it Journal of Dynamical and Control Systems}, 2017, vol.~23, no.~4, pp.~825--837.

15. Evstaf'eva V.~V. Periodicheskie resheniya sistemy differentsial'nykh uravnenij s gisterezisnoj nelinejnost'yu pri nalichii nulevogo
sobstvennogo chisla [Periodic solutions of a system of differential equations with hysteresis nonlinearity in the presence of eigenvalue zero].
{\it Ukrainskij matematicheskij zhurnal} [{\it Ukrainian Mathematical Journal}], 2018, vol.~70, no.~8, pp.~1085--1096. (In Russian)

16. Evstaf'eva V.~V. O sushchestvovanii dvukhtochechno-kolebatel'nykh reshenij vozmu\-shchennoj relejnoj sistemy s gisterezisom
[On the existence of two-point oscillatory solutions of a perturbed relay system with hysteresis].
{\it Differentsial'nye uravneniya} [{\it Differential Equa\-tions}], 2021, vol.~57, no.~2, pp.~169--178. (In Russian)

17. Evstaf'eva V.~V. Sushchestvovanie $T/k$-periodicheskikh reshenij nelinejnoj neavto\-nom\-noj sistemy s kratnym chislom matritsy
[Existence of $T/k$-periodic solutions of a nonlinear nonautonomous system whose matrix has a multiple eigenvalue].
{\it Matematicheskie zametki} [{\it Mathematical Notes}], 2021, vol.~109, no.~4, pp.~529--543. (In Russian)

18. Evstaf'eva V.~V. Sushchestvovanie dvukhtochechno-kolebatel'nykh reshenij relejnoj neavtonomnoj sistemy s kratnym
sobstvennym chislom veshestvennoj simmetricheskoj mat\-ri\-tsy
[Existence of two-point oscillatory solutions of a relay nonautonomous system with multiple eigenvalue of a real symmetric matrix].
{\it Ukrainskij matematicheskij zhurnal} [{\it Ukra\-inian Mathematical Journal}], 2021, vol.~73, no.~5, pp.~640--650. (In Ukrainian)

19. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Continuous dependence on parameters and boundedness of solutions to a hysteresis
system. {\it Applications of Mathematics}, 2022, vol.~67, no.~1, pp.~65--80.
\newpage

20. Leonov G.~A., Shumafov M.~M., Teshev V.~A., Aleksandrov K.~D. Differential equations with hysteresis operators. Existence of
solutions, stability, and oscillations. {\it Diffe\-rential Equations}, 2017, vol.~53, no.~13, pp.~1764--1816.

21. Solovyov A.~M., Semenov M.~E., Meleshenko P.~A., Reshetova O.~O., Popov M.~A., Kabulo\-va~E.~G. Hysteretic nonlinearity and unbounded
solutions in oscillating systems. {\it Procedia Engineering}, 2017, vol.~201, pp.~578--583.

22. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Dinamika i sinkhronizatsiya tsiklicheskikh struktur ostsillyatorov s
gisterezisnoj obratnoj svyaz'yu [Dynamics and syn\-chronization in feedback cyclic structures with hysteresis oscillators].
{\it Vestnik of Saint Peter\-sburg University. Applied Mathematics. Computer Science. Control Processes},
2020, vol.~16, iss.~2, pp.~186--199. \\ https://doi.org/10.21638/11701/spbu10.2020.210 (In Russian)

23. Fursov A.~S., Todorov T.~S., Krylov P.~A., Mitrev R.~P. O sushchestvovanii kolebatel'\-nykh rezhimov v odnoj nelinejnoj sisteme s
gisterezisami [On the existence of oscillatory modes in a nonlinear system with hysteresis].
{\it Differentsial'nye uravneniya} [{\it Differential Equa\-tions}], 2020, vol.~56, no.~8, pp.~1103--1121. (In Russian)

24. Fursov A.~S., Mitrev R.~P., Krylov P.~A., Todorov T.~S. O sushchestvovanii periodi\-ches\-kogo rezhima v odnoj nelinejnoj sisteme
[On the existence of a periodic mode in a nonlinear system].
{\it Differentsial'nye uravneniya} [{\it Differential Equa\-tions}], 2021, vol.~57, no.~8, pp.~1104--1115. (In Russian)

25. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Synchronization in feedback cyclic structures
of oscillators with hysteresis. {\it Stability and Control Processes: SCP~2020. Lecture Notes in Control and Information Sciences --- Proceedings}.
Cham, Springer Publ., 2022, pp.~119--125.

26. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Nepodvizhnye tochki otobrazhe\-niya, porozhdennogo sistemoj obyknovennykh
differentsial'nykh uravnenij s relejnym giste\-re\-zisom
[Fixed points of a mapping generated by a system of ordinary differential equations with relay hysteresis].
{\it Differentsial'nye uravneniya} [{\it Differential Equa\-tions}], 2022, vol.~58, no.~4, pp.~456--469. (In Russian)

27. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of periodic modes in automatic control system with a three-position relay.
{\it Intern. Journal of Control}, 2020, vol.~93, no.~4, pp.~763--770.

28. Kamachkin A.~M., Shamberov V.~N. Opredelenie bifurkatsionnoj struktury prostran\-stva pa\-ra\-metrov metodom dekompozitsii
[The research into the parameters' space bifurca\-tion structure by the method of decomposition].
{\it Sistemy upravleniya i informatsionnye tekhno\-lo\-gii} [{\it Control Systems and Information Technologies}],
2012, no.~4~(50), pp.~11--13. (In Russian)

29. Kamachkin A.~M., Sogonov S.~A., Shamberov V.~N. Vynuzhdennye periodicheskie resheniya ne\-linejnykh mnogosvyaznykh sistem
[Forced periodic solutions of nonlinear multi-coupling systems].
{\it Sistemy upravleniya i informatsionnye tekhnologii} [{\it Control Systems and Information Technologies}],
2014, no.~1~(55), pp.~12--15. (In Russian)

30. Kamachkin A.~M., Shamberov V.~N. Sushchestvovanie periodicheskikh dvizhenij v neav\-tonomnykh mnogomernykh nelinejnykh sistemakh
[Existence of periodic motions in non-autonomous multidimensional nonlinear systems].
{\it Sistemy upravleniya i informatsion\-nye tekhnologii} [{\it Control Systems and Information Technologies}],
2015, no.~1~(59), pp.~16--19. (In Russian)

\vskip1.5mm

Received:  June 23, 2022.

Accepted: September 01, 2022.


\vskip6mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Victoria V. Yevstafyeva} --- PhD in Physics and Mathematics, Associate Professor; \\ v.evstafieva@spbu.ru

\vskip2mm \textit{Alexander M. Kamachkin} --- Dr. Sci. in Physics and Mathematics, Professor; a.kamachkin@spbu.ru

\vskip2mm \textit{Dmitriy K. Potapov} --- PhD in Physics and Mathematics, Associate Professor; d.potapov@spbu.ru \par%
%
%
}
