
{\normalsize

\vskip 4.2mm%6mm

\noindent{\bf Thermal processes in natural gas pipeline transport%$\,^*$%
}

}

\vskip 1.5mm%2mm

{\small

\noindent{\it V. A. Suleymanov%$^{1,2}%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.5mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
Russian Research Institute for natural gases and gas technologies
``Gazprom'',

\noindent%
%\hskip2.45mm%
15-1, Proektiruemyj proezd N 5538, pos. Razvilka, s. p.
Razvilkovskoe, Leninsky dist.,

\noindent%
%\hskip2.45mm%
Moscow region, 142717, Russian Federation;

\noindent%
%$^2$~%
Gubkins' National University of oil and gas, 65, Leninsky pr.,
Moscow,

\noindent%
%\hskip2.45mm%
119991, Russian Federation

%\noindent%
%$^1$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,
%
%\noindent%
%%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:} Suleymanov  V. A.  Thermal
processes in natural gas pipeline transport. {\it Vestnik of
Saint~Pe\-ters\-burg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04  (In Russian)

\vskip2.0mm%3mm

{\leftskip=7mm\noindent A commonly used premise in pipeline
hydraulics where the work of friction forces performed at the
movement of real gas in the gas pipeline completely turns into
thermal energy is verified in the article. By means of the
integral definition of Clausius entropy, it is shown that the
premise of the conversion of friction forces into thermal energy
of gas flow is justified with an acceptable accuracy for
engineering applications in relation to the one-dimensional
formulation of the task regarding the determination of the
longitudinal temperature field of gas.\\[1mm]
\textit{Keywords}: gas transportation, gas pipeline,
one--dimensional model of flow, nonequilibrium thermodynamics,
entropy, thermal balance.
\par}

\vskip 5%6
mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Kanibolotskiy A. M., Bondarev E. A., Vasilev O. F., Voevodin A.
F. {\it Neizotermicheskoye techenie gaza w~trubah} [{\it
Non-isothermal gas flow in pipes}]. Novosibirsk, Nauka Publ.,
1978, 126~p. (In Russian)

2. Suleymanov V. A. Raschyot nestatsionarnyh rezhimov raboty
gazoprovodov [Calculation of non-stationary modes of gas pipelines
operation]. {\it Izvestya AN USSR. Energetika i~transport} [{\it
Energy and Transport}], 1987, no.~1, pp.~142--152. (In Russian)

3. Schlichting H. {\it Boundary layer theory}. New York,
McGraw-Hill Publ., 1968. 702~p. (Russ. ed.: Schlichting~H. {\it
Teoriya pogranichnogo sloya}. Moscow, Nauka Publ., 1974, 712~p.)

4. Chernyy G. G. {\it Gazovaya dinamika} [{\it Gas dynamics}].
Moscow, Nauka Publ., 1988, 424~p. (In Russian)

5. Kondepudi D., Prigogine I. {\it Modern thermodynamics: From
heat engines to dissipative structures}. New York, John Wiley and
Sons Publ., 1998, 552~p. (Russ. ed.: Prigogin~I., Kondepudi~D.
{\it Sovremennaya termodynamika: Ot teplovyh mashin do
dissipativnyh struktur}. Moscow, Mir Publ., 2002, 461~p.)

6. Vulis L. A. {\it Termodinamika gazovyh potokov} [{\it
Thermodynamics of gas flows}]. Moscow, Gosenergoizdat Publ., 1950,
304~p. (In Russian)

7. Charnyy I. A. {\it Osnovy gazovoi dinamiki} [{\it Fundamentals
of gas dynamics}]. Moscow, Gostoptehizdat Publ., 1961, 210~p. (In
Russian)

8. Strahovich K. I. {\it Gidro- i gazodinamika} [{\it Hydro and
gas dynamics}]. Moscow, Nauka Publ., 1980, 313~p. (In Russian)

9. Kochin N. E., Kibel I. A., Roze N. V. {\it Teoreticheskaya
gidrodinamika}. V 2~ch. [{\it Theoretical hydrodynamics}.
In~2~ch.]. Moscow, Fizmatgiz Publ., 1963, ch.~2, 728~p. (In
Russian)

10. Hodanovich I. E. {\it Analiticheskie osnovy proektirovaniya i
ekspluatatsii magistralnyh gazoprovodov} [{\it Analytical bases of
design and operation of main gas pipelines}]. Moscow,
Gostoptehizdat Publ., 1961, 128~p. (In Russian)


\vskip 1.5mm

Received:  July 29, 2020.

Accepted: August 13, 2020.
%
%
\vskip4.2mm A~u~t~h~o~r'~s \ i~n~f~o~r~m~a~t~i~o~n:
%
%
\vskip2mm \textit{Vladimir A. Suleymanov} --- PhD in Physics and
Mathematics, Associate Professor; %\\
sul1943@mail.ru\par
%
}
