

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 3%2
mm

{\footnotesize



1. Schumpeter J. \textit{Theorie der wirtschaftlichen
Entwicklung}. Leipzig, Duncker und Humblot Press, 1912, 395 p.
[Schumpeter J. \textit{The theory of economic development}.
Oxford, Oxford University Press, 1961, 255~p.]

2. Acemoglu D., Cao D. Innovation by entrants and incumbents.
\textit{Journal of Economic Theory}, 2015, vol.~157, pp.~255--294.

3. Christensen C., Raynor M. \textit{The innovator's solution}.
Boston, Harvard Business School Press, 2003, 265~p.

4. Klimek P., Hausmann R., Thurner S. Empirical confirmation of
creative destruction from world trade data. \textit{CID Working
Paper}, 2012, vol.~238, pp.~1--13.

5. Iwai K. Schumpeterian dynamics. Pt 1. An evolutionary model of
innovation and imitation. \textit{Journal of Economic Behavior and
Organization}, 1984, vol.~5, no.~2, pp.~159--190.

6. Iwai K. Schumpeterian dynamics. Pt 2. Technological progress,
firm growth and ``economic selection. \textit{Journal of Economic
Behavior and Organization}, 1984, vol.~5, no.~3--4, pp.~321--351.

7. Henkin G. M., Polterovich V. M. A difference-differential
analogue of the Burgers equation: stability of the two-wave
behavior. \textit{Journal of Nonlinear Science}, 1994, vol.~4,
pp.~497--517.

8. Polterovich V. M., Henkin G. M. Evolucionnaya model
vzaimodeystviya processov sozdaniya i zaimstvovamiya tehnologiy
[An evolutionary model with interaction of the processes of
development and adoption of technologies]. \textit{Economics and
Mathematical Methods}, 1988, vol.~24, pp.~1071--1083. (In~Russian)

9. Polterovich V. M., Henkin G. M. An evolutionary model of
economic growth. \textit{Matekon}, 1990, vol.~26, no.~3,
pp.~44--64.

10. Kirillov A. N., Sazonov A. M. Global schumpeterian dynamics
with structural variations. \textit{Bulletin of the South Ural
State University. Series Mathematical Modelling, Programming $\&$
Computer Software $($Bulletin SUSU MMCS$)$}, 2019, vol.~12, no.~3,
pp.~17--27.

11.  Kirillov A. N., Sazonov A. M. Globalnaya ustojchivost v
modeli nelinejnoj shumpeterovskoj dinamiki [Global stability in
model of non-linear Schumpeterian dynamics]. \textit{Transactions
of KarRC RAS}, 2018, vol.~7, pp.~34--40. (In~Russian)

12. Lefschetz S. \textit{Differential equations: geometric
theory}. Princeton, Princeton University Press, 1967, 390~p.

13. Nemytskii V. V., Stepanov V. V. \textit{The qualitative theory
of differential equations}. Princeton, Princeton University Press,
1960, 523~p.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 18, 2020.

Accepted: October 23, 2020.

\vskip 6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Alexander N. Kirillov} --- Dr. Sci. in Physics
and Mathematics, Associate Professor; \\
krllv1812@yandex.ru


\vskip 2mm \textit{Alexander M. Sazonov} --- Postgraduate Student;
sazon-tb@mail.ru


}
