

{\small


\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize


1. Poikonen S., Wang X., Golden B.  The vehicle routing problem with drones: Extended models and connections. \textit{Networks}, 2017, no.~70(1), pp.~34--43. https://doi.org/10.1002/net.21746

2. Theverge.com. \textit{Theverge Official Website, Drones could make Amazon’s dream of free delivery profitable} --- \textit{The Verge.} 2015. Available at: https://www.theverge.com/2015/6/3/8719659/amazon-prime-air-drone-delivery-profit-free-shipping-small-items (accessed: June 20, 2021). 

3. Radzki G., Thebbotuwawa A., Bocewick G.  Uavs flight routes optimization in changing weather conditions --- constraint programming approach. \textit{Applied Computer Science}, 2019, vol.~15, no.~3, pp.~5--20. \\ https://doi.org/10.23743/acs-2019-17

4. Kaggle.com. \textit{Kaggle Official Website, Hash Code Archive} --- \textit{Drone Delivery Homepage}, 2021. Available at: https://www.kaggle.com/c/hashcode-drone-delivery (accessed: June 20, 2021).

5. Euchi J. Genetic scatter search algorithm to solve the one-commodity pickup and delivery vehicle routing problem. \textit{J. of Modelling in Management}, 2017, vol.~12(1), pp.~2--18.\\ https://doi.org/10.1108/JM2-10-2015-0077

6. Euchi J., Sadok A. Hybrid genetic-sweep algorithm to solve the vehicle routing problem with drones. \textit{Physical Communication}, 2021, vol.~44.  https://doi.org/10.1016/j.phycom.2020.101236

7. Erdogan S., Miller-Hooks E. A Green Vehicle Routing Problem. \textit{Transportation Research. Pt E. Logistics and Transportation Review}, 2012, vol.~48(1), pp.~100--114. \\ https://doi.org/10.1016/j.tre.2011.08.001

8. Fleischmann B. \textit{The vehicle routing problem with multiple use of vehicles}. Technical report. Hamburg, Universitat Press, 1990.

9. Azi N., Gendreau M., Potvin J.-V.  An adaptive large neighborhood search for a vehicle routing problem with multiple routes. \textit{Computers and Operations Research}, 2014, vol.~41, pp.~167--173.  \\ https://doi.org/10.1016/j.cor.2013.08.016

10. Cattaruzza D., Absi N., Feillet D., Vidal T. A memetic algorithm for the multi trip vehicle routing problem. \textit{European Journal of Operational Research}, 2014, vol.~236(3), pp.~833--848. \\ https://doi.org/10.1016/j.ejor.2013.06.012

11. Cheikh M., Jarbou B. A variable neighborhood search algorithm for the vehicle routing problem with multiple trips. \textit{Electronic Notes in Discrete Mathematics}, 2015, vol.~47, pp.~277--284.\\ https://doi.org/10.1016/j.endm.2014.11.036

12. Ovsyannikov D. A., Mizintseva M. A., Balabanov M. Yu., Durkin A. P.,
Edamenko N. S., Koti\-na~E.~D. Optimization of dynamics of trajectory bundles using smooth and nonsmooth functionals. Pt~1. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~1, pp.~73--84. https://doi.org/10.21638/11701/spbu10.2020.107 (In Russian) 

13. Popkov A. S. Optimal program control in the class of quadratic splines for linear systems. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~4, pp.~462--470. https://doi.org/10.21638/11701/spbu10.2020.411

14. Drivotin O. I. On numerical solution of the optimal control problem based on a method using the second variation of a trajectory. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~2, pp.~283--295. \\ https://doi.org/10.21638/11701/spbu10.2019.211

15. Github.com. \textit{Github Official Website}. Implementation of the MDPGA. Available at: \\ https://github.com/LaLa-Lisa/Drones$\_ $delivery$\_ $compet (accessed: June 20, 2021).



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December 22, 2021.

Accepted: February 01, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
\textit{Anastasia Y. Markelova} --- Student; anastasiya\_markel@mail.ru \par

\vskip 2mm
\textit{Alexander L. Allahverdyan} --- Student;  aleka\_alexander@mail.ru \par

\vskip 2mm
\textit{Alexey A. Martemyanov} --- Student;  lyohich999@yandex.ru \par

\vskip 2mm
\textit{Inga S. Sokolova} --- Student; Sokolova.ing@gmail.com \par

\vskip 2mm
\textit{Ovanes L. Petrosian} --- PhD in Physics and Mathematics, Associate Professor;\\  petrosian.ovanes@yandex.ru \par%

\vskip 2mm
\textit{Mikhail V. Svirkin} --- PhD in Physics and Mathematics, Associate Professor;\\  msvirkin@spbu.ru \par%
%
}
