

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1. O’Kelly M. E. Activity levels at hub facilities in interacting
networks. {\it Geogr. Anal.}, 1986, vol.~18(4), pp.~343--356.

2. O’Kelly M. E. The location of interacting hub facilities. {\it
Transp. Sci.}, 1986, vol.~20, pp.~92--105.

3. Alumur S., Kara B. Y. Network hub location problems: the state
of the art. {\it European Journal of Oper. Research}, 2008,
vol.~190, pp.~1--21.

4. Campbell J. F., O’Kelly M. E. Twenty-five years of hub location
research. {\it Transp. Sci.}, 2012, vol.~46(2), pp.~153--169.

5. O’Kelly M. E., Miller H. J. Solution strategies for the single
facility minimax hub location problem. {\it Papers in Regional
Science}, 1991, vol.~70(4), pp.~367--380.

6. Klincewicz J. G. Heuristics for the $p$-hub location problem.
{\it European Journal of Oper. Research}, 1991, vol.~53,
pp.~25--37.

7. Skorin-Kapov D., Skorin-Kapov J., O’Kelly M. E. Tight linear
programming relaxations of uncapacitated $p$-hub median problems.
{\it European Journal of Oper. Research}, 1996, vol.~94,
pp.~582--593.

8. Kim H., O’Kelly M. E. Reliable $p$-hub location problems in
telecommunication networks. {\it Geogr. Anal.}, 2009, vol.~41(3),
pp.~283--306.

9. O’Kelly M. E. Network hub structure and resilience. {\it Netw.
Spat. Econ.}, 2015, vol.~15(2), pp.~235–251.

10. Ebery J., Krishnamoorthy M., Ernst A. T., Boland N. The
capacitated multiple allocation hub location problems:
formulations and algorithms. {\it European Journal of Oper.
Research}, 2000, vol.~120, pp.~614--631.

11. Lee H., Shi Y., Nazem S. M., Kang S. Y., Park T. H., Sohn M.
H. Multicriteria hub decision making for rural area
telecommunication networks. {\it European Journal of Oper.
Research}, 2001, vol.~133, pp.~483--495.

12. Campbell J. F. Integer programming formulations of discrete
hub location problems. {\it European Journal of Oper. Research},
1994, vol.~72, pp.~387--405.

13. Campbell J. F., Ernst A. T., Krishnamoorthy M. Hub location
problems. {\it Facility location: applications and theory}. Eds by
Z.~Drezner, H.~Hamacher. Berlin, Springer Press, 2002,
pp.~373--406.

14. Campbell J. F. Location and allocation for distribution
systems with transshipments and transportation economies of scale.
{\it Annals of Oper. Research}, 1992, vol.~40, pp.~77--99.

15. Fazlollahtabar H. Capacitated location-allocation hub covering
problem in manufacturing-customer interaction. {\it Journal of
Appl. Comput. Math.}, 2015, vol.~4, pp.~243--245. DOI:
10.4172/2168-9679.1000243

16. Lordan O., Sallan J. M., Simo P., Gonzalez-Prieto D.
Robustness of airline alliance route networks. {\it Communications
in Nonlinear Science and Numerical Simulation}, 2015, vol.~22,
no.~1, pp.~587--595.

17. Lozkins A., Bure V. M. The probabilistic method of finding the
local-optimum of clustering. {\it Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2016, iss.~1, pp.~28--37.

18. Lozkins A., Bure V. M. The method of clusters stability
assessing. {\it Stability and Control Processes in memory of V. I.
Zubov (SCP). 2015 Intern. Conference.} IEEE, 2015, pp.~479--482.



\vskip 2mm

{\bf For citation:} Lozkins  A., Bure V. M. Single hub
location-allocation  problem under robustness clustering concept.
{\it Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~13,
iss.~\issuenum, pp.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06


}
