
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm


{\footnotesize


1. \textit{Vasilev F. P.} On finite difference methods for the
solution of Stefan's single-phase problem~// U.S.S.R. Comput.
Math. Math. Phys. 1963. Vol.~3(5). P.~1175--1191.

2. \textit{ Kurbatova G. I.,  Ermolaeva N. N.} Analysis of the
cylinder glaciation models in seawater~// Applied Mathematics and
Information Sciences. 2017. Vol.~11(3).  P.~925--930.


3. \textit{Samarskii A. A., Moiseyenko B. D.} An economic
continuous calculation scheme for the stefan multidi\-mensional
problem~// U.S.S.R. Comput. Math. Math. Phys. 1965. Vol.~5(5).
P.~43--58.

4. \textit{Budak B. M.,  Sobol'eva E. N.,  Uspenskii A. B.}  A
difference method with coefficient smoothing for the solution of
Stefan problems~// U.S.S.R. Comput. Math. Math. Phys. 1965.
Vol.~5(5).  P.~59--76.

5. \textit{Eyres N. R.,  Hartree D. R.,   Ingham J.} et al.  The
calculation of variable heat flow in solids~// Philosophical
Transactions of the Royal Society. Series~A. 1946. Vol.~240.
P.~1--57.


6. \textit{Ермолаева Н. Н., Курбатова Г. И.} Нестационарная модель
нарастания морского льда~// Вестн. С.-Петерб. ун-та техно\-логии и
дизайна. Сер.~1. Естественные и технические науки. 2017. №~1.
С.~3--8.

7. \textit{Tichonov A. N., Samarskii A. A.} Equations of
mathematical physics. New York et al., USA: Pergamon Press Ltd.,
1963. 781~p.

8. \textit{Олейник О. А.} Об одном методе решения общей задачи
Стефана~// Докл. АН СССР.  1960. Т.~135, №~5. С.~1054--1057.


9. \textit{Будак Б. М., Васильев Ф. П., Успенский А. Б.}
Разностные методы  решения некото\-рых  краевых задач  типа
Стефана~// Численные методы в~газовой динамике. М.: ВЦ МГУ,
1965.\linebreak С.~139--183.

10. \textit{Krivovichev G. V., Ermolaeva N. N., Kurbatova G. I.,
Miheev S. A.} Mathematical modelling of the glaciation process~//
International Journal of Pure and Applied Mathematics. 2017.
Vol.~113(5). P.~609--616.

11. \textit{Shamsundar N., Sparrow E. M.} Analysis of
multidimensional conduction phase change via the enthalpy model~//
J. Heat Transfer. 1975. Vol.~97(3). P.~333--340.

12.  \textit{  Васильев В. И., Максимов А. М., Петров Е. Е.,
Цыпкин Г. Г.}  Тепломассо\-перенос в~промерзающих и протаивающих
грунтах. М.: Наука, Физмат\-лит, 1996.  224~с.




\vskip 1.5mm


%\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

\noindent Статья поступила в~редакцию 30 ноября 2017 г.; принята
к~печати 14 июня 2018~г.


\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Курбатова Галина Ибрагимовна}~--- д-р физ.-мат.
наук, проф.; g.kurbatova@spbu.ru





}
