
{\normalsize

\vskip 4.2mm%6mm

\noindent{\bf Determining the ability to work of the system,
the structure\\ of which is given using graph%$\,^*$%
}

}

\vskip 1.5mm%2mm

{\small

\noindent{\it A.~G.~Karpov, V.~A.~Klemeshev, D.~Yu.~Kuranov%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.5mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:}  Karpov~A.~G., Klemeshev~V.~A.,
Kuranov~D.~Yu. Determining the ability to work of the system, the
structure of which is given using graph. {\it Vestnik of
Saint~Pe\-ters\-burg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04  (In Russian)

\vskip2.0mm%3mm

{\leftskip=7mm\noindent A system of algorithms for the analysis of
systems of different nature, the structure of which is given using
graphs of great complexity, is proposed. The analysis consists in
checking the connectivity and physical realizability of the
system, the structure of which is given by the graph, as well as
in checking the absence of non-working loops. The proposed
algorithms can be used not only to develop new systems but also to
diagnose operating equipment and troubleshooting. The approach to
determining the physical realizability of a graph is that first a
system of basis cycles is constructed. After that it is determined
whether each branch is included in one of them. The operation of
the system of algorithms is demonstrated by the example of an
electrical system. However, the results obtained can be extended
to systems of a different nature, for example, using
electromechanical analogies.\\[1mm]
\textit{Keywords}: graph, graph connectivity, fundamental cycle.
\par}

\vskip 3.2mm%5mm

\noindent \textbf{References} }

\vskip 1.5%2mm

{\footnotesize

1. Nechepurenko~M.~I., Popkov~V.~K., Mainagashev~S.~M.
\textit{Algoritmy i programmy re\-she\-niya zadach na grafah i
setyah} [\textit{Algorithms and programs for solving problems on
graphs and networks}]. Novosibirsk, Nauka Publ., 1990, 520~p. (In
Russian)

2. %\textit{Седжвик~Р.} Фундаментальные алгоритмы на C++. Алгоритмы на графах/Пер. с англ. СПб., ООО <<ДиаСофтЮП>>, 2002. 496~с.
%\textit{Седжвик~Р.} Алгоритмы на C++ / пер. с англ. А.~А.~Моргунова; под ред. Ю.~Н.~Артеменко. М.: ООО ``И.Д.~Вильямс'', 2016, 1056~с.
Sedgewick~R. \textit{Algorithms in C++}. Boston, Addison-Wesley
Professional, 2009, 672~p. (Rus. ed.: Sedgewick~R.
\textit{Algoritmy na C++}. Moscow, Williams Publ., 2016, 1056~p.)


%3. \textit{Новиков~Ф.~А.} Дискретная математика для программистов. СПб.: Питер, 2004. 368~с.
3. Novikov~F.~A. \textit{Diskretnaya matematika dlya
programmistov} [\textit{Discrete mathematics for programmers}].
Saint Petersburg, Piter Publ., 2004, 368~p. (In Russian)

%4. \textit{Курапов~С.~В.}, \textit{Давидовский~М.~В.} Проверка планарности и построение топологического рисунка плоского графа (поиском в глубину) // Прикладная дискретная математика. 2016. № 2(32). С.~100--114.
4. Kurapov~S.~V., Davidovsky~M.~V. Proverka planarnosti i
postroenie topologicheskogo risunka ploskogo grafa (poiskom v
glubinu) [Planarity testing and constructing the topological
drawing of a plane graph (DFS)]. \textit{Prikladnaya Diskretnaya
Matematika} [\textit{Applied Discrete Mathematics}], 2016,
no.~2(32), pp.~100--114. https://doi.org/10.17223/20710410/32/7
(In Russian)

%5. Быкова~В.~В. \textit{О мерах целостности графов: обзор.} // Прикладная дискретная математика. 2014. N 4(26). pp.~96--111.
5. Bykova~V.~V. O merah tselostnosti grafov: obzor [Measures for
graph integrity: a comparative survey]. \textit{Prikladnaya
Diskretnaya Matematika} [\textit{Applied Discrete Mathematics}],
2014, no.~4(26), pp.~96--111. (In Russian)

%6. \textit{Львович~А.~Ю.} Электромеханические системы. Л.: Изд-во Ленингр. ун-та. 1989. 296~с.
6. L'vovich~A.~Yu. \textit{Elektromehanicheskie sistemy}
[\textit{Electromechanical systems}]. Leningrad, Leningrad State
University Publ., 1989, 296~p. (In Russian)

%7. \textit{Свами~М.}, \textit{Тхуласираман~К.} Графы, сети и алгоритмы /пер. с англ. М.~В.~Горбатовой и др.; под ред. В.~А.~Горбатова. М.: Мир, 1984 (2013). 455~с.
7. Swamy~M.~N.~S., Thulasiraman~K. \textit{Graphs, Networks, and
Algorithms}. New York, Wiley-Interscience Publ., 1981, 592~p.
(Rus. ed.: Swamy~M., Thulasiraman~K. \textit{Grafy, seti i
algoritmy}. Moscow, Mir Publ., 1984, 455~p.)


\vskip 1.5mm

Received:  November 01, 2019.

Accepted: February 13, 2020.
%
%
\vskip4.2mm A\,u\,t\,h\,o\,r\,s' \
i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
%
%
\vskip1.8mm \textit{Andrey G. Karpov} --- Dr. Sci. in Technics,
Professor; a.g.karpov@spbu.ru
%
\vskip1.8mm \textit{Vladimir A. Klemeshev} --- PhD in Physics and
Mathematics, Associate Professor; v.klemeshev@spbu.ru
%
\vskip1.8mm \textit{Dmitriy Yu. Kuranov} --- PhD in Physics and
Mathematics, Assistant; d.kuranov@spbu.ru\par
%
}
