

{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm


1. Управление проектами / под ред. И.~И.~Мазура, В.~Д.~Шапиро. М.:
Высшая школа, 2001. 875~с.

%\bibitem{Gray2003Project}
2.~\textit{Грей~К. Ф., Ларсон~Э.~У.} Управление проектами / пер.
с~англ. М.: Дело и~сервис, 2003. 528~с. (\textit{Gray~C.~G.,
Larson~E.~W.} Project Management.)

%\bibitem{Project2008Aguide}
3. Руководство к~своду знаний по~управлению проектами (Руководство
PMBOK). Newtown Square: Project Management Institute, 2008. 463~p.

%\bibitem{Kelley1961Critical}
4.~\textit{Kelley~J.~E.} Critical-path planning and scheduling:
mathematical basis~// Oper. Res. 1961. Vol.~9, N~3. P.~296--320.

%\bibitem{Malcolm1959Application}
5.~\textit{Malcolm~D.~G., Roseboom~J.~H., Clark~C.~E., Fazar~W.}
Application of a technique for research and development program
evaluation~// Oper. Res. 1959. Vol.~7, N~5. P.~646--669.

%\bibitem{Cuninghamegreen1976Projections}
6.~\textit{Cuninghame-Green~R.~A.} Projections in minimax algebra
// Math. Program. 1976. Vol.~10. P.~111--123.

%\bibitem{Zimmermann1981Linear}
7.~\textit{Zimmermann~U.} Linear and combinatorial optimization in
ordered algebraic structures. Vol.~10. Annals of Discrete
Mathematics. Amsterdam: Elsevier, 1981.  390~p.

%\bibitem{Butkovic2009Introduction}
8.~\textit{Butkovi\v{c}~P., Aminu~A.} Introduction to max-linear
programming~// IMA J. Manag. Math. 2009. Vol.~20, N~3.
P.~233--249.

%\bibitem{Kolokoltsov1997Idempotent}
9.~\textit{Маслов~В.~П., Колокольцов~В.~Н.} Идемпотентный анализ
и~его применение в~оптимальном управлении. М.: Физматлит, 1994.
144~с.

%\bibitem{Krivulin2009Methods}
10.~\textit{Кривулин~Н.~К.} Методы идемпотентной алгебры в~задачах
моделирования и~анализа сложных систем. СПб.: Изд-во С.-Петерб.
ун-та, 2009. 256~с.

%\bibitem{Butkovic2010Maxlinear}
11.~\textit{Butkovi\v{c}~P.} Max-linear Systems. Springer
Monographs in Mathematics. London: Springer, 2010. 272~p.

%\bibitem{Krivulin2013Explicit}
12.~\textit{Krivulin~N.} Explicit solution of a tropical
optimization problem with application to project scheduling~//
Mathematical Methods and Optimization Techniques in Engineering~/
eds: D.~Biolek, H.~Walter, I.~Utu, C.~von~Lucken. Athens: WSEAS
Press, 2013. P.~39--45.

%\bibitem{Krivulin2014Aconstrained}
13.~\textit{Krivulin~N.} A constrained tropical optimization
problem: complete solution and application example~// Tropical and
Idempotent Mathematics and Applications. Vol.~616 of Contemporary
Mathematics~/ eds: G.~L.~Litvinov, S.~N.~Sergeev. Providence: AMS,
2014. P.~163--177.

%\bibitem{Krivulin2015Amultidimensional}
14.~\textit{Krivulin~N.} A multidimensional tropical optimization
problem with nonlinear objective function and linear
constraints~// Optimization. 2015. Vol.~64, N~5. P.~1107--1129.

%\bibitem{Krivulin2015Extremal}
15.~\textit{Krivulin~N.} Extremal properties of tropical
eigenvalues and solutions to tropical optimization problems~//
Linear Algebra Appl. 2015. Vol.~468. P.~211--232.

%\bibitem{Krivulin2015Tropical}
16.~\textit{Krivulin~N.} Tropical optimization problems in project
scheduling~// Proc. 7th Multidisciplinary Intern. Conf. on
Scheduling: Theory and Applications / eds: Z.~Hanz\'{a}lek,
G.~Kendall, B.~McCollum, P.~\v{S}\r{u}cha. MISTA, 2015.
P.~492--506. URL: http://schedulingconference.org/
proceedings/2015/mista2015.pdf (дата обращения: 01.04.2016).

%\bibitem{Krivulin2015Tropicaloptimization}
17.~\textit{Krivulin~N.} Tropical optimization problems with
application to project scheduling with minimum makespan~// Ann.
Oper. Res. 2015. P.~1--18.

%\bibitem{Tkindt2006Multicriteria}
18.~\textit{T{\textquoteright}kindt~V., Billaut~J.~C.}
Multicriteria Scheduling. Berlin: Springer, 2006. 360~p.
%\end{thebibliography}
%\\


\vskip 2mm

{\bf Для цитирования:} Кривулин Н.~К.,~Губанов С.~А. Решение
задачи сетевого планирования на основе методов тропической
оптимизации // Вестник Санкт-Петербургского университета. Сер.~10.
Прикладная математика. Информатика. Процессы управления.
\issueyear. Вып.~\issuenum. С.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06





}
