


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1.~\textit{Upravlenie proektami} [\textit{Project management}].
Eds I.~I.~Mazur, V.~D.~Shapiro. Moscow, Vysshaya Shkola Publ.,
2001, 875~p. (In Russian)

2.~Gray~C. G., Larson~E.~W. \textit{Project Management}. New York,
McGraw-Hill Irwin, 2002, 574~p. (Russ. ed.: Gray~C.~G.,
Larson~E.~W. {\it Upravlenie proektami}. Moscow, Business and
Service Publ., 2003, 528~p.)

3.~\textit{A Guide to the Project Management Body of Knowledge
$($PMBOK Guide$)$}. Newtown Square, Project Management Institute,
2008, 459~p. (Russ. ed.: {\it Rukovodstvo k svodu znanii po
upravleniu proektami $($Rukovodstvo PMBOK$)$}. Newtown Square,
Project Management Institute, 2008, 463~p.)

4.~Kelley~J.~E. Critical-path planning and scheduling:
mathematical basis. \textit{Oper. Res.}, 1961, vol.~9, no.~3,
pp.~296--320.

5.~Malcolm~D.~G., Roseboom~J.~H., Clark~C.~E., Fazar~W.
Application of a technique for research and development program
evaluation. \textit{Oper. Res.}, 1959, vol.~7, no.~5,
pp.~646--669.

6.~Cuninghame-Green~R.~A. Projections in minimax algebra.
\textit{Math. Program.}, 1976, vol.~10, pp.~111--123.

7.~Zimmermann~U. {\it Linear and Combinatorial Optimization in
Ordered Algebraic Structures}. Vol.~10. Annals of Discrete
Mathematics. Amsterdam, Elsevier Press, 1981, 390~p.

8.~Butkovi\v{c}~P., Aminu~A. Introduction to max-linear
programming. \textit{IMA J. Manag. Math.}, 2009, vol.~20, no.~3,
pp.~233--249.

9.~Maslov~V.~P., Kolokol'tsov~V.~N. \textit{Idempotentnii analiz i
ego primenenie v optimal'nom upravlenii} [\textit{Idempotent
analysis and its applications in optimal control}]. Moscow,
Fizmatlit Publ., 1994, 144~p. (In Russian)

10.~Krivulin~N.~K. \textit{Metody idempotentnoi algebry v zadachah
modelirovania i analiza slozhnih sistem} [\textit{Methods of
idempotent algebra for problems in modeling and analysis of
complex systems}]. Saint Petersburg, Saint Petersburg University
Publ., 2009, 256~p.  (In Russian)

11.~Butkovi\v{c}~P. \textit{Max-linear Systems}. Springer
Monographs in Mathematics. London, Springer Press, 2010, 272~p.

12.~Krivulin~N. Explicit solution of a tropical optimization
problem with application to project scheduling.
\textit{Mathematical Methods and Optimization Techniques in
Engineering}. Eds D.~Biolek, H.~Walter, I.~Utu, C.~von~Lucken.
Athens, WSEAS Press, 2013, pp.~39--45.

13.~Krivulin~N. A constrained tropical optimization problem:
complete solution and application example. \textit{Tropical and
Idempotent Mathematics and Applications}. Vol.~616 of Contemporary
Mathematics. Eds G.~L.~Litvinov, S.~N.~Sergeev. Providence, AMS,
2014, pp.~163--177.

14.~Krivulin~N. A multidimensional tropical optimization problem
with nonlinear objective function and linear constraints.
\textit{Optimization}, 2015, vol.~64, no.~5, pp.~1107--1129.

15.~Krivulin~N. Extremal properties of tropical eigenvalues and
solutions to tropical optimization problems. \textit{Linear
Algebra Appl.}, 2015, vol.~468, pp.~211--232.

16.~Krivulin~N. Tropical optimization problems in project
scheduling. \textit{Proc. 7th~Multidisciplinary Intern. Conf. on
Scheduling: Theory and Applications}. Eds Z.~Hanz\'{a}lek,
G.~Kendall, B.~McCollum, P.~\v{S}\r{u}cha. MISTA, 2015,
pp.~492--506. (Available at:
http://schedulingconference.org/proceedings/2015/ mista2015.pdf;
accessed: 01.04.2016).

17.~Krivulin~N. Tropical optimization problems with application to
project scheduling with minimum makespan. \textit{Ann. Oper.
Res.}, 2015, pp.~1--18.

18.~T'kindt~V., Billaut~J.~C. \textit{Multicriteria Scheduling}.
Berlin, Springer Press, 2006, 360~p.


\vskip 2mm

{\bf For citation:} Krivulin N.~K.,~Gubanov S.~A. Solution of a
project scheduling problem by using methods of tropical
mathematics. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06


}
