
{\footnotesize


\vskip4mm \noindent {\small\textbf{Литература} }

\vskip3mm

1. \textit{Tikhonov V.~S., Safronov A.~I.} Analysis of
postbuckling drillstring vibrations in rotary drilling of
extended-reach wells // Transactions ASME. J. Energy Resources
Tech. 2011. Vol.~133, N~4. P.~43102.

2. \textit{Tikhonov V.~S., Safronov A.~I., Gelfgat M.~Ya.} Method
of dynamic analysis of rod-in-hole buckling // Proc. 8th Biennial
ASME Conference on Engineering Systems Design and Analysis.
Torino, Italy, 2006. P.~N~ESDA2006-95059.

3. \textit{Светлицкий В.~А.} Механика стержней: в~2~т. Т.~2.
Динамика. М.: Высшая школа, 1987. 304~с.

4. \textit{Malyugin~A.~A., Kazunin~D.~V., Kuznetsov~N.~V.}
Drillstring-hole calculation in drilling simulator // Mechanics
--- Seventh Polyakhov’s Reading. Intern. Conference. Saint
Petersburg, 2015. IEEE Xplore. DOI: 10.1109/POLYAKHOV.2015.7106755

5. \textit{Басарыгин Ю.~М., Булатов А.~И., Проселков Ю.~М}.
Технология бурения нефтяных и газовых скважин. М.: ООО
«Недра-Бизнесцентр», 2002. 632~с.

6. \textit{Юнин Е.~К.} Автоколебания в глубоком бурении. М.:
Книжный дом «Либроком», 2013. 264~с.

7. \textit{Сароян А.~Е.} Теория и практика работы бурильной
колонны. М.: Недра, 1990. 263~с.

8. \textit{Leine~R.~I., van Campen~D.~H., Keultjes W.~J.~G.}
Stick-Slip whirl interaction in drill-string dynamics // J. Vib.
Acoust. 2002. Vol.~124. P.~209--220.

9. \textit{Navarro-Lopez~E.~M., Suarez R.} Modelling and analysis
of stick-slip behavior in a drillstring under dry friction //
Congreso anual de la AMCA. 2004. P.~330--335.




\vskip 3mm

{\bf Для цитирования:}   Малюгин А.~А., Казунин Д.~В. Расчет
колебаний бурильной колонны в режиме реального времени в составе
тренажерных систем
// Вестник Санкт-Петербургского университета.
Прикладная математика. Информатика. Процессы управления.
\issueyear. Т.~13. Вып.~\issuenum. С.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10. \issueyear.\issuenum08



}
