


{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm

1. Tikhonov~V.~S., Safronov~A.~I. Analysis of postbuckling
drillstring vibrations in rotary drilling of extended-reach wells.
\textit{Transactions ASME. J. Energy Resources Tech}., 2011,
vol.~133, no.~4, pp.~43102.

2. Tikhonov~V.~S., Safronov~A.~I., Gelfgat~M.~Ya. Method of
dynamic analysis of rod-in-hole buckling.  \textit{Proceeding 8th
Biennial ASME Conference on Engineering Systems Design and
Analysis}. Torino, Italy, 2006, ESDA2006-95059.

3. Svetlitsky~V.~A. {\it Mekhanika sterghnei. V 2 t. T.~2.
Dinamika} [\textit{Rod Mechanics. In 2~vol. Vol.~2. Dynamics}].
Moscow, Visshaya shkola Publ., 1987, 304~p. (In Russian)

4. Malyugin~A.~A., Kazunin~D.~V., Kuznetsov~N.~V. Drillstring-hole
calculation in drilling simulator. \textit{Mechanics --- Seventh
Polyakhov’s Reading}. Intern. Conference. Saint Peters\-burg,
Russia, 2015, IEEE Xplore. DOI: 10.1109/POLYAKHOV.2015.7106755

5. Basarygin~Y.~M., Bulatov~A.~I., Proselkov~Y.~M. {\it Tehnologia
burenia neftianykh i gazovykh skvazhin} [\textit{Technology of
drilling oil and gas wells}]. Moscow, Nedra-Businesscenter Publ.,
2002, 632~p. (In Russian)

6. Yunin~E.~K. {\it Avtokolebania v glubokom burenii}
[\textit{Self-oscillations in deep drilling}]. Moscow, Librokom
Publ., 2013, 264~p. (In Russian)

7. Saroyan~A.~E. {\it Teoria i praktika raboty buril'noi kolonny}
[\textit{Theory and ptactice of drillstring work}]. Moscow, Nedra
Publ., 1990, 263~p. (In Russian)

8. Leine~R.~I., van~Campen~D.~H., Keultjes~W.~J.~G. Stick-Slip
whirl interaction in drill-string dynamics. \textit{J. Vib.
Acoust.}, 2002, vol.~124, pp.~209--220.

9. Navarro-Lopez~E.~M., Suarez~R. Modelling and analysis of
stick-slip behavior in a drillstring under dry friction.
\textit{Congreso anual de la AMCA}, 2004, pp.~330--335.




\vskip 3mm

{\bf For citation:}   Malyugin À.~À., Kazunin D.~V. Calculation of
drillstring vibrations in real time as part of training system.
{\it Vestnik of Saint Petersburg University. Applied mathematics.
Computer science. Control processes}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
