
{\small

\vskip4.5%6
mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. \textit{Baibich M. N., Broto J. M., Fert A., Nguyen Van Dau F., Petroff F., Etienne P., Creuzet G., Friederich A., Chazelas J.} Giant magnetoresistance of (001)Fe/(001)Cr magnetic superlattices // Physical Review Letters. 1988. Vol.~61. Iss.~21. P.~2472--2475.

2. \textit{Binasch G., Grunberg P., Saurenbach F., Zinn W.} Enhanced magnetoresistance in layered magnetic structures with antiferromagnetic interlayer exchange // Physical Review B. 1989. Vol.~39. Iss.~7. P.~4828--4830.

3. \textit{Куранов Д. Ю., Андреева Т. А., Бедрина М. Е.} Расчет потенциала ионизации фталоцианинатов цинка и графена на поверхности диэлектриков // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2022. Т.~18. Вып.~1. С.~52--62. https://doi.org/10.21638/11701/spbu10.2022.104

4. \textit{Ustinov V. V.} Spin-flop transition scenario in finite layered antiferromagnets // Journal of Magnetism and Magnetic Materials. 2007. Vol.~310. Iss.~2. P.~2219--2221.

5. \textit{Lauter-Pasyuk V., Lauter H., Toperverg B., Romashev L., Ustinov V.} Transverse and lateral structure of the spin-flop phase in Fe/Cr antiferromagnetic superlattices // Physical Review Letters. 2002. Vol.~89. Iss.~16. P.~167203.

6. \textit{Бабиков В. В.} Метод фазовых функций в квантовой механике. М.: Наука, 1976. 288~c.

7. \textit{Lekner J.} Theory of reflection of electromagnetic and particle waves. Dordrecht: Springer Science+Business Media, 1987. 281~p.

8. \textit{Zimmerman K. M.} Advanced analysis techniques for $X$-ray reflectivities: theory and application: doctoral dissertation in chemistry. Karlsruhe: University of Dortmund, 2005. 190~p.

9. \textit{De Haan V. O., van Well A. A., Sacks P. E., Adenwalla S., Felcher G. P.} Toward the solution of the inverse problem in neutron reflectometry // Physica B: Physics of Condensed Matter.  1996. Vol.~221. Iss.~1--4. P.~524--532.

10. \textit{Lynn J. E., Seeger P. A.} Resonance effects in neutron scattering lengths of rare-earth nuclides // Atomic Data and Nuclear Data Tables. 1990. Vol.~44. Iss.~2. P.~191--207.

11. \textit{Nikova E. S., Salamatov Yu. A., Kravtsov E. A., Bodnarchuk V. I., Ustinov V. V.} Experimental determination of gadolinium scattering characteristics in neutron reflectometry with reference layer // Physica B: Physics of Condensed Matter. 2019. Vol.~552. P.~58--61.

12. \textit{Aksenov V. L., Lauter-Pasyuk V. V., Lauter H., Nikitenko Yu. V., Petrenko A. V.} Polarized neutrons at pulsed sources in Dubna // Physica B: Physics of Condensed Matter.  1996. Vol.~335. Iss.~1--4. P.~147-152.

13. \textit{Nikova E. S., Salamatov Yu. A., Kravtsov E. A., Ustinov V. V.} Application of a Gd reference layer for the study of magnetic metallic nanostructures by neutron reflectometry // Journal of Surface Investigation. $X$-ray, Synchrotron and Neutron Techniques. 2021. Vol.~15. N~5. P.~899--902.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 27 июля 2022~г.

Cтатья принята к~печати 1 сентября 2022~г.

\vskip4.5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Саламатов Юрий Александрович} --- канд. физ.-мат. наук; salamatov@imp.uran.ru

\vskip2mm \textit{Никова Екатерина Сергеевна} --- nikova@imp.uran.ru

\vskip2mm \textit{Девятериков Денис Игоревич} --- devidor@imp.uran.ru

\vskip2mm \textit{Кравцов Евгений Алексеевич} --- д-р физ.-мат. наук; kravtsov@imp.uran.ru



}
