
{\small

\vskip6mm
%\newpage
 \noindent \textbf{Литература}

}

\vskip3
mm

{\footnotesize

1. \textit{Тимошенко С.\,П., Войновский-Кригер С.} Пластинки и оболочки /
пер. с англ. Г.\,С.~Шапиро; под ред. И.\,К.~Снитко.
М.: Наука, 1966. 636~с.
(\textit{Timoshenko~S.\,P., Woinowsky-Krieger~S.}
Theory of plates and shells. 2$^\text{nd}$~ed.)

2. \textit{Meleshko V.\,V.}
Selected topics in the history of the two-dimensional biharmonic problem~//
Appl. Mech. Rev. 2003. Vol.~56. N~1. P.~33--85.

3. \textit{Meleshko V.\,V.}
Bending of an elastic rectangular clamped plate: exact versus 'engineering' solutions~//
Journal of Elasticity. 1997. Vol.~48. N~1. P.~1--50.

4. \textit{Ceribasi S., Altay G., Cengiz Dokmeci M.}
Static analysis of superelliptical clamped plates by Galerkin's method~//
Thin-Walled Structures. 2008. Vol.~46. N~2. P.~122--127.

5. \textit{Khan Y., Tiwari P., Ali R.}
Application of variational methods to a rectangular clamped plate problem~//
Computers and Mathematics with Applications. 2012. Vol.~63. N~4. P.~862--869.

6. \textit{Altunsaray E., Bayer I.}
Deflection and free vibration of symmetrically laminated quasi-isotropic
thin rectangular plates for different boundary conditions~//
Ocean Eng. 2013. Vol.~57. P.~197--222.

7. \textit{Ceribasi S., Altay G.}
Free vibration of super elliptical plates with constant and variable thickness
by Ritz method~//
Journal of Sound and Vibration. 2009. Vol.~319. N~1--2. P.~668--680.

8. \textit{Altunsaray E.}
Static deflections of symmetrically laminated quasi-isotropic super-elliptical
thin plates~//
Ocean Eng. 2017. Vol.~141. P.~337--350.

9. \textit{Nwoji C. U., Onah H. N., Mama B. O., Ike C. C.}
Ritz variational method for bending of rectangular kirchhoff plate under transverse
hydrostatic load distribution~//
Mathematical Modelling of Engineering Problems. 2018. Vol.~5. N~1. P.~1--10.

10. \textit{Aginam C.\,H., Chidolue C.\,A., Ezeagu C.\,A.}
Application of direct variational method in the analysis of isotropic thin rectangular
plates~//
ARPN Journal of Engineering and Applied Sciences. 2012. Vol.~7. N~9. P.~1128--1138.

11. \textit{Festus O., Okeke E.\,T., John W.}
Strain-displacement expressions and their effect on the deflection and
strength of plate~//
Advances in Science, Technology and Engineering Systems. 2020. Vol.~5. N~5. P.~401--413.

12. \textit{Wang X., Yuan Z.}
Buckling analysis of isotropic skew plates under general in-plane
loads by the modified differential quadrature method~//
Applied Mathematical Modelling. 2018. Vol.~56. P.~83--95.

13. \textit{Ike C.\,C., Onyia M.\,E., Rowland-Lato E.\,O.}
Generalized integral transform method for bending and buckling analysis of
rectangular thin plate with two opposite edges simply supported and other
edges clamped~//
Advances in Science, Technology and Engineering Systems. 2021. Vol.~6. N~1. P.~283--296.

14. \textit{Imrak E., Fetvaci C.}
The deflection solution of a clamped rectangular thin plate carrying uniformly load~//
Mechanics Based Design of Structures and Machines. 2009. Vol.~37. N~4. P.~462--474.

15. \textit{Meleshko V.\,V., Gomilko A.\,M., Gourjii A.\,A.}
Normal reactions in a clamped elastic rectangular plate~//
Journal of Engineering Mathematics. 2001. Vol.~40. P.~377--398.

16. \textit{Matrosov A.\,V., Suratov V.\,A.}
Stress-strain state in the corner points of a clamped plate
under uniformly distributed normal load~//
Materials Physics and Mechanics. 2018. Vol.~36. N~1. P.~124--146.

17. \textit{Matrosov A.\,V.}
An exact analytical solution for a free-supported micropolar rectangle
by the method of initial functions~//
Zeitschrift f\"ur Angewandte Mathematik und Physik. 2022. Vol.~73. N~2. P.~74.

18. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
A superposition method in the analysis of an isotropic rectangle~//
Applied Mathematical Sciences. 2016. Vol.~10. N~54. P.~2647--2660.

19. \textit{Голоскоков Д.\,П., Матросов А.\,В.}
Метод начальных функций в расчете изгиба защемленной по контуру тонкой ортотропной
пластинки~//
Вестник Санкт-Петербургского университета. Прикладная математика. Информатика.
Процессы управления. 2021. Т.~17. Вып.~4. С.~330--344. https://doi.org/10.21638.11701/spbu20.2021.402

20. \textit{Лурье А.\,И.}
Пространственные задачи теории упругости / пер. с англ.
М.: Гостехиздат, 1955. 491~с. (\textit{Lur'e A.\,I.}
Three dimensional problems of theory of elasticity.)

21. \textit{Власов В.\,З.}
Метод начальных функций в задачах теории упругости~//
Известия АН СССР. ОТН. 1955. №~7. С.~46--69.

22. \textit{Vlasov V.\,Z.}
Method of initial functions in problems of theory of thick plates and shells~//
Proceedings of 9$^\text{th}$ Intern. Congress Appl. Mech. 1957. N~6. P.~321--330.

23. \textit{Малиев А.\,С.}
К выбору функций общего решения в задаче равновесия изотропного упругого тела~//
Сб. науч. трудов Ленингр. электротехнич. ин-та. 1952. Вып.~4. С.~180--244.

24. \textit{Sundara Raja Iyengar K.\,T., Pandya S.\,K.}
Analysis of orthotropic rectangular thick plates~//
Fibre Sci. Technol. 1983. Vol.~18, N~1. P.~19--36.

25. \textit{Galileev S.\,M., Matrosov A.\,V.}
Method of initial functions in the computation of sandwich plates~//
Intern. Appl. Mech. 1995. Vol.~31. N~6. P.~469--476.

26. \textit{Kovalenko M.\,D.}
The lagrange expansions and nontrivial null-representations in terms of homogeneous
solutions~//
Dokl. Physics. 1997. Vol.~42. N~2. P.~90--92.

27. \textit{Dubey S.\,K.}
Analysis of homogeneous orthotropic deep beams~//
Journal of Struct. Eng. (Madras). 2005. Vol.~32. N~2. P.~109--116.

28. \textit{Patel R., Dubey S.\,K., Pathak K.\,K.}
Analysis of RC brick filled composite beams using MIF~//
Procedia Eng. 2013. N~51. P.~30--34.

29. \textit{Galileev S.\,M., Tabakov P.\,Y.}
Mathematical foundations of the method of initial functions for the application
to anisotropic plates~//
2$^\text{nd}$ Intern. Conference on Mech. Nanotechnol. Cryog. Eng. 2013. P.~59--63.

30. \textit{Patel R., Dubey S.\,K., Pathak K.\,K.}
Analysis of infilled beams using method of initial functions and
comparison with FEM~//
Intern. Journal of Eng. Sci. Technol. 2014. N~17. P.~158--164.

31. \textit{Matrosov A.\,V.}
A numerical-analytical decomposition method in analyses of complex structures~//
2014 Intern. Conference on Computer Technologies in Physical and Engineering
Applications, ICCTPEA 2014. Proceedings.
St~Petersburg. 2014. P.~104--105. N~6893305.

32. \textit{Matrosov A.\,V., Shirunov G.\,N.}
Numerical-analytical computer modeling of a clamped isotropic thick plate~//
2014 Intern. Conference on Computer Technologies in Physical and
Engineering Applications, ICCTPEA 2014. Proceedings.
St~Petersburg. 2014. P.~96.
N~6893300.


33. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Comparison of two analytical approaches to the analysis of grillages~//
2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov, SCP 2015. Proceedings.
St~Petersburg: Izdatel’skii Dom Fedorovoi~G.~V., 2015. P.~382--385.
N~7342169.

34. \textit{Matrosov A.\,V.}
A superposition method in analysis of plane construction~//
2015 Intern. Con\-fe\-rence on ``Stability and Control Processes'' in memory
of V.~I.~Zubov, SCP 2015. Proceedings.
St~Pe\-ters\-burg: Izdatel’skii Dom Fedorovoi~G.~V., 2015. P.~414--416.
N~7342156.

35. \textit{Olodo E.\,T., Adanhounme V., Hounkonnou M.\,N.}
Exact solution of the harmonic problem for a rectangular plate in flat deformation
by the method of initial functions~//
Intern. Journal of Appl. Mech. Eng. 2017. Vol.~22. N~2. P.~349--361.

36. \textit{Matrosov A.\,V., Shirunov G.\,N.}
Analyzing thick layered plates under their own weight by the method of initial
functions~//
Materials Physics and Mechanics. 2017. Vol.~31. N~1--2. P.~36--39.

37. \textit{Asutkar P., Shinde S.\,B., Patel R.}
Study on the behaviour of rubber aggregates concrete beams using analytical approach~//
Intern. Journal of Eng. Sci. Technol. 2017. N~20. P.~151--159.

38. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical approach in analyzing an orthotropic rectangular plate with a
crack~//
Materials Physics and Mechanics. 2018. Vol.~36. N~1. P.~137--141.

39. \textit{Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P., Yu G.}
On the exact solutions of the biharmonic problem of the theory of
elasticity in a half-strip~//
Zeitschrift f\"ur Angewandte Mathematik und Physik. 2018. Vol.~69. P.~121.

40. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical solutions in the analysis of thin elastic plates~//
AIP Conference Proceedings.  American Institute of Physics Publ.
2018. % Страницы не указываются! 1959,
N~070012.

41. \textit{Owczarek S., Owczarek M.}
Heat transport analysis in rectangular shields using the Laplace
and Poisson equations~//
Energies. 2020. Vol.~13. P.~1714.

42. \textit{Matrosov A.\,V., Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P.}
Method of initial functions and integral Fourier transform in some problems
of the theory of elasticity~//
Zeitschrift f\"ur Angewandte Mathematik und Physik. 2020. Vol.~71. N~1. P.~24.

43. \textit{Lam\'e G.}
Le\c{c}on sur la th\'eorie math\'emathique de
l'\'elasticit\'e des corps solids. Paris: Bachelier, 1852. 335~p.

44. \textit{Matrosov A.\,V.}
Computational peculiarities of the method of initial functions~//
Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial
Intelligence and Lecture Notes in Bioinformatics). 2019. P.~37--51.

%\pagebreak
\vskip 2.5%1.5
mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 8 марта 2022~г.

Cтатья принята к~печати 21 июня 2022~г.

\vskip6mm

К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Алцыбеев Глеб Олегович}
--- магистр математики; gleb.alcybeev@gmail.com \par%
%
\vskip2 mm \textit{Голоскоков Дмитрий Петрович}
--- д-р техн. наук, проф.; dpg1954@mail.ru \par%
%
\vskip2 mm \textit{Матросов Александр Васильевич}
--- д-р физ.-мат. наук, доц.; avmatrosov@mail.ru \par%
%
%
}
