
{\normalsize

\vskip 6mm

\noindent{\bf The superposition method in the problem of bending of a thin isotropic plate clamped along the contour %$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it G.~O.~Alcybeev$^1$,
                     D.~P.~Goloskokov$^2$,
                     A.~V.~Matrosov$^1$ %

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by Russian Foundation%
% for Basic Research (project N 20-07-00531 A).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
$^1$~%
St\,Petersburg State University, 7--9, Universitetskaya nab.,
St\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation


\noindent%
$^2$~%
St\,Petersburg Bonch-Bruevich
State University of Telecommunications, 22, pr.~Bol'shevikov,

\noindent%
\hskip2.45mm%
St\,Petersburg, 193232, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Alcybeev G. O., Goloskokov D. P., Matrosov A. V. The superposition method in the problem of bending of a thin isotropic plate clamped along the contour. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p5}--\pageref{p5e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05 (In Russian)

\begin{hyphenrules}{english}

\vskip2mm

{\leftskip=7mm\noindent In this work, the general solution of the differential equation for the bending of a
thin isotropic plate under the action of a normal load applied to its plane is
constructed by the superposition method.
The solutions obtained by the method of initial functions in the form of trigonometric
series are taken as two solutions, each of which allows satisfying the boundary
conditions on two opposite sides of the plate.
Two ways of satisfying the boundary conditions of a clamped plate are
studied: the method of expansion into trigonometric Fourier series and the collocation
method.
It is shown that both methods give the same results and sufficiently fast
convergence of the solution at all points of the plate except for small neighborhoods
of the corner points.
The constructed solution made it possible to study the behavior
of the shear force in the corner points. Computational experiments
have shown that when keeping 390 terms in the trigonometric series of the solution,
the shear force is close to zero, but not identically equal.\\[1mm]
\textit{Keywords}: isotropic plate, bending of a thin plate,
clamped plate, method of initial functions, MIF, computer algebra, Maple. \par}

\vskip6mm%5

\end{hyphenrules}

%\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Timoshenko S.\,P., Woinowsky-Krieger S.}
\textit{Theory of plates and shells}. 2$^\text{nd}$ ed. New York, McGraw-Hill Publ.,
1987, 580~p.
(Rus. ed.: {Timoshenko S.\,P., Woinowsky-Krieger~S.}
\textit{Plastinki i obolochki}.
Moscow, Nauka Publ., 1966, 636~p.)

2. {Meleshko V.\,V.}
Selected topics in the history of the two-dimensional biharmonic problem.
\textit{Appl. Mech. Rev.}, 2003, vol.~56, no.~1, pp.~33--85.

3. {Meleshko V.\,V.}
Bending of an elastic rectangular clamped plate: exact versus 'engineering' so\-lu\-tions.
\textit{Journal of Elasticity}, 1997, vol. 48, no.~1, pp.~1--50.

4. {Ceribasi S., Altay G., Cengiz Dokmeci M.}
Static analysis of superelliptical clamped plates by Galerkin's method.
\textit{Thin-Walled Structures}, 2008, vol.~46, no.~2, pp.~122--127.

5. {Khan Y., Tiwari P., Ali R.}
Application of variational methods to a rectangular clamped plate problem.
\textit{Computers and Mathematics with Applications}, 2012, vol.~63, no.~4, pp.~862--869.

6. {Altunsaray E., Bayer I.}
Deflection and free vibration of symmetrically laminated quasi-isotropic
thin rectangular plates for different boundary conditions.
\textit{Ocean Eng.}, 2013, vol.~57, pp.~197--222.

7. {Ceribasi S., Altay G.}
Free vibration of super elliptical plates with constant and variable thickness
by Ritz method.
\textit{Journal of Sound and Vibration}, 2009, vol.~319, no.~1--2, pp.~668--680.

8. {Altunsaray E.}
Static deflections of symmetrically laminated quasi-isotropic super-elliptical
thin plates.
\textit{Ocean Eng.}, 2017, vol.~141, pp.~337--350.

9. {Nwoji C. U., Onah H. N., Mama B. O., Ike C. C.}
Ritz variational method for bending of rectangular kirchhoff plate under transverse
hydrostatic load distribution.
\textit{Mathematical Modelling of Engineering Problems},
2018, vol.~5, no.~1, pp.~1--10.%\pagebreak

10. {Aginam C.\,H., Chidolue C.\,A., Ezeagu C.\,A.}
Application of direct variational method in the analysis of isotropic thin rectangular
plates.
\textit{ARPN Journal of Engineering and Applied Sciences}, 2012, vol.~7, no.~9,
pp.~1128--1138.

11. {Festus O., Okeke E.\,T., John W.}
Strain-displacement expressions and their effect on the deflection and
strength of plate.
\textit{Advances in Science, Technology and Engineering Systems}, 2020, vol.~5, no.~5,
pp.~401--413.

12. {Wang X., Yuan Z.}
Buckling analysis of isotropic skew plates under general in-plane
loads by the modified differential quadrature method.
\textit{Applied Mathematical Modelling}, 2018, vol.~56, pp.~83--95.

13. \textit{Ike C.\,C., Onyia M.\,E., Rowland-Lato E.\,O.}
Generalized integral transform method for bending and buckling analysis of
rectangular thin plate with two opposite edges simply supported and other
edges clamped.
\textit{Advances in Science, Technology and Engineering Systems}, 2021, vol.~6, no.~1,
pp.~283--296.

14. {Imrak E., Fetvaci C.}
The deflection solution of a clamped rectangular thin plate carrying uniformly load.
\textit{Mechanics Based Design of Structures and Machines}, 2009, vol.~37, no.~4,
pp. 462--474.

15. {Meleshko V.\,V., Gomilko A.\,M., Gourjii A.\,A.}
Normal reactions in a clamped elastic rectangular plate.
\textit{Journal of Engineering Mathematics}, 2001, vol.~40, pp.~377--398.

16. {Matrosov A.\,V., Suratov V.\,A.}
Stress-strain state in the corner points of a clamped plate
under uniformly distributed normal load.
\textit{Materials Physics and Mechanics}, 2018, vol.~36, no.~1, pp.~124--146.

17. {Matrosov A.\,V.}
An exact analytical solution for a free-supported micropolar rectangle
by the method of initial functions.
\textit{Zeitschrift f\"ur Angewandte Mathematik und Physik}, 2022,
vol.~73, no.~2, p.~74.

18. {Goloskokov D.\,P., Matrosov A.\,V.}
A superposition method in the analysis of an isotropic rectangle.
\textit{Applied Mathematical Sciences}, 2016, vol.~10, no.~54, pp.~2647--2660.

19. {Goloskokov D.\,P., Matrosov A.\,V.}
Metod nachal’nykh funktcii v raschete izgiba zashchemlennoi po konturu tonkoi ortotropnoi
plastinki [Method of initial functions in analyses of the
bending of a thin orthotropic plate clamped along the contour].
\textit {Vestnik of Saint Petersburg
University. App\-lied Mathematics. Computer Science. Control Processes}, 2021,
vol.~17, iss.~4, pp.~330--344. \\ https://doi.org/10.21638.11701/spbu20.2021.402 (In Russian)

20. \textit{Lur'e A.\,I.}
\textit{Three dimensional problems of theory of elasticity}.
New York, Willey Publ., 1964, 495~p.
(Rus. ed.: Lur'e A.\,I. \textit{Prostranstvenny`e zadachi teorii uprugosti}.
Moscow, Gostechisdat Publ., 1955, 491~p.)

21. {Vlasov V.\,Z.}
Metod nachal’nykh funktcii v zadachakh teorii uprugosti
[Method of initial functions in problems of the theory of elasticity].
\textit{Izv. Akad. Nauk SSSR. OTN}, 1955, no. 7, pp.~49--69. (In Russian)

22. {Vlasov V.\,Z.}
Method of initial functions in problems of theory of thick plates and shells.
\textit{Proceedings of 9$^{th}$ Intern. Congress Appl. Mech.}, 1957, no.~6, pp.~321--330.

23. {Maliev A.\,S.}
K vyboru funktcii obshchego resheniia v zadache ravnovesiia izotropnogo
uprugogo tela [On the choice of functions in general solutions of the problem of the equilibrium of an isotropic elastic body].
\textit{Sbornik nauch. trudov Leningrad Elektrotehnical Institute},
1952, iss.~4, pp.~180--244 (In Russian)

24. {Sundara Raja Iyengar K.\,T., Pandya S.\,K.}
Analysis of orthotropic rectangular thick plates.
\textit{Fibre Sci. Technol.}, 1983, vol.~18, no.~1, pp.~19--36.

25. {Galileev S.\,M., Matrosov A.\,V.}
Method of initial functions in the computation of sandwich plates.
\textit{Intern. Appl. Mech.}, 1995, vol.~31, no.~6, pp.~469--476.

26. {Kovalenko M.\,D.}
The lagrange expansions and nontrivial null-representations in terms of homogeneous
solutions.
\textit{Dokl. Physics}, 1997, vol.~42, no. 2, pp.~90--92.

27. {Dubey S.\,K.}
Analysis of homogeneous orthotropic deep beams.
\textit{Journal of Struct. Eng.} (Madras), 2005, vol.~32, no. 2, pp.~109--116.

28. {Patel R., Dubey S.\,K., Pathak K.\,K.}
Analysis of RC brick filled composite beams using MIF.
\textit{Procedia Eng.}, 2013, no.~51, pp.~30--34.

29. {Galileev S.\,M., Tabakov P.\,Y.}
Mathematical foundations of the method of initial functions for the application
to anisotropic plates.
\textit{2$^{nd}$ Intern. Conference on Mech. Nanotechnol. Cryog. Eng.}, 2013, pp.~59--63.

30. {Patel R., Dubey S.\,K., Pathak K.\,K.}
Analysis of infilled beams using method of initial functions and
comparison with FEM.
\textit{Intern. Journal of Eng. Sci. Technol.}, 2014, no.~17, pp.~158--164.

31. {Matrosov A.\,V.}
A numerical-analytical decomposition method in analyses of complex structures.
\textit{2014 Intern. Conference on Computer Technologies in
Physical and Engineering Applications, ICCTPEA 2014, Proceedings}.
St~Petersburg, 2014, pp.~104--105, no.~6893305.

32. {Matrosov A. V., Shirunov G. N.}
Numerical-analytical computer modeling of a clamped isotropic thick plate.
\textit{2014 Intern. Conference on Computer Technologies in Physical and
Engineering Applications, ICCTPEA 2014, Proceedings}.
St~Petersburg, 2014, p.~96, no.~6893300.

33. {Goloskokov D.\,P., Matrosov A.\,V.}
Comparison of two analytical approaches to the analysis of grillages.
\textit{2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov, SCP 2015, Proceedings}.
St~Petersburg, `Dom Fedorovoi~G.~V.' Press, 2015, pp.~382--385, no.~7342169.

34. {Matrosov A.\,V.}
A superposition method in analysis of plane construction.
\textit{2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov, SCP 2015, Proceedings}.
St~Petersburg, `Dom Fedorovoi~G.~V.' Press, 2015, pp.~414--416, no.~7342156.

35. {Olodo E.\,T., Adanhounme V., Hounkonnou M.\,N.}
Exact solution of the harmonic problem for a rectangular plate in flat deformation
by the method of initial functions.
\textit{Intern. Journal of Appl. Mech. Eng.}, 2017, vol.~22, no.~2, pp.~349--361.

36. {Matrosov A.\,V., Shirunov G.\,N.}
Analyzing thick layered plates under their own weight by the method of initial
functions.
\textit{Materials Physics and Mechanics}, 2017, vol.~31, no.~1--2, pp.~36--39.

37. {Asutkar P., Shinde S.\,B., Patel R.}
Study on the behaviour of rubber aggregates concrete beams using analytical approach.
\textit{Intern. Journal of Eng. Sci. Technol.}, 2017, no.~20, pp.~151--159.

38. {Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical approach in analyzing an orthotropic rectangular plate with a
crack.
\textit{Materials Physics and Mechanics}, 2018, vol.~36, no.~1, pp.~137--141.

39. {Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P., Yu G.}
On the exact solutions of the biharmonic problem of the theory of
elasticity in a half-strip.
\textit{Zeitschrift f\"ur Angewandte Mathematik und Physik}, 2018, vol.~69, p.~121.

40. {Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical solutions in the analysis of thin elastic plates.
\textit{AIP Conference Proceedings.} American Institute of Physics Publ.,
2018, no.~070012.

41. {Owczarek S., Owczarek M.}
Heat transport analysis in rectangular shields using the Laplace
and Poisson equations.
\textit{Energies}, 2020, vol.~13, p.~1714.

42. {Matrosov A.\,V., Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P.}
Method of initial functions and integral Fourier transform in some problems
of the theory of elasticity.
\textit{Zeitschrift f\"ur Angewandte Mathematik und Physik},
2020, vol.~71, no.~1, p.~24.

43. {Lam\'e G.}
\textit{Le\c{c}on sur la th\'eorie math\'emathique de
l'\'elasticit\'e des corps solids}
[\textit{Lectures on the mathematical theory of elasticity of solids}].
Paris, Bachelier Publ., 1852, 335~p.

44. {Matrosov A.\,V.}
Computational peculiarities of the method of initial functions.
\textit{Lecture Notes in Computer Science (including subseries Lecture Notes in
Artificial
Intelligence and Lecture Notes in Bioinformatics)},
2019, pp.~37--51. %11619 LNCS

\vskip1.5mm

Received:  March 8, 2022.

Accepted: June 21, 2022.


\vskip6mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Gleb O. Alcybeev}
--- Master of Mathematics; gleb.alcybeev@gmail.com \par%
%
\vskip2mm \textit{Dmitriy P. Goloskokov}
--- Dr. Sci. in Engineering Sciences, Professor; dpg1954d@mail.ru \par%
%
\vskip2mm \textit{Alexander V. Matrosov}
--- Dr. Sci. in Physics and Mathematics, Associate Professor;\\
avmatrosov@mail.ru \par%
%
%
}
