
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1.
{\it  Dall'Agnol F.\:F., De Assis T.\:A., Forbes R.\:G.}
Physics-based derivation of a formula for the mutual depolarization of two post-like field emitters
// Journal of Physics: Condensed Matter. 2018. Vol.~30. Iss.~37. N 375703 (5 p).

2.
{\it Liang~Y.} %\:W.
Ge-doped ZnO nanowire arrays as cold field emitters with excellent perfor\-man\-ce
//  Nano\-tech\-no\-lo\-gy. 2019. Vol.~30. Iss.~37. N 375603 (8 p).

3.
%{\it Давидович М.В.,  Яфаров Р.К.}
%Импульсные и~статические автоэмиссионные ВАХ-углеродных нанокластерных структур: %эксперимент и~его интерпретация.
%//   Журнал технической физики, 2019, Том.~89, вып.8. С. 1282--1293.
%
{\it  Davidovich M.\:V., Yafarov R.\:K.}
Pulsed and static field emission VAC of carbon nano\-clus\-ter structures: experiment and its  interpretation
//  Tech. Phys. 2019. Vol.~64. Iss.~8. P. 1210--1220.


4.
%{\it Попов Е.О., Колосько А.Г., Филиппов С.В.}
%Проверка применимости закона полевой эмиссии к~исследованию многоострийных полевых эмиттеров методом анализа степени предэкспоненциального множителя напряжения.
%//  Письма в~Журнал технической физики, 2019, Том.~89, вып.8. С. 1282--1293.
%
{\it Popov E.\:O., Kolosko A.\:G., Filippov S.\:V.}
 A test for the applicability of the field emission law to studying multitip field emitters by analysis of the power index of the preexponential voltage factor
//  Tech. Phys. Lett. 2019. Vol.~45. Iss.~9. P. 916--919.


5.
{\it  Kaur G., Saini K., Tripath A.\:K., Jain V., Deva D., Lahiri I.}
Room temperature growth and field emission characteristics of CuO nanostructures
//  Vacuum. 2017. Vol.~139. P. 136--142.


6.
{\it  Lee S.\:W., Kang J.\:S., Lee H.\:R., Park S.\:Y., Jang J., Par K.\:C.}
Enhanced and stable electron emission of carbon nanotube emitters with graphitization
//   Vacuum. 2015. Vol.~121. P. 212--216.


7.
{\it Riyajuddin S., Kumar S., Soni K., Gaur S.\:P., Badhwar D., Ghosh K.}
Study of field emission properties of pure graphene-CNT heterostructures connected via seamless interface
//  Nanotechnology. 2019. Vol.~30. Iss. 38. N 385702 (10 p).


8.
{\it  Tripathi P, Gupta B.\:K., Bankar P.\:K., More M.\:A., Late D.\:J., Srivastava O.\:N.}
Gra\-phe\-ne nanosheets assisted carbon hollow cylinder for high performance field emission applications
//  Materials Research Express. 2019. Vol.~6. Iss. 9. N 095066 (10 p).


9.
{\it  De Assis T.\:A., Dall'Agnol F.\:F.}
Mechanically stable nanostructures with desirable characteristic field enhancement factors: a response from scale invariance in electrostatics
//  Nanotechnology. 2016. Vol.~27. Iss. 44. N 44LT01 (6 p).


10. {\it Миролюбов Н.\:Н.} Методы расчета электростатических
полей. М.: Высшая школа, 1963. 209~с.
%
%{\it Mirolyubov N.\:N.} Metody rascheta elektrostaticheskikh poley [Methods of calculating electrostatic fields]. Moscow, Vysshaya Shkola,  1963, 209 p. (In Russian)


11. {\it Доронин Г.\:Г., Виноградова Е.\:М.} Моделирование диодной
полевой эмиссионной системы с~диэлектрической прослойкой
//   Процессы управления и~устойчивость. 2019. Т. 6. № 1. С. 73--77.


%{\it Doronin G.\:G., Vinogradova E.\:M.}
%Diode field emission system with a dielectric layer modeling
% // The L Annual International Conference on Control Processes and Stability (CPS'19). Abstracts / Ed. by N. V. Smirnov. St. Petersburg: Publishing House Fedorova G.V., 2019. P. 73--77.


12.
{\it Vinogradova E.\:M., Egorov N.\:V., Doronin G.\:G.}
The shart-edged field cathode mathe\-ma\-ti\-cal mo\-deling //
14th International Baltic Conference on Atomic Layer Deposition, BALD 2016. Proceedings.  2016.  P. 68--70.


13. {\it Бугаев А.\:С., Виноградова Е.\:М., Егоров Н.\:В., Шешин
Е.\:П.} Автоэлектронные катоды и~пушки.
 Долгопрудный: ИД «Интеллект», 2017. 288 с.

%{\it Bugaev A.\:S., Vinogradova E.\:M., Egorov N.\:V., Sheshin E.\:P.}
%Avtoelektronnyye katody i pushki [Field-electron cathodes and guns]. Dolgo\-prudny, ID "Intellect", 2017, 288 p. (In Russian)


14.
%{\it Виноградова E.M., Егоров H.B., Телевный Д.С.}
%Расчет триодной полевой эмиссионной системы с~модулятором
%//   Журнал технической физики, 2014, Том.~84, вып.2. С. 139--144.
%
{\it  Vinogradova E.\:M., Egorov N.\:V., Televnyi D.\:S.}
  Calculation of a triode field-emission system with a modulator
//  Tech. Phys. 2014. Vol.~59. Iss. 2. P. 291--296.


15.
{\it Vinogradova E.\:M., Egorov E.\:N., Televnyy D.\:S.}
Mathematical modeling of field emitter array
//  Vacuum.  2016. Vol. 127. P. 45--50.


16.
%{\it Виноградова Е.М., Доронин Г.Г., Егоров Н.В.}
%Математическое моделирование двумерной диодной системы с~полевым эмиттером лезвийной формы.
%//   Журнал технической физики, 2020, Том.~90, вып. 4. С. 540--543.
%
{\it Vinogradova E.\:M., Egorov N.\:V., Doronin G.\:G.}
Mathematical simulation of a 2D diode system with a blade-shaped field emitter //
Tech. Phys. 2020. Vol.~65. Iss. 4. P.  514--518.



\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 3 марта 2020~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip1.5mm\textit{Виноградова Екатерина Михайловна} --- д-р физ.-мат. наук,
        проф.; e.m.vinogradova@spbu.ru

\vskip1.5mm\textit{Доронин Григорий Геннадьевич} --- аспирант; fluctum@gmail.com

}
