
{\normalsize

\vskip 4.2mm%6mm

\noindent{\bf Mathematical modeling of two-dimentional periodic system of field emitters%$\,^*$%
}

}

\vskip 1.5mm%2mm

{\small

\noindent{\it E. M. Vinogradova, G. G. Doronin%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.5mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:}  Vinogradova  E. M., Doronin  G. G.
Mathematical modeling of two-dimentional periodic system of field emitters. {\it Vestnik of
Saint~Pe\-ters\-burg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04  (In Russian)

\vskip2.0mm%3mm

{\leftskip=7mm\noindent The work is devoted to a two-dimensional periodic system of field emitters mathematical modeling. Field-emission electron-vacuum devices are actively used in many fields of science and technology. In this article the field cathode as a periodic system of emitters of infinite length and the same shape, located on a flat substrate and at the same distance from each other, is investigated. Anode is a plane parallel to the substrate. To calculate the electrostatic potential distribution the influence of each emitter is replaced by the influence of a charged filament. To solve the boundary value problem for the Poisson equation the  variables  separation method in Cartesian coordinates is used. The potential distribution was found in an analytical form in the entire area of the system. In accordance with the formulas obtained, numerical calculations were carried out and the effect of emitter packing density on the electrostatic potential distribution is shown.\\[1mm]
\textit{Keywords}: field emitter array, field cathode, boundary-value problem, electrostatic potential,  Poisson equation, mathematical modeling.
\par}

\vskip 5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

    1.
    Dall'Agnol F. F., De Assis T. A., Forbes R. G.  Physics-based derivation of a formula for the mutual depolarization of two post-like field emitters.
    {\it  Journal of Physics: Condensed Matter}, 2018, vol.~30, iss.~37, N 375703 (5 p).

    2.
    Liang~Y.  W.    Ge-doped ZnO nanowire arrays as cold field emitters with excellent perfor\-man\-ce.
      {\it Nano\-tech\-no\-lo\-gy}, 2019, vol.~30, iss.~37, N 375603 (8 p).

    3.
    %{\it Давидович М.В.,  Яфаров Р.К.}
    %Импульсные и статические автоэмиссионные ВАХ-углеродных нанокластерных структур: %эксперимент и его интерпретация.
    %//   Журнал технической физики, 2019, Том.~89, вып.8. С. 1282-1293.
    %
    Davidovich M. V., Yafarov R. K.     Pulsed and static field emission VAC of carbon nano\-clus\-ter structures: experiment and its  interpretation.
      {\it  Tech. Phys.}, 2019, vol.~64, iss.~8, pp. 1210--1220.


    4.
    %{\it Попов Е.О., Колосько А.Г., Филиппов С.В.}
    %Проверка применимости закона полевой эмиссии к исследованию многоострийных полевых эмиттеров методом анализа степени предэкспоненциального множителя напряжения.
    %//  Письма в Журнал технической физики, 2019, Том.~89, вып.8. С. 1282-1293.
    %
    Popov E. O., Kolosko A. G., Filippov S. V.  A test for the applicability of the field emission law to studying multitip field emitters by analysis of the power index of the preexponential voltage factor.   {\it Tech. Phys. Lett.}, 2019, vol.~45, iss.~9, pp. 916--919.


    5.
    Kaur G., Saini K., Tripath A. K., Jain V., Deva D., Lahiri I.
    Room temperature growth and field emission characteristics of CuO nanostructures.
      {\it  Vacuum}, 2017, vol.~139, pp. 136--142.


    6.
    Lee S.\:W., Kang J.\:S., Lee H.\:R., Park S.\:Y., Jang J., Par K.\:C.
    Enhanced and stable electron emission of carbon nanotube emitters with graphitization.
       {\it  Vacuum}, 2015, vol.~121, pp. 212--216.


    7.
    Riyajuddin S., Kumar S., Soni K., Gaur S.\:P., Badhwar D., Ghosh K.
    Study of field emission properties of pure graphene-CNT heterostructures connected via seamless interface.  {\it Nanotechnology}, 2019, vol.~30, iss. 38, N 385702 (10 p).


    8.
    Tripathi P., Gupta B.\:K., Bankar P.\:K., More M.\:A., Late D.\:J., Srivastava O.\:N.
    Gra\-phe\-ne nanosheets assisted carbon hollow cylinder for high performance field emission applications.     {\it  Materials Research Express}, 2019, vol.~6, iss. 9, N 095066 (10 p).


    9.
    De Assis T.\:A., Dall'Agnol F.\:F.
    Mechanically stable nanostructures with desirable characteristic field enhancement factors: a response from scale invariance in electrostatics.
    {\it  Nanotechnology}, 2016, vol.~27, iss. 44, N 44LT01 (6 p).


    10.
%   Миролюбов Н.\:Н. {\it Методы расчета электростатических полей}. М.: Высшая школа, 1963. 209 с.
    %
    Mirolyubov N.\:N. {\it Metody rascheta elektrostaticheskikh poley} [{\it Methods of calculating electrostatic fields}]. Moscow, Vysshaya Shkola Publ.,  1963, 209 p. (In Russian)


    11.
%   {\it Доронин Г.\:Г., Виноградова Е.\:М.}
%   Моделирование диодной полевой эмиссионной системы с диэлектрической прослойкой
%   //   Процессы управления и устойчивость. 2019. Т. 6. № 1. С. 73-77.
%
    Doronin G.\:G., Vinogradova E.\:M. Modelirovanie diodnoy polevoy emissionnoy sistemy s dielektricheskoy prosloikoy
    [Diode field emission system with a dielectric layer modeling].
    {\it The L Annual International Conference on Control Processes and Stability (CPS'19)}. Abstracts. Ed. by N. V. Smirnov. St. Petersburg, Publishing House Fedorova G. V., 2019, pp. 73--77. (In Russian)


    12.
    Vinogradova E.\:M., Egorov N.\:V., Doronin G.\:G.
    The shart-edged field cathode mathe\-ma\-ti\-cal mo\-deling.
    {\it 14th International Baltic Conference on Atomic Layer Deposition, BALD 2016. Proceedings},  2016,  pp.~68--70.


    13.
%   {\it Бугаев А.\:С., Виноградова Е.\:М., Егоров Н.\:В., Шешин Е.\:П.}
%   Автоэлектронные катоды и пушки.
%   Долгопрудный: ИД «Интеллект», 2017, 288 с.
%
    Bugaev A.\:S., Vinogradova E.\:M., Egorov N.\:V., Sheshin E.\:P.
    {\it Avtoelektronnyye katody i pushki} [{\it Field-electron cathodes and guns}]. Dol\-go\-prud\-ny, ID ``Intellect’’ Publ., 2017, 288 p. (In Russian)


    14.
    %{\it Виноградова E.M., Егоров H.B., Телевный Д.С.}
    %Расчет триодной полевой эмиссионной системы с модулятором
    %//   Журнал технической физики, 2014, Том.~84, вып.2. С. 139-144.
    %
    Vinogradova E.\:M., Egorov N.\:V., Televnyi D.\:S.
    Calculation of a triode field-emission system with a modulator.
    {\it  Tech. Phys.}, 2014, vol.~59, iss. 2, pp. 291--296.


    15.
    Vinogradova E.\:M., Egorov E.\:N., Televnyy D.\:S.
    Mathematical modeling of field emitter array.
    {\it Vacuum},  2016, vol. 127, pp. 45--50.


    16.
    %{\it Виноградова Е.М., Доронин Г.Г., Егоров Н.В.}
    %Математическое моделирование двумерной диодной системы с полевым эмиттером лезвийной формы.
    %//   Журнал технической физики, 2020, Том.~90, вып.4. С. 540--543.
    %
    Vinogradova E.\:M., Egorov N.\:V., Doronin G.\:G.
    Mathematical simulation of a 2D diode system with a blade-shaped field emitter.
    {\it Tech. Phys.}, 2020, vol.~65, iss. 4, pp.  514--518.


\vskip 1.5mm

Received:  March 03, 2020.

Accepted: May 28, 2020.
%
%
\vskip4.2mm A\,u\,t\,h\,o\,r\,s' \
i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
%
%
\vskip2mm \textit{Ekaterina M. Vinogradova} --- Dr. Sci. in
Physics and Mathematics, Professor;\\ e.m.vinogradova@spbu.ru
%
\vskip2mm \textit{Grigoriy G. Doronin} --- Postgraduate Student;
fluctum@gmail.com\par
%
}
