

{\footnotesize

\vskip 2mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 1.5mm



1. Ovsyannikov~A.\,D., Ovsyannikov~D.\,A., Durkin~À.\,P., Chang
S.-L. Op\-timizatsiia sogla\-suyushchei sektsii uskoritelya s
prostranstvenno odnorodnoi kvadrupol'noi fokusirovkoi
[Op\-timization of matching section of an accelerator with a
spatially uniform quadrupole focusing]. {\it Zhurnal Tekhnicheskoi
Fiziki} [{\it Technical Physics}], 2009,  vol.~79,  issue~11,
pp.~102--105. (In Russian)


2. Pervukhin~V.\,V. Fokusirovka i deklasterizatsiya ionov v
peremennom kvadrupol'nom elektricheskom pole [Ion focusing and
declusterization in alternating quadrupole electric field].   {\it
Pis'ma v Zhurnal Tekhnicheskoi Fiziki} [{\it Technical Physics
Letters}], 2005, vol.~31, issue~14, pp.~16--21.  (In Russian)


3. Ponomarev~A. G.,  Magilin~D. V.,  Miroshnichenko~V. I.,
Ponomareva~A. A. Ionno-opti\-ches\-kie svoistva kvadrupol'nykh
linz s konicheskoi aperturoi  [Ion-optical properties of
quad\-rupole lenses with conical aperture]. {\it Prikladnaia
fizika}  [{\it Applied Physics}], 2011, issue~3, pp.~117--124. (In
Russian)


4. Burns~L.\,R.,  Bouas~J.\,D.,  Matteson~S.,  Weathers~D.\,L.
Evaluation of a novel design for an electrostatic quadrupole
triplet ion beam lens. {\it  Nucl. Instr. and Meth.  B.} 2007,
vol.~261, no.~1--2, pp.~75--78.


5.  Vinogradova~E., Sergeev~V. The Field Gun with the Thin Emitter
Mathematical Modeling.\linebreak {\it 20th Intern. Workshop on
Beam Dynamics and Optimization $($BDO$)$}, 2014,  pp.~186--187.


6. Vinogradova~E. M.,  Egorov~N. V.,  Televnyi~D. S. Raschet
triodnoi polevoi emissionnoi sistemy s modulyatorom [Calculation
of a triode field-emission system with a modulator]. {\it Zhurnal
Tekhnicheskoi Fiziki} [{\it Technical Physics}], 2014,  vol.~84,
issue~2,  pp.~139--144.  (In Russian)


7. Vinogradova~E. M., Dolgov~S. L.,  Egorov~N. V. Raschet
electrostaticheskogo potentsiala v mnogoostriinykh i
odnoostriinykh polevykh sistemakh [Calculation of electrostatic
potential in multi-tip and single-tip field emission systems].
{\it Vestnik of Saint Petersburg University. Series 10. Applied
mathematics. Computer science. Control processes},  2007, issue~1,
pp.~29--37.  (In Russian)

8. Egorov~N. V.,  Vinogradova~E. M.,  Baranov~R. Yu. Raschet
elektrostaticheskogo polya sistemy soosnykh
aksial'no-simmetrichnykh elektrodov [Calculation of the
electrostatic field produced by a system of coaxial axially
symmetric electrodes]. {\it Radiotekhnika i elektronika} [{\it
Journal of Communications Technology and Electronics}], 2007,
vol.~52, issue~2,  pp.~212--217.  (In Russian)

9. Gerus~V. L. {\it Fizicheskie osnovy electronno-luchevykh
priborov} [{\it Basic physics of the electron-beam devices}].
Moscow, Nauka Publ., 1993, 352~p.  (In Russian)




}
