
{\normalsize

\vskip 6mm

\noindent{\bf Direct solution of a minimax location problem on the
plane\\ with rectilinear metric in a rectangular area}

}

\vskip 1.5mm

{\small

\noindent{\it P.~V.~Plotnikov, N.~K.~Krivulin}

\vskip 1.5mm

{\footnotesize \noindent St.\,Petersburg State University, 7--9,
Universitetskaya nab., St.\,Petersburg, 199034, Russian Federation

}

\vskip3mm

\noindent \textbf{For citation:}  Plotnikov P.~V.,~Krivulin N.~K.
Direct solution of a minimax location problem on the plane with
rectilinear metric in a rectangular area. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/spbu10.\issueyear.\issuenum04

\vskip3mm

{\leftskip=7mm\noindent A minimax single-facility location problem
with rectilinear (Manhattan) metric is examined under constraints
on the feasible location region, and a direct, explicit solution
of the problem is suggested using methods of tropical (idempotent)
mathematics. When no constraints are imposed, this problem, which
is also known as the Rawls problem or the messenger boy problem,
has known geometric and algebraic solutions. In the present
article, a solution to the problem is investigated subject to
constraints on the feasible region, which is given by a
rectangular area. At first, the problem is represented in terms of
tropical mathematics as a tropical optimization problem, a
parameter is introduced to represent the minimum value of the
objective function, and the problem is reduced to a parametrized
system of inequalities. This system is solved for one variable,
and the existence conditions of solution are used to obtain
optimal values of the second parameter by using an auxiliary
optimization problem. Then, the obtained general solution is
transformed into a set of direct solutions, written in a compact
closed form for different cases of relations between the initial
parameters of the problem. Graphical illustrations of the solution
are given for several positions
of the feasible location region on the plane.\\[1mm]
\textit{Keywords}: Rawls location problem, constrained location,
rectilinear metric, idempotent semifield, tropical optimization,
complete solution.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize


1.~Baccelli~F., Cohen~G., Olsder~G.~J., Quadrat J.-P.
\textit{Synchronization and linearity}. Chichester, Wiley Press,
1993, 514~p. (Wiley Series in Probability and Statistics)

2.~Maslov~V.~P., Kolokol’tsov~V.~N. \textit{Idempotentnyj analiz i
ego primenenie v optimal’nom upravlenii \textup{[}Idempotent
analysis and its applications in optimal control\textup{]}.}
Moscow, Fizmatlit Publ., 1994, 144~p. (In Russian)

3.~Cuninghame-Green~R.~A. Minimax algebra and applications.
\textit{Advances in Imaging and Electron Physics, vol.~90} / ed.
by P.~W.~Hawkes. San Diego, Academic Press, 1994, pp.~1--121.
DOI:~10.1016/S1076-5670(08)70083-1

4.~Golan~J.~S. \textit{Semirings and affine equations over them}.
New York, Springer Press, 2003, 256~p. (Vol.~556 of Mathematics
and its Applications). DOI:~10.1007/978-94-017-0383-3

5.~Heidergott~B., Olsder~G.~J., van der Woude~J. \textit{Max plus
at work}. Princeton, Princeton University Press, 2006, 226~p.
(Princeton Series in Applied Mathematics)

6.~McEneaney~W.~M. \textit{Max-plus methods for nonlinear control
and estimation}. Boston, Birkh\"{a}user Press, 2006, 241~p.
(Systems and Control: Foundations and Applications).
DOI:~10.1007/0-8176-4453-9

7.~Itenberg~I., Mikhalkin~G., Shustin~E.~I. \textit{Tropical
algebraic geometry}. Basel, Birkh\"{a}user Press, 2007, 104~p.
(Vol.~35 of Oberwolfach Seminars). DOI:~10.1007/978-3-7643-8310-7

8.~Gondran~M., Minoux~M. \textit{Graphs, dioids and semirings}.
New York, Springer Press, 2008, 383~p. (Vol.~41 of Operations
Research/ Computer Science Interfaces).
DOI:~10.1007/978-0-387-75450-5

9.~Butkovi\v{c}~P. \textit{Max-linear systems}. London, Springer
Press, 2010, 272~p. (Springer Monographs in Mathematics).
DOI:~10.1007/978-1-84996-299-5

10.~Krivulin~N.~K. A multidimensional tropical optimization
problem with nonlinear objective function and linear constraints.
\textit{Optimization}, 2015, vol.~64, no.~5, pp.~1107--1129. DOI:
10.1080/ 02331934.2013.84062

11.~Krivulin~N.~K. Algebraic solutions to multidimensional minimax
location problems with Chebyshev distance. \textit{Recent
Researches in Applied and Computational Mathematics. Intern.
conference on Applied and Computational Mathematics
$($ICACM'11$)$}, WSEAS, 2011, pp.~157--162.

12.~Krivulin~N.~K. Algebraic solution to a constrained rectilinear
minimax location problem on the plane. \textit{Multimedia
Technology $($ICMT$)$, 2011 Intern. conference on}. IEEE, 2011,
pp.~6216--6220. DOI: 10.1109/ICMT.2011.6002526

13.~Krivulin~N.~K. A new algebraic solution to multidimensional
minimax location problems with Chebyshev distance. \textit{WSEAS
Transactions on Mathematics}, 2012, vol.~11, no.~7, pp.~605--614.

14.~Krivulin~N.~K. An extremal property of the eigenvalue of
irreducible matrices in idempotent algebra and solution of the
Rawls location problem. \textit{Vestnik of Saint Petersburg
University. Mathematics}, 2011, vol.~44, iss.~4, pp.~272--281.
DOI:~10.3103/S1063454111040078

15.~Krivulin~N.~K., Plotnikov~P.~V. On an algebraic solution of
the Rawls location problem in the plane with rectilinear metric.
\textit{Vestnik of Saint Petersburg University. Mathematics},
2015, vol.~48, iss.~2, pp.~75--81. DOI:~10.3103/S1063454115020065

16.~Elzinga~J., Hearn~D.~W. Geometrical solutions for some minimax
location problems. \textit{Transport. Sci.}, 1972, vol.~6, no.~4,
pp.~379--394. DOI:~10.1287/trsc.6.4.379

17.~Francis~R.~L. A geometrical solution procedure for a
rectilinear distance minimax location problem. \textit{AIIE
Trans.}, 1972, vol.~4, no.~4, pp.~328--332.
DOI:~10.1080/05695557208974870

18.~Krivulin~N.~K., Plotnikov~P.~V. Using tropical optimization to
solve minimax location problems with rectilinear metric on the
line. \textit{Vestnik of Saint Petersburg University.
Mathematics}, 2016, vol.~3(61), iss.~4, pp.~602--614.
DOI:~10.3103/S1063454116040087



\vskip5mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.5mm \textit{Plotnikov Pavel V.}~--- postgraduate student;
pavplot@gmail.com


\vskip1.5mm \textit{Krivulin Nikolai K.}~--- Dr. Sci. in physics
and mathematics, professor; nkk@math.spbu.ru



}
