
{\small

\vskip6mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. {\em Резинкина~М.~М., Ерисов~А.~В., Пелевин~Д.~Е., Лобжанидзе~Л.Э.}
Экспериментальное исследование влияния индуцированной и остаточной намагниченности
ферромагнитных конструкций на ослабление геомагнитного поля в жилых помещениях~// Вестник Харьковск. политехнич. ин-та. 2009. Вып.~41. С.~111--120.

2. {\em Розов~В.~Ю., Завальный~А.~В., Золотов~С.~М., Грецких~С.~В.}
Методы нормализации статического геомагнитного поля в жилых домах //
Електротехнiка i електромеханiка. 2015. Вып.~2. С.~35--40.

3. {\em Amoskov V.~M., Bazarov A.~M., Belyakov V.~A., Gapionok E.~I., Kaparkova M.~V.,
Kukh\-tin~V.~P., Lam\-zin~E.~A., Lyublin B.~V., Sytchevsky S.~E.} Modelling of magnetic
field perturbations in electrophysical devices due to the steel reinforcement
of buildings // Technical Physics. 2017. Vol.~62. N~10. P.~1466--1472. %\\
https://doi.org/10.1134/S1063784217100048

4. {\em Amoskov V., Bazarov A., Kaparkova M., Kukhtin V., Lamzin~E., Lyublin~B.,
Belyakov~V., Sytchevsky~S., Gribov~Y.} Modeling magnetic effects of steel rebar
of concrete surroundings for electrophysical apparatus~//
RuPAC. 2016. THPSC007. С.~553--555. \\
https://doi.org/10.18429/JACoW-RuPAC2016-THPSC007

5. {\em Amoskov V., Bazarov A., Belyakov V., Gapionok E., Gribov Y., Kaparkova~M.,
Kukhtin~V., Lamzin~E., Lyublin~B., Ovsyannikov~D., Sytchevsky~S.}
Calculation of magnetic field from steel rebar of building with machine
producing high stray field // Fusion Eng. Des. 2018. Vol.~135.
P.~165--173. \\
https://doi.org/10.1016/j.fusengdes.2018.07.026

6. Oфициальный сайт ИТЭР 26.06.2021~г. URL: www.iter.org (дата обращения: 26.06.2021~г.).

7. {\em Amoskov V.~M., Belov A.~V., Belyakov V.~A., Gapionok E.~I., Gribov Y.~V.,
Kukhtin V.~P., Lam\-zin E.~A., Mita Y., Ovsyannikov A.~D., Ovsyannikov D.~A.,
Patisson~L., Sytchevsky~S.~E., Zavad\-skiy~S.~V.} Magnetic model MMTC-2.2
of ITER tokamak complex // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2019. T.~15. Вып.~1. С.~5--21. %\\
https://doi.org/10.21638/11702/spbu10.2019.101

8. {\em Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S.} Stray magnetic field produced by ITER Tokamak
Complex // Plasma Devices Oper. 2009. Vol.~17. N~4. P.~230--237.

9. {\it Conley C.~C. } A review of the biological effects of very low magnetic fields: Report NASA TN D-5902. Washington, D.~C.: National Aeronautics and Space Administration, 1970. N~20546. 25~p.

10. {\em Wang X., Li B., Xu M., Li D., Jiang J.} Long-term memory was impaired in one-trial
passive avoidance task of day-old chicks hatching from hypomagnetic field space //
China Sci. Bull. 2003. Vol.~48. N~22. P.~2454--2457. %\\
 https://doi.org/10.1360/03wc0231

11. {\em Zhang B., Lu H., Xi W., Zhou X., Xu S., Zhang K., Jiang J., Li Y., Guo A.}
Exposure to hypomagnetic field space for multiple generations causes amnesia
in {\it Drosophila melanogaster} // Neuroscience Letters.
2004. Vol.~371. N~2--3. P.~190--195. %\\
https://doi.org/10.1016/j.neulet.2004.08.072

12. {\em Zhang X., Li J.-F., Wu Q.-J., Li B., Jiang J. }
Effects of hypomagnetic field in noradrenergic activities in the brainstem
of golden hamster // Bioelectromagnetics. 2007. Vol.~28. P.~155--158. \\
https://doi.org/10.1002/bem.20290

13. {\em Binhi V.~N., Prato F.~S. } Biological effects of the hypomagnetic field. An analytical review of experiments and theories //
PLoS One. 2017.
Vol.~12. N~6. P.~1--51.\\
 https://doi.org/10.1371/journal.pone.0179340

14. {\em Johnson-Groh M., Merzdorf J.} NASA’s Goddard Space Flight Center,
Greenbelt.
URL:\\
https://www. nasa.gov/feature/nasa-researchers-track-slowly-splitting-dent-in-earth-s-magnetic-field
(дата обращения: 19.08.2020~г.).

15. {\em Ahmad M., Galland P., Ritz T., Wiltschko R., Wiltschko W.}
Magnetic intensity affects cryptochrome-dependent responses in {\it Arabidopsis thaliana} //
Planta. 2007. Vol.~225. P.~615--624.\\
 https://doi.org/10.1007/s00425-006-0383-0

16. {\em Buchachenko A. L., Kuznetsov D. A.} Magnetic field affects enzymatic ATP synthesis //
Journal of Amer. Chem. Soc. 2008. Vol.~130. N~39. P.~12868--12869. %\\
https://doi.org/10.1021/ja804819k

17. {\em Hore P.~J.} Are biochemical reactions affected by weak magnetic fields? //
Proceedings Natl. Acad. Sci. USA. 2012. January 31. Vol.~109. N~5. P.~1357--1358. %\\
https://doi.org/10.1073/pnas.1120531109

18. {\em Servick K.} Humans --- like other animals --- may sense Earth’s magnetic field //
 Science. 2019. Vol.~363. Iss.~6433. P.~1257--1258. %\\
https://doi.org/10.1126/science.363.6433.1257

19. {\em Sarimov R.~M., Binhi V.~N., Milyaev V.~A.} The influence of geomagnetic
field compensation on human cognitive processes // Biophysics. 2008.
Vol.~53. P.~433--441. \\ https://doi.org/10.1134/S0006350908050205


20. {\em Van Huizen A.~V., Morton J.~M., Kinsey L.~J., Von Kannon D.~G., Saad~M.~A.,
Birkholz~T.~R., Czajka~J.~M., Cyrus~J., Barnes~F.~S., Beane~W.~S. }
Weak magnetic fields alter stem cell-mediated growth // Science Advances.
2019. Vol.~5. Iss.~1. Article N~7201. %\\
https://doi.org/10.1126/sciadv.aau7201

21. {\it Shimojo S., Wu D.-A., Kirschvink J. } New evidence for a human magnetic
sense that lets your brain detect the Earth’s magnetic field //
The Conversation. URL:
https://theconversation.com/\linebreak new-evidence-for-a-human-magnetic-sense-that-lets-your-brain-detect-the-earths-magnetic-field-113536 \linebreak(дата обращения: 18.03.2019 г.).

22. {\em Thoss F., Bartsch B.}
The human visual threshold depends on direction and strength of a weak magnetic field //
Journal of Comparative Physiology A. 2003. Vol.~189. P.~777--779. \\
https://doi.org/10.1007/s00359-003-0450-y

23. {\em Походзей Л.~В.} Гипогеомагнитные условия как фактор риска для здоровья
человека // Труды II Междунар. конфeренции <<Электромагнитные поля и здоровье человека>>.
М., 1999. С.~135--136.

24. {\em Нахильницкая З. Н., Мастрюкова В. М., Андрианова Л. А. Бородкина~А.~Т.}
Реакция организма на воздействие <<нулевого>> магнитного поля // Космическая биология
и авиакосмическая медицина. 1978. №~2. С.~74--76.

25. Санитарно-эпидемиологические правила и нормативы. СанПиН 2.1.8/2.2.4.2490-09
<<Электромагнитные поля в производственных условиях>>. Утв. Глав. гос. сан. врачом Российской Федерации 2~марта 2009~г.; введ. 15~марта 2009~г.  М.:  Роспотребнадзор, 2009. 1~c.

26. Санитарно-эпидемиологические правила и нормативы СанПиН 2.1.8/2.2.4.2489-09
<<Гипогеомагнитные поля в производственных, жилых и общественных зданиях и сооружениях>>.  Утв. Глав. гос. сан. врачом Российской Федерации 2~марта 2009~г.; введ. 15~марта 2009~г. М.:  Роспотребнадзор, 2009. 13~c.

27. {\em Korovkin N., Diop C.~Y.} Minimization of electromagnetic fields
intensity and optimization of electrical wiring networks in healthcare facilities //
2016 IEEE NW Russia Young Researchers in Electrical and Electronic Engineering
Conference (EIConRusNW). 2016. P.~604--607. \\
https://doi.org/10.1109/EIConRusNW.2016.7448255

28. World magnetic model calculator.
URL:\\
www.geomag.bgs.ac.uk/data\_service/models\_compass/igrf\_calc.html (дата обращения: 26.06.2021~г.).

29. {\em Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S.} Assessment of error field from ferromagnetic
surrounding of ITER tokamak: ferromagnetic rebar of Tokamak Complex building //
Plasma Devices Oper. 2008. Vol.~16. N~4. P.~225--233. \\
https://doi.org/10.1080/10519990802433875

30. {\em Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S.} Stray magnetic field produced by ITER tokamak
complex // Plasma Devices Oper. 2009. Vol.~17. P.~230--237. %\\
https://doi.org/10.1080/10519990903043599

31. {\em Amoskov V., Belov A., Belyakov V., Gribov Y., Kavin A., Kukhtin~V.,
Lamzin~E., Lobanov~K., Maximen\-kova~N., Mineev~A., Sytchevsky~S.}
Stray magnetic field at plasma initiation produced by ferromagnetic elements
of the ITER Tokamak Complex //
Plasma Devices Oper. 2009. Vol.~17. N~4. P.~238--249. %\\
 https://doi.org/10.1080/10519990903043623

32. {\em Карауш С. А., Кузнецов А. В.} Влияние металлических фасадных систем на
геомагнитное поле внутри помещений // Вестник Томск. гос.
архитектурно-строит. ун-та. 2013. Т.~38. №~1. С.~83--87.

33. {\em Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S.} Assesment of error field from solitary
ferromagnetic elements located outside of ITER tokamak //
Plasma Devices Oper. 2008. Vol.~16. P.~171--179. \\
https://doi.org/10.1080/10519990802249289

34. {\em Amoskov V., Gribov Y., Lamzin E., Sythevsky S.}
Assessment of $n=1$ ``overlap'' error field produced by localized steel objects
placed at different levels of ITER Tokamak building //
Fusion Eng. Des. 2019. Vol.~148. Article N~111271. %\\
https://doi.org/10.1016/j.fusengdes.2019.111271

35. {\em Amoskov V.~M., Belov A.~V., Belyakov V.~A., Belyakova T.~F., Gribov Yu.~A.,
Kukhtin V.~P., Lamzin~E.~A., Sytchevsky~S.~E.} Computation technology based on
KOMPOT and KLONDIKE codes for magnetostatic simulations in tokamaks //
Plasma Devices Oper. 2008. Vol.~16. P.~89--103. \\
https://doi.org/10.1080/10519990802018023
\pagebreak

36. {\em Беляков В. А., Сычевский С. Е.} Особенности технологии численного
моделирования электромагнитных полей термоядерных реакторов на основе токамаков //
Известия Рос. академии наук. Энергетика. 2014. №~1. С.~141--149.

37. {\em Розов~В.~Ю., Левина~С.~В.}, Моделирование статического геомагнитного
поля внутри помещений современных жилых домов //
Технична Електродинамiка. 2014. №~4. С.~8--10.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 11 мая 2022~г.

Cтатья принята к~печати 21 июня 2022~г.

\vskip4.5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip1.7mm \textit{Диоп Шейх Ятма} --- аспирант; cheikhyatma@gmail.com

\vskip1.7mm \textit{Капаркова Марина Викторовна} --- kaparkova-sci@yandex.ru

\vskip1.7mm \textit{Кухтин Владимир Петрович} --- канд. физ.-мат. наук, вед. науч. сотр.; kykhtin-sci@yandex.ru

\vskip1.7mm \textit{Макаров Анатолий Александрович} --- makapov@sintez.niiefa.spb.ru

\vskip1.7mm \textit{Родин Игорь Юрьевич} --- канд. техн. наук,
зам. ген. директора по термоядерным и магнитным технологиям;
rodin@sintez.niiefa.spb.su

\vskip1.7mm \textit{Сычевский Сергей Евгеньевич} --- д-р физ.-мат. наук; sytch@sintez.niiefa.spb.su

\vskip1.7mm \textit{Фирсов Алексей Анатольевич} --- firsov-sci@yandex.ru\par


}
