
{\normalsize

\vskip 4.5%6
mm
%\newpage

\noindent{\bf Numerical models for analysis and adjustment of magnetic field in medical\\ centers. I. Simulation of geomagnetic field
disturbances %$^{*}$
 }

}

\vskip 2%3
mm

{\small

\noindent{\it —.~Y. Diop$^{1,2}$, M.~V. Kaparkova$^3$, V.~P. Kukhtin$^3$, A.~A. Makarov$^3$,
I.~Y. Rodin$^3$,\\ S.~E. Sytchevsky$^{1,3}$, A.~A. Firsov$^3$%
%, I.~ќ. Famylia%$\,^2$%

 }

\vskip 2.0%3
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ –абота выполнена в рамках государственного %
%задани€ по теме N 0827-2018-0003 Ђ‘ундаментальные исследовани€ %
%океанологических процессов, определ€ющих состо€ние и эволюцию морской %
%среды под вли€нием естественных и антропогенных факторов, на основе %
%методов наблюдени€ и моделировани€ї.\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation


\noindent%
$^2$~%
Ministry of Health and Social Action, Fann Residence,

\noindent%
\hskip2.45mm%
ul. Aime Cesaire, Dakar, Republic Senegal



\noindent%
$^3$~%
D. V. Efremov Institute of Electrophysical Apparatus, 3, Doroga na Metallostroy, St\,Petersburg,

\noindent%
\hskip2.45mm%
196641, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 1.5%3%
mm


\noindent \textbf{For citation:}  Diop~—.~Y., Kaparkova~M.~V.,
Kukhtin~V.~P., Makarov~A.~A., Rodin~I.~Y., Sytchevsky~S.~E., Firsov~A.~A.
Numerical models for analysis and adjustment of magnetic field in
medical centers. I. Simulation of geomagnetic field disturbances. {\it Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p6}--\pageref{p6e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum06 (In Russian)

\vskip1.5%2
mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent The study investigates possible disturbances of the EarthТs
geomagnetic field  associated with ferromagnetic structures of clinical
buildings. An original methodology has been applied for 3D field mapping
of hospital areas in the Senegalese Radiotherapy (RT) Centre. The RT unit will
be located in a bunker with thick steel walls to ensure safety of patients and
staff. Steel reinforcement will provide the shielding effect lowering the field
level in the therapy room.
A detailed numerical model has been created to simulate an expected field map
in the RT bunker. The model reflects the actual geometry and reinforcement pattern
of the building as well as adopted national standards for hypomagnetic field
environment. The field maps generated with the EM codes KLONDIKE and KOMPOT form
a basis for validation in comparative computations with the other codes
(COMSOL Multiphysics, etc).
\\[1mm]
\textit{Keywords}: EarthТs geomagnetic field, steel magnetization, field simulation.\par}

\vskip4.5%6
mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Rezinkina M.~M., Erisov A.~V., Pelevin D.~E., Lobjanidze L.~E.
Experimentalnoe issledovanie vliyaniya indutsirovannoj i ostatochnoj namagnichennosti
ferromagnitnyh konstruktsij na oslablenie geomagnitnogo polya v zhilyh pometsheniyah
[Experimental researches of influence of induced and residual magnetizing in
ferromagne\-tic constructions on weakening of geomagnetic field in dwellings
apartments]. {\em Vestnik of KharТkov Polytechnical Institute}, 2009, iss.~41, pp.~111--120. (In Russian)

2. Rozov V.~Yu., Zavalnyi A.~V., Zolotov S.~M., Gretskikh S.~V.
Metody normalizatsii staticheskogo geomagnitnogo polyav zhilyh gomah
[The normalization methods of the static geomagnetic field inside houses].
{\em Elektrotekhnika i elektromekhanika} [{\em Electrotechnics and Electromechanics}], 2015, iss.~2, pp.~35--40. (In Russian)

3. Amoskov V.~M., Bazarov A.~M., Belyakov V.~A., Gapionok E.~I., Kaparkova M.~V.,
Kukhtin V.~P., Lamzin E.~A., Lyublin B.~V., Sytchevsky S.~E. Modelling of magnetic
field perturbations in electrophysical devices due to the steel reinforcement
of buildings. {\em Technical Physics}, 2017, vol.~62, no.~10, pp.~1466--1472.\\
https://doi.org/10.1134/S1063784217100048

4. Amoskov V., Bazarov A., Kaparkova M., Kukhtin V., Lamzin E., Lyublin B.,
Belyakov~V., Sytchevsky~S., Gribov~Y. Modeling magnetic effects of steel rebar
of concrete surroundings for electrophysical apparatus.
{\em Proceedings RuPAC}, 2016, THPSC007, pp.~553--555.\\
https://doi.org/10.18429/JACoW-RuPAC2016-THPSC007

5. Amoskov V., Bazarov A., Belyakov V., Gapionok E., Gribov Y., Kaparkova~M.,
Kukhtin~V., Lamzin~E., Lyublin~B., Ovsyannikov~D., Sytchevsky~S.
Calculation of magnetic field from steel rebar of building with machine
producing high stray field. {\em Fusion Eng. Des.}, 2018, vol.~135,
pp.~165--173.\\ https://doi.org/10.1016/j.fusengdes.2018.07.026

6. Official cite of ITER organization. Available at: www.iter.org (accessed: June 26, 2021).

7. Amoskov V.~M., Belov A.~V., Belyakov V.~A., Gapionok E.~I., Gribov Y.~V.,
Kukhtin V.~P., Lam\-zin~E.~A., Mita Y., Ovsyannikov A.~D., Ovsyannikov D.~A.,
Patisson~L., Sytchevsky~S.~E., Za\-vad\-skiy~S.~V. Magnetic model MMTC-2.2
of ITER tokamak complex. {\em Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15,
iss.~1, pp.~5--21.\\
 https://doi.org/10.21638/11702/spbu10.2019.101

8. Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lam\-zin~E.,
Maximenkova~N., Sytchevsky~S. Stray magnetic field produced by ITER Tokamak
Complex. {\em Plasma Devices Oper.}, 2009, vol.~17, no.~4, pp.~230--237.

9. Conley C.~C. {\it A review of the biological effects of very low magnetic fields}.
Report NASA TN D-5902. Washington, D.~C., National Aeronautics and Space Administration Publ., 1970, no.~20546, 25~p.

10. Wang X., Li B., Xu M., Li D., Jiang J. Long-term memory was impaired in one-trial
passive avoidance task of day-old chicks hatching from hypomagnetic field space.
{\em China Sci. Bull.}, 2003, vol.~48, no.~22, pp.~2454--2457. %\\
https://doi.org/10.1360/03wc0231

11. Zhang B., Lu H., Xi W., Zhou X., Xu S., Zhang K., Jiang J., Li Y., Guo A.
Exposure to hypomagnetic field space for multiple generations causes amnesia
in {\it Drosophila melanogaster}. {\em Neuroscience Letters},
2004, vol.~371, no.~2--3, pp.~190--195. %\\
https://doi.org/10.1016/j.neulet.2004.08.072

12. Zhang X., Li J.-F., Wu Q.-J., Li B., Jiang J.
Effects of hypomagnetic field in noradrenergic activities in the brainstem
of golden hamster. {\em Bioelectromagnetics}, 2007, vol.~28, pp.~155--158. \\
https://doi.org/10.1002/bem.20290

13. Binhi V.~N., Prato F.~S. Biological effects of the hypomagnetic field.
An analytical review of experiments and theories. {\em PLoS One}, 2017,
vol.~12, no.~6, pp.~1--51.\\
 https://doi.org/10.1371/journal.pone.0179340

14. Johnson-Groh M., Merzdorf J. NASAТs Goddard Space Flight Center,
Greenbelt.
Available at: %\\
https://www.nasa.gov/feature/nasa-researchers-track-slowly-splitting-dent-in-earth-s-magnetic-field
 (ac\-ces\-sed: August 19, 2020).

15. Ahmad M., Galland P., Ritz T., Wiltschko R., Wiltschko W.
Magnetic intensity affects cryptochrome-dependent responses in {\it Arabidopsis thaliana}.
{\em Planta}, 2007, vol.~225, pp.~615--624.\\
 https://doi.org/10.1007/s00425-006-0383-0

16. Buchachenko A. L., Kuznetsov D. A. Magnetic field affects enzymatic ATP synthesis.
{\em Journal of Amer. Chem. Soc.}, 2008, vol.~130, no.~39, pp.~12868--12869. %\\
https://doi.org/10.1021/ja804819k

17. Hore P.~J. Are biochemical reactions affected by weak magnetic fields?
{\em Proceedings Natl. Acad. Sci. USA}, 2012, January 31, vol.~109, no.~5, pp.~1357--1358. %\\
https://doi.org/10.1073/pnas.1120531109

18. Servick K. Humans --- like other animals --- may sense EarthТs magnetic field.
 {\em Science}, 2019, vol.~363, iss.~6433, pp.~1257--1258. %\\
https://doi.org/10.1126/science.363.6433.1257

19. Sarimov R.~M., Binhi V.~N., Milyaev V.~A. The influence of geomagnetic
field compensation on human cognitive processes. {\em Biophysics}, 2008,
vol.~53, pp.~433--441. \\https://doi.org/10.1134/S0006350908050205

20. Van Huizen A.~V., Morton J.~M., Kinsey L.~J., Von Kannon D.~G., Saad~M.~A.,
Birkholz~T.~R., Czajka~J.~M., Cyrus~J., Barnes~F.~S., Beane~W.~S.
Weak magnetic fields alter stem cell-mediated growth. {\em Science Advances},
2019, vol.~5, iss.~1, Article no.~7201. %\\
https://doi.org/10.1126/sciadv.aau7201

21. Shimojo S., Wu D.-A., Kirschvink J. New evidence for a human magnetic
sense that lets your brain detect the EarthТs magnetic field.
{\it The Conversation}. Available at: https://theconversation.com/new-evidence-for-a-human-magnetic-sense-that-lets-your-brain-detect-the-earths-magnetic-field-113536 (acces\-sed: March 18, 2019).

22. Thoss F., Bartsch B.
The human visual threshold depends on direction and strength of a weak magnetic field.
{\em Journal of Comparative Physiology A}, 2003, vol.~189, pp.~777--779. \\
https://doi.org/10.1007/s00359-003-0450-y

23. Pokhodzey L.~V. Hipogeomagnitnye usloviya kak faktor riska dlya zdoroviya
cheloveka [Hypo\-geo\-magnetic field as health hazard].
{\em Trudy II Mezhdunarodnoi konferentsii ``Elektromagnitnie polia i zdarovie cheloveka''} [{\em Transactions of II Intern. Conference ``Electromagnetic fields and health to means''}].
Moscow, 1999, pp.~135-136.
(In Russian)

24. Nakhilnitzkaya Z.~N., Mastryukova V.~M., Andrianova L.~A., Borodkina A. T.
Reaktsiya organizma na vozdejsvie ``nulevogo'' magnitnogo polya
[Biological response to the ``zero'' magnetic field].
{\em Kosmicheskaya biologiya i aviakosmicheskaya meditsina} [{\it Cosmical Biology and Aviacosmical Medicine}], 1978, no.~2, pp.~74--76. (In Russian)

25. {\it Sanitarno-epidemiologicheskie pravila i normativy}
[{\it National hygienic and sanitary standards and codes}],
SanPiN 2.1.8/2.2.4.2490-09. {\it Elektromagnitnye polya v proizvodstvennyh usloviyah}
[{\it Industrial environment. Electro\-magnetic fields}]. Moscow, Rospotrebnadzor Publ., 2009, 1~p. (In Russian)

26. {\it Sanitarno-epidemiologicheskie pravila i normativy}
[{\it National hygienic and sanitary standards and codes}],
SanPiN 2.1.8/2.2.4.2489-09. {\it Gipogeomagnitnye polya v proizvodstvennyh, zhilyh i
obtshestvennyh zdaniyah i sooruzheniyah}
[{\it Hypomagnetic field in industrial, dwelling and public buildings}].
Moscow, Rospotrebnadzor Publ., 2009, 13~p. (In Russian)

27. Korovkin N., Diop C.~Y. Minimization of electromagnetic fields
intensity and optimization of electrical wiring networks in healthcare facilities.
{\em 2016 IEEE NW Russia Young Researchers in Electrical and Electronic Engineering
Conference (EIConRusNW)}, 2016, pp.~604--607. \\
https://doi.org/10.1109/EIConRusNW.2016.7448255

28. {\it World magnetic model calculator}.
Available at:\\
www.geomag.bgs.ac.uk/data\_service/models\_compass/igrf\_calc.html (accessed: June 26, 2021).

29. Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S. Assessment of error field from ferromagnetic
surrounding of ITER tokamak: ferromagnetic rebar of Tokamak Complex building.
{\em Plasma Devices Oper.}, 2008, vol.~16, no.~4, pp.~225--233. \\
https://doi.org/10.1080/10519990802433875

30. Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S. Stray magnetic field produced by ITER tokamak
complex. {\em Plasma Devices Oper.}, 2009, vol.~17, pp.~230--237. %\\
https://doi.org/10.1080/10519990903043599

31. Amoskov V., Belov A., Belyakov V., Gribov Y., Kavin A., Kukhtin~V.,
Lamzin~E., Lobanov~K., Maximen\-kova~N., Mineev~A., Sytchevsky~S.
Stray magnetic field at plasma initiation produced by ferromagnetic elements
of the ITER Tokamak Complex.
{\em Plasma Devices Oper.}, 2009, vol.~17, no.~4, pp.~238--249. %\\
 https://doi.org/10.1080/10519990903043623

32. Karaush S.~A., Kuznetsov A.~V.
Vliyanie metallicheskih fasadnyh sistem na geomagnitnoe pole vnutri pometshenij
[Effect of metal facade systems on geomagnetic field of indoors].
{\em Vestnik of Tomsk State Architectural and Building University},
2013, vol.~38, no.~1, pp.~83--87. (In Russian)

33. Amoskov V., Belov A., Belyakov V., Gribov Y., Kukhtin V., Lamzin~E.,
Maximenkova~N., Sytchevsky~S. Assesment of error field from solitary
ferromagnetic elements located outside of ITER tokamak.
{\em Plasma Devices Oper.}, 2008, vol.~16, pp.~171--179. %\\
https://doi.org/10.1080/10519990802249289

34. Amoskov V., Gribov Y., Lamzin E., Sythevsky S.
Assessment of $n=1$ ``overlap'' error field produced by localized steel objects
placed at different levels of ITER Tokamak building.
{\em Fusion Eng. Des.}, 2019, vol.~148, Article no.~111271. %\\
https://doi.org/10.1016/j.fusengdes.2019.111271

35. Amoskov V.~M., Belov A.~V., Belyakov V.~A., Belyakova T.~F., Gribov Yu.~A.,
Kukhtin V.~P., Lamzin~E.~A., Sytchevsky~S.~E. Computation technology based on
KOMPOT and KLONDIKE codes for magnetostatic simulations in tokamaks.
{\em Plasma Devices Oper.}, 2008, vol.~16, pp.~89--103. \\
https://doi.org/10.1080/10519990802018023

36. Belyakov V.~A., Sytchevsky S.~E. Osobennosti tekhnologii chislennogo
modelirovaniya elektromagnitnyh polej termoyadernyh reaktorov na osnove tokamakov
[Aspects of EM field simulations for designing, analyzing and optimizing the
tokamak-type fusion reactors].
{\em Izvestiya Rossiiskoi akademii nauk. Energetika} [{\it Proceedings of Russian Academy of Sciences. Energetics}], 2014, no.~1, pp.~141--149.
(In Russian)

37. Rozov V.~Y., Levina S.~V. Modelirovanie staticheskogo geomagnitnogo
polya vnutri pometshenij sovre\-mennyh zhilyh domov
[Modeling of the static geomagnetic field indoor dwelling houses].
{\em Tehnichna Electrodina\-mika}, 2014, no.~4, pp.~8--10. (In Russian)


\vskip1.5mm Received:  May 11, 2022.

Accepted: June 21, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Cheikh Yatma Diop} --- Postgraduate Student; cheikhyatma@gmail.com \par
%
\vskip2mm \textit{Marina V. Kaparkova} ---  kaparkova-sci@yandex.ru \par
%
\vskip2mm \textit{Vladimir P. Kukhtin} --- PhD in Physics and Mathematics, Senior Scientist; kukhtin-sci@yandex.ru \par
%
\vskip2mm \textit{Anatoly A. Makarov} --- makapov@sintez.niiefa.spb.ru \par
%
\vskip2mm \textit{Igor Yu. Rodin} --- PhD in Engineering Sciences, Deputy Director General; rodin@sintez.niiefa.spb.su \par
%
\vskip2mm \textit{Sergey E. Sytchevsky} --- Dr. Sci. in Physics and Mathematics; sytch@sintez.niiefa.spb.su \par
%
\vskip2mm \textit{Alexey A. Firsov} --- firsov-sci@yandex.ru \par
%
%
}
