
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm


1. \it Rivlin R. S., Ericksen J. L. \rm Stress-deformation
relations for isotropic materials~//  Journal of Rational
Mechanics and Analysis. 1955. Vol.~4, N~2. P.~323--425.

2. \it Dunn J. E., Rajagopal K. R. \rm Fluids of differential
type: Critical review and thermodynamic analysis~//  Intern.
Journal of Engineering Science. 1995. Vol.~33, N~5. P.~689--729.

3. \it Dunn J. E., Fosdick R. L. \rm Thermodynamics, stability,
and boundedness of fluids of complexity 2 and fluids of second
grade~// Archive for Rational Mechanics and Analysis. 1974.
Vol.~56. P.~191--252.

4. \it Rajagopal K. R. \rm On some unresolved issues in non-linear
fluid dynamics~// Russian Mathematical Surveys. 2003. Vol.~58,
N~2. P.~319--300.

5. \it Арефьев Н. Н., Штин С. М. \rm Метод определения
реологических характеристик сапропеля~//  Горн. информ.-аналит.
бюл. (науч.-технич. журн.). 2007. №~1. С.~41--47.

6. \it Kazatchkov  I. B.,  Hatzikiriakos S. G. \rm Relaxation
effects of slip in shear flow of linear molten polymers~//
Rheologica Acta.  2010. Vol.~49, N~3. P.~267--274.

7. \it Hatzikiriakos  S. G. \rm Wall slip of molten polymers~//
Progress in Polymer Science. 2012. Vol.~37, N~4.  P.~624--643.

8. \it  Макарова М.~А., Пышнограй И.~Г., Пышнограй Г.~В.,  Алтухов
Ю.~А.,  Головичева И.~Э.,  Трегубова Ю.~Б.,  Третьяков И.~В.,
Афонин Г.~Л.,  Аль Джода Х.~Н.~А. \rm Постановка мезоскопических
граничных условий для скорости проскальзывания на~границе~//
Ползуновский вестник. 2012. №~3-1.\linebreak С.~61--74.

9. \it Ивицкий И. И. \rm Моделирование пристенного скольжения
полимера~// Технологический аудит и~резервы производства. 2014.
Т.~5, №~3~(19). С.~8--11.

10. \it Толстой Д. М. \rm Скольжение жидкостей и~дисперсных систем
по твердым поверхностям: докт. дис. М.: Моск. станкоинструмент.
ин-т, 1953. 349~с.

11. \it Hron J., Le Roux C.,  Malek J.,  Rajagopal K.R. \rm Flows
of incompressible fluids subject to Navier’s slip on the boundary
// Computers and Mathematics with Applications. 2008. Vol.~56.
P.~2128--2143.

12. \it Le Roux C. \rm Existence and uniqueness of the flow of
second-grade fluids with slip boundary conditions~// Archive for
Rational Mechanics and Analysis. 1999. Vol.~148. P.~309--356.

13. \it Busuioc A. V.,  Ratiu T. S. \rm The second grade fluid and
averaged Euler equations with Navier-slip boundary conditions~//
Nonlinearity. 2003. Vol.~16. P.~1119--1149.

14. \it Baranovskii E. S. \rm Existence results for regularized
equations of second-grade fluids with wall slip~// Electronic
Journal of Qualitative Theory of Differential Equations. 2015.
N~91. P.~1--12.

15. \it  Шлихтинг Г. \rm Теория пограничного слоя / пер. с~нем.
Г.~А. Вольперта; под ред. Л.~Г.~Лойцянского. М.: Наука‚ 1974.
712~с. [{\it Schlichting H.} Grenzschicht-Theorie. Karlsruhe:
Verlag, 1951, 483~s.]


\vskip 2mm

{\bf Для цитирования:}  {\it Барановский Е. С., Артемов М. А.}
О~стационарном течении жидкостей второго порядка в~канале~//
Вестник Санкт-Петербургского университета. Прикладная математика.
Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01




}
