{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Rivlin R. S., Ericksen J. L. Stress-deformation relations for
isotropic materials. {\it   Journal of Rational Mechanics and
Analysis}, 1955, vol.~4, no.~2, pp.~323--425.

2. Dunn J. E., Rajagopal K. R. Fluids of differential type:
Critical review and thermodynamic analysis. {\it Intern. Journal
of Engineering Science}, 1995, vol.~33, no.~5, pp.~689--729.

3. Dunn J. E., Fosdick R. L. Thermodynamics, stability, and
boundedness of fluids of complexity 2 and fluids of second grade.
{\it Archive for Rational Mechanics and Analysis}, 1974, vol. 56,
pp.~191--252.

4. Rajagopal K. R. On some unresolved issues in non-linear fluid
dynamics. {\it Russian Mathematical Surveys}, 2003, vol. 58,
no.~2, pp.~319--300.

5. Aref'ev N. N., Shtin S. M.  Metod opredelenija reologicheskih
harakteristik sapropelja [Method for determination of rheological
properties of sapropel]. {\it Gorn. inform.-analit. bjul.
(nauch.-tehnich. zhurn.)} [{\it Mining Informational and
Analytical Bulletin. Scientific and Technical Journal}], 2007,
no.~1, pp.~41--47. (In Russian)

6. Kazatchkov  I. B.,  Hatzikiriakos S. G. Relaxation effects of
slip in shear flow of linear molten polymers. {\it Rheologica
Acta}, 2010, vol.~49, no.~3, pp.~267--274.

7. Hatzikiriakos  S. G. Wall slip of molten polymers. {\it
Progress in Polymer Science}, 2012, vol.~37, no.~4,  pp.~624--643.

8. Makarova M.~A., Pyshnograj I.~G., Pyshnograj G.~V.,  Altuhov
Ju.~A.,  Golovicheva I.~Je.,  Tregubova~Ju.~B.,  Tret'jakov~I.~V.,
Afonin~G.~L.,  Al' Dzhoda~H.~N.~A.  Postanovka mezoskopicheskih
granichnyh uslovij dlja skorosti proskal'zyvanija na granice
[Formulation of mesoscopic boundary conditions for the slip
velocity on the boundary]. {\it Polzunovsky Vestnik} [{\it
Polzunovsky Journal}], 2012, no.~3-1, pp.~61--74. (In Russian)

9. Ivickij I. I. Modelirovanie pristennogo skol'zhenija polimera
[Modeling of wall slip of polymers].  {\it Tehnologicheskij audit
i rezervy proizvodstva} [{\it Technology Audit and Production
Reserves}], 2014, vol.~5, no.~3~(19), pp.~8--11. (In Russian)

10. Tolstoy D. M. {\it Skol'zhenie zhidkostej i dispersnyh sistem
po tverdym poverhnostjam} [{\it Slipping liquids and disperse
systems on solid surfaces}]. Doct. dis. Moscow, Moscow
Machine-Instrument Institute, 1953, 349~p. (In Russian)

11. Hron J., Le Roux C.,  Malek J.,  Rajagopal K. R. Flows of
incompressible fluids subject to Navier’s slip on the boundary.
{\it Computers and Mathematics with Applications}, 2008, vol.~56,
pp.~2128--2143.

12. Le Roux C. Existence and uniqueness of the flow of
second-grade fluids with slip boundary conditions. {\it Archive
for Rational Mechanics and Analysis}, 1999, vol.~148,
pp.~309--356.

13. Busuioc A. V.,  Ratiu T. S. The second grade fluid and
averaged Euler equations with Navier-slip boundary conditions.
{\it Nonlinearity}, 2003, vol.~16, pp.~1119--1149.

14. Baranovskii E. S. Existence results for regularized equations
of second-grade fluids with wall slip. {\it Electronic Journal of
Qualitative Theory of Differential Equations}, 2015, no.~91,
pp.~1--12.

15. Schlichting H. {\it Grenzschicht-Theorie} [{\it Boundary-layer
theory}]. Karlsruhe, Verlag Publ., 1951, 483~s. (Russ. ed.:
Schlichting H. {\it Teorija pogranichnogo sloja}. Moscow, Nauka
Publ., 1974, 712~p.)





\vskip 2mm

{\bf For citation:}  Baranovskii E. S., Artemov M. A. Steady flows
of second-grade fluids in a channel. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
