

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Gasymov M.~G., Levitan B.~M.  Opredelenie differencial'nogo
operatora po dvum spektram [Definition of a differential operator
from two spectrums]. \emph{Uspekhi matematicheskikh nauk
$[$Russian Mathematical Surveys$]$}, 1964, vol.~19, iss.~2~(116),
pp.~3--63. (In Russian)

2. Levitan B.~M., Sargsyan I.~S. \emph{Vvedenie v spektral'nuyu
teoriyu} [\textit{Introduction to spectral theory}]. Moscow, Nauka
Publ., 1970, 672~p. (In Russian)

3. Levitan B.~M. \emph{Teoriya operatorov obobschennogo sdviga}
[\textit{Theory of generalized shift operators}]. Moscow, Nauka
Publ., 1973, 312~p. (In Russian)

4. Yurko V.~A. Obratnaya zadacha dlya differentsial'nyh uravneniy
s osobennost'yu [The inverse problem for differential equations
with singularity]. \emph{Differentsial'niye uravnenia
$[$Differential equations$]$}, 1992, vol.~28, iss.~8,
pp.~1355--1362. (In Russian)

5. Yurko V.~A. O vosstanovlenii differencial'nyh operatorov
Shturma---Liuvillya s osobennost'yu vnutri intervala [On the
reconstruction of the Sturm---Liouville differential operators
with a feature inside the interval]. \emph{Matematicheskie zametki
$[$Mathematical Notes$]$}, 1998, vol.~64, iss.~1, pp.~143--156.
(In Russian)

6. Yurko V.~A. O kraevyh zadachah s usloviyami razryva vnutri
intervala [On boundary value problems with discontinuity
conditions inside the interval]. \emph{Differentsial'niye
uravnenia $[$Differential equations$]$}, 2000, vol.~36, iss.~8,
pp.~1139--1140. (In Russian)

7. Yurko V.~A. \emph{Vvedenie v teoriyu obratnih spektral'nih
zadach} [\textit{Introduction to the theory of inverse spectral
problems}]. Moscow, Fizmatlit Publ., 2007, 384~p. (In Russian)

8. Provotorov V.~V., Volkova A.~S.  \textit{Nachal'no-kraevie
zadachi s raspredelennimi parametrami na grafe} [\textit{Initial
boundary value problems with distributed parameters on the
graph}]. Voronezh, Nauchnaya kniga Publ.,  2014,  188~p. (In
Russian)

9. Vladimirov V.~S. \textit{Uravneniya matematicheskoi fiziki}
[\textit{Equations of mathematical physics}]. Moscow, Nauka Publ.,
1971, 512~p. (In Russian)

10. Provotorov V. V. \textit{Sobstvennye funktsii kraevyh zadach
na grafah i prilozheniya} [\textit{Eigenfunctions of boundary
value problems on graphs and applications}]. Voronezh, Nauchnaya
kniga Publ., 2008, 247~p. (In Russian)

11. Avdonin S., Murzabekova G., Nurtazina K. Source identification
for the differential equation with memory. \textit{Trends in
Mathematics. Research Perspective}. Birkh$\ddot {\rm a}$user,
Springer International Publishing Switzerland, 2017, pp.~111--120.

12. Avdonin S., Kurasov P. Inverse problems for quantum trees.
\textit{Inverse Problems Imag.}, 2008, vol.~2, iss.~1.
pp.~3973--3991.

13. Avdonin S., Bell J., Nurtazina K. Determining distributed
parameters in a neuronal cable model on a tree graph.
\textit{Mathematic Methods in the Applied Sciences}, 2017,
vol.~40, iss.~11, pp.~3973--3991.

14. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

15. Bieberbach L. \textit{Analiticheskoe prodolzenie
}[\textit{Analytical continuation}]. Moscow, Nauka Publ., 1967,
240~p. (In Russian)

16. Karelin V.~V., Bure V.~M., Svirkin M.~V. Obobchennaja model
rasprostranenija informacii v neprerivnom vremeni [The generalized
model of information dissemination in continuous time].
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~1, pp.~74--80. https://doi.org/10.21638/11701/spbu
10.2017.107 (In Russian)


17. Aliseiko A. N. Matricy Lyapunova dlya klassa sistem s
eksponencial'nym yadrom [Lyapunov matrices for a class of systems
with an exponential core]. \textit{Vestnik of Saint Petersburg
Universi\-ty. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~3, pp.~228--240.
https://doi.org/10.21638/11701/spbu 10.2017.301 (In Russian)


18. Avdonin S., Edward J.  Exact controllability for string with
attached masses. \textit{SIAM J. Control Optim}, 2018, vol.~56,
iss.~2, pp.~945--980. https://doi.org/10.1137/15M1029333

19. Provotorov V.~V.,  Ryazhskikh V.~I., Gnilitskaya Yu.~A. Unique
weak solvability of a nonlinear initial boundary value problem
with distributed parameters in a netlike region. \textit{Vestnik
of Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2017, vol.~13, iss.~3, pp.~264--277.
https://doi.org/10.21638/11701/spbu10.2017.304

20. Zhabko A.~P., Tikhomirov O.~G., Chizhova O.~N. On
stabilization of a class of systems with time proportional delay.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2018, vol.~14,
iss.~2, pp.~165--172.
https://doi.org/10.21638/11702/spbu10.2018.209

21. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredelennymi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \textit{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224.
https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)

22. Provotorov V.~V., Provotorova E.~N.  Optimal control of the
linearized Navier---Stokes system in a netlike domain.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~4, pp.~428--441.
https://doi.org/10.21638/11701/spbu10.2017.409

23. Ponomarev A.~A. Approksimaciya obratnoi svyazi v regulyatore
``predictor---corrector'' yavnoi funkcii [Approximation of
feedback in the ``predictor---corrector'' regulator by an explicit
function]. \textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~2, pp.~193--208. https://doi.org/10.21638/11701/spbu
10.2017.206  (In Russian)

24. Kuptsova S.~E., Kuptsov S.~Yu., Stepenko N.~A. On the limiting
behavior of a time-delay system's solution. \textit{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2018, vol.~14, iss.~2, pp.~173--182.
https://doi.org/10.21638/11702/spbu10.2018.2010

25. Iliashenko O., Krasnov S., Sergeev S. Calculation of high-rise
construction limitations for non-resident housing fund in
megacities. \emph{E3S Web of Conferences.  International
Scientific Conference on High-Rise Construction, HRC}, 2018,
vol.~33, iss.~6, paper no. 030062017, pp. 03006.

26. Artemov M.~A.,  Baranovskii E.~S.,  Zhabko A.~P.,  Provotorov
V.~V. On a 3D model of non-isothermal flows in a pipeline network.
\emph{Journal of Physics: Conference Series}, 2019, vol.~1203,
Article ID 012094. https://doi.org/10.1088/1742-6596/1203/1/012094


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  May 15, 2019.

Accepted: June 06, 2019.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Aleksei~P.~Zhabko} --- Dr. Sci. in Physics and
Mathematics, Professor; zhabko.apmath.spbu@mail.ru

\vskip2mm\textit{Karlygash B. Nurtazina} ---  PhD in  Physics and
Mathematics, Associate Professor; knurtazina@mail.ru

\vskip2mm\textit{Vyacheslav~V.~Provotorov} --- Dr. Sci. in Physics
and Mathematics, Professor; wwprov@mail.ru

}
