
{\normalsize

\vskip 6mm

\noindent{\bf Improving the efficiency of decision-making during emergency situations\\ in cyberphysical distributed production systems%$^*$%
}

}

\vskip 2mm

{\small

\noindent{\it D. V. Shelkovyy$^{1}$, O. Yu. Sivchenko$^{2}$, E. E. Usina$^{2}$, A. N. Bykov$^{2}$%
%, I.~Î. Famylia%$~^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%%\vspace{-3mm}%
%\parindent=7mm
%%
%%\vskip 0.0mm
%\hskip 4mm$^{*}$ This work was supported by the Russian Science% %Foundation (project N~19-11-00223).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
Russian Federation Security Guard Service Federal Academy,

\noindent%
\hskip2.45mm%
35,~Priborostroitel'naya ul., Orel, 302015, Russian Federation


\noindent%
$^2$~%
St. Petersburg Federal Research Center of the Russian Academy of Sciences,

%\noindent%
%\hskip2.45mm%
%St. Petersburg Institute for informatics and automation of the Russian Academy of Sciences,

\noindent%
\hskip2.45mm%
39, 14-ia linia V. O., St. Petersburg, 199178, Russian Federation


%\noindent%
%$^2$~%
%St.~Petersburg State University, 7--9, Universitetskaya nab.,
%St.~Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:}   Shelkovyy D. V., Sivchenko O.
Yu., Usina E. E., Bykov A. N. Improving the efficiency of
decision-making during emergency situations in cyberphysical
distributed production systems. {\it Vestnik of Saint~Peters\-burg
Uni\-versity. Applied Mathematics. Computer Science. Control
Processes}, \issueyear,
vol.~17, iss.~\issuenum, pp.~\pageref{p7}--\pageref{p7e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum07  (In Russian)

\vskip2.0%3
mm

{\leftskip=7mm\noindent This paper presents results of approbation of existing mathematical models, enabling operative assessment of the required link resource to serve data streams, generated by the elements of technical vision subsystem in cyberphysical distributed production systems. Simulation experiments allowed to discover dependencies between achievable multimedia traffic packet processing delay in switching systems and link-level resource, reserved for respective data transfer. Obtained dependencies are to be used during design of algorithm for link resource control for increasing speed of decision making in emergency.\\[1mm]
\textit{Keywords}: link resource, quality of service, sensory system, cyberphysical system, distributed production system, operational efficiency, emergency.
\par}

\vskip 4.5%6
mm

\noindent \textbf{References} }

\vskip 1.8%2
mm

{\footnotesize

1. Abreu J. Business processes improvement on maintenance management: A case study. \textit{Procedia Technology}, 2013, vol.~9, pp.~320--330.

2. Fleischmann H., Kohl J., Franke J., Reidt A. Improving maintenance processes with distributed monitoring systems. \textit{13-th International Conference on Industrial Informatics}, 2016, vol.~13, pp.~377--382.

3. Yin S., Kaynak O. Big data for modern industry: Challenges and trends. \textit{Proceedings of IEEE}, 2015, vol.~103, no.~2, pp.~143--146.

4. Kranzer S. An intelligent maintenance planning framework prototype for production systems. \textit{18-th Annual International Conference on Industrial Technology. Proceedings of IEEE}, 2017, pp.~1124--1129.

5. Vatamaniuk I. V., Iakovlev R. N. Obobshchennye teoreticheskie
modeli kiberfizicheskih system [Generalized theoretical models of
cyberphysical systems]. \textit{Izvestiya Iugo-Zapadnogo
gosudarstvennogo universiteta} [\textit{Proceedings of the
Southwest State University}], 2019, vol.~23, no.~6, pp.~161--175.
(In Russian)

6. Osborne E. D., Simha A. \textit{Traffic engineering with MPLS}.
Moscow, Cisco Press, 2003, 608~p.%\pagebreak

7. Calinescu R. C., Camara Moreno J., Paterson C. Socio-cyber-physical systems: models, op\-por\-tu\-ni\-ties, open challenges. \textit{5-th International Workshop on Software Engineering for Smart Cyber-Phy\-si\-cal Sys\-tems}. York, 2019, pp.~2--6.

8. Levakov A., Sokolov A., Sokolov N. Models of incoming traffic in packet networks. \textit{T-Comm.}, 2015, vol.~9, no.~5, pp.~91--94.

9. Shelkovyy D. V. Model' uzla kommutatsii korporativnoj mul'tisensornoj seti svyazi [The model company multiservice network node model].  \textit{Nauchnye vedomosti Belgorodskogo gosudarstvennogo universiteta. Ekonomika. Informatika} [\textit{Scientific of lists of Belgorod State University. Economics. Informatics}], 2017, no.~42, pp.~148--157. (In Russian)

10. Gama J. On evaluating stream learning algorithm.
\textit{Machine Learning}, 2013, vol.~90, iss.~3, pp.~317--346.

11. Millan G., Lanfranc G. A fast multifractal model for self-similar traffic flows in high-speed computer networks. \textit{Procedia Computer Science}, 2013, vol.~17, pp.~420--425.

12. Shelkovyy D. V., Mironov O. Y., Basov O. O. Modelirovanie potokov dannykh real'nogo vremeni v zashhishhennykh korporativnykh mul'tiservisnykh setyakh svyazi na osnove determinirovannogo setevogo ischisleniya [The real-time data streams modelling in secure corporate multiservice communication networks by application of deterministic network calculus theory]. \textit{Nauchnye vedomosti Belgorodskogo gosudarstvennogo universiteta} [\textit{Scientific of lists of Belgorod State University. Economics. Informatics}], 2018, vol.~45, no.~3, pp.~584--594. (In Russian)

13. Kuchuk G. A. Metod operativnoj otsenki statisticheskikh kharakteristik agregirovannogo trafika [Method of the aggregated traffic statistical descriptions operative estimation]. \textit{Àviatsionno-kosmicheskaya tekhnika i tekhnologiya. Nauchno-tekhnicheskij zhurnal} [\textit{Aerospace engineering and technology. Scientific and technical Journal}]. Khar'kov, 2013, no.~7, pp.~211--214. (In Russian)

14. Vegesna S. \textit{IP quality of service}. Moscow, Cisco
Press, 2001, 368~p. (Russ. ed.: Vegesna S. \textit{Kachestvo
obsluzhivaniya v setyah IP}. Moscow, Izdat. Dom ``Vill'ams’’
Publ., 2003, 368~p.)

15. Nguen T. Formal requirements modeling for simulation-based verification. \textit{11-th International Modelica Conference}, 2015, pp.~622--635.



16. {\it Rekomendatsiya MSEH-T Y. 1541. Trebovaniya k setevym
pokazatelyam kachestva dlya sluzhb, osnovannykh na protokole IP.
Seriya Y. Global'naya informatsionnaya infrastruktura, aspekty
mezhsetevogo protokola i seti posleduyushhikh pokolenij}. [{\it
ITU-T Recommendation. Y. 1541. Re\-qui\-re\-ments for network
performance indicators for IP-based services. Series Y. Global
information in\-fra\-struc\-ture, aspects of the internetwork
protocol and the next-generation network}]. ITU, 2011.

17. Kireeva N. V., Chupakhina L. R., Karaulova O. A. Àpproksimatsiya multicast trafika s pomoshh'yu uravneniya Lindli [Approximation of the multicast traffic by using the lindley equation]. \textit{Mezhdunarodnyj zhurnal prikladnykh i fundamental'nykh issledovanij} [{\it International Journal of Applied and Basic Research}], 2017, no.~4--2, pp.~313--317. (In Russian)

18. Levonevskij D. K., Vatamanyuk I. V., Malov D. À. Obespechenie dostupnosti servisov korporativnogo intellektual'nogo prostranstva posredstvom upravleniya potokom vkhodnykh dannykh [Ensuring the availability of corporate intellectual space services by controlling the flow of input data]. \textit{Programmnaya inzheneriya} [{\it Software engineering}], 2019, vol.~10, no.~1, pp.~20--29. https://doi.org/10.17587/prin.10.20-29 (In Russian)

19. Malov D. À., Edemskij À. Y., Savel'ev À. I. Razrabotka sistemy proaktivnoj lokalizatsii kiberfizicheskogo prostranstva na osnove metodov mashinnogo obucheniya [Development of a proactive cyber-physical localization system based on machine learning methods]. \textit{Informatsionnye tekhnologii i vychislitel'nye sistemy} [{\it Information technology and computing systems}], 2018, no.~4, pp.~72--83. https://doi.org/10.14357/20718632180408 (In Russian)



\vskip 1.5mm

Received:  August 28, 2020.

Accepted: January 15, 2021.


\vskip6 mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:


\vskip2 mm \textit{Denis V. Shelkovyy} --- shelkoydenis@mail.ru

\vskip2 mm \textit{Oleg Yu. Sivchenko} --- oleg.sivchenko@yandex.ru

\vskip2 mm \textit{Elizaveta E. Usina} --- Junior Scientific Collaborator; lizzzi96@mail.ru

\vskip2 mm \textit{Àleksandr N. Bykov} --- 124alex.96@mail.ru\par
%
}
