

{\footnotesize

\vskip 2mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 1.5mm



1. {Bure~V.~M.} Metodologicheskie aspekty statisticheskogo analiza
v tochnom zemledelii [Methodological aspects of statistical
analysis in precision agriculture]. {\it Russian Agricultural
Sciences,} 2007, no.~6, pp.~54--56. (In Russian)

2. { Mitrofanova~O.~A., Bure~V.~M., Kanash~E.~V.} Matematicheskii
modul' dlia avtomatizatsii kolorimetricheskogo metoda otsenki
obespechennosti rastenii azotom [Mathematical module to automate
the colorimetric method for estimating nitrogen status of plants].
{\it Vestnik of Saint Petersburg University. Series~10. Applied
mathematics. Computer science. Control processes}, 2016, issue~1,
pp.~85--91. (In Russian)

3. {Yakushev~V.~P., Bure~V.~M.} Otsenka bioekvivalentnosti dvukh
uchastkov na sel'skokhoziaistvennom pole [Approach to evaluating
bioequivalence of two plots on an agricultural field]. {\it
Russian Agricultural Sciences,} 2006, no.~5, pp.~38--40. (In
Russian)

4. {Dem'ianov~V.~V., Savel'eva~E.~A.} {\it Geostatistika: teoriia
i praktika} [{\it Geostatistics: theory and practice}]. Moscow,
Nuclear Safety Institute of the Russian Academy of Sciences, Nauka
Publ., 2010, 327~p. (In Russian)

5. {Bure~V.~M.} Metodologiia primeneniia binarnoi regressii v
tochnom zemledelii [Methodology of using binary regression in
precision agriculture]. {\it Poluektov's readings}, 2014,
pp.~118--121. (In Russian)

6. {Yakushev~V.~P., Bure~V.~M., Parilina~E.~M.} {\it Binarnaia
regressiia i ee primenenie v agrofizike} [{\it Binary regression
and its application in agrophysics}]. Saint Petersburg, Agrophys.
Institute Publ., 2015, 36~p. (In Russian)

7. { Fernandes~G.~B., Artes~R.} Spatial dependence in credit risk
and its improvement in credit scoring. {\it European J. of
Operational Research,} 2016, no.~249, pp.~517--524.

8. {Bure~V.~M., Parilina~E.~M. } {\it Teoriia veroiatnostei i
matematicheskaia statistika} [{\it Probability theory and
mathematical statistics}]. Saint Petersburg, Lan' Publ., 2013,
416~p. (In Russian)




\vskip 2mm

{\bf For citation:} Bure V.~M.,~Mitrofanova O.~A. Prediction of
the spatial distribution of ecological data\linebreak using
kriging and binary regression. {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathema-\linebreak tics. Computer
science. Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10.\issueyear.\issuenum09



}
