

{\small



\vskip4.5mm%6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Beyrer C., Wirtz A. L., O’Hara G., L\'eon N., Kazatchkine M.
The expanding epidemic of HIV-1 in the Russian Federation. {\it
PLoS Med}, 2017, vol.~14(11), pp.~1002462. \\
https://doi.org/10.1371/journal.pmed.1002462

2. Gosudarstvennyy doklad ``O sostoyanii
sanitarno-epidemiologicheskogo blagopoluchiya naseleniya v
Rossiyskoy Federatsii v 2018 godu'' [State report ``On the state
of the sanitary-epidemiological well-being of the population in
the Russian Federation in 2018'']. {\it Russian Federal Service
for Surveillance on Consumer Rights Protection and Human Wellbeing
(Rospotrebnadzor)}, 2018, pp.~116--120. (In Russian)

3. Gupta~R.~K., Abdul-Jawad~S., McCoy~L.~E. et al. HIV-1 remission
following CCR5$\Delta$ 32/$\Delta$32 haematopoietic stem-cell
transplantation. {\it Nature}, 2019, vol.~568, pp.~244--248.

4.  Kermack~W.~O., McKendrick~A.~G. A Contribution to the
mathematical theory of epidemics. {\it Proceedings of the Royal
Society}, 1927, pp.~700--721.

%\bibitem{sirsol}
5. Harko~T., Lobo~F.~S.~N., Mak~M.~K. Exact analytical solutions
of the Susceptible-Infected-Recovered (SIR) epidemic model and of
the SIR model with equal death and birth rates. {\it Applied
Mathematics and Computation}, 2014, no.~236, pp.~184--194.

%\bibitem{mseir}
6.  Hethcote H. The mathematics of infectious diseases. {\it SIAM
Review}, 2000, no.~42(4), pp.~599--653.

%\bibitem{kolzhid}
7.  Kolesin~I.~D., Zhitkova~E.~M. {\it Matematicheskiye modeli
epidemiy $[$Mathematical models of epidemics$]$}. Saint
Petersburg, Solo  Publ.,~2004, 90~p. (In Russian)

%\bibitem{nos}
8. Nosova E. A.  Models of control and spread of HIV-infection.
{\it Mathematical biology and bioinformatics}, 2012, vol.~7.2,
pp.~632--675. https://doi.org/10.17537/2012.7.632


9.  Babadzanjanz L. K., Boyle J. A., Sarkissian D. R., Zhu J.
Parameter identification for oscillating chemical reactions
modelled by systems of ordinary differential equations. {\it
Journal of Computational Methods in Sciences and Engineering},
2003, vol.~3, no.~2, pp.~223–232.

10. {\it World Health Organization.} Available at: \\
https://www.who.int/news-room/fact-sheets/detail/hiv-aids
 (ac\-ces\-sed: August 10, 2019).

11. {\it UNAIDS.  Ambitious  treatment  targets:  writing  the
final chapter of the AIDS epidemic}. Geneva, UNAIDS Publ., 2014.
Available at:\\
%
https://www.unaids.org/sites/default/files/media$\_$asset/JC2670$\_$UNAIDS$\_$Treatment$\_$Targets$\_$en.pdf
 (accessed: August 10, 2019).

12. {\it Rasporyazheniye Pravitel'stva RF ot 20 oktyabrya 2016 g.,
no.~2203-r ``O Gosudarstvennoy strategii protivodeystviya
rasprostraneniyu VICH-infektsii v RF na period do 2020 g. i
dal'neyshuyu perspektivu'' $[$Decree of the Government of the
Russian Federation of October 20, 2016, no.~2203-r ``On the state
strategy for counteracting the spread of HIV Infection in the
Russian Federation for the period until 2020 and the future''$]$}.
Available at:\\
http://static.government.ru/media/files/cbS7AH8vWirXO6xv7C2mySn1JeqDIvKA.pdf
 (accessed: August 10, 2019). (In Russian)



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 21, 2019.

Accepted: November 07, 2019.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 1.5mm%2mm
\textit{Sergei V. Sokolov} --- PhD in Physics and Mathematics,
Associate Professor; s.sokolov@spbu.ru

\vskip 1.5mm%2mm
\textit{Alexandra L. Sokolova} --- Master; alsokolova@etu.ru

}
