
{\normalsize

\vskip 4mm%6mm

\noindent{\bf Analysis of the phase structure of fluid vibrations
with floating\\ longitudinally compressed elastic plate in
nonlinear
interaction\\ of the surface progressive waves$^*$%
}

}

\vskip 2mm

{\small

\noindent{\it A.~A.~Bukatov%$~^1$%
%, I.~Î. Famylia%$~^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.0mm
\hskip 4mm$^{*}$ This work is carried out within the framework of the State Order N~0827-2019-0003.%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%óíèâåðñèòåò, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
Marine Hydrophysical Institute of the Russian Academy of Sciences,
2, Êàpitanskaya ul., Sevastopol,

\noindent%
%\hskip2.45mm%
299011, Russian Federation


%\noindent%
%$^2$~%
%St.~Petersburg State University, 7--9, Universitetskaya nab.,
%St.~Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:}   Bukatov A. A. Analysis of the
phase structure of fluid vibrations with floating longitudinally
compressed elastic plate in nonlinear interaction of the surface
progressive waves. {\it Vestnik of Saint~Peters\-burg
Uni\-versity. Applied Mathematics. Computer Science. Control
Processes}, \issueyear,
vol.~16, iss.~\issuenum, pp.~\pageref{p1}--\pageref{p1e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum01  (In Russian)

\vskip2.0%3
mm

{\leftskip=7mm\noindent Based on the asymptotic expansions
obtained by the multi-scale method up to the third order of
smallness for the potential velocity of liquid particles and the
plate-fluid surface elevation, the dispersion properties of the
vibrations generated by the interaction of progressive surface
wave harmonics of finite amplitude are analyzed in the article.
The effect of nonlinearity of acceleration of vertical
displacements of an elastic plate on the dispersion
characteristics of wave disturbances is studied. The dependence of
the vibration frequency is estimated by taking into account the
nonlinearity of the first and second approximations values, the
plate thickness, and the longitudinal compressive force. It is
shown that the sign of the amplitude of the second interacting
harmonic and the nonlinearity of the acceleration of vertical
displacements of the longitudinally compressed elastic plate
affect the vibration phase. It was found that with a decrease in
the wavelength of the initial harmonic, the influence of the
plate's nonlinearity vertical acceleration is enhanced. The
presence of compressive force is manifested in a decrease in the
frequency of vibrations of the wave disturbance in comparison with
the frequency obtained in the absence of longitudinal compression,
both with a positive and negative sign
of the second interacting harmonic amplitude.\\[1mm]
\textit{Keywords}: ice plate fluctuations, waves of finite
amplitude, nonlinear interaction of waves, flexural deformation of
a plate, longitudinal compressive force, phase characteristics.
\par}

\vskip 4.5%6
mm

\noindent \textbf{References} }

\vskip 1.8%2
mm

{\footnotesize

1. Kheisin D.~E. Nestatsionarnaya zadacha o kolebaniyakh
beskonechnoy plastinki, plavayushchey na poverkhnosti ideal'noy
zhidkosti [Nonstationary problem of infinite plate fluctuations
floating on the ideal fluid surface]. \textit{Izvestiya AN SSSR.
Mekhanika i Mashinostroyenie} [\textit{News of AN USSR. Mechanics
and Machine-building}], 1962, no.~1, pp.~163--167. (In Russian)

2. Bukatov A.~E., Cherkesov L.~V. Transient vibrations of an
elastic plate floating on a liquid surface. \textit{Intern. Appl.
Mechanics}, 1970, vol.~6, no.~8, pp.~878--883. %\\
https://doi.org/10.1007/BF00889434

3. Tkachenko V.~A., Yakovlev V.~V. Unsteady bending-gravitational
waves in fluid-plate system. \textit{Intern. Appl. Mechanics},
1984, vol.~20, no.~3, pp.~266--271.
https://doi.org/10.1007/BF00883145\pagebreak

4. Daffy D.~G. The response of floating ice to a moving, vibrating
load. \textit{Cold Regions Science and Technology}, 1991, vol.~20,
pp.~51--64. https://doi.org/10.1016/0165-232X(91)90056-M

5. Squire V.~A., Hosking R.~J., Kerr A.~D., Langhorne P.~J. {\it
Moving loads on ice plates.} Dordrecht, Kluwer Acad. Publ., 1996,
236~p. https://doi.org/10.1007/978-94-009-1649-4

6. Sturova I.~V. Wave generation by an oscillating submerged
cylinder in the presence of a floating semi-infinite elastic
plate. \textit{Fluid Mech.}, 2014, vol.~49, no.~4, pp.~504--514.
https://doi.org/10.1134/S0015462814040103

7. Batyaev E.~A., Khabakhpasheva T.~I. Hydroelastic waves in a
channel covered with a free ice sheet. \textit{Fluid Mech.}, 2015,
vol.~50, no.~6, pp.~775--788.
https://doi.org/10.1134/S0015462815060071

8. Bukatov A.~E. Effect of longitudinal compression on transient
vibrations of an elastic plate floating on the surface of a
liquid. \textit{Intern. Appl. Mechanics}, 1981, vol.~17, no.~1,
pp.~75--79.\\ https://doi.org/10.1007/BF00885650

9. Pozhuev V.~I., Polyakova N.~P. {Nestatsionarnaya zadacha o
vozdejstvii podvizhnoj nagruzki na ledyanoj pokrov}
[{Nonstationary problem about effect of a moving load on an ice
cover}]. \textit{Stroitelnay mekhanica i raschet sooruzheniy}
[\textit{Structural mechanics and calculation of structures}],
1990, no.~6, pp.~46--50. (In Russian)

10. Bukatov A.~E., Zharkov V.~V. Formation of the ice cover’s
flexural oscillations by action of surface and internal ship
waves. Pt~1. Surface waves. \textit{Intern. J. Offshore and Polar
Engineering}, 1997, vol.~7, no.~1, pp.~1--12.

11. Kerr A.~D. The critical velocities of a moving on a floating
ice plate that is subjected to in-plane forces. \textit{Cold
Regions Science and Technology}, 1983, vol.~6, pp.~267--276.

12. Schulkes R.~M.~S.~M., Hosking R.~J., Sneyd A.~D. Waves due to
a steadily moving source on a floating ice plate. Pt~2. \textit{J.
Fluid Mech.}, 1987, vol.~180, pp.~297--318.\\
https://doi.org/10.1017/S0022112087001812

13. Bukatov A.~E., Bukatov A.~A. Propagation of surface wave of
finite amplitude in a basin with floating broken ice.
\textit{Intern. J. Offshore and Polar Engineering}, 1999, vol.~9,
no.~3, pp.~161--166.

14. Gladunand O.~M., Fedosenko V.~S. Nonlinear steady-state
oscillations of an elastic plate floating on the surface of a
liquid of finite depth. \textit{Fluid Mech.}, 1989, vol.~24,
no.~3, pp.~448--455.\\ https://doi.org/10.1007/BF01051589

15. Gol’dshtein R.~V., Marchenko A.~V. O dlinnykh volnakh v
sisteme ledianoi pokrov---zhidkost pri nalichii ledovogo szhatiia
[{Long waves in the ice–fluid system subject to ice pressure}].
 \textit{Electrical and Mechanical Properties of Ice}. Collection
of scientistic work of AANII. Leningrad, Gidrometeoizdat Publ.,
1989, pp.~188--205. (In Russian)

16. Il’ichev A.~T. Soliton-like structures on a water-ice
interface. \textit{Russian Mathematical Surveys}, 2015, vol.~70,
no.~6, pp.~1051--1103.
https://doi.org/10.1070/RM2015v070n06ABEH004974

17. Bukatov A.~E., Bukatov A.~A. Finite-amplitude waves in a
homogeneous fluid with a floating elastic plate. \textit{ J. Appl.
Mech. Tech. Phys.}, 2009, vol.~50, no.~5, pp.~785--791.\\
https://doi.org/10.1007/s10808-009-0107-x

18. Bukatov A.~E., Bukatov A.~A. Nonlinear oscillations of a
floating elastic plate. \textit{Intern. Appl. Mechanics}, 2011,
vol.~46, no.~10, pp.~1139--1146.
https://doi.org/10.1007/s10778-011-0406-9

19. Bukatov A.~E., Bukatov A.~A. Interaction of surface waves in a
basin with floating broken ice. \textit{Physical Oceanography},
2003, no.~6, pp.~313--332.
https://doi.org/10.1023/B:POCE.0000013230.35798.a4

20. Bukatov A.~E., Bukatov A.~A. Phase structure of fluid
fluctuations with a floating elastic ice plate under nonlinear
interaction of progressive surface waves. \textit{Physical
Oceanography}, 2018, [e-journal] vol.~25(1), pp.~3--17.
https://doi.org/10.22449/1573-160X-2018-1-3-17

21. Bukatov A.~A. Nonlinear vibrations of a floating
longitudinally compressed elastic plate in the interaction of wave
harmonics of finite amplitude. \textit{Fluid Dynamics}, 2019,
vol.~54, no.~2, pp.~194--204.
https://doi.org/10.1134/S0015462819020046

22. Nayfeh A.~H. \textit{Perturbation methods}. New York,
Wiley--Interscience Publ., 1973 (Russ. ed.: Nayfeh~A.~N. {\it
Metody vozmushchenii}. Moscow, Mir Publ., 1976, 455~p.)

23. Kheisin D.~Y.  {\it Dinamika ledianogo pokrova}
 [\textit{Dynamics of floating ice covers}]. Leningrad,
Gid\-ro\-me\-teoiz\-dat Publ., 1967, 215~p. (In Russian)


\vskip 1.5mm

Received:  January 20, 2020.

Accepted: August 13, 2020.


\vskip5%6
mm A~u~t~h~o~r'~s \ i~n~f~o~r~m~a~t~i~o~n:

\vskip1.5%2
mm \textit{Anton A. Bukatov} --- PhD in Physics and
Mathematics; newisland@list.ru
%
}
