
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1.\emph{Olemskoy~I.~V.} Fifth-order four-stage method for
numerical integration of spe\-ci\-al sys\-tems~// Comput. Math.
Math. Phys. 2002. Vol.~42. P.~1135--1145.

2. \emph{Olemskoy~I.~V.} Structural approach to the design of
explicit one-stage methods // Comput. Math. Math. Phys. 2003.
Vol.~43. P.~918--931.

3. \emph{Олемской~И.~В.} Модификация алгоритма выделения
структурных особенностей~// Вестн. \mbox{С.-Петерб.} ун-та. Сер.
10. Прикладная математика. Информатика. Процессы управления. 2006.
Вып.~2. С.~55--64.

4. \emph{Olemskoy~I.~V., Eremin ~A.~S., Ivanov A. P.} Sixth order
method with six stages for integrating special systems of ordinary
differential equations~// 2015 Intern. Conference on ``Stability
and Control Processes'' in memory of V.~I.~Zubov. SCP--2015.
Proceedings. 2015. P.~110--113.

5. \emph{Butcher~J.~C.} On Runge---Kutta processes of high
order~// Journal of the Australian Mathematical Society. 1964.
Vol.~4. P.~179--194.

6. \emph{Tsitouras~Ch., Famelis~I.~Th.} On phase-fitted modified
Runge---Kutta pairs of order 6(5)~// Intern. conference of
Numerical Analysis and Applied Mathematics: Extended Abstracts.
Crete, 2006. P.~1962--1965.

7. \emph{Chammud~(Hammud)~G.~M.} A three-dimensional family of
seven-step Runge---Kutta methods of order 6. Numerical Methods and
Programming~// Advanced Computing. 2001. Vol.~2. P.~159--166.

8. \emph{Хайрер~Э., Нерсетт~С., Ваннер~Г.} Решение обыкновенных
дифференциальных уравнений. Нежесткие задачи / пер. с~англ.
И.~А.~Кульчицкого, С.~C.~Филиппова; под ред.~С.~C.~Филиппова. М.:
Мир, 1990. 512~c. (\emph{Hairer~E., Norsett~S., Wanner~G.} Solving
ordinary differential equations.)

9. \emph{Шиманчук~Д.~В., Шмыров~А.~С.} Построение траектории
возвращения в~окрестность коллинеарной точки либрации системы
Солнце---Земля~// Вестн. С.-Петерб. ун-та. Сер. 10. Прикладная
математика. Информатика. Процессы управления. 2013. Вып.~2.
C.~76--85.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

\noindent Статья поступила в~редакцию 22 февраля 2018 г.; принята
к печати 14 июня 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Олемской Игорь Владимирович}~--- д-р физ.-мат.
наук, проф.; i.olemskoj@spbu.ru

\vskip2mm \textit{Коврижных Николай Александрович}~--- аспирант;
sagoyewatha@mail.ru

}
