


\zagol{517.958}{O. I. Drivotin}{COVARIANT DESCRIPTION OF
  PHASE SPACE DISTRIBUTIONS}{



\vspace{-3mm}\parindent=7mm



%{\copyright} А.~В.~Буре, 2014

\textit{Drivotin Oleg Igorevich} --- doctor of physical and
mathematical sciences,  professor; o.drivotin@ spbu.ru






\vskip 3mm

\emph{Дривотин Олег Игоревич} ---  доктор физико-математических
наук,  профессор; o.drivotin@ spbu.ru



%$^{1}$ Работа выполнена при частичной финансовой поддержке
%Российского фонда фундаментальных исследований (грант
%№~16-08-00890).

{\copyright} Санкт-Петербургский государственный университет, 2016


}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp04 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\emph{\doivyp/spbu10.\issueyear.\issuenum04 } }\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp04 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp/spbu10.\issueyear.\issuenum04}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize

\noindent St.~Petersburg State University, 7--9, Universitetskaya
nab.,\\ St.~Petersburg, 199034, Russian Federation



\vskip2.5mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}



\item The concept of phase space
for particles moving in the 4-dimen\-sional space time is
formulated. Definition of particle distribution density as
differential form is given. The degree of the distribution density
form may be different in various cases. The Liouville and the
Vlasov equations are written in tensor form with use of such
tensor operations as the Lie dragging and the Lie derivative. The
presented approach is valid in both non-relativistic and
relativistic cases. It should be emphasized that this approach
does not include the concepts of phase volume and distribution
function. The covariant approach allows using arbitrary systems of
coordinates for description of the particle distribution. In some
cases, making use of special coordinates grants the possibility to
construct analytical solutions. Besides, such an approach is
convenient for description of degenerate distributions, for
example, of the Kapchinsky--Vladimirsky distribution, which is
well-known in the theory of charged particle beams. It can be also
applied for description of particle distributions in curved space
time. Refs~25.

\textit{Keywords}: Liouville equation, Vlasov equation, phase
space, phase density, particle distribution density,
self-consistent distribution, degenerate distribution.



\end{list}

}

\vskip3mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it О.~И.~Дривотин}

\vskip2mm \noindent{\bf КОВАРИАНТНОЕ ОПИСАНИЕ РАСПРЕДЕЛЕНИЙ\\
В~ФАЗОВОМ ПРОСТРАНСТВЕ}

\vskip2.5mm


{\footnotesize


\noindentСанкт-Петербургский государственный университет,
Российская Федерация, \\ 199034, Санкт-Петербург, Университетская
наб., 7--9



\vskip2.5mm


\item Сформулирована концепция фазового пространства
для частиц, движущихся в~4-мер\-ном пространстве-времени. Дано
определение плотности распределения частиц как дифференциальной
формы. Уравнения Лиувилля и~Власова записаны в~тензорном виде
с~использованием таких тензорных операций как перенос Ли
и~производная Ли. Представленный подход применим как
в~нерелятивистском, так и~в~релятивистском случаях. Следует
подчеркнуть, что данный подход не~содержит понятий фазового объема
и функции распределения. Ковариантный подход позволяет
использовать любые системы координат для описания распределений
частиц. В~некоторых случаях использование специальных координат
дает возможность строить аналитические решения. Кроме того, такой
подход удобен для описания вырожденных распределений, например
распределения Капчинского--Владимирского, хорошо известного
в~теории пучков заряженных частиц. Он также может быть применен
для описания распределений частиц в~искривленном
пространстве-времени. Библиогр. 25~назв.

{\it Ключевые слова}: уравнение Лиувилля, уравнение Власова,
фазовое пространство, фазовая плотность, плотность распределения
частиц, самосогласованное распределение, вырожденное
распределение.



}

\end{list}


\vskip2mm

\indent {\bf 1. Introduction.} Covariant approach is commonly in
use in general relativity. But it can be also applied in
classical theory, where processes in space and time are
considered. Covariance means using of  objects that can be defined
without introducing coordinates, for example, tensors. Covariant
tensor equality is not associated with any coordinate chart.
Nevertheless, if coordinates are specified, a tensor equality can
be regarded as a set of equalities of corresponding tensor
components.

Customary forms of the Liouville and the Vlasov equations  contain
partial derivatives  of a distribution function  with respect to
space coordinates and components of the momentum vector   [1, 2].
Therefore, they cannot be regarded as covariant, because
differentiating with respect to vector components is not covariant
operation. Covariant approach allows making use such operation as
gradient of function, which components are derivatives with
respect to coordinates in some space. But in general case,
components of the momentum vector cannot be taken as global
coordinates in a phase space, as it is explained in section~2.

In all of these works, the concept of distribution function was
employed. The definition of a distribution function requires
making use the concept of phase volume. As distinct from the works
cited above, presented here approach does not include the concepts
of distribution function and phase volume. The particle
distribution density is introduced by a natural way as a
differential form of some degree. The main ideas of the present
work were previously formulated in works~[3,~4].

Kinetic equations in covariant form were also  written down in
some  works
(see, for example, [5--7]). %\cite{holm,holm2008,plasmas2013}).
But  forms of  top degree only [5, 7] and particle distribution
function [6, 7] were employed there.




The presented here approach is valid both for nonrelativistic and
relativistic cases equally. The difference between these cases
relates only to the form of dynamics equations. In classical
problems covariant approach has also great importance. It allows
making use of various coordinates in the phase space. It is
required, for example, in problems concerned with self-consistent
particle distributions for a charged particle beam. Besides, this
approach allows to consider degenerate distributions that are
described by forms of lower degree.

In fact, such approach was used in numerous works devoted to
self-consistent distributions for a cylindrical beam and for a
beam with varying cross-section radius
(``breathing'' beam) [8--15]. %\cite{dr2,dr3,drDok,dr4,dr51,dr52,dr6,dr7}.
In these works, the space of  motion integrals was introduced, and
particle density was defined in this space. Under some conditions,
the phase density can be expressed through the introduced density.
It was convenient to consider the phase density as a differential
form, and the motion integrals  as phase coordinates. It gave
possibility to construct new solutions of the Vlasov equation. For
example,  they can be obtained as  a linear combinations of
degenerate distributions, or  as  solutions of some integral
equation [9--15].
%\cite{dr3,drDok,dr4,dr51,dr52,dr6,dr7}.

To verify that these distributions are solutions of the Vlasov
equation, we can take into account that the phase density
conserves along the characteristic lines of this equation. To
provide rigorous proof, we need an equation where one can
substitute these distribution. One of the purposes of this article
is to write down such equation. Therefore, formalization of the
approach applied in works [8--15]
%\cite{dr2,dr3,drDok,dr4,dr51,dr52,dr6,dr7}
is offered in this article.







The article is organized as follows. In section 2 the  concept of
phase space is introduced. Section 3 is devoted to a definition of
phase density. Section 4 deals with the Liouville and the Vlasov
equations, which are written in covariant form. The difference
between these two equations consists only in  a way of computation
of the force acting on the particles. In the Liouville equation
the force is external one, while in the Vlasov equation it should
be computed using a particle distribution the equation is written
for. In   section 5 the case of electric charged matter is
considered. Relation between the phase density and the
4-dimensional current density entering the Maxwell equations is
obtained. As the conception of the four-dimensional current
density is applicable both in relativistic as in nonrelativistic
cases, this relation is valid in both cases. In   section 6 two
known examples are considered to show how new approach works. They
are the Brillouin flow [16] and the Kapchinsky--Vladimirsky
distribution [17]. Section 7 contains short discussion of the
results.





%For example, expressions with integrals should
%contain only differential forms under integral signs.



\indent {\bf 2. Phase space.} Physical processes occur in the
4-dimensional spacetime. Des-\linebreak cription of motion of a
particle requires specifying not only its position in spacetime,
but also its velocity. To identify state of a particle with
account of its velocity we should define a phase space. When a
phase space is defined, state of a particle can be regarded as a
point in it.

Consider an open domain $D$ in the spacetime. Assume that there
exists some foliation formed by disjoint spacelike surfaces
filling $D.$ Let's parameterize these surfaces with a continuous
parameter $t.$


Assume also that there exists a system of diffeomorphic mappings
of these surfaces to some selected surface. Call this selected
surface the configuration space and denote it by $C.$
%Denote points in $C$ by $x.$
The assumption introduced above means that the domain $D$ can be
represented as $T\times C,$ where $T$ denotes an interval where
the parameter $t$ varies, $t\in T.$ Such approach is widely used
in general relativity, and it is called $3+1$ splitting of the
spacetime
[18--20]. %\cite{adm,dirac,gour}.



When time passes, particles move from one surface to another. One
can describe dynamics of particles as  dynamics of their images in
the configuration space. Call the tangent bundle [21] of the
configuration space the phase space, and denote it by $M,$  ${\rm
dim}M=6.$ Points in $M$ will be denoted by $q,$ $q\in M.$



Such phase space  is senseless from the physical point of view,
but it can be used. In order to construct a meaningful phase
space, let's apply the fundamental physical concept of reference
frame. Following to  works [22, 23], let us introduce a congruence
of observers in $D.$ Call one of them  the main observer and call
the others the local observers. Assume that the main observer can
measure the time in $D.$ Assume that at any instant of time
measured by the main observer one can find a surface such that all
events of it are simultaneous from the point of view of all
observers of the congruence. Call such surface the layer of
simultaneous events. It is easy to see that the layers of
simultaneous events form a foliation in $D.$


Assume that there exists a system of diffeomorphic mappings of
these layers to one selected layer such that for any event  $P$
its image is the intersection of the selected layer with worldline
of an observer from the congruence that passes through $P.$ The
selected layer will be also called the configuration space, as
previously.

The congruence of the observers and the system of the introduced
mapping form a reference frame. It can be shown that  coordinates
of image of an event in the configuration space can be regarded as
spatial coordinates of the event and time measured by the main
observer is  temporal coordinate of the event [22, 23]. As
previously, call the tangent bundle of the configuration space the
phase space. Note that this definition is valid both in classical
and relativistic cases.




Phase space associated with a reference frame is preferable,
%Using of a reference frame, the configuration space associated with,
%and corresponding phase space is preferable
because all values entering equations describing physical
processes have physical sense. For example, in temporal-spatial
coordinates associated with a reference frame components of the
electromagnetic field tensor are components of the electric field
and components of the magnetic field. Further we shall consider
only such phase space.

According to definition of the tangent bundle [21], for every
$x\in C$ there exists a neighborhood $U$ and a homeomorphic
mapping $\Phi:$ $p^{-1}(U)\mapsto U\times T_xU$ such that
$p_1\Phi=p.$ Here $T_xU$ denotes the tangent space at the point
$x,$ which is fiber of the bundle, $p$ and $p_1$ denote
projections of $M$ and $U\times T_xU$ on $U$ correspondingly.
%Therefore, three coordinates in the phase space
%and three coordinates in the fiber $T_xU$
%can be taken as 6 coordinates in the neighbourhood $U$ of a point $q$
%where $x=p(q).$
It is clear that if one take three spatial coordinates $x^1,$
$x^2,$ $x^3,$ then corresponding components of velocities can be
taken as coordinates in $T_xU,$ and these 6 numbers can be taken
as coordinates locally
 in $p^{-1}(U)$.

Global coordinates in the phase space can be introduced as
follows. Consider a subregion in the phase space corresponding to
some subregion in the configuration space, which will be denoted
also by $C,$ instead of the whole phase space. It allows  taking
into account cases when spatial coordinates of some coordinate
chart are defined not in all configuration space.


Assume that $C$ is simply connected. Specify coordinates in $C,$
and assume that components of the metric tensor in these
coordinates are continuously differentiable in~$C.$


Take some point $x_0\in C.$ Consider the boundary problem
\begin{equation} \frac{\partial v^i}{\partial
x^j}+\Gamma^i_{jk}v^k=0,\quad v(x_0)=v_0, \label{eq:par}
\end{equation}
where $v_0$ is some vector, $v_0\in T_{x_0}C,$ and $\Gamma^i_{jk}$
denotes the Christoffel symbol of the second kind. Here and
further we use the Einstein summation convention according to
which summation is meant over all allowed values of repeated upper
and lower indices.

The equation of parallel transport of a vector $v$ along a line
$x=x(\lambda)$ can be written in the form
$$
\frac{d v^i}{d\lambda}+\Gamma^i_{jk}v^k\frac{dx^j}{d\lambda}=
\left(\frac{\partial v^i}{\partial
x^j}+\Gamma^i_{jk}v^k\right)\frac{dx^j}{d\lambda}=0.
$$
Therefore, the problem (\ref{eq:par}) describes a vector field
such that any vector of this field at a point $x$ can be regarded
as a result of parallel transport of the vector $v_0$ along any
line connecting points $x$ and $x_0.$

This boundary problem for the system of linear differential
equations has unique solution for a simply connected region.
Indeed, solution of the problem (\ref{eq:par}) consists in finding
of 3-dimensional surfaces in the phase space which tangent vectors
are an-\linebreak nihilated by forms
$\omega_{(i)}=dv^i+\Gamma^i_{jk}v^k\,dx^j,$ $i=\overline{1,n}.$ It
is sufficient for solvability that all $d\omega_{(i)}=0.$
Differentiating $\omega_{(i)},$ we get
$d\omega_{(i)}=\Gamma^i_{jk}dv^k\wedge dx^j=0,$ as Christoffel
symbols are permutation symmetric.


Therefore, for each vector $v\in T_xC$ we can find parallel vector
$P_{x_0}v\in T_{x_0}C$ at the point $x_0.$ Mapping $v\mapsto
P_{x_0}v$ is continuously differentiable, as it is set by the
Green functions of the problem (\ref{eq:par}). Then three
coordinates in the configuration space and three components of
$P_{x_0}v$ in these coordinates can be taken as coordinates of the
point of the phase space specified by $x$ and $v.$ Besides,
continuous differentiability of the mapping ensures that
transition functions between various coordinates are
differentiable. It means that phase space $M$ is differentiable
manifold.

%In what follows, we shall take phase coordinates  in this way.


If particles always lie on the same surface in the phase space, or
distribution density does not depend on some coordinate, then the
phase space $M$ can be taken as correspon\-ding subspace of the
initial phase space. In this case dimension of the phase space
under consideration is less then dimension of the initial phase
space, and coordinates are not ne\-cessarily spatial coordinates
and velocity coordinates and can represent a mixture of both
kinds.



\indent {\bf 3. Phase density.} In this section we shall concern
various types of distributions, all of which can be described on
the base of a common approach.

As a simplest case, consider continuous media that occupies an
open set in the phase space.
%$G_0,$ $G_0\subset M.$
Within the framework of this model, particle number in an open
subregion $G,$ $G\subset M,$ is not necessarily integer. Call the
differential form
 $n(t,q)$   of degree $m=\dim M$
such that integration of the form over each  open set $G$ gives
particle number in $G$ the particle distribution density in the
phase space, or the phase density:
%\equation
$$
\int\limits_Gn=N_G.
$$
%\label{eq:volumepart}
%\endequation
The boundaries  of $G$ and the form $n$ are assumed sufficiently
smooth for integration being possible.

Consider also another case when particle are distributed on an
oriented surface $S$ in the phase space that can move, $\dim S=p,$
$0<p<m.$ Call the differential form $n(t,q)$ of degree $p$ defined
on the surface $S$ such that for any open set $G,$ $G\subset M,$
$$
%\equation
\int\limits_{G\cap S}n=N_G
%\label{eq:surfacepart}
%\endequation
$$
the particle distribution density for this case. This form depends
on orientation of the surface, which is defined by an ordered set
of $m-p$ vectors. A change of the orientation can result in change
of sign of the form components [24]. Assume that form $n$ and the
surface $S$ are also sufficiently smooth for integration being
possible.
%For example,
%it is sufficient for integrability
%that components of $n$ be continuously
%differentiable with respect to coordinates on the surface.

At last, consider the case of ensemble of pointlike particles.
Define the scalar function
\begin{equation} \delta_{q'}(q)=
\begin{cases}
{1,\qquad q=q',\cr 0, \qquad q\neq q'.}
\end{cases}
\label{eq:delta}
\end{equation}
If  $q'$ depends on $t,$ then this function is also function of
$t.$ All functions which values are nonzero only in finite set of
points can be represented as linear combination of the functions
of form (\ref{eq:delta}). Restrict ourselves only to combinations
with all coefficients equal to~$1$:
\begin{equation}
n(t,q)=\sum\limits_{i=1}^N\delta_{q_{(i)}}(q),\qquad q_{(i)}\neq
q_{(j)},\quad {\rm if}\quad i\neq j. \label{eq:sumdelta}
\end{equation}
In this class of functions, define an operation of taking sum of
function values in all points $q_{(i)},$ where the function value
is nonzero:
\begin{equation} \sum\limits_{q\in G}
n(t,q)\equiv\sum\limits_{i:\, q_{(i)}\in G} n(t,q_{(i)}).
\label{eq:intdelta}
\end{equation}
Operation defined by equation (\ref{eq:intdelta}) is analogous to
integration of the form of higher degree over $G.$ A scalar
function can be regarded as the differential form of degree $0.$
Therefore, equation (\ref{eq:intdelta}) set a rule of integration
of a form of degree $0$ over open set $G.$ As previously, call
function of form (\ref{eq:sumdelta}) the phase density for system
of pointlike particles if
$$
%\equation
\sum\limits_{q\in G} n(t,q)=N_G.
%\label{eq:pointpart}
%\endequation
$$
It is easy to understand that the phase density is given by
equality (\ref{eq:sumdelta}), where  $q_{(i)}$ are positions of
the particles in the phase space, $i=\overline{1,N},$ $N$ is the
total number of particles in the ensemble.


These three cases  can be combined as follows.
%if we introduce a functional
%representing integration operation.
Denote by $G_0$ a region in the phase space enclosing all open
sets $G$ which can be considered. Consider a linear space $\cal F$
of some integrable test functions defined on the set $G_0.$
%which will be assumed sufficiently smooth and integrable.
Define functional $<n,f>$ as
$$
\int\limits_{G_0}n(t,q)f(q),\quad \int\limits_{G_0\cap
S}n(t,q)f(q), \quad \sum\limits_{q\in G_0}n(t,q)f(q)
$$
in the first, the second, and the third cases correspondingly,
$f\in{\cal F}.$ Then definition of the phase density $n$ can be
written in the form
%\equation
$$
<n,\chi_G>=N_G,
%\label{eq:defphaseden}
%\endequation
$$
where $\chi_G$ is the characteristic function of the set $G,$
$G\subset G_0:$
$$
\chi_G(q)=
\begin{cases}
{1,\quad q\in G, \cr 0,\quad q\notin G.}
\end{cases}
$$


\indent {\bf 4. The Liouville and the Vlasov Equations.} At each
instant of time $t\in T$, particle dynamics equations define a
vector field $f(t,q)$ in the phase space. Assume that for each
$t\in T,$ $q\in M$
%and for each instance of time $t\in T$
there exists a unique integral line passing through point $q.$ For
example, if components of $f(t,q)$ in Cartesian coordinates are
continuously differentiable with respect to coordinates and the
time, it will be so. The time can be taken as a parameter for the
integral lines.

We shall use operation of the Lie dragging [24] to describe how
the phase density changes when the time passes. Lie dragging  of a
point $q$ is the point gotten by displacement of $q$ along the
integral curve passing through $q$ by the parameter increment
$\delta t.$ Denote it by $F_{f,\delta t}q.$ By virtue of
uniqueness of the integral curve passing through a point, this
mapping is reversible.

The mapping  $F_{f,\delta t}q$ induces the following coordinate
transformation. For each point $q,$ let's take coordinates of its
preimage. Such transformation can be regarded as shift of the
system of coordinates. Denote these coordinates as $q^1_{(f,\delta
t)},$\ldots, $q^6_{(f,\delta t)}.$

\smallskip
Let  some tensor field $T$ be defined in the phase space.
Define tensor at the point $F_{f,\delta t}q$ as follows: its
components in coordinates $q^i_{(f,\delta t)},$ are equal to
components of $T$ at the point $q$ in the initial coordinates.
Such tensor is called the Lie dragging of the tensor $T$ along
vector field $f$ by the parameter increment $\delta t.$ Denote
this tensor by $F_{f,\delta t}q.$

How do phase density changes when particles move? It is easy to
understand that degree of the differential form describing
particle distribution does not change, because we can take dragged
vectors of basis at the initial point $q$ as the  basis vectors at
the dragged point $F_{f,\delta t}q.$ Assume also that the
particles do not appear and disappear. Therefore, integrals of the
phase density over any set should be the same as integral over
dragged set. For example, for a form $n$ of top degree $m$
$$
\int\limits_{F_{f,\delta t}G}n(t+\delta t,q)=\int\limits_G n(t).
$$
Here $F_{f,\delta t}G$ denotes an image of the set $G,$ that is
set all points of which are images of points of $G.$ Introducing
coordinates $q^i_{(f,\delta t)}$ we see that $F_{f,\delta t}G$
looks in these coordinates as $D$ in coordinates $q^i.$ Therefore,
to ensure equality of the integrals for any region it is necessary
and sufficient that the following equation will be satisfied
\begin{equation} n(t+\delta t,F_{f\,\delta t}q)=F_{f,\,\delta
t}n(t,q). \label{eq:master}
\end{equation}
It is easy to see that analogous reasons take place when degree of
form $n$ is less than $m.$ Therefore, equation (\ref{eq:master})
is valid in these cases also.

Vector field $f$ depends on the force acting on a particle. Let us
call equation (\ref{eq:master}) the covariant form of the
Liouville equation if the force is purely external. Let us call
equation (\ref{eq:master}) the covariant form of the Vlasov
equation if the force is determined  also by a self field, by
which we mean field produced by the particle ensemble. In the
first case, the equation (\ref{eq:master}) can be regarded as a
differential equation. Though it does not contain derivatives, it
describes such object as differential form. In the second case,
the equation (\ref{eq:master}) can be regarded as an
integro-differential equation, because usually it is possible to
represent the self field in an integral form with use of the Green
functions. We assume here that structure of separate particles can
be ignored, and one should take into account only phase density
while computing the force acting from the self field. Account of a
particle structure gives an additional term in the Vlasov equation
which is called the collision integral. This term is sufficient
only at high densities, and it will be omitted from further
consideration here.

Consider the case when the particle distribution is described by a
top degree form. How does this form change at some point $q$ of
the phase space depending on the time? Assume that its only
component $\tilde n$ is continuously differentiable with respect
to phase coordinates and time.

Let at some instance of time $t$ the phase density at a point $q$
is equal to $n(t,q).$ At the instance $t+\delta t$ it will be
equal to $n(t+\delta t,q)=F_{f\,\delta t}n(t,F_{f\,-\delta t}q),$
as the phase density changes according to equation
(\ref{eq:master}). Introduce the derivative of a differential form
with respect to the parameter $t$ as a form which components are
derivatives of corresponding components with respect to $t.$ Then
we obtain the Liouville and the Vlasov equation in the form
\begin{equation} \frac{\partial n}{\partial t}= \lim\limits_{\delta
t\rightarrow 0} \frac{n(t+\delta t,q)-n(t,q)}{\delta t}= -\lie
n(t,q). \label{eq:master6}
\end{equation}
Here $\lie n(t,q)$ denotes the Lie derivative of the phase density
along the vector field $f,$ which can be defined  as follows. The
Lie derivative of a tensor field $T$ along a vector field $f$  is
$$
%\equation
\lie T=\lim\limits_{\delta t\rightarrow 0} \frac{T-F_{f,\,\delta
t}T}{\delta t}.
%\label{eq:lee}
%\endequation
$$

The equation (\ref{eq:master6}) for density form of top degree was
considered also in   works   [5, 7]. For this case, it is easy to
understand that the solution of (\ref{eq:master6}) also satisfies
to the equation (\ref{eq:master}) [5].


Components of the Lie derivative of a differential form $T$ of
degree $p$   can be determined from the equalities
\begin{equation} (\lie
T)_{i_1\ldots i_p}= \frac{\partial T_{i_1\ldots i_p}}{\partial
q^k} f^k +\frac{\partial f^j}{\partial q^{i_1}} \cdot
T_{j\,i_2\ldots i_p} + \ldots \frac{\partial   f^{j}}{\partial
q^{i_{p}}}\cdot T_{i_1\ldots i_{p-1}\,j}. \label{eq:leeform}
\end{equation}
Summation is meant over possible values of repeated  indices.



When the phase space is associated with a reference frame, the
dynamics equations can be written in the form [24]
\begin{equation}
\frac{dx^i}{dt}=v^i,\quad m \sum_{j=1}^3g_{ij}(\frac{d}{dt}(\gamma
v))^j =Q_i, \quad i=1,2,3, \label{eq:partdynamics2}
\end{equation}
where $g_{ij}$ and $(d/dt(\gamma v))^j$ are spatial components of
the metric tensor and of covariant derivative of vector $\gamma v$
correspondingly, $\gamma$ is reduce energy of a particle, $Q$
denotes\linebreak 3-dimensional   force vector acting on a
particle.



For example, if particles move in the electromagnetic field, then
\begin{equation} Q_i=  e\left(E_i+\sum_{j=1}^3v^jB_{ij}\right),
\label{eq:emforce}
\end{equation}
where $e$ and $m$ are electric charge and mass of a particle, $E$
is the electric field intensity, and $B$ is the magnetic   flux
density, $B_{ij}= \mu_0g^{-1/2}g_{il}g_{jm}\varepsilon^{klm}H_k$
[24], $g$ is the determinant of the spatial part of the metric
tensor, $\varepsilon^{klm}$ are the 3-dimensional Levi--Civita
symbols, $H$ is the magnetic field intensity, $\mu_0$ is the
magnetic constant.



As an example, consider ensemble of nonrelativistic particles
%($\gamma=1$)
in the flat spacetime which dynamics is described by equation
(\ref{eq:partdynamics2}) with force term (\ref{eq:emforce}). Take
Cartesian coordinates in the configuration space and Cartesian
components of velocities as coordinates in the phase space.
According to (\ref{eq:emforce}) components of the force acting on
a particle does not depend on corresponding components of
velocities. Then in the right hand side of equality
(\ref{eq:leeform}) one should take into account only the first
term, and equation (\ref{eq:master6}) takes the form
$$
%\equation
\frac{\partial\tilde n}{\partial t}+\sum\limits_{i=1}^3
v^i\frac{\partial \tilde n}{\partial x^i}+ \sum\limits_{i=1}^3
\frac em (E_i+\sum\limits_{i=1}^3B_{ij}v^j)\frac{\partial \tilde
n}{\partial v^i}=0.
%\label{eq:tradvlas}
%\endequation
$$
This form of the Vlasov equation is widely used in applied
problems, for example, in the theory of   charged particle beams.


The simplest particular case
%when the Liouville equation in the form (\ref{eq:master}) can be considered
is an ensemble consisting of one particle. In this case, the
particle density is $\delta_{q_{(1)}(t)}(q).$ This scalar function
is equal to $1$ only at the point where the particle is located at
the instant of time $t,$ and is equal to $0$ at other points. It
is easy to understand that this density satisfies to the equation
(\ref{eq:master}).

Density for a  system of $N$ particles taken in the form
(\ref{eq:sumdelta}) also satisfies to the equation
(\ref{eq:master}), which can be regarded as the Liouville equation
if particle interaction is neglected and the Vlasov equation
otherwise.


\indent {\bf 5. Computation of self electromagnetic field.} The
electromagnetic field can\linebreak be described by the tensor of
electromagnetic field $F.$ When the first coordinate is
tempo-\linebreak ral, for example, $x^0=ct,$ and the other three
are spatial, components of the tensor are
$$
\|F_{ik}\|=
\begin{pmatrix}
{0 & E_1/c&E_2/c&E_3/c \cr -E_1/c&0&-B_{12}&-B_{13} \cr
-E_2/c&B_{12}&0&-B_{23} \cr -E_3/c&B_{13}&B_{23}&0}
\end{pmatrix}
.
$$

For simplicity, consider the case when the source of the
electromagnetic field is electrically charged matter describing by
the differential form $J$ of the third degree in the 4-dimensional
spacetime, the integral of which over smooth oriented
3-dimensional surface $S$ gives the quantity of charge passing
through $S$ in the direction of its orientation:
$$
\int\limits_SJ=Q_S.
$$
This form is known as the current density form [24]. In the
coordinates associated with a reference frame, spatial component
$J_{123}$ is the charge density, and the other components are
equal to components of the current density form of the second
degree in the 3-dimensional configuration space with an accuracy
up to the sign.

Then the Maxwell equations can be written in the form [24]
%\equation
%\begin{cases}
%{
$$
dF=0,
%\cr
\quad d\mystar F=J/(\varepsilon_0 c)
%}
,
$$
%\end{cases}
%\label{eq:farad}
%\endequation
where $\mystar$ denotes sequential application of the Hodge
operator denoted as ${}^*$ and lowering  of indices with the
4-dimensional metric tensor:
$$
(\mystar F)_{ik}=g_{il}g_{km}(\hodge F)^{lm},\qquad (\hodge
F)^{lm}=|g|^{-1/2}\varepsilon^{ijlm}F_{ij},
$$
$g$ is determinant of the metric tensor, $\varepsilon^{ijlm}$ is
the 4-dimensional  Levi--Civita symbol, $\varepsilon_0$ is
electric constant.


In what follows, we shall concern ourselves how to express the
current density $J$ through the phase density $n.$ For simplicity,
assume that the phase density is also described by the form of top
degree $6.$

Consider a simple connected subregion $C$ of the configuration
space. According to the previous, in the phase space, which is
tangent bundle of $C,$ one can introduce six coordinates, three of
them being coordinates in $C.$ It means that they are spatial
coordinates. Another three coordinates can be expressed through
these spatial coordinates and components of velocity at this
point, and, conversely, velocity at some point can be expressed
through these six coordinates.



Denote the spatial coordinates by $x^i,$ $x^i=q^i,$ $i=1,2,3.$
Assume that the particles occupy some region in the phase space.
Denote the section of this region at the point $\{x^1,x^2,x^3\}$
by $\Omega(x^1,x^2,x^3).$ Let us call $\Omega(x^1,x^2,x^3)$ the
set of admissible values of the phase coordinates $q^4,q^5,q^6$ at
the point of $C$ with coordinates $x^1,x^2,x^3.$ A value of
particle velocity is admissible only if it corresponds to some
point from $\Omega(x^1,x^2,x^3)$.

Integrating the current density form over $\Omega(x^1,x^2,x^3)$
  we obtain the density in the configuration space
%\equation
$$
J_{123}(x)
%dx^1\wedge dx^2\wedge dx^3
=\int\limits_{\Omega(x^1,x^2,x^3)} n_{123456}(t,q)\,dq^4\wedge
dq^5\wedge dq^6.
%\label{eq:J123}
%\endequation
$$
%Note that a value of particle velocity
%is admissible only
%if it corresponds to some  point from $\Omega(x^1,x^2,x^3)$.
%It requires that integration of the phase density here and further
%should be performed
%over the set $\Omega(x^1,x^2,x^3)$.





In order to find another components of the current density, for
example, $J_{012},$ we take a point $x$ in the spacetime, and
consider a small 3-dimensional cell spanned by the edge vectors
$\delta x^0e_{(0)},$ $\delta x^1e_{(1)},$ $\delta x^2e_{(2)}.$
Here $e_{(i)}$
%$i=\overline{0,3}$
denotes basic vector of the coordinate basis.
%displacement vectors
%$\delta x_{(0)},$ $\delta x_{(1)},$ $\delta x_{(2)}$
%where
%$\delta x_{(i)}^j=\delta_i^j\delta x^i,$ $i,j=\overline{0,2}.$
%Here $\delta_i^j$ denotes the Kronecker symbol.
%These vectors can be regarded as the edge vectors of this cell.
The cell contains points with coordinates $ x^0+\alpha \delta
x^0,$ $ x^1+\beta \delta x^1,$ $ x^2+\gamma \delta x^2,$ $\alpha,
\beta, \gamma\in [1,0],$ and  is a part of some $3$-dimensional
surface in the spacetime. Let the orientation of that surface is
specified by the basic vector $e_{(3)}.$ As configuration space is
associated with a reference frame, $x^0$ is temporal coordinate.
For definiteness, let $x^0=t.$ Denote this  cell by $C_{012}.$ Its
smallness means that the dependence of the phase density and of
the current density on $x^0$, $x^1$, $x^2$ can be neglected within
the cell with  an accuracy up to terms  of higher order of
smallness.


According to definition of the current density, the quantity of
charge passing through the cell $C_{012}$ in the direction $\delta
x_{(3)}$ is equal to
$$
\int\limits_{C_{012}}J= -J(\delta x^0e_{(0)},\delta
x^1e_{(1)},\delta x^2e_{(2)})= -J_{012}\delta x^0\delta x^1\delta
x^2.
$$
The minus sign appears here in accordance with the integration
rule [24] because orientation of the cell is specified by the
vector $e_{(3)},$ and the set of the vectors  $\{e_{(3)},$
$e_{(0)},$ $e_{(1)},$ $e_{(2)}\}$ is negatively oriented.

Let us express this quantity through the phase density. For given
$\delta t,$ particles passing through the cell $C_{012}$ have the
coordinate $x^3$ differing from the coordinate $x^3$ of the cell
less then $(dx^3/dt) \delta t.$ Consider the 4-dimensional cell
spanned by the edges vectors $\delta x^0e_{(0)},$ $\delta
x^1e_{(1)},$ $\delta x^2e_{(2)},(dx^3/dt)\delta t\, e_{(3)}.$
Denote it by $C_{0123}.$ The cell $C_{012}$ is one of its  faces.
Not all of particles passing through $C_{0123}$ have world lines
that cross the 3-dimensional cell $C_{012},$ because their
velocity have nonvanishing   components $dx^0/dt,$ $dx^1/dt,$ and
$dx^2/dt,$ which can be regarded as longitudinal relative to the
cell $C_{012}.$ Therefore, their world lines may cross  other
faces of the cell  $C_{0123},$ which can be considered as flank
faces. But under assumption that the phase density varies slowly,
for every particle leaving the 4-di-\linebreak mensional  cell
through flank boundary, there exists a particle entering the
4-dimensional cell through opposite flank boundary with the same
velocity. Therefore number of particles crossing the face
$C_{012}$ is equal to number of particles in the cell $C_{012}.$

In order to calculate their number, consider number of particle in
the 6-dimensional  cell in the phase space with edge vectors
$\delta x^1e_{(1)},$ $\delta x^2e_{(2)},$ $(dx^3/dt)\delta t\,
e_{(3)},$ $\delta q_{(4)},$ $\delta q_{(5)},$ $\delta q_{(6)}$:
$$
n_{123456}(t,q) dx^1\wedge dx^2\wedge dx^3\wedge dq^4 \wedge
dq^5\wedge dq^6 (\delta x^1e_{(1)},\delta
x^2e_{(2)},\!(dx^3\!/\!dt)\,\delta t e_{(3)}, \delta
q_{(4)},\delta q_{(5)},\delta q_{(6)}\!)\!=
%\label{eq:cellnumber}
$$
$$
=n_{123456}(t,q)\delta x^0\delta x^1\delta x^2 v^3 dq^4 \wedge
dq^5\wedge dq^6 (\delta q_{(4)},\delta q_{(5)},\delta q_{(6)}),
$$
here $\delta q_{(4)},$ $\delta q_{(5)},$ $\delta q_{(6)}$ are some
linearly independent vectors with vanishing spatial components.
%Note, that the third argument can be written as $v\delta t$
%as $dx^3(dx^i)=0,$ if $i\neq 3.$
%By this reason, we can regard  (\ref{eq:cellnumber}) as sought value, and can write
Integrating over all admissible values of the phase coordinates
$q^4, q^5, q^6,$ we get the equality
$$
%\equation
J_{012}=-\int\limits_{\Omega(x^1,x^2,x^3)}n_{123456}(t,q)v^3(t,q)
\,dq^4 \wedge dq^5\wedge dq^6.
$$
%\label{eq:J012}
%\endequation
Analogously, we have
$$
J_{013}=\int\limits_{\Omega(x^1,x^2,x^3)}n(t,q)_{123456}v^2(t,q)
\,dq^4 \wedge dq^5\wedge dq^6,
$$
$$
J_{023}=-\int\limits_{\Omega(x^1,x^2,x^3)}n(t,q)_{123456}v^1(t,q)
\,dq^4 \wedge dq^5\wedge dq^6.
$$






\indent {\bf 6. Particle distributions for charged particle beam.}
Finding analytical solutions of the Vlasov equation is very
complicated problem. It arises in charged particle beam physics
for high current beam. The solutions of the Vlasov equation for
high current beam are often called self-consistent distributions,
because particles move in the field that is produced by them. A
lot of papers are devoted to self-consistent distributions.

We give here two   examples of stationary particle distributions
in the phase space for charged particle beam, the Brillouin flow
[16], and the Kapchinsky--Vladimirsky distribution [17]. They are
degenerate distributions, because dimension of support of them is
less then dimension of the phase space. The stationarity means
that the phase density does not depend on the time.

In both cases, consider nonrelativistic uniformly charged
cylindrical beam in uniform longitudinal magnetic field
$H=(0,0,H_z).$ Self field can be found from the Poisson
equation\newpage
$$
\Delta \varphi=-{e\varrho_0}/{\varepsilon_0},
$$
where $\varrho_0$ is spatial density of the particles inside the
beam cross-section.

Assume that all particles have the same longitudinal velocity.
Transverse particle motion is described by equations
(\ref{eq:partdynamics2}) and (\ref{eq:emforce}) where
$E_r=e\varrho_0r/(2\varepsilon_0),$ $E_{\varphi}=E_z=0,$
$B_{r\varphi}=\mu_0rH_z,$ $B_{rz}=B_{\varphi z}=0.$ Integrating
these equations, we get following integrals of transverse motion
[8--15]:
%\cite{dr2,dr3,drDok,dr4,dr51,dr52,dr6,dr7}.
\begin{equation} M=r^2(\dot\varphi+\omega_0), \label{eq:M}
\end{equation}
\begin{equation} H=\dot r^2+\omega^2r^2+M^2/r^2. \label{eq:H}
\end{equation}
Here $r,\varphi,z$ are cylindrical coordinates, overdot denotes
differentiation with respect to $t,$ $\omega_0=eB_z/(2m),$
$\omega^2=\omega_0^2-e\varrho_0/(m\varepsilon_0)={\rm const},$ $e,
m$ are charge and mass of the particle,
%$B_z$ is longitudinal component of the magnetic flux density,
%In this case, magnetic flux is equal to $\Phi=\int B_{r\varphi}\,dr\wedge d\varphi$
%\cite{drivmono}. Hence,
$B_z=B_{r\varphi}/r={\rm const}.$


The Brillouin flow is trivial example, and can be described
without concerning of the phase density. But we apply the approach
developed here to show how it works. In the Brillouin flow all
particles rotate around the beam axis with the same angular
velocity. It is easy to find this velocity and the particle
spatial density: $\dot\varphi=-\omega_0,$
$\varrho=m\omega_0^2\varepsilon_0/e.$ That means that for all
particles $M=0,$ and $H=0.$




In order to introduce the phase space, consider a transverse slice
of the beam moving along the axis: $z\in (z_0+v^zt,z_0+\delta
z+v^zt),$ $\delta z$ being assumed small enough to consider that
all particles of the slice have the same value of the coordinate
$z.$ As assumed previously, all particles of the slice have also
the same longitudinal component of the velocity. Therefore, the
phase space for the particles of this slice is 4-dimensional in
the general case. But in the case of the Brillouin flow, all the
particles of the slice lie on the surface $M=0,$ and $H=0.$ Let us
take this surface as the phase space. This phase space is
2-dimensional. Spatial coordinates $r$  and $\varphi$ can be taken
as coordinates also in the phase space, $r<R,$ where $R$ is the
beam radius. Then the Vlasov equation (\ref{eq:master6}) takes the
form
$$
\frac{\partial n_{r\varphi}}{\partial t}+ \dot r\frac{\partial
n_{r\varphi}}{\partial r}+ \dot \varphi\frac{\partial
n_{r\varphi}}{\partial \varphi}=0.
$$
This equation is satisfied, because all terms are equal to $0.$

Consider the Kapchinsky--Vladimirsky distribution. It is also
called the micro-\linebreak canonical distribution, because all
the particles have the same value of the energy of the transverse
motion $H=H_0.$ For every admissible value of $M$ there exists a
set of particle trajectories, for which $r$ and $\varphi$ change
in accordance with equations (\ref{eq:M}), (\ref{eq:H}). Rotation
of some trajectory by an arbitrary angle around the beam axis
gives another trajectory with the same $M.$ Assume that the
particles are evenly distributed on all the trajectories with the
same $M$ differing by the rotation angle.

Denote the phase of the particle on the trajectory by $\theta,$
and take $M,$ $\theta$ and $\varphi$ as  coordinates in the phase
space, which is the surface $H=H_0.$ Then the Vlasov equation
takes the form

$$
%\equation
\frac{\partial n_{\varphi\theta M}}{\partial t}+ \dot
\varphi\frac{\partial n_{\varphi\theta M}}{\partial \varphi}+ \dot
\theta\frac{\partial n_{\varphi\theta M}}{\partial \theta}+ \dot
M\frac{\partial n_{\varphi\theta M}}{\partial M}=0.
%\label{eq:v3}
%\endequation
$$
%The Kapchinsky-Vladimirsky distribution is stationary one, therefore
The first term is equal to $0$ according to the stationarity of
the distribution. The second term is  equal to $0$ according to
the above assumption about uniformity of azimuthal distribution.
The forth term is equal to $0$ as $M$ conserves. Therefore, we
obtain from the Vlasov equation that the  particles should be
evenly distributed on phases $\theta$ of the trajectories, as
$\dot \theta\neq 0$.\newpage

The Vlasov equation is satisfied, and the problem seems to be
solved, but it is more complicated because the solution is
obtained under assumption that beam is uniformly charged. Let us
show that the spatial density of the beam is uniform if the
particles are uniformly distributed on $M$ on a segment
 $(-M_0,M_0).$

First of all, note that beam boundary $r=R$ can be reached only by
particles with $M=0.$ As $\dot r=0$ at $r=R,$ we have that
$H_0=\omega^2R^2.$


It can be seen from (\ref{eq:H}) that radial velocity changes as
$$
%\equation
\dot r=\pm\sqrt{H-\omega^2r^2-\frac{M^2}{r^2}}
%\label{eq:vr}
%\endequation
$$
along a particle trajectory. It is easy to get that maximal value
of $|M|$ is reached when the particle moves along circular
trajectory: $\dot r=0.$ For circular trajectory
$r=\sqrt{|M|/\omega},$ and therefore $H=2\omega|M|.$ Taking into
account that $H=\omega^2R^2,$ we get that maximal value of $|M|$
is $M_0=\omega R^2/2.$



Let us introduce other coordinates in the phase space: $x,$ $y,$
$M$, where $x$ and $y$ are Cartesian coordinates in the
configuration space. Components $n_{xyM}$ and $n_{\phi\theta M}$
are related by the tensor component transformation rule, which in
this case can be written as
$$
n_{xyM}=2n_{\varphi\theta M}\cdot\det \biggl\vert
\begin{pmatrix}
{\frac{\partial\varphi}{\partial
x}&\frac{\partial\varphi}{\partial y}\cr
\frac{\partial\theta}{\partial x}&\frac{\partial\theta}{\partial
y}}
\end{pmatrix}
\biggr\vert =\frac{2n_{\varphi\theta M}}{r|\dot r|}.
$$
Here we take into account that each trajectory passes twice
through every point in the phase space that lies on it, when the
particle approaches to the axis, and when the particle moves away
from the axis.
%Therefore a point with some $x$ and $y$ should be taken into account twice.
These cases differ only by the sign of the radial component of
velocity. The multiplier $2$ is written in compliance with this
reason.
%,but it is unsufficient as it depends on the density normalization.


Then
$$
\varrho= \int\limits_{-M_0}^{M^0}n_{xyM}\,dM=
\frac{2n_{\varphi\theta M}}r \int\limits_{-M_0}^{M_0}
\frac{dM}{(H_0-M^2/r^2-\omega^2r^2)^{1/2}}=2\pi n_{\varphi\theta
M}={\rm const}.
$$
Thus, we have proved that  spatial density is uniform inside the
beam cross-section. That means that uniform phase density defined
on the surface $H=H_0,$ $M\in(-M_0,M_0)$ corresponds to the
Kapchinsky--Vladimirsky distribution.









\indent {\bf 7. Conclusion.} The covariant theory of the phase
space distributions for particles moving in the spacetime is
presented. If there are introduced coordinates in the spacetime,
it is possible to consider a phase space. It turns out that a
phase space is not necessarily associated with a reference frame.
But from physical point of view, it is preferable to use phase
space associated with a reference frame. As it is shown in the
works [22, 23] the reference frame can be defined by the same
manner both in relativistic and nonrelativistic cases. Therefore,
the concept of  phase space associated with a reference frame is
the same for both cases. The differences between both cases are
related only to the way of specifying of the metric tensor and to
the form of motion equations.


The approach presented here does not use the concept of phase
volume, as compared to the common approach. If one introduces the
phase volume, then particle distribution function $\overline n$
can be defined as multiplier in the equality $n={\overline
n}\Omega_P$ [2, 7], where $n$ is the phase density form of top
degree and $\Omega_P$ is the phase volume form (the Liouville
6-form in [7]).

Firstly, that approach requires rigorous definition of the phase
volume form. In\linebreak\newpage\noindent work [7] the Liouville
6-form is defined in the 7-dimensional space, and reduction to
the\linebreak 6-dimensional space is carried out only for the case
of the flat Minkowski spacetime. In the present approach the phase
space is 6-dimensional, and the 7-dimensional space is required
only for computation of self force using the Maxwell equations
that contain 4-dimensional electric current density.

Secondly, the definition of the phase density as the distribution
function can be used only in the case of nondegenerate
distribution, when particles are distributed in some open
subdomain of the phase space. By this reason, such approach  faces
difficulties for degenerate distributions, when particles are
distributed on some surface in the phase space.

As it is shown by the examples, the   approach presented here is
simple in use, and plainer, because it does not contain
unnecessary conception of the phase volume.

The  theory presented here is rigorous basis for consideration of
particle distributions for a charged particle beam, particularly,
of degenerate distributions. Degenerate particle distributions are
often used as model distributions, for example, for numerical
solutions of the optimization problems for charged particle
accelerators [25].


The theory can be also used in other problems concerned with
self-consistent field of moving particles. For example, the
problem of self-gravitating star matter is of interest in
cosmology. Another problem, where this theory can be applied, is
magnetized matter, for example, gas of neutrons.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\input{04/lit-ra}

%%%%%N DOI в ссылке!!!!!!!!!!

\input{04/ref-s}

%%%%%N DOI в ссылке!!!!!!!!!!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize




%\thispagestyle{empty}

\vskip 3mm

%\thispagestyle{empty}


\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\it{Вестник~СПбГУ.~Сер.~10.~Прикладная~математика.~Информатика...~\issueyear.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\it{Вестник~СПбГУ.~Сер.~10.~Прикладная~математика.~Информатика...~\issueyear.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.

%\vskip 1mm

\noindent Статья поступила в~редакцию 15 февраля 2016~г.

\vskip 1mm

\noindent Статья принята к~печати 26 мая 2016~г.

}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vskip 5mm


%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak

%\vskip 3mm

%\textit{Буре Артем Владимирович}~--- аспирант; e-mail:
%bure.artem@gmail.com

%\vskip 2mm

%\emph{Bure Artem Vladimirovich}~--- post-graduate student; e-mail:
%bure.artem@gmail.com

%}
