

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1. Liboff~R.~L. {\it Introduction to the Theory of Kinetic
Equations.} New York, John Wiley and Sons Publ., 1969, 397~p.


2. De~Groot~S.~R., van Leeuwen~W.~A., van Weert~Ch.~G. {\it
Relativistic Kinetic  Theory.} Amsterdam, North Holland Publ.
Comp., 1980, 417~p.

3. Drivotin~O.~I. Covariant Formulation of the Vlasov Equation.
{\it Proc. IPAC'2011.} San-Sebastian, Spain, 2011 (Available at:
http:
//accelconf.web.cern.ch/accelconf/IPAC2011/papers/wepc114.pdf;
acces-\linebreak sed: 20.05.2016).

4. Drivotin~O.~I. Degenerate Solutions of the Vlasov Equation.
{\it Proc. RUPAC'2012.} Saint Petersburg, Russia, 2012 (Available
at: http:
//accelconf.web.cern.ch/accelconf/rupac2012/papers/tuppb028.pdf;
ac-\linebreak cessed: 20.05.2016).

5. Holm~D., Marsden~J., Ratiu~T. The   Euler-Poincare Equations
and Semidirect Products with Applications to Continuum Theories.
{\it Adv. Math.,} 1998, vol.~137, pp.~1--81.

6. Gibbons~J., Holm~D.~D., Tronci~C. Vlasov moments, integrable
systems and singular solutions. {\it Phys. Lett. A,} 2008,
vol.~372, pp.~1024--1033.

7. Squire~J., Quin~H., Tang~W.~M., Chandre~C. The Hamiltonian
Structure and Euler-Poincare formulation of the Vlasov--Maxwell
and gyrokinetic systems. {\it Phys. Plasmas,} 2013, vol.~20,
pp.~022501.

8. Drivotin~O.~I., Ovsyannikov~D.~A. Determination of the
Stationary Solutions of the Vlasov Equation for an Axially
Symmetric Beam of Charged Particles in a Longitudinal Magnetic
Field. {\it USSR Comput. Maths. Math. Phys.,} 1987, {vol.~27},
pp.~62--70.

9. Drivotin~O.~I., Ovsyannikov~D.~A. New Classes of Stationary
Solutions of Vlasov's Equation for an Axially Symmetrical Beam of
Charged Particles of Constant Density. {\it USSR Comput. Maths.
Math. Phys.,} 1989, {vol.~29}, pp.~195--199.

10. Drivotin~O.~I., Ovsyannikov~D.~A. On Self-Consistent
Distributions for a Charged Partice Beam in a Longitudinal
Magnetic Field. {\it Dokl. Phys.,} 1994, vol.~39, pp.~1--4.

11. Drivotin~O.~I., Ovsyannikov~D.~A. New Classes of Uniform
Distributions for Charged Particles in Magnetic Field. {\it Proc.
PAC'97.} Vancouver, Canada, 1998, pp.~1943--1945.


12. Drivotin~O.~I., Ovsyannikov~D.~A. Samosoglasovannye
raspredeleniya zaryazhennykh chastits v prodol'nom magnitnom pole.
I [Self-Consistent Distributions
 of Charged Particles
in Longitudinal Magnetic Field. I]. {\it Vestnik of Saint
Petersburg University. Series 10. Applied mathematics. Computer
science. Control processes,} 2004, issue~1, pp.~3--15. (In
Russian)



13. Drivotin~O.~I., Ovsyannikov~D.~A. Samosoglasovannye
raspredeleniya zaryazhennykh chastits v prodol'nom magnitnom pole.
II [Self-Consistent Distributions
 of Charged Particles
in Longitudinal Magnetic Field. II]. {\it Vestnik of Saint
Petersburg University. Series 10. Applied mathematics. Computer
science. Control processes,} 2004, issue~2, pp.~70--81. (In
Russian)




14. Drivotin~O.~I., Ovsyannikov~D.~A. Modeling of Self-Consistent
Distributions for Longitudinally Non-Uniform Beam. {\it Nucl.
Instr. Meth. Phys. Res.,} 2006,  vol.~A~558, pp.~112--118.



15. Drivotin~O.~I., Ovsyannikov~D.~A. Self-Consistent
Distributions for Charged Particle Beam in Magnetic Field. {\it
Intern. J. Modern Phys. A,} 2009,  {vol. 24}, pp. 816--842.

16.
 Brillouin~L.
A Theorem of Larmor and Its Importance for Electrons in Magnetic
Fields. {\it Phys. Rev.,} 1945,  {vol.~67}, pp.~260--266.

17.
 Kapchinsky~I.
{\it Theory of Resonance  Linear Accelerators}. New York, Harwood
Academic Press, 1985, 398~p.



18.
 Arnowitt~R., Deser~S., Misner~C.~W.
The Dynamics of General Relativity.
 {\it Gravitation: An Introduction to Current Research.}
Ed. by L. Witten. New York, Wiley Press, 1962, pp.~227--264.

19. Dirac~P.~A.~M. Fixation of Coordinates in the Hamiltonian
Theory of Gravitation. {\it Phys. Rev.}, 1958,  vol. 114, pp.
924--930.

20. Gourgoulhon~E.  3+1  {\it Formalism in General Relativity}.
Berlin, Springer Press, 2012, 294~p.



21.
 Godbillon~C. {\it  Geometrie Differentielle et Mechanique Analitique}
[{\it Differential Geometry and Analytical Mechanics}]. Paris,
Hermann Press, 1969, 183~p.

22. Drivotin~O.~I.
 {\it Reference Frames in Classical and Relativistic Physics}.
 arXiv:1403.1787
(Available at: http://arxiv.org/pdf/1403.1787v1.pdf; accessed:
20.05.2016).

23. Drivotin~O.~I.
 Rigorous Definition of the Reference Frame.
{\it Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes,} 2014, issue~4,
pp.~25--36.

24. Drivotin~O.~I. {\it Matematicheskie osnovy teorii polya} [{\it
Mathematical Foundations of the Field Theory}]. Saint Petersburg,
  Saint Petersburg State University Publ., 2010, 168~p. (In
Russian)

25. Drivotin~O.~I., Starikov~D.~A. Second Order Method for Beam
Dynamics Optimization. {\it Proc. RUPAC'2014.} Obninsk, Russia,
2014 (Available at:
http://accelconf.web.cern.ch/accelconf/rupac2014/
papers/tupsa15.pdf; accessed: 20.05.2016).



\vskip 2mm

{\bf For citation:} Drivotin O. I. Covariant description of phase
space distributions. {\it Vestnik of Saint Pe-\linebreak tersburg
University. Series~10. Applied mathematics. Computer science.
Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/spbu10.\issueyear.\issuenum04


}
