
{\small

\vskip4.5%6
mm \noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. {\it Якушев В. П., Буре В. М., Митрофанова О. А., Митрофанов~Е.~П.}
К~вопросу автоматизации построения вариограмм в задачах точного земледелия // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~2. С.~177--185. %\\
https://doi.org/10.21638/11701/spbu10.2020.209

2. {\it Буре В. М., Митрофанов Е. П., Митрофанова О. А., Петрушин~А.~Ф.}
Выделение однородных зон сельскохозяйственного поля для закладки опытов с~помощью беспилотного летательного аппарата // Вестник Санкт-Пе\-тер\-бург\-ско\-го университета. Прикладная математика. Информатика. Процессы управления. 2018. Т. 14. Вып. 2. С. 145--150. \\https://doi.org/10.21638/11701/spbu10.2018.206 

3. {\it Митрофанов Е. П., Митрофанова О. А., Буре В. М.}
Перспективы создания единой системы хранения и обработки данных дистанционного зондирования для мониторинга состояния посевов // Информационно-ресурсная цифровая платформа развития сельского хозяйства: сб. материалов конференции в рамках выставки <<Агрорусь>>, Санкт-Петербург, 2--5~сентября 2020~г. СПб., 2020. С.~32--35.

4. {\it Su X., Li J., Cui Y., Meng X., Wang Y. }
Review on the work of agriculture ontology research group // Journal of Integrative Agriculture. 2012. Vol.~11. N~5. P.~720--730.

5. {\it Wei Y., Wang R., Hu Y., Wang X.}
From web resources to agricultural ontology: a method for semi-automatic construction // Journal of Integrative Agriculture. 2012.  Vol.~11. N~5. P.~775--783.

6. {\it Anandhi V., Venkitapirabu J., Natarajan S. K., Sumathi C. S. }
Ontology for crop management~--- A core vocabulary of agricultural activity // International Journal of Current Microbiology and Applied Sciences. 2020. Vol.~9. N~9. P. 3364--3368.

7. {\it Abbasi R., Martinez P., Ahmad R.}
An ontology model to represent aquaponics 4.0~sys\-tem’s knowledge // Information Processing in Agriculture. 2021. %\\
https://doi.org/10.1016/j.inpa.2021.12.001 (In Press) 


8. {\it  Bonacin R., Nabuco O. F., Pierozzi Jr. I.}
Ontology models of the impacts of agriculture and climate changes on~water resources: Scenarios on interoperability and information recovery // Future Generation Computer Systems. 2016. Vol.~54. P.~423--434.

9. {\it Pakdeetrakulwong U., Hengpraprohm K. }
An ontology-based knowledge management for organic and good agricultural practice agriculture: A case study of Nakhon Pathom Province, Thailand // Thai Interdisciplinary Research. 2018. Vol.~13. N~4. P.~26--34.

10. {\it  Qin X., Zhang H., Zheng H.}
Research on intelligent retrieval system for agricultural information resources based on ontology // IOP Conference. Journal of Physics: Conference Series. 2019. Vol.~1168. N~022041.

11. {\it Drury B., Fernandes R., Moura M. F., Lopes A. A.}
A survey of semantic web technology for agriculture // Information Processing in Agriculture. 2019. Vol. 6. P.~487--501.

12. {\it Zheng Y., He Q., Qian P., Li Z.}
Construction of the ontology-based agricultural knowledge management system // Journal of Integrative Agriculture. 2012. Vol.~11. N~5. P.~700--709.

13. {\it Li D., Kang L., Cheng X., Li D., Ji L., Wang K., Chen Y. }
An ontology-based knowledge representation  and implement method for crop cultivation standard // Mathematical and computer modelling. 2013. Vol.~58. P.~466--473.

14. {\it Mouromtsev D.}
Semantic reference model for individualization of information processes in IoT heterogeneous environment // Electronics. 2021. N~2523.

15. {\it Wang X., Chen N., Chen Z., Yang X., Li J. }
Earth observation metadata ontology model for spatiotemporal-spectral semantic-enhanced satellite observation discovery: a case study of soil moisture monitoring // Journal GIScience and Remote Sensing. 2016. Vol.~53. Iss.~1. P.~22--44.

16. {\it Gruber T. R. }
Toward principles for the design of ontologies used for knowledge sharing // International Journal of Human-Computer Studies. 1995. Vol.~43. P.~907--928.

17. {\it Ngo Q. H., Kechadi T., Le-Khac N.-A.}
OAK: Ontology-based knowledge map model for digital agriculture // arXiv. 2020. N~2011.11442.

18. {\it Gupta S., Sabitha A. S. }
Designing ontology for massive open online courses using Protege // 8$^{\rm th}$ International Conference on Reliability, Infocom Technologies and Optimization (Trends and Future Directions), June 4--5, 2020. India, 2020. P.~403--406.

19. {\it Jambhulkar S. V., Karale S. J. }
Semantic web application generation using Protege tool // Online International Conference on Green Engineering and Technologies (IC-GET). 2016. N~39794780.

20. Официальный сайт PostgreSQL. URL: https://www.postgresql.org/ (дата обращения: 13.03. 2022).

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 15 марта 2022~г.

Cтатья принята к~печати 5 мая 2022~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Митрофанова Ольга Александровна}  --- канд. техн. наук; omitrofa@gmail.com 

\vskip2mm \textit{Митрофанов Евгений Павлович}  --- мл. науч. сотр.; mjeka@bk.ru 

\vskip2mm \textit{Буре Наталья Анатольевна}  --- канд. филол. наук; nataly.bure@gmail.com 

}
