
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Ontological approach application to the design\\ of a geospatial experimental database for information support\\ of research in precision agriculture %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it O.~A.~Mitrofanova$^{1,2}$, E.~P.~Mitrofanov$^{1,2}$, N.~A.~Bure$^2$%
%, I.~ќ. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ –абота выполнена в рамках государственного %
%задани€ по теме N 0827-2018-0003 Ђ‘ундаментальные исследовани€ %
%океанологических процессов, определ€ющих состо€ние и эволюцию морской %
%среды под вли€нием естественных и антропогенных факторов, на основе %
%методов наблюдени€ и моделировани€ї.\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
Agrophysical Research Institute, 14, Grazhdanskiy pr., St\,Petersburg,

\noindent%
\hskip2.45mm%
195220, Russian Federation


\noindent%
$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Mitrofanova O.~A., Mitrofanov E.~P., Bure N.~A. Ontological approach application to the design of a geospatial experimental database for information support of research in precision agriculture. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum, pp.~\pageref{p6}--\pageref{p6e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum06 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent Thanks to the development of information technologies and computing resources, it became possible to obtain and process big data, including geospatial data. Most research in the field of precision farming is interdisciplinary in nature, with experimental field data used by disparate scientific groups. In this connection, it became necessary to develop a unified web-based system for storing, organizing, and exchanging experimental information between researchers. The first step in achieving this goal was to create a geospatial database. Since the system being developed in the future may require extensions, modifications, adjustments, integration into other projects, it seems appropriate to use the ontology to form the database structure. The most popular tools were used as the main tools: the ontology language OWL (Ontology Web Language), the Protege 5.5 development environment. The main initial information obtained in the course of experimental studies carried out at the biopolygon: weather data, agrochemical indicators (sampling of soil and plants with georeferencing), agrophysical parameters (humidity, electrical conductivity), remote sensing data. Based on the results of the analysis of the current state of research in the field of storage and systematization of experimental information in crop production, as well as a survey of ARI employees, a prototype of the database structure was formed based on the ontological approach. Nine parent classes were defined as the foundation: Field, Crop rotation~--- experience, Agrotechnology, Yield, Meteo, Ground samples, Orthophoto, Calendar, and Dictionary~--- units of measurement.\\[1mm]
\textit{Keywords}: ontology, precision agriculture, field experiments, biopolygon, OWL, Protege.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. {Iakushev V. P., Bure V. M., Mitrofanova O. A., Mitrofanov E. P.} K~voprosu avtomatizatsii postroeniia variogramm v zadachakh tochnogo zemledeliia [On the issue of semivariograms constructing automation for precision agriculture problems]. {\it Vestnik of Saint Peterburg University. Applied Mathe\-ma\-tics. Computer Science. Control Processes,} 2020, vol.~16, iss.~2, pp.~177--185. \\https://doi.org/10.21638/11701/spbu10.2020.209 (In Russian)

2. {Bure V. M., Mitrofanov E. P., Mitrofanova O. A., Petrushin A. F.} Vydelenie odnorodnykh zon sel'skokhoziaistvennogo polia dlia zakladki opytov s pomoshch'iu bespilotnogo letatel'nogo apparata [Selection of homogeneous zones of agricultural field for laying of experiments using unmanned aerial vehicle]. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes,} 2018, vol.~14, iss.~2, pp.~145--150. %\\
https://doi.org/10.21638/11701/spbu10.2018.206 (In Russian)

3. {Mitrofanov E. P., Mitrofanova O. A., Bure V. M.} Perspektivy sozdaniia edinoi sistemy khraneniia i~obrabotki dannykh distantsionnogo zondirovaniia dlia monitoringa sostoianiia posevov [Prospects of the unified system creation for storing and processing remote sensing data for monitoring the state of crops].  {\it Information and resource digital platform for the development of agriculture}. Collection of conference materials within the framework of the exhibition ``AgrorusТ\,\,\!ТТ. Saint Petersburg, September 2--5, 2020. St~Pe\-ters\-burg, 2020, pp.~32--35. (In Russian)

4. { Su X., Li J., Cui Y., Meng X., Wang Y.} Review on the work of agriculture ontology research group. {\it Journal of Integrative Agriculture}, 2012, vol.~11, no.~5, pp.~720--730.

5. {Wei Y., Wang R., Hu Y., Wang X.}
From web resources to agricultural ontology: a method for semi-automatic construction. {\it Journal of Integrative Agriculture}, 2012, vol.~11, no.~5, pp.~775--783.

6. {Anandhi V., Venkitapirabu J., Natarajan S. K., Sumathi C. S.} Ontology for crop management~--- A core vocabulary of agricultural activity. {\it International Journal of Current Microbiology and Applied Sciences}, 2020, vol.~9, no.~9, pp.~3364--3368.

7. {Abbasi R., Martinez P., Ahmad R.} An ontology model to represent aquaponics 4.0 systemТs knowledge. {\it Information Processing in Agriculture}, 2021. %\\
https://doi.org/10.1016/j.inpa.2021.12.001 (In Press)

8. {Bonacin R., Nabuco O. F., Pierozzi Jr. I.} Ontology models of the impacts of agriculture and climate changes on water resources: Scenarios on interoperability and information recovery. {\it Future Generation Computer Systems}, 2016, vol.~54, pp.~423--434.

9. {Pakdeetrakulwong U., Hengpraprohm K.} An ontology-based knowledge management for organic and good agricultural practice agriculture: A case study of Nakhon Pathom Province, Thailand. {\it Thai Interdisciplinary Research}, 2018, vol.~13, no.~4, pp.~26--34.

10. {Qin X., Zhang H., Zheng H.} Research on intelligent retrieval system for agricultural information resources based on ontology. {\it IOP Conference. Journal of Physics: Conference Series}, 2019, vol.~1168, no.~022041.

11. { Drury B., Fernandes R., Moura M. F., Lopes A. A.} A survey of semantic web technology for agriculture. {\it Information Processing in Agriculture}, 2019, vol.~6, pp.~487--501.

12. {Zheng Y., He Q., Qian P., Li Z.} Construction of the ontology-based agricultural knowledge management system. {\it Journal of Integrative Agriculture}, 2012, vol.~11, no.~5, pp.~700--709.

13. {Li D., Kang L., Cheng X., Li D., Ji L., Wang K., Chen Y.} An ontology-based knowledge representation  and implement method for crop cultivation standard. {\it Mathematical and computer modelling}, 2013, vol.~58, pp.~466--473.

14. {Mouromtsev D.}
Semantic reference model for individualization of information processes in IoT heterogeneous environment. {\it Electronics}, 2021, no.~2523.

15. {Wang X., Chen N., Chen Z., Yang X., Li J.} Earth observation metadata ontology model for spatiotemporal-spectral semantic-enhanced satellite observation discovery: a case study of soil moisture monitoring. {\it Journal GIScience and Remote Sensing}, 2016, vol.~53, iss.~1, pp.~22--44.

16. {Gruber T. R.} Toward principles for the design of ontologies used for knowledge sharing. {\it International Journal of Human-Computer Studies}, 1995, vol.~43, pp.~907--928.

17. {Ngo Q. H., Kechadi T., Le-Khac N.-A.} OAK: Ontology-based knowledge map model for digital agriculture. {\it arXiv}, 2020, no.~2011.11442.

18. {Gupta S., Sabitha A. S.} Designing ontology for massive open online courses using Protege. {\it 8$^{th}$ International Conference on Reliability, Infocom Technologies and Optimization (Trends and Future Directions)}, June~4--5, 2020. India, 2020, pp.~403--406.

19. {Jambhulkar S. V., Karale S. J.} Semantic web application generation using Protege tool. {\it Online International Conference on Green Engineering and Technologies (IC-GET)}, 2016, no.~39794780.

20. {\it Official website of PostgreSQL}. Available at: \url{https://www.postgresql.org/} (accessed: March 13, 2022).


\vskip1.5mm Received:  March 15, 2022.

Accepted: May 05, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Olga A. Mitrofanova}  --- PhD in Engineering; omitrofa@gmail.com \par
%
\vskip2mm \textit{Evgenii P. Mitrofanov}  --- Junior Researcher; mjeka@bk.ru \par
%
\vskip2mm \textit{Nataliya A. Bure}  --- PhD in Phylology; nataly.bure@gmail.com \par
%
%
}
