
{\small

\vskip4.5%6
mm \noindent \textbf{Литература}

}

\vskip1.8%2
mm

{\footnotesize


1. \textit{Пропой А. И.}  Элементы теории оптимальных дискретных процессов. М.: Наука, 1973. 255~c.

2.  \textit{Овсянников Д. А.}  Математические методы управления пучками. Л.: Изд-во Ленингр. ун-та, 1980. 228~с.

3. \textit{Овсянников Д. А.}  Моделирование и оптимизация динамики пучков заряженных частиц. Л.: Изд-во Ленингр. ун-та, 1990. 312~с.

4.  \textit{Kotina E. D., Ovsyannikov A. D.}   On simultaneous optimization of programmed and perturbed motions in discrete sys\-tems~// Proceedings of 11th International IFAC Workshop on Control Applications of Optimization (CAO 2000). 2000. Vol.~1. P.~183--185.

5.  \textit{Kotina E. D.}   Control discrete systems and their applications to beam dynamics op\-timi\-za\-tion~// Proceedings of International Conference Physics and Control (PhysCon 2003). 2003. Vol.~3. P.~997--1002. N~1237041.

6.  \textit{Kotina E. D.}   Discrete optimization problem in beam dy\-na\-mics~// Nuclear Instruments and Methods in Physics Research. Section A. Accelerators, Spectrometers, Detectors and Associated Equipment. 2006. Vol.~558. Iss.~1. P.~292--294.

7.    \textit{Куржанский А. Б.}  Управление и наблюдение в условиях неопределенности. М.: Физматлит, 1977. 394~c.

8.  \textit{Bondarev B. I., Durkin A. P., Ovsyannikov A. D.}   New mathematical optimization models for RFQ structures~// Proceedings of 1999 Particle Accelerator Conference. New York, 1999. P.~2808--2810.

9. \textit{Овсянников А. Д.}  Управление пучком заряженных частиц с учетом их взаимодействия~// Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика. Информатика. Процессы управления. 2009.  Вып.~2. C.~82--92.

10. \textit{Овсянников А. Д.}  Математические модели оптимизации динамики пучков. СПб.: ВВМ, 2014. 181~с.

11.  \textit{Mizintseva M. A., Ovsyannikov D. A.}   On the minimax problem of beam dynamics optimiza\-tion~// Proceedings of the 25th Russian Particle Accelerator Conference (RuPAC 2016). 2016. P.~360--362.

12.  \textit{Mizintseva M. A., Ovsyannikov D. A.}   Minimax problem of simultaneous optimization of smooth and non-smooth func\-tio\-nals~// Proceedings of 2017 Constructive non-smooth analysis and related topics (dedicated to the memory of V.~F.~Demyanov). IEEE. 2017. P.~1--4.

13.  \textit{ Ovsyannikov D. A., Mizintseva M. A., Ovsyannikov A. D.}   Joint optimization of smooth and non-smooth functionals on beams of trajec\-to\-ries~// Proceedings of the International Conference Optimal Control and Differential Games (dedicated to the 110th anniversary of L.~S.~Pontryagin). 2018. P.~203--205.

14. \textit{Овсянников Д. А., Мизинцева М. А., Балабанов М. Ю., Дуркин А. П., Едаменко~Н.~С., Котина~Е.~Д., Овсянников~А.~Д.}  Оптимизация динамики пучков траекторий c использованием гладких и негладких функционалов. Ч.~1~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~1. С.~73--84. \\
https://doi.org/10.21638/11702/spbu10.2020.107

15. \textit{Демьянов В. Ф.}  Минимакс: дифференцируемость по направлениям. Л.: Изд-во Ленингр. ун-та, 1974. 112~с.

16. \textit{Котина Е. Д.}  К теории определения поля перемещений на основе уравнения переноса в дискретном случае~// Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика. Информатика. Процессы управления. 2010. Вып.~3. С.~38--43.

17. \textit{Котина Е. Д., Леонова Е. Б., Плоских В. А.}  Обработка радионуклидных изображений с использованием дискретных систем~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2019. Т.~15. Вып.~4. С.~544--554. %\\
https://doi.org/10.21638/11702/spbu10.2019.410

18. \textit{Golovkina A., Ovsyannikov D., Olaru S.}  Performance optimization of radioactive waste transmutation in accelerator driven system~// Cybernetics and Physics. 2018. Vol.~7. N~4. P.~210--215.

19. \textit{Kluchevskaia Yu. D., Polozov S. M.}   Beam dynamics simulation in a linear accelerator for Cern future circular collider~// Cybernetics and Physics. 2020. Vol.~9. N~2. P.~98--102.

20. \textit{Kurzhanski A. B., Varaiya P.}  Optimization of output feedback control under set-membership uncertainty~// Journal of Optimization Theory and Applications. 2011. Vol.~151. N~1. P.~11--32.

21. \textit{Бортаковский А. С.}  Теорема разделения в задачах управления пучками траек\-то\-рий детерминированных линейных переключаемых систем~// Изв. Рос. акад. наук. Теория и системы управления. 2020. №~2. С.~37--63.

22.  \textit{Bortakovskii A. S., Nemychenkov G. I.}  Suboptimal control of bunches of trajectories of discrete\linebreak\newpage\noindent deterministic automaton time-invariant systems~// Journal of Computer and Systems Sciences In\-ter\-na\-tional. 2017. Vol.~56. N~6. P.~914--929.%\pagebreak

23.  \textit{Panteleev A. V., Pis’mennaya V. A.}  Application of a memetic algorithm for the optimal control of  bunches of trajectories of nonlinear deterministic systems with incomplete feedback~// Journal of Computer and Systems Sciences International. 2018. Vol.~57. N~1. P.~25--36.




\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 18 октября 2020~г.

Cтатья принята к~печати 5 апреля 2021~г.

\vskip6mm К~о~н~т~а~к~т~н~а~я \ и~н~ф~о~р~м~а~ц~и~я:

%\vskip1.5mm%2mm

\vskip1.5%2
mm\textit{Котина Елена Дмитриевна} --- д-р физ.-мат. наук, проф.; e.kotina@spbu.ru

\vskip1.5%2
mm\textit{Овсянников Дмитрий Александрович} --- д-р физ.-мат. наук, проф.; d.a.ovsyannikov@spbu.ru \par
%
}
