

\noindent{\small UDC 517.929.4  \hfill {\footnotesize Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}\\
MSC 74G55

}

\vskip2mm

\noindent{\bf Countable stability of a weak solution of a
parabolic differential-difference\\ system
with distributed parameters on the graph%$^{*}$%

 }

\vskip2.5mm

\noindent{\it  V.~V.~Provotorov$\,^1$%
, S.~M.~Sergeev$\,^2$%
, V.~N.~Hoang$\,^1$%
%, I.~О. Famylia%$\,^2$%

}

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by the Russian
%Foundation for Basic Research (research project N
%20-07-00531).\par
%%
%%\vskip 2.0mm
%%
\indent{\copyright} Санкт-Петербургский государственный
университет, \issueyear%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum05 } }\hfill\thepage}%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum05}}}%
% для оформления нижнего колонтитула
\cfoot{} %

\vskip2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
Voronezh~State~University,~1,~Universitetskaya~pl.,~Voronezh,

\noindent%
\hskip2.45mm%
394006, Russian Federation

\noindent%
$^2$~%
Peter the Great St. Petersburg Polytechnic
University,~29,~Polytechnicheskaya ul.,

\noindent%
\hskip2.45mm%
St.~Petersburg, 195251, Russian~Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,
%
%\noindent%
%%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

{\small \noindent \textbf{For citation:}
Provotorov~V.~V.,~Sergeev~S.~M.,~Hoang~V.~N.  Countable stability
of a weak solution of a parabolic differential-difference system
with distributed parameters on the graph. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Pro\-ces\-ses}, \issueyear, vol.~16,
iss.~\issuenum,
pp.~\pageref{p5}--\pageref{p5e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05

\vskip3mm

{\leftskip=7mm\noindent The article proposes an analog of E.
Rothe's method (semi-discretization with respect to the time
variable) for construction convergent different schemes when
analyzing the countable stability of a weak solution of an initial
boundary value problem of the parabolic type with distributed
parameters on a graph in the class of summable functions. The
proposed method leads to the study of the input initial boundary
value problem to analyze the boundary value problem in a weak
setting for elliptical type equations with distributed parameters
on the graph. By virtue of the specifics of this method, the
stability of a weak solution is understood in terms of the
spectral criterion of stability (Neumann's countable stability),
which establishes the stability of the solution with respect to
each harmonic of the generalized Fourier series of a weak solution
or a segment of this series. Thus, there is another possibility
indicated, in addition to the Faedo---Galerkin method, for
constructing approaches to the desired solution of the initial
boundary value problem, to analyze its stability and the way to
prove the theorem of the existence of a weak solution to the input
problem. The approach is applied to finding sufficient conditions
for the countable stability of weak solutions to other initial
boundary value problems with more general boundary conditions~---
in which elliptical equations are considered with the boundary
conditions of the second or third type. Further analysis is
possible to find the conditions under which Lyapunov stability is
established. The approach can be used to analyze the optimal
control problems, as well as the problems of stabilization and
stability of differential systems with delay. Presented method of
finite difference opens new ways for approximating the states of a
parabolic system, analyzing their stability in the numerical
implementation and algorithmization of optimal control problems.\\[1mm]
\textit{Keywords}: parabolic differential-difference system,
distributed parameters on the graph, weak solution, countable
stability.

}

}

\vskip 4mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{1. Introduction.} The paper provides a fairly sufficiently
total approach of using ideas of the method of finite difference
and some principles of construction converging different schemes
when analyzing initial boundary value problems  with distributed
parameters on the graph in the class of summable up functions. The
essence of the approach is not new --- it is based on the method
of E. Rote (1930), named in scientific literature by the method of
semi-digitization (see, for example, [1]).  This approach has been
realized and proved in connection with the classic domains of
spatial variable change [1, 2].  Further fundamental results of
the study on the solvability of initial boundary value problems in
network-like domains [3--5] allowed to transfer the ideas and
results of [1, 2] without much difficulty in the case of parabolic
equations with distributed parameters on the graph. Below is a
analogy of the Rote method [2, p. 189] which essentially reduce
the analysis of the input initial boundary value problem to the
study of the boundary value problem for elliptical type equations
with distributed parameters on the graph. Thus, there is another
possibility [1, 2, 6], besides the Faedo---Galerkin method, to
construction approaches to the desired solution of the initial
boundary value problem, to analyze its stability and the way to
prove the theorem of the existence of a weak solution to the input
problem.  The approach is applied to finding sufficient conditions
for the stability of weak solutions to other initial boundary
value problems with more total boundary conditions --- in which
elliptical equations are considered with the boundary conditions
of the second or third type. The solvability of such problems is
proved similarly to the reasoning for the problem with the
boundary conditions of the first type.



 \textbf{2. Notations, concepts and basic statements.} In the represented work  uses concepts and notations accepted in the works [6--10]:
$\Gamma$ is bounded oriented geometric graph with edges $\gamma$
parameterized segment $[0,1]$; $\partial\Gamma$ and $J(\Gamma)$
are many boundary $\zeta$ and interior $\xi$ nodes of the graph,
respectively; $\Gamma_0$ is join all the edges of the graph
$\Gamma$ that do not contain endpoints;
$\Gamma_{t}=\Gamma_0\times(0,t)$
($\gamma_{t}=\gamma_{0}\times(0,t)$), $\partial
\Gamma_{t}=\partial \Gamma\times(0,t)$ ($t\in(0,T]$, $T<\infty$ is
arbitrary fixed constant).

In the course of the work  the Lebesgue  integral is used by
$\Gamma$ or $\Gamma_{t}$:
$\int\limits_{\Gamma}f(x)dx=\sum\limits_{\gamma}\int\limits_{\gamma}f(x)_\gamma
dx$ or
$\int\limits_{\Gamma_{t}}f(x,t)dxdt=\sum\limits_{\gamma}\int\limits_{\gamma_{t}}f(x,t)_\gamma
dxdt$, $f(\cdot)_\gamma$  is narrowing the function $f(\cdot)$ to
the edge $\gamma$.

Necessary spaces and sets: $C^1[\Gamma]$ is space of continuous
and differentiable on $\Gamma$ functions (derivative at the
endpoints of the ribs is understood as one-sided), $L_{p}(\Gamma)$
($p=1,2$) is the Banach space of measurable on $\Gamma_0$
functions summarized with a $p$ degree (similar to space
$L_{p}(\Gamma_T)$); $L_{2,1}(\Gamma_{T})$ is the space of function
from $L_1(\Gamma_{T})$ with the norm, defined by the ratio
$\|u\|_{L_{2,1}(\Gamma_{T})}=\int\limits_0^T(\int\limits_{\Gamma}u^2(x,t)dx)^{1/2}dt;$
$W_{\,2}^{1}(\Gamma)$ is the space of functions from
$L_{2}(\Gamma)$ having a generalized first order derivative  also
from $L_{2}(\Gamma)$; $W_{\,2}^{1,0}(\Gamma_{T})$ is the space
functions from $L_{2}(\Gamma_{T})$ having a generalized first
order derivative by $x$ belonging $L_{2}(\Gamma_{T})$ (similarly
entered the space $W_{\,2}^{1}(\Gamma_{T})$).


Below is the difference-differential analogue of the parabolic
equation
\begin{equation}\label{eq1}
{{\begin{array}{*{20}c}
 \frac{\partial y(x,t)}{\partial t}-\frac{\partial }{\partial x }\left(a(x)\frac{\partial y(x,t)}{\partial x}\right)+b(x)y(x,t)=f(x,t),\quad x,t\in \Gamma_{T},
 \end{array} }}
\end{equation}
with measurable bounded on $\Gamma_0$ functions $a(x)$, $b(x)$
summable with the square:
\begin{equation}\label{eq2}
{{\begin{array}{*{20}c} 0<a_\ast\leq a(x)\leq
a^\ast,\,\,|b(x)|\leq \beta,\,\,x\in \Gamma_0.
 \end{array} }}
\end{equation}

Introduce space states of the parabolic system and auxiliary
spaces (see [6, 8, 9]). To do this in space $W_{\,2}^{1}(\Gamma)$
consider the bilinear form
\[
{{\begin{array}{*{20}c}
\ell(\mu,\nu)=\int\limits_{\Gamma}\left(a(x)\frac{d \mu(x)}{d
x}\frac{d \nu(x)}{d x}+b(x)\mu(x)\nu(x)\right)dx.
 \end{array} }}
\]

The following statement to take place [11].



\textbf{Lemma 1.}  \emph{Let fulfill conditions} (2) \emph{and
function $u(x)\in W^1_{\,2}(\Gamma)$ is such that
$\ell(u,\nu)-\int\limits_{\Gamma}f(x)\eta(x)dx=0$ for any
$\eta(x)\in W^1_{\,2}(\Gamma)$, $f(x)\in L_2(\Gamma)$ is fixed
function.  Then for any edge $\gamma\subset\Gamma$  narrowing
$a(x)_\gamma\frac{du(x)_\gamma}{dx}$ continuously at the endpoints
of the edge $\gamma$.}


Let's designate through $\Omega_a(\Gamma)$ a set of functions
$u(x)\in C^1[\Gamma]$ that meet the conditions of Lemma 1 and
ratios
\[
{{\begin{array}{*{20}c} \sum\limits_{\gamma\in
R(\xi)}a(1)_\gamma\frac{du (1)_\gamma}{dx}
 =\sum\limits_{\gamma\in r(\xi)}a(0)_\gamma\frac{du (0)_\gamma}{dx}
 \end{array} }}
\]
in all the nodes $\xi\in J(\Gamma)$ (here $R(\xi)$ and $r(\xi)$
are sets of edges $\gamma$, respectively oriented  ``to node
$\xi$'' and ``from node  $\xi$''). The closing of the set
$\Omega_a(\Gamma)$  in norm $W^1_{\,2}(\Gamma)$  relabel
$W^1(a,\Gamma)$. In addition, if we assume that the functions
$u(x)\in\Omega_a(\Gamma)$ satisfy the boundary condition
$u(x)|_{\partial\Gamma}=0$, then we will get space
$W^1_{\,0}(a,\Gamma)$.


Next, let's designate through $W^{1,0}_{\,\,0}(a,\Gamma_{T})$ the
closure in the norma $W_{\,2}^{1,0}(\Gamma_{T})$ the set of
differentiable  functions $\Omega(\Gamma_{T})$, equal to zero near
the boundary $\partial \Gamma_{T}$ and satisfying ratios
\[
{{\begin{array}{*{20}c} \sum\limits_{\gamma\in
R(\xi)}a(1)_\gamma\frac{\partial u(1,t)_\gamma}{\partial x}
=\sum\limits_{\gamma\in r(\xi)}a(0)_\gamma\frac{\partial
u(0,t)_\gamma}{\partial x}
\end{array} }}
\]
for all nodes $\xi\in J(\Gamma)$ and for any  $t\in [0,T]$.
Analogously let's introduce space $W^{1}_{\,\,0}(a,\Gamma_{T})$ as
the closure in the norma $W_{\,2}^{1}(\Gamma_{T})$ set of
functions $\Omega(\Gamma_{T})$.


The space $W^{1,0}_{\,\,0}(a,\Gamma_{T})$ describes many states
$y(x,t)$ of the parabolic system (1),
$W^{1}_{\,\,0}(a,\Gamma_{T})$ is auxiliary space.


For functions $y(x,t)\in W^{1,0}_{\,\,0}(a,\Gamma_{T})$  we
consider equation (1) with initial and boundary conditions
\begin{equation}\label{eq3}
{{\begin{array}{*{20}c} y\mid_{t=0}=\varphi(x)\in L_2(\Gamma),
\quad y\mid_{x\in\partial\Gamma_T}=0;
 \end{array} }}
\end{equation}
the first equality in (3) have meaning sense and is understood
almost everywhere.



\textbf{Remark  1.} In the paper in detail be considered  the
first initial boundary value problem (1), (3) (the boundary
condition of Dirichlet  in ratios (3)), for the rest  types of
boundary conditions given the necessary comment.


Below are the subsidiary statements in space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$ and the main fragments of their
evidence, the full evidence is given in the work [6].


\textbf{Definition 1.} \emph{A weak solution to the initial
boundary value problem} (1), (3)   \emph{of class
$W_{\,2}^{1,0}(\Gamma_{T})$ is called a function $y(x,t)\in
W^{1,0}_{\,\,0}(a,\Gamma_{T})$ that satisfies the integral
identity}
\begin{equation}\label{eq4}
{{\begin{array}{*{20}c}
-\int\limits_{\Gamma_{T}}y(x,t)\frac{\partial \eta(x,t)}{\partial
t}dxdt+\ell_T(y,\eta)=
\int\limits_{\Gamma}{\varphi}(x)\eta(x,0)dx+\int\limits_{\Gamma_{T}}{f}(x,t)\eta(x,t)
dxdt
 \end{array} }}
\end{equation}
\emph{for any $\eta(x,t)\in W^{1}_{\,\,0}(a,\Gamma_{T})$ that is
zero at $t=T$. Here $\ell_T(y,\eta)$ is bilinear form, defined by
the ratio}
\[
{{\begin{array}{*{20}c}
\ell_T(y,\eta)=\int\limits_{\Gamma_{T}}\left(a(x)\frac{\partial
y(x,t)}{\partial x}\frac{\partial \eta(x,t)}{\partial
x}+b(x)y(x,t)\eta(x,t)\right)dxdt.
 \end{array} }}
\]



In proving the solvability of the problem (1), (3) in space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$ is used a special basis of  space
$W^1_{\,0}(a,\Gamma)$, that is a system of generalized
eigenfunctions of the boundary value problem
\begin{equation}\label{eq5}
{{\begin{array}{*{20}c}
-\frac{d}{dx}\left(a(x)\frac{du(x)}{dx}\right)+b(x)u(x)=\lambda
u(x),\,\,\,u(x)|_{\partial\Gamma}=0
\end{array} }}
\end{equation}
in class $W^1(a,\Gamma)$ [11--13]. This problem is to find many
such numbers (eigenvalues of the boundary value problem (5)), each
of which corresponds to at least one nontrivial generalized
solution $u(x)\in W^1_{\,0}(a,\Gamma)$ (generalized eigenfunction)
that satisfies an integral identity $\ell(u,\eta)=\lambda(u,\eta)$
for any function $\eta(x)\in W^1_{\,0}(a,\Gamma)$ (here and
everywhere below through $\left(\cdot,\cdot\right)$ designated the
scalar product in $L_{\,2}(\Gamma)$ or $L_{\,2}(\Gamma_T)$). The
following statement is true.


\textbf{Lemma 2.}   \emph{Let the assumptions} (2) \emph{be
fulfilled. Then the spectral problem} (5) \emph{has an denumerable
set of real eigenvalues $\{\lambda_i\}_{i\geq 1}$} (\emph{numbered
in ascending order, with regard for their multiplicity})
\emph{with a limit point on infinity} (\emph{eigenvalues
$\lambda_i$ are positive, with the exception of maybe the final
number of the first}). \emph{The system of generalized
eigenfunctions $\{u_i(x)\}_{i\geq 1}$ forms a basis in
$W_{\,0}^{1}(a,\Gamma)$ and $L_2(\Gamma)$, orth-normalized in
$W_{\,0}^{1}(a,\Gamma)$.}


\textbf{Remark 2.} If $b(x)\geq0$ in (2), as is the case in
applications, then all the eigenvalues of the spectral problem (5)
are nonnegative.



\textbf{Theorem 1.} \emph{For any $f(x)\in L_{2,1}(\Gamma_T)$,
$\varphi(x)\in L_2(\Gamma)$ and for any $0<T<\infty$ the initial
boundary value problem} (1), (3) \emph{is weak  solvable in space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$.}


With proof of theorem we construct  the Faedo---Galerkin's
approximations on the basis $\{u_i(x)\}_{i\geq 1}$: the
approximate solutions $y^N(x,t)$ (natural $N$ is fixed) of problem
(1), (3) have form  $y^N(x,t)=\sum\limits_{i=1}^Nc_i^N(t)u_i(x)$,
where $c_i^N(t)$ are absolutely continuous on $[0,T]$ functions
($c'_i(t)\in L_2(0,T)$), defined from the system
\[
{{\begin{array}{*{20}c} \left(\frac{\partial y^N}{\partial
t},u_i\right)+\int\limits_{\Gamma}\left(a(x)\frac{\partial
y^N(x,t)}{\partial x}\frac{d u_i(x)}{d
x}+b(x)y^N(x,t)u_i(x)\right)dx= \left({f},u_i\right),\,\\
c_i^N(0)=({\varphi},u_i),\,\,i=\overline{1,N}.
 \end{array} }}
\]



Further reasoning based on a priori estimates of norm of weak
solutions (1), (3) and construction the subsequence
$\left\{y^{N_k}\right\}_{k\geq1}$ of sequence
$\left\{y^N\right\}_{N\geq1}$, weakly converge to solution
$y(x,t)\in W^{1,0}_{\,\,0}(a,\Gamma_{T})$    in a norm of
$W^{1,0}_{\,\,0}(\Gamma_{T})$ (weak compactness
$\left\{y^{N_k}\right\}_{k\geq1}$). Namely, it is shown that for a
approximate solution $y^N(x,t)$ is inequality
\[
{{\begin{array}{*{20}c} \|y^N\|_{2,\Gamma_t} \leq
C(t)\left(\|y^N(x,0)\|_{L_2(\Gamma)}+2\|{f}\|_{L_{2,1}(\Gamma_t)}\right)
 \end{array} }}
\]
for any $t\in[0,T]$, where $\|\cdot\|_{2,\Gamma_t}$ is a norm of
$W^{1,0}(\Gamma_{t})$, the function $C(t)$ is limited to
$t\in[0,T]$ ($C(t)\leq C^*, 0<C^*<\infty$), not depend on $N$, is
determined by the value $T$ and permanent $a^\ast$, $\beta$. From
this inequality, taking into account the ratio
$c_i^N(0)=({\varphi},u_i)$ ($i=\overline{1,N}$)  and by virtue of
inequalities
\[
{{\begin{array}{*{20}c}
\|y^N(x,0)\|_{L_2(\Gamma)}=\|\sum\limits_{i=1}^N({\varphi},u_i)u_i(x)\|\leq
\sqrt{\sum\limits_{i=1}^N|({\varphi},u_i)|}\leq\|\varphi\|_{L_2(\Gamma)}
 \end{array} }}
\]
($\|\cdot\|$ is Euclidean norm:
$\|\omega\|=\sqrt{\sum\limits_{i=1}^N\omega_i^2}$ )  it should be
\begin{equation}\label{eq6}
{{\begin{array}{*{20}c} \|y^N\|_{2,\Gamma_t} \leq
C(t)\left(\|\varphi\|_{L_2(\Gamma)}+2\|{f}\|_{L_{2,1}(\Gamma_t)}\right),
 \end{array} }}
\end{equation}
that means independent of $N$ estimate $\|y^N\|_{2,\Gamma_t} \leq
C\,\,(C>0)$.


The latter means: from the sequence $\left\{y^N\right\}_{N\geq1}$
with limited totality elements $y^N$ can be distinguish the
subsequence $\left\{y^{N_k}\right\}_{k\geq1}$, that converge
weakly  to certain element $y\in W^{1,0}(a,\Gamma_{T})$ at a norm
$W^{1,0}_{\,\,0}(\Gamma_{T})$  ($\left\{y^{N_k}\right\}_{k\geq1}$
converge weakly to $y$ together with $\frac{\partial
y^{N_k}}{\partial x}$ at a norm $L_2(\Gamma_T)$). As a result of
the consequent reasoning become clear that the all sequence
$\left\{y^N\right\}_{N\geq1}$ is weakly converges to an element
$y\in W^{1,0}_{\,\,0}(a,\Gamma_{T})$  (so as
$\|\cdot\|_{W^{1,0}(\Gamma_{T})}\leq\|\cdot\|_{2,\Gamma_T}$).
Element $y(x,t)$ is a weak solution problem (1), (4).


\textbf{Theorem 2.} \emph{If the conditions of the theorem 1, then
initial boundary value problem } (1), (3) \emph{has only a weak
solution in the space  $W^{1,0}_{\,\,0}(a,\Gamma_{T})$  for any
$0<T<\infty$.}



Proof of uniqueness by virtue of linearity problem (1), (3) is the
standard way:  assumes the existence of two different solutions
${y}_1(x,t)$, ${y}_2(x,t)$ of class
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$. Where and from (6)  it should be
inequality $\|{y}\|_{2,\Gamma_T}\leq0$
(${y}(x,t)={y}_1(x,t)-{y}_2(x,t)$)  for any $T>0$, and that means,
coincidence solutions ${y}_1(x,t)$, ${y}_2(x,t)$ in space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$ (${y}_1(x,t)={y}_2(x,t)$ almost
everywhere).



\textbf{Corollary.} A weak solution of initial boundary value
problem (1), (3) continuously depends on the source data $f(x,t)$
and $\varphi(x)$. Thus shows the correctness of Hadamard initial
boundary value problem (1), (3) in the space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$ for any $0<T<\infty$.


\textbf{Remark 3.} Statements of Theorems 1 and 2 are preserved
under substitution $[0, T]$ on $[t_0,T]$ ($t_0>0$), the initial
condition in the ratio (3) is replaced by
$y\mid_{t=t_0}=\varphi(x)$.


\textbf{Remark 4.} Boundary condition in (3) can be
non-homogeneity:
\[
{{\begin{array}{*{20}c} y(x,t)\mid_{x\in\partial\Gamma}=\phi(x,t).
 \end{array} }}
\]
Proof of Theorems 1 and 2 in this case literally repeat the above
reasonings. For this as a preliminary introduces a new unknown
function $\widetilde{y}(x,t)=y(x,t)-\Phi(x,t)$ (here $\Phi(x,t)$
is a arbitrary function of $L_2(\Gamma_T)$,  having generalized
derivative $\frac{\partial\Phi}{\partial x}\in L_2(\Gamma_T)$ and
satisfying (almost everywhere) non-homogeneity boundary
condition). The integral identities in definition 1 be changed
respectively.



\textbf{3. Differential-difference system.} Below make use of
analog of the Rote method  [2, p. 189], which essentially reduce
the analysis of initial boundary value problem (1), (3) to the
study of the boundary value problem for elliptical type equations
with distributed parameters on the graph $\Gamma$. In space
$W^{1,0}_{\,\,0}(a,\Gamma_{T})$  consider the equation (1) and
dissect  the domain $\Gamma_{T}$ planes $t=k\tau$,
$k=0,1,2,...,M$, $\tau=\frac{T}{M}$, in addition denote by
$\Gamma^k_{T}$ section $\Gamma_{T}$ the plane  $t=k\tau$. Equation
(1) will replace differential-difference
\begin{equation}\label{eq7}
{{\begin{array}{*{20}c} \frac{1}{\tau}(u(k)-u(k-1))-\frac{d }{d x
}\left(a(x)\frac{d u(k)}{d x}\right)+b(x)u(k)=f_\tau(k)
\\
\\
 (k=1,2,...,M),
 \end{array} }}
\end{equation}
where
\[
{{\begin{array}{*{20}c} f_\tau(k)=
f_\tau(x,k)=\frac{1}{\tau}\int\limits^{k\tau}_{(k-1)\tau}f(x,t)dt\in
L_2(\Gamma).
 \end{array} }}
\]

Functions $u(k)$ ($k=1,2,...,M$) will define as a solution to the
equation system (7) that meets the conditions
\begin{equation}\label{eq8}
{{\begin{array}{*{20}c} u(0)=\varphi(x),\quad
u(k)\mid_{x\in\partial\Gamma}=0\,\,(k=1,2,...,M).
 \end{array} }}
\end{equation}
Ratios (7), (8) is the boundary value problem for the system of
elliptical equations (7).


\textbf{Remark 5.} Ratios (7), (8) are analogous to the implicitly
difference scheme of the first order of approximation on the time
variable $t$ for the initial boundary value problem (1), (3), set
in space $W^{1,0}_{\,\,0}(a,\Gamma_{T})$, with an elliptical
operator $-\frac{d }{d x }\left(a(x)\frac{d u}{d x}\right)+b(x)u$,
$u\in W^{1}_{\,0}(a,\Gamma)$.

\textbf{Definition 2.} \emph{ A weak solution to a boundary value
problem} (7), (8) \emph{is called functions}
$u(k)=W^1_{\,0}(a,\Gamma)$ $(k=0,1,2,...,M)$, $u(0)=\varphi(x)$
($\varphi(x)\in L_2(\Gamma)$), \emph{satisfying an integral
identity}

\begin{equation}\label{eq9}
{{\begin{array}{*{20}c}
\int\limits_{\Gamma}u(k)_t\,\eta(x)dx+\ell(u(k),\eta)=
\int\limits_{\Gamma}f_\tau(k)\,\eta(x) dx
\\
(k=1,2,...,M)
 \end{array} }}
\end{equation}
\emph{for any $\eta(x)\in W^1_{\,0}(a,\Gamma)$; equality
$u(0)=\varphi(x)$  is understood almost everywhere,}
\[
{{\begin{array}{*{20}c} u(k)_t=
u(x,k)_t=\frac{1}{\tau}(u(k)-u(k-1)).
 \end{array} }}
\]



We will establish the correctness of the statements, similar to
presented in Theo\-rems~1 and~2.

\textbf{Theorem 3.} \emph{The following statements take place}:

1. \emph{For any  $k_0\geq0$ and any $\varphi(x)\in L_2(\Gamma)$
weak solution $u(k)$ is uniquely defined at $k_0\leq k\leq M$
($k_0<M<\infty$)}.

2. \emph{A weak solution of the initial boundary value problem}
(1), (3) \emph{is the limit of functions $u(k)$, calculated from
ratios} (7), (8).

P r o o f. Beforehand we will obtain an $u(k)$ a priori estimate
that not dependent on $\tau$. Out of the ratio
$u(k-1)^2=(u(k)-\tau u(k)_t)^2=u(k)^2+\tau^2u(k)_t^2-2\tau
u(k)u(k)_t$ follow relation
\begin{equation}\label{eq10}
{{\begin{array}{*{20}c} 2\tau
u(k)u(k)_t=u(k)^2+\tau^2(u(k)_t)^2-u(k-1)^2.
 \end{array} }}
\end{equation}
Let as take in the ratio (9) $\eta(x)=2\tau u(k)$ and granting
(10), as well as the lower boundary $a_*$ for $a(x)$ (see (2)) get
inequality
\[
{{\begin{array}{*{20}c}
\int\limits_{\Gamma}u(k)^2dx-\int\limits_{\Gamma}u(k-1)^2dx+\tau^{2}\int\limits_{\Gamma}(u(k)_t)^2dx+
2a_*\tau\int\limits_{\Gamma}(\frac{du(k)}{dx})^2dx\leq
\\[0.3cm]
\leq
-2\tau\int\limits_{\Gamma}b(x)u(k)^2dx+2\tau\int\limits_{\Gamma}f_\tau(k)u(k)dx,
 \end{array} }}
\]
from here (everywhere below through $\|\cdot\|_{2,\Gamma}$ the
marked norm in space $W^1_{\,2}(\Gamma)$)
\[
{{\begin{array}{*{20}c}
\|u(k)\|^2_{2,\Gamma}-\|u(k-1)\|^2_{2,\Gamma}+\tau^2\|u(k)_t\|^2_{2,\Gamma}+
2a_*\tau\|\frac{du(k)}{dx}\|^2\leq
\\[0.2cm]
\leq
-2\tau\int\limits_{\Gamma}b(x)u(k)^2dx+2\tau\int\limits_{\Gamma}f_\tau(k)u(k)dx\leq
\\
\leq 2\beta \tau
\|u(k)\|^2_{2,\Gamma}+2\tau\|f_\tau(k)\|_{2,\Gamma}\|u(k)\|_{2,\Gamma}.
 \end{array} }}
\]
As a result, with $k=1,2,...,M$,
\begin{equation}\label{eq11}
{{\begin{array}{*{20}c}
\|u(k)\|^2_{2,\Gamma}-\|u(k-1)\|^2_{2,\Gamma}+\tau^2\|u(k)_t\|^2_{2,\Gamma}+
2a_*\tau\|\frac{du(k)}{dx}\|^2\leq
\\[0.2cm]
\leq \varrho \tau
\|u(k)\|^2_{2,\Gamma}+2\tau\|f_\tau(k)\|_{2,\Gamma}\|u(k)\|_{2,\Gamma},
 \end{array} }}
\end{equation}
where $\varrho=2\beta$. The latest inequality ensue from
\begin{equation}\label{eq12}
{{\begin{array}{*{20}c}
\|u(k)\|^2_{2,\Gamma}-\|u(k-1)\|^2_{2,\Gamma} \leq \varrho \tau
\|u(k)\|^2_{2,\Gamma}+2\tau\|f_\tau(k)\|_{2,\Gamma}\|u(k)\|_{2,\Gamma}.
 \end{array} }}
\end{equation}

1. Let $\|u(k)\|_{2,\Gamma}+\|u(k-1)\|_{2,\Gamma}>0$, then divide
both parts of inequality (12) on
$\|u(k)\|_{2,\Gamma}+\|u(k-1)\|_{2,\Gamma}$ and taking into
account
\[
{{\begin{array}{*{20}c}
\frac{\|u(k)\|_{2,\Gamma}}{\|u(k)\|_{2,\Gamma}+\|u(k-1)\|_{2,\Gamma}}\leq
1,
 \end{array} }}
\]
come to an estimate
\begin{equation}\label{eq13}
{{\begin{array}{*{20}c}
\|u(k)\|_{2,\Gamma}\leq\frac{1}{1-\varrho\tau}\|u(k-1)\|_{2,\Gamma}
+\frac{2\tau}{1-\varrho\tau}\|f_\tau(k)\|_{2,\Gamma},
 \end{array} }}
\end{equation}
when $\tau<\frac{1}{2\varrho}$.\pagebreak

2. Let $\|u(k)\|_{2,\Gamma}+\|u(k-1)\|_{2,\Gamma}=0$, then from
the ratio (12) follows $0\leq \varrho \tau
\|u(k)\|_{2,\Gamma}+2\tau\|f_\tau(k)\|_{2,\Gamma}$, that means
\[
{{\begin{array}{*{20}c} \|u(k)\|_{2,\Gamma}\leq \varrho \tau
\|u(k)\|_{2,\Gamma}-\|u(k-1)\|_{2,\Gamma}+2\tau\|f_\tau(k)\|_{2,\Gamma},
 \end{array} }}
\]
that again leads to an estimate  (13).

Given the recursively of the estimate (13), we get
\[
{{\begin{array}{*{20}c}
\|u(k)\|_{2,\Gamma}\leq\frac{1}{(1-\varrho\tau)^k}\|u(0)\|_{2,\Gamma}
+2\tau\sum\limits_{s=1}^k\frac{1}{(1-\varrho\tau)^{k-s+1}}\|f_\tau(s)\|_{2,\Gamma}\leq
\\
\leq
\frac{1}{(1-\varrho\tau)^k}\left(\|u(0)\|_{2,\Gamma}+2\tau\sum\limits_{s=1}^k\|f_\tau(s)\|_{2,\Gamma}\right)\leq
\\
\leq e^{2\varrho
T}\left(\|u(0)\|_{2,\Gamma}+2\|f_\tau(k)\|_{2,1,\Gamma_T}\right).
 \end{array} }}
\]
Here
$\|f_\tau(k)\|_{2,1,\Gamma_T}=\tau\sum\limits_{s=1}^k\|f_\tau(s)\|_{2,\Gamma}$,
the latest inequality follows from the ratios
$\frac{\varrho\tau}{1-\varrho\tau}k\leq \frac{\varrho
T}{1-\varrho\tau}\leq 2\varrho T$ at $\tau<\frac{1}{2\varrho}$ and
$\frac{1}{(1-\varrho\tau)^k}\leq e^{2\varrho T}$. Thus, a estimate
has been obtained
\begin{equation}\label{eq14}
{{\begin{array}{*{20}c} \|u(k)\|_{2,\Gamma}\leq e^{2\varrho
T}\left(\|u(0)\|_{2,\Gamma}+2\|f_\tau(k)\|_{2,1,\Gamma_T}\right).
 \end{array} }}
\end{equation}



Further, summing up the inequality (11) by $k$ from $1$ to $m\leq
M$ and using the estimate (14), we come to
\begin{equation}\label{eq15}
{{\begin{array}{*{20}c}
\|u(m)\|^2_{2,\Gamma}+2a_*\tau\sum\limits_{k=1}^m\|\frac{du(k)}{dx}\|^2
+\tau^2\sum\limits_{k=1}^m\|u(k)_t\|^2_{2,\Gamma}\leq
\\[0.3cm]
\leq c_1\left(
\|\varphi\|^2_{2,\Gamma}+\|f_\tau(m)\|^2_{2,1,\Gamma_T}\right),\quad
m=\overline{1,M},
 \end{array} }}
\end{equation}
where $c_1$ it depends only on $a_*$, $\beta$ and $T$;
$\|f_\tau(m)\|_{2,1,\Gamma_T}\leq \|f\|_{L_{2,1}(\Gamma_T)}$.
Going over in the resulting inequality to the limit, when
$M\rightarrow\infty$ we get a limited totality sequence
$\{u(m)\}\subset W^{1}_{\,0}(a,\Gamma)$ ($\|u(m)\|_{2,\Gamma}\leq
\widetilde{c}_1$, $m=1,2,...$), from which you can choose a
subsequence $\{u(m_i)\}$, weakly convergent  to a certain element
$u(x)\in W^{1}_{\,0}(a,\Gamma)$. The first statement of the
theorem is proven.



Let's show the correctness of the second statement. Introduce
piecewise constant interpolations $\widetilde{u}(x,t)$ by $t$ for
$u(k)$, namely: $\widetilde{u}(x,t)=u(k)$, when
$t\in((k-1)\tau,k\tau]$, $k=\overline{1,M}$. It is clear that
$\widetilde{u}(x,t)$ will be elements of space
$W^{1,0}_{\,\,0}(a,\Gamma_T)$ and for them by virtue of (15) take
place estimate
\begin{equation}\label{eq16}
{{\begin{array}{*{20}c}
\|\widetilde{u}\|_{2,\Gamma_T}+\|\frac{\partial
\widetilde{u}}{\partial x}\|_{2,\Gamma_T} \leq c_2,
 \end{array} }}
\end{equation}
constant $c_2$ not depend on $\tau$. Going over in (16) to the
limit when $M\rightarrow\infty$ we get a limited totality sequence
$\{\widetilde{u}\}\subset W^{1,0}_{\,\,0}(a,\Gamma_T)$ from which
you can choose a subsequence, weakly convergent  to a certain
element $u(x,t)\in W^{1,0}_{\,\,0}(a,\Gamma_T)$.  Let's show that
the function $u(x,t)$ satisfies the integral identity (4), i.~e.
is a weak solution from $W^{1,0}_{\,\,0}(a,\Gamma_T)$ of the
initial boundary value problem (1), (3). Set this identity for
fairly smooth functions $\eta(x,t)$, equal to zero on
$\partial\Gamma_T$ and at $t=T$: let's $\eta(x,t)\in
C^1(\Gamma_{T+\tau})$, it's zero on $\partial\Gamma_T$ and on
$t=T$.  We construct  for $\eta(x,t)$ averaging
$\eta(k)=\eta(x,k\tau)$, interpolations $\widetilde{\eta}(x,t)$
and $\widetilde{\eta}(x,t)_t$
($\eta(k)_t=\frac{1}{\tau}(\eta(k+1)-\eta(k))$. It's easily to
verify that interpolations $\widetilde{\eta}$,
$\frac{\partial\widetilde{\eta}}{\partial x}$,
$\widetilde{\eta}_{t}$ on $\Gamma_T$ uniformly converge to
functions $\eta(x,t)$, $\frac{\partial\eta(x,t)}{\partial x}$ and
$\frac{\partial\eta(x,t)}{\partial t}$, respectively, in addition
$\widetilde{\eta}(x,t)=0$, $t\in [T,T+\tau]$.

Under $\eta(k)_t=\frac{1}{\tau}(\eta(k+1)-\eta(k))$ correctly
\begin{equation}\label{eq17}
{{\begin{array}{*{20}c} \tau\sum\limits_{k=1}^M
u(k)_t\eta(k)=-\tau\sum\limits_{k=1}^M u(k)\eta(k)_t-u(0)\eta(1).
 \end{array} }}
\end{equation}


Summing the identities (9) at $\eta(x)=\tau\eta(k)$ over $k$ from
$1$ until $M$ and taking into account  (17), as well as
$\eta(M)=\eta(M+1)=0$, get
\[
{{\begin{array}{*{20}c} -\tau\sum\limits_{k=1}^M
\int\limits_{\Gamma}u(k)\eta(k)_tdx-\int\limits_{\Gamma}\varphi(x)\eta(1)dx+
\tau\sum\limits_{k=1}^M \ell(u(k),\eta(k))=
\\
=\tau\sum\limits_{k=1}^M (f_\tau(k),\eta(k))
 \end{array} }}
\]
or
\begin{equation}\label{eq18}
{{\begin{array}{*{20}c}
-\int\limits_{\Gamma_T}\widetilde{u}(x,t)\widetilde{\eta}(x,t)_tdxdt+
\ell_T(\widetilde{u},\widetilde{\eta})-\int\limits_{\Gamma}\varphi(x)\eta(1)dx=
\\
=\int\limits_{\Gamma_T}f(x,t),\widetilde{\eta}(x,t)dxdt.
 \end{array} }}
\end{equation}
In the ratio (18), going over  to the limit on the chosen above
weakly convergent in $W^{1,0}_{\,\,0}(a,\Gamma_T)$ the subsequence
of the sequence $\{\widetilde{u}(x,t)\}$ ($u(x,t)\in
W^{1,0}_{\,\,0}(a,\Gamma_T)$ is limit function), we get an
integral identity (4), at means the function $u(x,t)$ is a weak
solution of the initial boundary value problem (1), (3) of the
space $W^{1,0}_{\,\,0}(a,\Gamma_T)$. By virtue of the uniqueness
of  solution $u(x,t)$ (Theorem 1) and the estimate (16) the whole
sequence $\{\widetilde{u}(x,t)\}$ is weakly converged to $u(x,t)$.
The theorem is fully proven.


\textbf{Remark 6.} The first statement of the theorem (essentially
there is a method of finite difference) provides another
possibility (except for the Faedo---Galerkin method, presented by
the statement of the Theorem 1) of constructing approximations to
the solution, along the way realizing  (along with the second
statement of the theorem) and proof of the  theorem of the
existence of the initial boundary value problem (1), (3). The
approach used also applies to finding solutions to other initial
boundary value problem. In them, the boundary conditions of the
second or third type is added to the elliptical equations (7). The
solvability of such problems is proved similar to reasoning for
the problem (7), (8). Finally, both the Faedo---Galerkin method
and the of finite difference method open the way to approximate
the states of the system in numerical realization (construction
algorithms) of the posed problems.



\textbf{4. The countably stability of the differential-difference
system of equations (7), (8).} We do not seek to a possible
generality of define the concept of countably stability of the
differential-difference equations or systems of equations, as we
are interested in approaches to the analysis of the quality of the
differential-difference system of equations (7), (8),
approximating the initial boundary value problem (1), (3).

In the assumptions of section 3, consider the
differential-difference system of equations (7), (8) in a weak
formulation (9). Let's introduce the following  of Fourier series
on the system $\{u_i(x)\}_{i\geq 1}$ (see Lemma 2):
\begin{equation}\label{eq19}
{{\begin{array}{*{20}c} u(k)=\sum\limits_i u^i(k)u_i(x),\quad
f_\tau(k)=\sum\limits_i f^i_\tau(k)u_i(x),\quad
\varphi=\sum\limits_i \varphi^i u_i(x),
 \end{array} }}
\end{equation}
where $u^i(k)=(u(k),u_i)$, $f^i_\tau(k)=(f_\tau(k),u_i)$,
$\varphi^i=(\varphi,u_i)$.

D. Neumann introduced the concept of countably stability of the
difference schemes of evolutionary equations [14]. Below is an
analogue of this concept, following the work of  [15, p. 44].



\textbf{Definition 3.} \emph{Differential-difference system} (7),
(8) \emph{is called countably stability, if for each coefficient
$u_\tau(k)$ of the Fourier series} (19) \emph{take place
inequality}
\[
{{\begin{array}{*{20}c} |u(k)|\leq
C_{1\,n}|\varphi^n|+C_{2\,n}|f^n|,
\end{array} }}
\]
\emph{where constants $C_{1\,i}, C_{2\,i}$ are uniformly bounded
at} $0\leq k\tau\leq T$,
$|f^ni|=\max\limits_{k=\overline{1,M}}|f^i_\tau(k)|$.



For $\eta(x)=u_i(x)$, $i=1,2,...$, get
\[
{{\begin{array}{*{20}c} u^i(k)-u^i(k-1)+\tau\lambda_iu^i(k)=\tau
f^i_\tau(k-1),\,\,u^i(0)=\varphi^i
\\
(k=1,2,...,M),
 \end{array} }}
\]
$f^i_\tau(k-1)$ it's chosen as $f^i(t_{k})$:
$f^i(t_{k})=(f(x,t_{k}),u_i(x))$. The sequential exclusion of the
unknown $u^i(j)$, $j=1,2,...,k$, reduce to a ratio
\[
{{\begin{array}{*{20}c} u^i(k)= r_i^k\varphi^i+\tau
r_i\sum\limits_j r_i^{k-i}f^i_\tau(j-1)
\\
(k=1,2,...,M),
 \end{array} }}
\]
here $r_i=(1+\tau\lambda_i)^{-1}$. From here take place estimate
\[
{{\begin{array}{*{20}c} |u^i(k)|\leq |r_i|^k|\varphi^i|+\tau
|r_i|\sum\limits_j |r_n^{k-j}||f^i_\tau(j-1)|\leq
\\
\leq|r_i|^k|\varphi^i|+\tau
|r_i|\frac{1-|r_i|^{k}}{1-|r_i|}|f^i|,\quad
|f^i|=\max\limits_{k=\overline{1,M}}|f^i_\tau(k)|
\\
(k=1,2,...,M).
 \end{array} }}
\]

As $0<r_i<1$ ($i=1,2,...$) then $|r_i|^k<1$ and $\tau
|r_i|\frac{1-|r_i|^{k}}{1-|r_i|}<\tau
|r_i|\frac{1}{1-|r_i|}<T+\frac{1}{\lambda_1}$, it means,
the coefficients of  $|\varphi^i|$ and $|f^i|$ are uniformly
bounded at any value $\tau>0$ and do not depend on $\tau$,
$\varphi$ and $f$. This means that the spectral criterion of
counting stability of definition 3 be fulfilled:
differential-difference system (7), (8) is absolutely countably
stability.

\textbf{5. Example.} We consider the example reduced in the work
[10]. Let $\Gamma$ is a graph-star with edges $\gamma_\ell$,
$\ell=1,2,3$,  and a interior node $\xi$ (to simplify the
formulas, let's assume that  the edges $\gamma_\ell$, $\ell=1,2$,
are parameterized by a segment $[0,\pi/2]$, $\gamma_3$ is
parameterized by a segment $[\pi/2,\pi]$). In space
$W^{1,0}_{\,\,0}(a,\Gamma_T)$,  consider the initial boundary
value problem  (1), (3) at $a(x)=1$, $b(x)=0$ and $f(x,t)=0$:
\begin{equation}\label{eq20}
{{\begin{array}{*{20}c}
 \frac{\partial y(x,t)}{\partial t}=\frac{\partial^2 y(x,t)}{\partial x^2},\,\,
 y\mid_{t=0}=\varphi(x),\,x\in\Gamma, \,\, y\mid_{x\in\partial\Gamma_T}=0.
 \end{array} }}
\end{equation}


The weak solution $y(x,t)\in W^{1,0}_{\,\,0}(1,\Gamma_T)$ of
problem (20) is determined by identity
\[
{{\begin{array}{*{20}c}
-\int\limits_{\Gamma_{T}}y(x,t)\frac{\partial \eta(x,t)}{\partial
t}dxdt+\int\limits_{\Gamma_{T}}\frac{\partial y(x,t)}{\partial
t}\frac{\partial \eta(x,t)}{\partial
t}dxdt=\int\limits_{\Gamma}\varphi(x)\eta(x,0)dx
 \end{array} }}
\]
for any function $\eta(x,t)\in W^{1}_{\,0}(1,\Gamma_{T})$ that is
zero at $t=T$.



Let's define the differential-difference analog of the system (20)
(see (7)) ratios
\[
{{\begin{array}{*{20}c} \frac{1}{\tau}(y(k)-y(k-1))-\frac{d^2
y(k)}{d x^2}=0,\,\,k=1,2,...\,,
 \end{array} }}
\]
\[
{{\begin{array}{*{20}c} y(0)=\varphi,\quad
y(k)|_{\partial\Gamma}=0,
 \end{array} }}
\]
$y(k)\in W^1_{\,0}(a,\Gamma)$ ($k=1,2,...$), $\varphi(x)\in
L_2(\Gamma)$.\pagebreak


Functions $y(k)$ ($k=1,2,...$)  are defined by virtue of
recurrence ratios for integral identities
\[
{{\begin{array}{*{20}c}
(y(k)-y(k-1),\eta(x))+\tau(\frac{dy(k)}{dx},\frac{d\eta}{dx})=0\,\,\,\,
\forall \, \eta(x)\in W^1_{\,0}(a,\Gamma),\,\, k=1,2,...,
 \end{array} }}
\]
here $y(0)=\varphi(x)$, $x\in\Gamma$.

Easily to show [11--13], that the spectral problem (5) (under
$a(x)=1$, $b(x)=0$) in the weak formulation defines a set of
eigenvalues $\{\lambda_i\}_{i\geq1}$ ($\lambda_i=i^2$)  and system
of generalized eigenfunctions $\{u_i\}_{i\geq1}$, where
eigenvalues when  $i=2j-1$  is  prime numbers,  when $i=2j$   have
multiplicity 2, the corresponding generalized eigenfunctions are
determined by the relations ($j=1,2,...$)
\[
{{\begin{array}{*{20}c} {u_{2j-1} (x) = \left\{
{{\begin{array}{*{20}c}
 {\cos(2j-1)(x-\frac{\pi}{2}),\,x \in\gamma_1,} \hfill \\
 {\cos(2j-1)(x-\frac{\pi}{2}),\,x \in\gamma_2,}   \hfill \\
 {\cos(2j-1)(x-\frac{\pi}{2}),\,x \in\gamma_3,}  \hfill \\
\end{array} }} \right. }
 \end{array} }}
\]
\[
{{\begin{array}{*{20}c} {u_{2j,1} (x) = \left\{
{{\begin{array}{*{20}c}
 {\sin2j(x-\frac{\pi}{2}),\,x \in\gamma_1,} \hfill \\
 {0,\,\,\,x \in\gamma_2,}  \hfill \\
 {\sin2j(x-\frac{\pi}{2}),\,x \in\gamma_3,} \hfill \\
\end{array} }} \right. }\quad
{u_{2j,2} (x) = \left\{ {{\begin{array}{*{20}c}
 {0,\,\,\,x \in\gamma_1,}  \hfill \\
 {\sin2j(x-\frac{\pi}{2}),\,x \in\gamma_2,} \hfill \\
 {\sin2j(x-\frac{\pi}{2}),\,x \in\gamma_3.} \hfill \\
\end{array} }} \right. }
 \end{array} }}
\]



Let $\eta(x)=u_i(x)$ ($i=1,2,...$) then the ratios connecting
Fourier's coefficients $y^i(k)$, $\varphi^i$ of the elements
$y(k)$, $\varphi$  for each $i=1,2,...$, take the form of
\[
{{\begin{array}{*{20}c} y^i(k)-y^i(k-1)+\tau
i^2y^i(k)=0,\,\,y^i(0)=\varphi^i,\,\, k=1,2,...\,.
 \end{array} }}
\]
From here   $y^i(k)= (1+\tau i^2)^{-k}\varphi^n$ and for any
$\tau>0$
\[
{{\begin{array}{*{20}c} |y^i(k)|\leq \frac{1}{(1+\tau
i^2)^{k}}|\varphi^n|,\,\, k=1,2,...\,.
 \end{array} }}
\]
The absolute countably stability of the differential-difference
system is obvious. The last inequality have as a consequence
stability of the system to norm $L_2(\Gamma)$:
\[
{{\begin{array}{*{20}c} \|y(k)\|_{L_2(\Gamma)}\leq
\|\varphi\|_{L_2(\Gamma)},\,\, k=1,2,...\,.
 \end{array} }}
\]



\textbf{6. Conclusion.} The work outlines an approach to the
analysis of the differential system with distributed parameters on
the graph, which, not using the Faedo---Galerkin method,
establishes the theorem of the existence of a solution to the
initial boundary value problem (1), (3) and at the same time gives
you the opportunity  to obtain the conditions of stability
(countably stability) of the investigated problem. The proposed
method can be used for solve other initial boundary value
problems. In this case, the boundary conditions of the second or
third types is added to the elliptical equations (7). Note also,
the used approach  it is not difficult to extend to the case when
$\Gamma$ is a netlike domain of Euclidean space $\mathbb{R}^n$
($n\geq2$).

Further analysis is possible on the way to finding the conditions
of the Lyapunov stability of problem (1), (3). The approach can be
used to analyze the optimal control problems of [16--20], as well
as the problems of stabilization  and stability of differential
systems with  delay [21--27].


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
\input{05/ref-s-eng}% для английской статьи

%\newpage
\input{05/lit-ra-eng}% для английской статьи

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\thispagestyle{empty}

\vskip 3mm

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}}%
% для оформления нижнего колонтитула
\cfoot{} %

}
