

{\small



\vskip4.5%6
mm

\noindent \textbf{References} }

\vskip 1.5%2
mm

{\footnotesize



1. Lions J.-L. \textit{Nekotorye metody resheniya nelineinykh
kraevykh zadach} [\textit{Some methods of solving non-linear
boundary value problems}]. Moscow, Mir Publ., 1972, 587~p. (In
Russian)\pagebreak

2. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

3. Provotorov V.~V., Sergeev S.~M., Part A.~A. Solvability of
hyperbolic systems with distributed parameters on the graph in the
weak formulation. \emph{Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019,
vol. 15, iss. 1, pp. 107--117.
https://doi.org/10.21638/11702/spbu10.2019.2003

4. Provotorov V.~V., Ryazhskikh V.~I., Gnilitskaya Yu.~A.  Unique
weak solvability of nonlinear initial boundary value problem with
distributed parameters in the netlike domain. \emph{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2017, vol. 13, iss. 3, pp. 264--277.
https://doi.org/10.21638/11701/spbu10.2017.304

5. Artemov M. A.,  Baranovskii E. S., Zhabko A. P., Provotorov V.
V.  On a 3D model of non-isothermal flows in a pipeline network.
\emph{Journal of Physics. Conference Series}, 2019, vol. 1203,
Article ID 012094. https://doi.org/10.1088/1742-6596/1203/1/012094

6. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredekennemi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \textit{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224.
https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)

7. Provotorov V. V., Provotorova E. N. Optimal control of the
linearized Navier---Stokes system in a netlike domain.
\emph{Vestnik of Saint Petersburg University.  Applied
Mathematics. Computer Science. Control Processes}, 2017, vol. 13,
iss. 4, pp. 431--443.
https://doi.org/10.21638/11702/spbu10.2017.409

8. Zhabko A. P., Nurtazina K. B., Provotorov V. V.  About one
approach to solving the inverse problem for parabolic equation.
\emph{Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2019, vol. 15, iss. 3, pp.
323--336.\\   https://doi.org/10.21638/11702/spbu10.2019.303

9. Zhabko A. P.,  Provotorov V. V., Balaban O. R.  Stabilization
of weak solutions of pa\-ra\-bo\-lic systems with distributed
parameters on the graph. \emph{Vestnik of Saint Petersburg
University. Ap\-plied Mathematics. Computer Science. Control
Processes}, 2019, vol. 15, iss. 2, pp. 187--198.\\
https://doi.org/10.21638/11702/spbu10.2019.203

10. Zhabko~A.~P.,~Shindyapin~A.~I.,~Provotorov~V.~V.  Stability of
weak solutions of parabolic systems with distributed parameters on
the graph. \textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2019, vol. 15,
iss. 4, pp. 457--471.\\
https://doi.org/10.21638/11702/spbu10.2019.404

11. Volkova A.~S., Provotorov V.~V.  Generalized solutions and
generalized eigenfunctions of boundary-value problems on a
geometric graph. \emph{Russian Mathematics}, 2014, vol. 58, no. 3,
pp.~1--13. https://doi.org/10.3103/S1066369X14030013

12. Provotorov V. V. Eigenfunctions of  the Sturm---Liouville
problem on astar graph. \emph{Sbornik  Mathematics}, 2008, vol.
199, no. 10, pp. 1523--1545.

13. Provotorov V.~V. Razlozenie po sobstvennym funkciyam zadachi
Shturma---Liuvillya na grafe-puchke [Expansion  of eigenfunctions
of Sturm---Liouville problem on astar graph]. \emph{Russian
Mathematics}, 2008, vol. 3, pp. 45--57. (In Russian)

14. Neuman J., Richtmyer R.~D.  A method for the numerical
calculation of hydrodynamic shocks. \emph{Journal of  Appl.
Phys.}, 1950, vol. 21, no. 3, pp. 37--52.

15. Marchuk G. I. \emph{Metodi vichislitel'noi matematiki}
[\textit{Methods of computational mathematics}]. Moscow, Nauka
Publ., 1977, 456~p. (In Russian)

16. Provotorov V. V. Boundary control of a parabolic system with
delay and distributed parameters on the graph. \emph{International
Conference ``Stability and Control Processes'' in memory of V. I.
Zubov (SCP)}. St.~Petersburg, Russia, 2015, pp. 126--128.

17. Podvalny S. L., Podvalny E. S.,  Provotorov V. V.  The
controllability of parabolic systems with delay and distributed
parameters on the graph. \emph{Procedia Computer Sciense}, 2017,
vol.~103, pp.~324--330.

18. Podvalny S.~L., Provotorov V.~V.  Opredelenie startovoi
funkcii v zadache nabludeniy parabolicheskoi sistemi na grafe
[Determining the starting function in the task of observing the
parabolic system with distributed parameters on the graph].
\emph{Vestnik of Voronezh State Technical University}, 2014, vol.
10, no.~6, pp. 29--35. (In Russian)

19. Karelin V.~V.  Shtrafnye funkcii v zadache upravleniya
processom nabludeniya [Penalty functions in the control problem of
an observation process]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss. 4, pp. 109--114. (In Russian)

20. Karelin V.~V., Bure V.~M., Svirkin M.~V. Obobchennaja model
rasprostranenija informacii v neprerivnom vremeni [The generalized
model of information dissemination in continuous time].
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~1, pp.~74--80. https://doi.org:10.21638/11701/spbu
10.2017.107 (In Russian)


21. Alexandrova I.~V., Zhabko A.~P.  A new LKF approach to
stability analysis of linear systems with uncertain delays.
\emph{Automatica}, 2018, vol.~91, pp.~173--178.

22. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \emph{WSEAS Transactions on Systems and Control},
2014, vol.~9, pp.~388--397.

23. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions of solutions for nonlinear multiconnected
time-delay systems. \emph{Circuits  Systems and Signal
Processing}, 2016, vol.~35, no.~10, pp. 3531--3554.

24. Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze
prognoza s ustoichivym lineinym priblizheniem [Plasma
stabilization by prediction with stable linear approximation].
\emph{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2011, iss.~1,
pp.~116--133. (In Russian)

25. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. Existence of
subharmonic solutions to a hysteresis system with sinusoidal
external influence. \emph{Electronic Journal of Differential
Equations}, 2017, no.~140, pp.~1--10.

26. Krasnov S., Sergeev S., Titov A., Zotova Y.  Modelling of
digital communication surfaces for products and services
promotion. \emph{International Scientific Conference ``Digital
Transformation on Manufacturing, Infrastructure and Service''}.
St. Petersburg, Russia, 2019,  vol. 497, pp. 012032.\\
https://doi.org/10.1088/1757-899X/497/1/012032

27. Borisoglebskaya L. N., Provotorova E. N., Sergeev S. M.,
Khudyakov A. P.  Automated sto\-rage and retrieval system for
Industry 4.0 concept. \emph{International Scientific Workshop
``Advanced Tech\-no\-lo\-gies in Material Science, Mechanical and
Automation Engineering'', MIP: ENGINEERING--2019, IOP~Conference.
Series Mater. Sci. Eng.}, 2019, vol. 537, pp. 032036.\\
https://doi.org/10.1088/1757-899X/537/3/032036

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 17, 2020.

Accepted: October 23, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Vyacheslav V. Provotorov} --- Dr. Sci. in
Physics and Mathematics, Professor;
 wwprov@mail.ru

\vskip 2mm \textit{Sergey M. Sergeev} ---  PhD in Technics;
sergeev2@yandex.ru

\vskip 2mm \textit{Hoang Van Nguyen} --- Postgraduate Student;
fadded9x@gmail.com


}
