

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. {\it International Business Ecosphere}. Available at:\\ https://www.tutorialspoint.com/international/business/management country/attractiveness.htm (ac\-ces\-sed: October 06, 2021).

2. {Prakash A., Suvojit C. B.} {\it Managing social and economic change with information technology}. Harrysburg, Idea group Publ., 1994, 191~p.

3. {Barbora G.} The host country attractiveness from perspective of selected FDI indices. {\it Intern. J. of Interdisciplinarity in Theory and Practice}, 2016, vol.~9, pp.~58--64.

4.  {Zhou C.} The index system of national economy and socialty. {\it Contemporary China}, 2010, pp.~89--109.

5. {Bure V. M., Parilina E. M., Sedakov A. A.} {\it Applied statistics methods in R and Excel}. $3^{\rm rd}$~ed. St~Pe\-ters\-burg, Lan Publ., 2019, 196~p.

6. {Bure V. M., Parilina E. M.} {\it Probability theory and mathematical statistics}. $1^{\rm st}$~ed. St~Petersburg, Lan Publ., 2013, 416~p.

7. {Kovaleva M. A., Voloshin S. B.}
{\it Data analysis}. Moscow, World of Science Publ., 2019, 48~p.

8. {\it The World Bank}. Available at: http://data.worldbank.org/indicator (accessed: October 01, 2021).

9. {\it National Bureau of Statistics}. Available at: http://www.stats.gov.cn/tjsj/ndsj/ (accessed: September 30, 2021).  (In Chinese)

10. {Iakushev V. P., Bure V. M., Mitrofanova O. A., Mitrofanov E. P.}
 Theoretical foundations of probabilistic and statistical forecasting of agrometeorological risks. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~2, pp.~174--182. https://doi.org/10.21638/11701/spbu10.2021.207

11. {Iakushev V. P., Bure V. M., Mitrofanova O. A., Mitrofanov E. P.}.
K voprosu avtomatizatsii po\-stroe\-niia variogramm v zadachakh tochnogo zemledeliia [On the issue of semivariograms con\-struc\-ting auto\-mation for precision agriculture problems]. {\it Vestnik of Saint Petersburg University. Ap\-plied Ma\-the\-ma\-tics. Com\-pu\-ter Scien\-ce. Control Processes}, 2020, vol.~16, iss.~2, pp.~177--185.
 https://doi.org/10.21638/11701/spbu10.2020.209



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 19, 2021.

Accepted: February 01, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Dongfang Qi} --- Postgraduate Student; st073409@student.spbu.ru \par


\vskip 2mm
 \textit{Vladimir M. Bure} --- Dr. Sci. in Technics, Professor; vlb310154@gmail.com
 \par
%
%
}
