
{\small

\vskip4.5%6
mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. {\it	Hu Zh., Metaxas D., Axel L.} Functional imaging and modeling of the~heart~// Intern. Workshop on Functional Imaging and Modeling of the Heart. FIMH. 2005. P.~369--383.

2. {\it	Sallin E.} Fiber orientation and ejection fraction in the human LV // Biophysical Journal. 1969. Vol.~9. P.~954--964.

3. {\it	Hu Zh.} In vivo strain and stress estimation of the heart left and right ventricles from MRI images // Medical Image Analysis. 2003. Vol.~7. P.~435--444.

4. {\it	Chadwick R.~S.} Mechanics of the left ventricle // Journal of Biophysics. 1982. Vol.~39. P.~279--288.

5. {\it	Shoucri R.~M.} The pressure-volume relation and the mechanics of left ventricular con\-trac\-tion~// Japanese Heart Journal. 1990. Vol.~31. P.~713--729.

6. {\it	Shoucri R.~M.} Theoretical study of pressure-volume relation in left ventricle // American Journal of Physiology. 1991. Vol.~260. P.~H282--H291.

7. {\it	Shoucri R.~M.} Active and passive stresses in the myocardium // American Journal of Physiology. 2000. Vol.~279. P.~H2519--H2528.

8. {\it	Shoucri R.~M.} The calculation of the intramyocardial stress // Technology and Health Care. 2002. Vol.~10. P.~11--22.

9. {\it Shoucri	R.~M.} Equivalence of two approaches to study the stress-strain relation in the myocardium //  WIT Transactions on Biomedicine and Health. Modelling in Medicine and Biology. 2009. Vol.~13. \mbox{P.~3--16.}

10. {\it Le Rolle V., Carrault G., Richard P.-Y., Pibarot Ph.,  Durand L.-G., Hern\'andez A.~I.} A~tissue-level electrome\-cha\-nical model of the left ventricle: Application to the analysis of intraven\-tri\-cular pressure // Acta Biotheoretica.  2009. Vol.~57. Iss.~4. P.~457--478.

11. {\it	Mirsky I., McGill P.~L., Janz R.~F.} Mechanical behavior of ventricular aneurisms // Bulletin of Mathematical Biology. 1978. Vol.~40. N~4. P.~451--464.

12. {\it Campbell K.~B., Simpson A.~M., Campbell S.~G., Granzier H.~L., Slinker B.~K.}   Dynamic left ventricular elastance: a model for integrating cardiac muscle contraction into ventricular pressure-volume relationships // Journal of Applied Physiology. 2008.  Vol.~104. P.~958--975.

13. {\it	Kerckhoffs R.\,C.\,P., Faris\,O.\,P., Bovendeerd P.\,H.\,M., Prinzen\,F.\,W., Smits\,K., McVeigh\,E.\,R., Arts\,T.} Electromechanics of paced left ventricle simulated by straightforward mathematical model: com\-pa\-ri\-son with experiments // American Journal of Physiology. Heart and Circulatory Physiology. 2005. Vol.~289. N~5. Р.~H1889--H1897.

14. {\it	Radichkina A., Tregubov V.}  Mathematical simulation of the left ventricle during the systole contraction // Biomechanics. Intern. Conference of the Polish Society of Biomecha\-nics: Book of abstracts. Warsaw, 2010. P.~185--186.

15. {\it Трегубов В.~П., Радичкина А.~О.} Математическое моделирование кинематики левого желудочка сердца человека в процессе его сокращения // Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика. Информатика.  Процессы управления. 2013. Вып.~4. С.~67--73.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 25 мая 2021~г.

Cтатья принята к~печати 21 июня 2022~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Трегубов Владимир Петрович} --- д-р физ.-мат. наук, проф.; v.tregubov@spbu.ru

\vskip2mm \textit{Егорова Надежда Константиновна} --- аспирант; nadezhda\_ego@mail.ru


}
