

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm



1. Pontryagin L. S., Boltyanskii V. G., Gamkrelidze R. V.,
Mischenko E. F.  \textit{Mathematicheskaya teoriya optimalnnich
processov }[\textit{Mathematical theory of optimal processes}].
Moscow, Nauka Publ., 1969, 384~p. (In Russian)

2. Lee E. B., Markus L.  \textit{Foundations of optimal control
theory}. Malabar, FL, Krieger Publ. Co., 1986, 586~p. (Russ. ed.:
Lee E. B., Markus L. \textit{Osnovy teorii optimalnogo
upravleniya}. Moscow, Nauka Publ., 1972, 574~p.)

3. Filippov A. F. \textit{O nekotoryh voprosah optimalnogo
upravleniya} [\textit{About some problems of automatic control}].
\textit{Vestnik of Moscow University. Series~1. Mathematics and
mechanics}, 1959, no.~2, pp.~25--38. (In Russian)


4. Ovsyannikov D. A.  \textit{Matematicheskie metody upravleniya
puchkami} [\textit{Mathematical methods of pencils control}].
Leningrad, Leningrad State University Publ., 1980, 228~p. (In
Russian)


5. Nikolskii S. M. \textit { Kurs matematicheskogo analiza. V 2
t.} [\textit{A course of mathematical analysis. In 2~vol.}].
Moscow, Fizmathlit Publ., 2001, vol.~II, 592~p. (In Russian)

6. Hartman F.  \textit{Ordinary differential equations.} London,
John Wiley \& Sons, 1964, 612~p. (Russ. ed.: Hartman F.
\textit{Obyknovennie differencialnie uravneniya}. Moscow, Mir
Publ., 1970, 720~p.)

7. Gantmaher F. R.  \textit{Teoriya matrits} [\textit{Theory of
matrich}]. 2nd ed. Moscow, Nauka Publ., 1966, 576~p. (In Russian)

8. Nikolskii M. S., Belyaevskikh E. A.  Teoremy suschestvovanya
optimalnogo upravleniya dlya nekotorih zadach upravleniya puchkami
trajectorii [Existence theorems of optimal control for some
problems of control by pencils of trajectories]. \textit{Vestnik
of Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes,} 2017, vol.~13, iss.~1, pp.~113--118.
(In Russian)



\vskip 2mm

{\bf For citation:}   Nikolskii M. S., Belyaevskikh E. A. L. S.
Pontryagin maximum principle for some optimal control problems by
trajectories pencils. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
\issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
