

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm



1.  Dmitrishin D.,  Hagelstein P.,  Khamitova A., Stokolos A. On
the stability of cycles by delayed feedback control. {\it Linear
and Multilinear Algebra}, 2016, vol.~64,  issue~8, pp.~1538--1549.

2.  Dmitrishin D., Khamitova A.,  Stokolos A., Tohaneanu M.
{Extremal trigonometric polynomials and the problem of optimal
stabilization of chaos}. {\it Harmonic analysis, partial
differential equations, complex analysis, banach spaces, and
operator theory}. {\it Association for Women in Mathematics
Series}, 2016, vol.~2 (unpublished).


3. Morg\"ul \"O. {On the stability of delayed feedback
controllers}. {\it Physics Letters A}, 2003, vol.~314,
pp.~278--285.

4. Horn R. A., Johnson C. {\it Matrix analysis}. Cambridge,
Cambridge University Press, 1985, 561~p.

5. Dmitrishin D.,  Khamitova A. Methods of harmonic analysis in
nonlinear dynamics. {\it Comptes rendus mathematique}, 2013,
vol.~351, issues~9--10, pp.~367--370.

6.  Dmitrishin D., Khamitova A.,  Stokolos A. Fej\'er polynomials
and Chaos. {\it Springer Proceedings in Mathematics and
Statistics}, 2014, vol.~108, pp.~49--75.



\vskip 2mm

{\bf For citation:}  Khamitova A. D. Characteristic polynomials
for a cycle of non-linear discrete systems with time delays. {\it
Vestnik of Saint Petersburg University. Series~10. Applied
mathematics. Computer science. Control processes}, \issueyear,
issue~\issuenum, pp.~\pageref{p10}--\pageref{p10e}.
\doivyp/spbu10.\issueyear.\issuenum10




}
