

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1. John F. Plane strain problems for a perfectly elastic material
of harmonic type. {\it Commun. Pure and Appl. Math.}, 1960,
vol.~13, no.~2, pp.~239--296.

2. Lurie A.\,I. {\it Nelineynaya teoria uprugosti} [{\it
Non-linear elasticity}]. Moscow, Nauka Publ., 1980, 512~p. (In
Russian)

3. Chernykh K. F., Litvinenkova Z. N. {\it Teoria bolshih uprugih
deformatsiy} [{\it Theory of large elastic deformations}].
Leningrad,  Leningrad State University Publ., 1988, 256~p. (In
Russian)

4. Varley E., Cumberbatch E. Finite deformation of elastic
materials surrounding cylindrical holes. {\it Journal of
Elasticity}, 1980, vol.~10, no.~4, pp.~341--405.

5. Ru C. Q. On complex-variable formulation for finite plane
elastostatics of harmonic materials. {\it Acta Mechanica}, 2002,
vol.~156, no.~3--4, pp.~219--234.

6. Ru C.\,Q., Schiavone P., Sudak L.\,J., Mioduchowski A.
Uniformity of stresses inside an elliptic inclusion in finite
plane elastostatics. {\it Intern. Journal of Non-linear
mechanics}, 2005, vol.~38, no.~2--3, pp.~281--287.

7. Malkov V. M., Malkova Yu. V. Ploskaya zadacha nelineynoy
uprugosti dlya garmonicheskogo materiala [Plane problem of
non-linear elasticity for harmonic material]. {\it Vestnik of
Saint Petersburg State University. Series 1. Mathematics.
Mechanics. Astronomy}, 2008, issue 3, pp.~114--126. (In Russian)

8. Malkov V. M., Malkova Yu. V., Stepanova V. A. Dvuhkomponentnaya
ploskost is materiala Dzhona s mezhfaznoy treshchinoy,
nagruzhennoy davleniem [Bi-material plane of John's material with
interface crack loaded by pressure]. {\it Vestnik of Saint
Petersburg State University. Series 1. Mathematics. Mechanics.
Astronomy}, 2013, issue 3, pp.~113--125. (In Russian)

9. Malkov V. M., Malkova Yu. V. Ploskie zadachi uprugosti dlya
polulineynogo materiala [Plane problems of elasticity for
semi-linear material]. {\it Vestnik of Saint Petersburg State
University. Series 1. Mathematics. Mechanics. Astronomy}, 2012,
issue 3, pp.~93--106. (In Russian)

10. Malkov V. M., Malkova Yu. V. Ploskie zadachi o
sosredotochennyih silah dlya polulineynogo materiala [Plane
problems of concentrated forces for semi-linear material]. {\it
Vestnik of Saint Petersburg State University. Series 10. Applied
mathematics. Computer science. Control processes}, 2013, issue 3,
pp.~83--96. (In Russian)

11. Malkov V. M., Malkova Yu. V. Issledovanie nelineynoy zadachi
Flamana [Investigation of non-linear Flamant's problem]. {\it Izv.
RAN. Mekhanika tverdogo tela} [{\it Izv. RAS. Mechanics of
solids}], 2006, no.~5, pp.~68--78. (In Russian)

12. Malkov V. M., Malkova Yu. V. Analiz singulyarnosti
napryazheniy v nelineynoy zadache Flamana dlya nekotoryih modeley
materiala [Analysis of singularity of stresses in non-linear
Flamant's problem for some material models]. {\it Prikladnaia
matematika i~mekhanika} [{\it Applied mathematics and mechanics}],
2008, vol.~72, no.~3, pp.~453--462. (In Russian)

13. Malkov V. M. {\it Vvedenie v nelineynuyu uprugost} [{\it
Introduction in non-linear elasticity}]. Saint Petersburg, Saint
Petersburg State University Publ., 2010, 276~p. (In Russian)

14. Muskhelishvili N. I. {\it Nekotorye osnovnye zadachi
matematicheskoy teorii uprugosti} [{\it Some basic problems of
mathematical theory of elasticity}]. Moscow,  Nauka Publ., 1966,
708~p. (In Russian)

15. Malkova Yu. V. {\it Nekotorye zadachi dlya dvuhkomponentnoy
ploskosti s krivolineynyimi treshchinami} [{\it Some problems for
bi-material plane with curvilinear cracks}]. Saint Petersburg,
Saint Petersburg State University Publ., 2008, 160~p. (In Russian)



}
