
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Astrom K.~J.} Oscillations in systems with relay feedback~// Adaptive Control, Filtering and Signal Processing.
New York: Springer-Verlag, 1995. P.~1--25.

2. {\it Yu C.-C.} Autotuning of PID controllers: relay feedback approach. New York: Springer-Verlag, 1999. 235~p.

3. {\it Zou X., Siegel R.~A.} Modeling of oscillatory dynamics of a simple enzyme-diffusion system
with hysteresis. The case of lumped permeabilities~// J. Chem. Phys. 1999. Vol.~110. N~4. P.~2267--2279.

4. {\it Northrop R.~B.} Endogenous and exogenous regulation and control of physiological systems.
London: Chapman $\&$ Hall, 2000. 452~p.

5. {\it Li B., Siegel R.~A.} Global analysis of a model pulsing drug delivery oscillator
based on chemomechanical feedback with hysteresis~// Chaos. 2000. Vol.~10. N~3. P.~682--690.

6. {\it Grasman J.} Asymptotic methods for relaxation oscillations and applications.
New York: Springer-Verlag, 1987. 221~p.

7. {\it Jackson E.~A.} Perspectives of nonlinear dynamics. In 2 vol. New York: Cambridge University Press, 1991. Vol.~1. 469~p.; Vol.~2. 633~p.

8. {\it Scott S.~K.} Oscillations, waves and chaos in chemical kinetics. New York: Oxford University Press, 1994. 90~p.

9. {\it Epstein I.~R., Showalter K.} Nonlinear chemical dynamics: Oscillations, patterns, and chaos~// J. Phys. Chem.
1996. Vol.~100. N~31. P.~13132--13147.

10. {\it Macki J.~W., Nistri P., Zecca P.} Mathematical models for hysteresis~//
SIAM Review. 1993. Vol.~35. N~1. P.~94--123.

11. {\it Varigonda S., Georgiou T.~T.} Dynamics of relay relaxation oscillators~//
IEEE Trans. Automat. Control. 2001. Vol.~46. N~1. P.~65--77.

12. {\it Зубов В.~И.} Динамика управляемых систем. СПб.: Изд-во С.-Петерб. ун-та, 2004. 380~с.

13. {\it Александров А.~Ю., Соколов С.~В.} Устойчивость и~оценки
решений некоторых классов нелинейных систем~// Труды Средневолжск.
матем. об-ва. 2005. Т.~7. \No~1. С.~113--123.

14. {\it Barron M.~A., Sen M.} Synchronization of four coupled van der Pol oscillators~// Nonlin. Dyn.
2009. Vol.~56. N~4. P.~357--367.

15. {\it Евстафьева В.~В.} О необходимых условиях существования
периодических решений в динамической системе с~разрывной
нелинейностью и~внешним периодическим воздействием~// Уфимск.
матем. журн. 2011. Т.~3. \No~2. С.~20--27.

16. {\it Кузнецова А.~С.} Динамика системы управления, содержащей ансамбль осцилляторов,
связанных через обратную связь~// Журн. Средневолжск. матем. об-ва. 2011. Т.~13. \No~2. С.~63--69.

17. {\it Balanov Z., Krawcewicz W., Rachinskii D., Zhezherun A.} Hopf bifurcation in symmetric
networks of coupled oscillators with hysteresis~// J. Dyn. Differ. Equations. 2012. Vol.~24. N~4. P.~713--759.

18. {\it Yevstafyeva V.~V.} Existence of the unique $kT$-periodic
solution for one class of nonlinear systems~// J. Sib. Fed. Univ. Math. \& Phys. 2013. Vol.~6. N~1. P.~136--142.

19. {\it Евстафьева В.~В.} Об условиях существования
двухточечно-колебательного периодического решения в~неавтономной
релейной системе с~гурвицевой матрицей~// Автоматика
и~телемеханика. 2015. \No~6. C.~42--56.

20. {\it Камачкин А.~М., Хитров Г.~М., Шамберов В.~Н.} Нормальные
формы матриц в~задачах декомпозиции и~управления многомерных
систем~// Вестн. С.-Петерб. ун-та. Прикладная математика.
Информатика. Процессы управления. 2017. Т.~13. Вып.~4.
С.~417--430.

21. {\it Hooton E., Balanov Z., Krawcewicz W., Rachinskii D.} Noninvasive stabilization of periodic orbits
in $O_4$-symmetrically coupled systems near a Hopf bifurcation point~//
Intern. Journal Bifurcation and Chaos. 2017. Vol.~27. N~6. P.~1750087-1--18.

22. {\it Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V.} Existence of periodic
solutions to automatic control system with relay nonlinearity and sinusoidal
external influence~// Intern. Journal Robust Nonlinear Control. 2017. Vol.~27. N~2. P.~204--211.

23. {\it Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V.} Existence of subharmonic
solutions to a hysteresis system with sinusoidal external influence~//
Electron. Journal Differential Equations. 2017. N~140. P.~1--10.

24. {\it Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V.} On uniqueness and
properties of periodic solution of second-order nonautonomous system with
discontinuous nonlinearity~// J. Dyn. Control Syst. 2017. Vol.~23. N~4. P.~825--837.

25. {\it Евстафьева В.~В.} Периодические решения системы дифференциальных уравнений
с гистерезисной нелинейностью при наличии нулевого собственного
числа~// Укр. матем. журн. 2018. Т.~70. \No~8. С.~1085--1096.

26. {\it Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V.} Existence of periodic
modes in automatic control system with a three-position relay~//
Intern. Journal Control. 2020. Vol.~93. N~4. P.~763--770.

27. {\it Rozikov U.~A.} An introduction to mathematical billiards. Singapore: World Scientific Publishing Co. Pte. Ltd., 2019. 224~p.

\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 17 февраля 2020~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Камачкин Александр Михайлович} --- д-р физ.-мат. наук, проф.; a.kamachkin@spbu.ru

\vskip2mm\textit{Потапов Дмитрий Константинович} --- канд. физ.-мат. наук, доц.; d.potapov@spbu.ru

\vskip2mm\textit{Евстафьева Виктория Викторовна} --- канд. физ.-мат. наук, доц.; v.evstafieva@spbu.ru

}
