
{\normalsize

\vskip 6mm

\noindent{\bf Dynamics and synchronization in feedback cyclic structures\\ with hysteresis oscillators%$\,^*$%
}

}

\vskip 2mm

{\small

\noindent{\it A.~M.~Kamachkin, D.~K.~Potapov, V.~V.~Yevstafyeva%$\,^1$%
%, I.~О. Famylia%$\,^1$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by the Russian
%Scientific Found (grant no.~17-11-017079).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Dynamics and synchronization in feedback cyclic structures
with hysteresis oscillators. {\it Vestnik of Saint~Peters\-burg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p10}--\pageref{p10e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum10  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Consider the dynamics of complex systems with cyclic links. The systems have the ring structures composed of hysteresis-feedback oscillators.
In one of these systems, each oscillator has an additional feedback with the next oscillator. Sufficient conditions for the existence of periodic
and recurrent motions are established. The periodic motion corresponds to a synchronous process occurring in such cyclic structures.
In particular cases, we obtain the conditions for synchronization, as well as the stability conditions for synchronous oscillatory processes.\\[1mm]
\textit{Keywords}: complex system dynamics, cyclic structure, oscillator, hysteresis feedback, syn\-chro\-ni\-zation, stability.
\par}

\vskip 6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Astrom K.~J. Oscillations in systems with relay feedback. {\it Adaptive Control, Filtering and Signal Processing.}
New York, Springer-Verlag Publ., 1995, pp.~1--25.

2. Yu C.-C. {\it Autotuning of PID controllers: relay feedback approach.}
New York, Springer-Verlag Publ., 1999, 235~p.

3. Zou X., Siegel R.~A. Modeling of oscillatory dynamics of a simple enzyme-diffusion system
with hysteresis. The case of lumped permeabilities. {\it J. Chem. Phys.}, 1999, vol.~110, no.~4, pp.~2267--2279.

4. Northrop R.~B. {\it Endogenous and exogenous regulation and control of physiological systems.}
London, Chapman $\&$ Hall Publ., 2000, 452~p.

5. Li B., Siegel R.~A. Global analysis of a model pulsing drug delivery oscillator
based on chemomechanical feedback with hysteresis. {\it Chaos}, 2000, vol.~10, no.~3, pp.~682--690.

6. Grasman J. {\it Asymptotic methods for relaxation oscillations and applications.}
New York, Springer-Verlag Publ., 1987, 221~p.

7. Jackson E.~A. {\it Perspectives of nonlinear dynamics.} In 2 vol. New York, Cambridge University Press, 1991, vol.~1, 469~p., vol.~2, 633~p.

8. Scott S.~K. {\it Oscillations, waves and chaos in chemical kinetics.} New York, Oxford University Press, 1994, 90~p.

9. Epstein I.~R., Showalter K. Nonlinear chemical dynamics: Oscillations, patterns, and chaos. {\it J. Phys. Chem.},
1996, vol.~100, no.~31, pp.~13132--13147.

10. Macki J.~W., Nistri P., Zecca P. Mathematical models for hysteresis. {\it SIAM Review}, 1993, vol.~35, no.~1, pp.~94--123.

11. Varigonda S., Georgiou T.~T. Dynamics of relay relaxation oscillators.
{\it IEEE Trans. Automat. Control}, 2001, vol.~46, no.~1, pp.~65--77.

12. Zubov V.~I. {\it Dinamika upravlyaemykh sistem} [{\it Dynamics of control systems}]. St. Petersburg, Saint Petersburg University Press, 2004,
380~p. (In Russian)

13. Aleksandrov A.~Yu., Sokolov S.~V. Ustojchivost' i otsenki reshenij nekotorykh klassov nelinejnykh sistem
[Stability and estimations of solutions for some classes of nonlinear systems].
{\it Trudy Srednevolzhskogo matematicheskogo obshchestva} [{\it Proc. Middle Volga Math. Soc.}],
2005, vol.~7, no.~1, pp.~113--123. (In Russian)

14. Barron M.~A., Sen M. Synchronization of four coupled van der Pol oscillators. {\it Nonlin. Dyn.},
2009, vol.~56, no.~4, pp.~357--367.

15. Evstaf'eva V.~V. O neobhodimykh usloviyakh sushchestvovaniya periodicheskikh reshenij v dinamicheskoj sisteme s razryvnoj nelinejnost'yu i
vneshnim periodicheskim vozdejstviem [On necessary conditions for existence of periodic solutions in a dynamic system with discontinuous nonlinearity
and an external periodic influence]. {\it Ufimskij matematicheskij zhurnal} [{\it Ufa Math. Journal}], 2011, vol.~3, no.~2, pp.~20--27. (In Russian)

16. Kuznetsova A.~S. Dinamika sistemy upravleniya, soderzhashchej ansambl' ostsillyatorov, svyazannykh cherez obratnuyu svyaz'
[The dynamics of coupled oscillators with a feedback].
{\it Zhurnal Srednevolzhskogo matematicheskogo obshchestva} [{\it Middle Volga Math. Soc. Journal}],
2011, vol.~13, no.~2, pp.~63--69. (In Russian)

17. Balanov Z., Krawcewicz W., Rachinskii D., Zhezherun A. Hopf bifurcation in symmetric
networks of coupled oscillators with hysteresis. {\it J. Dyn. Differ. Equations}, 2012, vol.~24, no.~4, pp.~713--759.

18. Yevstafyeva V.~V. Existence of the unique $kT$-periodic
solution for one class of nonlinear systems. {\it J. Sib. Fed. Univ. Math. {\rm \&} Phys.}, 2013, vol.~6, no.~1, pp.~136--142.

19. Evstaf'eva V.~V. Ob usloviyakh sushchestvovaniya dvukhtochechno-kolebatel'nogo periodichesko\-go resheniya v neavtonomnoj relejnoj sisteme s
gurvitsevoj matritsej [On existence conditions for a two-point oscillating periodic solution in an non-autonomous relay system with a Hurwitz matrix].
{\it Avtomatika i telemekhanika} [{\it Automat. Remote Control}], 2015, no.~6, pp.~42--56. (In Russian)

20. Kamachkin A.~M., Chitrov G.~M., Shamberov V.~N. Normal'nye formy matrits v zadachakh dekompozitsii i upravleniya mnogomernykh sistem
[Normal matrix forms to decomposition and control problems for manydimensional systems].
{\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes},
2017, vol.~13, iss.~4, pp.~417--430. (In Russian)

21. Hooton E., Balanov Z., Krawcewicz W., Rachinskii D. Noninvasive stabilization of periodic orbits
in $O_4$-symmetrically coupled systems near a Hopf bifurcation point.
{\it Intern. Journal Bifurcation and Chaos}, 2017, vol.~27, no.~6, pp.~1750087-1--18.

22. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of periodic
solutions to automatic control system with relay nonlinearity and sinusoidal
external influence. {\it Intern. Journal Robust Nonlinear Control}, 2017, vol.~27, no.~2, pp.~204--211.

23. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of subharmonic
solutions to a hysteresis system with sinusoidal external influence.
{\it Electron. Journal Differential Equations}, 2017, no.~140, pp.~1--10.

24. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. On uniqueness and
properties of periodic solution of second-order nonautonomous system with
discontinuous nonlinearity. {\it J. Dyn. Control Syst.}, 2017, vol.~23, no.~4, pp.~825--837.

25. Evstaf'eva V.~V. Periodicheskie resheniya sistemy differentsial'nykh uravnenij s gisterezisnoj nelinejnost'yu pri nalichii nulevogo
sobstvennogo chisla [Periodic solutions of a system of differential equations with hysteresis nonlinearity in the presence of eigenvalue zero].
{\it Ukrainskij matematicheskij zhurnal} [{\it Ukrainian Math. Journal}], 2018, vol.~70, no.~8, pp.~1085--1096. (In Russian)

26. Kamachkin A.~M., Potapov D.~K., Yevstafyeva V.~V. Existence of periodic modes in automatic control system with a three-position relay.
{\it Intern. Journal Control}, 2020, vol.~93, no.~4, pp.~763--770.

27. Rozikov U.~A. {\it An introduction to mathematical billiards.} Singapore, World Scientific Publishing Co. Pte. Ltd., 2019, 224~p.

\vskip 1.5mm

Received:  February 17, 2020.

Accepted: May 28, 2020.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm \textit{Alexander M. Kamachkin} --- Dr. Sci. in Physics and Mathematics, Professor; a.kamachkin@spbu.ru

\vskip2mm \textit{Dmitriy K. Potapov} --- PhD in Physics and Mathematics, Associate Professor; d.potapov@spbu.ru

\vskip2mm \textit{Victoria V. Yevstafyeva} --- PhD in Physics and
Mathematics, Associate Professor;\\ v.evstafieva@spbu.ru\par
%
}
