
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Isaac C. A., Baker C. J., Mortensen T., van der Werf D.
P., Charlton M.} Compression of positron clouds in the independent
particle regime // Physical Review Letters. 2011. Vol.~107.
P.~033201(1--4).

2. \textit{Isaac C. A.} Motional sideband excitation using
rotating electric fields // Physical Review A. 2013. Vol.~87.
P.~043415(1--7).

3. \textit{Eseev M. K., Meshkov I. N.}  Traps for storing charged
particles and antiparticles in high precision experiments // Phys.
Usp. 2016. Vol.~59. P.~304--317.

4. \textit{Meshkov I. N., Eseev M. K., Ovsyannikov A. D.,
Ovsyannikov D. A., Ponomarev V. A.} Analysis of the particle
dynamics stability in the Penning---Malmberg---Surko trap // Proc.
XXV~Russian Particle Accelerator Conference. Saint Petersburg,
2016. P.~64. doi: 10.18429/JACoW-RuPAC2016-WECAMH03

5. \textit{Meshkov I. N., Ovsyannikov A. D., Ovsyannikov D. A.,
Eseev M. K.} Study of the stability of charged particle dynamics
in a Penning---Malmberg---Surko trap with a rotating field //
Papers of Academy of Science RAN. 2017. Vol.~476, N~6.
P.~630--634. doi: 10.7868/S0869565217300065


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 9 ноября 2018 г.

Cтатья принята к~печати 18 декабря 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Овсянников Александр Дмитриевич}  ---  канд.
физ.-мат. наук, доц.; ovs74@mail.ru

}
