
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. \itshape Koch W., Holthausen M.~C. \upshape A chemist's guide
to density functional theory. Second ed. Weinheim, Germany:
Wiley-VCH Verlag GmbH, 2001. 306~p.

2. \itshape Юренев П. В., Щербинин А. В., Степанов Н. Ф. \upshape
Применимость методов TD-DFT для расчета электронного спектра
поглощения гексаамминорутения (II) в~водном растворе // Журн. физ.
химии. 2010. Т. 84. № 1. С. 44–48.

3. \itshape Tawada  Y., Tsuneda  T., Yanagisawa  S.  \upshape A
long-range-corrected time-dependent density functional theory //
The Journal of Chemical Physics. 2004. Vol. 120. P. 8425.

4. \itshape Maslov~V. \upshape Interpretation of the electronic
spectra of phthalocyanines with transition metals from
quantum-chemical calculations by the density functional method //
Optics and Spectroscopy. 2006. Vol.~101. N 6. P. 853--861.

5. \itshape Safonov A., Bagaturyants A.,   Sazhnikov  V. \upshape
Assessment of TDDFT- and CIS-based methods for calculating
fluorescence spectra of (dibenzoylmethanato)boron difluoride
exciplexes with aromatic hydrocarbons // Journal of Molecular
Modeling. 2017. Vol. 164. N 23. P. 164--167.

6. \itshape Kohn~W., Becke A.  D., Parr  R.  G. \upshape Density
functional theory of electronicstructure // Journal Physical
Chemistry. 1996. Vol. 100. N 31. P. 12974--12980.

7. \itshape Kohn~ W., Sham~ L. \upshape Self-consistent equations
including exchange and correlation effects // Physical Review.
1965. Vol. 140. N 4A. P. A1133--A1138.

8. \itshape Perdew J. P., Wang Y. \upshape Accurate and simple
analytic representation of the electron-gas correlation energy //
Physical Review. 1992. Vol. B45.  P. 13244--13249.

9. \itshape Becke A. D. \upshape Density-functional
exchange-energy approximation with correct asymptotic behaviour //
Physical Review A. 1988. Vol. 38. P. 3098--3100.

10. \itshape Lee C., Yang~W., Parr~R.~G. \upshape Development of
the Colle---Salvetti correlation-energy formula into a functional
of the electron density // Physical Review B. 1988. Vol. 37. N 2.
P. 785--789.


11. \itshape Zhao Y., Truhlar D. \upshape The M06 suite of density
functional for main group thermochemistry, thermochemical
kinetics, noncovalent interactions, excited states, and transition
elements: two new functional and systematic testing of four
M06-class functional and 12 other functional // Theoretical
Chemistry Accounts. 2008. Vol. 120. N 1--3. P. 215--241.

12. \itshape Zhao Y., Truhlar D. \upshape Density functional for
spectroscopy: no long-range self-interaction error, good
performance for rydberg and charge-transfer states, and better
performance on average than B3LYP for ground states // Journal of
Physical Chemistry A. 2006. Vol. 110. N 49. P. 13126--13130.

13. \itshape Adamo C., Barone V. \upshape Toward reliable density
functional methods without adjustable parameters: The PBE0 model
// Journal of Chemical Physics. 1999. Vol. 110. N 13. P.
6158--6170.

14. \itshape Веселова Т. В., Викторова Е. Н., Клочков В. П.,
Макушенко А. М., Резникова И. И., Столбова О. В. \upshape
Спектральные и~люминесцентные свойства фталимидов в~парах
и~растворах // Оптика и~спектроскопия. 1995. Т. 79. № 1. С.
60--76.

15. \itshape Андреева~Т.~А., Бедрина~М.~Е. \upshape Влияние
гибридных потенциалов метода DFT на результаты исследования
жидкокристаллической фазы вещества // Вестн. С.-Петерб. ун-та.
Сер. 10. Прикладная математика. Информатика. Процессы управления.
2015.  Вып. 1. C. 16--25.

16. \itshape Андреева~Т.~А., Бедрина~М.~Е. \upshape  Зависимость
результатов расчета по методу функционала электронной плотности от
способа представления волновой функции // Вестн. С.-Петерб. ун-та.
Прикладная математика. Информатика. Процессы управления. 2018. Т.
14. Вып. 1. C. 52--59.

17.  \itshape Аристов  А. В.,  Семенов С. Г.  \upshape
Квантовомеханическая интерпретация электронных спектров
аминофталимидов в~газовой фазе и~в~растворах // Теоретическая
и~экспериментальная химия. 1984. Т. 28. № 6. С. 713--717.



\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 9 сентября 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip4mm%6mm
К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Андреева Татьяна Анатольевна} --- канд. физ.-мат.
наук, доц.;  \text{t.a.andreeva@spbu.ru}

\vskip2mm\textit{Бедрина Марина Евгеньевна}~--- д-р физ.-мат.
наук, доц.; \text{m.bedrina@spbu.ru}

\vskip2mm\textit{Овсянников Дмитрий Александрович}~--- студент;
\text{d-ovs@yandex.ru}

}
