
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Zaitzev~A., Talashkin~G., Sokolova~Yu. {\em Transport na
magnitnom podvese} [{\em Maglev transportation}]. Saint
Petersburg, Saint Petersburg State Transport University Publ.,
2010, 160~p. (In Russian)

2. Bakhvalov~Yu., Bocharov~V., Vinokurov~V., Nagorsky~V. {\em
Transport s magnitnym podvesom} [{\em Vehicles with magnetic
suspension}]. Eds by V.~Bocharov, V.~Nagorsky. Moscow,
Mashinostroenie Publ., 1991, 320~p. (In Russian)

3. Dzenzersky~V., Omelyanenko~V., Vasiliev~S., Matin~V.,
Sergeev~S. {\em Vysokoskorostnoj magnitnyj transport s
electrodinamicheskoj levitatsiej} [{\em High-speed levitating
transport with electrodynamic suspension}]. Kiev, Naukova dumka
Publ., 2001, 482~p. (In Russian)

4. Kim~K. {\em Sistemy elektrodvizheniya a ispol'zovaniem
magnitnogo podvesa i sverhprovodimosti} [{\em Transportation
systems employing magnetic suspension and superconducting magnet
technology}]. Moscow, Educational and Methodological Centre for
Rail Transport Technology Publ., 2007, 360~p. (In Russian)

5. Glukhih~V., Belyakov~V., Mineev~A. {\em Fiziko-tehnicheskie
osnovy upravlyaemogo termoyadernogo sinteza} [{\em Applied physics
of thermonuclear fusion}]. Saint Petersburg, Saint Petersburg
Polytechnic University Publ., 2006, 348~p. (In Russian)

6. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Baranov~G.~A.,
Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N.,
Gapionok~E.~I., Zaitzev~A.~A., Kaparkova~M.~V., Kukhtin~V.~P.,
Labusov~A.~N., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A.,
Mikhailov~V.~M., Nezhentzev~A.~N., Rodin~I.~Yu., Sytchevsky~S.~E.,
Firsov~A.~A., Khokhlov~M.~V., Shatil~N.~A. Predictive
electromagnetic simulation adapted for maglev railroad system
development. {\em VANT. Series Thermonuclear syntesis}, 2014,
vol.~37, iss.~4, pp.~84--95.

7. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V.,
Belyakov~V.~A., Belyakova~T.~F., Firsov~A.~A., Gapionok~E.~I.,
Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S.,
Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N.,
Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Yu., Shatil~N.~A.,
Sychevsky~S.~E., Vasiliev~V.~N., Zaitzev~A.~A. Simulation of
electrodynamic suspension systems for levitating vehicles. I.
Modelling of electromagnetic behaviour of maglev vehicles with
electrodynamic suspension. {\em Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2014, iss.~4, pp.~5--15.

8. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V.,
Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N., Gapionok~E.~I.,
Zaitzev~A.~A., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A.,
Larionov~M.~S., Maximenkova~~N.~A., Mikhailov~V.~M.,
Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyan\-nikov~A.~D.,
Rodin~I.~Yu., Sychevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Simulation of electrodynamic suspension systems for levitating
vehicles. II. Validation of computational models. {\em Vestnik of
Saint Petersburg University. Series~10. Applied Mathematics.
Computer Science. Control Processes}, 2015, iss.~2, pp.~18--32.

9. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V.,
Belyakov~V.~A., Belyakova~T.~F., Firsov~A.~A., Gapionok~E.~I.,
Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S.,
Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N.,
Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Yu., Shatil~N.~A.,
Sychevsky S.~E., Vasiliev~V.~N., Zaitzev~A.~A. Simulation of
electrodynamic suspension systems for levitating vehicles. III.
Continuous track systems. {\em Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2015, iss.~3, pp.~4--21.

10. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V.,
Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N., Gapionok~E.~I.,
Zaitzev~A.~A., Zenkevich~M.~Yu., Kaparkova~M.~V., Kukhtin~V.~P.,
Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A., Mikhailov~V.~M.,
Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~A.~D.,
Rodin~I.~Yu., Sychevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Simulation of electrodynamic\linebreak\newpage\noindent suspension
systems for levitating vehicles. IV. Discrete track systems. {\em
Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes}, 2016, iss.~3,
pp.~4--17.

11. Zhuravlyov Yu.~N. {\em Aktivnye magnitnye podshipniki.
Teoriya, raschet, primenenie} [{\em Magnetic bearings. Theory,
calculation, application}]. Saint Petersburg, Saint Petersburg
Polytechnika Publ., 2003, 204~p. (In Russian)

12. Bartenev~Yu.~G., Basalov~V.~G., Vargin~A.~M., Vyalukhin~V.~M.,
Dmitriev~N.~A., Zhukov~D.~A., Igrunov~V.~I., Korzakov~V.~N.,
Koshelev~V.~V., Lashmanov~V.~N., Logvin~Yu.~V., Petrik~A.~N.,
Selyakin~A.~G., Semyonov~G.~P., Stryukov~V.~N., Ushakov~A.~Yu.,
Chaika~A.~I., Chernykh~S.~O., Shagaliev~R.~M., Shatokhin~A.~V.,
Shlykov~S.~N., Shmakov~E.~L., Yarulin~D.~R. Multipurpose compact
supercomputer. {\em VANT. Series Mathematic modelling of physical
processes}, 2012, iss.~2, pp.~78--89.

13. Amoskov~V., Arslanova~D., Baranov~G., Bazarov~A., Belyakov~V.,
Firsov~A., Kaparkova~M., Kavin~A., Khokhlov~M., Kukhtin~V.,
Kuzmenkov~V., Labusov~A., Lamzin~E., Lantzetov~A., Larionov~M.,
Nezhentzev~A., Ovsyannikov~D., Ovsyannikov~A., Rodin~I.,
Shatil~N., Sytchevsky~S., Vasiliev~V., Zapretilina~E.,
Zenkevich~M. Modelling EMS maglev systems to develop control
algorithms. {\em Cybernetics and Physics}, 2018, vol.~8, no.~1,
pp.~11--17.

14. Post R.~F., Ryutov D.~D. The Inductrack: A simpler approach to
magnetic levitaiton. Livermore, Lawrence Livermore National
Laboratory Publ., UCRL-ID-124115, May 1996, 10~p.

15. Post R.~F., Ryutov D.~D. The Inductrack approach to magnetic
levitaiton. Livermore, Lawrence Livermore National Laboratory
Publ., UCRL-ID-138593, April 2000, 6~p.

16. Post R.~F. {\em  Inductrack magnet configuration}. U.~S.
Patent no.~6633217, 2003, 13~p.

17. Post R.~F. {\em Laminated track design for Inductrack maglev
systems}. U.~S.~Patent no.~6758146, 2004, 12~p.

18. Hoburg J.~F., Post R.~F. A laminated track for the Inductrack
System. Theory and Experiment. Livermore, Lawrence Livermore
National Laboratory Publ., UCRL-CONF-201819, January 2004, 5~p.

19. Hoburg J.~F., Post R.~F. A laminated track for the Inductrack
System: Theory and Experiment. {\it 18th Intern. Conference on
Magnetically Levitated Systems and Linear Drives}. Shanghai,
China, October 25--29, 2004, 17~p.

20. Halbach~K. Applications of permanent magnets in accelerators
and electron storage rings. {\em Journal of Applied Physics},
1985, vol.~57, p.~3605.

21. Amoskov~V.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F.,
Gribov~Yu.~A., Kukhtin~V.~P., Lamzin~E.~A., Sytchevsky~S.~E.
Computation technology based on KOMPOT and KLONDIKE codes for
magnetostatic simulations in tokamaks. {\em Plasma Devices Oper.},
2008, vol.~16, p.~89.

22. Belov~A., Doinikov~N., Duke~A., Kokotkov~V., Korolkov~M.,
Kotov~V., Kukhtin~V., Lamzin~E., Sytchevsky~S. Transient
electromagnetic analysis in tokamaks using TYPHOON code. {\em
Fusion Engineering and Design}, 1996, vol.~31, pp.~167--180.

23. Amoskov~V., Arslanova~D., Belov~A., Belyakov~V., Belyakova~T.,
Gapionok~E., Krylova~N., Kukhtin~V., Lamzin~E., Maximenkova~N.,
Mazul~I., Sytchevsky~S. Global computational models for EM
transient analysis and design optimization of the ITER machine.
{\em Fusion Eng. Des.}, Sept.~2012, vol.~87, pp.~1519--1532.

24. Belov~A., Belyakova~T., Gornikel~I., Kuchinsky~V., Kukhtin~V.,
Lamzin~E., Semchenkov~A., Shatil~N., Sytchevsky~S. 3D field
simulation of complex systems with permanent magnets and
excitation coils. {\em IEEE Transactions on Applied
Superconductivity}, 2008, vol.~18, no.~2, pp.~1609--1612.

25. Tamm~I. {\em Fundamentals of the theory of electricity}.
Moscow, Mir Publ., 1979, 695~p.

26. Shneerson~G. {\em Polya i perehodnye processy v apparature
sverhsil'nyh tokov} [{\em Fields and transients in high-power
facilities}]. Moscow, Energoatomizdat Publ., 1992, 413~p. (In
Russian)

27. Koskin Yu. P., Tzeitlin L. A. {\em Sinhronnye mashiny s
nemagnitnym rotorom} [{\em Synchronous machi\-nes with
non-magnetic rotor}]. Leningrad, Energoatomizdat Publ., 1990,
279~p. (In Russian)

28. Amoskov~V.~M., Arslanova~D.~N., Belov~A.~V., Belyakov~V.~A.,
Vasiliev~V.~N., Glukhih~V.~A., Zaitzev~A.~A., Kaparkova~M.~V.,
Korotkov~V.~A., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S.,
Mikhailov~V.~M., Nezhentzev~A.~N., Rodin~I.~Yu., Sychevsky~S.~E.,
Filatov~O.~G., Firsov~A.~A., Shatil~N.~A. {\em Kombinirovannyj
magnitnyj podves transportnogo sredstva} [{\em Hybrid
electromagnetic suspension system for levitated vehicles}].
Russian patent no.~2573524, 2014, 14~p. (In Russian)

29. Amoskov~V.~M., Arslanova~D.~N., Belov~A.~V., Belyakov~V.~A.,
Vasiliev~V.~N., Kaparkova~M.~V., Korotkov~V.~A., Kukhtin~V.~P.,
Lamzin~E.~A., Larionov~M.~S., Mikhailov~V.~M., Nezhentzev~A.~N.,
Rodin~I.~Yu., Sychevsky~S.~E., Filatov~O.~G., Firsov~A.~A.,
Shatil~N.~A. {\em Elektromagnitnoe ustrojstvo, puteprovod i
transportnoe sredstvo, snabzhennye takim ustrojstvom} [{\em An
electromagnetic suspension, a track, and a levitated vechicle}].
Russian patent no.~2579416, 2014, 29~p. (In Russian)

30. Amoskov~V.~M., Arslanova~D.~N., Belov~A.~V., Belyakov~V.~A.,
Vasiliev~V.~N., Glukhih~V.~A., Zaitzev~A.~A., Kaparkova~M.~V.,
Korotkov~V.~A., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S.,
Mizintzev~A.~V., Mikhailov~V.~M., Nezhentzev~A.~N.~, Rodin~I.~Yu.,
Sychevsky~S.~E., Filatov~O.~G., Firsov~A.~A., Shatil~N.~A. {\em
Magnitnyj podves transportnogo sredstva dlya kombinirovannogo
puteprovoda} [{\em An electromagnetic suspension system for a
combined-type track}]. Russian patent no.~2573135, 2014, 20~p. (In
Russian)

31. Amoskov~V.~M., Arslanova~D.~N., Belov~A.~V., Belyakov~V.~A.,
Vasiliev~V.~N., Kaparkova~M.~V., Korotkov~V.~A., Kukhtin~V.~P.,
Lamzin~E.~A., Larionov~M.~S., Mikhailov~V.~M., Nezhentzev~A.~N.,
Rodin~I.~Yu., Sychevsky~S.~E., Filatov~O.~G., Firsov~A.~A.,
Shatil~N.~A. {\em Sverhprovodyatshee elektromagnitnoe ustrojstvo,
magnitnyj podves i transportnoe sredstvo, snabzhennye takim
ustrojstvom} [{\em A superconductions electromagnetic suspension,
a track, and a levitated vechicle}]. Russian patent no.~2566507,
2014, 24~p. (In Russian)

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent
Received:  August 27, 2018.

Accepted: September 25, 2018.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Victor M. Amoskov} --- PhD in Physics and
Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Daria N. Arslanova} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Alexandr M. Bazarov} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Alexandr V. Belov} --- Leading scientist;
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Valery A. Belyakov} --- Dr. Sci. in Physics and
Mathematics, Professor; belyakov@sintez.niiefa.spb.su

\vskip2mm\textit{Alexey A. Firsov} --- sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Elena I. Gapionok} --- sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Marina V. Kaparkova} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Vladimir P. Kukhtin} --- PhD in Physics and
Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Evgeny A. Lamzin} --- Dr. Sci. in Physics and
Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Mikhail S. Larionov} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Alexandr V. Mizintzev} --- PhD in Technics;
 info@nfenergo.ru

\vskip2mm\textit{Valery M. Mikhailov} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Andrey N. Nezhentzev} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Dmitrij A. Ovsyannikov} --- Dr. Sci. in Physics
and Mathematics, Professor; dovs45@mail.ru

\vskip2mm\textit{Alexandr D. Ovsyannikov} --- PhD in Physics and
Mathematics, Assistant Professor; ovc74@mail.ru

\vskip2mm\textit{Igor Yu. Rodin} --- PhD in Technics;
rodin@sintez.niiefa.spb.su

\vskip2mm\textit{Nikolay A. Shatil} --- PhD in Technics;
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Sergey E. Sytchevsky} --- Dr. Sci. in Physics and
Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Vyacheslav N. Vasiliev} ---
sytch@sintez.niiefa.spb.su

\vskip2mm\textit{Margarita Yu. Zenkevich} --- PhD in Chemistry;
m.sorbent@mail.ru

}
