
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Пых Ю. А.} Равновесие и~устойчивость в~моделях
популяционной динамики. М.: Наука, 1983. 182~c.

2. {\it Свирежев Ю. М., Логофет Д. О.} Устойчивость биологических
сообществ. М.: Наука, 1978. 352~с.

3. {\it Hofbauer J., Sigmund K.} Evolutionary games and population
dynamics. Cambridge: Cambridge University Press, 1998. 323~p.


4. {\it Britton N. F.} Essential mathematical biology. London;
Berlin; Heidelberg: Springer,  2003. 335~p.





5. {\it  Yoshizawa~T.} Stability theory by Liapunov's second
method. Tokyo: The Math. Soc. of  Japan, 1966. 223~p.



6. {\it Подвальный С. Л., Провоторов В. В.} Стартовое управление
параболической системой с~распределенными параметрами на графе
 //  Вестн. С.-Петерб. ун-та.
Сер.~10. Прикладная математика. Информатика. Процессы управления.
2015. Вып. 3. C.~126--142.


7. {\it Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A.}
Unique weak solvability of a nonlinear ini\-tial boundary value
problem with distributed parameters in a netlike domain
 //  Вестн. С.-Петерб. ун-та.
%Сер.~10:
Прикладная математика. Информатика. Процессы управления.  2017. Т.
13. Вып. 3. C.~264--277.
%doi:  10.21638/11701/spbu10.2017.304


8. {\it Aleksandrov A., Mason O.} Diagonal stability of a class of
discrete-time positive switched systems with delay
// IET Control Theory \& Applications. 2018. Vol.~12. N~6. P.~812--818.



9. {\it Chen F., Wu L., Li Z.} Permanence and global attractivity
of the discrete Gilpin---Ayala type population model // Computers
and Mathematics with Applications. 2007. Vol.~53. P.~1214--1227.


10. {\it Lu Z., Wang W.}  Permanence and global attractivity for
Lotka---Volterra difference systems // J. Math. Biol. 1999. Vol.
39. P. 269--282.


  11. {\it Kaszkurewicz E., Bhaya A.} Matrix diagonal stability in systems and
computation. Boston; Basel; Berlin: Birkhauser, 1999. 267~p.


12.  {\it Chen F.} Some new results on the permanence and
extinction of nonautonomous Gilpin---Ayala type competition model
with delays // Nonlinear Analysis: Real World Applications. 2006.
Vol.~7. P.~1205--1222.





13. {\it Зубов В. И.} Независимость эволюционного развития видов
от последействий // Докл. РАН. 1992. Т.~323. № 4. С.~632--635.


14. {\it Lu G., Lu Zh., Enatsu Y.} Permanence for Lotka---Volterra
systems with multiple delays // {Nonlinear Analysis: Real World
Applications}. 2011. Vol. 12. N~5. P.~2552--2560.



15. {\it Bao J., Mao X., Yin G., Yuan C.} Competitive
Lotka---Volterra population dynamics with jumps // {Nonlinear
Analysis}. 2011. Vol. 74. P. 6601--6616.



 16. {\it Zhu C., Yin G.}
On hybrid competitive Lotka---Volterra ecosystems // Nonlinear
Analysis. 2009. Vol. 71. P. 1370--1379.




17. {\it  Aleksandrov A. Yu.,  Aleksandrova E. B.,  Platonov A.
V.}
 Ultimate boundedness conditions for a hybrid model of population dynamics //
Proc. 21st Mediterranean conference on Control and Automation,
June 25--28, 2013. Platanias-Chania, Crite,  Greece, 2013.
P.~622--627.


18. {\it Aleksandrov A. Yu., Chen Y., Platonov A. V.} Permanence
and ultimate boundedness  for discrete-time switched models of
population dynamics // {Nonlinear Dynamics and Systems Theory}.
2014. Vol.~14. N~1. P.~1--10.


19. {\it Александров А. Ю., Платонов  А. В.} О предельной
ограниченности и~перманентности решений одного класса дискретных
моделей динамики популяций с~переключениями
 //
Вестн. С.-Петерб. ун-та. Сер. 10. Прикладная математика.
Информатика. Процессы управления.
 2014.  Вып. 1. С. 5--16.


20. {\it Nakata Y., Muroya Y.} Permanence for nonautonomous
Lotka---Volterra cooperative systems with delays // Nonlinear
Analysis. 2010. Vol.~11. P.~528--534.


21. {\it Lu G., Lu Z., Lian X.} Delay effect on the permanence for
Lotka---Volterra cooperative system // Nonlinear Analysis. 2010.
Vol.~11. P.~2810--2816.


22. {\it Xu R., Wang Z.} Periodic solutions of a nonautonomous
predator-prey system with stage structure and time delays // J.
Comput. Appl. Math. 2006. Vol. 196. P.~70--86.

23. {\it Jingru Z., Chen L.} Permanence and global stability for a
two-species cooperative system with time delays in a two-patch
environment //
 Comput. Math. Appl. 1996. Vol.~32. P.~101--108.


24. {\it Xu R., Chaplain M. A. J., Davidson F. A.} Permanence and
periodicity of a delayed ratio-dependent predator-prey model with
stage structure // J. Math. Anal. Appl. 2005. Vol.~303.
P.~602--621.



    25.             {\it Александров А. Ю., Воробьева А. А., Колпак Е. П.}
О диагональной устойчивости некоторых классов сложных систем
с~запаздыванием // Вестн. С.-Петерб. ун-та. Прикладная математика.
Информатика. Процессы управления. 2018. Т. 14. Вып. 2. С. 72--88.






26. {\it Liberzon D.,  Morse A. S.} Basic problems in stability
and design of switched systems // IEEE Control Systems Magazine.
1999. Vol.~19. N~15. P.~59--70.


27. {\it Shorten R.,  Wirth F.,  Mason O.,  Wulf K., King C.}
Stability criteria for switched and hybrid systems // SIAM Rev.
2007. Vol. 49. N~4. P. 545--592.



28. {\it Aleksandrov A., Mason O.} Absolute stability and
Lyapunov---Krasovskii functionals for switched nonlinear systems
with time-delay // Journal of the Franklin Institute. 2014. Vol.
351. P. 4381--4394.


\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 1 апреля 2020~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip4.5mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Александров Александр Юрьевич} --- д-р физ.-мат.
наук,  проф.; a.u.aleksandrov@spbu.ru

}
