
{\normalsize

\vskip 5mm%6mm

\noindent{\bf Permanence conditions for models of population
dynamics\\
with switches and delay$\,^*$%
}

}

\vskip 2mm

{\small

\noindent{\it A. Yu. Aleksandrov%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was  supported by the
Russian Foundation for Basic Research (grant N 19-01-00146-a).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation


%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Aleksandrov A. Yu. Permanence
conditions for models of population dynamics with switches and
delay. {\it Vestnik of Saint~Peters\-burg Uni\-versity. Applied
Mathematics. Computer Science. Control Processes}, \issueyear,
vol.~16, iss.~\issuenum, pp.~\pageref{p1}--\pageref{p1e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum01  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Some classes of discrete and continuous
generalized Volterra models of population dynamics with parameter
switching and constant delay are studied. It is assumed that there
are relationships of the type ``symbiosis'', ``compensationism''
or ``neutralism'' between any two species in a biological
community. The goal of the work is to obtain sufficient conditions
for the permanence of such mo\-dels. Original constructions of
common Lyapunov---Krasovsky functionals are proposed for families
of subsystems corresponding to the switched systems under
consideration. Using the constructed functionals, conditions are
derived that guarantee permanence for any admissible switching
laws and any constant nonnegative delay. These conditions are
constructive and are formulated in terms of the existence of a
positive solution for an auxiliary system of linear algebraic
inequalities. It should be noted that, in the proved theorems, the
persistence of the systems is ensured by the positive coefficients
of natural growth and the beneficial effect of populations on each
other, whereas the ultimate boundedness
 of species numbers is provided by the intraspecific competition.
An example is presented  demonstrating the effectiveness of the
developed approaches.\\[1mm]
\textit{Keywords}: population dynamics,  permanence, ultimate
boundedness, switches, delay,  Lya\-pu\-nov---Krasovskii
functional.
\par}

\vskip 6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Pykh Yu. A.} {\it Ravnovesie i ustojchivost' v modeljah
populjacionnoj dinamiki} [{\it Equilibrium and stability in models
of population dynamics}]. Moscow, Nauka Publ., 1983, 182~p. (In
Russian)


2.  Svirezhev Yu. M., Logofet D. O. {\it Ustojchivost'
biologicheskih soobshhestv} [{\it Stability of biolojical
communities}]. Moscow, Nauka Publ., 1978, 352~p. (In Russian)

3. {Hofbauer J., Sigmund K.} {\it Evolutionary games and
population dynamics.} Cambridge, Cambridge University Press, 1998,
323~p.

4. { Britton N. F.} {\it Essential mathematical biology}. London,
Berlin, Heidelberg, Springer Publ.,  2003, 335~p.




{5.} {Yoshizawa~T.} {\it Stability theory by Liapunov's second
method}. Tokyo, The Math. Soc. of  Japan Publ., 1966, 223~p.





6. {Podval'nyi S. L., Provotorov V. V.}  {Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe}
[Start control of a parabolic system with distributed parameters
on a graph]. {\it Vestnik of Saint Petersburg University. Series
10.  Applied Mathematics. Computer Science. Control Processes},
 2015, iss.~3, pp.~126--142. (In Russian)


7. {Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A.}
Unique weak solvability of a nonlinear initial boundary value
problem with distributed parameters in a netlike domain. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes},
 2017, vol.~13, iss.~3, pp.~264--277.
%DOI:  10.21638/11701/spbu10.2017.304


8. { Aleksandrov A., Mason O.} Diagonal stability of a class of
discrete-time positive switched systems with delay. {\it IET
Control Theory $\&$ Applications}, 2018, vol.~12, N~6,
pp.~812--818.


9. {Chen F., Wu L., Li Z.} Permanence and global attractivity of
the discrete Gilpin---Ayala type population model. {\it Computers
and Mathematics with Applications}, 2007, vol.~53, pp.~1214--1227.


10. {Lu Z., Wang W.}  Permanence and global attractivity for
Lotka---Volterra difference systems. {\it  J. Math. Biol.}, 1999,
vol. 39, pp. 269--282.


11. { Kaszkurewicz E., Bhaya A.} {\it Matrix diagonal stability in
systems and computation.} Boston, Basel, Berlin, Birkhauser Press,
1999, 267~p.


12.  {Chen F.} Some new results on the permanence and extinction
of nonautonomous Gilpin---Ayala type competition model with delays.
{\it Nonlinear Analysis: Real World Applications}, 2006, vol.~7,
pp. 1205--1222.






13. Zubov V. I. Nezavisimost' jevoljucionnogo razvitija vidov ot
posledejstvij [Independence of evolutionary development of species
from aftereffects]. {\it Doklady RAN} [Proceedings of Russian
Academy of Sciences], 1992, vol.~323, N~4, pp.~632--635. (In
Russian)



14. Lu G., Lu Zh., Enatsu Y. Permanence for Lotka---Volterra systems
with multiple delays. {\it Nonlinear Analysis: Real World
Applications}, 2011, vol. 12, N~5, pp.~2552--2560.


    15. Bao J., Mao X., Yin G., Yuan C. Competitive Lotka---Volterra population
dynamics with jumps. {\it Nonlinear Analysis}, 2011, vol. 74, pp.
6601--6616.



 16. {Zhu C., Yin G.}
On hybrid competitive Lotka---Volterra ecosystems. {\it Nonlinear
Analysis}, 2009, vol.~71, pp. 1370--1379.










17. {Aleksandrov A. Yu.,  Aleksandrova E. B.,  Platonov A. V.}
 Ultimate boundedness conditions for a hybrid model of population dynamics.
{\it Proc. 21st Mediterranean conference on Control and
Automation},  June 25--28, 2013. Platanias-Chania, Crite,  Greece,
2013, pp.~622--627.


18. {Aleksandrov A. Yu., Chen Y., Platonov A. V.} Permanence and
ultimate boundedness  for discrete-time switched models of
population dynamics. {\it Nonlinear Dynamics and Systems Theory},
2014, vol.~14, N~1, pp.~1--10.




19. Aleksandrov A. Yu., Platonov A. V. O predel'noj
ogranichennosti i permanentnosti re\-she\-nij odnogo klassa
diskretnyh modelej dinamiki populjacij s perekljuchenijami [On the
ultimate boundedness and permanence of solutions for a class of
discree-time switched models of population dynamics]. {\it Vestnik
of Saint Petersburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes,}
 2014,  iss. 1,
pp.~5--16. (In Russian)







20. Nakata Y., Muroya Y. Permanence for nonautonomous
Lotka---Volterra cooperative systems with delays. {\it Nonlinear
Analysis}, 2010, vol. 11, pp.~528--534.



21. Lu G., Lu Z., Lian X. Delay effect on the permanence for
Lotka---Volterra cooperative system. {\it Nonlinear Analysis},
2010, vol.~11, pp.~2810--2816.

22. Xu R., Wang Z. Periodic solutions of a nonautonomous
predator-prey system with stage structure and time delays. {\it J.
Comput. Appl. Math.}, 2006, vol.~196, pp.~70--86.

23. Jingru Z., Chen L. Permanence and global stability for a
two-species cooperative system with time delays in a two-patch
environment. {\it Comput. Math. Appl.}, 1996, vol.~32,
pp.~101--108.


24. Xu R., Chaplain M. A. J., Davidson F. A. Permanence and
periodicity of a delayed ratio-dependent predator-prey model with
stage structure. {\it J. Math. Anal. Appl.}, 2005, vol.~303,
pp.~602--621.





25. Aleksandrov A. Yu., Vorob'eva A. A., Kolpak E. P. O
diagonal'noj ustojchivosti nekotoryh klassov slozhnyh sistem s
zapazdyvaniem [On the diagonal stability of some classes of
complex systems]. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes,}
 2018, vol.~14, iss. 2,
pp. 72--88. (In Russian)


26. {Liberzon D.,  Morse A. S.} Basic problems in stability and
design of switched systems.
 {\it IEEE Control Systems Magazine},  1999, vol.~19, N~15,
pp.~59--70.


27. {Shorten R.,  Wirth F.,  Mason O.,  Wulf K., King C.}
Stability criteria for switched and hybrid systems. {\it SIAM
Rev.,} 2007, vol. 49, N~4, pp. 545--592.


28. Aleksandrov A., Mason O. Absolute stability and
Lyapunov---Krasovskii functionals for switched nonlinear systems
with time-delay. {\it Journal of the Franklin Institute}, 2014,
vol. 351, pp.~4381--4394.

\vskip 1.5mm

Received:  April 01, 2020.

Accepted: May 28, 2020.


\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm \textit{Alexander Yu. Aleksandrov} --- Dr. Sci. in
Physics and Mathematics, Professor;\\ a.u.aleksandrov@spbu.ru
%
}
