

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1.	Von Bekesy G. \"Ueber die Empfindlichkeit des stehenden und sitzenedn Men\-schen gegen sinusf\"ormige Ersch\"utterungen [About the sensitivity of standing and sitting people to sinusoidal vibrations]. {\it Akustische Zeitschrift}, 1939, vol.~4, pp.~360--369.

2.	Coermann R. R. The mechanical impedance of the human body in sitting and standing position at low frequencies. {\it Human factor}, 1962, vol.~4, pp.~227--253.

3.	Griffin M. J. Vertical vibration of seated subjects: effects of posture, vibration level, and frequency. {\it Aviation Space and Environmental Medicine}, 1975, vol.~46, pp.~269--276.

4. Paddan G.\,S., Griffin M.\,J. A review of the transmission of translational seat vibration to the head. {\it J. of Sound and Vibration}, 1998, vol.~215, iss.~4, pp.~863--882.

5.	Paddan G.\,S., Griffin M.\,J. The transmission of translational seat vibration to the head---I. Vertical seat vibration. {\it J. of Biomechanics}, 1988, vol.~21, iss.~3, pp.~191--197.

6.	Fairley T.\,E., Griffin M.\,J. The apparent mass of the seated human body. Vertical vibration.  {\it J. of Biomechanics}, 1989, vol.~22, no.~2, pp.~81--94.

7. Potemkin B. A., Frolov K. V. Postroenie dinamitheskoy modeli tela thelove\-ka-operatora, podverzhennogo deistviju shirokopolosnih sluthainih vibratsiy [Cons\-truc\-tion of dynamic model of human body for man-operator exposed to broad\-band random vibra\-tions]. {\it Vibration-Isolation of Machine and Vibration-Protec\-tion of Man-Operator}. Ed. by K.~V.~Frolov. Moscow, Nauka Publ., 1973, pp.~17--30. (In Russian)

8.	Muksian R., Nash C.\,D. A model for response of seated humans to sinusoidal displacements of the seat. {\it J. of Biomechanics}, 1974, vol.~7, pp.~207--215.

9.	Muksian R., Nash C.\,D. On frequency-depended damping coefficient in lum\-ped-parameter models of human being. {\it J. of Biomechanics}, 1976, vol.~9, pp.~339--342.

10.	Wan~Y., Schimmels~J.\:M. A Simple model that captures the essential dy\-na\-mics of a seated human exposed to whole body vibration. {\it Advances in Bioen\-gi\-nee\-ring}, 1995, vol.~31, ASME-Publ. (Bioengineering Division), pp.~333--334.

11. {Matsumoto Y., Griffin M.\,J.} Modelling the dynamic mechanisms associated with the principal resonance of the seated human body. {\it Clinical Biomechanics}, 2001, vol.~16, suppl.~1,  pp.~S31--S44.

12. {Bai X.-X., Xu S.-X., Cheng W., Qian L.-J.} On 4-degree-of-freedom bio\-dynamic models of seated occupants: Lumped-parameter modeling. {\it J. of Sound and Vibration}, 2017, vol.~402, no.~18, pp.~122--141.

13.	{Abbas~W., Abouelatta~O.\:B., El-Azab~M., Elsaidy~M., Megahed~A.\:A.}  Op\-ti\-mi\-za\-tion of biodynamic seated human models using genetic algorithms. {\it  En\-gi\-nee\-ring}, 2010, vol.~2, pp.~710--719.

14.  Boileau P.-\’{E}., Rakheja S. Whole-body vertical biodynamic response charac\-teristics of the seated vehicle driver: measurement and model development. {\it Intern. J. of Ind. Ergonomics}, 1998, vol.~22, pp.~449--472.

15. Zhang E., Xu L. A., Liu Z. H., Li X. L. Dynamic modeling and vibration cha\-rac\-te\-ris\-tics of multi-DOF upper part system of seated human body. {\it Chine Journal of En\-gi\-nee\-ring Design}, 2008, vol.~15, pp.~244--249.

16. {Yoshimura T., Nakai K., Tamaoki G.} Multi-body dynamics modelling of seated human body under exposure to whole-body vibration. {\it Industrial Health}, 2005, vol.~43, pp.~441--447.

17. {Tregubov~V.~P., Egorova~ N.~K.} Model'noe izuchenie vliianiia mnogosustavnykh myshts na chastotnye kharakteristiki tela cheloveka [Model study of the influence of multi-joint muscles on the frequency characteristics of the human body]. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~2, pp.~150--164. \\ https://doi.org/10.21638/11701/spbu10.2020.207 (In Russian)



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 10, 2022.

Accepted: February 01, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Vladimir P. Tregubov} --- Dr. Sci. in Physics and Mathematics, Professor; v.tregubov@spbu.ru \par


\vskip 2mm
 \textit{Nadezhda K. Egorova} --- Postgraduate Student; nadezhda\_ego@mail.ru \par
%
%
}
