
{\small

%\vskip6mm
\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. {\it Brinker F.} Commissioning of the European XFEL injector // Proceedings of the Intern. Particle Accel. Conference IPAC'16. Busan, 2016. P.~1044--1047.
    	
2. {\it Dowell D.~H.},  {\it Akre R.}, {\it Ding Y.}, {\it Emma P.}, {\it Frisch J.}, {\it Gilevich~S.},  {\it Hays~G.}, {\it Hering~Ph.}, {\it Huang~Z.}, {\it Iverson~R.}, {\it Limborg-Deprey~C.}, {\it Loos~H.}, {\it Miahnahri~A.}, {\it Schmerge~J.}, {\it Turner~J.}, {\it Welch~J.}, {\it White~W.}, {\it Wu~J.}, {\it Froelich~L.}, {\it Limberg~T.}, {\it Prat E}. Commissioning results or the LCLS injector // Proceedings of 29$^{\rm th}$ Intern. Free Electron Laser Conference FEL’2007. Novosibirsk, 2007. P.~276--278.
    	
3. {\it Feinberg Ya.~B.} Particles acceleration in plasma // Sov. Atomic Energy. 1959. N~6. 431~p.
    	
4.  {\it Muggli~P.}, {\it Kimura~W.}, {\it Kallos~E.}, {\it Katsouleas~T.}, {\it Kusche~K.}, {\it Pavlishin~I.}, {\it Stolyarov~D.}, {\it Ya\-ki\-menko~V.} Plasma wakefield acceleration experiments using two subpicosecond electron bunches // Pro\-cee\-dings of 22$^{\rm nd}$~Par\-tic\-le Accel. Conference PAC’07. Albuquerque, 2007. P.~3073--3075.
    	
5.  {\it Hogan M.~J.}, {\it Barnes C.~D.}, {\it Clayton C.~E.}, {\it Decker F.~J.}, {\it Deng S.}, {\it Emma~P.}, {\it Huang~C.}, {\it Iver\-son~R.~H.}, {\it Johnson~D.~K.}, {\it Joshi~C.}, {\it Katsouleas~T.}, {\it Krejcik~P.}, {\it Lu~W.}, {\it Marsh~K.~A.}, {\it Mori~W.~B.}, {\it Mugg\-li~P.}, {\it O’Connell~C.~L.}, {\it Oz~E.}, {\it Siemann~R.~H.}, {\it Walz~D}. Multi-GeV energy gain in a plasma-wakefield accelerator // Phys. Rev. Lett. 2005. Vol.~95. Iss.~054802. P.~1--4.
    	
6.  {\it Tajima T.}, {\it Dowson J.~M}. Laser electron accelerator // Phys. Rev. Lett. 1979. Vol.~43. Iss.~4. P.~267--270.
    	
7. {\it Leemans W.}, {\it Esarey E.} Laser-driven plasma-wave electron accelerators // Phys. Today. 2009. Vol.~62. P.~44.
    	
8. {\it Leurent V.}, {\it Michel P.}, {\it Clayton C.~E.}, {\it Pollock B.}, {\it Doeppner T.}, {\it Ralph J.}, {\it Pak A.}, {\it Wang T.}, {\it Joshi C.}, {\it Tynan G.}, {\it Divol L.}, {\it Palastro J.}, {\it Glenzer S.}, {\it Froula D}. Experimental demonstration of $X$-ray betatron radiation spectrum from laser accelerated electron beams // Proceedings of 11$^{\rm th}$ European Particle Accel. Conference EPAC’08. Genoa, 2008. P.~2809--2811.
    	
9. {\it Wiggins S.~M.}, {\it Welsh G.~H.}, {\it Wiggins S.~M.}, {\it Welsh G.~H.}, {\it Issac R.~C.}, {\it Brunetti E.}, {\it Shanks R.~P.}, {\it Cipiccia S.}, {\it Anania M.~P.}, {\it Manahan G.~G.}, {\it Aniculaesei C.}, {\it Ersfeld B.}, {\it Islam M.~R.}, {\it Jaroszynski D.~A.}, {\it Gillespie W.~A.}, {\it MacLeod A.~M}. The production of high quality electron beams in the ALPHA-X laser wakefield accelerator // Proceedings of 2$^{\rm nd}$ Intern. Particle Accel. Conference IPAC’11. Geneva, 2011. P.~1956--1958.
    	
10. {\it Leemans W.}, {\it Esarey E.}, {\it Geddes C.~G.~R.}, {\it Schroeder C.~B.}, {\it Toth Cs.}, {\it Van Tilborg J.}, {\it Ca\-ry~J.~R.}, {\it Nieter C}. Mono-energetic beams from laser plasma interactions // Proceedings of Particle Accel. Conference PAC’05. Knoxville, 2005. P.~69--71.
    	
11. {\it Kotaki H.}, {\it Hayashi Y.}, {\it Kawase K.}, {\it Mori M.}, {\it Kando M.}, {\it Homma T.}, {\it Koga J.~K.}, {\it Bulanov S.~V.} Control and pulsewidth-measurement of laser accelerated electron beams // Proceedings of the 1$^{\rm st}$ Intern. Particle Accel. Conference IPAC’10. Kyoto, 2010. P.~3608--3610.
    	
12. {\it Yamazaki A.}, {\it Maekawa A.}, {\it Tsujii R.}, {\it Uesaka M.}, {\it Kinoshita K.}, {\it Hosokai T.}, {\it Zhidkov A.} Manipulation of electron beam generation with modified magnetic circuit on laser-wakefield acceleration // Proceedings of 22$^{\rm nd}$ Particle Accel. Conference PAC’07. Albuquerque, 2007. P.~2790--2792.
    	
13. {\it Clayton C.}, {\it Ralph J.}, {\it Albert F.}, {\it Fonseca R.}, {\it Glenzer S.}, {\it Joshi C.}, {\it Lu W.}, {\it Marsh K.}, {\it Martins S.}, {\it Mori W.}, {\it Pak A.}, {\it Tsung F.}, {\it Pollock B.}, {\it Ross J.}, {\it Silva L.}, {\it Froula D}. Laser wakefield acceleration beyond 1 GeV using ionization induced injection // Proceedings of 11$^{\rm th}$ Particle Accel. Conference PAC’11. Rochester, 2011. P.~707--711.
    	
14. {\it Hubbard R.~F.}, {\it Gordon D.~F.}, {\it Jones T.~G.}, {\it Penano J.~R.}, {\it Sprangle P.}, {\it Ting A.}, {\it Hafizi B.}, {\it Zig\-ler~A.}, {\it Kaganovich~D.} Simulation of accelerated electron spectra in laser wakefield accelerators // Proceedings of Particle Accel. Conference PAC’03. Portland, 2003. P.~716--718.
    	
15. {\it Malka V.}, {\it Faure J.}, {\it Glinec Y.}, {\it Lifschitz A}. Laser-plasma wakefield acceleration: concepts, tests and premises // Proceedings of European Particle Accel. Conference EPAC’06. Edinburgh, 2006. P.~10--13.
    	
16. {\it Bulanov S.}, {\it Naumova N.}, {\it Pegoraro F.}, {\it Sakai J.} Particle injection into the wave acceleration phase due to nonlinear wake wave breaking // Phys. Rev.~E. 1998. Vol.~58. N~R5257.
    	
17. {\it Bulanov S.~V.}, {\it Brantov A.~V.}, {\it Esirkepov T.~Zh.}, {\it Kando M.}, {\it Kotaki H.}, {\it Bychenkov V.} Controlled electron injection into the wake wave using plasma density inhomogeneity // Physics of Plasmas. 2008. Vol.~15. N~073111.
    	
18. {\it Bulanov S.~V.}, {\it Tajima T.}, {\it Esirkepov T.}, {\it Pirozhkov A.}, {\it Jinglong~Ma}, {\it Kando M.}, {\it Fukuda Y.}, {\it Chen~L.}, {\it Daito I.}, {\it Ogura K.}, {\it Homma T.}, {\it Hayashi Y.}, {\it Kotaki H.}, {\it Sagisaka A.}, {\it Mori M.}, {\it Koga J.}, {\it Ka\-wa\-chi~T.}, {\it Daido H.}, {\it Kimura T.}, {\it Kato Y.} Frequency multiplication of light back reflected from a relativistic wake wave // Phys. of Plasmas. 2007. Vol.~14. N~123106.
    	
19. {\it Tomassini P.}, {\it Galimberti M.}, {\it Giulietti A.}, {\it Giulietti D.}, {\it Gizzi L.~A.}, {\it Labate L.}, {\it Pegoraro F.} Production of high-quality electron beams in numerical experiments of laser wakefield acceleration with longitudinal wave breaking // Phys. Rev. Spec. Topics  Acc. and Beams. 2003. Vol.~6. N~121301.
    	
20. {\it Umstadter D.}, {\it Kim J.~K.}, {\it Dodd E.} Laser injection of ultrashort electron pulses into wakefield plasma waves // Phys. Rev. Lett. 1996. Vol.~76. P.~2073--2076.
    	
21. {\it Esarey E.}, {\it Hubbard R.~F.}, {\it Leemans W.~P.}, {\it Ting A.}, {\it Sprangle P.} Electron injection into plasma wakefields by colliding laser pulses // Phys. Rev. Lett. 1997. Vol.~79. P.~2682.
    	
22. {\it Esarey E.}, {\it Leemans W.~P.} Nonparaxial propagation of ultrashort laser pulses in plasma channels // Phys. Rev. E. 1999. Vol.~59. P.~1082--1095.
    	
23. {\it Polozov S.~M.} A possible scheme of electron beam bunching in laser plasma accelerators // Nuclear Instruments and Methods in Physics Research~A. 2013. Vol.~729. P.~517--521.
    	
24. {\it Polozov S.~M.} 2D beam dynamics simulation in linear mode LPWA channel with pre-modulation stage // Problems of Atomic Science and Technology. Series Nuclear Physics Investigations. 2013. Vol.~6. N~88. P.~29--34.
    	
25. {\it Polozov S.~M.}, {\it Rashchikov V.~I.} Capturing coefficient increase and energy spread decrease in LPWA // Journal of Physics: Conference Series. 2016. Vol.~747. N~012075.
    	
26. {\it Polozov S.~M.}, {\it Rashchikov V.~I.} Longitudinal motion stability of electrons inside the plasma channel of LPWA // Cybernetics and Physics. 2018. Vol.~7~(4). P.~228--232.
    	
27. {\it Polozov S.~M.}, {\it Rashchikov V.~I.} Simulation studies on the radiofrequency gun saturated emission // Cybernetics and Physics. 2020. Vol.~9~(2). P.~103--106.
    	
28. {\it Semenov T.~A.}, {\it Zhvaniya I.}, {\it Ivanov K.}, {\it Dzhidzhoev M.~S.}, {\it Volkov R.}, {\it Tsymbalov I.}, {\it Save\-l’ev~A.}, {\it Gordienko V.~M.} Electron acceleration up to MeV level under nonlinear interaction of subtera\-watt femtosecond laser chirped pulses with Kr clusters // Laser Phys. Lett. 2019. Vol.~16. N~115401.
    	
29. {\it Shkurinov A.~P.}, {\it Balakin A.}, {\it Dzhidzhoev M.~S.}, {\it Gordienko V.}, {\it Esaulkov M.}, {\it Zhvaniya I.}, {\it Iva\-nov~K.}, {\it Kotelnikov I.}, {\it Kuzechkin N.}, {\it Ozheredov I.}, {\it Panchenko V.}, {\it Savelev A.~B.}, {\it Smirnov M.}, {\it Solyan\-kin~P.} Interaction of high-intensity femtosecond radiation with gas cluster beam: effect of pulse duration on joint terahertz and $X$-ray emission // IEEE Trans. Terahertz Sci. Technol. 2017. Vol.~7. P.~70--79.
    	
30. {\it Shkurinov A.~P.}, {\it Balakin A.}, {\it Gildenburg V.}, {\it Gordienko V.}, {\it Kuzechkin N.}, {\it Yiming~Zhu}, {\it Solyan\-kin~P.}, {\it Pavlichenko I.}, {\it Semenov T.} Directional terahertz beam generation under interaction of an intense femtosecond laser pulse with a cluster jet // Journal of the Optical Society of America. 2021. Vol.~B~38~(11). N~3515.
    	
31. {\it Polozov S.~M.}, {\it Rashchikov V.~I.} Simulation studies of beam dynamics in 50 MeV linear accelerator with laser plasma electron gun // Cybernetics and Physics. 2021. Vol.~10~(4). P.~260--264.
    	
32. {\it Masunov E.~S.}, {\it Polozov S.~M.} High intensity ion beams in rf undulator linac // Phys. Rev. ST. 2008. Vol.~AB~11. N~074201.
    	
33. {\it Masunov E.~S.}, {\it Polozov S.~M.} The new version of BEAMDULAC code for high intensity ion beam dynamics // Problems of Atomic Science and Technology. Series Nuclear Physics Investigations. 2006. Vol.~3~(47). P.~119--121.
    	
34. {\it Masunov E.~S.}, {\it Polozov S.~M.} BEAMDULAC code for numerical simulation of 3D beam dynamics in a high-intensity undulator linac // Nuclear Instruments and Methods in Physics Research. 2006. Vol.~A~558. P.~184--187.
    	
35. {\it Воронков А.~В.}, {\it Масунов Э.~С.}, {\it Полозов С.~М.}, {\it Ращиков В.~И.} Расчет динамики пучка в ускорителях, работающих на бегущей волне, с учетом эффекта нагрузки током // Атомная энергия. 2019. Т.~109. Вып.~2. С.~84--89.
    	
36. {\it Masunov E.~S.}, {\it Polozov S.~M.}, {\it Rashchikov V.~I.}, {\it Voronkov A.~V.} Stationary and transient beam dynamics simulation results comparison for traveling wave electron linac with beam loading // Problems of Atomic Science and Technology. Series Nuclear Physics Investigations. 2012. Vol.~4~(80). P.~96--99.
    	
37. {\it Kluchevskaia Yu.~D.}, {\it Polozov S.~M.} Beam dynamics simulation in a linear accelerator for CERN Future Circular Collider // Cybernetics and Physics. 2020. Vol.~9~(2). P.~98--102.
    	
38. {\it Ашанин~И.~А.}, {\it Ключевская~Ю.~Д.}, {\it Махоро~А.~А.}, {\it Механикова~В.~Ю.}, {\it Мосолова~О.~А.}, {\it Полозов~С.~М.}, {\it Проников~А.~И.}, {\it Ращиков~В.~И.} Динамика пучка в линейном ускорителе-инжекторе Специализированного источника синхротронного излучения 4-го поколения ИССИ-4 // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2019. Т.~15. Вып.~1. С.~126--139. https://
    	 doi.org/10.21638/11702/spbu10.2019.110
    	
39 {\it Масунов Э.~С.} Эффекты нагрузки током в ускорителях заряженных частиц.  М.: Изд-во МИФИ, 1999. 122~c.

\vskip 1.2%5
mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 августа 2022~г.

Cтатья принята к~печати 1 сентября 2022~г.

\vskip4.0%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip1.2mm \textit{Ашанин Илья Андреевич} --- ilya.ashanin@mail.ru

\vskip1.2mm \textit{Ключевская Юлия Денисовна} --- канд. техн. наук; kluchevskaia@mail.ru

%\newpage
\vskip1.2mm
\textit{Полозов Сергей Маркович} --- д-р физ.-мат. наук; smpolozov@mephi.ru

\vskip1.2mm \textit{Ращиков Владимир Иванович} --- канд. техн. наук; virashchikov@mephi.ru\par
%
}
