
{\normalsize

\vskip 4.5%6
mm
%\newpage

\noindent{\bf Linear electron accelerator for energy 8--50~MeV with injection\\ from an electron source based on cluster plasma systems$^{*}$
 }

}

\vskip 2%3
mm

{\small

\noindent{\it I.~A.~Ashanin, Yu.~D.~Kluchevskaia, S.~M.~Polozov, V.~I.~Rashikov%
%, I.~Î. Famylia%$\,^2$%

 }

\vskip 2%3
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent~$^{*}$ This work was financially supported by the Ministry of Science and Higher Education of the Russian Federation (contract N~075-15-2021-1358 dated September 12, 2021).\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
National Research Nuclear University ``MEPhI'',
    31, Kashirskoe sh., Moscow,

\noindent%
%\hskip2.45mm%
115409, Russian Federation



%\noindent%
%$^2$~%
%St\,Petersburg State University, 7--9, Universitetskaya nab., %St\,Petersburg,
%
%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2%3
mm


\noindent \textbf{For citation:}  Ashanin~I.~A., Kluchevskaia~Yu.~D., Polozov~S.~M., Rashikov~V.~I. Linear electron accelerator for energy 8--50~MeV with injection from an electron source based on cluster plasma systems. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p3}--\pageref{p3e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum03 (In Russian)

\vskip2.0mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent For many years, one of the key problems of modern accelerator physics has been an increase of the rate of the energy gain in RF linear electron accelerators. The physical limits of the accelerating field intensity for metallic accelerating structures have been practically reached; therefore, new acceleration schemes are being considered, primarily acceleration in plasma and wakefield acceleration. The second aim is the generation of ultrashort (100~fs and less) electron bunches, for which RF photoguns are traditionally used. In this case, for RF photoguns, a serious problem that limits the intensity of electrons in a bunch is the influence of the own space charge during emission and acceleration in the near-cathode region, where the beam is weakly relativistic and the influence of the space charge on its dynamics plays the determinative role. The possibility of using a plasma cathode source as an injector for RF accelerator will considered. In the future, this may make it possible to bypass the limitations inherent in RF photoguns (sufficient influence of the space charge on the beam dynamics in the near-cathode region) and acceleration in the laser-plasma channel (low electron capture coefficient in the acceleration mode, wide energy spectrum --- 10\,\% or more at energies of tens and hundreds of megaelectrons). It is proposed to develop a combined accelerator in which a bunch generated in a laser-plasma channel is injected into a traditional metal structure. It is supposed that could be possible to generate a short (from 0.1 to 1.0~ps) electron bunches with an energy of several hundred kiloelectrons, which will make it possible to consider such source as an alternative to the photocathode. Next, the beam must be captured in the ac\-ce\-leration mode in a normally conducting section and accelerated to an energy of 50~MeV with the possibility of energy tuning. The features of such accelerator, the features of the electron bunch capturing in the acceleration mode, and the possible values of the energy spectrum in such a system will considered.
\\[1mm]
\textit{Keywords}: synchrotron radiation, free electron laser, accelerating structure, beam dynamics, transverse emittance.\par}

\vskip4.5%6
mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Brinker F. Commissioning of the European XFEL injector. \textit{Proceedings of the Intern. Particle Accel. Conference IPAC'16}. Busan, 2016, pp.~1044--1047.
		
2. Dowell D.~H.,  Akre R., Ding Y., Emma P., Frisch J., Gilevich S.,  Hays G., Hering Ph., Huang~Z., Iverson R., Limborg-Deprey C., Loos H., Miahnahri A., Schmerge J., Turner J., Welch J., White W., Wu J., Froelich L., Limberg~T., Prat E. Commissioning results or the LCLS injector. \textit{Proceedings of 29$^{th}$~Intern. Free Electron Laser Conference FEL’2007}. Novosibirsk, 2007, pp.~276--278.
		
3. Feinberg Ya.~B. Particles acceleration in plasma. \textit{Sov. Atomic Energy}, 1959, no.~6, 431~p.
		
4.  Muggli P., Kimura W., Kallos E., Katsouleas T., Kusche K., Pavlishin I., Stolyarov D., Yakimen\-ko~V. Plasma wakefield acceleration experiments using two subpicosecond electron bunches. \textit{Proceedings of 22$^{nd}$~Par\-tic\-le Accel. Conference PAC’07}. Albuquerque, 2007, pp.~3073--3075.
		
5.  Hogan M.~J., Barnes C.~D., Clayton C.~E., Decker F.~J., Deng S., Emma P., C.~Huang, Iver\-son~R.~H., Johnson D.~K., Joshi C., Katsouleas T., Krejcik P., Lu W., Marsh K.~A., Mori W.~B., Mugg\-li~P., O’Con\-nell~C.~L., Oz E., Siemann R.~H., Walz D. Multi-GeV energy gain in a plasma-wakefield accelerator. \textit{Phys. Rev. Lett.}, 2005, vol.~95, iss.~054802, pp.~1--4.
		
6.  Tajima T., Dowson J.~M. Laser electron accelerator. \textit{Phys. Rev. Lett.}, 1979, vol.~43, iss. 4, pp.~267--270.
		
7. Leemans W., Esarey E. Laser-driven plasma-wave electron accelerators. \textit{Phys. Today}, 2009, vol.~62, p.~44.
		
8. Leurent V., Michel P., Clayton C.~E., Pollock B., Doeppner T., Ralph J., Pak A., Wang T., Jo\-shi~C., Tynan G., Divol L., Palastro J., Glenzer S., Froula D. Experimental demonstration of $X$-ray beta\-tron radiation spectrum from laser accelerated electron beams. \textit{Proceedings of 11$^{th}$~European Particle Accel. Conference EPAC’08}. Genoa, 2008, pp.~2809--2811.
		
9. Wiggins S.~M., Welsh G.~H., Wiggins S.~M., Welsh G.~H., Issac R.~C., Brunetti E., Shanks~R.~P., Cipiccia S., Anania M.~P., Manahan G.~G., Aniculaesei C., Ersfeld B., Islam M.~R., Jaro\-szyn\-ski~D.~A., Gillespie W.~A., MacLeod A.~M. The production of high quality electron beams in the ALPHA-X laser wakefield accelerator. \textit{Proceedings of 2$^{nd}$~Intern. Particle Accel. Conference IPAC’11}. Geneva, 2011, pp.~1956--1958.
		
10. Leemans W., Esarey E., Geddes C.~G.~R., Schroeder C.~B., Toth Cs., Van Tilborg J., Cary J.~R., Nieter C. Mono-energetic beams from laser plasma interactions. \textit{Proceedings of Particle Accel. Conference PAC’05}. Knoxville, 2005, pp.~69--71.
		
11. Kotaki H., Hayashi Y., Kawase K., Mori M., Kando M., Homma T., Koga J.~K., Bulanov S.~V. Control and pulsewidth-measurement of laser accelerated electron beams. \textit{Proceedings of the 1$^{st}$~Intern. Particle Accel. Conference IPAC’10}. Kyoto, 2010, pp.~3608--3610.
		
12. Yamazaki A., Maekawa A., Tsujii R., Uesaka M., Kinoshita K., Hosokai T., Zhidkov A. Manipulation of electron beam generation with modified magnetic circuit on laser-wakefield acceleration. \textit{Proceedings of 22$^{nd}$~Particle Accel. Conference PAC’07}. Albuquerque, 2007, pp.~2790--2792.
		
13. Clayton C., Ralph J., Albert F., Fonseca R., Glenzer S., Joshi C., Lu W., Marsh K., Mar\-tins~S., Mori W., Pak A., Tsung F., Pollock B., Ross J., Silva L., Froula D. Laser wakefield accele\-ration beyond 1~GeV using ionization induced injection. \textit{Proceedings of 11$^{th}$~Particle Accel. Conference PAC’11}. Roches\-ter, 2011, pp.~707--711.
		
14. Hubbard R.~F., Gordon D.~F., Jones T.~G., Penano J.~R., Sprangle P., Ting A., Hafizi B., Zigler~A., Kaganovich~D. Simulation of accelerated electron spectra in laser wakefield accelerators. \textit{Proceedings of Particle Accel. Conference PAC’03}. Portland, 2003, pp.~716--718.
		
15. Malka V., Faure J., Glinec Y., Lifschitz A. Laser-plasma wakefield acceleration: concepts, tests and premises. \textit{Proceedings of European Particle Accel. Conference EPAC’06}. Edinburgh, 2006, pp.~10--13.
		
16. Bulanov S., Naumova N., Pegoraro F., Sakai J. Particle injection into the wave acceleration phase due to nonlinear wake wave breaking. \textit{Phys. Rev. E}, 1998, vol.~58, no.~R5257.
		
17. Bulanov S.~V., Brantov A.~V., Esirkepov T.~Zh., Kando M., Kotaki H., Bychenkov V. Controlled electron injection into the wake wave using plasma density inhomogeneity. \textit{Physics of Plasmas}, 2008, vol.~15, no.~073111.
		
18. Bulanov S.~V., Tajima T., Esirkepov T., Pirozhkov A., Jinglong~Ma, Kando M., Fukuda Y., Chen~L., Daito I., Ogura K., Homma T., Hayashi Y., Kotaki H., Sagisaka A., Mori M., Koga J., Kawa\-chi~T., Daido H., Kimura T., Kato Y. Frequency multiplication of light back reflected from a relativistic wake wave. \textit{Phys. of Plasmas}, 2007, vol.~14, no.~123106.
		
19. Tomassini P., Galimberti M., Giulietti A., Giulietti D., Gizzi L.~A., Labate L., Pegoraro F. Production of high-quality electron beams in numerical experiments of laser wakefield acceleration with longitudinal wave breaking. \textit{Phys. Rev. Spec. Topics  Acc. and Beams}, 2003, vol.~6, no.~121301.
		
20. Umstadter D., Kim J.~K., Dodd E. Laser injection of ultrashort electron pulses into wakefield plasma waves. \textit{Phys. Rev. Lett.}, 1996, vol.~76, pp.~2073--2076.
		
21. Esarey E., Hubbard R.~F., Leemans W.~P., Ting A., Sprangle P. Electron injection into plasma wakefields by colliding laser pulses. \textit{Phys. Rev. Lett.}, 1997, vol.~79, p.~2682.
		
22. Esarey E., Leemans W.~P. Nonparaxial propagation of ultrashort laser pulses in plasma channels. \textit{Phys. Rev. E}, 1999, vol.~59, pp.~1082--1095.
		
23. Polozov S.~M. A possible scheme of electron beam bunching in laser plasma accelerators. \textit{Nuclear Instruments and Methods in Physics Research A}, 2013, vol.~729, pp.~517--521.
		
24. Polozov S.~M. 2D beam dynamics simulation in linear mode LPWA channel with pre-modulation stage. \textit{Problems of Atomic Science and Technology. Series Nuclear Physics Investigations}, 2013, vol.~6, no.~88, pp.~29--34.
		
25. Polozov S.~M., Rashchikov V.~I. Capturing coefficient increase and energy spread decrease in LPWA. \textit{Journal of Physics: Conference Series}, 2016, vol.~747, no.~012075.
		
26. Polozov S.~M., Rashchikov V.~I. Longitudinal motion stability of electrons inside the plasma channel of LPWA. \textit{Cybernetics and Physics}, 2018, vol.~7~(4), pp.~228--232.
		
27. Polozov S.~M., Rashchikov V.~I. Simulation studies on the radiofrequency gun saturated emission. \textit{Cybernetics and Physics}, 2020, vol.~9~(2), pp.~103--106.
		
28. Semenov T.~A., Zhvaniya I., Ivanov K., Dzhidzhoev M.~S., Volkov R., Tsymbalov I., Save\-l’ev~A., Gordienko V.~M. Electron acceleration up to MeV level under nonlinear interaction of subtera\-watt femtosecond laser chirped pulses with Kr clusters. \textit{Laser Phys. Lett.}, 2019, vol.~16, no.~115401.
		
29. Shkurinov A.~P., Balakin A., Dzhidzhoev M.~S., Gordienko V., Esaulkov M., Zhvaniya I., Iva\-nov~K., Kotelnikov I., Kuzechkin N., Ozheredov I., Panchenko V., Savelev A.~B., Smirnov M., Solyan\-kin~P. Interaction of high-intensity femtosecond radiation with gas cluster beam: effect of pulse duration on joint terahertz and $X$-ray emission. \textit{IEEE Trans. Terahertz Sci. Technol.}, 2017, vol.~7, pp.~70--79.
		
30. Shkurinov A.~P., Balakin A., Gildenburg V., Gordienko V., Kuzechkin N., Yiming~Zhu, Solyan\-kin~P., Pavlichenko I., Semenov T. Directional terahertz beam generation under interaction of an in\-ten\-se femtosecond laser pulse with a cluster jet. \textit{Journal of the Optical Society of America}, 2021, vol.~B~38 (11), no.~3515.
		
31. Polozov S.~M., Rashchikov V.~I. Simulation studies of beam dynamics in 50 MeV linear accelerator with laser plasma electron gun. \textit{Cybernetics and Physics}, 2021, vol.~10~(4), pp.~260--264.
		
32. Masunov E.~S., Polozov S.~M. High intensity ion beams in rf undulator linac. \textit{Phys. Rev. ST}, 2008, vol.~AB~11, no.~074201.
		
33. Masunov E.~S., Polozov S.~M. The new version of BEAMDULAC code for high intensity ion beam dynamics. \textit{Problems of Atomic Science and Technology. Series Nuclear Physics Investigations}, 2006, vol.~3~(47), pp.~119--121.
		
34. Masunov E.~S., Polozov S.~M. BEAMDULAC code for numerical simulation of 3D beam dynamics in a high-intensity undulator linac. \textit{Nuclear Instruments and Methods in Physics Research}, 2006, vol.~A~558, pp.~184--187.
		
35. Voronkov A.~V.,  Masunov E.~S., Polozov S.~M., Rashchikov V.~I. Raschet dinamiki puchka v uskoriteliakh, rabotaiushchikh na begushchei volne, s uchetom effekta nagruzki tokom [Beam dynamics simulation in accelerators operating on a traveling wave, taking into account the beam loading effect]. \textit{Atomic Energy}, 2010, vol.~109~(2), pp.~84--89. (In Russian)
		
36. Masunov E.~S., Polozov S.~M., Rashchikov V.~I., Voronkov A.~V. Stationary and transient beam dynamics simulation results comparison for traveling wave electron linac with beam loading. \textit{Problems of Atomic Science and Technology. Series Nuclear Physics Investigations}, 2012, vol.~4~(80), pp.~96--99.
		
37. Kluchevskaia Yu.~D., Polozov S.~M. Beam dynamics simulation in a linear accelerator for CERN Future Circular Collider. \textit{Cybernetics and Physics}, 2020, vol.~9~(2), pp.~98--102.
		
38. Ashanin~I.~A., Kluchevskaia~Yu.~D., Makhoro~A.~A., Mechanikova~V.~Yu., Mosolova~O.~A., Polozov~S.~M., Pronikov~A.~I., Rashchikov~V.~I. Dinamika puchka v lineinom uskoritele-in\-zhek\-to\-re Spetsializirovannogo istochnika sinkhrotronnogo izlucheniia 4-go pokoleniia ISSI-4 [Beam dy\-na\-mics simulation in the linear accelerator used as an injector for the 4$^{\rm th}$~generation Specialized Synchrotron Radiation Source SSRS-4]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~1, pp.~126--139. \\ https://doi.org/10.21638/11702/spbu10.2019.110 (In Russian)
		
39. Masunov E.~S. \textit{Effekty nagruzki tokom v uskoriteliakh zariazhennykh chastits $[$Beam loading effects in particle accelerators$]$}. Moscow, Office MEPhI Publ., 1999, 122~p. (In Russian)


\vskip1.5mm Received:  August 02, 2022.

Accepted: September 01, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%

\vskip2mm \textit{Ilya A. Ashanin} --- ilya.ashanin@mail.ru

\vskip2mm \textit{Yulia D. Kluchevskaia} --- PhD in Engineering; kluchevskaia@mail.ru

\vskip2mm \textit{Sergey M. Polozov} --- Dr. Sci. in Physics and Mathematics; smpolozov@mephi.ru

\vskip2mm \textit{Vladimir I. Rashchikov} --- PhD in Engineering; virashchkov@mephi.ru \par
%
%
}
