

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2.5mm

1. Lur'e A. I. {\it Sovremennye problemy mehaniki. Nekotorye
nelinejnye zadachi teorii avtomaticheskogo regulirovanija
$[$Modern mechanics problems. Certain nonlinear tasks of the
automatic control theory$]$}. Moscow, State Publ. techn.-theor.
lit., 1951, 216~p. (In Russian)

2. Letov A. M. {\it Ustojchivost' nelinejnyh reguliruemykh sistem.
2 izd. $[$Stability of nonlinear control systems$]$}. 2nd ed.
Moscow, State Publ. phys.-math. lit., 1962, 483~p. (In Russian)

3. Troitskij V. A. O kanonicheskikh preobrazovanijakh uravnenij
teorii avtomaticheskogo regulirovanija pri nalichii kratnykh
kornej [About canonical transformations of equations of the
automatic control theory in the presence of the multiple roots].
{\it Applied Mathematics and Mechanics}, 1957, vol.~21, iss.~4,
pp.~574--577. (In Russian)

4. Nelepin R. A., Kamachkin A. M., Turkin I. I., Shamberov V. N.
{\it Algoritmicheskij sintez  nelinejnykh sistem upravleniya
$[$Algorithmic synthesis of the nonlinear control systems$]$}.
Leningrad, Leningrad University Publ., 1990, 240~p. (In Russian)

5. Petrov V. V., Gordeev A. A. {\it Nelinejnye servomehanizmy
$[$Nonlinear servomechanisms$]$}. Moscow, Machinostroenie Publ.,
1979, 471~p. (In Russian)

6. Derusso P. M., Rob J. R., Close C. M., Desrochers A. A.  {\it
State Variables for Engineers}. 2nd ed. New York, Wiley --
Interscience Press, 1998, 575~p.

7. Kamachkin A. M., Shamberov V. N. Dekompozitsiya mnogomernykh
nelinejnykh sistem so slozhnymi strukturami [Decomposition of
multy-space nonlinear systems with complicated structures]. {\it
Book of Abstracts of XII Inter. Conference ``Stability and
Oscillations of Nonlinear Control systems'' (Pyatnitskiy's
conference, STAB--2012)}. Moscow, IPU RAS Publ., 2012,
pp.~162--163. (In Russian)

8. Kamachkin A. M., Shamberov V. N. Metod dekompozitsii v
mnogomernykh dinamicheskikh sistemakh [Decomposition method to the
manydimensional dynamical systems]. {\it Stability and control
processes. Vseross. Konferentsiya, posvyashchennaya 80-letiyu so
dnya rozhdeniya V.~I.~Zubova}. Saint Petersburg, Saint Petersburg
University Publ., 2010, p.~69. (In Russian)

9. Kamachkin A. M., Shamberov V. N. Sushchestvovanie i
ustojchivost' periodicheskikh reshenij neavtonomnykh mnogomernykh
nelinejnykh system [Existens and stability of the periodical
solutions for the nonautonomous manydimensional nonlinear
systems]. {\it Sovremennye metody prikladnoj matematiki, teorii
upravlenija i komp'juternykh tehnologij (PMTUKT--2014). Sb. Trudov
VII Mezhdunar. Nauch. Konferentsii} [{\it Modern methods of
applied mathematics, theory of management and computer's
technology $($PMTUKT--2014$)$, Coll. works of VII Intern.
Scientific Conference}]. Voronezh, Nauchnaya kniga Publ., 2014,
pp.~175--177. (In Russian)

10. Kamachkin A. M., Shamberov V. N. The Decomposition Method of
Research into the Nonlinear Dynamical Systems' Space of
Parameters. {\it Applied Mathematical Sciences}, 2015, vol.~9,
no.~81, pp.~4009--4018.

11. Aung P. V., Shamberov V. N.   Vynuzhdennye kolebaniya v
sisteme s suhim treniem, nahodyashkhejsya pod vneshnim
garmonicheskim vozdejstviem [Forced oscillations into the system
with dry friction under the external harmonic action]. {\it
Control systems and information technologies}. Voronezh, Nauchnaya
kniga Publ., 2014, no.~4(58), pp.~4--6. (In Russian)

12. Kamachkin A. M., Shamberov V. N.  Sushchestvovanie
periodicheskikh dvizhenij v neavtonomnykh mnogomernykh nelinejnykh
sistemakh [Existence of the periodical motions for the
nonautonomous manydimentional nonlinear systems]. {\it Control
systems and information technologies}. Voronezh, Nauchnaya kniga
Publ., 2015, no.~1(59), pp.~16--19. (In Russian)

13. Kamachkin A. M., Shamberov V. N. Opredelenie bifurkatsionnoj
struktury prostranstva parametrov metodom dekompozitsii
[Defenition of the bifurcation structure into the parametric space
by means of the decomposition method]. {\it Control systems and
information technologies}. Voronezh, Nauchnaya kniga Publ., 2012,
no.~4(50), pp.~11--13. (In Russian)

14. Kamachkin A. M., Sogonov S. A., Shamberov V. N. Vynuzhdennye
periodicheskie resheniya nelinejnykh mnogosvyaznykh system [Forced
periodical solutions of the nonlinear multiply connected systems].
{\it Control systems and information technologies}. Voronezh,
Nauchnaya kniga Publ.,  2014, no.~1(55), pp.~8--12. (In Russin)

15. Kamachkin A. M., Shamberov V. N. Parametricheskaya
dekompozitsiya v zadachakh issledovaniya dinamicheskogo povedeniya
nelinejnykh system [Parametric decomposition for problems of
research of the dynamic behavior of nonlinear systems]. {\it
Sovremennye metody prikladnoj matematiki, teorii upravlenija i
komp'uternykh tehnologij (PMTUKT--2015), Sb. Trudov VIII
Mezhdunar. Nauch. Konferentsii}  [{\it Modern methods of applied
mathematics, theory of management and computer's technology
$($PMTUKT--2015$)$, Coll. works of VIII Intern. Scientific
Conference}].   Voronezh, Nauchnaya kniga Publ., 2015,
pp.~169--172. (In Russian)

16. Potapov D. K. Upravlenie spektral'nymi zadachami dlja
uravnenij s razryvnymi operatorami [Control of spectral problems
for equations with discontinuous operators]. {\it Trudy Instituta
matematiki i mekhaniki Ural. otd. RAS}  [{\it  Works of a
Institute of mathematics and mechanics Ural. department RAS}],
2011, vol.~17, no.~1, pp.~190--200. (In Russian)

17. Yevstafyeva V. V. O neobhodimykh usloviyakh sushchestvovaniya
periodicheskikh reshenij v dinamicheskoj sisteme s razryvnoj
nelinejnost'yu i vneshnim periodicheskim vozdejstviem [ On
recessary conditions for existens of periodic solutions in a
dynamic system with discontinuous nonlinearity and an external
periodic influence]. {\it Ufa Math. Journal}, 2011, vol.~3, no.~2,
pp.~20--27. (In Russian)

18. Kamachkin A. M., Shamberov V. N. The method of parametrical
decomposition. Base subsystems and their state space. {\it Intern.
Conference ``Stability and Oscillations of Nonlinear Control
Systems'' (Pyatnitskiy's Conference)}, IEEE, 2016, pp.~7541190.
DOI: 10.1109/stab.2016.7541190

19. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V.
Non-existence of periodic solutions to non-autonomous second-order
differential equation with discontinuous nonlinearity. {\it
Electron. Journal of Differential Equations}, 2016, no.~4,
pp.~1--8.

20. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. Existence of
solutions for second-order differential equations with
discontinuous right-hand side. {\it Electron. Journal of
Differential Equations}, 2016, no.~124, pp.~1--9.

21. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. Existence of
periodic solutions to automatic control system with relay
nonlinearity and sinusoidal external influence. {\it Intern.
Journal of Robust Nonlinear Control}, 2017, vol.~27, no.~2,
pp.~204--211.

22. Yevstafyeva V. V. On existence conditions for a two-point
oscillating periodic solution in an non-autonomous relay system
with a Hurwitz matrix. {\it Automation and Remote Control}, 2015,
vol.~76, no.~6, pp.~977--988.

23. Potapov D. K. Continuous approximation for a 1D analog of the
Gol'dshtik model for separated flows of an incompressible fluid.
{\it Numerical Anal. and Applicat.}, 2011, vol.~4, no.~3,
pp.~234--238.

24. Potapov D. K. Sturm-Liouville's problem with discontinuous
nonlinearity. {\it Differential Equations}, 2014, vol.~50, no.~9,
pp.~1272--1274.

25. Potapov D. K. Existence of solutions, estimates for the
differential operator, and a ``separating'' set in a boundary
value problem for a second-order differential equation with a
discontinuous nonlinearity. {\it Differential Equations}, 2015,
vol.~51, no.~7, pp.~967--972.

26. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. Solution to
second-order differential equations with discontinuous right-hand
side. {\it Electron. Journal of Differential Equations}, 2014,
no.~221, pp.~1--6.

27. Kamachkin A. M., Chitrov G. M., Shamberov V. N. Special Matrix
Transformations of Essentially Nonlinear Control Systems. {\it
Intern. Conference ``Constructive nonsmoth analysis and related
topics'' to the memory of V.~F.~Demyanov (CNSA--2017)}, IEEE,
2017, pp.~138--140. DOI: 10.1109/CNSA.2017.7973966


28. Kamachkin A. M., Chitrov G. M., Shamberov V. N. Algebraical
aspects of parametrical decomposition method. {\it 2015 Intern.
Conference ``Stability and Control Processes'' in memory of
V.~I.~Zubov (SCP--2015)}, IEEE, 2015, pp.~52--54. DOI:
10.1109/SCP.2015.7342056

29. Lancaster P. {\it Theory of matrices}. New York, London,
Academic Press, 1969, 326~p. (Russ. ed.: Lancaster P. {\it Teoriya
matrits}. Moscow, Nauka Publ., 1978, 280~p.)



\vskip 2mm

{\bf For citation:}  Kamachkin A. M., Chitrov G. M., Shamberov V.
N. Normal matrix forms to decomposition and control problems for
manydimensional systems. {\it Vestnik of Saint Petersburg
Uni-\linebreak versity. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
