
{\small

\vskip4mm%6mm

\noindent \textbf{References} }

\vskip 1.5mm%2mm

{\footnotesize

1. Ausiello G., Crescenzi P., Gambosi G., Kann V.,
Marchetti-Spaccamela A., Protasi M. \textit{Complexity and
approximation}. Berlin, Heidelberg, Springer-Verlag Publ., 1999,
524~p.

2. Ehrgott M. \textit{Multicriteria optimization}. Berlin,
Heidelberg, Springer-Verlag Publ., 2005, 323~p. \looseness=-1

3. Podinovskiy V.~V., Noghin V.~D. \textit{Pareto-optimal'nye
resheniya
  mnogokriterial'nyh zadach} [\textit{Pareto-optimal solutions of multicriteria
  problems}]. Moscow, Fizmatlit Publ., 2007, 256~p. (In Russian)

4. Figueira J.~L., Greco S., Ehrgott M. \textit{Multiple criteria
decision analysis:
  state of the art surveys}. New York, Springer-Verlag Publ., 2005, 1048~p.

5. Noghin V.~D. \textit{Reduction of the Pareto Set: An axiomatic
approach}.
  Cham, Springer Intern. Publ., 2018, 232~p.

6. Klimova O.~N. The problem of the choice of optimal chemical
composition of
  shipbuilding steel. \textit{Journal of Computer and Systems Sciences International},
  2007, vol.~46(6), pp. 903--907.

7. Noghin V.~D., Prasolov A.~V. The quantitative analysis of trade
policy: a
  strategy in global competitive conflict.
  \textit{Intern. Journal of Business Continuity and Risk
  Management}, 2011, vol.~2(2), pp.~167--182.
\looseness=-1

8. Angel E., Bampis E., Gourv\'es L., Monnot J.
(Non)-approximability for
  the multicriteria TSP(1,2). \textit{Fundamentals of Computation Theory 2005: 15th Intern. Symposium.
  Lecture Notes in Computer Science.} Vol.~3623. Lubeck, Germany, 2005, pp.~329--340.

9. Buzdalov M., Yakupov I., Stankevich A. Fast implementation of
the
  steady-state NSGA-II algorithm for two dimensions based on incremental
  non-dominated sorting. \textit{Proceedings of the 2015 Annual conference on
  Genetic and Evolutionary Computation (GECCO--15)}. Madrid, Spain, 2015, pp.~647--654.
\looseness=-1

10. Deb K., Pratap A., Agarwal S., Meyarivan T. A fast and elitist
  multiobjective genetic algorithm: NSGA-II. \textit{IEEE Transactions on
  Evolutionary Computation}, 2002, vol.~6(2), pp.~182--197.
\looseness=-1

11. Li H., Zhang Q. Multiobjective optimization problems with
complicated Pareto
  sets, MOEA/D and NSGA-II. \textit{IEEE Transactions on Evolutionary Computation},
  2009, vol.~13(2), pp.~284--302.
\looseness=-1

12. Yuan Y., Xu H., Wang B. An improved NSGA-III procedure for
evolutionary
  many-objective optimization. \textit{Proceedings of the 2014 Annual conference on
  Genetic and Evolutionary Computation (GECCO--14)}. Vancouver, BC, Canada, 2014, pp.~661--668.

13. Zitzler E., Brockhoff D., Thiele L. The hypervolume indicator
revisited: On
  the design of Pareto-compliant indicators via weighted integration.
  \textit{Proceedings of conference on Evolutionary Multi-Criterion
  Optimization.
  Lecture Notes in Computer Science}. Vol.~4403.
  Berlin, Springer Publ., 2007, pp.~862--876.

14. Zitzler E., Laumanns M., Thiele L. SPEA2: Improving the
strength
  Pareto evolutionary algorithm. \textit{Evolutionary Methods
  for Design, Optimization and Control with Application to Industrial Problems:
  Proceedings of EUROGEN 2001 conference}.
  Athens, Greece, 2001, pp.~95--100.

15. Garcia-Martinez C., Cordon O., Herrera F. A taxonomy and an
empirical
  analysis of multiple objective ant colony optimization algorithms for the
  bi-criteria TSP. \textit{European Journal of Operational Research}, 2007, vol.~180,
  pp.~116--148.

16. Psychas I.~D., Delimpasi E., Marinakis Y. Hybrid evolutionary
algorithms for
  the multiobjective traveling salesman problem. \textit{Expert Systems with
  Applications}, 2015, vol.~42(22), pp.~8956--8970.

17. Reinelt G. TSPLIB --- a traveling salesman problem library.
\textit{ORSA Journal on
  Computing}, 1991, vol.~3(4), pp.~376--384.

18. Zakharov A.~O., Kovalenko Yu.~V. Reduction of the Pareto set
in bicriteria
  assymmetric traveling salesman problem.
  \textit{OPTA--2018. Communications in Computer and Information Science}. Vol.~871.
  Eds by A.~Eremeev, M.~Khachay, Y.~Kochetov, P.~Pardalos.
  Cham, Springer Intern. Publ., 2018, pp.~93--105.

19. Noghin V.~D. Reducing the Pareto set algorithm based on an
arbitrary finite
  set of information ``quanta''. \textit{Scientific and Technical Information Processing},
  2014, vol.~41(5), pp.~309--313.

20. Klimova O.~N., Noghin V.~D. Using interdependent information
on the relative
  importance of criteria in decision making. \textit{Computational Mathematics and Mathematical Physics},
  2006, vol.~46(12), pp.~2080--2091.

21. Noghin V.~D. Reducing the Pareto set based on set-point
information.
  \textit{Scientific and Technical Information Processing}, 2011, vol.~38(6), pp.~435--439.

22. Zakharov A.~O. Pareto-set reduction using compound information
of a closed
  type. \textit{Scientific and Technical Information Processing}, 2012, vol.~39(5), pp.~293--302.

23. Emelichev V.~A., Perepeliza V.~A. Complexity of vector
optimization problems
  on graphs. \textit{Optimization: A Journal of Mathematical Programming and Operations
  Research}, 1991, vol.~22(6), pp.~906--918.
\looseness=-1

24. Vinogradskaya T.~M., Gaft M.~G. Tochnaya verhn'ya otzenka
chisla
  nepodchinennyh reshenii v mnogokriterial'nyh zadachah [The least upper
  estimate for the number of nondominated solutions in multicriteria
  problems]. \textit{Avtomatica i Telemekhanica} [\textit{Automation and Remote Control}],
  1974, vol.~9, pp.~111--118. (In Russian)

25. Reeves C.~R. Genetic algorithms for the operations researcher.
\textit{INFORMS Journal
  on Computing}, 1997, vol.~9(3), pp.~231--250.

26. Eremeev A. V., Kovalenko Y. V. Genetic algorithm with optimal
recombination
  for the asym\-met\-ric travelling salesman problem. \textit{Large-Scale Scientific Computing 2017.
  Lecture Notes of Computer Science}, 2018, vol.~10665, pp.~341--349.

27. Whitley D., Starkweather T., McDaniel S., Mathias K. A
comparison of
  genetic sequencing operators. \textit{Proceedings of the Fourth Intern.
  conference on Genetic Algorithms}. San Diego, California, USA, 1991, pp.~69--76.

28. Radcliffe N.~J. The algebra of genetic algorithms.
\textit{Annals of Mathematics and
  Artificial Intelligence}, 1994, vol.~10(4), pp.~339--384.

29. Jaszkiewicz A., Zielniewicz P. Pareto memetic algorithm with
path relinking
  for bi-objective traveling salesperson problem. \textit{European Journal of
  Operational Research}, 2009, vol.~193, pp.~885--890.
\looseness=-1

30. Kumar R., Singh P.~K. Pareto evolutionary algorithm hybridized
with local search
  for bi-objective TSP.
  \textit{Hybrid Evolutionary Algorithms. Studies in Computational Intelligence.} Vol.~75.
  Eds by A.~Abraham, C.~Grosan, H.~Ishibuchi.
   Berlin, Heidelberg, Springer Publ., 2007, pp.~361--398.

31. Lust T., Teghem J. The multiobjective traveling salesman
problem: A survey
  and a new approach.
  \textit{Advances in Multiobjective Nature Inspired
  Computing. Studies in Computational Intelligence.} Vol.~272.
  Eds by C.~A.~Coello Coello, C.~Dhaenens, L.~Jourdan.
  Berlin, Heidelberg, Springer Publ., 2010, pp.~119--141.

32. {\it Multiobjective optimization library.} URL:
http://home.ku.edu.tr/$\sim$moolibrary/ (accessed: 09.02.2018).

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

Received:  May 18, 2018.

Accepted: September 25, 2018.

\vskip4.5mm%6mm
A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm%2mm
\textit{Aleksey O. Zakharov} --- PhD in Physics and
Mathematics; a.zakharov@spbu.ru

\vskip1.5mm%2mm
\textit{Yulia V. Kovalenko} --- PhD in Physics and Mathematics;
julia.kovalenko.ya@yandex.ru\par
%
}
