
{\small

\vskip4%6
mm \noindent \textbf{Литература}

}

\vskip1.8%3
mm

{\footnotesize

%\bibitem{Kras1956}
1. \emph{Красовский Н. Н.}
О применении второго метода Ляпунова для уравнений с запаздываниями времени~// Прикладная математика и механика. 1956. Т.~20. №~3. С.~315--327.

%\bibitem{KharZhab2003}
2. \emph{Kharitonov V.~L., Zhabko A.~P.}
Lyapunov\,---\,Krasovskii approach to the robust stability analysis of time-delay systems~//
Automatica. 2003. Vol.~39. P.~15--20.

%\bibitem{Khar_book}
3. \emph{Kharitonov V.~L.}
Time-delay systems: Lyapunov functionals and matrices. Basel: Birkh\"auser, 2013. 311~p.

%\bibitem{Niculescu2001}
4. \emph{Niculescu S.-I.}
Delay effects on stability: A robust control approach. Heidelberg: Springer, 2001. 383~p.


%\bibitem{Voronezh2014}
5. \emph{Александров~А.~Ю., Жабко~А.~П., Жабко~И.~А.}
Оценка области асимптотической устойчивости решений однородных дифференциально-разностных систем~// Системы управления и информационные технологии. 2014. Т.~55. №~1. С.~4--7.

%\bibitem{Voronezh}
6. \emph{Александров~А.~Ю., Жабко~А.~П., Печерский~В.~С.}
Функционалы полного типа для некоторых классов однородных дифференциально-разностных систем~//
Труды 8-й Междунар. конференции <<Современные методы прикладной математики, теории управления и компьютерных технологий>>. Воронеж: Научная книга, 2015. С.~5--8.

%\bibitem{TDS2019}
7. \emph{Zhabko A.~P., Alexandrova I.~V.}
Lyapunov direct method for homogeneous time delay systems~//
Proceedings of 15th IFAC Workshop on Time Delay Systems. Sinaia, Romania, 2019. Vol.~52. N~18. P.~79--84.

%\bibitem{AleksZhab2012}
8. \emph{Александров~А.~Ю., Жабко~А.~П.}
Об асимптотической устойчивости решений нелинейных систем с запаздыванием~// Сиб. мат. журн. 2012. Т.~53. №~3. С.~393--403.

%\bibitem{AleksZhab2014_TAC}
9. \emph{Aleksandrov~A.~Yu., Hu~G.-D., Zhabko~A.~P.}
Delay-independent stability conditions for some classes of nonlinear systems~//
IEEE Trans. Autom. Control. 2014. Vol.~59. N~8. P.~2209--2214.

%\bibitem{AleksZhab2014_AML}
10. \emph{Aleksandrov~A.~Yu., Zhabko~A.~P.}
Delay-independent stability of homogeneous systems~//
Applied Mathematics Letters. 2014. Vol.~34. P.~43--50.

%\bibitem{Automatica2021}
11. \emph{Zhabko A.\,P., Alexandrova I.\,V.}
Complete type functionals for homogeneous time delay systems~// Automatica. 2021. Vol.~125. Art. no.~109456. %\\
https://doi.org/10.1016/j.automatica.2020.109456

%\bibitem{EfimovWeighted2020}
12. \emph{Efimov D., Aleksandrov A.}
Analysis of robustness of homogeneous systems with time delays using Lyapunov\,---\,Krasovskii functionals~//
International Journal of Robust and  Nonlinear Control. 2020. P.~1--17. %\\
https://doi.org/10.1002/rnc.5115

%\bibitem{Portilla2021}
13. \emph{Portilla G., Alexandrova I.~V., Mondi\'e S.}
Estimates for weighted homogeneous delay systems: A~Lya\-pu\-nov\,---\,Kra\-sov\-skii\,---\,Ra\-zu\-mik\-hin approach //
American Control Conference (ACC'2021) (ac\-cep\-ted for publication).

%\bibitem{Efimov2016}
14. \emph{Efimov D.,  Polyakov A.,  Perruquetti W., Richard J.~P.}
Weighted homogeneity for time-delay systems: finite-time and independent of delay stability~//
IEEE Trans. Autom. Control. 2016. Vol.~61. N~1. P.~210--215.

%\bibitem{Zubov}
15. \emph{Зубов~В.~И.}
Устойчивость движения. М.: Высшая школа, 1984. 232~с.

%\bibitem{Rosier1992}
16. \emph{Rosier L.}
Homogeneous Lyapunov function for homogeneous continuous vector field~//
Systems $\&$ Control Letters. 1992. Vol.~19. P.~467--473.

%\bibitem{Kras_book}
17. \emph{Красовский Н. Н.}
Некоторые задачи теории устойчивости движения. М.: Гос. изд-во физ.-мат. лит., 1959. 211~с.

%\bibitem{MelchNic2007}
18. \emph{Melchor-Aguilar D., Niculescu S.-I.}
Estimates of the attraction region for a class of nonlinear time-delay systems~//
IMA Journal of Mathematical Control Information. 2007. Vol.~24. N~4. P.~523--550.

%\bibitem{Portilla2021_IJC}
19. \emph{Portilla G., Alexandrova I.~V., Mondi\'e S., Zhabko A. P.}
Estimates for solutions of ho\-mo\-ge\-neous time-delay systems: Comparison of Lya\-pu\-nov\,---\,Kra\-sov\-skii and Lya\-pu\-nov\,---\,Ra\-zu\-mik\-hin techniques~//
International Journal of Control (submitted for publication).


%\pagebreak
\vskip 1.2mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 14 февраля 2021~г.

Cтатья принята к~печати 5 апреля 2021~г.

\vskip4%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip1.5 mm \textit{Александрова Ирина Васильевна} --- канд. физ.-мат. наук, доц.; i.v.aleksandrova@spbu.ru\par%
%
\vskip1.5 mm \textit{Жабко Алексей Петрович} --- д-р физ.-мат. наук, проф.; a.zhabko@spbu.ru\par%
%
}
