
{\normalsize

\vskip 4%6
mm

\noindent{\bf Lyapunov\,---\,Krasovskii functionals for homogeneous systems\\ with multiple delays$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it I.~V.~Alexandrova, A.~P.~Zhabko%$\,^{2,3}$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian Science Foundation  (project N~19-71-00061).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Alexandrova I.\,V., Zhabko A.\,P. Lya\-pu\-nov\,---\,Kra\-sov\-skii functionals for ho\-mo\-ge\-neous systems with multiple delays. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~17,~iss.~\issuenum,~pp.~\pageref{p8}--\pageref{p8e}. (In Russian)\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08

\vskip2mm

{\leftskip=7mm\noindent In this article, explicit constructions of Lya\-pu\-nov\,---\,Kra\-sov\-skii functionals are proposed for homogeneous systems with multiple constant delays and homogeneity degree of the right-hand sides strictly greater than one. The constructions are based on the Lyapunov functions suitable for the analysis of corresponding systems with all delays equal to zero. The letter systems are assumed to be asymptotically stable. It is proved that the proposed functionals satisfy the conditions of the Krasovskii theorem, and hence it allows us to establish the asymptotic stability of the trivial solution for arbitrary values of delays. The functionals are applied to the estimation of the attraction region of the trivial solution.\\[1mm]
\textit{Keywords}: time delay systems, homogeneous systems, asymptotic stability, Lya\-pu\-nov\,---\,Kra\-sov\-skii functionals, attraction region.
\par}

\vskip4%6
mm

\noindent \textbf{References} }

\vskip 3%2
mm

{\footnotesize

1. Krasovskii N.~N. O primenenii vtorogo metoda Lyapunova dlya uravnenij s zapazdyvaniyami vremeni [On  the second Lyapunov method application to the equations with delay].
\emph{Prikladnaya matematika i mechanika $[$Applied Mathematics and Mechanics$]$}, 1956, vol.~20, no.~3, pp.~~315--327. (In Russian)

2. Kharitonov V.~L., Zhabko A.~P.
Lyapunov\,---\,Krasovskii approach to the robust stability analysis of time-delay systems.
\emph{Automatica}, 2003, vol.~39, pp.~15--20.

3. Kharitonov V.~L.
\emph{Time-delay systems: Lyapunov functionals and matrices}. Basel, Birkh\"auser Publ., 2013, 311~p.

4. Niculescu S.-I.
\emph{Delay effects on stability: A robust control approach}. Heidelberg, Springer Publ., 2001, 383~p.

5. Aleksandrov~A.~Yu., Zhabko~A.~P., Zhabko~I.~A.
Ocenka oblasti asimptoticheskoj ustojchivosti reshenij odnorodnyh differencial'no-raznostnyh sistem
[Estimation of the asymptotic stability do\-mains for solutions of homogeneous differential-difference systems].
\emph{Sistemy upravleniya i informa\-ci\-on\-nye tekhnologii $[$Control Systems and In\-for\-ma\-tion Technologies$]$}, 2014, vol.~55, no.~1, pp.~4--7. (In Russian)

6. Aleksandrov~A.~Yu., Zhabko~A.~P., Pecherskii~V.~S.
Funkcionaly polnogo tipa dlya nekotoryh klassov odnorodnyh differencial'no-raznostnyh sistem
[Complete type functionals for some classes of homogeneous differential-difference systems]. \emph{Proceedings of 8th International Conference ``Mo\-dern Methods of Applied Mathematics, Control Theory and Computer Technology’’}. Voronezh, Scien\-ce Book Publ. House, 2015, pp.~5--8. (In Russian)

7. Zhabko A.~P., Alexandrova I.~V.
Lyapunov direct method for homogeneous time delay systems. \emph{Proceedings of 15th IFAC Workshop on Time Delay Systems}. Sinaia, Romania, 2019, vol.~52, no.~18, pp.~79--84.

8. Aleksandrov~A.~Yu., Zhabko~A.~P. Оb assimptoticheskoy ustoichivosti resheniy nelineinyh system s zapazdyvaniem [On the asymptotic stability of solutions of nonlinear systems with delay]. \emph{Siberian Mathematical Journal}, 2012, vol.~53, no.~3, pp.~393--403. (In Russian)

9. Aleksandrov~A.~Yu., Hu~G.-D., Zhabko~A.~P.
De\-lay-in\-de\-pen\-dent stability conditions for some classes of nonlinear systems.
\emph{IEEE Trans. Autom. Control}, 2014, vol.~59, no.~8, pp.~2209--2214.

10. Aleksandrov~A.~Yu., Zhabko~A.~P.
De\-lay-in\-de\-pen\-dent stability of homogeneous systems.
\emph{Applied Mathematics Letters}, 2014, vol.~34, pp.~43--50.

11. Zhabko A.~P., Alexandrova I.~V.
Complete type functionals for homogeneous time delay systems. \emph{Automatica}, 2021, vol.~125, art.~no.~109456. %\\
https://doi.org/10.1016/j.automatica.2020.109456

12. Efimov D., Aleksandrov A.
Analysis of robustness of homogeneous systems with time delays using Lyapunov\,---\,Krasovskii functionals.
\emph{International Journal of Robust and  Nonlinear Control}, 2020, pp.~1--17. %\\
https://doi.org/10.1002/rnc.5115

13. Portilla G., Alexandrova I.~V., Mondi\'e S.
Estimates for weighted homogeneous delay systems: A~Lya\-pu\-nov\,---\,Kra\-sov\-skii\,---\,Ra\-zu\-mik\-hin approach.
\emph{American Control Conference (ACC'2021)} (accepted for publication).

14. Efimov D.,  Polyakov A.,  Perruquetti W., Richard J.~P.
Weighted homogeneity for time-delay systems: finite-time and independent of delay stability.
\emph{IEEE Trans. Autom. Control}, 2016, vol.~61, no.~1, pp.~210--215.

15. Zubov V.~I. \emph{Ustojchivost' dvizheniya $[$Stability of motion$]$}. Moscow, Vysshaya shkola Publ., 1984, 232~p. (In Russian)

16. Rosier L.
Homogeneous Lyapunov function for homogeneous continuous vector field.
\emph{Systems $\&$ Control Letters}, 1992, vol.~19, pp.~467--473.

17. Krasovskii N.~N. \emph{Nekotorye zadachi teorii ustojchivosti dvizheniya $[$Some problems of the stability theory of motion$]$}. Moscow, Fis.-Mat. Lit. Publ., 1959, 211~p. (In Russian)

18.  Melchor-Aguilar D., Niculescu S.-I.
Estimates of the attraction region for a class of nonlinear time-delay systems.
\emph{IMA Journal of Mathematical Control Information}, 2007, vol.~24, no.~4, pp.~523--550.

19. Portilla G., Alexandrova I.~V., Mondi\'e S., Zhabko A. P.
Estimates for solutions of ho\-mo\-ge\-neous time-delay systems: Comparison of Lya\-pu\-nov\,---\,Kra\-sov\-skii and Lya\-pu\-nov\,---\,Ra\-zu\-mik\-hin tech\-ni\-ques. \emph{International Journal of Control} (submitted for publication).

\vskip1.5mm Received:  February 14, 2021.

Accepted: April 05, 2021.


\vskip6mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip1.5mm \textit{Irina V. Alexandrova} --- PhD in Physics and Mathematics, Associate Professor;\\ i.v.aleksandrova@spbu.ru \par%
%
\vskip1.5mm \textit{Alexey P. Zhabko} --- Dr. Sci. in Physics and Mathematics, Professor; a.zhabko@spbu.ru \par%
%
}
