
{\small

\vskip1.5mm%6mm

\noindent \textbf{References} }

\vskip 1.5mm%2mm

{\footnotesize

1. Bj\"{o}rneborn L., Ingwersen P. Toward a~basic framework for
webometrics. \emph{Journal of the American Society for Information
Science and Technology}, 2004, vol.~55(14), pp.~1216--1227.

2. Thelwall M. A history of webometrics. \emph{Bulletin of the
American Society for Information Science and Technology}, 2012,
vol.~38(6), pp.~18--23.

3. Broder A., Kumar R., Maghoull F., Raghavan P., Rajagopalan S.,
Stata~R., Tomkins~A., Wiener~J. Graph structure in the web.
\emph{Journal of Computer Networks}, 2000, vol.~33(1--6),
pp.~309--320.

4. Ortega J.~L., Aguillo I.~F. Visualization of the Nordic
Academic Web: Link analysis using social network tools.
\emph{Information Processing $\&$ Management}, 2008, vol.~44~(4),
pp.~1624--1633.

5. Thelwall M., Harries G. The connection between the research of
a~university \& counts of links to its web pages: An investigation
based upon a~classification of the relationships of pages to the
research of the host university. \emph{Journal of the American
Society for Information Science and Technology}, 2003, vol.~54(7),
pp.~593--699.

6. Babak A., Babak S. Graph theory application and web page
ranking for website link structure improvement. \emph{Behavior
$\&$ Information Technology}, 2009, vol.~28~(1), pp.~63--72.\\
https://doi.org/10.1080/01449290701840948

7. Liu Y., Ma Z.~M., Zhou C. Web Markov skeleton processes and
their applications. \emph{Tohoku Mathematical Journal}, 2011,
vol.~63, pp.~665--695.

8. Shokin Y.~I., Klimenko O.~A., Rychkova E.~V., Shabalnikov I.~V.
Website rating for scientific and research organizations of the
Siberian Branch of Russian Academy of Sciences.
\emph{Computational Technologies.} 2008, vol.~13~(3),
pp.~128--135.

9. Dehmer M., Dobrynin A.~A., Konstantinova E.~V., Vesnin A.~Y.,
Klimenko O.~A, Shokin Y.~I., Rychkova E.~V., Medvedev A.~N.
Analysis of webspaces of the Siberian Branch of the Russian
Academy of Sciences and the Fraunhofer---Gesellschaft.
\emph{Information Technology in Industry.} 2018, vol.~6~(1),
pp.~1--6.

10. Meusel R., Vigna S., Lehmberg O., Bizer C. The graph structure
in the web~--- analy\-zed on different aggregation levels.
\emph{The Journal of Web Science}, 2015, vol.~1, pp.~33--47.\\
https://doi.org/10.1561/106.00000003

11. Pant G., Srinivasan P., Menczer F. Crawling the web. {\it Web
dynamics}. Eds by M.~Levene, A.~Poulovassilis. Berlin, Springer
Publ., 2004, pp.~153--178.

12. Yadav M., Goyal N. Comparison of open source crawlers~---
a~review. \emph{International Journal of Scientific $\&$
Engineering Research}, 2015, vol.~6~(9), pp.~1544--1551.

13. Pechnikov A.~A., Lankin A.~V. Development of a~program for
collecting data on the structure of websites. \emph{Proceedings of
the Karelian Research Center of the Russian Academy of Sciences},
2016, vol.~8, pp.~81--90. https://doi.org/10.17076/mat381

14. Bar-Yossef Z., Keidar I., Schonfeld U. Do not crawl in the
DUST: Different URLs with similar text. \emph{Proceedings of the
16th International World-Wide Web Conference}, 2007, pp.~111--120.
https://doi.org/10.1145/1242572.1242588

15. Cormen T.~H., Leiserson C.~E., Rivest R.~L., Stein C.
Breadth-first search. \emph{Introduc\-tion to Algorithms.} 2nd ed.
Cambridge, Massachusetts, MIT Press and McGraw-Hill Publ., 2001,
pp.~531--539.

16. {\it The Open Graph Viz Platform}. Available at:
https://gephi.org (accessed: 10.01.2019).

17. Brin S., Page L. The anatomy of a~Large-Scale Hypertextual Web
Search Engine. \emph{Computer Networks and ISDN Systems}, 1998,
vol.~30~(1--7), pp.~107--117.

18. Pandurangan G., Raghavan P., Upfal E. Using PageRank to
characterize web structure.\linebreak\newpage\noindent {\it
Proceedings of the 8th Annual International Conference: Computing
and Combi\-natorics}, 2000, vol.~2387, pp.~330--339.

19. Pechnikov A.~A. Web resources of the Russian university:
Self-organization or admini\-strative impact?
%Research using St.~Petersburg State University as a~case study.
\emph{Electronic Libraries}, 2015, vol.~18~(6), pp.~277--295.

20. Baeza-Yates R., Castillo C. Crawling the infinite web: Five
levels are enough. {\it Procee\-dings of the Third Workshop on Web
Graphs (WAW) of the Lecture Notes in Computer Science. Algorithms
and Models for the WebGraph}, 2004, vol.~3243, pp.~156--167.

21. Pechnikov A.~A. On evaluating the value of the pages of
a~website. \emph{Informatiza\-tion of Education and Science},
2015, vol.~4~(28), pp.~28--40.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

Received: March 03, 2019.

Accepted: June 06, 2019.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm%2mm
\textit{Anthony M.~Nwohiri}~--- PhD; anwohiri@unilag.edu.ng

\vskip1.5mm%2mm
\textit{Andrey A.~Pechnikov}~--- Dr. Sci. in Technics;
pechnikov@krc.karelia.ru

}
