
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. {\em Douglas~D.~H.} {Least cost path in GIS using an
accumulated cost surface and slope lines~// Cartographica. 1994.
Vol.~31. P.~37--51.}

2. {\em Tomlin~D.} {Propagating radial waves of travel cost in a
Grid~// International Journal of Geographical Information Science.
2010. Vol.~24(9). P.~1391--1413.}

3. {\em Yu~C., Lee~J., Munro-Stasiuk~M.} {Extensions to least-cost
path algorithms for roadway planning~// International Journal of
Geographical Information Science. 2003. Vol.~17(4). P.~361--376.}

4. {\em Эльсгольц~Л.~Э.} {Дифференциальные уравнения и
вариационное исчисление. М.: Наука, 1969. 424~c.}

5. {\em Люстерник~Л.~А., Лаврентьев~М.~А.} {Курс вариационного
исчисления. М.: ГОНТИ, 1938. 192~c.}

6. {\em Mordukhovich~B.~S.} {Variational analysis and generalized
differentiation. II. Berlin; Heidelberg: Springer-Verlag Publ.,
2006. XXII. 610~p.}

7. {\em Rindler~F.} {Calculus of variations. Berlin: Springer Intern.
Publishing, 2018. XII. 444~p.}

8. {\em Треногин~В.~А.} {Функциональный анализ. М.: Наука, 1980.
495~с.}

9. {\em Бандурин~Н.~Г., Гуреева~Н.~А.} {Метод и пакет программ для
численного решения систем существенно нелинейных обыкновенных
интегродифференциально-алгебраических уравнений~// Матем.
моделирование. 2012. Т.~24(2). С.~3--16.}

10. {\em Курош~А.~Г.} {Курс высшей алгебры. М.: Наука, 1965. 431~с.}

11. {\em Li~X., Zhao~G., Li~B.} {Generating optimal path by level
set approach for a mobile robot moving in static/dynamic
environments~// Applied Mathematical Modelling. 2020. Vol.~85. P.~210--230.}

12. {\em Sprunk~C., Lau~B., Pfaff~P.} et al. {An accurate and
efficient navigation system for omnidirectional robots in
industrial environments~// Autonomous Robots. 2016. Vol.~41(2). P.~473--493.}


%\pagebreak
\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 декабря 2020~г.

Cтатья принята к~печати 15 января 2021~г.

\vskip6mm%
К\,о\,н\,т\,а\,к\,т\,н\,а\,я \ и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Аббасов Меджид Эльхан оглы}
--- д-р физ.-мат. наук, проф.; m.abbasov@spbu.ru

\vskip2 mm \textit{Шарлай Артем Сергеевич} --- преп.;
sharlayar@mail.ru

}
