
{\normalsize

\vskip 6mm

\noindent{\bf Searching for the cost-optimal road trajectory on the relief of the terrain$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it M.~E.~Abbasov$^{1,2}$, A.~S.~Sharlay$^3$%
%, A. Y. Gorchakov$\,^{2,3,4}$%
%, A. J. Duysenbaeva$\,^{1}$%
%, M. A. Posypkin$\,^{2,3}$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ The necessary conditions
for a minimum in the considered problem  (section 2) were obtained
at the IPME RAS with the financial support of the Russian Science
Foundation (project N~20-71-10032).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

\noindent%
$^2$~%
Institute for Problems in Mechanical
Engineering of the Russian Academy of Sciences,

\noindent%
\hskip2.45mm%
61, Bolshoy pr. V. O., St.\,Petersburg,
199178, Russian Federation


\noindent%
$^3$~%
Military Educational Institute  of Logistics named after General
of the Army A. V. Khruleov,

\noindent%
\hskip2.45mm%
1, Suvorovskaya ul., St.\,Petersburg, 198504, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm%3mm


\noindent \textbf{For citation:}  Abbasov~M.~E.,
Sharlay~A.~S. Searching for the cost-optimal road trajectory on the relief of the terrain. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~17,~iss.~\issuenum,~pp.~\pageref{p1}--\pageref{p1e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum01  (In Russian)

\newpage %\vskip3mm

{\leftskip=7mm\noindent The article analyzes the problem of obtaining the cost-optimal trajectory for building a road. Using the apparatus of mathematical modelling, the authors derive the cost functional, the argument of which is the function that describes the path trajectory. The resulting functional after some additional transformations is written in a simpler form. For the problem of the calculus of variations obtained in this manner, an optimality condition is derived. This condition takes into account the specifics of the constructed functional. Unlike the classical Euler---Lagrange condition, it leads not to a differential, but to an integro-differential equa\-tion. An illustrative example of the numerical solution of the obtained equation using the met\-hods of computational mathematics is provided.\\[1mm]
\textit{Keywords}: calculus of variations, optimization, integro-differential equations.
\par}

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Douglas~D.~H. Least cost path in GIS using an accumulated
cost surface and slope lines. \textit{Cartographica}, 1994, vol.~31, pp.~37--51.

2. Tomlin~D. Propagating radial waves of travel cost in a grid.
\textit{International Journal of Geographical Information
Science}, 2010, vol.~24(9), pp.~1391--1413.

3. Yu~C., Lee~J., Munro-Stasiuk~M. Extensions to least-cost
path algorithms for roadway planning. \textit{International
Journal of Geographical Information Science}, 2003, vol.~17(4),
pp.~361--376.

4. Elsgolc~L.~E. \textit{Differencialnye uravneniya i variacionnoe
ischislenie $[$Differential equations and calculus of
variations$]$}. Moscow, Nauka Publ., 1969, 424~p. (In Russian)

5. Lyusternik~L.~A., Lavrentev~M.~A. \textit{Kurs variacionnogo
 ischisleniya $[$Course of calculus of
variations$]$}. Moscow, GONTI Publ., 1938, 192~p. (In Russian)

6. Mordukhovich~B.~S. {\it Variational analysis and generalized
differentiation. II}. Berlin, Heidelberg, Springer-Verlag Publ.,
2006, XXII, 610~p.

7. Rindler~F. {\it Calculus of variations}. Berlin, Springer Intern. Publ.,
2018, XII, 444~p.

8. Trenogin~V.~A. {\it   Funkcionalnyj
analiz $[$Functional analysis$]$}. Moscow, Nauka Publ., 1980, 495~p. (In Russian)

9. Bandurin~N.~G., Gureeva~N.~A. Metod i paket programm dlia
chislennogo resheniia sistem sushchestvenno nelineinykh obyknovennykh
integro-differentsial'no-algebraicheskikh uravnenii  [A method and a software package for numerical solution of the systems of nonlinear
ordinary integrodifferential-algebraic equations].
\textit{Matematicheskoe modelirovanie $[$Mathematical Modeling$]$}, 2012, vol.~24(2), pp.~3--16. (In Russian)

10. Kurosh~A.~G.  {\it Kurs vysshej
algebry $[$Higher algebra course$]$}. Moscow, Nauka Publ., 1965, 431~p. (In Russian)

11. Li~X., Zhao~G., Li B. Generating optimal path by level set
approach for a mobile robot moving in static/dynamic environments.
\textit{Applied Mathematical Modelling}, 2020, vol.~85, pp.~210--230.

12. Sprunk~C., Lau~B., Pfaff~P. et al. An accurate and
efficient navigation system for omnidirectional robots in
industrial environments. {\it Autonomous Robots}, 2016, vol.~41(2), pp.~473--493.

\vskip1.5mm Received:  December 02, 2020.

Accepted: January 15, 2021.


\vskip6mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Majid E. Abbasov}~--- Dr. Sci. in Physics and Mathematics, Professor; m.abbasov@spbu.ru

\vskip2mm \textit{Artyom S. Sharlay}~--- Lecturer;
sharlayar@mail.ru

}
