{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm


1. {Bure~V.~M.} Metodologiia primeneniia binarnoi regressii v
tochnom zemledelii [Methodology of using binary regression in
precision agriculture]. {\it Mathematical models in theoretical
ecology and agriculture: materials of Intern. Seminar dedicated to
the memory of Professor Ratmir Alexandrovich Poluektov
$($Poluektov's reading$)$,} 2014, pp.~118--121. (In Russian)

2. {Yakushev~V.~P., Bure~V.~M., Parilina~E.~M.} {\it Binarnaia
regressiia i ee primenenie v agrofizike} [{\it Binary regression
and its application in agrophysics}]. Saint Petersburg, Agrophys.
Institute, 2015, 36~p. (In Russian)

3. {Bure~V.~M.,  Mitrofanova~O.~A.} Prognoz prostranstvennogo
raspredeleniia ekologicheskikh dannykh s primeneniem kriginga i
binarnoi regressii [Prediction of the spatial distribution of
ecological data using kriging and binary regression]. {\it Vestnik
of Saint Peterburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes,} 2016, iss.~3, pp.~97--105.
(In Russian)

4. { Mitrofanova~O.~A., Bure~V.~M., Kanash~E.~V.} Matematicheskii
modul' dlia avtomatizatsii kolorimetricheskogo metoda otsenki
obespechennosti rastenii azotom [Mathematical module to automate
the colorimetric method for estimating nitrogen status of plants].
{\it Vestnik of Saint Peterburg University. Series 10. Applied
mathematics. Computer Science. Control Processes,} 2016, iss.~1,
pp.~85--91. (In Russian)

5. {\it UAV Geoscan-401}. Available at: https://www.geoscan.aero
(accessed: 01.04.2017).




\vskip 2mm

{\bf For citation:} Bure  V.~M.,~Kanash E.~V.,~Mitrofanova O.~A.
Analysis of plants color characteristics using aerophotos with
different factors of qualitative indicators. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
