
{\normalsize

\vskip 6mm

\noindent{\bf Stability of homogeneous nonstationary systems of
differential-difference\\ equations with linearly time
delay.%$\,^*$%
}

}

\vskip 2mm

{\small

\noindent{\it A. V. Ekimov%$\,^1$%
, O. N. Chizhova%$\,^2$%
, U. P.
Zaranik%$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation


%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Ekimov A. V., Chigova O. N.,
Zaranik U. P. Stability of homogeneous nonstationary systems of
differential-difference equations with linearly time delay. {\it
Vestnik of Saint~Peters\-burg Uni\-versity. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~15,
iss.~\issuenum, pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum01  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent These systems can be considered as a model
for the spread of the epidemic in the population. In addition,
systems with linearly increasing delay describe the dynamics
of the information server, mixing tank, the process of formation
of traffic jams on the ring road, etc. For the study, the concept
of an average system is introduced. This approach allows us to reduce
the analysis of the Lyapunov stability problem of the zero solution
of the original system to the investigation of the zero solution
of the averaged system. Sufficient conditions for stationary system
stability are formulated. Then the application of Razumihin's approach
to the study of stability original system is used. The Lyapunov function
is constructed. As a result, new sufficient conditions for the asymptotic
stability of the zero solution of nonstationary homogeneous systems with
a linearly increasing time delay are obtained. These conditions
are the generalization of well-known results for the linear systems
with a linearly increasing time delay.\\[1mm]
\textit{Keywords}: homogeneous differential-difference system,
linearly increasing time delay, asymp\-totic stability.
\par}

\vskip 6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Bellman R., Cooke K. L.}{ {\em  Differentsialno-raznostnyie
uravneniya} [{\em Differential-difference equations}]. Мoscow, Мir
Publ., 1967, 548~p. (In Russian)}

2. {Zhabko A. P., Chizhova O. N.} { Analiz ustoychivosti
odnorodnogo differentsialno-raznostnogo uravneniya s lineynyim
zapazdyivaniem [Stability analysis of homogeneous
differential-difference equation with linear delay]. {\em Vestnik
of Saint Petersburg University. Series~10. Applied Mathematics.
Computer Science. Control Processes,} 2015, iss.~3, pp.~105--115.
(In Russian)}

3. {Zhabko A. P., Chizhova O. N.}{ Gibridnuj metod analiza
ustoichivosti linejnuh differencialno-raznostnuh sistem s linejno
vozrastaushchim zapazdyvaniem [Hybrid method of stability analysis
of linear difference-differential systems with linear increasing
decelerating]. {\em Tambov University Reports. Series Natural and
Technical Sciences}, 2015, vol.~20, no.~4, pp.~843--850. (In
Russian)}

4. {Zhabko A., Chizhova O.,  Zaranik U.}{ Stability analysis of
the linear time delay systems with linearly increasing delay. {\em
Cybernetics and Physics}, 2016, vol.~5, no.~2, pp.~67--72. }
%

5. {Valeev K. G.}{ Lineynyie differentsialnyie uravneniya s
zapazdyvaniem, lineyno zavisyaschim ot argumenta  [Linear
differential equations with linear time-delay]. {\em  Siberian
Mathematical Journal}, 1964, vol.~5, no.~2, pp.~75--83.
 (In Russian)}

6. {Laktionov A. A., Zhabko A. P.} { Method of difference
transformations for differential systems with linear time-delay.
{\em  Proceeding of the First IFAC Conference LTDS--98}. France,
Grenoble, 1998, pp.~201--205. }


7. {Kuptsova S. E.}{ Ob asimptoticheskom povedenii reshenij sistem
nelinejnuh nestacionarnuh dif\-ferencialnuh uravnenij  [On the
asymptotic  behavior of nonlinear nonstationary differential
equation solutions]. {\em Proceeding of Middle-Volga Mathematical
Society}, 2006, vol.~8, no.~1, pp.~235--243. (In Russian)}
%

8. {Tikhomirov O. G., Temkina E. V.}{ Asimptoticheskoe polojenie
pokoia dlia sistem odno\-rod\-nyhnestatsyonarnyh differentialnyh
uravnenii [Asymptotic quiescent position for systems of
homo\-ge\-neousnon-autonomous differential equations]. {\em
Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes}, 2014, iss.~3,
pp.~58--65. (In Russian)}

9. {Zhabko A. P.,  Tikhomirov O. G., Сhizhova O. N.}{ Ustoychivost
asimptoticheskogo polozheniya pokoya vozmuschennyh odnorodnyh
nestatsionarnyh sistem [Stability of the asymptotic quiescent
position of perturbed homogeneous nonstationary systems]. {\em
Proceedings of Middle-Volga Mathematical Society}, 2018, vol.~10,
no.~1, pp.~13--22. (In Russian)}

10. {Zubov V. I.}{ {\em Ustoichivost dvizheniya }[{\em Stability
of motions}]. Moscow, Visshaya shkola Publ., 1973, 272~p. (In
Russian)}

11. {Krasovskij N. N.}{ Ob ustoichivosti po pervomu priblizheniyu
[On stability by the first approximation]. {\em Journal of Applied
Mathematics and Mechanics}, 1955, vol.~19, no.~5, pp.~516--530.
(In Russian)}

12. {Malkin I. G.}{ {\em Teoriya ustojchivosti dvizhenij} [{\em
The theory of motion stability}]. Moscow, Leningrad, Gostekhizdat
Publ., 1952, 432~p. (In Russian)}

13. { Alexandrov A. Yu.}{{\em Ustoichivost dvizhenij neavtonomnyh
dinamicheskih sistem }[{\em The stability of motion of
nonautonomous dynamical systems}]. St.~Petersburg, Saint
Petersburg State University Publ., 2004, 184~p. (In Russian)}

14.  {Alexandrov A. Yu., Zhabko A. P.}{ Ob asimptoticheskoy
ustoychivosti resheniy nelineynyh sistem s zapazdyvaniem [On the
asymptotic stability of nonlinear system solutions with delay].
{\em Siberian Mathematical Journal}, 2012, vol.~53, no.~3,
pp.~495--508. (In Russian)}

15.  {Grebenschikov B. G., Klechin Yu. I.}{ Ob ustoychivosti odnoy
odnorodnoy nestatsionarnoy sistemy s lineynym zapazdyvaniem
[Stability of a homogeneous nonstationary system with linear
delay]. {\em Differential Equations}, 2003, vol.~39, no.~12,
pp.~1600--1604. (In Russian)}
%

16. { Krasovskij N. N.}{ {\em Nekotoryie zadachi teorii
ustoychivosti dvizheniya} [{\em Some problems of the theory of
stability of motion}]. Moscow, Fizmatgiz Publ., 1959, 212~p. (In
Russian)}
%

17. {\em  Razumikhin B. S.}{ Ob ustoichivosti sistem s
zapazdyvaniem [Stability of systems with delay]. {\em  Journal of
Applied Mathematics and Mechanics}, 1956, vol.~20, no.~4,
pp.~500--512. (In Russian)}

\vskip 1.5mm

Received:  July 06, 2019.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip2mm \textit{Alexander V. Ekimov} --- PhD in Physics and
Mathematics, Associate Professor; a.ekimov@spbu.ru

\vskip2mm \textit{Olga N. Chizhova} --- PhD in Physics and
Mathematics, Associate Professor; o.chizhova@spbu.ru

\vskip2mm \textit{Uliana P. Zaranik} --- PhD in Physics and
Mathematics, Senior Lecture; u.zaranik@spbu.ru\par
%
}
