
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Jaeschke E. J., Khan S., Schneider J. R., Hastings J. B.} High brightness photo injectors for brilliant light sources // Synchrotron light sources and free-electron lasers / Eds by E. Jaeschke et al. Switzerland: Springer International Publ., 2014. 1840 p.

2. \textit{Sukhikh L., Kube G., Bajt S., Lauth W., Popov Y., Potylitsyn A.} Backward transition radiation in the extreme ultraviolet region as a tool for the transverse beam profile diagnostic // Phys. Rev. ST AB. 2014. Vol. 17. P. 112805. 

3. \textit{Doucas G., Kimmitt M.\,F., Doria A., Gallerano G.\,P., Giovenale E., Messina G., And\-rews~H.\,L., Brownell~J.\,H.} Determination of longitudinal bunch shape by means of coherent Smith---Pur\-cell ra\-diation // Phys. Rev. ST AB. 2002. Vol. 5. P. 072802. 

4. \textit{Tsesses S., Bartal G., Kaminer I.} Light generation via quantum interaction of electrons with periodic nanostructures // Phys. Rev. A. 2017. Vol. 95. P. 013832.

5. \textit{Liu W.} Coherent and tunable light radiation from nanoscale surface plasmons array via an exotic Smith---Purcell effect // Optics Letters. 2015. Vol. 40. P. 4579.

6. \textit{Potylitsyn A. P., Ryazanov M. I., Strikhanov M. N., Tishchenko A. A.} Diffraction radiation from relativistic particles. Vol. 239. Berlin: Springer-Verlag, 2010. 278 p.

7. \textit{Cai W., Shalaev V.} Optical metamaterials. New York: Springer, 2009. 200 p.

8. \textit{Tishchenko A. A., Sergeeva D. Yu.}  Near-field resonances in photon emission via interaction of electrons with coupled nanoparticles // Phys. Rev. B. 2019. Vol. 100. P. 235421.
 
9. \textit{Sergeeva D. Yu.,  Tishchenko A. A., Strikhanov M. N.} Microscopic theory of Smith---Purcell radiation from 2D photonic crystal // Nucl. Instrum. and Methods. B. 2017. Vol. 402. P. 206--211.



\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 7 сентября 2019~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Тищенко Алексей Александрович} --- канд. физ.-мат. наук; tishchenko@mephi.ru 


\vskip2mm \textit{Сергеева Дарья Юрьевна} --- канд. физ.-мат. наук; e-mail: dysergeyeva@mephi.ru 


\vskip2mm \textit{Гараев Дамир Ильдарович} --- garaev-dam-ir@mail.ru 

}
