
{\normalsize

\vskip 4.5mm%6mm

\noindent{\bf On the reducing the number of equations in the
problem of radiation\\ of a cluster of interacting particles$^{*}$
}

}

\vskip 2mm

{\small

\noindent{\it A. A. Tishchenko$\,^{1,2}$%
, D. Yu. Sergeeva$\,^{1,3}$%
, D. I. Garaev$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian Science Foundation (project 19-72-00178).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
National Research Nuclear University ``MEPhI'', 31, Kashirskoye
sh., Moscow,

\noindent%
\hskip2.45mm%
 115409, Russian Federation


\noindent%
$^2$~%
National Research Center ``Kurchatov Institute'', 1, Akademika
Kurchatova pl., Moscow,

\noindent%
\hskip2.45mm%
 123182, Russian Federation


\noindent%
$^3$~%
Laboratory of Radiation Physics, Belgorod National Research
University, 2a, Koroleva ul.,

\noindent%
\hskip2.45mm%
Belgorod, 308034, Russian Federation

%\noindent%
%$^1$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%
%\noindent%
%\hskip2.45mm%
%St.\,Petersburg, 199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip1.8mm%3mm


\noindent \textbf{For citation:}  Tishchenko A. A., Sergeeva D.
Yu., Garaev D. I. On the reducing the number of equations in the
problem of radiation of a cluster of interacting particles. {\it
Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathematics.
Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~16, iss.~\issuenum,~pp.~\pageref{p6}--\pageref{p6e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum06  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent In this paper we investigate analytically polarization radiation excited due to interaction of an electron with a cluster of coupled subwavelength particles. The results are valid both for nonrelativistic and for relativistic charged particles. The expression for the Fourier image of radiation field has been obtained, which allows direct calculating spectral and angular density of the radiated energy. In general case, to find the radiation field with taking into account the interaction between particles, it is necessary to solve a system of $N!$ self-consistent tensor equations, where $N$ is the number of particles in the cluster. We suggest the algorithm for reducing the system of $N!$ equations to $N$ equations. The reduction in the number of equations is achieved through the calculation of the fields at the each point in which the dipole moment is, rather than through calculation of the fields from the every source. This facilitates considerably the finding solutions in problems of radiation for the clusters of particles.\\[1mm]
\textit{Keywords}: radiation from charged particles, interaction, subwavelength particles.
\par}

\vskip4mm%5mm

\noindent \textbf{References} }

\vskip 1.8mm%2mm

{\footnotesize

1. Jaeschke E. J., Khan S., Schneider J. R., Hastings J. B. High brightness photo injectors for brilliant light sources. \textit{Synchrotron light sources and free-electron lasers}. Eds by E. Jaeschke et al. Switzerland, Springer International Publ., 2014, 1840 p.

2. Sukhikh L., Kube G., Bajt S., Lauth W., Popov Y., Potylitsyn A. Backward transition radiation in the extreme ultraviolet region as a tool for the transverse beam profile diagnostic. \textit{Phys. Rev. ST AB}, 2014, vol. 17, p. 112805.

3. Doucas G., Kimmitt M. F., Doria A., Gallerano G. P., Giovenale E., Messina G., Andrews H. L., Brownell J. H. Determination of longitudinal bunch shape by means of coherent Smith---Purcell radiation. \textit{Phys. Rev. ST AB}, 2002, vol. 5, p. 072802.

4. Tsesses S., Bartal G., Kaminer I. Light generation via quantum interaction of electrons with periodic nanostructures. \textit{Phys. Rev., A}, 2017, vol. 95, p. 013832.

5. Liu W. Coherent and tunable light radiation from nanoscale surface plasmons array via an exotic Smith---Purcell effect. \textit{Optics Letters}, 2015, vol. 40, p. 4579.

6. Potylitsyn A. P., Ryazanov M. I., Strikhanov M. N., Tishchenko A. A. \textit{Diffraction radiation from relativistic particles}. Vol. 239. Berlin, Springer-Verlag Publ., 2010, 278 p.

7. Cai W., Shalaev V. \textit{Optical metamaterials}. New York, Springer Publ., 2009, 200 p.

8. Tishchenko A. A., Sergeeva D. Yu. Near-field resonances in photon emission via interaction of electrons with coupled nanoparticles.  \textit{Phys. Rev., B}, 2019, vol. 100, p. 235421.

9. Sergeeva D. Yu.,  Tishchenko A. A., Strikhanov M. N. Microscopic theory of Smith---Purcell radiation from 2D photonic crystal. \textit{Nucl. Instrum. and Methods, B}, 2017, vol. 402, pp. 206--211.


\vskip1.5mm Received:  September 07, 2019.

Accepted: May 28, 2020.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Alexey A. Tishchenko} --- PhD in Physics and Mathematics; tishchenko@mephi.ru


\vskip2mm \textit{Daria Yu. Sergeeva} --- PhD in Physics and Mathematics; dysergeyeva@mephi.ru


\vskip2mm \textit{Damir I. Garaev} --- garaev-dam-ir@mail.ru

}
