

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Post-quantum cryptography. $10^{\mbox {\scriptsize th}}$ International Conference, PQCrypto 2019, Chongqing, China, May 8--10, 2019, Proceedings. {\it Lecture Notes in Computer Science series}. Cham, Springer Publ., 2019, vol.~11505, pp.~1--269.

2. Shor P. W. Polynomial-time algorithms for prime factorization and discrete logarithms on quantum computer. \textit{SIAM Journal of Computing}, 1997, vol.~26, pp.~1484--1509.

3. Jozsa R. Quantum algorithms and the fourier transform. \textit{Proc. 
Roy. Soc. London. Series A}, 1998, vol.~454, pp.~323--337.

4. Yan~S.~Y. Quantum attacks on public-key cryptosystems. Boston, Springer Publ., 2013, 207 p.

5. Moldovyan~D.~N. New form of the hidden logarithm problem and its algebraic support. {\it  Bulletin of Academy of Sciences of Moldova. Mathematics}, 2020, no.~2(93), pp.~3--10.

6. Moldovyan~ N.~A., Moldovyan~A.~A. Candidate for practical post-quantum signature scheme. {\it Vest\-nik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~4, pp. 455--461. 
https://doi.org/10.21638/11701/spbu10.2020.410

7. Moldovyan~D.~N. Post-quantum public key-agreement scheme based on a new form of the hidden logarithm problem. \textit{Computer Science Journal of Moldova}, 2019, vol.~27, no.~1(79), pp.~56--72.

8. Moldovyan~A.~A., Moldovyan~ D.~N., Moldovyan~ N.~A. 
Post-quantum commutative encryption algorithm. \textit{Computer Science Journal of Moldova}, 2019, vol.~27, no.~3(81), pp.~299--317.  

9. Moldovyan~ D.~N. A unified method for setting finite non-commutative associative algebras and their properties. \textit{Quasigroups and Related Systems}, 2019, vol.~27, no.~2, pp.~293--308.

10. Moldovyan~D.~N., Moldovyan~A.~A., Moldovyan~N.~A.   Post-quantum signature schemes for ef\-fi\-cient hardware implementation. \textit{Microprocessors and Microsystems}, 2021, vol.~80, pp.~103487.\\
https://doi.org/10.1016/j.micpro.2020.103487

11. Moldovyan~N.~A., Moldovyanu~P.~A. New primitives for digital signature algorithms. {\it  Quasigroups and Related Systems}, 2009, vol.~17, no.~2, pp.~271--282. 

12. Moldovyan~ D.~N., Moldovyan~A.~A., Moldovyan~N.~A. A new concept for designing post-quantum digital signature algorithms on non-commutative algebras. {\it  Voprosy kiberbezopasnosti $[$Cibersecurity questions$]$}, 2022, no. 1(47), pp.~18--25. https://doi.org/10.21681/2311-3456-2022-1-18-25 

13. Shuaiting~Q., Wenbao~H., Yifa~Li,  Luyao~J. Construction of extended multivariate public key cryptosystems.  {\it  International Journal of Network Security}, 2016, vol.~18, no.~1, pp.~60--67.

14. Jintai~D., Dieter~S. Multivariable public key cryptosystems. 2004.\\
https://eprint.iacr.org/2004/350.pdf (accessed: February  24, 2022).


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December~22, 2021.

Accepted: May~05, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Nikolay A. Moldovyan} --- Dr. Sci. in Engineering, Professor, Chief Researcher; nmold@mail.ru \par


\vskip 2mm
 \textit{Alexandr A. Moldovyan} --- Dr. Sci. in Engineering, Professor, Chief Researcher; maa1305@yandex.ru 
 \par
%
%
}
