
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Menezes A. J., Van Oorschot P. C., Vanstone S. A.}
Handbook of applied cryptography. Boca Raton, FL: CRC Press, 1997.
780~p.

2. \textit{Shor P. W.} Polynomial-time algorithms for prime
factorization and discrete logarithms on quantum computer~// SIAM
Journal of Computing. 1997. Vol.~26. P.~1484--1509.

3. \textit{Buchmann J., Dahmen E.} Post-quantum cryptography~/ ed.
by D.~J.~Bernstein. Berlin; Heidelberg: Springer, 2009. 245~p.

4. \textit{Merkle R. Ch.} Secrecy, authentication, and public key
systems: technical report N~1979-1. Ctanford, 1979. 193~p.

5. \textit{McEliece R. J.} A public-key cryptosystem based on
algebraic coding theory~// DSN Progress Report 42--44. 1978.
P.~114--116.

6. \textit{Hoffstein J., Pipher J.,  Silverman J. H.} NTRU: A ring
based public key cryptosystem~// Algorithmic Number Theory (ANTS
III). Portland, OR, June 1998~/ ed. by J.~P.~Buhler.  Berlin:
Springer-Verlag, 1998. P.~267--288. (Lecture Notes in Computer
Science, vol.~1423.)

7. \textit{Courtois N.} The security of Hidden Field Equations
(HFE)~// Topics in Cryptology --- CT-RSA 2001. Berlin; Heidelberg:
Springer, 2001. P.~266--281. (Lecture Notes in Computer Science,
vol.~2020.)

8. Post-quantum cryptography // 9th Intern. conference, PQCrypto
2018. Fort Lauderdale, FL, USA, April 9--11, 2018, Proceedings.
Berlin; Heidelberg: Springer, 2018. (Lecture Notes in Computer
Science, vol.~10786.)

9. Federal Register :: Announcing Request for Nominations for
Public-Key Post-Quantum Cryptographic Algorithms~// Federal
Register. The Daily Journal of the United States Goverment. URL:
https://www.gpo.gov/fdsys/pkg/FR-2016-12-20/pdf/2016-30615.pdf
(дата обращения: 15.01.2019).

10. \textit{Verma G. K.} A proxy blind signature scheme over braid
groups~// Intern. Journal of Network Security. 2009. Vol.~9, N~3.
P.~214--217.

11. \textit{Myasnikov A., Shpilrain V., Ushakov A.} A practical
attack on a braid group based cryptographic protocol~// Advances
in Cryptology --- CRYPTO'05. Berlin: Springer-Verlag, 2005.
P.~86--96. (Lecture Notes in Computer Science, vol. 3621.)

12. \textit{Moldovyan N. A., Moldovyan A. A.} Finite
non-commutative associative algebras as carriers of hidden
discrete logarithm problem~// Bulletin of the South Ural State
University. Series Mathematical Modelling, Programming \& Computer
Software (Bulletin SUSU MMCS). 2019. Vol.~12, N~1. P.~66--81.

13. \textit{Moldovyan D. N.} Cryptoschemes over hidden conjugacy
search problem and attacks using homomorphisms~// Quasigroups and
Related Systems. 2010. Vol.~18, N~2. P.~165--176.

14. \textit{Moldovyan D. N.} Post-quantum public key-agreement
scheme based on a new form of the hidden logarithm problem~//
Computer Science Journal of Moldova. 2019. Vol.~27, N~1~(78).
P.~56--72.

15. \textit{Молдовян Д. Н., Молдовян Н. А.} Особенности строения
групп векторов и~синтез криптографических схем на~их основе~//
Вестн. С.-Петерб. ун-та. Сер.~10. Прикладная математика.
Информатика. Процессы управления. 2011. Вып.~4. С.~84--93.

16. \textit{Молдовян Н. А., Абросимов И. К., Ковалева И. В.}
Постквантовый протокол бесключевого шифрования~// Вопросы защиты
информации. 2017. №~3~(118). С.~3--13.

17. \textit{Schnorr C. P.} Efficient signature generation by smart
cards~// Journal of Cryptology. 1991. Vol.~4, N~3. P.~161--174.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 14 февраля 2019 г.

Cтатья принята к~печати 15 марта 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Молдовян Николай Андреевич}~---  д-p техн. наук,
проф., гл. науч. сотр.; nmold@mail.ru

\vskip2mm \textit{Абросимов Иван Константинович}~---  мл. науч.
сотр.; ivnabr@yandex.ru

}
