
{\normalsize

\vskip 4.5%6%
mm

\noindent{\bf Analytical and numerical solutions of two-dimensional problems of heat\\ conduction and electronic optics$^{*}$
}

}

\vskip 2.2%3%
mm

{\small

\noindent{\it G. I. Kurbatova, E. M. Vinogradova%$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2.2%3%
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent~$^{*}$ This work was supported by the Russian Foundation for Basic Research (grant N 20-07-01086).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize



\noindent%
%$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2,5%3%
mm


\noindent \textbf{For citation:}  Kurbatova G. I., Vinogradova  E. M.
	Analytical and numerical solutions of two-di\-mensional problems of heat conduction and electronic optics. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~17, iss.~\issuenum,~pp.~\pageref{p3}--\pageref{p3e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum03 (In Russian)

\vskip3mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent This work is devoted to a comparative analysis of the effectiveness of various methods for the numerical solution of a non-stationary two-dimensional problem of heat conduction in a cylindrical coordinate system in the absence of axial symmetry. The analysis is carried out on the basis of the obtained analytical solution of the two-dimensional problem of heat conduction in a steady state. The results of this work are of great applied importance in calculating the processes of gas transportation through offshore pipelines, as well as in calculating the electrostatic field of focusing systems during transportation of charged particle beams in problems of electronic optics.
\\[1mm]
\textit{Keywords}: offshore gas pipelines, frontal interval method, heat exchange model, numerical method with increased accuracy, electronic optics.\par}

\vskip6mm
%\pagebreak

\end{hyphenrules}

\noindent \textbf{References} }

\vskip 3mm

{\footnotesize

1.  Samarskii A. A., Vabishchevich P. N. {\it Additivnyie skhemy dlia zadach matematicheskoy fiziki} [{\it Additive schemes for problems of mathematical physics}].  Moscow, Nauka Pabl., 2001, 319~p. (In Russian)


2. { Kurbatova G. I., Klemeshev V. A.}
Effective numerical methods for calculating non-stationary heat and glaciation dynamic processes for offshore gas pipelines. {\it 	Energy},  2020, vol.~205, no.~117995~(7~p).


3. Kurbatova G. I., Yermolayeva N. N., Filippov V. B., Filippov K. B. {\it Proyektirovaniye gazoprovodov v severnykh moryakh}
[{\it Design of gas pipelines in the northern seas}]. St. Petersburg,  Lan' Publ., 2020,  352~p. (In Russian)


4. Samarskii A. A.,  Nikolaev E. S. {\it Metody resheniya setochnykh uravneniy} [{\it Numerical methods for grid equations}].  Moscow, Nauka Publ., 1978, 561~p. (In Russian)



5. { Vinogradova E. M., Egorov N. V., Starikova A. V., Varayun M. I.} Calculating a multipole cylindrical electrostatic system. {\it  Technical Physics}, 2017, vol.~87, iss.~5,  pp.~791--794.


\vskip1.5mm Received:  August 06, 2021.

Accepted: October 13, 2021.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Galina I. Kurbatova} --- Dr. Sci. in Physics and Mathematics, Professor; gi\underline{\ }kurb@mail.ru \par

\vskip2mm \textit{Ekaterina M. Vinogradova} --- Dr. Sci. in Physics and Mathematics, Professor;\\ e.m.vinogradova@spbu.ru \par
%
%
}
