
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1.    \textit{Журавлев Ю. И., Рязанов В. В.}  О~решении задач
распознавания по прецедентам при большом числе классов // Докл.
Академии наук. Математика. 2017.  Т.~96(2). С.~488--490.

2. \textit{Zhuravlev Yu. I., Laptin Yu. P., Vinogradov A. P.,
Zhurbenko~N.~G., Lykhovyd~O.~P., Bere\-zov\-skyi~O.~A.}   Linear
classifiers and selection of informative features // Pattern
Recognition and Image Analysis. 2017. Vol.~27. N~3. P.~426--432.

3.  \textit{Котина Е. Д.}    К~теории определения поля перемещений
на основе уравнения переноса в~дискретном случае // Вестн.
С.-Петерб. ун-та. Сер. 10. Прикладная математика. Информатика.
Процессы управления. 2010.  Вып.~3.  С.~38--43.

4. \textit{Kotina E., Pasechnaya G.}   3D velocity field for heart
tomography // Proceedings  of 2015 Inter\-na\-tional Conference on
``Stability and Control Processes'' in memory of
V.~I.~Zubov~(SCP). Saint Petersburg. 2015. P.~646--647.

5. \textit{Kotina E. D., Latypov V. N., Ploskikh V. A.}  Universal
system for tomographic reconstruction on GPUs // Problems of
Atomic Science and Technology. 2013.  N~6(88).  P.~175--178.

6. \textit{Kotina E. D., Ploskikh V. A.}  Data processing and
quantitation in nuclear medicine // RuPAC 2012 Contributions to
the Proceedings --- 23rd Russian Particle Accelerator Conference.
2012. P.~526--528.

7. \textit{Kotina E. D., Ploskikh V. A., Babin A. V.} Radionuclide
methods application in cardiac studies~// Problems of Atomic
Science and Technology. 2013. Vol.~88(6). P.~179--182.

8. \textit{Kotina E. D., Pasechnaya G. A.}  Optical flow-based
approach for the contour detection in radionuclide images
processing // Cybernetics and Physics. 2014. Vol.~3. N~2.
P.~62--65.

9. \textit{Horn B. K. P., Schunck B. G.}  Determining optical flow
// Artificial Intelligence. 1981. Vol.~17. N~11. P.~185--203.

10. \textit{Anandan P. A.}  A computational framework and an
algorithm for the measurement of visual motion // International
Journal of Computer Vision. 1989. Vol.~2. P.~283--310.

11. \textit{Barron J., Fleet D.}   Performance of optical flow
techniques // International Journal of Computer Vision. 1994.
Vol.~12. P.~43--77.

12. \textit{Black M. J., Anandan P. A.} The robust estimation of
multiple motions: Parametric and piecewise-smooth flow fields //
CVIU. 1996. Vol.~63. P.~75--104.

13. \textit{Fleet D., Weiss J.}  Optical flow estimation //
Mathematical Models in Computer Vision: The Handbook. Ch.~15.
Berlin: Springer, 2005. P.~239--258.

14. \textit{ Papenberg N., Bruhn A., Brox T.} et al. Highly
accurate optic flow computation with theoretically justified
warping // International Journal of Computer Vision. 2006.
Vol.~67(2). P.~141--158.

15. \textit{Котина Е. Д.}  О~сходимости блочных итерационных
методов
// Изв. Иркутск. гос. ун-та. Сер. Математика. 2012. Т.~3. С.~41--55.

16. \textit{Lucas B. D., Kanade T.} An iterative image
registration technique with an application to stereo vision //
Proceedings of Imaging Understanding Workshop. 1981. P.~121--130.

17. \textit{Bruhn A., Weickert J., Schnorr C.} Lucas/Kanade Meets
Horn/Schunck: Combining local and global optic flow methods //
International Journal of Computer Vision. 2005. Vol.~61(3).
P.~211--231.

18. \textit{Овсянников Д. А.}  Математические методы управления
пучками. Л.: Изд-во Ленингр. ун-та, 1980. 228~с.

19. \textit{Овсянников Д. А.} Моделирование и~оптимизация динамики
пучков заряженных частиц. Л.: Изд-во Ленингр. ун-та, 1990. 312~с.

20. \textit{Kotina E. D.}  Discrete optimization problem in beam
dynamics // Nuclear Instruments and Methods in Physics Research.
Section A. Accelerators, Spectrometers, Detectors and Associated
Equip\-ment. 2006. Vol.~558. Iss.~1. P.~292--294.

21. \textit{Расселл Д., Кох Р.} Оператор Собеля. VSD, 2013. 106~с.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 8 сентября 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Котина Елена Дмитриевна} --- д-р физ.-мат. наук,
проф.; e.kotina@spbu.ru

\vskip2mm \textit{Леонова Екатерина Борисовна} --- аспирант;
st062324@student.spbu.ru

\vskip2mm \textit{Плоских Виктор Александрович} --- канд.
физ.-мат. наук, доц.;  v.ploskikh@spbu.ru

}
