
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Solution of a local boundary problem for a non-linear non-stationary system\\ in the class of discrete controls%$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it A.~N.~Kvitko, N.~N.~Litvinov%$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Kvitko A.~N., Litvinov  N.~N.
 Solution of a local boundary problem for a non-linear non-stationary system in the class of discrete controls. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum, pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent This article proposes an algorithm of construction for the discrete controlling function which is restricted by a norm and provides transition for the wide class of the systems of non-stationary nonlinear ordinary differential equations from the initial state to the setting final state. A constructive sufficient condition that provides this transition is obtained. Efficiency of the method is demonstrated by the solution of the robot-manipulator control problem and its numerical modeling.
\\[1mm]
\textit{Keywords}: discrete control, non-linear non-stationary system, stabilization, boundary conditions.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

%\bibitem {Kalman1971}
1. {Kalman R. E., Falb P. L., Arbib M. A.} \textit{Ocherki po matematicheskoj teorii sistem} [\textit{Topics in mathematical system theory}]. Moscow, Mir Publ., 1971, 399~p. (In Russian)

%\bibitem {Petrov1968}
2. {Petrov N. N.} Lokal'naya upravlyaemost' avtonomnyh sistem [Local controllability of autonomous systems]. \textit{Differencial'nye uravneniya} [\textit{Differential Equations}], 1968, vol.~4, no.~7, pp.~1218--1232. (In Russian)

%\bibitem {Petrov1969}
3. {Petrov N. N.} Reshenie odnoj zadachi teorii upravlyaemosti [A solution of a certain problem in control theory]. \textit{Differencial'nye uravneniya} [\textit{Differential Equations}], 1969, vol.~5, no.~5, pp.~962--963. (In Russian)

%\bibitem {Vereschagin1972}
4. {Vereshchagin I. F.} \textit{Metody issledovaniya rezhimov poleta apparata peremennoj massy} [\textit{Methods for investigating flight regimes of changing mass apparatus}]. Perm', Perm' State University Press,  1972, vol.~2, 294~p. (In Russian)

%\bibitem {Zubov1975}
5. {Zubov V. I.} \textit{Lekcii po teorii upravleniya} [\textit{Lectures in control theory}]. Moscow, Nauka Publ., 1975, 496~p. (In Russian)

%\bibitem {Furi1985}
6. {Furi M., Nistri P., Pera M. P., Zezza P.} Linear controllability by piecewise constant controls with assigned switching times. \textit{J. Optim. Theory Appl.}, 1985, vol.~45, iss.~2, pp.~219--229.\\
https://doi.org/10.BF00939978

%\bibitem{Seilova2005}
7. {Seilova R. D., Amanov T. D.} Construction of piece wise constant controls for linear impulsive systems. \textit{Proceedings of International Symposium ``Reliability and quality’’}, 2005, pp.~4--5.

%\bibitem {Kvitko2019}
8. {Kvitko A. N., Maksina A. M., Chistyakov S. V.} On a method for solving a local boundary problem for a nonlinear stationary system with perturbations in the class of piecewise constant controls. \textit{Intern. J. Robust Nonlinear Control}, 2019, vol.~29, pp.~4515--4536.

%\bibitem{Baier2009}
9. {Baier R., Gerdts M.} A computational method for non-convex reachable sets using optimal control. \textit{European Control Conference (ECC)}. Budapest, Hungary, 2009, pp.~97--102.

%\bibitem{Plotnikov2012}
10. {Plotnikov A. V., Arsiry A. V., Komleva T. A.} Piecewise constant controller linear fuzzy systems. \textit{Intern. J. Ind. Math.}, 2012, vol.~4, no.~2, pp.~77--85.

%\bibitem {Kvitko2012}
11. {Kvitko A. N., Yakusheva D. B.} Reshenie zadachi sinteza diskretnoj stabilizacii s uchetom nepolnoj informacii dlya nelinejnoj stacionarnoj upravlyaemoj sistemy [Synthesis of discrete stabilization for a non-linear stationary control system under incomplete information].
\textit{Vestnik of Saint Petersburg University. Mathematics. Mechanics. Astronomy}, 2012, vol.~45, iss.~2, pp.~65--72. (In Russian)

%\bibitem {Peregudova2014}
12. {Peregudova O. A., Filatkina E. V.} O stabilizacii nelinejnyh sistem kaskadnogo vida s kusochno-postoyannym upravleniem [On stabilization of cascade-type non-linear systems with piecewise constant control]. \textit{Review Appl. Ind. Math.}, 2014, vol.~21, no.~1, pp.~80--82. (In Russian)

%\bibitem{Bobkov2021}
13. {Popkov A. S.} Postroenie mnozhestv dostizhimosti i upravliaemosti v spetsial'noi lineinoi zadache upravleniia [Construction of reachability and controllability sets in a special linear control problem]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Sciences. Control Pro\-cesses}, 2021, vol.~17, iss.~3, pp.~294--308.
https://doi.org/10.21638/11701/spbu10.2021.307 (In Russian)

%\bibitem{Gryn1996}
14. {Gryn L.} Discrete feedback stabilization of semilinear control systems. \textit{Control, Optim. Calc. Var.}, 1996, vol.~1, pp.~207--224.

%\bibitem{Gabdrakhimov2008}
15. {Gabdrakhimov A. F.} O stabilizacii linejnyh stacionarnyh upravlyaemyh sistem s nepolnoj obratnoj svyaz'yu [On the stabilization of linear stationary control systems with incomplete feedback]. \textit{Vestnik of Udmurtsky University. Mathematics. Mechanics. Computer Sciences}, 2008, iss.~2, pp.~30--31. (In Russian)

%\bibitem {Lizina2013}
16. Lizina E. A., Shchennicov V. N., Shchennicova E. V. Stabilizaciya nepreryvno-diskretnoj sistemy s periodicheskoj matricej koefficientov [Stabilization of continuous-discrete system with periodic matrix of coefficients]. \textit{Izv. vyssh. uchebn. zaved. Povolzhsk. region. Fiz.-mat. nauki. Fizika} [\textit{Proceedings of Higher Educational Investigations. Povolzhsk Region. Physics and Mathematics Sciences. Physics}], 2013, no.~1(25), pp.~181--195. (In Russian)

%\bibitem{Lapin1992}
17. {Lapin S. V.} Kusochno-postoyannaya stabilizaciya sistem, linejnyh otnositel'no upravleniya [Piecewise-constant stabilization of systems that are linear with respect to control]. \textit{Аvtomatikа i te\-le\-mek\-hanikа} [\textit{Autom. Remote Control}], 1992, vol.~53, iss.~6, pp.~37--45. (In Russian)

%\bibitem{Ailon1988}
18. {Ailon A., Segev R.} Driving a linear constant system by a piecewise constant control. \textit{Intern. J. Control}, 1988, no.~47, pp.~815--825.

%\bibitem {shushlyapin1993}
19. {Shushlyapin E. A.} On the equivalency of piecewise-constant control with a unknown number of switchings and arbitrary amplitude bounded control in a terminal problem for a linear non-stationary
system. \textit{J. Sov. Math.}, 1993, no.~65(2), pp.~1550--1554.

%\bibitem {Bulgakov2001}
20. {Bulgakov A. I., Zhukovskii S. E.} Beng-beng princip dlya linejnogo differencial'nogo uravneniya vtorogo poryadka [The ``bang-bang’’ principle for second order linear differential equations]. \textit{Vestnik of Tambov State University},
2001, vol.~6, iss.~2, pp.~150--154. (In Russian)

%\bibitem{Alzabut2007}
21. {Alzabut J. O.} Piecewise constant control of boundary value problem for linear impulsive differential systems. \textit{Math. Methods Eng.}, 2007, pp.~123--129.

%\bibitem{MaksimovChadov2012}
22. {Maksimov V. P., Chadov A. L.} Ob odnom klasse upravlenij dlya funkcional'no- differencial'noj nepreryvno-diskretnoj sistemy [On a class of controls for a functional-differential continuous-discrete system]. \textit{Izvestiia vysshikh uchebnykh zavedenii. Matematika} [\textit{Proceedings of Higher Educational Investigations. Mathematics}], 2012, no.~9, pp.~72--76. (In Russian)

%\bibitem {Oaks1976}
23. {Oaks O. J., Cook G.} Piecewise linear control of nonlinear systems. \textit{IEEE Transactions on Industrial Electronics and Control Instrumentation}, 1976, no.~IECI-23(1), pp.~56--63.

%\bibitem{Sachkov2009}
24. {Sachkov Y.\;L., Ardentov A.\;A., Mashtakov A.\;P.} Konstruktivnoe reshenie zadachi upravleniya na osnove metoda nil'potentnoj approksimacii [Constructive solution to control problem via nilpotent approximation method]. \textit{Programmnye sistemy: teoriia i prilozheniia} [\textit{``Program Systems: Theory and Applications’’}], Pereslavl’-Zalesskij, Russia, 2009. Proceedings of Program Systems Institute Scientific Conference, 2009, vol.~2, pp.~5--23. (In Russian)


%\bibitem{Urkevich2000}
25. {Yurkevich V.\;D.} \textit{Sintez nelinejnyh nestacionarnyh sistem upravleniya s raznotempovymi processami} [\textit{Design of two-time-scale non-linear time-varying control systems}]. St Petersburg, Nauka Publ., 2000, 287~p. (In Russian)

%\bibitem {Kuznetsov2011}
26. {Kuznetsov A.\;V.} Usloviya lokal'noj optimal'nosti dlya nelinejnyh upravlyaemyh sistem v klasse kusochno-postoyannyh upravlenij [Local optimality conditions for non-linear controlled systems in the class of piecewise-constant control laws]. \textit{Vestnik of Rjazan' State Radiotechnical University}, 2011, vol.~38, no.~4, pp.~125--128. (In Russian)

%\bibitem {Smirnov1997}
27. {Smirnov E.\;Y.} \textit{Stabilizaciya programmnyh dvizhenij} [\textit{Stabilization of programmed motion}]. St Petersburg, Saint Petersburg University Press, 1997, 301~p. (In Russian)

%\bibitem {Barbashin1967}
28. {Barbashin E.\;A.} \textit{Vvedenie v teoriyu ustojchivosti dvizheniya} [\textit{Introduction to stability theory}]. Moscow, Nauka Publ., 1967, 224~p. (In Russian)

%\bibitem {Afanasiev_2013}
29. {Afanas'ev V.\;N., Kolmanovskii V.\;B., Nosov V.\;R.} \textit{Matematicheskaya teoriya konstruirovaniya sistem upravleniya} [\textit{Mathematical theory of control systems design}]. Moscow, Vysshaya shkola Publ., 2003, 614~p. (In Russian)

%\bibitem {Kvitko2018}
30. {Kvitko A.\,N.} Solution of the local boundary value problem for a
nonlinear non-stationary system in the class of synthesising controls with account of perturbations.
\textit{Inter. J. Control}, 2020, vol.~93, no.~8, pp.~1931--1941. https://doi.org/10.1080/00207179.2018.1537520


\vskip1.5mm Received:  April 13, 2021.

Accepted: February 01, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Aleksandr N. Kvitko} --- Dr. Sci in Physics and Mathematics, Professor; alkvit46@mail.ru \par
%
\vskip2mm \textit{Nikolay N. Litvinov} --- Postgraduate Student; st080999@student.spbu.ru \par
%
%
}
