

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1.  Bure V. M., Karelin V. V. O zadache planirovanija raboty
terminala [On the problem of planning the terminal]. {\it Vestnik
of Saint Petersburg University. Series 10. Applied mathematics.
Computer science. Control processes}, 2015,  issue~2, pp.~32--38.
(In Russian)

2.  Belzunce F., Martinez-Puertas H.,  Ruiz Jose M.  Onal location
of redundant components for systems with dependent components.
{\it European J. of Operational Research}, 2013, vol.~230,
issue~3, pp.~573--580.

3.   Sobhani A.,  Wahab M. I. M., Neumann W. P.   Investigating
work-related ill health effects in optimizing the performance of
manufacturing systems. {\it European J. of Operational Research},
2015, vol.~241, issue~1, pp.~708--718.

4.  Tang W., Zheng J., Zhang J.   Viability decision  of linear
discrete-time stochastic  systems with probability criterion. {\it
J. Control Theory  Appl.},  2009, vol.~7,  no.~3, pp.~297--300.

5. Yakushev V. P., Karelin V. V., Bure V. M., Bajesovskij podhod v
zadache upravlenija kislotnost'ju sredy  [Bayesian approach for
control soil acidity].  {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathematics. Computer science.
Control processes},  2013,  issue~3, pp.~168--179.  (In Russian)

6. Karelin V. V., Bure V. M.  Optimal'noe razmeshhenie centra
kollektivnogo pol'zovanija  [Optimal allocation of a collective
use center].  {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes},  2014,  issue~4, pp.~36--43. (In Russian)

7.  Polyakova L.N., Karelin V. V., Bure V. M., Chitrow G. M.
Tochnye shtrafnye funkcii v zadache upravlenija odnoj sistemoj
massovogo obsluzhivanija  [Exact penalty function in the problem
of a queuing system].  {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathematics. Computer science.
Control processes},  2015,  issue~1, pp.~75--82.  (In Russian)

8.  Bure V. M., Karelin V. V.,  Elfimov A. N.  Ob odnoj zadache
upravlenija determinirovannoj sistemoj obsluzhivanija [On a
control problem of a deterministic system service]. {\it Vestnik
of Saint Petersburg University. Series~10. Applied mathematics.
Computer science. Control processes},  2015, issue~4,
pp.~100--112. (In Russian)

9.  Bayram  A.,  Solak  S.,   Johnson  M.  Stochastic models for
strategic resource allocation in nonprofit foreclosed housing
acquisitions. {\it European J. of Operational Research}, 2014,
vol.~233, issue~1, pp.~246--262.

10.   Rizhikov Y. I. {\it Queuing theory, and inventory
management}. Saint Petersburg, Peter Publ., 2001, 384~p.

11.     Taha Hamdy A. {\it Operations Research: An Introduction.}
8th ed. Pearson Prentice Hall, Pearson Education Press, 2007,
812~p.

12. Waters D. {\it Inventory control and management}.   New York,
Wiley Press, 2003, 408~p.


\vskip 2mm

{\bf For citation:} Bure V. M., Karelin V. V., Polyakova L. N.
Probabilistic model of terminal services. {\it Vestnik of Saint
Petersburg University. Series~10. Applied mathematics. Computer
science. Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}.
\doivyp/spbu10.\issueyear.\issuenum03



}
