

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



{1}. Sontag~E.~D. \textit {Mathematical control theory:
Deterministic finite dimensional systems}. 2nd ed. New York,
Springer Press, 1998, 544~p.

{2}. Khalil~H. \textit {Nonlinear systems}. Englewood Cliffs, NJ,
Prentice Hall Press, 2002, 766~p.

{3}. Slotine~J., Li~W. {\it Applied nonlinear control}. Englewood
Cliffs, NJ, Prentice Hall Press,   1991, 476~p.

{4}. Lewis~L., Vrabie~D.~L., Syrmos~V.~L. {\it Optimal control}.
Hoboken, NJ, John Wiley \& Sons Press,  2012, 552~p.

{5}. Geering~H.~P. {\it Optimal control with engineering
applications}. Berlin, Heidelberg,  Springer-Verlag Press, 2007,
134~p.

{6}. Sepulchre~R., Jankovic~V., Kokotovic~P. {\it Constructive
nonlinear control}.  New York, Springer Press, 1997, 324~p.

{7}. Fossen~T.~I. {\it Guidance and control of ocean vehicles}.
New York, John Wiley \& Sons Press, 1999, 480~p.

{8}. Do~K., Pan~J. {\it Control of ships and underwater vehicles.
Design for underactuated and nonlinear marine systems}. London,
Springer-Verlag Press, 2009, 402~p.

{9}. Zubov~V.~I.  {\it Kolebania v nelineinyh i upravliaemyh
sistemah} [{\it Oscillations in nonlinear and controlled
systems}]. Leningrad, Sudpromgiz Publ., 1962, 630~p. (In Russian)

{10}. Zubov~V.~I.  {\it Teoria upravlenia sudnom i drugimi
podvizhnymi ob'ektami} [{\it Theory of optimal control of ships
and other moving objects}]. Leningrad, Sudpromgiz Publ., 1966,
352~p. (In Russian)

{11}. Zubov~V.~I. {\it Theorie de la Commande}. Moscow, Mir Publ.,
1978, 470~p.

{12}. Artstein~Z. Stabilization with relaxed controls. \textit
{Nonlinear Analysis}, 1983, vol.~7, pp.~1163--1173.

{13}. Sontag~E.~D. A Lyapunov-like characterization of asymptotic
controllability.     \textit {SIAM Journal of Control and
Optimization}, 1983, vol.~21, pp.~462--471.

{14}. Freeman~R.~A., Kokotovic~P.~V. Inverse optimality in robust
stabilization.     \textit {SIAM Journal of Control and
Optimization}, 1966, vol.~34, pp.~1365--1391.

{15}.  Almobaied~M., Eksin~I., Guzelkaya~M. A new inverse optimal
control method for discrete-time systems. \textit {Proceedings of
12th International Conference on Informatics in Control,
Automation and Robotics}, 2015, pp.~275--280.

{16}. Hahn~W., Baartz~A.~P.~\textit {Stability of motion}. London,
Springer Press, 1967, 446~p.

{17}. Jurdjevic~V., Quinn~J. P. Controllability and stability.
\textit {Journal of Differential Equations}, 1978, vol.~28 (3),
pp.~381--389.

{18}. Hudon~N., Guay~M. Construction of control Lyapunov functions
for damping stabilization of control affine  systems. {\it
Proceedings of 48th IEEE Conference on Decision and Control and
28th Chinese Control Conference}. Shanghai, China, 2009,
pp.~8008--8013.

{19}. Beeler~S.~C., Tran~H.~T., Banks~H.~T. Feedback control
methodologies for nonlinear systems. \textit {Journal of
Optimization Theory and Applications}, 2000, vol.~107 (1),
pp.~1--33.

{20}. Wernrud~A., Rantzer~A. On approximate policy iteration for
continuous-time systems. \textit{Proceedings of 44th Conference on
Decision and Control and European Control Conference}. Seville,
December 2005, pp.~213--220.

{21}. Veremey~E.~I. Special spectral approach to solutions of SISO
LTI H-optimization problems. \textit {Intern. Journal of
Automation and Computing}, 2019, vol.~16 (1), pp.~112--128.

{22}. Sotnikova~M.~V., Veremey~E.~I. Dynamic positioning based on
nonlinear MPC.     \textit {IFAC Proceedings Volumes (IFAC
PapersOnline)}, 2013, vol.~9 (1), pp.~31--36.

{23}. Veremey~E.~I. Separate filtering correction of
observer-based marine positioning control laws. \textit {Intern.
Journal of Control}, 2017, vol.~90 (8), pp.~1561--1575.

{24}. Veremey~E.~I. Optimization of filtering correctors for
autopilot control laws with special structures. \textit {Optimal
Control Applications and Methods}, 2016, vol.~37 (2),
pp.~345--348.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  February 24, 2020.

Accepted: August 13, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r'\,s \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Evgeny I. Veremey} --- Dr. Sci. in Physics and
Mathematics, Professor%, Head of the department
; e\_veremey@mail.ru


}
