
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip1.5mm


1. \textit{Красовский~Н.~Н.} Некоторые задачи теории устойчивости
движения. М.: Гос. изд-во физ.-мат. лит., 1959. 211~с.

2. \textit{Hale J.\,K.} Theory of functional differential
equations. New York: Springer, 1977. 365~p.

3. \textit{Kharitonov~V.~L.} Time-delay systems. Lyapunov
functionals and matrices. Basel: Birkh\"au\-ser, 2013. 311~p.

4. \textit{Kharitonov~V.~L., Zhabko~A.~P.}
\mbox{Lyapunov--Krasovskii} approach for robust stability of time
delay systems~// Automatica. 2003. Vol.~39. P.~15--20.

5. \textit{Ochoa~G., Vel\'azquez~J.~E., Kharitonov~V.~L.,
Mondi\'e~S.} Lyapunov Matrices for Neutral Type Time Delay Systems
// Topics in Time Delay Systems~/ eds J.~J.~Loiseau et al.
Heidelberg: Springer-Verlag, 2009. P.~61--71.

6. \textit{Egorov~A.~V., Mondi\'e~S.} Necessary stability
conditions for linear delay systems~// Automa\-tica. 2014.
Vol.~50. P.~3204--3208.

7. \textit{Medvedeva~I.~V., Zhabko~A.~P.} Synthesis of Razumikhin
and \mbox{Lyapunov--Krasovskii} appro\-aches to stability analysis
of time-delay systems~// Automatica. 2015. Vol.~51. P.~372--377.

8. \textit{Jarlebring~E., Vanbiervliet~J., Michiels~W.}
Characterizing and computing the $\mathcal{H}_2$ norm of
time-delay systems by solving the delay Lyapunov equation~// IEEE
Trans. on~Autom. Contr. 2011. Vol.~56(4). P.~814--825.

9. \textit{Сумачева~В.~А., Харитонов~В.~Л.} Вычисление
$\mathcal{H}_2$ нормы передаточной матрицы системы нейтрального
типа~// Дифференциальные уравнения и~процессы управления. 2014.
№~4. С.~22--32.

10. \textit{Egorov~A.~V., Mondi\'{e}~S.} A stability criterion for
the single delay equation in terms of the Lyapunov matrix~//
Вестн. С.-Петерб. ун-та. Сер.~10. Прикладная математика.
Информатика. Процессы управления. 2013. Вып.~1. С.~106--115.

11. \textit{Huesca~E., Mondi\'e~S., Santos~J.} Polynomial
approximations of the Lyapunov matrix of a class of time delay
systems~// 8th IFAC Workshop on Time Delay Systems. Sinaia,
Romania, 2009. P.~261--266.

12. \textit{Егоров~А.~В.} Вычисление матриц Ляпунова для систем
с~запаздыванием~// Труды XII Всерос. совещания по~проблемам
управления. М., 2014. С.~1292--1303.

13. \textit{Чашников~М.~В.} Анализ устойчивости линейных систем
с~запаздывающим аргументом: дис. на~соискание учен. степени канд.
физ.-мат. наук. СПб.: С.-Петерб. ун-т, 2010. 94~с.

14. \textit{Bellman~R., Cooke~K.} Differential difference
equations. New York: Academic Press, 1963. 465~p.






}
