

{\footnotesize

\vskip 2mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 1.5mm



1. Krasovskii~N.~N. \textit{Nekotorye zadachi teorii ustojchivosti
dvizheniya} [\textit{Some problems in the theory of stability of
motion}]. Moscow, Fizmatlit Publ., 1959, 211~p. (In Russian)

2. Hale J.\,K. \textit{Theory of functional differential
equations}. New York, Springer, 1977, 365~p.

3. Kharitonov~V.~L. \textit{Time-delay systems. Lyapunov
functionals and matrices}. Basel, Birkh\"au\-ser, 2013, 311~p.

4. Kharitonov~V.~L., Zhabko~A.~P. \mbox{Lyapunov--Krasovskii}
approach for robust stability of time delay systems.
\textit{Automatica}, 2003, vol.~39. pp.~15--20.

5. Ochoa~G., Vel\'azquez~J.~E., Kharitonov~V.~L., Mondi\'e~S.
Lyapunov matrices for neutral type time delay systems.
\textit{Topics in Time Delay Systems}. Eds J.~J.~Loiseau et al.
Heidelberg, Springer-Verlag, 2009, pp.~61--71.

6. Egorov~A.~V., Mondi\'e~S. Necessary stability conditions for
linear delay systems. \textit{Automatica}, 2014, vol.~50,
pp.~3204--3208.

7. Medvedeva~I.~V., Zhabko~A.~P. Synthesis of Razumikhin and
\mbox{Lyapunov--Krasovskii} appro\-aches to stability analysis of
time-delay systems. \textit{Automatica}, 2015, vol.~51,
pp.~372--377.

8. Jarlebring~E., Vanbiervliet~J., Michiels~W. Characterizing and
computing the $\mathcal{H}_2$ norm of time-delay systems by
solving the delay Lyapunov equation. \textit{IEEE Trans. on Autom.
Contr.}, 2011, vol.~56(4), pp.~814--825.

9. Sumacheva~V.~A., Kharitonov~V.~L. Vychislenie $\mathcal{H}_2$
normy peredatochnoj matricy sistemy nejtral'nogo tipa [On
$\mathcal{H}_2$ norm of the transfer matrix of neutral type
time-delay system]. \textit{Differenci\-alnye uravneniya i
processy upravleniya} [\textit{Differential Equations and Control
Processes}], 2014, vol.~4, pp.~22--32. (In Russian)

10. Egorov~A.~V., Mondi\'{e}~S. A stability criterion for the
single delay equation in terms of the Lyapunov matrix.
\textit{Vestnik of Saint~Petersburg University. Series 10. Applied
mathematics. Computer science. Control processes}, 2013, issue~1,
pp.~106--115.

11. Huesca~E., Mondi\'e~S., Santos~J. Polynomial approximations of
the Lyapunov matrix of a class of time delay systems. \textit{8th
IFAC Workshop on Time Delay Systems}. Sinaia, Romania, 2009,
pp.~261--266.

12. Egorov~A.~V. Vychislenie matric Lyapunova dlya sistem s
zapazdyvaniem [Computation of the Lyapunov matrices for time delay
systems]. \textit{Trudy XII Vseros. soveshchaniya po problemam
upravleniya} [\textit{Proceedings of the 12th All-Russian
Conference on Control Problems}]. Moscow, Russia, 2014,
pp.~1292--1303. (In Russian)

13. Chashnikov~M.~V. \textit{Analiz ustojchivosti linejnyh sistem
s zapazdyvayushchim argumentom} [\textit{Stability analysis of
linear time delay systems}]. PhD. Dis. Saint~Petersburg,
Saint~Peter\-sburg State University, 2010, 94~p. (In Russian)

14. Bellman~R., Cooke~K. \textit{Differential difference
equations}. New York, Academic Press, 1963, 465~p.




}
