
{\small

\vskip4.5%6
mm
%\newpage
 \noindent \textbf{Литература}

}

\vskip3
mm

{\footnotesize

1. {\it Зубов В. И.} Колебания в нелинейных и управляемых системах.
Л.: Судпромгиз,  1962. 631~с.


2. {\it Provotorov V. V., Sergeev S. M., Hoang V. N.}
Point control of a differential-difference system with distributed parameters on the graph~//
Вестник Санкт-Петербургского университета.
Прикладная математика.
Информатика. Процессы управления.  2021. Т.~17. Вып.~3. C.~277--286.
https://doi.org/10.21638/11701/spbu10.2021.305\pagebreak


3. {\it Zhabko A. P., Provotorov V. V.,  Ryazhskikh V. I.,  Shindyapin A. I.}
Optimal control of a differential-difference parabolic systems with distributed parameters
on the graph~//
Вестник Санкт-Петербургского университета.
Прикладная математика.
Информатика. Процессы управления.  2021. Т.~17. Вып.~4. C.~433--448.
https://doi.org/10.21638/11701/spbu10.2021.411


4.  {\it Tkhai V. N.} Model with coupled subsystems //
{Automation and Remote Control}. 2013. Vol.~74. N~6. P.~919--931.




5.   {\it Sedighi H. M.,  Daneshmand F.}    Nonlinear transversely vibrating beams by the homotopy
perturbation method with an auxiliary term~//  {
 Journal of Applied and Computational Mechanics}.  2015. Vol.~1. N~1. P.~1--9.




6. {\it Park Y., Lee C.} Dynamic investigation of non-linear behavior of
hydraulic
cylinder in mold oscillator
using PID control process~//  Journal of Applied and Computational Mechanics. 2021. Vol.~7. N~1.
P.~270--276.



7. {\it Aleksandrov A. Yu., Stepenko N. A.} Stability analysis of gyroscopic systems
with delay under   synchronous and asynchronous switching~//
Journal of Applied and Computational Mechanics.
2022. Vol.~8. N~3.  P.~1113--1119.


8. {\it Демидович Б. П.} Лекции по математической теории устойчивости. М.: Наука,
1967.  472~с.

9. {\it Pavlov A., Pogromsky A., van  de Wouw N.,  Nijmeijer H.}
Convergent dynamics,
a tribute to Boris Pavlovich Demidovich~// Syst. Control Lett. 2004. Vol.~52. P.~257--261.


10. {\it Ruffer B., van de Wouw N., Mueller M.}
Convergent systems vs. incremental stability~// Syst. Control Lett.
2013. Vol. 62. P. 277--285.


11.  {\it Chen F.} Some new results on the permanence and extinction of
nonautonomous Gilpin\,---\,Ayala type competition model with delays~// Nonlinear Analysis:
Real World Applications. 2006. Vol.~7. P.~1205--1222.


12. {\it Aleksandrov A., Aleksandrova E.} Convergence conditions for some
classes of nonlinear systems~// Syst. Control Lett. 2017.
Vol.~104. P.~72--77.



13. {\it Mei W., Efimov D., Ushirobira R., Aleksandrov A.} On convergence
conditions for
generalized Persidskii systems~// Intern. Journal of Robust Nonlinear Control. 2022.
Vol.~32. N~6. P.~3696--3713.


14.  {\it Pliss V. A.} Nonlocal problems of the theory of oscillations.
London: Academic Press,
 1966. 306~p.



15. {\it Атаева Н. Н.} Свойство конвергенции для разностных систем //
Вестник Санкт-Пе\-тер\-бург\-ско\-го университета.
 Сер.~10.                         Прикладная математика.
Информатика. Процессы управления.
 2004. Вып.~4. С.~91--98.


16. {\it Yakubovich V.} Matrix inequalities in stability theory for nonlinear control
systems. III. Absolute stability of forced vibrations //
{Automation and Remote Control}. 1964. Vol.~7.  P.~905--917.


17. {\it Нгуен Д. Х.} Условия конвергенции некоторых классов нелинейных
разностных систем // Вестник Санкт-Петербургского университета.
Сер. 10. Прикладная математика.
Информатика. Процессы управления.  2011.  Вып.~2. С.~90--96.



18. {\it  Aleksandrov A. Yu.} Some convergence and stability conditions for nonlinear
systems // Differ. Equ. 2000. Vol.~36. N~4. P.~613--615.

19. {\it Kosov A. A., Shchennikov V. N.} On the convergence phenomenon in
complex almost periodic systems // Differ Equ. 2014. Vol.~50. N~12. P.~1573--1583.



20. {\it Стрекопытов С. А., Стрекопытова М. В.}
О конвергенции динамических ква\-зи\-пе\-рио\-ди\-чес\-ких систем //
Вестник Санкт-Петербургского университета.
Прикладная математика.
Информатика. Процессы управления.  2022. Т.~18. Вып.~1. C.~79--86. \\
https://doi.org/10.21638/11701/spbu10.2022.106



21. {\it Пых Ю. А.} Равновесие и устойчивость в моделях популяционной
динамики. М.: Наука, 1983. 182~c.


22. {\it Hofbauer J., Sigmund K.} Evolutionary games and population dynamics.
Cambridge: Cambridge University Press, 1998. 323~p.



23. {\it Britton N. F.} Essential mathematical biology.
London; Berlin; Heidelberg: Springer,  2003. 335~p.


24. {\it  Aleksandrov A. Yu.,  Aleksandrova E. B.,  Platonov A. V.}
 Ultimate boundedness conditions for a hybrid model of population dynamics //
Proceedings of 21$^{\rm st}$ Mediterranean conference on Control and
Automation.  June~25--28. 2013. Platanias-Chania, Crite,  Greece, 2013.
P.~622--627.



25. {\it Халанай А., Векслер Д.} Качественная  теория импульсных систем /
пер. с румынск.; под ред.
В. П. Рубаника. М.: Мир, 1971. 312~c.


%\pagebreak
\vskip 1.2mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 23 апреля 2022~г.

Cтатья принята к~печати 1 августа 2022~г.

\vskip6mm

К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Александров Александр Юрьевич}  --- д-р физ.-мат.
наук,  проф.;
  a.u.aleksandrov@spbu.ru \par%
%
%
}
