

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. Bachmann M., Dusberg F., Langer C., Herdl F., Bergbreiter L., Dams F., Miya\-ka\-wa N., Eg\-gert~T., Pahl\-ke~A., Ed\-ler~S., Prom\-mes\-ber\-ger~C., Lawrowski~R., Hausladen~M., Schreiner R. Vacuum-sealed field emission electron gun. {\it Journal of Vacuum Science and Technology~B. Nanotechnology and Microelectronics},  2020, vol.~38, iss.~2, no.~023203.
%  DOI: 10.1116/1.5139316


2. Tripathi P., Gupta B. K., Bankar P. K.,  More M. A., Late D. J., Srivastava O. N. Graphene nanosheets assisted carbon hollow cylinder for high-performance field emission applications. {\it Materials Research Express}, 2019, vol.~6, iss.~9, no.~095066.
% DOI: 10.1088/2053-1591/ab3030
%(10p)

3. Jones W. M., Lukin D., Scherer  A. Practical nanoscale field emission devices for integrated circuits. {\it Applied Physics Letters},  2017, vol.~110, iss.~26, no.~263101.
% (4p)263101
% DOI: 10.1002/adom.201900504

4. Sominskii G. G., Tumareva T. A., Taradaev E. P.,  Rukavitsyna A. A., Givargizov M. E., Ste\-pa\-no\-va~A.~N. Annular multi-tip field emitters with metal-fullerene protective coatings. {\it Technical Physics}, 2019,  vol.~64, iss.~2, pp.~270--273.
% DOI: 10.1134/S106378421902021X

5. Nguyen H. D., Kang J. S., Li M., Hu Y. High-performance field emission based on nanostructured tin selenide for nanoscale vacuum transistors. {\it Nanoscale}, 2019,  vol.~11, iss.~7, pp.~3129--3137.
% DOI: 10.1039/c8nr07912a


6. Vinogradova E. M., Egorov N. V., Televnyi D. S. Calculation of a triode field-emission system with a~modulator. {\it Technical Physics}, 2014,  vol.~59, iss.~2, pp.~291--296.
%DOI: 10.1134/S1063784214020236

7. Egorov N. V., Vinogradova E. M. Mathematical modeling of the electron beam formatting systems on the basis of field emission cathodes with various shapes. {\it User Modeling and User-Adapted Interaction}, 2003, vol.~72, iss.~2, pp.~103--111.
  %DOI:10.1016/S0042-207X(03)00107-6


8.  Maji\'c M. R. A., Gray F., Augui\'e B., Ru E. C. L. Electrostatic limit of the $T$-matrix for electromagnetic scattering: Exact results for spheroidal particles. {\it Journal of Quantitative Spectroscopy and Radiative Transfer}, 2017, vol.~200, pp.~50--58.
 % DOI: 10.1016/j.jqsrt.2017.05.031 	


9. Maji\'c M. R. A., Gray F., Augui\'e B., Ru E. C. L. Spheroidal harmonic expansions for the solution of Laplace’s equation for a point source near a sphere. {\it Physical Review E}, 2017, vol.~95,  iss.~3, no.~033307.
%DOI: 10.1103/PhysRevE.95.033307

10. Techaumnat B., Huynh V., Hidaka K. Three-dimensional lectromechanical analysis of a conducting prolate spheroid on a grounded plane. {\it IEEE Transactions on Dielectrics and Electrical Insulation}, 2014, vol.~21,  iss.~1, pp.~80--87, no.~6740728.
% DOI: 10.1109/TDEI.2013.004294

11. Xue C., Edmiston R., Deng S. Image theory for Neumann functions in the prolate spheroidal geometry. {\it Advances in Mathematical Physics}, 2018, vol.~2018, no.~7683929.
% DOI: 10.1155/2018/7683929

%{ \it Vinogradova E. M.,  Egorov N. V., Mutul M. G., Shen C.-C.}
%Calculation of the electrostatic potential of the diode system based on a sharp edged %field cathode.
%Tech. Phys. \textbf{55}(5) 591-594 (2010)
%%%% potential
%Maslova, T.A., Vinogradova, E.M.
%Diode system on the basis of field emitter with semi-ellipsoid shape mathematical modeling.
%{ \it 2016 Young Researchers in Vacuum Micro/Nano Electronics, VMNE-YR 2016 - Proceedings}, N 7880411.
%% DOI: 10.1109/VMNEYR.2016.7880411 	

12. Abramowitz M., Stegun I. A. {\it  Handbook of mathematical functions with formulas, graphs, and mathematical tables}. Washington, DC, NBS Press,   1964,  1046~p. (Ap\-plied Mat\-he\-ma\-tics. Se\-ries~55).


13. Bateman H., Erdelyi A. {\it Higher transcendental functions}.  In 2~vol. New York, Toronto, London, McGraw-Hill Book Company Inc., 1953,  vol.~1, 302~p.

14. Gradshteyn I. S., Ryzhik I. M. {\it  Table of integrals, series, and products}. 7th ed.  Amsterdam, Bos\-ton, Heidelberg, London, New York, Oxford, Paris, San Diego, San Francisco, Singapore, Sydney, To\-kyo, Academic Press, 2007, 1171~p.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December 18, 2020.

Accepted: April 05, 2021.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Nickolay V. Egorov}  --- Dr. Sci. in Physics and Mathematics, Professor; robby7@mail.ru

\vskip 2mm \textit{Ekaterina M. Vinogradova}  --- Dr. Sci. in Physics and Mathematics, Professor;\\ e.m.vinogradova@spbu.ru \par%
%
%
}
