
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. {\it Graham R. L., Lawler E. L., Lenstra J. K., Rinnooy~Kan~A.~H.~G.} Optimization and ap\-pro\-xi\-ma\-tion in deterministic
sequencing and scheduling: A survey~// Annals of Discrete Mathematics. 1979. Vol.~5. N~10. P.~287--326.



2. {\it Lenstra J. K., Rinnooy~Kan~A.~H.~G.,  Brucker P.} Complexity of machine scheduling problems~// Annals of Discrete Mathematics. 1977. Vol.~1. P.~343--362.


3. {\it Лазарев А. А., Садыков Р. Р., Севастьянов С. В.} Схема приближенного решения задачи  $1|r_i|L_{\max}$~//
Дискретный анализ и исследование операций. Сер.~2. 2006. Т.~13. №~1. С.~57--76.

4. {\it Baker K. R.} Introduction to sequencing and scheduling. New York:  John Wiley $\&$ Son, 1974. 318~p.



5. {\it Kanet J. J., Sridharan V.} Scheduling with inserted idle time: problem taxonomy and literature review~// Operations Research. 2000. Vol.~48. N~1. P.~99--110.


6. {\it Григорьева Н. С.} Алгоритм ветвей и границ для задачи составления расписаний на параллельных процессорах~//
Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика. Информатика. Процессы управления. 2009. Вып.~1. С.~44--55.


7. {\it Григорьева Н. С.} Задача минимизации максимального временного смещения для параллельных процессоров~//
Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика. Информатика. Процессы управления. 2016. Вып.~4. С.~51--65.




8. {\it Grigoreva N. S.}  Multiprocessor scheduling with inserted idle time to minimize the maximum lateness~//
Proceedings of the 7th Multidisciplinary International Conference of Scheduling: Theory and Applications.
Prague: MISTA, 2015. P.~814--816.

9.{\it Grigoreva N. S.}   Single machine inserted idle time scheduling
with release times and due dates //  Proceedings. DOOR2016. Vladivostoc, Russia. September 19--23, 2016. Ceur-WS. 2016. Vol.~1623.\linebreak P.~336--343.

10. {\it Schrage L.} Optimal solutions to resource constrained network scheduling problems. Unpublished manuscript. 1971.

11. {\it Kise H., Ibaraki T., Mine H.} Performance analysis of six  approximation algorithms for the one-machine maximum  lateness scheduling problem with  ready times~// Journal of the Operations  Research Society of Japan. 1979.  N~22. P.~205--224.

12. {\it Potts C. N.} Analysis of a heuristic for one machine sequencing with release dates and delivery times~// Operations Research. 1980. Vol.~28. P.~1436--1441.

13. {\it Hall L. A., Shmoys D. B.} Jackson's rule for single-machine scheduling: making a good heuristic better~// Mathematics of Operations Research. 1992.  Vol.~17. N~1. P.~22--35.

14. {\it Nowicki E., Smutnicki C.} An approximation algorithm for a single-machine scheduling problem with release times and delivery times~//  Discrete Applied Mathematics. 1994. Vol.~48. P.~69--79.

15. {\it Hall L.  A.,  Shmoys D. B.} Approximation algorithms for constrained  scheduling problems~//  Proceedings of the 30th IEEE Symposium on Foundations  of Computer Science. IEEE Computer Society Press. 1989. P.~134--139.

16. {\it Mastrolilli M.} Efficient approximation schemes for scheduling problems with release dates and delivery times~// Journal of Scheduling. 2003. Vol.~6. P.~521--531.

17. {\it Carlier J.} The one machine sequencing problem~// European Journal of Operational Research. 1982. Vol.~11.  P.~42--47.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 12 февраля 2021~г.

Cтатья принята к~печати 4 июня 2021~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Григорьева Наталья
Сергеевна} --- канд. физ.-мат. наук, доц.;
n.s.grig@gmail.com

}
