

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. {\textnormal Chashnikova~V.} The sufficient conditions of the
measuring basis optimality on the fixed time interval.  {\itshape
AIP Conference Proceedings}, 2018, vol.~1978, art. no.~100004.

2. {\textnormal Chashnikov~M.} The stochastic characteristics
stability in the problem of the dynamic filtration with delay.
{\itshape AIP Conference Proceedings}, 2017, vol.~1863, art.
no.~170003.

3. {\textnormal Elyasberg~P.~E.} {\itshape Opredelenie dvizheniya
po rezultatam izmereniy} [{\itshape Solution of motion after
measuring results}]. Moscow, Nauka~Publ., 1976, 416~p. (In
Russian)

4. {\textnormal Chashnikova~V.} Choosing a measuring basis to
estimate parameters of a dynamic object.  {\itshape AIP Conference
Proceedings}, 2016, vol.~1738, article no.~160004.

5. {\textnormal Churov~E.~P., Suvorov~E.~F.} {\itshape
Kosmicheskie sredstva sudovozhdeniya} [{\itshape Space navigation
facilities}]. Moscow, Transport~Publ., 1979, 287~p. (In Russian)



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 18, 2020.

Accepted: October 23, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Mikhail V. Chashnikov} --- PhD in Physics and
Mathematics, Associate Professor;\\ m.chashnikov@spbu.ru

\vskip 2mm \textit{Valentina V. Chashnikova} --- PhD in Physics
and Mathematics, Associate Professor;\\ v.chashnikova@spbu.ru


}
