
{\small

\vskip6
mm \noindent \textbf{Литература}

}

\vskip3
mm

{\footnotesize

1. \emph{Fishman G.} Monte-Carlo: concepts, algorithms and applications. New York: Springer, 1995. 722~p.

2. \emph{Kudryavtsev O.} Approximate Wiener\,---\,Hopf factorization and Monte-Carlo methods for Levy processes~// Probability Theory and its Applications. 2019. Vol.~64(2). P.~186--208.

3. \emph{Girsanov I.} On the transformation of a class of random processes using a completely continuous measure replacement~// Probability Theory and its Applications. 1960. Vol.~5. P.~314--330.

4. \emph{Новиков~А.} Об одном тождестве для стохастических интегралов~// Теория вероятностей и ее применения. 1972. №~4. С.~761--765.

5. \emph{Kloeden P., Platen E.} Numerical solution of stochastic differential equations. New York: Springer, 1995. 632~p.

6. \emph{Carr P.} Randomization and American put~// Rev. Financ. Stud. 1996. N~11. P.~597--626.

7. \emph{Kuznetsov~A., Kyprianou~A.\,E., Pardo~J.\,C., van Schaik~K.} A Wiener\,---\,Hopf Monte-Carlo simulation technique for L\'{e}vy processes~// Ann. Appl. Prob. 2011. N~21. P.~2171--2190.

8. \emph{Ferreiro-Castilla~A., Kyprianou~A.\,E., Scheichl~R., Suryanarayana~G.} Multilevel Monte-Carlo simulation for L\'{e}vy processes based on the Wiener\,---\,Hopf factorization~// Stoch. Process. Appl. 2014. N~124. P.~985--1010.

9. \emph{Beliavsky~G., Danilova~N., Ougolnitsky~G.} Calculation of probability of the exit of a stochastic process from a band by Monte-Carlo method: A Wiener\,---\,Hopf factorization~// Mathematics. 2019. N~7. P.~581--597.

10. \emph{Beliavsky~G.\,I., Danilova~N.\,V.} The combined Monte-Carlo method to calculate the capital of the optimal portfolio in nonlinear models of financial indexes~// Siberian Electronic Mathematical Reports. 2014. N~11. P.~1021--1034.

11. \emph{Aubin J.-P.} Viability theory. New York, USA: Springer-Verlag, 1991. 342~p.

12. \emph{Ougolnitsky G.} Sustainable management. New York, USA: Nova Science Publ. Hauppauge, 2011. 287~p.

13. \emph{Ширяев~А.\,Н.} О мартингальных методах в~задачах о~пересечении границ броуновским движением~// Современные проблемы математики. 2007. Вып.~8. С.~3--78.

14. \emph{Casella~G., Robert~C.~P., Wells~M.~T.} Generalized accept-reject sampling chemes~// Institute of Mathematical Statistics. 2004. P.~342--347.

15. \emph{Камачкин~А. М., Степенко~Н. А., Хитров~Г. М.} К теории конструктивного построения линейного регулятора~// Вестник Санкт-Петербургского университета. Прикладная  математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~3. С.~326--344. \\
https://doi.org/10.21638/11701/spbu10.2020.309

%\pagebreak
\vskip 1.2mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 3 июня 2021~г.

Cтатья принята к~печати 1 февраля 2022~г.

\vskip6mm

К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Белявский Григорий Исаакович}~--- д-р техн. наук, проф.; gbelyavski@sfedu.ru\par%
%
\vskip2 mm \textit{Данилова Наталья Викторовна}~--- канд. физ.-мат. наук, доц.; nvdanilova@sfedu.ru\par%
%
\vskip2 mm \textit{Угольницкий Геннадий Анатольевич}~--- д-р физ.-мат. наук, проф.; gaugolnickiy@sfedu.ru\par%
%
%
}
