

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i raspredekennemi parametrami na grafe [Synthesis of optimal boundary control of parabolic systems with delay and distributed parameters on the graph]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2017, vol.~13, iss.~2, pp.~209--224. https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)

2. Provotorov V. V., Provotorova E. N. Optimal control of the linearized Navier\,---\,Stokes system in a netlike domain. \emph{Vestnik of Saint Petersburg University.  Applied Mathematics. Computer Science. Control Processes}, 2017, vol.~13, iss.~4, pp.~431--443.
https://doi.org/10.21638/11701/spbu10.2017.409

3. Provotorov V. V. Boundary control of a parabolic system with delay and distributed parameters on the graph. \emph{International Conference ``Stability and Control Processes'' in memory of V.~I.~Zubov (SCP)}. St.~Petersburg, Russia, 2015, pp.~126--128.

4. Podvalny S.~L., Provotorov V.~V. Startovoe upravlenie parabolicheskoj sistemoj s raspredelennymi parametrami na grafe [Starting control of a parabolic system with distributed
parameters on a graph]. \textit{Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes}, 2015, iss.~3, pp.~126--142. (In Russian)

5. Provotorov V. V., Sergeev S. M., Hoang V. N. Countable stability of a weak solution of a parabolic differential-difference system with distributed parameters on the graph. \emph{Vestnik of Saint Petersburg Uni\-ver\-sity. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~4, pp.~402--414. https://doi.org/10.21638/11701/spbu10.2020.405


6. Zhabko~A.~P.,~Shindyapin~A.~I.,~Provotorov~V.~V.  Stability of weak solutions of pa\-ra\-bo\-lic systems with distributed parameters on the graph. \textit{Vestnik of Saint Petersburg University. Ap\-plied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~4, pp.~457--471.\\ https://doi.org/10.21638/11701/spbu10.2019.404

7. Podvalny S. L., Provotorov V. V., Podvalny E. S.  The controllability of parabolic systems with delay and distributed parameters on the graph. \emph{Procedia Computer Sciense}, 2017, vol.~103, pp.~324--330.


8. Volkova A.~S., Provotorov V.~V.  Generalized solutions and generalized eigenfunctions of boundary-value problems on a geometric graph. \emph{Russian Mathematics}, 2014, vol.~58, no.~3,  pp.~1--13.  Available at: http://www.scopus.com/authid/detail.uri?authorid=24451043200 (accessed: February 10, 2021).

9. Provotorov V.~V. Razlozenie po sobstvennym funkciyam zadachi Shturma\,---\,Liuvillya na grafe-puchke [Expansion  of eigenfunctions of Sturm\,---\,Liouville problem on astar graph]. \emph{Russian Mathematics}, 2008, vol.~3, pp.~45--57. (In Russian)

10. Zhabko A. P.,  Provotorov V. V., Balaban O. R.  Stabilization of weak solutions of pa\-ra\-bo\-lic systems with distributed parameters on the graph. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~2, pp.~187--198.\\ https://doi.org/10.21638/11701/spbu10.2019.203

11. Provotorov V.~V., Sergeev S.~M., Part A.~A. Solvability of hyperbolic systems with dis\-tri\-bu\-ted parameters on the graph in the weak formulation. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~1, pp.~107--117.\\
https://doi.org/10.21638/11701/spbu10.2019.103


12. Lions J.-L. \textit{Quelques m\'{e}thodes de r\'{e}solution des probl\`{e}mes aux limites non lin\'{e}aires} [\textit{Some methods of solving non-linear boundary value problems}]. Paris, Dunod-Gauthier-Villars Publ., 1969, 554~p. (In French). (Rus. ed.: Lions J.-L. \textit{Nekotorye metody resheniya nelineinykh kraevykh zadach}. Moscow, Mir Publ., 1972, 587~p.)

13. Alexandrova I.~V., Zhabko A.~P.  A new LKF approach to stability analysis of linear systems with uncertain delays. \emph{Automatica}, 2018, vol.~91, pp.~173--178.

14. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic stability conditions for certain classes of mechanical systems with time delay. \emph{WSEAS Transactions on Systems and Control}, 2014, vol.~9, pp.~388--397.

15. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic stability conditions of solutions for nonlinear multiconnected time-delay systems. \emph{Circuits  Systems and Signal Processing}, 2016, vol.~35, no.~10, pp.~3531--3554.

16.	Karelin V.~V.  Shtrafnye funkcii v zadache upravleniya processom nabludeniya [Penalty functions in the control problem of an observation process]. \emph{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2010, iss.~4, pp.~109--114. (In Russian)

17. Karelin V.~V., Bure V.~M., Svirkin M.~V. Obobchennaja model rasprostranenija informacii v neprerivnom vremeni [The generalized model of information dissemination in continuous time]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2017, vol.~13, iss.~1, pp.~74--80. https://doi:10.21638/11701/spbu 10.2017.107 (In Russian)

18.	Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze prognoza s ustoichivym lineinym priblizheniem [Plasma stabilization by prediction with stable linear approximation]. \emph{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2011, iss.~1, pp.~116--133. (In Russian)

19.	Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. Existence of periodic modes in automatic control system with a three-position relay. \emph{Intern. Journal Control}, 2020, vol.~93, no.~4, pp.~763--770.

20. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V. On uniqueness and properties of periodic solution of second-order nonautonomous system with discontinuous nonlinearity. \emph{J. Dyn. Control Syst.}, 2017, vol.~23, no.~4, pp.~825--837.

21. Artemov M. A.,  Baranovskii E. S., Zhabko A. P., Provotorov V. V.  On a 3D model of non-iso\-ther\-mal flows in a pipeline network. \emph{Journal of Physics. Conference Series}, 2019, vol.~1203, Art. ID~012094. https://doi.org/10.1088/1742-6596/1203/1/012094

22. Provotorov V.~V., Ryazhskikh V.~I., Gnilitskaya Yu.~A.  Unique weak solvability of nonlinear initial boundary value problem with distributed parameters in the netlike domain. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2017, vol.~13, iss.~3, pp.~264--277. https://doi.org/10.21638/11701/spbu10.2017.304


23. Krasnov S., Zotova E., Sergeev S., Krasnov A., Draganov M. Stochastic algorithms in multimodal 3PL segment for the digital environment. {\it IOP Conference. Series Materials Science and Engineering}, 2019, vol.~618, conference~1.
https://doi.org/10.1088/1757-899X/618/1/012069

24. Krasnov S., Sergeev S., Zotova E., Grashchenko N. Algorithm of optimal management for the efficient use of energy resources. {\it E3S Web of Conferences}, 2019, vol.~110, no.~02052.\\  https://doi.org/10.1051/e3sconf/201911002052

25. Golosnoy A. S., Provotorov V. V., Sergeev S. M., Raikhelgauz L. B., Kravets O. Ja. Software engineering math for network applications. {\it Journal of Physics. Conferences Series}, 2019, vol.~1399(4), no.~044047.
https://doi.org/10.1088/1742-6596/1399/4/044047


\vskip 2%1.5
mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  March 15, 2021.

Accepted: June 04, 2021.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Vyacheslav V. Provotorov} --- Dr. Sci. in Physics and Mathematics, Professor;  wwprov@mail.ru \par

\vskip 2mm \textit{Sergey M. Sergeev} ---  PhD in Technics, Associate Professor;   sergeev2@yandex.ru \par


\vskip 2mm \textit{Nguyen Hoang Van} --- Postgraduate Student; fadded9x@gmail.com \par
%
%
}
