
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. {\it	Xiao R., Sun H., Chen W.} An equivalence between generalized maxwell model and fractional zener model // Mechanics of Materials. 2016. Vol.~100. P.~148--153.

2. {\it	Sethuraman V., Makornkaewkeyoon K., Khalf A., Madihally S.~V.} Influence of scaffold forming techniques on stress relaxation behavior of polycaprolactone scaffolds // Journal of Applied Polymer Science. 2013. Vol.~130. P.~4237--4244.

3. {\it	Shazly T.~M., Artzi N., Boehning F., Edelman E.~R.}  Viscoelastic adhesive mechanics of aldehyde-mediated soft tissue sealants // Biomaterials. 2008. Vol.~29. P.~4584--4591.

4. {\it	Feng Z., Seya D., Kitajima T., Kosawada T., Nakamura T., Umezu M.} Visco\-elastic characteristics of contracted collagen gels populated with rat fibroblasts or cardio\-myocytes  //  Journal of Artificial Organs. 2010. Vol.~13. P.~139--144.

5.	{\it Tirella A., Mattei G., Ahluwalia A.}  Strain rate viscoelastic analysis of soft and highly hydrated biomaterials // Journal of Biomedical Materials Research. 2014. Vol.~102. P.~3352--3360.

6. {\it Capocardo~L., Costa~J., Giusti~S., Buoncompagni~L., Meucci~S., Corti~A., Mattei~G., Ahluwalia~A.} Real-time cellular impedance monitoring and imaging of biological barriersin a dual-flow membrane bioreactor // Biosensors and Bioelectronics. 2019. Vol.~140. P.~1--9.

7.	{\it Kizilova N.~N.} Presser wave propagation in liquid field // Fluid dynamics. 2006. Vol.~41. N~3. P.~434--446.

8.	{\it Orne D., Liu Y.~K.} A mathematical model of spinal response to impact // Journal of Biomechanics. 1971. Vol.~4. N~1. P.~49--71.

9. {\it Braunsmann C., Proksch R., Revenko I., Sch\"affer T. E.} Creep compliance mapping by atomic force microscopy // Polymer. 2014. Vol.~55. P.~219--225.

10.	{\it Petit-Zeman S.} Regenerative medicine // Nature Biotechnology. 2001. Vol.~19. P.~201--206.

11. {\it O'Brien F.~J.} Biomaterials $\&$ scaffolds for tissue engineering // Materials Today. 2011. Vol.~14. P.~88--95. %\\
https://doi.org/10.1016/S1369-7021(11)70058-X

12.	{\it Smith B.~D., Grande D.~A.} The current state of scaffolds for musculoskeletal regenerative applications // Nature Reviews Rheumatology. 2015. Vol.~11. P.~213--222.

13.	{\it Agarwal R., Garc\'{i}a A. J.} Biomaterial strategies for engineering implants for enhanced osseointegration and bone repair // Advanced Drug Delivery Reviews. 2015. Vol.~94. P.~53--62.

14.	{\it  Deng C.~X., Hong X., Stegemann J.~P.} Ultrasound imaging techniques for spatio\-temporal characterization of composition, microstructure, and mechanical properties in tissue engineering // Tissue Engineering. Pt B. Reviews. 2015. Vol.~22. P.~311--321.

15.	{\it Hong X., Annamalai R.~T., Kemerer T.~S., Deng C.~X., Stegemann J.~P.} Multimo\-de ultrasound viscoelastography for three-dimensional interrogation of microscale mecha\-ni\-cal properties in heterogeneous biomaterials // Biomaterials. 2018. Vol.~178. P.~11--22.

16.	{\it Argatov I.~I.} Mathematical modeling of linear viscoelastic impact: Application to drop impact testing of articular cartilage // Tribology International. 2013. Vol.~63. P.~213--225.

17. {\it	Thompson G.~T.} In vivo determination of mechnical properties of the human ulna by means of mechanical impedance tests: Experimental results and improved mathemati\-cal model  // Medical and Biological Engineering. 1976. Vol.~14. P.~253--262.

18.	{\it	Che Yu-Lin.} Alternative form of standard linear solid model for characterizing stress relaxation and creep: Including a novel parameter for quantifying the ratio of fluids to solids of a viscoelastic solid // Frontiers in Materials. 2020. P.~7--11. %\\  https://doi.org/10.3389/fmats.2020.00011

19.	{\it Трегубов В.~П., Егорова Н.~К.} Моделирование биомеханических систем с нецелым числом степеней свободы // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика.  Процессы управления. 2020. Т.~16. Вып.~3. С.~267--276.\\
https://doi.org/10.21638/11701/spbu10.2020.305

%\pagebreak
\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 18 декабря 2020~г.

Cтатья принята к~печати 5 апреля 2021~г.

\vskip5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Трегубов Владимир Петрович} --- д-р физ.-мат. наук, проф.; v.tregubov@spbu.ru

\vskip2 mm \textit{Егорова Надежда Константиновна} --- аспирант; nadezhda\_ego@mail.ru

}
