

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Hawkes~P.\:W. The correction of electron len saberrations. {\it
Ultramicroscopy}, 2015, vol.~156,\linebreak pp.~A1--A64.

2. %\bibitem{2}
 Baranova L. A., Read  F. H.,  Cubric D.
 Computational simulation of an electrostatic aberration
 corrector for a low-voltage scanning electron microscope.
{\it  Nuclear Instruments and Methods in Physics Research A},
2004, vol.~519, pp.~42--48.

%\bibitem{3}
3. Baranova L. A., Read  F. H. Minimisation of the aberrations of
electrostatic lens systems composed of quadrupole and octupole
lenses. {\it International Journal of Mass Spectro\-met\-ry},
1999, vol.~189, pp.~19--26.

%\bibitem{4}
4. Munro E., Rouse J., Liu H., Wang L. Aberration correction for
electron beam inspection, metrology and lithography. {\it Journal
of Vacuum Science and Technology B: Microelectronics and Nanometer
Structures}, 2008, vol.~26, no.~6, pp.~2331--2336.

%\bibitem{5}
5. Zach J., Haider M. Aberration correction in a low voltage SEM
by a multipole corrector. {\it  Nuclear Instruments and Methods in
Physics Research A}, 1995, vol.~363, pp.~316--325.

%\bibitem{6}
6. Vinogradova E. M., Egorov E. N., Televnyy D. S. Mathematical
modeling of field emitter array. {\it Vacuum},  2016, vol.~127,
pp.~45--50.

%\bibitem{7}
7. Vinogradova E. M., Egorov E. N., Klimakov A. A. Mathematical
simulation of a diode system with a cylindrical field-emission
tip. {\it   Technical Physics}, 2015, vol.~60, no.~2,
pp.~176--179.


%\bibitem{8}
8. Starikova A. V., Vinogradova E. M.  The electrostatic octupole
lens mathematical modeling.  {\it   2016 Young Researchers in
Vacuum Micro/Nano Electronics, VMNE-YR 2016 --- Proceedings},
16~March, 2017,  Article no.~7880416.

%\bibitem{9}
9.
%Виноградова Е. М., Старикова А. В.
%Математическое моделирование квадрупольной электростатической линзы
%{\it   Вестник СПбГУ. Серия 10. Прикладная математика. Информатика. Процессы управления. 2016, %Вып. 1, cc.~19--27.
%\\
Vinogradova E. M., Lisrtukova A. V. Matematicheskoe modelirovanie
kvadrupol'noj jelektro-\linebreak staticheskoj linzy [The
electrostatic quadrupole lens mathematical modeling]. {\it Vestnik
of Saint Petersburg\linebreak  State University. Series 10.
Applied Mathematics. Computer Science. Control Processes}, 2016,
iss.~1, pp.~19--27. (In Russian)

%\bibitem{10}
10.
 Vinogradova E. M., Egorov  N. V.,  Starikova A. V., Varayun  M. I.
Calculating a Multipole Cylindrical Electrostatic System. {\it
Technical Physics}, 2017, vol.~62, no.~5, pp.~791--794.

%\bibitem{11}
11. Vinogradova E. M., Starikova~А. В. The multipole lens
mathematical modeling. {\it  Proceedings of RuPAC 2016}. Saint
Petersburg, Russia, Saint Petersburg State University Publ., 2016,
pp.~535--537.






\vskip 2mm

{\bf For citation:}   Vinogradova E. M., Starikova A. V., Varayun'
M. I. Multipole electrostatic system mathematical modeling. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~13,
iss.~\issuenum, pp.~\pageref{p3}--\pageref{p3e}.
\doivyp/spbu10.\issueyear.\issuenum03



}
