
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Pal B., Sana Sh. S., Chaudhuri K.} A three layer
multi-item production-inventory model for multiple suppliers and
retailers~// Economic Modelling. 2012. Vol.~29. P.~2704–-2710.

2. {\it Ben-Daya M., Al-Nassar A.} An integrated inventory
production system in a three-layer supply chain~// Production
Planning and Control. 2008. Vol.~19~(2). P.~97--104.

3. {\it Bhattacharya D. K.} On multi-item inventory~// European J.
of Operational Research. 2005. Vol.~162. P.~786--791.

4. {\it Brandimarte P.} Multi-item capacitated lot-sizing with
demand uncertainty~// Intern. J. of Production Research. 2006.
Vol.~44~(15). P.~2997--3022.

5. {\it Kamali A., Fatemi Ghomia S.~M.~T., Jolai F.} A
multi-objective quantity discount and joint optimization model for
coordination of a single-buyer multi-vendor supply chain~//
Computers and Mathematics with Applications. 2011. Vol.~62.
P.~3251--3269.

6. {\it Полякова Л.\,Н., Буре В.\,М., Карелин В.\,В.} Максиминный
подход к~оценке объема заказа то-\linebreak вара в~условиях
падения спроса~// Вестн. С.-Петерб. ун-та. Прикладная математика.
Информатика. Процессы управления. 2018. T.\,14. Вып.~4.
C.~352--361. htpps://doi.org/10.21638/11702/spbu10.2018.408

7. {\it Буре В. М., Карелин В. В., Буре А. В.} Оценка объема
заказа товара при возможном падении спроса~// Вестн. С.-Петерб.
ун-та. Прикладная математика. Информатика. Процессы управления.
2018. T.~14. Вып.~3. C.~252--260.
htpps://doi.org/10.21638/11702/spbu10.2018.306

8. {\it Буре В. М., Карелин В. В., Полякова Л. Н., Ягольник И. В.}
Моделирование процесса заказа для кусочно-линейного спроса
с~насыщением~// Вестн. С.-Петерб. ун-та. Прикладная математика.
Информатика. Процессы управления. 2017. T.~13. Вып.~2.
C.~138--146.

9. {\it Bure V. M., Karelin V. V., Myshkov S. K., Polyakova L. N.}
Determination of order quantity with piecewise-linear demand
function with saturation~// Intern. J. of Applied Engineering
Research. 2017. Vol.~12. N~18. P.~7857--7862.

10. {\it Bure V. M., Karelin V. V., Polyakova L. N.} Probabilistic
model of terminal services~// Applied Mathematical Sciences. 2016.
Vol.~10. N~39.  P.~1945--1952.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 15 мая 2019 г.

Cтатья принята к~печати 6 июня 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Буре Владимир Мансурович}~---  д-p техн. наук,
проф.; vlb310154@gmail.com

\vskip2mm \textit{Карелин Владимир Витальевич}~---  канд.
физ.-мат. наук, доц.; vlkarelin@mail.ru

\vskip2mm \textit{Полякова Людмила Николаевна}~---  д-p физ.-мат.
наук, проф.; lnpol07@mail.ru

\vskip2mm \textit{Флегонтов Александр Владимирович}~---  д-p
физ.-мат. наук, проф.; flegontoff@yandex.ru

}
