
{\normalsize

\vskip 6mm

\noindent{\bf On stabilization of a class of systems with time
proportional delay}

}

\vskip 1.5mm

{\small

\noindent{\it A. P. Zhabko, O. G. Tikhomirov, O. N. Ñhizhova}

\vskip 1.5mm

{\footnotesize \noindent St.\,Petersburg State University, 7--9,
Universitetskaya nab., St.\,Petersburg, 199034, Russian Federation

}

\vskip3mm

\noindent \textbf{For citation:}  Zhabko A. P., Tikhomirov O. G.,
Ñhizhova O. N. On stabilization of a class of systems with time
proportional delay. {\it Vestnik of Saint~Petersburg University.
App-\linebreak lied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10.\issueyear.\issuenum09

\vskip3mm

{\leftskip=7mm\noindent In this paper, we investigate a
possibility of the linear difference-differential system
stabi-\linebreak lization with time proportional delay by the
linear observation. Using the sufficient conditions of asymptotic
stability for the linear systems with linearly increasing delay,
we obtain some conditions of the asymptotic evaluation system
existence for the original system. Then we use the asymptotic
evaluation system for the construction of the stabilizing control
and derive the sufficient conditions
for the existence of such control.\\[1mm]
\textit{Keywords}: system of linear differential-difference
equations, linearly increasing time delay, asymptotic stability,
stabilizing control, asymptotic evaluation system.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Bellman R., Cooke K. L. \emph{Differential-difference
equations. London, United Kingdom}, 1963, 461~p. (Russ. ed.:
Bellman R., Cooke K. L. \emph{Differencial'no-raznostnye
uravnenija}. Moscow, Mir Publ., 1967, 548~p.)

2. Zhabko A. P., Chizhova O. N. Analiz ustojchivosti odnorodnogo
differencial'no-raznostnogo uravnenija s linejnym zapazdyvaniem
[Stability analysis of homogeneous  differential-difference
equation  with linear delay]. {\it Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Sciences.
Control Processes}, 2015, iss. 3, pp. 105--115. (In Russian)

3. Zhabko A. P., Chizhova O. N. Gibridnyj metod analiza
ustojchivosti linejnyh differencial'no-raznostnyh sistem s linejno
vozrastajushhim zapazdyvaniem [Hybrid method for analyzing the
stability of linear differential-difference systems with linearly
increasing delay]. {\it Vestnik of Tambov University. Series
Natural and technical sciences}, 2015, vol. 20, no. 4, pp.
843--850. (In Russian)

4. Laktionov A. A., Zhabko A. P. Method of difference
transformations for differential systems with linear time-delay.
{\it Proceeding of the First IFAC Conference LTDS-98}. France,
1998, pp. 201--205.

5. Grebenshhikov   B. G. Metody issledovanija ustojchivosti sistem
s linejnym zapazdyvaniem [Methods for investigating the stability
of systems with linear delay]. {\it Siberian Mathematical
Journal}, 2001, vol. 42, no. 1, pp. 41--51. (In Russian)

6. Grebenshhikov B. G., Lozhnikov A. B. O stabilizacii odnoj
sistemy s posledejstviem [On stabilization of one system with
aftereffect]. {\it Automation and Remote Control}, 2011, no. 1,
pp. 13--26. (In Russian)

7. Zhabko A. P., Chizhova O. N. On stabilization of systems of
linear equations with linear increasing time delay by observation.
{\it Proceedings of RuPAC2016}. Saint Petersburg, Russia, 2016,
pp.~261--263. (Available at:
http://accelconf.web.cern.ch/AccelConf/rupac2016/papers/tupsa024.pdf
(accessed: 15.01.2018).)



\vskip5mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.5mm \textit{Zhabko Aleksei P.} --- Dr. Sci. in physics and
mathematics, professor; zhabko.apmath.spbu@mail.ru

\textit{Tikhomirov Oleg G.} --- PhD Sci. in physics and
mathematics, associate professor;\\ olegtikhomirov@mail.ru

\textit{Chizhova Ol'ga N.} --- PhD Sci. in physics and
mathematics, associate professor;\\ chizhovolg@yandex.ru


}
