

\noindent{\small UDC 519.8  \hfill {\footnotesize Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}\\
MSC 90C33

}

\vskip2mm

\noindent{\bf Spatial market equilibrium in the case of linear transportation costs$^{*}$%

 }

\vskip2.5mm

\noindent{\it  A.\,Y. Krylatov, Y.\,E. Lonyagina, R.\,I. Golubev%$\,^1$%
%, I.~О. Famylia%$\,^2$%
%, I.~О. Famylia%$\,^2$%

}

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian
Foundation for Basic Research (project N 19-31-90109).\par
%%
%%\vskip 2.0mm
%%
\indent{\copyright} Санкт-Петербургский государственный
университет, \issueyear%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum09 } }\hfill\thepage}%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum09}}}%
% для оформления нижнего колонтитула
\cfoot{} %

\vskip2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

{\small \noindent \textbf{For citation:} Krylatov A.\,Y.,
Lonyagina Y.\,E.,  Golubev R.\,I.  Spatial market equilibrium in
the case of linear transportation costs. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Pro\-ces\-ses}, \issueyear, vol.~16,
iss.~\issuenum,
pp.~\pageref{p9}--\pageref{p9e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum09

\vskip3mm

{\leftskip=7mm\noindent In this article, we study the spatial
market equilibrium in the case of fixed demands and supply values,
the requirement of equality in regard to overall supply and
overall demand, and linear transportation costs. The problem is
formulated as a nonlinear optimization program with dual variables
reflecting supply and demand prices. It is shown that the unique
equilibrium commodity assignment pattern is obtained explicitly
via equilibrium prices. Moreover, it is proved that in order to
obtain absolute values of equilibrium prices, it is necessary to
establish a certain base market price. Therefore, once the base
market price is given, then other prices are adjusted according to
spatial market equilibrium.\\[1mm]
\textit{Keywords}: spatial market equilibrium, non-linear
optimization, multipliers of Lagrange, Karush---Kuhn---Tucker
conditions.

}

}

\vskip 4mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\bf 1. Introduction.}  The modern market was formed mainly due to
the division of labor. Actually, the market already lost its
national and territorial boundaries and turned into a global
market for commodities from spatial perspectives. The sale and
purchase of commodities can occur at completely different prices,
bounded above by the price of de\-mand, and below~--- by the price
of supply. Actual prices depend primarily on the struc\-tu\-re of
market and transaction costs, which incorporate the transportation
costs. There are several structures of the market.
\begin{itemize}
    \setlength\itemsep{0.05em}
    \item Perfect competition markets: many small firms with homogeneous products.
    \item Monopoly: there is only one company on the market that pro\-duces unique products.
    \item Monopolistic competition: there are many small firms on the market whose pro\-ducts are heterogeneous.
    \item Oligopoly: there are a small number of large firms with homogeneous or he\-te\-ro\-ge\-neous products on the market.
\end{itemize}

For each of the above structures, it is possible to determine such
a situation (point) in the market, when neither the buyer nor the
seller is interested in changing the current situation. The price
at which the product offered on the market corresponds to the
demand is called the equilibrium. The market mechanism begins to
work, exerting pressure on prices from the lower and upper sides
to achieve an equilibrium price. The study of the market, as well
as the principles of its functioning and regulatory mechanisms,
today seems to be relevant and necessary for understanding the
essence of the socio-economic processes that are currently taking
place throughout the world.

The first consideration of the spatial price equilibrium problem
was made in [1]. The foundations for the study of spatial
production, consumption, and trade of commodities was given in
[2]. Up-to-date there exists a wide range of computational
techniques for co\-ping with such kind of problems [3--7].
Comprehensive mathematical models concerning spatial equilibrium
are studied in [8--10]. Spatial equilibrium models are commonly
ex\-ploi\-ted to solve the traffic assignment problem [11--14].
Moreover, its applications can be found in energy markets [15, 16]
and telecommunication markets [17].

In this paper, we study the spatial market equilibrium in the case
of linear transportation costs. The problem is formulated in a
form of nonlinear optimization program in Section 2. The supply
and demand price functions are assumed to be given as well as the
unit transaction cost functions, which are assumed to incorporate
the unit transportation costs. The unique equilibrium commodity
assignment pattern is obtained explicitly via equilibrium prices
in Section 3. Moreover, in Section 3 it is proved that in order to
obtain absolute values of equilibrium prices, the market moderator
has to establish the basic market price. Conclusions are given in
Section~4.

%%%
%%%    PROBLEM FORMULATION
%%%

%\vspace{0.3cm}

{\bf 2. Spatial market equilibrium.}  Consider the set of
suppliers $M$ and the set of consumers $N$, which are associated
with commodity production, distribution, and consumption. We
denote by $s_i$ the supply of $i \in M$, and by $\lambda_i$~---
the price of a unit of the $i$th supply, $\lambda = (\lambda_1,
\ldots, \lambda_m)^{\rm T}$. By $d_j$ we denote the demand of $j
\in N$, and by $\mu_j$~--- the price of a unit of the $j$th
demand, $\mu = (\mu_1, \ldots, \mu_n)^{\rm T}$. Finally, let
$x_{ij} \geq 0$ be the commodity volume between a pair $(i, j)$,
while $c_{ij} (x_{ij})$ is the cost of the transaction of a unit
of $x_{ij}$. Let us also introduce the indicator of market
relations:
\begin{equation*}
    \delta_{ij} = \left\{
    \begin{array}{ll}
        1 & \mbox{for } x_{ij} > 0 ,\\
        0 & \mbox{for } x_{ij} = 0 ,
    \end{array}
    \right. \quad \forall (i,j) \in M \times N .
\end{equation*}

{\bf Definition.} Commodity assignment pattern $x$ is the
\textit{spatial market equilibrium} if and only if
\begin{equation*}
    \begin{array}{ll}
        \lambda_i + c_{ij} (x_{ij}) = \mu_j & \mbox{for} \quad  x_{ij} > 0 ,
        \\
        \lambda_i + c_{ij} (x_{ij}) \geq \mu_j & \mbox{for} \quad x_{ij} = 0 ,
    \end{array}
    \quad \forall (i,j) \in M \times N .
\end{equation*}

Thus, if the sum of the $i$-th supplier's price and the
transaction costs between $i$ and $j$ exceeds the demand price of
$j$-th consumer, then the pair $(i, j)$ will not have any market
relations. The commodity assignment pattern $x^*$ such as
\begin{equation}
    \label{func1}
    x^* = \mathrm{arg} \min_x \sum\limits_{i \in M} \sum\limits_{j \in N} \int\limits_0^{x_{ij}} c_{ij}(u)du
\end{equation}
subject to
\begin{equation} \label{constr1}
    \sum \limits_{j \in N} x_{ij} = s_i \quad \forall i \in M,
\end{equation}
\begin{equation} \label{constr2}
    \sum \limits_{i \in M} x_{ij} = d_j \quad \forall j \in N,
\end{equation}
\begin{equation} \label{constr3}
    x_{ij} \ge 0 \quad  \forall i,j \in M \times N,
\end{equation}
under
\begin{equation} \label{req}
    \sum \limits_{i \in M} s_i = \sum \limits_{j \in N} d_j ,
\end{equation}
is proved to be spatial market equilibrium [10, 18].

%%%
%%%    BOUNDARY PERTURBATION
%%%


\vspace{0.3cm}

{\bf 3. Pricing mechanism in case of linear transaction costs.}
Within the present paper, we examine spatial market equilibrium in
case of linear transaction costs. In other words, we assume that
\begin{equation*}
    c_{ij} (x_{ij}) = a_{ij}+b_{ij}x_{ij} \quad : \quad a_{ij} \geq 0, b_{ij} > 0 \quad \forall (i,j) \in M \times N.
\end{equation*}

{\bf Lemma 1.} {\it Assume that demands and supplies are fixed in
the spatial market and satisfy the requirement} (\ref{req}). {\it
The spatial market equilibrium under linear transaction costs is
obtained by the following commodity assignment pattern: }
\begin{equation} \label{f4}
    x_{ij} = \left\{
    \begin{array}{ll}
        \frac{\mu_j - \lambda_i - a_{ij}}{b_{ij}}, & \mbox{ if } \mu_j - \lambda_i > a_{ij},\\
        0, &  \mbox{ if } \mu_j - \lambda_i \leq a_{ij},
    \end{array}
    \right. \quad \forall i \in M, \;  j \in N,
\end{equation}
{\it where $(\lambda,\mu)$ are such that}
\begin{equation} \label{equat2}
    \left(
    \begin{matrix}
        B_\mu & - B
        \\
        B^{\rm T} & B_\lambda

    \end{matrix}
    \right)
    \left(
    \begin{matrix}
        \mu
        \\
        \lambda
    \end{matrix}
    \right)=
    \left(
    \begin{matrix}
        d_1 + \sum\limits_{i \in M} \frac{a_{i1}\delta_{i1}}{b_{i1}}
        \\
        \vdots
        \\
        d_n + \sum\limits_{i \in M} \frac{a_{in}\delta_{in}}{b_{in}}
        \\
        s_1 + \sum\limits_{j \in N} \frac{a_{1j}\delta_{1j}}{b_{1j}}
        \\
        \vdots
        \\
        s_m + \sum\limits_{j \in N} \frac{a_{mj} \delta_{mj}}{b_{mj}}
    \end{matrix}
    \right),
\end{equation}
{\it while }
\begin{equation*}
    B_\mu = \left(
    \begin{matrix}
        \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} & \cdots & 0
        \\
        \vdots & \ddots & \vdots
        \\
        0 & \cdots & \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}}
    \end{matrix}
    \right), \quad
    B_{\lambda} = \left(
    \begin{matrix}
        -\sum\limits_{j \in N} \frac {\delta_{1j}}{b_{1j}} & \cdots & 0
        \\
        \vdots & \ddots & \vdots
        \\
        0 & \cdots & -\sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}}
    \end{matrix}
    \right)
\end{equation*}
{\it and}
\begin{equation*}
    B = \left(
    \begin{matrix}
        \frac{\delta_{11}}{b_{11}} & \cdots & \frac{\delta_{m1}}{b_{m1}}
        \\
        \vdots & \ddots & \vdots
        \\
        \frac{\delta_{1n}}{b_{1n}} & \cdots & \frac{\delta_{mn}}{b_{mn}}
    \end{matrix}
    \right).
\end{equation*}

\so{Proof}. Let us consider Lagrangian of the problem
\eqref{func1}--\eqref{constr3}:
\begin{equation*}
    L = \sum\limits_{i \in M} \sum\limits_{j \in N} \int\limits_0^{x_{ij}} c_{ij}(u) du + \sum\limits_{i \in M}\lambda_i \left( \sum\limits_{j \in N} x_{ij} - s_i \right) +
\end{equation*}
\begin{equation*}
    + \sum \limits_{j \in N} \mu_j \left( -\sum\limits_{i \in M} x_{ij} + d_j \right) + \sum\limits_{i \in M} \sum\limits_{j \in N} \xi_{ij}(-x_{ij}),
\end{equation*}
where $\lambda_i$, $\mu_j$, and $\xi_{ij} \geq 0$ for $i \in M$,
$j \in N$ are multipliers of Lagrange, according to Kuhn---Tucker
conditions
\begin{equation} \label{f1}
    \frac{\partial L}{\partial x_{ij}} = c_{ij} (x_{ij}) + \lambda_i - \mu_j - \xi_{ij} = 0 ~\quad \forall i \in M, \; j \in N,
\end{equation}
\begin{equation*}
    \frac{\partial L }{\partial \lambda_i} = -\sum\limits_{j \in N} x_{ij} + s_i = 0 \quad \forall \; i \in M,
\end{equation*}
\begin{equation*}
    \frac{\partial L }{\partial \mu_j} = -\sum\limits_{i \in M} x_{ij} + d_j = 0 \quad \forall \; j \in N,
\end{equation*}
\begin{equation*}
    \xi_{ij}(-x_{ij}) = 0 \quad \forall \; i \in M, \; j \in N.
\end{equation*}
Since $\xi_{ij}(-x_{ij}) = 0$ for all $(i,j) \in M \times N$, then
\begin{equation*}
    \begin{array}{l}
        \mbox{if } x_{ij} > 0 \Rightarrow \xi_{ij} = 0,
        \\
        \mbox{if } x_{ij} =0 \Rightarrow \xi_{ij} \ge 0,
    \end{array} \quad \forall (i,j) \in M \times N,
\end{equation*}
hence, due to (\ref{f1}):
\begin{equation} \nonumber
    c_{ij} (x_{ij})
    \begin{cases}
        = \mu_j - \lambda_i, \quad \mbox{if } x_{ij} > 0,
        \\
        \ge \mu_j - \lambda_i, \quad \mbox{if } x_{ij} = 0,
    \end{cases} \quad \forall (i,j) \in M \times N,
\end{equation}
or in case of linear transaction costs:
\begin{equation} \nonumber
    a_{ij} + b_{ij} x_{ij}
    \begin{cases}
        = \mu_j - \lambda_i, \quad \mbox{if } x_{ij} > 0,
        \\
        \ge \mu_j - \lambda_i, \quad \mbox{if } x_{ij} = 0,
    \end{cases} \quad \forall (i,j) \in M \times N,
\end{equation}
that leads to
\begin{equation} \nonumber
    \begin{array}{ll}
        x_{ij} = \frac{\mu_j - \lambda_i - a_{ij}}{b_{ij}}, & \mbox{if } x_{ij} > 0,
        \\
        a_{ij} \geq \mu_j - \lambda_i, & \mbox{if } x_{ij} = 0,
    \end{array} \quad \forall (i,j) \in M \times N,
\end{equation}
consequently, commodity volume between pair $(i, \; j)$ depends on
value of $a_{ij}$:
\begin{equation*}
    \begin{array}{l}
        \mbox{if } a_{ij} \geq \mu_j - \lambda_i \Rightarrow x_{ij} = 0,
        \\
        \mbox{if } a_{ij} < \mu_j - \lambda_i \Rightarrow x_{ij} > 0,
    \end{array} \quad \forall (i,j) \in M \times N,
\end{equation*}
so the expression \eqref{f4} holds.

Now we substitute $x_{ij}$ into the balance equations and get the
following expressions:
\begin{equation*}
    \sum \limits_{j \in N} \mu_j \frac{\delta_{ij}}{b_{ij}} - \sum\limits_{j \in N} \lambda_i \frac{\delta_{ij}}{b_{ij}} = \sum\limits_{j \in N} \frac{a_{ij} \delta_{ij}}{b_{ij}}+s_i \quad \forall i \in M,
\end{equation*}
\begin{equation*}
    \sum \limits_{i \in M} \mu_j \frac{\delta_{ij}}{b_{ij}} - \sum\limits_{i \in M} \lambda_i \frac{\delta_{ij}}{b_{ij}} = \sum\limits_{i \in M} \frac{a_{ij} \delta_{ij}}{b_{ij}}+d_j \quad \forall j \in N,
\end{equation*}
that in a matrix form is equivalent to \eqref{equat2}.

The lemma is proved.


The next lemma proves that the system of linear equations
\eqref{equat2} has infinitely many solutions.

{\bf Lemma 2.} {\it The following statements hold:
    \begin{itemize}
        \item the left-side matrix from \eqref{equat2} is singular, and its rank is $m+n-1;$
        \item the system of linear equations \eqref{equat2} is solvable.
\end{itemize}}
\so{Proof}.

I. Let us sum rows from the first one to $n$ in the left-side
matrix from \eqref{equat2}:
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}} ; -\frac{\delta_{11}}{b_{11}} - \cdots -\frac{\delta_{1n}}{b_{1n}} ; \cdots; -\frac{\delta_{m1}}{b_{m1}} - \cdots - \frac{\delta_{mn}}{b_{mn}} \right)
\end{equation*}
that is
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}} ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}} \right)
\end{equation*}
and let us sum rows from $n + 1$ to $n+m$ in the left-side matrix
from \eqref{equat2}:
\begin{equation*}
    \left( \frac{\delta_{11}}{b_{11}} + \cdots + \frac{\delta_{m1}}{b_{m1}}  ; \cdots ; \frac{\delta_{1n}}{b_{1n}}  + \cdots + \frac{\delta_{mn}}{b_{mn}}  ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots - \sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}} \right)
\end{equation*}
that is
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}} ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}} \right) .
\end{equation*}
As one can see, obtained rows are equal. Therefore, the left-side
matrix from \eqref{equat2} is singular.

Moreover, according to (\ref{constr2}), $\sum \limits_{i \in M}
x_{ij} = d_j$ for any $j \in N$, then there exists at least one
$x_{ij} > 0$ for any $j \in N$. In other words, $\sum \limits_{i
\in M} \delta_{ij} \geq 1$ for any $j \in N$ and, consequently,
$\sum\limits_{i \in M} \frac{\delta_{ij}}{b_{ij}} > 0$ for any $j
\in N$. Thus, it is clear that the first $n$ rows are mutually
linearly independent. On the other hand, according to
(\ref{constr1}), $\sum \limits_{j \in N} x_{ij} = s_i$ for any $i
\in M$, then there exists at least one $x_{ij} > 0$ for any $i \in
M$. In other words, $\sum \limits_{j \in N} \delta_{ij} \geq 1$
for any $i \in M$ and, consequently, $\sum\limits_{j \in N}
\frac{\delta_{ij}}{b_{ij}} > 0$ for any $i \in M$. Thus, it is
clear that the rows from $n+1$ to $n+m$ are mutually linear
independent. However, the sum of the first $n$ rows is equal to
the sum of rows from $n+1$ to $n+m$. Consequently, the
Gauss---Seidel method achieves a trapezoid matrix which dimension
is $m+n-1$. Therefore, the rank of the left-side matrix from
\eqref{equat2} is $m+n-1$.

II. According to the Kronecker---Capelli theorem, for a system to
be solvable, it is necessary and sufficient that the rank of the
extended matrix of this system be equal to the rank of its main
matrix. Construct an extended matrix of the system
\begin{equation*}
    \bar{A}=\left(
    \begin{matrix}
        \begin{matrix}
            \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} & \cdots & 0
            \\
            \vdots & \ddots & \vdots
            \\
            0 & \cdots & \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}}
        \end{matrix}
        & - B & &
        \begin{matrix}
            d_1 + \sum\limits_{i \in M} \frac{a_{i1} \delta_{i1}}{b_{i1}}
            \\
            \vdots
            \\
            d_n + \sum\limits_{i \in M} \frac{a_{in} \delta_{in}}{b_{in}}
        \end{matrix}
        \\
        B^{\rm T} &
        \begin{matrix}
            -\sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} & \cdots & 0
            \\
            \vdots & \ddots & \vdots
            \\
            0 & \cdots & -\sum\limits_{j \in N} \frac {\delta_{mj}}{b_{mj}}
        \end{matrix} & &
        \begin{matrix}
            s_1 + \sum\limits_{j \in N} \frac{a_{1j} \delta_{1j}}{b_{1j}}
            \\
            \vdots
            \\
            s_m + \sum\limits_{j \in N} \frac{a_{mj} \delta_{mj}}{b_{mj}}
        \end{matrix}
    \end{matrix}
    \right) .
\end{equation*}
It is clear that $\mathrm{rank} \bar{A} \leq m+n$ since
$\mathrm{dim} \bar{A} = (m+n) \times (m+n+1).$ On the other hand,
according to the first part of the proof, $\mathrm{rank} \bar{A}
\geq m+n-1.$ Hence, $ m+n-1 \leq \mathrm{rank} \bar{A} \leq m+n.$
Let us sum rows from the first one to $n$ in the matrix $\bar{A}$:
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; d_1 +\sum\limits_{i \in M} \frac{a_{i1} \delta_{i1}}{b_{i1}}+ \cdots + d_n + \sum\limits_{i \in M} \frac{a_{in} \delta_{in}}{b_{in}} \right)
\end{equation*}
that is
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}} ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}} ; \sum\limits_{j \in N} d_j +\sum\limits_{j \in N} \sum\limits_{i \in M} \frac{a_{ij} \delta_{ij}}{b_{ij}} \right)
\end{equation*}
and let us sum rows from $n + 1$ to $n+m$ in the matrix $\bar{A}$:
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; s_1 + \sum\limits_{j \in N} \frac{a_{1j} \delta_{1j}}{b_{1j}} + \cdots + s_m + \sum\limits_{j \in N} \frac{a_{mj} \delta_{mj}}{b_{mj}} \right)
\end{equation*}
that is
\begin{equation*}
    \left( \sum\limits_{i \in M} \frac{\delta_{i1}}{b_{i1}} ; \cdots ; \sum\limits_{i \in M} \frac{\delta_{in}}{b_{in}} ; - \sum\limits_{j \in N} \frac{\delta_{1j}}{b_{1j}} ; \cdots ; - \sum\limits_{j \in N} \frac{\delta_{mj}}{b_{mj}} ; \sum\limits_{i \in M} s_i + \sum\limits_{i \in M} \sum\limits_{j \in N} \frac{a_{ij} \delta_{ij}}{b_{ij}} \right) .
\end{equation*}
Since $\sum\limits_{i \in M} s_i = \sum\limits_{j \in N} d_j$,
then the sum of the first $n$ rows is equal to the sum of rows
from $n+1$ to $n+m$. Thus, $\mathrm{rank} \bar{A} < m+n$ and,
hence, $\mathrm{rank} \bar{A} = m+n-1.$ Therefore, the rank of the
extended matrix of the system \eqref{equat2} is equal to the rank
of its main matrix.

The lemma is proved.

Proved lemmas lead that the following theorem holds.

{\bf Theorem.} {\it In the case of fixed demands and supplies,
requirement} (\ref{req}){\it, and linear transaction costs, there
is only one independent spatial market price for the equilibrium
commodity assignment pattern.}

\so{Proof}. According to Lemma 1, spatial market equilibrium in
case of linear trans\-ac\-tion costs is obtained by the unique
commodity assignment pattern \eqref{f4} with demand and supply
prices that satisfy the system of linear equations \eqref{equat2}.
According to Lemma~2, the system of linear equations
\eqref{equat2} is solvable with respect to $m+n$ variables
(prices), while the rank of the main matrix is $m+n-1$. Therefore,
there is only one independent variable, while all others depend on
it.

The theorem is proved.

The conducted study revealed an important conclusion: only one
price value is independent value. In other words, once the basic
market price is given, then other prices are adjusted according to
spatial market equilibrium.

{\bf 4. Conclusion.} In this paper, we study the spatial market
equilibrium and examine the case of linear transaction costs.
Obtained results show that the dual variables, which are the
Lagrange multipliers, reflect supply and demand prices. Thus, when
this problem is solved, the equilibrium commodity assignment
pattern is obtained as well as the equilibrium prices. Moreover,
we find out that to obtain absolute value of equilibrium prices
someone (actually the market moderator) has to give the basic
market price. Once the basic market price is given, then other
prices are adjusted according to spatial market
equilibrium.\pagebreak


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
\input{09/ref-s-eng}% для английской статьи

%\newpage
\input{09/lit-ra-eng}% для английской статьи

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\thispagestyle{empty}

\vskip 3mm

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}}%
% для оформления нижнего колонтитула
\cfoot{} %

}
