

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. {Samuelson P.} Spatial price equilibrium and linear
programming. {\it American Economic Review}, 1952, vol.~42,
pp.~283--303.

2. {Takayama T., Judge G.} \textit{Spatial and temporal price and
allocation models.} Amsterdam, North-Holland Publ. Co., 1971,
528~p.

3. {Allevi E., Gnudi A., Konnov I.} Combined methods for dynamic
spatial auction market models. {\it Optimization and Engineering},
2012, vol.~13, pp.~401--416.

4. {Guder F., Morris J., Yoon S.} Parallel and serial successive
overrelaxation for multicommodity spatial price equilibrium
problem. {\it Transportation Science}, 1992, vol.~26, pp.~48--58.

5. {Migdalas A., Pardalos P., Storoy S.} \textit{Parallel
computing in optimization.} Amsterdam, Kluwer Academic Publ.,
1997, 608~p.

6. {Nagurney A., Nicholson C., Bishop P.} Massively parallel
computation of large-scale spatial price equilibrium models with
discriminatory ad valorem tariffs. {\it Annals of Operations
Research}, 1996, vol.~68, pp.~281--300.

7. {Sharpe W.} Capital asset prices: A theory of market
equilibrium under conditions of risk. {\it Journal of Finance},
1964, vol.~19, pp.~425--442.

8. {Konnov I.} \textit{Equilibrium models and variational
inequalities.} Amsterdam, Elsevier Press, 2007, 250~p.

9. {Krylatov A., Zakharov V., Tuovinen T.} \textit{Optimization
models and methods for equilibrium traffic assignment.} Cham,
Switzerland, Springer International Publ., 2020, 239~p.

10. {Patriksson M.} \textit{The traffic assignment problem: models
and methods.} New York, Dover Publ., 1994, 222~p.

11. {Dafermos S.} Traffic equilibrium and variational
inequalities. {\it Transportation Science}, 1980, vol.~14,
pp.~42--54.

12. {Krylatov A., Zakharov V.} Competitive traffic assignment in a
green transit network. {\it Inter-national Game Theory Review},
2016, vol.~18(2), pp.~1640003.

13. {Krylatov A., Zakharov V., Malygin I.} Competitive traffic
assignment in road networks. {\it Transport and
Telecommunication}, 2016, vol.~17(3), pp.~212--221.

14. {Zakharov V., Krylatov A.} Transit Network Design for Green
Vehicles Routing. {\it Advances in Intelligent Systems and
Computing}, 2015, vol.~360, pp.~449--458.

15. {Anderson E., Philpott A.} Optimal offer construction in
electricity markets. {\it Mathematics of Operations Research},
2002, vol.~27, pp.~82--100.

16. {Popov I., Krylatov A., Zakharov V., Ivanov D.} Competitive
energy consumption under transmission constraints in a
multi-supplier power grid system. {\it International Journal of
Systems Science}, 2017, vol.~48(5), pp.~994--1001.

17. {Courcoubetis C., Weber R.} \textit{Pricing communications
networks: Economics, technology and modelling.} New York, Wiley
Publ., 2003, 380~p.

18. {Nagurney A.} \textit{Network economics: a variational
inequality approach.} Amsterdam, Kluwer Academic Publ., 1993,
347~p.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 18, 2020.

Accepted: October 23, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Alexander Y. Krylatov} ---  Dr. Sci. in Physics
and Mathematics, Professor; %\\
a.krylatov@spbu.ru

\vskip 2mm \textit{Yulia E. Lonyagina} --- Research Engineer;
st010070@student.spbu.ru

\vskip 2mm \textit{Ruslan I. Golubev} ---  Postgraduate Student;
st012690@student.spbu.ru


}
