
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

{1}. {\it James R. W.} Application of wave forecast to marine
navigation~//     Comparative Biochemistry \& Physiology a
comparative physiology. 1957. Vol.~43,  N~1. P.~195--205.

{2}. {\it Hagiwara Hideki, Spaans J. A.} Practical weather routing
of sail-assisted motor vessels~// Journal of Navigation. 1987.
Vol.~40, N 1.  P.~96--119.

{3}. {\it Hagiwara H.} Weather routing of (sail-assisted) motor
vessels. PhD thesis. Delft: Delft University of Technology, 1989.
336~p.

{4}. {\it Faulkner F. D.}  Numerical methods for determining
optimum ship routes~// Journal of the Institute of navigation.
Winter 1963. Vol.~10, N~4.  P.~351--367.

{5}. {\it Bleick W. E., Faulkner F. D.} Minimal-time ship
routing~// Journal of Applied Meteorology. 1965. Vol.~4, N~2.
P.~217--221.

{6}. {\it Bijlsma S. J.} A computational method for the solution
of optimal control problems in ship routing~// Journal of the
Institute of navigation. 2001. Vol.~48, N~3.  P.~145--154.

{7}. {\it Petrie G. L., Bongert K. J., Maclean W. M.}  A new
approach to vessel weather routing and performance analysis~//
Marine Technology. 1984. Vol.~21.  P.~19--41.

{8}.    {\it Motte R. H., Calvert S.} On the selection of discrete
grid systems for on-board micro-based weather routing~// The
Journal of Navigation. 1990. Vol.~43.  P.~104--117.

{9}. {\it Maki A., Akimoto Y., Nagata Y.} et al.  A new
weather-routing system that accounts for ship stability based on a
real-coded genetic algorithm~// Journal of Marine Science and
Technology. 2011. Vol.~16, N~3.  P.~311--322.

{10}. {\it Kang M. H., Choi H. R., Kim H. S.} et al. Development
of a maritime transportation planning support system for car
carriers based on genetic algorithm~// Applied Intelligence. 2012.
Vol.~36, N~3.  P.~585--604.

{11}. {\it Tsou M. C., Cheng H. C. }  An Ant Colony Algorithm for
efficient ship routing~// Polish Maritime Research. 2013. Vol.~20,
N~3.  P.~28--38.

{12}. {\it Veremei E. I., Sotnikova M. V.} Optimal routing based
on weather forecast~// Intern. Journal of Open Information
Technologies. 2016. Vol.~4, N~3.  P.~55--61.

{13}. {\it Eskild Hege. }Development of a method for weather
routing of ships: master thesis. Norwegian: Norwegian University
of science and technology, 2014. 143~p.

{14}. {\it Liu Feng, Pang Fuwen.}  Calculation of minimum-time
ship route using rhumb algorithm~// Journal of Dalian marine
college. February 1994. Vol.~20, N~1.  P.~14--18.

{15}. {\it Yang Zhenzhong, Liu Shiqi.}  Calculation of speed loss
for ships operating at heavy sea~// Navigation of China. 1990.
Vol.~27, N~2.  P.~35--40.

{16}. {\it Kltazawa Takamune, Kuroi Masaaki.}  Critical speed of
container ship in rough sea //Journal of the Society of naval
architects of Japan. December 1975. N~138.  P.~269--276.





\vskip 2mm

{\bf Для цитирования:} {\it Ван~Х., Ли~П., Сюэ~Ю., Коровкин~М.~В.}
Построение маршрута с~помощью улучшенного метода изохрон при
минимизации времени плавания и~с~учетом прогноза погоды~// Вестник
Санкт-Петербургского университета. Прикладная математика.
Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06



}
