

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

{1}. James R.W. ~Application of wave forecast to marine
navigation.     \textit{ Comparative Biochemistry $\&$  Physiology
a comparative physiology}, 1957, vol.~43, no.~1, pp.~195--205.

{2}. Hagiwara Hideki, Spaans J. A. ~Practical weather routing of
sail-assisted motor vessels. \textit{Journal of Navigation}, 1987,
vol.~40, no.~1, pp.~96--119.

{3}. Hagiwara H. \textit{Weather routing of (sail-assisted) motor
vessels.} PhD thesis. Delft, Delft University of Technology, 1989,
336~p.

{4}. Faulkner F. D. ~Numerical methods for determining optimum
ship routes. \textit{ Journal of the Institute of navigation},
Winter 1963, vol.~10, no.~4, pp.~351--367.

{5}. Bleick W. E., Faulkner F. D. ~Minimal-time ship routing.
\textit{Journal of Applied Meteorology}, 1965, vol.~4, no.~2,
pp.~217--221.

{6}. Bijlsma S. J. ~A computational method for the solution of
optimal control problems in ship routing. \textit{Journal of the
Institute of navigation}, 2001, vol.~48, no.~3, pp.~145--154.

{7}. Petrie G. L., Bongert K. J., Maclean W. M. ~A new approach to
vessel weather routing and performance analysis. \textit{Marine
Technology}, 1984, vol.~21, pp.~19--41.

{8}. Motte R. H.,  Calvert S. ~On the selection of discrete grid
systems for on-board micro-based weather routing. \textit{The
Journal of Navigation}, 1990, vol.~43, pp.~104--117.

{9}. Maki A., Akimoto Y., Nagata Y. et al. ~A new weather-routing
system that accounts for ship stability based on a real-coded
genetic algorithm. \textit{Journal of Marine Science and
Technology}, 2011, vol.~16, no.~3, pp.~311--322.

{10}. Kang M.~H., Choi H.~R., Kim H.~S. et al. Development of a
maritime transportation planning support system for car carriers
based on genetic algorithm. \textit{ Applied Intelligence}, 2012,
vol.~36, no.~3, pp.~585--604.

{11}. Tsou M. C., Cheng H. C. ~An Ant Colony Algorithm for
efficient ship routing. \textit{ Polish Maritime Research}, 2013,
vol.~20, no.~3, pp.~28--38.

{12}. Veremei E. I., Sotnikova M. V. ~Optimal routing based on
weather forecast. \textit{ Intern. Journal of Open Information
Technologies}, 2016, vol.~4, no.~3, pp.~55--61.

{13}. Eskild Hege. \textit{Development of a method for weather
routing of ships.} Master thesis. Norwegian, Norwegian University
of science and technology, 2014, 143~p.

{14}. Liu Feng, Pang Fuwen. ~Calculation of minimum-time ship
route using rhumb algorithm. \textit{Journal of Dalian marine
college}. February 1994, vol.~20, no.~1, pp.~14--18.

{15}. Yang Zhenzhong, Liu Shiqi. ~Calculation of speed loss for
ships operating at heavy sea. \textit{Navigation of China},  1990,
vol.~27, no.~2, pp.~35--40.

{16}. Kltazawa Takamune, Kuroi Masaaki. ~Critical speed of
container ship in rough sea. \textit{ Journal of the$ $ Society of
naval architects of Japan}. December 1975, no.~138, pp.~269--276.






\vskip 2mm

{\bf For citation:}  Wang H., Li P., Xue Yu.,~Korovkin M.~V.
Application of improved isochron method  in ship's minimum voyage
time weather routing. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
\issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06


}
