


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm

1. Bychkov U.~A., Zolotnickii V.~M., Chernishov E.~P.
\textit{Osnovi teorii elektricheskih cepei} [\textit{Theory basics
of electrical circuits$:$ a book for high schools}]. Saint
Petersburg, Lan Publ., 2002, 464~p. (In Russian)

2. Mathanov P.~N. \textit{Osnovi analiza electricheskih cepei.
Lineinie cepi} [\textit{Electrical circuits basics. Linear
circuit}]. Moscow, Visshaya shkola Publ., 1990, 400~p. (In
Russian)

3. Kazunin D.~V. \textit{Chislennoe modelirovanie tehnologicheskih
processov tankerov i terminalov} [\textit{Numerical modeling of
tankers and terminals technological processes}]. Novorossisk,
Admiral Ushakov MGA Publ., 2009, 267~p. (In Russian)

4.  Tarjan R.~E. Depth first search and linear graph algorithm.
\textit{SIAM Journal on Computing}, 1972, vol.~1, no.~2, pp.~146--160.

5. Pissanetsky S. \textit{Sparse matrix technology}. New York,
Academic Press, 1984, 428 p. (Russ. ed.: Pissanecki~S.
\textit{Tehnologiia razrågennih matric}. Moscow, Mir Publ., 1988,
411~p.)

6. Osterby O., Zlatev Z. Direct methods for sparse matrices.
\textit{Lecture Notes in Computer Science}. Berlin, Heidelberg,
Springer-Verlag, 1983, vol.~157, 130~p. (Russ. ed.: Osterby~O.,
Zlatev~Z. \textit{Priamie metody dlia razregennih matric}. Moscow,
Mir Publ., 1987, 120~p.)

7. Duff I.~S., Reid J.~K. An implementation of Tarjan’s algorithm
for the block triangularization of a matrix. \textit{ACM
Transactions on Mathematical Software}, 1978, vol.~4,
pp.~137--147.

8. Besekerskii V.~A., Popov E.~P. \textit{Teoriya sistem
avtomaticheskogo upravleniya$:$ lineinie sistemi. Nelineinie
sistemi. Impuls sistemi. Cifrovie i adaptivnie sistemi. Kriterii
ustoichivosti. Sluchainie processi} [\textit{Theory of system's
automatic control$:$ linear systems. Non-linear systems. Impulse
of system. Digital and adaptives of systems. Stability criterions.
Random processes}]. Saint Petersburg, Professia Publ., 2004,
747~p. (In Russian)



\vskip 1mm

{\bf For citation:} Kostygova D.~M., Kazunin D.~V. Mathematical
real time model of mining excavator electrical systems. {\it
Vestnik of Saint Petersburg University. Applied mathematics.
Computer science. Control processes}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
