{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Bobadilla~J., Ortega~F., Hernando~A., Guti\'{e}rrez~A.
Recommender systems survey. {\it  Knowledge Based Systems}, 2013,
vol.~46, pp.~109--132.

2. Herlocker~J.~L., Konstan~J.~A., Terveen~L.~G., Riedl~J.~T.
Evaluating Collaborative Filtering Re\-com\-men\-der Systems. {\it
ACM Transactions on Information Systems}, 2004, vol.~22, no.~1,
pp.~5--53.

3. Xiaoyuan~Su, Khoshgoftaar~T.~M. A Survey of Collaborative
Filtering Techniques. {\it Advances in Artificial Intelligence},
2009, vol.~2009, 19~p.

4. Melville~P., Mooney~R., Nagarajan~R. Content-Boosted
Collaborative Filtering for Improved Re\-com\-men\-da\-ti\-ons.
{\it  Mater. of the conference}, University of Texas, AAAI-02,
Austin, TX, USA, 2002, pp.~187--192.

5. Nogin~V.~D. {\it  Prinjatie reshenij v mnogokriterial'noj
srede: kolichestvennyj podhod} [{\it  Decision making in
multicriteria environment: a quantitative approach}]. Moscow,
Fizmatlit Publ., 2005, 176~p. (In Russian)

6. Saaty~T.~L.  {\it The Analytic Hierarchy Process}. New York,
Mc\,Graw-Hill Press, 1980, 273~p. (Russ. ed.: Saaty~T.~L. {\it
Metod analiza ierarhii}. Moscow, Radio i Svyaz Publ., 1993,
278~p.)

7. D'jakonov~A.~G. Algoritmy dlja rekomendatel'noj sistemy:
tehnologija lenkor [Algorithms for a recommender system: lenkor
technology]. {\it Biznes-informatika} [{\it  Business and computer
science}], 2012, no.~1~(19), pp.~32--39. (In Russian)

8. Nogin~V.~D. Aksiomaticheskij podhod k suzheniju mnozhestva
Pareto: vychislitel'nye aspekty [Axioma\-tic approach to reduce
the Pareto set: computational aspects]. {\it Intern. Journal
``Information Theories and Applications''}, 2013, vol.~20, no.~4,
pp.~352--359. (In Russian)

9. Bogdanova~A.~V., Nogin~V.~D. Suzhenie mnozhestva Pareto na
osnove prostejshih naborov nechjotkoj informacii ob otnositel'noj
vazhnosti kriteriev [Reduction îf the Pareto set based on simple
sets of information about the relative importance of criteria].
{\it Vestnik of Saint Petersburg State University. Series 10.
Applied mathematics. Computer science. Control processes}, 2007,
issue~2, pp.~3--17. (In Russian)

10. Nogin~V.~D. Algoritm suzhenija mnozhestva Pareto na osnove
proizvol'nogo konechnogo nabora ``kvantov'' informacii [Reducing
of the Pareto Set Algorithm Based on an Arbitrary Finite Set of
Information ``Quanta'']. {\it Iskusstvennyi intellekt i~priniatie
reshenii} [{\it Artificial Intellect and Decision Making}], 2013,
no.~1, pp.~63--69. (In Russian)

11. Saaty~T.~L. Decision making with the analytic hierarchy
process. {\it Intern. J. Services Sciences}, 2008, vol.~1, no.~1,
pp.~83--98.

12. Tereljanskij~P.~V. Interpoljacionnyj raschet pravogo
sobstvennogo vektora polozhitel'noj obratno\-sim\-met\-rich\-noj
dinamicheskoj matricy [Interpolation of the right eigenvector of
positive antisymmetric dynamic matrix]. {\it Prilozhenie k~zhurn.
``Sovremennye problemy nauki i~obrazovaniia''} [{\it Supplement to
the journal ``Modern problems of science and education''}].
Available at: http://online.rae.ru/278 [accessed: 13.04.2015]. (In
Russian)

13. Nogin~V.~D. Uproshhennyj variant metoda analiza ierarhij na
osnove nelinejnoj svertki kriteriev [A Simplified Variant of the
Analytic Hierarchy Processes Based on a Nonlinear Scalarizing
Function]. {\it Z. vychisl. matematiki i matem. fiziki} [{\it
Computational Mathematics and Mathematical Physics}], 2004,
vol.~44, no.~7, pp.~1259--1268. (In Russian)


}
