

{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm


1. Ranking Web of Universities (Main page). Date Views November~2,
2014. URL: www.webometrics. info (дата обращения: 15.06.2015).

2. {\it Thelwall M., Zuccala A.} A university-centred European
Union link analysis // Scientometrics. 2008. Vol.~75, N~3.
P.~407--420.

3. {\it Smith A. G.} A tale of two web spaces; comparing sites
using Web Impact Factors // Journal of Documentation. 1999.
Vol.~55, N~5. P.~577--592.

4. {\it Nicolaisen J.} Citation analysis // Annual Review of
Information Science and Technology. 2007. Vol.~41. P.~609--641.


5. {\it Ortega J. L., Aguillo I., Cothey V., Scharnhorst A.} Maps
of the academic web in the European Higher Education Area: an
exploration of visual web indicators // Scientometrics. 2008.
Vol.~74, N~2. P.~295--308.

6. {\it Chevalier A., Dommes A., Martins D., Valerian C.}
Searching for information on the web: role of aging and ergonomic
quality of website // HCI'07 Proc. of the 12th Intern. conference
on Human-Computer Interaction: interaction design and usability.
Berlin: Springer-Verlag, 2007. P.~691--700.

7. {\it Harper S., Chen A. Q.} Web accessibility guidelines
// Journal World Wide Web. 2012. Vol.~15, issue~1. P.~61--88.

8. {\it Zeng L., Proctor R. W., Salvendy G.} Integration of
Creativity into Website Design // Proc. of the 13th Intern.
Conference on Human-Computer Interaction. Pt~I. New Trends.
Berlin: Springer-Verlag, 2009. P.~769--776.

9. {\it Huntington P., Nicholas D., Jamali H. R.} Site navigation
and its impact on content viewed by the virtual scholar: a deep
log analysis // Journal of Information Science. 2007. Vol.~33,
N~5. P.~598--610.

10. {\it Broder A., Kumar R., Maghoul F., Raghavan P., Rajagopalan
S., Stata~R., Tomkins~A., Wiener~J.} Graph structure in the Web:
Experiments and models //  WWW9. 2000. Vol.~33, N~1--6.
P.~309--320.


11. {\it Thelwall M.} Webometrics and Social Web Research Methods.
Wolverhampton: University of Wolverhampton, 2013. URL:
http://www.scit.wlv.ac.uk/\~cm1993/papers/IntroductionToWebometrics
AndSocialWebAnalysis.pdf (дата обращения:  07.08.2015).

12. {\it Thelwall M., Wilkinson D., Musgrove P.~B.} National and
International University departmental web site interlinking. Pt~2.
Link patterns // Scientometrics. 2005. Vol.~64, N~2. P.~187--208.

13. {\it Heaps H. S.} Information retrieval: computational and
theoretical aspects (Library and information science series).
London: Academic Press, 1978. 344~p.

14. {\it Gelbukh A. F., Sidorov G.} Zipf and Heaps Laws'
Coefficients Depend on Language // CIC Ling~'01. Proc. of the
Second Intern. Conference on Computational Linguistics and
Intelligent Text Proces-\linebreak sing. UK, London:
Springer-Verlag, 2001. P.~332--335.

15. {\it Zhang H.} Discovering power laws in computer programs //
Information Processing and Management. Intern. Journal. 2009.
Vol.~45, issue~4. P.~477--483.

16. {\it Kubo M., Sato H., Matsubara T.} Word familiarity
distributions to understand Heaps' law of vocabulary growth of the
internet forums // KES'11. Proc. of the 15th Intern. Conference on
Knowledge-based and intelligent information and engineering
systems. Berlin; Heidelberg: Springer-Verlag, 2011. Pt~III.
P.~627--636.

17. {\it Блеканов И. С., Сергеев С. Л., Мартыненко И. А.}
Построение тематико-ориентированных веб-краулеров с~использованием
обобщенного ядра // Науч.-техн. ведомости С.-Петерб. гос.
политехн. ун-та, 2012. T.~5, №~157. С.~9--15.

18. {\it Блеканов И. С., Максимов А. Ю.} Вебометрические
исследования сегмента университетского Веба с~помощью поискового
робота // Процессы управления и~устойчивость: Труды 44-й междунар.
науч. конференции аспирантов и~студентов / под ред.
Н.~В.~Смирнова, Т.~Е.~Смирновой. СПб.: Издат. дом С.-Петерб.
ун-та, 2013. С.~403--408.

19. {\it Blekanov I. S., Sergeev S. L., Maksimov A. I.} Analysis
of the topology of large Web segments using Broder’s bow-tie model
//  Life Science Journal. 2014. Vol.~11. P.~258–261.






}
