


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1. Ranking Web of Universities (Main page). Date Views November 2,
2014. Available at: www.webometrics.info (accessed: 15.06.2015).


2. Thelwall M., Zuccala A. A university-centred European Union
link analysis. \emph{Scientometrics}, 2008, vol.~75, no.~3,
pp.~407–420.

3. Smith A. G. A tale of two web spaces; comparing sites using Web
Impact Factors. \emph{Journal of Documentation}, 1999, vol.~55,
no.~5, pp.~577--592.

4. Nicolaisen J. Citation analysis. \emph{Annual Review of
Information Science and Technology}, 2007, vol.~41, pp.~609--641.

5. Ortega J. L., Aguillo I., Cothey V., Scharnhorst A. Maps of the
academic web in the European Higher Education Area: an exploration
of visual web indicators. \emph{Scientometrics}, 2008, vol.~74,
no.~2, pp.~295--308.

6. Chevalier A., Dommes A., Martins D., Valerian C. Searching for
information on the web: role of aging and ergonomic quality of
website. \emph{HCI'07 Proc. of the 12th Intern. conference on
Human-Computer Interaction: interaction design and usability}.
Berlin, Springer-Verlag, 2007, pp.~691–700.

7. Harper S., Chen A. Q. Web accessibility guidelines.
\emph{Journal World Wide Web}, 2012, vol.~15, issue~1, pp.~61--88.

8. Zeng L., Proctor R. W., Salvendy G. Integration of Creativity
into Website Design. \emph{Proc. of the 13th Intern. Conference on
Human-Computer Interaction. Pt I. New Trends}. Berlin,
Springer-Verlag, 2009, pp.~769--776.

9. Huntington P., Nicholas D., Jamali H. R. Site navigation and
its impact on content viewed by the virtual scholar: a deep log
analysis. \emph{Journal of Information Science}, 2007, vol.~33,
no.~5, pp.~598--610.

10. Broder A., Kumar R., Maghoul F., Raghavan P., Rajagopalan S.,
Stata R., Tomkins~A., Wiener~J. Graph structure in the Web:
Experiments and models. {\it WWW9}, 2000, vol.~33, no.~1--6,
pp.~309--320.

11. Thelwall M. \emph{Webometrics and Social Web Research
Methods}. Wolverhampton, Universi-\linebreak ty of Wolverhampton,
2013. Available at:
http://www.scit.wlv.ac.uk/\~cm1993/papers/IntroductionTo
WebometricsAndSocialWebAnalysis.pdf (accessed: 07.08.2015).

12. Thelwall M., Wilkinson D., Musgrove P. B. National and
International University departmental web site interlinking. Pt 2.
Link patterns. \emph{Scientometrics}, 2005, vol.~64, no.~2,
pp.~187--208.

13. Heaps H. S. \emph{Information retrieval: computational and
theoretical aspects} (\emph{Library and informa-\linebreak tion
science series}). London, Academic Press, 1978, 344~p.

14. Gelbukh A. F., Sidorov G. Zipf and Heaps Laws' Coefficients
Depend on Language. \emph{CICLing~'01. Proc. of the Second Intern.
Conference on Computational Linguistics and Intelligent Text
Processing}. UK. London, Springer-Verlag, 2001, pp.~332--335.

15. Zhang H. Discovering power laws in computer programs.
\emph{Information Processing and Management. Intern. Journal},
2009, vol.~45, issue~4, pp.~477--483.

16. Kubo M., Sato H., Matsubara T. Word familiarity distributions
to understand heaps' law of vocabulary growth of the internet
forums. \emph{KES'11. Proc. of the 15th Intern. Conference on
Knowledge-based and intelligent information and engineering
systems}. Berlin, Heidelberg, Springer-Verlag, 2011, pt~III,
pp.~627--636.

17. Blekanov I., Sergeev S., Martynenko I. Postroenie
tematiko-orientirovannykh veb-kraulerov s~ispol'zovaniem
obobshchennogo iadra [Construction of subject-oriented
Web-crawlers using a generalized kernel]. \emph{Nauch.-tekhn.
vedomosti S.-Peterb. gos. politekhn. un-ta} [\emph{Scientific and
technical bulletins of Saint Petersburg State Polytechnic
University}], 2012, vol.~5, no.~157, pp.~9--15. (In Russian)

18. Maksimov A., Blekanov I. Vebometricheskie issledovaniia
segmenta universitetskogo Veba s~pomoshch'iu poiskovogo robota
[The webometric research of the university Web segment using the
Web-crawler]. \emph{Protsessy upravleniia i~ustoichivost'. Trudy
44-i mezhdunar. nauch. konferentsii aspirantov i~studentov}
[\emph{Control Processes and Stability. Proc. of the 44th Intern.
Scientific Conference for post-graduates and undergraduate
students}]. Saint Petersburg, Saint Petersburg State University
Press, 2013, pp.~403--408.


19. Blekanov I. S., Sergeev S. L., Maksimov A. I. Analysis of the
topology of large Web segments using Broder’s bow-tie model.
\emph{Life Science Journal}, 2014, vol.~11, pp.~258--261.




}
