


{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm

1. {\it Pravila optovogo rynka elektricheskoi energii
i~moshchnosti} [{\it The Wholesale Electricity
and\linebreak\newpage\noindent Capacity Market Rules.}]. Appr. by
the Russian Federation Government Resolution no.~1172 of December
27, 2010.  (In Russian)

2. {\it Federal'nyi zakon ot~26 marta 2003 g. no.~35-FZ ``Ob
elektroenergetike''} (s izmeneniiami i~dopolneniiami) [{\it
Federal Law no.~35-FZ of March 26, 2003 ``On the Electric Power
Industry''}] (with amendments). (In Russian)

3. {\it Prilozhenie no.~13 k~Dogovoru  o~prisoedinenii k~torgovoi
sisteme  optovogo  rynka.  Reglament  opredeleniia ob'emov
fakticheski  postavlennoi  na~optovyi  rynok moshchnosti} [{\it
Appendix no.~13 to Wholesale Market Trading System Accession
Contract. Regulation for Determination of the Capacity Delivery to
the Wholesale Market}].  Available at:
http://www.np-sr.ru/regulation/joining/reglaments/ index.htm
(accessed: 21.02.2016). (In Russian)

4.  Asarin A. E., Bestuzheva K. N. {\it Vodno-energeticheskie
raschety} [{\it Water and energy calculations}]. Moscow,
Energoatomizdat Publ., 1986, 224~p. (In Russian)

5. Protasov I. D. {\it Teorija igr i issledovanie operacij} [{\it
Game theory and operations research}]. Moscow, Helios ARV Publ.,
2006, 368~p. (In Russian)


6.  Clemen R., Reilly T. {\it Making Hard Decisions with
DecisionTools: An Introduction to Decision Analysis.} 3rd ed.
Stamford, CT, Cengage, 2014, 844~p.


7.  Budylin M. A., Sokolov S. V. Model' opredelenija optimal'nogo
plana raspolagaemoj moshhnosti GES s uchetom ee ravnomernogo
raspredelenija [Model for determination the optimal plan of the
available capacity of the HPPs with uniform distribution]. {\it
Sovremennye problemy nauki i obrazovanija} [{\it Modern problems
of science and education}], 2014, no.~06. Available at:
http://www.science-education.ru/ru/article/view?id=16520.
(accessed: 21.02.2016). (In Russian)


8.   De Groot Morris. {\it Optimal Statistical Decisions.} Wiley,
Wiley Classics Library Publ., 2004. 512~p. (Originally publ.
1970).





}
