

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Martinez S.,  Bullo F.
  Optimal sensor placement and motion coordinationfor target tracking.
  {\it Automatica}, 2006, vol.~42, pp.~661--668.

2. Olfati-Saber R.,  Murray R. M.
  Consensus problems in networks ofagents with switching topology
and time-delays.
  {\it IEEE Trans. Automat. Control},  2004,
vol.~49, no.~9,  pp.~1520--1533.


3. Garcia-Planas M. I.
  Analyzing control properties of multiagent linear systems.
   {\it  Cybernetics and Physics}, 2020, vol.~9, no.~2, pp.~81--85.



4. {Provotorov V. V., Sergeev S. M., Hoang V. N.}
Point control of a differential-difference system with distributed parameters on the graph.
{\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
 2021, vol.~17, iss.~3, pp.~277--286. \\
https://doi.org/10.21638/11701/spbu10.2021.305




5. {Zhabko A. P., Provotorov V. V.,  Ryazhskikh V. I.,  Shindyapin A. I.}
Optimal control of a differential-difference parabolic systems with distributed parameters
on the graph.
{\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
 2021, vol.~17, iss.~4, pp.~433--448. 
https://doi.org/10.21638/11701/spbu10.2021.411






6. Wagner I.,    Bruckstein A. M.
   Row straightening by local interactions.
  {\it Circuits, Systems and Signal Processing}, 1997, vol.~16, no.~3,
pp.~287--305.



7. Shcherbakov  P. S.
   Formation control. The Van Loan scheme and other algorithms.
  {\it Automation and Remote Control}, 2011, vol.~72, no.~10, pp.~681--696.


8. Kvinto Ya. I.,   Parsegov S. E.
    Equidistant arrangement of agents on line:
Analysis of the algorithm and its generalization.
   {\it Automation and Remote Control}, 2012, vol.~73, no.~11, pp.~1784--1793.






9. Parsegov S. E., Polyakov A. E.,  Shcherbakov P. S.
   Nonlinear control protocol for uniform allocation
of agents on a segment. {\it Dokl. Math.}, 2013, vol.~87, no.~1,  pp.~133--136.





10. Aleksandrov  A., Fradkov A.,  Semenov A.
   Delayed and switched control of formations on a line segment:
Delays and switches do not matter.
  {\it IEEE Trans. Automat. Control}, 2020, vol.~65, no.~2, pp.~794--800.


11. Aleksandrov  A., Semenov A.,  Fradkov A.
   Discrete-time deployment of agents on a line segment:
Delays and switches do not matter.
  {\it Automation and Remote Control}, 2020, vol.~81, no.~4, pp.~637--648.



12. Aleksandrov A. Yu.,  Andriyanova N. R.
  Fixed-time stability of switched systems with application to a
problem of formation control.
  {\it Nonlinear Analysis. Hybrid Systems}, 2021, vol.~40, no.~101008. 	


13. Kaszkurewicz E.,   Bhaya A.
{\it Matrix diagonal stability in systems and computation.}
   Boston, Basel, Berlin, Birkhauser Press, 1999, 267~p.


14. Aleksandrov A., Mason O.
   Diagonal Lya\-pu\-nov\,---\,Kra\-sov\-skii functionals for discrete-time
positive systems with delay.
   {\it Syst. Control Lett.}, 2014, vol.~63, pp.~63--67.


15. Aleksandrov A.,  Mason O.
  Diagonal stability of a class of discrete-time positive switched
systemswith delay.
  {\it IET Control Theory $\&$ Applications}, 2018, vol.~12, no.~6,
pp.~812--818.


16. Lin H.,   Antsaklis P. J.
   Stability and stabilizability of switched linear systems:
A survey of recent results.
  {\it IEEE Trans. Automat. Control}, 2009, vol.~54, no.~2, pp.~308--322.

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 08, 2022.

Accepted: February 01, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Alexander Yu. Aleksandrov} --- Dr. Sci. in Physics and
Mathematics, Professor;\\ a.u.aleksandrov@spbu.ru \par

\vskip 2mm \textit{Al'bert I. Arakelov} --- Student;  arakelov.albert@yandex.ru \par
%
}
