
{\normalsize

\vskip 6mm

\noindent{\bf Approximate factorization of positive matrices by
using methods\\ of tropical optimization$^{*}$ }

}

\vskip 2.5mm

{\small

\noindent{\it N.~K.~Krivulin, E.~Yu.~Romanova %$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2.5mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent\indent~$^{*}$ This work was supported by the
Russian Foundation for Basic Research (grant N~20-010-00145).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Krivulin~N.~K., Romanova~E.~Yu.
Approximate factorization of positive matrices by using methods of
tropical optimization. {\it Vest\-nik of Saint Petersburg
University. Applied Mathe\-ma\-tics. Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~16, iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The problem of rank-one factorization of
positive matrices with missing (unspecified) entries is considered
where a matrix is approximated by a product of column and row
vectors that are subject to box constraints. The problem is
reduced to the constrained approximation of the matrix, using the
Chebyshev metric in logarithmic scale, by a matrix of unit rank.
Furthermore, the approximation problem is formulated in terms of
tropical mathematics that deals with the theory and applications
of algebraic systems with idempotent addition. By using methods of
tropical optimization, direct analytical solutions to the problem
are derived for the case of an arbitrary positive matrix and for
the case when the matrix does not contain columns (rows) with all
entries missing. The results obtained allow one to find the
vectors of the factor decomposition by using expressions in a
parametric form which is ready for further analysis and immediate
calculation. In conclusion, an example of approximate rank-one
factorization of a matrix with missing entries is provided.
\\[1mm]
\textit{Keywords}: positive matrix factorization, rank-one matrix
approximation, log-Chebyshev distance function, tropical
optimization, max-algebra.\par}

%\vskip6mm
\pagebreak

\noindent \textbf{References} }

\vskip 2.5mm

{\footnotesize

1.~Aissa-El-Bey~A., Seghouane~K. Sparse canonical correlation
analysis based on rank-1 matrix approximation and its application
for FMRI signals.
\textit{2016 IEEE Intern. Conference on Acoustics, Speech and Signal Processing (ICASSP).} %, Shanghai, China.
IEEE, 2016, pp.~4678--4682.\\
https://doi.org/10.1109/ICASSP.2016.7472564

2.~Kannan~R., Ishteva~M., Park~H. Bounded matrix factorization for
recommender system.
%\textit{Knowl. Inf. Syst.},
\textit{Knowledge and Information Systems}, 2014, vol.~39, no.~3,
pp.~491--511. https://doi.org/10.1007/s10115-013-0710-2

3.~Xiu~X., Kong~L. Rank-one and sparse matrix decomposition for
dynamic MRI.
%\textit{Numer. Algebra Control Optim.},
\textit{Numerical Algebra, Control and Optimization}, 2015,
vol.~5, no.~2, pp.~127--134.
https://doi.org/10.3934/naco.2015.5.127

4.~Belachew~M.~T., Gillis~N. Solving the maximum clique problem
with symmetric rank-one non-negative matrix approximation.
%\textit{J. Optim. Theory Appl.},
\textit{Journal of Optimization Theory and Applications}, 2017,
vol.~173, no.~1, pp.~279--296.
https://doi.org/10.1007/s10957-016-1043-6

5.~Krivulin~N. Rating alternatives from pairwise comparisons by
solving tropical optimization problems.
\textit{2015 12th Intern. Conference on Fuzzy Systems and Knowledge Discovery (FSKD).} %/ ed. by Z.~Tang, and J.~Du, S.~Yin, L.~He, R.~Li.
IEEE, 2015, pp.~162--167.
https://doi.org/10.1109/FSKD.2015.7381933

6.~Krivulin~N. Using tropical optimization techniques to evaluate
alternatives via pairwise comparisons.
\textit{2016 Proceedings of the 7th SIAM Workshop on Combinatorial Scientific Computing.} %/ ed. by A.~H.~Gebremedhin, E.~G.~Boman, B.~Ucar.
SIAM, 2016, pp.~62--72.
https://doi.org/10.1137/1.9781611974690.ch7

7.~Gillis~N. Introduction to nonnegative matrix factorization.
\textit{SIAG/OPT Views and News}, 2017, vol.~25, no.~1, pp.~7--16.

8.~Kumar~N.~K., Schneider~J. Literature survey on low rank
approximation of matrices.
%\textit{Linear Multilinear Algebra},
\textit{Linear and Multilinear Algebra}, 2017, vol.~65, no.~11,
pp.~2212--2244. https://doi.org/10.1080/03081087.2016.1267104

9.~Feldman~D., Tassa~T. More constraints, smaller coresets:
constrained matrix approximation of sparse big data.
\textit{Proceedings of the 21st ACM SIGKDD Intern. Conference on Knowledge Discovery
and Data Mining.} %, Sydney, NSW, Australia.
New York, ACM Press, 2015, pp.~249--258.
https://doi.org/10.1145/2783258.2783312

10.~Kyrillidis~A. Simple and practical algorithms for
$\ell_{p}$-norm low-rank approximation.
\textit{34th Con\-fe\-ren\-ce on Uncertainty in Artificial Intelligence.} % (UAI), Monterey, CA.
Corvallis, AUAI Press, 2018, pp.~414--424.

11.~Gillis~N., Shitov~Y. Low-rank matrix approximation in the
infinity norm.
%\textit{Linear Algebra Appl.},
\textit{Linear Algebra and its Applications}, 2019, vol.~581,
no.~15, pp.~367--382. https://doi.org/10.1016/j.laa.2019.07.017

12.~Panyukov~A., Chaloob~K.,  Mezal~Y. Approximation of a matrix
with positive elements by a matrix of a unit rank.
\textit{2018 IEEE Symposium on Computer Applications and Industrial Electronics (ISCAIE).} %Penang, Malaysia, April, 2018.
IEEE, 2018, pp.~234--237.
https://doi.org/10.1109/ISCAIE.2018.8405476

13.~Krivulin~N.~K., Romanova~E.~Yu. Rank-one approximation of
positive matrices based on methods of tropical mathematics.
%\textit{Vestnik St.~Petersburg Univ. Math.},
\textit{Vestnik Saint~Petersburg University. Mathematics}, 2018,
vol.~51, no.~2, pp.~133--143.
https://doi.org/10.3103/S106345411802005X

14.~Krivulin~N.~K., Romanova~E.~Yu. On the rank-one approximation
of positive matrices using tropical optimization methods.
%\textit{Vestnik St.~Petersburg Univ. Math.},
\textit{Vestnik Saint~Petersburg University. Mathematics}, 2019,
vol.~52, no.~2, pp.~145--153.
https://doi.org/10.1134/S1063454119020080

%15.~Маслов~В.~П., Колокольцов~В.~Н.
%\textit{Идемпотентный анализ и его применение в оптимальном управлении.}
%М.: Физматлит, 1994, 144~с.
15.~Maslov~V.~P., Kolokol’tsov~V.~N. \textit{Idempotentnyj analiz
i ego primenenie v optimal’nom upravlenii} [\textit{Idempotent
analysis and its applications in optimal control}]. Moscow,
Fizmatlit Publ., 1994, 144~p. (In Russian)

16.~Heidergott~B., Olsder~G.~J., van der Woude~J. \textit{Max Plus
at work.} Princeton, Princeton University Press, 2006, 226~p.
(Princeton Series in Applied Mathematics)

17.~McEneaney~W.~M. \textit{Max-plus methods for nonlinear control
and estimation.} Boston, Birkh\"auser Press, 2006, 241~p. (Systems
and Control: Foundations and Applications)\\
https://doi.org/10.1007/0-8176-4453-9

%18.~Кривулин~Н.~К.
%\textit{Методы идемпотентной алгебры в задачах моделирования и анализа сложных систем.}
%СПб: Изд-во С.-Петерб. ун-та, 2009. 256~с.
18.~Krivulin~N.~K. \textit{Metody idempotentnoj algebry v
zadachakh modelirovaniya i analiza slozhnykh sistem}
[\textit{Methods of idempotent algebra for problems in modeling
and analysis of complex systems}]. Saint Petersburg, Saint
Petersburg University Press, 2009, 256~p. (In Russian)

19.~Butkovi\v{c}~P. \textit{Max-linear systems.} London, Springer
Press, 2010, 272~p. (Springer Monographs in Mathematics)
https://doi.org/10.1007/978-1-84996-299-5

20.~Krivulin~N. A constrained tropical optimization problem:
Complete solution and application example.
\textit{Tropical and Idempotent Mathematics and Applications.} %/ ed. by G.~L.~Litvinov and S.~N.~Sergeev
Providence, AMS Press, 2014, pp.~163--177. (Vol.~616 of
Contemporary Mathematics) https://doi.org/10.1090/conm/616/12308

21.~Krivulin~N. Tropical optimization problems.
\textit{Advances in Economics and Optimization.} %/ ed. by L.~A.~Petrosyan, J.~V.~Romanovsky, D.~W.~K.~Yeung.
New York, Nova Science Publ., 2014, pp.~195--214. (Economic
Issues, Problems and Perspectives)

22.~Krivulin~N. Extremal properties of tropical eigenvalues and
solutions to tropical optimization problems.
%\textit{Linear Algebra Appl.},
\textit{Linear Algebra and its Applications}, 2015, vol.~468,
pp.~211--232.\\ https://doi.org/10.1016/j.laa.2014.06.044\newpage

23.~Krivulin~N. A multidimensional tropical optimization problem
with nonlinear objective function and linear constraints.
\textit{Optimization}, 2015, vol.~64, no.~5, pp.~1107--1129.\\
https://doi.org/10.1080/02331934.2013.840624


\vskip1.5mm Received:  October 18, 2020.

Accepted: October 23, 2020.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Nikolai K. Krivulin} --- Dr. Sci. in Physics and
Mathematics, Professor; nkk@math.spbu.ru

\vskip2mm \textit{Elizaveta Yu. Romanova} --- Student;
romanova.ej@gmail.com\par
%
%
}
