{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. {Yakushev V. P., Bure V. M.} Metodologicheskie podkhodi k
ocenke optimal'nogo momenta vremeni provedeniya
agrotekhnologicheskikh meropriyatii [Methodological approaches to
the estimation of the optimal moment in time for the conducting of
the agrotechnological event]. {\it Dokl. RASXN} [{\it Reports of
RAAS}], 2001, no.~4, pp.~27--29. (In Russian)

2. {Yakushev V. P., Bure V. M.} Statisticheskaja ocenka
raspredelenija optimal'nogo momenta vremeni provedenija
agrotekhnicheskogo meropriyatija  [Statistical evaluation of the
distribution of the optimum moment in time for the agrotechnical
event]. {\it Dokl. RASXN} [{\it Reports of RAAS}], 2002, no.~3,
pp.~11--13. (In Russian)

3. {Bure A. V. }  Ocenka momenta vremeni pojavlenija sobitija
[Evaluation of the time moment for the occurrence of an event].
 {\it Vestnik of Saint Petersburg  University. Series~10.
Applied mathematics. Computer science. Control processes}, 2014,
issue~1, pp.~23--29. (In Russian)


4. {Bure A. V.} Ocenka momenta vremeni krizisnogo sostoyaniya
bol'nogo po medicinskim bazam dannix [Estimation of the crisis
time of patient’s state using medical database]. {\it Trudi XLIII
mezdynarodnoi naychnoi konferencii aspirantov i studentov} [{\it
Proc. of XLIII Intern. science of conference of post-graduate
students and students}]. Saint-Petersburg, Saint Petersburg State
University Publ., 2012, pp.~272--276. (In Russian)

5. {Barker K., Haimes Ya. Y.} Assessing uncertainty in extreme
events: Applications to risk-based decision making in
interdependent infrastructure sectors.  {\it Reliability
Engineering and System Safety}, 2009, vol.~94, issue~4,
pp.~830--837.

6. {Feller W.} {\it An introduction to probability theory and its
applications. In 2~vol.}  New York, London, Sydney, John Wiley,
Inc., 1957, 738~p. (Russ. ed.: Feller W. {\it Vvedenie v teoriu
veroyatnostei i ee prilozenia: in 2~t.} Moscow, Mir Publ., 1984,
vol.~2, 752~p.)


}
