

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. Babadzanjanz L.~K. Suschestvovaniye prodolgeniya i predstavleniye resheniya v nebesnoy mechanike [Existence of the continuations and representation of the solutions in celestial mechanics]. \textit{Trudy ITA AN SSSR} [\textit{Proceedings of the ITA AS USSR}],  1978, vol.~XVII, pp.~3--45. (In Russian)

2. Babadzanjanz L.~K. Metod ryadov Taylora [The Taylor series method]. \textit{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2010, iss.~3, pp.~13--29. (In~Russian)

3. Babadzanjanz L. K. Metod dopolnitelnih peremennih [The additional variables method].  \textit{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2010, iss.~4, pp.~3--11. (In Russian)

4. Babadzanjanz L.~K., Bregman K.~M. Algorithm metoda dopolnitelnih peremennih [Algorithm of the additional variables method]. \textit{Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes}, 2012, iss.~2, pp.~3--12. (In Russian)

5. Babadzanjanz L.~K., Bol'shakov A.~I. Primenenie metoda ryadov
Taylora dlya resheniya obiknovennih differentsialnih uravneniy
[Implementation of the Taylor series method for solving ordinary
differential equations]. \textit{Vychislitelnye Metody i
Programmirovanie $[$Numerical Methods and Programming}], 2012,
vol.~13, iss.~4, pp.~497--510. (In~Russian)

6. Alesova I.~M., Babadzanjanz L.~K., Pototskaya I.~Yu., Pupysheva
Yu.~Yu., Saakyan A.~T. High-precision numerical integration of
equations in dynamics. \textit{International scientific conference
on mechanics ``The Eighth Polyakhov's Reading’’, Saint Petersburg,
2018}, \textit{AIP Conference Proceedings}, 2018, vol.~1959,
no.~080005. https://doi.org/10.1063/1.5034722

7. Babadzanjanz L.~K., Pototskaya I.~Yu, Pupysheva Yu.~Yu. Estimates for Taylor series method to linear total systems of PDEs. \textit{Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~1, pp.~3--11.

8. Babadzanjanz L.~K., Bregman A.~M., Bregman K.~M., Kasikova P.~V., Petrosyan L.~A.  Polniye systemy uravneniy v zadache dvuh tel [Total systems of equations to the two-body problem]. \textit{Engineering sciences --- from theory to applications. Coll. papers on LXI Internanional Conference.} Novosibirsk, SIBAK Publ., 2016, vol.~8(56), pp.~13--21. (In Russian)

9. Gaishun I.~V. \textit{Vpolne razreshimiye mnogomerniye differentsialniye uravneniya} [\textit{Completely sol\-vable multidimensional differential equations}]. Minsk, Belarus, Nauka i technika Publ., 1983, 272~p. (In Russian)

10. Poincare H. Memoire sur les courbes definies par une equation differentielle. \textit{Journal de mathematiques pures et appliquees}, 1886, series~4, vol.~2, pp.~151--218.

11. Steffensen J.~F. On the restricted problem of three bodies. \textit{Mat.-Fys. Medd. Danske}, Viden-skab., Selskab, 1956, vol.~30, no.~18, pp.~75--83.

12. Steffensen J.~F. On the problem of three bodies in the plane. \textit{Mat.-Fys. Medd. Danske}, Viden-skab., Selskab, 1957, vol.~31. no.~3. pp.~98--123.

13. Babadzanjanz L.~K., Pototskaya I.~Yu., Pupysheva Yu.~Yu. Error estimates for numerical integration of ODEs in the minimax formulation. \textit{2017 Constructive Nonsmooth Analysis and Related Topics (Dedicated to the memory of V. F. Demyanov), CNSA 2017, Proceedings}. Saint Petersburg, Russia, 2017. https://doi.org/10.1109/CNSA.2017.7973932

14. Bellman R. \textit{Introduction to matrix analysis}. 2nd ed. Philadelphia, SIAM Publ., 1997, 403~p.

15. Babadzanjanz L.~K. \textit{Method beskonechnih system v
zadachah nebesnoy mechaniki} [\textit{Infinite system method in
celestial mechanics problems}]. Dis. of Dr. Sci. in Physics and
Mathematics. Saint Petersburg, Saint Petersburg State University
Publ., 1985, 236~p. Available at:\\
http://www.apmath.spbu.ru/ru/staff/babadzhanyants/publ/publ27.pdf (accessed: November 01, 2020).
(In Russian)


16. Antonov V.~A. \textit{Elementy teorii gravitatsionnogo potentsiala i necotoriye sluchayi ego yavnogo vyrageniya} [\textit{Elements of the theory of gravitational potential and some cases of its explicit expression}]. Saint Petersburg, Saint Petersburg State University Press, 2008, 208~p. (In Russian)

17. Antonov V.~A. \textit{Vvedeniye v teoriyu nyutonovskogo
potentsiala}  [\textit{Introduction to the theory of Newtonian
potential}]. Moscow, Nauka Publ., 1988, 270~p. (In Russian)

18. Kondratiev B.~P. \textit{Teoriya potentsiala (noviye metodi i
zadachi s recheniyami)} [\textit{Potential theory (New methods and
problems with solutions)}]. Moscow, Mir Publ., 2007, 512~p. (In
Russian)

19. Sretensky L.~N. \textit{Teoriya nyutonovskogo potentsiala}
[\textit{Theory of Newtonian potential}]. Moscow, Leningrad,
Gostechizdat Publ., 1946, 322~p. (In Russian)

20. Uchaykin V.~V. \textit{Mechanika. Osnovy mekhaniki sploshnyh
sred. Zadachi i upragnenia} [\textit{Mechanics. Fundamentals of
continuum mechanics. Tasks and exercises}]. Moscow, Ijevsk,
Institute of computer science Publ., 2002, 179~p. (In Russian)


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  November 03, 2020.

Accepted: January 15, 2021.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Levon K. Babadzanjanz} --- Dr. Sci. in Physics and Mathematics, Professor; levon-lkb@yandex.ru

\vskip 2mm \textit{Irina Yu. Pototskaya} --- PhD in Physics and Mathematics, Associate Professor;\\ irinapototskaya@yandex.ru

\vskip 2mm \textit{Yulia Yu. Pupysheva} --- PhD in Physics and Mathematics, Associate Professor; j\_poupycheva@mail.ru \par
%
%
}
