


\zageng{517.977.56}{V.~V. Provotorov$^1$,~ E.~N.
Provotorova$^2$}{OPTIMAL CONTROL OF THE LINEARIZED NAVIER---STOKES
SYSTEM\\ IN A NETLIKE DOMAIN%$^*$
}{



\vspace{-3mm}\parindent=7mm



%{\copyright} А.~В.~Буре, 2014

\textit{Provotorov Vyacheslav Vasil'evich} --- doctor of  physics
and mathematics sciences, professor;\\ wwprov@mail.ru


\textit{Provotorova Elena Nikolaevna} --- PhD of  physical and
mathematical sciences, associate\\ professor; enprov@mail.ru

\vskip 2mm

\emph{Провоторов Вячеслав Васильевич} --- доктор
физико-математических наук, профессор;\\ wwprov@mail.ru

\emph{Провоторова Елена Николаевна} --- кандидат
физико-математических наук, доцент;\\ enprov@mail.ru

\vskip 2mm

%$^*$ Работа выполнена при финансовой поддержке
%Санкт-Петербургского государственного университета (грант №
%9.38.205.2014).


{\copyright} Санкт-Петербургский государственный университет,
\issueyear %
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp03 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum09}}\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp03 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum09}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




{\footnotesize

\noindent $^1$ Voronezh State University,  1, Universitetskaya
square, Voronezh,

\noindent\hskip2.45mm 394006, Russian Federation


\noindent $^2$ Voronezh State Technical University,  14,
Moskovskii pr., Voronezh,

\noindent\hskip2.45mm 394026, Russian Federation






\vskip3mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item This work is a natural extension of research into optimal
control problems of evolution equations with distributed
parameters on a geometrical graph (network) of one of the authors
in the direction of increasing the dimension of a spatial variable
and the functions describing the state of the study of the
Navier---Stokes equations. At the same time is examined a simple
case of the absence of convective effect (laminar flow of an
incompressible viscous fluid) --- linearized system of
Navier---Stokes equations in a net-like domain. It proves unique
solvability of the initial boundary value problem in the weak
formulation which is based on the Faedo---Galerkin method using a
special basis (the set of generalized eigenfunctions of the
special spectral problem) and a priori estimates of norms
solutions such as power inequalities. The proof is constructive:
to construct a sequence of approximate solutions that converges
weakly to the exact solution of the problem. Problems are analyzed
with distributed and a start control with a final observation,
widespread in applications, that provides the necessary and
sufficient conditions for the existence of optimal controls in
terms of the conjugate states of the respective systems.
Sufficient attention is paid to the synthesis of the optimal
control action, and analogues of established finite-dimensional
case for Kalman results have been obtained. Although, the use of
this method is demonstrated by examples of optimal control theory,
this method has a highly susceptible to generalization and
applicable to a wide class of linear problems. Refs~15.

{\it Keywords}: linearized Navier---Stokes system, net like
domain, weak solutions, optimal control, control synthesis.

\end{list}

}

\vskip4mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it В.~В. Провоторов$^1$, Е. Н. Провоторова$^2$}

\vskip4mm \noindent{\bf ОПТИМАЛЬНОЕ УПРАВЛЕНИЕ\\ ЛИНЕАРИЗОВАННОЙ
СИСТЕМОЙ НАВЬЕ---СТОКСА\\  В~СЕТЕПОДОБНОЙ ОБЛАСТИ}

\vskip1.8mm


{\footnotesize


\noindent $^1$~Воронежский государственный университет, Российская
Федерация,

\noindent\hskip2.45mm 394006, Воронеж, Университетская площадь, 1

%\newpage

\noindent $^2$~Воронежский государственный технический
университет, Российская Федерация,

\noindent\hskip2.45mm 394026, Воронеж, Московский пр., 14


\vskip4mm


\item Рассматривается начально-краевая задача для линеаризованной системы
Навье---Стокса в~сетеподобной области, в~основу анализа которой
положены  результаты О.~А.~Ладыженской, Н.~Н.~Уральцевой,
Ж.-Л.~Лионса и~А.~В.~Фурсикова  для уравнений с~частными
производными в~классических областях. Методом Фаэдо---Галеркина,
используя спе\-циальный базис (множество обобщенных собственных
функций специальной спектральной задачи) и~априорные оценки нормы
решения типа энергетических неравенств, показана однозначная
разрешимость рассматриваемой начально-краевой задачи в~слабой
постановке. При этом строится последовательность приближенных
решений, слабо сходящаяся к~точному решению задачи. Приведен
анализ распространенных в~приложениях задач распределенного
и~стартового управлений с~финальным наблюдением, получены
необходимые и~достаточные условия существования оптимальных
управлений в~терминах сопряженных состояний соответствующих
систем. Решена задача синтеза оптимального управления для случая
отсутствия ограничений на~управляющие воздействия и~получены
аналоги известных для конечномерного случая результатов Калмана.
Используемый в~работе подход является естественным при анализе
широкого класса задач оптимального управления, которые описываются
с помощью корректных по~Адамару начально-краевых задач;
представленные результаты являются основополагающими при
исследовании задач оптимального управления динамикой ламинарных
течений многофазных сред, а~также при изучении поведения плоских
и~сферических волн с~сильным разрывом на~фронте, который двигается
с~заданной скоростью. Библиогр. 15~назв.

\textit{Ключевые слова}: линеаризованная система Навье---Стокса,
сетеподобная область, слабые решения, оптимальное управление,
синтез управления.


}

\end{list}


\vskip2.5mm

\vskip2.5mm

\textbf{1. Introduction.} In the applied problems of
hydrodynamics, the system of two equations
\begin{equation}\label{eq1}
{{\begin{array}{*{20}c} \frac{\partial Y}{\partial t}-\nu\triangle
Y+\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial x_i}+\nabla p=
f,
 \end{array} }}
\end{equation}
\begin{equation}\label{eq2}
{{\begin{array}{*{20}c} \mathrm{div}\,
Y=0\left(\sum\limits_{i=1}^n \frac{\partial Y}{\partial
x_i}=0\right)
 \end{array} }}
\end{equation}
in a pair of functions $\{Y(x,t),p(x,t)\}$ (the Navier---Stokes
system in the evolutionary case~[1, p.~77], where
$Y=\{Y_1,Y_2,...,Y_n\}$ is a vector function, $p$ denotes a scalar
function, $x\in \mathbb{R}^n$) describes the dynamics of an
incompressible viscous medium with the coefficient of viscosity
$\nu$, the velocity vector $Y$ of hydraulic flow and the
convective component defined by the term
$\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial x_i}$ in
expression~(1). In many cases (first of all, in laminar
processes), the convective component is absent, equation~(1)
becomes linear and system~(1), (2) is called the linearized
Navier---Stokes system.

The papers~[2--5] studied on systematic basis different optimal
control problems for evolutionary equations with distributed
parameters on a geometrical graph (net). The present work is a
natural continuation of the cited research towards increasing the
dimension of the spatial variable $x$ ($x\in \mathbb{R}^n$,
$n\geq2$) and also the dimension of the functions that describe
the system state. Note that the simpler case without the
convective effect (i.~e., the laminar flow of an incompressible
viscous medium) is considered below. We touch a rather wide range
of optimal control issues for distributed parameter systems on
netlike domains, namely, the unique solvability of the
corresponding initial boundary value problem and the analysis of
optimal control problems that are commonly encountered in
applications (distributed and starting control). Sufficient
attention is paid to the design of optimal control actions.


\textbf{2. Necessary notations, concepts and definitions.}
Consider an open bounded domain $\Im$ of the Euclidean space
$\mathbb{R}^n$ that has a netlike structure~[3, 4], i.~e.,
$\Im=(\bigcup\limits_k\Im_k)\bigcup(\bigcup\limits_lS_l)$, where
$S_l$ is a surface that separates adjacent domains $\Im_k$,
$\partial\Im$ indicates the boundary of $\Im$ (initially, the
smoothness of $\partial\Im$ is not important). The locus of
conjugation of the adjacent domains $\Im_k$ will be called the
node locus and further denoted by $\xi$; it represents the union
of surfaces $S_l(\xi)$ whose number coincides with the number of
conjugated domains, that is, $\xi=\bigcup\limits_l S_l(\xi)$.
Throughout the paper, we use measurable functions and the Lebesgue
integral. The latter over the domain $\Im$ is comprehended as the
sum of the integrals over the domains $\Im_k$, i.~e.,
$\int\limits_{\Im}fdx=\sum \limits_{k}\int\limits_{\Im_k}fdx$.

For a vector function $Y(x,t)=\{y_1(x,t),y_2(x,t),...,y_n(x,t)\}$
($x=\{x_1,x_2,...,x_n\}$) defined in a domain
$\Im_T=\Im\times(0,T)$ ($T<\infty$), consider the linearized
Navier---Stokes system
\begin{equation}\label{eq25}
{{\begin{array}{*{20}c} \frac{\partial Y}{\partial t}-\nu\triangle
Y+\nabla p= f,
 \end{array} }}
\end{equation}
\begin{equation}\label{eq26}
{{\begin{array}{*{20}c} \mathrm{div}\,Y=0,
 \end{array} }}
\end{equation}
with the relationships
\begin{equation}\label{eq27}
{{\begin{array}{*{20}c} Y|_{S^-_l(\xi)}=Y|_{S^+_l(\xi)},
 \end{array} }}
\end{equation}
\begin{equation}\label{eq28}
{{\begin{array}{*{20}c} \sum \limits_{l}\frac{\partial Y}{\partial
n^-_l}|_{S^-_l(\xi)}+\sum \limits_{l}\frac{\partial Y}{\partial
n^+_l}|_{S^+_l(\xi)}=0
 \end{array} }}
\end{equation}
holding for each node locus $\xi$ (which are known in the
literature as the conjugation conditions, see~[3--5]); here
$S^-_l(\xi)$ and $S^+_l(\xi)$ mean the unilateral surfaces for
$S_l(\xi)$ defined by the direction of the normals $n^-_l$ and
$n^+_l$ to the surfaces $S^-_l(\xi)$ and $S^+_l(\xi)$,
respectively. Supplementing (3)--(6) with the initial conditions
\begin{equation}\label{eq29}
{{\begin{array}{*{20}c} Y(x,0)=Y_0(x),~ \,\,x\in \Im,
 \end{array} }}
\end{equation}
at time $t=0$ and the boundary conditions
\begin{equation}\label{eq30}
{{\begin{array}{*{20}c} Y|_{\partial\Im}=0
 \end{array} }}
\end{equation}
on the boundary of the continuous medium volume, we obtain the
initial boundary value problem~(3)--(8) to find the functions
$Y(x,t)$ and $p(x,t)$ ($p(x,t)$ is a scalar function) in the
closed domain of ${\Im}_T$
($\overline{\Im}_T=(\Im\cup\partial\Im)\times[0,T]$).

In the applied problems of hydrodynamics, the netlike domain $\Im$
is actually a hydrosystem caused by a pressure $p$ (with a
pressure gradient $\nabla p=\mathrm{grad}\,p$) that distributes
the flows of a fluid (a multiphase medium); the function $Y(x,t)$
describes the velocity vector of the hydraulic flow in the domain
$\Im_T$; relationships~(3), (4) reflect the dynamics of an
incompressible fluid with the coefficient of viscosity $\nu>0$ in
the domain $\bigcup\limits_k\Im_k\times(0,T)$; the balance
equalities (5), (6) define the fluid flow conditions in the node
loci of the hydrosystem $\Im$; finally, $f(x,t)$ denotes the
density of external forces. The transfer process of the multistage
medium is isothermal.

Let us define a weak solution of the initial boundary value
problem~(3)--(8). To this end, introduce necessary spaces and
present preliminary considerations.

Designate by $L_2(\Im)^n$ the space of measurable functions
(classes)  $\mu=\{\mu_1,\mu_2,...,\mu_n\}$ that are square
summable over the domain $\Im$. For $\mu,\rho \in L_2(\Im)^n$, the
scalar product is defined by
\begin{equation}\label{eq31}
{{\begin{array}{*{20}c}
\left(\mu,\rho\right)=\sum\limits_{i=1}^n\int\limits_\Im\mu_i(x)\rho_i(x)dx,
 \end{array} }}
\end{equation}
where $\|\mu\|=(\mu, \mu)^{1/2}$. Assume that $D(\Im)^n$ forms the
space of functions that are infinitely differentiable in the
domain $\Im$ and have compact supports in $\Im$. Let
$\mathfrak{D}(\Im)^n=\{\phi: \phi\in D(\Im)^n,\,\,
\mathrm{div}\,\phi =0\}$ and denote by  $\mathfrak{D}'(\Im)^n$ the
conjugate space for $\mathfrak{D}(\Im)^n$ (here and in the sequel,
the symbol $'$ indicates conjugate spaces). Define the space
$\mathcal{H}(\Im)$ as the closure of $\mathfrak{D}(\Im)^n$ in the
norm $L_2(\Im)^n$ with the scalar product~(9),
$\|\mu\|_{\mathcal{H}(\Im)}=\left(\mu,\mu\right)^{1/2}$ and
$\mathcal{H}(\Im)=\mathcal{H}(\Im)'$.

Consider a space $\mathcal{H}^1(\Im)$ consisting of the elements
$\mu\in L_2(\Im)^n$ that have the generalized derivative
$\frac{\partial\mu}{\partial x}\in L_2(\Im)^n$
($\frac{\partial\mu}{\partial x_i}\in L_2(\Im)$,
$i=\overline{1,n}$). The space $\mathcal{H}^1(\Im)$ is equipped
with the norm
$\|\mu\|_{\mathcal{H}^1(\Im)}=(\|\mu\|^2_{L_2(\Im)}+\|\frac{\partial\mu}{\partial
x}\|^2_{L_2(\Im)})^{1/2}$ and represents a Hilbert space with the
scalar product
$\left(\mu,\rho\right)_{\mathcal{H}^1(\Im)}=(\mu,\rho)+(\frac{\partial\mu}{\partial
x},\frac{\partial\rho}{\partial x})$.

Next, define a space $V^1_{\,0}(\Im)$ as the closure in the norm
$\mathcal{H}^1(\Im)$ for the set of elements
$\mu\in\mathfrak{D}(\Im)^n$ satisfying the conjugation conditions
%\[{{\begin{array}{*{20}c}
$\sum \limits_{l}\frac{\partial \mu}{\partial
n^-_l(\xi)}|_{S^-_l(\xi)}+\sum \limits_{l}\frac{\partial
\mu}{\partial n^+_l}|_{S^+_l(\xi)}=0. $\linebreak% \end{array} }}}\]
In other words, $V^1_{\,0}(\Im)$ is the subspace of functions from
$\mathcal{H}^1(\Im)$ that ``satisfy the conjugation conditions''
in all node loci $\xi$ of the domain $\Im$ and ``vanish'' on
$\partial\Im$. Note that the space $V^1_{\,0}(\Im)$ can be
equivalently defined as the closure in the norm
$\mathcal{H}^1(\Im)$ for the set of elements
$\mu\in\mathfrak{D}_\circ(\Im)^n\subset \mathfrak{D}(\Im)^n$ (in
contrast to the elements of the set $\mathfrak{D}(\Im)^n$, the
ones of $\mathfrak{D}_\circ(\Im)^n$ satisfy the stated conjugation
conditions).

Consider the bilinear form
\begin{equation}\label{eq32}
{{\begin{array}{*{20}c} \rho(u,v)=
\sum\limits_{i,j=1}^n\int\limits_{\Im}\frac{\partial u_j}{\partial
x_i}\frac{\partial v_j}{\partial x_i}dx,
\end{array} }}
\end{equation}
in functions $u,v,\omega$ such that the integrals in the above
representation are convergent.

\textbf{Lemma.} \emph{The bilinear form} (10) \emph{is continuous
on ${V}^1_{\,0}(\Im)\times {V}^1_{\,0}(\Im)$}.

P r o o f. Applying the Cauchy---Bunyakowsky---Schwartz inequality
to the functions $\frac{\partial u_j}{\partial x_i}$ and
$\frac{\partial v_j}{\partial x_i}$ in the right-hand side of
form~(10) yields
\begin{equation}\label{eq34}
{{\begin{array}{*{20}c} |\int\limits_{\Im}\frac{\partial
u_j}{\partial x_i}\frac{\partial v_j}{\partial x_i}dx|\leq
\sqrt{\int\limits_{\Im}(\frac{\partial u_j}{\partial
x_i})^2dx}\sqrt{\int\limits_{\Im}(\frac{\partial v_j}{\partial
x_i})^2dx}\leq\|u_j\|_{V^1_0(\Im)}\|v_j\|_{V^1_0(\Im)}.
\end{array} }}
\end{equation}
And the statement of this lemma follows from inequality~(11).

Introduce the spaces of functions $u(x,t)$ of the variables
$x,t\in \Im_T$ and consider $u$ as a function of $t$ taking values
in the space of functions of $x$. Particularly, if $V$ represents
a Hilbert space, then denote by $L_2(0,T;V)$ the space of
functions (classes) $u: (0,T)\rightarrow V$ that are measurable,
take values from $V$ and
\[
{{\begin{array}{*{20}c}
\|u\|_{L_2(0,T;V)}=\left(\int\limits_{0}^T\|u(t)\|^2_Vdt\right)^{1/2}<\infty.
 \end{array} }}
\]
Note that the equality $L_2(\Im_T)^n=L_2(0,T;L_2(\Im)^n)$ holds
obviously.

Next, introduce the following spaces: $W^{1,0}(\Im_{T})$ as the
space of functions $u(x,t)\in L_{2}(\Im_{T})^n$ that have the
generalized first derivative with respect to $x$ belonging to
$L_{2}(\Im_{T})^n$, with the norm in $W^{1,0}(\Im_{T})$ defined by
\[
{{\begin{array}{*{20}c} \|u\|_{W^{1,0}(\Im_{T})}=
\left(\|u\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
x}\|^2_{L_2(\Im_T)^n}\right)^{1/2};
 \end{array} }}
\]
$W^{1}(\Im_{T})$ as the space of functions from $L_{2}(\Im_T)^n$
that have the generalized first derivatives also belonging to
$L_{2}(\Im_T)^n$, with the norm defined by
\[
{{\begin{array}{*{20}c} \|u\|_{W^{1}(\Im_{T})}=
\left(\|u\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
t}\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
x}\|^2_{L_2(\Im_T)^n}\right)^{1/2}.
 \end{array} }}
\]

Using the properties of the traces of elements from
$W^{1}(\Im_{T})$ on each section of $\Im_{T}$ by the plane $t=t_0$
($t_0\in [0,T]$) as elements of $L_2(\Im)^n$ that are continuous
in $t$ in the norm $L_2(\Im)^n$ (see $[6$, p.~$70]$), define
${\Omega}_0(\Im_{T})$ as the set of functions $u(x,t)\in
W^{1}(\Im_{T})$ belonging %\linebreak\newpage\noindent
to the class $V^1_{\,0}(\Im)$ for fixed $t\in [0,T]$. Denote by
$W_{\,0}^{1}(\Im_{T})$ the closure of the set
${\Omega}_0(\Im_{T})$ in the norm $W^{1}(\Im_{T})$.\newpage

Next, let $\widehat{\Omega}_0(\Im_{T})$ be the set of all
functions $u(x,t)\in W^{1,0}(\Im_{T})$ that

a) have the finite norm
\begin{equation}\label{eq36}
{{\begin{array}{*{20}c} \|u\|_{2,\Im_{T}}=
\mathop{\mathrm{max}}\limits_{0\leq t\leq
T}\left\|u(\cdot,t)\right\|_{L_{2}(\Im)^n}+\left\|\frac{\partial
u}{\partial x}\right\|_{L_{2}(\Im_{T})^n};
\end{array} }}
\end{equation}

b) have the trace defined on the sections of the domain $\Im_{T}$
by the plane $t=t_0$ ($t_0\in[0,T]$) as a function of the class
$V^1_0(\Im)$, i.~e., for each element $u\in
\widehat{\Omega}_0(\Im_{T})$ and fixed $t\in [0,T]$ there exists a
sequence $\{u_n\}$ of functions $u_n(x,t)\in V^1_{\,0}(\Im)$
converging to this trace in the norm $\mathcal{H}^1(\Im)$;

c) are continuous in $t$ in the norm $\mathcal{H}^1(\Im)$ on
$[0,T]$, i.~e., for any $t\in[0,T]$, $\|u(\cdot,t+\Delta
t)-u(\cdot,t)\|_{\mathcal{H}^1(\Im)}\rightarrow 0$ as $\Delta t
\rightarrow 0$ uniformly on the interval $[0,T]$.

Designate by $V_{\,\,0}^{1,0}(\Im_{T})$ the closure of the set
$\widehat{\Omega}_0(\Im_{T})$ in norm~(12); in addition,
$W_{\,0}^{1,0}(\Im_{T})$ is the closure of the set
$\widehat{\Omega}_0(\Im_{T})$ in the norm $W^{1,0}(\Im_{T})$ whose
elements possess property (b) only. Clearly,
$V_{\,\,0}^{1,0}(\Im_{T})\subset W_{\,0}^{1,0}(\Im_{T})\subset
W^{1,0}(\Im_{T})$. The space $V_{\,\,0}^{1,0}(\Im_{T})$ is used
below to prove the solvability of problem~(3)--(8), whereas the
spaces $W_{\,0}^{1,0}(\Im_{T})$, $W^{1,0}(\Im_{T})$, and
$W_{\,0}^{1}(\Im_{T})$ play auxiliary roles.

\textbf{Remark 1.} If $Y\in V_{\,\,0}^{1,0}(\Im_{T})$, then $Y=0$
on $\partial\Im$, i.~e., relationships~(5), (6), and (8) should be
treated as the conditions of belonging of $Y$ to the space
$V_{\,\,0}^{1,0}(\Im_{T})$. Equality~(7) is considered almost
everywhere on $\Im$.

\textbf{Remark 2.} The statement of Lemma remains in force for the
functions that are defined in the domain
$\Im_\tau=\Im\times(0,\tau)$ and have traces for any
$t\in(0,\tau)$, where $\tau$ takes any fixed value within the
interval $[0,T]$. The proof of this result is exactly the same.

Remark~2 naturally leads to the following definition of the
solution of problem (3)--(8), where the initial data (i.~e., the
functions $f$ and $Y_0$) satisfy the conditions
\begin{equation}\label{eq37} {{\begin{array}{*{20}c} f(x,t)\in
L_{2,1}(\Im_T),\quad Y_0(x)\in \mathcal{H}(\Im).
\end{array} }}
\end{equation}
Here $L_{2,1}(\Im_T)$ is a space whose elements belong to
$L_1(\Im_T)$ and have the finite norm
$\|f\|_{L_{2,1}(\Im_T)}=\int\limits_0^T(\int\limits_\Im
f^2dx)^{1/2}dt$,~ $\,L_{2}(\Im_T)\subset L_{2,1}(\Im_T)$.

\textbf{Definition.} \emph{A weak solution of the initial boundary
value problem} (3)--(8) \emph{is a pair $\{Y,p\}$ as follows. The
function $Y(x,t)\in V_{\,0}^{1,0}(\Im_{T})$  satisfies the
integral identity}
\begin{equation}\label{eq38}
{{\begin{array}{*{20}c}
(Y(x,t),\eta(x,t))-\int\limits_{\Im_t}Y(x,\tau)\frac{\partial\eta(x,\tau)}{\partial \tau}dxd\tau+\nu\int\limits_0^t\rho(Y,\eta)d\tau=\\
=(Y_0(x),\eta(x,0))+\int\limits_{\Im_t}f(x,\tau)\eta(x,\tau)dxd\tau
\end{array} }}
\end{equation}
\emph{for any $t\in[0,T]$ and any $\eta(x,t)\in
W_{\,0}^{1}(\Im_{T})$, while the function $p(x,t)$ belongs to the
class $\mathfrak{D}'(\Im_T)^n$. Here $\mathfrak{D}'(\Im_T)^n$ is
the conjugate space for the space $\mathfrak{D}(\Im_T)^n$, the
elements of $\mathfrak{D}(\Im_T)^n$ are infinitely differentiable
in $\Im_T$ functions with a compact support from $\Im_T$ $($see
the analogous spaces $\mathfrak{D}(\Im)^n$ and
$\mathfrak{D}'(\Im)^n)$.}

\textbf{Remark 3.} Despite the apparent rigor, the above
definition of a solution of problem~(3)--(8) (i.~e., a pair
$\{Y,p\}$) has the explicit ambiguity caused by the variational
statement~(14) of this problem ``eliminating'' the function
$p(x,t)$. Notably, there is no information concerning the function
$p(x,t)$ except for relationship~(14), and hence \emph{it suffices
to find an appropriate function $p(x,t)$ within the class}, i.~e.,
$p(x,t)\in \mathfrak{D}'(\Im_T)^n$. In terms of applications, this
is an acceptable condition that guarantees the nonzero fluid
dynamics in the domain $\Im_{T}$ (as a matter of fact, in many
applications $p(x,t)$ is an a priori given function). According to
the aforesaid, in the sequel we consider the function $Y(x,t)$ as
a ``solution'' of problem~(3)--(8); the existence of the function
$p(x,t)$ and its belonging to the class $\mathfrak{D}'(\Im_T)^n$
directly follow from the existence of $Y(x,t)$ within the class
$V_{\,0}^{1,0}(\Im_{T})$.

The forthcoming sections are dedicated to the unique weak
solvability of the initial boundary value problem~(3)--(8) and the
optimal control problem of system~(3)--(6). Some considerations
are similar to the ones presented in~[1, p. 77] and [3--5].

\textbf{3. Unique weak solvability of problem (3)--(8).} The idea
to prove the existence of a unique weak solution of
problem~(3)--(8) remains the same as in~[3--5] for similar
distributed parameter problems on a geometrical graph (network),
but there is an essential difference that forms the main obstacle.
In particular, the domain of variation of the spatial variable in
problem~(3)--(8) is the bounded domain $\Im$ of the Euclidean
space $\mathbb{R}^n$, i.~e., the spatial variable and the function
$Y(x,t)$ are both \emph{vectors}. This feature causes additional
technical difficulties, mostly affecting the structure and
properties of the spaces that are selected to describe the weak
solutions of problem~(3)--(8).

Prior to proving the existence of a weak solution of the initial
boundary value problem~(3)--(8), in the domain $\Im$ consider the
spectral problem
\[
{{\begin{array}{*{20}c} -\nu\triangle U= \lambda U,\quad
U|_{\partial\Im}=0,
 \end{array} }}
\]
by analogy to its counterpart on a graph~[7]. This problem is to
find the set of numbers $\lambda$ each associated with at least
one nontrivial solution $U(x)\in V_{\,0}^{1}(\Im)$ satisfying the
identity
\[
{{\begin{array}{*{20}c} \nu((U,\eta))= \lambda (U,\eta)
 \end{array} }}
\]
for any function $\eta(x)\in V_{\,0}^{1}(\Im)$; here
$((\cdot,\cdot))$ denotes the scalar product of the form
\[
{{\begin{array}{*{20}c} ((U,\eta))=\sum\limits_{i=1}^n
(\frac{\partial U}{\partial x_i},\frac{\partial \eta}{\partial
x_i})_{L_2(\Im)^n}.
 \end{array} }}
\]
This means that $U(x)$ is a generalized eigenfunction from the
class $V_{\,0}^{1}(\Im)$ and $\lambda$ is the corresponding
eigenvalue. Then the following properties of the eigenvalues and
generalized eigenfunctions still take place, by analogy with the
ones presented in the paper~[2].

1. \emph{The eigenvalues are real and have finite multiplicities,
and they can be indexed in the ascending order of their magnitudes
taking into account multiplicities, i.~e., $\{\lambda_i\}_{i\geq
1};$ the generalized eigenfunctions are indexed accordingly,
$\{U_i(x)\}_{i\geq 1}$.}

2. \emph{The system of the generalized eigenfunctions
$\{U_i(x)\}_{i\geq 1}$ forms an orthogonal basis in the spaces
$V_{\,0}^{1}(\Im)$ and  $L_2(\Im)^n$.}

\textbf{Remark 4.} These properties remain in force for the
spectral problem, where the boundary condition
$U|_{\partial\Im}=0$ is replaced by the more general one of the
form
\[
{{\begin{array}{*{20}c} \frac{\partial U}{\partial n}+\sigma
U|_{\partial\Im}=0
 \end{array} }}
\]
(each domain $\partial\Im_l\cap\partial\Im$ has a specific
constant $\sigma$, and $\frac{\partial U}{\partial n}$ designates
the derivative along the inner normal inside the domain $\Im$). In
this case, the generalized eigenfunction belongs to the space
$V^{1}(\Im)$ (the definitions of the spaces $V^{1}(\Im)$ and
$V_{\,0}^{1}(\Im)$ differ in the boundary conditions,
$V|_{\partial\Im}=0$ and the above-mentioned general boundary
condition, used in the description of the set $\Omega$) and also
satisfies the identity
\[
{{\begin{array}{*{21}c} \nu((U,\eta))+\sigma
(U,\eta)_{\partial\Im}=\lambda(U,\eta)
\end{array} }}
\]
for any function $\eta(x)\in V^{1}(\Im)$. Here
$(\cdot,\cdot)_{\partial\Im}$ denotes the scalar product~(9) on
$\partial\Im$ and $\lambda$ is an eigenvalue.

\textbf{Theorem 1.} \emph{There exists at least one weak solution
of the initial boundary value problem } (3)--(8) \emph{for
arbitrary finite $T>0$.}

P r o o f.  Use the system of the eigenfunctions
$\{U_i(x)\}_{i\geq1}$ as a basis to represent the approximate
solution $Y_m(x,t)$ in the form
\[
{{\begin{array}{*{20}c} Y_m(x,t)= \sum\limits_{i=1}^m
g_{im}(t)U_i(x)
\end{array} }}
\]
(the scalar functions $g_{im}(t)$ are absolutely continuous on
$[0,T]$) that satisfies the system
\begin{equation}\label{eq39}
{{\begin{array}{*{20}c} (\frac{\partial Y_m}{\partial
t},U_i)+\nu\rho(Y_m,U_i)=(f,U_i),~ \,\,i=\overline{1,m},~
\,\,t\in[0,T],
\end{array} }}
\end{equation}
\begin{equation}\label{eq40}
{{\begin{array}{*{20}c} Y_m(x,0)=Y_{0m}(x),
\end{array} }}
\end{equation}
where $Y_{0m}(x)=\sum\limits_{i=1}^m g^0_{im}U_i(x)$
($g^0_{im}=g_{im}(0))$, $Y_{0m}(x)\rightarrow Y_0(x)$ in the norm
$\mathcal{H}(\Im)$.

System~(15), (16) is a system of differential equations in the
functions $g_{i\,m}(t)$, which allows to find $Y_m$ for any
$t\in[0,T]$. Let us demonstrate this by obtaining the a priori
estimates of the norms of $Y_m$ in $V^{1,0}_{\,\,0}(\Im_T)$.

Multiplication of (15) by $g_{i\,m}(t)$ and summation over
$i=\overline{1,m}$ yield
\begin{equation}\label{eq41}
{{\begin{array}{*{20}c} \frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\rho(Y_m,Y_m)=(f,Y_m).
\end{array} }}
\end{equation}
In expression~(17), the left-hand side is
$\frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\|(Y_m)_x\|^2_{L_2(\Im)^n}$ and the
right-hand side obeys the estimate $(f,Y_m)\leq
\|f\|_{L_2(\Im)^n}\|Y_m\|_{L_2(\Im)^n}$. In combination with~(17),
it follows that
\[
{{\begin{array}{*{20}c} \frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\|(Y_m)_x\|^2_{L_2(\Im)^n}\leq
\|f\|_{L_2(\Im)^n}\|Y_m\|_{L_2(\Im)^n}.
\end{array} }}
\]
And integration over $t$ between $0$ and $t$ gives the inequality
\begin{equation*}%\label{eq42}
{{\begin{array}{*{20}c}
\frac{1}{2}\|Y_m\|^2_{L_2(\Im)^n}+\nu\int\limits_0^t\|(Y_m)_x\|^2_{L_2(\Im_t)^n}d\tau\leq%\\
\end{array} }}
\end{equation*}
\begin{equation}\label{eq42}
{{\begin{array}{*{20}c}
\leq\frac{1}{2}\|Y_m(\cdot,0)\|^2_{L_2(\Im)^n}+\|f\|^2_{L_{2,1}(\Im_t)}\mathop{\mathrm{max}}\limits_{\tau\in[0,
t]}\|Y_m(\cdot,\tau)\|_{L_2(\Im)^n}
\end{array} }}
\end{equation}
for arbitrary $t\in[0,T]$.

Introduce the notation
$z(t)=\mathop{\mathrm{max}}\limits_{\tau\in[0,
t]}\|Y_m(\cdot,\tau)\|_{L_2(\Im)}$ and multiply the both sides of
inequality~(18) by 2 to get
\[
{{\begin{array}{*{20}c} z^2(t)+2\nu\|(Y_m)_x\|^2_{L_2(\Im_t)} \leq
 \|Y_m(\cdot,0)\|_{L_2(\Im)^n}z(t)+2\|f\|^2_{L_{2,1}(\Im_t)}z(t)
\end{array} }}
\]
as long as $\|Y_m(\cdot,0)\|^2_{L_2(\Im)^n}\leq z(t)$. Then
\[
{{\begin{array}{*{20}c} z^2(t)\leq J(t),
\\
\|(Y_m)_x\|^2_{L_2(\Im_t)^n} \leq\frac{1}{2\nu}J(t),
 \end{array} }}
\]
with
$J(t)=\|Y_m(\cdot,0)\|_{L_2(\Im)^n}z(t)+2\|f\|^2_{L_{2,1}(\Im_t)^n}z(t)$.
The last two inequalities lead to the estimate
\[
{{\begin{array}{*{20}c}
\|Y_m\|_{2,\Im_t}=z(t)+\|(Y_m)_x\|_{L_2(\Im_t)^n} \leq (1+ \frac{1}{\sqrt{2\nu}})J^{1/2}(t)\leq \\
\leq (1+
\frac{1}{\sqrt{2\nu}})\left(\|Y_m(\cdot,0)\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right)^{1/2}\|Y_m\|^{1/2}_{2,\Im_t}
 \end{array} }}
\]
or, for any $t\in[0,T]$,
\begin{equation}\label{eq43}
{{\begin{array}{*{20}c} \|Y_m\|_{2,\Im_t}\leq
(1+\frac{1}{\sqrt{2\nu}})^2\left(\|Y_m(\cdot,0)\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right).
 \end{array} }}
\end{equation}

\newpage

Taking into consideration formula~(19), the expansion
$Y_{0\,m}(x)=\sum\limits_{i=1}^m g^0_{i\,m}U_i(x)$, as the
convergence $Y_{0\,m}(x)\rightarrow Y_0(x)$ in the norm
$\mathcal{H}(\Im)$, we have $\|Y_m(\cdot,0)\|_{L_2(\Im)^n}\leq
c\|Y_0\|_{L_2(\Im)^n}$ (where $c>0$ is a constant independent of
$m$) and, using~(19), the estimate
\begin{equation}\label{eq44}
{{\begin{array}{*{20}c} \|Y_m\|_{2,\Im_t}\leq
(1+\frac{1}{\sqrt{2\nu}})^2\left(c\|Y_0\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right)\leq
\\
\leq C^*\left(\|Y_0\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right),
\end{array} }}
\end{equation}
where $C^*>0$ is a constant independent of $m$. The resulting
estimate~(20) plays a dual role:

1) for any index $m$, the norms of the approximate solutions
$Y_m(x,t)$ and their generalized derivatives $\frac{\partial
Y_m(x,t)}{\partial x}$ in the space $\mathcal{H}(\Im)$ are bounded
by a constant $C$ that is independent of $m$, i.~e.,
%\[
%{{\begin{array}{*{20}c}
$\|Y_m\|_{L_2(\Im)^n}\leq C,~ \,\,
\|\frac{\partial Y_m(\cdot,t)}{\partial x}\|_{L_2(\Im)^n}\leq C;$
%\end{array} }}
%\]

2) for any index $m$, the norms of the approximate solutions
$Y_m(x,t)$ are estimated by the norms of the initial data $Y_0(x)$
and $f(x,t)$ of the initial boundary value
problem~(3)--(8).\linebreak %
\indent With this in mind, employ the following well-known result
for a sequence $\{Y_m\}_{m\geq1}$ with the collectively bounded
norms of elements, see~[7, p.~31]. In a sequence
$\{Y_m\}_{m\geq1}$, it is possible to separate a subsequence
$\left\{Y_{m_k}\right\}_{k\geq1}$ that weakly converges in
norm~(12)\linebreak to a certain element $Y\in
V_{\,\,0}^{1,0}(\Im_{T})$ (in fact,
$\left\{Y_{m_k}\right\}_{k\geq1}$ weakly converges to $Y$ in the
norm $L_2(\Im_T)^n$ together with $\frac{\partial
Y_{m_k}}{\partial x}$). Show that the element $Y(x,t)$ is a
solution of prob-\linebreak lem~(3)--(8).%\linebreak %
%\indent

Multiply expression~(15) by an absolutely continuous on $[0,T]$
function $d_i(t)$, perform summation over $i=\overline{1,m}$ and
integrate the result over $t$ between $0$ and $t$:
\begin{equation}\label{eq46}
{{\begin{array}{*{20}c}
(Y_m(x,t),\Phi_m(x,t))-\int\limits_{\Im_t}Y_m(x,\tau)\frac{\partial\Phi_m(x,\tau)}{\partial
\tau}dxd\tau+\nu\int\limits_0^t\rho(Y_m,\Phi_m)d\tau=
\\
=(Y_0(x),\Phi_m(x,0))+\int\limits_{\Im_t}f(x,\tau)\Phi_m(x,\tau)dxd\tau,
\end{array} }}
\end{equation}
where $\Phi_m(x,t)=\sum\limits_{i=1}^md_i(t)U_i(x)$.

Denote by $\Sigma$ the set of all functions $\Phi_m(x,t)$ with
arbitrary $d_i(t)$ possessing the above properties and with
arbitrary natural indexes $m$. The set $\Sigma$ is dense in
$W_{\,0}^{1}(\Im_{T})$. This follows from the density of the set
$\{U_i(x)\}_{i\geq 1}$ in $V^1_{\,0}(\Im)$, the continuity of
$\Phi_m(x,t)$ in $t$ in the norm $\mathcal{H}^1(\Im)$ on $[0,T]$,
the belonging $\Phi_m(x,t)\in V^1_{\,0}(\Im)$ for each fixed
$t\in[0,T]$, and the definition of the space $W^1_{\,0}(\Im_T)$.

In~(21), fix the function $\Phi_m(x,t)=\Phi_{m^*}^*(x,t)\in
\Sigma$, i.~e.,
\[
{{\begin{array}{*{20}c}
\Phi_{m^*}^*(x,t)=\sum\limits_{i=1}^{m^*}d^*_i(t)U_i(x),
\end{array} }}
\]
and, starting from index $m_k\geq m^*$, pass to the limit in the
above subsequence $\left\{Y_{m_k}\right\}_{k\geq1}$, observing
that the integral $\int\limits_0^t\rho(Y_{m_k},\Phi_{m^*}^*)d\tau$
converges to $\int\limits_0^t\rho(Y,\Phi_{m^*}^*)d\tau$ by Lemma.
Passage to the limit yields formula~(21) for the limiting function
$Y(x,t)$, and hence for $\eta(x,t)=\Phi_{m^*}^*(x,t)$ the function
$Y(x,t)$ is a weak solution of the initial boundary value
problem~(3)--(8) from $V_{\,\,0}^{1,0}(\Im_{T})$ due to the
density of the set $\Sigma$ in $W_{\,0}^{1}(\Im_{T})$.

To complete the proof, it remains to argue the existence of a
function $p(x,t)\in \mathfrak{D}'(\Im_T)^n$. Here the line or
reasoning is as follows. The obtained function $Y(x,t)$ as a weak
solution of problem~(3)--(8) satisfies identity~(14) for $t=T$;
therefore, by choosing\linebreak\newpage\noindent formally
$\frac{\partial Y}{\partial t}-\nu\triangle
Y+\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial x_i}- f=F$, we
have $(F,\eta)=0$ for any element $\eta \in \mathfrak{D}(\Im_T)^n$
due to~(13) and (14) (recall that $\mathfrak{D}(\Im_T)^n$ is dense
in $W_{\,0}^{1}(\Im_{T})$, which means the belonging of $F$ to the
space $\mathfrak{D}'(\Im_T)^n$). Moreover, this element has the
representation $F=-\mathrm{grad}\,p$, where the function $p(x,t)$
is a certain element of the space $\mathfrak{D}'(\Im_T)^n$. The
proof of Theorem~1 is finished.

\textbf{Remark 5.} The proof of this theorem contains a deeper
statement regarding a weak solution $Y(x,t)$: the function
$Y(x,t)$ has the derivative $\frac{\partial Y(x,t)}{\partial t}$
with respect to the variable $t$ that belongs to the class
$L_{2}(0,T;V^1_{\,0}(\Im))$, which follows from the representation
of the elements $Y_{m_k}(x,t)$ of the subsequence
$\left\{Y_{m_k}\right\}_{k\geq1}$ for the limiting function
$Y(x,t)$.

Now, show that problem~(3)--(8) does not have two different
solutions from the class $V_{\,0}^{1,0}(\Im_{T})$. Assume that
there exist two such solutions, $Y_1(x,t)$ and $Y_2(x,t)$. Then
their difference $Y(x,t)=Y_1(x,t)-Y_2(x,t)$ is a weak solution of
problem~(3)--(8) ($f(x,t)=0$, $Y_0(x)=0$) from the class
$V_{\,0}^{1,0}(\Im_{T})$. The solution $Y(x,t)$ as the limiting
element of the sequence $Y_m(x,t)$ satisfies the same estimate as
(20) with the zero right-hand side (see the proof of Theorem~1).
Hence, $Y(x,t)=0$ and the solutions $Y_1(x,t)$ and $Y_2(x,t)$
coincide. In fact, we have established the following result.

\textbf{Theorem 2.} \emph{The initial boundary value problem}
(3)--(8) \emph{has a unique weak solution in the space
$V_{\,0}^{1,0}(\Im_{T})$.}

\textbf{Corollary.} A weak solution of the initial boundary value
problem~(3)--(8)  continuously depends on the initial data
$f(x,t)$ and $Y_0(x)$, which appears from the above-mentioned
estimate~(20). Hence, by Theorems~1 and 2, problem~(3)--(8) is
well-posed in the sense of Hadamard.


\textbf{4. Optimal control problem}. Next, we study two types of
optimal control problems that are common in applications, namely,
distributed control and starting control (with terminal
observations). In the former case, control action appears in the
right-hand side of the Navier---Stokes system (i.~e., defines the
density of external forces); in the latter case, it defines the
initial condition of the system at $t=0$. In both cases, the
physical problem is to speed up an incompressible viscous
multiphase medium to a given vector velocity field by a given
(terminal) time $t=T$.

Consider a given Hilbert space $\mathbb{U}$ of control actions
$\upsilon(x,t)$ and a given space $V_{\,0}^{1,0}(\Im_{T})$ of the
states $Y(\upsilon)$ of the Navier---Stokes system. Note that the
choice of the state space affects the choice of the control space
(and vice versa); in this connection, for optimal distributed and
starting control problems we believe that $\mathbb{U}$ is a
subspace of $L_{2}(\Im_T)^n$ and $L_{2}(\Im)^n$, respectively. In
both cases, system observations are performed on the domain
$\Im_T$ at terminal time $t=T$ (other types of observations,
e.~g., boundary ones are also possible). Let $C: L_2(\Im_{T})^n
\rightarrow H$ be a linear continuous operator (the observation
operator), with $H$ indicating the space of observations (here and
in the sequel, $H=L_{2}(\Im)^n$ and observations are perfect in
the sense of no noises), i.~e., $CY(\upsilon)=DY(\upsilon)(x,T)$,
where $D: H\rightarrow H$ is a linear bounded operator. On a
closed convex set $\mathbb{U}_\partial$ of the space $\mathbb{U}$,
introduce an objective function $J(\upsilon)$ defined by two
operators, namely, the transition operator from the control action
$\upsilon$ to the state $Y(\upsilon)$ and the transition operator
from the state $Y(\upsilon)$ to the observation $CY(\upsilon)$,
i.~e.,
\begin{equation}\label{eq22}
{{\begin{array}{*{20}c}
J(\upsilon)=\|CY(\upsilon)-z_0\|^2_H+(N\upsilon,\upsilon)_{\mathbb{U}}=
\|DY(\upsilon)(x,T)-z_0\|^2_H+(N\upsilon,\upsilon)_{\mathbb{U}},
 \end{array} }}
\end{equation}

\noindent where $z_0(x,t)\in L_{2}(\Im_T)^n$ is a given
observation; $N: \mathbb{U} \rightarrow \mathbb{U}$ denotes a
linear continuous Hermitean operator;
$(N\upsilon,\upsilon)_{\mathbb{U}}\geq
\varsigma\|\upsilon\|_{\mathbb{U}}$ ($\varsigma>0$ specifies a
fixed constant). The term $(N\upsilon,\upsilon)_{\mathbb{U}}$ in
the representation of the objective function $J(\upsilon)$
guarantees the coercivity of the quadratic component of the
objective function $J(v)$ (see~[1, p. 13]).

\emph{The optimal distributed (or starting) control problem for
the Navier---Stokes system} \emph{is to find}
$\mathop{\mathrm{inf}}\limits_{v\in  \mathbb{U}_\partial}J(v).$
\emph{An element $u\in \mathbb{U_\partial}$ is called an optimal
control action of the system} \emph{if it minimizes the objective
function $J(v)$ on the set $\mathbb{U}_\partial$.}

\textbf{Distributed control.} Consider a given linear bounded
operator $B: \mathbb{U}\rightarrow L_{2,1}(\Im_T)$. Then
equation~(3) takes the form
\begin{equation}\label{eq23}
{{\begin{array}{*{20}c} \frac{\partial Y}{\partial t}-\nu\triangle
Y+\nabla p= f+B\upsilon;
 \end{array} }}
\end{equation}
the state $\{Y(\upsilon)(x,t), p(\upsilon)(x,t)\}$ of system~(23),
(4)--(6) is defined by a weak solution of the initial boundary
value problem~(22), (4)--(8). Its well-posedness in the sense of
Hadamard follows from the results of Section~3. The state
$Y(\upsilon)$ has continuous dependence on the control action
$\upsilon$ (as the mapping $\upsilon\rightarrow Y(\upsilon)$ is
continuous). Therefore, it is possible to use the minimization
methods of positive definite quadratic forms defined on a closed
convex set of a Hilbert space~[1, Ch.~I] (in addition, see~[8,
Ch.~I] and~[3, 4]). Further analysis is similar to the papers~[3,
4], which explored the issues of optimal control design for
distributed parameter systems on a graph (network).

For system~(23), or (4)--(6), define the conjugate state
$\omega(\upsilon)(x,t)\in W_{\,0}^{1}(\Im_{T})$,
$\omega(\upsilon)(x,T)=D^*(DY(T;\upsilon)-z_0)$ ($D^*$ is the
conjugate operator for $D$), as the function satisfying the
integral identity
\[
{{\begin{array}{*{20}c}
-\int\limits_{\Im_T}\frac{\partial\omega(\upsilon)(x,\tau)}{\partial
\tau}\eta(x,\tau)dxd\tau+
\nu\int\limits_0^T\rho(\omega(\upsilon),\eta)d\tau=0
\end{array} }}
\]
for any functions $\eta(x,t)\in W^{1,0}_{\,\,0}(\Im_T)$ (as a
matter of fact, this is a variational statement that
``eliminates'' the function $p(x,t)$ and has obvious analogy with
(14)). To prove the existence of a unique weak solution
$\omega(\upsilon)$, it suffices to apply Theorem~1, where $t$ is
replaced by $T-t$.

Under the above conditions, we arrive at the following result,
which is similar to Theorem~5 from~[3].

\textbf{Theorem 3.} \emph{ For an element
$u(x,t)\in\mathbb{U}_\partial$ to be an optimal distributed
control action of system} (23), (4)--(6), \emph{a necessary and
sufficient condition is the following relationships}:

\[
{{\begin{array}{*{20}c}
(Y(u)(x,t),\eta(x,t))-\int\limits_{\Im_t}Y(u)(x,\tau)\frac{\partial\eta(x,\tau)}{\partial
\tau}dxd\tau+ \nu\int\limits_0^t\rho(Y(u),\eta)d\tau=
\\
=(Y_0(x),\eta(x,0))+\int\limits_{\Im_t}(f(x,\tau)+Bu(x,\tau))\eta(x,\tau)dxd\tau
\end{array} }}
\]
\emph{for any $t\in[0,T]$ and any $\eta(x,t)\in
W_{\,0}^{1}(\Im_{T});$}
\[
{{\begin{array}{*{20}c}
-\int\limits_{\Im_T}\frac{\partial\omega(u)(x,\tau)}{\partial
\tau}\eta(x,\tau)dxd\tau+
\nu\int\limits_0^T\rho(\omega(u),\eta)d\tau=0
\end{array} }}
\]
{\it for any} $\eta(x,t)\in W^{1,0}_{\,0}(\Im_T)$;
\begin{equation}\label{eq29}
{{\begin{array}{*{20}c}
\int\limits_{\Im_{T}}\left(\omega(u)(x,t)+Nu(x,t)\right)
\left(v(x,t)-u(x,t)\right)dxdt\geq 0
\end{array} }}
\end{equation}
\emph{for any} $v\in \mathbb{U}_\partial$.

\emph{Here} $Y(u)\in V^{1,0}_{\,\,0}(\Im_{T})$,~  $\omega(u)\in
W_{\,0}^{1}(\Im_{T}), $ \emph{and}
$\omega(u)(x,T)=D^*[DY(T;u)-z_0]$,~ $x\in\Im$.\newpage

\textbf{Remark 6.} A version of distributed control is the case of
set point control of system~(3)--(6), which plays an important
role for applications. The right-hand side $f$ in~(3) is replaced
by $\sum\limits_{j=1}^m\upsilon_j(t)\otimes \delta(x-x_j)$, where
$\upsilon(t)=\{\upsilon_1(t),\upsilon_2(t),...,\upsilon_m(t)\}\in
L_2(0,T)^m$ and $x_j\in\bigcup\limits_k \Im_k$. This setting means
that point control actions are applied at fixed points of the
domain $\Im$.

The state $Y(\upsilon)$ is defined in the variational statement as
an element of the space $V^{1,0}_{\,\,0}(\Im_{T})$ that satisfies
the integral identity
\[
{{\begin{array}{*{20}c}
(Y(\upsilon)(x,t),\zeta(x,t))-\int\limits_{\Im_t}Y(\upsilon)(x,\tau)\frac{\partial\zeta(x,\tau)}{\partial \tau}dxd\tau+\nu\int\limits_0^t\rho(Y(\upsilon),\zeta)d\tau=\\
=(Y_0(x),\zeta(x,0))+\int\limits_{\Im_t}f(x,\tau)\zeta(x,\tau)dxd\tau+\sum\limits_{j=1}^m\int\limits_0^t\upsilon_j(\tau)\zeta(x_j,\tau)d\tau
\end{array} }}
\]
for any $t\in[0,T]$ and any $\zeta(x,t)\in
{W}_{\,0}^{2,1}(\Im_{T})$. Here ${W}_{\,0}^{2,1}(\Im_{T})$ is the
closure of the elements of $\widetilde{\mathfrak{D}}(\Im_T)^n$ in
the norm of the space $H^{2,1}(\Im_{T})=\{g:\,g,\frac{\partial
g}{\partial x_j},\frac{\partial^2 g}{\partial x_i\partial x_j},
\frac{\partial g}{\partial t}\in L_2(\Im_{T})^n\}$ (see the
properties of $H^{2,1}(\Im_{T})$ in~[1, p.~126]). If the boundary
$\partial\Im_{T}$ of the domain $\Im_{T}$ is sufficiently smooth,
then the conjugate state $\omega(\upsilon)$ represents an element
of the space ${W}_{\,0}^{2,1}(\Im_{T})$ such that
$\omega(\upsilon)(x,T)=0$.


\textbf{Starting control.} Consider another example of control of
system~(3)--(6), which arises in the course of analyzing the
transfer dynamics of multiphase media. A control action
$\upsilon(x)\in \mathbb{U}$ is applied at the initial time,
defining the initial condition~(7) ($Y_0(x)=\upsilon(x)$), i.~e.,
\[
{{\begin{array}{*{20}c} Y(x,0)=\upsilon(x),~ \,x\in \Im.
\end{array} }}
\]

The state $\{Y(\upsilon)(x,t), p(\upsilon)(x,t)\}$ of
system~(3)--(6) is defined by a weak solution $Y(\upsilon)(x,t)$
of the initial boundary value problem~(3)--(6), (8), (24) (in the
integral identity~(14), the function $Y_0(x)$ is replaced by
$\upsilon(x)$) and by an arbitrary function $p(x,t)$ belonging to
the class $\mathfrak{D}'(\Im_T)^n$. Like the case of distributed
control, the well-posedness of problem~(3)--(6), (8), (24) in the
sense of Hadamard follows from the results of Section~3. The
conjugate state $\omega(\upsilon)(x,t)$ of system~(3)--(6) is
defined by the integral identity~(24); in addition,
$\omega(\upsilon)(x,T)=D^*(DY(T;\upsilon)-z_0)$, $x\in\Im$ (the
last equality holds almost everywhere on $\Im$).

Then we have the following statement, which is analogous to
Theorem~7 from~[4].

\textbf{Theorem 4.} \emph{For an element
$u(x)\in\mathbb{U}_\partial$ to be an optimal starting control
action of system}~(3)--(6), \emph{a necessary and sufficient
condition is the relationships}:
\[
{{\begin{array}{*{20}c}
(Y(u)(x,t),\eta(x,t))-\int\limits_{\Im_t}Y(u)(x,\tau)\frac{\partial\eta(x,\tau)}{\partial \tau}dxd\tau+\nu\int\limits_0^t\rho(Y(u),\eta)d\tau=\\
=(u(x),\eta(x,0))+\int\limits_{\Im_t}f(x,\tau)\eta(x,\tau)dxd\tau
\end{array} }}
\]
\emph{for any $t\in[0,T]$ and any $\eta(x,t)\in
W_{\,0}^{1}(\Im_{T});$}
\[
{{\begin{array}{*{20}c}
-\int\limits_{\Im_T}\frac{\partial\omega(u)(x,\tau)}{\partial
\tau}\eta(x,\tau)dxd\tau+
\nu\int\limits_0^T\rho(\omega(u),\eta)d\tau=0
\end{array} }}
\]
\emph{for any functions $\eta(x,t)\in W^{1,0}_{\,\,0}(\Im_T);$}
\newpage\begin{equation}\label{eq29}
{{\begin{array}{*{20}c}
\int\limits_{\Im}\left(\omega(u)(x,0)+Nu(x)\right)
\left(v(x)-u(x)\right)dxdt\geq 0
\end{array} }}
\end{equation}
\emph{for any} $v\in \mathbb{U}_\partial$.

\emph{Here} $Y(u)\in V^{1,0}_{\,\,0}(\Im_{T})$,~  $\omega(u)\in
W_{\,0}^{1}(\Im_{T}),$ \emph{and}
$\omega(u)(x,T)=D^*[DY(T;u)-z_0]$,~ $x\in\Im$.


\textbf{5. Synthesis of optimal control (feedback).} Consider the
optimal control problem without constraints imposed on control
actions, i.~e., $\mathbb{U}_\partial$ coincides with $\mathbb{U}$.
Then it is possible to set $v=u\pm\nu$ in relationships~(24) and
(25). Owing to arbitrary $v\in \mathbb{U}$, these relationships
become equalities and hence the optimal distributed and starting
control actions satisfy the equalities
$$\omega(u)(x,t)+Nu(x,t)=0,~\, \omega(u)(x,0)+Nu(x)=0, $$
$u(x,t)=-N^{-1}\omega(u)(x,t)$, and $u(x)=-N^{-1}\omega(u)(x,0)$.
Consequently, the optimal distri-\linebreak buted control action
is constructed by solving the system of two integral identities
(variational relations):
\begin{equation}\label{eq1}
{{\begin{array}{*{20}c}
\int\limits_{\Gamma}Y(x,t)\eta(x,t) dx-\int\limits_{\Gamma_{t}}Y(x,t)\frac{\partial \eta(x,t)}{\partial t}dxdt+\ell_{t}(Y,\eta)=\\
=\int\limits_{\Gamma}Y_0(x)\eta(x,h)dx+
\int\limits_{\Gamma_{t}}f(x,t)\eta(x,t) dxdt-
\int\limits_{\partial\Gamma_{t}}N^{-1}\omega(x,t)\eta(x,t) dxdt
 \end{array} }}
\end{equation}
for any $t\in[0,T]$ and any function $\eta(x,t)\in
W^{1}_{\,0}(\Gamma_{T})$;
\begin{equation}\label{eq1}
{{\begin{array}{*{20}c}
-\int\limits_{\Im_T}\frac{\partial\omega(u)(x,\tau)}{\partial
\tau}\zeta(x,\tau)dxd\tau+
\nu\int\limits_0^T\rho(\omega(u),\zeta)d\tau=0
\end{array} }}
\end{equation}
for any functions $\zeta(x,t)\in W^{1,0}_{\,\,0}(\Im_T)$. The
optimal distributed control action has the form
\begin{equation}\label{eq1}
u(x,t)=-N^{-1}\omega(x,t).
\end{equation}

To find the optimal starting control action, one has to solve the
system of integral identities that is similar to~(26) and (27), in
which
\begin{equation}\label{eq1}
u(x)=-N^{-1}\omega(x,0).
\end{equation}

Formulas~(28) and (29) realize the synthesis of optimal
distributed and starting control  of systems~(23), (4)--(6) and
(3)--(6), respectively. More specifically, optimal control actions
are defined through conjugate states, which actually implements
the feedback principle by the states of each system.

\textbf{Remark 7.} Under the accepted assumptions, it is possible
to establish deeper results of the synthesis of optimal control,
that generalize the well-known Kalman results for bounded
operators.


\textbf{6. Conclusion.} This paper has considered the applied
problems of distributed and starting control for the linearized
Navier---Stokes system. The optimal control  conditions in terms
of the conjugate states of systems~(23), (4)--(6) and (3)--(6)
have been established, as well as some analogues of the well-known
Kalman results of the finite-dimensional case (formulas~(28) and
(29)) have been obtained. The described algorithm is applicable to
many optimization problems for differential systems whose states
are defined by weak solutions of evolutionary equations on similar
networks as in the papers~[3--5]. Interestingly, other researchers
considered alternative approaches to the stability
analysis~[9--11] and stabilization~[12, 13] of the solutions to
some applications-relevant classes of complex systems, yet with
the same treatment of the optimal control existence conditions.
Also note that the problem under study may have peculiarities in
form of stochastic components~[14] or discontinuous
nonlinearities~[15] in the representation of evolutionary
systems~(3) and~(22).




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%\input{02/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{09/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize




%\thispagestyle{empty}

\vskip 3mm

%\thispagestyle{empty}


\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. А. П.~Жабко.

\vskip 1mm

\noindent Статья поступила в~редакцию 7 октября 2016~г.

\vskip 1mm

\noindent Статья принята к~печати 12 октября 2017~г.

}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vskip 5mm


%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak

%\vskip 3mm

%\textit{Буре Артем Владимирович}~--- аспирант; e-mail:
%bure.artem@gmail.com

%\vskip 2mm

%\emph{Bure Artem Vladimirovich}~--- post-graduate student; e-mail:
%bure.artem@gmail.com

%}
