

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm

1. Lions J.-L. \textit{Some methods of solving non-linear boundary
value problems}. Paris, Dunod-Gauthier-Villars, 1969, 581 p.
(Russ. ed.: Lions J.-L. \textit{Nekotorye metody resheniya
nelineinykh kraevykh zadach}. Moscow, Mir Publ., 1972, 587 p.).

2. Provotorov V.~V., Gnilitskaya Yu.~A. Boundary control of a wave
system in the space of generalized solutions on a graph.
\textit{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2013, iss.~3,
pp.~112--120.

3. Provotorov V.~V. Optimal control of a parabolic system with
distributed parameters on a graph. \textit{Vestnik of Saint
Petersburg University. Series 10. Applied Mathematics. Computer
Science. Control Processes}, 2014, iss.~3, pp.~154--163.

4. Podvalny S.~L., Provotorov V.~V. Starting control of a
parabolic system with distributed parameters on a graph.
\textit{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2015, iss.~3,
pp.~126--142.

5. Podvalny S.~L., Provotorov V.~V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \textit{2015 Intern. Conference ``Stability and
Control Processes'' in memory of V.~I. Zubov (SCP)}, 2015,
pp.~117--119.

6. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407 p. (In Russian).

7. Volkova A.~S., Provotorov V.~V. Generalized solutions and
generalized eigenfunctions of boundary-value problems on a
geometric graph. \textit{Russian Mathematics (Proceeding of Higher
Educational Institutions)}, 2014, vol.~58, no.~3, pp.~1--13.

8. Fursikov A.V. \textit{Optimal'noe upravlenie raspredelennymi
sistemami. Teoriya i prilozheniya} [\textit{Optimal control of
distributed systems. Theory and applications}]. Novosibirsk,
Nauchnaya kniga Publ., 1999, 352~p. (In Russian).

9. Aleksandrov A.~Yu., Zhabko A.~P. On the asymptotic stability of
solutions of nonlinear systems with delay. \textit{Siberian
Mathematical Journal}, 2012, vol.~53, no.~3, pp.~393--403.

10. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \textit{WSEAS Transactions on Systems and
Control}, 2014, vol.~9, pp.~388--397.

11. Aleksandrov A.~Yu., Zhabko A.~P. On stability of the solutions
of a class of nonlinear delay systems. \textit{Autom. Remote
Control}, 2006, vol.~67, no.~9, pp.~1355--1365.

12. Veremey E.~I., Korchanov V.~M. Multiobjective stabilization of
the dynamic systems from a certain class. \textit{Avtomatics and
Telemechanics}, 1988, no.~9, pp.~126--137.

13. Veremey E.~I., Sotnikova M.~V. Plasma stabilization by
prediction with stable linear approximation. \textit{Vestnik of
Saint Petersburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes}, 2011, iss.~1, pp.~116--133.

14. Karelin V.~V. Penalty functions in the control problem of an
observation process. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss.~4, pp.~109--114.

15. Kamachkin A.~M., Yevstafyeva V.~V. Oscillations in a relay
control system at an external disturbance. \textit{Control
Applications of Optimization 2000. Proceedings of the 11th IFAC
Workshop}, 2000, vol.~2, pp.~459--462.






\vskip 3mm

{\bf For citation:}   Provotorov V. V., Provotorova E. N. Optimal
control of the linearized Navier---Stokes system in a netlike
domain. {\it Vestnik of Saint Petersburg University. Applied
Mathematics. Com-\linebreak puter Science. Control Processes},
\issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p9}--\pageref{p9e}. \doivyp/
spbu10.\issueyear.\issuenum09


}
