

{\footnotesize

\vskip 2mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 1.5mm



{1}. {Chaumette F., Hutchinson S. } Visual Servo Control: Basic
Approaches. {\it  IEEE Robotics}  \& {\it Automation Magazine},
2006, vol.~13, no.~4, pp.~82--90.

{2}. {Cherubini A., Chaumette F., Oriolo G.} An image-based visual
servoing scheme for following paths with nonholonomic mobile
robots. {\it Intern. Conference on Control, Automation, Robotics
and Vision }({\it ICARCV-2008}). Hanoi, Vietnam, France, 2008,
pp.~108--113.

{3}. {Mariottini G. L., Oriolo G., Prattichizzo D.} Image-Based
Visual Servoing for Nonholonomic Mobile Robots Using Epipolar
Geometry. {\it IEEE Trans. on Robotics}, 2007, vol.~23, no.~1,
pp.~87--100.

{4}. {Hashimoto K., Noritsugu T.} Visual servoing of nonholonomic
cart. {\it IEEE Intern. Conference on Robotics and Automation}.
Albuquerque, NM, USA, 1997, pp.~1719--1724.

{5}. {Veremey E. I., Sotnikova M. V.} Mnogotzelevaja structura
zakonov upravlenija morskimi podvizhnimi ob'ektami [Multipurpose
structure of control laws for marine ships]. {\it Trudy
XII~Vseros. soveshchaniia po~problemam upravleniia
$($VSPU-2014$)$} [{\it Transactions of XII~Russ. Conference of
cont-\linebreak rol problems $($VSPU-2014$)$}]. Moscow, 2014, June
16--19. Moscow, Trapeznikov Institute of control problems RAS,
2014, pp.~3289--3300. (In Russian)

{6}. {Szeliski R.} {\it Computer Vision: Algorithms and
Applications}. London, Springer-Verlag, 2011, 812~p.

{7}. {Veremey E. I.} Dynamical Correction of Positioning Control
Laws. {\it Proc. of the 9th IFAC Conferen-\linebreak ce on Control
Applications in Marine Systems }({\it CAMS-2013}). Osaka, Japan,
September 17--20, 2013,\linebreak  pp.~31--36.





}
