
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm


{\footnotesize

1. \textit{Freeman L. C.} A set of measures of centrality based on
betweenness~// Sociometry. 1977. Vol.~40. P.~35--41.

2. \textit{Levin D. A., Peres Y.} Markov chains and mixing times.
Providence, Rhode Island: Amer. Mathematical Soc., 2017. 447~p.

3. \textit{Page L., Brin S., Motwani R., Winograd T.} The PageRank
citation ranking: Bringing order to the web.: technical report.
Stanford: Stanford InfoLab, 1998. 17~p.

4. \textit{Pons P., Latapy M.} Computing communities in large
networks using random walks~// Journal of Graph Algorithms and
Applications. 2006. Vol.~10(2). P.~191--218.

5. \textit{Avrachenkov K. E., Mazalov V. V., Tsynguev B. T.} Beta
current flow centrality for weighted networks~// Proceedings of
CSoNET--2015, LNCS. 2015. Vol.~9197. P.~216--227.

6. \textit{Brandes U., Fleischer D.} Centrality measures based on
current flow~// Proceedings of the 22nd annual conference on
Theoretical Aspects of Computer Science. 2005. P.~533--544.

7. \textit{Mazalov V., Tsynguev B.} Kirchhoff centrality measure
for collaboration network~// CSoNet--2016. LNCS, 2016. Vol.~9795.
P.~147--157.

8. \textit{Bogomolnaia A., Jackson M. O.} The stability of hedonic
coalition structures~// Games and Economic Behavior. 2002.
Vol.~38(2). P.~201--230.

9. \textit{Mazalov V. V., Avrachenkov K. E., Trukhina L. I.,
Tsynguev B. T.} Game-theoretic centrality measures for weighted
graphs~// Fundamenta Informaticae. 2016. Vol.~145(3). P.~341--358.

10. \textit{Fortunato S., Barthelemy M.} Resolution limit in
community detection~// Proceedings of the National Academy of
Sciences USA. 2007. Vol.~104(1). P.~36--41.

11. \textit{Girvan M., Newman M.\,E.\,J.} Community structure in
social and biological networks~// Proceedings of the National
Academy of Sciences USA. 2002. Vol.~99(12). P.~7821--7826.

12. \textit{Fortunato S.} Community detection in graphs~// Physics
Reports. 2010. Vol.~486(3). P.~75--174.

13. \textit{Zachary W. W.} An information flow model for conflict
and fission in small groups~// Journal of Anthropological
Research. 1977. Vol.~33(4). P.~452--473.

14. \textit{Jackson M. O.} Social and economic networks.
Princeton: Princeton University Press, 2010. 520~p.

15. \textit{Kaur R., Singh S.} A survey of data mining and social
network analysis based anomaly detection techniques~// Egypt Inf.
Journal. 2016. Vol.~17(2). P.~199--216.

16. \textit{Newman M. E., Girvan M.} Finding and evaluating
community structure in networks~// Physical Review E. 2004.
Vol.~69(2). P.~026113.

17. \textit{Meila M., Shi J.} A Random walks view of spectral
segmentation~// Proceedings of AISTATS. 2001. P.~1--6.

18. \textit{Myerson R. B.} Graphs and cooperation in games~//
Math. Oper. Res. 1977. Vol.~2. P.~225--229.

19. \textit{Avrachenkov K., Kondratev A., Mazalov V.} Cooperative
Game Theory approaches for network partitioning~// Computing and
Combinatorics / eds.: Y. Cao, J. Chen. COCOON. 2017. LNCS. 2017.
Vol.~10392. P.~591--603.

20. \textit{Copic J., Jackson M., Kirman A.} Identifying community
structures from network data via maximum likelihood methods~// The
B. E. Journal of Theoretical Economics. 2009. Vol.~9, iss.~1.
\mbox{P.~1635--1704.}

21. Wolfram Research, Inc. (www.wolfram.com). Mathematica Online.
Champaign, IL., 2018.

22. \textit{Vinh N. X., Epps J., Bailey J.} Information theoretic
measures for clusterings comparison: Variants, properties,
normalization and correction for chance~// Journal of Machine
Learning Research. 2010. Vol.~11. P.~2837--2854.

23. \textit{Kvalseth T. O.} Entropy and correlation: Some comments
// Systems, Man and Cybernetics, IEEE Transactions on. 1987. Vol.~17(3). P.~517--519.

24. \textit{Strehl A., Ghosh J.} Cluster ensembles -- a knowledge
reuse framework for combining multiple partitions~// Journal of
Machine Learning Research. 2002. Vol.~3. P.~583--617.

25. \textit{Hubert L., Arabie P.} Comparing partitions~// Journal
of Classification. 1985. Vol.~2(1). \mbox{P.~193--218.}

26. \textit{Steinley D.} Properties of the Hubert-Arabie adjusted
Rand index~// Psychol. Methods. 2004. Vol.~9(3). P.~386--396.

27. \textit{Lusseau D., Schneider K., Boisseau O. J.} et al. The
bottlenose dolphin community of Doubtful Sound features a large
proportion of long-lasting associations~// Behav. Ecol. Sociobiol.
2003. Vol.~54. P.~396--405.



\vskip 1.5mm


%\noindent Статья рекомендована к~печати проф. Н. В. Егоровым.

%\vskip 1.5mm

\noindent Статья поступила в~редакцию 30 мая 2018 г.; принята
к~печати 14 июня 2018~г.


\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Мазалов Владимир Викторович}~--- д-р физ.-мат.
наук, проф.; vmazalov@krc.karelia.ru


\vskip2mm \textit{Никитина Наталия Николаевна}~--- канд. техн.
наук; nikitina@krc.karelia.ru \par}
