

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Beletsky~V.~V. \textit{Dvizheniye iskusstvennogo sputnika
otnositel'no tsentra mass} [\textit{Motion of the satellite around
its center of mass}]. Moscow, Nauka Publ., 1965, 416~p. (In
Russian)

2.  Beletsky~V.~V. \textit{Dvizheniye sputnika otnositel'no
tsentra mass v gravitatsionnom pole} [\textit{Motion of the
satellite around its center of mass in a gravitational field}].
Moscow, Moscow State University Publ., 1975, 308~p. (In Russian)

3. Markeev~A.~P. \textit{Tochki libracii v nebesnoi mehanike i
kosmodinamike} [\textit{Libration points in celestial mechanics
and cosmodynamics}]. Moscow, Nauka Publ., 1978, 312~p. (In
Russian)

4. Shmyrov~V.~A. Stabilizacija upravljaemogo orbital'nogo
dvigenija kosmicheskogo apparata v okrestnosti kollinearnoj tochki
libracii $L_1$ [Stabilization of the orbital motion of the
spacecraft in the neighborhood of the collinear libration points
$L_1$]. \textit{Vestnik of Saint Petersburg University. Series~10.
Applied Mathematics. Computer Science. Control Processes}, 2005,
iss.~2, pp.~193--199. (In Russian)

5. Shymanchuk~D.~V. Modelirovanie orbital'nogo upravljaemogo
dvizhenija kosmicheskogo apparata v okrestnosti kollinearnoj
tochki libracii $L_1$ [Modelling orbital controlled motion of a
spacecraft in the neighborhood of the collinear libration point
$L_1$]. \textit{Vestnik of Saint Petersburg University. Series~10.
Applied Mathematics. Computer Science. Control Processes}, 2009,
iss.~3, pp.~86--92. (In Russian)

6. Shmyrov~A., Shymanchuk~D. Maneuvering in near-Earth space with
the use of the collinear libration points. \textit{Intern.
conference on Mechanics --- Seventh Polyakhov's Reading}, 2015,
art. no.~7106777, pp.~1--5.

7. Shmyrov~A., Shymanchuk~D., Sokolov~L. The interception problem
of a celestial body with the use of the collinear libration
points. \textit{Intern. conference on ``Stability and Control
Processes'' in memory of V.~I.~Zubov $($SCP$)$: Proceedings}.
Saint Petersburg, IEEE, 2015, art. no.~7342068, pp.~129--131.

8. Kane~T.~R., Marsh~E.~L. Attitude stability of a symmetric
satellite at the equilibrium points in the restricted three-body
problem. \textit{Celestial Mechanics}, 1971, vol.~4, pp.~78--90.

9. Guzzetti~D., Howell~K.~C. Natural periodic orbit-attitude
behaviors for rigid bodies in three-body periodic orbits.
\textit{Acta Astronautica}, 2017, vol.~130, pp.~97--113.

10. Markeev~A.~P. \textit{Teoreticheskaya mekhanika}
[\textit{Theoretical Mechanics}].  Moscow, Nauka Publ., 1990,
416~p. (In Russian)

11. Branets~V.~N., Shmyglevskiy~I.~P. \textit{Primeneniye
kvaternionov v zadachakh oriyentatsii tverdogo tela} [\textit{The
use of quaternions in problems of the rigid body orientation}].
Moscow, Nauka Publ., 1973, 320~p. (In Russian)

12. Golubev~Y.~F. Algebra kvaternionov v kinematike tverdogo tela
[Quaternion algebra in rigid body kinematics]. \textit{Preprints
of Keldysh Institute of applied mathematics}, 2013, no.~39, 23~p.
Available at: http://library.keldysh.ru/preprint.asp?id=2013-39
(accessed: 27.09.2016).

13. Shymanchuk~D.~V., Shmyrov~A.~S. Postroenie traektorii
vozvrashhenija v okrestnost' kollinearnoj tochki libracii sistemy
Solnce---Zemlja [Construction of the trajectory of the return in
the neighborhood of the collinear libration point of the
Sun---Earth system]. \textit{Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2013, iss.~2, pp.~76--85. (In Russian)

14. Artemieva~N.~A., Bakanas~E.~S., Barabanov~S.~I.,
Vityazev~A.~V., Volkov~V.~A., Glazachev~D.~O., Degtyar'~V.~G.,
Yemel'yanenko~V.~V., Ivanov~B.~A., Kochetova~O.~M.,
Kulikova~N.~V., Medvedev~Y.~D., Naroyenkov~S.~A., Nemchinov~I.~V.,
Pechernikova~G.~V., Pol'~V.~G., Popova~O.~P., Rykhlova~L.~V.,
Svettsov~V.~V., Simonov~A.~V., Sokolov~L.~L., Timerbayev~R.~M.,
Chernetenko~Y.~A., Shor~V.~A., Shuvalov~V.~V.,
Shustov~B.~M.\textit{ Asteroidno-kometnaya opasnost': vchera,
segodnya, zavtra} [\textit{Asteroid-comet hazard: yesterday, today
and tomorrow}]. Moscow, Fizmatlit Publ., 2013, 384~p. (In Russian)





\vskip 2mm

{\bf For citation:}  Shymanchuk D.~V. Modeling of controlled
coupled attitude-orbit motion in the neighborhood of collinear
libration point $L_1$. {\it Vestnik of Saint Petersburg
University. Applied Mathe-\linebreak matics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}. \doivyp/
spbu10.\issueyear.\issuenum03



}
