

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

%1.~\textit{Гладких~И.~В., Светланова Ж.~В.}
%Измерение значимости характеристик товара в маркетинговых исследованиях //
%Вестн. С.-Петерб. ун-та. Сер.~8. Менеджмент. 2006. Вып.~2. С.~65--87.

1.~Gladkikh~I.~V., Svetlanova~Zh.~V. Izmerenie znachimosti
kharakteristik tovara v marketingovykh issledovaniyakh [The
measurement of product characteristics importance in marketing
research]. \textit{Vestnik of Saint Petersburg University. Series
8. Management}, 2006, issue 2, pp.~65--87. (In Russian)

%2.~\textit{Thurstone~L.~L.}
%A law of comparative judgment //
%Psychological Review. 1927. Vol.~34, N~4. P.~273--286.
%DOI:10.1037/h0070288

2.~Thurstone~L.~L. A law of comparative judgment.
\textit{Psychological Review}, 1927, vol.~34, no.~4, pp.~273--286.
DOI:10.1037/h0070288

%3.~\textit{Дэвид~Г.}
%Метод парных сравнений / пер. с англ. Н.~Космарской, Д.~Шмерлинга; под ред. Ю.~Адлера.
%М.: Статистика, 1978. 144~с.
%(David~H.~A. The method of paired comparisons. Vol.~12 of Griffin’s Statistical Monographs and Courses. London: Griffin, 1963. 124~p.)

3.~David~H.~A. \textit{The method of paired comparisons}.  London,
Griffin, 1963, 124~p. (Vol.~12 of Griffin’s Statistical Monographs
and Courses.) (Russ. ed.: David~G. \textit{Metod parnykh
sravnenij}. Moscow, Statistika Publ., 1978, 144~p.)

%4.~\textit{Саати~Т.}
%Принятие решений. Метод анализа иерархий / пер. с англ. Р.~Г.~Вачнадзе.
%М.: Радио и связь, 1993. 315~с.
%(Saaty~T.~L. The analytic hierarchy process: planning, priority setting, resource allocation. New York: McGraw-Hill, 1980. 281~p.)

4.~Saaty~T.~L. \textit{The analytic hierarchy process: planning,
priority setting, resource allocation}. New York, McGraw-Hill,
1980, 281~p. (Russ. ed.: Saaty~T. \textit{Prinyatie reshenij.
Metod analiza ierarkhij}. Moscow, Radio i svyaz', 1993, 315~p.)

%5.~\textit{Ногин~В.~Д.}
%Упрощенный вариант метода анализа иерархий на основе нелинейной свертки критериев //
%Журн. вычисл. математики и матем. физ. 2004. Т.~44, \textnumero7. С.~1261--1270.

5.~Nogin~V.~D. Uproshhennyj variant metoda analiza ierarkhij na
osnove nelinejnoj svertki kriteriev [A~simplified variant of a
method for the analysis of hierarchies, based on a nonlinear
convolution of criteria]. \textit{Zhurnal Vychislitel'noi
Matematiki i Matematicheskoi Fiziki} [\textit{Journal of
Computational Mathematics and Mathematical Physics}], 2004,
vol.~44, no.~7, pp.~1261--1270. (In Russian)

%6.~\textit{Saaty~T.~L., Vargas~L.~G.}
%Comparison of eigenvalue, logarithmic least squares and least squares methods in estimating ratios //
%Math. Modelling. 1984. Vol.~5, N~5. P.~309--324.
%DOI:10.1016/0270-0255(84)90008-3

6.~Saaty~T.~L., Vargas~L.~G. Comparison of eigenvalue, logarithmic
least squares and least squares methods in estimating ratios.
\textit{Math. Modelling}, 1984, vol.~5, no.~5, pp.~309--324.
DOI:10.1016/0270-0255(84)90008-3

%7.~\textit{Barzilai~J.}
%Deriving weights from pairwise comparison matrices //
%J. Oper. Res. Soc. 1997. Vol.~48, N~12. P.~1226--1232.
%DOI:10.1057/palgrave.jors.2600474

7.~Barzilai~J. Deriving weights from pairwise comparison matrices.
\textit{J. Oper. Res. Soc.}, 1997, vol.~48, no.~12,
pp.~1226--1232. DOI:10.1057/palgrave.jors.2600474

%8.~\textit{Chu~M.~T.}
%On the optimal consistent approximation to pairwise comparison matrices //
%Linear Algebra Appl. 1998. Vol.~272, N~1-3. P.~155--168.
%DOI:10.1016/S0024-3795(97)00329-7

8.~Chu~M.~T. On the optimal consistent approximation to pairwise
comparison matrices. \textit{Linear Algebra Appl.}, 1998,
vol.~272, no.~1--3, pp.~155--168.
DOI:10.1016/S0024-3795(97)00329-7

%9.~\textit{Farkas~A., Lancaster~P., R\'{o}zsa~P.}
%Consistency adjustments for pairwise comparison matrices //
%Numer. Linear Algebra Appl. 2003. Vol.~10, N~8. P.~689--700.
%DOI:10.1002/nla.318

9.~Farkas~A., Lancaster~P., R\'{o}zsa~P. Consistency adjustments
for pairwise comparison matrices. \textit{Numer. Linear Algebra
Appl.}, 2003, vol.~10, no.~8, pp.~689--700. DOI:10.1002/nla.318

%10.~\textit{Elsner~L., van~den~Driessche~P.}
%Max-algebra and pairwise comparison matrices, II //
%Linear Algebra Appl. 2010. Vol.~432, N~4. P.~927--935.
%DOI:10.1016/j.laa.2009.10.005

10.~Elsner~L., van~den~Driessche~P. Max-algebra and pairwise
comparison matrices. II. \textit{Linear Algebra Appl.}, 2010,
vol.~432, no.~4, pp.~927--935. DOI:10.1016/j.laa.2009.10.005

%11.~\textit{Tran~N.~M.}
%Pairwise ranking: Choice of method can produce arbitrarily different rank order //
%Linear Algebra Appl. 2013. Vol.~438, N~3. P.~1012--1024.
%DOI:10.1016/j.laa.2012.08.028

11.~Tran~N.~M. Pairwise ranking: Choice of method can produce
arbitrarily different rank order. \textit{Linear Algebra Appl.},
2013, vol.~438, no.~3, pp.~1012--1024.
DOI:10.1016/j.laa.2012.08.028

%12.~\textit{Gursoy~B.~B., Mason~O., Sergeev~S.}
%The analytic hierarchy process, max algebra and multi-objective optimisation //
%Linear Algebra Appl. 2013. Vol.~438, N~7. P.~2911--2928.
%DOI:10.1016/j.laa.2012.11.020

12.~Gursoy~B.~B., Mason~O., Sergeev~S. The analytic hierarchy
process, max algebra and multi-objective optimisation.
\textit{Linear Algebra Appl.}, 2013, vol.~438, no.~7,
pp.~2911--2928. DOI: 10.1016/j.laa.2012.11.020

%13.~\textit{Маслов~В.~П., Колокольцов~В.~Н.}
%Идемпотентный анализ и его применение в оптимальном управлении. М.: Физматлит, 1994. 144~с.

13.~Maslov~V.~P., Kolokol’tsov~V.~N. \textit{Idempotentnyj analiz
i ego primenenie v optimal'nom upravlenii} [\textit{Idempotent
analysis and its applications in optimal control}]. Moscow,
Fizmatlit Publ., 1994, 144~p. (In Russian)

%14.~\textit{Golan~J.~S.}
%Semirings and affine equations over them. Vol.~556 of Mathematics and Its Applications
%New York: Springer, 2003.
%256~p.

14.~Golan~J.~S. \textit{Semirings and affine equations over them}.
New York, Springer, 2003, 256~p. (Vol.~556 of Mathematics and Its
Applications.)

%15.~\textit{Heidergott~B, Olsder~G.~J., van der Woude~J.}
%Max plus at work. Princeton Series in Applied Mathematics.
%Princeton: Princeton University Press, 2006. 226~p.

15.~Heidergott~B., Olsder~G.~J., van der Woude~J. \textit{Max plus
at work}. Princeton, Princeton University Press, 2006, 226~p.
(Princeton Series in Applied Mathematics.)

%16.~\textit{Кривулин~Н.~К.}
%Методы идемпотентной алгебры в задачах моделирования и анализа сложных систем.
%СПб.: Изд-во С.-Петерб. ун-та, 2009. 256~с.

16.~Krivulin~N.~K. \textit{Metody idempotentnoj algebry v
zadachakh modelirovaniya i analiza slozhnykh sistem}
[\textit{Methods of idempotent algebra for problems in modeling
and analysis of complex systems}]. Saint Petersburg, Saint
Petersburg University Publ., 2009, 256 p. (In Russian)

%17.~\textit{Кривулин~Н.~К., Гладких~И.~В.}
%Методы построения матрицы результатов парных сравнений на основе тропической математики //
%Модели и методы тропической математики в прикладных задачах экономики и управления: сборн. науч. статей / под ред. Н.~К.~Кривулина.
%СПб.: ВВМ, 2013. С.~4--32.

17.~Krivulin~N.~K., Gladkikh~I.~V. Metody postroeniya matritsy
rezul'tatov parnykh sravnenij na osnove tropicheskoj matematiki
[Tropical mathematics-based methods for constructing a consistent
matrix of pairwise comparisons]. \textit{Modeli i metody
tropicheskoj matematiki v prikladnykh zadachakh ehkonomiki i
upravleniya} [\textit{Models and methods of tropical mathematics
with applications to problems in economics and management}]. Saint
Petersburg, VVM Publ., 2013, pp.~4--32. (In Russian)

%18.~\textit{Кривулин~Н.~К., Гладких~И.~В.}
%Построение согласованной матрицы парных сравнений в маркетинговых исследованиях на основе методов тропической математики //
%Вестн. С.-Петерб. ун-та. Сер.~8. Менеджмент. 2015. Вып.~1. С.~3--43.

18.~Krivulin~N.~K., Gladkikh~I.~V. Postroenie soglasovannoj
matritsy parnykh sravnenij v marketingovykh issledovaniyakh na
osnove metodov tropicheskoj matematiki [Computation of the
consistent pairwise comparison matrix in marketing research by
using methods of tropical mathematics]. \textit{Vestnik of Saint
Petersburg University. Series 8. Management}, 2015, issue~1,
pp.~3-43. (In Russian)

%19.~\textit{Krivulin N.}
%Rating alternatives from pairwise comparisons by solving tropical optimization problems //
%12th Intern. Conference on Fuzzy Systems and Knowledge Discovery (FSKD) / eds Z.~Tang, J.~Du, S.~Yin, L.~He, R.~Li.
%IEEE, 2015. P.~162--167.
%DOI:10.1109/FSKD.2015.7381933

19.~Krivulin N. Rating alternatives from pairwise comparisons by
solving tropical optimization problems. \textit{12th Intern.
Conference on Fuzzy Systems and Knowledge Discovery $($FSKD$)$}.
Eds  Z.~Tang, J.~Du, S.~Yin, L.~He, R.~Li. IEEE, 2015,
pp.~162--167. DOI:10.1109/FSKD.2015.7381933

%20.~\textit{Krivulin N.}
%Using tropical optimization techniques to evaluate alternatives via pairwise comparisons //
%Proc. 7th SIAM Workshop on Combinatorial Scientific Computing / eds A.~H.~Gebremedhin, E.~G.~Boman, B.~Ucar.
%Philadelphia: SIAM, 2016. P.~62--72.
%DOI:10.1137/1.9781611974690.ch7

20.~Krivulin N. Using tropical optimization techniques to evaluate
alternatives via pairwise comparisons. \textit{Proc. 7th SIAM
Workshop on Combinatorial Scientific Computing}. Eds
A.~H.~Gebremedhin, E.~G.~Boman, B.~Ucar. Philadelphia, SIAM, 2016,
pp.~62--72. DOI:10.1137/1.9781611974690.ch7

%21.~\textit{Krivulin N.}
%Extremal properties of tropical eigenvalues and solutions to tropical optimization problems //
%Linear Algebra Appl. 2015. Vol.~468. P.~211--232.
%DOI:10.1016/j.laa.2014.06.044

21.~Krivulin N. Extremal properties of tropical eigenvalues and
solutions to tropical optimization problems. \textit{Linear
Algebra Appl.}, 2015, vol.~468, pp.~211--232.
DOI:10.1016/j.laa.2014.06.044

%22.~\textit{Krivulin N.}
%Solving a tropical optimization problem via matrix sparsification //
%Relational and Algebraic Methods in Computer Science. Vol.~9348 of Lecture Notes in Comput. Sci. / eds W.~Kahl, M.~Winter, J.~N.~Oliveira.
%Cham: Springer, 2015. P.~326--343.
%DOI:10.1007/978-3-319-24704-5\_20

22.~Krivulin N. Solving a tropical optimization problem via matrix
sparsification. \textit{Relational and Algebraic Methods in
Computer Science}. Vol.~9348 of Lecture Notes in Comput. Sci. Eds
W.~Kahl, M.~Winter, J.~N.~Oliveira. Cham, Springer, 2015,
pp.~326--343. DOI:10.1007/978-3-319-24704-5\_20

%23.~\textit{Krivulin N.}
%A maximization problem in tropical mathematics: A complete solution and application examples //
%Informatica. 2016. Vol.~27, N~3. P.~587--606.
%DOI:10.15388/Informatica.2016.101

23.~Krivulin N. A maximization problem in tropical mathematics: A
complete solution and application examples. \textit{Informatica},
2016, vol.~27, no.~3, pp.~587--606.
DOI:10.15388/Informatica.2016.101



\vskip 2mm

{\bf For citation:} Krivulin N.~K.,~Ageev V.~A.,~Gladkikh I.~V.
Application of methods of tropical optimization for evaluating
alternatives based on pairwise comparisons. {\it Vestnik of Saint
Petersburg University. Applied mathematics. Computer science.
Control processes}, \issueyear, volume~13, issue~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}.
\doivyp/spbu10.\issueyear.\issuenum03



}
