
{\normalsize

\vskip 4mm%\vskip 6mm

\noindent{\bf A generalized Gibbs' lemma and a Wardrop
equilibrium}

}

\vskip 1.8mm%\vskip 2mm

{\small

\noindent{\it V.~N.~Malozemov, N.~A.~Solovyeva%$\,^1$%
%, I.~О. Famylia%$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.8mm%\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2mm%\vskip 3mm


\noindent \textbf{For citation:}  Malozemov V.~N., Solovyeva N.~A.
A generalized Gibbs' lemma and a Ward-\linebreak rop equilibrium.
{\it Vestnik of Saint~Petersburg University. Applied Mathematics.
Computer Science. Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p4}--\pageref{p4e}.\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04  (In Russian)

\vskip 2mm%\vskip 3mm

{\leftskip=7mm\noindent In the article, a generalized Gibbs'
lemma is stated and proved. A conclusion of this lemma
cor\-res\-ponds to a definition of Wardrop equilibrium
in transport networks. This allows us to naturally introduce
a well known convex programming problem with linear constraints
whose solution is a Wardrop equilibrium vector. The complicated
definition of the Wardrop equilibrium is analyzed in detail
(typical examples are given). The reason of the Braess paradox'
appearance is specified. A large example, that illustrates how the
Wardrop equilibrium vector changes when a road with zero driving
time is added into the transport network, is also given.\\[1mm]
\textit{Keywords}: generalized Gibbs' lemma, Wardrop equilibrium,
Braess paradox, convex programming.
\par}

\vskip 4mm%\vskip 5mm

\noindent \textbf{References} }

\vskip 1.8mm%\vskip 2mm

{\footnotesize

1. Danskin J. M. \emph{The theory of max-min and its application
to weapons allocation problems}. Berlin, Heidelberg, New York,
Springer-Verlag Publ., 1967, 128 p. (Russ. ed.: Danskin J. M.
\emph{Teoriya max-min i ee prilozheniya k zadacham raspredeleniya
vooruzheniy}. Moscow, Sov. Radio Publ., 1970, 200 p.)

2. Braess~D., Nagurney~A., Wakolbinger~T. On a paradox of a
traffic planning. \emph{Trans\-portation Science}, 2005, vol.~39,
no.~4, pp.~446--450.

3. Wardrop J.~G. Some theoretical aspects of road traffic
research. \emph{Proceedings of the Institute of Civil Engineers},
1952, pt II, pp.~325--378.

4. Patriksson~ M. \emph{The traffic assignment problem: models and
methods.} Mineola, Dover Publ., 2015, 240 p.

5. Mazalov V. V. \emph{Matematicheskaia teoria igr i priloghenia}
[\emph{Mathematical theory of games and applications}]. Saint
Petersburg,  Publishing house ``Lan{'}\,'', 2016, 448~p.


\vskip1.5mm Received:  August 21, 2018.

Accepted: March 15, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip 1.8mm%\vskip 2mm
\textit{Vasiliy N. Malozemov}~--- Dr. Sci. in Physics and
Mathematics, Professor; v.malozemov@sbpu.ru

\vskip 1.8mm%\vskip 2mm
\textit{Natalia A. Solovyeva}~--- PhD in Physics and Mathematics,
Senior Teacher; vinyo@mail.ru\par
%
}
