


\zageng{519.8}{R. V. Voronov}{THE FAULT-TOLERANT METRIC
DIMENSION\\
OF THE KING'S GRAPH%$^*$
}{



\vspace{-3mm}\parindent=7mm



%{\copyright} А.~В.~Буре, 2014

\textit{Voronov Roman Vladimirovich} --- PhD of technical
sciences, associate professor;\\ rvoronov76@gmail.com


\vskip 2mm

\emph{Воронов Роман Владимирович} --- кандидат технических наук,
доцент; rvoronov76@gmail.com

\vskip 2mm

%$^*$ Работа выполнена при финансовой поддержке
%Санкт-Петербургского государственного университета (грант №
%9.38.205.2014).


{\copyright} Санкт-Петербургский государственный университет,
\issueyear %
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp03 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum02}}\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp03 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum02}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize \noindent Petrozavodsk State University, 33, Lenina
pr., Petrozavodsk, \\ 185910, Russian Federation



\vskip2.3mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item The concept of resolving the set within a graph is related to the optimal
placement problem of access points in an indoor positioning
system. A vertex $w$ of the undirected connected graph $G$
resolves the vertices $u$ and $v$ of $G$ if the distance between
vertices $w$ and $u$ differs from the distance between vertices
$w$ and $v$. A subset $W$ of vertices of $G$ is called a resolving
set, if every two distinct vertices of $G$ are resolved by some
vertex of $w \in W$. The metric dimension of $G$ is a minimum
cardinality of its resolving set.The set of access points of the
indoor positioning system corresponds to the resolving set of
vertices in the graph.The minimum number of access points required
to locate each of the vertices corresponds to the metric dimension
of graph. A resolving set $W$ of the graph $G$ is fault-tolerant
if $W \set minus \{w\}$ is also a resolving set of $G$, for each
$w \in W$. The fault-tolerant metric dimension of the graph $G$ is
a minimum cardinality of the fault-tolerant resolving set. In the
indoor positioning system the fault-tolerant resolving set
provides correct information even when one of the access points is
not working. The article describes a special case of a graph
called the king's graph, or the strong product of two paths.The
king's graph is a building model in some indoor positioning
systems. In this article we give an upper bound for the
fault-tolerant metric of the king's graph and a formula for a
particular case of the king's graph. Refs~20. Figs~2.

{\it Keywords}: fault-tolerant metric dimension, strong product
graphs, king's graph, access points of indoor positioning system.

\end{list}

}

\vskip3mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it Р. В. Воронов}

\vskip2mm \noindent{\bf ОТКАЗОУСТОЙЧИВАЯ МЕТРИЧЕСКАЯ РАЗМЕРНОСТЬ\\
ГРАФА ХОДОВ ШАХМАТНОГО КОРОЛЯ}

\vskip2mm


{\footnotesize


\noindent Петрозаводский государственный университет, Российская
Федерация,\\ 185910, Петрозаводск, пр. Ленина, 33

\vskip2.3mm


\item В некотором приближении аналогом задачи оптимального размещения
точек доступа системы внутреннего позиционирования служит задача
определения метрической размерности графа и~построения его
разрешающего множества. Пусть вершина $w$ неориентированного
связного графа $G$ различает вершины $u$ и~$v$ графа $G$, если
расстояние между вершинами $w$ и~$u$ отличается от расстояния
между вершинами $w$ и~$v$. Подмножество $W$ вершин графа $G$
называется разрешающим, если для каждой пары вершин $u$ и~$v$
графа $G$ найдется различающая их вершина $w \in W$. Метрическая
размерность графа~--- это минимальное число вершин в~разрешающем
подмножестве. Точкам доступа системы внутреннего позиционирования
соответствует разрешающее множество вершин графа, а~минимально
необходимому числу точек доступа~--- метрическая размерность
графа. Разрешающее множество называется отказоустойчивым, если оно
остается разрешающим, даже если из него удалить любую его вершину.
Отказоустойчивая метрическая размерность графа~--- это минимальное
число вершин в~отказоустойчивом разрешающем подмножестве, что
в~системе внутреннего позиционирования соответствует возможности
определения местоположения объекта даже в~случае потери информации
от одной из точек доступа. Рассмотрен один частный случай
графа~--- сильное произведение двух простых цепей, называемое
иначе графом ходов шахматного короля. Установлена верхняя граница
для отказоустойчивой метрической размерности графа ходов короля
и~приведена формула для одного частного случая. Библиогр. 20~назв.
Ил.~2.

\textit{Ключевые слова}: отказоустойчивая метрическая размерность,
сильное произведение графов, граф ходов короля, точки доступа
системы внутреннего позиционирования.


}

\end{list}


\vskip2.5mm

{\bf Introduction.} The concepts of the graph theory is used to
describe the problem of navigation in the network~[1] and in
indoor positioning system to model the floorplan of the building.
The building floorplan is modeled by the undirected connected
graph $G=(V,\;E)$, where the vertices of the set $V$ represent
small zones, and the edges of the set $E$ denote the possibility
of moving directly between zones. A zone may consist of only one
room, and big rooms may be partitioned into several zones. The
distance $d(u,v)$ between vertices $u$ and $v$ is the minimum
number of edges in the path having these two vertices as its
endpoints.

In some vertices of the graph we can place the landmarks of the
navigation system or access points of the indoor positioning
system~[2]. The set of access points of the indoor positioning
system corresponds to the resolving set of vertices in graph. The
minimum number of access points required to locate each of the
vertices is called the metric dimension.

Formally, let $W=\{w_1,\ldots,w_k\}$ be an ordered subset of
vertices of graph $G$. The ordered $k$-tuple
$r(v\;|\;W)=(d(v,w_1),\ldots,d(v,w_k))$ is called {\it a
representation} of the vertex $v$ with respect to~$W$. The subset
of vertices $W \subset V$ is called a {\it resolving set}, if
every two vertices $u$, $v$ have distinct representations
$r(u\;|\;W)$ and $r(v\;|\;W)$. {\it The metric dimension}
$\beta(G)$ of the graph $G$ is a minimum cardinality of the
resolving set for $G$. A resolving set with the minimum number of
vertices is called a {\it metric basis} for $G$.

In other words, the metric dimension of the graph $G$ is the
smallest integer $m$, for which subset $W \subset V$ exists, such
that $\vert W\vert = m$ and for every pair of vertices $u, v \in
V$ there is $w \in W$, that the distance between the vertices $w$
and $u$ is not equal to the distance between the vertices $w$ and
$v$. We also will say, that a vertex $w$ of the graph $G$ resolves
the vertices $v_1$ and $v_2$ in $G$ (is able to distinguish $v_1$
and $v_2$), if $d(w,\;v_1)\ne d(w,\;v_2)$.

A resolving set $W$ of the graph $G$ is {\it fault-tolerant} if $W
\setminus \{w\}$ is also a resolving set of $G$, for each $w \in
W$. The {\it fault-tolerant metric dimension} $\beta'(G)$ of $G$
is a minimum cardinality of the fault-tolerant resolving set. A
fault-tolerant resolving set of cardinality $\beta'(G)$ is called
{\it a fault-tolerant metric basis} of {G}.

The strong product $G_1 \boxtimes G_2$ of the graphs $G_1 = (V_1,
E_1)$ and $G_2 = (V_2, E_2)$ is the graph $G = (V, E)$, such that
$V = V_1 \times V_2$ and two distinct vertices $(u_1, u_2)$ and
$(v_1, v_2)$ are adjacent in $G$ if and only if

$u_1=v_1$ and $(u_2,v_2) \in E_2$, or

$u_2=v_2$ and $(u_1,v_1) \in E_1$, or

$(u_1,v_1) \in E_1$ and $(u_2,v_2) \in E_2$.

Now we denote $P_m = (I_m,J_m)$~--- path graph, where $m$ is
natural number, $I_m=\{1,\ldots,m\}$ and
$J_m=\{(i,i+1)\;|\;i=1,\ldots,m-1\}$.

The {\it king's graph} with natural parameters $(m, n)$ is a graph
$P_m \boxtimes P_n$, that represents all legal moves of the king
chess piece on a $m \times n$ chessboard. The vertex set of the $m
\times n$ king's graph is the Cartesian product $V=I_m \times
I_n$. It is easy to check, that
$d(v_1,\;v_2)=\max\{|i_1-i_2|,\;|j_1-j_2|\}$ for any two vertices
$v_1=(i_1,\;j_1)$ and $v_2=(i_2,\;j_2)$ of graph $P_m \boxtimes
P_n$.

It is known that $\beta(P_n \boxtimes P_n)=3$~[3], $\beta'(P_n
\boxtimes P_n)=4$~[4] for $n \ge 2$. The following theorem is
proved in~[5].

{\bf Theorem 1}~[5]{\bf .} {\it For any integers $n$ and $m$ such
that $2 \le m < n$,}
$$
\beta(P_m \boxtimes P_n)=\left\lceil \frac{n + m - 2}{m-1}
\right\rceil.
$$

Figure 1 shows graph $P_3 \boxtimes P_{12}$. Vertices of metric
basis are black, $\beta(P_3 \boxtimes P_{12})=7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%fig1

%\input graph1.tex

%\begin{figure}[htbp]
\begin{center}
\begin{picture}(280,55)
\put(0,0){\circle{6}} \put(25,0){\circle{6}}
\put(50,0){\circle*{6}} \put(75,0){\circle{6}}
\put(100,0){\circle{6}} \put(125,0){\circle{6}}
\put(150,0){\circle*{6}} \put(175,0){\circle{6}}
\put(200,0){\circle{6}} \put(225,0){\circle{6}}
\put(250,0){\circle*{6}} \put(275,0){\circle{6}}
\put(0,25){\circle{6}} \put(25,25){\circle{6}}
\put(50,25){\circle{6}} \put(75,25){\circle{6}}
\put(100,25){\circle{6}} \put(125,25){\circle{6}}
\put(150,25){\circle{6}} \put(175,25){\circle{6}}
\put(200,25){\circle{6}} \put(225,25){\circle{6}}
\put(250,25){\circle{6}} \put(275,25){\circle{6}}
\put(0,50){\circle*{6}} \put(25,50){\circle{6}}
\put(50,50){\circle{6}} \put(75,50){\circle{6}}
\put(100,50){\circle*{6}} \put(125,50){\circle{6}}
\put(150,50){\circle{6}} \put(175,50){\circle{6}}
\put(200,50){\circle*{6}} \put(225,50){\circle{6}}
\put(250,50){\circle{6}} \put(275,50){\circle*{6}}
\put(3,0){\line(1,0){19}} \put(28,0){\line(1,0){19}}
\put(53,0){\line(1,0){19}} \put(78,0){\line(1,0){19}}
\put(103,0){\line(1,0){19}} \put(128,0){\line(1,0){19}}
\put(153,0){\line(1,0){19}} \put(178,0){\line(1,0){19}}
\put(203,0){\line(1,0){19}} \put(228,0){\line(1,0){19}}
\put(253,0){\line(1,0){19}} \put(3,25){\line(1,0){19}}
\put(28,25){\line(1,0){19}} \put(53,25){\line(1,0){19}}
\put(78,25){\line(1,0){19}} \put(103,25){\line(1,0){19}}
\put(128,25){\line(1,0){19}} \put(153,25){\line(1,0){19}}
\put(178,25){\line(1,0){19}} \put(203,25){\line(1,0){19}}
\put(228,25){\line(1,0){19}} \put(253,25){\line(1,0){19}}
\put(3,50){\line(1,0){19}} \put(28,50){\line(1,0){19}}
\put(53,50){\line(1,0){19}} \put(78,50){\line(1,0){19}}
\put(103,50){\line(1,0){19}} \put(128,50){\line(1,0){19}}
\put(153,50){\line(1,0){19}} \put(178,50){\line(1,0){19}}
\put(203,50){\line(1,0){19}} \put(228,50){\line(1,0){19}}
\put(253,50){\line(1,0){19}} \put(0,3){\line(0,1){19}}
\put(25,3){\line(0,1){19}} \put(50,3){\line(0,1){19}}
\put(75,3){\line(0,1){19}} \put(100,3){\line(0,1){19}}
\put(125,3){\line(0,1){19}} \put(150,3){\line(0,1){19}}
\put(175,3){\line(0,1){19}} \put(200,3){\line(0,1){19}}
\put(225,3){\line(0,1){19}} \put(250,3){\line(0,1){19}}
\put(275,3){\line(0,1){19}} \put(0,28){\line(0,1){19}}
\put(25,28){\line(0,1){19}} \put(50,28){\line(0,1){19}}
\put(75,28){\line(0,1){19}} \put(100,28){\line(0,1){19}}
\put(125,28){\line(0,1){19}} \put(150,28){\line(0,1){19}}
\put(175,28){\line(0,1){19}} \put(200,28){\line(0,1){19}}
\put(225,28){\line(0,1){19}} \put(250,28){\line(0,1){19}}
\put(275,28){\line(0,1){19}} \put(2,2){\line(1,1){21}}
\put(27,2){\line(1,1){21}} \put(52,2){\line(1,1){21}}
\put(77,2){\line(1,1){21}} \put(102,2){\line(1,1){21}}
\put(127,2){\line(1,1){21}} \put(152,2){\line(1,1){21}}
\put(177,2){\line(1,1){21}} \put(202,2){\line(1,1){21}}
\put(227,2){\line(1,1){21}} \put(252,2){\line(1,1){21}}
\put(2,27){\line(1,1){21}} \put(27,27){\line(1,1){21}}
\put(52,27){\line(1,1){21}} \put(77,27){\line(1,1){21}}
\put(102,27){\line(1,1){21}} \put(127,27){\line(1,1){21}}
\put(152,27){\line(1,1){21}} \put(177,27){\line(1,1){21}}
\put(202,27){\line(1,1){21}} \put(227,27){\line(1,1){21}}
\put(252,27){\line(1,1){21}} \put(23,2){\line(-1,1){21}}
\put(48,2){\line(-1,1){21}} \put(73,2){\line(-1,1){21}}
\put(98,2){\line(-1,1){21}} \put(123,2){\line(-1,1){21}}
\put(148,2){\line(-1,1){21}} \put(173,2){\line(-1,1){21}}
\put(198,2){\line(-1,1){21}} \put(223,2){\line(-1,1){21}}
\put(248,2){\line(-1,1){21}} \put(273,2){\line(-1,1){21}}
\put(23,27){\line(-1,1){21}} \put(48,27){\line(-1,1){21}}
\put(73,27){\line(-1,1){21}} \put(98,27){\line(-1,1){21}}
\put(123,27){\line(-1,1){21}} \put(148,27){\line(-1,1){21}}
\put(173,27){\line(-1,1){21}} \put(198,27){\line(-1,1){21}}
\put(223,27){\line(-1,1){21}} \put(248,27){\line(-1,1){21}}
\put(273,27){\line(-1,1){21}}
\end{picture}
%\caption{Граф $G_{3,12}$}
%\label{pic0_3_12}
%\end{center}
%\end{figure}
%\begin{center}
\vskip 3mm {\small{\it Fig. 1.} Metric basis for graph $P_3}
\boxtimes P_{12}$
\end{center}

In this paper we study the problem of finding a sharp bound for
the fault-tolerant metric dimension of the king's graph and the
exact value for a particular case. We assume that $n > m$ for the
graph $P_m \boxtimes P_n$. The case $m > n$ is considered
analogously.

{\bf Related works.} The problems of finding the metric dimension
of a graph were introduced independently by Slater (1975) and
Harary and Melter (1976)~[6, 7]. Melter studied the metric
dimension problem for the tree. Garey and Johnson (1979) noted
that determining the metric dimension of the graph is an
NP-complete problem. Khuller, Raghavachari, Rosenfeld (1996)
described the application of the metric dimension problem in the
field of computer science and robotics and outlined the graphs
with metric dimension 1 and 2~[8]. Chartrand, Eroh, Johnson,
Oellermann (2000) described the application in chemistry~[9]. The
strong metric dimension problem was introduced by Seb{\"o} and
Tannier (2004)~[10]. Fehr, Gosselin, Oellermann (2006) studied the
metric dimension for different types of graphs, for exsample
Cayley digraphs~[11]. The concept of the fault-tolerant metric
dimension was introduced by Hernando, Mora, Slater, Wood
(2008)~[12]. Okamoto, Phinezy, Zhang (2010) introduced the concept
of local metric dimension~[13]. The metric dimension of the random
graph was considered by Bollobas, Mitsche, Pralat (2012)~[14]. The
formulas for metric dimension of many graph classes were
studied~[15--17]. Zejnilovi{\'c}, Mitsche, Gomes and Sinopoli
(2016) extended the metric dimension to the graphs with missing
edges~[18].

{\bf The main results.} We present the main result in the form of
two theorems.

The first theorem gives the upper bounds for the fault-tolerant
metric dimension of the king's graph.

{\bf Theorem 2.} {\it For any integers $n$ and $m$, such that $2
\le m < n$, the following assertion hold. If $(m-1)$ is a divisor
of $(n-2)$, then
$$
\beta'(P_m \boxtimes P_n) \le 2\frac{n-2}{m-1} + 3,
$$
otherwise}
$$
\beta'(P_m \boxtimes P_n) \le 2\left\lceil \frac{n-1}{m-1}
\right\rceil + 2.
$$

There is a formula for the fault-tolerant metric dimension for a
partcular case of king's graph in second theorem.

{\bf Theorem 3.} {\it For any integers $n$ and $m$, such that $m$
is even, $m \ge 2$, $n \ge 2m - 1$ and $(m-1)$ is a divisor of
$(n-1)$,}
$$
\beta'(P_m \boxtimes P_n) = 2\frac{n-1}{m-1} + 2.
$$

First we introduce some definitions and prove some lemmas.

For the integers $m$, $n$, $j$, such that $2 \le m < n$ and $j \in
\{1,\ldots,n\}$, $V_j$ denotes the vertex subset of graph $P_m
\boxtimes P_n$, where $V_j=\{(i,j)\;|\; i=1,\ldots,m\}$. We
introduce the notation

$$
V_{j_1,\;j_2}=\bigcup_{j=j_1}^{j_2} V_j.
$$

{\bf Lemma 1.} {\it Let $2 \le m < n$ be integers. Let $W$ be a
resolving set of graph $G=P_m \boxtimes P_n$. If $v_1=(i_1,\;j')$,
$v_2=(i_2,\;j')$ are vertices of $G$ and $w=(i,\;j)\in W$, such
that $|j-j'| \ge m-1$, then vertex $w$ does not resolve the
vertices $v_1$ and $v_2$.}

P\,r\,o\,o\,f.\; Since $|i-i'|\le m-1$ for all $i'=1,\ldots,m$,
then
$$
d(w,\;v_1)=d(w,\;v_2)=|j-j'|.
$$
Hence, then vertex $w$ does not resolve the vertices $v_1$ and
$v_2$. Lemma is proved.

{\bf Lemma 2.} {\it Let $2 \le m < n$ be integers. Let $W$ be a
resolving set of graph $P_m \boxtimes P_n$. Then for any
$j'\in\{1,\ldots,n\}$ there exists vertex $w=(i,\;j)\in W$, such
that $|j-j'| < m-1$.}

P\,r\,o\,o\,f.\; Suppose, for the contrary, that exists
$j'\in\{1,\ldots,n\}$, such that for all $w=(i,\;j)\in W$ we have
$|j-j'|\ge m-1$. We now take any distinct
$i_1,\;i_2\in\{1,\ldots,m\}$. According to the Lemma~1, no vertex
$w \in W$ resolve the vertices $v_1=(i_1,\;j')$ and
$v_2=(i_2,\;j')$. This contradiction proves the lemma.

{\bf Lemma 3.} {\it Let $2 \le m < n$ be integers and let $W$ be a
resolving set of graph $P_m \boxtimes P_n$. Let
$j'\in\{1,\ldots,n\}$. If there exists only one vertex
$w=(i,\;j)\in W$, such that $|j-j'| < m-1$, then $j=j'$.}

P\,r\,o\,o\,f.\; Suppose, for the contrary, that exists
$j'\in\{1,\ldots,n\}$, that there exists only one vertex
$w=(i,\;j)\in W$, such that $|j-j'| < m-1$, but $j \ne j'$.

Let $i_1=i$. If $i < m$, then let $i_2=i + 1$. If $i = m$, then
let $i_2=i - 1$. Let $v_1=(i_1,\;j')$, $v_2=(i_2,\;j')$. Then
$d(w,\;v_1)=|j-j'|$, $d(w,\;v_2)=|j-j'|$, hence
$d(w,\;v_1)=d(w,\;v_2)$ and vertex $w \in W$ does not resolve the
vertices $v_1$ and $v_2$. In addition, according to the Lemma~1,
no vertex in $W\setminus\{w\}$ that distinguish vertices $v_1$ and
$v_2$.

This contradiction proves the lemma.

Lemmas~2 and~3 lead to the next results.

{\bf Corollary 1.} {\it Let $2 \le m < n$ be integers and let $W$
be a resolving set of graph $P_m \boxtimes P_n$. Then for all
$j\in\{1,\ldots,n\}$ there exists $w \in W$, such that $w \in
V_{j}$ or exist two distinct vertices $(i_1,\;j_1)\in W$ and
$(i_2,\;j_2)\in W$, that $|j-j_1| < m-1$ and $|j-j_2| < m-1$.}

{\bf Corollary 2.} {\it Let $2 \le m < n$ be integers and let $W$
be a fault-tolerant resolving set of graph $P_m \boxtimes P_n$.
Then for all $j\in\{1,\ldots,n\}$ there exist two distinct
vertices $w_1,w_2 \in W$, such that $w_1,w_2 \in V_{j}$ or exist
three distinct vertices $(i_1,\;j_1)\in W$, $(i_2,\;j_2)\in W$ and
$(i_3,\;j_3)\in W$, that $|j-j_1| < m-1$, $|j-j_2| < m-1$ and
$|j-j_3| < m-1$.}

{\bf Lemma 4}~[19]{\bf .} {\it A resolving set $W$ of a graph $G$
is fault-tolerant if and only if every pair of vertices in $G$ is
resolved by at least two elements of $W$.}

{\bf Lemma 5.} {\it Let $G = P_m \boxtimes P_n$, where $m$ is
even, $n \ge m \ge 2$. Let $W$ be a fault-tolerant resolving set
of $G$. Then for all $j \in \{0, \ldots, n - m + 1 \}$,}
$$
\left| V_{j+1,\;j+m-1} \bigcap W \right| \ge 2.
$$

P\,r\,o\,o\,f.\; Let $j \in \{0, \ldots, n - m + 1 \}$, $V' =
V_{j+1,\;j+m-1}$, $v_1=\left(\frac m2, j+\frac m2 \right)$, $v_2=$
$\left(\frac m2+1, j+\frac m2 \right)$. In this case $v_1, v_2 \in
V'$. Let $V$ be the vertex set of graph $G$.

By Lemma~4 for the vertices $v_1$, $v_2$ there exist $w_1,w_2 \in
W$, $w_1 \ne w_2$, such that $d(w_1, v_1) \ne d(w_1, v_2)$ and
$d(w_2, v_1) \ne d(w_2, v_2)$.

Consider a vertex $w=(i,k) \in V \setminus V'$. Since $\left|i -
\frac m2 \right| \le \frac m2$, $\left|i - \frac m2 - 1 \right|
\le \frac m2$ and $|k-j-\frac m2| \ge \frac m2$ we have
$d(w,v_1)=|k-j-\frac m2|$ and $d(w,v_2)=|k-j-\frac m2|$. Hence
$d(w,v_1)=d(w,v_2)$ and no vertex in $V \setminus V'$ is able to
distinguish $v_1$ and $v_2$.

Thus $w_1, w_2 \in V' \bigcap W$. Therefore, the proof is
complete.

{\bf Lemma 6.} {\it Let $G = P_m \boxtimes P_n$, where $m \ge 2$
and $n\ge 2$. Let $W$ be a fault-tolerant resolving set of $G$ and
let $j \in \{ 1, \ldots, n \}$. If exist distinct vertices
$w_1,w_2 \in W$, that $W=\{w_1,w_2\}$ or $d(w, v_1)=d(w, v_2)$ for
any $w \in W \setminus \{w_1, w_2\}$ and for each pair of distinct
vertices $v_1,v_2 \in V_j$, then $w_1,w_2 \in V_j$.}

P\,r\,o\,o\,f.\; Let $G$, $j$, $w_1$ and $w_2$ be as in the
hypotheses. Let $V$ be the vertex set of graph $G$. By Lemma~4 for
every pair of vertices $v_1, v_2 \in V_j$ there are at least two
vertices of $W$, which are able to distinguish $v_1$ and $v_2$.
Hence, we have that $d(w_1, v_1) \ne d(w_1, v_2)$ and $d(w_2, v_1)
\ne d(w_2, v_2)$ for all different $v_1,v_2 \in V$.

We will show that $w_1 \in V_j$. Suppose, for the contrary, that
$w_1=(i,j_1)$ and $j_1 \ne j$. If $i=1$, then $w_1$ is not able to
distinguish $v_1=(1,j) \in V_j$ and $v_2=(2,j) \in V_j$. If $i>1$,
then $w_1$ is not able to distinguish $v_1=(i,j) \in V_j$ and
$v_2=(i-1,j) \in V_j$. In both cases we have
$d(w_1,v_1)=d(w_1,v_2)=|j_1-j|$ and we get a contradiction.

The proof that $w_2 \in V_j$ is deduced analogously.

Lemma is proved.

{\bf Lemma 7.} {\it Let $G = P_m \boxtimes P_n$, where $m \ge 2$
and $n\ge 2m-3$. Let $W$ be a fault-tolerant resolving set of $G$
and let $\tilde V_j = V_{\max\{1,j-m+2\},\;\min\{n,j+m-2\}}$,
where $j \in \{1, \ldots, n \}$. If
$$
\left|\tilde V_j \bigcap W \right| = 2,
$$
then $\tilde V_j \bigcap W \subset V_j$.}

P\,r\,o\,o\,f.\; Let $j \in \{1, \ldots, n \}$ and let
$\{w_1,w_2\}=\tilde V_j \bigcap W$. Let $V$ be the vertex set of
graph $G$. We differentiate two cases for $V \setminus \tilde
V_j$.

{\it Case 1}: $V \setminus \tilde V_j \ne \emptyset$. Consider a
vertex $w=(i,k) \in V \setminus \tilde V_j$ and any different
vertices $v_1=(i_1, j) \in V_j$, $v_2=(i_2, j) \in V_j$. Since $|i
- i_1| \le m-1$, $|i - i_2| \le m-1$ and $|k-j| \ge m-1$ we have
$d(w,v_1)=|k-j|$ and $d(w,v_2)=|k-j|$. Hence $d(w,v_1)=d(w,v_2)$
and no vertex in $V \setminus \tilde V_j$ is able to distinguish
$v_1$ and $v_2$. Thus no vertex in $W \setminus \{w_1,w_2\}$ is
able to distinguish any two different vertices $u,v \in V_j$.
Therefore, by Lemma~6 $w_1,w_2 \in V_j$.

{\it Case 2}: $V \setminus \tilde V_j = \emptyset$. In this case
we have $W=\{w_1,w_2\}$, by Lemma~6 $w_1,w_2 \in V_j$ and we
conclude the proof.

{\bf Lemma 8.} {\it Let $G = P_m \boxtimes P_n$, where $m \ge 2$
and $n\ge m$. Let $W$ be a fault-tolerant resolving set of $G$.
Then}
$$
\left|V_{n-m+1,\;n} \bigcap W \right| \ge 3.
$$

P\,r\,o\,o\,f.\; By Corollary 2 we have $\left| V_n \bigcap W
\right| \ge 2$ or $\left| V_{n-m+2,\;n} \bigcap W \right| \ge 3$
and, ad-\linebreak ditionally, $\left| V_{n-1} \bigcap W \right|
\ge 2$ or $\left| V_{n-m+1,\;n} \bigcap W \right| \ge 3$. Anyway
we get $\left| V_{n-m+1,\;n} \bigcap W \right| \ge 3$.\linebreak
The lemma is proved.

Now we present the proof of the Theorem~2.

P\,r\,o\,o\,f.\; Let $2 \le m < n$ be integers and let $G=P_m
\boxtimes P_n$. In paper~[20] is shown, how construct a resolving
set $W$ (a metric generator) for graph $G$, such that
$$
|W| = k = \left\lceil \frac{n-1}{m-1} \right\rceil + 1.
$$
We use that construction and consider two cases.\newpage

{\it Case 1}: $(m-1)$ is a divisor of $(n-2)$. Let
$$
w_{1t}=\left\{
\begin{array}{ll}
(1,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{if } t \mbox{ is odd},\\
(m,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{otherwise},\\
\end{array}
\right.
$$
$$
t=1,\ldots, k,
$$
$$
w_{2t}=\left\{
\begin{array}{ll}
(m,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{if } t \mbox{ is odd},\\
(1,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{otherwise},\\
\end{array}
\right.
$$
$$
t=1,\ldots, k-1,
$$
$$
w_{2k}=\left\{
\begin{array}{ll}
(1,\; n),~ & \mbox{if } k \mbox{ is odd},\\
(m,\; n),~ & \mbox{otherwise},\\
\end{array}
\right.
$$
$$
w_{3t}=\left\{
\begin{array}{ll}
(1,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{if } t \mbox{ is odd},\\
(m,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{otherwise},\\
\end{array}
\right.
$$
$$
t=1,\ldots, k-1,
$$
$$
w_{3k}=\left\{
\begin{array}{ll}
(1,\; n-1), &~ \mbox{if } k \mbox{ is odd},\\
(m,\; n-1), &~ \mbox{otherwise}.\\
\end{array}
\right.
$$

For $i=1,\ldots,3$~ let
$$
W_i=\left\{w_{it}\; \left| \; t=1,\ldots,k \right.\right\}.
$$

$W_1$ is resolving sets of $G$~[20]. Analogously we can show that
$W_2$, $W_3$ are resolving sets of $G$.

Let $U=\{w_{1k-1}, w_{1k}, w_{3k}\}$. It is obviously, that
$w_{1k-1}=w_{3k-1}$, $w_{1k}=w_{2k}$, $w_{3k}=w_{2k-1}$, $W_1
\setminus U = W_3 \setminus U$, $(W_1 \setminus U) \cap (W_2
\setminus U) = \emptyset$. Let $W=W_1 \bigcup W_2 \bigcup W_3$. We
differentiate five cases. If $w\in W_1 \setminus U$, then $W_2
\subset W \setminus \{w\}$. If $w\in W_2 \setminus U$, then $W_1
\subset W \setminus \{w\}$. If $w=w_{1k-1}$, then $W_2 \subset W
\setminus \{w\}$. If $w=w_{1k}$, then $W_3 \subset W \setminus
\{w\}$. If $w=w_{3k}$, then $W_1 \subset W \setminus \{w\}$. We
can point out that, in any case, $W \setminus \{w\}$ is resolving
sets of $G$. Thus $W$ is a fault-tolerant resolving set.

{\it Case 2}: $(m-1)$ is not a divisor of $(n-2)$. Let

$$
w_{1t}=\left\{
\begin{array}{ll}
(1,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{if } t \mbox{ is odd},\\
(m,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{otherwise,}\\
\end{array}
\right.
$$
$$
w_{2t}=\left\{
\begin{array}{ll}
(m,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{if } t \mbox{ is odd},\\
(1,\; \min\{n,\;(t-1)(m-1)+1\}), &~ \mbox{otherwise,}\\
\end{array}
\right.
$$
$$
t=1,\ldots, k.
$$

For $i=1,2$~ let
$$
W_i=\left\{w_{it}\; \left| \; t=1,\ldots,k \right.\right\}.
$$

$W_1$, $W_2$ are resolving sets of $G$~[20].

It is obviously, that $W_1 \bigcap W_2 = \emptyset$. Let $W = W_1
\bigcup W_2$. We differentiate two cases for $w \in W$. If $w\in
W_1$, then $W_2 \subset W \setminus \{w\}$, if $w\in W_2$, then
$W_1 \subset W \setminus \{w\}$. We can point out that, in any
case, $W \setminus \{w\}$ is resolving sets of $G$. Thus $W$ is a
fault-tolerant resolving~set.

This proves the theorem.

Now we present the proof of the Theorem~3.

P\,r\,o\,o\,f.\; Let $n$ and $m$ be integers, such that $m$ is
even, $m \ge 2$, $n \ge 2m - 1$ and $(m-1)$ is a divisor of
$(n-1)$. Let $W$ be a fault-tolerant metric basis of $P_m
\boxtimes P_n$, and let $V$ be the vertex set of $P_m \boxtimes
P_n$.

We denote $k = \frac{n-m}{m-1}$. By Lemma~5 we have for all $t\in
\{0,\ldots,k-1\}$
$$
\left| V_{t(m-1)+1,\;(t+1)(m-1)} \bigcap W \right| \ge 2.
$$
By Lemma~8 we have
$$
\left| V_{n-m+1,\;n} \bigcap W \right| \ge 3.
$$

We consider two cases.

{\it Case 1}. If there exists $t\in \{0,\ldots,k-1\}$ such that
$$
\left| V_{t(m-1)+1,\;(t+1)(m-1)} \bigcap W \right| \ge 3,
$$
since $V$ is the union of sets, that are disjoint,
$$
V=\bigcup_{t=0}^{k-1} V_{t(m-1)+1,\;(t+1)(m-1)} \bigcup
V_{n-m+1,\;n},
$$
then
$$
|W| \ge 2(k-1)+3+3 = 2k+4.
$$

{\it Case 2}. We assume, that for all $t\in \{0,\ldots,k-1\}$,
\begin{equation}
\label{vrv_eq1} \left| V_{t(m-1)+1,\;(t+1)(m-1)} \bigcap W \right|
= 2.
\end{equation}
We first consider that $t = 0$:
$$
\left| V_{1,\;m-1} \bigcap W \right| = 2.
$$
Then Lemma~7 leads to $V_{1,\;m-1} \bigcap W \subset V_1$, in
particular
\begin{equation}
\label{vrv_eq2} \left| V_1 \bigcap W \right| = 2.
\end{equation}
We now take $t=1$ in~(\ref{vrv_eq1}) and we get
$$
\left| V_{m,\;2(m-1)} \bigcap W \right| = 2.
$$
Since $V_{2,\;m-1} \bigcap W = \emptyset$ we can notice, that
$$
\left| V_{2,\;2(m-1)} \bigcap W \right| = 2.
$$
Then Lemma~7 leads to $V_{2,\;2(m-1)} \bigcap W \subset V_m$, in
particular
\begin{equation}
\label{vrv_eq3} \left| V_{2,\;m} \bigcap W \right| = 2.
\end{equation}
Further it is analogically proved by mathematical induction, that
\begin{equation}
\label{vrv_eq4} \left| V_{t(m-1)+2,\;(t+1)(m-1)+1} \bigcap W
\right| = 2
\end{equation}
for all $t=1,\ldots,k-2$.

By Lemma~5 we have
\begin{equation}
\label{vrv_eq5} \left| V_{(k-1)(m-1)+2,\;k(m-1)+1} \bigcap W
\right| \ge 2
\end{equation}
and
\begin{equation}
\label{vrv_eq6} \left| V_{k(m-1)+2,\;n} \bigcap W \right| \ge 2.
\end{equation}
Since $V$ is the union of sets, that are disjoint,
$$
V=\bigcup_{t=0}^k V_{t(m-1)+2,\;(t+1)(m-1)+1} \bigcup V_1,
$$
and taking into account the above
(\ref{vrv_eq2})--(\ref{vrv_eq6}), we deduce
$$
|W| \ge 2k+4.
$$
According to the two cases above we have
$$
\beta'(P_m \boxtimes P_n) = |W| \ge 2k+4=2\frac{n-1}{m-1}+2.
$$
By Theorem~2 we have $\beta'(P_m \boxtimes P_n) \le
2\frac{n-1}{m-1}+2$. Hence
$$
\beta'(P_m \boxtimes P_n) = 2\frac{n-1}{m-1}+2.
$$

This proves the theorem.

Figure 2 shows graph $P_3 \boxtimes P_{11}$. Vertices of the
fault-tolerant metric basis are black, $\beta'(P_3 \boxtimes
P_{11})=12$.\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%fig2

%\input graph2.tex

\begin{center}
\begin{picture}(255,55)
\put(0,0){\circle*{6}} \put(25,0){\circle{6}}
\put(50,0){\circle*{6}} \put(75,0){\circle{6}}
\put(100,0){\circle*{6}} \put(125,0){\circle{6}}
\put(150,0){\circle*{6}} \put(175,0){\circle{6}}
\put(200,0){\circle*{6}} \put(225,0){\circle{6}}
\put(250,0){\circle*{6}} \put(0,25){\circle{6}}
\put(25,25){\circle{6}} \put(50,25){\circle{6}}
\put(75,25){\circle{6}} \put(100,25){\circle{6}}
\put(125,25){\circle{6}} \put(150,25){\circle{6}}
\put(175,25){\circle{6}} \put(200,25){\circle{6}}
\put(225,25){\circle{6}} \put(250,25){\circle{6}}
\put(0,50){\circle*{6}} \put(25,50){\circle{6}}
\put(50,50){\circle*{6}} \put(75,50){\circle{6}}
\put(100,50){\circle*{6}} \put(125,50){\circle{6}}
\put(150,50){\circle*{6}} \put(175,50){\circle{6}}
\put(200,50){\circle*{6}} \put(225,50){\circle{6}}
\put(250,50){\circle*{6}} \put(3,0){\line(1,0){19}}
\put(28,0){\line(1,0){19}} \put(53,0){\line(1,0){19}}
\put(78,0){\line(1,0){19}} \put(103,0){\line(1,0){19}}
\put(128,0){\line(1,0){19}} \put(153,0){\line(1,0){19}}
\put(178,0){\line(1,0){19}} \put(203,0){\line(1,0){19}}
\put(228,0){\line(1,0){19}} \put(3,25){\line(1,0){19}}
\put(28,25){\line(1,0){19}} \put(53,25){\line(1,0){19}}
\put(78,25){\line(1,0){19}} \put(103,25){\line(1,0){19}}
\put(128,25){\line(1,0){19}} \put(153,25){\line(1,0){19}}
\put(178,25){\line(1,0){19}} \put(203,25){\line(1,0){19}}
\put(228,25){\line(1,0){19}} \put(3,50){\line(1,0){19}}
\put(28,50){\line(1,0){19}} \put(53,50){\line(1,0){19}}
\put(78,50){\line(1,0){19}} \put(103,50){\line(1,0){19}}
\put(128,50){\line(1,0){19}} \put(153,50){\line(1,0){19}}
\put(178,50){\line(1,0){19}} \put(203,50){\line(1,0){19}}
\put(228,50){\line(1,0){19}} \put(0,3){\line(0,1){19}}
\put(25,3){\line(0,1){19}} \put(50,3){\line(0,1){19}}
\put(75,3){\line(0,1){19}} \put(100,3){\line(0,1){19}}
\put(125,3){\line(0,1){19}} \put(150,3){\line(0,1){19}}
\put(175,3){\line(0,1){19}} \put(200,3){\line(0,1){19}}
\put(225,3){\line(0,1){19}} \put(250,3){\line(0,1){19}}
\put(0,28){\line(0,1){19}} \put(25,28){\line(0,1){19}}
\put(50,28){\line(0,1){19}} \put(75,28){\line(0,1){19}}
\put(100,28){\line(0,1){19}} \put(125,28){\line(0,1){19}}
\put(150,28){\line(0,1){19}} \put(175,28){\line(0,1){19}}
\put(200,28){\line(0,1){19}} \put(225,28){\line(0,1){19}}
\put(250,28){\line(0,1){19}} \put(2,2){\line(1,1){21}}
\put(27,2){\line(1,1){21}} \put(52,2){\line(1,1){21}}
\put(77,2){\line(1,1){21}} \put(102,2){\line(1,1){21}}
\put(127,2){\line(1,1){21}} \put(152,2){\line(1,1){21}}
\put(177,2){\line(1,1){21}} \put(202,2){\line(1,1){21}}
\put(227,2){\line(1,1){21}} \put(2,27){\line(1,1){21}}
\put(27,27){\line(1,1){21}} \put(52,27){\line(1,1){21}}
\put(77,27){\line(1,1){21}} \put(102,27){\line(1,1){21}}
\put(127,27){\line(1,1){21}} \put(152,27){\line(1,1){21}}
\put(177,27){\line(1,1){21}} \put(202,27){\line(1,1){21}}
\put(227,27){\line(1,1){21}} \put(23,2){\line(-1,1){21}}
\put(48,2){\line(-1,1){21}} \put(73,2){\line(-1,1){21}}
\put(98,2){\line(-1,1){21}} \put(123,2){\line(-1,1){21}}
\put(148,2){\line(-1,1){21}} \put(173,2){\line(-1,1){21}}
\put(198,2){\line(-1,1){21}} \put(223,2){\line(-1,1){21}}
\put(248,2){\line(-1,1){21}} \put(23,27){\line(-1,1){21}}
\put(48,27){\line(-1,1){21}} \put(73,27){\line(-1,1){21}}
\put(98,27){\line(-1,1){21}} \put(123,27){\line(-1,1){21}}
\put(148,27){\line(-1,1){21}} \put(173,27){\line(-1,1){21}}
\put(198,27){\line(-1,1){21}} \put(223,27){\line(-1,1){21}}
\put(248,27){\line(-1,1){21}}
\end{picture}
%\caption{Граф $G_{3,12}$}
%\label{pic0_3_12}
%\end{center}
%\end{figure}
%\begin{center}
\vskip 4mm {\small{\it Fig 2}. The fault-tolerant metric basis for
graph $P_3 \boxtimes P_{11}$}
\end{center}

{\bf Conclusion.} Theorem~3 leads to the following inference. The
fault-tolerant metric basis for a partcular case of the king's
graph contains two times more vertices than the metric basis does.
Our conjecture consists of the statement that the upper bound for
the fault-tolerant metric dimension of the king's graph from
Theorem~2 is an exact value.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\input{02/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{02/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize




%\thispagestyle{empty}

\vskip 3mm

%\thispagestyle{empty}


\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. А. П.~Жабко.

\vskip 1mm

\noindent Статья поступила в~редакцию 11 декабря 2016~г.

\vskip 1mm

\noindent Статья принята к~печати 8 июня 2017~г.

}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vskip 5mm


%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak

%\vskip 3mm

%\textit{Буре Артем Владимирович}~--- аспирант; e-mail:
%bure.artem@gmail.com

%\vskip 2mm

%\emph{Bure Artem Vladimirovich}~--- post-graduate student; e-mail:
%bure.artem@gmail.com

%}
