

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Krilatov A. Yu. Optimal'nye strategii upravlenija transportnymi
potokami na seti iz parallel'nyh kanalov [Optimal strategies for
traffic flow management on the transportation network of parallel
links]. {\it Vestnik of Saint Petersburg University. Series 10.
Applied Mathematics. Computer Science. Control Processes}, 2014,
iss.~2, pp.~120--129. (In Russian)

2. Raj F. S., George A. On the metric dimension of few network
sheets. {\it Robotics, Automation, Control and Embedded Systems
--- RACE, Intern. conference on robotics. IEEE}, 2015, pp.~1--6.

3. Melter R. A., Tomescu I. Metric bases in digital geometry. {\it
Computer Vision, Graphics, and Image Processing}, 1984, vol.~25,
no.~1, pp.~113--121.

4. Chaudhry M. A., Javaid I., Salman M. Fault-tolerant metric and
partition dimension of graphs. {\it Utilitas Mathematica}, 2010,
vol.~83, pp.~187--199.

5. Barrag\'an-Ram\'{\i}rez G. A., Rodr\'{\i}guez-Vel\'azquez J. A.
The local metric dimension of strong product graphs. {\it Graphs
and Combinatorics}, 2016, vol.~32, no.~4, pp.~1263--1278.

6. Harary F., Melter R. A. On the metric dimension of a graph.
{\it Ars Combinatoria}, 1976, vol.~2, pp.~191--195.

7. Slater P. J. Leaves of trees. {\it Proc. 6th Southeastern
Conference on Combinatorics, Graph Theory and Computing}, 1975,
pp.~549--559.

8. Khuller S., Raghavachari B., Rosenfeld A. Landmarks in graphs.
{\it Discrete Applied Mathematics}, 1996, vol.~70, no.~3,
pp.~217--229.

9. Chartrand G., Eroh L., Johnson M. A., Oellermann O. R.
Resolvability in graphs and the metric dimension of a graph. {\it
Discrete Applied Mathematics}, 2000, vol.~105, pp.~99--113.

10. Seb{\"o} A., Tannier E. On metric generators of graphs. {\it
Mathematics of Operations Research}, 2004, vol.~29, no.~2,
pp.~383--393.

11. Fehr M., Gosselin S., Oellermann O. The metric dimension of
Cayley digraphs. {\it Discrete Mathematics}, 2006, vol.~306,
pp.~31--41.

12. Hernando C., Mora M., Slater P. J., Wood D. R. Fault-tolerant
metric dimension of graphs. {\it Proc. Intern. conference
Convexity in Discrete Structures, Ramanujan Mathematical Society
Lecture Notes}, 2008, no.~5, pp.~81--85.

13. Okamoto F., Phinezy B., Zhang P. The local metric dimension of
a graph. {\it Mathematica Bohemica}, 2010, vol.~135, no.~3,
pp.~239--255.

14. Bollobas B., Mitsche D., Pralat P. {\it Metric dimension for
random graphs. arXiv preprint arXiv:1208.3801}, 2012 (Available
at: https://arxiv.org/pdf/1208.3801.pdf. (accessed: 1.12.2016).)

15. Epstein L., Levin A., Woeginger G. J. The (weighted) metric
dimension of graphs: hard and easy cases. {\it Algorithmica},
2015, vol.~72, no.~4, pp.~1130--1171.

16. Imran M. On dimensions of some infinite regular graphs
generated by infinite hexagonal grid. {\it Utilitas Mathematica},
2013, vol.~92, pp.~3--15.

17. Klein D. J., Yi E. A comparison on metric dimension of graphs,
line graphs, and line graphs of the subdivision graphs. {\it
European Journal of Pure and Applied Mathematics}, 2012, vol.~5,
no.~3, pp.~302--316.

18. Zejnilovi{\'c} S., Mitsche D., Gomes J., Sinopoli B. Extending
the metric dimension to graphs with missing edges. {\it
Theoretical Computer Science}, 2016, vol.~609, pp.~384--394.

19. Javaid I., Salman M., Chaudhry M. A., Shokat S.
Fault-tolerance in resolvability. {\it Utilitas Mathematica},
2009, vol.~80, pp.~263--275.

20. Rodr\'{\i}guez-Vel\'azquez J. A., Kuziak D., Yero I. G.,
Sigarreta J. M. The metric dimension of strong product graphs.
{\it Carpathian Journal of Mathematics}, 2015, vol.~31, no.~2,
pp.~261--268.



\vskip 2mm

{\bf For citation:}  Voronov   R. V. The fault-tolerant metric
dimension of the king's graph. {\it Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02



}
