
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \emph{Олемской~И.~В.} Модификация алгоритма выделения
структурных особенностей~// Вестн.\linebreak С.-Петерб. ун-та.
Сер.~10. Прикладная математика. Информатика. Процессы управления.
2006. Вып.~2. С.~55--64.

2. \emph{Olemskoy~I.~V.}  Structural approach to the design of
                     explicit one-stage methods~// Com\-put.
                     \,Math.\,Math.\,Phys. 2003. Vol.~43. P.~918--931.


3. \emph{Eremin~A.~S., Olemskoy~I.~V.} An embedded method for
integrating systems of struc\-tu\-ra\-lly separated ordinary
differential equations~// Comput.\,Math.\,Math.\,Phys. 2010.
Vol.~50. N~3. P.~414--427.


4. \emph{Olemskoy~I.~V.}  A fifth-order five-stage embedded method
of the Dormand---Prince type~// Comput. Math. Math. Phys. 2005.
Vol.~45. P.~1140--1150.


5. \emph{Olemskoy~I.~V.} Fifth-order four-stage
                            method for
                           numerical integration of spe\-ci\-al
                           sys\-tems~// Comput. Math. Math. Phys. 2002. Vol.~42. P.~1135--1145.

6. \emph{Olemskoy~I.~V., Eremin~A.~S., Ivanov~A.~P.}\ Sixth order
method with six stages for integrating special systems of ordinary
differential equations~// 2015 International Conference on
Stability and Control Processes in memory of V.~I.~Zubov.
SCP--2015. Proceedings. 2015. P.~110--113.


7. \emph{Olemskoy~I.~V., Eremin~A.~S.} An embedded pair of method
of orders 6(4) with 6~stages for special systems of ordinary
differential equations~// International Conference of Numerical
Analysis and Applied Mathematics. ICNAAM 2016. Rodos: American
Institute of Physics, 2016. Vol.~1738. Art.~N~160010.



8. \emph{Olemskoy~I.~V., Eremin~A.~S., Kovrizhnykh~N.~A.}
 Embedded methods of order six for special systems of
ordinary differential equations~// Applied Mathematical Sciences.
2017. Vol.~11(1). P.~31--38.
https://doi.org/10.12988/ams.2017.610260

9. \emph{Olemskoy~I.~V., Kovrizhnykh~N.~A.}\ A family of
sixth-order methods with six stages~// Вестн. С.-Петерб.ун-та.
Прикладная математика. Информатика. Процессы управления. 2018.
Т.~14. Вып.~3. С.~215--229.
https://doi.org/10.21638/11702/spbu10.2018.303

10. \emph{Eremin~A.~S., Kovrizhnykh~ N.~A., Olemskoy~ I.~V.}
 An explicit one-step multischeme sixth order method for
systems of special structure~// Applied Mathematics and
Compu\-ta\-tion. 2018. Vol.~347. P.~853--864.
https://doi.org/10.1016/j.amc.2018.11.053


11. \emph{Hairer~E., Nersett~S.~P., Wanner~G.} Solving ordinary
differential equation~I: Nonstiff problems. 3~ed. Berlin;
Heidelberg: Springer-Verlag, 2008. 528~p.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 ноября 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Олемской Игорь Владимирович}~---  д-p физ.-мат.
наук, проф.; i.olemskoj@spbu.ru

\vskip2mm \textit{Коврижных Николай Александрович}~---  канд.
физ.-мат. наук, ассистент; sagoyewatha@mail.ru

\vskip2mm \textit{Фирюлина Оксана Сергеевна}~---  канд. физ.-мат.
наук, ст. преподаватель; firyulina.oxana@mail.ru

}
