
{\normalsize

\vskip 6mm

\noindent{\bf Two-parametric family of sixth order numerical
methods for solving systems\\ of ordinary differential equations%$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it I.~V.~Olemskoy, N.~A.~Kovrizhnykh, O.~S.~Firyulina%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,

\noindent%
%\hskip2.45mm%
St.\,Petersburg, 199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Olemskoy ~I. ~V., Kovrizhnykh
~N. ~A., Firyulina ~O.~S. Two-parametric family of sixth order
numerical methods for solving systems of ordinary differential
equations. {\it Vestnik of Saint~Petersburg University. Applied
Mathematics. Computer Science. Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p7}--\pageref{p7e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum07  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The paper is devoted to the construction
of economical explicit sixth-order numerical method for solving
structurally partitioned systems of ordinary differential
equations. The general form of the method, which algorithmically
uses the properties of the system structure, is presented.
Conditions of order six, which the parameters of the method must
satisfy, are derived. The simplifying conditions are found, which
reduces the large nonlinear system of order conditions to a
solvable smaller system. A solution with two free parameters is
obtained. Economic explicit sixth-order schemes for systems of
ordinary differential equations are presented. Numerical tests to
compare to known explicit sixth-order one-step methods are
performed.\\[1mm]
\textit{Keywords}: order, the order conditions, simplifying
conditions.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Olemskoy~I.~V. Modifikatsiya algoritma vydeleniya strukturnykh
osobennostei [Modi\-fi\-ca\-tion of structural properties
detection algorithm]. {\it Vestnik of Saint Petersburg
Univer\-si\-te\-ty. Series~10. Applied Mathematics. Computer
Sciences. Control Processes}, 2006, iss.~2, pp.~55--64. (In
Russian)

2. Olemskoy~I.~V.  Structural approach to the design of
          explicit one-stage methods. {\it Com\-put.
         \,Math.\,Math.\,Phys.}, 2003, vol.~43, pp.~918--931.


3. Eremin~A.~S., Olemskoy~I.~V. An embedded method for integrating
systems of struc\-tu\-ra\-lly separated ordinary differential
equations. \emph{Comput.\,Math.\,Math.\,Phys.}, 2010, vol.~50,
no.~3, pp.~414--427.


4. Olemskoy~I.~V.  A fifth-order five-stage embedded method of the
Dormand---Prince type. \emph{Comput. Math. Math. Phys.}, 2005,
vol.~45, pp.~1140--1150.


5. Olemskoy~I.~V. Fifth-order four-stage method for numerical
integration of spe\-ci\-al sys\-tems. \emph{Comput. Math. Math.
Phys.}, 2002, vol.~42, pp.~1135--1145.

6. Olemskoy~I.~V., Eremin~A.~S., Ivanov~A.~P.\ Sixth order method
with six stages for integrating special systems of ordinary
differential equations. \emph{2015 International  Conference on
Stability and Control Processes in memory of V.~I.~Zubov.
SCP--2015. Proceedings}, 2015, pp.~110--113.


7. Olemskoy~I.~V., Eremin~A.~S.\ An embedded pair of method of
orders 6(4) with 6 stages for special systems of ordinary
differential equations. \emph{International Conference of
Numerical Analysis and Applied Mathematics. ICNAAM 2016}. Rodos,
American Institute of Physics Press, 2016, vol.~1738,
~art.~no.~160010.


8. Olemskoy~I.~V., Eremin~ A.~S., Kovrizhnykh~N.~A. \ Embedded
methods of order six for special systems of ordinary differential
equations. \emph{Applied Mathematical Sciences}, 2017, vol.~11(1),
pp.~31--38. https://doi.org/10.12988/ams.2017.610260

9. Olemskoy~I.~V., Kovrizhnykh~N.~A.  A family of sixth-order
methods with six stages. {\it Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Sciences.
Control Processes}, 2018, vol.~14, iss.~3, pp.~215--229. %\\
https://doi.org/10.21638/11702/spbu10.2018.303

10. Eremin~A.~S., Kovrizhnykh~ N.~A., Olemskoy~ I.~V. An explicit
one-step multischeme sixth order method for systems of special
structure. \emph{Applied Mathematics and Compu\-ta\-ti\-on}, 2018,
vol.~347, pp.~853--864. https://doi.org/10.1016/j.amc.2018.11.053


11. Hairer~E., Nersett~S.~P., Wanner~G. \emph{Solving ordinary
differential equation~I: Nonstiff problems}. 3~ed. Berlin,
Heidelberg, Springer-Verlag Press, 2008, 528~p.


\vskip1.5mm Received:  November 02, 2019.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%


\vskip2mm \textit{Igor V. Olemskoy} ---  Dr. Sci. in Physics and
Mathematics, Professor; i.olemskoj@spbu.ru

\vskip2mm \textit{Nikolai A. Kovrizhnykh} ---  PhD in Physics and
Mathematics, Assistant; sagoyewatha@mail.ru

\vskip2mm \textit{Oxana S. Firyulina} ---  PhD in Physics and
Mathematics, Senior Lecturer; firyulina.oxana@mail.ru

}
