
{\small

\vskip6 mm \noindent \textbf{Литература}

}

\vskip2 mm

{\footnotesize


1. IPCC, 2012: Managing the risks of extreme events and disasters to advance climate change adaptation: A special report of Working Groups I and II of the Intergovernmental Panel on Climate Change / eds: С.~B.~Field, V.~Barros, T.~F.~Stocker, D.~Qin, D.~J.~Dokken, K.~L.~Ebi, M.~D.~Mastrandrea, K.~J.~Mach, G.-K.~Plattner, S.~K.~Allen, M.~Tignor, P.~M.~Midgley. Cambridge, UK; New York, USA: Cambridge University Press, 2012. 582~p.

2. {\it Дробжева Я. В., Волобуева О. В.}
Метеорологические прогнозы и их экономическая полезность: учеб. пособие. СПб.: Изд-во <<Адмирал>>, 2016. 116~с.

3. {\it Вильфанд Р. М., Страшная А. И., Береза О. В.}
О динамике агроклиматических показателей условий сева, зимовки и формирования урожая основных зерновых культур // Труды Гидромет\-цент\-ра России. 2016. Вып.~360. С.~45--78.

4. {\it Zhang F., Chen Y., Zhang J., Guo E., Wang R., Li D. }
Dynamic drought risk assessment for maize based on crop simulation model and multi-source drought indices // Journal of Cleaner Production. 2019. Vol.~233. P.~100--114.

5. {\it Liu X., Guo P., Tan Q., Xin J., Li Y., Tang Y. }
Drought risk evaluation model with interval number ranking and its application // Science of the Total Environment. 2019. Vol.~685. P.~1042--1057.

6. {\it Страшная А. И., Береза О. В., Тарасова Л. Л., Максименкова Т. А., Шуль\-гин~И.~А., Пу\-ри\-на~И.~Э., Чекулаева Т. С.}
Современное состояние и проблемы агрометеорологического обеспечения сельского хозяйства России // Гидрометеорологические исследования и прогнозы. 2019. №~4~(374). С.~219--240.

7. {\it Park S., Im J., Park S., Rhee J.}
Drought monitoring using high resolution soil moisture through multi-sensor satellite data fusion over the Korean peninsula // Agricultural and Forest Meteorology. 2017. Vol.~237. P.~257--269.

8. {\it Gobbett D. L., Nidumolu U., Crimp S.}
Modelling frost generates insights for managing risk of minimum temperature extremes // Weather and Climate Extremes. 2020. Vol.~27. N~100176.

9. {\it Crimp S., Bakar K. S., Kokic P., Jin H., Nicholls N., Howden M.}
Bayesian space-time model to analyse frost risk for agriculture in Southeast Australia // International Journal of Climatology. 2015. Vol.~35. P.~2092--2108.

10. {\it Van Hinsbergen C., van Lint J., van Zuylen H.}
 Bayesian committee of neural networks to predict travel times with confidence intervals // Transportation Research. Pt C: Emerging Technologies. 2009. Vol.~17. P.~498--509.

11. {\it Xiao L., Liu L., Asseng S., Xia Y., Tang L., Liu B., Cao W., Zhu Y.}
Estimating spring frost and its impact on yield across winter wheat in China // Agricultural and Forest Meteorology. 2018. Vol.~260--261. P.~154--164.

12. {\it Фролов А. В., Страшная А. И.}
 О засухе 2010 года и ее влиянии на урожайность зерновых культур // Анализ условий аномальной погоды на территории России летом 2010 года / под ред. Н.~П.~Шакиной. М.: Изд-во <<Триада ЛТД>>, 2011. С.~22--31.

13. {\it Якушев В. П., Буре В. М., Митрофанова О. А., Митрофанов Е. П.}
К вопросу автоматизации построения вариограмм в задачах точного земледелия // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~2. С.~177--185. %\\
https://doi.org/10.21638/11701/spbu10.2020.209

14. {\it Буре В. М., Канаш Е. В., Митрофанова О. А.}
Анализ характеристик цвета растений по аэрофотоснимкам с различными факторами качественных показателей // Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2017. Т.~13. Вып.~3. С.~278--285. %\\
https://doi.org/10.21638/11701/spbu10.2017.305


\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 27 декабря 2020~г.

Cтатья принята к~печати 5 апреля 2021~г.

\vskip6mm К~о~н~т~а~к~т~н~а~я \ и~н~ф~о~р~м~а~ц~и~я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Якушев Виктор Петрович}  --- акад. РАН, д-р сельхоз. наук; vyakushev@agrophys.com

\vskip2mm\textit{Буре Владимир Мансурович}  --- д-р техн. наук, проф.; vlb310154@gmail.com

\vskip2mm\textit{Митрофанова Ольга Александровна}  --- канд. техн. наук; omitrofa@gmail.com

\vskip2mm\textit{Митрофанов Евгений Павлович}  --- мл. науч. сотр.; mjeka@bk.ru \par
%
}
