
{\normalsize

\vskip 6mm

\noindent{\bf The study of nonlinear deformation of a plane\\ %
with an elliptical inclusion for harmonic materials%$\,^*$%
}

}

\vskip 2.5mm

{\small

\noindent{\it V.\,M. Malkov, Yu.\,V. Malkova%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2.5mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N~18-71-00006).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}  Malkov V.\,M.,  Malkova Yu.\,V.
The study of nonlinear deformation of a plane with an elliptical
inclusion for harmonic materials. {\it Vestnik of
Saint~Pe\-ters\-burg University. Ap\-plied Mathe\-ma\-tics.
Computer Science. Control Processes}, \issueyear, vol.~16,
iss.~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum03  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Analytical methods are used to study
nonlinear deformation of a plane with an elliptical inclusion. The
elastic properties of a material of the plane and inclusion are
described with a semi-linear material. The external load is
constant no\-mi\-nal~(Piola) stresses at infinity. At the
inclusion boundary, the conditions of the continuity for stresses
and displacements are satisfied. Semi-linear material belongs to
the class of harmonic, the methods of the theory of functions of a
complex variable are applicable to solving nonlinear plane
problems. Stresses and displacements are expressed in terms of two
analytical functions of a complex variable, determined by the
boundary conditions on the inclusion contour. It is assumed that
the stress state of an inclusion is uniform (the tensor of nominal
stresses is constant). This hypothesis made it possible to reduce
the difficult nonlinear problem of conjugation of two elastic
bodies to the solution of two more simpler problems for a plane
with an elliptical hole. The validity of this hypothesis is
justified by the fact that the constructed solution exactly
satisfies all the equations and boundary conditions of the
problem. The same hypothesis was used earlier by other authors to
solve linear and nonlinear problems of an elliptical inclusion. In
the article, a comparative analysis of the stresses and strains is
carried out for two models of harmonic materials~--- semi-linear
and John's. Various variants of values of elasticity parameters of
the inclusion and matrix have been considered.\\[1mm]
\textit{Keywords}: nonlinear plane problem, elliptical inclusion,
harmonic material, method of complex-variable functions.
\par}

\vskip 5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {John F.} Plane strain problems for a perfectly elastic
material of harmonic type. \textit{ Commun. Pure and Applied
Mathematics}, 1960, vol.~13, no.~2, pp.~239--296.

2. {Lurie A.\,I.} \textit {Nelineynaya teoria uprugosti
$[$Non-linear elasticity$]$}. Moscow, Nauka Publ., 1980, 512~p.
(In Russian)

3. {Lurie A.\,I.} {\it Teoria uprugosti $[$Theory of
elasticity$]$}. Moscow, Nauka Publ., 1970, 940~p. (In Russian)

4. {Morozov N.\,F.} {\it Matematicheskie voprosy teorii treschin
$[$Mathematical problems theory of cracks$]$}. Moscow, Nauka
Publ., 1984, 256~p. (In Russian)

5. { Zubov L.\,M.}  \textit{Nonlinear theory of dislocations and
declinations in elastic bodies}. Berlin, Springer Publ., 1997,
205~p.

6. {Malkov V.\,M., Malkova Yu.\,V.} Ploskye zadachi uprugosti dlya
polulineynogo materiala [Plane problems of elasticity for
semi-linear material].  {\it Vestnik of Saint Petersburg
University. Se\-ries~1. Ma\-the\-ma\-tics. Mechanics. Astronomy},
2012, iss.~3, pp.~93--106. (In Russian)

7. {Malkov V.\,M., Malkova Yu.\,V.} Ploskye zadachi o
sosredotochennykh silah dlya polulineynogo materiala [Plane
problems on concentrated forces for semi-linear material]. {\it
Vestnik of Saint Petersburg University. Se\-ries~10. Applied
Mathematics. Computer Science. Control Processes}, 2013, iss.~3,
pp.~83--96. (In Russian)

8. {Malkov V.\,M., Malkova Yu.\,V.} Stresses analysis of a plane
with elliptical inclusion for the model of the semi-linear
material. \textit{Intern. Conference on Mechanics --- Eigth
Polyakhov's Reading, AIP Conference Proceedings 1959}. 2018. Art.
no.~070022, pp.~1--8. https://doi.org/10.1063/1.5034697

9. {Varley E., Cumberbatch E}. Finite deformation of elastic
materials surrounding cylindrical holes.  {\it Journal of
Elasticity}, 1980, vol.~10, no.~4, pp.~341--405.

10. {Ru C.\,Q}. On complex-variable formulation for finite plane
elastostatics of harmonic materials. {\it Acta Mechanica}, 2002,
vol.~156, no.~3--4, pp.~219--234.

11. {Ru C.\,Q., Schiavone P., Sudak L.\,J., Mioduchowski A.}
Uniformity of stresses inside an elliptic inclusion in finite
plane elastostatics. {\it Intern. Journal of Non-linear
mechanics}, 2005, vol.~38, no.~2--3, pp.~281--287.

12. {Malkov V.\,M., Malkova Yu.\,V.} Ploskaya zadacha nelineynoy
uprugosti dlya garmonicheskogo materiala [Plane problem of
non-linear elasticity for harmonic material]. {\it Vestnik of
Saint Petersburg University. Se\-ries~1. Mathematics. Mechanics.
Astronomy}, 2008, iss.~3, pp.~114--126. (In Russian)

13. {Malkova Y.\,V., Malkov V.\,M.} Large deformation  of a plate
with an elastic elliptic inclusion for John's harmonic material.
\textit{``Stability and Control Processes'' in memory of V.\,I.
Subov (SCP), 2015 Intern. Conference}. Saint Petersburg, 2015, pp.
410--413.

14. {Domanskaia T.,  Malkov V.,  Malkova Yu.} Bi-material plane of
John's harmonic material with a point force at interface.
\textit{XXIV Intern. Congress of Theor. and Appl. Mech. (ICTAM)},
21--26 August 2016. Montreal,  Canada, 2016, pp.~1958--1959.

15. {Malkov V.\,M., Malkova Yu.\,V., Domanskaya T.\,O.} Analiz
napryazheniy dvuhkomponentnoy ploskosti i poluploskosti pri
deystvii sosredotochennoy sily dlya dvuh modeley garmonicheskogo
materiala [Analysis of stresses of bi-material plane and
half-plane at action of a point force for two models of harmonic
materials]. {\it Vestnik of Saint Petersburg University.
Se\-ries~10. Applied Mathematics. Computer Science. Control
Processes}, 2016, iss.~1, pp.~38--52. (In Russian)

16. {Malkov V.\,M., Malkova Yu.\,V.} Modelirovanie nelineinoy
deformacii ploskosti s ellipticheskim otverstiem ili vklucheniem
garmonicheskim materialom Djona [Modeling nonlinear deformation of
a plate with an elliptic hole or inclusion by John's harmonic
material]. {\it Vestnik of Saint Petersburg University.
Mathematics. Mechanics. Astronomy}, 2017, vol.~4(62), iss.~1,
pp.~121--130.\\
https://doi.org/10.21638/11701/spbu01.2017.114 (In Russian)%\pagebreak

17. {Malkov V.\,M.,  Malkova Yu.\,V.} Modeling nonlinear
deformation of a plate with an elliptic inclusion by John's
harmonic material. {\it Vestnik Saint~Pe\-ters\-burg University.
Mathematics}, 2017, vol.~50, iss.~1, pp.~74--81.

18. { Wang Xu.} Three-phase  elliptical inclusion with internal
uniform hydrostatic stresses in finite plane elastostatics. {\it
Acta Mechanica}, 2011, vol.~219, no.~1--2, pp.~93--97.

19. {Wheeler L.\,T.} Finite deformation of a harmonic elastic
medium containing an ellipsoidal cavity. {\it Intern. Journal of
Solids Struct.}, 1985, vol.~21, pp.~799--804.

20.  {Malkov V.\,M., Malkova Yu.\,V., Petrukhin R.\,R.}
Vzaimodeistvie ellipticheskogo otverstiya s megfaznoy  granicei
dvuh poluploskostey [Interaction of an elliptic hole with
interface of two bonded half-planes].  {\it Vestnik of Saint
Petersburg University. Se\-ries~10. Applied Mathematics. Computer
Science. Control Processes}, 2016, iss.~3, pp.~73--87. (In
Russian)

21. {Malkov V.\,M., Malkova Yu.\,V.} Deformaciya plastinu s
uprugim ellipticheskim vklucheniem [De\-for\-mation of a plate
with elliptic elastic inclusion].   {\it Vestnik Saint Petersburg
University. Mathematics. Mechanics. Astronomy}, 2015, vol.~2(60),
iss.~4, pp.~617--632. (In Russian)

22. {Malkov V.\,M.} \textit{Vvedenie v nelineynuyu uprugost
$[$Introduction to non-linear elasticity$]$}. Saint Petersburg,
Saint Petersburg University Press, 2010, 276~p. (In Russian)

23. {Muskhelishvili N.\,I.} \textit{Nekotorye osnovnye zadachi
matematicheskoy teorii uprugosti $[$Some basic problems of
mathematical theory of elasticity$]$}. Moscow, Nauka Publ., 1966,
708~p. (In Russian)



\vskip 1.5mm

Received:  June 16, 2020.

Accepted: October 23, 2020.
%
%
\vskip4.2mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:
%
%
\vskip2mm \textit{Venyamin M. Malkov} --- Dr. Sci. in Physics and
Mathematics, Professor; v.malkov@spbu.ru
%
\vskip2mm \textit{Yulia V. Malkova } --- PhD in Physics and
Mathematics, Associate Professor; y.malkova@spbu.ru\par
%
}
