
{\small

\vskip6mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. \emph{Moreno J. L.} Foundations of sociometry:
anintroduction // Sociometry. 1941. Vol.~4~(1). P.~15--35.

2. \emph{Campion M. A., Medsker G. J., Higgs A. C.} Relations
between workgroup characteristics and effectiveness: implications
for design in effective workgroups // Pers. Psychol. 1993.
Vol.~46~(4). P.~823--847.

3. \emph{Guti\'{e}rrez J. H., Astudillo C. A.,
Ballesteros-P\'{e}rez P., Mora-Meli\'{a} D., Candia-V\'{e}jar A.}
The multiple team formation problem using sociometry// Computers
\& Operations Research. 2016. Vol.~75. P.~150--162.

4. \emph{Agust\'{i}n-Blas L. E., Salcedo-Sanz S., Ortiz-Garc\'{i}a
E. G., Portilla-Figueras A., P\'{e}rez-Belli\-do~A.~M.,}
\emph{Jim\'{e}nez-Fern\'{a}ndez S.} Team formation based on group
technology: a hybrid grouping gene\-tic algorithm approach //
ComputOperRes. 2011. Vol.~38~(2). P.~484--495.

5. \emph{Chen R.-C.} Grouping optimization based on social
relationships // Mathematical Problems in Engineering. 2012. Vol.~2012. Art.~ID~170563. P.~1--19.

6. \emph{Chen R.-C., Li J. Y., Ma N. J., Chang Y. T.} Application
of sociometry and genetic algorithm to selection of classofficers
// Information (Japan). 2013. Vol.~16~(2A). P.~1233--1241.

7. \emph{Новиков Д. А.} Теория управления организационными
системами. 2-е изд. М.: Физматлит, 2007. 584~с.

8. \emph{Ballesteros-P\'{e}rez P., Gonz\'{a}lez-Cruz M. C.,
Fern\'{a}ndez-Diego~M.} Proposal for a new method using
sociometric techniques for optimal workgroups // Proceedings of the
18$^{\rm th}$ International congress on project management
and engineering. Alca\~{n}iz, 2014. P.~001--002.

9. \emph{Ballesteros-P\'{e}rez P., Gonz\'{a}lez-Cruz M. C.,
Fern\'{a}ndez-Diego~M.} Human resource allocation management in
multiple projects using sociometric techniques // Intern. Journal
of Proj. Manag. 2012. Vol.~30~(8). P.~901--913.

10. \emph{Губко М. В., Новиков Д. А.} Теория игр в управлении
организационными системами. М.: Синтег, 2002. 138~c.

11. \emph{Мишин С. П.} Оптимальные иерархии управления в
экономических системах. М.: ПМСОФТ, 2004. 190~c.

12. \emph{Васин А. А.} Некооперативные игры в природе и обществе.
М.: МАКС Пресс, 2005. 412~с.

13. \emph{Fudenberg D., Tirole J.} Game theory. Cambridge: MIT
Press, 1995. 604~p.

14. \emph{Myerson R. B.} Game theory: analysis of conflict.
London: Harvard University Press, 1991. 600~p.

15. \emph{Potters J., Sefton M., Heijden E.} Hierarchy and
opportunism in teams: Discussion
paper. Tilburg: Tilburg University.
2005. N~2005--109. 32~p.

16. \emph{Milgrom P., Roberts J.} Economics. Organization and
management. New York.: Prentice-Hall, 1991.~621~p.

17. \emph{Camerer C.} Behavioral game theory. Experiments in
strategic interaction. Princeton: Princeton University Press,
2003. 568~p.

18. \emph{Новиков Д. А., Чхартишвили А. Г.} Рефлексивные игры. М.:
Синтег, 2003. 149~c.

19. \emph{Губко М. В.} Математические модели оптимизации
иерархических структур. М.: ЛЕНАНД, 2006. 264~с.

20. \emph{Новиков Д. А.} Механизмы функционирования многоуровневых
организационных систем. М.: Фонд <<Проблемы управления>>, 1999.
161~с.

21. \emph{Караваев А. П.} Модели и методы управления составом
активных систем. М.: ИПУ РАН, 2003. 151~с.

22. \emph{Storer N. W., Crane D.} Invisible colleges. Diffusion of
knowledge in scientific communities // Medical History. 1977. Vol.~21. P.~221--222.

23. \emph{Van Raan A. F. J.}  Measurement of central aspects of
scientific research: performance, interdisciplinarity, structure
// Measurement: interdisciplinary research and perspectives. 2005.
Vol.~3~(1). P.~1--19.

24. \emph{Andr\'{e}s A.} Measuring academic research. Oxford:
Chandos Publ., 2009. 186~p.

25. \emph{Савицкая Д. В.} Нормальная форма (0,1)-матриц и
алгоритмы ее построения // Вестник Санкт-Петербургского университета. Сер.~10. Прикладная математика.
Информатика. Процессы управления. 2008. Вып.~4. С.~85--97.

26. \emph{Кормен Т. Х., Лейзерсон Ч. И., Ривест Р. Л., Штайн~К.}
Алгоритмы: построение и анализ. 2-е изд. / пер. с англ. И.~В.~Красикова, Н.~А.~Ореховой, В.~Н.~Романова; под ред.
И.~В.~Красикова. М.: Изд-во <<Вильямс>>, 2006. 1296~с.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 31 мая 2022~г.

Cтатья принята к~печати 1 сентября 2022~г.

\vskip4.5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip1.5%2
mm \textit{Лежнина Елена Александровна} --- канд. физ.-мат. наук, доц.;
e.lezhnina@spbu.ru

\vskip1.5%2
mm \textit{Хитров Геннадий Михайлович} --- канд. физ.-мат. наук, доц.;
chitrow@gmail.com

\vskip1.5%2
mm \textit{Калинина Елизавета Александровна} --- д-р физ.-мат. наук, проф.;
e.kalinina@spbu.ru

\vskip1.5%2
mm \textit{Кононов Иван Александрович} --- студент; st087920@student.spbu.ru


}
