
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Working groups: creation and management %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it E. A. Lezhnina, G. M. Khitrov, E. A. Kalinina, I.
A. Kononov %
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St~Petersburg State University, 7--9, Universitetskaya nab., St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:} Lezhnina E. A., Khitrov G. M.,
 Kalinina E. A., Kononov I. A. Working groups: creation and
management. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p14}--\pageref{p14e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum14 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent In modern management, one of the most popular and effective
approaches to organizing activities is the creation of temporary
working groups. An important indicator is the effectiveness of
such groups, which strongly depends on the internal structure of
the working group and the relationship between team members. For
the effective functioning of the group, it is necessary that the
group consists of a leader and subordinates. The artificial
appointment of a team leader often proves ineffective. The article
solves the problem of dividing the team into working groups,
taking into account the relationship between individual
personalities. Two algorithms are proposed: the first one divides
the team into separate groups of possible leaders and
subordinates, the second one makes effective working groups. The
effectiveness of the group is calculated based on the ee
efficiency function, which takes into account interpersonal
relationships. Practical and numerical experiments were carried
out to verify the adequacy of the model.\\[1mm]
\textit{Keywords}: working groups, adjacency matrix, hierarchical
clustering algorithm.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Moreno J. L. Foundations of sociometry: anintroduction.
\emph{Sociometry}, 1941, vol.~4~(1), pp.~15--35.

2. Campion M. A., Medsker G. J., Higgs A. C. Relations between
workgroup characteristics and effectiveness: implications for
design in effective workgroups. \emph{Pers. Psychol.}, 1993,
vol.~46~(4), pp.~823--847.

3. Guti\'{e}rrez J. H., Astudillo C. A., Ballesteros-P\'{e}rez P.,
Mora-Meli\'{a}~D., Candia-V\'{e}jar~A. The multiple team formation
problem using sociometry. \emph{Computers $\&$ Operations Research},
2016, vol.~75, pp.~150--162.

4. Agust\'{i}n-Blas L. E., Salcedo-Sanz S., Ortiz-Garc\'{i}a~E.~G., Portilla-Figueras~A., P\'{e}rez-Bellido~ A.~M.,
Jim\'{e}nez-Fern\'{a}ndez~S. Team formation based on group
technology: a hybrid grouping genetic algorithm approach.
\emph{ComputOperRes}, 2011, vol.~38~(2), pp.~484--495.

5. Chen R.-C. Grouping optimization based on social relationships.
\emph{Mathematical Problems in Engineering}, 2012, vol.~2012, Art.~ID~170563, pp.~1--19.

6. Chen R.-C., Li J. Y., Ma N. J., Chang Y. T. Application of
sociometry and genetic algorithm to selection of classofficers.
\emph{Information (Japan)}, 2013, vol.~16~(2A), pp.~1233--1241.

7. Novikov D. A. \emph{Teoriia upravleniia organizatsionnymi
sistemami $[$Theory of management of organizational systems$]$}.
2$^{\rm nd}$~ed. Moscow, Physmathlit Publ., 2007, 584~p. (In Russian)

8. Ballesteros-P\'{e}rez P., Gonz\'{a}lez-Cruz M. C.,
Fern\'{a}ndez-Diego M. Proposal for a new method using sociometric
techniques for optimal workgroups. \emph{Proceedings of the
18$^{th}$ International congress on project
management and engineering}. Alca\~{n}iz, 2014, pp.~001--002.

9. Ballesteros-P\'{e}rez P., Gonz\'{a}lez-Cruz M. C.,
Fern\'{a}ndez-Diego M. Human resource allocation management in
multiple projects using sociometric techniques. \emph{Intern.
Journal of Proj. Manag.}, 2012, vol.~30~(8), pp.~901--913.

10. Gubko M. V., Novikov D. A. \emph{Teoriia igr v upravlenii
organizatsionnymi sistemami $[$Game theory in the management of
organizational systems$]$}. Moscow, Sinteg Publ., 2002, 138~p. (In
Russian)

11. Mishin S. P. \emph{Optimal'nye ierarhii upravleniia v
ekonomicheskih sistemah $[$Optimal management hierarchies in
economic systems$]$}. Moscow, PMSOFT Publ., 2004, 190~p. (In
Russian)

12. Vasin A. A. \emph{Nekooperativnye igry v prirode i obshchestve
$[$Non-cooperative games in nature and society$]$}. Moscow, MAKS
Press, 2005, 412~p. (In Russian)

13. Fudenberg D., Tirole J.\emph{ Game theory.} Cambridge, MIT
Press, 1995, 604~p.

14. Myerson R. B. \emph{Game theory: analysis of conflict.}
London, Harvard University Press, 1991, 600~p.

15. Potters J., Sefton M., Heijden E. \emph{Hierarchy and
opportunism in teams}. Discussion paper. Tilburg, Tilburg University Press, 2005, no.~2005--109, 32~p.

16. Milgrom P., Roberts J. \emph{Economics. Organization and
management}. New York, Prentice-Hall Publ., 1991, 621~p.

17. Camerer C. \emph{Behavioral game theory. Experiments in
strategic interaction}. Princeton, Princeton University Press,
2003, 568 p.

18. Novikov D. A., Chkhartishvili A. G. \emph{Refleksivnye igry
$[$Reflexive games$]$.} Moscow, Sinteg Publ., 2003, 149~p. (In
Russian)

19. Gubko M. V. \emph{Matematicheskiie modeli optimizatsii
ierarhicheskih struktur $[$Mathematical models of optimization of
hierarchical structures$]$.} Moscow, LENAND Publ., 2006, 264~p.
(In Russian)

20. Novikov D. A. \emph{Mehanizmy funktsionirovaniia
mnogourovnenyh organizatsionnyh sistem $[$Me\-cha\-nisms of
functioning of multilevel organizational systems$]$.} Moscow,
``Management problems'' foun\-da\-tion Publ., 1999, 161~p. (In Russian)

21. Karavaev A. P. \emph{Modeli i metody upravleniia sostavom
aktivnyh sistem $[$Models and methods of active systems
composition management$]$.} Moscow, IPU RAS Publ., 2003, 151~p. (In
Russian)

22. Storer N. W., Crane D. Invisible colleges. Diffusion of
knowledge in scientific communities. \emph{Medical History}, 1977,
vol.~21, pp.~221--222.

23. Van Raan A. F. J.  Measurement of central aspects of
scientific research: performance, interdisciplinarity, structure.
\emph{Measurement: interdisciplinary research and perspectives},
2005, vol.~3~(1), pp.~1--19.

24. Andr\'{e}s A. \emph{Measuring academic research}. Oxford,
Chandos Publ., 2009, 186~p.

25. Savitskaia D. V. Normal'naia forma (0,1)-matrits i
algoritmy ee postroeniia [The normal form of (0,1)-matrices and
algorithms for its construction].  \emph{Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Sciences. Control
Processes}, 2008, iss.~4, pp.~85--97. (In Russian)

26. Cormen Th. H., Leiserson Ch. E., Rivest R. L., Stein C.
\emph{Introduction to algorithms}. 2$^{\rm nd}$~ed. Cambridge,
Massachusetts, London, England, MIT Press and McGraw-Hill, 2001,
1312~p. (Rus ed.: Cormen~Th.~H., Leiserson~Ch.~E., Rivest~R.~L.,
Stein~C. {\it Algoritmy: postroenie i analiz}. Moscow, Viliams Press,
2006, 1296~p.).


\vskip1.5mm Received:  May 31, 2022.

Accepted: September 01, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%

\vskip2mm \textit{Elena A. Lezhnina} --- PhD in Physics and Mathematics,
Associated Professor; e.lezhnina@spbu.ru

\vskip2mm \textit{Gennady M. Khitrov} --- PhD in Physics and Mathematics, Associated Professor; chitrow@gmail.com

\vskip2mm \textit{Elizaveta A. Kalinina} --- Dr. Sci. in Physics and Mathematics, Professor; e.kalinina@spbu.ru

\vskip2mm \textit{Ivan A. Kononov} --- Student; st087920@student.spbu.ru \par
%
%
}
