

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Aubin J.-P., Cellina A.} {\it Differential inclusions}.
Berlin, Springer-Verlag Publ., 1984, 344~p.

2. {Polovinkin E. S.} {\it Mnogoznachnyj analiz i differencialnye
vklyucheniya} [{\it Multivalued analysis and differential
inclusions}]. Moscow, Fizmatlit Publ., 2014, 597~p. (In Russian)

3. {Blagodatskih V. I.} {\it Vvedenie v optimalnoe upravleniye}
[{\it Introduction to optimal control}]. Moscow, Vysshaya shkola
Publ., 2001, 239~p. (In Russian)

4. {Blagodatskih V. I., Filippov A. F.} Differencialnye
vklyucheniya i optimalnoe upravlenie. Differential inclusions and
optimal control. {\it Proceedings of the Steklov Institute of
Mathematics}, 1985, vol.~169, pp.~194--252. (In Russian)

5. {Filippov A. F.} {\it Differencialnye uravneniya s razryvnoj
pravoj chastyu} [{\it Differential equations with discontinuous
right-hand side}]. Moscow, Nauka Publ., 1985, 226~p. (In Russian)

6. {Watbled F.} On singular perturbations for differential
inclusions on the infinite interval. {\it Journal of Mathematical
Analysis and Applications}, 2005, vol.~310, no.~2, pp.~362--378.

7. {Gama R., Smirnov G., Watbled F.} Stability and optimality of
solutions to differential inclusions via averaging method. {\it
Set-Valued and Variational Analysis}, 2014, vol.~22, no.~2,
pp.~349--374.

8. {Chengi Yi.} Existence of solutions for a class of nonlinear
evolution inclusions with nonlocal conditions. {\it Journal of
Optimization Theory and Applications}, 2014, vol.~162, no.~1,
pp.~13--33.

9. {Sandberg M.} Convergence of the forward Euler method for
nonconvex differential inclusions. {\it SIAM J. Numer. Anal.},
2008, vol.~47, no.~1, pp.~308--320.

10. {Bastien J.} Convergence order of implicit Euler numerical
scheme for maximal monotone differential inclusions. {\it Z.
Angew. Math. Phys.},  2013, vol.~64, pp.~955--966.

11. {Beyn W-J., Rieger J.} The implicit Euler scheme for one-sided
Lipschitz differential inclusions. {\it Discrete and Continuous
Dynamical Systems. Series B}, 2010, vol.~14, no.~2, pp.~409--428.

12. {Lempio F.} Modified Euler methods for differential
inclusions. {\it Set-Valued Analysis and Differential Inclusions.
A Collection of Papers resulting from a Workshop held in
Pamporovo}. Bulgaria, September 17--21, 1990. Eds by
A.~B.~Kurzhanski, V.~M.~Veliov.  Progr. Systems Control Theory 16.
Boston, Basel, Berlin, Birkhauser Verlag Publ., 1993,
pp.~131--148.

13. {Veliov V.} Second order discrete approximations to strongly
convex differential inclusions. {\it Systems Control Lett.}, 1989,
no.~13, pp.~263--269.

14. {Taubert K.} Dierenzenverfahren fiir Schwingungen mit
trockener und zdher Reibung und fiir Regelungssysteme. {\it Numer.
Math.}, 1976, no.~26, pp.~379--395.

15. {Nikol'skiy M. S.} Ob approksimacii mnozhestva dostizhimosti
dlya upravlyaemogo processa [On approximation of the attainability
domain of control process]. {\it Mat. Zametki} [{\it Mat. notes}],
1987, no.~41, pp.~71--76. (In Russian)

16. {Nikol'skiy M. S.} Ob odnom metode approksimacii mnozhestva
dostizhimosti dlya differencialnogo vklyucheniya [On a method for
approximation of attainable set for a differential inclusion].
{\it Journal of Vych. Mat. Math. Phys.}, 1988, vol.~28,
pp.~1252--1254. (In Russian)

17. {Panasyuk A. I.} Equations of attainable set dynamics. Pt 1.
Integral funnel equations. {\it Journal of Optim. Theory Appl.},
1990, no.~64, pp.~349--366.

18. {Baier R., Gerdts M., Xausa I.} Approximation of reachable
sets using optimal control algorithms. {\it Numer. Algebra Control
Optim.}, 2013, vol.~3, pp.~519--548.

19. {Dontchev A., Lempio F.} Difference methods for differential
inclusions: A survey. {\it SIAM Rev.}, 1992, vol.~34, iss.~2,
pp.~263--294.

20. {Schilling K.} An algorithm to solve boundary value problems
for differential inclusions and applications in optimal control.
{\it Numer. Funct. Anal. and Optimiz.}, 1989, vol.~10, iss.~7,
pp.~733--764.

21. {Bonnans J. F., Shapiro A.} {\it Perturbation analysis of
optimization problems}. New York, Springer Science+Business Media,
2000, 600~p.

22. {Demyanov V. F.} {\it Usloviya ehkstremuma i variacionnoe
ischislenie} [{\it Extremum conditions and variation calculus}].
Moscow, Vysshaya shkola Publ., 2005, 335~p. (In Russian)

23. {Kantorovich~L.~V., Akilov~G.~P.} {\it Funkcionalnyj analiz}
[{\it Functional analysis}]. Moscow, Nauka Publ., 1977, 741~p. (In
Russian)

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  April 8, 2018.

Accepted: September 25, 2018.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip2mm\textit{Alexander V. Fominyh} --- PhD in Physics and
Mathematics, Assistant; alexfomster@mail.ru

}
