
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

1. {\it Craciun E.~M.,  Barbu L.}  Compact closed form solution of
the incremental plane states in a pre-stressed elastic composite
with an elliptical hole // Zeitschrift fur Angewandte Mathematik
und Mechanik (ZAMM). 2015. Vol.~95. P.~193--199.\pagebreak

2. {\it  Wang X.-F., Xing F.,  Hasebe N.,  Prasad P.~B.~N.} A
point dislocation interacting with an elliptical hole located at a
Bi-material interface // Appl. Mechanics and Materials. 2012.
Vol.~151. P.~75--79.

3. {\it  Mogilevskaya S.~G., Crouch S.~L.} A Galerkin boundary
integral method for multiple circular elastic inclusions //
Intern. J. for Numerical Methods in Eng. 2001. Vol.~52.
P.~1069--1106.

4. {\it  Wang J., Crouch S.~L., Mogilevskaya S.~G.} A complex
boundary integral method for multiple circular holes in an
infinite plane // Eng. Anal. with Boundary Elements. 2003.
Vol.~27. P.~789--802.

5. {\it  Dejoie A., Mogilevskaya S.~G., Crouch S.~L.} A boundary
integral method for multiple circular holes in an elastic
half-plane // Eng. Anal. with Boundary Elements. 2006. Vol.~30.
P.~450--464.

6. {\it  Verruijt A.} A complex variable solution for a deforming
circular tunnel in an elastic half-plane // Intern. J. for
Numerical and Analytical Methods in Geomechanics. 1997. Vol.~21.
P.~77--89.

7. {\it  Verruijt A.} Deformations of an elastic half plane with a
circular cavity // Intern. J. Solids and Structures. 1998.
Vol.~35. P.~2795--2804.

8. {\it  Kooi C.~B.,   Verruijt A.} Interaction of circular holes
in an infinite elastic medium // Tunneling and Underground Space
Technology. 2001. Vol.~16. P.~59--62.

9. {\it Wang X.-F.,  Hasebe N.} Green's function of a point
dislocation for the bending of a composite infinite plate with an
elliptical hole at interface // Archive of Appl. Mechanics. 2001.
Vol.~71. P.~233--248.

10. {\it Ukadgaonker V.~G.,  Awasare P.~J.} Interaction effect of
rectangular hole and arbitrarily oriented elliptical hole or crack
in infinite plate subjected to uniform tensile loading at infinity
//  Indian J. Eng. and Materials Sciences. 1999. Vol.~6. P.~125--134.

11. {\it Okumura M., Hasebe N., Nakamura T.} Bimaterial plane with
elliptic hole under uniform tension normal to the interface //
Intern. J. Fracture. 1995. Vol.~71.  P.~293--310.

12. {\it Sun Y.-F., Peng Y.-Z.} Analytic solutions for the
problems of an inclusion of arbitrary shape embedded in a
half-plane // Appl. Math. and Computation. 2003. Vol.~140.
P.~105--113.

13. {\it Малькова Ю.\,В.} Некоторые задачи для двухкомпонентной
плоскости с~криволинейными трещинами. СПб.: Изд-во С.-Петерб.
ун-та, 2008. 160~с.

14. {\it Мусхелишвили Н.\,И.} Некоторые основные задачи
математической теории упругости. М.: Наука, 1966. 708 с.

15. {\it Греков М.\,А.} Слабо искривленная трещина около границы
соединения двух различных материалов // Вестн. С.-Петерб. ун-та.
Сер.~1. Математика. Механика. Астрономия. 2008. Вып.~1.
С.~93--101.

16. {\it Мальков В.\,М., Малькова Ю.\,В.} Трещина в~форме дуги
окружности, расположенная вблизи поверхности раздела материалов //
Вестн. С.-Петерб. ун-та. Сер.~1. Математика. Механика. Астрономия.
2010. Вып.~1. С.~93--104.

17. {\it Мальков В.\,М., Малькова Ю.\,В., Иванов В.\,А.}
Бесконечная плоскость с~круговым включением, имеющим отслоение
на~части границы // Вестн. С.-Петерб. ун-та. Сер. 10. Прикладная
математика. Информатика. Процессы управления. 2009. Вып.~4.
С.~152--166.

18. {\it  Malkov V.~M.,  Malkova Yu.~V.} Deformation of
bi-material plane with elliptic hole // 2nd Intern. Conf. on
Emission Electronics (ICEE). 2014.  P.~1--5. DOI:
10.1109/Emission.2014.6893967 (URL:
http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6893967\&newsearch=true\&queryText
=Deformation of bi-material plane with elliptic hole; дата
обращения: 19.05.2016).

19. {\it  Malkov V.~M.,  Malkova Yu.~V.} The state of stress of
bi-material plate with an elliptic hole // Intern. Conf. on
Mechanics --- Seventh Polyakhov's Reading. 2015.  P.~1--4. DOI:
10.1109/Polyakhov. 2015.7106753 (URL:
http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7106753\&newsearch=
true\&queryText=The state of stress of bi-material plate with an
elliptic hole; дата обращения: 19.05.2016).


\vskip 2mm

{\bf Для цитирования:} Мальков В.~М., Малькова Ю.~В., Петрухин
Р.~Р. Взаимодействие эллиптического отверстия  с межфазной
границей двух полуплоскостей // Вестник Санкт-Петербургского
университета. Сер.~10. Прикладная математика. Информатика.
Процессы управления. \issueyear. Вып.~\issuenum.
С.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07



}
