

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm

1. Craciun E.~M.,  Barbu L.  Compact closed form solution of the
incremental plane states in a pre-stressed elastic composite with
an elliptical hole. {\it Zeitschrift fur Angewandte Mathematik und
Mechanik (ZAMM),} 2015, vol.~95, pp.~193--199.

2. Wang X.-F., Xing F.,  Hasebe N.,  Prasad P.~B.~N. A point
dislocation interacting with an elliptical hole located at a
Bi-material interface. {\it Appl. Mechanics and Materials}, 2012,
vol.~151, pp.~75--79.

3. Mogilevskaya S.~G., Crouch S.~L. A Galerkin boundary integral
method for multiple circular elastic inclusions. {\it Intern. J.
for Numerical Methods in Eng.}, 2001, vol. 52, pp. 1069--1106.

4. Wang J., Crouch S.~L., Mogilevskaya S.~G. A complex boundary
integral method for multiple circular holes in an infinite plane.
{\it Eng. Anal. with Boundary Elements}, 2003, vol.~27,
pp.~789--802.

5. Dejoie A., Mogilevskaya S.~G., Crouch S.~L. A boundary integral
method for multiple circular holes in an elastic half-plane. {\it
Eng. Anal. with Boundary Elements}, 2006, vol.~30, pp.~450--464.

6. Verruijt A. A complex variable solution for a deforming
circular tunnel in an elastic half-plane. {\it Intern. J. for
Numerical and Analytical Methods in Geomechanics}, 1997, vol.~21,
pp.~77--89.

7. Verruijt A. Deformations of an elastic half plane with a
circular cavity. {\it Intern. J. Solids and Structures}, 1998,
vol.~35, pp.~2795--2804.

8. Kooi C.~B.,   Verruijt A. Interaction of circular holes in an
infinite elastic medium. {\it Tunneling and Underground Space
Technology}, 2001, vol.~16, pp.~59--62.

9. Wang X.-F.,  Hasebe N. Green's function of a point dislocation
for the bending of a composite infinite plate with an elliptical
hole at interface. {\it Archive of Appl. Mechanics}, 2001,
vol.~71, pp.~233--248.

10. Ukadgaonker V.~G.,  Awasare P.~J. Interaction effect of
rectangular hole and arbitrarily oriented elliptical hole or crack
in infinite plate subjected to uniform tensile loading at
infinity. {\it Indian J. Eng. and Materials Sciences}, 1999,
vol.~6, pp.~125--134.

11. Okumura M., Hasebe N., Nakamura T. Bimaterial plane with
elliptic hole under uniform tension normal to the interface. {\it
Intern. J. Fracture}, 1995, vol.~71,  pp.~293--310.

12. Sun Y.-F., Peng Y.-Z. Analytic solutions for the problems of
an inclusion of arbitrary shape embedded in a half-plane. {\it
Appl. Math. and Computation}, 2003, vol.~140, pp.~105--113.

13. Malkova Yu.\,V. {\it Nekotorye zadachi dlya dvuhkomponentnoy
ploskosti s krivolineynyimi treshchi-\linebreak nami} [{\it Some
problems for bi-material plane with curvilinear cracks}]. Saint
Petersburg, Saint Petersburg State University Publ., 2008, 160~p.
(In Russian)

14. Muskhelishvili N.\,I. {\it Nekotorye osnovnye zadachi
matematicheskoy teorii uprugosti} [{\it Some basic problems of
mathematical theory of elasticity}]. Moscow,  Nauka Publ., 1966,
708~p. (In Russian)

15. Grekov M.\,A. Slabo iskrivlennaya treshchina okolo granicy
soedineniya dvuh razlichnyh materialov [A slightly curved crack
near the interface in dissimilar materials]. {\it Vestnik of Saint
Petersburg University. Series~1. Mathematics. Mechanics.
Astronomy}, 2008, issue~1, pp.~93--101. (In Russian)

16. Malkov V.~M.,  Malkova Yu.~V. Treshchina v forme dugi
okruzhnosti, raspolozhennaya vblizi poverhnosti razdela materialov
[A circular arc crack near to an interface]. {\it Vestnik of Saint
Petersburg University. Series~1. Mathematics. Mechanics.
Astronomy},  2010, issue~1, pp.~93--104. (In Russian)

17.  Malkov V.~M.,  Malkova Yu.~V., Ivanov V.~A. Beskonechnaya
ploskost s krugovym vklyucheniem, imeyushchim otsloenie na chasti
granicy [Infinite plane with circular inclusion debonding on part
interface]. {\it Vestnik of Saint Petersburg University.
Series~10.  Applied mathematics. Computer science. Control
processes}, 2009, issue~4, pp.~152--166. (In Russian)

18. Malkov V.~M.,  Malkova Yu.~V. Deformation of bi-material plane
with elliptic hole. {\it 2nd Intern. Conf. on Emission Electronics
$($ICEE$)$}, 2014,  pp.~1--5. DOI: 10.1109/Emission.2014.6893967
(Available
at:~http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6893967\&newsearch=true\&queryText=De\linebreak
\noindent formation of bi-material plane with elliptic hole;
accessed: 19.05.2016).

19. Malkov V.~M.,  Malkova Yu.~V. The state of stress of
bi-material plate with an elliptic hole. {\it Intern. Conf. on
Mechanics --- Seventh Polyakhov's Reading}, 2015,  pp.~1--4. DOI:
10.1109/Polyakhov. 2015. 7106753 (Available at:
http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7106753\&new\linebreak
\noindent search=true\&queryText=The state of stress of
bi-material plate with an elliptic hole; accessed: 19.05.2016).



\vskip 2mm

{\bf For citation:} Malkov V.~M., Malkova Yu.~V., Petrukhin R.~R.
Interaction of an elliptic hole with\linebreak interface of two
bonded half-planes. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathema-\linebreak tics. Computer science.
Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
