
{\footnotesize


\vskip5mm \noindent {\small \textbf{Литература} }

\vskip3mm


1. {\it Haurie A.} A note on nonzero-sum differential games with
bargaining solutions // Journal of Optimization Theory and
Applications. 1976. Vol.~18, issue~1. P.~31--39.

2. {\it Петросян Л. А.} Устойчивость решений дифференциальных игр
со многими участниками // Вестн. Ленингр. ун-та. Сер.~1.
Математика, Механика, Астрономия. 1977. Вып.~4. С.~46--52.

3. {\it Петросян Л. А.} Сильно динамически устойчивые
дифференциальные принципы оптимальности // Вестн. С.-Петерб.
ун-та. Сер.~1. Математика. Механика. Астрономия. 1993. Вып.~4.
С.~35--40.

4. {\it Петросян Л. А., Данилов Н. Н.} Устойчивость решений
неантагонистических дифферен\-циаль\-ных игр с~трансферабельными
выигрышами // Вестн. Ленингр. ун-та. Сер.~1. Математика. Механика.
Астрономия. 1979. Вып.~1. С.~52--59.

5. {\it Petrosian O. L.} Looking forward approach in cooperative
differential games // Intern. Game Theory Review. 2016. Vol.~18,
issue~2. P.~1--14. DOI: 10.1142/S0219198916400077.

6. {\it Petrosian O. L., Barabanov A. E.} Looking forward approach
in cooperative differential games with uncertain-stochastic
dynamics // Journal of Optimization Theory and Applications. 2016.
P.~1--20. DOI: 10.1007/s10957-016-1009-8.

7. {\it Bellman R.} Dynamic programming. Princeton: Princeton
University Press, 1957.  550~p.

8. {\it Gromova E. V., Petrosian O. L.} Control of informational
horizon for cooperative differential game of pollution control //
2016 Intern. conference stability and oscillations of nonlinear
control systems (Pyatnitskiy's conference). 2016. DOI:
10.1109/STAB.2016.7541187.

9. {\it Petrosyan L. A., Zaccour G.} Time-consistent Shapley value
allocation of pollution cost reduction // J. econ. dyn. control.
2003. Vol.~27, issue~3. P.~381--398.

10. {\it Petrosyan L. A., Yeung D. W. K.} Dynamically stable
solutions in randomly-furcating differential games // Trans.
Steklov inst. math. 2006. Vol.~253, issue~1. P.~208--220.

11. {\it Jorgensen S., Martin-Herran G., Zaccour G.} Agreeability
and time consistency in linear-state differential games // Journal
of Optimization Theory and Applications. 2003. Vol.~119, issue~1.
P.~49--63.

12. {\it Petrosjan L. A.} Strongly time-consistent differential
optimality principles // Vestnik of Saint Petersburg University.
Series~1. Mathematics. Mechanics. Astronomy. 1993. Issue~4.
P.~40--46.

13. {\it Yeung D. W. K., Petrosyan L. A.} Subgame-consistent
economic optimization. New York: Springer, 2012.  395~p.

14. {\it Basar T., Olsder G. J.} Dynamic noncooperative game
theory. London: Academic Press, 1995.  535~p.

15. {\it Jorgensen S., Yeung D. W. K.} Inter- and
intergenerational renewable resource extraction // Annals of
Operations Research. 1999. Vol.~88, issue~0. P.~275--289.


\vskip 2mm

{\bf Для цитирования:} Петросян О.~Л. Решение с~информационной
дискриминацией в~коопе\-ративных дифференциальных играх
с~бесконечной продолжительностью // Вестник Санкт-Петербургского
университета. Прикладная математика. Информатика. Процессы
управления. \issueyear. Том.~13. Вып.~\issuenum.
С.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02







}
