

{\footnotesize

\vskip 5mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm



1. Egorov~N.~V., Antonova~L.~I., Antonov~S.~R. Study of the
emission properties of a W-Cs$_3$Sb field-emission cathode.
\textit{Journal of Surface Investigation. X-ray, Synchrotron and
Neutron Technique}, 2007, vol.~1, issue~4, pp.~487--495.
% Study of the emission properties of a W-Cs$_3$Sb field-emission cathode
%Journal of Surface Investigation. X-ray, Synchrotron and Neutron Techniques
%August 2007, Volume 1, Issue 4, pp 487–492

2. Egorov~N.~V., Karpov~A.~G., Antonova~L.~I., Fedorov~A.~G.,
Trofimov~V.~V., Antonov~S.~R. Technique for investigating the
spatial structure of thin films at a nanolevel. \textit{Journal of
Surface Investigation. X-ray, Synchrotron and Neutron Techniques},
2011, vol.~5, issue~5, pp.~992--995.
% Technique for investigating the spatial structure of thin films at a nanolevel
%   N. V. EgorovA. G. KarpovL. I. AntonovaA. G. FedorovV. V. TrofimovS. R. Antonov
% Journal of Surface Investigation. X-ray, Synchrotron and Neutron Techniques
% October 2011, 5:992

3. %Kossel D., Deutscher K, Hirshberg K. // Advances in electronics and electron physics. 1969. V. 28a. P. 419 – 438.
Kossel~D., Deutscher~K, Hirshberg~K. Interference photocathodes.
\textit{Advances in electronics and electron physics}, 1969,
vol.~28a, pp.~419--431.

4. Szozyrlowski~J. Determination of optical constants of real thin
films. \textit{J. Phys. D}. \textit{Appl. Phys.}, 1978, vol.~11,
pp.~583--594.

5. %Sizelove J.R., Love III J.A. // Appl.Optics. 1967. V. 6. P. 356--365.
Sizelove~J.~R., Love~III~J.~A. Analysis of Translucent and Opaque
Photocathodes. \textit{Appl. Optics}, 1967, vol.~6, pp.~356--357.

6. Timan H. Optical characteristics and constants of high
efficiency photoemitters. \textit{Revue Technique Thomson CSF},
1976, vol.~8, pp.~49--80.
% H. Timan, Optical characteristics and constants of high efficiency photoemitters, Revue Technique Thomson-CSF 8 (1976) 49

%%[7] {\color{red} \Large \verb!http://shazam.econ.ubc.ca/intro/glshetl.htm.!}
7. Karpov~A.~G., Klemeshev~V.~A., Trofimov~V.~V. Matematicheskie
osnovy metodov obrabotki informacii dielektricheskoi spektrometrii
tonkikh plenok [Mathematical foundations of information processing
methods for dielectric spectroscopy of thin films].
\textit{Vestnik of Saint Petersburg State University. Series 10.
Applied mathematics. Computer sciences. Control processes}, 2015,
issue~4, pp.~13--26. (In Russian)

8. Pshenichny~B.~P., Danilin~Y.~M. \textit{Chislennye metody v
ekstremal`nykh zadachakh} [\textit{Numerical methods in extreme
tasks}]. Moscow, Nauka Publ., 1975, 320~p. (In Russian)

9. %Tyurin Yu.N., Makarov A.A. Statistical analysis of the data on the computer. M .: INFRA-M, 1998. 528 p.
Tiurin~Iu.~N., Makarov~A.~A. \textit{Statisticheskii analiz
dannykh na komp'iutere} [\textit{Statistical analysis of the data
on the computer}]. Moscow, Infra-M Publ., 1998, 528~p. (In
Russian)

10. %Dai Y.H., Yuan Y. // The IMA Journal of Numerical Analysis. 1996. V. 16. P. 155 – 176.
Dai~Y.~H., Yuan~Y. Convergence properties of the Fletcher---Reeves
method. \textit{The IMA Journal of Numerical Analysis}, 1996,
vol.~16. pp.~155--164.

11. Kaiser~W.~J., Bell~L.~D. Direct investigation of subsurface
interface electronic structure by ballistic-electron-emission
microscopy. \textit{Phys. Rev. Lett.}, 1988, vol.~60, pp.
1406--1410.
% Direct investigation of subsurface interface electronic structure by ballistic-electron-emission microscopy
% W. J. Kaiser and L. D. Bell
% Phys. Rev. Lett. \textbf{60}, 1406 (1988) – Published 4 April 1988


\vskip 2mm

{\bf For citation:} Karpov A.~G., Klemeshev V.~A. Method for
determining optical constants and the thickness of the thin film.
{\it Vestnik of Saint Petersburg University. Applied mathematics.
Computer science. Control processes}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02

}
