
{\normalsize

\vskip 4mm

\noindent{\bf Mathematical modeling of the deformation of
composite plane\\ with interface crack for semi-linear material}

}

\vskip 1.5mm

{\small

\noindent{\it T.\,O. Domanskaya, V.\,M. Malkov, Yu.\,V. Malkova}

\vskip 1.5mm

{\footnotesize \noindent St.\,Petersburg State University, 7--9,
Universitetskaya nab., St.\,Petersburg, 199034, Russian Federation

}

\vskip2.5mm

\noindent \textbf{For citation:}  Domanskaya T.\,O., Malkov
V.\,M., Malkova Yu.\,V. Mathematical modeling of the deformation
of composite plane with interface crack for semi-linear material.
{\it Vestnik of Saint~Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~14,
iss.~\issuenum, pp.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02

\vskip2.5mm

{\leftskip=7mm\noindent The exact analytical solutions have been
obtained for the nonlinear problems (plane-strain and
plane-stress) for the bi-material plane with an interface crack.
The plane is formed by joining of two half-planes made from
different materials. Mechanical properties of half-planes are
described with the model of semi-linear material. The application
of this model has allowed using the methods of the complex
functions in the nonlinear boundary value problems. For this
particular case the problem is solved for the plane with a free
interface crack at given constant nominal (Piola) stresses at
infinity. The expressions for nominal stresses, Cauchy stresses
and displacements are obtained. From the general solutions the
asymptotic expansions of these functions have been constructed in
vicinities of crack tips. It is established that in the nonlinear
problem of uniaxial extension of a plane with a free crack the
formulas which give the crack disclosing differ by a constant
factor from the formulas of linear elasticity. The stress
intensity factors (SIF) of nonlinear and linear problems coincide.
The nominal stresses have the root singularity
at the tips of a crack; the Cauchy stresses have no singularity.\\[1mm]
\textit{Keywords}: bi-material plane, plane-strain problem,
plane-stress problem, method of complex functions, interface
crack, semi-linear material.
\par}

\vskip3.5mm

\noindent \textbf{References} }

\vskip 1.5mm

{\footnotesize

1. {John F.} Plane strain problems for a perfectly elastic
material of harmonic type. {\it Commun. Pure and Applied
Mathematics}, 1960, vol. 13, no. 2. pp. 239--296.

2. {Lurie A.\,I.} {\it Nelineynaya teoria uprugosti $[$Non-linear
elasticity$]$}. Moscow, Nauka Publ., 1980, 512~p. (In Russian)

3. {Chernykh K.\,F., Litvinenkova Z.\,N.} {\it Teoria bolshih
uprugih deformatsiy $[$Theory of large elastic\linebreak
deformations$]$}. Leningrad, Leningrad State University Publ.,
1988, 256 p. (In Russian)

4. Zubov L.\,M.  {\it Nonlinear theory of dislocations and
disclinations in tlastic bodies}. Berlin, Springer Press, 1997.
205~p.

5. {Malkov V.\,M., Malkova Yu.\,V.} Ploskye zadachi uprugosti dlya
polulineynogo materiala [Plane problems of elasticity for
semi-linear material].  {\it Vestnik of Saint Petersburg
University. Series 1. Mathematics. Mechanics. Astronomy}, 2012,
iss. 3, pp. 93--106. (In Russian)

6. {Malkov V.\,M., Malkova Yu.\,V.} Ploskye zadachi o
sosredotochennykh silah dlya polulineynogo materiala [Plane
problems on concentrated forces for semi-linear material]. {\it
Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2013, iss. 3,
pp. 83--96. (In Russian)

7. {Malkov V.\,M., Malkova Yu.\,V., Domanskaya T.\,O.} Analiz
napryazheniy dvuhkomponentnoy ploskosti i poluploskosti pri
deystvii sosredotochennoy sily dlya dvuh modeley garmonicheskogo
materiala [Analysis of stresses of bi-material plane and
half-plane at action of a point force for two models of harmonic
materials]. {\it Vestnik of Saint Petersburg University. Series
10. Applied Mathematics. Computer Science. Control Processes},
2016, iss. 1, pp. 38--52. (In Russian)

8. {Varley E., Cumberbatch E}. Finite deformation of elastic
materials surrounding cylindrical holes. {\it Journal of
Elasticity}, 1980, vol. 10, no. 4, pp. 341--405.

9. {Ru C.\,Q}. On complex-variable formulation for finite plane
elastostatics of harmonic materials. {\it Acta Mechanica}, 2002,
vol. 156, no. 3--4, pp. 219--234.

10. {Ru C.\,Q., Schiavone P., Sudak L.\,J., Mioduchowski A.}
Uniformity of stresses inside an elliptic inclusion in finite
plane elastostatics. {\it Intern. Journal of Non-linear
mechanics}, 2005, vol. 38, no. 2--3, pp.~281--287.

11. {Malkov V.\,M., Malkova Yu.\,V.} Ploskaya zadacha nelineynoy
uprugosti dlya garmonicheskogo materiala [Plane problem of
non-linear elasticity for harmonic material]. {\it Vestnik of
Saint Petersburg University. Series 1. Mathematics. Mechanics.
Astronomy}, 2008, iss. 3, pp. 114--126. (In Russian)

12. {Malkov V.\,M., Malkova Yu.\,V.} Modelirovanie nelineinoy
deormacii ploskosti s ellipticheskim otverstiem ili vklucheniem
garmonicheskim materialom Djona [Modeling nonlinear deformation of
a plate with an elliptic inclusion by John's harmonic material].
{\it Vestnik of Saint Petersburg University. Mathe-\linebreak
matics. Mechanics. Astronomy}, 2017, vol. 4 (62), iss. 1, pp.
121--130. (In Russian) DOI: 10.21638/11701/ spbu01.2017.114

13. { Mal'kov V.\,M.,  Mal'kova Yu.\,V.} Modeling nonlinear
deformation of a plate with an elliptic inclusion by John's
harmonic material. {\it  Vestnik of Saint Petersburg University,
Mathematics}, 2017, vol.~50, iss. 1, pp. 74--81. © Allerton Press,
Inc., 2017. DOI:10.3103/S1063454117010095

14. {Malkov V.\,M., Malkova Yu.\,V., Stepanova V.\,A.}
Dvuhkomponentnaya ploskost is materiala Dzhona s mezhfaznoy
treshinoy, nagruzhennoy davleniem [Bi-material plane of John's
material with interface crack loaded by pressure]. {\it Vestnik of
Saint Petersburg University. Series 1. Mathematics. Mechanics.
Astronomy}, 2013, iss. 3, pp. 113--125. (In Russian)

15. { Domanskaia T.,  Malkov V.,  Malkova Yu.} Bi-material plane
of John's harmonic material with a point force at interface. {\it
XXIV International Congress of Theoretical and Applied Mechanics
$($ICTAM$)$}, 21--26 August 2016. Montreal,  Canada, 2016, pp.
1958--1959.

16. {Domanskaya T.\,O., Malkov V.\,M., Malkova Yu.\,V.}
Nelineinaya zadacha dlya compozitnoy plastinu s mejfaznoy
trechinoy dlya garmonicheskogo materiala Djona [Nonlinear problem
for bi-material plate with interface crack for harmonic John's
material]. {\it  2nd International conference ``Deformation and
Failure of Composite Materials and Structures''} (DFCMS--2016).
October 2016. Moscow, Institute of Engineering RAS Publ., 2016,
pp. 33--35.  (In Russian)

17. {Malkov V.\,M.} {\it Vvedenie v nelineynuyu uprugost
$[$Introduction to non-linear elasticity$]$}. Saint Petersburg,
Saint Petersburg State University Publ., 2010, 276 p. (In Russian)

18. {Malkova Yu.\,V.} {\it Nekotorye zadachi dlya dvuhkomponentnoy
ploskosti s krivolineynyimi treshinami $[$Some problems for
bi-material plane with curvilinear cracks$]$}. Saint Petersburg,
Saint Petersburg State University Publ., 2008, 160 p. (In Russian)

19. {Ito Yu. et all.} {\it Stress intensity factors handbook}. In
2 vol. Oxford etc., Oxford University Press, 1985--1986. (Russ.
ed.: Ito Yu. et all. {\it Spravochnik po koefficientam
intensivnosty napryajenyi}. Moscow, Mir Publ., 1990, vol. 1, 447
p.; vol. 2, 1014 p.)




\vskip4mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.2mm \textit{Domanskaya Tatyana O.}~--- postgraduate
student; tanyath57@gmail.com

\vskip1.2mm \textit{Malkov Venyamin M.}~--- Dr. Sci. in physics
and mathematics, professor; v.malkov@spbu.ru

\vskip1.2mm \textit{Malkova Yulia V.}~--- PhD Sci. in physics and
mathematics, associate professor;  y.malkova@spbu.ru
\par}
