

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Endsley M. R. Situation awareness misconceptions and misunderstandings. \textit{Journal of Cognitive Engineering and Decision Making}, 2015, vol.~9, no.~1, pp.~4--32. https://doi.org/10.1177/1555343415572631

2. Raikov A. N. Accelerating decision-making in transport emergency with artificial intelligence. \textit{Advances in Science, Technology and Engineering Systems Journal}, 2020, vol.~5, no.~6, pp.~520--530. https://dx.doi.org/10.25046/aj050662

3. Burenok V. M. The directions and problems of applying artificial intelligence. \textit{Intern. Con\-fe\-ren\-ce ``Artificial Intelligence. Problems and Solutions''}. Moscow, 2018, pp.~24--119.

4. Gorodetskii V. I., Grushinskii M. S., Kabalov A. V. Mul'tiagentnye sistemy (obzor) [Multiagent systems (review)]. \textit{Novosti iskusstvennogo intellekta} [\textit{Artificial Intelligence News}], 1998, no.~2, pp.~64--116. (In Russian)

5. Kalyaev I. A., Gaiduk A. R., Kapustyan S. G. \textit{Modeli i algoritmy kollektivnogo upravleniya v gruppakh robotov} [\textit{Models and algorithms of collective control in robot groups}]. Moscow, Fizmatlit Publ., 2009, 280~p. (In Russian)

6. Abrosimov V. K.,	Mochalkin A. N., Skobelev P. O. A behavioral strategy of an autonomous robot in an opposing environment: Situational awareness and self-organization. \textit{The 19$^{th}$ Intern. Conference ``Complex Systems: Control and Modeling Problems''}. Samara, Ofort-S Publ., 2017, pp.~45--53.

7. Larichev O. I. \textit{Teoriya i metody prinyatiya reshenii} [\textit{Theory and methods of decision making}]. Moscow, Logos Publ., 2000, 296~p. (In Russian)

8. Karpov V. E., Karpova I. P., Kulinich A. A. \textit{Sotsial'nye soobshchestva robotov} [\textit{Social communities of robots}]. Moscow, Lenand Publ., 2019, 352~p. (In Russian)

9. Rao A. S., Georgeff M. P. BDI agents: From theory to practice. \textit{The 1$^{st}$ Intern. Conference on Multi-Agent Systems (ICMAS--95)}. San Francisco, USA, 1995, pp.~312--319.

10. Czaplicka A., Chmieland A., Ho{\l}yst J. A. Emotional agents at the square lattice. \textit{Acta Physica Polonica A}, 2010, vol.~117, no.~4, pp.~688--694.

11. Abrosimov V. K. \textit{Kollektivy letatel'nykh apparatov} [\textit{Collectives of aircrafts}]. Moscow, Nauka Publ., 2017, 304~p. (In Russian)

12. Reynolds C. Flocks, herds, and schools: a distributed behavioral model. \textit{Computer Graphics}, 1987, vol.~21, no.~4, pp.~25--34.

13. Raikov A. \textit{Cognitive semantics of artificial intelligence: A new perspective}. Singapore, Springer Publ., 2021, 110~p. https://doi.org/10.1007/978-981-33-6750-0

14. Nu X., Eberhart R. Solving constrained nonlinear optimization problems with particle swarm optimization. \textit{The 6$^{th}$ World Multiconference on System Cybernetics and Informatics}. Orlando, Florida, USA, 2002, pp.~203--206.

15. Ruchkin K. A., Danilov A. V. Design of a multi-agent system for predicting the behavior of a dynamic system in real time. \textit{Iskusstvennyi intellekt} [\textit{Artificial Intelligence}], 2011, no.~4, pp.~449--460.

16. Abrosimov V. K. Role allocation in a group of control objects: general purpose approach. \textit{Recent Developments in Intelligent Nature-Inspired Computing}, IGI Global Publ., 2017, pp.~206--224.

17. Abrosimov V. K. The property of agent's sacrifice: definition, measure, effect and applications. \textit{Intern. Journal Reasoning-based Intelligent Systems}, 2016, vol.~8, no.~1/2, pp.~76--83.

18. Pinciroli C., Beltrame G. Buzz: An extensible programming language for heterogeneous swarm robotics. \textit{2016 IEEE/RSJ Intern. Conference on Intelligent Robots and Systems (IROS)}, 2016, pp.~3794--3800. https://doi.org/10.1109/IROS.2016.7759558

\vskip 2%1.5
mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  May 19, 2021.

Accepted: October 13, 2021.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Vyacheslav K. Abrosimov} --- Dr. Sci. in Engineering, Professor; avk787@yandex.ru \par

\vskip 2mm \textit{Alexander Yu. Mazurov} --- PhD in Physics and Mathematics, Junior Researcher;\\ alexander.mazurov08@gmail.com \par
%
}
