
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm


{\footnotesize

1. {\em Wardrop~J.~G.} {Some theoretical aspects of road traffic
research // Proc. Institution of Civil Engineers. 1952. Vol.~2.
P.~325--378.}

2. {\em Beckmann~M.~J., McGuire~C.~B., Winsten~~C.~B.} {Studies in
the economics of transportation. New Haven, CT: Yale University
Press, 1956. 359~p.}

3. {\em Sheffi~Y.} {Urban transportation networks: equilibrium
analysis with mathematical programming methods. New Jersey:
Prentice-Hall Inc.; Englewood Cliffs, 1985. 416~p.}

4. {\em Yang~H., Huang~H.-J.} {The multi-class, multi-criteria
traffic network equilibrium and systems optimum problem //
Transportation Research. Pt B: Methodological. 2004. Vol. 38. P.
1--15.}

5. {Введение в~математическое моделирование транспортных потоков /
под ред. В.~А.~Дружининой, И.~А.~Волковой. М.: Моск. физ.-техн.
ин-т, 2010. 360~с.}

6. {\em Di~X., Liu~H.~X.} {Boundedly rational route choice
behavior: A review of models and methodologies // Transportation
Research. Pt B: Methodological. 2016. Vol.~85. P.~142--179.}

7. {\em Шелейховский~Г.~В.} {Транспортные основания композиции
городского плана. Л.: Гипрогор, 1936. 150~с.}

8. {\em Брегман~Л.~М.} {Доказательство сходимости метода Г. В.
Шелейховского для задачи с~транспортными ограничениями // Журн.
вычисл. математики и~матем. физики. 1967. Т.~7, №~1. С.~147--156.}

9. {\em Wilson~A.~G.} {Entropy in urban and regional modelling.
London: Pion, 1970. 166~p.}

10. {\em    Федоров~В.~П., Лосин~Л.~А.} {Методы математического
моделирования для проек\-ти\-ро\-ва\-ния городской транспортной
системы на досетевом уровне // Транспорт Российской Федерации.
2012. №~2(39). С.~30--33.}

11. {\em    Федоров~В.~П.} {Формирование вариантов развития
городских транспортных сетей: разработка метода // Транспорт
Российской Федерации. 2012. №~3--4(40--41). С.~17--21.}

12. {\em    Patriksson~M.} {A mixed user-equilibrium and
system-optimal traffic flow for connected vehicles stated as a
complementarity problem // Computer-Aided Civil and Infrastructure
Engineering. 2017. Vol.~32(7). P.~562--580.}

13. {\em Konnov~I.~V.} {On auction equilibrium models with network
applications // Netnomics. 2015. Vol.~16. P. 107--125.}

14. {\em Konnov~I.~V.} {Vector network equilibrium problems with
elastic demands // Journal of Global Optimization. 2013. Vol. 57.
P. 521--531.}

15. {\em Mazalov~V.~V., Melnik~A.~V.} {Equilibrium prices and
flows in the passenger traffic problem // International Game
Theory Review. 2016. Vol. 18(1).} (URL:
https://www.worldscientific.com/doi/
abs/10.1142/S0219198916500018; дата обращения:  04.04.2018~г.)

16. {\em Lien~J.~W., Mazalov~V.~V., Melnik~A.~V., Zheng~J.}
{Wardrop equilibrium for networks with the BPR latency function //
Lecture Notes in Computer Science (including subseries Lecture
Notes in Artificial Intelligence and Lecture Notes in
Bioinformatics). 2016. Vol. 9869. P. 37--49.}

17. {\em Krylatov A.Yu.} Network flow assignment as a fixed point
problem // Journal of Applied and Industrial Mathematics. 2016.
Vol. 10(2). P. 243--256.

18. {\em    Krylatov~A.~Yu., Shirokolobova~A.~P.} {Projection
approach versus gradient descent for network’s flows assignment
problem // Lecture Notes in Computer Science. 2017. Vol.~10556.
P.~345--350.}

19. {\em Zakharov V. V., Krylatov A. Yu.} Competitive routing of
traffic flows by navigation providers // Automation and Remote
Control. 2016. Vol. 77, N 1. P. 179--189.

20. {\em Krylatov~A.~Y., Zakharov~V.~V., Malygin~I.~G.}
{Competitive traffic assignment in Road Networks // Transport and
Telecommunication. 2016. Vol.~17, N~3. P.~212--221.}

21. {\em    Patriksson~M.} {The traffic assignment problem: models
and methods. Utrecht, The Netherlands: VSP, 1994. 223~p.}

22. {\em    Крылатов~А.~Ю.} {Оптимальные стратегии управления
транспортными потоками на сети из параллельных каналов // Вестн.
С.-Петерб. ун-та. Сер. 10. Прикладная математика. Информатика.
Процессы управления. 2014. Вып.~2. С.~121--130.}



\vskip 1.5mm

\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.

\vskip 1.5mm

\noindent Статья поступила в~редакцию 6 октября 2017~г.; принята
к~печати 15 марта 2018~г.


\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Крылатов Александр Юрьевич}~--- канд. физ.-мат.
наук, доцент; a.krylatov@spbu.ru


\vskip2mm \textit{Широколобова Анастасия Павловна}~--- ассистент;
 a.shirokolobova@spbu.ru





}
