
{\normalsize

\vskip 6mm

\noindent{\bf Equilibrium route flow assignment in linear network
as a system\\ of linear equations}

}

\vskip 1.5mm

{\small

\noindent{\it A.~Yu.~Krylatov$^{1,2}$, A.~P.~Shirokolobova$^1$}

\vskip 1.5mm

{\footnotesize \noindent $^1$~St.\,Petersburg State University,
7--9, Universitetskaya nab., St.\,Petersburg,

\noindent\hskip2.45mm 199034, Russian Federation


\noindent $^2$~Solomenko Institute of Transport Problems, 13, 12th
line of V. O., St.\,Petersburg,

\noindent\hskip2.45mm 199178, Russian Federation






}

\vskip3mm

\noindent \textbf{For citation:}  Krylatov A.~Yu., Shirokolobova
A.~P. Equilibrium route flow assignment in linear network as a
system of linear equations. {\it Vestnik of Saint~Petersburg
University. Applied Mathematics. Computer Science. Control
Processes},\,\issueyear,
vol.~14,~iss.~\issuenum,~pp.~\pageref{p3}--\pageref{p3e}.
\doivyp/spbu10.\issueyear.\issuenum03

\vskip3mm

{\leftskip=7mm\noindent Decision making requires possibilities to
influence the object. In urban traffic area it is crucial to
influence traffic flows. However, first of all, decision maker
needs comprehensive information about traffic flows. From a
practical perspective, the most valuable is information about
route flows, unlike information about link flows. In this paper, a
route flow traffic assignment model in a linear network is
studied. Linear road network (linear link performance function)
gives a chance to reduce traffic assignment problem to a system of
linear equations and conditions in the form of linear
inequalities. The directed graph represents road network. Route
flow traffic assignment problem is presented as a nonlinear
constrained problem. The theorem about the reduction of a route
flow traffic assignment problem in linear road network to the
system of linear equations is proved. Implementation of developed
approach to an example of the linear road network is disassembled
in details.\\[1mm]
\textit{Keywords}: constrained nonlinear optimization, user
equilibrium of Wardrop, route flow traffic assignment.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Wardrop~J.~G.} Some theoretical aspects of road traffic
research. {\em Proc. Institution of Civil Engineers}, 1952,
vol.~2, pp.~325--378.

2. {Beckmann~M.~J., McGuire~C.~B., Winsten~~C.~B.} {\em Studies in
the economics of transportation}. New Haven, CT, Yale University
Press, 1956, 359~p.

3. {Sheffi~Y.} {\em Urban transportation networks: equilibrium
analysis with mathematical programming methods}. New Jersey,
Prentice-Hall Inc., Englewood Cliffs Publ., 1985, 416~p.

4. {Yang~H., Huang~H.-J.} {The multi-class, multi-criteria traffic
network equilibrium and systems optimum problem. {\em
Transportation Research}, {\em pt B. Methodological}, 2004,
vol.~38, pp.~1--15.}

5. {\em Vvedenie v matematicheskoe modelirovanie transportnyh
potokov} [{\em Introduction to mathematical modelling of traffic
flows}]. Pod red. V. A.~Druzhininoj, I. A.~Volkovoj. Moscow,
Moscow phys. and techn. University Publ., 2010, 360~p. (In
Russian)

6. {Di~X., Liu~H.~X.} Boundedly rational route choice behavior: A
review of models and methodologies. {\em Transportation Research,
pt B. Methodological}, 2016, vol.~85, pp.~142--179.

7. {Sheleykhovskiy~G.~V.} {\em Transportnye osnovaniya
kompozictsii gorodskogo plana} [{\em Transportation basis for
urban planning}]. Leningrad, Giprogor Publ., 1936, 150~p. (In
Russian)

8. {Bregman~L.~M.} {Dokazatel'stvo skhodimosti metoda
G.~V.~Sheleykhovskiy dlya zadachi s trans-\linebreak portnymi
ogranicheniyami [The proof of convergence of the Sheleykhovskiy's
method for the problem with transportation constraints]. {\em
Computational Mathematics and Mathematical Physics}, 1967, vol.~7,
no.~1, pp.~147--156.} (In Russian)

9. {Wilson~A.~G.} {\em Entropy in urban and regional modelling}.
London, Pion Press, 1970, 166~p.

10. {Fedorov~V.~P., Losin~L.~A.} Metody matematicheskogo
modelirovaniya dlya proektirovaniya gorodskoy transportnoy sistemy
na dosetevom urovne [Mathematical modelling methods in designing
urban transport system on pre-network level]. {\em Transport of
Russian Federation}, 2012, no.~2(39), pp.~30--33. (In Russian)

11. {Fedorov~V.~P.} Formirovanie variantov razvitiya gorodskikh
transportnykh setey: razrabotka metoda [Working out the method for
forming variations for development of urban transport networks].
{\em Transport of Russian Federation}, 2012, no.~3--4(40--41),
pp.~17--21. (In Russian)

12. {Patriksson~M.} A mixed user-equilibrium and system-optimal
traffic flow for connected vehicles stated as a complementarity
problem. {\em Computer-Aided Civil and Infrastructure
Engineering}, 2017, vol.~32(7), pp.~562--580.

13. {Konnov~I.~V.} {On auction equilibrium models with network
applications}. {\em Netnomics}, 2015, vol.~16, pp.~107--125.

14. {Konnov~I.~V.} {Vector network equilibrium problems with
elastic demands}. {\em Journal of Global Optimization}, 2013,
vol.~57, pp.~521--531.

15. {Mazalov~V.~V., Melnik~A.~V.} {Equilibrium prices and flows in
the passenger traffic problem}. {\em International Game Theory
Review}, 2016, vol.~18(1). (Available at:
https://www.worldscientific.com/
doi/abs/10.1142/S0219198916500018; accessed: 04.04.2018)

16. {Lien~J.~W., Mazalov~V.~V., Melnik~A.~V., Zheng~J.} {Wardrop
equilibrium for networks with the BPR latency function}. {\em
Lecture Notes in Computer Science (including subseries Lecture
Notes in Artificial Intelligence and Lecture Notes in
Bioinformatics)}, 2016, vol.~9869, pp.~37--49.

17. Krylatov A.Yu. Network flow assignment as a fixed point
problem. {\em Journal of Applied and Industrial Mathematics},
2016, vol.~10(2), pp.~243--256.

18. {Krylatov~A.~Yu., Shirokolobova~A.~P.} {Projection approach
versus gradient descent for network’s flows assignment problem}.
{\em Lecture Notes in Computer Science}, 2017, vol.~10556,
pp.~345--350.

19. Zakharov V. V., Krylatov A. Yu. Competitive routing of traffic
flows by navigation providers. {\em Automation and Remote
Control}, 2016, vol.~77, no.~1, pp.~179--189.

20. {Krylatov~A.~Y., Zakharov~V.~V., Malygin~I.~G.} {Competitive
traffic assignment in Road Networks}. {\em Transport and
Telecommunication}, 2016, vol.~17, no.~3, pp.~212--221.

21. {Patriksson~M.} {The traffic assignment problem: models and
methods. Utrecht, The Netherlands, VSP Press, 1994, 223 p.}

22. {Krylatov~A.~Yu.} {Optimalnye strategii upravleniya
transportnymi potokami na seti iz parallelnyh kanalov [Optimal
strategies for traffic flow management on the transportation
network of parallel links].} {\em Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2014, iss.~2, pp.~121--130. (In Russian)




\vskip5mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.5mm \textit{Krylatov Alexander Yu.}~--- PhD Sci. in
physics and mathematics, associate professor;\\
a.krylatov@spbu.ru

\vskip1.5mm \textit{Shirokolobova Anastasiya P.}~---  assistant;
a.shirokolobova@spbu.ru




}
