

{\small



\vskip4.5%6
mm

\noindent \textbf{References} }

\vskip 1.5%2
mm

{\footnotesize



1. {Park J.\,J., Kuipers B.} A smooth control law for graceful
motion of differential wheeled mobile robots in 2D environment.
{\it 2011 IEEE International Conference on Robotics and
Automation}, 2011, pp.~4896--4902.

2. {Popkov A.\,S.} Application of the adaptive method for optimal
stabilization of a nonlinear object. {\it 2016 International
Conference Stability and Oscillations of Nonlinear Control Systems
(Pyatnitskiy's Conference)}, 2016, pp.~1--3.

3. {Popkov A.\,S., Smirnov N.\,V., Smirnova T.\,E.} On
modification of the positional optimization method for a class of
nonlinear systems. {\it ACM International Conference Proceeding
Series}, 2018, pp.~46--51.%\pagebreak

4. {Balashevich N.\,V., Gabasov R., Kirillova F.\,M.} Chislennye
metody programmnoy i po\-zi\-tsion\-noy optimizatsii lineynyh
sistem upravleniya [Numerical methods of program and positional
optimization of linear control systems]. {\it Journal of
Computational Mathematics and Mathematical Physics}, 2000,
vol.~40(6), pp.~838--859. (In Russian)

5. {Girdyuk D.\,V., Smirnov N.\,V., Smirnova T.\,E.} Optimal
control of the profit tax rate based on the~nonlinear dynamic
input-output model. {\it ACM International Conference Proceeding
Series}, 2018,\linebreak pp.~80--84.

6. {Baranov O.\,V., Smirnov N.\,V., Smirnova T.\,E., Zholobov
Y.\,V.} Design of a quadrocopter with PID-controlled fail-safe
algorithm. {\it Journal of Wireless Mobile Networks, Ubiquitous
Computing, and Dependable Applications}, 2020, vol.~11(2),
pp.~23--33.

7. {\it GAMS Development Corporation: Solver Manuals}. Available
at:\\
http://www.gams.com/latest/docs/S\!\_\!MAIN.html$\#$SOLVERS\!\_\!MODEL\!\_\!TYPES
(accessed: September~15, 2020).

8. {Babadzanjanz L.\,K., Pototskaya I.\,Yu.} {\it Upravlenie po
kriteriyu raskhoda v mehanicheskih sistemah} [{\it Control by
expense criteria in mechanical systems}]. St.~Petersburg,
Saint~Petersburg State University Press, 2003, 137~p. (In Russian)


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 08, 2020.

Accepted: October 23, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Alexander S. Popkov} ---  Postgraduate Student,
Research Engineer; alexandr.popkoff@gmail.com


}
