

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm



1. {Batyukov~A.~M.} Analiz tsifrovykh izobrazhenii, osnovannyi na
postroenii statsionarnogo potoka na grafe [Digital images
processing based on graph stationary flow construction]. {\it
Vestnik of Saint Petersburg University. Series 10. Applied
mathematics. Computer science. Control processes}, 2015, issue~2,
pp.~115--122. (In Russian)

2. {Grishkin~V.~M.} Komp'iuternaia sistema monitoringa sostoianiia
ob'ektov kul'turnogo naslediia. [Computer system for monitoring
monuments representing cultural heritage]. {\it Vestnik of Saint
Petersburg. University. Series 10. Applied mathematics. Computer
science. Control processes}, 2009, issue~3, pp.~181--188. (In
Russian)

3. {Flowers~M., Weisz~R., Heiniger~R.} Remote sensing of winter
wheat filler density for early nitrogen application decisions.
{\it Agronomy Journal}, 2001, vol.~93, no.~4, pp.~783--789.

4. {Graeff~S., Pfenning~J., Claupein~W., Liebig~H.~P.} Evaluation
of image analysis to determine the N-fertilizer demand of broccoli
plants. {\it Advances in Optical Technologies}, 2008, pp.~1--8.

5. {Deshmukh~K. S.} Disease detection of crops using hybrid
algorithm. {\it Intern. Journal of Engineering Research and
Technology}, 2012, vol.~1, no.~10, pp.~1--5.

6. {McMullen~S. K., Schatz~B., Rush~C.~M.} Assessing foliar
disease of wheat image analysis. {\it Proc. of the Summer Crops
Field Day Sponsored by the Cooperative Research, Education and
Extension Team}. Bushland, Tex, USA, 2004, pp.~32--38.

7. {Yakushev~V.~P., Kanash~E.~V., Konev~A.~A. et~al.} {\it
Teoreticheskie i metodicheskie osnovy vydeleniia odnorodnykh
tekhnologicheskikh zon dlia differentsirovannogo primeneniia
sredstv khimizatsii po opticheskim kharakteristikam poseva.
Prakticheskoe posobie} [{\it Theoretical and methodological
foundations of homogeneous areas selection for the differentiated
application of chemicals by the optical characteristics of crop.
Practical guide}]. Saint Petersburg, Agrophys. institute Publ.,
2010, 60~p. (In Russian)

8. {Fairchild~M.~D. } {\it Color appearance models}. Rochester,
USA, John Wiley \& Sons, Ltd., 2005, 385~p.

9. {Bure~V.~M.} {\it Metodologiia statisticheskogo analiza
opytnykh dannykh} [{\it Statistical analysis methodology of the
experimental data}]. Saint Petersburg, Saint Petersburg State
University Publ., 2007, 141~p. (In Russian)

10. {Bure~V.~M., Parilina~E.~M. } {\it Teoriia veroiatnostei i
matematicheskaia statistika. Uchebnoe posobie} [{\it Probability
theory and mathematical statistics. Educational guide}]. Saint
Petersburg, Lan' Publ., 2013, 416~p. (In Russian)

11. {Yakushev~V.~P., Bure~V.~M.} {\it Podkhody k obnaruzheniiu
statisticheskikh zavisimostei} [{\it Approaches to detect
statistical relationships}]. Saint Petersburg, Saint Petersburg
State University Publ., 2003, 64~p.



}
