
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1.  Von Neumann J.,  Morgenstern O. Theory of games and economic
behavior. Princeton, Princeton University Press, 1953, 666~p.

2.  Basar T. Time consistency and robustness of equilibria in
noncooperative dynamic games.  {\it Dynamic Policy Games in
Economics}. Eds by F.~Van~der~Ploeg, A.~de~Zeew. Amsterdam,
North-Holland, Elsevier Science Publ., 1989, pp.~9--54.

3. Beard R., McDonald S. Time consistent fair water sharing
agreements. {\it  Ann. Intern. Soc. Dyn. Games}. Boston,
Birkhauser Publ., 2007, vol.~9, pp.~393--410.

4. Marin-Solano J. Time-consistent equilibria in a differential
game model with time inconsistent preferences and partial
cooperation. {\it Dynamic Games in Economics}. Berlin, Springer
Publ., 2014, \mbox{pp.~219--238}.

5.   Yeung  D. W. K.,   Petrosyan L. A.  Cooperative stochastic
differential games. New York, Springer-Verlag Publ., 2006, 253~p.

6. Petrosyan L. A. Strongly time-consistent differential
optimality principles. {\it Vestnik of Saint Petersburg
University. Series Matematics. Mechanics. Astronomy}, 1993, no.~4,
pp.~35--40.

7.  Petrosyan L. A., Gromova E. V. On an approach to constructing
a characteristic function in cooperative differential games. {\it
Automation and Remote Control}, 2017, vol.~78, no.~9,
pp.~1680--1692.

8. Petrosyan L.,  Zaccour G. Time-consistent Shapley value
allocation of pollution cost reduction. {\it   Journal of Economic
Dynamics and Control}, 2003,  vol.~27, no.~3, pp.~381--398.

9.  Petrosyan L. A.  Time consistency of the optimality principles
in non-zero sum differential games. {\it  Lecture Notes in Control
and Information Sciences}, 1991, vol.~157, pp.~299--311.

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm


Received:  August 28, 2018.

Accepted: September 25, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip2mm\textit{Yaroslavna B. Pankratova} ---  PhD in Physics and
Mathematics; y.pankratova@spbu.ru

\vskip2mm\textit{Leon A. Petrosyan} --- Dr. Sci. in Physics and
Mathematics, Professor; l.petrosyan@spbu.ru

}
