
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Analysis of simplified gas transportation models. Calculation of the gas\\ leak location in a pipeline %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it G.~I.~Kurbatova, E.~M.~Vinogradova, V.~A.~Klemeshev%$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Kurbatova~G.~I., Vinogradova~E.~M., Klemeshev~V.~A. 
Analysis of simplified gas transportation models. Calculation of the gas leak location in a pipeline. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum, pp.~\pageref{p5}--\pageref{p5e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent An approach to a simplified calculation of the characteristics of a steady gas flow through a~pipeline is proposed. In this approach, the pressure is calculated using an isothermal model; the temperature analysis is reduced to a cubic equation solving. A simple analytical gas leak point coordinate dependence on the pressure and gas flow values is obtained at outlet from the pipeline. The result of comparison of calculations for the general and simplified models of gas flow in pipelines is presented. A criterion has been determined for the fulfillment of which it is permissible to use a simplified approach to calculating the gas characteristics and the leak point coordinates. Using an example of practical interest, the high accuracy of the calculation according to the proposed approach of both pressure and temperature in the flow and the gas leak coordinate in the pipeline is demonstrated.
\\[1mm]
\textit{Keywords}: natural gas flow, mathematical model, simplifications, analytical calculation of pressure, temperature, coordinates of the leak.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Murvay~P.~S. Silea~I. A survey on gas leak detection and 
localization techniques. \textit{J.~Loss Prev. Process Ind.}, 2012, vol.~25, pp.~966--973.

2. Lapteva~T.~I., Mansurov~M.~N. Obnaruzhenie utechek pri neustanovivshemsia techenii v trubakh 
[Transient leak detection flow in pipes]. 
\textit{Neftegazovoe delo} [\textit{Oil and Gas Affair}], 2006, pp.~1--15. (In Russian)

3. Zhu H., Lin P., Pen Q. 
A CFD (computational fluid dynamics) simulation for oil leakage from damaged submarine pipeline. 
\textit{Energy}, 2014, vol.~64, pp.~887--899.\\
https://doi.org/10.1016/j.energy.2013.10.037  

4. Thiberville~C., Wang~Y., Waltrich~P., Williams~W., Kam~S.~I.
Modeling of smart pigging for pipeline leak detection: 
From mathematical formulation to large-scale application. 
\textit{SPE Gas \textup{\&} Oil Technology Showcase and Conference}, 21--23 October, 2019. Dubai, UAE, Society of Petroleum Engineers Publ., 2019, pp.~1--27. %\\
https://doi.org/10.2118/198648-MS  

5. Butikov~Iu.~A., Chura~N.~I., Shirochenski~S.~I. 
\textit{Sovremennye distantsionnye metody~i apparatura kontrolia utechek iz magistralnykh truboprovodov} [\textit{Modern remote sensing methods and equipment for monitoring leaks from main pipelines}] 
Moscow, IRTs Gazprom Publ., 1995, 43~p. (Ser. Avtomatizaciia, te\-le\-mek\-ha\-ni\-za\-ciia i sviaz s gazovoi promyshlennostiu [Series Automatization, telemechanization and bond with gas industry]).  (In Russian) 



6. Liu~A.~E. 
Overview: Pipeline accounting and leak detection by mass balance, 
theory and hardware implementation. Los Angeles, Quantum Dynamics Inc. Publ., 2008, 15~p.


7. Vasilev~O.~F., Bondarev~E.~A., Voevodin~A.~F.,  Kanibolotskii~M.~A. 
\textit{Neizotermicheskoe techenie gaza v trubakh} [\textit{Non-isothermal gas flow in pipes}].  
Novosibirsk, Nauka Publ., 1978, 128~p. (In Russian)

8. Obibuike~U.~Ju., Ekwueme~S.~T., 
Ohia~N.~P., Igwilo~K.~Ch., Onyejekwe~I.~M., Igbojionu~A.~Ch.
Analytical model for the estimation of leak location in natural gas pipeline. \textit{International Journal of Oil, Gas and Coal Engineering}, 2019, vol.~7, no.~4,  pp.~95--102. %\\
https://doi.org/10.11648/j.ogce.20190704.12

9. Fukushima~K., Maeshima~R., Kinoshita~A., Shiraishi~H., Koshijima~I.  
Gas pipeline leak detection system using the online simulation method.  
\textit{Comp. Chem. Engng.}, 2000, vol.~24, pp.~453--456.

10. Voevodin~A.~F., Nikiforovskaya~V.~S.
Chislennyy metod opredeleniya mesta utechki zhidkosti ili gaza v truboprovode [A numerical method for identifying the location of a fluid leak in a pipeline]. \textit{Sibirian Journal Industrial Mathematics}, 2009, vol.~12, no. 1(37), pp.~25--30. (In Russian) 

11. Selezniov~V.~E., Boichenko~A.~L., Prialov~S.~N.
Operativnoe obnaruzhenie razryvov magistral'nykh gazoprovodov 
[Prompt detection of gas pipeline ruptures]. \textit{Matematicheskoe modelirovanie} [\textit{Mathematical modeling}], 2006, vol.~18, no.~2,  pp.~101--112. (In Russian)

12. Korshunov~S. \textit{Identifikatsiia utechek gaza. Magistral'nye gazoprovody vysokogo davleniia} [\textit{Iden\-ti\-fi\-ca\-tion of gas leaks. High pressure main gas pipelines}]. Saarbr\"ucken, Lambert Academic Publ., 2014, 218~p.


13. Kurbatova~G.~I., Ermolaeva~N.~N., Filippov~V.~B.,  Filippov~K.~B. 
\textit{Proektirovanie gazopro\-vo\-dov v severnykh moriakh} [\textit{Design of gas pipelines in the northern seas}]. 
St~Petersburg, Lan' Publ., 2020, 352~p. (In Russian)

14. Kurbatova~G.~I., Klemeshev~V.~A. Matematicheskii apparat obnaruzheniia mesta utechki v ga\-zo\-pro\-vo\-dakh [Mathematical apparatus for detecting a leak in gas pipelines]. \textit{Matematicheskoe mo\-de\-li\-ro\-va\-nie} [\textit{Ma\-the\-ma\-ti\-cal modeling}], 2021, vol.~33, no.~8, pp.~27--41. (In Russian)

15. Alarc\'on-Ramos~L.~\'A.,  P\'erez~P.~P.~G.
A useful application of a simulator for leak events in pipelines.  
\textit{International Journal of Applied Mathematics, Computational Science and Systems Engineering}, 2021, vol.~3, pp.~76--84.

16. Kurbatova~G.~I., Ermolaeva~N.~N. Sensitivity analysis of the gas transmission offshore pipeline model to variations of the model parameters. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019,  vol.~15, iss.~1,  pp.~47--61.\\
https://doi.org/10.21638/11702/spbu10.2019.104

17. Sivukhin~D.~V. \textit{Obshchii kurs fiziki}. V 5 t. T. 2. \textit{Termodinamika i molekuliarnaia fizika} 
[\textit{General course of physics}. In~5~vol. Vol.~2. \textit{Thermodynamics and molecular physics}]. Moscow, Fizmatlit Publ., 2006, 544~p. (In Russian) 

18. Reid~R., Prausnitz~J., Sherwood~T. 
\textit{The properties of gases and liquids}. 
New York, McGraw-Hill Inc. Publ., 1977, 548~p. 
(Rus. ed.: Reid~R., Prausnitz~J., Sherwood~T.
\textit{Svoystva gazov i zhidkostey}. Leningrad, Chemistry Publ., 1982, 592~p.)


19. Kurbatova~G., Klemeshev~V., Philippov~V.
Calculation of depressurization coordinate in underground and offshore gas pipelines. \textit{Journal of Physics: Conference Series}, 2022, vol.~2162, no.~012023, pp.~1--14. %\\
https://doi.org/10.1088/1742-6596/2162/1/012023


\vskip1.5mm Received:  March 18, 2022.

Accepted: May 05, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Galina I. Kurbatova} --- Dr. Sci. in Physics and Mathematics, Professor; g.kurbatova@spbu.ru \par
%
\vskip2mm \textit{Ekaterina M. Vinogradova} --- Dr. Sci. in Physics and Mathematics, Professor; e.m.vinogradova@spbu.ru \par
%
\vskip2mm \textit{Vladimir A. Klemeshev} --- PhD in Physics and Mathematics, Associate Professor; v.klemeshev@spbu.ru \par
%
%
}
