{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm


1.~Kerzner~H. \textit{Project management.} Hoboken, Wiley, 2013,
1296~p.


2.~Cuninghame-Green~R.~A. Projections in minimax algebra.
\textit{Math. Program.}, 1976, vol.~10, pp.~111--123.
DOI:~10.1007/BF01580656


3.~Zimmermann~U. \textit{Linear and combinatorial optimization in
ordered algebraic structures. Vol.~10 of Annals of Discrete
Mathematics.} Amsterdam, Elsevier, 1981, 390~p.
DOI:~10.1002/net.3230130312

4.~Butkovi\v{c}~P., Aminu~A. Introduction to max-linear
programming. \textit{IMA J. Manag. Math.}, 2009, vol.~20, no.~3,
pp.~233--249. DOI:~10.1093/imaman/dpn029

5.~Maslov~V.~P., Kolokol’tsov~V.~N. \textit{Idempotentnyj analiz i
ego primenenie v optimal’nom upravlenii \textup{[}Idempotent
analysis and its applications in optimal control\textup{]}.}
Moscow, Fizmatlit Press, 1994, 144~p. (In Russian)

6.~Golan~J.~S. \textit{Semirings and affine equations over them.
Vol.~556 of Mathematics and Its Applications.} New York, Springer,
2003, 256~p. DOI:~10.1007/978-94-017-0383-3

7.~Heidergott~B, Olsder~G.~J., van der Woude~J. \textit{Max Plus
at work. Princeton Series in Applied Mathematics.} Princeton,
Princeton University Press, 2006, 226~p.

8.~Krivulin~N.~K. \textit{Metody idempotentnoj algebry v zadachakh
modelirovaniya i analiza slozhnykh sistem \textup{[}Methods of
idempotent algebra for problems in modeling and analysis of
complex systems\textup{]}.} Saint Petersburg, Saint Petersburg
State University Publ., 2009, 256~p. (In Russian)

9.~Butkovi\v{c}~P. \textit{Max-linear systems. Springer Monographs
in Mathematics.} London, Springer, 2010, 272~p.
DOI:~10.1007/978-1-84996-299-5

10.~Krivulin~N. Explicit solution of a tropical optimization
problem with application to project scheduling.
\textit{Mathematical Methods and Optimization Techniques in
Engineering}. Eds. by D.~Biolek, H.~Walter, I.~Utu, C.~von Lucken.
Athens, WSEAS Press, 2013, pp.~39--45.

11.~Krivulin~N. A multidimensional tropical optimization problem
with nonlinear objective function and linear constraints.
\textit{Optimization}, 2015, vol.~64, no.~5, pp.~1107--1129.
DOI:~10.1080/02331934.2013. 840624

12.~Krivulin~N. A constrained tropical optimization problem:
complete solution and application example. \textit{Tropical and
Idempotent Mathematics and Applications. Vol.~616 of Contemporary
Ma-\linebreak thematics}. Eds by G.~L.~Litvinov, S.~N.~Sergeev.
Providence, AMS Publ., 2014, pp.~163--177. DOI:
10.1090/conm/616/12308

13.~Krivulin~N. A maximization problem in tropical mathematics: a
complete solution and application examples. \textit{Informatica},
2016, vol.~27, no.~3, pp.~587--606. DOI:
10.15388/Informatica.2016.101

14.~Krivulin~N.~K., Gubanov~S.~A. Reshenie zadachi setevogo
planirovanija na~osnove metodov tropicheskoj optimizacii [Solution
of a project scheduling problem by using methods of tropical
mathematics]. \textit{Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer Science. Control
Processes}, 2016, iss.~3, pp.~62--72. (In Russian)
DOI:~10.21638/11701/spbu10.2016.306

15.~Butkovi\v{c}~P., Tam~K.~P. On some properties of the image set
of a max-linear mapping. \textit{Tropical and Idempotent
Mathematics. Vol.~495 of Contemporary Mathematics}. Eds. by
G.~L.~Litvinov, S.~N.~Sergeev. Providence, AMS Publ., 2009,
pp.~115--126. DOI:~10.1090/conm/495/09694




\vskip 2mm

{\bf For citation:} Krivulin~N.~K., Gubanov~S.~A. The use of
tropical optimization methods in problems of project scheduling.
{\it Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~13,
iss.~\issuenum, pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
