
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1.  Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

2. Provotorov V.~V., Volkova A.~S.  \textit{Nachal'no-kraevie
zadachi s raspredelennimi parametrami na grafe} [\textit{Initial
boundary value problems with distributed parameters on the
graph}]. Voronezh, Nauchnay kniga Publ.,  2014,  188~p. (In
Russian)

3. Volkova A.~S., Provotorov V.~V.  Obobshhennye reshenija i
obobshhennye sobstvennye funkcii kraevyh zadach na geometricheskom
grafe [Generalized solutions and generalized eigenfunctions of
boundary-value problems on a geometric graph]. \emph{Izvestija
vysshih uchebnyh zavedenij. Mathematica} [\emph{Russian
Mathematics. Proceeding of Higher Educational Institutions}],
2014, vol.~58, no.~3, pp.~3--18. (In Russian)

4. Volkova A.~S., Gnilitskaya Yu.~A., Provotorov V.~V. On the
solvability of boundary-value problems for parabolic and
hyperbolic equations on geometrical graphs.  \emph{Automation and
Remote Control}, 2014, vol.~75, no.~2, pp.~405--412.

5. Part À.~À.  Razrechimost nachal'no-kraevoi zadachi
giperbolicheskogo tipa s raspredelennimi parametrami na grafe
[Solvability of initial-boundary value problem of hyperbolic type
with distributed parameters on the graph]. \emph{Management
systems and information technologies}, 2016, vol.~3, pp.~19--23.
(In Russian)

6. Provotorov V.~V. Boundary control of a parabolic system with
delay and distributed parameters on the graph.  \emph{Intern.
conference ``Stability and Control Processes'' in memory of V.~I.
Zubov} (\emph{SCP}). Saint Petersburg, 2015, pp.~126--128.

7. Podvalny S.~L., Provotorov V.~V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \emph{Intern. conference ``Stability and Control
Processes'' in memory of V.~I. Zubov} (\emph{SCP}). Saint
Petersburg, 2015, pp.~117--119.

8. Provotorov V. V., Provotorova E. N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredekennemi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \emph{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Sciense. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224. (In Russian)

9. Provotorov V. V., Provotorova E. N.  Optimal control of the
linearized Navier---Stokes system in a netlike domain.
\emph{Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Sciense. Control Processes}, 2017, vol.~13, iss.~4,
pp.~428--441. doi.org/10.21638/11701/spbu10.2017.409 (In Russian)

10. Provotorov V.~V. Boundary control of a parabolic system with
distributed parameters on a graph in the class of summable
functions. \emph{Automation and Remote Control}, 2015, vol.~76,
iss.~2, pp.~318--322.

11. Provotorov V. V.,  Ryazhskikh V. I., Gnilitskaya Yu. A. Unique
weak solvability of a nonlinear initial boundary value problem
with distributed parameters in a netlike region. \emph{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Sciense. Control Processes}, 2017, vol.~13, iss.~3, pp.~264--277.
doi.org/10.21638/11701/spbu10.2017.304

12. Karelin V.~V.  Shtrafnye funkcii v zadache upravleniea
processom nabludeniya [Penalty functions in the control problem of
an observation process]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss.~4, pp.~109--114.  (In Russian)

13. Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze
prognoza s ustoichivym lineinym pribligeniem [Plasma stabilization
by prediction with stable linear approximation]. \emph{Vestnik of
Saint Petersburg University. Series 10. Applied Mathematics.
Computer Science. Control Processes}, 2011, iss.~1, pp.~116--133.
(In Russian)

14.  Aleksandrov A.~Yu., Zhabko A.~P. On stability of the
solutions of a class of nonlinear delay systems. \emph{Automation
and Remote Control}, 2006, vol.~67, no.~9, pp.~1355--1365.

15. Sidnenko T.~I., Sergeev S.~M. Modelirovanie dvigenia
porozdennogo sprosa na agrarnom rynke v esloviyah asimmetrii
informacii [Modeling movements spawned by the demand for the
agricultural market in terms of information asymmetry].
\emph{Proceedings of Saint Petersburg State Agrarian}, 2015,
no.~39,\linebreak pp.~268--270. (In Russian)

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent
Received:  June 27, 2018.

Accepted: December 18, 2018.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Vyacheslav V. Provotorov} --- Dr. Sci. in Physics
and Mathematics, Professor; e-mail: wwprov@mail.ru

\vskip2mm\textit{Sergei M. Sergeev} --- PhD in Technics, Associate
Professor; sergeev2@yandex.ru

\vskip2mm\textit{Anna A. Part} --- anna\_razinkova@mail.ru

}
