
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf To the problem of the pursuit in quasilinear differential lag games%$^{*}$
 }

}

\vskip 2.5%3
mm

{\small

\noindent{\it E.\,M.\,Mukhsinov %
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2.5%3
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\noindent%
%$^2$~%
%St\,Petersburg State University, 7--9, Universitetskaya nab.,% %St\,Petersburg,
%
%\noindent%
%\hskip2.45mm%
%199034, Russian Federation


\noindent%
%$^2$~%
Tajik State University of Law, Business and Politics, 2, $17^{\rm th}$ mkr-n, Khujand,

\noindent%
%\hskip2.45mm%
735700, Republic of Tajikistan


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2.5%3
mm


\noindent \textbf{For citation:}  Mukhsinov E. M. To the problem of the pursuit in quasilinear differential lag games. {\it Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p3}--\pageref{p3e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum03 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent In the field of the theory of differential
games defined in a finite-dimensional space, fundamental works were
carried out by L. S. Pontryagin, N. N. Krasovskiy, B. N. Pshenichny,
L.~S.~Pet\-ro\-syan, M. S. Nikol’skiy, N. Yu. Satimov and others. L. S. Pontryagin and his students consider differential games separately,
from the point of view of the pursuer and from the point of view of the evader,
which inevitably connects the differential game with two different problems.
In this paper, in a Hilbert space, we consider the pursuit problem in the sense of L. S. Pontryagin for a quasilinear differential game,
when the dynamics of the game is described by a differential equation of retarded type with a closed linear operator ge\-ne\-ra\-ting a~strongly
continuous semigroup. Two main theorems on the solvability of the pursuit problem are proved.
In the first theorem, a set of initial positions is found from which it is possible to complete the pursuit with a guaranteed pursuit time.
The second theorem defines sufficient conditions on the optimality of the pursuit time.
The results obtained ge\-ne\-ralize the results of works by P. B. Gusyatnikov, M. S. Nikol'skiy, E. M. Mukhsinov, and M.~N.~Mu\-ro\-do\-va,
in which it is described by a differential equation of retarded type in a Hil\-bert space.
Our results make it possible to study delayed-type conflict-controlled systems not only with lumped, but also with distributed parameters.
\\[1mm]
\textit{Keywords}: pursuit problem, delay differential game,
Hilbert space, optimality of pursuit time.\par}

\vskip5%6
mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Pontrjagin L. S., Boltyanskiy V. G., Gamkrelidze R. V., Mishenko E. F.
{\it Matematicheskaya teoriya optimalnikh processov $[$Mathematical theory of optimal processes$]$}. Moscow, Nauka Publ., 1983, 393~p. (In Russian)

2. Balakrishnan A. V.
{\it Prikladnoy funcsionalniy analiz $[$Applied functional analysis$]$}. Moscow, Nauka Publ., 1980, 384~p. (In Russian)

3. Arguchinsev A. V., Srochko V. A. Procedura reguljarizacii bilinejnyh zadach optimal'nogo upravlenija na osnove konechnomernoj modeli
 $[$Procedure for regularization of bilinear optimal control problems based on a finite-dimensional model$]$.
{\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2022, vol.~18, no.~1, pp.~179--187.\\
https://doi.org/10.21638/11701/spbu10.2022.115 (In Russian)

4. Pontrjagin L. S. Linejnye differencial'nye igry presledovanija $[$Linear differential games of pursuit$]$.
{\it Matematicheskii sbornik} [{\it Mathematical collection}], 1980, vol.~112(154), no.~3, pp.~307--331. %
%http://dx.doi.org/10.1070/SM1981v040n03ABEH001815
(In Russian)

5. Krasovskiy N. N., Subbotin A. I.
{\it Pozicionnye differencial'nye igry $[$Positional differential games$]$}. Moscow, Nauka Publ., 1974, 456~p. (In Russian)

6. Gustyanikov P. B., Nikolskiy M. S. Ob optimal'nosti vremeni presledovaniya $[$On the optimality of the pursuit time$]$.
{\it Proceedings of the USSR Academy of Sciences}, 1969, vol. 184, no.~3, pp.~518--521. (In Russian)

7. Satimov N. Yu., Tukhtasinov M. Ob igrovyh zadachah na fiksirovannoj otrezke v upravlyaemyh evolyucionnyh uravneniyah pervogo poryadka
 $[$On game problems on a fixed interval in controlled first-order evolution equations$]$.
{\it Mathematical Notes}, 2006, vol.~80, no.~4, pp.~613--626. (In Russian)

8. Petrosyan L. A.
{\it Differencial'nye igry presledovaniya $[$Differential pursuit games$]$}. Leningrad, Leningrad State University Press, 1977, 222~p. (In Russian)

9. Mamadaliev N. Ob odnoj zadache presledovaniya s integral'nymi ogranicheniyami na upravleniya igrokov
 $[$On a pursuit problem with integral constraints on the players' controls$]$.
{\it Siberian Mathematical journal}, 2015, vol.~56, no.~1, pp.~129--148. https://doi.org/10.1134/S0037446615010115 (In Russian)

10. Friedman A. Differential games of purpsuit in Banach space.
{\it Journal of Mathematical Analysis and Applications}, 1969, vol.~25, pp.~93--113.

11. Osipov Yu. S. K teorii differencial'nyh igr v sistemah s raspredelennymi parametrami $[$On the theory of differential games in systems with distributed parameters$]$.
{\it Proceedings of the USSR Academy of Sciences}, 1975, vol.~223, no.~6, pp.~1314--1317. (In Russian)

12. Mukhsinov E. M. Ob optimal'nosti vremeni presledovaniya v differencial'nyh igrah $[$On the optimality of pursuit time in differential games$]$.
{\it Managed systems} (Novosibirsk), 1982, no.~2, pp.~80--87. (In Russian)

13. Mukhsinov E. M., Murodova M. N. Zadacha presledovaniya dlya differencial'noj igry s zapazdyvayushchim argumentom v beskonechnomernom prostranstve
$[$The pursuit problem for a delayed differential game in an infinite-dimensional space$]$.
{\it Bulletin of the Tajik National University. Series of natural sciences}, 2018, no.~3, pp.~79--86. (In Russian)

14. Hille E., Phillips R. S.
{\it Functional analysis and semi-groups}. New York, Colloquium Publ., 1957, 819~p. (Rus. ed.: Hille E., Phillips R. {\it Funktsional'nyi analiz i polugruppy}. Moscow, Inostr. lit. Publ., 1962, 830~p.)

15. Nakagiri S. Structural properties of functional differential equations in Banach spaces.
{\it Journal of Mathematical Analysis and Applications}, 1988, vol.~25, pp.~353--398.

16. Kantorovich L. V., Akilov G. P.
{\it Funkcional'nyj analiz $[$Functional analysis$]$}. Moscow, Nauka Publ., 1977, 744~p. (In Russian)

17. Castaing C., Valadier М. Convex analysis and measurable multifunctions.
{\it Lecture Notes Math.}, 1977, vol.~580, pp.~1--278.


\vskip1.5mm Received:  August 25, 2021.

Accepted: June 21, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r's \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Edgor M. Mukhsinov} --- PhD in Physics and Mathematics, Associate Professor;\\
 yodgor.mukhsinov@gmail.com \par
%
%
}
