

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Wardrop J.
Some theoretical aspects of road traffic research.
{\it Proceedings of the Institute of Civil Engineers}, 1952, vol.~1(3), pp.~325--362.

2. Krylatov A., Zakharov V., Malygin I.
Competitive traffic assignment in road networks.
{\it Transport and Telecommunication}, 2016, vol.~17(3), pp.~212--221.

3. Krylatov A., Zakharov V.
Competitive traffic assignment in a green transit network.
{\it International Game Theory Review}, 2016, vol.~18(2), p.~1640003.

4. Zakharov V., Krylatov A., Ivanov D.
Equilibrium traffic flow assignment in case of two navigation providers.
{\it IFIP Advances in Information and Communication Technology}, 2013, vol.~408, pp.~156--163.

5. Zakharov V., Krylatov A.
Transit network design for green vehicles routing.
{\it Advances in Intelligent Systems and Computing}, 2015, vol.~360, pp.~449--458.

6. Beckman M., McGuire C., Winsten C.
\textit{Studies in economics of transportation.
RM-1488}. Santa Monica, RAND Corporation Publ., 1955, 232~p.

7. Sheffi Y.
\textit{Urban transportation in networks: equilibrium analysis with mathematical program\-ming methods.}
New Jersey, Prentice-Hall, Inc., Englewood Cliffs Press, 1985, 416~p.

8. Yang H., Huang H.-J.
The multi-class, multi-criteria traffic network equilibrium and system optimum problem.
{\it Transportation Research Part B}, 2004, vol.~38, pp.~1--15.

9. Krylatov A.
Reduction of a minimization problem for a convex separable function with linear constraints to a fixed point problem.
{\it Journal of Applied and Industrial Mathematics}, 2018, vol.~12(1), pp.~98--111.

10. Krylatov A., Shirokolobova A.
Equilibrium route flow assignment in linear network as a system of linear equations.
{\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Sciences. Control Processes}, 2018, vol.~14, iss.~2, pp.~103--115.

11. Krylatov A., Zakharov V., Tuovinen T.
{\it Optimization models and methods for equilibrium traffic assignment}.
New York, Springer Intern. Publ., 2020, 239~p.

12. Krylatov A., Shirokolobova A.
Projection approach versus gradient descent for network's flows assignment problem.
{\it Lecture Notes in Computer Science}, 2017, vol.~10556, pp.~345--350.


\vskip 2%1.5
mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December 29, 2020.

Accepted: January 15, 2021.

%\vskip 6mm

\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Anastasiya P. Raevskaya} --- PhD in Physics and
Mathematics, Associate Professor;\\ a.raevskaya@spbu.ru

\vskip 2mm \textit{Alexander Y. Krylatov} ---  Dr.~Sci. n Physics and Mathematics, Professor; a.krylatov@spbu.ru \par
%
%
}
