
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Bobb L., Kieffer R., Lefevre T., Mazzoni S., Aumeyr T.,
Karataev~P., Billing~M., Conway~J., Shanks~J.} Feasibility of
diffraction radiation for noninvasive beam diagnostics as
characterized in a storage ring // Phys. Rev. Accel. Beams. 2018.
Vol.~21. P.~032801.

2. \textit{Sukhikh L., Kube G., Bajt S., Lauth W., Popov Y.,
Potylitsyn A.} Backward transition radiation in the extreme
ultraviolet region as a tool for the transverse beam profile
diagnostic // Phys. Rev. ST Accel. Beams. 2014. Vol.~17.
P.~112805.

3. \textit{Potylitsyn A. P., Ryazanov M. I., Strikhanov M. N.,
Tishchenko A. A}. Diffraction radiation from relativistic
particles. Berlin: Springer-Verlag, 2011. 278~p.

4. \textit{Doucas G., Kimmitt M. F., Doria A., Gallerano G. P.,
Giovenale E., Messina G., Andrews~H.~L., Brownell~J.~H.}
Determination of longitudinal bunch shape by means of coherent
Smith---Purcell radiation // Phys. Rev. ST AB. 2002. Vol.~5.
P.~072802.

5. \textit{Andrews H. L., Taheri F. B., Barros J., Bartolini R.,
Cassinari L., Clarke~C., Le~Corre~S., Delerue~N., Doucas~G.,
Fuster-Martinez~N., Konoplev~I., Labat~M., Perry~C., Reichold~A.,
Stevenson~S., Grosjean~M.~V.} Longitudinal profile monitors using
coherent Smith---Purcell radiation // Nucl. Instr. and Methods~A.
2014. Vol.~740. P.~212--215.

6. \textit{Alexeyev V. I., Eliseyev A. N., Irribarra E., Kishin I.
A., Kubankin A. S., Nazhmudinov~R.~M.} Observation of parametric
$X$-ray radiation in an anomalous diffraction region // Physics
Letters~A. 2016. Vol.~380. P.~2892--2896.

7. \textit{Sergeeva D. Y., Potylitsyn A. P., Tishchenko A. A.,
Strikhanov~M.~N.} Smith---Purcell radiation from periodic beams //
Optics Express. 2017. Vol.~25. P.~26310.

8. \textit{Гарибян Г. М., Ши Ян}. Рентгеновское переходное
излучение. Ереван: Изд-во АН Арм. ССР, 1983. 320~с.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 12 ноября 2018 г.

Cтатья принята к~печати 18 декабря 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Тищенко Алексей Александрович} --- канд.
физ.-мат. наук; tishchenko@mephi.ru

\vskip2mm \textit{Сергеева Дарья Юрьевна} --- dysergeyeva@mephi.ru

}
