
{\normalsize

\vskip 6mm

\noindent{\bf On the dispersion relation of radiation from charged
particles\\ in periodic structures$\,^*$}

}

\vskip 3mm%2mm

{\small

\noindent{\it A. A.
Tishchenko$\,^{1,2}$%
, D. Yu. Sergeeva$\,^{1,2}$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Ministry of
Science and Higher Education of the Russian Federation  in the
framework of Federal Targeted Program ``Research and Development
in the Priority Directions of Development of the Scientific and
Technological Complex of Russia for 2014--2020'' (agreement on
November 24, 2017, N~14.616.21.0088, ID RFMEFI61617X0088).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
National Research Nuclear University ``MEPhI'', 31, Kashirskoe
sh., Moscow,

\noindent%
\hskip2.45mm%
115409, Russian Federation

\noindent%
$^2$~%
National Research Center ``Kurchatov Institute'', 1, Akademika
Kurchatova pl., Moscow,

\noindent%
\hskip2.45mm%
123182, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip4mm%3mm


\noindent \textbf{For citation:}  Tishchenko A. A., Sergeeva D.
Yu. On the dispersion relation of radiation from charged particles
in periodic structures. {\it Vestnik of Saint~Petersburg
University. Applied\linebreak Mathematics. Computer Science.
Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p11}--\pageref{p11e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum11  (In Russian)

\vskip4mm%3mm

{\leftskip=7mm\noindent In this paper we considered analytically
one of the key features describing the radiation from charged
particles in periodic structures. It is shown that the dispersion
relation in the radiation from periodic structures with a finite
number of elements, both for polarization radiation mechanism and
forbremsstrahlung-type mechanism, including those in undulators
and wigglers, does not take into account all the details of the
spectral-angular distribution. Based on the analysis of the
asymptotic expression which allows one to represent the ratio of
squares of sines as the sum of delta functions, the factor has
been obtained that takes into account the contribution of
additional peaks. The expression depends on the number of elements
of the periodic structure, and in the limiting case of very large
number of elements turns into well-known asymptotic expression.
The resulting expression has been obtained in the form helpful for
further mathematical
analysis, including the use of saddle point technique.\\[1mm]
\textit{Keywords}: radiation from charged particles, dispersion
relation, periodic structures.
\par}

\vskip6mm%5mm

\noindent \textbf{References} }

\vskip 3mm%2mm

{\footnotesize

1. Bobb L., Kieffer R., Lefevre T., Mazzoni S., Aumeyr T.,
Karataev P., Billing M., Conway J., Shanks~J. Feasibility of
diffraction radiation for noninvasive beam diagnostics as
characterized in a storage ring. \textit{Phys. Rev. Accel. Beams},
2018, vol.~21, pp.~032801.

2. Sukhikh L., Kube G., Bajt S., Lauth W., Popov Y., Potylitsyn A.
Backward transition radiation in the extreme ultraviolet region as
a tool for the transverse beam profile diagnostic. \textit{Phys.
Rev. ST Accel. Beams}, 2014, vol.~17, pp.~112805.

3. Potylitsyn A. P., Ryazanov M. I., Strikhanov M. N., Tishchenko
A. A. \textit{Diffraction radiation from relativistic particles}.
Berlin, Springer-Verlag Press, 2011, 278~p.

4. Doucas G., Kimmitt M. F., Doria A., Gallerano G. P., Giovenale
E., Messina G., Andrews H. L., Brownell J. H. Determination of
longitudinal bunch shape by means of coherent Smith---Purcell
radiation. \textit{Phys. Rev. ST AB}, 2002, vol.~5, pp.~072802.

5. Andrews H. L., Taheri F. B., Barros J., Bartolini R., Cassinari
L., Clarke C., Le Corre S., Dele\-rue~N., Doucas G.,
Fuster-Martinez N., Konoplev I., Labat M., Perry C., Reichold A.,
Stevenson S., Gros\-jean~M.~V. Longitudinal profile monitors using
coherent Smith---Purcell radiation. \textit{Nucl. Instr. and
Me\-thods~A}, 2014, vol.~740, pp.~212--215.

6. Alexeyev V. I., Eliseyev A. N., Irribarra E., Kishin I. A.,
Kubankin A. S., Nazhmudinov R. M. Observation of parametric
$X$-ray radiation in an anomalous diffraction region.
\textit{Physics Letters A}, 2016, vol.~380, pp.~2892--2896.

7. Sergeeva D. Y., Potylitsyn A. P., Tishchenko A. A., Strikhanov
M. N. Smith---Purcell radiation from periodic beams.
\textit{Optics Express}, 2017, vol.~25, pp.~26310.

8. Garibian G. M., Yang C. {\it Rentgenovskoye perekhodnoye
izdaniye} [{\it X-ray transition radiation}]. Yerevan, Academy of
Science Arm. Sov. Soc. Republic, 1983, 320~p. (In Russian)


\vskip2mm %1.5mm %
Received:  November 12, 2018.

Accepted: December 18, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Alexey A. Tishchenko }--- PhD in Physics and
Mathematics; tishchenko@mephi.ru

\vskip2mm \textit{Daria Yu. Sergeeva }--- dysergeyeva@mephi.ru

}
