
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm



1. \emph{Калинина Е. А.} Общие собственные числа двух матриц~//
Дальневост. матем. журн. 2013. Т.~13, №~1. С.~52--60.

2.  \emph{Mailybaev A. A.} Computation of multiple eigenvalues and
generalized eigenvectors for matrices dependent on parameters~//
Numer. Linear Algebra Appl. 2006. N~13. P.~419--436.

3.  \emph{Schucan T. H., Weidenm\"{u}ller H. A.} Perturbation
theory for the effective interaction in nuclei~// Ann. Physics.
1973. N~76. P.~483--501.

4. \emph{Karow M.} Eigenvalue condition numbers and a formula of
Burke, Lewis and Overton~// Electron. J. Linear Algebra. 2006.
N~15. P.~143--153.

5.  \emph{Kressner D., Pel\'{a}ez M. J., Moro J.} Structured
H\"{o}lder condition numbers for multiple eigenvalues~// SIAM J.
Matrix Anal. Appl. 2009. Vol.~31, N~1. P.~175--201.

6. \emph{Burke J. V., Lewis A. S., Overton M.} Optimization and
pseudospectra, with applications to robust stability~// SIAM J.
Matrix Anal. Appl. 2003. Vol.~25, N~1. P.~80--104.

7. \emph{Jarlebring E., Kvaal S., Michiels W.} Computing all pairs
$(\lambda;\mu)$ such that $\lambda$ is a double eigenvalue of
$A+\mu B$~// SIAM J. Matrix Anal. Appl. 2011. N~32. P.~902--927.

8. \emph{Muhi\v{c} A., Plestenjak B.} A method for computing all
values $\lambda$ such that $A+\lambda B$ has a multiple
eigenvalue~// Linear Algebra Appl. 2014. N~440. P.~345--359.

9. \emph{Фаддеев Д. К., Фаддеева В.~Н.} Вычислительные методы
линейной алгебры. М.: Физматгиз, 1960.~656 с.

10. \emph{Littlewood D. E.} The theory of group characters and
matrix representations of groups. Oxford: Oxford University Press,
1950. 310~p.

11. \emph{Horn R. A., Johnson Ch. R.} Topics in matrix analysis.
New York: Cambridge University Press, 1991. 607~p.

12. \emph{MacDuffee C. C.} The Theory of Matrices. New York:
Chelsea Publ. Company, 1956. 110~p.

13. \emph{Фаддеев Д. К.} Лекции по~алгебре. М.: Наука, 1984.
416~с.

14. \emph{Гантмахер Ф. Р.} Теория матриц. 2-е изд. / пер. с англ.
М.: Наука, 1966. 576~с. ({\it Gantma-\linebreak cher~F.~R.} Theory
of matrices)

15. \emph{Strassen V.} Gaussian Elimination is not Optimal~//
Numerische Mathemetik. 1969. N~13. P.~354--356.

16. \emph{Уилкинсон Дж. Х.} Алгебраическая проблема собственных
значений / пер. с~англ. В.~В.~Вое\-водина, В.~Н.~Фаддеевой. М.:
Наука, 1970. 564~с. ({\it Wilkinson~J.~H.} The algebraic
eigenvalue problem)


}
