

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Kalinina E. A. Obshchie sobstvennye chisla dvuh matric [Common
eigenvalues of two matrices]. \emph{Far Eastern Mathematical
Journal}, 2013, vol.~13, no.~1, pp.~52--60. (In Russian)

2.  Mailybaev A. A. Computation of multiple eigenvalues and
generalized eigenvectors for matrices dependent on parameters.
\emph{Numer. Linear Algebra Appl.}, 2006, no.~13, pp.~419--436.

3.  Schucan T. H., Weidenm\"{u}ller H. A. Perturbation theory for
the effective interaction in nuclei. \emph{Ann. Physics.}, 1973,
no.~76, pp.~483--501.

4. Karow M. Eigenvalue condition numbers and a formula of Burke,
Lewis and Overton. \emph{Electron. J. Linear Algebra}, 2006,
no.~15, pp.~143--153.

5. Kressner D., Pel\'{a}ez M. J., Moro J. Structured H\"{o}lder
condition numbers for multiple eigenvalues. \emph{SIAM J. Matrix
Anal. Appl.}, 2009, vol.~31, no.~1, pp.~175--201.

6. Burke J. V., Lewis A. S., Overton M. Optimization and
pseudospectra, with applications to robust stability. \emph{SIAM
J. Matrix Anal. Appl.}, 2003, vol. 25, no.~1, pp.~80--104.

7. Jarlebring E., Kvaal S., Michiels W. Computing all pairs
$(\lambda;\mu)$ such that $\lambda$ is a double eigenvalue of
$A+\mu B$. \emph{SIAM J. Matrix Anal. Appl.}, 2011, no.~32,
pp.~902--927.

8. Muhi\v{c} A., Plestenjak B. A method for computing all values
$\lambda$ such that $A+\lambda B$ has a multiple eigenvalue.
\emph{Linear Algebra Appl.}, 2014, no.~440, pp.~345--359.

9. Faddeev D. K., Faddeeva V. N. \emph{Vychislitel'nyie metody
lineinoi algebry $[$Numerical methods of linear algebra$]$.}
Moscow, GIFML Publ., 1960, 656~p. (In Russian)

10. Littlewood D. E. \emph{The theory of group characters and
matrix representations of groups.} Oxford, Oxford University
Press, 1950, 310~p.

11. Horn R. A., Johnson Ch. R. \emph{Topics in matrix analysis.}
New York, Cambridge University Press, 1991, 607~p.

12. MacDuffee C. C. \emph{The Theory of Matrices.} New York,
Chelsea Publ. Company, 1956, 110~p.

13. Faddeev D. K. \emph{Lekcii po algebre $[$Lections in
algebra$]$}. Moscow, Nauka Publ., 1984, 416~p. (In Russian)

14. Gantmacher F. R. {\it Theory of matrices}. Providence, RI, AMS
Chelsea Publ. Company, 1960, vol.~2, 276~p. (Russ. ed.:
Gantmacher~ F.~R. {\it Teoriia matric}. Moscow, Nauka Publ., 1966,
576~p.)

15. Strassen V. Gaussian Elimination is not Optimal.
\emph{Numerische Mathematik.} 1969, no.~13, pp.~354--356.

16. Wilkinson J. H. {\it The algebraic eigenvalue problem}.
Oxford, Clarendon Press, 1965,~662~p. (Russ. ed.: Wilkinson~J.~H.
{\it Algebraicheskaia problema sobstvennyh znachenii}. Moscow,
Nauka Publ., 1970, 564~p.)




}
