

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm

1. {Demyanov V. F.} {\it Uslovija jekstremuma i variacionnoe
ischislenie} [{\it Extremum conditions and variation calculus}].
Moscow, Vysshaja shkola Publ., 2005, 334~p. (In Russian)

2. {Demyanov V. F., Tamasyan G. Sh.} O prjamyh metodah reshenija
variacionnyh zadach [On direct methods for solving variation
problems]. \textit{Trudy Instituta matematiki i mekhaniki UrO RAN}
[{\it Works of Institute of mathematics and mechanics of UrB
RAS}], 2010, vol.~16, no.~5, pp.~36--47. (In Russian)

3. Demyanov~V.~F., Dolgopolik M. V. Kodifferenciruemye funkcii v
banahovyh prostranstvah: metody i prilozhenija k zadacham
variacionnogo ischislenija [Codifferentiable functions in Banach
spaces: methods and applications to Problems of Variation
Calculus]. \textit{Vestnik of Saint Petersburg State University.
Series~10. Applied mathematics. Computer science. Control
processes}, 2013, issue~3, pp.~48--66. (In Russian)

4. Karelin V. V. Tochnye shtrafy v~odnoi zadache upravleniia
[Penalty functions in a control problem].  \textit{Avtomatika
i~telemekhanika}  [\textit{Automation and Remote Control}], 2004,
no.~3, pp.~483--492. (In Russian)

5. Demyanov V. F., Giannessi F., Karelin V. V. Optimal control
problems via exact penalty functions. \textit{Journal of Global
Optimization}, 1998, vol.~12, pp.~215--223.

6. Demyanov V. F., Rubinov A. M. {\it Osnovy negladkogo analiza i
kvazidifferencial'noe ischislenie} [{\it Basics of nonsmooth
analysis and quasidifferentiable optimization}]. Moscow, Nauka
Publ., 1990, 432~p. (In Russian)

7. Zubov V. I. {\it Lekcii po teorii upravlenija} [{\it Lectures
on optimal control}]. Moscow, Nauka Publ., 1975, 495~p. (In
Russian)

8. Egorov A. I. {\it Osnovy teorii upravlenija} [{\it Basics of
control theory}]. Moscow, Fizmatlit Publ., 2004, 502~p. (In
Russian)

9. Daugavet V. A. {\it Chislennye metody kvadratichnogo
programmirovanija} [{\it Numerical methods of quadratic
programming}]. Saint Petersburg, Saint Petersburg State University
Publ., 2001, 128~p. (In Russian)

10. Krylov I. A. Chislennoe reshenie zadachi ob optimal'noi
stabilizatsii sputnika [Numerical solution of the problem of the
optimal stabilization of an artificial satellite].  {\it Zhurn.
vychisl. matem.  i~matem. fiziki} [\textit{USSR Computational
Mathematics and Mathematical Physics}], 1968, vol.~8, issue~1,
pp.~284--291. (In Russian)

11. Gabasov R. Voprosy konstruktivnoj teorii optimal'nogo
upravlenija [Questions on constructive theory of optimal control].
{\it Vestn. Belorus. gos. un-ta. Ser.~1. Fizika. Matematika.
Informatika} [\textit{Vestnik of Byelorussian State University.
Series~1. Physics. Mathematics. Computer science}], 1981, no.~3,
pp.~55--61. (In Russian)





}
