{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Cormen T., Leiserson C., Rivest R., Stein C. {\it Introduction
to Algorithms.} 3rd ed. Cambridge, Massachusetts, MIT Press, 2009,
1312 p. (Russ. ed.: Cormen T., Leiserson C., Rivest R., Stein C.
{\it Algoritmy: Postroenie i Analiz.} Moscow, ``Williams'' Publ.,
2013, 1328~p.)

2. Levitin A. {\it Introduction to the Design \verb"&" Analysis of
Algorithms.} Boston, Massachusetts, Addison-Wesley, 2003, 497 p.
(Russ. ed.: Levitin~A. {\it Algoritmy: Vvedenie v Razrabotku i
Analiz.} Moscow, ``Williams'' Publ., 2006, 576~p.)

3. Pugh W. Skip Lists: A Probabilistic Alternative to Balanced
Trees. {\it Communications of the ACM}, 1990, vol.~33, no.~6,
pp.~668--676.

4. Bezlepkin V. V., Kukhtevich V. O., Obraztsov E. P., Migrov Yu.
A., Shaleninov~A.~A., Deulin~A.~A. {\it Programmno-tehnicheskij
Kompleks ``Virtual'nyj Energoblok AES s VVER'' dlja Proverki
Proektnyh Reshenij AES-2006} [{\it ``Virtual Power Unit of Nuclear
Power Plant with Pressurized Water Reactor'' Instrume-ntal Complex
Employment for Verifying Design Solutions}]. Available at:
http://www.gidropress.podolsk.ru/files/proceedings/mntk2013/documents/mntk2013-168.pdf
(accessed: 21.10.2015). (In Russian)

5. {\it Gorizonty Atoma (16.02.2013): Virtual'naja AES} [{\it Atom
Perspectives $($16.02.2013$)$: Virtual NPP}] News Agency ``Russian
Atomic Community''. Available at:
http://www.atomic-energy.ru/video/40025 (accessed: 15.09.2015).
(In Russian)

6. Kalinin D. V. {\it Mnogofunkcional'nyj Graficheskij Redaktor
Videokadrov BPU v Sostave Modeli-\linebreak\ rujush-hego Kompleksa
``Virtual'nyj Energoblok''} [{\it Multifunctional Graphics Editor
of Soft Panels within ``Virtual Power Unit'' Computer Complex}].
Available at:
http://docs.google.com/viewer?a=v\verb"&"pid=sites\verb"&"src
id=ZGVmYXVsdGRvbWFpbnxzaGFyaW5nc3BhY2UxNnxneDo0YWI3NTRhM2JlZTMxODE5
(acces-\linebreak sed: 20.02.2016). (In Russian)

7. Orekhov M. Yu. {\it Specialized Container and String Systems Employment in Vector Graphics Environment Development.} Available at: http://ieeexplore.ieee.org/xpl/articleDetails.jsp\verb"?"arnumber= 7342211\verb"&"new-search=true\verb"&"searchWithin="First\verb"%"20Name":Mikhail\verb"&"searchWithin="Middle\verb"%"20Name":Yu.\\ \verb"&"searchWithin="Last\verb"%"20Name":Orekhov (accessed: 15.02.2016).

8. Orekhov M. Yu. Bystrodejstvujushhaja Strokovaja Sistema na C++
[C++ Quick-operating String System]. {\it Processy Upravlenija i
Ustojchivost'} [{\it Control Processes and Stability}], 2014,
vol.~1, no.~1, pp.~363--368. (In Russian)

9. Orekhov M. Yu. Primenenie Podstroki v Realizacii
Bystrodejstvujuschej Strokovoj Sistemy na C++ [Substring
Employment in C++ Quick-operating String System Implementation].
{\it Vestnik of Saint Petersburg University. Series~10. Applied
mathematics. Computer science. Control processes}, 2015, issue~2,
pp.~134--149. (In Russian)

10. {\it International Standard ISO/IEC 14882:2014(E): Information
Technology — Programming Languages — C++.} 4th ed. 2014-12-15. §
12.8. Copying and moving class objects [class.copy] para. 31.
Available at:
http://www.iso.org/iso/home/store/catalogue\verb"_"tc/catalogue\verb"_"detail.htm\verb"&"csnumber=64029
(accessed: 20.12.2015).

11. Stroustrup B. {\it The C++ Programming Language.} Special ed.
Boston, Massachusetts, Addison-Wesley, 2000, 1040 p. (Russ. ed.:
Stroustrup B. {\it Jazyk Programmirovanija C++}. Ìoscow, Binom
Press, 2004, 1104 p.)

12. Blanchette J., Summerfield M. {\it C++ GUI Programming with Qt
4.} 2nd ed. Upper Saddle River, New Jersey, Prentice Hall, 2008,
752 p. (Russ. ed.: Blanchette J., Summerfield M. {\it Qt4:
Programmirovanie GUI na C++.} Ìoscow, Kudits Press, 2008, 736 p.)


}
