

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm



1. Markeev~A.\:P. \emph{Tochki libratsii v nebesnoi mekhanike i
kosmodinamike} [\emph{Libration points in celestial mechanics and
space dynamics}]. Moscow, Nauka Publ., 1978, 312~p. (In Russian)

2. Shmyrov~V.\:A. Stabilizatsiia upravliaemogo orbitalnogo
dvizheniia kosmicheskogo apparata v okrestnosti kollinearnoi
tochki libratsii $L_1$ [Stabilization of controlled orbital motion
of a spacecraft in the neighbourhood of the collinear libration
point $L_1$]. \emph{Vestnik of Saint Petersburg State University.
Series 10. Applied mathematics. Computer science. Control
processes}, 2005, issue~2, pp.~193--199. (In Russian)

3. Sim\'o~C., Stuchi~T.\:J. Central stable/unstable manifolds and
the destruction of KAM Tori in the planar Hill problem. {\it
Physica D}., 2000, vol.~140, issues~1--2, pp.~1--32.

4. Shmyrov~A.\:S., Shmyrov~V.\:A. Ob asimptoticheskoi
ustoichivosti po otnosheniiu k chasti peremennykh orbitalnogo
dvizheniia     kosmicheskogo apparata v okrestnosti kollinearnoi
tochki libratsii [On the asymptotic stability with respect to a
part of the      variables of the orbital motion of a spacecraft
in the neighbourhood of a collinear libration point].
\emph{Vestnik of Saint Petersburg State University. Series~10.
Applied mathematics. Computer science. Control processes}, 2009,
issue~4, pp.~250--257. (In Russian)

5. Shmyrov~A., Shmyrov~V. On controllability region of orbital
motion near $L_1$. \emph{Applied Mathematical Sciences}, 2015,
vol.~9~(145--148), pp.~7229--7236.

6. Shmyrov~A.\:S., Shmyrov~V.\:A. Sintez optimalnogo upravleniia
orbitalnym dvizheniiem v okrestnosti kollinearnoi tochki libratsii
[Optimal orbital motion control synthesis in the neighbourhood of
a collinear libration point]. \emph{Vestnik of Saint Petersburg
State University. Series 1. Mathematics. Mechanics. Astronomy},
2012, issue~4, pp.~139--146. (In Russian)

7. Birkhoff~G.\:D. \emph{Dynamical systems}. Providence, R.~I.,
American Mathematical Society, 1966,\linebreak 305~p. (Russ. ed.:
Birkhoff~G.~D. \emph{Dinamicheskie sistemy}. Izhevsk, Udmurtskii
University Publ., 1999,\linebreak 408~p.)\newpage

8. Gantmaher~F.\:R. \emph{Lektsii po analiticheskoi mekhanike}
[\emph{Lectures on the analytical mechanics}]. Moscow, Fizmatlit
Publ., 2005, 264~p. (In Russian)




\vskip 3mm

{\bf For citation:} Maliavkin G.~P., Shmyrov V.~A., Shmyrov A.~S.
Design of the stabilizing control of the orbital motion using the
analytical representation of an invariant manifold in the vicinity
of a collinear libration point. {\it Vestnik of Saint Petersburg
University. Applied mathematics. Computer science. Control
processes}, \issueyear, volume~13, issue~\issuenum,
pp.~\pageref{p10}--\pageref{p10e}.
\doivyp/spbu10.\issueyear.\issuenum10




}
