
{\normalsize

\vskip 6
mm

\noindent{\bf Optimal boundary control of string oscillations by displacement\\ at two ends with specified values of deflection function\\ at intermediate moments of time% $^{*}$%
}

}

\vskip 3%2
mm

{\small

\noindent{\it V.~R.~Barseghyan %

}

\vskip 3%2
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by Russian %
%Foundation for Basic Research (project N 20-07-00531 A).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

%\noindent%
%$^3$~%
%St\,Petersburg State University, 7--9, Universitetskaya nab.,
%St\,Petersburg,
%
%\noindent%
%\hskip2.45mm%
%199034, Russian Federation




\noindent%
%$^3$~%
Institute of Mechanics of the National Academy of Sciences of the Republic of Armenia,  %
 
\noindent%
%\hskip2.45mm%
24B, Marshal Baghramyan pr., Yerevan, 0019, Armenia

\noindent%
%\hskip2.45mm%
Yerevan State University, 1, ul. Alec Manukyan, Yerevan, %
%
%\noindent%
%\hskip2.45mm%
0025, Armenia


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip4%3
mm


\noindent \textbf{For citation:} Barseghyan V. R. Optimal boundary control of string oscillations by displacement at two ends with specified values of deflection function at intermediate moments of time. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p10}--\pageref{p10e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum10 (In Russian)

\begin{hyphenrules}{english}

\vskip4%2
mm

{\leftskip=7mm\noindent We consider the problem of optimal boundary control for the equation of string vibrations with given initial, final conditions and given values of the string deflection function at intermediate moments of time and with a quality criterion specified over the entire time interval. Using the method of separation of variables and methods of optimal control theory with multipoint intermediate conditions, optimal boundary controls are constructed for arbitrary numbers of the first harmonics. As an application of the proposed constructive approach, a boundary optimal control is built with a given string deflection function at an intermediate moment of time.\\[1mm]
\textit{Keywords}: string vibrations, optimal boundary control, optimal vibration control, intermediate conditions, variables separation. \par}

%\vskip 6mm

\end{hyphenrules}

\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. 	Butkovskiy A. G. {\it Teoriya optimal'nogo upravleniya sistemami s raspredelennymi parametrami} [{\it Theory of optimal control of systems with distributed parameters}]. Moscow, Nauka Publ., 1965, 476~p. (In Russian)

2. 	Znamenskaya L. N. {\it Upravlenie uprugimi kolebaniyami} [{\it Control of elastic vibrations}]. Moscow, Fizmatlit Publ., 2004, 176~p. (In Russian)

3. Zuazua E. {\it Controllability of partial differential equations.} Madrid, Universidad Autonoma Press, 2002, 311~p.

4.	Abdukarimov M. F. {Ob optimal'nom granichnom upravlenii smeshcheniyami protsessa vy\-nuzh\-den\-nykh kolebaniy na dvukh kontsakh struny} [On optimal boundary control of displacements in the process of forced vibrationson both ends of a string]. {\it Dokl. Akad. Nauk Republic of Tadzhikistan}, 2013, vol.~56, no.~8, pp.~612--618. (In Russian)

5.	Andreev A. A., Leksina S. V. {Zadacha granichnogo upravleniya dlya sistemy volnovykh uravneniy} [The boundary control problem for the system of wave equations]. {\it Vestnik of Samara State Technical University. Series Physics and Mathematics Sciences}, 2008, no.~1(16), pp.~5--10. (In Russian)

6. 	Gibkina N. V., Sidorov M. V., Stadnikova A. V. {Optimal'noe granichnoe upravlenie kole\-ba\-niya\-mi odnorodnoy struny} [Optimal boundary control of vibrations of uniform string]. {\it Radio\-elek\-tro\-nics and in\-for\-ma\-tiсs}, 2016, no.~2, pp.~3--11. (In Russian)

7. 	Il'in V. A., Moiseev E. I. Optimization of boundary controls of string vibrations. {\it Russian Mathematical Surveys}, 2005, vol.~60, iss.~6, pp.~1093--1119. \\
https://doi.org/10.1070/RM2005v060n06ABEH004283

8. 	Moiseev E. I., Kholomeeva A. A. On an optimal boundary control problem with a dynamic boundary condition. {\it Differential Equations}, 2013, vol.~49, pp.~640--644.\\
https://doi.org/10.1134/S0012266113050133

9. 	Moiseev E. I., Kholomeyeva A. A., Frolov A. A. {Granichnoe upravlenie smeshcheniem protsessa kolebaniy pri granichnom uslovii tipa tormozheniya za vremya, men'shee kriticheskogo} [Boundary displacement control for the oscillation process with boundary conditions of damping type for a time less than critical]. {\it Proceedings of the Intern. Conference ``Mathematical Modelling in Applied Sciences, ICMMAS--17’’. St~Petersburg Polytechnical University, July, 24--28, 2017. Results of science and technology. Series Modern Mathematics and its Applications. Thematic overview}, no.~160.  Moscow, VINITI Publ., 2019, pp.~74--84. (In Russian)

10. 	Kopets M. M. {Zadacha optimal'nogo upravleniya protsessom kolebaniya struny} [The problem of optimal control of the string vibration process]. {\it The theory of optimal solutions}. Kiev, V.~M.~Glush\-kov Institute of Cybernetics NAS of Ukraine Publ., 2014, pp.~32--38. (In Russian)

11. 	Barseghyan V. R.  Optimal control of string vibrations with nonseparate state function conditions at given intermediate instants. {\it Automation and Remote Control}, 2020, vol.~81, iss.~2, pp.~226--235. https://doi.org/10.1134/S0005117920020034

12. 	Barseghyan V. R. About one problem of optimal control of string oscillations with non-separated multipoint conditions at intermediate moments of time. {\it Stability, Control and Differential Games}. Eds A.~Tarasyev, V.~Maksimov, T.~Filippova. {\it Lecture Notes in Control and Information Sciences. Proceedings}. Cham, Springer Publ., 2020, pp.~13--25. %\\
https://doi.org/10.1007/978-3-030-42831-0\_2

13. 	Barseghyan V. R., Saakyan M. A. {Optimal'noe upravlenie kolebaniyami struny s zadannymi sostoyaniyami v promezhutochnye momenty vremeni} [The optimal control of wire vibration in the states of the given intermediate periods of time]. {\it Proceedings of NAS of Republic Armenia. Mechanics}, 2008, vol.~61, no.~2, pp.~52--60. (In Russian)

14.	Barseghyan V. R. {Ob odnoy zadache granichnogo optimal'nogo upravleniya kolebaniyami struny s ogranicheniyami v promezhutochnye momenty vremeni} [About one problem of optimal boundaery control of string vibrations with restrictions in the intermediate moment of time]. {\it Pro\-cee\-dings of the 11$^{th}$ Intern. Chetaev Conference  ``Analytical mechanics, stability and control’’}, June, 13--17, 2017, vol.~3, pt~1. Kazan, Kazan Scientific Research Tech. University Publ., 2017, pp.~119--125. (In Russian)

15. 	Barseghyan V. R., Solodusha S. V. {Zadacha granichnogo upravleniya kolebaniyami struny smeshcheniem levogo kontsa pri zakreplennom pravom kontse s zadannymi znacheniyami funktsii progiba v promezhutochnye momenty vremeni} [The problem of boundary control of string vibrations by displacement of the left end when the right end is fixed with the given values of the deflection function at intermediate times]. {\it Russian Universities Reports. Mathematics}, 2020, vol.~25, no.~130, pp.~131--146. (In Russian)

16. 	Barseghyan V. R., Movsisyan L. A. Optimal control of the vibration of elastic systems described by the wave equation. {\it Intern. Applied Mechanics}, 2012, vol.~48, iss.~2, pp.~234--239. \\
http://dx.doi.org/10.1007/s10778-012-0519-9

\newpage

17.	Barseghyan V. R. {\it Upravlenie sostavnykh dinamicheskikh sistem i sistem s mnogotochechnymi promezhutochnymi usloviyami} [{\it Control of compound dynamic systems and of systems with multipoint intermediate conditions}]. Moscow, Nauka Publ., 2016, 230~p. (In Russian)

18. 	Korzyuk V. I., Kozlovskia I. S. {Dvukhtochechnaya granichnaya zadacha dlya uravneniya kolebaniya struny s zadannoy skorost'yu v nekotoryy moment vremeni.~II} [Two-point boundary problem for the equation of string vibration with the given velocity at the certain moment of time.~II]. {\it Proceedings of the Institute of Mathematics NAS of Belarus}, 2011, vol.~19, no.~1, pp.~62--70. (In Russian)

19. 	Tikhonov A. N., Samarskii A. A. {\it Uravneniya matematicheskoy fiziki} [{\it Equations of mathema\-ti\-cal physics}]. Moscow, Nauka Publ., 1977, 736~p. (In Russian)

20. 	Krasovsky N. N. {\it Teoriya upravleniya dvizheniem} [{\it The theory of motion control}]. Moscow, Nauka Publ., 1968, 476~p. (In Russian)

\vskip1.5mm

Received:  December 5,  2021.

Accepted: June  21, 2022.


\vskip6mm A~u~t~h~o~r's \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Vanya R. Barseghyan} ---  Dr. Sci. in Physics and Mathematics, Professor, Leading Scientific\\ Researcher; barseghyan@sci.am \par%
%
%
}
