
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it     Буре В. М., Карелин В. В., Буре А. В.} Оценка объема
заказа товара при возможном падении спроса~// Вестн. С.-Петерб.
ун-та.  Прикладная математика. Информатика. Процессы управления.
2018. Т.~14. Вып.~3. C. 252--260. doi:
org/10.21638/11702/spbu10.2018.306

2. {\it  Буре В. М., Карелин В. В., Полякова Л. Н., Ягольник И.
В.}  Моделирование процесса заказа для кусочно-линейного спроса
с~насыщением~// Вестн. С.-Петерб. ун-та.  Прикладная математика.
Информатика. Процессы управления. 2017. Т.~13. Вып.~2.
С.~138--146.

3. {\it Bure V. M., Karelin V. V., Myshkov S. K., Polyakova L. N.}
Determination of order QUANTITY with piecewise-linear demand
function with saturation~//  Intern. Journal of Applied
Engineering Research.  2017. Vol.~12, N~18. P.~7857--7862.

4. {\it Giri B. C., Sharma S.} Optimal ordering policy for an
inventory system with linearly increasing demand and alowable
shortages under two levels trade credit financing~// Oper. Res.
Intern. Journal. 2016. Vol.~16.  P.~25--50.

5. {\it Aggarwal S. P., Jaggi C. K.}  Ordering policies of
deteriorating items under permissible delay in payments~//  J.
Oper. Res. Soc.  1995. Vol.~46, N~5. P.~658--662.

6. {\it     Dave U.} Letters and viewpoints on  economic order
quantity under conditions of permissible delay in payments~// J.
Oper. Res. Soc. 1985. Vol.~46,  N~5. P.~1069--1070.

7. {\it     Chen S. C., Teng J. T., Skouri K.}  Economic
production quantity models for deteriorating items with up-stream
full trade credit and down-stream partial trade credit~// Intern.
J. Prod. Econ.  2013. Vol.~155.  P.~302--309.

8. {\it     Giri B. C., Sharma S.}  An integrated inventory model
for a deteriorating item with allowable shortages and credit
linked wholesale price~//  Optim. Lett. 2015. Vol.~37.
P.~624--637. doi: 10.1007/s11590-014-0810-2

9. {\it     Goyal S.  K.}  Economic order quantity under
conditions of permissible delay in payments~// J.~Oper. Res. Soc.
1985. Vol.~36(4). P.~335--338.

10. {\it    Huang Y. F.} Optimal retailer’s ordering policies in
the EOQ model under trade credit financing~// J. Oper. Res. Soc.
2003. Vol.~54(9). P.~1011--1015.

11. {\it Huang Y. F., Hsu K. H.}  An EOQ model under retailer
partial trade credit policy in supply chain~// Intern. J. Prod.
Econ. 2008. Vol. 112(2). P. 655–664.

12. {\it    Jamal A. M. M., Sarker B. R., Wang S.}  An ordering
policy for deteriorating items with allowable shortages and
permissible delay in payment~// J. Oper. Res. Soc. 1997.
Vol.~48(8). P.~826--833.

13. {\it    Khanra S, Ghosh S. K., Chaudhuri K. S.} An EOQ model
for a deteriorating item with time dependent quadratic demand
under permissible delay in payment~// Appl. Math. Comput. 2011.
Vol.~218(1). P.~1--9.

14. {\it    Khanra S., Mandal B., Sarkar B.} An inventory model
with time dependent demand and shortages under trade credit policy
// Econ. Model. 2013. Vol.~35. P.~349--355.

15. {\it    Maihami R., Abadi I. N. K.}  Joint control of
inventory and its pricing for non-instantaneously deteriorating
items under permissible delay in payments and partial backlogging
// Math. Comp. Model. 2012. Vol.~55(5--6). P.~1722--1733.

16. {\it Bure   V. M., Karelin V. V., Polyakova  L. N.}
Probabilistic model of terminal services~// Appl. Math. Sci. 2016.
Vol.~10(39). P.~1945--1952.


17. {\it  Макаров В. Л., Рубинов А. М.} Математическая теория
экономической динамики  и~равновесия. М.: Наука, 1973.  336~с.


18. {\it Демьянов В. Ф.} Минимакс: дифференцируемость по
направлениям. Л.: Изд-во Ленингр. ун-та, 1974. 112~с.


19. {\it Полякова Л. Н.} О множестве возможных направлений
в~задачах со~связанными ограничениями~// Вестн. Ленингр. ун-та.
1984.  №~1.   С.~32--37.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 28 августа 2018 г.

Cтатья принята к печати 25 сентября 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Полякова Людмила Николаевна}  ---  д-p физ.-мат.
наук, проф.;  lnpol07@mail.ru

\vskip2mm \textit{Буре Владимир Мансурович}  ---  д-p техн. наук,
проф.; vlb310154@gmail.com

\vskip2mm \textit{Карелин Владимир Витальевич}  ---  канд.
физ.-мат. наук, доц.; vlkarelin@mail.ru

}
