
{\normalsize

\vskip 6mm

\noindent{\bf Maximin approach in estimating of the goods order
volume\\ under condition of falling demand}

}

\vskip 2mm

{\small

\noindent{\it L. N. Polyakova,  V. M. Bure, V. V. Karelin%$\,^1$%
%, I.~Î. Famylia%$\,^2$%
%, I.~Î. Famylia%$\,^2$%
}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Polyakova  L. N.,  Bure V. M.,
Karelin V. V. Maximin approach in estimating of the goods order
volume under condition of falling demand. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes},\,\issueyear,
vol.~14,~iss.~\issuenum,~pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The paper considers the problem of
choosing the optimal strategy of behaviour trading company in the
maxim in approach. Suppose that as a result of marketing research,
it was determined that in some unknown moment of time there would
be a noticeable change demand, the time points are known. It is
assumed that the trading company uses the following wholesale
order schemegoods. All ordered goods are divided into two parts,
with the first batch goods arrive immediately, and it must be sold
within a certain period $[0, T_{1}]$. The second batch of goods is
shipped at time $T$, however, the interval of time $[T_{1}, T]$
the second batch of goods are sold at a discount and a full not
implemented. The times $T_{1}$ and $T$ are was chosen by the
trading company from the condition of maximizing income. The need
to consider such a scheme wholesale order due to the fact that,
firstly, the warehouses of a trading company have limited volume
and cannot accommodate the entire volume of goods ordered  and
secondly, the manufacturer cannot offer all the ordered batch
goods, since not all goods can be produced in the initial (zero)
point in time when order is made. At time $T_{1}$ the trading
company will fully sell the first batch of goods and receive
funds, part of which she will pay to the manufacturer company. At
time $T$ there is a completion of the full realization of all
purchased goods. Selection of moments time $T_{1}$ and $T$ allows
for trade company to determine the volume of the first batch of
ordered goods and the total amount of all goods ordered from the
manufacturing company. In work, a mathematical model is suggested
that allows making the best choice order strategy for a trading
company under the condition of falling demand at some unknown time
from the interval. It is assumed that the interval is known. The
minimum function with compelled constraints is investigated. Under
some assumptions on the objective function and multi-valued
mapping, the form of the
derivative in directions is found.\\[1mm]
\textit{Keywords}: stock level, random demand, shortage of goods,
discount, maximin, directional derivative, multi-valued mapping.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Bure V. M., Karelin V. V., Bure A. V.} Ocenka ob'ema zakaza
tovara pri vozmozhnom padenii sprosa [Evaluation of the volume of
ordering of goods while possible demand drop]. {\it Vestnik of
Saint Peterburg University. Applied Mathematics. Computer Science.
Control Processes}, 2018, vol.~14, iss. 3, pp.~252--260. doi:
org/10.21638/11702/spbu10.2018.306 (In Russian)

2. {Bure V. M., Karelin V. V., Polyakova L. N., Yagolnik I. V.}
Modelirovanie processa zakaza dlya kusochno-linejnogo sprosa s
nasyshcheniem [Modeling of the ordering process for
piecewise-linear demand with saturation].{\it Vestnik of Saint
Peterburg University. Applied Mathematics. Computer Science.
Control Processes}, 2017, vol.~13, iss.~2, pp.~138--146. (In
Russian)

3. {Bure V. M., Karelin V. V., Myshkov S. K., Polyakova L. N.}
Determination of order QUANTITY with piecewise-linear demand
function with saturation. {\it Intern. Journal of Applied
Engineering Research},  2017, vol.~12, no.~18, pp.~7857--7862.

4.  {Giri B. C.,   Sharma S.} Optimal ordering policy for an
inventory system with linearly increasing demand and alowable
shortages under two levels trade credit financing. {\it Oper. Res.
Intern. Journal},   2016, vol.~16, pp.~25--50.

5. {Aggarwal S. P, Jaggi C. K.}  Ordering policies of
deteriorating items under permissible delay in payments. {\it
Oper. Res. Intern. Journal},   1995, vol.~46, no.~5, pp.~658--662.

6. {Dave U.}  Letters and viewpoints on  economic order quantity
under conditions of permissible delay in payments. {\it  J. Oper.
Res. Soc.},    1985, vol.~46, no.~5, pp.~1069--1070.

7. {Chen S. C, Teng J. T., Skouri K.}  Economic production
quantity models for deteriorating items with up-stream full trade
credit and down-stream partial trade credit. {\it Intern. J. Prod.
Econ.}, 2013, vol.~155, pp.~302--309.

8. {Giri B. C., Sharma S.} An integrated inventory model for a
deteriorating item with allowable shortages and credit linked
wholesale price. {\it Optim. Lett.}, 2015, vol.~37, pp.~624--637.
doi: 10.1007/s11590-014-0810-2

9.    Goyal S. K. Economic order quantity under conditions of
permissible delay in payments. {\it J. Oper. Res. Soc.},  1985,
vol.~36(4), pp.~335--338.

10. {Huang Y. F.}    Optimal retailer’s ordering policies in the
EOQ model under trade credit financing.  {\it  J. Oper. Res.
Soc.}, 2003, vol.~54(9), pp.~1011--1015.

11. {Huang Y. F., Hsu K. H.}    An EOQ model under retailer
partial trade credit policy in supply chain. {\it  Intern. J.
Prod. Econ.}, 2008, vol.~112(2), pp.~655--664.

12. {Jamal A. M. M., Sarker B. R., Wang S.}    An ordering policy
for deteriorating items with allowable shortages and permissible
delay in payment. {\it  J. Oper. Res. Soc.}, 1997, vol.~48(8),
pp.~826--833.

13. {   Khanra S., Ghosh S. K., Chaudhuri K. S.}    An EOQ model
for a deteriorating item with time dependent quadratic demand
under permissible delay in payment. {\it  Appl. Math. Comput.},
2011, vol.~218(1), pp.~1--9.

14. {Khanra S., Mandal B., Sarkar B.}  An inventory model with
time dependent demand and shortages under trade credit policy.
{\it Econ. Model.}, 2013, vol.~35, pp.~349--355.

15. {Maihami R., Abadi I. N. K.}   Joint control of inventory and
its pricing for non-instantaneously deteriorating items under
permissible delay in payments and partial backlogging. {\it  Math.
Comp. Model.}, 2012, vol.~55(5–6), pp.~1722--1733.

16. {Bure V.~M., Karelin V.~V., Polyakova L. N.} Probabilistic
model of terminal services. {\it  Appl. Math. Sci.}, 2016,
vol.~10(39),   pp.~1945--1952.

17. {Makarov V. L., Rubinov A. M.} {\it Matematicheskaya teoriya
ehkonomicheskoj dinamiki i rav\-no\-ve\-siya $[$Mathematical
theory economic dynamics and balance$]$}. Moscow, Nauka Publ.,
1973, 336~p. (In~Russian)

18. {Demyanov V. F.} {\it Minimaks: differenciruemost' po
napravleniyam $[$Minimax: differentiability in directions$]$}.
Leningrad, Leningrad State University  Publ., 1974, 112~p. (In
Russian)

19. {Polyakova L. N.} O mnozhestve vozmozhnyh napravlenij v
zadachah so svyazannymi ogranicheniyami [On the set of possible
directions in problems with related restrictions]. {\it Vestnik of
Le\-nin\-grad University}, 1984, no.~1, pp.~32--37. (In Russian)

\vskip1.5mm Received:  August 28, 2018.

Accepted: September 25, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Ludmila N. Polyakova}~--- Dr. Sci. in Physics
and Mathematics, Professor; lnpol07@mail.ru

\vskip2mm \textit{Vladimir M. Bure}~--- Dr. Sci. in Technics,
Professor; vlb310154@gmail.com

\vskip2mm \textit{Vladimir V. Karelin}~--- PhD in Physics and
Mathematics, Associate Professor; vlkarelin@mail.ru

}
