

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1.  Provotorov V.~V.    Optimal’noe upravlenie parabolicheskoi
sistemoi s raspredelennymi parametrami na grafe  [Optimal control
of parabolic systems with distributed parameters on the graph].
\emph{Vestnik of Saint Petersburg State University. Series 10.
Applied Mathematics. Computer Science. Control Processes}, 2014,
iss.~3, pp.~154--163. (In Russian)

2. Provotorov V.~V.   Startovoe upravlenie parabolicheskoi
sistemoi s raspredelennymi parametrami na grafe  [Start control of
parabolic systems with distributed parameters on the graph].
\emph{Vestnik of Saint Petersburg State University. Series 10.
Applied Mathematics. Computer Science. Control Processes}, 2015,
iss.~3, pp.~126--142. (In Russian)

3. Provotorov V. V. Boundary control of a parabolic system with
delay and distributed parameters on the graph. \emph{Intern.
conference ``Stability and Control Processes'' in memory of
V.~I.~Zubov} (SCP). Saint Petersburg, Saint Petersburg State
University Press, 2015, pp.~126--128.

4. Podvalny S. L., Provotorov V. V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \emph{Intern. conference ``Stability and Control
Processes'' in memory of V.~I.~Zubov} (SCP). Saint Petersburg,
Saint Petersburg State University Press, 2015, pp.~117--119.

5.    Provotorov V. V., Volkova A. S.   Nachal'no-kraevie zadachi
s raspredelennimi parametrami na grafe [Initial-boundary value
problems with distributed parameters on the graph]. Voronezh,
Nauchnaya kniga Publ., 2014, 188~p. (In Russian)

6. Provotorov V. V.   Boundary control of a parabolic system with
distributed parameters on a graph in the class of summable
functions.  \emph{Automation and Remote Control}, 2015, vol.~76,
no.~2, pp.~318--322.

7.   Lions J.-L.  \emph{Controle optimal de sistemes gouvernes par
des eqations aux derivees partielles}  [\emph{Optimum control of
the systems described by the equations with private derivative}].
Paris, Dunod Gauthier-Villars, 1968, 402 p. (Russ. ed.:
\emph{Lions~J.-L. Optimal’noe upravlenie sistemami, opisyvaemymi
uravnenijami s chastnymi proizvodnymi}. Moscow, Mir Publ., 1972,
414~p.).

8.    Volkova A. S., Provotorov V. V.  Obobshonnie reshenija i
obobshonnie sobstvennie funkcii kraevih zadach na geometricheskom
grafe [Generalized solutions and generalized eigenfunctions of the
boundary value problems on a geometric graph].  \emph{Izvestia
vyssh. ucheb. zavedenij. Mathematica} [\emph{Proceedings of Higher
Educational Institutions. Mathematics}], 2014, no.~3, pp.~3--18.
(In Russian)

9.    Provotorov V. V.    Razlozhenie po sobstvennim funkcijam
zadachi Shturma---Liuvillja na grafe-puchke [The expansion in
eigenfunctions of the Sturm---Liouville problem on a graph
bundle]. \emph{Izvestia vyssh. ucheb. zavedenij. Mathematica}
[\emph{Proceedings of Higher Educational Institutions.
Mathematics}], 2008, no.~3, pp.~50--62. (In Russian)

10.   Ladyzhenskaya Î. À.   \emph{Kraevie zadachi matematicheskoi
fiziki} [\emph{Boundary-value problems of mathematical physics}].
Moscow, Nauka Publ., 1973, 407~p. (In Russian)

11. Podval'ny S. L., Provotorov V. V. Optimizatsionnye zadachi
dlia evoliutsionnykh sistem s~ras- predelennymi parametrami
na~grafe
  [Optimal problems for evolution system with
distributed parameters on the graph]. \emph{Sovremennye metody
prikladnoi matematiki, teorii upravleniia i~komp'iuternykh
tekhnologii $($PMTUKT-2014$)$: sb. trudov VII Mezhdunar.
konferentsii} [\emph{Modern methods of Applied Mathematics,
Control Theory and Computer Technology} (\emph{PMTUKT-2014})].
{\it VII Intern. scientific conference}. Voronezh, Nauchnaia kniga
Publ., 2015, pp.~282--286. (In Russian)


12.    Podval'ny. S. L., Provotorov V. V.  Optimizacija po
startovim uslovijam parabolicheskoi sistemi s raspredelennimi
parametrami na grafe [Optimization for starting conditions of the
parabolic system with distributed parameters on the graph].
\emph{Control systems and information technologies}, 2014,
vol.~58, no.~4, pp.~70--74. (In Russian)

13.   Volkova A. S., Gnilitskaya Yu. A., Provotorov V. V.    On
the solvability of Boundary-Value problems for parabolic and
hyperbolic equations on geometrical graphs. \emph{Automation and
Remote Control}, 2014, vol.~75, no.~2, pp.~405--412.

14.    Aleksandrov À. Yu., Zhabko À. P.  Ob asimptoticheskoi
ustoichivosti reshenii nelineinyh sistem s zapazdyvaniem [On
asymptotic stability of solutions of nonlinear systems with
delay]. \emph{Automation and Remote Control},  2013, vol.~54,
no.~4, pp.~4--7.  (In Russian)

15.   Aleksandrov À. Yu., Zhabko À. P.    Ob  ustoichivosti
reshenii odnogo klassa nelineinyh sistem s zapazdyvaniem [On the
stability of solutions of a class nonlinear systems with delay].
\emph{Siberian Mathematical Journal}, 2003, vol. 44, no.~6,
pp.~1217--1228. (In Russian)

16.    Veremey Å. I., Korchanov V. Ì.  Mnogocelevaja stabilizacija
dinamicheskih sistem odnogo klassa [A multipurpose stabilization
of dynamical systems of a class]. \emph{Automation and Remote
Control}, 1988, no.~9, pp.~126--137.  (In Russian)

17.     Veremey Å. I., Sotnikova Ì. V.    Stabilizacija plazmy na
baze prognoza s ustojchivym linejnym priblizheniem [Plasma
stabilization on the basis of the forecast with steady linear
approach]. \emph{Vestnik of Saint Petersburg State University.
Series 10. Applied Mathematics. Computer Science. Control
Processes}, 2011, iss.~1, pp.~116--133.  (In Russian)

18.    Karelin V. V.    Shtrafnye funkcii v zadache upravlenija
processom nabljudenija [Penal functions in a problem of management
of supervision process]. \emph{Vestnik of Saint Petersburg State
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss.~4, pp.~109--114.  (In Russian)

19.   Potapov D. Ê.   Optimal’noe upravlenie raspredelennymi
sistemami ellipticheskogo tipa vysokogo porjadka so spektral'nym
parametrom i razryvnoi nelineinost'u [Optimal control of
distributed high order systems of elliptic type with a spectral
parameter and a discontinuous nonlinearity]. \emph{Izvestia RAN.
TiSU $[$Proceedings of Russian Academy of Sciences. Series
TeSU$]$}, 2013, no.~2, pp.~19--24. (In Russian)

20.   Kamachkin A. M., Yevstafyeva V. V.   Oscillations in a relay
control system at an external disturbance. \emph{Control
Applications of Optimization--2000. Proceedings of the 11th IFAC
Workshop}, 2000, vol.~2, pp.~459--462.





\vskip 2mm

{\bf For citation:}  Provotorov V. V., Provotorova E. N. Synthesis
of optimal boundary control of parabolic systems with delay and
distributed parameters on the graph. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
