
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Multi-purpose robotic arm control system %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it M.~A.~Smirnova, M.~N.~Smirnov, N.~V.~Smirnov %
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St~Petersburg State University, 7--9, Universitetskaya nab., St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Smirnova M.\,A., Smirnov M.\,N., Smirnov N.\,V. Multi-purpose robotic arm control system. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p15}--\pageref{p15e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum15 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent The purpose of this work is to create methods and algorithms for the formation of multi-purpose automatic control systems for the robotic arm, as well as to develop specialized software for computer modeling of the developed algorithms on the example of a real robotic arm. The methods of forming multi-purpose automatic motion control systems for various objects are developed, and the features of using a multi-purpose structure for control dynamic objects are studied.
\\[1mm]
\textit{Keywords}: automatic control, robotic arm, computer modeling.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Zubov V.\,I. {\it Lekcii po teorii upravlenija} [{\it Lections on control theory}]. St~Petersburg, Lan' Press, 2009, 496~p. (In Russian)

2. Zubov V.\,I. {\it Matematicheskie metody issledovanija sistem avtomaticheskogo regulirovanija} [{\it Mathematical methods of research of automatic control systems}]. Leningrad, Mashinostroenie Publ., 1974, 336~p. (In Russian)

3. Miroshnik I.\,V. {\it Teorija avtomaticheskogo upravlenija. Nelinejnye i optimal'nye sistemy} [{\it Auto\-ma\-tic control theory. Non\-li\-near and optimal systems}]. St~Petersburg, Piter Publ., 2005, 271~p. (In Russian)

4. Olsson G., Piani D. {\it Cifrovye sistemy avtomatizacii i upravlenija} [{\it Digital systems of automa\-tization and control}]. St~Petersburg, Nevskij Dialekt Publ., 2001, 557~p. (In Russian)

5. Cherneckij V.\,I., Diduk G.\,A., Potapenko A.\,A. {\it Matematicheskie metody i algoritmy issle\-dovanija avtomaticheskih sistem} [{\it Mathematical methods and algorithms of automatic systems re\-search}]. Leningrad, Jenergija Publ., 1970, 374~p. (In Russian)

6. Janushevskij R.\,T. {\it Teorija linejnyh optimal'nyh mnogosvjaznyh sistem upravlenija} [{\it The theory of linear optimal multivariable control systems}]. Moscow, Nauka Publ., 1973, 464~p. (In Russian)

7. Bosgra O.\,H., Kwakernaak H., Meinsma G. Design methods for control systems. {\it Notes for a
course of the Dutch Institute of Systems and Control}. Delft, Dutch Institute of Systems and Control Publ., 2006, 325~p.

8. Doyle J., Francis B., Tannenbaum A. {\it Feedback control theory}. New York,  Macmillan Publ. Co., 1992, 227~p.

9. Singh P., Deepak B.\,B.\,V.\,L., Sethi T., Murthy M.\,D.\,P.
Real-time object detection and tracking using color feature and motion. {\it Intern. Conference on Communication and Signal Pro\-ces\-sing}. Melvisharam, India, 2015, pp.~1252--1257.

10. Popkov A.\,S. Optimal program  control in the class  of quadratic splines for linear systems. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~4, pp.~462--470. https://doi.org/10.21638/11701/spbu10.2020.411

11. Zhabko A.\,P., Zhabko N.\,A., Jakovlev P.\,V. Metod optimal'nogo dempfirovanija V.\,I. Zubova v zadache upravlenija odnoj giroskopicheskoj sistemoj [Zubov's optimum damping method in the control problem of one gyroscope system]. {\it Vestnik of Saint Petersburg University. Applied Mathema\-tics. Computer Sciences. Control Processes}, 2022, vol.~18, iss.~2, pp.~278--284. \\ https://doi.org/10.21638/11701/spbu10.2022.208 (In Russian)

12. Veremei E.\,I., Korchanov V.\,M. Multiobjective stabilization of a certain class of dynamic systems. {\it Automation and Remote Control}, 1989, no.~49, pp.~1210--1219.

13. Veremej E.\,I. {\it Linejnye sistemy s obratnoj svjaz'ju} [{\it Linear systems with feedback}]. St~Peters\-burg, Lan' Press, 2013, 448~p. (In Russian)

14. Veremej E.\,I., Korchanov V.\,M. Mnogocelevaja stabilizacija dinamicheskih sistem odnogo klassa [Multipurpose stabilisation of one class of dynamic systems]. {\it Avtomatika i telemehanika $[$Automatics and Telemechanics$]$}, 1988,
no.~9, pp.~126--137. (In Russian)

15. Veremej E.\,I.  Sintez zakonov mnogocelevogo upravlenija dvizheniem morskih obektov [Synthe\-sis of multipurpose control for marine objects motion]. {\it Giroskopija i navigacija $[$Giroscopics and Navigation$]$}, 2009, no.~4, pp.~3--14. (In Russian)

16. Smirnov N.\,V., Smirnov A.\,N., Smirnova M.\,A., Smirnov M.\,N. Combined control syn\-the\-sis algorithm. {\it 2017 Constructive Nonsmooth Analysis and Related Topics (Dedicated to the memory of V.~F.~Demyanov), CNSA 2017 -- Proceedings.} St~Petersburg, 2017, pp.~194--196.

17. Smirnova M.\,A., Smirnov M.\,N., Smirnova T.\,E., Smirnov N.\,V. Multi-purpose control laws in motion control systems. {\it Information (Japan)}, 2017, vol.~20~(4), pp.~2265--2272.

18. Smirnov M.\,N., Smirnova M.\,A., Smirnova T.\,E., Smirnov N.\,V. The problem of synthesis the control laws with uncertainties in external disturbances. {\it Lecture Notes in Engineering and Computer Science}, 2017, vol.~2227, pp.~276--279.

19. Smirnov M.\,N., Smirnova M.\,A., Smirnova T.\,E., Smirnov N.\,V. The issues of mul\-ti\-pur\-pose control laws construction. {\it Lecture Notes in Engineering and Computer Science}, 2017, vol.~2227, pp.~194--196.

20. Smirnova M.\,A., Smirnov M.\,N. Multipurpose control laws in trajectory tracking prob\-lem. {\it Intern. Journal of Applied Engineering Research}, 2016, vol.~11~(22), pp.~11104--11109.

21. Vitrant E., Canudas-De-Vit C., Georges D., Alamir M. Remote stabilization via time-varying communication network delays: application to TCP networks. {\it IEEE Con\-fe\-rence in Control Applicati\-ons}, 2004, vol.~1, pp.~474--479.


\vskip1.5mm Received:  August 13, 2022.

Accepted: September 01, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%

\vskip2mm \textit{Maria A. Smirnova} ---  PhD in Physics and Mathematics, Senior Lecturer; mariya.smirnova@spbu.ru

\vskip2mm \textit{Mikhail N. Smirnov} ---  PhD in Physics and Mathematics, Associate Professor;\\ mikhail.smirnov@spbu.ru

\vskip2mm \textit{Nikolay V. Smirnov} ---  Dr. Sci. in Physics and Mathematics, Professor; n.v.smirnov@spbu.ru \par
%
%
}
