

{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1. {Gutman E.~M.} {\it Mechanochemistry of solid surfaces}.
Singapore, World Scientific, 1994, 325~p.

2. {Dolinskiy~V.~M.} Raschet nagruzhennykh trub, podverzhennykh
korrozii [Calculations on loaded tubes exposed to corrosion]. {\it
Khim. i neftyanoye mashinostroyeniye} [{\it Chemical and Petroleum
Engineering}], 1967, no.~2, pp.~9--10. (In Russian)

3. {Pavlov~P.~A., Kadyrbekov~B.~A., Kolesnikov~V.~A.} {\it
Prochnost' staley v korrozionnykh sredakh} [{\it Strength of
Steels in Corrosive Environments}]. Alma-Ata, Nauka Publ., 1987,
272~p. (In Russian)

4. {Naumova~G.~A., Ovchinnikov~I.~G.} {\it Raschety na prochnost'
slozhnykh sterzhnevykh sistem i truboprovodnykh konstruktsiy s
uchetom korrozionnykh povrezhdeniy} [{\it Strength Calculations of
Compound Frameworks and Pipeline Structures with Taking into
Account Corrosion Damages}]. Saratov, Saratov. State Tech.
University Publ., 2000, 227~p.  (In Russian)

5. {Bergman~R.~M., Levitsky~S.~P., Haddad~J., Gutman~E.~M.}
Stability loss of thin-walled cylindrical tubes, subjected to
longitudinal compressive forces and external corrosion. {\it
Thin-Walled Structures}, 2006, vol.~44, no.~7, pp.~726--729.

6. {Rusanov~A.~I.} Mekhanokhimiya rastvoreniya: kineticheskiy
aspekt [Mechanochemistry of dissolution: kinetic aspect]. {\it
Zhurnal obshchey khimii} [{\it Russian Journal of General
Chemistry}], 2007, vol.~77, no.~4, pp.~529--542. (In Russian)

7. {Ovchinnikov~I.~I., Ovchinnikov~I.~G., Zanin~A.~A.,
Zelentsov~D.~G., Korotkaya~L.~I.} Problema optimal'nogo
proyektirovaniya nagruzhennykh konstruktsiy, podvergayushchikhsya
vozdeystviyu agressiv-\linebreak nykh sred (obzor) [Problem of
optimum design of the loaded constructions which are exposed to
influence\linebreak\newpage\noindent of aggressive environments
(review)]. {\it Internet-zhurnal Naukovedeniye} [{\it On-line
Journal Naukovedenie}], 2012, no.~4~(13), p.~97. (In Russian)

8. {Elishakoff~I., Ghyselinck~G., Miglis~Y.} Durability of an
elastic bar under tension with linear or nonlinear relationship
between corrosion rate and stress. {\it Journal of Applied
Mechanics, Trans. ASME}, 2012, vol.~{79}~(2), p.~21013.

9. {Lokoshchenko~A.~M., Sokolov~A.~V.} Polzuchest' i dlitel'noye
razrusheniye tsilindricheskoy obolochki pod vneshnim davleniyem v
prisutstvii agressivnoy sredy [Creep and long-time fracture of a
cylindrical shell under external pressure in the presence of an
aggressive medium]. {\it Izv. Rossiyskoy akademii nauk. Mekhanika
tverdogo tela} [{\it Proc. of the Russian Academy of science.
Mechanics of Solids}], 2014, no.~1, pp.~65--76. (In Russian)

10. {Pronina~Yu.~G.} Mekhanokhimicheskaya korroziya pologo
tsilindra iz ideal'nogo uprugo-plasticheskogo materiala pod
deystviyem postoyannogo davleniya [Mechanochemical corrosion of an
ideal elasto-plastic quill cylinder under the constant pressure].
{\it Vestnik of Saint Petersburg University. Series~1.
Mathematics. Mechanics. Astronomy}, 2006, issue~3, pp.~121--130.
(In Russian)

11. {Pronina~Yu.~G.} Ravnomernaya mekhanokhimicheskaya korroziya
poloy sfery iz ideal'nogo uprugoplasticheskogo materiala pod
deystviyem postoyannogo davleniya [Equal mechanochemical corrosion
of an ideal elasto-plastic hollow sphere under constant pressure].
{\it Vestnik of Saint Petersburg University. Series~1.
Mathematics. Mechanics. Astronomy}, 2009, issue~1, pp.~113--122.
(In Russian)

12. {Pronina~Y.~G.} Thermoelastic stress analysis for a tube under
general mechanochemical corrosion conditions. {\it Proceedings of
the 4th Intern. Conference on Computational Methods for Coupled
Problems in Science and Engineering, COUPLED PROBLEMS--2011},
2011, pp.~1408--1415.

13. {Sedova O.~S., Pronina Y.~G.} Taking account of hydrostatic
pressure in the modeling of corrosion of thick spherical shells.
{\it Proceedings of Intern. Conference on Mechanics~--- Seventh
Polyakhovs Reading}, 2015, p.~7106771.

14. {Tanchenko~A.~Yu., Litvinenko~A.~V., Chepurnoy~A.~D.,
Kostenko~Yu.~V., Tkachuk~N.~A.} Metod pryamogo konechnogo
vozmushcheniya chislennykh modeley pri issledovanii
dinamicheskikh, zhestkostnykh i prochnostnykh kharakteristik
tonkostennykh elementov mashinostroitel'nykh konstruktsiy. {\it
Vestnik of Bryansk State Technical University}, 2014, vol.~4 (44),
pp.~114--124. (In Russian)

15. {Tkachuk N.~N., Chepurnoy A.~D., Skripchenko N.~B., Litvinenko
A.~V., Tkachuk N.~A.} Mnogourovnevyye modeli v zadache analiza
kontaktnogo vzaimodeystviya slozhnoprofil'nykh tel: algoritmy,
realizatsiya i analiz primenimosti (okonchaniye) [Multilevel
Models Applied for the Analysis of the Contact Interaction of
Geometrically-Complex Bodies: Algorithms, Implementation and
Applicability Analysis (final part)]. {\it
Kuznechno-shtampovochnoye proizvodstvo. Obrabotka materialov
davleniyem} [{\it Forging and Stamping Production. Material
Working by Pressure}], 2014, no.~8, pp.~6--8. (In Russian)

16. {Sedova~O.~S., Pronina~Y.~G.} Generalization of the Lame
problem for three-stage decelera-\linebreak ted corrosion process
of an elastic hollow sphere. {\it Mechanics Research
Communications}, 2015, vol.~65,\linebreak  pp.~30--34.

17. {Yang~Y., Zhang~T., Shao~Y., Meng~G., Wang~F.} New
understanding of the effect of hydrostatic pressure on the
corrosion of Ni--Cr--Mo--V high strength steel. {\it Corrosion
Science}, 2013, vol.~73, pp.~250--261.

18. {Gasratova~N.~A., Shamina~V.~A.} Ob odnom podkhode k resheniyu
osesimmetrichnykh zadach lineynoy teorii uprugosti [On a certain
approach for solving the axisymmetric problem of linear elasticity
theory]. {\it Vestnik of Saint Petersburg University. Series~1.
Mathematics. Mechanics. Astronomy}, 2007, issue~2, pp.~101--106.
(In Russian)

19. %\bibitem{Bauer2011}
{Voronkova~E.~B., Eriksson~A., Bauer~S.~M.} Nonclassical theories
of shells in application to soft biological tissues. {\it Advanced
Structured Materials}, 2011, vol.~15, pp.~647--654.

20. {Gasratova~N.~A.} Resheniye nekotorykh klassicheskikh
prostranstvennykh zadach teorii uprugosti v napryazheniyakh
[Solution of Some Classic Three-Dimensional Problems of Elasticity
Theory]. {\it Molodoy uchenyy} [{\it Young Scientist}], 2014,
no.~3~(62), pp.~1--6. (In Russian)

21. {Zhukova~I.~V., Kolpak~E.~P.} Matematicheskiye modeli
zlokachestvennoy opukholi [Mathematical models of malignant
tumour].  {\it Vestnik of Saint Petersburg University. Series~10.
Applied mathematics. Computer science. Control processes}, 2014,
issue~3, pp.~5--18. (In Russian)

22. {Mal'kov~V.~M., Kabrits~S.~A., Mansurova~S.~E.}
Matematicheskoye modelirovaniye nelineynoy deformatsii
elastomernogo sloya [Mathematic modeling of nonlinear deformation
elastomeric layer]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, 2011, issue~3, pp.~56--63. (In Russian)

23. {Kabrits~S.~A., Shamina~V.~A.} Izgib obolochki vrashcheniya
poperechnoy siloy i momentom [Bending shell of revolution by
transverse force and moment]. {\it Vestnik of Saint Petersburg
University. Series~1.  Mathematics. Mechanics. Astronomy}, 2014,
issue~2, pp.~261--270. (In Russian)

24. {Kolpak~E.~P., Mal'tseva~L.~S.} Bol'shiye deformatsii
rezinovykh membran [Large Deformation Rubber Membrane]. {\it
Molodoy uchenyy} [{\it Young Scientist}], 2014, no.~16,
pp.~78--84. (In Russian)

25. {Kolpak~E.~P., Mal'tseva~L.~S.} Kruglaya ploskaya membrana pri
bol'shikh deformatsiyakh [Circle\linebreak flat membrane for large
deformations]. {\it Privolzhskiy nauchnyy vestnik} [{\it
Scientific and Practical Journal Volga Scientific Bulletin}],
2014, no.~11--1~(39), pp.~5--10. (In Russian)

26. {Grekov~M.~A., Kostyrko~S.~A.} Plenochnoye pokrytiye na
sherokhovatoy poverkhnosti uprugogo tela [A film coating on a
rough surface of an elastic body]. {\it Prikladnaya matematika i
mekhanika} [{\it Applied Mathematics and Mecanics}], 2013,
vol.~77, issue~1, pp.~113--128. (In Russian)

27. {Mal'kov~V.~M., Mal'kova~Yu.~V., Stepanova~V.~A.}
Dvukhkomponentnaya ploskost' iz materiala Dzhona s mezhfaznoy
treshchinoy, nagruzhennoy davleniyem [Bi-material plane of John’s
material with interface crack loaded by pressure].  {\it Vestnik
of Saint Petersburg University. Series~1. Mathematics. Mechanics.
Astronomy}, 2013, issue~3, pp.~113--125. (In Russian)

28. {Sedova~O.~S.} Stress distribution in the neighborhood of a
corrosion pit on the outer surface of an elastic spherical shell.
{\it Proceedings of 2nd Intern. Conference on Emission Electronics
(ICEE). Selected papers}. Eds N.~V.~Egorov, D.~A.~Ovsyannikov,
E.~I.~Veremey. Saint~Petersburg, Saint~Petersburg State University
Publ., 2014, pp.~78--81.

29. {Pavlovskiy~V.~A., Chistov~A.~L.} Modelirovaniye dinamiki
zapolneniya rezervuara real'nym gazom [Modelling of real gas tank
fill-up dynamics].  {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, 2014, issue~3, pp.~46--57. (In Russian)

30. {Pavlovsky~V.~A., Chistov~A.~L.} Computation parameters of
cargo reservoir fill-up process on cng-vessels in MATLAB. {\it
Proceedings of Intern. conference on computer technologies in
physical and engineering applications (ICCTPEA)}. Ed.
E.~I.~Veremey. Saint~Petersburg, Saint~Petersburg State
University; IEEE (IEEE Catalog number CFP14BDA-USB), 2014, p.~136.



}
