
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3 mm

{\footnotesize

1. {\it Toth R.}  Multiple degree-of-freedom nonlinear spinal
model~// Proceeding of 19th Annual Con\-ference on Engineering in
Medicine and Biology.  San Francisco, California, 1967.
P.~126--132.

2. {\it Bai Xian-Xu, Xu Shi-Xu, Cheng Wei, Qian Li-Jun.} On
4-degree-of-freedom bio\-dynamic models of seated occupants:
Lumped-parameter modeling~// Journal of Sound and Vibration. 2017.
Vol.~402. N~18.  P.~122--141.

3. {\it Thompson G.~T.} In vivo determination of mechnical
properties of the human ulna by mechanical impedance tests:
Experimental results and improved mathematical model~// Medical
and Biological Engineering. 1976. Vol.~14. P.~253--262.

4. {\it Orne D.} The in vivo driving-point impedance of the human
ulna --– a viscoelastic beam modal~// Journal of Biomechanics.
1974. Vol.~7. P.~249--257.

5. {\it Kizilova N.~N.} Presser wave propagation in liquid field
// Fluid dynamics. 2006. Vol.~41. N~3. P.~434--446.

6. {\it Андронов А.~А., Хайкин С.~Э.} Теория колебаний. М.; Л.:
ОНТИ НКТП СССР, 1937. 519~с.

7. {\it Андронов А.~А., Витт А.~А., Хайкин С.~Э.}   Теория
колебаний. М.: Физматгиз, 1959.  916~с.

8. {\it Пановко Я.~Г., Губанова И.~И.} Устойчивость и~колебания
упругих систем. М.: Наука, 1987.  352~с.

9. {\it Orne D., King L. Y.} A mathematical model of spinal
response to impact~// Journal of Bio\-me\-cha\-nics. 1971. Vol.~4.
N~1. P.~49--71.

10. {\it Жарнов А.~М., Жарнова О.~А.} Биомеханические процессы
в~межпозвонковом диске шейного отдела позвоночника при его
движении~// Рос. журн. биомеханики. 2013. Т.~17. № 1. С.~32--40.

11. {\it Трегубов В.~П., Егорова Н.~К.} Модельное изучение влияния
многосуставных мышц  на частотные характеристики тела человека~//
Вестн. С.-Петерб. ун-та. Прикладная математика. Информатика.
Процессы управления. 2020. Т.~16. Вып.~2. С.~150--164. \\
https://doi.org/10.21638/11702/spbu10.2020.207

12. {\it Ciach M., Awrejcewicz J., Maciejczak A., Radek M.}
Experimental and numerical investigations of C5--C6 cervical
spinal segment before and after discectomy using the Cloward
operation technique~// Acta of Bioengineering and Biomechanics.
1999. Vol.~1. N~1. P.~101--105.

\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 24 июня 2020~г.

Cтатья принята к~печати 13 августа 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Трегубов Владимир Петрович}~---  д-р физ.-мат.
наук, проф.; v.tregubov@spbu.ru

\vskip2mm\textit{Егорова Надежда Константиновна}~---  аспирант;
nadezhda\_ego@mail.ru

}
