
{\normalsize

\vskip 6mm

\noindent{\bf Zubov's optimum damping method in the control problem \\ of one gyroscope system$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it A.~P. Zhabko, N.~A. Zhabko, P.~V. Yakovlev %

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by Russian Foundation for Basic Research (project N 20-07-00531 A).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^3$~%
St\,Petersburg State University, 7--9, Universitetskaya nab.,
St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Zhabko~A.~P., Zhabko~N.~A., Yakovlev~P.~V. Zubov's optimum damping method in the control problem of one gyroscope system. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p8}--\pageref{p8e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08 (In Russian)

\begin{hyphenrules}{english}

\vskip2mm

{\leftskip=7mm\noindent The article considers the control problem of the aircraft cabin simulator with a four-axis gimbal gyroscopic system. The difficulty of the control problem of standard three-axis gimbal gyroscopic system is the presence of the phenomena ``gimbal lockТТ when the two axes of the system become collinear or close to collinear. One of the applied solutions to avoid ``gimbal lockТТ is to use of the fourth additional gimbal. Such fore-axis gimbal systems are presented in the works of various autors. However, the problem of an optimal control of four-axis gimbal gyroscopic system is still under the question. Sufficient conditions for the solvability of the control problem are obtained on the base of the one-to-one interconnection between the movement of the cabin, the angular velocities of the cabin axes and the necessary deviations of gimbals rotation angles. This result is presented in lemmas. According this obtained sufficient conditions,  the algorithm for constructing a control of the gimbal system in terms of optimal damping process of movement, according to Zubov's method, is proposed.\\[1mm]
\textit{Keywords}: dumping, optimal control, gyroscope, rotation control. \par}

%\vskip6mm%5

\end{hyphenrules}

\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {\textnormal Jie~M., Qinbei~X.} Four-axis gimbal system application based on gimbal self-adaptation adjustment. {\itshape Proceedings of the 34$^{th}$ Chinese Control Conference}. Hangzhou, China, July~28--30, 2015, pp.~8866--8871.

2. {\textnormal McConnel~K.G.} Kinematic of three-axis gimbal system. {\itshape Proceedings of the Third Southeastern Conference on Theoretical and Applied Mechanics}. S. Carolina, Columbia, March~31\,---\,April~01, 1966, pp.~515--541.

3. {\textnormal Veremey~E.~I.} On practical application of ZubovТs optimal damping concept.{\itshape Vestnik of Saint Petersburg University.} {\itshape Applied Mathematics. Computer Sciences. Control Processes}, 2020, vol.~16, iss.~3, pp.~293--315. %\\
https://doi.org/10.21638/11701/spbu10.2020.307

4. {\textnormal Zubov~V.~I.} {\itshape Lektsii po teorii upravleniya} [{\itshape Lectures on control theory}]. Moscow, Nauka~Publ., 1975, 496~p. (In Russian)

5. {\textnormal Ekimov~A.~V., Zhabko~A.~P., Yakovlev~P.~V.} Ustoichivost differencialno-raznostnyh sistem s proportsionalnym zapazdyvaniem. I. Lineynye upravlyaemye sistemy [The stability of differential-difference systems with proportional time delay. I. Linear controlled systems]. {\itshape Vestnik of Saint Petersburg University.} {\itshape Applied Mathematics. Computer Scien\-ces. Control Processes}, 2020, vol.~16, iss.~3, pp.~316--325. \\https://doi.org/10.21638/11701/spbu10.2020.308 (In Russian)

\vskip1.5mm

Received:  January 12, 2022.

Accepted: May 05, 2022.


\vskip6mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Aleksei P. Zhabko}  --- Dr. Sci. in Physics and Mathematics, Professor; zhabko.apmath.spbu@mail.ru \par%
%
\vskip2mm \textit{Natalya A. Zhabko} --- PhD in Physics and Mathematics, Associate Professor; ztasha@mail.ru \par%
%
\vskip2mm \textit{Pavel V. Yakovlev} --- PhD in Physics and Mathematics, Associate Professor; w330433@gmail.com \par%
%
%
}
