
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. \textit{Meleshko V.\,V.}
Selected topics in the history of the two-dimensional biharmonic problem
//
Applied Mechanics Rev. 2003. Vol.~56. N~1. P.~33--85.

2. \textit{Ramachandra Rao B.\,S., Narasimham G.\,L.}
Eigenfunction analysis for bending of clamped rectangular orthotropic plates
//
Intern. Journal of Solids Structures. 1973. Vol.~9. P.~481--493.

3. \textit{Li R., Zhong Y., Tian B., Liu Yu.}
On the finite integral transform method for exact bending solutions
of fully clamped orthotropic rectangular thin plates
//
Applied Mathematics Letters. 2009. Vol.~22. P.~1821--1827.

4. \textit{An C., Gu J., Su J.}
Exact solution of bending problem of clamped orthotropic rectangular thin plates
//
Journal of the Brazilian Society of Mechanical Sciences and Engineering. 2016.
Vol.~38. N~2. P.~601--607.

5. \textit{Dalaei M., Kerr A. D.}
Analysis of clamped rectangular orthotropic plates subjected
to a uniform lateral load
//
Intern. Journal of Mechanical Sciences. 1995. Vol.~37. N~5. P.~527--535.

6. \textit{Eburlitu F., Alatancang L.} Analytical bending solutions of clamped orthotropic rectangular thin plates with
the symplectic superposition method
//
Applied Mathematics and Mechanics. 2018. Vol.~39. N~3. P.~311--323.

7. \textit{Mbakogu F.\,C., Pavlovic M.\,N.}
Bending of clamped orthotropic rectangular plates: A variational symbolic solution
//
Computers and Structures. 2000. Vol.~77. N~2. P.~117--128.

8. \textit{Dalaei M., Kerr A.\,D.}
Analysis of clamped rectangular orthotropic plates subjected to
a uniform lateral load
//
Intern. Journal of Mechanical Sciences. 1995. Vol.~37. N~5. P.~527--535.

9. \textit{Meleshko V.\,V., Gomilko A.\,M., Gourjii A.\,A.}
Normal reactions in a clamped elastic rectangular plate
//
Journal of Engineering Mathematics. 2001. Vol.~40. P.~377--398.

10. \textit{Мелешко В.\,В.}
Бигармоническая задача для прямоугольника: история и современность
//
Мат. методы и физ.-мех. поля. 2004. Т.~47. №~3. С.~45--68.

11. \textit{Агарёв В.\,А.}
Метод начальных функций для двумерных краевых задач теории упругости.
Киев: Изд-во АН~УССР, 1963. 204~с.

12. \textit{Лурье А.\,И.}
Пространственные задачи теории упругости.
М.: Гостехиздат, 1955. 495~с.\linebreak (\textit{Lur'e A.\,I.}
Three dimensional problems of theory of elasticity.)

13. \textit{Matrosov A.\,V.}
Computational peculiarities of the method of initial functions
//
Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial
Intelligence and Lecture Notes in Bioinformatics). 2019. P.~37--51. %11619 LNCS.

14. \textit{Суратов В.\,А., Матросов А.\,В.}
Метод начальных функций в расчете защемленной пластинки
// Процессы управления и устойчивость. 2017. Т.~4(20). №~1. С.~238--244.

15. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical solutions in the analysis of thin elastic plates
//
AIP Conference Proceedings. 2018. N~070012.

16. \textit{Matrosov A.\,V., Suratov V.\,A.}
Stress-strain state in the corner points of a clamped plate
under uniformly distributed normal load
//
Materials Physics and Mechanics. 2018. Vol.~36. N~1. P.~124--146.

17. \textit{Matrosov A.\,V.}
A numerical-analytical decomposition method in analyses of complex structures
//
2014 Intern. Conference on Computer Technologies in Physical and Engineering
Applications (ICCTPEA--2014). Proceedings. 2014. P.~104--105. % 6893305

18. \textit{Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P., Yu G.}
A boundary value problem in the theory of elasticity for a rectangle: exact solutions
//
Zeitschrift fur Angewandte Mathematik und Physik. 2020. Vol.~71. N~6. P.~199.

19. \textit{Matrosov A.\,V.}
A superposition method in analysis of plane construction
//
2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov (SCP--2015). Proceedings. 2015. P.~414--416. N~7342156.

20. \textit{Matrosov A.\,V., Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P.}
Method of initial functions and integral Fourier transform in some problems
of the theory of elasticity
//
Zeitschrift fur Angewandte Mathematik und Physik. 2020. Vol.~71. N~1. P.~24.

21. \textit{Kovalenko M.\,D., Abrukov D.\,A., Menshova I.\,V.,
Kerzhaev A.\,P., Yu G.}
Exact solutions of boundary value problems in the theory of plate bending
in a half-strip: basics of the theory
//
Zeitschrift fur Angewandte Mathematik und Physik. 2019. Vol.~70. N~4. P.~98.

22. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Comparison of two analytical approaches to the analysis of grillages
//
2015 Intern. Conference on ''Stability and Control Processes'' in memory
of V.~I.~Zubov (SCP--2015). Proceedings. 2015. P.~382--385. N~7342169.

23. \textit{Matrosov A.\,V., Shirunov G.\,N.}
Analyzing thick layered plates under their own weight by the method of initial
functions
//
Materials Physics and Mechanics. 2017. Vol.~31. N~1--2. P.~36--39.

24. \textit{Matrosov A.\,V., Shirunov G.\,N.}
Numerical-analytical computer modeling of a clamped isotropic thick plate
//
2014 Intern. Conference on Computer Technologies in Physical and
Engineering Applications (ICCTPEA--2014). Proceedings. 2014. P.~96. N~6893300.

25. \textit{Тимошенко С.\,П., Войновский-Кригер С.} Пластинки и оболочки /
пер. с англ. Г.~С. Шапиро; под ред. И.~К. Снитко.
М.: Наука, 1966. 636~с.
(\textit{Timoshenko S.\,P., Woinowsky-Krieger S.}
Theory of plates and shells. $2^{\rm nd}$ ed.)

26. \textit{Kovalenko M.\,D.}
On a property of the biorthogonal expansions over homogeneous solutions
//
Doklady Akademii Nauk. 1997. Vol.~352. N~2. P.~193--195.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 21 мая 2021~г.

Cтатья принята к~печати 13 октября 2021~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Голоскоков Дмитрий Петрович}
--- д-р техн. наук, проф.; dpg1954@mail.ru

\vskip2mm \textit{Матросов Александр Васильевич}
--- д-р физ.-мат. наук, доц.; avmatrosov@mail.ru,\\ a.matrosov@spbu.ru


}
