
{\normalsize

%\vskip 6mm
\newpage

\noindent{\bf Method of initial functions in analyses of the
bending of a thin orthotropic plate clamped along the contour%$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it D.~P.~Goloskokov$\,^1$, A.~V.~Matrosov$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
$^1$~%
The Bonch-Bruevich Saint Petersburg
State University of Telecommunications,

\noindent%
\hskip2.45mm%
22, pr.~Bol'shevikov, St. Petersburg, 193232, Russian Federation



\noindent%
$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Goloskokov D.\,P., Matrosov A.\,V.
Method of initial functions in analyses of the
bending of a thin orthotropic plate clamped along the contour. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~17, iss.~\issuenum, pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent In this paper, the method of initial functions (MIF) is used to solve the problem of
bending an orthotropic plate clamped along all four sides, under the influence of a
normal load uniformly distributed over its surface. The solution is obtained in the
form of an exponential series with unknown coefficients. The algorithm of the method
is such that on two opposite sides the boundary conditions (equality to zero of
displacements and angles of rotation) are satisfied exactly, while on a pair of two
other opposite sides the boundary conditions are satisfied with an arbitrary degree
of accuracy by the collocation method. All studies were carried out using the Maple
analytical computing system. This system allows you to perform calculations with an
arbitrary mantissa in the representation of real numbers. Calculations with a long
mantissa overcome one of the main disadvantages of the MIF: the computational
instability of its algorithm, which arises under certain parameters of the problem.
The computational stability of the obtained solution is investigated, as well as the
stress-strain state in the neighbourhood of the corner points of the plate. It is shown
that the moments and shear forces tend to zero when approaching the corners of the
plate with a single change in sign.
\\[1mm]
\textit{Keywords}: orthotropic plate, bending of a thin plate,
clamped plate, method of initial functions, computer algebra, Maple.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. {Meleshko V.\,V.}
Selected topics in the history of the two-dimensional biharmonic problem.
\textit{Applied Mechanics Rev.}, 2003, vol.~56, no.~1, pp.~33--85.

2. {Ramachandra Rao B.\,S., Narasimham G.\,L.}
Eigenfunction analysis for bending of clamped rectangular orthotropic plates.
\textit{Intern. Journal of Solids Structures}, 1973, vol.~9, pp.~481--493.

3. {Li R., Zhong Y., Tian B., Liu Yu.}
On the finite integral transform method for exact bending solutions
of fully clamped orthotropic rectangular thin plates.
\textit{Applied Mathematics Letters}, 2009, vol.~22, pp.~1821--1827.

4. {An C., Gu J., Su J.}
Exact solution of bending problem of clamped orthotropic rectangular thin plates.
\textit{Journal of the Brazilian Society of Mechanical Sciences and Engineering}, 2016,
vol.~38, no.~2, pp.~601--607.

5. {Dalaei M., Kerr A. D.}
Analysis of clamped rectangular orthotropic plates subjected
to a uniform lateral load.
\textit{Intern. Journal of Mechanical Sciences}, 1995, vol.~37, no.~5, pp.~527--535.

6. {Eburlitu F., Alatancang L.}
Analytical bending solutions of clamped orthotropic rectangular thin plates with
the symplectic superposition method.
\textit{Applied Mathematics and Mechanics}, 2018, vol.~39, no.~3, pp.~311--323.

7. {Mbakogu F.\,C., Pavlovic M.\,N.}
Bending of clamped orthotropic rectangular plates: A variational symbolic solution.
\textit{Computers and Structures}, 2000, vol.~77, no.~2, pp.~117--128.

8. {Dalaei M., Kerr A.\,D.}
Analysis of clamped rectangular orthotropic plates subjected to
a uniform lateral load.
\textit{Intern. Journal of Mechanical Sciences}, 1995, vol.~37, no.~5, pp.~527--535.

9. {Meleshko V.\,V., Gomilko A.\,M., Gourjii A.\,A.}
Normal reactions in a clamped elastic rectangular plate.
\textit{Journal of Engineering Mathematics}, 2001, vol.~40, pp.~377--398.

10. {Meleshko V.\,V.}
Bigarmonicheskaia zadacha dlia priamougol`nika: istoriia i sovremennost`
[Biharmonic problem for a rectangle: history and modernity].
\textit{Mat. metody i fiz.-meh. polja} [\textit{Math. methods and phys.-mech. fields}], 2004, vol.~47, no.~3, pp.~45--68.
(In Russian)

11. {Agaryov V.\,A.}
\textit{Metod nachal`ny`kh funktcii` dlia dvumerny`kh kraevy`kh zadach teorii uprugosti}
[\textit{Method of initial functions for two-dimensional boundary value
problems of elasticity theory}].
Kiev,
Publ. House AS UkrSSR, 1963, 204~p. (In Russian)

12. {Lur'e A.\,I.}
\textit{Three dimensional problems of theory of elasticity}. New York, Willey Publ., 1964, 491~p.
(Rus. ed.: Lur'e A.\,I. \textit{Prostranstvenny`e zadachi teorii uprugosti}.
Moscow, Gostechizdat Publ., 1955, 495~p.)

13. {Matrosov A.\,V.}
Computational peculiarities of the method of initial functions.
\textit{Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial
Intelligence and Lecture Notes in Bioinformatics)}, 2019, pp.~37--51. %11619 LNCS.

14. {Suratov V.\,A., Matrosov A.\,V.}
Metod nachal`ny`kh funktcii` v raschete zashchemlennoi` plastinki
[The method of initial functions in analysing a clamped plate].
\textit{Processy upravlenija i ustojchivost'} [\textit{Control Processes and Stability}], 2017, vol.~4, no.~20, pp.~238--244.
(In Russian)

15. {Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical solutions in the analysis of thin elastic plates.
\textit{AIP Conference Proceedings}, 2018, no.~070012.

16. {Matrosov A.\,V., Suratov V.\,A.}
Stress-strain state in the corner points of a clamped plate
under uniformly distributed normal load.
\textit{Materials Physics and Mechanics}, 2018, vol.~36, no.~1, pp.~124--146.

17. {Matrosov A.\,V.}
A numerical-analytical decomposition method in analyses of complex struc\-tu\-res.
\textit{2014 Intern. Conference on Computer Technologies in
Physical and Engineering Applications (ICCTPEA--2014). Proceedings}, 2014, pp. 104--105.

18. {Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P., Yu G.}
A boundary value problem in the theory of elasticity for a rectangle: exact solutions.
\textit{Zeitschrift fur Angewandte Mathematik und Physik}, 2020, vol.~71, no.~6, p.~199.

19.  {Matrosov A.\,V.}
A superposition method in analysis of plane construction.
\textit{2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov (SCP--2015). Proceedings}, 2015, pp.~414--416, no.~7342156.

20. {Matrosov A.\,V., Kovalenko M.\,D., Menshova I.\,V., Kerzhaev A.\,P.}
Method of initial functions and integral Fourier transform in some problems
of the theory of elasticity.
\textit{Zeitschrift fur Angewandte Mathematik und Physik}, 2020, vol.~71, no.~1, p.~24.

21. {Kovalenko M.\,D., Abrukov D.\,A., Menshova I.\,V.,
Kerzhaev A.\,P., Yu G.}
Exact solutions of boundary value problems in the theory of plate bending
in a half-strip: basics of the theory.
\textit{Zeitschrift fur Angewandte Mathematik und Physik}, 2019, vol.~70, no.~4, p.~98.

22. {Goloskokov D.\,P., Matrosov A.\,V.}
Comparison of two analytical approaches to the analysis of gril\-lages.
\textit{2015 Intern. Conference on ``Stability and Control Processes'' in memory
of V.~I.~Zubov (SCP--2015). Proceedings}, 2015, pp.~382--385, no.~7342169.

23. \textit{Matrosov A.\,V., Shirunov G.\,N.}
Analyzing thick layered plates under their own weight by the method of initial
functions.
\textit{Materials Physics and Mechanics}, 2017, vol.~31, no.~1--2, pp.~36--39.

24. {Matrosov A.\,V., Shirunov G.\,N.}
Numerical-analytical computer modeling of a clamped isotropic thick plate.
\textit{2014 Intern. Conference on Computer Technologies in Physical and
Engineering Applications (ICCTPEA--2014). Proceedings}, 2014, p.~96, no.~6893300.

25. Timoshenko S.\,P., Woinowsky-Krieger S.
\textit{Theory of plates and shells.} $2^{\rm nd}$ ed. New York, McGraw-Hill Publ., 1987,
580~p.
(Rus. ed.: {Timoshenko S.\,P., Woinowsky-Krieger S.}
\textit{Plastinki i obolochki}. Moscow, Nauka Publ., 1966, 636~p.)

26. {Kovalenko M.\,D.}
On a property of the biorthogonal expansions over homogeneous solutions.
\textit{Proceedings of Academy Sciences}, 1997, vol.~352, no.~2, pp.~193--195.


\vskip1.5mm Received:  May 21, 2021.

Accepted: October 13, 2021.

\vskip4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip1.5mm \textit{Dmitry P. Goloskokov}
--- Dr. Sci. in Engineering, Professor; dpg1954d@mail.ru \par
%
\vskip1.5mm \textit{Alexander V. Matrosov}
--- Dr. Sci. in Physics and Mathematics, Associate Professor;\\
avmatrosov@mail.ru, a.matrosov@spbu.ru \par
%
%
}
