
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. O’Kelly M. E. Activity levels at hub facilities in interacting
networks. {\it Geogr. Anal.}, 1986, vol.~18(4), pp.~343--356.

2. O’Kelly M. E. The location of interacting hub facilities. {\it
Transp. Sci.}, 1986, vol.~20, pp.~92--105.

3. Klincewicz J. G. Heuristics for the $p$-hub location problem.
{\it European Journal of Oper. Research}, 1991, vol.~53,
pp.~25--37.

4. Skorin-Kapov D., Skorin-Kapov J., O’Kelly M. E. Tight linear
programming relaxations of uncapacitated $p$-hub median problems.
{\it European Journal of Oper. Research}, 1996, vol.~94,
pp.~582--593.

5. O’Kelly M. E., Miller H. J. Solution strategies for the single
facility minimax hub location problem. {\it Papers in Regional
Science}, 1991, vol.~70(4), pp.~367--380.

6. Kim H., O’Kelly M. E. Reliable $p$-hub location problems in
telecommunication networks. {\it Geogr. Anal.}, 2009, vol.~41(3),
pp. 283--306.

7. O’Kelly M. E. Network hub structure and resilience. {\it Netw.
Spat. Econ.}, 2015, vol.~15(2),\linebreak pp.~235--251.

8. Ebery J., Krishnamoorthy M., Ernst A. T., Boland N. The
capacitated multiple allocation hub location problems:
formulations and algorithms. {\it European Journal of Oper.
Research}, 2000, vol.~120, pp.~614--631.

9. Lee H., Shi Y., Nazem S. M., Kang S. Y., Park T. H., Sohn M. H.
Multicriteria hub decision making for rural area telecommunication
networks. {\it European Journal of Oper. Research}, 2001,
vol.~133, pp.~483--495.

10. Wishart D. Mode analysis: A generalization of nearest neighbor
which reduces chaining effects. {\it Numerical Taxonomy}, 1969,
pp. 282--311.

11. Hartigan J. {\it Clustering algorithms}. New York, USA, John
Wiley Publ., 1975, 364 p.

12. Hartigan J.  Statistical theory in clustering. {\it J.
Classification}, 1985, vol.~2, pp.~63--76.

13. Volkovich Z., Brazly Z., Morozensky L. A statistical model of
cluster stability. {\it Pattern Recognition},  2008, vol.~41,
pp.~2174--2188.

14. Volkovich Z., Brazly Z., Toledano-Kitai D., Avros R. The
Hotelling's metric as a cluster stability measure. {\it Computer
Modelling and New Technologies}, 2010, vol.~14, pp.~65--72.


15. Pelleg D., Moore A. $X$ means extending $k$-means with
efficient estimation of the number of clusters. {\it Proceedings
of the 17th Intern. conference on Machine Learning.} San
Francisco, USA, Morgan Kaufmann Publ., 2000, pp.~727--734.

16.  Barzily Z., Golani M., Volkovich Z. On a simulation approach
to cluster stability validation. {\it Special Issue, Mathematical
and Computer Modeling in Applied Problems.} Moscow, Institute
Informatics Problems RAS Publ., 2008, pp.~86--112.

17. Toledano-Kitai D., Avros R., Volkovich Z., Weber G.-W.,
Yahalom O. A binomial noised model for cluster validation. {\it
Journal of Intelligent and Fuzzy Systems, Special Issue, Recent
Advances in Intelligent $\&$ FuzzySystems}, 2013, pp.~417--427.

18. Lozkins~A., Bure~V. M. The probabilistic method of finding the
local-optimum of clustering. {\it Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2016, iss.~1, pp.~28--37.

19. Lozkins~A., Bure~V. M. The method of clusters stability
assessing. {\it Stability and Control Processes in memory of
V.~I.~Zubov~(SCP)}, {\it 2015 Intern. conference}, {\it IEEE},
2015, pp.~479--482.

20. Lozkins~A. Bure~V. M. Single hub location-allocation problem
under robustness clustering concept. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, 2017, vol.~13, iss.~4, pp.~398--406.
https://doi.org/10.21638/11701/spbu10.2017.406

21. Lim~C., Sherali~H.~D., Uryasev~S. Portfolio optimization by
minimizing conditional value-at-risk via nondifferentiable
optimization. {\it Computational Optimization and Applications},
2010, vol.~46, no.~3, pp.~391--415.

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm


Received:  August 7, 2018.

Accepted: September 25, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip2mm\textit{Aleksejs Lozkins} --- Postgraduate Student;
aleksejs.lozkin@gmail.com

}
