
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 3mm%2mm

{\footnotesize

1. Manning C. D., Raghavan P., Sch\"utze H. \textit{Introduction
to information retrieval}. Cambridge, Cambridge University Press,
2008, 544~p.

2. Bentley J. L. Multidimensional binary search trees used for
associative searching. \textit{Communications of the ACM}, 1975,
vol.~18, no.~9, pp.~509--517.

3. Samet H. \textit{Foundations of multidimensional and metric
data structures}. San-Francisco, Morgan Kaufmann Publ., 2006,
1024~p.

4. Cayton L. Fast nearest neighbor retrieval for bregman
divergences. \textit{Proceedings of the 25th Intern. conference on
Machine Learning}. San Francisco, Morgan Kaufmann Publ., 2008,
pp.~112--119.

5. Coviello E., Mumtaz A., Chan A., Lanckriet G. That was fast!
Speeding up NN search of high dimensional distributions.
\textit{Proceedings of the 25th Intern. conference on Machine
Learning}. San Francisco, Morgan Kaufmann Publ., 2013,
pp.~468--476.

6. Li C., Chang E., Garcia-Molina H., Wiederhold G. Clustering for
approximate similarity search in high-dimensional spaces.
\textit{Knowledge and Data Engineering, IEEE Transactions on},
2002, vol.~14, no.~4, pp.~792--808.

7. Arya S., Mount D. M. Approximate nearest neighbor queries in
fixed dimensions. \textit{Proceedings of the fourth annual
ACM-SIAM Symposium on Discrete algorithms. SODA}, Society for
Industrial and Applied Mathematics, 1993, pp.~271--280.

8. Andoni A., Indyk P. Near-optimal hashing algorithms for
approximate nearest neighbor in high dimensions.
\textit{Foundations of Computer Science. FOCS'06. 47th Annual IEEE
Symposium on}, 2006, pp.~459--468.

9. Indyk P., Motwani R. Approximate nearest neighbors: towards
removing the curse of dimensionality. \textit{Proceedings of the
30th Annual ACM Symposium on theory of computing}, 1998,\linebreak
pp.~604--613.

10. Andoni A., Indyk P., Nguyen H. L., Razenshteyn I. Beyond
Locality-Sensitive Hashing. \textit{SODA}, 2014, pp.~1018--1028.

11. Li K., Malik J. \textit{Fast $k$-nearest neighbour search via
prioritized DCI}. ArXiv preprint ArXiv:1703.00440, 2017.

12. Li K., Malik J. Fast $k$-nearest neighbour search via dynamic
continuous indexing. \textit{Intern. Conference on Machine
Learning}, 2016, pp.~671--679.

13. Pereira F., Tishby N., Lee L. Distributional clustering of
English words. \textit{Proceedings of the 31st annual meeting on
Association for Computational Linguistics}, 1993, pp.~183--190.

14. Baker L. D., McCallum A. K. Distributional clustering of words
for text classification. \textit{Proceedings of the 21st annual
Intern. ACM SIGIR conference on Research and Development in
Information Retrieval}, 1998, pp.~96--103.

15. Slonim N., Tishby N. The power of word clusters for text
classification. \textit{23rd European Colloquium on Information
Retrieval Research}, 2001, vol.~1, p.~200.

16. Bekkerman R., El-Yaniv R., Tishby N., Winter Y. On feature
distributional clustering for text categorization.
\textit{Proceedings of the 24th annual Intern. ACM SIGIR
conference on Research and Development in Information Retrieval},
2001, pp.~146--153.

17. Dhillon I. S., Mallela S., Kumar R. A divisive information
theoretic feature clustering algorithm for text classification.
\textit{The Journal of Machine Learning Research}, 2013, vol. 3,
pp.~1265--1287.

18. Dobrynin V., Patterson D., Rooney N. Contextual document
clustering. \textit{Advances in Information Retrieval}. Berlin,
Heidelberg, Springer Publ., 2004, pp.~167--180.\\

\newpage

19. Lin J. Divergence measures based on the Shannon entropy.
\textit{Information Theory, IEEE Transactions on}, 1991, vol.~37,
no.~1, pp.~145--151.

20. Lee L. Measures of distributional similarity.
\textit{Proceedings of the 37th annual meeting of the Association
for Computational Linguistics on Computational Linguistics}, 1999,
pp.~25--32.

21. Topsoe F. Some inequalities for information divergence and
related measures of discrimination. \textit{Information Theory,
IEEE Transactions on}, 2000, vol.~46, no.~4, pp.~1602--1609.

22. Guntuboyina A., Saha S., Schiebinger G. Sharp inequalities for
$f$-divergences. \textit{IEEE Transactions on Information Theory},
2014, vol.~60, no.~1, pp.~104--121.

23. Sason I. L. Tight bounds for symmetric divergence measures and
a refined bound for lossless source coding. ArXiv preprint.
ArXiv:1403.7164 [cs.IT], 2014.

24. Capra J. A., Singh M. Predicting functionally important
residues from sequence conservation. \textit{Bioinformatics},
2007, vol.~23, no.~15, pp.~1875--1882.

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm


Received:  June 5, 2018

Accepted: September 25, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip2mm\textit{Vladimir Yu. Dobrynin} --- PhD in Physics and
Mathematics, Associate Professor; v.dobrynin@bk.ru

\vskip2mm\textit{Niall Rooney} --- PhD in Informatics;
niall@aiqudo.com

\vskip2mm\textit{Julian A. Serdyuk} --- Master; julian@aiqudo.com

}
