
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Петросян Л. A.,  Седаков A. A.} Многошаговые сетевые
игры с~полной информацией~// Математическая теория игр и~ее
приложения. 2009. Т.~1. №~2. С.~66--81.

2. \textit{Bulgakova M. A.,  Petrosyan L. A.} About strongly
time-consistency of core in the network game with pairwise
interactions~// Proceedings of 2016 International Conference
``Stability and Os\-cil\-la\-tions of Nonlinear Control Systems''.
2016. P.~157--160.

3. \textit{Kuzyutin D.,  Nikitina M.} Time consistent cooperative
solutions for multistage games with vector payoffs~// Operations
Research Letters. 2017. Vol.~45. Iss.~3. P.~269--274.

4. \textit{Булгакова M. A.} Решения сетевых игр с~попарным
взаимодействием // Вестн. С.-Петерб.\linebreak ун-та. Прикладная
математика. Информатика. Процессы управления. 2019. Т.~15. Вып.~1.
С.~147--156. %
% \\%
https://doi.org/10.21638/11702/spbu10.2019.112

5.  \textit{Petrosian O. L., Gromova E. V., Pogozhev S. V.} Strong
time-consistent subset of core in cooperative differential games
with finite time horizon~// Automation and Remote Control. 2018.
Vol.~79(10). P.~1912--1928.

6. \textit{Вольф Д. A., Захаров В. В., Петросян O. Л.}
О~существовании ПРД-ядра в~кооперативных дифференциальных играх~//
Математическая теория игр и~ее приложения. 2017. Т.~9(4).
С.~18--38.
%mtiip

7. \textit{Zakharov    V.,  O-Hun    Kwon.} Linear programming
approach in cooperative games~// Journal of    Korean Mathematical
Society. 1977. Vol.~34(2). P.~423--435.

8. \textit{Петросян Л., Седаков A., Бочкарев A.} Двухшаговые
сетевые игры~// Maтематическая тeoрия игр и~ее приложения. 2013.
Т.~5. Вып.~4. С.~84–-104.

9.  \textit{Bulgakova M. A.,  Petrosyan L. A.} Cooperative network
games with pairwise interactions~// Mathematical game theory and
applications. 2015. Vol.~4. N~7. P.~7--18.

10. \textit{Булгакова М. А., Петросян Л. А.} Многошаговые игры
с~попарным взаимодействием на полном графе~// Математическая
теория игр и~ее приложения. 2019. Т.~11. Вып.~1.  С.~3--20.

11.   \textit{Petrosyan L. A.} Stability of solutions in
$n$-person differential games~// Vestnik of Leningrad University.
1977. Vol.~1. N~19. P.~46--52.

12. \textit{Petrosyan L. A.} About new strongly time-consistency
solutions in cooperative differential games~// Proceedings of the
Steklov Institute of Mathematics. 1995. N~211.   P.~335--340.



\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 18 октября 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Булгакова Мария Александровна}  --- ассистент;
 mari\_bulgakova@mail.ru

\vskip2mm\textit{Петросян Леон Аганесович} --- д-р физ.-мат. наук,
проф.;  l.petrosyan@spbu.ru

}
