
{\normalsize

\vskip 6mm

\noindent{\bf About one multistage non-antagonistic network game\!$\,^*$%
}

}

\vskip 2mm

{\small

\noindent{\it М. А. Bulgakova, L. A. Petrosyan%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian Scientific Found (grant N 17-11-017079).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Bulgakova M. A., Petrosyan L.
A. About one multistage non-antagonistic network game. {\it
Vestnik of Saint~Peters\-burg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~15,
iss.~\issuenum, pp.~\pageref{p15}--\pageref{p15e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum15  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent In the paper, a multi-step
non-antagonistic game is considered. The game has a finite number
of stages, at the first stage a network is formed by
simultaneously choosing communication vectors, and at the next,
there are simultaneous non-antagonistic games, the payoffs in
which depend on the controls chosen in the previous stage, as well
as the behavior in the current stage. Players, at all stages
except the first, have the opportunity to modify the network by
removing any of their connections. A characteristic function is
constructed for the model in a new way based on the calculation of
optimal controls. For the case of a one-stage subgame, the
supermodularity of the characteristic function is proved. As a
solution, the Shapley value is considered, a simplification of the
formula for calculating the components of the Shapley value for
this characteristic function is given. Also, as a solution, a
subset of the core (PRD-core) is considered. Strong dynamic
stability has been proved for it. Work is illustrated by an
example.\\[1mm]
\textit{Keywords}: multistage games, supermodular function,
Shapley value, characteristic function, strongly time consistency,
PRD-core.
\par}

\vskip 5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Petrosyan L. A.,  Sedakov A. A. Mnogoshagovye setevye igry s
polnoj informaciej [Multistage network games with full
information]. \textit{Mathematical game theory and applications},
2009, vol.~1, no.~2, pp.~66--81. (In Russian)

2. Bulgakova M. A.,  Petrosyan L. A. About strongly
time-consistency of core in the network game with pairwise
interactions. \textit{Proceedings of 2016 International Conference
``Stability and Oscillations of Nonlinear Control Systems''},
2016, pp.~157--160.

3. Kuzyutin D.,  Nikitina M. Time consistent cooperative solutions
for multistage games with vector payoffs. \textit{Operations
Research Letters}, 2017, vol.~45, iss.~3, pp.~269--274.

4. Bulgakova M. A. Resheniya setevyh igr s poparnym
vzaimodejstviem [Solutions of network games with pairwise
interactions]. \textit{Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019,
vol.~15, iss.~1, pp. 147--156. \\
https://doi.org/10.21638/11702/
spbu10.2019.112 (In Russian)

5.  Petrosian O. L., Gromova E. V., Pogozhev S. V. Strong
time-consistent subset of core in cooperative differential games
with finite time horizon. \textit{Automation and Remote Control},
2018, vol.~79(10), pp.~1912--1928.

6. Wolf D. A., Zakharov V. V., Petrosian O. L. O sushchestvovanie
PRD-yadra v kooperativnyh differencial'nyh igrah [About existance
of PRD-core in cooperative differential  games].
 \textit{Mathematical game theory and applications}, 2017,
vol.~9(4), pp.~18--38. (In Russian)
%mtiip

7. Zakharov    V.,  O-Hun   Kwon. Linear programming approach in
cooperative games. \textit{Journal of    Korean    Mathematical
Society}, 1977, vol.~34(2), pp.~423--435.

8. Petrosyan L. A., Sedakov A. A., Bochkarev A. A. Dvuhshagovye
setevye igry [Two-stage network games]. \textit{Mathematical game
theory and applications}, 2013, vol.~5, iss.~4, pp.~84--104. (In
Russian)

9.  Bulgakova M. A.,  Petrosyan L. A. Cooperative network games
with pairwise interactions. \textit{Mathematical game theory and
applications}, 2015, vol.~4, no.~7, pp.~7--18.

10. \textit{Bulgakova М. А., Petrosyan L. А.} Mnogoshagovye igry s
poparnym vzaimodeystviem na polnom grafe [Multi-stage games with
pairwise interactions on full graph]. \textit{Mathematical game
theory and applications}, 2019, vol.~11, iss.~1, pp.~3--20. (In
Russian)

11.   Petrosyan L. A. Stability of solutions in \textit{n}-person
differential games. \textit{Vestnik of Leningrad University},
1977, vol.~1, no.~19, pp.~46--52.

12. Petrosyan L. A. About new strongly time-consistency solutions
in cooperative differential games. \textit{Proceedings of the
Steklov Institute of Mathematics}, 1995, no.~211,   pp. 335--340.


\vskip 1.5mm

Received:  October 18, 2019.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip2mm \textit{Maria A. Bulgakova} --- Assistant;
mari\_bulgakova@mail.ru

\vskip2mm \textit{Leon A. Petrosyan} --- Dr. Sci. in Physics and
Mathematics, Professor;  l.petrosyan@spbu.ru\par
%
}
