

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Schmid-Schonbein H. Rheological properties of human
erythrocytes and their influence upon anomalous viscosity of
blood. \textit{Physiol. Rev.}, 1971, vol.~63, pp.~14--219.

2. Jung J., Lyczkowski R. W., Panchal C. B., Hassanein A.
Multiphase haemodynamics simulation of pulsative flow in a
coronary artery. \textit{J. Biomechanics}, 2006, vol.~39, no.~20,
pp.~64--73.

3. Srivastava V. P. Two-phase model of blood flow through stenosed
tubes in the presence of a peripheral layer: applications.
\textit{J. Biomechanics}, 1996, vol.~29, pp.~1377--1382.

4. Gijsen F. G. H., Allanic E., Van De Vosse F. N., Janssen J. D.
The influence of the non-Newtonian properties of blood on the flow
in large arteries: unsteady flow in a 900 curved tube analysis.
\textit{J. Biomechanics}, 1999, vol.~32, pp.~705--713.

5. Baskurt O. K., Meiselman H. J. Blood rheology and
haemodynamics. \textit{Seminars in thrombosis and hemostasis},
2003, vol.~29(5), pp.~435--450.

6. Tregubov V.P., Zhukov N.K. Computer simulation of the blood
stream with availability of vessel pathologies. \textit{Russian J.
Biom}, 2017, vol.~2, pp.~201--210.

7. Cho Y. I., Kensey K. R. Effects of the non-Newtonian viscosity
of blood on flows in a diseased arterial vessel. Pt~1. Steady
Flows. \textit{Biorheology}, 1991, vol.~28, pp.~241--262.

8. Tokuda Y., Song M. H., Ueda Y., Usui A., Akita T., Yoneyama S.,
Maruyama S. Three-dimensional numerical simulation of blood flow
in the aortic arch during cardiopulmonary bypass. \textit{Europ.
J. Cardio-thoracic Surgery}, 2008, vol.~33, pp.~164--167.

9. Numata S., Itatani K., Kanda K., Doi K., Yamazaki S., Morimoto
K., Manabe K., Ikemoto K., Yaku H. Blood flow analysis of the
aortic arch using computational fluid dynamics. \textit{Europ. J.
Cardio-Thoracic Surgery}, 2016, vol.~49(6), pp.~1--8.

10. Tregubov V. P. Mathematical modelling of the non-Newtonian
blood flow in the aortic arc. \textit{Computer  Research and
Modeling}, 2017, vol.~9(2), pp.~259--269.

11. Tregubov V., Mukhtarova D. A model study of blood flow in
branching vessels. \textit{Vestnik of Saint Petersburg University.
Series 10. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~1, pp.~42--50.

12. Duta A., Tarbell J. M. Influence of non-Newtonian behavior of
blood on flow in elastic artery mofel. \textit{J. Biomech. Eng.},
1996, vol.~118, pp.~111--119.

13. Zhu Y., Granick S. Limits of hydrodynamic no-slip boundary
condition. \textit{Phys. Review Letters}, 2002, vol.~88,
pp.~102--106.

14. Zhu Y., Granick S. Rate-dependent slip of Newtonian liquid at
smooth surfaces. \textit{Phys. Review Letters}, 2001, vol.~87,
pp.~96--105.

15. Bessonov N., Sequeira A., Simakov S., Vassilevskji Yu.,
Volpert V. Methods of blood flow modeling. \textit{Math.  Mod.
Nature Phenomena}, 2016, vol.~11(1), pp.~1--25.

%\vskip3mm%
%\noindent \textbf{For citation:} Tregubov V. P., Rutkina
%S. V. Mathematical modelling of pulsativå blood flow in deformable
%arteries. {\it Vestnik SPbSU. Applied Mathematics. Computer
%Science. Control Processes}, \issueyear, vol.~14, iss.~\issuenum,
%pp.~\pageref{p8}--\pageref{p8e}.
%\doivyp/spbu10.\issueyear.\issuenum08




\vskip 1.5mm


\noindent Recommendation: prof. L. A. Petrosyan.

\vskip 1.5mm

\noindent Received:  23.10.2017; accepted: 15.03.2018.




\vskip6mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.5mm \textit{Tregubov Vladimir P.} --- Dr. Sci. in physics
and mathematics, professor;  v.tregubov@spbu.ru

\textit{Ratkina Svetlana V.} --- master, svet.ratkina@yandex.ru





}
