

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1.~Hussain\,M.\,M., Trajcevski\,G. Maximizing area-range sum for
spatial shapes (MAxRS3). {\it SSDBM18:\linebreak 30th
International Conference on Scientific and Statistical Database
Management}, July 9--11, 2018. Bozen-Bolzano, Italy; New York,
USA, ACM, 5~p.
 %\\
https://doi.org/10.1145/3221269.3221301

2.~Shegelman I. R., Lukashevich V. M. {\it Podgotovitel'nye raboty
v otechestvennoy sisteme leso\-pol'zovania  $[$Preparatory work in
the national forest management system}]. Monograph. Petrozavodsk,
Publishing House Petrozavodsk State University, 2012, 84~p. (In
Russian)

3.~Bentley J. Programming Pearls --- Algorithm design techniques.
{\it Communications of the ACM}, 1984, vol.~27, iss.~9,
pp.~865--873.

4.~Fischer P., H\"{o}ffgen K., Lefmann H., Luczak T.
Approximations with axis-aligned rectangles. {\it Fundamentals of
Computation Theory}, 1993, vol.~710, pp.~244--255.

5.~Fukuda T., Morimoto Y., Morishita S., Tokuyama T. Data mining
using two-dimensional opti\-mized~association rules: Scheme,
algorithms, and visualization. {\it ACM SIGMOD Record}, 1996,
no.~25(2),\linebreak pp.~13--23.

6.~Tamaki H., Tokuyama T. Algorithms for the maximum subarray
problem based on matrix multiplication. {\it Interdisciplinary
Information Sciences}, 2000, vol.~6, no.~2, pp.~99--104.

7.~Takaoka T. Efficient algorithms for the maximum subarray
problem by distance matrix multiplication. {\it Electronic Notes
in Theoretical Computer Science}, 2002, vol.~61, pp.~191--200.

8.~Daniels K., Milenkovic V., Roth D. {\it Finding the largest
rectangle in several classes of polygons}. Cambridge,
Massachusetts, Harvard University Press, 1995, 40~p.

9.~Nandy S. C., Bhattacharya B. B. A unified algorithm for finding
maximum and minimum object enclosing rectangles and cuboids. {\it
Computers Mathematical Applications (Computers and Mathematics
with Applications)}, 1995, vol.~29, no.~8, pp.~45--61.

10.~Backurs A., Dikkala N., Tzamos C. {\it Tight hardness results
for maximum weight rectangles}. arXiv preprint arXiv:1602.05837.
2016. Available at: https://arxiv.org/abs/1602.05837 (accessed:
May 15, 2019).

\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  April 29, 2019.

Accepted: November 07, 2019.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 1.5mm%2mm
\textit{Liudmila V. Shchegoleva} --- Dr. Sci. in Technics,
Associate Professor; schegoleva@petrsu.ru

\vskip 1.5mm%2mm
\textit{Roman V. Voronov} --- Dr. Sci. in Technics, Associate
Professor; rvoronov@petrsu.ru

\vskip 1.5mm%2mm
\textit{Leonid Sedov} --- Postgraduent Student;
leonid.sedov@liu.se

}
