
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

1. {\it Арнольд В. И.} Жёсткие и~мягкие математические модели. М.:
МЦНМО, 2008. 32~с.

2. {\it Kapitza S. P.} Global population blow-up and after. The
demographic revolution and information society: A Report to the
Club of Rome and the Global Marshall Plan Initiative. Hamburg:
Tolleranza, 2006. 272~p.

3. {\it Капица С. П.} Парадоксы роста: Законы развития
человечества. М.: Альпина Нон-фикшн, 2010. 192~с.

4. {\it Алескеров Ф. Т., Андриевская И. К., Пеникас Г. И.,
Солодков В. М.} Анализ математических моделей Базель II. М.:
Физматлит, 2013. 296~с.

5. {\it Губанов Д. А., Новиков Д. А., Чхартишвили А. Г.}
Социальные сети: модели информационного влияния, управления
и~противоборства. М.: Физматлит, 2010. 228~с.

6. {\it Батов А. В., Бреер В. В., Новиков Д. А., Рогаткин А. Д.}
Микро- и~макромодели социальных сетей. Ч. 2. Идентификация
и~имитационные эксперименты // Проблемы управления. 2014. №~6.
C.~45--51.

7. {\it Weidlich W.} Sociodynamics: a systematic approach to
mathematical modelling in the social sciences. Amsterdam: Harwood
Academic Publ., 2000. 380~p.

8. {\it McClelland K., Fararo T.} Purpose, meaning and action:
Control systems theory in sociology. London: Palgrave-Macmillan,
2006. 352~p.

9. {\it Давыдов А. А.} Математическая социология: обзор
зарубежного опыта // Социологические исследования. 2008. №~4.
C.~105--111.

10. {\it Акаев А. А.} Год бифуркации  в~динамике мировой экономики
// Вестник Российской академии наук. 2015. Т.~85, вып.~12.
C.~1059--1069.

11. {\it Mann S.} Chaos theory and strategic thought // Parameters
(US Army War College Quarterly). 1992. N~22. P.~54--68.

12. {\it Лепский В. Е.} Технологии управляемого хаоса --- оружие
разрушения субъективности развития // Информационные войны. 2010.
Т.~4, вып.~16. C.~69--78.

13. {\it Fradkov A. L., Pogromsky A. Yu.} Introduction to control
of oscillations and chaos. Singapore: World Scientific Publ. Co
Inc., 1999. 391~p. (World scientific series on nonlinear science.
Series a. Monographs and treatises. Vol.~35 (Book~35))

%13
14. {\it Chen G., Yu X.} Chaos control: Theory and applications.
Berlin; Heidelberg: Springer-Verlag, 2003. 369~p.

15. {\it Turchin P.} Historical dynamics: Why states rise and
fall. Princeton: Princeton University Press, 2003. 264~p.

16. {\it Haken H.} Synergetics, an introduction: Nonequilibrium
phase transitions and self-organization in physics, chemistry, and
biology. New York: Springer-Verlag, 1983. 367~p.

17. {\it Князева Е. Н., Курдюмов С. П.} Основания синергетики:
Режимы с обострением, самоорганизация, темпомиры. СПб.: Алетейя,
2002. 414~с.

18. {\it Леонов Г. А.} Теория управления. СПб.: Изд-во С.-Петерб.
ун-та, 2006. 233~с.

19. {\it Andrasik L.} Theory emerging instability via creative
perturbation --- the engine of socio-economic progress // Journal
of knowledge society / Intern. scientific journal. 2014. N~1(2).
P.~11--27.

20. {\it Давыдов А. А.} Арабские революции 2011 года: системная
диагностика // Системный мониторинг глобальных и~региональных
рисков: Арабская весна 2011~г. / отв. ред. А.~В.~Коротаев. М.:
Изд-во ЛКИ/URSS, 2012. C.~174--187.

21. {\it Цирель С. В.} Революции, волны революций и~Арабская весна
// Системный мониторинг глобальных и~региональных рисков: Арабская
весна 2011~г. / отв. ред. А.~В.~Коротаев. М.: Изд-во ЛКИ/URSS,
2012. C.~128--161.

22. {\it Коротаев А. В., Ходунов А. С., Бурова А. Н., Малков С.
Ю., Халтурина Д. А., Зинькина~Ю.~В.} Социально-демографический
анализ Арабской весны // Системный мониторинг глобальных
и~региональных рисков: Арабская весна 2011~г. / отв. ред.
А.~В.~Коротаев. М.: Изд-во ЛКИ/URSS, 2012. C.~28--76.

23. {\it Фитуни Л. Л.} Ближний Восток: технологии управления
протестным потенциалом // Азия и~Африка сегодня. 2011. Т.~12.
С.~8--16.

24. {\it Васильев А. М.} Цунами революций // Азия и~Африка
сегодня. 2011. Т.~3. С.~2--18.

%19
25. {\it Коротаев А. В., Зинькина Ю. В.} Египетская революция
2011~г. Структурно-де\-мо\-гра\-фи\-чес\-кий анализ // Азия
и~Африка сегодня. 2011. Т. 6(647). С.~10--16.

26. {\it Сундиев И. Ю., Смирнов А. А.} Теория и~технологии
социальной деструкции (на примере «цветных революций»). М.: Ин-т
эконом. стратегий, 2016. 433~с.

27. {\it Goldstone J.} Towards a fourth generation of
revolutionary theory // Annual Review of Political Science. 2001.
N~4. P.~139--187.

28. {\it Goldstone J., Bates R., Epstein D., Gurr T., Lustik M.,
Marshall M., Ulfelder J., Woodward~M.} A global model for
forecasting political instability // The Americal Journal of
Political Science. 2010. Vol.~54, N~1. P.~190--208.

29. {\it Komlos J., Nefedov S.} Compact macromodel of
pre-industrial population growth // Historical methods. 2002.
N~35. P.~92--94.

30. {\it Turchin P.} Dynamical feedbacks between population growth
and sociopolitical instability in agrarian states // Journal of
Anthropological and Related Sciences. 2005. N~1. P.~1--19.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

31. {\it Dunning T.} Resource dependence, economic performance,
and political stability // Journal of Conflict Resolution. 2005.
N~49. P.~451--482.

32. {\it Richardson L.} Weather prediction by numerical process.
Cambridge: Cambridge University Press, 1922. 262~p. (London, UK,
reprinted by Dover, 1965. 236~p.).

33. {\it Lynch P.} The origins of computer weather prediction and
climate modeling // Journal of Computational Physics. 2008.
N~227(7). P.~3431--3444.

34. {\it Leonov G. A.} Dynamic principles of prognosis and control
// Chaos theory: modeling, simulation and applications. Pt~1.
Plenary and keynote talks / eds: C.~H.~Skiadas, I.~Dimotikalis,
C.~Skiadas. Singapore: World Scientific Publ. Co., 2011.
P.~21--29.


35. {\it Leonov G. A., Kudryashova E. V., Kuznetsov N. V.}
Modeling and identification of the Tunisian social system in
2011--2014: Bifurcation, revolution, and controlled stabilization
// Preprints. 1st IFAC Conference on modelling, identification and
control of nonlinear systems. 2015. P.~735--739.


36. Sustainable society foundation. Full report ``Sustainable
society index 2012'' (2012). URL:
http://www.ssfindex.com/ssi2014/wp-content/uploads/pdf/ssi2012.pdf
(дата обращения: 28.03.2016 г.).
%Available at: http://www.ssfindex.com/ssi2014/wp-content/uploads/pdf/ssi2012.pdf (accessed: 28.03.2016)

37. {\it Арнольд В. И., Афраймович В. С., Ильяшенко Ю. С.,
Шильников Л. П.} Теория бифуркаций // Динамические системы–5.
Итоги науки и~техники. Сер. Современные проблемы математики.
Фундам. направления. М.: ВИНИТИ, 1986. Т.~5. C.~5--218.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
38. {\it Филатов С.} Тунисский бунт. Бессмысленный и~беспощадный
// Русский обозреватель. 2011. URL:
http://www.rus-obr.ru/idea/9335 (дата обращения 28.03.2016~г.).
%(Available at: http://www.rus-obr.ru/idea/9335 (accessed: 28.03.2016)).

%36
39. Global food markets group. U. K. Government. The 2007/08
Agricultural price spikes: causes and policy implications. London,
2008. URL: http://www.growthenergy.org/images/reports (дата
обращения: 28.03.2016~г.).
%(Available at: http://www.growthenergy.org/images/reports / accessed: 28.03.2016)).

40. {\it Кашина А. А.} Стратегия Туниса в~области образования //
Ближний Восток и~современность. 2010. Т.~42. C.~50--73.

41. {\it Кашина А. А.} Социальная политика Тунисской республики
последней трети ХХ --- начала ХХI века: автореф. дис. ... канд.
полит. наук. М., 2012. 24~c.

42. Times Higher Education World University Rankings, 2014. URL:
http://www.\linebreak
timeshighereducation.co.uk/world-university-rankings (дата
обращения: 28.03.2016~г.).
% Available at: http://www.timeshighereducation.co.uk/world-university-rankings (accessed: 28.03.2016).

43. The Academic Ranking of World Universities, 2014. URL:
http://www.shanghairanking.com (дата обращения: 28.03.2016~г.).
% Available at: http://www.shanghairanking.com (accessed 28 March 2016).

44. {\it Ландау Л. Д.} К~проблеме турбулентности // Докл. АН~СССР.
1944. Т.~44(8). C.~339--342.

45. {\it Brinton C.} The anatomy of revolution. New York: Vintage
Books, 1965. 320~p.

46. {\it Леонов Г. А.} Динамические принципы прогнозирования
и~управления // Проблемы управления. 2008. №~5. C.~31--35.

47. {\it Leonov G. A.} Strange attractors and classical stability
theory. Saint Petersburg: Saint Petersburg University Press, 2008.
161~p.


48. {\it Леонов Г. А.} О математическом образовании в~России
и~Санкт-Петербурге. Прошлое, настоящее, будущее //
Дифференциальные уравнения и~процессы управления. 2012. Т.~2.
С.~4--8.


49. {\it Abramovich S., Kuznetsov N. V., Leonov G. A.} V. A.
Yakubovich --- mathematician, ``father of the field'', and herald
of intellectual democracy in science and society //
IFAC-PapersOnLine. 2015. Vol.~48, issue~11. P.~001--003.




\vskip 1mm

{\bf Для цитирования:}  Леонов Г. А., Кузнецов Н. В., Кудряшова Е.
В. Тунис 2011–2014. Бифуркация, революция и~управляемая
стабилизация
// Вестник Санкт-Петербургского университета. Сер.~10.
Прикладная математика. Информатика. Процессы управления.
\issueyear. Вып.~\issuenum. С.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10. \issueyear.\issuenum08



}
