

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. Bandiera L., Tsiropoulos V. A framework to assess debt sustainability under the Belt and Road Initiative. \textit{Journal of Development Economics}, 2020, vol.~146, no.~102495.

2. Lall S. V., Lebrand M. Who wins, who loses? Understanding the spatially differentiated effects of the belt and road initiative. \textit{Journal of Development Economics}, 2020, vol.~146, no.~102496.

3. Petrosyan L. A. Ustojchivost' reshenij v differencial'nyh igrah so mnogimi uchastnikami [Stability of solutions in differential games with many participants]. \textit{Vestnik of Leningrad University}, 1977, no.~19, pp.~46--52.  (In Russian)

4. Sedakov A. A., Zhen M. Opinion dynamics game in a social network with two influence nodes. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~1, pp.~118--125. https://doi.org/10.21638/11702/spbu10.2019.109

5. Bala V., Goyal S. A noncooperative model of network formation. \textit{Econometrica}, 2000, vol.~68, iss.~5, pp.~1181--1229.

6. Jackson M. O., Watts A. On the formation of interaction networks in social coordi\-na\-tion games. \textit{Games and Economic Behavior}, 2002, vol.~41, iss.~2, pp.~265--291.

7. Song Y., van der Schaar M. Dynamic network formation with incomplete information. \textit{Economic Theory}, 2015, vol.~59, iss.~2, pp.~301--331.

8. Atabati O., Farzad B. A strategic model for network formation. \textit{Computational Social Networks}, 2015, vol.~2, iss.~1, pp.~1--14.

9. Avrachenkov K., Elias J., Martignon F., Petrosyan L. A. A Nash bargaining solution for coope\-ra\-tive network formation games. \textit{Networking}, 2011, vol.~6640, pp.~307--318.

10. Petrosyan L. A., Sedakov A. A. Multistage network games with perfect information. \textit{Automation and Remote Control}, 2014, vol.~75, iss.~8, pp.~1532--1540.

11. Petrosyan L. A., Danilov N. N. Ustojchivye reshenija
neantagonisticheskih dif\-fe\-ren\-ci\-al'nyh igr s tranzitivnymi vyigryshami [Stability of solutions in non-zero sum differential games with transferable payoffs]. \textit{Vestnik of Leningrad University}, 1979, no.~1, pp.~52--59.  (In Russian)

12. Gao H., Petrosyan L. A., Qiao H., Sedakov A. Cooperation in two-stage games on undirected networks. \textit{Journal of Systems Science and Complexity}, 2017, vol.~30, iss.~3, pp.~680--693.

13. Pankratova Y. B., Petrosyan L. A. New characteristic function for multistage dynamic games. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2018, vol.~14, iss.~4, pp.~316--324. https://doi.org/10.21638/11701/spbu10.2018.404

14. Sun P., Parilina E. M. Stochastic model of network formation with asymmetric players. \textit{Automation and Remote Control}, 2021, vol.~82, iss.~6, pp.~1065--1082.

15. Khmelnitskaya A., Sel\c{c}uk \"{O}., Talman D. The Shapley value for directed graph games. \textit{Operations Research Letters}, 2016, vol.~44, iss.~1, pp.~143--147.

16. Gillies D. \textit{Some theorems on $n$-person games}. PhD Dissertation. Princeton, Princeton Univer\-si\-ty Press, 1953, 31~p.

17. Shapley L. S. Cores of convex games. \textit{International Journal of Game Theory}, 1971, vol.~1, iss.~1, pp.~11--26.

18. Sun P., Parilina E. Network formation with asymmetric players and chance moves. \textit{Mathematics}, 2021, vol.~9, no.~814.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent
\pagebreak
Received:  July 28, 2021.

Accepted: February 01, 2022.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Ping Suna}  --- Postgraduate Student;
sunping920925@163.com \par%

\vskip 2mm \textit{Elena M. Parilina} --- Dr. Sci. in Physics and Mathematics, Professor; e.parilina@spbu.ru \par%

\vskip 2mm \textit{Hongwei Gaob} --- PhD in Physics and Mathematics, Associate Professor;  gaohongwei@qdu.edu.cn \par%
%
%
}
