
{\normalsize

\vskip 6mm

\noindent{\bf Information and program support of the analysis and processing of holographic information% $^{*}$%
 }

}

\vskip 3mm

{\small

\noindent{\it A.~G.~Karpov$^1$, V.~V.~Trofimov$^1$, A.~G.~Fedorov$^{1,2}$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work  was supported by the Russian %Foundation for Basic Research (project N 19-31-90033).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation


\noindent%
$^2$~%
North-Eastern Federal University,
58, ul. Belinskogo, Yakutsk, Republic of Sakha (Yakutia),

\noindent%
\hskip2.45mm%
677027, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:} Karpov~A.~G., Trofimov~V.~V., Fedorov~A.~G. Information and program support of the analysis and processing of holographic information. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~17,~iss.~\issuenum,~pp.~\pageref{p9}--\pageref{p9e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum09 (In Russian)

\vskip3mm

\begin{hyphenrules}{english}

{\leftskip=7mm\noindent The research of thin films of various materials on nano- and microlevel is undoubtedly topical. Three-dimensional images of thin films can significantly increase the level of the received results. Intellectual computer support of researches assumes the existence or creation of mathematical and the software that implements the experimental program. Such support can most effectively be realized with the help of an information and expert system, based on a holographic electron microscope. In this work we presented an information and expert
system for solving this problem. When creating instrumental, hardware and software tools for non-destructive research of the 3D structure of objects, we proceeded from the assumption that the most complete information about the object of research can be obtained only with a comprehensive approach to the analysis of the structure of the object using complementary techniques that allow obtaining data as a 3D image.\\[1mm]
\textit{Keywords}: electronic holography, image processing, information-expert system, diagnostics of nanostructures, information module, tool module.\par}

\end{hyphenrules}

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Kartashev~V.~A., Kartashev~V.~V. Izobrazhenie nanorel'efa pri interpretacii izmerenij metodom immitacionnogo modelirovaniya [Obtaining of nanoscale surface images by simulation of stm measuring process]. {\it Nano- i mikrosistemnaya tekhnika} [{\it Nano- and microsystem technology}], 2016, vol.~18, pp.~131--133. (In Russian)

2. Ignatov~I.~I., Mosin~O.~V. Issledovanie strukturno-funkcional'nyh svojstv fullerensoderzhashchego minerala shungita i mikrokristallicheskogo alyumosilikata ceolita metodami elementnogo analiza, PEM, IK i DNES-spektroskopii [Research of the structural-functional properties of the fullerene-like shungite and micro-crystalline alumosilicate mineral zeolite by elemental analysis, TEM, IR and DNES]. {\it Nano- i mikrosistemnaya tekhnika} [{\it Nano- and microsystem technology}], 2016, vol.~18, pp.~357--366. (In Russian)

3. Egorov~O.~V. {\it Tekhnicheskaya mikroskopiya} [{\it Technical microscopy}]. Moscow, Tekhnosfera Publ., 2007, 376~p. (In Russian)

4. Egorov~N.~V., Karpov~A.~G., Antonova~L.~I., Fedorov~A.~G., Trofimov~V.~V. Technique for investigating the spatial structure of thin films at a nanolevel. {\it Journal of Surface Investigation: $X$-Ray, synchrotron and neutron techniques}, 2011, vol.~5, no.~5, pp.~992--995.

5. Egorov~N.~V., Karpov~A.~G. {\it Diagnosticheskie informacionno-ekspertnye sistemy} [{\it Diagnostic information and expert systems}]. St. Petersburg, St. Petersburg University Press, 2002, 490~p. (In Russian)

6. Edgar~V., Lawrence~F.~A., David~C.~J. {\it Introduction to electron holography}. New York, Kluwer Academic/Plenum Publ., 1999, 354~p.

7. Fink~H.-W., Stocker~W., Schmid~H. Holography with low-energy electrons. {\it Phys. Rev. Lett.}, 1990, vol.~65, no.~10, pp.~1204--1206.

8. Egorov~N.~V., Antonova~L.~I., Tatarinov~P.~S. et al. Bezlinzovyj nizkoenergeticheskij proekcionnyj mikroskop dlya osevoj elektronnoj golografii (kendroskop) [Lens-free low-energy projection microscope for axial electronic holography (kendroscope)]. {\it Pribory i tekhnika eksperimenta} [{\it Instruments and experimental techniques}], 2000, no.~5, pp.~157--158. (In Russian)

9. Gonzalez R., Woods R. {\it Digital image processing. International version}. $3^{\rm rd}$~ed. Upper Saddle River, New York, USA, Prentice Hall Publ., 2008, 976~p.

10. Miano J. {\it Compressed image file formats: JPEG, PNG, GIF, XBM, BMP ACM}. Boston, Addison Wesley Longman Press, 1999, 264~p.

11. Morin~R., Degiovanni~A. Interferometry with low-energy electrons. {\it JVST B --- Microelectronics and nanometer structures}, 1995, vol.~13(2), pp.~407--409.

12. Nussbaumer~H.~J. {\it Fast Fourier transform and convolution algorithms}. Berlin, Heidelberg, Springer Publ., 1981, 276~p.

13. Fedorov~A.~G., Karpov~A.~G. Chislennoe vosstanovlenie golograficheskikh izobrazhenii dlia issledovaniia struktury tonkikh plenok [Numerical restoration of holographic images for research of structure of thin films]. {\it Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes}, 2011, iss.~2, pp.~76--80. (In Russian)

14. Smart~Ju., Hock~K., Csomor~S. {\it Cross-platform GUI programming with wxWidgets}. Upper Saddle River, New York, USA,  Prentice Hall Publ. as part of Bruce Perens’ Open Source Series, 2006, 700~р.

15. Zharkov~S.~М. Methods of modern transmission electron microscopy in material study. {\it Journal of Siberian Federal University. Chemistry}, 2009, vol.~4, iss.~2, pp.~294--306.


\vskip1.5mm Received:  October 8, 2020.

Accepted: October 13, 2021.


\vskip6mm A\,u\,t\,h\,o\,r\,s'\,  i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%


\vskip1.5mm \textit{Andrey G. Karpov} --- Dr. Sci. in Engineering, Professor; a.g.karpov@spbu.ru \par%

\vskip1.5mm \textit{Vasiliy V. Trofimov} ---  Senior Lecturer; v.v.trofimov@spbu.ru \par%

\vskip1.5mm \textit{Arthur G. Fedorov} --- PhD in Engineering, Associate Professor; ag.fedorov@s-vfu.ru \par%
%
}
