


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm

1. Hill A. V.  {\it First and last experiments in muscle
mechanics}. Cambridge, New York,  University Press, 1970, 144~p.
(Russ. ed.: Hill~A.~V. {\it Mehanica myshechnogo sokrascheniya}.
Moscow, Mir Publ., 1972, 184~p.)

2. Volkenshteyn M. V.  {\it Biofizika} [{\it Biophisics}]. Moscow,
Nauka Publ., 1981, 576~p.     (In Russian)

3. Bagshau C. R. {\it Muscle contraction}. New York,  Springer
Press, 1982, 128~p. (Russ. ed.: Bagshau~C.~R. {\it Myshechnoe
sokraschenie}. Moscow, Mir Publ., 1989, 128~p.)


4. {\it Biologitchesky entsyklopedischeskiy slovar} [{\it
Biological Encyclopedic Dictionary}]. Moscow, Sov. encyclopedia
Publ., 1989, 863~p. (In Russian)


5. Barkinblit M., Gerdyaev A., Tarasova A.  {\it Zadathi po
fiziologii theloveka i givotnyh} [{\it Human and animal physiology
objectives}]. Moscow,  MIROS Publ., 1995, 176~p.      (In Russian)


6.  Keener J., Sneyd J. Mathematical physiology. {\it
Interdisciplinary Applied Mathematics}. 1998, vol.~8.
pp.~727--737.



7. Rubin A. B. {\it Biofizika} [{\it Biophisics}]. Moscow, Moscow
State University Publ., 2004, 469~p. (In Russian)

8. Novoselov V. S., Korolev V. S. Model vozbugdeniya myshtsy
[Model muscle excitation]. {\it SICPRO-05}. Moscow, IPU RAN Publ.,
2005, pp.~367--374. (In Russian)

9. Novoselov V. S. {\it Statistitheskaya dinamika} [{\it
Statistical dinamics}]. Saint Petersburg, Saint Petersburg
University  Publ., 2009, 393~p. (In Russian)

10. Novoselov V. S.  O matematithsheskoy modeli vozbugdeniya
kletok serdtsa [A mathematical model of excitation of the heart
cells]. {\it Vestnik of  Saint Petersburg University.  Series~10.
Applied mathematics. Computer science. Control processes}, 2013,
issue~3, pp.~58--66. (In Russian)

11. Davydov A. S.  Nelineynaya Biofizika [Non-linear Biophisics].
{\it Matematicheskoe modelirovanie} [{\it Mathematical modeling.
Processes in non-lenear environments}]. Moscow, Nauka Publ., 1986,
pp.~223--260. (In Russian)



\vskip 1mm

{\bf For citation:} Novoselov V.~S. Molecular mathematical model
of the skeletal muscle reduction. {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathematics. Computer science.
Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
