
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Tregubov V. P.} Problems of mechanical model identification for human body under vibration // Mechanism and Machine Theory. 2000. Vol.~35. P.~491--504.

2. {\it Coermann R. R.} The mechanical impedance of the human body in sitting and standing position at low frequencies // Human factors. 1962. Vol.~4. P. 227--253.

3. {\it Griffin M. J.}  Vertical vibration of seated subjects: effects of posture, vibration level, and frequency // Aviation Space and Environmental Medicine. 1975. Vol. 46. P. 269--276.

4. {\it Fairley T. E., Griffin M. J.} The apparent mass of the seated human body: Vertical vibration //  Journal of Biomechanics. 1989. Vol. 22. N~2. P. 81--94.

5.  {\it Потёмкин Б. А., Фролов К. В.}  Построение динамической
модели тела че\-ло\-ве\-ка-оператора, подверженного действию
широкополосных случайных вибра\-ций~// Виброизоляция машин и~
виброзащита человека-оператора / отв. ред. К.~В. Фролов. М.:
Наука, 1973. C. 17--30.

6. {\it Bai Xian-Xu, Xu Shi-Xu, Cheng Wei, Qian Li-Jun.} On 4-degree-of-freedom bio\-dynamic models of seated occupants: Lumped-parameter modeling // Journal
of Sound and Vibration. 2017. Vol.~402. N~18.  P.~122--141.

7.  {\it Wan~Y., Schimmels~J.\:M.}  A simple model that captures the essential dyna\-mics of a seated human exposed to whole body vibration // Advances in Bioengineering. 1995. Vol. 31. ASME publ.-BED (Bioengineering Division). P. 333--334.

8.  {\it Abbas~W., Abouelatta~O.\:B., El-Azab~M., Elsaidy~ M., Megahed  A.\:A.}  Opti\-mi\-zation of biodynamic seated human models using genetic algorithms // Engineering. 2010. Vol.~2. P. 710--719.

9. {\it Boileau P.~E., Rakheja S.} Whole-body vertical biodynamic response characteristics of the seated vehicle driver: measurement and model development // International Journal of Ind. Ergonomics. 1998.
Vol. 22. P. 449--472.


10. {\it Zhang E., Xu L.~A., Liu Z.~H., Li X.~L.} Dynamic modeling
and vibration characteristics of multi-DOF upper part system of
seated human body // Chine Journal of Engineering Design. 2008.
Vol.~15. P.~244--249.


11. {\it Трегубов В.\: П., Егорова Н.\: К.} О единственности
решения задачи определения параметров механических моделей тела
человека, подверженного вибрационному воздействию //
Вестн.\linebreak С.-Петерб. ун-та. Прикладная математика.
Информатика.  Процессы управления. 2019. Т. 15.\, Вып.~4.
С.~565--577. https://doi.org/10.21638/11702/spbu10.2019.412

12. {\it Bae~J.-J., Kang N.} Development of a five-degree-of-freedom seated human model and pa\-ra\-metric studies for its vibrational characteristics // Shock and Vibration. 2018. Article ID 1649180. 15~p.\linebreak https://doi.org/10.1155/2018/1649180

13. {\it Yoshimura ~T., Nakai~ K., Tamaoki~ G.} Multi-body dynamics modelling of seated human body under exposure to whole-body vibration // Industrial Health. 2005. Vol.~43. P.~441--447.

14. {\it Panjabi    M.\: M.,  Andersson G.\:B., Jorneus L., Hult E., Mattsson ~L.} In vivo measurements of spinal column vibrations // The Journal of Bone and Joint Surg. 1986. Vol. 68-A. P.~695--702.

15. {\it Kitazaki S., Griffin M.} A modal analysis of whole body vertical vibration using a finite element model of the human body // Journal of Sound Vibration. 1997. Vol.~200. P.~83--105.

16. {\it    Трегубов В.~П., Селезнева Н.~А.} Математическое моделирование динамики шейного отдела позвоночника при импульсных воздействиях // Вестн. С.-Петерб. ун-та.  Cер.~10. Прикладная математика. Информатика.  Процессы управления. 2016. Вып.~1. С.~53--65.

17. {\it Хилл А.~В.} Механика мышечного сокращения. Старые и~новые
опыты / пер. с~англ. Ю.~А.~Шаронова; под ред. Г.~М. Франка. М.:
Мир, 1972. 183~с. ({\it Hill A.~V.} First and last experiments in
muscle mechanics.)

18. {\it    Huxley A.\: F.} Muscle structure and theories of contraction // Progr. Biophys. and Biophys. Chem. 1957. Vol.~7. P.~255--318.

19. {\it    Дещеревский В.~И.}  Математические  модели   мышечного сокращения. М.:  Нау\-ка, 1977. 160~с.

20. {\it Tregubov V.~P.} Development of the muscle kinetic theory and cyclic movements~// Acta of Bioengineering and Biomechanics. 2003. Vol.~5. Suppl.~1.  P.~512--519.

21. {\it Кликунова К.~А., Трегубов В.~П.} Математическое
моделирование переходных режимов\linebreak\newpage\noindent
мышечного сокращения
// Вестн. С.-Петерб. ун-та. Сер. 10. Прикладная математика.
Информатика. Процессы управления. 2008. Вып.~3.  С.~56--62.

22. {\it    Тregubov V. P., Azanchevsky V. V., Zarin A., Klikunova K.} Mechanical models of the intervertebral disk and cervical spine~// Lecture Notes of the ICB Seminars. Warsaw, 2007. Vol.~79. P.~41--54.

23. {\it Глухарев К.~К., Потёмкин Б.~А., Фролов К.~В.} Особенности
биодинамики тела человека при вибрациях // Виброзащита
человека-оператора и~вопросы моделирования / отв. ред.
К.~В.~Фро\-лов. М.: Наука, 1973. С.~22--28.

24. Санитарные нормы 2.2.4/2.1.8.566-96. М.: Министерство здравоохранения России,  1997. 35~с.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 7 марта 2020~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Трегубов Владимир Петрович} --- д-р физ.-мат. наук, проф.; v.tregubov@spbu.ru

\vskip2mm \textit{Егорова Надежда Константиновна} --- аспирант; nadezhda\_ego@mail.ru


}
