

\noindent{\small UDC 519.63  \hfill {\footnotesize Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}\\
MSC 35F10, 65D30, 70F05

}

\vskip2mm

\noindent{\bf Estimates for Taylor series method to linear total systems of PDEs%$^{*}$%

 }

\vskip2.5mm

\noindent{\it  L.~K. Babadzanjanz, I.~Yu. Pototskaya, Yu.~Yu. Pupysheva%$\,^1$%
%, I.~О. Famylia%$\,^2$%
%, I.~О. Famylia%$\,^2$%

}

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ M. V. Bulatov and E. V. Chistyakova
%acknowledge the financial support from the Russian Foun\-dation
%for Basic Research (projects N 18-51-54001,  18-01-00643,
%18-29-10019).\par
%%
%%\vskip 2.0mm
%%
\indent{\copyright} Санкт-Петербургский государственный
университет, \issueyear%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum03 } }\hfill\thepage}%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum03}}}%
% для оформления нижнего колонтитула
\cfoot{} %

\vskip2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

{\small \noindent \textbf{For citation:} Babadzanjanz L.~K., Pototskaya I.~Yu., Pupysheva Yu.~Yu. Estimates for Taylor series method to linear total systems of PDEs. {\it Vestnik of Saint~Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}.\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum03

\vskip3mm

{\leftskip=7mm\noindent A large number of differential equations
can be reduced to polynomial form. As was shown in a number of
works by various authors, one of the best methods for the
numerical solution of the initial value problem for such ODE
systems is the method of Taylor series. In this article we
consider the Cauchy problem for the total linear PDE system, and
then --- a theorem about the accuracy of its solutions by this
method is formulated and proved. In the final part of the article,
four examples of total systems of partial differential equations
to the well-known two-body problem are proposed: two of them are
related to the Kepler equation, one to the motion of a point in
the orbit plane, and the last to the motion of the orbit plane.\\[1mm]
\textit{Keywords}: Taylor series  method, total linear PDE system, polynomial system, numerical PDE system integration.

}

}

\vskip 4mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{Introduction.} Issues considering in this article are: the
formulation of the Cauchy problem for total systems of partial
differential equations including polynomial and linear; the Taylor
series method; local error estimation for linear total Cauchy
problem. As examples, we consider four total polynomial systems to
the elliptical  two body problem.


\textbf{Initial value problem (IVP or Cauchy problem for
polynomial and linear total systems).} Consider the total system
of partial differential equations [1] with the initial conditions
\begin{equation}
\frac{\partial x_j}{\partial t_\nu}=f_{\nu,j}(x_1,\ldots,
x_n,t_1,\ldots, t_s), \quad x_j(t_0)=x_{0,j},\quad
j=1,\ldots,n,\;\; \nu=1,\ldots, s.
\end{equation}

Numerical methods for solving this problem are oriented to the general case when the right-hand sides $f_{\nu,j}$ belong to the class of smooth or piecewise smooth functions. At the same time, in many applied problems, for which numerical methods are developed, it is quite possible to reduce the problem (1) to the case when the functions $f_{\nu,j}$ are algebraic polynomials in $x_1,\ldots, x_n$ (by introducing the special additional variables [2, 3]). In these cases, the obtained Cauchy problem is called polynomial, and it can be written as
\begin{equation}
\frac{\partial x_j}{\partial t_\nu}=\sum_{m\in[1:L+1]}\sum_{i\in I(m)} a_{\nu,j,m}[i]x^i,\quad x_j(t_0)=x_{0,j},\quad j=1,\ldots,n,\;\;\nu=1,\ldots,s,
\end{equation}
\begin{equation*}
x=(x_1,\ldots, x_n)\in C^n,\;\; i=(i_1,\ldots, i_n),\;\; x^i=x_1^{i_1}\cdot\ldots\cdot x_n^{i_n},\; x_j,\; x_{0,j},\; t_{\nu},\;t_{0,\nu},\; a_{\nu,j,m}\in C,
\end{equation*}
\begin{equation*}
|i|=i_1+\ldots+i_n,\quad I(m)=\{i\in Z^n\; | i_1,\ldots, i_n\geq 0,\;|i|=m\},\quad L\in[0:+\infty).
\end{equation*}

This is IVP to total system of polynomial PDEs (or the total polynomial Cauchy problem). For small $x_1,\ldots, x_n$    the equations (1) one often linearizes and utilizes as first approximations. In what follows we will write down the linear problem as

 \begin{equation}
 \frac{\partial x}{\partial t_{\nu}}=a_{\nu}+A_{\nu}x, \quad x(t_0)=x_0,\quad \nu=1,\ldots,s,
 \end{equation}
\begin{equation*}
x=(x_1,\ldots,x_n),\quad x_0 =(x_{0,1},\ldots,x_{0,n})\in C^n,
\end{equation*}
\begin{equation*}
a_{\nu}=(a_{\nu,1},\ldots,a_{\nu,n})\in C^n,\quad |a_{\nu}|=\max_{i\in[1:n]}|a_i|,
\end{equation*}
\begin{equation*}
t=(t_1,\ldots,t_s),\quad t_0=(t_{0,1},\ldots,t_{0,s})\in C^s,\quad A_{\nu}=(a_{\nu,i,j}),\quad a_{\nu,i,j}\in C,
\end{equation*}
denote its solution by $x(t,t_0,x_0)$ or $x(t)$. In addition, we will utilize the designations
\begin{gather}
x^{(k)}=\frac{\partial^{|k|}x}{\partial t^k},\quad |k|=k_1+\ldots+k_s,\quad x_0^{(k)}=x^{(k)}(t_0),\notag\\ x^{(0)}=x,\;\;x_0^{(0)}=x_0,\;\;|x|=\max_{i\in[1:n]}|x_i|,\quad O_{\rho}(t_0)=O_{\rho_1}(t_0)\times\ldots\times O_{\rho_s}(t_0),\notag\\
O_{\rho_{\nu}}(t_0)=\{t\in C^s|(\forall j\in[1:s],j\ne\nu)(t_j=t_{j,0}),\;|t_{\nu}-t_{0,\nu}|<\rho_{\nu}\},\\
T_M x(t,t_0,x_0)=\sum_{m=0}^M x_0^{(m)}\frac{(t-t_0)^m}{m!},\quad \delta T_M x(t,t_0,x_0)=x(t,t_0,x_0)-T_M x(t,t_0,x_0),\notag\\
m!=\prod_{\mu=1}^s m_{\mu}!,\;\;0!=1,\;\;k=(k_1,\ldots,k_s),\notag\\
M=(M_1,\ldots,M_s)\in[0:+\infty)^s,\quad \rho=(\rho_1,\ldots,\rho_s)\in(0,+\infty)^s,\notag
\end{gather}
where $T_M$ and $\delta T_M$  are the operators that put in
correspondence the Taylor polynomial $T_M x(t,t_0,x_0)$  and the
remainder $\delta T_M x(t,t_0,x_0)$  to the solution of the
problem (3). We denote as
$R(t_0,x_0)=(R_1(t_0,x_0),\ldots,R_s(t_0,x_0))$,
$R_{\nu}(t_0,x_0)$, the \textit{vector radius of convergence} of
the Taylor series and, instead, later in this paper as a domain
where Taylor~se\-ries converge we will utilize
$O_{\rho}(t_0)=O_{\rho_1}(t_0)\times\ldots\times O_{\rho_s}(t_0)$,
see above in (4) and be\-low~in Proposition).


\textbf{On the Taylor series method.} The Taylor series method
[4--8] for solving the Cauchy problem (3) consists in constructing
a table of
 approximate values $x_{t_w}=x(t_w)$  using the formula
\begin{equation}
x_{\tau_w}=T_{N_w}x(\tau_w,\tau_{w-1},x_{\tau_{w-1}}),\quad
w=1,2,\ldots,
\end{equation}
here
\begin{equation*}
N_w=(N_{w,1},\ldots,N_{w,s})\in(0:\infty)^s,\;\;\tau_0=t_0,\;\;\tau_w=\tau_{w-1}+h_w,
\end{equation*}
\begin{equation*}
\tau_w=(\tau_{w,1},\ldots,\tau_{w,s}),\;\;h_w=(h_{w,1},\ldots,h_{w,s})\in C^s,
\end{equation*}
and $h_w$ has to satisfy the inequalities
\begin{equation}
|h_{w,\nu}|<R_{\nu}(\tau_{w-1},x_{\tau_{w-1}}),\quad \nu=1,\ldots,s.
\end{equation}

The calculation of each value of $\tilde{x}_{\tau_w}$ is called
the step of the method, and $h_w$ is called \textit{the size of
this step} (or, briefly, \textit{the step}). In the general case
of integration along a curve in $C^s$ all $h_{w,\nu}$  are complex
numbers, and  points $\tau_w$  lie on this curve. To calculate
$\tilde{x}_{\tau_w}$ for some given $\tau_w$  with high accuracy
by formula (5), even for $\tau_w$  from its domain of convergence
(see (5)), the number of steps may turn out to be large, which can
cause a fast accumulation of rounding errors and an increased
processor time. That is why it is advisable to use the steps as
large as possible (in actual fact, one has to find all
$\rho_{\nu}$  as large as possible see (6) and Proposition).
\vspace{3mm}

\textbf{Local error estimation for linear total Cauchy problem.}

\textbf{Estimates.}
Now we turn to problem (3). In addition to (4), we will use also the notation
\begin{equation}
(A_{\nu}^{k_{\nu}}x)_i=\sum_{j=1}^n a_{\nu,i,j}x_j,\quad \rho_{\nu}=1/s_{\nu},\quad s_{\nu}=\parallel A_{\nu}\parallel_{\infty}=\max_{i\in[1:n]}s_{\nu,i},\quad s_{\nu,i}=\sum_{j=1}^n| a_{\nu,i,j}|,
\end{equation}
\begin{equation*}
T_{\mu}e^{\tau}=\sum_{m=0}^{\mu}\frac{\tau^m}{m!},\quad \delta
T_{\mu}e^{\tau}=e^{\tau}-T_{\mu}e^{\tau},\;\;\mu=1,2,\ldots\;.
\end{equation*}

\textbf{Proposition.} The solution $x(t,t_0,x_0)$ of the problem (3) is holomorphic on $O_{\rho_\nu}(t_0)$  separately  in $t_{\nu}$ and satisfies there the inequality
\begin{equation}
|\delta T_M x(t,t_0,x_0)|\leq(|x_0|+|a_{\nu}|\rho_{\nu})\delta T_{M_{\nu}}e^{|t_{\nu}-t_{0,\nu}|/\rho_{\nu}}.
\end{equation}

\textit{Proof}. Because of
\begin{equation*}
k=(k_1,\ldots, k_s),\quad \frac{\partial^{|k|}x}{\partial t^k}=\frac{\partial^{k_{\nu}}x}{\partial t^{k_{\nu}}}\;\Rightarrow\; x^{k_{\nu}}=A_{\nu}^{k_{\nu}}x+A_{\nu}^{k_{\nu}-1}a_{\nu},\quad |(A_{\nu}^{k_{\nu}}x)_i|\leq|x|\rho_{\nu}^{k_{\nu}},
\end{equation*}
then
\begin{equation*}
|\delta T_M x(t,t_0,x_0)|=\left|\sum_{l=M_{\nu}}^{+\infty}\left(A_{\nu}^{l}x+A_{\nu}^{l-1}a_{\nu}\right)(t_{\nu}-t_{0,\nu})^l/l!\right|\leq
\end{equation*}
\begin{equation*}
\leq\left(|x_0|+|a_{\nu}|\rho_{\nu}\right)\sum_{l=M_{\nu}+1}^{+\infty}\left|(t_{\nu}-t_{0,\nu})/\rho_{\nu}\right|^l/l!=\left(|x_0|+|a_{\nu}|\rho_{\nu}\right)\delta T_{M_{\nu}}e^{|t_{\nu}-t_{0,\nu}|/\rho_{\nu}},
\end{equation*}
which is the required result.


\textbf{Improving estimates: scaling transformations and choice of scaling factors.}
The smaller $s_{\nu}=\rho_{\nu}^{-1}$, the better the estimates (8). In order to be able to improve these estimates, it is natural to introduce a scaling transformation in (3):
\begin{equation}
x_j=\alpha_j y_j, \quad \alpha_j>0, \;\; j\in[1:n].
\end{equation}
In connection with (9), we write down the Cauchy problem
\begin{equation}
\frac{\partial y}{\partial t_{\nu}}=b_{\nu} +B_{\nu}y, \quad y(t_0)=y_0,\;\; \nu=1,\ldots,s,
\end{equation}
\begin{equation*}
y=(y_1,\ldots,y_n),\quad y_0=(y_{0,1},\ldots,y_{0,n}), \quad b_{\nu}=(b_{\nu,1},\ldots,b_{\nu,n}),\quad B_{\nu}=(b_{\nu,i,j}),
\end{equation*}
\begin{equation*}
y_i=\alpha_i^{-1}x_i,\quad b_{\nu,i}=\alpha_i^{-1}a_{\nu,i},\quad b_{\nu,i,j}=\alpha_i^{-1}\alpha_j a_{\nu,i,j},
\end{equation*}
and will use the designations (see (7)):
\begin{equation}
\rho_{\nu}(\alpha)=\frac{1}{s_{\nu}(\alpha)},\;\; s_{\nu}(\alpha)=\max_{i\in[1:n]}s_{\nu,i}(\alpha),\;\;s_{\nu,i}(\alpha)=\alpha_i^{-1}\sum_{j=1}^n \alpha_j|a_{\nu,i,j}|,\;\;\alpha=(\alpha_1,\ldots,\alpha_n).
\end{equation}
Using (8), one can easily prove that Proposition implies.

\textbf{Corollary}. \textit{The solution $x(t,t_0,x_0)$ of the
problem $(3)$ is holomorphic on $O_{\rho_{\nu}(\alpha)}(t_0)$
\mbox{$($see $(4))$} separately  in $t_{\nu}$ and satisfies there
the inequality}
\begin{equation}
|\delta T_M x_i(t,t_0,x_0)|\leq \alpha_i\left(|y_0|+|b_{\nu}|\rho_{\nu}(\alpha)\right)\delta T_{M_{\nu}}e^{|t_{\nu}-t_{0,\nu}|/\rho_{\nu}(\alpha)}.
\end{equation}

Ability to select scaling factors $\alpha_1,\ldots,\alpha_n$ to reduce the value $s_{\nu}(\alpha)$ makes  Corollary a real tool of automatically assigning a step size of integration with a priori guaranteed local error estimation. The use of this corollary leads to the \textit{minimax} problem \mbox{[6, 9--14]}. For linear ODEs, we previously used the Perron’s theorem [6, 9, 10]. We use it here too.

\textbf{Theorem (Perron)}. \textit{Let the matrix $P=(p_{i,j})$ be
positive, i. e. $p_{i,j}>0$ for all $i,j\in[1:n]$. Then the
following statements are true} [12]:

\textit{a) there is a single eigenvalue $\lambda(P)$  of this
matrix with the largest absolute value};

\textit{b) this eigenvalue is positive and simple, and the
corresponding eigenvector can be chosen positive};

\textit{c) the following equality holds}:
$$\lambda(P)=\min_{x_1,\ldots,x_n
>0}\max_{i\in[1:n]}\left(\sum_{j=1}^n p_{i,j}x_j/x_i\right).$$


R e m a r k  1. More general Frobenius theorem and other results about eigenvalues and eigen-vectors of non-negative matrices can be found in [13].

R e m a r k 2.  With any approach to choosing scaling factors (see
(9)), it is worth considering that in practical calculations it is
enough to use their rough approximations with a relative error
about 10 percents, since Corollary remains true for any positive
scale factors, on the one hand, and, on the other hand, their
small change (e. g. in the second valid digit) will not lead to a
noticeable deterioration in the estimate (12). In [6, 10], devoted
to the method of Taylor series for polynomial ODE systems (that
is, for systems (2) with $s=1$), it was noted that in applications
it is possible to restrict ourselves with the~Perron’s theorem by
replacing the matrix $A$ with a close matrix $A^{+}$ with positive
elements. Since when $s\ne 1$ the matrix $A_{\nu}$  is not square,
this idea should be slightly refined: one can supplement the
matrix $A_{\nu}$ with a square nonzero matrix
$A_{\nu}^{\sim}=(\tilde{a}_{\nu,i,j})$  by small modulo elements
and then, instead $A_{\nu}$, use
$A_{\nu}^{+}=(|\tilde{a}_{\nu,i,j}|)$. It is important here to
recall that the eigenvalues of a matrix depend continuously on its
elements [14, 15].

Thus, in applications we can assume that $|a_{\nu,i,j}|>0$ for all $i,j\in[1:n]$, and then as scaling factors $\alpha_1,\ldots,\alpha_n$  in Corollary it is natural to use the components of a positive eigenvector $\alpha^{*}=(\alpha_1^{*},\ldots,\alpha_n^{*})$ of the matrices $A_{\nu}^{+}=(|\tilde{a}_{\nu,i,j}|)$  corresponding to its eigenvalue $\lambda(A_{\nu}^{+})$, maximum in absolute value.


\textbf{Examples.} Here we consider four total polynomial systems
to the elliptic two-body problem (from the Bregman thesis [16] and
paper [17]), and then Corollary can be applied to their linearized
versions. First, we will consider the equations of the two-body
problem and their solution in relative Cartesian coordinates
centered on the point mass $m^0$. Next, before considering the
above four total systems, we give in the form of a table all
the~func\-tions and arguments used in them.

The considered examples may be of real interest to specialists in the field of mechanics, astronomy, celestial mechanics, astrometry, and astrodynamics.

{\it \textbf{The equations of the two-body problem and their
solution to the elliptic case.}} Consider the equations of motion
of a point mass $m$ in a central Newtonian field of mass $m^0$,
using relative Cartesian coordinates centered on the point mass
$m^0$:
\begin{equation*}
\ddot{\xi}_i=-\mu\xi_i r^{-3}\;\; (\mbox{or}\;\;
\dot{\xi}_i=\eta_i\;\;\dot{\eta}_i=-\mu\xi_i
r^{-3}),\;\;i\in[1:3],
\end{equation*}
and the general solution of these equations for the elliptic case:
\begin{equation}
\xi_i/a=A_i\sqrt{1-e^2}\sin E+B_i(\cos E-e),\;\;i\in[1:3],\quad r/a=(1-e\cos E),
\end{equation}
\begin{gather}
A_1=-\sin\omega\cos\Omega-\cos\omega\sin\Omega\cos i,\quad B_1=\cos\omega\cos\Omega-\sin\omega\sin\Omega\cos i,\notag\\
A_2=-\sin\omega\sin\Omega+\cos\omega\cos\Omega\cos i,\quad B_2=\cos\omega\sin\Omega+\sin\omega\cos\Omega\cos i,\\
\noindent A_3=\cos\omega\sin i,\quad\;\; B_3=\sin\omega\sin i,\notag
\end{gather}
\begin{equation}
E-e\sin E=M,\quad M=M_0+n(t-t_0),\quad n=\sqrt{\mu/a^3},\quad \mu=\gamma(m^0+m),
\end{equation}
where $a$ (semi-major axis), $e$ (eccentricity), $M_0$ (mean anomaly of the epoch $t_0$), $\Omega$ (longitude of the ascending node), $i$ (inclination), $\omega$ (pericenter argument) are Kepler's elements (arbitrary constants), and $E$ (eccentric anomaly), $M$ (mean anomaly) are functions of time; $\gamma$ is Newtonian universal constant of gravitation.

{\it \textbf{Functions and arguments used.}} Next, we are going to
write out four total polynomial systems: two for solving Kepler's
equation and two for the coordinates and velocities of the
two-body problem. For the reader’s convenience, we give Table of
the main functions (placed there into rect) and arguments. The
four total systems mentioned above are numbered (see the column N
in the Table) in an understandable way.
\begin{center}
{\small \textit{Table}. \textbf{Main functions and arguments}
\vspace{3mm}

%\nopagebreak[4]
\begin{tabular}{|c|c|c|}
\hline\rule{0pt}{3pt}
N&Functions&Arguments\\
\hline
%&&\\
\rule{0pt}{13pt}
1&\fbox{$\varphi_1=E$}\;,\;$\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1}$&$\tau_1=e,\;\tau_2=M$\\[1mm]
%&&\\
\hline
%&&\\
\rule{0pt}{14pt}
2&\fbox{$\varphi_1=E$}\;,\;$\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1},$&$t_1=t,\;t_2=a$,\\
&$\varphi_5=a^{-1/2}$&$t_3=e,\;t_4=M_0$\\[.5mm]
%&&\\
\hline
%&&\\
\rule{0pt}{13pt}
&\fbox{$\varphi_1=E$}\;,\;$\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1},$&$t_1=t,\;t_2=a,$\\
3&$\varphi_5=a^{-1/2},\;\varphi_6=(1-e^2)^{1/2},\;\varphi_7=(1-e^2)^{-1/2},$&$t_3=e,\;t_4=M_0$\\[.5mm]
&\fbox{$\varphi_8=\xi_1$}\;,\;\fbox{$\varphi_9=\xi_2$}\;,\;\fbox{$\varphi_{10}=\xi_3$}\;,&\\
\rule{0pt}{13pt}
&\fbox{$\varphi_{11}=\eta_1$}\;,\;\fbox{$\varphi_{12}=\eta_2$}\;,\;\fbox{$\varphi_{13}=\eta_3$}&\\[1mm]
%&&\\
\hline
%&&\\
\rule{0pt}{3pt}
&$\varphi_{14}=A_1,\;\varphi_{15}=A_2,\;\varphi_{16}=A_3,\;\varphi_{17}=B_1,\;\varphi_{18}=B_2,$&$t_5=i,\;t_6=\Omega,$\\
4&$\varphi_{19}=B_3,\;\varphi_{20}=A_4=\sin\omega\cos i,\;\varphi_{21}=B_4=\cos\omega\cos i,$&$t_7=\omega$\\
&$\varphi_{22}=A_5=\sin\Omega,\;\varphi_{23}=B_5=\cos\Omega$&\\[.5mm]
%&&\\
\hline
\end{tabular}
}
\end{center}
%\end{table}


To apply Corollary, it remains for the user to linearize the equations in the vicinity of the initial data, then write out the matrix $A_{\nu}^{+}-\lambda I$  and, finally, find the maximum eigenvalue in absolute value and the corresponding positive eigenvector.

%\begin{center}
%\underline{\textbf{Main functions and arguments list}}
%\end{center}
%\nopagebreak

%\vspace{2mm}
%\textbf{I}. Main functions for arguments $\tau_1=e,\;\tau_2=M$ are
%\begin{equation*}
%\fbox{$\varphi_1=E$}\;,\;\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1}.
%\end{equation*}
%\textbf{II}.  Main functions for arguments $t_1=t,\;t_2=a$, $t_3=e,\;t_4=M_0$, are
%\begin{equation*}
%\fbox{$\varphi_1=E$}\;,\;\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1},\;\varphi_5=a^{-1/2}.
%\end{equation*}
%\textbf{III}.  Main functions for arguments $t_1=t,\;t_2=a$, $t_3=e,\;t_4=M_0$, are
%\begin{gather*}
%\fbox{$\varphi_1=E$}\;,\;\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1},\;\varphi_5=a^{-1/2},\\
%\varphi_6=(1-e^2)^{1/2},\;\varphi_7=(1-e^2)^{-1/2},\;\fbox{$\varphi_8=\xi_1$}\;,\\
%\fbox{$\varphi_9=\xi_2$}\;,\;\fbox{$\varphi_{10}=\xi_3$}\;,
%\fbox{$\varphi_{11}=\eta_1$}\;,\;\fbox{$\varphi_{12}=\eta_2$}\;,\;\fbox{$\varphi_{13}=\eta_3$}\\
%\end{gather*}
%\textbf{IV}.  Main functions for arguments $t_5=i$, $t_6=\Omega$, $t_7=\omega$, are
%\begin{gather*}
%\varphi_{14}=A_1,\;\varphi_{15}=A_2,\;\varphi_{16}=A_3,\;\varphi_{17}=B_1,\;\varphi_{18}=B_2,\\
%\varphi_{19}=B_3,\;\varphi_{20}=A_4=\sin\omega\cos i,\;\varphi_{21}=B_4=\cos\omega\cos i,\\
%\varphi_{22}=A_5=\sin\Omega,\;\varphi_{23}=B_5=\cos\Omega\\
%\end{gather*}

{\it \textbf{The first total polynomial system for Kepler's
equation.}} Here, Kepler's equation (15) is used in order to write
out a total polynomial system that is satisfied by an eccentric
anomaly, considered as a function of eccentricity and mean
anomaly. Assuming \mbox{(see Table)} $\varphi_1=E$,
$\varphi_2=\sin E$, $\varphi_3=\cos E$, $\varphi_4=(1-e\cos
E)^{-1}$, $\tau_1=e$, $\tau_2=M$ and using the equality
$\varphi_1-\tau_1\sin\varphi_1=\tau_2$  as an implicit
representation of $\varphi_1(\tau_1,\tau_2)$, we get the equations
\begin{gather}
\frac{\partial\varphi_1}{\partial\tau_1}=\varphi_2\varphi_4,\quad\frac{\partial\varphi_1}{\partial\tau_2}=\varphi_4,\quad
\frac{\partial\varphi_2}{\partial\tau_1}=\varphi_2\varphi_3\varphi_4,\quad\frac{\partial\varphi_2}{\partial\tau_2}=\varphi_3\varphi_4,\quad
\frac{\partial\varphi_3}{\partial\tau_1}=-\varphi_2^2\varphi_4,\notag\\
\\
\frac{\partial\varphi_3}{\partial\tau_2}=-\varphi_2\varphi_4,\quad
\frac{\partial\varphi_4}{\partial\tau_1}=\varphi_3\varphi_4^2-\tau_1\varphi_2^2\varphi_4^3,\quad\frac{\partial\varphi_4}{\partial\tau_2}=-\tau_1\varphi_2\varphi_4^3.\notag
\end{gather}

{\it \textbf{The second total polynomial system for Kepler's
equation.}} Now we write out a total system that satisfies the
eccentric anomaly $E$, considered as a function of time $t$ and
three Keplerian elements $a,e,M_0$. Assuming

\begin{gather*}
\varphi_1=E,\;\varphi_2=\sin E,\;\varphi_3=\cos E,\;\varphi_4=(1-e\cos E)^{-1},\;\varphi_5=a^{-1/2},\\
t_1=t,\; t_2=a,\;t_3=e,\;t_4=M_0,
\end{gather*}
and using equality $\varphi_1-t_3\sin\varphi_1=t_4+\sqrt{\mu}t_2^{-3/2}(t_1-t_0)$ as an implicit function $\varphi_1(t_1,t_2,t_3,t_4)$ representation, we get the equations
\begin{gather}
\frac{\partial\varphi_1}{\partial t_1}=\sqrt{\mu}\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_1}{\partial t_2}=-\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_1}{\partial t_3}=\varphi_2\varphi_4,\quad\frac{\partial\varphi_1}{\partial t_4}=\varphi_4,\notag\\
\frac{\partial\varphi_2}{\partial t_1}=\sqrt{\mu}\varphi_3\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_2}{\partial t_2}=-\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_3\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_2}{\partial t_3}=\varphi_2\varphi_3\varphi_4,\quad\frac{\partial\varphi_2}{\partial t_4}=\varphi_3\varphi_4,\notag\\
\frac{\partial\varphi_3}{\partial t_1}=-\sqrt{\mu}\varphi_2\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_3}{\partial t_2}=\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_2\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_3}{\partial t_3}=-\varphi_2^2\varphi_4,\quad\frac{\partial\varphi_3}{\partial t_4}=-\varphi_2\varphi_4,\notag\\
\frac{\partial\varphi_4}{\partial t_1}=-\sqrt{\mu}t_3\varphi_2\varphi_4^3\varphi_5^3,\quad\frac{\partial\varphi_4}{\partial t_2}=\frac{3\sqrt{\mu}(t_1-t_0)}{2}t_3\varphi_2\varphi_4^3\varphi_5^5,\quad\frac{\partial\varphi_4}{\partial t_3}=\varphi_3\varphi_4^2-t_3\varphi_2^2\varphi_4^3,\\
\frac{\partial\varphi_4}{\partial t_4}=-t_3\varphi_2\varphi_4^3,\quad\frac{\partial\varphi_5}{\partial t_j}=0,\quad j=1,3,4,\quad\frac{\partial\varphi_5}{\partial t_2}=\frac{1}{2}\varphi_5^3.\notag
\end{gather}

{\it \textbf{The first total polynomial system for the two body
equations.}} The quantities
\begin{gather*}
\varphi_1=E,\quad\varphi_2=\sin E,\quad\varphi_3=\cos E,\quad\varphi_4=(1-e\cos E)^{-1},\\
\varphi_5=a^{-1/2},\quad\varphi_6=(1-e^2)^{1/2},\quad \varphi_7=(1-e^2)^{-1/2},\\
\varphi_{7+i}=\xi_i,\quad \varphi_{10+i}=\eta_i,\quad i=1,2,3,
\end{gather*}
we  consider as functions of time $t_1=t$  and elements  $t_2=a$,
$t_3=e$, $t_4=M_0$ and we assume elements $\Omega,i,\omega$ as
parameters. Using formulas (13)--(16) we obtain that these
functions satisfy the total system of partial differential
equations (the equations for $\varphi_1,\ldots,\varphi_5$ and (17)
are the same):
\begin{gather*}
\frac{\partial\varphi_1}{\partial t_1}=\sqrt{\mu}\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_1}{\partial t_2}=-\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_1}{\partial t_3}=\varphi_2\varphi_4,\quad\frac{\partial\varphi_1}{\partial t_4}=\varphi_4,\\
\\
\frac{\partial\varphi_2}{\partial t_1}=\sqrt{\mu}\varphi_3\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_2}{\partial t_2}=-\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_3\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_2}{\partial t_3}=\varphi_2\varphi_3\varphi_4,\quad\frac{\partial\varphi_2}{\partial t_4}=\varphi_3\varphi_4,\\
\\
\frac{\partial\varphi_3}{\partial t_1}=-\sqrt{\mu}\varphi_2\varphi_4\varphi_5^3,\quad\frac{\partial\varphi_3}{\partial t_2}=\frac{3\sqrt{\mu}(t_1-t_0)}{2}\varphi_2\varphi_4\varphi_5^5,\quad\frac{\partial\varphi_3}{\partial t_3}=-\varphi_2^2\varphi_4,\quad\frac{\partial\varphi_3}{\partial t_4}=-\varphi_2\varphi_4,\\
\\
\frac{\partial\varphi_4}{\partial t_1}=-\sqrt{\mu}t_3\varphi_2\varphi_4^3\varphi_5^3,\quad\frac{\partial\varphi_4}{\partial t_2}=\frac{3\sqrt{\mu}(t_1-t_0)}{2}t_3\varphi_2\varphi_4^3\varphi_5^5,\quad\frac{\partial\varphi_4}{\partial t_3}=\varphi_3\varphi_4^2-t_3\varphi_2^2\varphi_4^3,\\
\\
\frac{\partial\varphi_4}{\partial t_4}=-t_3\varphi_2\varphi_4^3,\quad\frac{\partial\varphi_5}{\partial t_j}=0,\quad j=1,3,4,\quad\frac{\partial\varphi_5}{\partial t_2}=\frac{1}{2}\varphi_5^3,\\
\frac{\partial\varphi_6}{\partial t_j}=\frac{\partial\varphi_7}{\partial t_j}=0,\quad j=1,2,4,\quad \frac{\partial\varphi_6}{\partial t_3}=-t_3\varphi_7,\quad \frac{\partial\varphi_7}{\partial t_3}=t_3\varphi_7^3,\\
\frac{\partial\varphi_{7+i}}{\partial t_1}=t_2\varphi_4\varphi_5^3\sqrt{\mu}(A_i\varphi_6\varphi_3-B_i\varphi_2),\\
\frac{\partial\varphi_{7+i}}{\partial t_2}=(\varphi_3 - t_3)B_i+\varphi_3\varphi_6 A_i+\frac{3}{2}\sqrt{\mu}(t_1-t_0)t_2\varphi_4\varphi_5^5(B_i\varphi_2 -A_i\varphi_3\varphi_6),\\
\frac{\partial\varphi_{7+i}}{\partial t_3}=t_2(A_i\varphi_3\varphi_2\varphi_4\varphi_6 -A_i t_3\varphi_2\varphi_7 -B_i(1+\varphi_2^2\varphi_4)),\\
\frac{\partial\varphi_{7+i}}{\partial t_4}=t_2\varphi_4(A_i\varphi_6\varphi_3-B_i\varphi_2),\\
\frac{\partial\varphi_{10+i}}{\partial t_1}=-(\mu t_3\varphi_2\varphi_4^3\varphi_5^4(A_i\varphi_6\varphi_3-B_i\varphi_2))-\mu\varphi_4^2\varphi_5^4(B_i\varphi_3+A_i\varphi_2\varphi_6),\\
\frac{\partial\varphi_{10+i}}{\partial t_2}=\frac{1}{2}\sqrt{\mu}\varphi_4\varphi_5^3(A_i\varphi_6\varphi_3-B_i\varphi_2)+\frac{3}{2}\mu(t_1-t_0)\varphi_4^2\varphi_5^6
[t_3\varphi_2\varphi_4(A_i\varphi_6\varphi_3-B_i\varphi_2)\;+\\
+\;(B_i\varphi_3+A_i\varphi_2\varphi_6)],\\
\frac{\partial\varphi_{10+i}}{\partial t_3}=\sqrt{\mu}\varphi_4^2\varphi_5(\varphi_3-t_3\varphi_2^2\varphi_4)(A_i\varphi_6\varphi_3-B_i\varphi_2)\;-\\
\qquad\qquad\qquad -\;\sqrt{\mu}\varphi_4\varphi_5
(\varphi_2\varphi_3\varphi_4 B_i+\varphi_2^2\varphi_4\varphi_6 A_i+t_3\varphi_3\varphi_7 A_i),\\
\frac{\partial\varphi_{10+i}}{\partial t_4}=\sqrt{\mu}\varphi_4^2\varphi_5[t_3\varphi_2\varphi_4(A_i\varphi_6\varphi_3-B_i\varphi_2)-(B_i\varphi_3+A_i\varphi_2\varphi_6)].
\end{gather*}

{\it \textbf{The second total polynomial system for the two body
equations.}} We consider the total system for
$\varphi_{13+i}=A_i$, $\varphi_{16+i}=B_i$, $i=1,2,3$, as
functions of elements $t_5=i$, $t_6=\Omega$, $t_7=\omega$. If, in
addition to these auxiliary functions (see (14)), four more
functions
\begin{gather*}
\varphi_{20}=A_4=\sin\omega\cos i,\quad \varphi_{21}=B_4=\cos\omega\cos i,\\
\varphi_{22}=A_5=\sin\Omega,\quad \varphi_{23}=B_5=\cos\Omega
\end{gather*}
%
are introduced, then the desired total system will be written in
the form
\begin{gather*}
\begin{split}
&\frac{\partial\varphi_{14}}{\partial t_6}=-\varphi_{15},\quad
\frac{\partial\varphi_{14}}{\partial t_7}=-\varphi_{17},\quad
\frac{\partial\varphi_{14}}{\partial t_5}=\varphi_{16}\varphi_{22},\\
&\frac{\partial\varphi_{17}}{\partial t_6}=-\varphi_{18},\quad
\frac{\partial\varphi_{17}}{\partial t_7}=\varphi_{14},\qquad
\frac{\partial\varphi_{17}}{\partial t_5}=\varphi_{19}\varphi_{22},\\
&\frac{\partial\varphi_{15}}{\partial t_6}=\varphi_{14},\qquad
\frac{\partial\varphi_{15}}{\partial t_7}=-\varphi_{18},\quad
\frac{\partial\varphi_{15}}{\partial t_5}=-\varphi_{16}\varphi_{23},\\
&\frac{\partial\varphi_{18}}{\partial t_6}=\varphi_{17},\qquad
\frac{\partial\varphi_{18}}{\partial t_7}=\varphi_{15},\qquad
\frac{\partial\varphi_{18}}{\partial t_5}=-\varphi_{19}\varphi_{23},\\
&\frac{\partial\varphi_{16}}{\partial t_6}=0,\qquad\quad
\frac{\partial\varphi_{16}}{\partial t_7}=-\varphi_{19},\quad\;
\frac{\partial\varphi_{16}}{\partial t_5}=\varphi_{21},\\
&\frac{\partial\varphi_{19}}{\partial t_6}=0,\qquad\quad
\frac{\partial\varphi_{19}}{\partial t_7}=\varphi_{16},\quad\quad
\frac{\partial\varphi_{19}}{\partial t_5}=\varphi_{20},\\
&\frac{\partial\varphi_{20}}{\partial t_6}=0,\qquad\quad
\frac{\partial\varphi_{20}}{\partial t_7}=\varphi_{21},\quad\quad
\frac{\partial\varphi_{20}}{\partial t_5}=-\varphi_{19},\\
&\frac{\partial\varphi_{21}}{\partial t_6}=0,\qquad\quad
\frac{\partial\varphi_{21}}{\partial t_7}=-\varphi_{20},\quad\;
\frac{\partial\varphi_{21}}{\partial t_5}=-\varphi_{16},\\
&\frac{\partial\varphi_{22}}{\partial t_6}=\varphi_{23},\qquad
\frac{\partial\varphi_{22}}{\partial t_7}=0,\qquad\quad
\frac{\partial\varphi_{22}}{\partial t_5}=0,\\
&\frac{\partial\varphi_{23}}{\partial t_6}=-\varphi_{22},\quad\;
\frac{\partial\varphi_{23}}{\partial t_7}=0,\qquad\quad
\frac{\partial\varphi_{23}}{\partial t_5}=0.\\
\end{split}
\end{gather*}

\textbf{Conclusion}. The main result of this article is the local
guaranteed a priori error estimate (12) for the solution of the
Cauchy problem (3) for the total linear system of partial
differential equations using the Taylor series method (see
consequently: equa\-tions~(3), designations (4), formulas to the
Taylor series method (5), inequality (8), scaling transformation
(9) (with (10)), designations (11), inequality (12), the Perron’s
theorem, the Remarks 1,2, inequality (12), and item just after
Remark 2). In the final part of the article, four examples of
total systems of partial differential equations to the well-known
two-body problem are proposed: two of them are related to the
Kepler equation, one to the motion of a point in the orbit plane,
and the last to the motion of the orbit plane.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
\input{03/ref-s-eng}% для английской статьи

%\newpage
\input{03/lit-ra-eng}% для английской статьи

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\thispagestyle{empty}

\vskip 3mm

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}}%
% для оформления нижнего колонтитула
\cfoot{} %

}
