
{\normalsize

\vskip 6mm

\noindent{\bf On the qualitative properties of the solution\\ of a
nonlinear boundary value problem
 in the dynamic theory of $p$-adic strings$^*$%
}

}

\vskip 2mm

{\small

\noindent{\it Kh. A. Khachatryan$^{1,2,3}$%
, H. S. Petrosyan$^{1,4}$%
%, I.~Î. Famylia%$~^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}%
\parindent=7mm
%%
%\vskip 0.0mm
\hskip 4mm$^{*}$ This work was supported by the Russian Science Foundation (project N~19-11-00223).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%óíèâåðñèòåò, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
Lomonosov Moscow State University, 1, Leninskiye Gory, GSP-1,
Moscow,

\noindent%
\hskip2.45mm%
119991, Russian Federation


\noindent%
$^2$~%
Yerevan State University, 1, Alex Manoogian ul., Yerevan,

\noindent%
\hskip2.45mm%
0025, Republic of Armenia

\noindent%
$^3$~%
National Academy of Sciences of the Republic of Armenia, 24/5,
Marshal Baghramyan pr., Yerevan,

\noindent%
\hskip2.45mm%
0019, Republic of Armenia

\noindent%
$^4$~%
Armenian National Agrarian University, 74, ul.  Teryana, Yerevan,

\noindent%
\hskip2.45mm%
0009, Republic of Armenia

%\noindent%
%$^2$~%
%St.~Petersburg State University, 7--9, Universitetskaya nab.,
%St.~Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:}   Khachatryan Kh. A., Petrosyan
H. S. On the qualitative properties of the solution\\ of a
nonlinear boundary value problem  in the dynamic theory of
$p$-adic strings. {\it Vestnik of Saint~Peters\-burg Uni\-versity.
Applied Mathematics. Computer Science. Control Processes},
\issueyear,
vol.~16, iss.~\issuenum, pp.~\pageref{p7}--\pageref{p7e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum07  (In Russian)

\vskip2.0%3
mm

{\leftskip=7mm\noindent The article considers a boundary value
problem for a class of singular integral equations with an almost
total-difference kernel and convex nonlinearity on the positive
half-line. This problem arises in the dynamic theory of $ p $-adic
open-closed strings. It is proved that any non-negative and
bounded solution of a given boundary value problem is a continuous
function and the difference between the limit and the solution is
itself an integrable function on the positive half-line. For a
particular case, it is proved that the solution is a monotonically
non-decreasing function. A uniqueness theorem is established in
the class of nonnegative and bounded functions. At the conclusion
of the article, a specific applied example of this boundary
problem is given.\\[1mm]
\textit{Keywords}: boundary value problem, convexity, continuity,
summability, monotonicity, solution limit.
\par}

\vskip 4.5%6
mm

\noindent \textbf{References} }

\vskip 1.8%2
mm

{\footnotesize

 1. Arefeva I. Ya.,  Dragovic B. G.,  Volovich I. V. Open and
closed $p$-adic strings and quadratic extensions of number fields.
\emph{Phys. Lett. B}, 1988, vol.~212, no.~3, pp.~283--291.

 2. Vladimirov V. S. Î nelineinyh uravneniyah $p$-àditcheskih
otkrytyh, zamknutyh i otkryto-zamknutyh strun [Nonlinear equations
for $p$-adic open, closed, and open-closed strings]. \emph{Theor.
and Math. Phys.}, 2006, vol.~149, iss.~3, pp.~354--367. (In
Russian)

 3. Brekke L.,  Freund P. G. O. $p$-Adic numbers in physics.
\emph{Phys. Rep.}, 1993, vol.~233,  no.~1, pp.~1--66.

 4. Khachatryan Kh. A. Î razreshimosti nekotoryh klassov
nelineinyh singuliarnyh kraevyh zadach, voznikauschih v teorii
$p$-àditcheskih otkryto-zamknutyh strun [Solvability of some
classes of nonlinear singular boundary value problems in the
theory of $p$-adic open-closed strings]. \emph{Theor. and Math.
Phys.}, 2019, vol.~200, iss.~1, pp.~106--117. (In Russian)

 5. Khachatryan Kh. A. Î razreshimosti nekotoryh nelineinyh granichnyh
zadach dlia singuliarnyh integral'nyh uravneniy tipa sviortki [On
the solvability of some nonlinear boundary value problems for
convolution type singular integral equations]. \emph{Trudy MMO},
2020, vol.~81, iss.~1, pp.~3--40. (In Russian)

 6. Rudin U. \emph{Functional analysis.} London, McGraw-Hill
Science/Engineering/Math. Publ., 1973, 448~p. (Russ. ed.: Rudin U.
{\it Functsional'niy analiz}. Moscow, Mir Publ., 1975, 444~p.)

 7. Kolmogorov A. N.,  Fomin S. V. \emph{Elementy teorii
 funktsiy i funktsional'nogo analiza} [\emph{Elements of the theory of
functions and functional analysis}]. 5th ed. Moscow, Nauka Publ.,
1981, 544~p. (In Russian)

 8. Khachatryan Kh. A. Existence and uniqueness of the
solution of one boundary value problem for the convolution
integral equation with monotonic nonlinearity. \emph{Izvestiya.
Mathematics}, 2020, vol.~84, no.~4, pp.~807--815.
https://doi.org/10.1070/IM8898

 9. Khachatryan Kh. A. O razreshimosti odnoy sistemy nelineinyh
integral'nyh uravneniy tipa Hammershteina na priamoy  [The
solvability of a system of nonlinear integral equations of
Hammerstein type on the whole line]. \emph{Proceedings of Saratov
University. Series Mathematics. Mechanics. Informatics}, 2019,
vol.~19, iss.~2, pp.~164--181. (In Russian)

 10. Aref'eva I. Ya.,  Koshelev A. S.,  Joukovskaya L. V.
Time evolution in superstring field theory on non-BPS brane.
I.~Rolling tachyon and energy-momentum conservation. \emph{J. High
Energy Phys.}, 2003, vol.~012,  no.~9, pp.~1--15.

 11. Aref'eva I. Ya. Skatyvauschiesia reshenia polevyh uravneniy
na neekstrimal'nyh branah i v\linebreak $p$-àditcheskih strunah
[Rolling tachyon on non-BPS branes and $p$-adic strings].
\emph{Proceedings of V.~A.~Stek\-lov Mathem. institute}, 2004,
vol.~245, pp.~40--47. (In Russian)

 12. Ohmori K. Toward open-closed string theoretical
description of rolling tachyon. \emph{Phys. Rev. D}, 2004,
vol.~69, no.~2, pp.~026008, hep-th/0306096.



\vskip 1.5mm

Received:  January 21, 2020.

Accepted: October 23, 2020.


\vskip6 mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:


\vskip2 mm \textit{Khachatur A. Khachatryan} --- Dr. Sci. in
Physics and Mathematics, Professor; khach82@rambler.ru

\vskip2 mm \textit{Haykanush S. Petrosyan} --- PhD in Physics and
Mathematics, Associate Professor; haykuhi25@mail.ru\par
%
}
