
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm


{\footnotesize


1. {\it Kaszkurewicz E., Bhaya A.} Matrix diagonal stability in
systems and computation. Boston, Basel, Berlin: Birkhauser, 1999.
267~p.

2. {\it Пых Ю. А.} Равновесие и~устойчивость в~моделях
популяционной динамики. М.: Наука, 1983. 182~c.

3. {\it  Berman A.,  Plemmons R. J.} Nonnegative matrices in the
mathematical sciences.  Philadelphia: SIAM,  1987. 361~p.


4. {\it  Barker G. P.,  Berman A.,   Plemmons R. J.}
 Positive diagonal solutions to the Lyapunov equations
// {Linear and Multilinear Algebra}. 1978. Vol.~5, N~4. P. 249--256.

5. Метод векторных функций Ляпунова в~теории устойчивости / под
ред. А.~А.~Во\-ро\-но\-ва, В.~М.~Матросова. М.: Наука, 1987.
312~c.



6. {\it  Sontag E. D.} Passivity gains and the ``secant
condition'' for stability // Systems and Control Letters. 2006.
Vol.~55. P.~177--183.



7. {\it Подвальный С. Л., Провоторов В. В.} Стартовое управление
параболической системой с~распределенными параметрами на графе
 //  Вестн. С.-Петерб. ун-та.
Сер.~10. Прикладная математика, Информатика. Процессы управления.
2015. Вып. 3. C.~126--142.


8. {\it Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A.}
Unique weak solvability of a nonlinear initial boundary value
problem with distributed parameters in a netlike domain
 //  Вестн. С.-Петерб. ун-та.
%Сер.~10:
Прикладная математика. Информатика. Процессы управления.  2017. Т.
13. Вып. 3. C.~264--277. DOI:  10.21638/11701/spbu10.2017.304











9. {\it Hofbauer J., Sigmund K.} Evolutionary games and population
dynamics. Cambridge: Cambridge University Press, 1998. 323~p.





10. {\it  Aleksandrov A. Yu.,  Aleksandrova E. B.,  Platonov A.
V.}
 Ultimate boundedness conditions for a hybrid model of population dynamics //
Proc. 21st Mediterranean conference on Control and Automation,
June 25--28, 2013. Platanias-Chania, Crite,  Greece, 2013.
P.~622--627.



11. {\it  Shorten R., Narenda K. S.}
 On the diagonal stability of a class of almost positive
switched systems~// Proc. American Control Conference,  June
30---July 02, 2010. Marriott Waterfront, Baltimore, MD, USA, 2010.
P.~6250--6255.


12. {\it Arcat M., Sontag E.} Diagonal stability of a class of
cyclic systems and its connection with the secant criterion
// Automatica. 2006. Vol.~42, N~9. P.~1531--1537.



13. {\it  Mason O., Shorten R.} On the simultaneous diagonal
stability of a pair of positive linear systems // Linear Algebra
and its Applications.  2006.
 Vol.~413.  P.~13--23.




14. {\it Aleksandrov A., Mason O.} Diagonal stability of a class
of discrete-time positive switched systems with delay
// IET Control Theory \& Applications. 2018. Vol.~12, N~6. P.~812--818.






 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^


15. {\it  Shorten R.,  Narendra K.} On a theorem of Redheffer
concerning diagonal stability // Linear Algebra and its
Applications. 2009. Vol.~431. P.~2317--2329.

16. {\it Kraaijevanger J. F. B.} A characterisation of Lyapunov
diagonal stability using Hadamard products // Linear Algebra and
its Applications. 1991. Vol.~151. P.~245--254.

17. {\it  Александров А. Ю. } Об абсолютной устойчивости одной
нелинейной системы дифферен\-циаль\-ных уравнений //  Труды
Всерос. науч. конференции <<Математическое   моделирование
и~крае\-вые задачи>>. Самара, 26--28  мая 2004 г.   Ч.~3.
%Дифференциальные уравнения и~краевые задачи,
Самара: СамГТУ,  2004. С.~13--15.

18. {\it Mason O.} Diagonal Riccati stability and positive
time-delay systems // Systems and Control Letters. 2012. Vol.~61.
%No. 1.
P.~6--10.

19. {\it  Aleksandrov A., Mason O.} Diagonal Riccati stability and
applications // Linear Algebra and its Applications.  2016.
 Vol.~492.  P.~38--51.

20. {\it Aleksandrov A., Mason O., Vorob'eva A.} Diagonal Riccati
stability and the Hadamard product // Linear Algebra and its
Applications. 2017. Vol.~534. P.~158--173.










21. {\it Александров А. Ю., Воробьева А. А.} Построение
функционалов Ляпунова---Красовского для одного класса нелинейных
систем с~запаздыванием // Процессы управления и~устойчивость.
2015. T. 2 (18), №~1. С.~17--22.

22. {\it Красовский Н.~Н.} О~применении второго метода Ляпунова
для уравнений с~запаздыванием времени
 // Прикл. математика и~механика.   1956. Т. 20. Вып.~3. C.~315--327.



23. {\it Мишина А. П., Проскуряков И. В.} Высшая алгебра.  М.:
Наука, 1965. 300~c.

24. {\it Britton N. F.} Essential mathematical biology. London;
Berlin; Heidelberg: Springer,  2003. 335~p. \indent25. {\it  Hale
J. K., Verduyn Lunel S. M.} Introduction to functional
differential equations. New York: Springer-Verlag, 1993. 458~p.

26. {\it Argunov A. V., Safronov V. M.} Demographic structure of
siberian roe deer ({\it Capreolus pygargus} pall.) population in
central Yakutia // Russian Journal of Ecology.   2013.   Vol.~44,
N~5.   P.~402--407.





27. {\it Gallagher B. K., Secor D. H.} Intensified environmental
and density-dependent regulation of white perch recruitment after
an ecosystem shift in the Hudson river estuary // Canadian Journal
of Fisheries and Aquatic Sciences.   2018. Vol.~75,   N~1.
P.~36--46.


28.  {\it  Novikov E. A.,  Panov V. V.,  Moshkin M. P.}
Density-dependent regulation in populations of red-backed voles
({\it Myodes rutilus}) in optimal and suboptimal habitats of
south-west Siberia // Biology Bulletin Reviews.  2012.  Vol.~73,
N~1. P.~49--58.

29. {\it Volkov S. V., Sharikov A. V., Basova V. B., Grinchenko O.
S.} Influence of small mammals abundance on the number and
selection of habitats by long-eared ({\it Asio otus}) and
short-eared ({\it Asio flammeus}) owls // Entomological Review.
2009.  Vol. 88,   N~10.   P.~1248--1257.



30. {\it Кожечкин В. В., Кельберг Г. В.} Влияние волка на
изменение структуры популяции марала ({\it Cevus tlaphus
sibiricus} sev) на территории заповедника Столбы // Труды
Тигирекского заповедника.   2005.   № 1.   С.~307--310.

%Базаров М.И. Распределение и~вертикальные суточные миграции рыб озера Таймыр // Биология внутренних вод.   2007.   № 4.   С. 62-69.


%Ярыш В. Л., Антонец Н. В., Балалаев А. К., Иванов С. П. Динамика численности косули европейской, зайца русака, и~хищничество горно-крымской лисицы в~Карадагском природном заповеднике // Экосистемы, их оптимизация и~охрана. 2014. Вып. 11. С. 131-137.

31.    {\it Sheremetev I. S., Rozenfeld S. B., Sipko T. P.,
Gruzdev A. R.}
 Extinction of large herbivore mammals: niche characteristics of musk ox
{\it Ovibos moschatus} and reindeer {\it Rangifer tarandus}
coexisting in isolation // Biology Bulletin Reviews. 2014.
Vol.~75, N~1. P. 62--73.




\vskip 1.5mm


\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

\vskip 1.5mm

\noindent Статья поступила в~редакцию 30 января 2018 г.; принята
к~печати 15 марта 2018~г.


\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Александров Александр Юрьевич}~--- докт.
физ.-мат. наук, профессор; a.u.aleksandrov@spbu.ru

\vskip2mm \textit{Воробьева Анна Алексеевна}~--- магистрант;
st012486@student.spbu.ru

\vskip2mm \textit{Колпак Евгений Петрович}~--- докт. физ.-мат.
наук, профессор; petrovich\_pmpu@mail.ru





}
