
{\normalsize

\vskip 6mm

\noindent{\bf On  the diagonal stability of some classes of
complex systems}

}

\vskip 1.5mm

{\small

\noindent{\it A. Yu. Aleksandrov, A. A. Vorob'eva, E. P. Kolpak}

\vskip 1.5mm

{\footnotesize \noindent St.\,Petersburg State University, 7--9,
Universitetskaya nab., St.\,Petersburg, 199034, Russian Federation

}

\vskip3mm

\noindent \textbf{For citation:}  Aleksandrov A. Yu., Vorob'eva A.
A., Kolpak E. P. On  the diagonal stability of some classes of
complex systems. {\it Vestnik of Saint~Petersburg University.
App-\linebreak lied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01

\vskip3mm

{\leftskip=7mm\noindent The paper deals with the problem of
diagonal stability of nonlinear difference-differential systems.
Certain classes of complex systems with delay and nonlinearities
of a sector type are studied. It is assumed that these systems
describe the interaction of two-dimensional blockswith a delay in
connections between the blocks. Two kinds of structure of
connections are investigated. For every kind, necessary and
sufficient conditions for the existence of diagonal
Lyapunov---Krasovskii functionals are found. The existence of such
functionals guarantees the asymptotic stability of the zero
solutions of considered systems for any nonnegative delay and any
admissible nonlinearities. These conditions are formulated in
terms of the Hurwitz property of specially constructed Metzler
matrices. The proposed approaches are used for the stability
analysis ofsome models of population dynamics. Generalized
Lotka---Volterra models composed of several interacting pairs of
predator-prey type are investigated. With the aid of the Lyapunov
direct method and diagonal Lyapunov---Krasovskii functionals,
conditions are derived under which equilibrium positions of the
considered models are globally asymptotically stable in the
positive orthant of the state space for any nonnegative delay. An
illustrative example and results of the numerical simulation are
presented
to demonstrate the effectiveness of the developed approaches.\\[1mm]
\textit{Keywords}: diagonal stability, complex system, delay,
population dynamics, Lyapunov---Krasovskii functional.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. { Kaszkurewicz E., Bhaya A.} {\it Matrix diagonal stability in
systems and computation.} Boston, Basel, Berlin, Birkhauser Press,
1999, 267~p.

2. {Pykh Yu. A.} {\it Ravnovesie i ustojchivost' v modeljah
populjacionnoj dinamiki} [{\it Equilibrium and stability in models
of population dynamics}]. Moscow, Nauka Publ., 1983, 182~p. (In
Russian)

3. {  Berman A.,  Plemmons R. J.} {\it Nonnegative matrices in the
mathematical sciences.}  Philadelphia, SIAM,  1987, 361~p.


4. { Barker G. P.,  Berman A.,   Plemmons R. J.}
  Positive diagonal solutions to the Lyapunov equations.
 {\it Linear and Multilinear Algebra}, 1978, vol.~5, no.~4, pp. 249--256.

5. {\it Metod vektornyh funkcij Ljapunova v teorii ustojchivosti}
[{\it Method of vector Lyapunov
functions\linebreak\newpage\noindent in stability theory}]. Ed. by
A. A. Voronov, V. M. Matrosov. Moscow, Nauka Publ., 1987, 312~p.
(In Russian)



6. {  Sontag E. D.} Passivity gains and the ``secant condition''
for stability.  {\it Systems and Control Letters}, 2006, vol.~55,
pp.~177--183.



7. {Podval'nyi S. L., Provotorov V. V.}  {Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe}
[Start control of a parabolic system with distributed parameters
on a graph]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer Science. Control
Processes},  2015, iss.~3, pp.~126--142. (In Russian)


8. {Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A.}
Unique weak solvability of a nonlinear initial boundary value
problem with distributed parameters in a netlike domain. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes},  2017, vol.~13, iss.~3,
pp.~264--277. DOI: 10.21638/11701/spbu10.2017.304











9. {Hofbauer J., Sigmund K.} {\it Evolutionary games and
population dynamics.} Cambridge, Cambridge University Press, 1998,
323~p.





10. {Aleksandrov A. Yu.,  Aleksandrova E. B.,  Platonov A. V.}
 Ultimate boundedness conditions for a hybrid model of population dynamics.
{\it Proc. 21st Mediterranean conference on Control and
Automation},  June 25---28, 2013. Platanias-Chania, Crite,
Greece, 2013, pp.~622--627.



11. { Shorten R., Narenda K. S.}
 On the diagonal stability of a class of almost positive
switched systems. {\it Proc. American Control Conference},  June
30---July 02, 2010. Marriott Waterfront, Baltimore, MD, USA, 2010,
pp.~6250--6255.


12. {Arcat M., Sontag E.} Diagonal stability of a class of cyclic
systems and its connection with the secant criterion. {\it
Automatica}, 2006, vol.~42, no.~9, pp.~1531--1537.



13. {  Mason O., Shorten R.} On the simultaneous diagonal
stability of a pair of positive linear systems. {\it Linear
Algebra and its Applications},  2006,
 vol.~413,  pp.~13--23.




14. { Aleksandrov A., Mason O.} Diagonal stability of a class of
discrete-time positive switched systems with delay. {\it IET
Control Theory $\&$ Applications}, 2018, vol.~12, no.~6,
pp.~812--818.






 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^


15. {  Shorten R.,  Narendra K.} On a theorem of Redheffer
concerning diagonal stability. {\it Linear Algebra and its
Applications}, 2009, vol.~431, pp.~2317--2329.

16. {Kraaijevanger J. F. B.} A characterisation of Lyapunov
diagonal stability using Hadamard products. {\it Linear Algebra
and its Applications}, 1991, vol.~151, pp.~245--254.

17. { Aleksandrov A. Yu.} Ob absoljutnoj ustojchivosti odnoj
nelinejnoj sistemy differencial'nyh uravnenij [{On the absolute
stability of a nonlinear system of differential equations}]. {\it
Proc. of All-Russian scientific conference ``Mathematical Modeling
and Boundary-Value Problems''},
 Samara, May 26---28, 2004,   pt~3.
Samara, SamGU Publ.,  2004, pp.~13--15. (In Russian)

18. {Mason O.} Diagonal Riccati stability and positive time-delay
systems.
{\it Systems and Control Letters}, 2012, vol.~61, %No. 1.
pp.~6--10.

19. { Aleksandrov A., Mason O.} Diagonal Riccati stability and
applications. {\it Linear Algebra and its Applications},  2016,
 vol.~492,  pp.~38--51.

20. {Aleksandrov A., Mason O., Vorob'eva A.} Diagonal Riccati
stability and the Hadamard product. {\it Linear Algebra and its
Applications}, 2017, vol.~534, pp.~158--173.










21. {Aleksandrov A.,  Vorob'eva A.} Postroenie funkcionalov
Ljapunova---Krasovskogo dlja odnogo klassa nelinejnyh sistem s
zapazdyvaniem [Construction of Lyapunov---Krasovskii functionals
for a class of nonlinear systems with delay]. {\it Control
Processes and Stability},
 2015, vol. 2,  no.~1, pp.~17--22. (In Russian)

22. {Krasovskii N. N. } O primenenii vtorogo metoda Ljapunova dlja
uravnenij s zapazdyvaniem vremeni [On the application of the
second Lyapunov method for equations with time delay]. {\it
Applied Mathematics and Mechanics},   1956, vol. 20, iss.~3,
pp.~315--327. (In Russian)



23. {Mishina A. P., Proskuryakov I. V.}  {\it Vysshaja algebra }
[{\it Higher algebra}]. Moscow, Nauka Publ., 1965, 300~p.  (In
Russian)

24. { Britton N. F.} {\it Essential mathematical biology}. London,
Berlin, Heidelberg, Springer Press,  2003, 335~p.

25. { Hale J. K.,  Verduyn Lunel S. M.} {\it Introduction to
functional differential   equations}. New York, Springer-Verlag,
1993, 458~p.

26. {Argunov A. V., Safronov V. M.} Demographic structure of
siberian roe deer ({\it Capreolus pygargus} pall.) population in
central Yakutia. {\it Russian Journal of Ecology},   2013,
vol.~44,    no.~5,   pp.~402--407.





27. {Gallagher B. K., Secor D. H.} Intensified environmental and
density-dependent regulation of white perch recruitment after an
ecosystem shift in the Hudson river estuary. {\it Canadian Journal
of Fisheries and Aquatic Sciences},
 2018,  vol.~75,   no.~1, pp.~36--46.


28.  { Novikov E. A.,  Panov V. V.,  Moshkin M. P.}
Density-dependent regulation in populations of red-backed voles
({\it Myodes rutilus}) in optimal and suboptimal habitats of
south-west Siberia. {\it Biology Bulletin Reviews},  2012,
vol.~73,   no.~1, pp.~49--58.

29. {Volkov S. V., Sharikov A. V., Basova V. B., Grinchenko O. S.}
Influence of small mammals\linebreak\newpage\noindent abundance on
the number and selection of habitats by long-eared ({\it Asio
otus}) and short-eared ({\it Asio flammeus}) owls. {\it
Entomological Review},  2009,  vol. 88, no.~10,   pp.~1248--1257.



30. {Kozhechkin V. V., Kel'berg G. V.} Vlijanie volka na izmenenie
struktury populjacii marala ({\it Cevus tlaphus sibiricus} sev) na
territorii zapovednika Stolby
 [Influence of the wolf on the change in the structure of the maral
population ({\it Cevus tlaphus sibiricus} sev) in the territory of
the Stolby reserve].  {\it Proceedings of the Tigirek Reserve},
2005,   no.~1,    pp.~307--310. (In Russian)

%Базаров М.И. Распределение и вертикальные суточные миграции рыб озера Таймыр // Биология внутренних вод.   2007.   № 4.   С. 62-69.


%Ярыш В. Л., Антонец Н. В., Балалаев А. К., Иванов С. П. Динамика численности косули европейской, зайца русака, и хищничество горно-крымской лисицы в Карадагском природном заповеднике // Экосистемы, их оптимизация и охрана. 2014. Вып. 11. С. 131-137.

31.    {Sheremetev I. S., Rozenfeld S. B., Sipko T. P., Gruzdev A.
R.}
 Extinction of large herbivore mammals: niche characteristics of musk ox
{\it Ovibos moschatus} and reindeer {\it Rangifer tarandus}
coexisting in isolation. {\it Biology Bulletin Reviews}, 2014,
vol.~75, no.~1, pp. 62--73.




\vskip5mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm \textit{Aleksandrov Alexander Yu.}~--- Dr. Sci. in
physics and mathematics, professor; %\\
a.u.aleksandrov@spbu.ru


\vskip1.5mm \textit{Vorob'eva Anna A.}~--- master;
st012486@student.spbu.ru


\vskip1.5mm \textit{Kolpak  Eugeny P.}~--- Dr. Sci. in physics and
mathematics, professor; petrovich\_pmpu@mail.ru





}
