
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Almedia J. E., Rosetti R., Coelho A. L. {\it Crowd simulation
modeling applied to emergency and evacuation simulations using
multi-agent systems}. arXiv:1303.4692. 2013.\\ Available at:
https://arxiv.org/abs/1303.4692 (accessed: 20.11.2018).

2. Kuligowski E. D., Peacock R. D. {\it A review of building
evacuation models --- 100}. Bureau Dr. Gaithersburg, MD 20899,
USA, National Institute of Standards and Technology Publ., 2005,
Technical Note 1680.

3. Tissera P. C., Printista M., Errecalde M. L. Evacuation
simulations using cellular automata. {\it JCS$\&$T}, 2007, vol.~7,
no.~1, pp.~14--20.

4. Hamacher H. W., Tjandra S. A. Mathematical modeling of
evacuation problems: A state of the art. {\it Pedestrian and
Evacuation Dynamics}, 2002, no.~24, pp.~227--266.

5. Lao A., Tekomono K. {\it Multi exit configuration of mesoscopic
pedestrian simulation}. arXiv: 1609.01475. 2016. Available at:
https://arxiv.org/abs/1609.01475 (accessed: 22.11.2018).

6. Shi M., Wai Ming Lee E., Ma Y. A newly developed mesoscopic
model on simulating pedestrian flow. {\it Procedia Engineering},
2018, vol.~211, pp.~614--620.

7. Fleischer L., Skutella M. Quickest flows over time. {\it
Society for Industrial and Applied Mathematics}, 2007, vol.~36,
no.~6, pp.~1600--1630.

8. Lin M., Jaillet P. On the quickest flow problem in dynamic
networks --- A parametric min-cost flow approach. {\it Proceedings
of the Twenty-Sixth Annual ACM-SIAM Symposium on Discrete
Algorithms}. San Diego, CA, USA, 2015, pp.~1343--1356.

9. Arumugam G. P., Augustine J., Golin J. G. et al. {\it Optimal
evacuation flows on dynamic paths with general edge capacities}.
arXiv:1606.07208v1 [cs.DS]. 2016. Available at:
https://arxiv.org/abs/1606.07208 (accessed: 02.03.2017).

10. Malodushev S. V., Rogov A. A. Determination of locations in
corporate Wi--Fi networks. Series {\it Mathematical Modelling,
Programming $\&$ Computer Software}, {\it Bulletin of the South
Ural State University}. 2016, vol.~9, no.~1, pp.~92--104.

11. Voronov R. V. The fault-tolerant metric dimension of the
king's graph. {\it Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~3, pp.~241--249.

12. Ford L. R., Fulkerson D. R. Constructing maximal dynamic flows
from static flows. {\it Operations Research}, 1958, vol.~6, no.~3,
pp.~419--433.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent
Received:  April 19, 2019.

Accepted: June 06, 2019.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Sergei V. Malodushev} --- PhD Sci. in
Engineering; svm@petrsu.ru

\vskip2mm\textit{Aleksandr A. Rogov}  --- Dr. Sci. in Engineering,
Professor; rogov@petrs.ru

\vskip2mm\textit{Roman V. Voronov} ---  Dr. Sci. in Engineering,
Associate Professor; rvoronov76@gmail.com

}
