
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Dyer M., Mohanaraj V.} Pairwise-interaction games //
{ICALP}. 2011. Vol.~1. P.~159--170.

2. \textit{Acemoglua D., Ozdaglarb A., Parandeh Gheibib A.} Spread
of (mis)information in social networks // {Games and Economic
Behavior}. 2010. Vol.~70, iss.~2. P.~194--227.

3. \textit{K\"onig M. D.,  Battistonb S.,  Napoletanoc M.,
Schweitzerb F.} The efficiency and stability of R$\, \& \,$D
networks // {Games and Economic Behavior}. 2012. Vol.~75, iss.~2.
P.~694--713.

4. \textit{Петросян Л. A.,  Седаков  A. A.} Многошаговые сетевые
игры с~полной информацией // {Математическая теория игр и~ее
приложения}. 2009. Т.~1, №~2. С.~66--81.

5. \textit{Bulgakova M. A.,  Petrosyan L. A.} About strongly
time-consistency of core in the network game with pairwise
interactions // {Proceedings of 2016 Intern. Conference
``Stability and Oscillations of Nonlinear Control Systems''}.
2016. P.~157--160.

6. \textit{Kuzyutin D.,  Nikitina M.} Time consistent cooperative
solutions for multistage games with vector payoffs // {Operations
Research Letters}. 2017. Vol.~45, iss.~3. P.~269--274.

7. \textit{Shapley L. S.}  Cores of convex games // {Intern.
Journal of Game Theory}. 1971. Vol.~1. P.~11--26.

8. \textit{Shapley L. S.} A value for $n$-person games //
Contributions to the theory of games. Vol. II / eds by H.~W.~Kuhn,
A.~W.~Tucker. Princeton: Princeton University Press, 1953.
Vol.~28. P.~307--317. ({An\-nals of Mathematical Studies})

9. \textit{Petrosyan L., Bulgakova M., Sedakov A.} Time-consistent
solutions for two-stage network games with pairwise interactions
// {Game Theory for Networking Applications}. 2018. P.~15--23.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 8 мая 2017 г.

Cтатья принята к~печати 18 декабря 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Булгакова Мария Александровна}  --- аспирант;
 mari$\underline{}$bulgakova@mail.ru

}
