
{\normalsize

\vskip 6mm

\noindent{\bf Solutions of network games with pairwise
interactions$\,^*$}

}

\vskip 1.5mm

{\small

\noindent{\it М. А. Bulgakova%$\,^1$%
%, N. L. Grebennikova$\,^2$%
%, K. Yu. Staroverova$\,^1$%
%, I.~О. Famylia%$\,^2$%
} %
\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ The work is supported by Russian Found of
Fundamental Research  (grant  N~17-51-53030).\par
%
}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\efootnote{
%%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by the Ministry of
%Science and Higher Education of the Russian Federation  in the
%framework of Federal Targeted Program ``Research and Development
%in the Priority Directions of Development of the Scientific and
%Technological Complex of Russia for 2014--2020'' (agreement on
%November 24, 2017 no.~14.616.21.0088, RFMEFI61617X0088
%identifier).\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%
%}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Bulgakova M. A. Solutions of
network games with pairwise interactions. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~15, iss.~\issuenum,
pp.~\pageref{p12}--\pageref{p12e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum12  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent This article is devoted to cooperative network
games with pairwise interaction. We consider a two-stage game, the first
stage of which represents a network-formation stage, and the second
is simultaneous bimatrix games, which take place between neighbours
over the network. The characteristic function is constructed, its
supermodularity is proved for the case of a one-step subgame starting
with the second stage. For a special class of networks (star-network),
a simplified formula for the Shapley vector is found, which does not
require the calculation of the values of the characteristic function
over all coalitions, but only over coalitions of dimension no more than two.\\[1mm]
\textit{Keywords}: cooperative games, convexity, Shapley value,
characteristic function.
\par}

\vskip 5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize


1. Dyer M., Mohanaraj V. Pairwise-interaction games.
\textit{ICALP}, 2011, vol.~1, pp.~159--170.

2. Acemoglua D., Ozdaglarb A., Parandeh Gheibib A. Spread of
(mis)information in social networks.  \textit{Games and Economic
Behavior}, 2010, vol.~70, iss.~2, pp.~194--227.

3. K\"onig M. D.,  Battistonb S.,  Napoletanoc M., Schweitzerb F.
The efficiency and stability of R$\, \& \,$D networks.
\textit{Games and Economic Behavior}, 2012, vol.~75, iss.~2,
pp.~694--713.

4. Petrosyan L. A.,  Sedakov  A. A.  Mnogoshagovye setevye igry
s~polnoy informatsiey   [Multistage network games with full
information]. \textit{Matematicheskaia teoria igr i ee
prilozhenia} [\textit{Мathematical game theory and applications}],
2009, vol.~1, no.~2, pp.~66--81. (In Russian)

5. Bulgakova M. A.,  Petrosyan L. A. About strongly
time-consistency of core in the network game with pairwise
interactions. \textit{Proceedings of 2016 Intern. Conference
``Stability and Oscillations of Nonlinear Control Systems''},
2016, pp.~157--160.

6. Kuzyutin D.,  Nikitina M. Time consistent cooperative solutions
for multistage games with vector payoffs. \textit{Operations
Research Letters}, 2017, vol.~45, iss.~3, pp.~269--274.

7. Shapley L. S.  Cores of convex games. \textit{Intern. Journal
of Game Theory}, 1971, vol.~1, pp.~11--26.

8. Shapley L. S. A value for $n$-person games. {\it Contributions
to the theory of games}, vol. II. Eds by H.~W.~Kuhn, A.~W.~Tucker.
Princeton, Princeton University Press, 1953, vol.~28,
pp.~307--317. ({Annals of Mathematical Studies})

9. Petrosyan L., Bulgakova M., Sedakov A. Time-consistent
solutions for two-stage network games with pairwise interactions.
\textit{Game Theory for Networking Applications}, 2018,
pp.~15--23.

\vskip 1.5mm

Received:  May 8, 2018.

Accepted: December 18, 2018.


\vskip5mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm \textit{Maria A. Bulgakova} --- Postgraduate Student;
mari$\underline{}$bulgakova@mail.ru\par
%

}
