

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1.  Kurbatova~G.~I.,  Popova~E.~A.,  Filippov~ B.~V.
\textit{Modeli morskih gazoprovodov} [\textit{Models of sea
gas-pipelines}]. Saint Petersburg, Saint Petersburg University
Publ.,  2005, 156~p. (In Russian)

2.  Ermolaeva N.~N., Kurbatova G.~I. Analiz podhodov k
modelirovaniju termodinamicheskih processovv v gazah pri visokih
davlenijah [The analysis of the approaches to the modeling of
thermodynamic processes in gas flow at hyperpressure].
\textit{Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer science. Control processes}, 2013, issue~1,
pp.~35--45. (In Russian)


3.  Reid  C., Prausnitz  M., Sherwood  K. \textit{The properties
of gases and liquids.} New  York, Saint~Louis, San Francisco,
MeGraw---Hill  Book  Company Publ., 1977, 688~p.


4. Vasilev~F.~P. O metode konechnih raznostej dlja reshenija
odnofaznoj zadachi Stefana [On finite difference methods for the
solution of Stefan's single-phase problem]. \textit{Zh. Vychisl.
Mat. Mat. Fiz.},    1963, vol.~3, no.~5, pp.~861--873. (In
Russian)

5.  Ermolaeva N.~N., Kurbatova G.~I. Kvasiodnomernaja
nestacionarnaja model processov v morskih gasoprovodah
[Quasione-dimensional non-stationary model of processes in a sea
gas-pipeline]. \emph{Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer science. Control
processes}, 2015, issue~3, pp.~55--66. (In Russian)\newpage

6. Roach~P.~J. \textit{Computational Fluid Dynamics}. Albuquerque,
Hermosa Publ., 1976, 618~p. (Russ ed.: Roach~P.~J.
\emph{V'ichislitelnaja gidrodinamika}. Moskow, Mir Publ., 1980,
616~p.)


\vskip 2mm

{\bf For citation:} Ermolaeva N. N. Computer modelling of the sea
GAS-pipeline glaciation and of the flow characteristics behavior
in unsteady regimes. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
