
{\small

\vskip4%6
mm \noindent \textbf{Литература}

}

\vskip1.8%3
mm

{\footnotesize

1. \textit{Gabor~В.} A new microscope principle~// Nature. 1948. N~161. P.~777--778.

2. \textit{Fink~H.-W.}, \textit{Stocker~W.}, \textit{Schmid~H.} Holography with low-energy electrons~// Phys. Rev. Lett. 1990. Vol.~65. N~10. P.~1204--1206.

3. \textit{Egorov~N.~V.}, \textit{Karpov~A.~G.}, \textit{Antonova~L.~I.}, \textit{Fedorov~A.~G.}, \textit{Tro\-fi\-mov~V.~V.} Technique for investigating the spatial structure of thin films at a nanolevel~// Journal of Surface Investigation: $X$-Ray, Synchrotron and Neutron Techniques. 2011. Vol.~5. N~5. P.~992--995.

4. \textit{Карпов~А.~Г.}, \textit{Трофимов~В.~В.}, \textit{Федоров~А.~Г.} Информационное обеспечение и программная поддержка анализа и обработки голографической информации~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2021. Т.~17. Вып.~4. С.~409--418. https://doi.org/10.21638/11701/spbu10.2021.409

5. \textit{Goodman~J.~W.} Introduction to Fourier optics. Second ed. New York: The McGraw-Hill Com\-pa\-nies, 1988. 457~p.

6. \textit{Schmidt~J.~W.} Numerical simulation of optical wave propagation with examples in MATLAB. Bellingham: SPIE, 2010. P.~133--146.

7. \textit{Schnars~U.}, \textit{Juptner~W.~P.~O.} Digital recording and numerical reconstruction of holograms~// Meas. Sci. Technol. 2002. Vol.~13. P.~85--101.

8. \textit{Latychevskaia~T.} Practical algorithms for simulation and reconstruction of digital in-line holograms~// Applied Optics. 2015. Vol.~54. P.~2424--2434.

9. \textit{Molony~K.~M.}, \textit{Hennelly~B.~M.}, \textit{Kelly~D.~P.}, \textit{Naughton~T.~J.} Reconstruction algorithms applied to in-line Gabor digital holographic microscopy~// Optics Communications. 2010. Vol.~283. P.~903--909.

10. \textit{Kreis~T.~M.}, \textit{Juptner~W.~P.~O.} Suppression of the dc term in digital holography~// Optical Engineering. 1997. Vol.~36. P.~2357--2360.

11. \textit{Latychevskaia~T.}, \textit{Fink~H.-W.} Solution to the Twin Image Problem in holography~// Phys. Rev. Lett. 2007. Vol.~98. N~233901.

12. \textit{Ersoy~O.~K.} Diffraction, Fourier optics, and imaging. New Jersey: John Wiley and Sons Inc., 2007. 429~p.

13. \textit{Voelz~D.~G.} Computational Fourier optics: a MATLAB tutorial.  Bellingham: SPIE, 2010. P.~199--205.

14. \textit{Schmidt~J.~D.} Numerical simulation of optical wave propagation with examples in MATLAB. Bellingham: SPIE, 2010. P.~115--130.

15. \textit{Kim~M.~K.} Principles and techniques of digital holographic microscopy~// SPIE. 2010. Vol.~1. N~018005(50).


%\pagebreak
\vskip 1.2mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 октября 2021~г.

Cтатья принята к~печати 1 февраля 2022~г.

\vskip4%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:


\vskip1.5 mm \textit{Федоров Артур Григорьевич} --- канд. техн. наук, доц.; ag.fedorov@s-vfu.ru \par%


\vskip1.5 mm \textit{Трофимов Василий Валерьевич} --- ст. преп.; v.v.trofimov@spbu.ru \par%


\vskip1.5 mm \textit{Карпов Андрей Геннадьевич} --- д-р техн. наук, проф.; a.g.karpov@spbu.ru \par%
%
}
