
{\normalsize

\vskip 6
mm

\noindent{\bf Numerical methods and algorithms for reconstruction of holographic images\\ with an flexibility choice of physical size of the object and observation area%$^{*}$%
 }

}

\vskip 2mm

{\small

\noindent{\it A.~G.~Fedorov$^{1,2}$, V.~V.~Trofimov$^1$, A.~G.~Karpov$^1$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work  was supported by the Russian Foundation %for Basic Research (project N 20-07-0108).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St\,Petersburg State University, 7--9, Universitetskaya nab.,
St\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation


\noindent%
$^2$~%
M. K. Ammosov North-Eastern Federal University,
58, ul. Belinskogo, Yakutsk,

\noindent%
\hskip2.45mm%
Republic of Sakha (Yakutia), 677027, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Fedorov~A.~G., Trofimov~V.~V., Karpov~A.~G.   Numerical methods and algorithms for reconstruction of holographic images with an flexibility choice of physical size of the object and observation area.
{\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p8}--\pageref{p8e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08 (In Russian)

\vskip2mm

{\leftskip=7mm\noindent Within the framework of this work, the numerical results of simulation and reconstruction of holographic images with different physical sizes of the object and observation areas are presented. Simple and practical approaches to relatively flexibility choice of physical areas (e.~g., units of $m^2$) in both planes are proposed. Algorithms are presented in the case when the dimensions of the plane of the object and observation coincide. Two-step scattering algorithms are presented for the simulation and reconstruction of holographic images with a relatively flexibility choice of the physical areas of the object plane and observation.\\[1mm]
\textit{Keywords}: electron holography, digital image processing, Fourier transform, Fresnel method, angular spectrum method.\par}


\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Gabor~В. A new microscope principle. {\it Nature}, 1948, no.~161, pp.~777--778.

2. Fink~H.-W., Stocker~W., Schmid~H. Holography with low-energy electrons. {\it Phys. Rev. Lett.}, 1990, vol.~65, no.~10, pp.~1204--1206.

3. Egorov~N.~V., Karpov~A.~G., Antonova~L.~I., Fedorov~A.~G., Trofimov~V.~V. Technique for investigating the spatial structure of thin films at a nanolevel. \textit{Journal of Surface Investigation: X-Ray, Synchrotron and Neutron Techniques}, 2011, vol.~5, no.~5, pp.~992--995.

4. Karpov~A.~G., Trofimov~V.~V., Fedorov~A.~G. Informacionnoe obespechen'e i programmnaya podderjka analiza i obrabotki golograficheskoy informacii [Information and program support of the analysis and processing of holographic information]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Process}, 2021, vol.~17, iss.~4, pp.~409--418.\\ https://doi.org/10.21638/11701/spbu10.2021.409 (In Russian)

5. Goodman~J.~W. \textit{Introduction to Fourier optics}. $2^{\rm nd}$~ed. New York, The McGraw-Hill Companies Publ., 1988, 457~p.

6. Schmidt~J.~W. \textit{Numerical simulation of optical wave propagation with examples in MATLAB}.   Bellingham, SPIE Publ., 2010, pp.~133--146.

7. Schnars~U., Juptner~W.~P.~O. Digital recording and numerical reconstruction of holograms. \textit{Meas. Sci. Technol.}, 2002, vol.~13, pp.~85--101.

8. Latychevskaia~T. Practical algorithms for simulation and reconstruction of digital in-line holograms. \textit{Applied Optics}, 2015,  vol.~54, pp.~2424--2434.

9. Molony~K.~M., Hennelly~B.~M., Kelly~D.~P., Naughton~T.~J. Reconstruction algorithms applied to in-line Gabor digital holographic microscopy. \textit{Optics Communications}, 2010, vol.~283, pp.~903--909.

10. Kreis~T.~M., Juptner~W.~P.~O. Suppression of the dc term in digital holography. \textit{Optical Engineering}, 1997, vol.~36,  pp.~2357--2360.

11. Latychevskaia~T., Fink~H.-W. Solution to the Twin Image Problem in holography. \textit{Phys. Rev. Lett.}, 2007, vol.~98, no.~233901.

12. Ersoy~O.~K. \textit{Diffraction, Fourier optics, and imaging}. New Jersey, John Wiley and Sons Inc. Press, 2007, 429~p.

13. Voelz~D.~G. \textit{Computational Fourier optics: a MATLAB tutorial}. Bellingham, SPIE Publ., 2010, pp.~199--205.

14. Schmidt~J.~D. \textit{Numerical simulation of optical wave propagation with examples in MATLAB}. Bellingham, SPIE Publ., 2010, pp.~115--130.

15. Kim~M.~K. Principles and techniques of digital holographic microscopy. \textit{SPIE}, 2010, vol.~1, no.~018005(50).


\vskip1.5mm Received:  October 02, 2021.

Accepted: February 01, 2022.


\vskip6mm A\,u\,t\,h\,o\,r\,s'\,  i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%


\vskip1.5mm \textit{Arthur G. Fedorov} --- PhD in Engineering, Associate Professor; ag.fedorov@s-vfu.ru \par%
%
\vskip1.5mm \textit{Vasiliy V. Trofimov} --- Senior Lecturer; v.v.trofimov@spbu.ru \par%
%
\vskip1.5mm \textit{Andrey G. Karpov} --- Dr. Sci. in Engineering, Professor; a.g.karpov@spbu.ru \par%
%
}
