{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Vedernikov V. V. Vlijanie kapilljarnogo podnjatija na
fil'traciju iz kanalov [Influence of capillary rise in the
filtration channel]. \textit{Gidrotehnicheskoe stroitel'stvo
$[$Hydraulic engineering$]$}, 1935, no.~5, pp.~20--27. (In
Russian)\newpage

2. Vedernikov V. V. Vlijanie kapilljarnosti grunta na fil'traciju
so svobodnoj poverhnost'ju [Effect of soil capillary filtration
with free surface]. \textit{Dokl. SSSR $[$Papers of Academy of
Sciences USSR$]$}, 1936, vol.~3(4), pp.~157--161. (In Russian)

3. Aravin V. I. Pritok gruntovyh vod k kotlovanu, ograzhdennomu
shpuntami [The inflow of groundwater to the trenches, fences
tongue]. \textit{Izvestia VNIIG $[$Proceeding Izvestia VNIIG$]$},
1937, vol.~20, pp.~74--89. (In Russian)

4. Kozlov V. S. Gidromehanicheskij raschet shpuntovyh peremychek
[Hydromechanical calculation sheet jumpers]. \textit{Izvestia
SSSR. OTH $[$Proceeding of USSR. OTN$]$}, 1939, no.~6,
pp.~89--110. (In Russian)

5. Vedernikov V. V. \textit{Teorija fil'tracii i ee primenenie v
oblasti irrigacii i drenazha} [{\it Filtration theory and its
application in the field of irrigation and drainage}]. Moscow;
Leningrad, Gosstroyizdat Publ., 1939, 248~p. (In Russian)

6. Nelson-Skvornyakov F. B. Gidromehanicheskij raschet protekanija
vody k kotlovanu [Hydro water flow calculation to the trench].
\textit{Izvestia SSSR. OTH $[$Proceeding of USSR. OTN$]$}, 1943,
vol.~7, pp.~90--94. (In Russian)

7. Nelson-Skvornyakov F. B. Nekotorye sluchai pritekanija
gruntovoj vody iz reki k kar'eru (kotlovanu)  [Hydro water flow
calculation to the trench]. \textit{Izvestia SSSR. OTH
$[$Proceeding of USSR. OTN$]$}, 1943, vol.~7, pp.~90--94. (In
Russian)

8. Nelson-Skvornyakov F. B. \textit{Fil'tracija v odnorodnoj
srede} [{\it Filtration in a homogeneous medium}]. 2-e ed. Moscow,
Soviet science Publ., 1949, 568~p. (In Russian)

9. Aravin V. I., Numerov S. N. \textit{Fil'tracionnye raschety
gidrotehnicheskih sooruzhenij} [{\it Filtration calculations of
hydraulic structures}]. Moscow, Stroyizdat Publ., 1948, 616~p. (In
Russian)

10. Vedernikov V. V. Fil'tracija pri nalichii drenirujushhego ili
vodonosnogo sloja [Filtering in the presence of drainage or
water-bearing layer]. \textit{Dokl. AN~SSSR $[$Papers of Academy
of Sciences USSR$]$}, 1949, vol.~69, no.~5, pp.~619--622. (In
Russian)

11. Aptekar L. D. Voprosy fil'tracionnogo rascheta gorizontal'nogo
drenazha sudohodnyh shljuzov i suhih dokov [Questions filtration
calculation of horizontal drainage shipping locks and dry docks].
\textit{Izvestia VNIIG $[$Proceeding Izvestia VNIIG$]$}, 1951,
vol.~46, pp.~80--105. (In Russian)

12. Polubarinova-Kochina P. Y. \textit{Teorija dvizhenija
gruntovyh vod} [\textit{Theory of movement of groundwater}]. 2nd
ed. Moscow, Nauka Publ., 1977, 664~p. (In Russian)

13. \textit{Razvitie issledovanij po teorii fil'tracii v SSSR
$($1917--1967$)$} [\textit{Development of research on the theory
of filtration in the USSR $($1917--1967$)$}]. Otv. red.
P.~Y.~Po\-lu\-ba\-ri\-no\-va-Ko\-chi\-na. Moscow, Nauka Publ.,
1969, 546~p. (In Russian)

14. Djukovskii N. E. Prosachivanie vody cherez plotiny [Seepage of
water through the dam]. \textit{Collected works}. Moscow,
Gostehizdat Publ., 1950, vol.~7, pp.~297--332. (In Russian)

15. Bereslavskii E. N. O nekotoryh gidrodinamicheskih modeljah,
svjazannyh s zadachej Zhukovskogo ob obtekanii shpunta [About some
hydrodynamic schemes of flow around the rabbet of Zhukovsky].
\textit{Dokl. RAN $[$Papers of RAN$]$}, 2013, vol.~448, no.~5,
pp.~529--533. (In Russian)

16. Bereslavskii E. N., Kochina P. Y. O nekotoryh uravnenijah
klassa Fuksa v gidro- i ajeromehanike [About some classes of
equations of Fuchs in the hydro- and aeromechanics].
\textit{Izvestia AN SSSR. MJG} [\textit{Proceeding of AN USSR.
Fluid Dynamics}], 1992, no.~5, pp.~3--7. (In Russian)

17. Bereslavskii E. N., Kochina P. Y. O differencial'nyh
uravnenijah klassa Fuksa, vstrechajushhihsja v nekotoryh zadachah
mehaniki zhidkostej i gazov [Differential equations of Fuchs class
encountered some problems of mechanics of liquids and gases].
\textit{Izvestia AN SSSR. MJG $[$Proceeding of AM USSR. Fluid
Dynamics$]$}, 1997, no.~5, pp.~9--17. (In Russian)

18. Kochina N. N., Bereslavskii E. N., Kochina P. Y.
\textit{Analiticheskaja teorija linejnyh differencial'nyh
uravnenij klassa Fuksa i nekotorye zadachi podzemnoj
gidromehaniki} [{\it Analytical theory of linear differential
equations of the Fuchs class and some problems of underground
hydromechanics}]. Pt~1. Preprint 567. Moscow, Institute of Problem
in Mechanics RAN Publ., 1996, 112~p. (In Russian)

19. Bereslavskii E. N. O konformnom otobrazhenii nekotoryh
krugovyh mnogougol'nikov na prjamougol'nik [Conformal mapping of
some circular polygons on a rectangle]. \textit{Izvestia vuzov.
Matematika $[$Proceeding of Higher Education Institutions.
Mathematics$]$}, 1980, no.~5, pp.~3--7. (In Russian)

20. Bereslavskii E. N. O differencial'nyh uravnenijah klassa
Fuksa, svjazannyh s konformnym otobrazheniem krugovyh
mnogougol'nikov v poljarnyh setkah [Differential equations of
Fuchs class associated with the conformal mapping of circular
polygons in polar grids]. \textit{Differenc. uravnenija
$[$Differential Equations$]$}, 1997, vol.~33, no.~3. pp.~297--301.
(In Russian)

21. Bereslavskii E. N. O nekotoryh differencial'nyh uravnenijah
klassa Fuksa, vstrechajushhihsja v zadachah mehaniki zhidkostej i
gazov [On some differential equations class Fuchs, occurring in
problems of mechanics of liquids and gases]. \textit{Differenc.
uravnenija $[$Differential Equations$]$}, 2012, vol.~48, no.~4,
pp.~590--594. (In Russian)

22. Bereslavskii E. N. Primenenie metoda Polubarinovoj-Kochinoj
dlja issledovanija fil'tracionnyh techenij iz kotlovanov,
ograzhdennyh shpuntami Zhukovskogo [Application of
Polubarinova-Kochina to study seepage flows from the trenches,
fenced tongue Zhukovsky]. \textit{Dokl. RAN $[$Papers of Academy
of RAN$]$}, 2014, vol.~455, no.~6, pp.~651--655. (In Russian)

23. Golubev V. V. \textit{Lekcii po analiticheskoj teorii
differencial'nyh uravnenij} [\textit{Lectures on the analytic
theory of differential equations}]. Moscow, Leningrad, Gostehizdat
Publ., 1950, 436~p. (In Russian)

24. Bereslavskii E. N. Modelirovanie obtekanija shpunta
Zhukovskogo [Simulation flow tongue Zhukovsky]. \textit{Dokl. RAN
$[$Papers of Academy of RAN$]$}, 2011, vol.~440, no.~1,
pp.~47--51. (In Russian)

\vskip 2mm

{\bf For citation:}  Bereslavskii E. N.  Modeling the movement of
groundwater from the pits, sur-\linebreak rounded with piles of
Zhukovsky. {\it Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, \issueyear,
vol.~13, iss.~\issuenum, pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
