

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

{1}. Fossen~T.\:I. \textit{Guidance and Control of Ocean
Vehicles}. New York, John Wiley \& Sons Press, 1999, 480~p.

{2}. Perez~T. \textit{Ship Motion Control: Course Keeping and Roll
Stabilization using Rudder and Fins}. London, Springer–Verlag,
2005, 300~p.

{3}. Hammound~S. Ship Motion Control Using Multi-Controller
Structure. \textit{Journal of Maritime Research}, 2012,
vol.~IX(1),  pp.~45--52.

{4}.  Veremey~E., Korchanov~V., Korovkin~M., Pogozhev~S. {\it
Komp'juternoe modelirovanie sistem upravlenija dvizheniem morskih
podvizhnyh ob'ektov} [\textit{Computer modeling of motion control
systems for marine mobile objects}]. Saint Petersburg, Research
Institute of Chemistry of Saint Petersburg University Publ., 2002,
370~p. (In Russian)

{5}. Veremey~E. Sintez zakonov mnogocelevogo upravlenija
dvizheniem morskih ob'ektov [Synthesis of the laws of
multi-purpose control of the motion of marine objects]. {\it
Giroskopija i~navigacija} [\textit{Gyroscopy and navigation}],
2009, no.~4, pp.~3--14. (In Russian)

{6}. Veremey~E. Algoritmy reshenija odnogo klassa zadach
$H_\infty$-optimizacii sistem upravlenija [Algorithms for solving
one class of $H_\infty$-optimization problems for control
systems]. {\it Izv. RAN. Teorija i~sistemy upravlenija}
[\textit{Proceedings of the Russian Academy of Sciences. Theory
and systems  control}], 2011, no.~3, pp.~53--61. (In Russian)

{7}. Veremey~E. Optimization of filtering correctors for autopilot
control laws with special structures. \textit{Optimal Control
Applications and Methods}, 2016, vol.~37, iss.~2, pp.~345--348.

{8}. Veremey~E. Irregular $H_\infty$-optimization of control laws
for marine autopilots. \textit{Constructive Nonsmooth Analysis and
Related Topics (dedi-cated to the memory of V.\:F.~Demyanov)
(CNSA)}. Saint Petersburg, 2017 Intern. Conference,     IEEE
Conference Publ., 2017, pp.~345--348.

{9}. Doyle~J., Francis~B., Tannenbaum~A. \textit{Feedback control
theory}. New York, Macmillan Publ. Co., 1992, vol.~XI, 227~p.

{10}. Boyd~S., L.~El~Ghaoui, Feron~E., Balakrishnan~V.
\textit{Linear Matrix Inequalities in System and Control Theory}.
Philadelphia, SIAM, 1994, 193~p.

{11}. Veremey~E., Sotnikova~M. Spectral Approach to
$H_\infty$-Optimal SISO Synthesis Problem. \textit{WSEAS
Transactions on Systems and Control}, 2014, vol.~9, art.~43,
pp.~415--424.




\vskip 2mm

{\bf For citation:}  Wang~Í., Veremey~E.~I., Xue~Y. A method of
the guaranteeing optimization for\linebreak the dynamics of ship
moving in wave. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Com-\linebreak puter Science. Control
Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p2}--\pageref{p2e}. \doivyp/
spbu10.\issueyear.\issuenum02



}
