

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Kjetsaa G.
{\it Attributed to Dostoevsky: The problem of attributing to Dostoevsky anonymous articles in Time and Epoch}.
Oslo, Solum Forlag A. S. Publ., 1986, 82~p.

2. Batura T. V.
Formalnye metody opredeleniya avtorstva tekstov [Formal methods for determining the authorship of texts].
{\it Bulleten’ Novosibirskogo gosudarstvennogo universiteta. Seria informatsionniye tehnologii} [{\it Novosibirsk State University Bulletin. Series Information Technology}],
2012, vol.~10(4), pp.~81--94. (In Russian)

3. Lebedev A. A.
{\it Vvedenie v prikladnuyu lingvistiku} [{\it Introduction to applied linguistics}].
Pe\-tro\-za\-vodsk, Petrozavodsk State University Press, 2019, 48~p. (In Russian)

4. Malyutov M. B.
Obzor metodov i primerov atribucii tekstov [Overview of methods and examples of text attribution].
{\it Review of Applied and Industrial Mathematics}.
Moscow, 2005, vol.~12(1), pp.~41--78. (In Russian)

5. Rogov A. A., Sedov A. V., Sidorov Y. V., Surovceva T. G.
{\it Matematicheskie metody atribucii tekstov} [{\it Mathematical methods for text attribution}].
Petrozavodsk, Petrozavodsk State University Press, 2014, 96~p. (In Russian)

6. Calle-Martin J., Miranda-Garcia A.
Stylometry and authorship attribution: Introduction to the special issue.
{\it English Studies}, 2012, vol.~93(3), pp.~251--258.

7. Farringdon J. M.
{\it Analyzing for Authorship}.
Cardiff, University of Wales Press, 1996, 324~p.

8. Stamatatos E.
A survey of modern authorship attribution methods.
{\it Journal of the American Society for Information Science and Technology},
2009, vol.~60(3), pp.~538--556.

9. Kotov A. A., Mineeva Z. I., Rogov A. A., Sedov A. V., Sidorov Y. V.
{\it Lingvisticheskie korpusy} [{\it Linguistic corpuses}].
Petrozavodsk, Petrozavodsk State University Press, 2014, 140~p. (In Russian)

10. Sidorov G., Velasquez F., Stamatatos E., Gelbukh A., Chanona-Hern\'andez L.
Syntactic \textit{n}-grams as machine learning features for natural language processing.
{\it Expert Systems with Applications}, 2014, vol.~41(3), pp.~853--860.

11. Rogov A. A., Kulakov K. A., Moskin N. D.
Programmnaya podderzhka v reshenii zadachi atribucii tekstov
[Software support in solving the problem of text attribution].
{\it Software Engineering}, 2019, vol.~10(5), pp.~234--240. (In Russian)

12. Breiman L.
Random forests. {\it Machine Learning}, 2001,  vol.~45(1), pp.~5--32.

13. Isert C.
The editing distance between trees.
{\it Ferienakademie B\"aume: Algorithmik und Kombinatorik}
[{\it Holiday Academy Trees: Algorithmics and Combinatorics}]. Sarntal, Italy, 1999, pp.~1--13.

14. Shchegoleva L. V., Lebedev A. A., Moskin N. D.
Metody analiza dannykh v zadache raz\-gra\-ni\-che\-niya fol’klornykh i avtorskikh tekstov
[Methods of data mining in the task of distinguishing bet\-ween folklore and author's texts].
{\it Voprosy Jazykoznanija} [{\it Questions of Linguistics}], 2020, vol.~2, pp.~61--74. (In Russian)


\vskip 2%1.5
mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December 25, 2020.

Accepted: October 13, 2021.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Roman V. Abramov} --- Student; monset008@gmail.com \par

\vskip 2mm \textit{Kirill A. Kulakov} --- PhD in Physics and Mathematics, Associate Professor; kulakov@cs.karelia.ru \par

\vskip 2mm \textit{Alexander A. Lebedev} --- PhD in Philology, Senior Lecturer;  perevodchik88@yandex.ru \par

\vskip 2mm \textit{Nikolai D. Moskin} --- PhD in Technics, Associate Professor; moskin@petrsu.ru \par


\vskip 2mm \textit{Alexander A. Rogov} --- Dr. Sci. in Technics, Professor; rogov@petrsu.ru \par
%
%
}
