

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Ovsyannikov D. A.  \textit{Matematicheskie metody upravleniya
puchkami} [\textit{Mathematical methods of bundles control}].
Leningrad, Leningrad State University Publ., 1980, 228~p. (In
Russian)

2. Pontryagin L. S., Boltyanskii V. G., Gamkrelidze R. V.,
Mischenko E. F.  \textit{Matematicheskaya teoriya optimal'nih
processov} [\textit{Mathematical theory of optimal processes}].
Moscow, Nauka Publ., 1969, 393~p. (In Russian)

3. Lee E. B., Markus L.  \textit{Foundations of optimal control
theory}. Malabar, FL, Krieger Pub. Co., 1986, 586 p.  (Russ. ed.:
Lee E. B., Markus L. \textit{Osnovy teorii optimal'nogo
uprevleniya}. Moscow, Nauka Publ., 1972, 574 p.)

4. Osipov Yu. S., Vasilyev F. P., Potapov M. M.  \textit{Osnovy
metoda dinamiceskoy regulyaqrizacii} [\textit{The basics of the
method of dynamic regularization}]. Moscow, Moscow State
University Publ., 1999, 237~p. (In Russian)

5. Hartman F.  \textit{Ordinary differential equations.} London,
John Wiley \& Sons, 1964, 612~p. (Russ. ed.: Hartman F.
\textit{Obyknovennie differencial'nie uravneniya.} Moscow, Mir
Publ., 1970, 719~p.)

6. Nikolskii S. M.  \textit{Kurs matematicheskogo analiza}
[\textit{A course of mathematical analysis}]. Moscow, Fizmatlit
Publ., 2001, vol.~II, 592~p.  (In Russian)




\vskip 2mm

{\bf For citation:} Nikolskii M. S., Belyaevskikh E. A. Existence
theorems for optimal control in some problems of trajectories
bundles control. {\it Vestnik of Saint Petersburg University.
Applied mathematics. Computer science. Control processes},
\issueyear, volume~13, issue~\issuenum,
pp.~\pageref{p11}--\pageref{p11e}. \doivyp/
spbu10.\issueyear.\issuenum11



}
