

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Zhabko A.~P., Tihomirov O.~G. Chizhova O.~N. O stabilizacii
klassa sistem s proporcional'nym zapazdyvaniem [On stability to
the class of systems with the proportional delay]. \emph{Vestnik
of Saint Peterburg University. Applied Mathematics. Computer
Science. Control Processes}, 2018, vol.~14, iss.~2, pp.~165--172.
https://doi.org/10.21638/11702/spbu10.2018.209 (In Russian)

2. Alexandrova I.~V., Zhabko A.~P.  A new LKF approach to
stability analysis of linear systems with uncertain delays.
\emph{Automatica}, 2018, vol.~91, pp.~173--178.

3. Provotorov V.~V. Boundary control of a parabolic system with
delay and distributed parameters on the graph.  \emph{Intern.
conference ``Stability and Control Processes'' in memory of V.~I.
Zubov} (\emph{SCP}). Saint Petersburg, Saint Petersburg University
Publ., 2015, pp.~126--128.

4. Podvalny S.~L., Provotorov V.~V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \emph{Intern. conference ``Stability and Control
Processes'' in memory of V.~I. Zubov} (\emph{SCP}). Saint
Petersburg, Saint Petersburg University Publ., 2015, pp.~117--119.

5. Provotorov V.~V. Boundary control of a parabolic system with
distributed parameters on a graph in the class of summable
functions. \emph{Automation and Remote Control}, 2015, vol.~76.
iss.~2, pp.~318--322.

6. Podvalny S.~L., Provotorov V.~V. Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe
[Starting control of a parabolic system with distributed
parameters on a graph]. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2015, iss.~3, pp.~126--142. (In Russian)

7. Provotorov V.~V.,  Gnilitskaya Yu.~A. Granichnoe upravlenie
volnovoi sistemoi v prostranstve obobshennyh reshenii na grafe
[Boundary control of a wave systems in the space of the
generalized solutions]. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2013, iss.~3, pp.~112--120. (In Russian)


8. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

9. Mihlin S.~G. \emph{Lineinye uravnenija v chastnyh proizvodnyh}
[\emph{Linear partial equation}]. Moscow, Vysshaja shkola Publ.,
1977, 431~p.  (In Russian)

10. Provotorov V.~V., Volkova A.~S.  \textit{Nachal'no-kraevie
zadachi s raspredelennymi parametrami na grafe} [\textit{Initial
boundary value problems with distributed parameters on the
graph}]. Voronezh, Nauchnay kniga Publ.,  2014,  188~p. (In
Russian)

11. Provotorov V.~V.  Sobstvennye funkcii zadachi
Shturma---Liuvillja na grafe-zvezde  [Eigenfunctions of the
Sturm---Liouville problem astar graph]. \emph{Mathematics}, 2008,
vol.~199, iss.~10, pp.~1523--1545.    (In Russian)

12. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredelennymi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \emph{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224.
https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)

13. Lions J.-L. \textit{Some methods of solving non-linear
boundary value problems}. Paris, Dunod  Gauthier-Villars, 1968,
587~p. (Russ. ed.: Lions J.-L. Nekotorye metody reshenia
nelineinyh kraevyh zadach. Moscow, Mir Publ., 1972, 414~p.)

14. Provotorov V.~V.,  Ryazhskikh V.~I., Gnilitskaya Yu.~A. Unique
weak solvability of a nonlinear initial boundary value problem
with distributed parameters in a netlike region. \emph{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2017, vol.~13, iss.~3, pp.~264--277.
https://doi.org/10.21638/11701/spbu10.2017.304

15. Provotorov V.~V., Provotorova E.~N.  Optimal control of the
linearized Navier---Stokes system in a netlike domain.
\emph{Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2017, vol.~13, iss.~4,
pp.~428--441. https://doi.org/10.21638/11701/spbu10.2017.409

16. Aleksandrov A.~Yu., Zhabko A.~P. O stabilizacii recheniya
odnogo klassa nelineinyh diffe\-ren\-cial'nyh sistem [On stability
of solutions to one class of nonlinear difference systems].
\emph{Siberian Mathematical Journal}, 2003, vol. 44, no.~6,
pp.~951--958. (In Russian)

17. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \emph{WSEAS Transactions on Systems and Control},
2014, vol.~9, pp.~388--397.

18. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions of solutions for nonlinear multiconnected
time-delay systems. \emph{Circuits  Systems and Signal
Processing}, 2016, vol.~35, no.~10, pp.~3531--3554.

19. Karelin V.~V.  Shtrafnye funkcii v zadache upravleniya
processom nabludeniya [Penalty functions in the control problem of
an observation process]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss.~4, pp.~109--114. (In Russian)

20. Kamachkin A.~M., Yevstafyeva V.~V.   Oscillations in a relay
control system at an external disturbance.  \emph{Control
Applications of Optimization 2000}. \emph{Proceedings of the 11th
IFAC Workshop}, 2000, vol.~2, pp.~459--462.

21. Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze
prognoza s ustoichivym lineinym priblizheniem [Plasma
stabilization by prediction with stable linear approximation].
\emph{Vestnik of Saint Petersburg University. Series 10. Applied
mathematics. Computer science. Control processes}, 2011, iss.~1,
pp.~116--133. (In Russian)


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 21, 2019.

Accepted: March 15, 2019.

\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Aleksei~P.~Zhabko} --- Dr. Sci. in Physics and
Mathematics, Professor; zhabko.apmath.spbu@mail.ru

\vskip2mm\textit{Vyacheslav~V.~Provotorov} --- Dr. Sci. in Physics
and Mathematics, Professor; wwprov@mail.ru

\vskip2mm\textit{Olesya~R.~Balaban} --- bal-olesya@mail.ru

}
