
{\small

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. DeGroot M.~H. Reaching a Consensus. \emph{Journal of the
American Statistical Association}, 1974, vol.~69, no.~345,
pp.~118--121.

2. Friedkin N.~E., Johnsen E.~C. Social influence and opinions.
\emph{Journal of Mathematical Sociology}, 1990, vol.~15, no.~3--4,
pp.~193--206.

3. Friedkin N.~E., Johnsen E.~C. Social influence networks and
opinion change. \emph{Advances in Group Processes}, 1999, vol.~16,
pp.~1--29.

4. Bauso D., Cannon M. Consensus in opinion dynamics as a repeated
game. \emph{Automatica}, 2018, vol.~90, pp.~204--211.

5. Bindel D., Kleinberg J., Oren S. How bad is forming your own
opinion? \emph{Games and Eco\-no\-mic Behavior}, 2015, vol.~92,
pp.~248--265.

6. Acemoglu D., Ozdaglar A. Opinion dynamics and learning in
social networks. \emph{Dynamic Games and Applications}, 2011,
vol.~1, no.~1, pp.~3--49.

7. Buechel B., Hellmann T., Kl{\"o}{\ss}ner S. Opinion dynamics
and wisdom under conformity. \emph{Journal of Economic Dynamics
and Control}, 2015, vol.~52, pp.~240--257.

8. Dandekar P., Goel A., Lee D.~T. Biased assimilation, homophily,
and the dynamics of polarization. \emph{Proceedings of the
National Academy of Sciences}, 2013, vol.~110, no.~15,
pp.~5791--5796.

9. Hegselmann R., Krause U. Opinion dynamics and bounded
confidence models, analysis, and simulation. \emph{Journal of
Artificial Societies and Social Simulation}, 2002, vol.~5, no.~3,
pp.~615--645.

10. Ghaderi J., Srikant R. Opinion dynamics in social networks
with stubborn agents: Equilibrium and convergence rate.
\emph{Automatica}, 2014, vol.~50, no.~12, pp.~3209--3215.

11. Golub B., Jackson M.~O. Naive learning in social networks and
the wisdom of crowds.     \emph{American Economic Journal:
Microeconomics}, 2010, vol.~{2}, no.~{1}, pp.~{112--49}.

12. Bure V., Parilina E., Sedakov A. Consensus in social networks
with heterogeneous agents and two centers of influence.
\emph{Stability and Control Processes in memory of V.~I.~Zubov
(SCP), 2015 Intern. Conference}, 2015, pp.~233--236.

13. Bure V., Parilina E., Sedakov A. Consensus in a social network
with two principals. \emph{Automation and Remote Control}, 2017,
vol.~78, no.~8, pp.~1489--1499.

14. Barabanov I.~N., Korgin N.~A., Novikov D.~A., Chkhartishvili
A.~G. Dynamic models of informational control in social networks.
\emph{Automation and Remote Control}, 2010, vol.~71, no.~11,
pp.~2417--2426.

15. Gubanov D.~A., Novikov D.~A., Chkhartishvili A.~G.
Informational influence and informational control models in social
networks. \emph{Automation and Remote Control}, 2011, vol.~{72},
no.~7, pp.~{1557--1597}.

16. Etesami S.~R., Ba{\c{s}}ar T. Game-theoretic analysis of the
Hegselmann---Krause model for opinion dynamics in finite
dimensions. \emph{IEEE Transactions on Automatic Control}, 2015,
vol.~{60}, no~{7}, pp.~{1886--1897}.

17. Krawczyk J.~B., Tidball M. A discrete-time dynamic game of
seasonal water allocation. \emph{Journal of Optimization Theory
and Applications}, 2006, vol.~128, no.~2, pp.~411--429.

18. Niazi M.~U.~B., \"{O}zg\"{u}ler A.~B., Y{\i}ld{\i}z A.
Consensus as a Nash equilibrium of a dynamic game. \emph{12th
Intern. Conference on Signal-Image Technology $\&$ Internet-Based
Systems}, 2016, pp.~{365--372}.

19. Ba{\c{s}}ar T., Olsder G.~J. \emph{Dynamic noncooperative game
theory}. 2nd ed. New York, Academic Press, 1999, 511~p.

20. Haurie A., Krawczyk J., Zaccour G. Games and dynamic games.
Singapore, World Scientific Press, 2012, 488~p.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm


Received:  September 11, 2018.

Accepted: December 18, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm\textit{Artem A. Sedakov} --- PhD in Physics and
Mathematics; a.sedakov@spbu.ru

\vskip2mm\textit{Mengke Zhen} --- Student; mengkezhen@163.com

}
