
{\normalsize

\vskip 6mm

\noindent{\bf Investigation of ultimate boundedness conditions of
mechanical
systems \\
via de\-com\-po\-si\-ti\-on$\,^*$}

}

\vskip 2mm

{\small

\noindent{\it A. Yu. Aleksandrov$\,^1$%
, J. Zhan$\,^2$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ The reported study was  supported by the
Russian Foundation for Basic Research (grant N~19-01-00146-a), by
the Saint Petersburg State University (project Id:  37569826), by
the National Natural Science Foundation of China (grant
N~61803007) and by the Rail Transit Joint Funds of Beijing Natural
Science Foundation and Traffic Control Technology (grant
N~L171001).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

\noindent%
$^2$~%
Beijing University of Technology, 100, Pingleyuan ul.,  Beijing,

\noindent%
\hskip2.45mm%
100124, Chinese People's Republic

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Aleksandrov A. Yu., Zhan J.
Investigation of ultimate boundedness conditions of mechanical
systems via decomposition. {\it Vestnik of Saint~Petersburg
University. Applied Mathematics. Computer Science. Control
Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}.\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent A mechanical system with linear velocity
forces and nonlinear homogeneous positional ones is stu\-died. It
is required to obtain conditions for the ultimate boundedness of
motions of this system. To solve the problem, the decomposition
method is used. Instead of the original system of the second order
equations, it is proposed to consider two auxiliary subsystems of
the first order. It should be noted that one of these subsystems
is linear, and another one is homogeneous. Using the Lyapunov
direct method, it is proved that if the zero solutionsof the
isolated subsystems are asymptotically stable, and the order of
homogeneity of the positional forces is less than one, then the
motions of the original system are uniformly ultimately bounded.
Next, conditions are determined under which perturbations do not
disturb the ultimate boundedness of motions. A theorem on uniform
ultimate boundedness by nonlinear approximation is proved. In
addition, it was shown thatfor some types of nonstationary
perturbations with zero mean values the conditions of this theorem
could be relaxed. A mechanical system with switched nonlinear
positional forces is also investigated. For the corresponding
family of systems, a common Lyapunov function is constructed. The
existence of such a function ensures that the motions of the
considered hybrid system are uniformly ultimately bounded for any
admissible switching law.
Examples are presented demonstrating the effectiveness of the developed approaches.\\[1mm]
\textit{Keywords}: mechanical system, ultimate boundedness,
homogeneous function, decomposition,  Lyapunov direct method.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. { Voronov A. A.} {\it Vvedenie v dinamiku slozhnyh upravljaemyh
sistem} [{\it Introduction in dynamics of complex control
systems}]. Moscow, Nauka Publ., 1985, 352~p. (In Russian)

2. {\it Metod vektornyh funkcij Ljapunova v teorii ustojchivosti}
[{\it Method of vector Lyapunov functions in stability theory}].
Eds by A.~A.~Voronov, V.~M.~Matrosov. Moscow, Nauka Publ., 1987,
312~p. (In Russian)



3. {Matrosov V. M.} {\it Metod vektornyh funkcij Ljapunova: analiz
dinamicheskih svojstv nelinejnyh sistem} [{\it Vector Lyapunov
function method: analysis of dynamical properties of nonlinear
systems}]. Moscow, Fizmatlit Publ., 2001, 384~p.  (In Russian)



4. {Zubov V. I.}  {\it Analiticheskaja dinamika giroskopicheskih
sistem} [{\it Analytical dynamics of gyroscopic systems}].
Leningrad, Sudostroenie Publ., 1970,  320~p. (In Russian)

5. { Merkin D. R.} {\it Giroskopicheskie sistemy}
                       [{\it Gyroscopic systems}].
 Moscow, Nauka Publ., 1974, 344~p.  (In Russian)


6. {Pyatnitskii E. S.} Princip dekompozicii v upravlenii
mehanicheskimi sistemami  [The principle of decomposition in the
control of mechanical systems]. {\it Doklady Akademii Nauk SSSR}
[{\it Papers of Academy of Sciences of the USSR}], 1988, vol.~300,
no.~2, pp.~300--303. (In Russian)

7. {Chernous'ko F. L.,  Anan'evskii I. M.,  Reshmin S. A. } {\it
Metody upravlenija nelinejnymi mehani\-cheskimi sistemami} [{\it
Methods of control of nonlinear mechanical systems}]. Moscow,
Fizmatlit Publ., 2006,\linebreak 328~p.  (In Russian)


8. {Podval'nyi S. L., Provotorov V. V.}  {Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe}
[Start control of a parabolic system with distributed parameters
on a graph]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer Science. Control
Processes},
 2015, iss.~3, pp.~126--142 (In Russian)


9. {Provotorov V. V.,  Ryazhskikh V. I.,  Gnilitskaya Yu. A.}
Unique weak solvability of a nonlinear initial boundary value
problem with distributed parameters in a netlike domain. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes},
 2017, vol.~13, iss.~3, pp.~264--277.
doi:  10.21638/11701/spbu10.2017.304




10. {Kosov A. A.} Issledovanie ustojchivosti singuljarnyh sistem
metodom vektor-funkcij Ljapunova [Stability investigation of
singular systems via vector Lyapunov functions method]. {\it
Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes},
 2005, iss.~4, pp.~123--129. (In Russian)






11. {Aleksandrov A. Yu., Chen Y., Kosov A. A., Zhang L.}
 Stability of hybrid mechanical
systems with switching linear force fields. {\it Nonlinear
Dynamics and Systems Theory}, 2011, vol.~11, no.~1, pp.~53--64.

12. {Aleksandrov A. Yu., Kosov A. A., Chen Y.} Stability and
stabilization of mechanical systems with switching. {\it
Automation and Remote Control}, 2011, vol.~72, no.~6,
pp.~1143--1154.



13. {Aleksandrov A. Yu., Aleksandrova E. B., Zhabko A. P.}
 Asymptotic stability conditions
for certain classes of mechanical systems with time delay. {\it
WSEAS Transactions on Systems and Control}, 2014, vol.~9,
pp.~388--397.


14.  {Aleksandrov A. Y.,  Aleksandrova E. B.} Asymptotic stability
conditions for a class of hybrid mechanical systems with switched
nonlinear positional forces. {\it Nonlinear Dynamics}, 2016,
vol.~83, no.~4, pp.~2427--2434.



15. {Demidovich B. P.} {\it Lekcii po matematicheskoj teorii
ustojchivosti}                             [{\it Lectures on the
mathema\-tical stability theory}]. Moscow, Nauka Publ.,
 1967,  472~p. (In Russian)



{16.} {Yoshizawa~T.} {\it Stability theory by Liapunov's second
method}. Tokyo,  The Math. Soc. of  Japan  Publ., 1966, 223~p.




17. {Fadeev S. S.} Uslovija predel'noj ogranichennosti reshenij
nelinejnyh mehanicheskih sistem s dominirovaniem giroskopicheskih
sil [Ultimate boundedness conditions of solutions of nonlinear
mechanical systems with domination of gyroscopic forces]. {\it
Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes,}
 2010, iss.~4, pp.~74--84. (In Russian)






18.  {Zubov V. I.} {\it Dinamika upravljaemyh sistem} [{\it
Dynamics of control systems}]. Saint Petersburg,  Saint Petersburg
University Publ.,
 2004,    380~p.    (In Russian)




19. {Bhat S.~P.,  Bernstein D.~S.} Geometric homogeneity with
applications to  finite-time stability. {\it Mathematics of
Control, Signals and Systems}, 2005, vol.~17,  pp.~101--127.


20. {Polyakov A.,  Efimov D.,  Perruquetti W.} Finite-time and
fixed-time stabilization: Implicit Lyapunov function approach.
{\it Automatica}, 2015, vol.~51, pp.~332--340.


21.  {Zubov V. I.} {\it Ustojchivost' dvizhenija} [{\it Motion
stability}].  Moscow, Vysshaya shkola Publ., 1973, 272~p. (In
Russian)


22.  {Rosier L.} Homogeneous Lyapunov function for homogeneous
continuous vector field. {\it Systems {\rm \&} Control Letters},
1992, vol.~19, pp.~467--473.




{23.} {Aleksandrov A. Yu.} Ob asimptoticheskoj ustojchivosti
reshenij sistem nestacionarnyh diffe\-rencial'nyh uravnenij s
odnorodnymi pravymi     chastjami   [On the asymptotic stability
of solutions of nonstationary differential equation systems with
homogeneous right-hand sides]. {\it Doklady RAN} [{\it Papers of
Russian Academy of Sciences}],
 1996, vol.~349, no.~3, pp.~295--296. (In Russian)



{24.} {Aleksandrov A. Yu.} Ob ustojchivosti ravnovesija
nestacionarnyh sistem [On the stability of equilibrium of
nonstationary systems]. {\it Applied Mathematics and Mechanics},
1996, vol.~60, no.~2, pp.~205--209.  (In Russian)








{25.} {\it Tikhomirov O. G.} Ustojchivost' odnorodnyh
nestacionarnyh sistem obyknovennyh diffe\-rencial'nyh uravnenij
[Stability of homogeneous systems of ordinary differential
equations]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer Science. Control
Processes,}
 2007, iss.~3, pp.~123--130. (In Russian)

\pagebreak


26.  {Bogoluybov N. N., Mitropol'skii Yu. A.} {\it
Asimptoticheskie metody v teorii nelinejnyh kolebanij} [{\it
Asymptotic methods in the theory of nonlinear oscillations}].
Moscow, Fizmatgiz Publ.,
 1963, 412~p. (In Russian)




27. {Liberzon D.,  Morse A. S.} Basic problems in stability and
design of switched systems.
 {\it IEEE Control Systems Magazine},  1999, vol.~19, no.~15,
pp.~59--70.


28. {Shorten R.,  Wirth F.,  Mason O.,  Wulf K., King C.}
Stability criteria for switched and hybrid systems. {\it SIAM
Rev.,} 2007, vol.~49, no.~4, pp. 545--592.

\vskip1.5mm Received:  January 21, 2019.

Accepted: March 15, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Alexander Yu. Aleksandrov} --- Dr. Sci. in
Physics and Mathematics, Professor;  a.u.aleksandrov@spbu.ru

\vskip2mm \textit{Jingyuan Zhan} --- PhD, Lecturer;
jyzhan@bjut.edu.cn

}
