

\noindent{\small UDC 512.552.18+003.26  \hfill {%\footnotesize
\scriptsize Вестник~СПбГУ.~Прикладная~математика.~Информатика\,...\,\issueyear.~Т.\,16.~Вып.\,\issuenum}\\
MSC 16P10

}

\vskip2.5%2
mm

\noindent{\bf Candidate for practical post-quan\-tum
signature scheme%$^{*}$%

 }

\vskip2.5%2
mm

\noindent{\it  N.~A.~Moldovyan, A.~A.~Moldovyan%$\,^1$%
%, I.~О. Famylia%$\,^2$%
%, I.~О. Famylia%$\,^2$%

}

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by the Russian
%Foundation for Basic Research (research project N
%20-07-00531).\par
%%
%%\vskip 2.0mm
%%
\indent{\copyright} Санкт-Петербургский государственный
университет, \issueyear%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum10 } }\hfill\thepage}%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum10}}}%
% для оформления нижнего колонтитула
\cfoot{} %

\vskip3%2.5
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^2$~%
St. Petersburg Federal Research Center of the Russian Academy of
Sciences,

%\noindent%
%%\hskip2.45mm%
%St. Petersburg Institute for Informatics and Automation of the
%Russian Academy of Sciences,

\noindent%
%\hskip2.45mm%
39, 14-ia linia, St.\,Petersburg, 199178, Russian Federation


%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,
%
%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3%2.5
mm

{\small \noindent \textbf{For citation:} Moldovyan~N.~A.,
Moldovyan~A.~A.  Candidate for practical post-quan\-tum signature
scheme. {\it Vestnik of Saint~Petersburg University. Applied
Mathematics. Com\-pu\-ter Science. Control Pro\-ces\-ses},
\issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p10}--\pageref{p10e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum10

\vskip3.5%3
mm

{\leftskip=7mm\noindent A new criterion of post-quantum security
is used to design a practical signature scheme based on the
computational complexity of the hidden discrete logarithm problem.
A 4-di-\linebreak men\-sio\-nal finite non-commutative associative
algebra is applied as algebraic support of the cryptoscheme.  The
criterion is formulated as computational intractability of the
task of constructing a periodic function containing a period
depending on the discrete logarithm value. To meet the criterion,
the hidden commutative group possessing the 2-dimensional
cyclicity is exploited in the developed signature scheme. The
public-key elements are computed depending on two vectors that are
generators of two different cyclic groups contained in the hidden
group. When computing the public key two types of masking
operations are used: $i)$ possessing the property of mutual
commutativity with the exponentiation operation and $ii)$ being
free of such property. The signature represents two integers and
one vector $S$ used as a multiplier in the verification equation.
To prevent attacks using the value $S$ as a fitting element the
signature verification
equation is doubled.\\[1mm]
\textit{Keywords}: digital signature, post-quantum cryptoscheme,
public key, hidden logarithm problem, finite non-commutative
algebra, associative algebra.

}

}

\vskip 4.5%4
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{1.~Introduction.} Current cryptographic standards of the
digital signature algorithms and public key-agreement protocols do
not provide post-quantum resistance, since they are based on the
computational difficulty of the factoring problem and of the
discrete logarithm problem which can be solved on a hypothetic
quantum computer in polynomial time~[1,~2]. The development of
practical public-key post-quantum cryptoschemes attracts much
attention of the cryptographic community~[3,~4].

One of the attractive approches to the development of post-quantum
signature schemes is applying the hidden discrete logarithm
problem (HDLP) as the base cryptographic primitive~[5--7]. The
rationale of the post-quantum security of the known signature
algorithms based on the HDLP takes into account that the quantum
algorithm for finding the discrete logarithm value exploits the
extremely high efficiency of quantum computer to perform a
discrete Fourier transform for a function that takes values in a
finite cyclic group~[1,~8]. To solve the problem of finding the
logarithm value $x,$ i.~e., to solve the equation $Y=G^x,$ where
$x<q$ is the unknown integer; $Y$ and $G$ are known elements of a
finite cyclic group of the prime order $q,$  one constructs a
periodic function $F(i,j)=Y^i\circ G^j$ in two integer variables
$i$ and $j,$ which contains a period with the length $(-1,x)$:
$F(i,j)=Y^i G^j=Y^{i-1} G^{j+x}=F(i-1,j+x).$ From the  discrete
Fourier transform results the perion length $(-1,x)$ is easily
computed.

For the case of the HDLP-based signature schemes considered in
papers~[5--7] one can construct the periodic function
$F(i,j)=Y^i\circ T\circ Z^j,$  where $Y,T$ and $Z$ are
$m$-dimensional vectors; $\circ$ is the multiplication operation
in the finite non-commutative associative algebra (FNAA) used as
algebraic support of the signature scheme. This function includes
period with the length $(-1,x),$ however, the function $F(i,j)$
takes on the values that lie in different cyclic groups and there
is no preferable cyclic group  for the values of this function.

Thus, the design criterion related to the know HDLP-based
signature algorithms can be formulated as the following one.

{\bf Criterion~1.} {\it The periodic functions $F(i,j)$
constructed on the base of public pa\-ra\-me\-ters of the
signature scheme and containing a period with the length depending
on the discrete logarithm value should take on values in different
finite cyclic groups contained in the FNAA. Besides, no cyclic
group can be pointed out as a preferable finite group for the
values of the function $F(i,j).$}

In present paper we use another design criterion for providing
post-quantum resistance of the HDLP-based signature algorithms. To
meet the accepted criterion, a new method of setting the HDLP is
used, which is characterized by the use of a hidden commutative
group with two-dimensional cyclicity and masking operations of the
following types: $i$)~ha\-ving the property of mutual
commutativity with the exponentiation operation in the hidden
group; $ii$) not having such a property.

\textbf{2.~Advanced criterion of post-quantum resistance.}
Criterion~1 takes into account the currently known quantum
algorithm for finding the period length for a periodic function
which values lie in some fixed finite cyclic group. However, one
can assume that in the future, novel quantum algorithms will be
developed that will effectively find the period length for
functions that take on values within the framework of the whole
FNAA used as algebraic support of the signature scheme. Taking
into account such potential possibility  the following {\it
advanced} criterion of the post-quantum resistance is applied in
this paper for the development of a post-quantum signature scheme.

{\bf Criterion~2.} {\it Based on the public parameters of the
signature scheme, the construction of a periodic function
containing a period with the length depending on the discrete
lo\-ga\-rithm value should be a computationally intractable task.}

To design a signature scheme satisfying this criterion it is used
the idea of masking periodicity depending on the discrete
logarithm value. To implement this idea, we propose to perform the
exponentiation operation, which introduces the main contribution
to the security, in a cyclic group (called basic cyclic group)
that is a subgroup of a hidden commutative group having
two-dimensional cyclicity. (A finite commutative group is called
group with the ${\mu}$-dimensional cyclicity, if its minimum
generator system includes ${\mu}$  elements possessing the same
order value~[9].)

To implement the said idea, there is used a hidden commutative
group having order $q^2$, in which every element (except the unit)
possesses order equal to the prime $q.$ The  public-key elements
are calculated based on two independent elements of the hidden
group. One of the latter is the generator of the base cyclic
group, and the second is used as a masking multiplier that imposes
a periodicity having length equal to the value $q$.

\textbf{3.~The used FNAA.} Consider a finite $m$-dimensional
vector space defined over the field $GF(p).$ Defining additionally
the vector multiplication operation that is distributive at the
right and at the left relatively the addition operation, one gets
the $m$-dimensional finite algebra. Some vector $A$ can be
represented in two forms:  $A=(a_0,a_1,\dots ,a_{m-1})$ and
$A=\sum_{i=0}^{m-1}a_i{\bf e}_i,$ where $a_0,a_1,\dots ,a_{m-1}\in
GF(p)$ are called coordinates; ${\bf e}_0,$ ${\bf e}_1,$ ... $,
{\bf e}_{m-1}$ are basis vectors.
 The vector multiplication operation ($\circ$) of two $m$-dimensional vectors  $A$ and $B$ is set as follows:

\begin{equation*}
A\circ B= \sum_{i=0}^{m-1}\sum_{j=0}^{m-1}a_ib_j({\bf e}_i\circ
{\bf e}_j),
\end{equation*}
where every of the products ${\bf e}_i\circ {\bf e}_j$ is to be
replaced by a single-component vector ${\lambda}{\bf e_k},$ here
${\lambda}\in GF(p),$ indicated in the cell at the intersection of
the $i$-th row and $j$-th column of so called basis vector
multiplication table (BVMT), like Table~1. To define associative
vector multiplication operation one should construct the BVMT that
defines associative multiplication of all possible triples of the
basis vectors $\left({\bf e}_i, {\bf e}_j, {\bf e}_k \right)$:
$\left({\bf e}_i\circ {\bf e}_j\right) \circ {\bf e}_k= {\bf
e}_i\circ \left({\bf e}_j \circ {\bf e}_k\right).$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Table 1

\begin{table}[h!]
\begin{center}
{\small

{\it Table 1.} {\bf The BVMT defining\\ the used FNAA
(${\lambda}\ne$~1; ${\lambda}\ne$~0)}%

}

\vskip 3mm

{\footnotesize

\begin{tabular}{|c|c|c|c|c|}

\hline

\multicolumn{1}{|c|}{$\circ$} & \multicolumn{1}{c|}{${\bf e}_0$} &
\multicolumn{1}{c|}{${\bf e}_1$} & \multicolumn{1}{c|}{${\bf
e}_2$} & \multicolumn{1}{c|}{${\bf e}_3$}
\\ \hline
%\endfirsthead

${\bf e}_0$ & ${\bf e}_0$ & ${\bf e}_3$ & ${\bf e}_0$ & ${\bf
e}_3$ \\ \hline ${\bf e}_1$ & ${\lambda}{\bf e}_2$ & ${\bf e}_1$ &
${\bf e}_2$ & ${\lambda}{\bf e}_1$ \\ \hline ${\bf e}_1$ & ${\bf
e}_2$ & ${\bf e}_1$ & ${\bf e}_2$ & ${\bf e}_1$ \\ \hline ${\bf
e}_0$ & ${\lambda}{\bf e}_0$ & ${\bf e}_3$ & ${\bf e}_0$ &
${\lambda}{\bf e}_3$ \\ \hline
\end{tabular}

}
\end{center}\vspace{-3mm}
\end{table}
%\vskip 2mm







To develop the signature scheme that meets Criterion~2 we have
used the 4-di\-men\-sional FNAA with the multiplication operation
defined by the BVMT shown in Table~1, where ${\lambda}\neq 1;$
${\lambda}\neq 0$~[5]. This FNAA contains global two-sided unit
$E$ that can be computed as
\begin{equation*}
E=\left(\frac{1}{1-{\lambda}},\frac{1}{1-{\lambda}},\frac{{\lambda}}{{\lambda}-1},\frac{1}{{\lambda}-1}\right).
\end{equation*}
The vectors $A$ satisfying the condition $a_0a_1\neq a_2a_3$ are
invertible. The vectors $N$ satisfying condition $n_0n_1=n_2n_3$
are non-invertible.

{\bf Proposition.} The number of the invertible vectors in the
considered 4-dimensional FNAA is equal to $\Omega =p\left(
p+1\right)\left( p-1\right)^2$.

P~r~o~o~f. The number of the locally invertible vectors is equal
to the number of all elements of the algebra ($p^4$) minus the
number on non-invertible vectors $N.$  Let us compu\-te the number
of the vectors $N$ for which we have $n_0n_1=n_2n_3.$ For the case
$n_1\neq 0$ ($p-1$ different values of $n_1$) the coordinades
$n_2$ and $n_3$ are arbitrary ($p^2$ variants) and
$n_0=n_2n_3n_1^{-1},$ therefore, we have $(p-1)p^2$ non-invertible
vectors related to this case. For the case $n_1= 0,$ at least, one
of the values $n_2$ and $n_3$ should be equal to 0 ($2p-1$
variants)\linebreak and in every of such variants the coordinate
$n_0$ is arbitrary. Therefore, the last case\linebreak gives
$p(2p-1)$ more non-invertible vectors. Totally, there exists
$(p-1)p^2+p(2p-1)=p^3+$\linebreak $p^2-p$ different non-invertible
vectors. For the value $\Omega$ we get: $\Omega
=p^4-p^3-p^2+p=p\left( p+1\right)\left( p-1\right)^2$. \hfill
$\square$

The value $\Omega$ is the order of multiplicative group of the
algebra. The maximum possible order of the invertible vectors in
the considered algebra is equal to $\left( p^2-1\right)$. To have
possibility to define the hidden commutative group containing
cyclic groups of the prime order $q$ having sufficiently large
size, we suppose the considered FNAA is defined over the finite
field $GF(p)$ with 256-bit characteristic $p=2q+1,$ where $q$ is a
255-bit prime.

A commutative group of the order $q^2$  can be set as computation
of its basis $<G,Q>$ including two independent vectors of the same
order $q.$ The procedure of setting the basis $<G,Q>$ is as
follows:

a) select a random invertible vector $R_1$ and compute
$G_1=R_1^{2(p+1)}\neq E;$

b) select a random invertible vector $R_2$ and compute
$G_2=R_2^{2(p+1)}\neq E;$

c) if $G_1\circ G_2=G_2\circ G_1,$ then go to step 1. Otherwise
take $G=G_1$;

d) select a random integer $r$ and compute $b=r^{2(p+1)}\bmod p
\neq 1;$

e) performing scalar multiplication, compute the vector  $Q=bG.$

At the output of this procedure we have the basis $<G,Q>$ of the
commutative group of the order $q^2$ which possesses the
2-dimensional cyclicity. One can easily see that the order of each
of the vectors $G$ and $Q$ is equal to the prime $q.$

\textbf{4.~Computation of the public-key.} The public-key
represents two triples of the 4-dimensional vectors
$(U_1,Y_1,Z_1)$  and $(U_2,Y_2,Z_2)$ that are computed as follows.

1. Generate at random the basis $<G,Q>$ of the hidden commutative
group $\Gamma$ possessing the 2-dimensional cyclicity.

2. Select two random integers $r_1$ and $r_2$ and compute the
vector $J=G^{r_1}\circ Q^{r_2}\in {\Gamma}.$

3. Generate at random the invertible vector $B_1$ and compute the
vector $Y_1=B_1\circ G\circ B_1^{-1}.$

4. Generate at random the invertible vector $A_1$ and the integer
$x$ ($1<x<q$). Then compute the vectors $U_1=A_1\circ G^x\circ
B_1^{-1}$ and $Z_1=B_1\circ Q\circ A_1^{-1}.$

5. Generate at random the invertible vector $B_2$ and compute the
vector $Y_2=B_2\circ J\circ B_2^{-1}.$

6. Generate at random  integer $w$ ($1<w<q$). Then compute the
vectors $W=Q^w,$ $A_2=A_1\circ W,$ $U_2=A_2\circ J^x\circ
B_2^{-1},$ and $Z_2=B_2\circ Q\circ A_2^{-1}.$

The integers $x,w$ and the vectors $G,$ $Q,$ $J,$ $A_1,$ $B_1,$
$A_2,$ $B_2,$ and $W$ are private elements. The private key
represents the subset $\left\{ x,G,Q,J,A_1,A_2,W\right\}$ of
private elements that are used when computing a signature. The
size of the public-key $(U_1,Y_1,Z_1);$ $(U_2,Y_2,Z_2)$ is equal
to 768 bytes.

{\it \textbf{Signature generation procedure$:$}}

${\bullet}$~Generate at random the integer $k$ ($1<k<q$)  and the
invertible vector $K.$ Then compute $V_1=A_1\circ G^k\circ K$ and
$V_2=A_2\circ J^k\circ W^{-1}\circ K.$

${\bullet}$~Using a specified hash function $f_H,$ compute the
first  signature element $e$: $e=f_H\left(M,V_1,V_2\right),$ where
$M$ is a document to be signed.

${\bullet}$~Compute the second signature element $s$ as one of two
solutions of the equation $s^2+xs=k \bmod q.$ If the equation has
no solution, then go to step~1.

${\bullet}$~Compute the third signature element $S=A_1\circ
Q^{-s}\circ K.$ (Note $S=A_2\circ W^{-1}\circ Q^{-s}\circ K.$)

On the average, computation of one 192-byte signature $(e,s,S)$
requires performing the signature generation procedure two times.
On the whole the computational difficulty of the signature
generation procedure is roughly equal to four exponentiation
operations in the 4-dimensional in FNAA.

{\it \textbf{Signature verification procedure$:$}}

${\bullet}$~Using the signature $\left(e,s,S\right)$ and the
public-key $\left(Y_1,Z_1,T_1\right);$ $\left(Y_2,Z_2,T_2\right)$
compute the vectors $V_1^{\prime}=\left(U_1\circ Y_1^{es}\circ
Z_1\right)^{s}\circ S$ and $V_2^{\prime}=\left(U_2\circ
Y_2^{es}\circ Z_2\right)^{s}\circ S.$

${\bullet}$~Compute the hash-function value
$e^{\prime}=f_H\left(M,V_1^{\prime},V_2^{\prime}\right).$

${\bullet}$~If $e^{\prime}=e$ and $S=\left(s_0,s_1,s_2,
s_3\right)$ is such that $s_0s_1\neq s_2s_3$, then the signature
is genuine. Otherwise the signature is rejected.

\textbf{5.~Correctness proof.} Correctness proof of the sigature
scheme consists in proving that the signature $(e,s,S)$ computed
correctly will pass the verification procedure as genuine
signature:

\begin{center}
$ V^{\prime}_1=\left(U_1 \circ Y_1^{es} \circ Z_1\right)^s\circ S=$ \\
$ =\left( A_1\circ G^x \circ B_1^{-1}\circ \left(B_1\circ G\circ B_1^{-1}\right)^{es}\circ B_1\circ Q\circ A_1^{-1}\right)^s\circ A_1\circ Q^{-s}\circ K=$\\
$  =A_1\circ G^{xs} \circ G^{es^2}\circ Q^s \circ A^{-1}\circ A_1\circ Q^{-s}\circ K=$ \\
$ =A_1\circ G^{es^2+xs}\circ K= A_1\circ G^{k}\circ K =V_1;$ \\
$  V^{\prime}_2=\left(U_2 \circ Y_2^{es} \circ Z_2\right)^s\circ S=$ \\
$ =\left( A_2\circ J^x \circ B_2^{-1}\circ \left(B_2\circ J\circ B_2^{-1}\right)^{es}\circ B_2\circ Q\circ A_2^{-1}\right)^s\circ A_2\circ W^{-1}\circ Q^{-s}\circ K=$\\
$ =A_2\circ J^{xs} \circ J^{es^2}\circ Q^s \circ A_2^{-1}\circ A_2\circ Q^{-w}\circ Q^{-s}\circ K= $\\
$ =A_2\circ J^{es^2+xs}\circ Q^{-w}\circ K= A_2\circ J^{k}\circ
W^{-1}\circ K =V_2.$
\end{center}

%\begin{equation*}
%\begin{aligned}
%& V^{\prime}_1=\left(U_1 \circ Y_1^{es} \circ Z_1\right)^s\circ S=  \\
%& =\left( A_1\circ G^x \circ B_1^{-1}\circ \left(B_1\circ G\circ B_1^{-1}\right)^{es}\circ B_1\circ Q\circ A_1^{-1}\right)^s\circ A_1\circ Q^{-s}\circ K=\\
%&  =A_1\circ G^{xs} \circ G^{es^2}\circ Q^s \circ A^{-1}\circ A_1\circ Q^{-s}\circ K= \\
%& =A_1\circ G^{es^2+xs}\circ K= A_1\circ G^{k}\circ K =V_1; \\
%&  V^{\prime}_2=\left(U_2 \circ Y_2^{es} \circ Z_2\right)^s\circ S= \\
%& =\left( A_2\circ J^x \circ B_2^{-1}\circ \left(B_2\circ J\circ B_2^{-1}\right)^{es}\circ B_2\circ Q\circ A_2^{-1}\right)^s\circ A_2\circ W^{-1}\circ Q^{-s}\circ K=\\
%&  =A_2\circ J^{xs} \circ J^{es^2}\circ Q^s \circ A_2^{-1}\circ A_2\circ Q^{-w}\circ Q^{-s}\circ K= \\
%& =A_2\circ J^{es^2+xs}\circ Q^{-w}\circ K= A_2\circ J^{k}\circ  W^{-1}\circ K =V_2.
%\end{aligned}
%\end{equation*}

Since $V^{\prime}_1=V_1$ and $V^{\prime}_2=V_2,$ the equality
$e^{\prime}=e$ holds true. Besides, in the signature $(e,s,S)$
computed correctly the invertibility condition $s_0s_1\neq s_2s_3$
is satisfied for the vector $S=\left( s_0,s_1,s_2,s_3 \right).$

\textbf{6.~Discussion.} Among nine post-quantum signature schemes
developed in framework of the NIST competition the algorithms
Falcon [https://falcon-sign.info/] and Dilithium
[https://pq-crystals.org/dilithium/index.shtml] attracts attention
from the view point of the trade off between performance and size
of the public-key and the  signature. Table~2 presents a rough
comparison of the proposed signature scheme with Falcon-512 and
Dilithium-1024x768 (versions related to the 128-bit security
level). The algorithm proposed in this article has a significant
advantage in the size of the signature. Besides, it has higher
performance of the signature verification procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Table 2


\begin{table}[h!]
\begin{center}
{\small

{\it Table 2.} {\bf Comparison with the signature schemes
Falcon-512,\\ Dilithium-1024x768, RSA-2048}%

}

\vskip 3mm

{\footnotesize

\begin{tabular}{|c|c|c|c|c|}

\hline

\multicolumn{1}{|c|}{Signature } & \multicolumn{1}{c|}{Signature }
& \multicolumn{1}{c|}{Public-key} & \multicolumn{1}{c|}{Signature
generation} & \multicolumn{1}{c|}{Signature verification}
\\
%\endfirsthead

scheme & size, bytes & size, bytes & rate, arbitrary units & rate,
arbitrary units \\ \hline \multicolumn{1}{|l|}{Falcon-512} & 657 & 897 & 50 & 25 \\
\hline \multicolumn{1}{|l|}{Dilithium-1024x768} & 2044 & 1184 & 15 & 10\\
\hline \multicolumn{1}{|l|}{RSA-2048} & 256 & 256 & 10 & $>50$\\
\hline \multicolumn{1}{|l|}{Proposed} & 192 & 768 & 40 & 60 \\
\hline
%
\end{tabular}

}
\end{center}\vspace{-3mm}
\end{table}
%\vskip 2mm










Consider construction of some periodic functions on the base of
public parameters of the proposed signature algorithm.

1. Suppose the function $F_1(i,j)=Y_1^i\left(Z_1\circ
U_1\right)^j=B_1\circ G^{i+xj}\circ Q^{j}\circ B_1^{-1}$ contains
a period with the length $\left({\delta}_i,{\delta}_j\right).$
Then, takin into account that $G$ and $Q$ are generators of
different cyclic groups of the same order $q$, we have:
${\delta}_i+x{\delta}_j\equiv 0 \bmod q$ and ${\delta}_j\equiv 0
\bmod q$  $\Rightarrow$ ${\delta}_i\equiv {\delta}_j\equiv 0 \bmod
q.$ The last means the function $F_1(i,j)$ possesses only the
periodicity connected with the value $q$ that is order of cyclic
groups contained in the hidden commutative group with
2-dimensional cyclicity.

2. Suppose the function $F_2(i,j)=\left(U_2\circ Z_2\right)^i\circ
\left(U_2\circ Y_2\circ Z_2\right)^j=A_2\circ G^{xi+xj+j}\circ
Q^{i+j}\circ A_2^{-1}$ includes a period with the length
$\left({\delta}_i,{\delta}_j\right).$ Then, we have
$x{\delta}_i+x{\delta}_j+{\delta}_j\equiv 0 \bmod q$ and
${\delta}_i+{\delta}_j\equiv 0 \bmod q$ $\Rightarrow$
${\delta}_i\equiv {\delta}_j\equiv 0 \bmod q.$ Thus, the function
$F_1(i,j)$ possesses only the periodicity connected with the value
$q.$

3. Suppose the function $F_3(i,j,k)=\left(U_2\circ
Z_2\right)^i\circ \left(U_2\circ Y^j_2\circ Z_2\right)^k=A_2\circ
G^{xi+xj+jk}\circ Q^{i+j}\circ A_2^{-1}$ includes a period with
the length $\left({\delta}_i,{\delta}_j,{\delta}_k\right).$ Then,
we have
$x{\delta}_i+x{\delta}_j+j{\delta}_i-i{\delta}_j-{\delta}_i{\delta}_j\equiv
0 \bmod q$ and ${\delta}_i+{\delta}_j\equiv 0 \bmod q.$ When
solving simultaneously the last two congruencies relatively the
unknowns ${\delta}_i$ and ${\delta}_j$,  one will obtain solutions
that depends on the values $i$ and $j$, except the solution
$\left( {\delta}_i,{\delta}_j\right)=(0,0)$. This means that the
function  $F_3(i,j,k)$ possesses only the periodicity with the
length $(q,q)$.

\textbf{7.~Conclusion.} An advanced criterion of post-quantum
security has been applied to develop a new HDLP-based digital
signature schemes that is a candidate for practical post-quantum
signature algorithms. The proposed design is characterized in
applying the hidden commutative group possessing 2-dimensional
cyclicity and masking operations that are not mutually commutative
with the exponentiation operation. Besides, a doubled verification
equation had been applied to prevent attacks using the signature
element $S$ as a fitting parameter.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
\input{10/ref-s-eng}% для английской статьи

%\newpage
\input{10/lit-ra-eng}% для английской статьи

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\thispagestyle{empty}

\vskip 3mm

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~16.~Вып.~\issuenum}}}%
% для оформления нижнего колонтитула
\cfoot{} %

}
