

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. Shor P. W. Polynomial-time algorithms for prime factorization
and discrete logarithms on quantum computer. \textit{SIAM Journal
of Computing}, 1997, vol.~26, pp. 1484--1509.

2. Yan S. Y. \textit{Quantum attacks on public-key cryptosystems}.
Boston, Springer Publ., 2013, 207~p.

3. \textit{Post-Quantum Cryptography. 9th International
Conference, PQCrypto 2018 Proceedings}. Fort Lauderdale, FL, USA,
April 9--11, 2018. (Lecture Notes in Computer Science, 2018,
vol.~10786.)

4. \textit{Post-Quantum Cryptography. 10th International
Conference, PQCrypto 2019 Proceedings}. Chongqing, China, May
8--10, 2019. (Lecture Notes in Computer Science, 2019,
vol.~11505.)

5. Moldovyan A. A., Moldovyan N. A. Post-quantum signature
algorithms based on the hidden discrete logarithm problem.
\textit{Computer Science Journal of Moldova}, 2018, vol. 26, no.
3(78), pp. 301--313.

6. Moldovyan A. A., Moldovyan N. A. Finite non-commutative
associative algebras as carriers of hidden discrete logarithm
problem. \textit{Bulletin of the South Ural State University.
Series Mathematical Modelling, Programming $\&$ Computer
Software}, 2019, vol.~12, no.~1, pp.~66--81.

7. Moldovyan N. A. Finite non-commutative associative algebras for
setting the hidden discrete lo\-ga\-rithm problem and post-quantum
cryptoschemes on its base. \textit{Bulletin of Academy of Sciences
of Moldova. Mathematics}, 2019, no.~1(89), pp.~71--78.

8. Jozsa R. Quantum algorithms and the fourier transform.
\textit{Proc. Roy. Soc. London. Series A}, 1998, vol.~454,
pp.~323--337.

9. Moldovyan~N. A. Fast signatures based on non-cyclic finite
groups. \textit{Quasigroups and Related Systems}, 2010, vol.~18,
no.~1, pp.~83--94.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 27, 2020.

Accepted: October 23, 2020.

\vskip 6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Nikolay A. Moldovyan} --- Dr. Sci. in Technics,
Professor, Chief Researcher; nmold@mail.ru

\vskip 2mm \textit{Alexandr A. Moldovyan} --- Dr. Sci. in
Technics, Professor, Chief Researcher; maa1305@yandex.ru


}
