

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



 1. {Timoshenko S.}\;\;\emph{Strength of materials.} 3rd
ed. Malabar, Florida, Krieger Publ. Co., 1983, 1010~p.

 2. {Beer F., Russell J. Jr. E., DeWolf J., Mazurek
D.}\;\;\emph{Mechanics of materials.} 7th ed. New York, McGraw
Hill Education Publ., 2014, 896~p.

 3. {Friedman Ya. B.}\;\;\emph{Mekhanicheskiye svoystva
materialov. Ch. 1. Deformatsiya i razrusheniye. $[$Mechanical
properties of metals. Pt 1. The deformation and fracture$]$}.
Moscow, Mashinostroyeniye Publ., 1974, 472~p. (In Russian)

 4. {Schneider S., Schneider S. G., da Silva H. M., De
Moura Neto C.}\;\;Study of the non-linear stress-strain behavior
in Ti--Nb--Zr alloys. \emph{Materials\; Research} [Online], 2005,
vol.~8, pp.~435--438.\\
https://doi.org/10.1590/S1516-14392005000400013

 5. {Schneider S. G., Nunes C. A., Rogero S. O., Higa O.
Z., Bressianil J. C.}\;\;{Mechanical properties and cytotoxic
evaluation of the Ti--3Nb--13Zr alloy. \emph{Biomechanica}, 2000,
vol.~8(1), pp.~84--87.}

 6. {Pavilainen G. V., Yushin R. Yu.}\;\;{Analiz ucheta
uprugoy transversal'noy izotropii i plasticheskoy anizotropii pri
izgibe kruglykh plastin [Analysis of taking into account elastic
transversal isotropy and plastic anisotropy when bending round
plates]. \emph{Vestnik of Saint Petersburg University. Series~1.
Ma\-the\-ma\-tics. Mechanics. Astronomy}, 2011, iss.~1,
pp.~122--131. (In Russian)}

 7. {Pavilainen G. V., Yushin R. Yu.}\;\;{An approximate
solution of elastic-plastic problem of circular strength different
(SD) plates. \emph{CNSA 2017. Constructive Nonsmooth Analysis and
Related Topics (de\-di\-ca\-ted to the memory of V.~F.~Demyanov)
(CNSA).} IEEE, 2017, pp.~7973999.\\
https://doi.org/10.1109/CNSA.2017.7973999}

 8. {\emph{Atlas of stress-strain curves.} 2nd ed.
United States, ASM International Press, 2002, 816~p.}

 9. {Sluzalec A.}\;\;{Stress-strain curve.
\emph{Introduction to nonlinear thermomechanics.} London, Springer
Press, 1992, pp.~45--47.}

 10. {Kariya T., Kurata H.}\;\;{\emph{Generalized least
squares.} England, Chichester, West Sussex, John Wiley \& Sons,
Ltd. Publ., 2004, 307~p.}

 11. {Luenberger D. G.}\;\;{\emph{Optimization by vector
space methods.} London, Wiley-Interscience Press, 1969, 344~p.}

 12. {Lang S.}\;\;{\emph{Algebra.} New York,
Springer-Verlag Press, 2002, xv+914~p.}

 13. {Shimura G.}\;\;{\emph{Arithmetic of quadratic
forms.} New York, Springer-Verlag Press, 2010, xii+238~p.}

 14. {Orekhov A. V.}\;\;{Criterion for estimation of
stress-deformed state of SD-materials. \emph{AIP Conference
Proceedings}, AIP Publ.,  2018, vol.~1959, pp.~070028.
https://doi.org/10.1063/1.5034703}

 15. {Orekhov A. V.}\;\;{Approksimatsionno-otsenochnyye
kriterii napryazhenno-deformiruyemogo sostoyaniya tverdogo tela
[Approximation-evaluation tests for a stress-strain state of
defor- mable solids]. \emph{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2018, vol.~14, iss.~3, pp.~230--242.
https://doi.org/10.21638/11702/spbu10.2018.304} (In Russian)

 16. {Krishnan V.}\;\;{\emph{Probability and random
processes.} Hoboken, New Jersey, John Wiley \& Sons, Inc. Publ.,
2006, 723~p.}

 17. {Ibe O.}\;\;{\emph{Fundamentals of applied
probability and random processes.} San Diego, Academic Press,
2014, 456~p.}

 18. {Lehmann E. L., Romano J. P.}\;\;{\emph{Testing
Statistical Hypotheses}. New York, Springer-Verlag Press, 2005,
xiv+786 p.}

 19. {Wald A.}\;\;{\emph{Sequential Analysis}. New York,
John Wiley \& Sons, Inc. Publ., 1947, 212~p.}

 20. {Chow Y. S.}\;\;{\emph{Great expectations: the
theory of optimal stopping.} Boston, Houghton Mifflin Press, 1971,
139~p.}

 21. {Sirjaev A. N.}\;\;{\emph{Statistical sequential
analysis: Optimal stopping rules.} New York, American Mathematical
Society Press, 1973, 174~p.}

 22. {Chung K. L.}\;\;{\emph{Lectures from Markov
processes to Brownian (Grundlehren Der Mathematischen
Wissenschaften).} New York, Springer-Verlag Press, 1982,
vii+242~p.}

 23. {Shiryaev A. N.}\;\;{\emph{Optimal stopping rules.}
Berlin, Heidelberg, Springer-Verlag Press, 2008, xii+220~p.
https://doi.org/10.1007/978-3-540-74011-7}


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  October 18, 2020.

Accepted: October 23, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Andrey V. Orekhov} --- Senior Lecturer;
a\_v\_orehov@mail.ru\par
%
%
}
