
{\footnotesize


\vskip4mm \noindent {\small \textbf{Литература} }

\vskip3mm


1. \itshape Dolgonos~G., Peslherbe~G. \upshape Conventional and
density-fitting local Moller---Plesset theory calculations of C-60
and its endohedral H-2@C-60 and 2H(2)@C-60 complexes~// Chemical
Physics Letters. 2011. Vol.~513, N~4--6. P.~236--240.

2. \itshape Williams~K., Eklund~C. \upshape Monte Carlo
simulations of H-2 physisorption in finite-diameter carbon
nanotube ropes~// Chemical Physics Letters. 2000. Vol.~320,
N~3--4. P.~352--358.

3. \itshape Koch~ W., Holthausen~ M.~C. \upshape A chemist's guide
to density functional theory. Second ed. Weinheim, Germany:
Wiley-VCH Verlag GmbH, 2001. 306~p.

4.  \itshape Андреева~Т.~А., Бедрина~М.~Е. \upshape Влияние
гибридных потенциалов метода DFT на результаты исследования
жидкокристаллической фазы вещества~// Вестн. С.-Петерб. ун-та.
Сер. 10. Прикладная математика. Информатика. Процессы управления.
2015.  Вып.~1. C.~16--25.

5. \itshape Каплан И. Г. \upshape Введение в теорию
межмолекулярных взаимодействий. М.: Наука, Гл. ред. физ.-мат.
лит., 1982. 312~с.

6. \itshape Semenov~S., Sigolaev~Y., Bedrina~M. \upshape Computer
simulation of the structure of large molecules: 2D
Polybuckminsterfullerenes and their Boraza Analogs with Bisingle
Nitrogen---Boron Bonds~// Russian Journal of General Chemistry.
2009. Vol.~79, N~12. P.~2658--2662.

7. \itshape Райк~А.~В., Бедрина~М.~Е. \upshape Моделирование
процесса адсорбции воды на поверхности кристаллов~// Вестн.
С.-Петерб. ун-та. Сер.~10. Прикладная математика. Информатика.
Процессы управления. 2011. Вып.~2. C.~67--75.

8. \itshape Andreeva~T., Bedrina~M., Egorov~N. \upshape
Dimerization of 4-cyano-4$'$-$n$-pentylbiphenyl in vacuum and
under constant electric field~// Journal of Vacuum Science and
Technology B.  2015.  Vol.~33, N~3. P.~03D102--1--7.

9. \itshape Lee~C., Yang~W., Parr~R.~G.  \upshape Development of
the Colle---Salvetti correlation-energy formula into a functional
of the electron density~// Physical Review B. 1988. Vol.~37.
P.~785--789.

10. \itshape Perdew~J., Ernzerhof~M., Burke~K. \upshape Rationale
for mixing exact exchange with density functional
approximations~// Journal of Chemical Physics.  1996. N~105.
P.~9982--9985.

11. \itshape Frisch~M.~J., Trucks~G.~W., Schlegel~H.~B. \upshape
et al. GAUSSIAN-09, Rev. C.01. Wallingford, CT: Gaussian Inc.,
2010.

12. \itshape Francl ~M.~M., Pietro~W.~J., Hehre~W.~J., Binkley~
J.~S., Gordon~ M.~S.  \upshape Selfconsistent molecular orbital
methods. XXIII. A polarizationtype basis set for secondrow
elements~// The Journal of Chemical Physics. 1982. Vol.~77.
P.~3654--3665.

13. \itshape Leininger~T., Nicklass~A., Stoll~H., Dolg~M.,
Schwerdtfeger~P.  \upshape The accuracy of the pseudopotentials
approximation. II. A comparison of various core sizes for indium
pseudopotentials in calculations for spectroscopic constants of
InH, InF, and InCl~// The Journal of Chemical Physics. 1996.
Vol.~105. P.~1052--1059.

14. \itshape Hay~P.~J., Wadt~W.~R.  \upshape Ab initio effective
core potentials for molecular calculations. Potentials for the
transition metal atoms Sc to Hg~// The Journal of Chemical
Physics. 1985. Vol.~82. P.~270--283.



\vskip 2mm

{\bf Для цитирования:}  {\it Васильев А.~А.,~Бедрина
M.~Е.,~Андреева Т.~А.} Зависимость результатов расчета по методу
функционала электронной плотности от способа представления
волновой функции
// Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~14.
Вып.~\issuenum. С.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06



}
