{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2.5mm
%%%%%%%%%%%â òðàíñëèò






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

1. \upshape Dolgonos~G., Peslherbe~G. \upshape Conventional and
density-fitting local Moller---Plesset theory calculations of C-60
and its endohedral H-2@C-60 and 2H(2)@C-60 complexes. \itshape
Chemical Physics Letters, \upshape 2011, vol.~513, no.~4--6,
pp.~236--240.

2. \upshape Williams~K., Eklund~C.  Monte Carlo simulations of H-2
physisorption in finite-diameter carbon nanotube ropes. \itshape
Chemical Physics Letters, \upshape 2000, vol.~320, no.~3--4,
pp.~352--358.

3. \upshape Koch~W., Holthausen~ M.~C. \itshape A chemist's guide
to density functional theory. \upshape Second ed. Weinheim,
Germany, Wiley-VCH Verlag GmbH Press, 2001, 306~p.

4.  \upshape Andreeva~T.~A., Bedrina~M.~E. Vliianie gibridnykh
potentsialov metoda DFT na rezul'taty issledovaniia
zhidkokristallicheskoi fazy veshchestva [The influence of hybrid
potentials of the DFT method on the results of study of liquid
crystal phase of a substance]. {\it Vestnik of Saint Petersburg
State University. Series 10. Applied Mathematics. Computer
Science. Control Processes},   2015,  iss.~1, pp.~16--25. (In
Russian)

5. \upshape Kaplan I. G. \itshape Vvedenie v teoriiu
mezhmolekuliarnykh vzaimodeistvii $[$Introduction to the theory of
intermolecular interactions$]$. \upshape Ìoscow, Nauka Publ.,
1982, 312~p.  (In Russian)

6. \upshape Semenov~S., Sigolaev~Y., Bedrina~M.  Computer
simulation of the structure of large molecules: 2D
Polybuckminsterfullerenes and their Boraza Analogs with Bisingle
Nitrogen---Boron Bonds. \itshape Russian Journal of General
Chemistry, \upshape 2009, vol.~79, no.~12, pp.~2658--2662.

7. \upshape Raik~A.~V., Bedrina~M.~E. Modelirovanie protsessa
adsorbtsii vody na poverkhnosti kristallov [Modeling of water
adsorption process on crystal surfaces]. \itshape Vestnik of Saint
Petersburg State University. Series 10. Applied Mathematics.
Computer Science. Control Processes, \upshape 2011, iss.~2,
pp.~67--75.  (In Russian)

8. \upshape Andreeva~T., Bedrina~M., Egorov~N. Dimerization of
4-cyano-4$'$-$n$-pentylbiphenyl in vacuum and under constant
electric field. \itshape Journal of Vacuum Science and Technology
B, \upshape 2015,  vol.~33, no.~3, pp.~03D102--1--7.

9. \upshape Lee~C., Yang~W., Parr~R.~G.  Development of the
Colle---Salvetti correlation-energy formula into a functional of
the electron density.  \itshape Physical Review B,  \upshape 1988,
vol.~37, pp.~785--789.

10. \upshape Perdew~J., Ernzerhof~M., Burke~K.  Rationale for
mixing exact exchange with density functional approximations.
\itshape Journal of Chemical Physics,  \upshape 1996, no.~105,
pp.~9982--9985.

11. \upshape Frisch~M.~J., Trucks~G.~W., Schlegel~H.~B. et al.
\itshape GAUSSIAN-09, Rev. C.01. \upshape Wallingford, CT,
Gaussian Inc., 2010.

12. \upshape Francl ~M.~M., Pietro~W.~J., Hehre~W.~J., Binkley~
J.~S., Gordon~ M.~S.  Selfconsistent molecular orbital methods.
XXIII. A polarizationtype basis set for secondrow elements.
\itshape The Journal of Chemical Physics,  \upshape 1982, vol.~77,
pp.~3654--3665.

13. \upshape Leininger~T., Nicklass~A., Stoll~H., Dolg~M.,
Schwerdtfeger~P.  The accuracy of the pseudopotential
approximation. II. A comparison of various core sizes for indium
pseudopotentials in calculations for spectroscopic constants of
InH, InF, and InCl. \itshape The Journal of Chemical Physics,
\upshape 1996, vol.~105, pp.~1052--1059.

14. \upshape Hay~P.~J., Wadt~W.~R.   Ab initio effective core
potentials for molecular calculations. Potentials for the
transition metal atoms Sc to Hg. \itshape The Journal of Chemical
Physics, \upshape 1985, vol.~82, pp.~270--283.




\vskip 2mm

{\bf For citation:} Vasiliev A.~A.,~Bedrina M.~E.,~Andreeva T.~A.
The dependence of calculation results on the density functional
theory from the means of presenting the wave function. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~14,
iss.~\issuenum, pp.~\pageref{p6}--\pageref{p6e}.
\doivyp/spbu10.\issueyear.\issuenum06


}
