
\zageng{517.956.45}{V.~V.~Provotorov$^1$,~V.~I.~Ryazhskikh$^2$
,~Yu.~A.~Gnilitskaya$^3$}{UNIQUE WEAK SOLVABILITY OF A NONLINEAR
INITIAL\\ BOUNDARY VALUE PROBLEM
WITH DISTRIBUTED PARAMETERS\\ IN A NETLIKE DOMAIN%$^*$
}{



\vspace{-3mm}\parindent=7mm



%{\copyright} А.~В.~Буре, 2014

\textit{Provotorov Vyacheslav Vasil'evich} --- doctor of physical
and mathematical sciences, professor; wwprov@mail.ru

\textit{Ryazhskikh Viktor Ivanovich} --- doctor of engineering
sciences, professor;  ryazhskih$\_$vi@mail.ru

\textit{Gnilitskaya Yuliya Aleksandrovna} --- PhD of  physical and
mathematical sciences, teacher;\\ uliya$\_$al@mail.ru


\vskip 2mm

\emph{Провоторов Вячеслав Васильевич} --- доктор
физико-математических наук, профессор;\\ wwprov@mail.ru

\emph{Ряжских Виктор Иванович} --- доктор технических наук,
профессор; ryazhskih$\_$vi@mail.ru

\emph{Гнилицкая Юлия Александровна} --- кандидат
физико-математических наук, преподаватель; uliya$\_$al@mail.ru

\vskip 2mm

%$^*$ Работа выполнена при финансовой поддержке
%Санкт-Петербургского государственного университета (грант №
%9.38.205.2014).


{\copyright} Санкт-Петербургский государственный университет,
\issueyear %

}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp03 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum04}}\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp03 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum04}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




{\footnotesize

\noindent $^1$ Voronezh State University,  1, Universitetskaya
square, Voronezh,

\noindent\hskip2.45mm 394006, Russian Federation


\noindent $^2$ Voronezh State Technical University,  14,
Moskovskii pr., Voronezh,

\noindent\hskip2.45mm 394026, Russian Federation



\noindent $^3$
Air~Force~Academy~named~after~professor~N.~E.~Zhukovsky~and~Y.~A.~Gagarin,


\noindent\hskip2.45mm  54a, ul. Starikh Bol'shevikov, Voronezh,


\noindent\hskip2.45mm   396064, Russian Federation




\vskip3mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item This paper considers a fairly wide range of issues
related to the solvability of the initial boundary value problem
of the Navier---Stokes equations with distributed parameters on
the net like region of the space ${\rm {\mathcal R}}^{n} $ ($n\ge
2$). The authors here develop an idea, advanced in their work for
the case of $n=1$ (the problems with distributed parameters on the
graph), in the direction of the dimension increase $n$ and in
forming the correct Hadamard conditions for the studied initial
boundary value problem. The general scheme of the study is
classical: the problem is solved in the functional space which is
selected (the space of feasible solutions) and a special basis is
formed for it, the problem of approximate solutions is settled by
the Faedo---Galerkin method, for which a priori estimates of the
energy inequalities type are set and the weak compactness of the
family of these solutions is shown based on these estimates. Using
non-burdensome conditions, the smoothness of the solution to the
time variable is demonstrated. The uniqueness of the weak solution
is shown in the particular case $n=2$, a feature quite often
encountered in practice. The estimate for the norm of weak
solution makes it possible to establish the continuous dependence
of the weak solution from the initial data of the problem. The
results obtained in this way are of interest to applications in
the field of fluid mechanics and related sections of continuum
mechanics, namely for the analysis of optimum control dynamics
problems of multiphase media. It should be noted that the methods
and approaches can be broadly generalized and are applicable to a
wide class of nonlinear problems. Refs~20.

{\it Keywords}: boundary value problem, distributed parameters on
the netlike domain, the existence of a weak solution, the
uniqueness conditions, Hadamard correctness.

\end{list}

}

\vskip4mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it В.~В. Провоторов$^1$, В.~И. Ряжских$^2$, Ю.~А.
Гнилицкая$^3$}

\vskip4mm \noindent{\bf ОДНОЗНАЧНАЯ СЛАБАЯ РАЗРЕШИМОСТЬ
НЕЛИНЕЙНОЙ\\ НАЧАЛЬНО-КРАЕВОЙ ЗАДАЧИ С~РАСПРЕДЕЛЕННЫМИ\\
ПАРАМЕТРАМИ В~СЕТЕПОДОБНОЙ ОБЛАСТИ}

\vskip1.8mm


{\footnotesize


\noindent $^1$~Воронежский государственный университет, Российская
Федерация,

\noindent\hskip2.45mm 394006, Воронеж, Университетская площадь, 1

\newpage

\noindent $^2$~Воронежский государственный технический
университет, Российская Федерация,

\noindent\hskip2.45mm 394026, Воронеж, Московский пр., 14


\noindent $^3$~Военно-воздушная академия имени профессора
Н.~Е.~Жуковского и~Ю.~А.~Гагарина,

\noindent\hskip2.45mm Российская Федерация, 396064, Воронеж, ул.
Старых большевиков, 54a

\vskip5mm


\item В работе рассматривается достаточно широкий
круг вопросов, относящихся к разрешимости начально-краевой задачи
типа Навье---Стокса с распределенными параметрами на сетеподобной
области ${\rm {\mathcal R}}^{n} $ ($n\ge 2$). Развиваются идеи,
представленные в работах авторов для случая $n=1$ (задачи с
распределенными параметрами на графе), в направлении увеличения
размерности $n$ и формируются условия корректности по Адамару
изучаемой начально-краевой задачи. Общая схема исследования
остается классической: выбирается функциональное пространство, в
котором решается задача (пространство допустимых решений) и
формируется специальный базис для него, строятся приближения
решений задачи по методу Фаэдо---Галеркина, для них
устанавливаются априорные оценки типа энергетических неравенств и
на основе этих оценок показывается слабая компактность
построенного семейства решений. С помощью необременительных
дополнительных условий находится гладкость решения по временной
переменной. Единственность слабого решения рассматривается для
частного случая $n=2$, достаточно часто встречающегося на
практике. Оценка для нормы слабого решения дает возможность
установить непрерывную зависимость слабого решения от исходных
данных задачи. Результаты, полученные таким путем, представляют
интерес для приложений в области гидромеханики и смежных разделах
механики сплошных сред, а именно, для анализа задач оптимального
управления динамикой многофазных сред. Следует отметить, что
используемые методы и подходы обладают достаточно большой
общностью и применимы к широким классам нелинейных задач.
Библиогр. 20~назв.

\textit{Ключевые слова}: начально-краевая задача, распределенные
параметры на сетеподобной области, существование слабого решения,
условия единственности, корректность по Адамару, слабые решения,
оптимальное граничное управление, синтез управления,
управляемость.


}

\end{list}


\vskip2.5mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{Introduction.} This paper considers the existence of a
weak solution of an $n$-dimensional nonlinear differential system
with distributed parameters in a connected bounded netlike domain,
which represents a geometric graph in the one-dimensional case. We
introduce the space of admissible solutions and, using the
Faedo---Galerkin method, establish the existence of a solution
from the class of summable on a netlike domain functions. Taking
into account the specifics of the Faedo---Galerkin method for the
construction of approximate solutions in form of cut-off
functions, we demonstrate that each such solution actually belongs
to the space of functions with summable derivatives with respect
to the time variable; the elements of this space satisfy an analog
of the energy balance equation. The uniqueness of a weak solution
is proved for the special case $n=2$. The obtained results can be
used to analyze optimal control problems for differential
distributed parameter systems in netlike domains, which have
interesting analogies with multiphase problems of hydrodynamics.
The paper continues the earlier research of~[1--3].


\textbf{Necessary notations, concepts and definitions.} Consider
an open bounded domain $\Im$ of the Euclidean space $\mathbb{R}^n$
($n\geq2$) that has a netlike structure~[1], i.~e.
$\Im=(\bigcup\limits_k\Im_k)\bigcup(\bigcup\limits_lS_l)$, where
$S_l$ is a surface that separates adjacent domains $\Im_k$,
$\partial\Im$ indicates the boundary of $\Im$. The locus of
conjugation of the adjacent domains $\Im_k$ will be called the
node locus and further denoted by $\xi$; it represents the union
of surfaces $S_l(\xi)$ whose number coincides with the number of
conjugated domains, that is, $\xi=\bigcup\limits_l S_l(\xi)$.

For a vector function $Y(x,t)=\{y_1(x,t),y_2(x,t),...,y_n(x,t)\}$
($x=\{x_1,x_2,...,x_n\}$) defined in a domain
$\Im_T=\Im\times(0,T)$ ($T<\infty$), consider the system

\begin{equation}\label{eq25}
{{\begin{array}{*{20}c} \frac{\partial Y}{\partial t}-\nu\triangle
Y+\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial x_i}=
f-\text{grad} \,p,
 \end{array} }}
\end{equation}
\begin{equation}\label{eq26}
{{\begin{array}{*{20}c} \text{div} Y=0\left(\sum\limits_{i=1}^n
\frac{\partial Y}{\partial x_i}=0\right)
 \end{array} }}
\end{equation}
with the relationships
\begin{equation}\label{eq27}
{{\begin{array}{*{20}c} Y|_{S^-_l(\xi)}=Y|_{S^+_l(\xi)},
 \end{array} }}
\end{equation}
\begin{equation}\label{eq28}
{{\begin{array}{*{20}c} \sum \limits_{l}\frac{\partial Y}{\partial
n^-_l}|_{S^-_l(\xi)}+\sum \limits_{l}\frac{\partial Y}{\partial
n^+_l}|_{S^+_l(\xi)}=0,
 \end{array} }}
\end{equation}
holding for each node locus $\xi$ (which are known in the
literature as the conjugation conditions, see~[3, 4]); here
$S^-_l(\xi)$ and $S^+_l(\xi)$ mean the unilateral surfaces for
$S_l(\xi)$ defined by the direction of the normals $n^-_l$ and
$n^+_l$ to the surfaces $S^-_l(\xi)$ and $S^+_l(\xi)$,
respectively. Supplementing (1)--(4) with the initial conditions
\begin{equation}\label{eq29}
{{\begin{array}{*{20}c} Y(x,0)=Y_0(x), \,x\in \Im
 \end{array} }}
\end{equation}
at time $t=0$ and the boundary conditions
\begin{equation}\label{eq30}
{{\begin{array}{*{20}c} Y|_{\partial\Im}=0,
 \end{array} }}
\end{equation}
we obtain the initial boundary value problem~(1)--(6) to find the
functions $Y(x,t)$ and $p(x,t)$ in the closed domain
$\overline{\Im}_T=(\Im\cup\partial\Im)\times[0,T]$.

In the applied problems of hydrodynamics, the netlike domain $\Im$
is actually a hydrosystem that distributes the flows of a fluid (a
multiphase medium); the function $Y(x,t)$ describes the velocity
vector of the hydraulic flow in the domain $\Im_T$;
relationships~(1), (2) (the Navier---Stokes system in the
evolutionary case [5, 6]) reflect the dynamics of an
incompressible fluid with the coefficient of viscosity $\nu>0$ in
the domain $\bigcup\limits_k\Im_k\times(0,T)$; the balance
equalities (3), (4) define the fluid flow conditions in the node
loci of the hydrosystem~$\Im$.

Let us define a weak solution of the initial boundary value
problem~(1)--(6) (a turbulent solution in the terminology of~[1]).
To this end, introduce necessary spaces and present preliminary
considerations.

Designate by $L_2(\Im)^n$ the space of measurable functions
(classes) $\mu=\{\mu_1,\mu_2,...,\mu_n\}$ that are square summable
over the domain $\Im$. For $\mu,\rho \in L_2(\Im)^n$, the scalar
product is defined by
\begin{equation}\label{eq31}
{{\begin{array}{*{20}c}
\left(\mu,\rho\right)=\sum\limits_{i=1}^n\int\limits_\Im\mu_i(x)\rho_i(x)dx,
 \end{array} }}
\end{equation}
where $\|\mu\|=(\mu, \mu)^{1/2}$. Assume that $D(\Im)^n$ forms the
space of functions that are infinitely differentiable in the
domain $\Im$ and have compact supports in $\Im$.

Let $\mathfrak{D}(\Im)^n=\{\phi: \phi\in D(\Im)^n$, div$\phi =0\}$
and denote by $\mathfrak{D}'(\Im)^n$ the conjugate space for
$\mathfrak{D}(\Im)^n$ (here and in the sequel, the symbol $'$
indicates conjugate spaces). Define the space $\mathcal{H}(\Im)$
as the closure of $\mathfrak{D}(\Im)^n$ in the norm $L_2(\Im)^n$
with the scalar product~(7),
$\|\mu\|_{\mathcal{H}(\Im)}=\left(\mu,\mu\right)^{1/2}$ and
$\mathcal{H}(\Im)=\mathcal{H}(\Im)'$.

Consider a space $\mathcal{H}^1(\Im)$ consisting of the elements
$\mu\in L_2(\Im)^n$ that have the generalized derivative
$\frac{\partial\mu}{\partial x}\in L_2(\Im)^n$, i.~e.
$\frac{\partial\mu}{\partial x_i}\in L_2(\Im)$,
$i=\overline{1,n}$. The space $\mathcal{H}^1(\Im)$ is equipped
with the norm
$\|\mu\|_{\mathcal{H}^1(\Im)}=(\|\mu\|^2_{L_2(\Im)}+\|\frac{\partial\mu}{\partial
x}\|^2_{L_2(\Im)})^{1/2}$ and represents a Hilbert space with the
scalar product
$\left(\mu,\rho\right)_{\mathcal{H}^1(\Im)}=(\mu,\rho)+(\frac{\partial\mu}{\partial
x},\frac{\partial\rho}{\partial x})$.

Next, define a space $V^1_{\,0}(\Im)$ as the closure in the norm
$\mathcal{H}^1(\Im)$ for the set of elements
$\mu\in\mathfrak{D}(\Im)^n$ satisfying the conjugation conditions
\[
{{\begin{array}{*{20}c} \sum \limits_{l}\frac{\partial
\mu}{\partial n^-_l(\xi)}|_{S^-_l(\xi)}+\sum
\limits_{l}\frac{\partial \mu}{\partial n^+_l}|_{S^+_l(\xi)}=0.
 \end{array} }}
\]
In other words, $V^1_{\,0}(\Im)$ is the subspace of functions from
$\mathcal{H}^1(\Im)$ that ``satisfy the conjugation conditions''
in all node loci $\xi$ of the domain $\Im$ and ``vanish'' on
$\partial\Im$.

Consider the two forms
\begin{equation}\label{eq32}
{{\begin{array}{*{20}c} \rho(u,v)=
\sum\limits_{i,j=1}^n\int\limits_{\Im}\frac{\partial u_j}{\partial
x_i}\frac{\partial v_j}{\partial x_i}dx,
\end{array} }}
\end{equation}

\begin{equation}\label{eq33}
{{\begin{array}{*{20}c} \varrho(u,v,\omega)=
\sum\limits_{i,k=1}^n\int\limits_{\Im}u_k \frac{\partial
v_i}{\partial x_k} \omega_idx
\end{array} }}
\end{equation}
in functions $u,v,\omega$ such that the integrals in the
representations above are convergent.

First, prove several auxiliary results that are similar to the
ones in [5, p.~79--81; 6, p.~71].

\textbf{Lemma 1.} \emph{The bilinear} (8) \emph{and trilinear} (9)
\emph{forms are continuous on ${V}^1_{\,0}(\Im)\times
{V}^1_{\,0}(\Im)$ and $L_4(\Im)^n\times {V}^1_{\,0}(\Im)\times
L_4(\Im)^n$, respectively}.

P\,r\,o\,o\,f.\, Applying the Cauchy---Bunyakowsky---Schwartz
inequality to the functions $\frac{\partial u_j}{\partial x_i}$
and $\frac{\partial v_j}{\partial x_i}$ in the right-hand side of
form~(8) yields
\begin{equation}\label{eq34}
{{\begin{array}{*{20}c} \big|\int\limits_{\Im}\frac{\partial
u_j}{\partial x_i}\frac{\partial v_j}{\partial x_i}dx\big|\leq
\sqrt{\int\limits_{\Im}\big(\frac{\partial u_j}{\partial
x_i}\big)^2dx}\sqrt{\int\limits_{\Im}\big(\frac{\partial
v_j}{\partial
x_i}\big)^2dx}\leq\|u_j\|_{V^1_0(\Im)}\|v_j\|_{V^1_0(\Im)}.
\end{array} }}
\end{equation}
By analogy, using the Cauchy---Bunyakowsky---Schwartz inequality
in the right-hand side of form~(9), first for the functions $u_k
\omega_i$ and $\frac{\partial v_i}{\partial x_k}$ and then for the
functions $u^2_k$ and $\omega^2_i$, we obtain
%\begin{equation}\label{eq35}
%{{\begin{array}{*{20}c} %
\begin{equation*}
\begin{array}
~\big| \int\limits_{\Im}u_k \frac{\partial v_i}{\partial x_k}
\omega_idx \big| \leq \sqrt{\int\limits_{\Im}(u_k
\omega_i)^2dx}\sqrt{\int\limits_{\Im}(\frac{\partial v_j}{\partial
x_i})^2dx}\leq %
\\ %
% \notag \\ %
\end{array}
\end{equation*}
\begin{equation}
\begin{array}
~\leq\sqrt[4]{\int\limits_{\Im}u^4_k dx}
\sqrt{\int\limits_{\Im}\big(\frac{\partial v_j}{\partial
x_i}\big)^2dx}\sqrt[4]{\int\limits_{\Im}\omega_i^4dx}\leq
\|u_k\|_{L_4(\Im)}\|v_j\|_{V^1_0(\Im)}\|\omega_i\|_{L_4(\Im)}.
%\end{array} }}
%\end{equation}
 \label{eq35}
\end{array}
\end{equation}

\noindent And the statement of this lemma follows from
inequalities~(10) and (11).

\textbf{Corollary.} Inequality~(11) implies the continuity of
form~(9) on $({V}^1_{\,0}(\Im)\cap L_4(\Im)^n)\times
{V}^1_{\,0}(\Im)\times L_4(\Im)^n$.

\textbf{Lemma~2.} \emph{For any $u,\omega\in {V}^1_0(\Im)$, the
following equalities are just}:

1) $\varrho(u,u,\omega)= -\varrho(u,\omega,u)$;

2) $\varrho(u,\omega,\omega)=0$;

3) $\varrho(\omega,\omega,\omega)=0$.

P\,r\,o\,o\,f.\, The first statement of this lemma follows from
representation~(9) on integrating by parts the integrals in all
terms over the domain $\Im$. Recall that the functions of the
class $V^1_{\,0}(\Im)$ vanish on the boundary $\partial\Im$. And
the second and third statements are a direct consequence of the
first one.

\textbf{Lemma~3.} \emph{Let sequences $\{u_m\}_{m\geq1}$ and
$\{v_m\}_{m\geq1}$ from $L_2(\Im)^n$ weakly converge in
$L_2(\Im)^n$ to elements $u$ and $v$, respectively. Then the
sequence $\{u_m v_m\}_{m\geq1}$ has weak convergence in
$L_2(\Im)^n$ to the element $uv$.}

P\,r\,o\,o\,f.\, It is necessary to show that
\[
{{\begin{array}{*{20}c} \int\limits_{\Im_T}u_m v_m\zeta dxdt
\mathop{\rightarrow}\limits_{m\rightarrow\infty}
\int\limits_{\Im_T}uv \zeta dxdt
\end{array} }}
\]
for any function $\zeta(x)\in \mathfrak{D}(\Im)^n$ satisfying the
conjugation conditions at all node loci $\xi$ of the domain $\Im$
(or for any $\zeta(x)\in V^1_{\,0}(\Im)$, due to the density of
the set of such functions in $V^1_{\,0}(\Im)$).

First, we take notice of an important fact ensuing from the weak
convergence of the sequences $\{u_m\}_{m\geq1}$ and
$\{v_m\}_{m\geq1}$: the elements $u_m$ and $v_m$ are collectively
bounded, i.~e. $\|v_m\|_{L_2(\Im)^n}+\|v\|_{L_2(\Im)^n}\leq c$ and
$\|u_m\|_{L_2(\Im)^n}+\|u\|_{L_2(\Im)^n}\leq c$. At the beginning,
demonstrate that the sequence $\{v_m\zeta\}_{m\geq1}$ strongly
converges to $v\zeta$ in the space $L_2(\Im)^n$. Let $\epsilon >0$
be an arbitrarily small number. As $\zeta(x)$, it is possible to
choose $\frac{\epsilon}{\|\zeta\|_{L_2(\Im)^n}}\zeta(x)$; then the
desired result follows from the chain of inequalities:
\[
{{\begin{array}{*{20}c} \|v_m\zeta-v\zeta\|_{L_2(\Im)^n}\leq
\|v_m-v\|_{L_2(\Im)^n}\|\zeta\|_{L_2(\Im)^n}\leq
\epsilon(\|v_m\|_{L_2(\Im)^n}+\|v\|_{L_2(\Im)^n})\leq\epsilon c.
\end{array} }}
\]

The statement of Lemma~3 is obvious from the estimates
\[
{{\begin{array}{*{20}c} \big|\int\limits_{\Im}u_m v_m\zeta
dx-\int\limits_{\Im}uv \zeta dx\big|= \int\limits_{\Im}\big|(u_m
v_m-uv) \zeta\big| dx\leq
\\
\leq\int\limits_{\Im}\left(\|u_m\|_{L_2(\Im)^n}
\|v_m\zeta-v\zeta\|_{L_2(\Im)^n}+ \|v\|_{L_2(\Im)^n}
\|u_m\zeta-u\zeta\|_{L_2(\Im)^n}\right)dx
\end{array} }}
\]
and the considerations above. The proof of Lemma~3 is finished.

Introduce the spaces of functions $u(x,t)$ of the variables
$x,t\in \Im_T=\Im\times(0,T)$ ($T<\infty$) and consider $u$ as a
function of $t$ taking values in the space of functions of $x$.
Particularly, if $V$ represents a Hilbert space, then denote by
$L_2(0,T;V)$ the space of functions (classes) $u: (0,T)\rightarrow
V$ that are measurable, take values from $V$ and
\[
{{\begin{array}{*{20}c}
\|u\|_{L_2(0,T;V)}=\left(\int\limits_{0}^T\|u(t)\|^2_Vdt\right)^{1/2}<\infty.
 \end{array} }}
\]
Note that the equality $L_2(\Im_T)^n=L_2(0,T;L_2(\Im)^n)$ holds
naturally.

Next, introduce the following spaces: $W^{1,0}(\Im_{T})$ as the
space of functions $u(x,t)\in L_{2}(\Im_{T})^n$ that have the
generalized first derivative with respect to $x$ belonging to
$L_{2}(\Im_{T})^n$, with the norm in $W^{1,0}(\Im_{T})$ defined by
\[
{{\begin{array}{*{20}c} \|u\|_{W^{1,0}(\Im_{T})}=
\left(\|u\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
x}\|^2_{L_2(\Im_T)^n}\right)^{1/2};
 \end{array} }}
\]
$W^{1}(\Im_{T})$ as the space of functions from $L_{2}(\Im_T)^n$
that have the generalized first derivatives also belonging to
$L_{2}(\Im_T)^n$, with the norm defined by
\[
{{\begin{array}{*{20}c} \|u\|_{W^{1}(\Im_{T})}=
\left(\|u\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
t}\|^2_{L_2(\Im_T)^n}+\|\frac{\partial u}{\partial
x}\|^2_{L_2(\Im_T)^n}\right)^{1/2}.
 \end{array} }}
\]

Using the properties of the traces of elements from
$W^{1}(\Im_{T})$ on each section of $\Im_{T}$ by the plane $t=t_0$
($t_0\in [0,T]$) as elements of $L_2(\Im)^n$ that are continuous
in $t$ in the norm $L_2(\Im)^n$  (see $[7$, p.~$70]$), define
${\Omega}_0(\Im_{T})$ as the set of functions $u(x,t)\in
W^{1}(\Im_{T})$ belonging to the class $V^1_{\,0}(\Im)$ for fixed
$t\in [0,T]$. Denote by $W_{\,0}^{1}(\Im_{T})$ the closure of the
set ${\Omega}_0(\Im_{T})$ in the norm $W^{1}(\Im_{T})$.

Next, let $\widehat{\Omega}_0(\Im_{T})$ be the set of all
functions $u(x,t)\in W^{1,0}(\Im_{T})$ that

a) have the finite norm
\begin{equation}\label{eq36}
{{\begin{array}{*{20}c} \|u\|_{2,\Im_{T}}=
\mathop{\max}\limits_{0\leq t\leq
T}\left\|u(\cdot,t)\right\|_{L_{2}(\Im)^n}+\left\|\frac{\partial
u}{\partial x}\right\|_{L_{2}(\Im_{T})^n};
\end{array} }}
\end{equation}

b) have the trace defined on the sections of the domain $\Im_{T}$
by the plane $t=t_0$ ($t_0\in[0,T]$) as a function of the class
$V^1_0(\Im)$, i.~e. for each element $u\in
\widehat{\Omega}_0(\Im_{T})$ and fixed $t\in [0,T]$, there exists
a sequence $\{u_n\}$ of functions $u_n(x,t)\in V^1_{\,0}(\Im)$
converging to this trace in the norm $\mathcal{H}^1(\Im)$;

c) for each $t\in[0,T]$, belong to the space $V^1_{\,0}(\Im)$ and
are continuous in $t$ in the norm $\mathcal{H}^1(\Im)$ on $[0,T]$,
i.~e. for any $t\in[0,T]$, $\|u(\cdot,t+\Delta
t)-u(\cdot,t)\|_{\mathcal{H}^1(\Im)}\rightarrow 0$ as $\Delta t
\rightarrow 0$ uniformly on the interval $[0,T]$.

Designate by $V_{\,\,0}^{1,0}(\Im_{T})$ the closure of the set
$\widehat{\Omega}_0(\Im_{T})$ in norm~(12); clearly,
$V_{\,0}^{1,0}(\Im_{T})\subset W^{1,0}(\Im_{T})$.

\textbf{Remark~1.} If $Y\in V_{\,\,0}^{1,0}(\Im_{T})$, then $Y=0$
on $\partial\Im$, i.~e. relationships~(3), (4), and (6) should be
treated as the conditions of belonging of $Y$ to the space
$V_{\,\,0}^{1,0}(\Im_{T})$. Equality~(5) is considered almost
everywhere on $\Im$.

\textbf{Remark~2.} The statements of Lemmas~1--3 remain in force
for the functions that are defined in the domain
$\Im_\tau=\Im\times(0,\tau)$ and have traces for any
$t\in(0,\tau)$, where $\tau$ takes any fixed value within the
interval $[0,T]$. The proofs of these results are exactly the
same.

Remark~2 naturally leads to the following definition of a solution
of problem (1)--(6), where the initial data (i.~e. the functions
$f$ and $Y_0$) satisfy the conditions
\begin{equation}\label{eq37}
{{\begin{array}{*{20}c} f(x,t)\in L_{2,1}(\Im_T),\quad Y_0(x)\in
\mathcal{H}(\Im).
\end{array} }}
\end{equation}
Here $L_{2,1}(\Im_T)$ is a space whose elements belong to
$L_1(\Im_T)$ and have the finite norm
$\|f\|_{L_{2,1}(\Im_T)}=\int\limits_0^T\left(\int\limits_\Im f^2dx
\right) ^{1/2}dt$,~ $L_{2}(\Im_T)\subset L_{2,1}(\Im_T)$.

\textbf{Definition.} \emph{A weak solution of the initial boundary
value problem} (1)--(6) \emph{is a pair $\{Y,p\}$ as follows. The
function $Y(x,t)\in V_{\,0}^{1,0}(\Im_{T})$ satisfies the integral
identity}
%\begin{equation}\label{eq38}
%{{\begin{array}{*{20}c}%
\begin{equation*}
\begin{array}
~(Y(x,t),\eta(x,t))-\int\limits_{\Im_t}Y(x,\tau)\frac{\partial\eta(x,\tau)}{\partial
\tau}dxd\tau+
\nu\int\limits_0^t\rho(Y,\eta)d\tau+\int\limits_0^t\varrho(Y,Y,\eta)d\tau=
\\
\end{array}
\end{equation*}
\begin{equation}\label{eq38}
\begin{array}
~=(Y_0(x),\eta(x,0))+\int\limits_{\Im_t}f(x,\tau)\eta(x,\tau)dxd\tau
\end{array} }}
\end{equation}
\emph{for any $t\in[0,T]$ and any $\eta(x,t)\in
W_{\,0}^{1}(\Im_{T})$, while the function $p(x,t)$ belongs to the
class $\mathfrak{D}'(\Im_T)^n$. Here $\mathfrak{D}'(\Im_T)^n$ is
the conjugate space for the space $\mathfrak{D}(\Im_T)^n$, the
elements of $\mathfrak{D}(\Im_T)^n$ are infinitely differentiable
in $\Im_T$ functions with a compact support from $\Im_T$ $($see
the analogous spaces $\mathfrak{D}(\Im)^n$ and
$\mathfrak{D}'(\Im)^n$$)$.}

\textbf{Remark~3.} Despite the apparent rigor, the above
definition of a solution of problem~(1)--(6) (i.~e. a pair
$\{Y,p\}$) has the explicit ambiguity caused by the variational
statement~(14) of this problem ``eliminating'' the function
$p(x,t)$. Notably, there is no information concerning the function
$p(x,t)$ except for relationship~(14), and hence \emph{it suffices
to find an appropriate function $p(x,t)$ within the class}, i.~e.
$p(x,t)\in \mathfrak{D}'(\Im_T)^n$. In terms of applications, this
is an acceptable condition that guarantees the nonzero fluid
dynamics in the domain $\Im_{T}$ (as a matter of fact, in many
applications $p(x,t)$ is an a priori given function). According to
the aforesaid, in the sequel we consider the function $Y(x,t)$ as
a ``solution'' of problem~(1)--(6); the existence of the function
$p(x,t)$ and its belonging to the class $\mathfrak{D}'(\Im_T)^n$
directly follow from the existence of $Y(x,t)$ within the class
$V_{\,0}^{1,0}(\Im_{T})$.\newpage

The forthcoming sections are dedicated to the existence of a weak
solution of the initial boundary value problem~(1)--(6). Some
considerations are similar to the ones presented in~[5, p. 77].


\textbf{Existence of weak solution of problem (1)--(6).} The idea
to prove the existence of at least one weak solution of
problem~(1)--(6) remains the same as in~[4, 8] for similar
distributed parameter problems on a geometrical graph (network),
but there is an essential difference that forms the main obstacle.
In particular, the domain of variation of the spatial variable in
problem~(1)--(6) is the bounded domain $\Im$ of the Euclidean
space $\mathbb{R}^n$, i.~e. the spatial variable and the function
$Y(x,t)$ are both \emph{vectors}. This feature causes additional
technical difficulties, mostly affecting the structure and
properties of the spaces that are selected to describe the weak
solutions of problem~(1)--(6). The above-mentioned spaces lose
many ``good'' properties intrinsic to the spaces of the functions
of one variable. The nonlinearity of problem~(1)--(6) has no small
share in this process (the term
$\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial x_i}$ in~(1)
defines the convection of an incompressible fluid~[9, p. 10]).

Prior to proving the existence of a weak solution of the initial
boundary value problem~(1)--(6), in the domain $\Im$ consider the
spectral problem
\[
{{\begin{array}{*{20}c} -\nu\triangle U= \lambda U,~ \quad
U|_{\partial\Im}=0,
 \end{array} }}
\]
by analogy to its counterpart on a graph $\Gamma$~[2]. This
problem is to find the set of numbers $\lambda$ each associated
with at least one nontrivial solution $U(x)\in V_{\,0}^{1}(\Im)$
satisfying the identity
\[
{{\begin{array}{*{20}c} \nu((U,\eta))= \lambda (U,\eta)
 \end{array} }}
\]
for any function $\eta(x)\in V_{\,0}^{1}(\Im)$; here
$((\cdot,\cdot))$ denotes the scalar product of the form
\[
{{\begin{array}{*{20}c} ((U,\eta))=\sum\limits_{i=1}^n
(\frac{\partial U}{\partial x_i},\frac{\partial \eta}{\partial
x_i})_{L_2(\Im)^n}.
 \end{array} }}
\]
This means that $U(x)$ is a generalized eigenfunction from the
class $V_{\,0}^{1}(\Im)$ and $\lambda$ is the corresponding
eigenvalue.

\textbf{Proposition~1.} \emph{The eigenvalues are real and have
finite multiplicities, and they can be indexed in the ascending
order of their magnitudes taking into account multiplicities,
i.~e. $\{\lambda_i\}_{i\geq 1}$; the generalized eigenfunctions
are indexed accordingly, $\{U_i(x)\}_{i\geq 1}$.}

\textbf{Proposition~2.} \emph{The system of the generalized
eigenfunctions $\{U_i(x)\}_{i\geq 1}$ forms an orthogonal basis in
the space $V_{\,0}^{1}(\Im)$ and in the space $L_2(\Im)^n$.}

These results are established by the methods presented in~[2].

\textbf{Remark~4.} These propositions remain in force for the
spectral problem, where the boundary condition
$U|_{\partial\Im}=0$ is replaced by the more general one of the
form
\[
{{\begin{array}{*{20}c} \frac{\partial U}{\partial n}+\sigma
U|_{\partial\Im}=0
 \end{array} }}
\]
(each domain $\Im_l$ has a specific constant $\sigma$, and
$\frac{\partial U}{\partial n}$ designates the derivative along
the inner normal inside the domain $\Im$). In this case, the
generalized eigenfunction belongs to the space $V^{1}(\Im)$ (the
definitions of the spaces $V^{1}(\Im)$ and $V_{\,0}^{1}(\Im)$
differ in the boundary conditions, $V|_{\partial\Im}=0$ and the
above-mentioned general boundary condition, used in the
description of the set $\Omega$) and also satisfies the identity
\[
{{\begin{array}{*{21}c} \nu((U,\eta))+\sum\limits_{\zeta\in
\partial\Im}\sigma U\eta=\lambda(U,\eta)
\end{array} }}
\]
for any function $\eta(x)\in W_{\,0}^{1}(S_l,\Im)$, $\lambda$ is
an eigenvalue.\newpage


\textbf{Theorem~1.} \emph{There exists at least one weak solution
of the initial boundary value problem } (1)--(6) \emph{for
arbitrary finite $T>0$.}

P r o o f. Use the system of the eigenfunctions
$\{U_i(x)\}_{i\geq1}$ as a basis to represent the approximate
solution $Y_m(x,t)$ as the cut-off function
\[
{{\begin{array}{*{20}c} Y_m(x,t)= \sum\limits_{i=1}^m
g_{i\,m}(t)U_i(x)
\end{array} }}
\]
(the scalar functions $g_{i\,m}(t)$ are absolutely continuous on
$[0,T]$) that satisfies the system
\begin{equation}\label{eq39}
{{\begin{array}{*{20}c} (\frac{\partial Y_m}{\partial
t},U_i)+\nu\rho(Y_m,U_i)+\varrho(Y_m,Y_m,U_i)=(f,U_i),~
\,\,i=\overline{1,m},~ \,\,t\in[0,T],
\end{array} }}
\end{equation}
\begin{equation}\label{eq40}
{{\begin{array}{*{20}c} Y_m(x,0)=Y_{0\,m}(x),
\end{array} }}
\end{equation}
where $Y_{0m}(x)=\sum\limits_{i=1}^m g^0_{im}U_i(x)$
($g^0_{im}=g_{im}(0))$; $Y_{0m}(x)\rightarrow Y_0(x)$ in the norm
$\mathcal{H}(\Im)$.

System~(15), (16) is a system of differential equations in the
functions $g_{im}(t)$, which allows to find $Y_m$ for any
$t\in[0,T]$. Let us demonstrate this by obtaining the a priori
estimates of the norms of $Y_m$ in $V^{1,0}_{\,\,0}(\Im_T)$.

Multiplication of (15) by $g_{im}(t)$ and summation over
$i=\overline{1,m}$ yield
\begin{equation}\label{eq41}
{{\begin{array}{*{20}c} \frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\rho(Y_m,Y_m)=(f,Y_m)
\end{array} }}
\end{equation}
(recall that $\varrho(Y_m,Y_m,Y_m)=0$ by statement~3 of Lemma~2).
In expression~(17), the left-hand side is
$\frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\|(Y_m)_x\|^2_{L_2(\Im)^n}$ and the
right-hand side obeys the estimate $(f,Y_m)\leq
\|f\|_{L_2(\Im)^n}\|Y_m\|_{L_2(\Im)^n}$. In combination with~(17),
it follows that
\[
{{\begin{array}{*{20}c} \frac{1}{2}\frac{\partial }{\partial
t}\|Y_m\|^2_{L_2(\Im)^n}+\nu\|(Y_m)_x\|^2_{L_2(\Im)^n}\leq
\|f\|_{L_2(\Im)^n}\|Y_m\|_{L_2(\Im)^n}.
\end{array} }}
\]
And integration over $t$ between $0$ and $t$ gives the inequality
%\begin{equation}\label{eq42}
%{{\begin{array}{*{20}c}
\begin{equation*}
\begin{array}
~\frac{1}{2}\|Y_m\|^2_{L_2(\Im)^n}+\nu\int\limits_0^t\|(Y_m)_x\|^2_{L_2(\Im_t)^n}d\tau\leq
\\%
\end{array}
\end{equation*}
\begin{equation}\label{eq42}
\begin{array}
~\leq\frac{1}{2}\|Y_m(\cdot,0)\|^2_{L_2(\Im)^n}+\|f\|^2_{L_{2,1}(\Im_t)}\mathop{\max}\limits_{\tau\in[0,
t]}\|Y_m(\cdot,\tau)\|_{L_2(\Im)^n}
\end{array}% }}
\end{equation}
for arbitrary $t\in[0,T]$.

Introduce the notation $z(t)=\mathop{\max}\limits_{\tau\in[0,
t]}\|Y_m(\cdot,\tau)\|_{L_2(\Im)}$ and multiply both sides of
inequality~(18) by 2 to get
\[
{{\begin{array}{*{20}c} z^2(t)+2\nu\|(Y_m)_x\|^2_{L_2(\Im_t)} \leq
 \|Y_m(\cdot,0)\|_{L_2(\Im)^n}z(t)+2\|f\|^2_{L_{2,1}(\Im_t)}z(t),
\end{array} }}
\]
as long as $\|Y_m(\cdot,0)\|^2_{L_2(\Im)^n}\leq z(t)$. Then
\[
{{\begin{array}{*{20}c}
z^2(t)\leq J(t), ~~~%\\
\|(Y_m)_x\|^2_{L_2(\Im_t)^n} \leq\frac{1}{2\nu}J(t),
 \end{array} }}
\]
with
$J(t)=\|Y_m(\cdot,0)\|_{L_2(\Im)^n}z(t)+2\|f\|^2_{L_{2,1}(\Im_t)^n}z(t)$.
The last two inequalities lead to the estimate
\[
{{\begin{array}{*{20}c}
\|Y_m\|_{2,\Im_t}=z(t)+\|(Y_m)_x\|_{L_2(\Im_t)^n} \leq \left(1+ \frac{1}{\sqrt{2\nu}}\right)J^{1/2}(t)\leq \\
\leq \left(1+
\frac{1}{\sqrt{2\nu}}\right)\left(\|Y_m(\cdot,0)\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right)^{1/2}\|Y_m\|^{1/2}_{2,\Im_t}
 \end{array} }}
\]
or, for any $t\in[0,T]$,\newpage

\begin{equation}\label{eq43}
{{\begin{array}{*{20}c} \|Y_m\|_{2,\Im_t}\leq
\left(1+\frac{1}{\sqrt{2\nu}}\right)^2\left(\|Y_m(\cdot,0)\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right).
 \end{array} }}
\end{equation}
Taking into consideration formula~(19), the expansion
$Y_{0\,m}(x)=\sum\limits_{i=1}^m g^0_{i\,m}U_i(x)$, as the
convergence $Y_{0\,m}(x)\rightarrow Y_0(x)$ in the norm
$\mathcal{H}(\Im)$, we have $\|Y_m(\cdot,0)\|_{L_2(\Im)^n}\leq
c\|Y_0\|_{L_2(\Im)^n}$ (where $c>0$ is a constant independent of
$m$) and, using~(19), the estimate
%\begin{equation}\label{eq44}
%{{\begin{array}{*{20}c}
\begin{equation*}
\begin{array}
~\|Y_m\|_{2,\Im_t}\leq \left(1+\frac{1}{\sqrt{2\nu}}\right)^2\left(c\|Y_0\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right)\leq\\%[0.2cm]
\end{array}
\end{equation*}
\begin{equation}\label{eq44}
\begin{array}
~\leq
C^*\left(\|Y_0\|_{L_2(\Im)^n}+2\|f\|_{L_{2,1}(\Im_t)}\right),
\end{array} }}
\end{equation}
where $C^*>0$ is a constant independent of $m$. The resulting
estimate~(20) pursues two goals, namely,

1) for any index $m$, the norms of the approximate solutions
$Y_m(x,t)$ and their generalized derivatives $\frac{\partial
Y_m(x,t)}{\partial x}$ in the space $\mathcal{H}(\Im)$ are bounded
by a constant $C$ that is independent of $m$, i.~e.
\begin{equation}\label{eq45}
{{\begin{array}{*{20}c}
\|Y_m\|_{L_2(\Im)^n}\leq C, \\[0.1cm]
\|\frac{\partial Y_m(\cdot,t)}{\partial x}\|_{L_2(\Im)^n}\leq C;
\end{array} }}
\end{equation}

2) for any index $m$, the norms of the approximate solutions
$Y_m(x,t)$ are estimated by~the~norms of the initial data $Y_0(x)$
and $f(x,t)$ of the initial boundary value problem
\mbox{(1)--(6)}.

With this in mind, employ the following well-known result for a
sequence $\{Y_m\}_{m\geq1}$ with the collectively bounded norms
(21) of elements [7, p.~31]. In a sequence $\{Y_m\}_{m\geq1}$, it
is possible to separate a subsequence
$\left\{Y_{m_k}\right\}_{k\geq1}$ that weakly converges in
norm~(12) to a certain element $Y\in V_{\,\,0}^{1,0}(\Im_{T})$ (in
fact, $\left\{Y_{m_k}\right\}_{k\geq1}$ weakly converges to $Y$ in
the norm $L_2(\Im_T)^n$ together with $\frac{\partial
Y_{m_k}}{\partial x}$). Show that the element $Y(x,t)$ is a
solution of problem \mbox{(1)--(6)}.

Multiply expression~(15) by an absolutely continuous on $[0,T]$
function $d_i(t)$, perform summation over $i=\overline{1,m}$ and
integrate the result over $t$ between $0$ and $t$:
%\begin{equation}\label{eq46}
%{{\begin{array}{*{20}c}
\begin{equation*}
\begin{array}
~(Y_m(x,t),\Phi_m(x,t))-\int\limits_{\Im_t}Y_m(x,\tau)\frac{\partial\Phi_m(x,\tau)}{\partial \tau}dxd\tau+\nu\int\limits_0^t\rho(Y_m,\Phi_m)d\tau+\\
\end{array}
\end{equation*}
\begin{equation}\label{eq46}
\begin{array}
~+\int\limits_0^t\varrho(Y_m,Y_m,\Phi_m)d\tau=
(Y_0(x),\Phi_m(x,0))+\int\limits_{\Im_t}f(x,\tau)\Phi_m(x,\tau)dxd\tau,
\end{array}% }}
\end{equation}
where $\Phi_m(x,t)=\sum\limits_{i=1}^md_i(t)U_i(x)$.

Denote by $\Sigma$ the set of all functions $\Phi_m(x,t)$ with
arbitrary $d_i(t)$ possessing the above properties and with
arbitrary natural indexes $m$. The set $\Sigma$ is dense in
$W_{\,0}^{1}(\Im_{T})$. This follows from the density of the set
$\{U_i(x)\}_{i\geq 1}$ in $V^1_{\,0}(\Im)$, the continuity of
$\Phi_m(x,t)\in\Sigma$ in $t\in[0,T]$, the belonging
$\Phi_m(x,t)\in V^1_{\,0}(\Im)$ for each fixed $t\in[0,T]$, and
the definition of the space $W^1_{\,0}(\Im_T)$.

In~(22), fix the function $\Phi_m(x,t)=\Phi_{m^*}^*(x,t)\in
\Sigma$, i.~e.
\[
{{\begin{array}{*{20}c}
\Phi_{m^*}^*(x,t)=\sum\limits_{i=1}^{m^*}d^*_i(t)U_i(x),
\end{array} }}
\]
and, starting from index $m_k\geq m^*$, pass to the limit in the
above subsequence $\left\{Y_{m_k}\right\}_{k\geq1}$. \newpage

\noindent First of all, note that the integrals
\[
{{\begin{array}{*{20}c}
\int\limits_0^t\rho(Y_{m_k},\Phi_{m^*}^*)d\tau,\quad
\int\limits_0^t\varrho(Y_{m_k},Y_{m_k},\Phi_{m^*}^*)d\tau\quad
\end{array} }}
\]
contain the terms mentioned in Lemma~3. According to the latter
(also, see Remark~2), these integrals converge to
\[
{{\begin{array}{*{20}c}
\int\limits_0^t\rho(Y,\Phi_{m^*}^*)d\tau,\quad
\int\limits_0^t\varrho(Y,Y,\Phi_{m^*}^*)d\tau,\quad
\end{array} }}
\]
respectively. Passage to the limit yields formula~(22) for the
limiting function $Y(x,t)$, and hence for
$\eta(x,t)=\Phi_{m^*}^*(x,t)$ the function $Y(x,t)$ is a weak
solution of the initial boundary value problem~(1)--(6) from
$V_{\,\,0}^{1,0}(\Im_{T})$ due to the density of the set $\Sigma$
in $W_{\,0}^{1}(\Im_{T})$.

To complete the proof, it remains to argue the existence of a
function $p(x,t)\in \mathfrak{D}'(\Im_T)^n$. Here the line of
reasoning is as follows. The obtained function $Y(x,t)$ as a weak
solution of problem~(1)--(6) satisfies identity~(14) for $t=T$;
therefore, by choosing formally $\frac{\partial Y}{\partial
t}-\nu\triangle Y+\sum\limits_{i=1}^nY_i\frac{\partial Y}{\partial
x_i}- f=F$, we have $(F,\eta)=0$ for any element $\eta \in
\mathfrak{D}(\Im_T)^n$ due to~(13) and (14) (recall that
$\mathfrak{D}(\Im_T)^n$ is dense in $W_{\,0}^{1}(\Im_{T})$, which
means the belonging of $F$ to the space $\mathfrak{D}'(\Im_T)^n$).
Moreover, this element has the representation $F=-$grad$p$, where
the function $p(x,t)$ is a certain element of the space
$\mathfrak{D}'(\Im_T)^n$. The proof of Theorem~1 is finished.

\textbf{Remark~5.} The proof of this theorem contains a deeper
statement regarding a weak solution $Y(x,t)$: the function
$Y(x,t)$ has the derivative $\frac{\partial Y(x,t)}{\partial t}$
with respect to the variable $t$ that belongs to the class
$L_{2}(0,T)$, which follows from the representation of the
elements $Y_{m_k}(x,t)$ of the subsequence
$\left\{Y_{m_k}\right\}_{k\geq1}$ for the limiting function
$Y(x,t)$.


\textbf{Unique weak solution of problem~(1)--(6).} The uniqueness
of a weak solution of the initial boundary value problem~(1)---(6)
is a complicated issue due to the arbitrary dimension $n$ of the
domain $\Im$. We manage to prove uniqueness in the special case
$n=2$, which is widespread in applications (also see~[5, p.~83]).
Here a prerequisite is to slightly reduce the class
$V_{\,0}^{1,0}(\Im_{T})$ of weak solutions by defining a
contraction $\widetilde{V}_{\,0}^{1,0}(\Im_{T})$ as the closure of
the set $\widetilde{\Omega}_0(\Im_{T})$ in norm~(12). The elements
of the set $\widetilde{\Omega}_0(\Im_{T})$ have the same
properties as those of the set $\widehat{\Omega}_0(\Im_{T})$ (see
items a)---c)), except item c) as follows:

c$^*$) for each $t\in[0,T]$, the elements belong to $V^1_0(\Im)$
and \textbf{\emph{are absolutely continuous}} in $t$ in the norm
$\mathcal{H}^1(\Im)$ on $[0,T]$.

In this case, $\widetilde{V}_{\,0}^{1,0}(\Im_{T})\subset
V_{\,0}^{1,0}(\Im_{T})$, the functions $u(x,t)$ belong to
$\widetilde{V}_{\,0}^{1,0}(\Im_{T})$ and have the generalized
derivative $\frac{\partial u(x,t)}{\partial t}\in
L_{2}(0,T;V^1_{\,0}(\Im))$. Theorem~1 remains in force for the
weak solutions of the class $\widetilde{V}_{\,0}^{1,0}(\Im_{T})$,
as its proof is the same as above; and the limiting function
$Y(x,t)$ has the derivative with respect to $t$ in the class
$L_{2}(0,T;V^1_{\,0}(\Im))$ (see Remark~5 to Theorem~1).

Prior to presenting the main result, let us prove the following
lemma by analogy to its counterpart in~[5, p.~83].

\textbf{Lemma~4.} \emph{If $n=2$, then there exists a constant
$c(\Im)$ such that}
\begin{equation}\label{eq47}
{{\begin{array}{*{20}c} \|v\|_{L_4(\Im)^2}\leq
c(\Im)\|v\|_{L_2(\Im)^2}^{1/2}\|v\|_{V_0^1(\Im)}^{1/2}
\end{array} }}
\end{equation}
\emph{for any $v\in V_{\,0}^1(\Im)\cap L_4(\Im)^2$.}

P\,r\,o\,o\,f.\, First, show inequality~(23) for any $v\in
D(\Im)^2$. Extend the vector function\linebreak\newpage\noindent
$v(x)=(v_1(x),v_2(x))$ to the whole space $\mathbb{R}^2$, defining
it as 0 beyond the domain $\Im$. Introduce the notation
$D_iv=\left\{\frac{\partial v_1(x)}{\partial x_i},\frac{\partial
v_2(x)}{\partial x_i}\right\}$ and majorize $v^2(x)$ in the
equalities
\[
{{\begin{array}{*{20}c} v^2(x)=2\int\limits_{-\infty}^{x_i}v(D_iv)
dx_i \quad (i=1,2).
\end{array} }}
\]
We have
\[
{{\begin{array}{*{20}c} v^2(x)\leq 2v_1(x_2),~ \quad v^2(x)\leq
2v_2(x_1),
\end{array} }}
\]
where
\[
{{\begin{array}{*{20}c} v_1(x_2)=\int\limits_{-\infty}^{+\infty}|v
||D_1v|dx_1,~ \quad v_2(x_1)=\int\limits_{-\infty}^{+\infty}|v
||D_2v|dx_2,
\end{array} }}
\]
and the symbol $|\cdot|$ denotes the magnitude of a vector in
$\mathbb{R}^2$. On this basis, the following chain of inequalities
holds:
\[
{{\begin{array}{*{20}c}
\|v\|^4_{L_4(\mathbb{R}^2)}=\int\limits_{\mathbb{R}^2}v^4(x)dx=\int\limits_{\mathbb{R}}\int\limits_{\mathbb{R}}v^4(x)dx_1dx_2\leq
4\int\limits_{\mathbb{R}} v_1(x_2)dx_2
\int\limits_{\mathbb{R}}v_2(x_1)dx_1=
\\
=  4 \int\limits_{\mathbb{R}^2} |v ||D_1v|dx
\int\limits_{\mathbb{R}^2}|v ||D_2v|dx \leq
4\|v\|_{L_2(\mathbb{R}^2)}\|D_1v\|_{L_2(\mathbb{R}^2)}\|v\|_{L_2(\mathbb{R}^2)}\|D_2v\|_{L_2(\mathbb{R}^2)}=
\\
=4\|v\|^2_{L_2(\mathbb{R}^2)}\|D_1v\|_{L_2(\mathbb{R}^2)}\|D_2v\|_{L_2(\mathbb{R}^2)}\leq
2\|u\|_{L_2(\mathbb{R}^2)}^2\left(\|D_1v\|^2_{L_2(\mathbb{R}^2)}+\|D_2v\|^2_{L_2(\mathbb{R}^2)}\right),
\end{array} }}
\]
yielding the estimate
\[
{{\begin{array}{*{20}c} \|v\|_{L_4(\mathbb{R}^2)}\leq
\sqrt[4]{2}\|v\|_{L_2(\mathbb{R}^2)}^{1/2}\left(\sum\limits_{i=1}^2\|D_iv\|^2_{L_2(\mathbb{R}^2)}\right)^{1/4}=
\sqrt[4]{2}\|v\|_{L_2(\Im)}^{1/2}\|v_x\|_{L_2(\Im)}^{1/2}
\end{array} }}
\]
for any $v\in D(\Im)^2$. And this estimate gives inequality~(23)
for any $v\in V_{\,0}^1(\Im)$ due to the density of $D(\Im)^2$ in
$V_{\,0}^1(\Im)$ with a fixed constant $c(\Im)>0$ that depends on
the measure of the domain $\Im$ only. The proof of Lemma~4 is
finished.

We will establish that the solution of the initial boundary value
problem~(1)--(6) is unique using estimate~(23) in the following
case, which is not very restricting in applications. Whenever
required, the space $V_{\,0}^1(\Im)$ is replaced by the space
$V_{\,0}^1(\Im)\cap L_4(\Im)^2$ but with the norm of
$V_{\,0}^1(\Im)$. In this case, all statements above remain in
force obviously.

\textbf{Theorem~2.} \emph{If the domain $\Im$ is of dimension 2},
\emph{then the initial boundary value problem} (1)--(6) \emph{has
a unique weak solution in the space
$\widetilde{V}_{\,0}^{1,0}(\Im_{T})$.}

P\,r\,o\,o\,f.\, Let $(Y_1,p_1)$ and $(Y_2,p_2)$ be two solutions
of problem~(1)--(6) that belong to the class
$\widetilde{V}_{\,0}^{1,0}(\Im_{T})$. In addition, denote
$\omega=Y_1-Y_2$ and $p=p_1-p_2$. According to the definition of a
weak solution $\omega$, we have the identity
%\begin{equation}\label{eq48}
%{{\begin{array}{*{20}c}
\begin{equation*}
\begin{array}
~(\omega(x,t),\eta(x,t))-\int\limits_{\Im_t}\omega(x,\tau)\frac{\partial\eta(x,\tau)}{\partial \tau}dxd\tau+\nu\int\limits_0^t\rho(\omega,\eta)d\tau\,+\\
\end{array}
\end{equation*}
\vspace*{-2mm}\begin{equation}\label{eq48}
\begin{array}
~+\,\int\limits_0^t\varrho(\omega,Y_1,\eta)d\tau+\int\limits_0^t\varrho(Y_1,\omega,\eta)d\tau+
\int\limits_0^t\varrho(\omega,\omega,\eta)d\tau=0
\end{array} %}}
\end{equation}
for any $t\in[0,T]$ and any $\eta(x,t)\in
\widetilde{V}_{\,0}^{1,0}(\Im_{T})$ (on the strength of
$\widetilde{V}_{\,0}^{1,0}(\Im_{T})\subset W_{\,0}^{1}(\Im_{T})$).
Since $\omega$ belongs to the class
$\widetilde{V}_{\,0}^{1,0}(\Im_{T})$, identity~(24) takes the form
%\begin{equation}\label{eq49}
%{{\begin{array}{*{20}c}
\begin{equation*}
\begin{array}
~\int\limits_{\Im_t}\frac{\partial\omega(x,\tau)}{\partial \tau}\eta(x,\tau)dxd\tau+\nu\int\limits_0^t\rho(\omega,\eta)d\tau\,+\\
\end{array}
\end{equation*}
\vspace*{-2mm}\begin{equation}\label{eq49}
\begin{array}
~+\,\int\limits_0^t\varrho(\omega,Y_1,\eta)d\tau+\int\limits_0^t\varrho(Y_1,\omega,\eta)d\tau+
\int\limits_0^t\varrho(\omega,\omega,\eta)d\tau=0
\end{array} %}}
\end{equation}
for any $t\in[0,T]$ and any $\eta(x,t)\in
\widetilde{V}_{\,0}^{1,0}(\Im_{T})$.\newpage

By letting $\eta(x,t)=\omega(x,t)\in
\widetilde{V}_{\,0}^{1,0}(\Im_{T})$ in~(25), we arrive at the
relationship
\[
{{\begin{array}{*{20}c}
\frac{1}{2}\|\omega(\cdot,t)\|^2_{L_2(\Im)}+\nu\int\limits_0^t\rho(\omega,\omega)d\tau\,+
\\
+\,\int\limits_0^t\varrho(\omega,Y_1,\omega)d\tau+\int\limits_0^t\varrho(Y_1,\omega,\omega)d\tau+
\int\limits_0^t\varrho(\omega,\omega,\omega)d\tau=0
\end{array} }}
\]
(note that
$\frac{1}{2}\frac{d}{dt}\|\omega(\cdot,t)\|^2_{L_2(\Im)^2}=\left(\frac{\partial
\omega(x,t)}{\partial t},\omega(x,t)\right)$. Taking into account
representation~(8) $\bigg(\rho(\omega,\omega)=
\sum\limits_{i,j=1}^n\int\limits_{\Im}\frac{\partial
\omega_j}{\partial x_i}\frac{\partial \omega_j}{\partial
x_i}dx=\|\omega_x(\cdot,t)\|^2_{L_2(\Im)^2}\bigg)$ and the
relationships of Lemma~2 ($\varrho(Y_1,\omega,\omega)=0$ and
$\varrho(\omega,\omega,\omega)=0$), we obtain
\begin{equation}\label{eq50}
{{\begin{array}{*{20}c}
\frac{1}{2}\|\omega(\cdot,t)\|^2_{L_2(\Im)^2}+\nu\int\limits_0^t\|\omega_x(\cdot,\tau)\|^2_{L_2(\Im)^2}d\tau=
-\int\limits_0^t\varrho(\omega,Y_1,\omega)d\tau.
\end{array} }}
\end{equation}
Now, estimate the absolute value of the integral in the right-hand
side of formula~(26) using~(9) and (11):
\[
{{\begin{array}{*{20}c}
\left|\int\limits_0^t\varrho(\omega,Y_1,\omega)d\tau\right|\leq
\alpha_1\int\limits_0^t\|\omega(\cdot,\tau)\|^2_{L_4(\Im)^2}\|Y_1(\cdot,\tau)\|_{V_{\,0}^{1}(\Im)}d\tau
\end{array} }}
\]
(here $\alpha_1>0$ is a fixed constant). The last inequality, in
combination with $\|v\|_{L_4(\Im)}\leq
\sqrt[4]{2}\|v\|_{L_2(\Im)}^{1/2}\|v_x\|_{L_2(\Im)}^{1/2}$ (see
the proof of Lemma~4), yields the estimate
\[
{{\begin{array}{*{20}c}
\left|\int\limits_0^t\varrho(\omega,Y_1,\omega)d\tau\right|\leq
\alpha_2\int\limits_0^t \|\omega(\cdot,\tau)\|_{L_2(\Im)^2}
\|\omega_x(\cdot,\tau)\|_{L_2(\Im)^2}
\|Y_1(\cdot,\tau)\|_{V_{\,0}^{1}(\Im)}d\tau
\end{array} }}
\]
($\alpha_2>0$ is a fixed constant). This inequality can be
transformed into
\[
{{\begin{array}{*{20}c}
\left|\int\limits_0^t\varrho(\omega,Y_1,\omega)d\tau\right| \leq
\nu\int\limits_0^t \|\omega_x(\cdot,\tau)\|^2_{L_2(\Im)}d\tau+
\alpha_3\int\limits_0^t\|Y_1(\cdot,\tau)\|^2_{V_{\,0}^{1}(\Im)}\|\omega(\cdot,\tau)\|^2_{L_2(\Im)^2}
d\tau
\end{array} }}
\]
($\alpha_3=\alpha_2/(4\nu)$,
$\alpha_2\|\omega_x(\cdot,\tau)\|_{L_2(\Im)^2}\|Y_1(\cdot,\tau)\|_{V_{\,0}^{1}(\Im)}\|\omega(\cdot,\tau)\|_{L_2(\Im)^2}\leq
\nu\|\omega_x(\cdot,\tau)\|^2_{L_2(\Im)^2}+\alpha_3\|Y_1(\cdot,\tau)\|^2_{V_{\,0}^{1}(\Im)}\|\omega(\cdot,\tau)\|^2_{L_2(\Im)^2}$).
Using~(26), it appears that
\[
{{\begin{array}{*{20}c} \|\omega(\cdot,t)\|^2_{L_2(\Im)^2}\leq
2\alpha_3\int\limits_0^t  \|Y_1(\cdot,\tau)\|^2_{V_{\,0}^{1}(\Im)}
\|\omega(\cdot,\tau)\|^2_{L_2(\Im)^2} d\tau.
\end{array} }}
\]
And the desired result $\omega(x,t)=0$ follows immediately, as
$\|\omega(\cdot,0)\|^2_{L_2(\Im)^2}=0$. The proof of Theorem~2 is
finished.


\textbf{Continuity in initial data.} While proving Theorem~1, we
have obtained the a priori estimates~(20)
\[
{{\begin{array}{*{20}c} \|Y_m\|_{2,\Im_t}\leq
C^*\left(\|Y_0\|_{L_2(\Im)^2}+2\|f\|_{L_{2,1}(\Im_t)}\right)
\end{array} }}
\]
for any $t\in[0,T]$ and all elements of the sequence
$\{Y_m\}_{m\geq1}$, where $C^*$ is a constant that depends on the
measure of $\Im$ only. Hence, these estimates hold for all
elements of the subsequence $\{Y_{m_k}\}_{k\geq1}$ converging to a
weak solution $Y(x,t)$. Passage to the limit over the weakly
convergent subsequence $\{Y_{m_k}\}_{k\geq1}$ as $k\rightarrow
\infty$ yields the estimate (at $t=T$)
\begin{equation}\label{eq52}
{{\begin{array}{*{20}c} \|Y\|_{2,\Im_T}\leq
C^*\left(\|Y_0\|_{L_2(\Im)^2}+2\|f\|_{L_{2,1}(\Im_T)}\right).
\end{array} }}
\end{equation}
Estimate~(27) for the norm of a weak solution $Y(x,t)$ from the
space $V_{\,0}^{1,0}(\Im_{T})$ (which is also valid for a weak
solution from the space $\widetilde{V}_{\,0}^{1,0}(\Im_{T})$)
brings to the following result.

\textbf{Theorem~3.} \emph{A weak solution of the initial boundary
value problem} (1)--(6) \emph{ in the space
$V_{\,0}^{1,0}(\Im_{T})$ $(\widetilde{V}_{\,0}^{1,0}(\Im_{T}))$
continuously depends on the initial data $f(x,t)$ and $Y_0(x)$.}


\textbf{Conclusion.} Note that all results derived here remain in
force for $n=1$ (e.~g. see~[10, 11]). In this case, the netlike
domain $\Im$ is a geometrical graph $\Gamma$, and
relationships~(3) and (4) at each internal node $\xi$ of this
graph are transformed into the Kirchoff-type boundary conditions
\begin{equation}\label{eq52}
{{\begin{array}{*{20}c} \sum\limits_{\gamma\in
R(\xi)}a(1)_{\gamma}\frac{\partial Y(1,t)_{\gamma}}{\partial x}
=\sum\limits_{\gamma\in r(\xi)}a(0)_{\gamma}\frac{\partial
Y(0,t)_{\gamma}}{\partial x}.
\end{array} }}
\end{equation}
Here $Y: \Gamma_T=\Gamma\times(0,T)\rightarrow
V^1_{\,0}(\Gamma_T)$ ($V^1_{\,0}(\Gamma_T)$ is an analog of the
space $V^1_{\,0}(\Im_T)$ for the graph $\Gamma$); $Y_\gamma$
denotes the restriction of the function $Y$ to the edge $\gamma$;
$a(x)$ means a fixed measurable bounded on $\Gamma$ function that
satisfies condition~(28); $R(\xi)$ and $r(\xi)$ are the sets of
edges directed to the node $\xi$ and from the node $\xi$,
respectively. (All edges of the graph are parameterized by the
interval $[0,1]$.) The described situation underlies the analysis
of optimal control problems on networks~[4, 8, 12, 13]. The
current paper further develops the ideas presented in~[1, 3] for
$n=1$ towards increasing the dimension $n$, as well as constructs
the well-posedness conditions of the initial boundary value
problem~(1)--(6) in the sense of Hadamard. The general scheme is
classical~[5, 6], as it includes the following steps: forming a
special basis for the spaces of admissible solutions; designing
approximate solutions of the problem by the Faedo---Galerkin
method; obtaining a priori estimates for the approximate solutions
in terms of energy balance inequalities; finally, proving the
compactness of the resulting family of solutions using the
obtained estimates. The smoothness of the solution in the spatial
variable is established by imposing additional requirements. The
results yielded by this approach are of certain interest for
applications in hydromechanics and allied branches of continuum
mechanics, namely, for the analysis of optimal control problems
for multiphase media dynamics. Interestingly, other
researchers~[14--18] considered alternative approaches to the
analysis of control problems, yet with the same treatment of the
admissible control existence conditions. Also note that the
problem under study may have a stochastic component in the
representation of equation~(1), and in this case it is necessary
to use the results established in~[19, 20].




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\input{04/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{04/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize



\vskip 3mm

%\thispagestyle{empty}



\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

\vskip 1mm

\noindent Статья поступила в~редакцию 17 января 2017~г.

\vskip 1mm

\noindent Статья принята к~печати 8 июня 2017~г.


}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vskip 5mm

%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak \vskip 3mm

%{\it Балонин Николай Алексеевич}~-- доктор технических наук,
%профессор; e-mail: korbendfs@mail.ru

%{\it Сергеев Михаил Борисович}~-- доктор технических наук,
%профессор,  директор; e-mail: mbse@mail.ru

%\vskip 2mm

%\emph{Balonin Nikolaj Alekseevich}~-- doctor of technical
%sciences, professor; e-mail: korbendfs@mail.ru


%\emph{Sergeev Mikhail Borisovich}~-- doctor of technical sciences,
%director; e-mail: mbse@mail.ru


%}


%\thispagestyle{empty}
