
{\footnotesize


\vskip4mm \noindent {\small \textbf{Литература} }

\vskip3mm


1. \textit{Елизаветин И. В., Шувалов Р. И., Буш В. А.} Принципы
и~методы радиолокационной съемки для целей формирования цифровой
модели местности~// Геодезия и~картография. 2009. №~1. C.~39--45.

2. \textit{Ferretti A., Monti-Guarnieri A., Prati C.} et al. InSAR
Principles: Guidelines for SAR interferometry processing and
interpretation~// URL:
http://www.esa.int/esapub/tm/tm19/TM-19\_ptA.pdf (дата обращения:
02.08.2016).

3. \textit{Zhengxiao Li, Bethel J.} Image coregistration in SAR
interferometry~// The Internati-onal Archives of the
Photogrammetry, Remote Sensing and Spatial Information Sciences.
Beijing, 2008. Vol.~XXXVII. Pt B1. P.~433--438.

4. \textit{Massonnet D., Feigl K. L.} Radar interferometry and its
application to changes in the earth’s surface~// Reviews of
Geophysics. 1998. Vol.~36, Iss.~4. P.~441--500.

5. \textit{Costantini M., Farina A., Zirilli F.} A fast phase
unwrapping algorithm for SAR interferometry~// IEEE Trans. GARS.
1999. Vol.~37, N~1. P.~452--460.

6. \textit{Mistry P., Braganza S., Kaeli D., Leeser M.}
Accelerating phase unwrapping and affine transformations for
optical quadrature microscopy using CUDA~// Proceedings of 2nd
Workshop on General Purpose Processing on Graphics Processing
Units. GPGPU: Conference. Washington, D.C., USA: ACM, 2009.
P.~28--37.

7. \textit{Karasev P. A., Campbell D. P., Richards M. A.}
Obtaining a 35x Speedup in 2D phase unwrapping using commodity
graphics processors~// Radar Conference. IEEE. 2007. P.~574--578.

8. \textit{Wu Z., Ma W., Long G., Li Y., Tang Q., Wang Z.} High
performance two-dimensional phase unwrapping on GPUs~//
Proceedings of the 11th ACM Conference on Computing Frontiers~---
CF'14. New York, NY, USA: ACM, 2014. P.~35:1--35:10.

9. \textit{Xin-Liang S., Xiao-Chun X.} GPU acceleration of range
alignment based on minimum entropy criterion~// Radar Conference.
IET International. 14--16 April 2013. P.~1--4.

10. \textit{Guerriero A., Anelli V. W., Pagliara A., Nutricato R.,
Nitti D. O.} High performance GPU implementation of InSAR
time-consuming algorithm kernels~// Proceedings of the
1st~WORKSHOP on the State of the art and Challenges of Research
Efforts at POLIBA. Bari, Italy:  Politecnico di Bari, 2014.
P.~383.

11. \textit{Zhang F., Wang B., Xiang M.} Accelerating InSAR raw
data simulation on GPU using CUDA~// Geoscience and Remote Sensing
Symposium (IGARSS). IEEE International. Bari, Italy: Politecnico
di Bari, 25--30 July 2010. P.~2932--2935.

12. \textit{Marinkovic P. S., Hanssen R. F., Kampes B. M.}
Utilization of parallelization algorithms in InSAR/PS-InSAR
processing~// Proceedings of the 2004 Envisat ERS Symposium (ESA
SP-572). Salzburg, Austria: ESA, 6--10 September 2004. P.~1--7.

13. \textit{Sheng G., Qi-Ming Z., Jian J., Cun-Ren L., Qing-xi T.}
Parallel processing of InSAR interferogram filtering with CUDA
programming~// Zhongguo Cehui Kexue Yanjiuyan, China. 2015.
Vol.~40, N~1. P.~67--88.

14. \textit{Верба В. С., Неронский Л. Б., Осипов И. Г., Турук В.
Э.} Радиолокационные системы землеобзора космического базирования.
M.: Радиотехника, 2010. 675~с.

15. \textit{Gabriel E., Fagg G. E., Bosilca G.} et al. Open MPI:
Goals, Concept, and Design of a Next Generation MPI
Implementation~// URL:
https://www.open-mpi.org/papers/euro-pvmmpi-2004-overview/euro-pvmmpi-2004-overview.pdf
(дата обращения: 30.06.2016).

16. \textit{Kampes B., Hanssen R., Perski Z.} Radar Interferometry
with Public Domain Tools pre- sentation~// URL:
http://doris.tudelft.nl/Literature/kampes\_fringe03.pdf (дата
обращения: 30.06.2016).

17. \textit{Frigo M., Johnson S. G.} FFTW: An Adaptive Software
Architecture for the FFT~// ICASSP conference proceedings.
Seattle, Washington, USA: IEEE,  15~May 1998. Vol.~3.
P.~1381--1384.

18. \textit{Larkin J.} Fast GPU Development with CUDA Libraries~//
URL:
https://www.olcf.ornl.gov/wp-content/uploads/2013/02/GPU\_libraries-JL.pdf
(дата обращения: 30.06.2016).

19. \textit{Demmel J., Dongarra J.} ST-HEC: Reliable and scalable
software for linear algebra computations on High End Computers~//
URL:
https://people.eecs.berkeley.edu/~demmel/Sca-LAPACK-Proposal.pdf
(дата обращения: 30.06.2016).

20. \textit{Феоктистов А. А., Захаров А. И., Гусев М. А., Денисов
П. В.} Исследование возможностей метода малых базовых линий
на~примере модуля SBaS программного пакета SARScape и~данных РСА
ASAR/ENVISat и~PALSAR/ALOS. Ч. 1. Ключевые моменты метода~// Журн.
радиоэлектроники. 2015. №~9. С.~1--26.

21. \textit{Reyes-Ortiz J. L., Oneto L., Anguita D.} Big Data
analytics in the cloud: Spark on Hadoop vs MPI/OpenMP on
Beowulf~// INNS Conference on Big Data 2015 Program. San
Francisco, USA. 8--10~August 2015. P.~121--130.

22. \textit{Kannan P.} Beyond Hadoop MapReduce Apache Tez and
Apache Spark~// URL: http://
www.sjsu.edu/people/robert.chun/courses/CS259Fall2013/s3/F.pdf
(дата обращения: 02.08.2016).

23. \textit{Nathan P.} Real-Time analytics with Spark Streaming~//
URL: http://viva-lab.ece.virginia.
edu/foswiki/pub/InSAR/RitaEducation/InSAR Technology Literature
Search.pdf (дата обращения: 02.08.2016).

24. \textit{Nagler E.} Introduction to Oozie~// Apache Oozie
Documentation. URL: http://www.cse.buffalo.
edu/bina/cse487/fall2011/Oozie.pdf (дата обращения: 02.08.2016).

25. \textit{Jhajj R.} Apache Hadoop Hue Tutorial~// URL:
https://examples.javacodegeeks.com/enterprise-java/apache-hadoop/apache-hadoop-hue-tutorial/
(дата обращения: 02.08.2016).

26. \textit{Потапов В. П., Попов C. Е.} Высокопроизводительный
алгоритм роста регионов для развертки интерферометрической фазы
на~базе технологии CUDA~// Программная инженерия. 2016. №~2.
C.~61--74.




\vskip 2mm

{\bf Для цитирования:}  {\it Потапов В. П., Костылев М. А., Попов
C. E.} Потоковая обработка радарных данных в~распределенной среде
Apache Spark
// Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p4}--\pageref{p4e}. \doivyp/
spbu10.\issueyear.\issuenum04



}
