{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm
%%%%%%%%%%%в транслит





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

1. Gnilitskaya Yu.~A. {\it Matematicheskoe modelirovanie i
chislennoe issledovanie processov v setepodobnyh ob'ektah,
opisyvaemyh evoljucionnymi uravneniajmi} [{\it Mathematical
modeling and numerical study of processes in netlike objects
described by evolutionary equations}]. Cand. Diss. of physical and
mathematical sciences. Voronezh,
Voronezh~State~Technical~University, 2015, 224~p. (In Russian)

2. Volkova A.~S., Provotorov V.~V. Obobshhennye reshenija i
obobshhennye sobstvennye funkcii kraevyh zadach na geometricheskom
grafe [Generalized solutions and generalized eigenfunctions of
boundary-value problems on a geometric graph]. \textit{Izvestija
vysshih uchebnyh zavedenij. Matematika $[$Russian Mathematics.
Proceeding of Higher Educatianal institutions$]$}, 2014, vol.~58,
no.~3, pp.~1--13. (In Russian)

3. Volkova A.~S., Gnilitskaya Yu.~A., Provotorov V.~V. On the
solvability of boundary-value problems for parabolic and
hyperbolic equations on geometrical graphs. \textit{Automation and
Remote Control}, 2014, vol.~75, no.~2, pp.~405--412.

4. Provotorov V.~V., Gnilitskaya Yu.~A. Granichnoe upravlenie
volnovoj sistemoj v prostranstve obobshhennyh reshenij na grafe
[Boundary control of a wave system in the space of generalized
solutions on a graph]. \textit{Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2013, iss.~3, pp.~112--120. (In Russian)

5. Lions J.-L. \textit{Some methods of solving non-linear boundary
value problems}. Paris, Dunod-Gauthier-Villars, 1969. 581~p.
(Russ. ed.: Lions~J.-L. \textit{Nekotorye metody resheniya
nelineinykh kraevykh zadach}. Moscow, Mir Publ., 1972, 587~p.).


6. Lions J.-L., Magenes E. \textit{Problemes aux limites non
homogenes et applications} [\emph{Nonhomogenes boundary value
problems and supplement}]. Paris, Dunod-Gauthier-Villars, 1968.
364~p. (Russ. ed.: Lions~J.-L., Magenes~E. \textit{Neodnorodnye
granichnye zadachi i ikh prilozheniya}. Moscow, Mir Publ., 1971,
371~p.).

7. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

8. Podvalny S.~L., Provotorov V.~V. Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe
[Starting control of a parabolic system with distributed
parameters on a graph]. \textit{Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science.
Control Processes}, 2015, iss.~3, pp.~126--142. (In Russian)

9. Kutateladze S.~S., Styrikovich M.~A. \textit{Gidrodinamkia
gazozhidkostnykh sistem} [\textit{Hydrodynamics of gas-liquid
systems}]. Moscow, Energiya Publ., 1976, 296~p. (In Russian)

10. Provotorov V.~V. Boundary control of a parabolic system with
distributed parameters on a graph in the class of summable
functions. \textit{Automation and Remote Control}, 2015, vol.~76,
no.~2, pp.~318--322.

11. Podvalny S.~L., Provotorov V.~V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \textit{Intern. Conference ``Stability and Control
Processes'' in memory of V.~I.~Zubov $($SCP$)$}, 2015,
pp.~117--119.

12. Provotorov V.~V. Optimal'noe upravlenie parabolicheskoj
sistemoj s raspredelennymi parametrami na grafe [Optimal control
of a parabolic system with distributed parameters on a graph].
\textit{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2014, iss.~3,
pp.~154--163. (In Russian)

13. Potapov D.~K. Optimal'noe upravlenie raspredelennymi sistemami
jellipticheskogo tipa vysokogo porjadka so spektral'nym parametrom
i razryvnoj nelinejnost'ju [Optimal control of higher order
elliptic distributed systems with a spectral parameter and
discontinuous nonlinearity]. \textit{Journal of Computer and
System Sciences International}, 2009, vol.~52, no.~2,
pp.~180--185. (In Russian)

14.  Aleksandrov A.~Yu., Zhabko A.~P. Ob ustojchivosti reshenij
odnogo klassa nelinejnyh raznostnyh sistem [On stability of
solutions to one class of nonlinear difference systems].
\textit{Sibirskij matematicheskij zhurnal $[$Siberian Mathematical
Journal}], 2003, vol.~44, no.~6, pp.~951--958. (In Russian)

15. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \textit{WSEAS Transactions on Systems and
Control}, 2014, vol.~9, pp.~388--397.

16. Aleksandrov A.~Yu., Platonov A.~V. Ob ustojchivosti i
dissipativnosti nekotoryh klassov slozhnyh sistem   [On stability
and dissipativity of some classes of complex systems].
\textit{Avtomatika i telemehanika  $[$Automation and Remote
Control}], 2009, vol.~70, no.~8, pp.~1265--1280. (In Russian)

17. Veremey E.~I., Korchanov V.~M. Mnogocelevaja stabilizacija
dinamicheskih sistem odnogo klassa [Multiobjective stabilization
of the dynamic systems from a certain class]. \textit{Avtomatika i
telemehanika  $[$Automation and Remote Control}], 1988, no.~9,
pp.~126--137. (In Russian)

18. Veremey E.~I., Sotnikova M.~V. Stabilizacija plazmy na baze
prognoza s ustojchivym linejnym priblizheniem [Plasma
stabilization by prediction with stable linear approximation].
\textit{Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes}, 2011, iss.~1,
pp.~116--133. (In Russian)

19. Karelin V.~V. Shtrafnye funkcii v zadache upravlenija
processom nabljudenija [Penalty functions in the control problem
of an observation process]. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss.~4, pp.~109--114. (In Russian)

20. Kamachkin A.~M., Yevstafyeva V.~V. Oscillations in a relay
control system at an external disturbance. \textit{Control
Applications of Optimization 2000: Proceedings of the 11th IFAC
Workshop}, 2000, vol.~2, pp.~459--462.




\vskip 2mm

{\bf For citation:}  Provotorov V.~V., Ryazhskikh V.~I.,
Gnilitskaya Yu.~A. Unique weak solvability of a nonlinear initial
boundary value problem with distributed parameters in a netlike
domain. {\it Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, \issueyear,
vol.~13, iss.~\issuenum, pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/spbu10.\issueyear.\issuenum04


}
