
{\normalsize

\vskip 4.8mm%6mm

\noindent{\bf On export duty managing}

}

\vskip 1.8mm%2mm

{\small

\noindent{\it A. V. Prasolov%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.8mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,

\noindent%
%\hskip2.45mm%
St.\,Petersburg, 199034, Russian Federation

%\noindent%
%\hskip2.45mm%


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip1.8mm%3mm


\noindent \textbf{For citation:}  Prasolov A. V. On export duty
managing. {\it Vestnik of Saint~Petersburg University. Applied
Mathematics. Computer Science. Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p11}--\pageref{p11e}.\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum11  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent When considering such economic phenomenon
as an export, the producers of the exported goods, the
participants in production within the country, consumers within
the country and abroad, the state with its customs and tax
services and other economic agents may come into the view. This
paper considers one (generalized) producer of the good, households
as consumers within the country and the government that sets the
export duty and manages the export income. The price outside the
country is considered to be constant, i.~e. does not depend on the
volume of exports. Since the interests of these participants in
the production, distribution and consumption of this good are very
different and often uncertain, the standard way would be to build
a Pareto-optimality region and allocate some strategy in it as a
solution. We made an attempt to estimate the boundary of the
Pareto-optimality domain but managed to construct only some of its
inner part, and the function, the largest value of which indicates
an acceptable equilibrium, was too complex for analytical
solutions. This prevented the use of such a well-known approach as
the Nash arbitration solution.  As a result, we proposed a method
that gives the best export duty from the point of view of the
government, which uses the income to expand production, which will
give a profit to both producers and households in the form of a
decrease in domestic prices. We specifically did not consider any
particular product because the restrictions defined by Customs
laws are very diverse both in countries and in products. The paper
presents one example with %\linebreak\newpage\noindent
illustrative
data and one~--- with real volumes of production and export of
wheat from the Russian
Federation.\\[1mm]
\textit{Keywords}: export duties, optimization, revenue
management.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Prasolov A. V. Ob odnom vozmozhnom podhode k analizu
protektsionizma  [On one possible approach to the analysis of
protectionism]. \textit{Economics and Mathematical Methods}, 1999,
no.~2, pp.~153--156. (In Russian)

2. Prasolov A. V. {\it Matematicheskie metody ekonomicheskoy
dinamiki} [\textit{Mathematical methods of economical dynamics}].
Second ed. St. Petersburg, ``Lan'' Publ., 2015, 352~p. (In
Russian)

3. Noghin V. D., Prasolov A. V. Mnogokriterial'naia otsenka
optimal'noy velichiny importnoy poshliny  [Multicriteria
evaluation of the optimal import duty]. \textit{Proceedings of the
System Analysis Institute RAS}, 2013, no.~2, pp.~34--44. (In
Russian)

4. Pugel T. A., Lindert P. H.  {\it Mezhdunarodnaia ekonomika}
[\textit{International economics}]. Tutorial. Transl. from
English. 11th ed. Moscow, ``Delo i Servis'' Publ., 2000,  798~p.
(In Russian)

5. Dixit A. K., Norman V. \textit{Theory of international trade, a
dual, general equilibrium approach}. Cambridge, Cambridge
University Press, 1980, 339~p.

6. {\it Tamojennye poshliny} [{\it Custom Duties}]. Available
at:\\
https://ru.wikipedia.org/wiki/Таможенные${\_}$пошлины (accessed:
March 20, 2019). (In Russian)

7. \textit{Nalogoviy Kodeks RF. Razd. VIII: Federal'nie nalogi.
Gl.~21. Nalog na dobavlennuiu stoimost'} [{\it Tax Codex RF, Pt
VIII. Federal taxes, ch.~21: value added tax}]. Available at:\\
https://base.garant.ru/10900200/ec7cc4fdc985caebec887eb34c5c1ee9/${\#}$block${\_}$20021
(acces\-sed:\,March\,20, 2019). (In Russian)

8. \textit{Ob utverzhdenii stavok vyvoznyh tamozhennyh poshlin na
tovary, vyvozimye iz Rossiyskoy Federatsii za predely
gosudarstv-uchastnikov soglasheniy o Tamozhennom souze, i o
priznanii utrativshymi silu  nekotoryh aktov Pravitel'stva
Rossiyskoy Federatsii} [\textit{About the statement of rates of
export customs duties on the goods exported from the Russian
Federation outside the States parties of agreements on the Customs
Union and about recognition become invalid for some acts of the
Government of the Russian}]. Resolution of RF from 30.08.2013,
no.~754 on 03.03.2016 Available at:\\
%
https://www.consultant.ru/document/cons${\_}$doc${\_}$LAW${\_}$151402/
(accessed:\,March\,20,\,2019). (In Russian)

9. Edgeworth F. Y. Appreciations of mathematical theories.
\textit{Economic Journal}, 1908, no.~18(72), pp.~541--556.

10. Dyubin G. N., Suzdal V. G. {\it Vvedenie v prikladnuiu teoriu
igr} [{\it Introduction to applied theory of games}]. Moscow,
Nauka Publ., 1981, 336~p. (In Russian)

11. Tarasevich L. S., Grebennikov P. I., Leusskii A. I. {\it
Mikroekonomika}  [\textit{Microeconomics}]. Мoscow, Yurite Publ.,
2006, 375~p. (In Russian)

12. Demidova М. {\it Eksport pshenitsy iz Rossii --- bezuslovnogo
lidera na mirovom rynke} [{\it Wheat exports from Russia~--- the
undisputed
leader in the world market}]. Available at:\\
%
https://moneymakerfactory.ru/biznes-plan/eksport-pshenitsyi/
(accessed: March 20, 2019). (In Russian)




\vskip1.5mm Received:  March 21, 2019.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%


\vskip1.5mm%2mm
\textit{Alexander V. Prasolov} ---  Dr. Sci. in Physics and
Mathematics, Professor; a.prasolov@spbu.ru



}
