
{\normalsize

\vskip 6mm

\noindent{\bf Optimization of dynamics of trajectory bundles  using \\
smooth and nonsmooth functionals. Part 1%\!$\,^*$%
}

}

\vskip 2mm

{\small

\noindent{\it D.~A.~Ovsyannikov$\,^1$%
, M.~A.~Mizintseva$\,^1$%
, M.~Yu.~Balabanov$\,^1$%
, A.~P.~Durkin$\,^2$%
, N. S. Edamenko$\,^1$%
,\\ E.~D.~Kotina$\,^1$%
, A.~D.~Ovsyannikov$\,^1$%
%, I.~О. Famylia%$\,^1$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by the Russian Scientific Found (grant N 17-11-017079).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

\noindent%
$^2$~%
Institute for Nuclear Research of the Russian Academy of Science,
7a, pr. 60-letia Oktiabria,

\noindent%
\hskip2.45mm%
Moscow, 117312, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Ovsyannikov~D.~A.,
Mizintseva~M.~A., Balabanov~M.~Yu., Durkin A.~P., Edamenko~N.~S.,
Ko\-ti\-na~E.~D., Ov\-syan\-ni\-kov~A.~D. Op\-ti\-mi\-za\-tion of
dynamics of trajectory bundles using smooth and nonsmooth
functionals. Part 1. {\it Vestnik of Saint~Peters\-burg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~16, iss.~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum07  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Many different works are devoted to the
problems of control and optimization in dynamic systems. Interest
in these tasks does not decrease with time. New challenges arise
in the development of technological processes in various fields of
science and technology, in particular, in the design and creation
of modern electrophysical equipment. In this paper, the problem of
optimization and control of trajectory beams is considered. The
problem of joint optimization of the program motion and the beam
of perturbed motions using a combination of smooth and nonsmooth
functionals is investigated. The first part deals with the
mathematical formulation of the given representation of the
variation of investigated functional and provides optimality
conditions in the form of a maximum principle. In the second part,
the problem of optimization of dynamics of charged particles in
the accelerator with spatially homogeneous quadrupole focusing
will be considered. Using a combination of smooth and non-smooth
functions allows you to set the functionals that most accurately
reflect the requirements for the dynamics of the charged particle
beam in accelerators.\\[1mm]
\textit{Keywords}: optimal control, controlled dynamic system,
trajectory ensemble, smooth functional, non-smooth functional,
maximum principle, charged particle beam, accelerator.
\par}

\vskip 6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Kurzhansky A. B. {\it Upravlenie i nabludenie v usloviah
neopredelennosti} [{\it Control in case of un\-cer\-tainty\,}].
Moscow, Fizmatlit Publ., 1977, 394 p. (In Russian)

2. Ovsyannikov D. A. {\it Matematicheskie metody upravlenia
puchkami} [{\it Mathemati\-cal methods of beam control\,}].
Leningrad, Leningrad State University Publ., 1980, 228 p. (In
Russian)

3. Ovsyannikov D. A. {\it Modelirovanie i optimizatsia dinamiki
puchkov zarjazhennih chastits} [{\it Mode\-ling and optimization
of charged particle beam dynamics\,}]. Leningrad, Leningrad State
University Publ., 1990, 312 p. (In Russian)

4. Ananyna T. F. Zadacha upravlenia pri nepolnyh dannyh [The
problem of control in case of partial data]. {\it Differential
Equations}, 1976, vol. 13, no.~4, pp. 612--620. (In Russian)

5. Panteleev A., Semenov V. V. {\it Sintez optimalnyh sistem
upravlenia pri nepolnoy informatsii}  [{\it Synthesis of optimal
control systems with incomplete information\,}]. Moscow, Moscow
Aviation Institute Publ. House, 1992, 191 p. (In Russian)

6. Bortakovsky A. S. Optimalnoe i suboptimalnoe upravlenia
puchkami traektoriy determiniro\-vannyh nepreryvno-diskretnyh
sistem [Optimal and suboptimal control of beams of trajectories of
deterministic continuous-discrete systems]. {\it Proceedings of
the Russian Academy of Sciences. Theory and control systems},
2009,  no. 1, pp. 18--33. (In Russian)

7. Kurzhanski A. B., Varaiya P. Dynamic optimization for
reachability problems. {\it Journal of Optimization Theory and
Applications}, 2001, vol. 108, pp. 227--251.

8.  Kotina E. D. Discrete optimization problem in beam dynamics.
{\it Nucl. Instrum. Methods Phys. Res. A}, 2006, vol. 558,  no. 1,
pp. 292--294.

9. Altsybeyev V. V.,  Ovsyannikov D. A. Optimization of beam
parameters in APF channel. {\it Proceedings of the 27th
International Linear Accelerator Conference, LINAC 2014}. Geneva,
2014, pp.~722--725.

10. Ovsyannikov D. A. Mathematical methods of optimization of
charged partical beams dyna\-mics. {\it Proceedings of the
European Partical Accelerator Conference.} Barselona, Spain, 1996,
vol. 2, pp. 1382--1384.

11. Bondarev B., Durkin A., Ovsyannikov A. New mathematical
optimization  models for RFQ structures. {\it Proceedings of the
Particle Accelerator Conference.} New York City, 1999, vol. 4, pp.
2808--2810.

12. Vinogradova T. K., Demyanov V. F. O printsipe minimaksa v
zadachah optimalnogo upravle\-nia [On the minimax principle in
optimal control problems]. {\it Reports of the USSR Academy of
Sciences}, 1973, vol. 213, no.~3, pp. 512--514. (In Russian)

13. Demyanov V. F., Vinogradova T. K., Nikulina V. N. et al. {\it
Negladkie zadachi teorii optimizatsii i upravlenia} [{\it
Non-Smooth problems of optimization and control theory\,}].
Leningrad, Leningrad Univer\-sity Publ., 1982, 324 p. (In Russian)

14. Ovsyannikov A. D. Ob odnom klasse zadach optimizatsii v
elektrostaticheskom pole  [On a class of optimization problems in
electrostatic field]. {\it Reports of the Academy of Sciences},
2013, vol. 453, no. 4, pp. 383--385. (In Russian)

15. Ovsyannikov A. D. Upravlenie programmnym i vozmushennym
dvizheniamy [Control of the program and perturbed movements]. {\it
Vestnik of Saint Petersburg University. Series 10. Applied
Ma\-the\-ma\-tics. Computer Science. Control Processes}, 2006,
iss. 4, pp. 111--124. (In Russian)

16.     Ovsyannikov A. D. Upravlenie puchkom zarjazhennih chastist
s uchetom ih vzaimodeystvia [Beam control of charged particles
taking into account their interaction]. {\it Vestnik of Saint
Petersburg University. Series 10. Applied Mathematics. Computer
Science. Control Processes}, 2009, iss. 2, pp.~82--92. (In
Russian)%\pagebreak

17. Ovsyannikov A. D. {\it Matematicheskie modeli optimizatsii
dinamiki puchkov}  [{\it Mathematical models of beam dynamics
optimization\,}]. Saint Petersburg, Publishing House “BBM”, 2014,
181 p. (In Russian)

18. Ovsyannikov D. A., Altsybeyev V. V. On the beam dynamics
optimization prob\-lem for an alternating-phase focusing linac.
{\it Phys. Part. Nuclei Lett.}, 2016, vol. 13, no. 7, pp.
775--779.

19.  Ovsyannikov D. A., Ovsyannikov A. D., Vorogushin M. F.,
Svistunov Yu. A., Dur\-kin~A.~P. Beam dynamics optimization:
models, methods and applications. {\it Nucl. Instrum. Methods
Phys. Res. A}, 2006, vol. 558, no.~1, pp. 11--19.

20. Ovsyannikov A. D., Durkin A. P., Ovsyannikov D. A., Svistunov
Y. A. Acceleration of different ion types in single RFQ structure.
{\it Problems of Atomic Science and Technology}, 2016, vol.
3(103), pp.~54--56.

21. Ovsyannikov D. A., Edamenko N. S. Modelirovanie dinamiki
puchkov zarjazhennih chastits [Modeling of charged particle beam
dynamics]. {\it Vestnik of Saint Petersburg University. Series 10.
Applied Mathematics. Computer Science. Control Processes}, 2013,
iss. 2, pp. 60--65. (In Russian)

22. Ovsyannikov A. D., Ovsyannikov D. A., Altsybeyev V. V., Durkin
A. P., Papkovich~V.~G. Application of optimization techniques for
RFQ design. {\it Problems of Atomic Science and Technology}, 2014,
vol. 3(91), pp. 116--119.

23. Ovsyannikov A. D., Ovsyannikov D. A., Chung S.-L. Optimization
of a radial matching section. {\it International Journal of Modern
Physics A}, 2009, vol. 24(5), pp. 952--958.

24. Ovsyannikov A. D., Ovsyannikov D. A., Chung S.-L. Optimization
of matching section of an accelerator with a spatially uniform
quadrupole focusing. {\it Technical Physics. The Russian Journal
of Appl. Phys.}, 2009, vol. 11, pp. 1663--1666.

25. Ovsyannikov D. A., Ovsyannikov A. D., Antropov I., Kozynchenko
V.  BDO-RFQ code and optimization models. {\it  Proceedings of the
International Conference of Physics and Control}, 2005, pp.
282--288.

26. Ovsyannikov D. A., Mizintseva M. A., Ovsyannikov A. D. Joint
optimization of  smooth and nonsmooth functionals on beams of
trajectories. {\it Optimal control and differential games.
Proceedings of the International Conference dedicated to the 110th
anniversary of the birth of Lev Semenovich Pontryagin}. Moscow,
Steklov Mathematical Institute of RAS Publ., 2018, pp. 203--205.

27. Balabanov M. Yu., Mizintseva M. A., Ovsyannikov D. A. Beam
dynamics optimiza\-tion in a linear accelerator. {\it Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2018, vol. 14, iss. 1, pp. 4--13.

28. Mizintseva M. А. Ob odnoi zadache minimizatsii gladkih i
neglagkih functsionalov [On one problem of minimization of smooth
and non-smooth functionals]. {\it Vestnik of Saint Petersburg
State University of Technology and Design. Series 1. Natural and
Technical Sciences}, 2018, no. 2, pp. 37--41. (In Russian)

29.  Mizintseva M., Ovsyannikov D. Minimax problem of simultaneous
optimization of smooth and non-smooth functionals. {\it
Constructive non-smooth  analysis and related topics. Proceedings
of Conference CNSA 2017}. IEEE, 2017, pp. 218--222.

30. Mizintseva M., Ovsyannikov D. On the minimax problem of beam
dynamics optimization. {\it Proceedings of the 25th Russian
Particle Accelerator Conference,  RuPAC 2016}. Saint Petersburg,
2016, pp. 360--362.

31. Pontryagin L. S., Boltyansky V. G., Gamkrelidze R. V.,
Mishchenko E. F. {\it Matematicheskaia teoria optimalnyh
protsessov} [{\it Mathematical theory of optimal processes\,}].
Moscow, Nauka Publ., 1969, 384 p. (In Russian)

32. Kapchinsky I. M. {\it Teoria lineinyh resonansnyh uskoritelei}
[{\it Theory of linear resonance accele\-rators\,}]. Moscow,
Energoizdat Publ., 1982, 239 p. (In Russian)

33. Golovkina A., Ovsyannikov D., Olaru S. Performance
optimization of radioactive waste transmutation in accelerator
driven system. {\it Cybernetics and Physics}, 2018, vol. 7, no. 4,
pp. 210--215.

34. Ovsyannikov D., Zavadskiy S. Pareto-optimal choice of
controlled dimension  for plasma stabilization system. {\it
IFAC-Papers OnLine}. Elsevier Science Publishing  Company Inc.
eISSN: 2405-8963, 2018, vol. 51, no. 32, pp. 175--178.

35. Bazhanov P., Kotina E., Ovsyannikov D., Ploskikh V.
Optimization algorithm of the velocity field determining in image
processing. {\it Cybernetics and Physics}, 2018,  vol. 7, no. 4,
pp. 174--181.

\vskip 1.5mm

Received:  March 02, 2019.

Accepted: February 13, 2020.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip2mm \textit{Dmitri A. Ovsyannikov} --- Dr. Sci. in Physics
and Mathematics, Professor; d.a.ovsyannikov@spbu.ru

\vskip2mm \textit{Maria A. Mizintseva} --- Magister;
m.mizintseva@spbu.ru

\vskip2mm \textit{Mihail Yu. Balabanov} --- PhD in Physics and
Mathematics, Senior Researcher Worker;\\ m.balabanov@spbu.ru

\vskip2mm \textit{Alexander  P. Durkin} --- PhD in Technics,
Associate Professor; durkinap@mail.ru

\vskip2mm \textit{Nikolai S. Edamenko} --- PhD in Physics and
Mathematics, Associate Professor; n.edamenko@spbu.ru

\vskip2mm \textit{Elena D. Kotina} --- Dr. Sci. in Physics and
Mathematics, Professor; e.kotina@spbu.ru

\vskip2mm \textit{Alexander D. Ovsyannikov} --- PhD in Physics and
Mathematics, Associate Professor;\\ a.ovsyannikov@spbu.ru\par
%
}
