
{\small

\vskip6mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. %\bibitem{vlad}
 {\it Владимиров Ю. С.} Системы отсчета в теории гравитации.
М: Энергоиздат, 1982. 256~с.


%\bibitem{math}
2.   {\it Sachs R. K., Wu H.}  General relativity for mathematicians.
New York: Springer, 1977. 291~p.


%\bibitem{driv14}
3. {\it Drivotin O. I.} Rigorous definition of the reference frame
// Вестник Санкт-Петербургского университета. Сер. 10. Прикладная математика.
Информатика. Процессы управления. 2014. Вып.~4. С.~25--36.

%\bibitem{lass}
4. {\it Lass H.}
Accelerating frames of reference and the clock paradox //
American Journal of Physics. 1963. Vol.~31. Iss.~4. P.~274--276.

%\bibitem{marsh}
5. {\it Marsh L. McL.}
Relativistic accelerated systems //
American Journal of Physics. 1965. Vol.~33. Iss.~11. P.~934--938.

%\bibitem{marzlin}
6. {\it Marzlin K. P.}
What is the reference frame of an accelerated observer? //
Physics Letters A. 1996. Vol.~215. P.~1--6.

%\bibitem{misnerbook}
7. {\it Misner C. W., Thorn K. S., Wheeler J. A.} Gravitation.
Princeton: Princeton University Press, 2017. 1279~p.

%\bibitem{misner}
8. {\it Manasse F. K., Misner C. W.}
Fermi normal coordinates
and some basic concepts in differential geometry //
Journal of Mathematical Physics. 1963. Vol.~4. Iss.~6. P.~735--745.

%\bibitem{driv15}
9. {\it Дривотин О. И.}
О плотности потока импульса гравитационного поля~// Вестник Санкт-Петербургского университета.  Прикладная математика.
Информатика. Процессы управления. 2021. Т.~17. Вып.~2. С.~137--147. %\\
https://doi.org/10.21638/11701/spbu10.2021.204


%\bibitem{drivmono}
10. {\it Дривотин О. И.} Математические основы теории поля.
СПб.: Изд-во С.-Петерб. ун-та, 2010. 168~с.

%\bibitem{pods}
11. {\it Podsosenov S. A., Foukzon J., Potapov A., Men'kova E.}
Electrodynamics in noninertial reference frames  //
Journal of Applied Mathematics and Physics. 2016. Vol.~4. P.~806--843.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 5 мая 2022~г.

Cтатья принята к~печати 21 июня 2022~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Дривотин Олег Игоревич} ---  д-р физ.-мат. наук, проф.;
 o.drivotin@spbu.ru

}
