
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf On the determination of spacetime geometry %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it O.~I.~Drivotin%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Drivotin O.~I. On the determination of spacetime geometry. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent A new approach allowing to determine
the metric tensor in various points
of the spacetime is proposed.
Such approach gives an opportunity
to investigate the simulta\-neity of events
not only locally, but also globally,
without using of the syn\-chro\-ni\-za\-tion procedure,
traditionally applied in the theory of the spacetime.
On the base of the method of simultaineity  determination
 described in the article,
it is possible to construct broad classes
of reference frames.
As an example, a reference frame is considered,
all ovservers of which move with
the same arbitrarily changing velocity
along some direction.
\\[1mm]
\textit{Keywords}: metric tensor, simultaneity,
reference frame, accelerated reference frame.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. %\bibitem{vlad}
 Vladimirov Yu. S. {\it Sistemy otscheta v teorii gravitatsii}
[{\it Reference frames in gravitation theory\,}].
Moscow, Energoizdat Publ., 1982, 256~p.
  (In Russian)


%\bibitem{math}
2.   Sachs R. K., Wu H.  {\it General relativity for mathematicians.}
New York, Springer Publ., 1977, 291~p.



%\bibitem{driv14}
3. Drivotin O.I.
 Rigorous definition of the reference frame.
{\it Vestnik of Saint Petersburg University. Series 10.
Applied Mathematics. Computer Science. Control Processes},
2014, iss.~4, pp.~25--36.

%\bibitem{lass}
4. Lass H.
Accelerating frames of reference and the clock paradox.
{\it American Journal of Physics}, 1963, vol.~31, iss.~4, pp.~274--276.

%\bibitem{marsh}
5. Marsh L. McL.
Relativistic accelerated systems.
{\it American Journal of Physics}, 1965, vol.~33, iss.~11, pp.~934--938.

%\bibitem{marzlin}
6. Marzlin K. P.
What is the reference frame of an accelerated observer?
{\it Physics Letters A}, 1996, vol.~215, pp.~1--6.

%\bibitem{misnerbook}
7. Misner C. W., Thorn K. S., Wheeler J. A. {\it Gravitation.}
Princeton, Princeton University Press, 2017, 1279~p.

%\bibitem{misner}
8. Manasse F. K., Misner C. W.
Fermi normal coordinates
and some basic concepts in differential geometry.
{\it Journal of Mathematical Physics}, 1963, vol.~4, iss.~6, pp.~735--745.

%\bibitem{driv15}
9. Drivotin O.~I.
O plotnosti potoka impulsa gravitatsionnogo polya
[On momentum flow density of the gravitational field].
 {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
  2021, vol.~17,  iss.~2, pp.~137--147.
(In Russian) \\
https://doi.org/10.21638/11701/spbu10.2021.204

%\bibitem{drivmono}
10. Drivotin O.~I.
{\it Matematicheskiye osnovy teorii polya}
[{\it Mathematical foundations of the field theory}].
St~Petersburg, St~Petersburg  University Press, 2010, 168~p.
(In Russian)

%\bibitem{pods}
11. Podsosenov S. A., Foukzon J., Potapov A., Men'kova E.
Electrodynamics in noninertial reference frames.
{\it Journal of Applied Mathematics and Physics}, 2016, vol.~4, pp.~806--843.


\vskip1.5mm Received:  May 5, 2022.

Accepted: June 21, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r's \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Oleg I. Drivotin} --- Dr. Sci. in Physics and Mathematics,
Professor; o.drivotin@spbu.ru \par
%
%
}
