

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2.5%2
mm

{\footnotesize



1.  Kuchkarov I.,  Petrosian O. On class of linear quadratic
non-cooperative differential games with continuous updating. {\it
Lecture Notes in Computer Science}, 2019, vol.~11548, pp.~635--650.

2.   Petrosian O.,   Tur A. Hamilton~--- Jacobi~--- Bellman equations for
non-cooperative differential games with continuous updating.
 {\it Mathematical
Optimization Theory and Ope\-rations Research. MOTOR 2019.}  Ed.  by
 I.~Bykadorov, V.~Strusevich,  T.~Tchemisova. {\it Communications in
Computer and Information Science}, 2019,  vol.~1090, pp.~178--191.

 3.
 Kuchkarov I.,  Petrosian O. Open-loop based strategies for
autonomous linear quadratic game models with continuous updating.
{\it Mathematical Optimization Theory and Operations Research. MOTOR
2020.}  Ed. by A.~Kononov, M.~Khachay, V.~Kalyagin, P.~Pardalos.
{\it Lecture Notes in Computer Science}, 2020, vol.~12095, pp.~212--230.


4.  Wang Z.,  Petrosian  O. On class of non-transferable utility
cooperative differential games with continuous updating. {\it
Journal of Dynamics $\&$ Games},  2020, vol.~7, no.~4, pp.~291--302.\\
https://doi.org/10.3934/jdg.2020020

5. Shi L., Petrosian O. L., Boiko A. V. Looking forward approach for dynamic
cooperative advertising game model. {\it Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2019, vol.~15, iss.~2, pp.~221--234. %\\
https://doi.org/10.21638/11702/spbu10.2019.206


6.  Petrosyan L.\,A.,  Murzov N.\,V.  Game-theoretic problems in
mechanics. {\it  Lithuanian Mathematical Collection}, 1966, vol.~3,
pp.~423--433.

7.  Petrosyan L.\,A.,  Shevkoplyas E.\,V.  Cooperative differential
games with random duration. {\it  Vestnik of Saint Peterburg
University. Series~1. Mathematics. Mechanics. Astronomia}, 2000,
iss.~4, pp.~18--23.

8.   Shevkoplyas  E.\,V. The Hamilton~--- Jacobi~--- Bellman equation for a class of differential games with random duration. {\it Autom. Remote
Control}, 2014, vol.~75, pp.~959--970.\\
https://doi.org/10.1134/S0005117914050142



9.   Bellman R. {\it Dynamic programming}. Princeton, Princeton
University Press, 1957, 342~p.

10.  Dockner E.\,J.,  Jorgensen S.,  Long N.\,V.,   Sorger G. {\it
Differential games in economics and management science}. Cambridge,
Cambridge University Press, 2000, 382~p.

11.  Kostyunin S.,  Palestini A.,  Shevkoplyas E. A differential
game-based approach to extraction of exhaustible resource with
random terminal instants. {\it Contributions to Game Theory and
Management}, 2012,  vol.~5, pp.~147--155.

12.   Petrosian  O.,  Tur A.,  Wang Z., Gao  H. Cooperative
differential games with continuous updating using
Hamilton\,---\,Jacobi\,---\,Bellman equation.  {\it Optimization methods and
software},  2020, pp.~1099--1127. https://doi.org/10.1080/10556788.2020.1802456


\vskip 2.5%1.5
mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  December~21, 2021.

Accepted: June 21, 2022.

%\vskip 6mm
\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Anna V. Tur} --- PhD in Physics and Mathematics,
Associate Professor; a.tur@spbu.ru \par


\vskip 2mm
 \textit{Ovanes L. Petrosian} --- PhD in Physics and
Mathematics, Associate Professor;\\ petrosian.ovanes@yandex.ru
 \par
%
%
}
