
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. \emph{Erneux Th.} Applied delay differential equations. New
York: Springer Science+Business Media, LLC, 2009. 204~p.

%   \bibitem{SmithBook}
2. \emph{Smith H.} An introduction to delay differential equations
with applications to the life sciences. New York: Springer
Science+Business Media, LLC, 2011. 172~p.

%   \bibitem{BellZenn}
3. \emph{Bellen A., Zennaro M.} Numerical methods for delay
differential eqautions. Oxford: Oxford University Press, 2013.
396~p.

%   \bibitem{GugHai2001}
4. \emph{Guglielmi N., Hairer E.} Implementing {R}adau {IIA}
methods for stiff delay differential equa\-ti\-ons // Computing.
2001. Vol.~67. N~1. P.~1--12.

%   \bibitem{MasTorVer2005}
5. \emph{Maset S., Torelli L., Vermiglio R.} Runge---Kutta methods
for retarded functional differential equations // Mathematical
Models and Methods in Applied Sciences. 2005.  Vol.~15. N~8.
P.~1203--1251.

%   \bibitem{Hairer1}
6. \emph{Hairer E., N\o rsett S. P., Wanner G.} Solving ordinary
differential equations~I: Nonstiff problems, 2~ed., 3rd corr.
print. Berlin; Heidelberg: Springer-Verlag, 2008. 528~p.

%   \bibitem{Shampine2005}
7. \emph{Shampine L. F.} Solving ODEs and DDEs with residual
control // Applied Numerical Mathe\-matics. 2005. Vol.~52.
P.~113--127.

%   \bibitem{OwrZen1992}
8. \emph{Owren B., Zennaro M.} Derivation of efficient,
continuous, explicit Runge---Kutta methods // SIAM Journal on
Scientific and Statistical Computing. 1992. Vol.~13.
P.~1488--1501.

%   \bibitem{CMMP2010}
9. \emph{Еремин А. С., Олемской И. В.} Вложенный метод
интегрирования систем структурно разделенных обыкновенных
дифференциальных уравнений // Журн. вычисл. математики и~матем.
физики. 2010. Т.~50. №\,3. C.~434--448.

%   \bibitem{OleKov2018}
10. \emph{Олемской И. В., Коврижных Н. А.}      Семейство
шестиэтапных методов шестого по\-ряд\-ка // Вестн. С.-Петерб.
ун-та. Прикладная математика. Информатика. Процессы управления.
2018. Т.~14. Вып.~3. С.~215--229.

%   \bibitem{ICCSA2017}
11. \emph{Eremin A. S., Kovrizhnykh N. A.} Continuous extensions
for structural Runge---Kutta me\-thods~// Computational Science
and Its Applications~--- ICCSA 2017 / eds. O. Gervasi et al.
Lecture Notes in Computer Science. 2017. Vol.~10405. P.~363--378.

%   \bibitem{ICNAAM15}
12. \emph{Eremin A. S., Olemskoy I. V.} Functional continuous
{R}unge---{K}utta methods for special sys\-tems~// Proceedings of
the International Conference on Numerical Analysis and Applied
Mathe\-matics 2015 (ICNAAM--2015). AIP Conference Proceedings.
2016. Vol.~1738. Art.~no.~100003.

%   \bibitem{FelNev1984}
13. \emph{Feldstein A., Neves K.\,W.} High order methods for
state-dependent delay differential equa\-ti\-ons with nonsmooth
solutions // SIAM Journal of Numerical Analysis. 1984. Vol.~21.
N~5. P.~844--863.

%   \bibitem{ICNAAM14}
14. \emph{Eremin A. S., Humphries A. R.} Efficient accurate
non-iterative breaking point detection and computation for
state-dependent delay differential equations // Proceedings of the
International Conference on Numerical Analysis and Applied
Mathematics 2014 (ICNAAM--2014). AIP Confe\-ren\-ce Proceedings.
2015. Vol.~1648. Art.~no.~150006.

%   \bibitem{Tavernini1971}
15. \emph{Tavernini L.} One-step methods for the numerical
solution of {Volterra} functional differential equations // SIAM
Journal of Numerical Analysis. 1971. Vol.~8. N~4. P.~786--795.

%   \bibitem{ActaNumer2009}
16. \emph{Bellen A., Guglielmi N., Maset S., Zennaro M.} Recent
trends in the numerical solution of retarded functional
differential equations // Acta Numerica. 2009. P.~1--110.

%   \bibitem{Miyatake2014}
17. \emph{Miyatake Yu.} An energy-preserving exponentially-fitted
continuous stage Runge---Kutta method for Hamiltonian systems //
BIT Numerical Mathematics. 2014. Vol.~54. P.~777--799.


%   \bibitem{HaleBook}
18. \emph{Hale J. K.} Theory of functional differential equations.
New York: Springer-Verlag, 1977. 366~p. %   %\bibitem{HaleBook} \emph{Хейл Дж.} Теория функционально-дифференциальных уравнений. Пер. с~англ. М.:~Мир, 1984. 421~c.

%   \bibitem{KimPimBook}
19. \emph{Kim A.V.} i-Smooth analysis: Theory and applications.
Beverly, MA: Scrivener Publishing LLC; Hoboken, NJ:
John Wiley \& Sons Inc., 2015. 296~p. %   %\bibitem{KimPimBook} \emph{Ким А.\,В., Пименов В.\,Г.} i-Гладкий анализ и~численные методы решения функ\-цио\-наль\-но-диф\-фе\-рен\-ци\-аль\-ных уравнений. Ижевск: РХД, 2004. 256~c.

%   \bibitem{ANM2019}
20. \emph{Eremin A.\,S.} Functional continuous Runge---Kutta
methods with reuse // Applied Numeri\-cal Mathematics. 2019.
Vol.~146. P.~165--181.

%   \bibitem{PaulReport}
21. \emph{Paul C.\,A.\,H.} A test set of functional differential
equations. Tech. Report  N~243. Manches\-ter: Manchester Centre
for Computational Mathematics, University of Manchester, Feb.
1994. 41~p.

%   \bibitem{MagpantayThesis}
22. \emph{Magpantay F.\,M.\,G.} On the stability and numerical
stability of a model state dependent delay differential equation:
PhD thesis. Montreal, Quebec, Canada: McGill University, 2011.
189~p.



\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 30 апреля 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Еремин Алексей Сергеевич} --- канд. физ.-мат.
наук; a.eremin@spbu.ru

}
