
{\normalsize

\vskip 6mm%6mm

\noindent{\bf Combined functional continuous method for delay
differential equations}

}

\vskip 2mm%2mm

{\small

\noindent{\it A.~S.~Eremin%$\,^1$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 2mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm%3mm


\noindent \textbf{For citation:}  Eremin~A.~S. Combined functional
continuous method for delay differential equa\-tions. {\it Vestnik
of Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent In the paper a combined numerical method
for discrete delay differential equations is presented. The method
is an embedded pair of type two explicit Runge---Kutta methods of
order four: a continuous method with six stages and a
stage-continuous method with seven stages. Their combination
provides an effective solution of discrete delay differential
equations. The combined method remains explicit for any values of
the delay: for small values the stage-continuous scheme is used
while for large delays a faster continuous scheme is applied. The
scheme to use is chosen automatically based on whether the delay
falls into the current step and a switch to the stage-continuous
scheme can be made at any stage when required. The embedding of
the methods lets to minimize the required number of the right-hand
side function computations. The order conditions and the proof of
their resolvability with the stated number of stages are
presented. Tests, confirming
the effectiveness of the proposed methods, are made.\\[1mm]
\textit{Keywords}: delay differential equations, continuous
methods, functional continuous method, stage-continuous method.
\par}

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Erneux Th. {\it Applied delay differential equations}. New
York, Springer Science+Business Media, LLC Press, 2009, 204~p.

%   \bibitem{SmithBook}
2. Smith H. {\it An introduction to delay differential equations
with applications to the life sciences}. New York, Springer
Science+Business Media, LLC Press, 2011, 172~p.

%   \bibitem{BellZenn}
3. Bellen A., Zennaro M. {\it Numerical methods for delay
differential eqautions}. Oxford, Oxford University Press, 2013,
396~p.

%   \bibitem{GugHai2001}
4. Guglielmi N., Hairer E. Implementing {R}adau {IIA} methods for
stiff delay differential equa\-ti\-ons. \emph{Computing}, 2001,
vol.~67, no.~1, pp.~1--12.

%   \bibitem{MasTorVer2005}
5. {Maset S., Torelli L., Vermiglio R.} Runge---Kutta methods for
retarded functional differential equations. \emph{Mathematical
Models and Methods in Applied Sciences}, 2005,  vol.~15, no.~8,
pp.~1203--1251.

%   \bibitem{Hairer1}
6. {Hairer E., N\o{}rsett S. P., Wanner G.} Solving ordinary
differential equations~I: Nonstiff problems, 2~ed., 3rd corr.
print. Berlin, Heidelberg, Springer-Verlag Press, 2008, 528~p.

%   \bibitem{Shampine2005}
7. {Shampine L. F.} Solving ODEs and DDEs with residual control.
\emph{Applied Numerical Mathema\-tics}, 2005, vol.~52,
pp.~113--127.

%   \bibitem{OwrZen1992}
8. {Owren B., Zennaro M.} Derivation of efficient, continuous,
explicit Runge---Kutta methods. \emph{SIAM Journal on Scientific
and Statistical Computing}, 1992, vol.~13, pp.~1488--1501.

%   \bibitem{CMMP2010}
9. Eremin A. S., Olemskoy I. V. An embedded method for integrating
systems of structurally separated ordinary differential equations.
\emph{Computational Mathematics and Mathematical Physics}, 2010,
vol.~50, no.~3, pp.~414--427.
%https://link.springer.com/article/10.1134/S0965542510030048

%   \bibitem{OleKov2018}
10. {Olemskoy I. V., Kovrizhnykh N. A.} Semeistvo shestietapnyh
metodov shestogo poriadka [A family of sixth-order methods with
six stages]. \emph{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2018, vol.~14,
no.~3, pp.~215--229. (In Russian)

%\emph{Олемской И.\,В., Коврижных Н.\,А.}      Семейство шестиэтапных методов шестого по\-ряд\-ка // Вестн. С.-Петерб. ун-та. Прикладная математика. Информатика. Процессы управления. 2018. Т.~14. Вып.~3. С.~215--229.

%   \bibitem{ICCSA2017}
11. {Eremin A. S., Kovrizhnykh N. A.} Continuous extensions for
structural {R}unge---{K}utta me\-thods. \emph{Computational
Science and its Applications --- ICCSA 2017.} Eds. O.~Gervasi et
al. \emph{Lecture Notes in Computer Science}, 2017, vol.~10405,
pp.~363--378.

%   \bibitem{ICNAAM15}
12. {Eremin A. S., Olemskoy I. V.} Functional continuous
Runge---Kutta methods for special systems. \emph{Proceedings of
the International Conference on Numerical Analysis and Applied
Mathema\-tics 2015 (ICNAAM--2015). AIP Conference Proceedings},
2016, vol.~1738, art.~no.~100003.

%   \bibitem{FelNev1984}
13. {Feldstein A., Neves K.\,W.} High order methods for
state-dependent delay differential equa\-tions with nonsmooth
solutions. \emph{SIAM Journal of Numerical Analysis}, 1984,
vol.~21, no.~5, pp.~844--863.

%   \bibitem{ICNAAM14}
14. {Eremin A.\,S., Humphries A.\,R.} Efficient accurate
non-iterative breaking point detection and computation for
state-dependent delay differential equations. \emph{Proceedings of
the International Conference on Numerical Analysis and Applied
Mathematics 2014 (ICNAAM--2014). AIP Confe\-ren\-ce Proceedings},
2015, vol.~1648, art.~no.~150006.

%   \bibitem{Tavernini1971}
15. {Tavernini L.} One-step methods for the numerical solution of
{Volterra} functional differential equations. \emph{SIAM Journal
of Numerical Analysis}, 1971, vol.~8, no.~4, pp.~786--795.

%   \bibitem{ActaNumer2009}
16. {Bellen A., Guglielmi N., Maset S., Zennaro M.} Recent trends
in the numerical solution of retarded functional differential
equations. \emph{Acta Numerica}, 2009, pp.~1--110.

%   \bibitem{Miyatake2014}
17. {Miyatake Yu.} An energy-preserving exponentially-fitted
continuous stage Runge---Kutta method for Hamiltonian systems.
\emph{BIT Numerical Mathematics}, 2014, vol.~54, pp.~777--799.


%   \bibitem{HaleBook}
18. {Hale J. K.} {\it Theory of functional differential
equations}.
New York, Springer-Verlag Press, 1977, 366~p. %   %\bibitem{HaleBook} \emph{Хейл Дж.} Теория функционально-дифференциальных уравнений. Пер. с англ. М.:~Мир, 1984. 421~c.

%   \bibitem{KimPimBook}
19. {Kim A. V.} {\it i-Smooth analysis: Theory and applications}.
Beverly, MA, Scrivener Publishing LLC, Hoboken, NJ,
John Wiley \& Sons Inc. Press, 2015, 296~p. %   %\bibitem{KimPimBook} \emph{Ким А.\,В., Пименов В.\,Г.} i-Гладкий анализ и численные методы решения функ\-цио\-наль\-но-диф\-фе\-рен\-ци\-аль\-ных уравнений. Ижевск: РХД, 2004. 256~c.

%   \bibitem{ANM2019}
20. {Eremin A. S.} Functional continuous Runge---Kutta methods
with reuse. \emph{Applied Numerical Mathematics}, 2019, vol.~146,
pp.~165--181.

%   \bibitem{PaulReport}
21. {Paul C.\,A.\,H.} \emph{A test set of functional differential
equations}. Tech. Report no.~243. Manches\-ter: Manchester Centre
for Computational Mathematics, University of Manchester Press,
Feb. 1994, 41~p.

%   \bibitem{MagpantayThesis}
22. {Magpantay F.\,M.\,G.} \emph{On the stability and numerical
stability of a model state dependent delay differential equation}.
PhD thesis. Montreal, Quebec, Canada, McGill University Press,
2011, 189~p.



\vskip1.5mm Received:  April 30, 2019.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip1.5mm%2mm
\textit{Alexey S. Eremin} --- PhD in Physics and Mathematics;
a.eremin@spbu.ru

}
