
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Von Bekesy G.} Ueber die Empfindlichkeit des stehenden und
sitzenedn Menschen gegen sinusfoermige Erschuetterungen  //
Akustische Zeitschrift. 1939. Vol.~4. P. 360--369.

2. {\it Coermann R. R.} The mechanical impedance of the human body
in sitting and standing position at low frequencies // Human
factor. 1962. Vol.~4. P. 227--253.

3. {\it Потёмкин Б. А., Фролов К. В.}  Построение динамической
модели тела человека-оператора, подверженного действию
широкополосных случайных вибраций // Виброизоляция машин
и~виброзащита человека-оператора / отв. ред. К. В. Фролов. М.:
Наука, 1973. C. 17--30.

4. {\it Griffin M. J.}  Vertical vibration of seated subjects:
effects of posture, vibration level, and frequency // Aviation
Space and Environmental Medicine. 1975. Vol. 46. P. 269--276.

5. {\it Paddan G. S., Griffin M. J.}  The transmission of
translational seat vibration to the head --- I. Vertical seat
vibration // Journal of Biomechanics. 1988. Vol.~21. Iss.~3.
P.~191--197.

6. {\it Fairley T. E., Griffin M. J.} The apparent mass of the
seated human body: Vertical vibration //  Journal of Biomechanics.
1989. Vol. 22. N~2. P. 81--94.

7. {\it Глухарев K. K., Потёмкин Б. А., Фролов К. В., Сиренко В.
Н.}  Элементы нелинейной теории колебаний в~анализе биомеханики
тела человека // Виброзащита человека-оператора и~вопросы
моделирования / отв. ред. К.~В.~Фролов. М.: Наука, 1973.
C.~12--22.

8. {\it Demic~M.\:S., Lukic~J.\:K. }  Human body under
two-directional random vibration // Journal of Low Frequency Noise
Vibration and Active Control. 2008. Vol.~27. N~3. P.~185–-201.

9. {\it Qiu ~Y., Griffin~M.\:J.} Biodynamic response of the seated
human body to single-axis and dual-axis vibration: effect of
backrest and non-linearity // Industrial Health. 2012. Vol.~50.
N~1. P.~37--51.

10. {\it Muksian~R., Nash~C.\:D.}  On frequency-depended damping
coefficient in lumped-parameter models of human being //  Journal
of Biomechanics. 1976. Vol. 9. P.~339--342.

11. {\it Wan~Y., Schimmels~J.\:M.}  A simple model that captures
the essential dynamics of a seated human exposed to whole body
vibration // Advances in Bioengineering. 1995. Vol.~31. ASME publ.
BED (Bioengineering Division). P.~333--334.

12. {\it  Liu~C., Qiu~Y., Griffin~M.\:J.} Dynamic forces over the
interface between a seated human body and a rigid seat during
vertical whole-body vibration //  Journal of Biomechanics. 2017.
Vol.~61. N~16. P.~176--182.

13. {\it Bai Xian-Xu, Xu Shi-Xu, Cheng Wei, Qian Li-Jun.} On
4-degree-of-freedom biodynamic models of seated occupants:
Lumped-parameter modeling // Journal of Sound and Vibration. 2017.
Vol.~402. N~18.  P.~122--141.

14. {\it Abbas~W., Abouelatta~O.\:B., El-Azab~M., Elsaidy~M.,
Megahed~A.\:A.}  Optimization of biodynamic seated human models
using genetic algorithms // Engineering. 2010. Vol.~2.
P.~710--719.

15. {\it Boileau~P.\:E., Rakheja~S.} Whole-body vertical
biodynamic response characteristics of the seated vehicle driver:
measurement and model development  // International Journal of
Ind. Ergonomics. 1998. Vol.~22. P.~449--472.

16. {\it Zhang~E., \,Xu~L.\:A.,\, Liu~Z.\:H., Li~X.\:L.\,}
\,Dynamic \,modeling\, and\, vibration\, characteristics~ of
multi-DOF upper part system of seated human body //  Chine Journal
of Engineering Design. 2008. Vol.~15. P.~244--249.


\vskip 1.5mm

%\newpage

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 7 августа 2019~г.

Cтатья принята к~печати 7 ноября 2019~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Трегубов Владимир Петрович} --- д-р физ.-мат.
наук, проф.; v.tregubov@spbu.ru

\vskip2mm \textit{Егорова Надежда Константиновна} --- аспирант;
nadezhda\_ego@mail.ru


}
