
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1.  {\it Li Y., Sun Y, Yeow J. T. W.} Nanotube field electron
emission: Principles, development, and applications
//  Nanotechnology. 2015. Vol.~26. Iss.~24. N~242001 (23~p.).
%DOI: 10.1088/0957-4484/26/24/242001
\pagebreak

2. {\it Kaur G., Pulagara N.V., Kumar R., Lahiri I.} Metal
foam-carbon nanotube-reduced graphene oxide hierarchical
structures for efficient field emission
// Diamond and Related Materials. 2020. Vol.~106. N~107847 (8~p.).
%DOI: 10.1016/j.diamond.2020.107847


3. {\it Grillo  A., Giubileo F., Iemmo L., Luongo G., Urban F.,
Passacantando  M., Di Bartolomeo  A.} Field emission from mono and
two-dimensional nanostructures
//      Materials Today: Proceedings. 2020. Vol.~20. P.~64--68.
%DOI: 10.1016/j.matpr.2019.09.005

4. {\it Lim J., Gupta A. P., Yeo S. J., Kong M., Cho C.-G., Kim S.
H., Ahn J. S., Mativenga~M., Ryu~J.} Design and fabrication of
CNT-based e-gun using stripe-patterned alloy substrate for X-ray
applications~//  IEEE  Transactions on Electron Devices. 2019.
Vol.~66. Iss.~12. N~8874963. P.~5301--5304.
    % DOI: 10.1109/TED.2019.2943870


5.
    {\it Filip V., Filip L. D., Wong H.}
Review on peculiar issues of field emission in vacuum
nanoelectronic devices
//  Solid-State Electronics.  2017. Vol.~138. P.~3--15.
%DOI: 10.1016/j.sse.2017.09.010

6.
    %{\it Соминский Г.Г., Сезонов В.Е., Тарадаев Е.П., Тумарева Т.А., Тарадаев С.П., Рукавицына А.А., Гиваргизов М.Е., Степанова А.Н.}
%Полевые эмиттеры для высоковольтных миниатюрных электронных устройств, работающих в техническом вакууме
%// Известия высших учебных заведений. Радиофизика. 2019. Т.~62, № 7-8. С.~603--612.
%
%\noindent
 {\it Sominskii G. G., Sezonov V. E., Taradaev E. P.,  Tumareva T. A., Taradaev S. P., Ruka\-vi\-tsy\-na~A.~A., Gi\-var\-gi\-zov~M.~E., Ste\-pa\-no\-va~A.~N. }
 Field emitters for miniature high-voltage electronic devices operating in technical vacuum
//  Radiophysics and Quantum Electronics. 2019. Vol.~62. Iss.~7--8. P.~539--546.
%DOI: 10.1007/s11141-020-10000-8


7. {\it Бугаев А. С., Виноградова Е. М., Егоров Н. В., Шешин Е.
П.} Автоэлектронные катоды и пушки. Долгопрудный: Издат. дом
<<Интеллект>>, 2017. 288~с.

%{\it Bugaev A.\:S., Vinogradova E.\:M., Egorov N.\:V., Sheshin E.\:P.}
%Avtoelektronnyye katody i pushki [Field-electron cathodes and guns]. Dolgo\-prudny, ID "Intellect", 2017, 288~p. (In Russian)

8.
 {\it Уфлянд Я.~С.} Метод парных уравнений в задачах математической физики. Л.: Наука, 1977. 220~с.

%{\it Uflyand Ya.S.} Metod parnykh uravneniy v zadachakh matematicheskoy fiziki  [Method of paired equations in problems of mathematical physics]. Leningrad, Nauka, 1977, 220~p. (in Russian)

9.
%{\it Лебедев Н.Н., Скальская И.П.}
%Распределение электричества на тонком гиперболоидальном сегменте
%// Ж. вычисл. матем. и матем. физ. 1967. Т.7,  № 2. С.348--356.
%
%
%\noindent
 {\it Lebedev N. N., Skal'skaya I. P.~}
Electrostatic distribution over a thin segment of a hyperboloid
// USSR Computational Mathematics and Mathematical Physics. 1967. Vol.~7. Iss.~2. P.~137--148.
% DOI: 10.1016/0041-5553(67)90008-0


10.
%{\it Гобсон Е.В.} Теория сферических и эллипсоидальных функций.  М.: Издательство иностранной литературы, 1952, 476~с.
%
{\it Hobson E.W.} The theory of spherical and ellipsoidal
harmonics. Cambrige: Cambridge University Press, 1931. 500~p.


11.
%{\it Виноградова Е.М., Егоров Н.В.}
%Математическое моделирование диодной системы на основе полевого эмиттера
%// ЖТФ. 2011. Т.81, № 9. С.~1--5.
%
%\noindent
{\it Vinogradova E. M., Egorov N. V.} Mathematical modeling of a
diode system based on a field emitter
// Technical Physics.  2011. Vol.~56. Iss.~9. P.~1219--1224.
% DOI: 10.1134/S1063784211090295


12.
  {\it Egorov N. V., Vinogradova E. M.}
Mathematical modeling of the electron beam formatting systems on
the basis of field emission cathodes with various shapes
// User Modeling and User-Adapted Interaction. 2003. Vol.~72. Iss.~2. P.~103--111.   %DOI:10.1016/S0042-207X(03)00107-6


13. {\it Abramowitz M., Stegun I. A.}  Handbook of mathematical
functions with formulas, graphs, and mathematical tables.
Washington, DC: NBS,  1964.  1046~p.  (Applied Mathe\-ma\-tics
Series 55).

14.
%{\it Градштейн И.С., Рыжик И.М.} Таблицы интегралов, сумм, рядов и произведений. М.: Физматгиз, 1963. 1100~с.
{\it  Gradshteyn I. S., Ryzhik I. M.} Table of integrals, series,
and products. 7th ed.  Amsterdam; Bos\-ton; Heidelberg; London;
New York; Oxford; Paris; San Diego; San Francisco; Singapore;
Sydney; To\-kyo: Academic Press, 2007. 1171~p.


15.
%{\it Бейтмен Г., Эрдейи А.} Высшие трансцендентные функции. Т.~1. М.: Наука, 1973. 296~с.
%
{\it  Bateman H., Erdelyi A.} Higher transcendental functions. In
2 vol.~New York; Toronto; London: McGraw-Hill Book Company Inc.,
1953.  Vol.~1. 302~p.




%\pagebreak
\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 26 января 2020~г.

Cтатья принята к~печати 13 августа 2020~г.

\vskip5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip1.8%2
mm \textit{Егоров Николай Васильевич} --- д-р физ.-мат.
наук,  проф.; robby7@mail.ru

\vskip1.8%2
mm \textit{Виноградова Екатерина Михайловна} --- д-р
физ.-мат. наук,  проф.; e.m.vinogradova@spbu.ru

}
