
{\normalsize

\vskip 6mm%6mm

\noindent{\bf Mathematical modeling of a field emitter with a hyperbolic shape$^{*}$%
}

}

\vskip 2mm%2mm

{\small

\noindent{\it N. V. Egorov, E. M. Vinogradova%$\,^1$%
%, A. Y. Gorchakov$\,^{2,3,4}$%
%, A. J. Duysenbaeva$\,^{1}$%
%, M. A. Posypkin$\,^{2,3}$%
%, I.~О. Famylia%$\,^2$%

}

\vskip 2mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian Foundation for Basic Research (grant N~20-07-01086).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm%3mm


\noindent \textbf{For citation:}  Egorov N. V., Vinogradova  E. M.
Mathematical modeling of a field emitter with a hyperbolic shape.
{\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty. Ap\-plied
Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~16,~iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent This article is devoted to modeling a
field emission diode system. The emitter surface is a hyperboloid
of rotation. The anode surface is a part of the hyperboloid of
rotation, in a particular case, a circular diaphragm. A boundary
value problem is formulated for the Laplace equation with
non-axisymmetric boundary conditions of the first kind. A 3D
solution was found by the variable separation method in the
prolate spheroidal coordinates. The electrostatic potential
distribution is presented in the form of the Legendre functions
expansions. The calculation of the expansion coefficients is
reduced to solving a system of linear equations with constant
coefficients. All geometric dimensions of the system are the
parameters of the problem.\\[1mm]
\textit{Keywords}: micro and nanoelectronics, field emitter, field
emission, mathematical modeling, electrostatic potential,
boundary-value problem, Legendre functions.
\par}

\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1.  Li Y., Sun Y., Yeow J. T. W. Nanotube field electron emission:
Principles, development, and applications. {\it Nanotechnology},
2015, vol.~26, iss.~24, no.~242001 (23~p.).
%DOI: 10.1088/0957-4484/26/24/242001

2. Kaur G., Pulagara N. V., Kumar R., Lahiri I. Metal foam-carbon
nanotube-reduced graphene oxide hierarchical structures for
efficient field emission. {\it Diamond and Related Materials},
2020, vol.~106, no.~107847 (8~p.).
%DOI: 10.1016/j.diamond.2020.107847


3. Grillo  A., Giubileo F., Iemmo L., Luongo G., Urban F.,
Passacantando  M., Di Bartolomeo  A. Field emission from mono and
two-dimensional nanostructures.  {\it   Materials Today:
Proceedings}, 2020, vol.~20, pp.~64--68.
%DOI: 10.1016/j.matpr.2019.09.005

4. Lim J., Gupta A. P., Yeo S. J., Kong M., Cho C.-G., Kim S. H.,
Ahn J. S., Mativenga M., Ryu J. Design and fabrication of
CNT-based e-gun using stripe-patterned alloy substrate for X-ray
applications.  {\it IEEE  Transactions on Electron Devices}, 2019,
vol.~66, iss.~12, no.~8874963, pp.~5301--5304.
% DOI: 10.1109/TED.2019.2943870


5. Filip V., Filip L. D., Wong H. Review on peculiar issues of
field emission in vacuum nanoelectronic devices. {\it Solid-State
Electronics},  2017, vol.~138, pp.~3--15.
%DOI: 10.1016/j.sse.2017.09.010

6.
%{\it Соминский Г.Г., Сезонов В.Е., Тарадаев Е.П., Тумарева Т.А., Тарадаев С.П., Рукавицына А.А., Гиваргизов М.Е., Степанова А.Н.}
%Полевые эмиттеры для высоковольтных миниатюрных электронных устройств, работающих в техническом вакууме
%// Известия высших учебных заведений. Радиофизика. 2019. Т.~62, № 7-8. С.~603--612.
%
%\noindent
Sominskii G. G., Sezonov V. E., Taradaev E. P.,  Tumareva T. A.,
Taradaev S. P., Ruka\-vi\-tsy\-na~A.~A., Givargizov M. E.,
Stepanova A. N. Field emitters for miniature high-voltage
electronic devices operating in technical vacuum. {\it
Radiophysics and Quantum Electronics}, 2019, vol.~62, iss.~7--8,
pp.~539--546.
%DOI: 10.1007/s11141-020-10000-8


7.
%{\it Бугаев А.\:С., Виноградова Е.\:М., Егоров Н.\:В., Шешин Е.\:П.}
%Автоэлектронные катоды и пушки.
%Долгопрудный: ИД «Интеллект», 2017, 288~с.
%
Bugaev A. S., Vinogradova E. M., Egorov N. V., Sheshin E. P.~{\it
Avtoelektronnyye katody i pushki} [{\it Field-electron cathodes
and guns}]. Dolgo\-prudny, ID Intellect Publ., 2017, 288~p. (In
Russian)

8.
%{\it Уфлянд Я.С.} Метод парных уравнений в задачах математической физики. Л.: Наука, 1977, 220~с.
%
Uflyand Ya. S. {\it Metod parnykh uravneniy v zadachakh
matematicheskoy fiziki}  [{\it Method of paired equations in
problems of mathematical physics}]. Leningrad, Nauka Publ., 1977,
220~p. (In Russian)

9.
%{\it Лебедев Н.Н., Скальская И.П.}
%Распределение электричества на тонком гиперболоидальном сегменте
%// Ж. вычисл. матем. и матем. физ. 1967. Т.7,  № 2. С.348--356.
%
%
%\noindent
Lebedev N. N., Skal'skaya I. P.~Electrostatic distribution over a
thin segment of a hyperboloid. {\it  USSR Computational
Mathematics and Mathematical Physics}, 1967, vol.~7, iss.~2,
pp.~137--148.
% DOI: 10.1016/0041-5553(67)90008-0


10.
%{\it Гобсон Е.В.} Теория сферических и эллипсоидальных функций.  М.: Издательство иностранной литературы, 1952, 476~с.
%
Hobson E. W. {\it  The theory of spherical and ellipsoidal
harmonics}. Cambrige, Cambridge University Press, 1931, 500~p.


11.
%{\it Виноградова Е.М., Егоров Н.В.}
%Математическое моделирование диодной системы на основе полевого эмиттера
%// ЖТФ. 2011. Т.81, № 9. С.~1--5.
%
%\noindent
Vinogradova E. M., Egorov N. V. Mathematical modeling of a diode
system based on a field emitter. {\it  Technical Physics},  2011,
vol.~56, iss.~9, pp.~1219--1224.
% DOI: 10.1134/S1063784211090295


12. Egorov N. V., Vinogradova E. M. Mathematical modeling of the
electron beam formatting systems on the basis of field emission
cathodes with various shapes. {\it User Modeling and User-Adapted Interaction}, 2003, vol.~72, iss.~2, pp.~103--111.   %DOI:10.1016/S0042-207X(03)00107-6


13. Abramowitz M., Stegun I. A. {\it  Handbook of mathematical
functions with formulas, graphs, and mathematical tables}.
Washington, DC, NBS Press,   1964,  1046~p. (Applied
Mathe\-ma\-tics Series 55).

14.
%{\it Градштейн И.С., Рыжик И.М.} Таблицы интегралов, сумм, рядов и произведений. М.: Физматгиз, 1963. 1100~с.
Gradshteyn I. S., Ryzhik I. M. {\it  Table of integrals, series,
and products}. 7th ed.  Amsterdam, Bos\-ton, Heidelberg, London,
New York, Oxford, Paris, San Diego, San Francisco, Singapore,
Sydney, To\-kyo, Academic Press, 2007, 1171~p.


15.
%{\it Бейтмен Г., Эрдейи А.} Высшие трансцендентные функции. Т.~1. М.: Наука, 1973. 296~с.
%
Bateman H., Erdelyi A. {\it   Higher transcendental functions}. In
2~vol. New York, Toronto, London, McGraw-Hill Book Company Inc.,
1953,  vol.~1, 302~p.



\vskip1.5mm Received:  January 21, 2020.

Accepted: August 13, 2020.


\vskip6mm A~u~t~h~o~r'~s \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Nickolay V. Egorov} --- Dr. Sci. in Physics and
Mathematics, Professor; robby7@mail.ru

\vskip2mm \textit{Ekaterina M. Vinogradova} --- Dr. Sci. in
Physics and Mathematics, Professor; e.m.vinogradova@spbu.ru

}
