
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. \textit{Ryazhenov~V., Gorokhova~S.\:G., Zhordania~K.\:I.,
Payanidi~Y.\:G., Bunyatyan~N.\:D.} Clinical and statistical
analysis of ovarian cancer incidence rate and identification of a
subgroup of patients with BRCA1/2 mutations in the Russian
Federation // Journal of Pharmaceutical Sciences and Research.
2018. N~10.  P.~2500--2502.

2. \textit{Chaplain~M.\:A., Sherratt~J.\:A.} A new mathematical
model for avascular tumor growth // Journal of Mathematical
Biology. 2000. Vol.~43. N~4. P.~291–-312.

3. \textit{Kolpak~E.\:P., Abuzyarova~R.\:T., Kabrits~S.\:A.}
Leukosis mathematical model // Asian Journal of Pharmaceutics.
2018.  N~1.  P.~S340--S345.

4.  \textit{Kuznetsov~M.\:B., Kolobov~A.\:V.} Influence of
chemotherapy on progression of biclonal tu\-mor~--- Analysis by
means of mathematical modeling // Biophysics (Russian Federation).
2019. Vol.~64(2).  P.~279--292.
https://doi.org/10.1134/S0006350919020118

5.      \textit{Kolpak~E.\:P., Frantsuzova~I.\:S., Kuvshinova~K.\:
V., Senkov~ R.\:E.} Neoplasm morbidity among the population of
Russia // Intern. Journal of Advanced Biotechnology and Research.
2017. Vol.~8(3). P.~2315--2322.

6.      \textit{Мерабишвили~В.\:М.} Онкологическая статистика
(традиционные методы, новые информа\-цион\-ные технологии):
руководство для врачей / под ред. В.~М.~Мерабишвили; Министерство
здравоохранения и социального развития; НИИ онкологии им.
Н.~Н.~Петрова; Популяционный раковый регистр Санкт-Петербурга.
СПб.: Полиграф. компания КОСТА, 2015, 223~c.

7.  \textit{Kroeger~P.\:T., Drapkin~R.} Pathogenesis and
heterogeneity of ovarian cancer // Curr Opin Obstet Gynecol. 2017.
Vol.~29(1). P.~26--34.
https://doi.org/10.1097/GCO.0000000000000340

8.  \textit{Karst~A.\:M., Drapkin ~R.} Ovarian cancer
pathogenesis: a model in evolution // Molecular genetic markers in
female reproductive cancers.  2010. N~932371. P.~13.
https://doi.org/10.1155/2010/932371

9.  \textit{Urmancheeva~A. \:F.} Chemotherapy for recurrent
ovarian cancer (literature review) // Scientific and practical
reviewed journal. Siberian Journal of Oncology. 2010. Vol.~3(39).
P.~28--33.

10. \textit{ Beishembaev~A.\:M., Zhordania~K.\:I.} Clinical and
histological features of purely stromal cell ovarian tumors //
Obstetrics, Gynecology and Reproduction. 2019.  Vol.~13. Iss.~4.
P.~289--296.\\
https://doi.org/10.17749/2313-7347.2019.13.4.289-296

11. \textit{Bamberger~E. \:S., Perrett~C.\:W.} Angiogenesis in
epithelian ovarian cancer // Mol. Pathol. 2002. Vol.~55(6).
P.~348–-359. https://doi.org/10.1136/mp.55.6.348

12. \textit{Devouassoux-Shisheboran~M., Genestie~C.} Pathobiology
of ovarian carcinomas. Chinese Journal of Cancer.  2015.
Vol.~34(1). P.~50--55. https://doi.org/10.5732/cjc.014.10273

13. \textit{Limei~Wang, Xiaoyan~Liu, Hong~Wang, Shuhe~Wang}.
Correlation of the expression of vascular endothelial growth
factor and its receptors with microvessel density in ovarian
cancer // Oncology Letters.  2013. Vol.~15. P.~175--180.
https://doi.org/10.3892/ol.2013.1349

14. \textit{Gershtein~E.\:S., Kushlinsky~D.\:N., Levkina~N.\:V.,
Tereshkina~ I.\:V., Nosov~V.\:B., Lak\-tio\-nov~K.\:P.,
Adamyan~L.\:V.} Relationship between the expression of VEGF signal
components and mat\-rix metalloproteinases in ovarian tumors //
Bulletin of Experimental Biology and Medicine.  2011.  Vol.~151.
Iss.~4.  P.~449--453.
https://doi.org/10.1007/s10517-011-1353-5.22448363

15. \textit{Bogush~T.\:A., Stenina~M.\:B., Bogush~E.\:A.,
Zarkua~V.\:T., Kalyuzhny~S.\:A., Mamichev~I.\:A.,
Tyulyandina~A.\:S., Tyulyandin~S.\:A., Polotsky~B.\:E.,
Davydov~M.\:M.} The quantitative indices of ERCC1 expression in
serous ovarian cancer tissue and the efficacy of first-line
platinum-based chemotherapy // Антибиотики и хроматография. 2018.
Т.~63. Вып.~1--2. С.~24--31.

16. \textit{Хохлова~С.\:В., Черкасова~М.\:В., Орел~Н.\:Ф. Лимарева
С. В., Базаева И. А., Горбунова~В.~А.} Каким больным раком яичника
показана комбинация трабектедина с пегилированным липосомальным
доксорубицином~// Вестник Российской академии медицинских наук.
2013. Т.~68. №~11. C.~115--121.
https://doi.org/10.15690/vramn.v68i11.852\pagebreak


17. \textit{Gatti~L., Beretta~G.\:L.} Ovarian cancer:
pathogenesis, diagnosis, and treatment // In\-ter\-na\-tio\-nal
Journal of Molecular Sciences. Version 1. 2017. Vol.~6. N~84.
P.~1--12.\\ https://doi.org/10.12688/f1000research.9977.1

18. \textit{Das~P.\:M., Bast~R.\:C.} Early detection of ovarian
cancer // Biomark Med.  2008. Vol.~2(3).  P.~291--303.
https://doi.org/10.2217/17520363.2.3.291

19.\textit{Chu~E., DeVita~V.\:T.} Physicians cancer chemotherapy
drug manual. New York: Jones and Bartlett Publ., 2007. 455~p.

20. \textit{Belyaev~A.\:М., Gafton~G.\:I., Levchenko~E.\:V.,
Karachun~A.\:М., Gulyaev~A.\:V., Senchik~K.\:Yu., Bespalov~V.\:G.,
Berlev~I.\:V.,  Urmancheeva~A.\:F., Guseinov~K.\:D.,
Semiletova~Yu.\:V., Mamontov~O.\:N., Kalinin~P.\:V.,
Kireeva~G.\:S., Belyaeva~O.\:A., Alexeev~V.\:V.} ChemoPerfuSion
technologies in treatment for malignant tumors // Вопросы
онкологии. 2015.  Vol.~61. N~3.  P.~477--485.

21. \textit{Cortez~A.\:J., Tudrej~P., Kujawa~K.\;A.,
Lisowska~K.\:M.} Advances in ovarian cancer therapy // Cancer
Chemother Pharmacol.  2018. Vol.~81(1). P.~17--38.
https://doi.org/10.1007/s00280-017-3501-8

22. The State of Cancer Care Provided to the Population of Russia
in 2018. Moscow: FSBI P.~A.~Herzen Moscow Cancer Research
Institute; Branch Office of FSBI NMRRC, Ministry of Health
of\linebreak Russia. 2018. P.~236. URL: http://www.oncology.
ru/service/statistics  (дата обращения: 22.05.2020 г.).
https://nnood.ru/wp-content/uploads/2019/04/Statichticheskijj-ezhegodnik-Gercena-2018.pdf


23. \textit{Merabishvili~V.\:M., Bogdanova~E.\:M.,
Urmancheeva~A.\:F., Chepik~O.\:F., Safronnikova~N.\:R.,
Laliantsi~E.\:I.} Age-related features of morbidity, mortality and
morphological verification of ovarian carcinoma~// Вопросы
онкологии.  2010.  Т.~56(2).  С.~144--51.

24. \textit{Aksel~E.\:M., Vinogradova~N.\:N.} Statistics of
malignant neoplasms of female reproductive organs~// Gynecologic
Oncology. 2018. N~3(27). P.~64--78.

25. \textit{Kolpak~E.\:P., Frantsuzova~I.\:S., Evmenova~E.\:O.}
Oncological diseases in St. Petersburg, Russia~// Drug Invention
Today.  2019.  Vol.~11(3).  P.~510--516.

26. \textit{Siegel~R.\:L., Miller~K.\:D., Jemal~A.} Cancer
statistics 2020~// CA: A Cancer Journal Clinicians. 2020. Vol.~70.
N~1.  P.~1--30. https://doi.org/10.3322/caac.21590


%\pagebreak
\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 октября 2020~г.

Cтатья принята к~печати 23 октября 2020~г.

\vskip5%6
mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2 mm \textit{Гончарова Анастасия Борисовна} --- канд.
физ.-мат. наук, ст. преп.; a.goncharova@spbu.ru

\vskip2 mm \textit{Колпак Евгений Петрович} --- д-р физ.-мат.
наук, проф.; e.kolpak@spbu.ru

\vskip2 mm \textit{Расулова Мадина Магомедаминовна} ---
магистрант; st054684@student.spbu.ru

\vskip2 mm \textit{Абрамова Алина Валерьевна} --- врач-онколог;
alinochkamv1991@gmail.com

}
