
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Modelling and design of permanent magnet multipoles for beam transport
and focusing. II. Configuring the quad%$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it V.~M.~Amoskov$^1$, V.~N.~Vasiliev$^1$, E.~I.~Gapionok$^1$,
G.~G.~Gulbekyan$^2$, N.~S.~Edamenko$^3$, I.~A.~Iva\-nenko$^2$,
N.~Y.~Kazarinov$^2$, I.~V.~Kalagin$^2$, M.~V.~Kaparkova$^1$,
V.~P.~Kukhtin$^1$, E.~A.~Lamzin$^1$, A.~A. Makarov$^1$,
A.~N.~Nezhentzev$^1$, D.~A.~Ovsyannikov$^3$,  D.~A.~Ovsyannikov~(jr)$^4$,
N.~F.~Osi\-pov$^2$, I.~Yu. Rodin$^1$,
S.~E.~Sytchevsky$^3$, A.~A.~Firsov$^1$, N.~A.~Shatil$^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
$^1$~%
Joint Stock Company ``D.~V.~Efremov Institute of Electrophysical
Apparatus'', 3, Doroga na Metallostroy,

\noindent%
\hskip2.45mm%
St~Petersburg, 196641, Russian Federation


\noindent%
$^2$~%
Joint Institute for Nuclear Research, 6, ul. Joliot-Curie, Moscow
Region, Dubna,

\noindent%
\hskip2.45mm%
141980, Russian Federation


\noindent%
$^3$~%
St~Petersburg State University, 7--9, Universitetskaya nab., St~Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation


\noindent%
$^4$~%
St~Petersburg State University of Industrial Technologies and Design, 18, Bolshaya Morskaya ul.,

\noindent%
\hskip2.45mm%
St~Petersburg, 191186, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Amoskov~V.~M., Vasiliev~V.~N., Gapionok~E.~I., Gulbekyan~G.~G., Edamenko~N.~S., Ivanenko~I.~A., Kazarinov~N.~Y., Kalagin~I.~V., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Makarov~A.~A., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~D.~A.~(jr), Osipov~N.~F., Rodin~I.~Yu., Sytchevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Modelling and design of permanent magnet multipoles for beam transport
and focusing. II. Configuring the quad. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02 (In Russian)

\vskip3.0%2.5
mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent An optimized magnetic specification has been searched for a PM quadrupole constructed for the DC-140 cyclotron in JINR, Dubna. The field inhomogeneity should be reduced to come closer to an ideal distribution. The quad parameters should be determined with very high mechanical and magnetic precision in order to reach the specified gradient. Results of the analytic study based on a 2D model gave initial values for the PM blocks dimensions and orientations. To ensure stringent performance criteria, parametrized 2D and 3D models of the quad were built. These models were used to optimize the magnet configuration, analyze its sensitivity to various errors and derive parameter tolerances. Additional adjustment to suitable field quality is foreseen using results of a trajectory analysis and acceptance inspection.
The design parameters for the best suited magnet configuration are presented and the performance criteria are defined. However, an electromagnetic analysis of the selected configuration has revealed that the relative field error adopted previously as the optimization criterion gives low accuracy estimate. Alternative estimations are proposed utilizing the field gradient error as the basic criterion to satisfy the constraint on the field inhomogeneity.
\\[1mm]
\textit{Keywords}: permanent magnet, quadrupole, beam transport,
direct and inverse problems, simulation.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 3.0%2.0
mm

{\footnotesize

1. Amoskov~V.~M., Vasiliev~V.~N., Gapionok~E.~I., Gulbekyan~G.~G., Edamenko~N.~S., Iva\-nen\-ko~I.~A., Kazarinov~N.~Y., Kalagin~I.~V., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Maka\-rov~A.~A., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~D.~A. (jr), Osipov~N.~F., Ro\-din~I.~Yu., Sytchevsky~S.~E., Firsov~A.~A.
Osobennosti razrabotki multipolnyh elementov na osnove postoyannyh magnitov dlya sistem transportirovki zaryazhennyh chastits. I. Metodika predvaritelnogo vybora parametrov i konfiguratsii magnitov
[Modelling and design of permanent magnet multipoles for beam transport
and focusing. I. Selection of optimal design and parameters].
{\em Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2021, vol.~17, iss.~4, pp.~313--329. (In Russian)
 https://doi.org/10.21638/11701/spbu.10.2021.401

2. Mitrofanov~S., Apel~P., Bashevoy~V., Bekhterev~V., Bogomolov~S., Borisov~O.,
Franko~J., Gikal~B., Gulbekyan~G., Ivanenko~I., Kalagin~I., Kazarinov~N.,
Mironov~V., Semin~V., Skuratov~V., Tikhomirov~A.
The DC130 project: new multipurpose applied science facility for FLNR.
{\em Proceedings of 14$^{th}$ Intern. Conference on Heavy Ion Accelerator Technology}.
Lanzhou, China, 2018, pp.~122--124.\\ https://doi.org/10.18429/JACoW-HIAT2018-WEOXA01

3. Kazarinov~N., Apel~P., Bekhterev~V., Bogomolov~S., Bashevoy~V., Borisov~O., Gulbekian~G., Franko~J., Ivanenko~I., Kalagin~I., Mironov~V., Mitrofanov~S., Tikhomirov~A., Semin~V., Skuratov~V.
Conceptual design of FLNR JINR radiation facility based on DC130 cyclotron.
{\em Proceedings of 61$^{th}$~Ad\-vanced Beam Dynamics Workshop on High-Intensity and High-Brightness Hadron Beams}.
Dae\-jeon, Ko\-rea, 2018, pp.~324--328.  https://doi.org/10.18429/JACoW-HB2018-WEP2PO028

4. Batygin V.~V., Toptygin I.~N.  {\em Problems in electrodynamics}.
London, New York, Academic Press, 1964, 587~p.
(Rus. ed.: Batygin~V.~V., Toptygin~I.~N. {\em Sbornik zadach po elektrodinamike}.
Moscow, Nauka Publ., 1970, 503~p.)

5. Thome R.~J., Tarrh J.~M. {\em MHD and fusion magnets: field and force design
concepts}. New York, Wiley Publ., 1982, 249~p.
(Rus. ed.: Thome~R.~J., Tarrh~J.~M.
{\em Magnitnye sistemy MGD-generatorov i termoyadernyh ustanovok. Osnovy rascheta polej i sil}.
Moscow, Energoatomizdat Publ., 1985, 282~p.)

6. Tikhonov A.~N., Arsenin V.~Ya. {\em Solutions of ill-posed problems}.
New York, Halsted Press, 1977, 288~p.
(Rus. ed.: Tikhonov~A.~N., Arsenin~V.~Ya. {\em Metody resheniya nekorrektnyh zadach}.
Moscow, Nauka Publ., 1979, 288~p.)

7. Krasnikov G.~E., Nagornov O.~V., Starostin N.~V.
{\em Modelirovanie fizicheskih processov s ispol'zovaniem paketa Comsol Multiphysics}
[{\em Simulation of physical processes with Comsol Multiphysics software}].
Moscow, NRNU MEPhI Publ., 2012, 184~p. (In Russian)

8. Prakht V.~A., Dmitrievskiy V.~A., Sarapulov F.~N. {\em Modelirovanie teplovyh
i elektromagnitnyh processov v elektrotehnicheskih ustanovkah. Programma COMSOL}
[{\em Simulation of thermal and electromagnetic processes in electrical devices.
COMSOL software}]. Moscow, Sputnik+ Publ., 2011, 158~p. (In Russian)

9. Zatonov I.~A. {Primenenie programmnogo paketa Elcut dlya podbora parametrov
magnitnogo polya betatrona} [{Using the computer code Elcut to select field parameters
in a betatron-type particle accelerator}]. {\it Proceedings of IV Russian forum on Space
Engineering for young scientists}. Tomsk, Tomsk Polytechnic University Press, 2016, pp.~130--135. (In Russian)

10. Yilong Liu, Alex T. L. Leong, Yujiao Zhao, Linfang Xiao, Henry K. F. Mak, Anderson Chun On Tsang, Gary K. K. Lau, Gilberto K. K. Leung, Ed X. Wu.
A low-cost and shielding-free ultra-low-field brain MRI scanner. {\em Nature Communications}, 2021, vol.~12,
no.~1, Art. no.~7238.\\ https://doi.org/10.1038/s41467-021-27317-1

11. O'Reilly~T., Teeuwisse W.~M., Webb A.~G. Three-dimensional MRI in a homogenous
27~cm diameter bore Halbach array magnet. {\em Journal of Magnetic Resonance}, 2019, vol.~307, Art. no.~106578.
\\ https://doi.org/10.1016/j.jmr.2019.106578

12. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Firsov~A.~A., Gapionok~E.~I., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Y., Shatil~N.~A., Sychevsky~S.~E., Vasiliev~V.~N., Zaitzev~A.~A.
Simulation of electrodynamic suspension systems for levitating vehicles.
I. Modelling of electromagnetic behaviour of maglev vehicles with
electrodynamic suspension. {\em Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science. Control
Processes}, 2014, iss.~4, pp.~5--15.

13. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N., Gapionok~E.~I., Zaitzev~A.~A., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Yu., Sychevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Chislennoe modelirovanie elektrodinamicheskih podvesov
levitatsionnyh transportnyh sistem. II. Verifikatsiya vychislitelnyh modelej
[Simulation of electrodynamic suspension systems for levitating vehicles.
II. Validation of computational models]. {\em Vestnik of Saint Petersburg
University. Series~10. Applied Mathematics. Computer Science. Control
Processes}, 2015, iss.~2, pp.~18--32. (In Russian)

14. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N., Gapionok~E.~I., Zaitzev~A.~A., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Y., Sychevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Chislennoe modelirovanie elektrodinamicheskih podvesov levitatsionnyh transportnyh
sistem. III. EDP s nepreryvnoj putevoj strukturoj
[Simulation of electrodynamic suspension systems for levitating vehicles. III. Continuous
track systems]. {\em Vestnik of Saint Petersburg University. Series~10. Applied
Mathematics. Computer Science. Control Processes}, 2015, iss.~3, pp.~4--21.
(In Russian)

15. Amoskov~V.~M., Arslanova~D.~N., Bazarov~A.~M., Belov~A.~V., Belyakov~V.~A., Belyakova~T.~F., Vasiliev~V.~N., Gapionok~E.~I., Zaitzev~A.~A., Zenkevich~M.~Y., Kaparkova~M.~V., Kukhtin~V.~P., Lamzin~E.~A., Larionov~M.~S., Maximenkova~N.~A., Mikhailov~V.~M., Nezhentzev~A.~N., Ovsyannikov~D.~A., Ovsyannikov~A.~D., Rodin~I.~Y., Sychevsky~S.~E., Firsov~A.~A., Shatil~N.~A.
Chislennoe modelirovanie elektrodinamicheskih podvesov levitatsionnyh transportnyh
sistem. IV. EDP s diskretnoj putevoj strukturoj
[Simulation of electrodynamic suspension systems for levitating vehicles.
IV. Discrete track systems]. {\em Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer Science. Control Processes}, 2016,
iss.~3, pp.~4--17. (In Russian)

16. Amoskov~V., Arslanova~D., Baranov~G., Bazarov~A., Belyakov~V., Firsov~A., Kaparkova~M., Kavin~A., Khokhlov~M., Kukhtin~V., Kuzmenkov~V., Labusov~A., Lamzin~E., Lantzetov~A., Larionov~M., Nezhentzev~A., Ovsyannikov~D., Ovsyannikov~A., Rodin~I., Shatil~N., Sytchevsky~S., Vasiliev~V., Zapretilina~E., Zenkevich~M.
Modelling EMS maglev systems to develop control algorithms.
{\it Cybernenics and Physics}, 2018, vol.~7, no.~1, pp.~11--17.

17. Amoskov~V.~M., Belov~A.~V., Belyakov~V.~A., Gapionok~E.~I., Gribov~Y.~V., Kukhtin~V.~P., Lamzin~E.~A., Mita~Y., Ovsyannikov~A.~D., Ovsyannikov~D.~A., Patisson~L., Sytchevsky~S.~E., Za\-vad\-skiy~S.~V.
Magnetic model MMTC-2.2 of ITER tokamak complex.
{\em Vestnik of Saint Petersburg Uni\-ver\-si\-ty.
Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~3, pp.~5--21. \\https://doi.org/10.21638/11702/spbu10.2019.301

18. Arslanova~D., Firsov~A., Kukhtin~V., Lamzin~E., Larionov~M., Nezhentzev~A., Ovsyannikov~D., Rodin~I., Shatil~N., Sytchevsky~S., Vasiliev~V., Zaitsev~A.
Power-efficient low-stray field hybrid magnets for MAGLEV technology.
{\it Cybernenics and Physics}, 2021, vol.~10, no.~3, pp.~117--121.
\\https://doi.org/10.35470/2226-4116-2021-10-3-117-121


\vskip1.5mm Received:  September 01, 2022.

Accepted: September 01, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Victor M. Amoskov} --- PhD in Physics and Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Vyacheslav N. Vasiliev} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Elena I. Gapionok} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Georgy G. Gulbekian} --- georgy@jinr.ru

\vskip2mm \textit{Nikolai S. Edamenko} --- PhD in Physics and Mathematics, Associate Professor; n.edamenko@spbu.ru

\vskip2mm \textit{Ivan A. Ivanenko} --- PhD in Physics and Mathematics; ivan@jinr.ru

\vskip2mm \textit{Nikolay Y. Kazarinov} --- PhD in Physics and Mathematics; nyk@jinr.ru

\vskip2mm \textit{Igor V. Kalagin} --- PhD in Physics and Mathematics; kalagin@jinr.ru

\vskip2mm \textit{Marina V. Kaparkova} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Vladimir P. Kukhtin} --- PhD in Physics and Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Evgeny A. Lamzin} --- Dr. Sci. in Physics and Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Anatoly A. Makarov} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Andrey N. Nezhentzev} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Dmitrij A. Ovsyannikov} --- Dr. Sci. in Physics and Mathematics, Professor; d.a.ovsyannikov@spbu.ru

\vskip2mm \textit{Dmitry A. Ovsyannikov} (\textit{jr}) --- d-ovs@yandex.ru

\vskip2mm \textit{Nikolai F. Osipov} --- onik@jinr.ru

\vskip2mm \textit{Igor Y. Rodin} --- PhD in Engineering; rodin@sintez.niiefa.spb.su

\vskip2mm \textit{Sergey E. Sytchevsky} --- Dr. Sci. in Physics and Mathematics; sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Alexey A. Firsov} --- sytch@sintez.niiefa.spb.su

\vskip2mm \textit{Nikolay A. Shatil} --- PhD in Engineering; sytch@sintez.niiefa.spb.su \par
%
%
}
