
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Cooperative game theory methods for text ranking%$^{*}$
}

}

\vskip 3%
mm

{\small

\noindent{\it V. V. Mazalov$^{1,2}$, V. A. Khitraya$^{1,2}$, A. V. Khitryi$^{1}^%
%, I.~ќ. Famylia%$\,^2$%

 }

\vskip 3%
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent\indent~$^{*}$ This work was  supported by the%
%Russian Foundation for Basic Research (grant N 19-01-00146-a).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize



\noindent%
$^1$~%
Federal Research Center ``Karelian Research Center 

\noindent%
\hskip2.45mm%
of the Russian Academy of SciencesТТ, 11, Pushkinskaya ul., Petrozavodsk,

\noindent%
\hskip2.45mm%
185910, Russian Federation



\noindent%
$^2$~%
Petrozavodsk State University, 33, ul. Lenina, Petrozavodsk, 

\noindent%
\hskip2.45mm%
185910, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2,5%3%
mm


\noindent \textbf{For citation:}  Mazalov V. V., Khitraya V. A., Khitryi A. V. Cooperative game theory methods for text ranking. {\it Vest\-nik of Saint Petersburg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum,~pp.~\pageref{p5}--\pageref{p5e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05 (In Russian)

\vskip3mm

%\pagebreak

\begin{hyphenrules}{english}

{\leftskip=7mm\noindent A method of ranking the corpus of texts of a news portal, based on measures of graph centrality, is proposed. Each text is assigned a vertex of a certain graph, and its structure is determined based on the semantic connectivity of the texts. As a measure of centrality, the Myerson value is used in a cooperative game on a graph, where the number of simple paths in a subgraph of a certain length m is chosen as a characteristic function For different values of {\it m}, the ranking based on the Myerson value will be different. For the final ranking, it is proposed to use the ranking procedure based on the tournament matrix. The operation of the ranking algorithm is illustrated by numerical examples related to a specific news porta.
\\[1mm]
\textit{Keywords}: text corpus of news, graph, centrality measure, Myerson value, tournament matrix, ranking procedure.\par}

\end{hyphenrules}

\vskip4.5%6
mm
%\pagebreak

\noindent \textbf{References} }

\vskip 2.5%3
mm

{\footnotesize

1. Silva A., Lozkins A., Bertoldi L.~R., Rigo S., Bure V.~M. Semantic textual similarity on Brazilian Portuguese: An approach based on language-mixture models. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~2, pp.~235--244.\\ https://doi.org/10.21638/11701/spbu10.2019.207 (In Russian)

2. Jones K. S. A statistical interpretation of term specificity and its application in retrieval. \emph{J. Documentation}, 2004, vol.~60, no.~5, pp.~493--502. https://doi.org/10.1108/00220410410560573

3. Page L., Brin S., Motwani R., Winograd T. The pagerank citation ranking: Bringing order to the Web. \emph{Proceedings of the 7$^{th}$ International World Wide Web Conference}. Brisbane, Australia, 1998, pp.~161--172. Available at: citeseer.nj.nec.com/page98pagerank.html (accessed: July 15, 2021).

4. Freeman L. C. A set of measures of centrality based on betweenness. \emph{Sociometry}, 1977, vol.~40, no.~1, pp.~35--41. http://dx.doi.org/10.2307/3033543

5. Brandes U. Centrality measures based on current flow. \emph{STACS 2005. 22$^{nd}$ Annual Symposium on Theoretical Aspects of Computer Science}. Stuttgart, Germany, February 24--26, 2005. Proceedings, Eds. by V.~Diekert, B.~Durand, vol. 3404 of Lecture Notes in Computer Science. Stuttgart, Springer Publ., 2005, pp.~533--544. https://doi.org/10.1007/978-3-540-31856-9\_44

6. Avrachenkov K., Litvak N., Medyanikov  V., Sokol M. Alpha current flow betweenness centrality. \emph{Algorithms and Models for the Web Graph. 10$^{th}$~International Workshop (WAW 2013)}. Cambridge, MA, USA, December 14--15, 2013. Proceedings. Eds. by A. Bonato, M. Mitzenmacher, P. Pralat, vol.~8305 of Lecture Notes in Computer Science. Cambridge, Springer Publ., 2013, pp.~106--117. \\ https://doi.org/10.1007/978-3-319-03536-9\_9

7. Avrachenkov K.~E., Mazalov V.~V., Tsynguev B.~T. Beta current flow centrality for weighted networks. \emph{Computational Social Networks. 4$^{th}$ International Conference (CSoNet 2015)}. Beijing, China, August 4--6, 2015. Proceedings, Lecture Notes in Computer Science, no.~9197, 2015, pp.~216Ц227. https://doi.org/10.1007/978-3-319-21786-4\_19

8. Newman M. E. J. A measure of betweenness centrality based on random walks. \emph{Social Networks}, 2005, vol.~27, pp.~39--54. http://dx.doi.org/10.1016/j.socnet.2004.11.009

9. Jackson M. O. \emph{Social and economic networks}. Princeton, USA, Princeton University Press, 2008, 504 p. https://doi.org/10.1515/9781400833993

10. G\Т{o}mez D., Gonz\Т{a}lez-Arang\Ф{u}ena E., Manuel C. et al. Centrality and power in social networks: a game theoretic approach. \emph{Math. Soc. Sci.}, 2003, vol.~46, no.~1, pp.~27--54. \\
https://doi.org/10.1016/S0165-4896(03)00028-3

11. Skibski O., Tomasz P., Talal R. Axiomatic characterization of game theoretic centrality. \emph{J. Artif. Intell. Res.}, 2018, vol.~62, p.~33--68. https://doi.org/10.1613/jair.1.11202

12. Mazalov V.~V., Trukhina L.~I. Generating functions and the Myerson vector in communication networks. \emph{Diskr. Mat.}, 2014, vol.~26, no.~3, pp.~65--75. https://doi.org/10.1515/dma-2014-0026

13. Avrachenkov K., Kondratev A.~Yu., Mazalov V.~V., Rubanov D.~G. Network partitioning as cooperative games. \emph{Computational social networks}, 2018, vol.~5, no.~11, pp.~1--28.

14. Mazalov V.~V., Khitraya V.~A. Modificirovannoe znachenie Maiersona dlya opredeleniya centralnosti vershin grafa [Modified Mayerson value for determining the centrality of graph vertices]. \emph{Matematicheskaia teoriia igr i ee prilozheniia} [\emph{Mathematical theory players and its supplements}], 2019, vol.~11, no.~2, pp.~19--39. (In Russian)

15. Mazalov V.~V., Nikitina N.~N. Metod maksimalnogo pravdopodobia dlya vydelenya soobshestv v commukacionnih setyah [Maximum likelihood method for detecting communities in communication networks]. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2018, vol.~14, no.~3, pp.~200--214. https://doi.org/10.21638/11701/spbu10.2018.302 (In Russian)

16. Korobov M. Morphological analyzer and generator for Russian and Ukrainian languages. \emph{Analysis of Images, Social Networks and Texts.} Eds. by M. Yu. Khachay, N. Konstantinova, A. Panchenko et al. Cham, Springer International Publ., 2015, vol.~542 of Communications in Computer and Information Science, pp.~320--332. http://dx.doi.org/10.1007/978-3-319-26123-231

17. Lovins J. B. Development of a stemming algorithm. \emph{Mech. Transl. Comput. Linguistics}, 1968, vol.~11, no.~12, pp.~22--31. Available at: http://www.mtarchive.info/MT1968-Lovins.pdf (accessed: July 15, 2021).

18. Van Rijsbergen C.~J., Robertson S.~E., Porter M. F. New models in probabilistic information retrieval. \emph{Computer Laboratory}. Cambridge, USA, Cambridge University Press, 1980, 613~p.

19. Harris Z. Distributional structure. \emph{Word}, 1954, vol.~10, no.~2-3, pp.~146--162.\\
Available at:  https://link.springer.com/chapter/10.1007/978-94-009-8467-71 (accessed: July 15, 2021).

20. Manning C. D., Raghavan P., Sch\Ф{u}tze H. \emph{Introduction to information retrieval.} Cambridge, USA, Cambridge University Press, 2008, 535~p.

21. Kondratev A.~A., Mazalov V.~V. Ranking procedure with the shapley value. \emph{Intelligent Information and Database Systems. 9$^{th}$ Asian Conference (ACIIDS 2017)}. Kanazawa, Japan, April 3--5, 2017. Proceedings, P. II / Eds. by N.~T.~Nguyen, S.~Tojo, L.~M.~Nguyen, B.~Trawinski, 2017, vol.~10192 of Lecture Notes in Computer Science, pp.~691--700. https://doi.org/10.1007/978-3-319-54430-4\_66


\vskip1.5mm Received:  August 21, 2021.

Accepted: February 01, 2022.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \,\ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Vladimir V. Mazalov} --- Dr. Sci. in Physics and Mathematics, Professor; vmazalov@krc.karelia.ru \par

\vskip2mm \textit{Vitalia A. Khitraya} --- Postgraduate Student, Senior Lecturer; dobvitalia@yandex.ru \par


\vskip2mm \textit{Andrei V. Khitryi} --- Postgraduate Student; andrey.khitryy@gmail.com \par
%
%
}
