


{\footnotesize

\vskip 3mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 2mm


1. {\it Prikaz Minzdravsotsrazvitiya Rossii ot 28 aprelya 2011 g.
no.~364 ``Ob utverzhdenii kontseptsii sozdaniya edinoy
gosudarstvennoy informatsionnoy sistemyi v sfere
zdravoohraneniya''} [{\it Order of the Health Ministry of Russia
dated April 28, 2011 no.~364 ``On approval of the concept of
creating a single state information system in the health
sector''}\,]. Available at: http://www.rosminzdrav.ru/documents/
7200-prikaz-minzdravsotsrazvitiya-rossii-364-ot-28-aprelya-2011-g
(accessed: 12.01.2016). (In Russian)


2. {\it Svidetelstvo o gosudarstvennoy registratsii programmy dlya
EVM no.~2014615574 ot 28 maya 2014 g.} [{\it Certificate of state
registration of the computer program no.~2014615574 on May 28,
2014}]. Available at:
http://www1.fips.ru/Archive/EVM/2014/2014.06.20/Index.htm
(accessed: 12.01.2016). (In Russian)

3.   Aoki N.,  Johnson-Throop K. A.,  Turley J. P. Outcomes and
methods in telemedicine evaluation. {\it Telemed. J. E. Health},
2003. vol.~9,  no.~4,   pp.~393--401.

4.  Vladzimirskiy A. V. Metodyi issledovaniya effektivnosti
telemeditsiny [Methods of study of the effectiveness of
telemedicine]. {\it Ukr. zhurn. telemed. med. telemat.}, 2005,
vol.~3, no.~1, p.~104. (In Russian)


5.  Vladzimirskiy A. V., Chelnokov A. N. Relevantnost
telemeditsinskoy konsultatsii [Relevance of telemedicine
consultation]. {\it Ukr. zhurn. telemed. med. telemat.}, 2006,
vol.~4, no.~1, p.~99--100. (In Russian)


6.  Vladzimirskiy A. V. {\it Otsenka effektivnosti telemeditsinyi}
[{\it Evaluation of the effectiveness of telemedicine}]. Donetsk,
OOO ``Tsifrovaya tipografiya'', 2007, 63~p. (In Russian)


7.  Kamaev I. A., Levanov V. M., Sergeev D. V. {\it Telemeditsina:
klinicheskie, organizatsionnyie, pravovyie, tehnologicheskie,
ekonomicheskie aspekty} [{\it Telemedicine: clinical,
organizational, legal, technological and economic aspects}].
Nizhniy Novgorod, Nizhniy Novgorod med. academy Publ., 2001,
100~p. (In Russian)


8.  Reshetnik D. A., Barbinov V. V., Litvinova E. V. {\it
Telemeditsina v dermatologii} [{\it Telemedicine in dermatology}].
Tuapse, OAO ``Tuapsinskaya tipografiya'', 2005, 160~p. (In
Russian)




}
