

{\footnotesize

\vskip 2mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 1.5mm




1. Siginer D. A., De Kee D., Chhabra R. P. {\it Advances in the
Flow and Reology of Non-Newtonian Fluids}. Intown, Elsevier Publ.,
1999, 1515~p.


2. Gijsen F. J. H., Allanic E., Van De Vosse F. N., Janssen J. D.
The influence of the non-Newtonian properties of blood on the flow
in large arteries: unsteady flow in a 900 curved tube. {\it
Journal of Biomechanics}, 1999, vol.~32, pp.~705--13.


3. Chen J., Lu X.-Y. Numerical investigation of the non-Newtonian
blood flow in a bifurcation model with non-planar branch. {\it
Journal of  Biomechanics},  2004, vol.~37, no.~12, pp.~1899--1911.


4. Hoogstraten H. W., Kootstra J. G., Hillen B., Krijger J. K. B.,
Wensing P. J. W. Numerical simulation of blood flow in an artery
with two successive bends. {\it Journal of  Biomechanics}, 1996,
vol.~29, no.~8, pp.~1075--1083.


5. Papaharilaou Y., Doorly D. J., Sherwin S. J. The influence of
out-in-plane geometry on pulsatile flow within a distal
end-to-side anastomosis. {\it Journal of  Biomechanics},  2002,
vol.~35, no.~9, pp.~1225--1239.


6. Quarteroni A., Tuveri M., Veneziani A. Computational vascular
fluid dynamics: problems, models and methods. {\it Computing and
Visualization in Science}, 2000, vol.~2, pp.~163--197.


7. Ratkina S. V., Tregubov V. P. Mathematical simulation of a
blood stream in large arteries. {\it Intern. Conf. of the Polish
Society of Biomechanics}. Book of abstr., 2010, pp. 187--188.


8. Migliavacca F., Yates R., Pennati G., Dubini G., Fumero R., De
Leval M. R. Calculating blood flow from Doppler measurements in
the systemic-to-pulmonary artery shunt after the Norwood
operation: a method based on CFD.  {\it Ultrasound in Medicine and
Biology}, 2000, vol.~26, no.~2, pp. 209--219.


9. Tregubov V. P., Radichkina A. O. Matematicheskoe modelirovanie
kinematiki levogo zheludochka serdtsa cheloveka v~protsesse ego
sokraschenia  [Mathematical modelling of the left ventricle
cinematic during a contraction]. {\it Vestnik of Saint Petersburg
University. Series~10. Applied mathematics. Computer science.
Control processes}, 2013, issue~4, pp.~67--73. (In Russian)





\vskip 2mm

{\bf For citation:} Tregubov V.~P.,~Mukhtarova D.~H. A model study
of blood flow in branching vessels. {\it Vestnik of Saint
Petersburg University. Applied mathematics. Computer science.
Control pro-\linebreak cesses}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/spbu10.\issueyear.\issuenum04



}
