

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1. Anggai S., Blekanov I. S., Sergeev S. L. Management and
information processing at virtual museum. \emph{IEEE 4th Intern.
ñonference on System Engineering and Technology $($ICSET$)$}.
Bandung, Indonesia, 2014, pp.~1--5.

2. Hassaan M. A., Burtscher M., Pingali K. Breadth first search on
cost-efficient Multi-GPU systems. \emph{2010 19th Intern.
conference on Parallel Architectures and Compilation Techniques
$($PACT$)$}. Vienna, 2010, pp.~539--540.

3. Stanescu L., Brezovan M., Burdescu D. D. Automatic mapping of
MySQL databases to NoSQL MongoDB. \emph{2016 Federated Conference
on Computer Science and Information Systems $($FedCSIS$)$}.
Gdansk, Poland, 2016, pp.~837--840.

4. Jia T., Zhao X., Wang Z., Gong D., Ding G. Model transformation
and data migration from Relational Database to MongoDB. \emph{2016
IEEE Intern. Congress on Big Data $($BigData Congress$)$}. San
Francisco, CA, USA, 2016, pp.~60--67.

5. Wu Q., Chen C., Jiang Y. Multi-source heterogeneous Hakka
culture heritage data management based on MongoDB. \emph{2016
Fifth Intern. conference on Agro Geoinformatics}. Tianjin, 2016,
pp.~1--6.

6. Anggai S., Blekanov I. S., Sergeev S. L. Design Muntoi
web-based framework and search engine analytics for thematic
virtual museums. \emph{4th Intern. conference on Interactive
Digital Media $($ICIDM$)$}. Bandung, Indonesia, 2015, pp.~1--5.

7. Brin S., Page L. The anatomy of a large-scale hypertextual Web
search engine. \emph{Proceedings of the Seventh Intern. conference
on World Wide Web 7 $($WWW7$)$}. Amsterdam, The Netherlands, 1998,
pp.~107--117.

8. Zobel J., Moffat A. Inverted files for text search engines.
\emph{Journal ACM Computing Surveys $($CSUR$)$}, 2006, vol.~38,
no. 2, article 6, pp.~1--56.

9. Manning C. D., Raghavan P., Schutze H. \emph{Introduction to
Information Retrieval}. New York, USA, Cambridge University Press,
2008, pp.~61--123.

10. Panev K., Berberich K. Phrase queries with inverted + direct
indexes. \emph{Intern. conference on Web Information Systems
Engineering}. Thessaloniki, Greece, 2014, pp.~156--169.

11. Anggai S., Blekanov I. S., Sergeev S. L. Construction inverted
index for dynamic collections visualization in thematic virtual
museums system. \emph{2017 3rd Intern. conference on Science and
Technology~--- Computer $($ICST$)$}. Jogjakarta, 2017,
pp.~186--189.

12. Salton G., Buckley C. \emph{Term Weighting approaches in
automatic text retrieval}. Cornell, Cornell University Press,
Department of Computer Science, 1987, pp.~323--327.

13. Deerwester S., Dumais S. T., Furnas G. W., Landauer T. K.,
Harshman R. Indexing by latent semantic analysis. \emph{Journal of
the American Society for Information Science}, 1990, vol.~41,
pp.~391--407.

14. Blei D. M., Ng A. Y., Jordan M. I. Latent dirichlet
allocation. \emph{The Journal of Machine Learning Research}, 2003,
vol.~3, no.~2, pp.~993--1022.

15. Singleton A. The economics of microservices. \emph{IEEE Cloud
Computing}, 2016, vol.~3, no.~5,\linebreak pp.~16--20.

16. Guo D., Wang W., Zeng G., Wei Z. Microservices architecture
based Cloudware Deployment Platform for service computing.
\emph{2016 IEEE Symposium on Service-Oriented System Engineering
$($SOSE$)$}. Oxford, UK, 2016, pp.~358--363.

17. Bakshi K. Microservices-based software architecture and
approaches. \emph{2017 IEEE Aerospace Conference}. Big Sky, MT,
USA, 2017, pp.~1--8.


\vskip 2mm

{\bf For citation:} Anggai S., Blekanov I. S., Sergeev S. L. Index
data structure, functionality and microservices in thematic
virtual museums. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes},
\issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p4}--\pageref{p4e}. \doivyp/
spbu10.\issueyear.\issuenum04


}
