
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. Novel Coronavirus Global Research and Innovation Forum: Towards
a Research Roadmap~// WHO. URL:
www.who.int/emergencies/diseases/novel-coronavirus-2019/global-research-on-novel-corona\linebreak
virus-2019-ncov (дата обращения: 15 июня 2020~г.).

2. {\it Layne S.\,P., Hyman J.\,M., Morens D.\,M., Taubenberger
J.\,K.} New coronavirus outbreak: Framing questions for pandemic
prevention~// Sci. Transl. Med. 2020. Vol.~12. Iss.~534.
N~eabb1469. \\
https://doi.org/10.1126/scitranslmed.abb1469\pagebreak

3. {\it Wu J.\,T., Leung K., Leung G.\,M.} Nowcasting and
forecasting the potential domestic and international spread of the
2019-nCoV outbreak originating in Wuhan, China: a modelling study
// Lancet. 2020. Vol.~395. Iss.~10225. P.~689--697. https://doi.org/10.1016/S0140-6736(20)30260-9

4. Models of Infectious Disease Agent Study~// MIDAS Coordination
Center.\\ URL: www.midasnetwork.us/ (дата обращения: 15 июня
2020~г.).

5. {\it Mandal M., Jana S., Nandi S.\,K., Khatua A., Adak S., Kar
T.\,K.} A model based study on the dynamics of COVID-19:
Prediction and Control~// Chaos, Solitons and Fractals. 2020.
Vol.~136. N~109889. https://doi.org/10.1016/j.chaos.2020.109889

6. {\it Fanelli D., Piazza F.} Analysis and forecast of COVID-19
spreading in China, Italy and France~// Chaos, Solitons and
Fractals. 2020. Vol.~134. N~109761.
https://doi.org/10.1016/j.chaos.2020.109761

7. {\it Bekirosab S., Kouloumpou D.} SBDiEM: A new mathematical
model of infectious disease dynamics~// Chaos, Solitons and
Fractals. 2020. Vol.~136. N~109828.\\
https://doi.org/10.1016/j.chaos.2020.109828

8. {\it Barmparis G.\,D., Tsironis G.\,P.} Estimating the
infection horizon of COVID-19 in eight countries with a
data-driven approach~// Chaos, Solitons and Fractals. 2020.
Vol.~135. N~109842.\\ https://doi.org/10.1016/j.chaos.2020.109842

9. {\it Kondratyev M.\,A.} Forecasting methods and models of
disease spread~// Computer Research and Modeling. 2013. Vol.~5.
Iss.~5. P.~863--882.

10. {\it Schmidt R., Waligora T.} Influenza forecast: Case-Based
Reasoning or statistics?~// Proceedings of the 11th International
conference on knowledge-based intelligent information and
engineering systems. Pt~I. Series Lecture Notes in Computer
Science. 2007. Vol.~4692. P.~287--294.

11. {\it Viboud C., Boelle P.\,Y., Carrat F., Valleron A.\,J.,
Flahault A.} Prediction of the spread of influenza epidemics by
the method of analogues~// American Journal of Epidemiology. 2003.
Vol.~158. Iss.~10. P.~996--1006.

12. Johns Hopkins Coronavirus Resource Center. URL:
https://coronavirus.jhu.edu/data (дата обращения: 29 июня
2020~г.).


\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 24 июля 2020~г.

Cтатья принята к~печати 13 августа 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm

\vskip1.5mm\textit{Захаров Виктор Васильевич}~---  д-р физ.-мат.
наук, проф.; v.zaharov@spbu.ru

\vskip1.5mm\textit{Балыкина Юлия Ефимовна}~---  канд. физ.-мат.
наук, доц.; j.balykina@spbu.ru

}
