
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Липский~В.} Комбинаторика для программистов / пер.
с~польск. В.~А.~Евстигнеева, О.~А.~Логиновой; под ред.
А.~П.~Ершова. М.: Мир, 1988. 213~с.

%\bibitem{AMK_Graph}
2. {\it Kovshov~A.\,M.} The creating of shared search algorithms
on the example of graph path searching // Modern science. 2018.
N~12-1. P.~48--51.

%\bibitem{SetPart}
3. {\it Djoci\'c~B., Miyakawa~M., Sekiguchi~S., Semba~I.,
Stojmenovi\'c~I.} A fast iterative algorithm for generating set
partitions
// The Computer Journal. 1989. Vol.~32. N~3. P.~281--282.

%\bibitem{ParallSetPart}
4. {\it Djoki\'c~B., Miyakawa~M., Sekiguchi~S., Semba~I.,
Stojmenovi\'c~I.}  Parallel algorithms for generating subsets and
set partitions // International Symposium on Algorithms. SIGAL.
1990. P.~76--85.

%\bibitem{ParallPart}
5. {\it Chen~G.\,H., Chern M.\,S.} Parallel generation of
permutations and combinations // BIT Numerical Mathematics. 1986.
Vol.~26. P.~277--283.

%\bibitem{Kokosinski}
6. {\it Kokosi\'nski~Z.} On generation of permutations through
decomposition of symmetric groups into cosets //
 BIT Numerical Mathematics. 1990. Vol.~30. P.~583--591.

%\bibitem{BoraUcar}
7. {\it U\c{c}ar~B.} Partitioning, matching, and ordering:
Combinatorial scientific computing with matrices and tensors.
Computer Science. Lyon: ENS de Lyon, 2019. 191~p.

%\bibitem{Deveci}
8. {\it Deveci~M., Kaya~K., U\c{c}ar~B.,
\c{C}ataly\"urek~\"U.\,V.} Hypergraph partitioning for multiple
communication cost metrics: Model and methods // Journal of
Parallel and Distributed Computing. 2015. Vol.~77. N~3. P.~69--83.

%\bibitem{JiangFengZhu}
9. {\it Jiang~H., Feng~H., Zhu~D.} An 5/4-approximation algorithm
for sorting permutations by short block moves // Proceedings of
the 25th International Symposium on Algorithms and Computation.
2014. P.~491--503.

%\bibitem{Brasil}
10. {\it Alexandrino~A., Miranda~G., Lintzmayer~C., Dias~Z.}
Approximation algorithms for sorting permutations by
length-weighted short rearrangements // Electronic Notes in
Theoretical Computer Science. 2019. Vol.~346. P.~29--40.

%\bibitem{GalvLeeDias}
11. {\it Galv\~ao~G.\,R., Lee~O., Dias~Z.} Sorting signed
permutations by short operations // Algorithms for Molecular
Biology. 2015. N~10. P.~1--17.

%\bibitem{CresPerezTod}
12. {\it Crespelle~C., Perez~A., Todinca~I.} An
%O($\text{n}^{\!{\scriptscriptstyle2\!}}$)
O($n^2$) time algorithm for the minimal permutation completion
problem // Discrete Applied Mathematics. 2019. Vol.~254.
P.~80--95.

%\bibitem{Albert}
13. {\it Albert~M.\,H., Lackner~M.-L., Lackner~M., Vatter~V.} The
complexity of pattern matching for 321-avoiding and skew-merged
permutations // Discrete Mathematics \& Theoretical Computer
Science. 2016. Vol.~18. N~2. P.~1--17.

%\bibitem{Lackner}
14. {\it Lackner~M.-L., Lackner~M.} A fast algorithm for
permutation pattern matching based on alternating runs //
Algorithmica. 2016. Vol.~75. N~1. P.~84--117.

%\bibitem{Molloy}
15. {\it Esta\~na~A., Molloy~K., Vaisset~M., Sibille~N.,
Sim\'eon~T., Bernad\'o~P., Juan Cort\'es~J.} Hybrid
parallelization of a multi-tree path search algorithm: Application
to highly-flexible biomolecules // Parallel Computing. 2018.
Vol.~77. P.~84--100.

%\bibitem{Olivera}
16. {\it Oliveira~A., Fertin~G., Dias~U., Dias~Z.} Sorting signed
circular permutations by super short operations // Algorithms for
Molecular Biology. 2018. Vol.~13. N~12. P.~13--18.

%\bibitem{GergelStrongin}
17. {\it Гергель~В.\,П., Стронгин~Р.\,Г.} Основы параллельных
вычислений для многопроцессорных вычислительных систем. Н.
Новгород: Изд-во ННГУ им.~Н.\,И.~Лобачевского, 2003. 184~с.

%\bibitem{Voevodin02}
18. {\it Воеводин~В.\,В., Воеводин~Вл.\,В.} Параллельные
вычисления. СПб.: БХВ-Петербург, 2002. 608~с.

%\bibitem{Stenly}
19. {\it Стенли~Р.} Перечислительная комбинаторика / пер. с~англ.
А.~И.~Барвинка, А.~А.~Лодкина; под ред.  А.~М.~Вершика. М.: Мир,
1990. 440~с.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 2 февраля 2020~г.

Cтатья принята к~печати 13 февраля 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Ковшов Александр Михайлович} --- канд. физ.-мат.
наук, доц.; a.kovshov@spbu.ru

}
