{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1.   Kurbatova~G.~I.,  Popova~E.~A.,  Filippov~B.~V. et al.
\textit{Modeli morskich gasoprovodov} [\textit{Models of sea
gas-pipelines}]. Saint Petersburg, Saint Petersburg State
University Publ.,  2005, 156~p. (In Russian)


2.  Ermolaeva N.~N., Kurbatova G.~I. Qwasiodnomernaja
nestacionarnaja model processov v morskih gasoprovodah
[Quasione-dimensional non-stationary model of processes in a sea
gas-pipeline]. \textit{Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, 2015, issue~3, pp.~55--66.    (In Russian)

3. Ermolaeva N.~N., Kurbatova G.~I. Analiz podhodov k
modelirovaniju termodinamicheskih proces-\linebreak sov v gasah
pri visokih davlenijah  [The analysis of the approaches to the
modeling of thermodynamic pro-\linebreak cesses in gas flow at
hyperpressure]. \textit{Vestnik of Saint Petersburg University.
Series 10. Applied mathe-\linebreak matics. Computer science.
Control processes}, 2013, issue~1, pp.~35--45. (In Russian)


4.  Reid R. C., Prausnitz J. M., Sherwood Th. K. \textit{The
properties of gases and liquids}.  New  York, Saint Louis, San
Francisco, MeGraw
--- Hill  Book  Company Publ., 1977, 592~p. (Russ. ed.: Reid Robert
C., Prausnitz John M., Sherwood Thomas K. \textit{Svoistva gazov i
zshidkostej}. Leningrad, Chemistry Publ., Leningr. otd., 1982,
592~p.)


\vskip 2mm

{\bf For citation:} Ermolaeva N.~N. Investigation of the influence
of gas transmission parameters on flow characteristics. {\it
Vestnik of Saint Petersburg University. Series~10. Applied
mathematics. Computer science. Control processes}, \issueyear,
issue~\issuenum, pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
