

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm

1. {Bryksin~V.~M., Evtiushkin~A.~V., Khvorova~L.~A.} Razrabotka
programmnogo kompleksa otsenki urozhainosti zernovykh kul'tur s
ispol'zovaniem matematicheskogo modelirovaniia i dannykh
distantsionnogo zondirovaniia Zemli [Development of a software
system for assessing crop yields using mathematical modeling and
remote sensing data from the Earth]. {\it Proceeding of Russian
Conference ``Mathematical models and information technologies in
agricultural biology: results and prospects''. October 14--15,
2010}. Saint Petersburg, ARI Press, 2010, pp.~76--80. (In Russian)

2. {Kleshchenko~A.~D., Naidina~T.~A.} Ispol'zovanie dannykh
distantsionnogo zondirovaniia dlia modelirovaniia
fiziologicheskikh protsessov rastenii v dinamicheskikh modeliakh
prognozirovaniia urozhaia [The use of remote sensing data to model
the physiological processes of plants in dynamic crop forecasting
models]. {\it Sovremennyie problemy distantsionnogo zondirovaniia
Zemli iz kosmosa  $[$Modern problems of remote sensing of the
Earth from space$]$}, 2011, vol.~8, no.~1, pp.~170--178. (In
Russian)

3. {Shutiaev~V.~P.} {\it Operatory upravleniia i iteratsionnye
algoritmy v zadachakh variatsionnogo usvoeniia dannykh} [{\it
Operators of control and iterative algorithms in problems of
variational data assimilation}]. Moscow, Nauka Publ., 2001, 240~p.
(In Russian)

4. {Kalnay~E.} {\it Atmospheric Modeling, Data Assimilation and
Predictability}. Cambridge, Cambridge University Press, 2003,
341~p.

5. {Olioso~A., Inoue~Y., Ortega-Farias S., Brisson~N.} Future
directions for advanced evapotrans-piration modeling: Assimilation
of remote sensing data into crop simulation models and SVAT
models. {\it Irrigation and Drainage Systems}, 2005, vol.~19,
pp.~377--412.

6. {Tikhonov~A.~N., Arsenin~V.~Ia.} {\it Metody resheniia
nekorrektnykh zadach} [{\it Methods for solving ill-posed
problems}]. Moscow, Nauka Publ., 1974, 223~p. (In Russian)

7. {Medvedev~S., Topaj~A.} Crop simulation model registrator and
polyvariant analysis. {\it IFIP Advances in Information and
Communication Technology $($AICT$)$}, 2011, vol.~359,
pp.~295--301.







\vskip 3mm

{\bf For citation:}   Topaj A.~G.,~Mitrofanov E.~P. Assimilation
of data in the imitative modeling of environmental processes by
the method of minimizing corrective perturbations. {\it Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p9}--\pageref{p9e}.
\doivyp/spbu10.\issueyear.\issuenum09


}
