

{\footnotesize

\vskip 5mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 3mm



1. Haurie A. A note on nonzero-sum differential games with
bargaining solutions. \emph{Journal of Optimization Theory and
Applications}, 1976, vol.~18, issue~1, pp.~31--39.

2. Petrosyan L. A. Ustojchivost' reshenij differencial'nyh igr so
mnogimi uchastnikami [Time-consistency of solutions in
multi-player differential games]. \emph{Vestnik of Leningrad State
University. Series~1. Mathematics. Mechanics. Astronomy}, 1977,
issue~4, pp.~46--52. (In Russian).

3. Petrosyan L. A. Sil'no dinamicheski ustojchivye
differencial'nye principy optimal'nosti [Strongly time-consistent
differential optimality principles]. \emph{Vestnik of Leningrad
State University. Series~1. Ma-\linebreak thematics. Mechanics.
Astronomy}, 1993, issue~4, pp.~40--46. (In Russian).

4. Petrosyan L. A., Danilov N. N. Ustojchivost' reshenij
neantagonisticheskih differencial'nyh igr s~transferabel'nymi
vyigryshami [Stability of solutions in non-zero sum differential
games with transferable payoffs]. \emph{Vestnik of Leningrad State
University. Series~1. Mathematics. Mechanics. Astronomy}, 1979,
issue~1, pp.~52--59. (In Russian).

5. Petrosian O. L. Looking forward approach in cooperative
differential games. \emph{Intern. Game Theory Review}, 2016,
vol.~18, issue~2, pp.~1--14. DOI: 10.1142/S0219198916400077.

6. Petrosian O. L., Barabanov A. E. Looking forward approach in
cooperative differential games with uncertain-stochastic dynamics.
\emph{Journal of Optimization Theory and Applications}, 2016,
pp.~1--20. DOI: 10.1007/s10957-016-1009-8.

7. Bellman R. \emph{Dynamic programming}. Princeton, Princeton
University Press, 1957, 550~p.

8. Gromova E. V., Petrosian O. L. Control of informational horizon
for cooperative differential game of pollution control.
\emph{Intern. conference stability and oscillations of nonlinear
control systems $($Pyatnitskiy's conference$)$}, 2016. DOI:
10.1109/STAB.2016.7541187.

9. Petrosyan L. A., Zaccour G. Time-consistent Shapley value
allocation of pollution cost reduction. \emph{J. econ. dyn.
control}, 2003, vol.~27, issue~3, pp.~381--398.

10. Petrosyan L. A., Yeung D. W. K. Dynamically stable solutions
in randomly-furcating differential games. \emph{Trans. Steklov
inst. math.}, 2006, vol.~253, issue~1, pp.~208--220.

11. Jorgensen S., Martin-Herran G., Zaccour G. Agreeability and
time consistency in linear-state differential games. \emph{Journal
of Optimization Theory and Applications}, 2003, vol.~119, issue~1,
pp.~49--63.

12. Petrosjan L. A. Strongly time-consistent differential
optimality principles. \emph{Vestnik of Saint Petersburg
University. Series~1. Mathematics. Mechanics. Astronomy}, 1993,
issue~4, pp.~40--46.  (In Russian).

13. Yeung D. W. K., Petrosyan L. A. \emph{Subgame-consistent
economic optimization}. New York, Springer Press, 2012, 395~p.

14. Basar T., Olsder G. J. \emph{Dynamic noncooperative game
theory}. London, Academic Press, 1995, 535~p.

15. Jorgensen S., Yeung D. W. K. Inter- and intergenerational
renewable resource extraction. \emph{Annals of Operations
Research}, 1999, vol.~88, issue~0, pp.~275--289.


\vskip 2mm

{\bf For citation:}  Petrosian O. L. Looking forward approach in
cooperative differential games with infinite-horizon. {\it Vestnik
of Saint Petersburg University. Series~10. Applied mathematics.
Computer science. Control processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02

}
