
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. Социальные сети в~России, лето 2017: цифры и~тренды. URL:
https://www.cossa.ru/289/166387/
https://www.slideshare.net/Taylli01/2017-77172443 (дата обращения:
20.08.2018).\newpage

2. {\it Kotenko I.~V., Chechulin A.~A., Shorov A.~V., Komashinsky
D.~V.} Analysis and evaluation of web pages classification
techniques for inappropriate content blocking // 14th Industrial
Conference on Data Mining, LNAI. New York e. a.: Springer-Verlag,
2014. Vol.~8557. P.~39--54.

3. {\it Novozhilov D.~A., Kotenko I.~V., Chechulin A.~A.}
Improving the categorization of web sites by analysis of Html-Tags
Statistics to Block inappropriate content // 9th Intern. Symposium
on Intelligent Distributed Computing. New York e. a.:
Springer-Verlag, 2016. P. 257--263.

4. {\it Kotenko I.~V., Chechulin A.~A., Komashinsky D.~V.}
Categorisation of web pages for protection against inappropriate
content in the Internet // Intern. Journal of Internet Protocol
Technology.  2017. Vol.~10(1). P.~61--71.

5. {\it Zadeh L., Abbasov A., Shahbazova S.} Fuzzy based
techniques in human like processing of social network data //
Intern. Journal of Uncertainty, Fuzziness and Knowledge-Based
Systems. Singapore: World Scientific, 2015. Vol.~23 (Suppl.~1).
P.~1--14.

6. {\it Gomzin A., Kuznetsov S.} Methods of construction of
socio-demographic profiles of Internet users // Programming and
Computer Software Journal. Moscow: ISP RAS, 2015. Vol.~27(4).
P.~129--144.

7. {\it Drobyshevskiy M., Korshunov A., Turdakov D.} Parallel
modularity computation for directed weighted graphs with
overlapping communities // Programming and Computer Software
Journal. Moscow: ISP RAS, 2016. Vol.~28(6). P.~153--170.

8. {\it Barabasi A., Bonabeau E.} Scale-free networks //
Scientific American Journal. 2003. Vol.~288(5). P.~50--59.

9. {\it Zhang E., Wang G., Gao K., Zhao X., Zhang Y.} Generalized
structural holes finding algorithm by bisection in social
communities // 6th Intern. Conference on Genetic and Evolutionary
Computing. 2013. P.~276--279.

10. {\it Liu Q., Zhang L.} Information cascades in online reading:
an empirical investigation of panel data // Library Hi Tech
Journal. 2016. Vol.~32(4). P.~687--705.

11. {\it Opsahl T., Agneessens F., Skvoretz J.} Node centrality in
weighted networks: Generalizing degree and shortest paths //
Social Networks Journal. 2010. Vol.~32(3). P.~245--251.

12. {\it Hickethier G., Tommelein I. D., Lostuvali B.} Social
network analysis of information flow in an IPD-project design
organization // 21st Annual Conference of the Intern. Group for
Lean Construction. 2013. P. 315--324.

13. {\it Sudhahar S., Veltri G., Cristianini N.} Automated
analysis of the US presidential elections using Big Data and
network analysis // Big Data $\&$ Society Journal. 2015.
Vol.~2(1). P.~1--28.

14. {\it Martinez A., Dimitriadis Y., Rubia B., Gomez E., de la
Fuente P.} Combining qualitative evaluation and social network
analysis for the study of classroom social interactions //
Computers $\&$ Education Journal. 2003. Vol.~41(4). P.~353--368.

15. {\it Lazer D., Pentland A. S., Adamic L., Aral S., Barabasi A.
L.} Life in the network: the coming age of computational social
science // Science Journal. New York: NIH Public Access, 2009.
Vol.~323(5915). P.~721.

16. {\it Melman S., Bobkov V., Cherkashin A.} Technology and
system visualization of large amounts of synoptic data // Journal
Information Science and Control Systems. 2015. Vol.~3(45).
P.~63--71.

17. {\it Hornostal O.} System of cluster analysis and
visualization of big data // Intern. Scientific Journal
Internauka. 2016. Vol.~1(6). P.~22--24.

18. {\it Averbukh V., Manakov D.} Analysis and visualization of
``big data'' // Intern. Scientific Conference Parallel
Computational Technologies. 2015. P.~332--340.

19. ParaPhraser.ru: Перефразирование и~синонимизация текста. URL:
www.paraphraser.ru (дата обращения: 20.08.2018).

20. {\it Kolomeec M.~V., Gonzalez-Granadillo G., Doynikova E.~V.,
Chechulin A.~A., Kotenko I.~V., Debar H.} Choosing models for
security metrics visualization // Computer Network Security.
Lecture Notes in Computer Science. New York e. a.:
Springer-Verlag, 2017. Vol.~10446. P.~75--87.

21. {\it Kolomeec M.~V., Chechulin A.~A., Pronoza A.~A., Kotenko
I.~V.} Technique of data visualization example of network topology
display for security monitoring // Journal of Wireless Mobile
Networks, Ubiquitous Computing, and Dependable Applications. 2016.
Vol.~7(1). P.~41--57.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 26 июня 2018 г.

Cтатья принята к~печати 25 сентября 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Проноза Антон Александрович} --- аспирант;
pronoza@gmail.com

\vskip2mm \textit{Виткова Лидия Андреевна} ---   науч. сотр.;
iskinlidia@gmail.com\newpage

\vskip2mm \textit{Чечулин Андрей Алексеевич}~--- канд. техн. наук,
вед. науч. сотр.; chechulin@comsec.spb.com

\vskip2mm \textit{Котенко Игорь Витальевич}~--- д-p техн. наук,
проф.; ivkote@comsec.spb.com

\vskip2mm \textit{Сахаров Дмитрий Викторович}~--- канд. техн.
наук, доц.; d.sakharov@rkn.gov.ru

}
