
{\normalsize

\vskip 4.5%6
mm

\noindent{\bf Mathematical model ``consumer\,---\,resource’’ on a liner range and its application for modeling the spread of late blight of potato%$^{*}$%
}

}

\vskip 2mm

{\small

\noindent{\it N. A. Gasratova %

}

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work was supported by Russian %
%Foundation for Basic Research (project N 20-07-00531 A).%\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^3$~%
St~Petersburg State University, 7--9, Universitetskaya nab.,
St~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation




}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2mm%3mm


\noindent \textbf{For citation:} Gasratova N. A. Mathematical model ``consumer\,---\,resource’’ on a liner range and its application for modeling the spread of late blight of potato. {\it Vestnik of Saint~Petersburg Uni\-ver\-si\-ty.
Ap\-plied Mat\-he\-matics. Computer Science. Control
Processes},\,\issueyear,
vol.~18,~iss.~\issuenum,~pp.~\pageref{p9}--\pageref{p9e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum09 (In Russian)

\begin{hyphenrules}{english}

\vskip2mm

{\leftskip=7mm\noindent A model of consumer distribution on a fixed resource, which is uniformly distributed through a linear area, is presented. The model is based on the Cauchy problem for a system of partial differential equations. The stability of the system is studied. The physical basis of the model is the spread of late blight over the territory of a trophic resource. A qualitative picture of the process under consideration coincides with field data obtained as a result of modeling. The model describes ``consumer’’ development not even at the moment, but through linear range. Thus assesment of damaged field square is possible.\\[1mm]
\textit{Keywords}: mathematical model of late blight development, late blight, mathematical model of phytopathology, linear range. \par}



\end{hyphenrules}

\vskip6mm%5
%\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Narouei-Khandan H. A., Shakya S. K., Garrett K. A., Goss E. M., Dufault~N.~S., Andrade-Piedra~J.~L., Asseng~S., Wallach~D., van~Bruggen A.~H.~C. BLIGHTSIM: A new potato late blight model simulating the response of \emph{Phytophthora infestans} to diurnal temperature and humidity fluctuations in relation to climate change. \emph{Pathogens}, 2020, vol.~9~(8), pp.~659--679.\\ https://doi.org/10.3390/pathogens9080659


2. Firester B., Shtienberg D., Blank L. Modelling the spatiotemporal dynamics of {\it Phytophthora infestans} at a regional scale. \emph{Plant Pathology}, 2018, vol.~67, pp.~1552--1561. \\    https://doi.org/10.1111/ppa.12860



3. Riznichenko G. Yu. {\it Matematicheskie metody v biologii i ekologii. Biofizicheskaya dinamika produkcionnyh processov}. V 2 ch. Ch. 1 [{\it Mathematical methods in biology and ecology. Biophysical dynamics of production processes}. In 2 pt. Pt 1]. Textbook for universities. 3$^{\rm rd}$~ed., revised and additional. Ìoscow, Yurayt  Publ., 2020, 210~p. (In Russian)


4. {Owolabi K. M.} Matematicheskoe issledovanie sistem s dvumia peremennymi s ispol'zovaniem adaptivnykh chislennykh metodov [Mathematical study of two-variable systems with adaptive numerical methods]. \emph{Siberian Journal of Calculating Mathematics}, 2016, vol.~19, no.~3, pp.~281--295. \\ https://doi.org/10.1134/S1995423916030046 (In Russian)



5. Filippov A.V. Fitoftoroz kartofelya [Potato late blight].\emph{ Zashchita i karantin rastenii} [\emph{Defence and quarantine of plans}], 2012, no.~5~(suppl.), pp.~61--87. (In Russian)

6. Chikin Yu. A. {\it Îbshchaya fitopatologiya}. Ch. 1 [{\it General phytopathology}. Pt 1]. Textbook. Tomsk, Tomsk State University Press, 2001, 170~p. (In Russian)

7. Skelsey P., Rossing W. A. H., Kessel G. J. T.,  van der Werf W. Invasion of\emph{ Phytophthora infestans} at the landscape level: How do spatial scale and weather modulate the consequences of spatial heterogeneity in host resistance? \emph{Phytopathology}, 2010, vol.~100~(11), pp.~1146--1161. \\ https://doi.org/10.1094/phyto-06-09-0148

8. Fry W. E., Gr\"unwald N. J. Introduction to Oomycetes. \emph{The Plant Health Instructor}, 2010. \\ https://doi.org/10.1094/PHI-I-2010-1207-01

9. Leifert C., Wilcockson S. J. \emph{Blight-MOP: Development of a systems approach for the management of late blight (caused by Phytophthora infestans) in EU organic potato production}. Newcastle, UK, University of Newcastle Press, 2005. Available at: orgprints.org/id/eprint/10650 (accessed: June 10, 2022).

10. Andrade-Piedra J. L., Hijmans R. J., Juárez~H.~S., Forbes~G.~A., Shtienberg~D., Fry~W.~E. Simulation of potato late blight in the Andes. II. Validation of the late blight model.  \emph{Phytopathology}, 2005, vol.~95~(10), pp.~1200--1208. https://doi.org/10.1094/PHYTO-95-1200

\vskip1.5mm

Received:  September 01, 2021.

Accepted: September 01, 2022.


\vskip6mm A~u~t~h~o~r's \ i~n~f~o~r~m~a~t~i~o~n:%

\vskip2mm \textit{Natalya A. Gasratova} --- PhD in Physics and Mathematics, Associate Professor; n.gasratova@spbu.ru \par%
%
%
}
