

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Provotorov V. V.  Metod monentov v zadache o gashenii kolebanii differencialnoi sistemi na grafe [Moment method in the problem of dampening oscillations of a differential system on a graph]. \emph{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2010, iss.~2, pp.~60--69.  (In Russian)

2. Artemov M. A.,  Baranovskii E. S., Zhabko A. P., Provotorov V. V.  On a 3D model of non-isothermal flows in a pipeline network. \emph{Journal of Physics. Conference Series}, 2019, vol.~1203, Article ID~012094. %\\
https://doi.org/10.1088/1742-6596/1203/1/012094

3. Provotorov V. V. Postroenie granichnih upravlenii v zadache o gashenii kolebanii sistemi iz $M$ strun [Construction of boundary controls in the problem of damping vibrations of a system of $M$ strings]. \emph{Vestnik of Saint Petersburg University. Series~10. Applied Mathematics. Computer Science. Control Processes}, 2012, iss.~1, pp.~60--69.  (In Russian)

4. Baranovskii E. S., Provotorov V. V., Artemov M. A., Zhabko A. P. Non-isothermal cree\-ping flows in a pipeline network: existence results. \emph{Symmetry}, 2021, vol.~13, Article ID~1300. \\
 https://doi.org/10.3390/sym13071300

5. Samarskii A. A. \emph{Teoriya raznostnih shem} [\emph{Theory of difference schemes}]. Moscow, Nauka Publ., 1973, 655~p.  (In Russian)

6. Zhabko~A.~P.,~Provotorov~V.~V.,~Shindyapin~A.~I.  Optimal control of a differential-difference parabolic system with distributed parameters on the graph. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~4, pp.~433--448. \\
 https://doi.org/10.21638/11701/spbu10.2021.411

7.  Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi fiziki}
[\textit{Boundary value problems of mathematical physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

8. Provotorov~V.~V.,~Sergeev~S.~M.,~Hoang~V.~N. Point control of a differential-difference system with distributed parameters on a graph. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~3, pp.~277--286. \\
https://doi.org/10.21638/11701/spbu10.2021.305

9. Volkova A.~S., Provotorov V.~V. Generalized solutions and generalized eigenfunctions
of boun\-dary-value problems on a geometric graph. \textit{Russian Mathematics} [\textit{Proceedings of Higher Educational in\-sti\-tu\-tions}], 2014, vol.~58, no.~3, pp.~1--13.

10. Podvalny S.~L., Provotorov V.~V.  Opredelenie startovoi funkcii v zadache nabludeniy parabolicheskoi sistemi na grafe [Determining the starting function in the task of observing the parabolic system with distributed parameters on the graph]. \emph{Vestnik of Voronezh State Technical University}, 2014, vol.~10, no.~6, pp.~29--35. (In Russian)

11. Fominyh A. V., Karelin V. V., Polyakova L. N., Myshkov S. K., Tregubov V. P. Metod kodifferencialnogo spuska v zadache nahozhdeniya globalnogo minimuma kusochno-affinnogo celevogo funkcionala v lineinih sistemah upravleniya [The codifferential descent method in the problem of finding the global minimum of a piecewise affine objective functional in linear control systems]. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~1, pp.~47--58. %\\
https://doi.org/10.21638/11701/spbu10.2021.105 (In Russian)

12. Zhabko A. P.,  Provotorov V. V., Balaban O. R.  Stabilization of weak solutions of parabolic systems with distributed parameters on the graph. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~2, pp.~187--198. \\
https://doi.org/10.21638/11702/spbu10.2019.203

13. Ekimov A. V., Zhabko A. P., Yakovlev P. V. The stability of differential-difference equations with proportional time delay. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~3, pp.~316--325. \\
https://doi.org/10.21638/11702/spbu10.2020.308

14. Zhabko A. P., Nurtazina K. B., Provotorov V. V. About one approach to
solving the inverse problem for parabolic equation. \emph{Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~3, pp.~322--335. \\
https://doi.org/10.21638/11702/spbu10.2019.303

15. Aleksandrov A. Yu., Tikhonov A. A. Analis ustoichivosti mehanicheskih sistem s raspredelennim zapazdivaniem na osnove decompozicii  [Stability analysis of mechanical systems with distributed delay via decomposition]. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~1, pp.~13--26. %\\
https://doi.org/10.21638/11701/spbu10.2021.102 (In Russian)

16. Provotorov V. V.  Matematicheskoe modelirovanie kolebatelnih processov podderzhivajushih rastyazhek uprugoi machti [Mathematical modeling of oscillatory processes of supporting stretch marks of elastic mast]. \emph{Vestnik of Saint Petersburg University. Se\-ries~10. Applied Mathematics. Computer Science. Control Processes}, 2006, iss.~2, pp.~28--35.   (In Russian)

17. Karelin V.~V., Bure V.~M., Svirkin M.~V. Obobchennaja model rasprostranenija informacii v neprerivnom vremeni [The generalized model of information dissemination in continuous time]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2017, vol.~13, iss.~1, pp.~74--80. %\\
https:// doi.org/10.21638/11701/spbu10.2017.107 (In Russian)

18. Kamachkin A. M., Potapov D. K., Yevstafyeva V. V.  Dinamika i sinhronizaciya ciklicheskih struktur oscillyatorov s gisterezisnoi obratnoi svyazu [Dynamics and synchronization in feedback cyclic structures with hysteresis oscillators]. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~2, pp.~186--199. \\
https://doi.org/10.21638/11701/spbu10.2020.210 (In Russian)

19. Daugavet V. A.,  Yakovlev P. V. Srednekvadratichnaya approksimaciya pryamougolnoi matrpci matricami menshego ranga  [Mean square approximation of a rectangular  matrix by matrices of lower rank].  \emph{Journal of Computational Mathematics and Mathematical Physics}, 1989, vol.~29, no.~10, pp.~1466--1479.  (In Russian)


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  May 12,  2022.

Accepted: June 21, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Aleksei P. Zhabko} --- Dr. Sci. in Physics and Mathematics, Professor; zhabko.apmath.spbu@mail.ru \par


\vskip 2mm
 \textit{Vyacheslav V. Provotorov} --- Dr. Sci. in Physics and Mathematics, Professor; wwprov@mail.ru \par


\vskip 2mm
 \textit{Sergey M. Sergeev} ---  PhD  in Engineering Sciences, Associate Professor;   sergeev2@yandex.ru
 \par
%
%
}
