

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. {Demyanov V. F., Rubinov A. M.} Kvazidifferentsial'nie
funktsionali [Quasidifferentiable functionals]. {\it Dokl. Akad.
Nauk SSSR} [{\it Papers of Academy of Sciences USSR}], 1980,
vol.~250, no.~1, pp.~21--25. (In Russian)
%

2. {Demyanov V. F., Rubinov A. M. } {\it Quasidifferential
calculus}. New York, Optimization Software Inc. Publ. Division,
1986, 288~p.

3. {Grzybowski J.,   Pallaschke  D.,
 Urba\'{n}ski R.}  A pre-classification and the separation law
for closed bounded convex sets. {\it Optimization Methods and
Software}, 2005,  vol.~20, pp.~219--229.

4. {Grzybowski J.,  Pallaschke  D.,
 Urba\'{n}ski R.}  Demyanov difference in infinite dimensional
 spaces. {\it Proceedings of CNSA, Saint Petersburg, Springer Optim.
Appl.}, 2014, vol.~87, pp.~13--24.

5.  {Pallaschke D., Urba\'nski R.}  Pairs of compact convex sets
--- Fractional arithmetic with convex sets. {\it Mathematics and its
Applications}, 2002, vol.~548, pp.~487--496.

6.   {Pallaschke D., Rolewicz S.} Foundations of mathematical
optimization. {\it Mathematics and its Applications}, 1997,
vol.~426,   pp.~417--429.

7. {Diamond P.,  Kloeden P., Rubinov A. M., Vladimirov A.}
Comperative properties of three metrics in the space of compact
convex sets. {\it Set-Valued Analysis}, 1997, vol.~5, no.~3,
pp.~267--289.

8.  {H\"ormander L.} Sur la fonction d' appui des ensembles
convexes dans un espace localement convexe [On the function of
support sets convex in a space that is locally convex]. {\it Arkiv
f\"or Matematik} [{\it Archives for Mathematics}], 1954, vol.~3,
pp.~181--186.

9. {Pinsker A. G. } The space of convex sets of a locally convex
space. {\it Trudy Leningrad Engineering-Economic Institute}, 1966,
vol.~63, pp.~13--17.

10. {Rubinov A. M.}  Abstract convexity, global optimization and
data classification.  {\it Opsearch}, 2001, vol.~38, pp.~247--265.

11.  {Urba\'nski  R. }  A generalization of the
Minkowski---R{\aa}dstr\"om---H\"ormander theorem. {\it Bull. Acad.
Polon. Sci. Series Sci. Math. Astr. Phys.},  1976, vol.~24,
pp.~709--715.

12.  {Rubinov  A. M., Akhundov I. S.}
 Differences of compact sets in the sense of Demyanov and its application
to non-smooth-analysis. {\it Optimization}, 1992, vol.~23,
pp.~179--189.

13.    Clarke F. H. {\it Optimization and Nonsmooth Analysis.} New
York, J.~Wiley Comp. Publ.,  1983, 306~p.

14.   {Husain T., Tweddle I.}
 On the extreme points of the sum of two compact convex sets.
{\it  Math. Ann.}, 1970, vol.~188, pp.~113--122.

15. {Gaudioso M.,~Gorgone E., Pallaschke D.} Separation of convex
sets by Clarke subdifferential. {\it Optimization}, 2011, vol.~59,
pp.~1199--1210.







\vskip 2mm

{\bf For citation:}   Grzybowski J., Pallaschke D., Urba\'{n}ski
R. The quasidifferential calculus, separation of convex sets and
the Demyanov difference. {\it Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}.
\doivyp/spbu10.\issueyear.\issuenum03



}
