
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. Berkeley Open Infrastructure for Network Computing  // BOINC:
офиц. сайт. https://boinc. berkeley.edu (дата обращения:
20.12.2019~г.)

2. \textit{Li Ch., Raghunathan  A., Jha N. K.} Secure virtual
machine execution under an untrusted management OS // IEEE 3rd
International Conference on Cloud Computing. Miami, 2010.
P.~172--179.

3. \textit{Ivashko E. E.} Enterprise desktop grids // CEUR
Workshop Proceedings. 2015. Vol.~1502. P.~16--21.

4. \textit{Afanasiev A. P., Bychkov I. V., Manzyuk M. O., Posypkin
M. A., Semenov A. A.,  \mbox{Zaikin O. S..}} Technology for
integrating idle computing cluster resources into volunteer
computing projects // 5th~In\-ter\-na\-tio\-nal Workshop on
Computer Science and Engineering: Information Processing and
Control Engineering, WCSE 2015-IPCE. Moscow, 2015. P.~109--114.

5. \textit{Afanasiev A. P., Bychkov I. V., Zaikin O. S., Manzyuk
M. O., Posypkin M. A.,  \mbox{Semenov A. A.}}  Concept of a
multitask grid system with a flexible allocation of idle
computational resources of supercomputers // Journal of Computer
and Systems Sciences International.  2017. Vol.~56.  N~4.
P.~701--707.

6. \textit{Marosi A. C., Kovacs J., Kacsuk P. K.} Towards a
volunteer cloud system // Future Generation Computer Systems.
2013. Vol.~29(6). P.~1442--1451.

7. WrapperApp --- BOINC // BOINC: офиц. сайт.
https://boinc.berkeley.edu/trac/wiki/\ WrapperApp (дата обращения:
18.03.2019~г.)

8. \textit{Khrapov N. P., Rozen V. V., Samtsevich A. I., Posypkin
M. A., Sukhomlin V. A., Oga\-nov~A.~R.} Using virtualization to
protect the proprietary material science applications in volunteer
computing // Open Engineering. 2018. Vol.~8. P.~57--60.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 16 апреля 2019~г.

Cтатья принята к~печати 13 февраля 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Храпов Николай Павлович} --- и.о. науч. сотр.,
аспирант; nkhrapov@gmail.com

}
