
{\normalsize

\vskip 4.5mm%6mm

\noindent{\bf Using virtualization technologies to protect
software and data \\ in volunteer computing systems%$^{*}$
}

}

\vskip 2mm

{\small

\noindent{\it N. P. Khrapov%$\,^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
Institute for Information Transmission Problems of the Russian
Academy of Sciences,

\noindent%
%\hskip2.45mm%
19, Bolshoy Karetny per., Moscow, 127051, Russian Federation

%\noindent%
%$^1$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%
%\noindent%
%\hskip2.45mm%
%St.\,Petersburg, 199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip1.8mm%3mm


\noindent \textbf{For citation:}  Khrapov N. P. Using
virtualization technologies to protect software and data in
volunteer computing systems. {\it Vest\-nik of Saint~Petersburg
University. Applied Mathematics. Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~16,~iss.~\issuenum,~pp.~\pageref{p6}--\pageref{p6e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum06  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent When solving computational problems,
research teams often use computational resources that are provided
for this by various organizations or individual volunteers.
Software and data used by the research team may be a subject of
intellectual property. For this reason, it becomes relevant to
protect software and data from potential intruders who can join
the project under the guise of volunteers. The article provides an
overview and an analysis of existing approaches to overcome this
problem in the general case. The possibilities of the BOINC
infrastructure, relevant for the development of various
information security scenarios, are considered in detail. The
concept of protecting data from unauthorized access, based on the
integration of the client side of BOINC with the VirtualBox
system, is proposed.\\[1mm]
\textit{Keywords}: protection of information, grid-systems,
volunteer computing, BOINC, vir\-tua\-li\-za\-tion, VirtualBox.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. \textit{Berkeley Open Infrastructure for Network Computing}.
Available at: https://boinc.berkeley.edu (accessed:  20.12.2019).

2. Li Ch., Raghunathan  A., Jha N. K. Secure virtual machine
execution under an untrusted ma\-na\-ge\-ment OS. \textit{IEEE 3rd
International Conference on Cloud Computing.} Miami, 2010,
pp.~172--179.

3. Ivashko E. E. Enterprise desktop drids.\textit{ CEUR Workshop
Proceeding}, 2015, vol. 1502, \mbox{pp. 16--21.}

4. Afanasiev A. P., Bychkov I. V., Manzyuk M. O., Posypkin M. A.,
Semenov A. A., \mbox{Zaikin O. S.} Technology for integrating idle
computing cluster resources into volunteer computing projects.
\textit{5th In\-ter\-na\-tio\-nal Workshop on Computer Science and
Engineering: Information Processing and Control Engineering}, WCSE
2015-IPCE. Moscow, 2015, pp.~109--114.

5. Afanasiev A. P., Bychkov I. V., Zaikin O. S., Manzyuk M. O.,
Posypkin M. A.,  \mbox{Semenov A. A.} Concept of a multitask grid
system with a flexible allocation of idle computational resources
of supercomputers.\textit{ Journal of Computer and Systems
Sciences International}, 2017, vol.~56, no.~4, pp.~701--707.

6. Marosi A. C., Kovacs J., Kacsuk P. K. Towards a volunteer cloud
system. \textit{Future Generation Computer Systems}, 2013,
vol.~29(6), pp.~1442--1451.

7. \textit{WrapperApp  BOINC}. Available at:
https://boinc.berkeley.edu/trac/wiki/WrapperApp (ac\-cessed:
18.03.2019).

8. Khrapov N. P., Rozen V. V., Samtsevich A. I., Posypkin M. A.,
Sukhomlin V. A., \mbox{Oganov A. R.} Using virtualization to
protect the proprietary material science applications in volunteer
computing. \textit{Open Engineering}, 2018, vol.~8, pp.~57--60.

\vskip1.5mm Received:  April 16, 2019.

Accepted: February 13, 2020.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Nikolay P. Khrapov} --- Researcher, Graduate
Student; nkhrapov@gmail.com

}
