
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Goloskokov D.\,P.}
Calculation of the ribbed plate in the mixed form ``deflection-function of efforts’’~//
2015 International Conference ``Stability and Control Processes’’ in memory of V.~I.~Zubov (SCP--2015). Proceedings. St. Petersburg: St. Petersburg State University, 2015. P.~386--388. N~7342170.

2. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Analysis of elastic systems with discontinuous parameters~//
2017 International Conference ``Constructive Nonsmooth Analysis and Related Topics’’ dedicated to the memory of V.~F.~Demyanov (CNSA--2017). Proceedings. St. Petersburg: St. Petersburg State University, 2017. N~7973959.

3. \textit{Qin X., Liu S., Shen Y., Peng L.}
Rib meshless optimization of stiffened plates resting on elastic foundation based on genetic algorithm~//
Chinese Journal of Theoretical and Applied Mechanics.
2020. Vol.~52. Iss.~1. P.~93--110.

4. \textit{Konev S.\,V., Fainshtein A.\,S., Teftelev I.\,E.} Application of Kantorovich\,---\,Vlasov method for sha\-ped plate bending problem~//
Lecture Notes in Mechanical Engineering.
5th International Conference on Industrial Engineering
(ICIE--2019). Sochi, Russian Federation.
March 25--29, 2019. Sochi, 2020. P.~91--100.

5. \textit{Qin X., Liu S.\,S., Peng L.\,X.} Bending analysis of skew ribbed plates with a meshfree method~//
IOP Conference. Series Materials Science and Engineering.
Vol.~531. Iss.~1.
2nd International Conference on Modeling in Mechanics and Materials.
Suzhou, China. March 29--31, 2019.

6. \textit{Sapountzakis E.\,J.} An improved model for the analysis of plates stiffened by parallel beams including creep and shrinkage effects: Application to concrete or to composite steel-concrete structures~//
International Journal on Engineering Applications.
2018. Vol.~6. Iss.~2. P.~57--70.

7. \textit{Meng X., Sha L., Tong L., Yang X.} Experimental research on flexural performance of prestressed ribbed slab and composite slab~//
Journal of Shenyang Jianzhu University (Natural Science).
2017. Vol.~33. Iss.~1. P.~77--85.

8. \textit{Peng L.\,X.} Bending analysis of rectangular ribbed plates by the moving-least square meshfree method~//
Chinese Journal of Computational Mechanics.
2012. Vol.~29. Iss.~2. P.~210--216.

9. \textit{Sapountzakis E.\,J., Mokos V.\,G.} Shear deformation effect in plates stiffened by parallel beams~//
Archive of Applied Mechanics.
2009. Vol.~79. Iss.~10. P.~893--915.

10. \textit{Sapountzakis E.\,J., Mokos V.\,G.} Analysis of plates stiffened by parallel beams~//
International Journal for Numerical Methods in Engineering.
2007. Vol.~70. Iss.~10. P.~1209--1240.

11. \textit{Sapountzakis E.\,J., Katsikadelis J.\,T.} A new model for slab and beam structures --- comparison with other models~//
Computers and Structures.
2002. Vol.~80. Iss.~5--6. P.~459--470.

12. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Comparison of two analytical approaches to the analysis of grillages~//
2015 International Conference ``Stability and Control Processes’’ in memory of V.~I.~Zubov (SCP--2015). Proceedings. St. Petersburg: St.~Pe\-ters\-burg State University, 2015. P.~382--385. N~7342169.

13. \textit{Goloskokov D.\,P., Matrosov A.\,V.}
Approximate analytical solutions in the analysis of thin elastic plates~//
AIP Conference Proceedings. St. Petersburg, 1959. P.~2018. N~070012.

14. \textit{Matrosov A.\,V., Goloskokov D.\,P.}
Analysis of elastic systems with nonsmooth boundaries~//
2017 International Conference ``Constructive Non\-smooth Analysis and Related Topics’’ dedicated to the memory of V.~F.~Demyanov (CNSA--2017). Proceedings. St. Petersburg: St. Petersburg State University, 2017. N 7973987.


15. \textit{Доннелл Л.\,Г.} Балки, пластины и оболочки / пер. с англ.;
под ред. Э.~И.~Григолюка. М.: Наука, 1982. 568~с. (\textit{Donnel L.\,G.} Beams, plates and shells.)

16. \textit{Тимошенко С.\,П., Войновский-Кригер С.} Пластинки и оболочки / пер. с англ. М.: Наука, 1966. 636~с.

17. \textit{Голоскоков Д.\,П.} Численно-аналитические методы расчета упругих тонкостенных конструкций нерегулярной структуры. СПб.: СПбГУВК, 2006. 258~c.


\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 4 февраля 2021~г.

Cтатья принята к~печати 5 апреля 2021~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Голоскоков Дмитрий Петрович}
--- д-р техн. наук, проф.; dpg1954@mail.ru

\vskip2mm \textit{Матросов Александр Васильевич}
--- д-р физ.-мат. наук, проф.; avmatrosov@mail.ru

}
