
{\normalsize

\vskip 4,5%6%
mm

\noindent{\bf Bending of a ribbed plate under complex loading%$^{*}$
}

}

\vskip 2,5%3%
mm

{\small

\noindent{\it D. P. Goloskokov$\,^1$, A. V. Matrosov$\,^2$%
%, I.~Î. Famylia%$\,^2$%

 }

\vskip 2,5%3%
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent\indent~$^{*}$ This work was  supported by the%
%Russian Foundation for Basic Research (grant N 19-01-00146-a).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\noindent%
%%$^1$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,% %St.\,Petersburg,

%\noindent%
%%\hskip2.45mm%
%199034, Russian Federation


\noindent%
$^1$~%
The Bonch-Bruevich St. Petersburg State University of Telecommunication,

\noindent%
\hskip2.45mm%
22, pr. Bol'shevikov, St.\,Petersburg, 193232, Russian Federation



\noindent%
$^2$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2,5%3%
mm


\noindent \textbf{For citation:}  Goloskokov D.\,P., Matrosov A.\,V. Bending of a ribbed plate under complex loading. {\it Vest\-nik of Saint Petersburg
University. Applied Mathe\-ma\-tics. Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~17, iss.~\issuenum,~pp.~\pageref{p2}--\pageref{p2e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum02 (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The article considers the problem of a rectangular plate, supported by a cross system of stiffening ribs, bending. In addition to the transverse load, the plate is subjected to forces in its plane, transmitted through the ribs. An analytical solution to the boundary value problem for the resolving differential equation with respect to the normal deflection of the plate, describing the deformation of a rectangular plate supported by stiffeners, is obtained. The solution is presented in the form of series in combinations of regular and special discontinuous functions, which converge quickly and lead to a simple computational algorithm. The influence of the ribs is taken into account in the equation in the form of additional terms containing factors with a delta function. This approach allows us to get rid of a number of assumptions regarding the interaction of the plate with its reinforcing elements. The use of the apparatus of generalized functions when modeling objects of this type simplifies the boundary conditions (there are no conditions for conjugation of various structural elements), but at the same time the differential equations become more complicated. The problem is reduced to the so-called partially degenerate equations. Development of analytical methods that allow obtaining exact solutions of differential equations of this type, and their introduction into computational practice, is one of the urgent tasks of the mechanics of objects with disturbed regularity.
\\[1mm]
\textit{Keywords}: plate, stiffeners, mathematical model, numerical-analytical methods, special discontinuous functions, Dirac function, Heaviside function, Fourier series, orthogonal series.\par}

\vskip6mm
%\pagebreak

\noindent \textbf{References} }

\vskip 3mm

{\footnotesize

1. Goloskokov D.\,P.
Calculation of the ribbed plate in the mixed form ``deflection-function of efforts’’. \textit{2015 International Conference ``Stability and Control Processes’’ in memory of
V.~I.~Zubov (SCP--2015). Proceedings}. St. Petersburg, St. Petersburg State University Press, 2015, pp.~386--388, no.~7342170.

2. Goloskokov D.\,P., Matrosov A.\,V.
Analysis of elastic systems with discontinuous parameters. \textit{2017 International Conference ``Constructive Nonsmooth Analysis and Related Topics’’
dedicated to the memory of V.~F.~Demyanov (CNSA--2017). Proceedings}. St. Petersburg, St. Petersburg State University Press, 2017, no.~7973959.

3. Qin X., Liu S., Shen Y., Peng L.
Rib meshless optimization of stiffened plates resting on elastic foundation based on
genetic algorithm.
\textit{Chinese Journal of Theoretical and Applied Mechanics},
2020, vol.~52, iss.~1, pp.~93--110.

4. Konev S.\,V., Fainshtein A.\,S., Teftelev I.\,E. Application of
Kantorovich---Vlasov method for shaped plate bending problem.
\textit{Lecture Notes in Mechanical Engineering}.
\textit{5th International Conference on Industrial Engineering (ICIE--2019)}, Sochi, Russian Federation, March 25--29, 2019. Sochi, 2020, pp.~91--100.

5. Qin X., Liu S.\,S., Peng L.\,X. Bending analysis of skew ribbed plates
with a meshfree method.
\textit{IOP Conference. Series Materials Science and Engineering},
vol.~531, iss.~1.
\textit{2nd International Conference on Modeling in Mechanics and Materials}. Suzhou, China, March 29--31, 2019.

6. Sapountzakis E.\,J. An improved model for the analysis of plates stiffened by parallel beams including creep and shrinkage effects: Application to concrete or to composite steel-concrete structures.
\textit{International Journal on Engineering Applications},
2018, vol.~6, iss.~2, pp.~57--70.

7. Meng X., Sha L., Tong L., Yang X. Experimental research on flexural
performance of prestressed ribbed slab and composite slab.
\textit{Journal of Shenyang Jianzhu University (Natural Science)},
2017, vol.~33, iss.~1, pp.~77--85.

8. Peng L.\,X. Bending analysis of rectangular ribbed plates by the
moving-least square meshfree method.
\textit{Chinese Journal of Computational Mechanics},
2012, vol.~29, iss.~2, pp.~210--216.

9. Sapountzakis E.\,J., Mokos V.\,G. Shear deformation effect in plates
stiffened by parallel beams.
\textit{Archive of Applied Mechanics},
2009, vol.~79, iss.~10, pp.~893--915.

10. Sapountzakis E.\,J., Mokos V.\,G. Analysis of plates stiffened by parallel beams.
\textit{International Journal for Numerical Methods in Engineering},
2007, vol.~70, iss.~10, pp.~1209--1240.

11. Sapountzakis E.\,J., Katsikadelis J.\,T. A new model for slab and beam structures --- comparison with other models.
\textit{Computers and Structures},
2002, vol.~80, iss.~5--6, pp.~459--470.

12. Goloskokov D.\,P., Matrosov A.\,V.
Comparison of two analytical approaches to the analysis of grillages. \textit{2015 International Conference ``Stability and Control Processes’’ in memory of V.~I.~Zubov (SCP--2015). Proceedings}. St.~Pe\-ters\-burg, St.~Pe\-ters\-burg State University Press, 2015, pp.~382--385, no.~7342169.

13. Goloskokov D.\,P., Matrosov A.\,V.
Approximate analytical solutions in the analysis of thin elastic plates. \textit{AIP Conference Proceedings}. St. Petersburg, 1959, p.~2018, no.~070012.

14. Matrosov A.\,V., Goloskokov D.\,P.
Analysis of elastic systems with nonsmooth boundaries.
\textit{2017 International Conference ``Constructive Non\-smooth Analysis and Related Topics’’ dedicated to the memory of V.~F.~Demyanov (CNSA--2017). Proceedings}. St. Petersburg, St. Petersburg State University Press, 2017, no.~7973987.

15. Donnel L.\,G. \textit{Beams, plates and shells}. New York, McGraw-Hill Press, 1976, 453~p. (Rus. ed.: Donnel L.\,G. {\it Balki, plastiny i obolochki}. Moscow, Nauka Publ., 1982, 568~p.)

16. Timoshenko S.\,P., Woinowsky-Krieger S.
\textit{Plastinki i obolochki} [\textit{Plates and shells}]. Moscow, Nauka Publ., 1966, 636~p. (In Russian)

17. Goloskokov D.\,P. \textit{Chisleno-analiticheskie metody rascheta uprugih tonkostenyh konstrukciy neregularnoy struktury} [\textit{Numerical and analytical methods of calculation for elastic slimness-walling constructions for non-regular structure}].
St. Petersburg, SPbGUVK Publ., 2006, 258~p. (In Russian)


\vskip1.5mm Received:  February 04, 2021.

Accepted: April 05, 2021.

\vskip6mm A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Dmitry P. Goloskokov}
--- Dr. Sci. in Engineering, Professor; dpg1954d@mail.ru

\vskip2mm \textit{Alexander V. Matrosov}
--- Dr. Sci. in Physics and Mathematics, Professor; avmatrosovd@mail.ru\par
%
%
}
