

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm








1. Littlechild~S. C., Owen~G. A simple expression for the Shapley
value in a special case. {\it Management Sci.}, 1973, vol.~20,
pp.~370--372.

2. Crocker L., Algina J.  {\it Introduction to Classical and
Modern Test Theory}. Boston, Cengage Learning, 2006, 527~p. (Russ.
ed.: Crocker~L., Algina~J. {\it Vvedeniye v klassicheskyu i
sovremennyu teoriu testov}. Moscow, Logos Publ., 2010,
668~p.)\newpage

3.  Lutsenko M. M., Shadrintseva N. V. Kooperativnyj i chastotnyj
podhody k naznacheniju vesov zadanij testa [Cooperative and
frequency approaches to assigning weights of the test]. {\it
Proceeding of Saint Petersburg University of  Railways}, 2014,
vol.~3(40), pp.~150--156. (In Russian)

4. Lutsenko M. M., Shadrintseva N. V. Kooperativnyj podhod k
naznacheniju vesov zadanij v pedagogicheskom teste [A cooperative
approach to assigning the weights of the tasks in the pedagogical
test]. {\it Matematicheskaja teorija igr i ee prilozhenija
$[$Mathematical game theory and its applications}], 2014, vol.~6,
iss.~4,  pp.~37--67. (In Russian)

5. Neiman~U. M., Khlebnikov~V. A. {\it Vvedenie v teoriju
modelirovanija i parametrizacii pedagogicheskih testov. 2-e izd.,
ispr. i dop. $[$Introduction to the theory of modelling and
parameterization of pedagogical tests}]. Moscow, Vysshaja shkola
Publ., 2000, 168~p. (In Russian)

6. {\it Handbook of Modern Item Response Theory}. Eds by Win~J.
Van~der Linden, R.~K.~Hambleton. New York, Springer-Verlag Publ.,
1997, 510~p.

7. Lutsenko M. M. Teoretiko-igrovoj podhod k ocenke tochnosti
testirovanija  [Game-theoretic approach to the assessment of
testing accuracy]. \textit{Matematicheskaja teorija igr i ee
prilozhenija $[$Mathematical game theory and its applications}],
2009, vol.~1, iss.~4,  pp.~63--77. (In Russian)

8. Lutsenko M. M., Shadrintseva N. V.  The Shapley and Banzaf
values for different courses of study. {\it The Sixth Intern
conference ``Game Theory and Management'': abstracts}. Saint
Petersburg, Saint Petersburg State University Press, 2012,
pp.~165--169.

9. Lutsenko M. M., Shadrintseva N. V. Shapley value in testing.
{\it Proceedings of the second Intern. conference ``Game theory
and management application'', ``Game theory, operations research
and applications''}. Hyderabad, India, Institute of public
enterprise Press, 2012,  pp.~47--49.

10. Mashler M., Solan E., Zamir S.  {\it Game theory}. Cambridge,
USA, Cambridge University Press, 2013, 1005~p.

11. Petrosiyan~L. A., Zenkevich~N. A., Shevkoplias~E. V. {\it
Teorija igr: uchebnik $[$Game theory: textbook}]. Saint
Petersburg, BHV-Petersburg Publ., 2012, 432~p. (In Russian)

12. Shapley L. S. {\it A value for N-person games. Contributions
to the Theory of Games II}. Eds by H.~W.~Kuhn, A.~W.~Tucker.
Princeton, Princeton University Press, 1953,  pp.~307--317.

13. Br\^{a}nzei R., Fragnelli V., Tijs~S. Tree-connected peer
group situations and peer group games. {\it Mathematical Methods
of Operations Research} (Princeton, New York), 2002, vol.~55,
pp.~93--106.

14. Gilles R. P., Owen G., Brink~R. van den. Games with permission
structures: The Cunjuctive Approach. {\it Intern. Journal of Game
Theory}, 1992,  vol.~20, iss.~3,  p.~277--294.

15. Rasmusen~E. {\it Games and information, An Introduction to
Game theory}. Oxford, UK; Cambridge, USA, Blackwell Publ., 1989,
560~p.

16. Ni D.,  Wang Y. Sharing a polluted river. {\it Games and
Economic Behavior}, 2007,  vol.~60,  pp.~176--186.





\vskip 2mm

{\bf For citation:}   Lutsenko M. M., Shadrinceva N. V. Shapley
weights of test items. {\it Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
