
{\normalsize

\vskip 6mm

\noindent{\bf On numerical solution of the optimal control
 problem based on a  method using  the second variation
of a trajectory%$\,^*$%
 }

}

\vskip 1.5mm

{\small

\noindent{\it O.~I.~Drivotin%$\,^1$%
%, N. L. Grebennikova$\,^2$%
%, K. Yu. Staroverova$\,^1$%
%, I.~О. Famylia%$\,^2$%
} %

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N 18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Drivotin O.~I. On numerical
solution of the optimal control  problem based on a~method using
the second variation of a trajectory. {\it Vestnik of
Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~15, iss.~\issuenum,
pp.~\pageref{p11}--\pageref{p11e}.\linebreak
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum11  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent A new approach for the numerical solution
of the optimal control problem is presented. This approach is
based on the parametrization of the control function and
computation of the first and the second derivatives of the cost
functional over parameters. Computation of the second derivatives
is carried out using an integral representation for the second
variation of the trajectory of a controlled dynamical system,which
is obtained in this work and includes a tensor of the third rank.
The proposed approach differs from the approach being used
previously, in which the second derivatives of the cost functional
are expressed through the matrix momenta. A numerical method based
on the second variation of the trajectory can be effective in
problems with a great number of parameters. Using the matrix
momenta, one should integrate a system of differential equations,
the number of which is quadratic in the number of parameters. In
the present approach, the number of the equation to be integrated
is determined only by the dimension of the phase space and can be
sufficiently
smaller.\\[1mm] \textit{Keywords}: optimal control, controlled
dynamical system, second variation, numerical methods of the
second order.
\par}

%\vskip 5mm
\newpage

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize


1. {Hartman P.} {\it Ordinary differential equations}. New York,
John Wiley \& Sons Publ., 1964, 612~p. (Russ. ed.:  Hartman~F.
{\it Obyknovennye differentsial'nye uravneniya}. Moscow, Mir
Publ., 1970, 720~p.)

2. {Pontryagin L. S., Boltyanskiy V. G., Gamkrelidze R. V.,
Mischenko E. F.} {\it Matematicheskaya teoriya optimal'nyh
protsessov $[$Mathematical theory of optimal processes$]$}.
Moscow, Nauka Publ., 1976, 392~p. (In Russian)

3. {Moiseev N. N.} {\it Chislennye metody v teorii optimal'nyh
sistem $[$Numerical methods in the optimal systems theory$]$}.
Moscow, Nauka Publ., 1971, 424~p. (In Russian)


4. {Pytlak R.} {\it Numerical methods for optimal control with
state constraints}. Berlin, Springer Press, 1999, 216~p. (Lect.
Notes. Math., vol.~1707.)

5. {Bryson A. E. Jr., Ho Yu-Chi.} {\it Applied optimal control}.
Waltham, Mass., Blaisdell Publ. Comp., 1969, 496 p. (Russ. ed.:
Braison A., Ho Yu-Shi. {\it Prikladnaya teoriya optimal'nogo
upravleniya}. Moscow, Mir Publ., 1972, 544~p.)
%/ пер. с англ. Э.М. Макашова, Ю.П. Плотникова; под. ред. А.М. Летова.


6. {Chernous'ko F. L., Banichuk N. V.} {\it Variatsionnye zadachi
mehaniki i upravleniya $[$Variational problems of mechanics and
control$]$}. Moscow, Nauka Publ., 1973, 238~p. (In Russian)


7. {Tsirlin V. M., Balakirev V. S., Dudnikov E. G.} {\it
Variatsionnye metody optimizatsii upravlyaemyh obyektov
$[$Variational methods of controlled objects optimization$]$}.
Moscow, Energiya Publ., 1976, 448~p. (In Russian)


8. {Fedorenko R. P.} {\it Priblizhennoye resheniye zadach
optimal'nogo upravleniya $[$Numerical solution of optimal control
problems$]$}. Moscow, Nauka Publ., 1978, 488~p. (In Russian)


9. {Bock H. G.} Numerical solution
 of nonlinear multipoint boundary value problems
 with applications to optimal control.
 {\it Z.~Ang. Math. Mech.}, 1978, vol.~58,  pp.~407--409.

10. {Bock H. G., Plitt K. J.}
 A multiple shooting algorithm for direct solution
 of optimal control problems.
 {\it Proc. 9th IFAC World Congress}. Budapest, Hungary,
 July~2--6, 1984, pp.~242--247.



11. {Krylov I. A., Chernous'ko F. L.} O metode posledovatel'nyh
priblizheniy dlya resheniya zadach optimal'nogo upravleniya $[$On
successive approximations method for solving of optimal control
problems$]$. {\it Zhurn. vychisl. matematiki i matem. fiziki
$[$Journal of Calculating Mathematics and Mathematical
Physics$]$}, 1962, vol.~2, no.~6, pp.~1132--1139. (In Russian)


12. {Krylov I. A., Chernous'ko F. L.} Algoritm metoda
posledovatel'nyh priblizheniy dlya zadach optimal'nogo upravleniya
$[$Algorithm of successive approximations method for optimal
control problems$]$. {\it Zhurn. vychisl. matematiki i matem.
fiziki $[$Journal of Calculating Mathematics and Mathematical
Physics$]$}, 1972, vol.~12, no.~1, pp.~14--34. (In Russian)



13. {Bryson A. E., Denham W. E.} A steepest ascent method for
solving optimum programming problems. {\it ASME J.~Appl. Mech.
Series~E}, 1962, vol.~29, pp.~247--257.


14. {Gorbunov V. K.} O svedenii zadach optimal'nogo upravleniya k
konechnomernym $[$On reduction of optimal control problems to
finite-dimensional ones$]$. {\it Zhurn. vychisl. matematiki i
matem. fiziki $[$Journal of Calculating Mathematics and
Mathematical Physics$]$}, 1978, vol.~18, no.~5, pp.~1083--1095.
(In Russian)


15. {Gorbunov V. K.} Metod parametrizatsii zadach optimal'nogo
upravleniya $[$Method of parameterization of optimal control
problems$]$. {\it Zhurn. vychisl. matematiki i matem. fiziki
$[$Journal of Calculating Mathematics and Mathematical
Physics$]$}, 1979, vol.~19, no.~2, pp.~292--303. (In Russian)



16. {Demyanov V. F., Rubinov A. M.} {\it Priblizhennye metody
resheniya extremal'nyh zadach $[$Numerical methods of extremal
control solving$]$}. Leningrad, Leningrad University Publ., 1968,
180~p. (In Russian)

17. {Vasil'ev F. P.} {\it Chislennye metody resheniya extremal'nyh
zadach $[$Numerical methods of extremal control solving$]$}.
Moscow, Nauka Publ., 1988, 552~p. (In Russian)

18. {Miele A.} Recent advances in gradient algoritms
 for optimal control problems.
 {\it J.~Optimization Theory and Applications}, 1975, vol.~17, no.~5/6,
 pp.~361--430.


19. {Mitter S. K.} Successive approximation method for the
solution of optimal control problems. {\it Automatica}, 1966,
vol.~3, pp.~135--149.


20.  {Longmuir  A. G.,  Bohn E. V.}
 Second-variation methods in dynamic optimization.
{\it J.~Optimization Theory and Applications}, 1969, vol.~3, no.~3, %\textnumero 3.
 pp.~164--173.



21.  {Gabasov R., Kirillova F. M.} {\it Osobye optimal'nye
upravleniya $[$Special optimal controls$]$}. Moscow, Nauka Publ.,
1973, 256~p. (In Russian)



22. {Gorbunov V. K., Lutoshkin I. V.} Razvitie i opyt primeneniya
metoda parametrizatsii v vyrozhdennyh zadachah dinamicheskoy
optimizatsii $[$Development and experience of application of
method of parameterization in degenerate problems of dynamical
optimization$]$. {\it Izvestiya Rossiyskoy akademii nauk. Teoriya
i sistemy upravleniya $[$Proceeding of Russian Academy of
Sciences. Theory and System of Management$]$}, 2004, iss.~5,
pp.~67--84. (In Russian)


23. {Golfetto W. A., Silva Fernandes S.}
 A review of gradient algorithms
 for numerical computations of optimal trajectories.
 {\it J.~Aerosp. Technol. Manag.}, 2012, vol.~4, no.~2, pp.~131--143.


24. {Henrion~R.} {\it La theorie de la variation seconde et ses
application en commande optimale $[$The theory of the second
variation and its application in optimal control$]$}. Academie
royale de Belgique. Memories de la classe des sciences, 1975,
t.~41, f.~7, 208~p.
%Palais des Academies. Bruxelles.
(Russ. ed.: Anrion R. {\it Teoriya vtoroy variatsii i ee
prilozheniya v optimal'nom upravlenii}. Moscow, Nauka Publ., 1979,
208~p.)


25. {Ovsyannikov D. A.} {\it Matematicheskiye metody upravleniya
puchkami $[$Mathematical methods of beam control$]$}. Leningrad,
Leningrad University Publ., 1980, 228~p. (In Russian)

26. {Ovsyannikov D. A.} {\it Modelirovaniye i optimizatsiya
dinamiki puchkov zaryazhennyh chastits $[$Modeling and
optimization of charged particle beam dynamics$]$}. Leningrad,
Leningrad University Publ., 1990, 312~p. (In Russian)


27. {Ovsyannikov D. A., Drivotin O. I.} {\it Modelirovaniye
intensivnyh puchkov zaryazhennyh chastits $[$Modeling of intensive
charged particle beams$]$}. Saint Petersburg, Saint Petersburg
University Publ., 2003, 176~p. (In Russian)


28. {Bublik B. N., Garashchenko F. G., Kirichenko N. F.} {\it
Strukturno-parametricheskaya optimizatsiya i ustoychivost'
dinamiki puchkov $[$Structural-parametrical optimization and
stability of beam dynamics$]$}. Kiev, Naukova dumka Publ., 1985,
304~p. (In Russian)

29. {Nikol'skiy M. S., Belyaevskih E. A.} Printsip maksimuma L. S.
Pontryagina dlya nekotoryh zadach optimal'nogo upravleniya
puchkami trayektoriy $[$L.~S.~Pontryagin maximum principle for
some problems of optimal control of trajectory bundles$]$. {\it
Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2018, vol.~14, iss.~1,
pp.~59--68. (In Russian)

\vskip 1.5mm

Received:  January 06, 2019.

Accepted: March 15, 2019.


\vskip5mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm \textit{Oleg I. Drivotin} --- Dr. Sci. in Physics and
Mathematics, Professor; drivotin@yandex.ru \par
%

}
