{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\it Якушев В. В.} Точное земледелие: теория и~практика. СПб.:
Агрофиз. науч.-исслед. ин-т, 2016. 364 с.

2. {\it Chen N., Zhang X., Wang C.}
Integrated open geospatial web service enabled cyber-physical in\-formation infrastructure for precision agriculture monitoring // Comput. Electron. Agric. 2015. Vol.~111. P. 78–91.

3. {\it Hohn M. E.}
Geostatistics and petroleum geology. 2nd ed. Dordrecht, The Netherlands: Springer, Science+Business Media, 1999. 235 p.

4. {\it Gomez J. L., Pastoriza F. T., Alvarez E. G., Oller P. E.}
Comparison between geostatistical interpolation and numerical weather model predictions for meteorological conditions mapping // Infrastructures. 2020. Vol. 5. N 15. DOI:10.3390/infrastructures5020015

5. {\it Paz-Ferreiro J., Vazquez E. V., Vieira S. R.}
Geostatistical analysis of a geochemical dataset // Bragantia. 2009. Vol. 69. P. 121--129.

6. {\it Olthoff A. E., Gomez C., Alday J. G., Martinez-Ruiz C.}
Mapping forest vegetation patterns in an Atlantic---Mediterranean transitional area by integration of ordination and geostatistical techniques // Journal of Plant Ecology. 2018. Vol. 11. Iss. 1. P. 114--122.

7. {\it Якушев В. П., Жуковский Е. Е., Петрушин А. Ф., Якушев В. В.}
Вариограммный анализ пространственной неоднородности сельскохозяйственных полей для целей точного земледелия: метод. пособие. СПб.: Агрофиз. науч.-исслед. ин-т, 2010. 52~с.

8. {\it Cambardella C. A., Moorman T. B., Novak J. M., Parkin T. B., Karlen D. L., Turko R. F.} et al.
 Field-scale variability of soil properties in central Iowa soils // Soil Science Society of America Journal. 1994. Vol. 58. P. 1501--1511.

9. {\it Jiang Q. X., Fu Q., Wang Z. L.}
Research on precision irrigation in Western Semiarid Area of Heilonngjiang province in China based on GIS //  Computer and Computing Technologies in Agriculture. 2008. Vol. 1. P. 359--370.

10. {\it Moustafa M. M., Yomota A.}
Use of a covariance variogram to investigate influence of subsurface drainage on spatial variability of soil-water properties // Agricultural Water Management. 1998. Vol. 37. P. 1--19.

11. {\it Якушев В. П., Буре В. М., Митрофанова О. А., Митрофанов
Е. П.} Применение методов геостатистики для анализа
целесообразности перехода к~технологиям дифференцированного
внесения агрохимикатов // Вестн. С.-Петерб. ун-та. Прикладная
математика. Информатика. Процессы управления. 2020. Т. 16. Вып. 1.
С. 31--40.

12. {\it Демьянов~В.~В., Савельева~Е.~А.} Геостатистика: теория
и~практика. М.: Ин-т проблем безопасности развития атомной
энергетики РАН; Наука, 2010. 327~с.

13. {\it Li Z., Zhang X., Clarke K. C., Liu G., Zhu R.}
An automatic variogram modeling method with high reliability fitness and estimates // Computers and Geosciences. 2018. Vol. 120. P. 48--59.


\vskip 2mm%1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 3 марта 2020 г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Якушев Виктор Петрович}  --- акад. РАН, д-р с.-х. наук; vyakushev@agrophys.com

\vskip2mm \textit{Буре Владимир Мансурович}  --- д-р техн. наук, проф.; vlb310154@gmail.com

\vskip2mm \textit{Митрофанова Ольга Александровна}  --- мл. науч. сотр.; omitrofa@gmail.com

\vskip2mm \textit{Митрофанов Евгений Павлович}  --- мл. науч.
сотр.; mjeka@bk.ru


}
