
{\small

\vskip4.5%6
mm \noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. \textit{Chang S. L., Piraveenan M.,  Pattison P., Prokopenko M.} Game theoretic modelling of in\-fec\-tious disease dynamics and intervention methods~// Journal of Biological Dynamic.  2020. P.~57--89.\\
https://doi.org/10.1080/17513758.2020.1720322
   	
2. \textit{Sokolov S. V., Sokolova A. L.} HIV incidence in Russia: SIR epidemic model-based analysis~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2019. Т.~15. Вып.~4. С.~616--623. %\\
 https://doi.org/10.21638/11702/spbu10.2019.416
	
3. \textit{Захаров В. В., Балыкина Ю. Е.} Прогнозирование динамики эпидемии коронавируса (COVID-19) на основе метода прецедентов~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~3. С.~249--259. \\ https://doi.org/10.21638/11701/spbu10.2020.303
   	
4. \textit{Smith D. L., Battle K. E., Hay S. I., Barker C. M., Scott~T.~W., McKen\-zie~F.~E.} Ross, McDonald, and a theory for the dynamics and control of mosquito-transmitted pathogens~// PLoS Pathog. 2012. Vol.~8. N~4. Art. no.~e1002588. %\\
 https://doi.org/10.1371/journal.ppat.1002588

5. \textit{McDonald G.} Epidemiological basis of malaria control~// Bull. World Health Organ. 1956. Vol.~15. N~3--5. P.~613--626.
		
6. \textit{Feng Z., Hernandez V.} Competitive exclusion in a vector-host model for the dengue fever~// Math. Biol. 1997. P.~523--544.
	
7. \textit{Qiu Z.} Dynamical behavior of a vector-host epidemic model with demographic structure~// Com\-pu\-ters $\&$ Mathematics with Applications.  2008. Vol.~56. N~12. P.~3118--3129.
	
8. \textit{Sirbu A., Lorento V., Servedio V., Tria F.} Opinion dynamics: models, extensions and external effects~// Physics and Society. 2016. Vol.~5. P.~363--401.
	
9. \textit{Bushman M., Antia R., Udhayakumar V., de Roode J. C.} Within-host competition can de\-lay evo\-lu\-tion of drug resistance in malaria~// PLoS Biol. 2018. Vol.~16. N~8. Art. no.~e2005712.\\
\url{https://doi.org/10.1371/journal.pbio.2005712}
		
10. \textit{Turner A., Jung C., Tan P., Gotika S.,  Mago V.} A comprehensive model of spread of malaria in humans and mosquitos~// SoutheastCon. 2015. P.~1--6. %\\
https://doi.org/10.1109/SECON.2015.7132968	
	
11. \textit{Hong H., Wang N., Yang J.} Implications of stochastic transmission rates for managing pandemic risks~// Rev. Financ. Stud. 2021.  https://doi.org/10.1093/rfs/hhaa132
	
12. \textit{G\’omez-Hern\’andez E. A., Ibarg\”uen-Mondrag\’on E.} A two patch model for the popula\-tion dynamics of mosquito-borne diseases~// J. Phys.: Conference Series. 2019. Vol.~1408. N~1. Art. no.~012002.
	
13. \textit{Kamgang J. C., Thron C. P.} Analysis of malaria control measures’ effectiveness using multistage vector model~// Bull. Math. Biol. 2019.  Vol.~81. P.~4366--4411.
	
14. \textit{Александров А. Ю.} Условия перманентности моделей динамики популяций с переключениями и запаздыванием~// Вестник Санкт-Петербургского университета. Прикладная математика. Информатика. Процессы управления. 2020. Т.~16. Вып.~2. С.~88--99. \\ https://doi.org/10.21638/11701/spbu10.2020.201
		
15.  \textit{Wiwanitkit V.} Unusual mode of transmission of dengue~// J. Infect. Dev. Ctries. 2009. Vol.~4. P.~051--054. https://doi.org/10.3855/jidc.145
		
16. \textit{Ndiaye S. M., Lam M., Mansal F.} Mod\’elisation d’un syst\`eme de p\^echerie avec maladie~// Ba\-che\-lor Thesis. 2017. P.~3--10.
	
17.	\textit{Aldila D., Seno H. A.} Population dynamics model of mosquito-borne disease trans\-mis\-sion, focusing on mosquitoes’ biased distribution and mosquito repellent use~// Bull. Math. Biol. 2019. Vol.~81. P.~4977--5008.
	
18. \textit{Lipsitch M., Cohen T., Cooper B., Robins J. M., Ma~S., Ja\-mes~L.,  Go\-pa\-lak\-rish\-na~G., Chew~S.~K., Tan~C.~C.,  Sa\-mo\-re~M. H., Fis\-man~D., Mur\-ray~M.} Transmission dynamics and control of severe acute respiratory syndrome~// Science. 2003. Vol.~300. P.~1966--1970.
	
19. \textit{Britton T.} Stochastic epidemic models: A survey~// Mathematical Biosciences. 2010. Vol.~225. Iss.~1. P.~24--35.

20. \textit{Lashari A. A., Zaman G.} Global dynamics of vector-borne diseases with horizontal transmission in host population~// Computers $\&$ Mathematics with Applications. 2011. Vol.~61. Iss.~4. P.~745--754.

21. \textit{Arquam M., Anurag S., Cherifi H.} Impact of seasonal conditions on vector-borne epidemiological dynamics~// IEEE Access. 2020. Vol.~8. P.~94510--94525.
	
22. \textit{Kim M., Paini D., Jurdak R.} Modeling stochastic processes in disease spread across a he\-te\-ro\-ge\-neous social system~// Proceedings of the National Academy of Sciences. 2019.  Vol.~116. N~2. P.~401--406.
	
23. \textit{Derdei B.} \'Etude de mod\`eles \'epid\'emiologiques: Stabilit\'e, observation et estimation de pa\-ra\-m\`et\-res~// HAL theses. 2013. P. 7--11. URL:\\ https://tel.archives-ouvertes.fr/tel-00841444/file/BicharaPhDThesis.pdf (дата обращения: 15.04.2022).
	
24. \textit{Hyman J. M., Li J.} An intuitive formulation for the reproductive number for the spread of diseases in heterogeneous populations~// Mathematical Biosciences. 2000. Vol.~167. N~1. P.~65--86.

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 28 апреля 2022~г.

Cтатья принята к~печати 5 мая 2022~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Ндиайе Серинь Моду} --- аспирант; mamounepourtoi@gmail.com

\vskip2mm \textit{Парилина Елена Михайловна} --- д-р физ.-мат. наук, проф.; e.parilina@spbu.ru


}
