
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf An epidemic model of malaria without and with vaccination.\\ Pt 1. A model of malaria without vaccination%$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it S. M. Ndiaye, E. M. Parilina%
%, I.~ќ. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ –абота выполнена в рамках государственного %
%задани€ по теме N 0827-2018-0003 Ђ‘ундаментальные исследовани€ %
%океанологических процессов, определ€ющих состо€ние и эволюцию морской %
%среды под вли€нием естественных и антропогенных факторов, на основе %
%методов наблюдени€ и моделировани€ї.\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Ndiaye S. M., Parilina E. M. An epidemic model of malaria without and with vaccination. Pt 1. A model of malaria without vaccination. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum, pp.~\pageref{p7}--\pageref{p7e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum07 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent We propose a mathematical model of the malaria epidemic in the human population (host), where the transmission of the disease is produced by a vector population (mosquito) known as the malaria mosquito. The malaria epidemic model is defined by a system of ordinary differential equations. The host population at any time is divided into four sub-populations: susceptible, exposed, infectious, recovered. Sufficient conditions for stability of equilibrium without disease and endemic equilibrium are obtained using the Lyapunov's function theory. We define the reproductive number characterizing the level of disease spreading in the human population. Numerical modeling is made to study the influence of parameters on the spread of vector-borne disease and to illustrate theoretical results, as well as to analyze possible behavioral scenarios.\\[1mm]
\textit{Keywords}: epidemic model, human population, malaria, sub-populations, modification epidemic SEIR model, reproductive number, endemic equilibrium.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Chang S. L., Piraveenan M.,  Pattison P., Proko\-pen\-ko~M. Game theoretic modelling of in\-fec\-tious disease dynamics and intervention methods. \textit{Journal of Biological Dynamic}, 2020, pp.~57--89.\\
https://doi.org/10.1080/17513758.2020.1720322
	
2. Sokolov S. V., Sokolova A. L. HIV incidence in Russia: SIR epidemic model-based analysis. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2019, vol.~15, iss.~4, pp.~616--623. %\\
https://doi.org/10.21638/11702/spbu10.2019.416
	
3. Zakharov V. V., Balykina Yu. E. Prognozirovanie dinamiki epidemii koronavirusa (COVID-19) na osnove metoda precedentov [Predicting the dynamics of the coronavirus (COVID-19) epidemic based on the case-based reasoning approach]. \textit{Vestnik of Saint~Pe\-ters\-burg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~3, pp.~249--259.\\ https://doi.org/10.21638/11701/spbu10.2020.303 (In Russian)
	
4. Smith D. L, Battle K. E., Hay S. I., Barker C. M., Scott~T.~W., Mc\-Ken\-zie~F.~E. Ross, McDonald, and a theory for the dynamics and control of mosquito-transmitted pathogens. \textit{PLoS Pathog.}, 2012, vol.~8, no.~4, art. no.~e1002588. %\\
 https://doi.org/10.1371/journal.ppat.1002588

5. McDonald G. Epidemiological basis of malaria control. \textit{Bull. World Health Organ.}, 1956, vol.~15, no.~3--5, pp.~613--626.
		
6. Feng Z., Hernandez V. Competitive exclusion in a vector-host model for the dengue fever. \textit{Math. Biol.}, 1997, pp.~523--544.
	
7. Qiu Z. Dynamical behavior of a vector-host epidemic model with demographic structure. \textit{Com\-pu\-ters $\&$ Mathematics with Applications}, 2008, vol.~56, no.~12, pp.~3118--3129.
	
8. Sirbu A., Lorento V., Servedio V., Tria F. Opinion dynamics: models, extensions and external effects. \textit{Physics and Society}, 2016, vol.~5, pp.~363--401.
	
9. Bushman M., Antia R., Udhayakumar V., de Roode J. C. Within-host competition can delay evolution of drug resistance in malaria. \textit{PLoS Biol}., 2018, vol.~16, no.~8, art. no.~e2005712. \\ https://doi.org/10.1371/journal.pbio.2005712
		
10. Turner A., Jung C., Tan P., Gotika S.,  Mago V. A comprehensive model of spread of malaria in humans and mosquitos. \textit{SoutheastCon}, 2015, pp.~1--6. %\\
 https://doi.org/10.1109/SECON.2015.7132968	
	
11. Hong H., Wang N., Yang J. Implications of stochastic transmission rates for managing pandemic risks. \textit{Rev. Financ. Stud.}, 2021. %\\
https://doi.org/10.1093/rfs/hhaa132
	
12. G\Тomez-Hern\Тandez E. A., Ibarg\Фuen-Mondrag\Тon E. A two patch model for the popula\-tion dynamics of mosquito-borne diseases. \textit{J. Phys.: Conference Series,} 2019, vol.~1408, no.~1, art. no.~012002.
	
13. Kamgang J. C., Thron C. P. Analysis of malaria control measuresТ effectiveness using multistage vector model. \textit{Bull. Math. Biol.},  2019, vol.~81, pp.~4366--4411.
	
14. Aleksandrov A. Yu. Usloviia permanentnosti modelei dinamiki populiatsii s perekliu\-che\-niia\-mi i zapazdyvaniem [Permanence conditions for models of population dynamics with switches and delay]. \textit{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~2, pp.~88--99. %\\
https://doi.org/10.21638/11701/spbu10.2020.201  (In Russian)
	
15.  Wiwanitkit V. Unusual mode of transmission of dengue. \textit{J. Infect. Dev. Ctries}, 2009, vol.~4, pp.~051--054. %\\
https://doi.org/10.3855/jidc.145
		
16. Ndiaye S. M., Lam M., Mansal F. Mod\Тelisation dТun syst\`eme de p\^echerie avec maladie. \textit{Bachelor Thesis}, 2017, pp. 3--10.
	
17.	Aldila D., Seno H. A. Population dynamics model of mosquito-borne disease trans\-mis\-sion, focusing on mosquitoesТ biased distribution and mosquito repellent use. \textit{Bull. Math. Biol.}, 2019, vol.~81, pp.~4977--5008.
	
18. Lipsitch M., Cohen T., Cooper B., Robins J. M., Ma~S., Ja\-mes~L.,  Go\-pa\-lak\-rish\-na~G., Chew~S.~K., Tan~C.~C.,  Sa\-mo\-re~M. H., Fis\-man~D., Mur\-ray~M. Transmission dynamics and control of severe acute respiratory syndrome. \textit{Science}, 2003, vol.~300, pp.~1966--1970.
	
19.  Britton T. Stochastic epidemic models: A survey. \textit{Mathematical Biosciences}, 2010, vol.~225, iss.~1, pp.~24--35.

20. Lashari A. A., Zaman G. Global dynamics of vector-borne diseases with horizontal transmission in host population. \textit{Computers $\&$ Mathematics with Applications}, 2011, vol.~61, iss.~4, pp.~745--754.

21. Arquam M., Anurag S., Cherifi H. Impact of seasonal conditions on vector-borne epidemiological dynamics. \textit{IEEE Access}, 2020, vol.~8, pp.~94510--94525.
	
22. Kim M., Paini D., Jurdak R. Modeling stochastic processes in disease spread across a he\-te\-ro\-ge\-neous social system. \textit{Proceedings of the National Academy of Sciences}, 2019, vol.~116, no.~2, pp.~401--406.
	
23. Derdei B. \'Etude de mod\`eles \'epid\'emiologiques: Stabilit\'e, observation et estimation de param\`etres. \textit{HAL theses}, 2013, pp.~7--11. Available at:\\
https://tel.archives-ouvertes.fr/tel-00841444/file/BicharaPhDThesis.pdf (accessed: April 15, 2022).
	
24. Hyman J. M., Li J. An intuitive formulation for the reproductive number for the spread of diseases in heterogeneous populations. \textit{Mathematical Biosciences}, 2000, vol.~167, no.~1, pp.~65--86.


\vskip1.5mm Received:  April 28, 2022.

Accepted: May 05, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Serine Modou Ndiaye} --- Postgraduate Student; mamounepourtoi@gmail.com \par
%
\vskip2mm \textit{Elena M. Parilina} --- Dr. Sci. in Physics and Mathematics, Professor; e.parilina@spbu.ru \par
%
%
}
