
{\small

\vskip6mm
%\newpage
\noindent \textbf{Литература}

}

\vskip2.5%3
mm

{\footnotesize

1. \textit{Jansson~M., Wahlberg~B.} A linear regression approach to state-space subspace system identification // Signal Processing. 1996. Vol.~2. P.~103--129. https://doi.org/10.1016/0165-1684(96)00048-5

	2. \textit{Herceg~S., Ujevic~Z., Bolf~A.\:N.} Development of soft sensors for isomerization process based on support vector machine regression and dynamic polynomial models // Chemical Engineering Research and Design. 2019. Vol.~149. P.~95--103.
https://doi.org/10.1016/j.cherd.2019.06.034
	

	3. \textit{Dette~H.} Optimal designs for identifying the degree of a polynomial regression // Annals of Statistics. 1995. Vol.~23. N~4. P.~1248--1266. https://doi.org/10.1214/aos/1176324708
	
	4. \textit{Kim~B., Ko~Ch.-Y., Wong~N.} Tensor network subspace identification of polynomial state space models // Automatica. 2018. Vol.~95. P.~187--196.
	 https://doi.org/10.1016/j.automatica.2018.05.015
	
	5.	\textit{Blondel~M., Ishihata~M., Fujino~A., Ueda~N.} Polynomial networks and factorization machines: New insights and efficient training algorithms // Proceedings of ICML 2016. New York City, 2016. P.~850--858.
	
	6. \textit{Blondel~M., Niculae~V., Otsuka~T., Ueda~N.}  Multi-output polynomial networks and factorization machines //  Proceedings of the 31$^{\rm st}$~International Conference on Neural Information Processing Systems (NIPS'17). Long Beach, 2017. P.~3351--3361.
	
	7. \textit{Chen~T., Guestrin~C.} XGBoost: A Scalable tree boosting system // Proceedings of the 22$^{\rm nd}$~ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD'16). San Francisco, 2016. P.~785--794. https://doi.org/10.1145/2939672.2939785
	
	8.	\textit{Hornik~K., Stinchcombe~M., White~H. } Multilayer feedforward networks are universal ap\-pro\-xi\-ma\-tors // Neural Networks. 1989. Vol.~2. P.~359--366.
	
	9.	\textit{Rao~S., Sethuraman~S., Ramamurthi~V.} A recurrent neural network for nonlinear time series prediction: a comparative study // IEEE 1992 Workshop on Neural Networks for Signal Processing (NNSP'92). Helsingoer, 1992. P.~531--539.
	
	10.	\textit{Kaheman~K., Kutz~J.\:N., Brunton~S.\:L.} SINDy-PI: a robust algorithm for parallel implicit sparse identification of nonlinear dynamics // Proceedings of the Royal Society A. 2020. Vol.~476. N~2242. Art. N~20200279.
	
	11.	\textit{Brunton~S.\:L., Joshua~L.\:P., Kutz~N.} Discovering governing equations from data by sparse identification of nonlinear dynamical systems // Proceedings of the National Academy of Sciences. 2016. Vol.~113. N~15. P.~3932--3937.
	
	12. \textit{Andrianov~S.\:N.} Dynamical modeling of control systems for particle beams. St~Petersburg: Publishing House of Saint Petersburg State University, 2004. 368~p.
	
	13. \textit{Dragt~A.} Lie methods for nonlinear dynamics with applications to accelerator physics. 2011. URL: inspirehep.net/record/955313/files/TOC28Nov2011.pdf (дата обращения: 10.08.2022).

	14. \textit{Andrianov~S.} Symbolic computation of approximate symmetries for ordinary differential equations // Mathematics and Computers in Simulation. 2001. Vol.~57. N~3--5. P.~147--154.

	15. \textit{Andrianov~S.} A matrix representation of the Lie transformation // Proceedings of the Abstracts of the International Congress on Computer Systems and Applied Mathematics. St~Petersburg, 1993. Vol.~14. P.~19--23.

	16. \textit{Ivanov~A., Golovkina~A., Iben~U.} Polynomial neural networks and taylor maps for dynamical systems simulation and learning // 24$^{\rm th}$~European Conference on Artificial Intelligence, including 10$^{\rm th}$ Conference on Prestigious Applications of Artificial Intelligence, PAIS 2020. Proceedings. IOS Press, 2020. P.~1230--1237. (Frontiers in Artificial Intelligence and Applications). https://doi.org/10.3233/FAIA200223
	
	17. \textit{Golovkina~A., Kozynchenko~V., Kulabukhova~N.} Reconstruction and identification of dynamical systems based on taylor maps // Computational Science and its Applications --- 21$^{\rm st}$~ International Conference, Proceedings. Pt VIII. Switzerland: Springer Nature, 2021. P. 360--369. (Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial Intelligence and Lecture Notes in Bioinformatics)). https://doi.org/10.1007/978-3-030-87010-2\_26
	
	18. \textit{Golovkina~A.\:G., Kozynchenko~V.\:A., Kulabukhova~N.\:V.} Reconstruction of ordinary differential equations from irregularly distributed time-series data // Proceedings of the 9$^{\rm th}$~International Conference ``Distributed Computing and Grid Technologies in Science and Education'' (GRID'2021). Dubna, Russia, July 5--9, 2021. Vol.~3041. P.~342--347.
	
	19. \textit{Головкина А. Г., Ганаева Д. Д.} Метод реконструкции нелинейных динамических систем по временным рядам // Процессы управления и устойчивость. 2022. Т.~9. №~1. С.~197--201.
	
	20. \textit{Клименко~И.\:С.} Реализация метода матричных отображений для решения системы дифференциальных уравнений // Процессы управления и устойчивость. 2022. Т.~9. №~1. С.~53--57.
	
	21. \textit{Cartwright~M.\:L.} Van der Pol’s equation for relaxation oscillations //
	Contributions to the theory of nonlinear oscillations. II. Princeton Ann. Math. Stud. Princeton: Princeton University Press,  1952. P.~3--18.
	
	22.\textit{ Abrevaya~G., Rish I., Aravkin A. Y., Cecchi G.,  Kozloski J., Polosecki P., Zheng P., Daw\-son~S.~R., Rhee J., Cox D.} Learning nonlinear brain dynamics: Van der Pol Meets LSTM //	bioRxiv 330548. https://doi.org/10.1101/330548
	
	23. LSODA. Ordinary differential equation solver for stiff or non-stiff system (September 2005). URL: http://www.nea.fr/abs/html/uscd1227.html (дата обращения: 10.08.2022).

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 11 августа 2022~г.

Cтатья принята к~печати 1 сентября 2022~г.

\vskip4.5%6
mm
К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:


\vskip1.8%2
mm \textit{Головкина Анна Геннадьевна} --- канд. физ.-мат. наук, доц.; a.golovkina@spbu.ru

\vskip1.8%2
mm \textit{Козынченко Владимир Александрович} ---  канд. физ.-мат. наук, доц.; v.kozynchenko@spbu.ru

\vskip1.8%2
mm \textit{Клименко Илья Сергеевич} --- магистрант; st062546@student.spbu.ru

}
