
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm


1.  {\it Giri B. C.,   Sharma S.} Optimal ordering policy for an
inventory system with linearly increasing demand and alowable
shortages under two levels trade credit financing // Oper. Res.
Intern.  J. 2016. Vol.~16. P.~25--50.

2. {\it Aggarwal S. P., Jaggi C. K.}  Ordering policies of
deteriorating items under permissible delay in payments// J. Oper.
Res. Soc. 1995. Vol.~46(5). P.~658--662.

3. {\it Dave U.}  Letters and viewpoints on ``economic order
quantity under conditions of permissible delay in payments'' // J.
Oper. Res. Soc. 1985. Vol.~46(5). P.~1069--1070.

4. {\it Chen S. C., Teng J. T., Skouri K.}  Economic production
quantity models for deteriorating items with up-stream full trade
credit and down-stream partial trade credit // Intern. J. Prod.
Econ. 2013. Vol.~155. P.~302--309.

5. {\it Giri B. C., Sharma S.} An integrated inventory model for a
deteriorating item with allowable shortages and credit linked
wholesale price // Optim. Lett. 2015. Vol.~37. P.~624--637.
DOI:10.1007/s11590-014-0810-2.

6. {\it Goyal S. K.} Economic order quantity under conditions of
permissible delay in payments // J. Oper. Res. Soc. 1985.
Vol.~36(4). P.~335--338.

7. {\it Huang Y. F.}    Optimal retailer’s ordering policies in
the EOQ model under trade credit financing  // J. Oper. Res. Soc.
2003. Vol.~54(9). P.~1011--1015.

8. {\it  Huang Y. F., Hsu K. H.}    An EOQ model under retailer
partial trade credit policy in supply chain // Intern. J. Prod.
Econ. 2008. Vol.~112(2). P.~655--664.

9. {\it    Jamal A. M. M., Sarker B. R., Wang S.}    An ordering
policy for deteriorating items with allowable shortages and
permissible delay in payment // J. Oper. Res. Soc. 1997.
Vol.~48(8). P.~826--833.

10. {\it  Khanra S., Ghosh S. K., Chaudhuri K. S.}    An EOQ model
for a deteriorating item with time dependent quadratic demand
under permissible delay in payment //  Appl. Math. Comput. 2011.
Vol.~218(1). P.~1--9.

11. {\it  Khanra S., Mandal B., Sarkar B.}  An inventory model
with time dependent demand and shortages under trade credit policy
// Econ. Model. 2013. Vol.~35. P.~349--355.

12. {\it   Maihami R., Abadi I. N. K.}   Joint control of
inventory and its pricing for non-instantaneously deteriorating
items under permissible delay in payments and partial backlogging
// Math. Comp. Model. 2012. Vol.~55(5–6). P.~1722--1733.

13. {\it  Bure V.~M., ~Karelin V.~V., Polyakova L. N.}
Probabilistic model of terminal services // Applied Mathematical
Sciences.  2016. Vol.~10(39).   P.~1945--1952.

14. {\it   Polyakova L. N., Karelin V. V.} On a continuous method
for minimizing of nonsmooth functions // Intern. conference
stability and control processes  in memory of V.~I.~Zubov (SCP):
Proceedings. Eds:   L.~A.~Petrosyan, A.~P.~Zhabko. Saint
Petersburg: Saint Petersburg University, 2015. P.~338--341.

15. {\it  Polyakova L., Karelin V.} Exact penalty functions method
for solving problems of nondifferentiable optimization //
Cybernetics and physics. 2014. Vol.~3, N~3. P.~124--129.

16. {\it Полякова Л. Н.}   О методе точных штрафных
квазидифференцируемых функций //  Журн. вычисл. математики и
матем. физики.  2001. Т.~41,   №~2. С.~225--238.



\vskip 2mm

{\bf Для цитирования:} {\it Буре В. М., Карелин В. В., Полякова Л.
Н., Ягольник И. В.} Моделирование процесса заказа для
кусочно-линейного спроса с~насыщением // Вестник
Санкт-Петербургского университета. Прикладная математика.
Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02




}
