

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1.  Giri B. C.,   Sharma S. Optimal ordering policy for an
inventory system with linearly increasing demand and alowable
shortages under two levels trade credit financing. {\it Oper. Res.
Intern.  J.}, 2016, vol.~16, pp.~25--50.

2. Aggarwal S. P., Jaggi C. K.  Ordering policies of deteriorating
items under permissible delay in payments. {\it J. Oper. Res.
Soc.}, 1995, vol.~46(5), pp.~658--662.

3. Dave U.  Letters and viewpoints on ``economic order quantity
under conditions of permissible delay in payments''.   {\it J.
Oper. Res. Soc.}, 1985, vol.~46(5), pp.~1069--1070.

4. Chen S. C., Teng J. T., Skouri K.  Economic production quantity
models for deteriorating items with up-stream full trade credit
and down-stream partial trade credit. {\it Intern. J. Prod.
Econ.}, 2013, vol.~155, pp.~302--309.

5. Giri B. C., Sharma S. An integrated inventory model for a
deteriorating item with allowable shortages and credit linked
wholesale price. {\it Optim. Lett.}, 2015, vol.~37, pp.~624--637.
DOI: 10.1007/s11590-014-0810-2.

6. Goyal S. K. Economic order quantity under conditions of
permissible delay in payments. {\it J. Oper. Res. Soc.}, 1985,
vol.~36(4), pp.~335--338.

7. Huang Y. F.    Optimal retailer’s ordering policies in the EOQ
model under trade credit financing. {\it J. Oper. Res. Soc.},
2003, vol.~54(9), pp.~1011--1015.

8. Huang Y. F., Hsu K. H.    An EOQ model under retailer partial
trade credit policy in supply chain. {\it  Intern. J. Prod.
Econ.}, 2008, vol.~112(2), pp.~655--664.

9. Jamal A. M. M., Sarker B. R., Wang S.    An ordering policy for
deteriorating items with allowable shortages and permissible delay
in payment. {\it    J. Oper. Res. Soc.},  1997, vol.~48(8),
pp.~826--833.

10. Khanra S., Ghosh S. K., Chaudhuri K. S.    An EOQ model for a
deteriorating item with time dependent quadratic demand under
permissible delay in payment.  {\it  Appl. Math. Comput.}, 2011,
vol.~218(1), pp.~1--9.

11. Khanra S., Mandal B., Sarkar B.   An inventory model with time
dependent demand and shortages under trade credit policy. {\it
Econ. Model.}, 2013, vol.~35, pp.~349--355.

12. Maihami R., Abadi I. N. K.   Joint control of inventory and
its pricing for non-instantaneously deteriorating items under
permissible delay in payments and partial backlogging. {\it Math.
Comp. Model.}, 2012, vol.~55(5--6), pp.~1722--1733.

13.   Bure~V.~M., ~Karelin V.~V., Polyakova L. N. Probabilistic
model of terminal services. {\it Applied Mathematical Sciences},
2016, vol.~10(39),   pp.~1945--1952.

14.   Polyakova L. N., Karelin V. V. On a continuous method for
minimizing of nonsmooth functions. {\it Intern. Conference
stability and control processes  in memory of
V.~I.~Zubov~$($SCP$)$. Proceedings}. Eds   L.~A.~Petrosyan,
A.~P.~Zhabko. Saint Petersburg, Saint Petersburg University Publ.,
2015, pp.~338--341.

15.   Polyakova L., Karelin V. Exact penalty functions method for
solving problems of nondifferentiable optimization. {\it
Cybernetics and physics}, 2014, vol.~3, no.~3, pp.~124--129.

16. Polyakova L. N.  O metode tochnyh shtrafnyh
kvazidifferenciruemyh funkcij [On the method of exact penalty
quasidifferential functions]. {\it  Journal of Computational
Mathematics and Mathematical Physics}, 2001, vol.~41,   no.~2,
pp.~225--238. (In Russian)



\vskip 2mm

{\bf For citation:}   Bure V. M.,  Karelin V. V., Polyakova  L.
N., Yagolnik I. V. Modeling of the ordering process for
piecewise-linear demand with saturation. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p2}--\pageref{p2e}.
\doivyp/spbu10.\issueyear.\issuenum02



}
