
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm



1. {\it{Quackenbush~J.}} Computational analysis of microarray data
// Nature reviews genetics. 2001. Vol.~2, N~6. P.~418--427.

2. {\it{Shamir~R., Sharan\:R.}} Algorithmic approaches to
clustering gene expression data // Current Topics in Computational
Biology. 2001. URL: http://citeseerx.ist.psu.edu/ (дата обращения:
15.09.2015).

3. {\it{Gordon~A.\:D.}} Classification. Prentice-Hall: Chapman \&
Hall/CRC Monographs on Statistics \& Applied Probability, 1999.
URL: http://www.citeulike.org/ (дата обращения: 20.08.2015).

4. {\it{Jain~A.\:K., Dubes~R.\:C.}} Algorithms for clustering
data. Prentice-Hall: Prentice-Hall, Inc., 1988. URL:
http://dl.acm.org/ (дата обращения: 14.06.2015).

5. {\it{Buhmann~J.}} Data clustering and learning // The Handbook
of Brain Theory and Neural Networks. 1995. P.~278--281.

6. {\it{Chakravarthy~S.\:V., Ghosh~J.}} Scale-based clustering
using the radial basis function network // Neural Networks. IEEE
Transactions. 1996. Vol.~7, N~5. P.~1250--1261.

7. {\it{Gordon~A.\:D.}} Identifying genuine clusters in a
classification // Computational Statistics \& Data Analysis. 1994.
Vol.~18, N~5. P.~561--581.

8. {\it{Hartigan~J.\:A.}} Statistical theory in clustering
// Journal of classification. 1985. Vol.~2, N~1. P.~63--76.


9. {\it{Milligan~G.\:W., Cooper~M.\:C.}} An examination of
procedures for determining the number of clusters in a data set
// Psychometrika. 1985. Vol.~50, N~2. P.~159--179.

10. {\it{Sugar~C.\:A., James~G.\:M.}} Finding the number of
clusters in a dataset // Journal of the American Statistical
Association. 2003. Vol.~98, N~463. P.~750--763.

11. {\it{Tibshirani~R., Walther~G.}} Cluster validation by
prediction strength // Journal of Computational and Graphical
Statistics. 2005. Vol.~14, N~3. P.~511--528.

12. {\it{Hubert~L., Schultz~J.}} Quadratic assignment as a general
data analysis strategy // British journal of mathematical and
statistical psychology. 1976. Vol.~29, N~2. P.~190--241.

13. {\it{Tibshirani~R., Walther~G., Hastie~T.}} Estimating the
number of clusters in a data set via the gap statistic // Journal
of the Royal Statistical Society. Series B (Statistical
Methodology). 2001. Vol.~63, N~2. P.~411--423.

14. {\it{Wishart~D.}} Mode analysis: A generalization of nearest
neighbor which reduces chaining effects~// Numerical taxonomy.
1969. Vol.~76, N~17. P.~282--311.

15. {\it{Hartigan~J.\:A.}} Clustering algorithms. New York: John
Wiley \& Sons, Inc., 1975. URL: http://dl.acm.org/ (дата
обращения: 28.08.2015).

16. {\it{Hartigan~J.\:A.}} Consistency of single linkage for
high-density clusters // Journal of the American Statistical
Association. 1981. Vol.~76, N~374. P.~388--394.

17. {\it{Cuevas~A.,~Febrero~M., Fraiman~R.}} Estimating the number
of clusters // Canadian Journal of Statistics. 2000. Vol.~28, N~2.
P.~367--382.

18. {\it{Cuevas~A., Febrero~M., Fraiman~R.}} Cluster analysis: a
further approach based on density estimation // Computational
Statistics \& Data Analysis. 2001. Vol.~36, N~4. P.~441--459.

19. {\it{Stuetzle~W.}} Estimating the cluster tree of a density by
analyzing the minimal spanning tree of a sample // Journal of
classification. 2003. Vol.~20, N~1. P.~25--47.

20. {\it{Pelleg~D., Moore~A.\:W.}} $X$-means: Extending $K$-means
with Efficient Estimation of the Number of Clusters // ICML. 2000.
P.~727--734.

21. {\it{Volkovich~Z., Brazly~Z., Toledano-Kitai~D., Avros~R.}}
The Hotelling's metric as a cluster stability measure // Computer
modelling and new technologies. 2010. Vol.~14. P.~65--72.

22. {\it{Barzily~Z., Volkovich~Z., Akteke-Ozturk~B.}} On a minimal
spanning tree approach in the cluster validation problem
// Informatica. Lith. Acad. Sci. 2009. Vol.~20, N~2. P.~187--202.

23. {\it{Hamerly~Y.\:F.\:G.}} PG-means: learning the number of
clusters in data // Advances in neural information processing
systems. 2007. Vol.~19. P.~393--400.

24. {\it{Breckenridge~J.\:N.}} Replicating cluster analysis:
Method, consistency, and validity // Multivariate Behavioral
Research. 1989. Vol.~24, N~2. P.~147--161.

25. {\it{Dudoit~S., Fridlyand~J.}} A prediction-based resampling
method for estimating the number of clusters in a dataset //
Genome biology. 2002. Vol.~3, N~7. research0036. URL: http://www.
genomebiology.com/ (дата обращения: 14.06.2015).

26. {\it{Lange~T., Roth~V., Braun~M.\:L., Buhmann~J.\:M.}}
Stability-based validation of clustering solutions~// Neural
computation. 2004. Vol.~16, N~6. P.~1299--1323.

27. {\it{Milligan~G.\:W., Cheng~R.}} Measuring the influence of
individual data points in a cluster analysis~// Journal of
classification. 1996. Vol.~13, N~2. P.~315--335.

28. {\it{Ben-Hur~A., Elisseeff~A., Guyon~I.}} A stability based
method for discovering structure in clustered data // Pacific
symposium on biocomputing. 2002. Vol.~7, N~6. P.~6--17.

29. {\it{Levine~E., Domany~E.}} Resampling method for unsupervised
estimation of cluster validity // Neural computation. 2001.
Vol.~13, N~11. P.~2573--2593.

30. {\it{Fowlkes~E.\:B., Mallows~C.\:L.}} A method for comparing
two hierarchical clusterings // Journal of the American
statistical association. 1983. Vol.~78, N~383. P.~553--569.



}
