

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1. Stevens H. Why outbreaks like coronavirus spread exponentially, and
how to ``flatten the curve''. \textit{The Washington Post}, March 14, 2020. Available at: \\ https://www.washingtonpost.com/graphics/2020/world/corona-simulator/ (accessed: November 15, 2020).

2. Van der Hofstad R.,  Janssen A.\,J.\,E.\,M.,  van Leeuwaarden J.\, S.\,H. Critical epidemics, random graphs and Brownian motion with a parabolic drift. \textit{Advances in Applied Probability}. Cambridge, Cambridge University Press, 2010, pp.~1187--1206.

3. Smith D.,  Moore L. The SIR model for spread of disease --- the differential equation model. \textit{MAA Publications}, Mathematical Association of America Publ., 2004. Available at:\\
https://www.maa.org/press/periodicals/loci/joma/the-sir-model-for-spread-of-disease-the-differential-equation-model (accessed: November 15, 2020).

4. Kato F., Tainaka K., Sone S., Morita S., Iida H., Yoshimura J. Combined effects of prevention and quarantine on a breakout in SIR model. \textit{Scientific Reports}, 2011, vol.~1, iss.~10, pp.~1--5.

5. Bo H., Yimin Z., Yongbin G., Guohui Z., Juan Z., Jin L., Li L. The analysis of isolation measures for epidemic control of COVID-19.
{\it Applied Intelligence}, 2021, vol.~51, pp.~3074--3085.

6. Sokolov S. V., Sokolova A. L. HIV incidence in Russia: SIR epidemic model-based analysis. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Sciences. Control Processes}, 2019, vol.~15,
iss.~4, pp.~616--623.
https://doi.org/10.21638/11701/spbu10.2019.416

7. Zakharov V.~V., Balykina Yu.~E.,  Balansovaya model' epidemii COVID-19 na osnove procentnogo prirosta [Balance model of the COVID-19 epidemic based on percentage growth]. {\it Informatika i avtomatizaciya}
[{\it Informatics and Automation}], 2021, vol.~20(5), pp.~1034--1064.\\ https://doi.org/10.15622/20.5.2  (In Russian)

8.  Sahneh F. D.,   Scoglio C.  Epidemic spread in human networks. \textit{2011 50$^{th}$ IEEE Conference on Decision and Control and European Control Conference}. Orlando, Florida, USA, 2011, pp.~3008--3013.

9. Youssef M., Scoglio C. An individual-based approach to SIR epidemics in contact networks. \textit{J. of Theoretical Biology}, 2011, vol.~283, pp.~136--144.

10. Pereira T., Young L. Control of epidemics on complex networks:
Effectiveness of delayed isolation. \textit{Phys. Rev. E}, 2015, vol.~92, iss.~2, pp.~022822(4).

11.  Alvarez-Zuzek L.~G.,  Stanley H.~E., Braunstein
L.~A. Epidemic model with isolation in multilayer networks. \textit{Sci.  Rep.}, 2015, vol.~5. https://doi.org/10.1038/srep12151

12. Albert R., Barab\'asi A. Statistical mechanics of complex networks. \textit{Rev. Mod. Phys.}, 2002, vol.~74, iss.~1, pp.~47--97.

13. Holme P., Saram\"{a}ki J. Temporal networks. \textit{Physics Reports}, 2012, vol.~519, pp.~97--125.

14. Mikheev V. IsolationSIRonBarabasi. \textit{GitHub repository}, GitHub, 2021. Available at: \\ https://github.com/keshmish/IsolationSIRonBarabasi.git (accessed: November 15, 2020).

15. Backer J., Klinkenberg D., Wallinga J. Incubation period of 2019 novel coronavirus (2019--$n$CoV) infections among travellers from Wuhan, China, January 20--28, 2020. \textit{Euro Surveill}, 2020, vol.~25, iss.~5, no.~2000062. https://doi.org/10.2807/1560-7917.ES.2020.25.5.2000062

16. Woelfel R., Corman V., Guggemos W. Clinical presentation and virological assessment of hospitalized cases of coronavirus disease 2019 in a travel-associated transmission cluster.
\textit{medRxiv}, 2020, no.~20030502. https://doi.org/10.1101/2020.03.05.20030502

17.  Liu Y.,  Gayle A. A.,  Wilder-Smith A.,  Rocklov J.
The reproductive number of COVID-19 is higher compared to SARS coronavirus. \textit{J. of Travel Medicine}, 2020, vol.~27,  no.~2.\\
https://doi.org/10.1093/jtm/taaa021

18. Kelly L. \textit{Kansas Governor Stay at home order N 20-18}. Manhattan,
Kansas State Government Publ., 2020. Available at:
https://governor.kansas.gov/wp-content/uploads/2020/04/20-18-Executed.pdf
 (accessed: November 15, 2020).


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 20, 2021.

Accepted: February 01, 2022.

\vskip 4.5mm%6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm
 \textit{Sergey E. Miheev} --- Dr. Sci. in Physics and Mathematics, Associate Professor; him2@mail.ru \par


\vskip 2mm
 \textit{Vikenty S. Mikheev} --- PhD in Physics and Mathematics;
vikentym@ksu.edu \par
%
%
}
