
{\normalsize

\vskip 6mm

\noindent{\bf Sensitivity analysis of the gas transmission
offshore pipeline model\\ to variations of the model parameters}

}

\vskip 2mm

{\small

\noindent{\it G. I. Kurbatova, N. N. Ermolaeva%$\,^1$%
%, I.~Œ. Famylia%$\,^2$%
%, I.~Œ. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,
St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm


\noindent \textbf{For citation:}  Kurbatova G.\,I., Ermolaeva
N.\,N. Sensitivity analysis of the gas transmission offshore
pipeline model to variations of the model parameters. {\it Vestnik
of Saint~Petersburg University. Applied Mathematics. Computer
Science. Control Processes},\,\issueyear,
vol.~15,~iss.~\issuenum,~pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Basic approaches to defining the coefficient
of hydraulic resistance and the   total heat transfer coefficient between
the gas and the ambient in the model of an unsteady nonisothermal gas
flow through an offshore gas-pipelines are considered. Model sensitivity
to variations of these coefficients is illustrated by the charts,
demonstrating influence of these coefficients on the basic flow
characteristics. The coefficient of hydraulic resistance and the
heat transfer coefficient calculations for one from test variant
of gas transmission are given. The calculation method of these
parameters from the experimental date, enabling to provide the validity
of model of the unsteady nonisothermal gas flow through
a sea gas pipeline when calculating certain pipeline is suggested.\\[1mm]
\textit{Keywords}: offshore gas-pipelines, gas transmission,
dynamic of glaciation, nonstationary flow, identification of
friction factors and of sensitivity analysis of the  gas
transmission offshore  pipeline model to variations of the model
parameters,   sensitivity analysis of the model.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Kurbatova G.~I., Ermolaeva N.~N. Qvaziodnomernaja
nestacionarnaja model processov v morskih gasoprovodah [Quasi
one-dimensional non-stationary model of the processes in the sea
gas pipelines]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer science. Control
processes}, 2015, iss.~3, pp.~55--66. (In Russian)


2. Kurbatova G.~I., Ermolaeva N.~N. The mathematical models of gas
transmission at hyper-pressure. {\it Applied Mathematical
Sciences}, 2014,  vol.~8, no.~124, pp.~6191--6203.

3. Ermolaeva N.~N. Computer modelling of the sea gas-pipeline
glaciation and of the flow characteristics behavior in unsteady
regimes.   {\it Vestnik of Saint Petersburg University. Series~10.
Applied Mathematics. Computer science. Control processes}, 2016,
iss.~4, pp.~75--85.

4.  Kurbatova~G.~I.,  Popova~E.~A.,  Filippov~B.~V. at all. {\it
Modeli morskikh gazoprovodov} [{\it Models of sea gas-pipelines}].
Saint Petersburg, Saint Petersburg University Publ.,  2005, 156~p.
(In Russian)

5.   Ermolaeva N.~N., Kurbatova~G.~I., Klemeshev V.~A. {\it
Svidetel'stvo ob ofitsial'noy registratsii programmy dlya EVM
no.~2017610826 ``Programma dlja rascheta harakteristik potoka
neustanovivshihsja techenii mnogo-komponentnoy smesi gasov po
morskim gasoprovodam v severnih morjah'' (SGPITM)} [{\it
Certificate of Official Registration of Computer Programs
N~2017610826 ``The program for calculating the flow
characteristics  of unsteady flows of a multicomponent gas mixture
through the offshore gas pipelines in the northern seas''
(SGPITM)}]. Date of receipt: 31.01.2017. Date of state
registration in the Register of computer programs: 23.03.2017. (In
Russian)

6.   Ermolaeva N.~N., Kurbatova~G.~I., Klemeshev V.~A. {\it
Svidetel'stvo ob ofitsial'noy registratsii programmy dlya EVM
no.~2017610817  ``Programma dlja rascheta harakteristik
ustanovivshihsja techenii mnogokomponentnoy smesi gasov v morskih
gasoprovodah pri sverhvisokih davlenijah s uchetom reljefa
trassi'' (SGTM)} [{\it Certificate of Official Registration of
Computer Programs N~2017610817  ``The program for calculating the
characteristics of steady-state flows of a multicomponent mixture
of gases in offshore gas pipelines at ultrahigh pressures, taking
into account the route relief'' (SGTM)}]. Date of receipt:
31.01.2017. Date of state registration in the Register of computer
programs: 23.03.2017. (In Russian)


7.   Ermolaeva N.~N., Kurbatova~G.~I.,Klemeshev V.~A., Mikova
V.~V. {\it Svidetel'stvo ob ofitsial'noy registratsii programmy
dlya EVM no.~2017610801   ``Programma dlja rascheta dinamiki
narastanija morskogo lda na ploskih i cillindricheskih
mnogosloynih poverhnostjah v severnih morjah'' (LED)} [{\it
Certificate of Official Registration of Computer Programs
N~2017610801 ``The program for calculating the dynamics of sea ice
growth on flat and cylindrical multilayer surfaces in the northern
seas'' (LED)}]. Date of receipt: 31.01.2017. Date of state
registration in the Register of computer programs: 23.03.2017. (In
Russian)

8.   Ermolaeva N.~N. Nestacionarnie modeli teploobmena i
transportirovki gasa po morskim gasoprovodam [Non-stationary
models of the heat exchange and the gas transportation through a
sea gas pipeline]. {\it Trudi Karel. nauch. centra RAN. Seria
Matematicheskoje modelirivanie i informacionnie tehnologii}, 2016,
iss.~8,  pp.~3--10.  (In Russian)

9.    Kurbatova G.~I., Ermolaeva N.~N. The models of heat transfer
in a sea gas-pipeline at the glaciation. {\it Mechanics ---
Seventh Polyakhov's Reading}, 2015 Intern. Conference on,  2015,
pp.~1--3.\newpage


10. Reid R. C., Prausnitz J. M., Sherwood Th. K. {\it The
properties of gases and liquids}. New York, St. Louis, San
Francisco, MeGraw-Hill  Book  Company Publ., 1977,  560~p. (Rus.
ed.: Reid~R., Prausnitz~J., Sherwood~Th. {\it Svoistva gazov i
ghidkostey.} Leningrad, Chemistry Publ., 1982, 592~p.)


11.   Haaland S. Simple and explicit formulas for the  friction
factor in turbulent pipe  flow.
 {\it   J. Fluids Engineering},  1983,  vol.~105,   pp.~89--90.

12.  {\it STO Gasprom  2-3.5-051-2006.  Normi tehnologicheskogo
proektirovania magistralnih gaso\-pro\-vo\-dov} [{\it Standards of
technological design of gas pipelines}]. Vved.    2006-07-03.
Moscow, ZAO Izd. Dom ``Poligrafiya'', 2006, 196~p. (In Russian)

13. Lee A.~L. , Gonzalez M.~H.,  Eakin B.~E. The viscosity of
natural gases.  {\it  Journal of Petroleum Technology},  1966,
vol.~18, no.~8,  pp.~997--1000.

14.  Schlichting H.   {\it Boundary-layer theory}.   New York,
McGraw-Hill Publ., 1955, 535~p. (Rus. ed.: Schlichting H. {\it
“ÂÓria pogranichnogo sloya.} Moscow, Nauka Publ., 1969, 743~p.)


15.  Kanibolotskiy M.~A., Babe G.~D., Bondarev E.~A., Voyevodin
A.~F. {\it Identifikatsiya modeley gidravliki} [{\it
Identification of hydraulic models}].   Novosibirsk, Nauka Publ.,
1980, 160~p. (In Russian)

16.  Kanibolotskiy M.~A., Vasil'yev O.~F., Bondarev E.~A.,
Voyevodin A.~F. {\it Neizotermicheskoye techeniye gaza v trubakh}
[{\it Non-isothermal flow of gas in the pipes}]. Novosibirsk,
Nauka Publ., 1978, 128~p. (In Russian)

17.  Kurbatova G.~I., Ermolaeva N.~N.  Parametricheskaya
identifikatsiya modeli ustanovivshegosya neizo-termicheskogo
techeniya gaza po morskomu gazoprovodu [Parametric identification
of a model of steady non-isothermal gas flow through a sea gas
pipeline]. {\it Morskiye intellektual'nyye tekhnologii} [{\it
Marine intellectual technology}], 2017, vol.~1, no.~1,  pp.~8--14.
(In Russian)

18. Ermolaeva N.~N., Kurbatova~G.~I., Klemeshev V.~A. {\it
Svidetel'stvo ob ofitsial'noy registratsii programmy dlya EVM
N~2017613635 ``Programma dlya identifikatsii parametrov
matematicheskoy modeli techeniya mnogokomponentnoy smesi gazov v
protyazhennykh morskikh gazoprovodakh'' (PIGTM)}. [{\it
Certificate of Official Registration of Computer Programs
no.~2017613635 ``Program for identifying the parameters of a
mathematical model of a multicomponent gas mixture flow in long
offshore gas pipelines'' (PIGTM)}]. Date of receipt: 31.01.2017.
Date of state registration in the Register of computer programs:
23.03.2017. (In Russian)

19.  Ermolaeva N.~N.  Issledovaniye vliyaniya parametrov
transportirovki gaza na kharakteristiki potoka [Investigation of
the influence  of gas transmission parameters on flow
characteristics]. {\it Vestnik of Saint Petersburg University.
Series~10. Applied Mathematics. Computer science. Control
processes}, 2016, iss.~3, pp.~53--61.

20.  Bellman R.~E., Kalaba R.~E.  {\it Quasilinearization and
nonlinear boundary-value problems}. New York, American Elsevier
Publ. Comp., 1965, 218~p. (Rus. ed.: Bellman R.~E., Kalaba R.~E.
{\it Kvazi\-linearizatsia i nelineinye kraevye zadachi.} Ãoscow,
Mir Publ., 1968. 183~p.)


\vskip1.5mm Received:  October 21, 2018.

Accepted: December 18, 2018.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Galina I. Kurbatova} --- Dr. Sci. in Physics and
Mathematics, Professor; g.kurbatova@spbu.ru

\vskip2mm \textit{Nadeczda N. Ermolaeva}  --- Dr. Sci. in Physics
and Mathematics, Associate Professor;\\ n.ermolaeva@spbu.ru

}
