
{\small

\vskip6mm
%\newpage

\noindent \textbf{Литература}

}

\vskip4mm%3mm

{\footnotesize

1. {\it Castro A.\,P.\,G., Wilson W., Huyghe J.\,M., Ito K., Alves J.\,L.} Intervertebral disc creep behavior assessment through an open source finite element solver~// Journal of Biomechanics. 2013. Vol.~47. P.~297--301.

2. {\it Gao X., Zhu Q., Gu W.} Prediction of glycosaminoglycan synthesis in intervertebral disc under mechanical loading~// Journal of Biomechanics. 2016. Vol.~49. P.~2655--2661.

3. {\it Guo L.-X., Li R., Zhang M.} Biomechanical and fluid flowing characteristics of intervertebral disc of lumbar spine predicted by poroelastic finite element method~// Acta of Bioengineering and Biomechanics. 2016. Vol.~18. N~2. P.~19--29.

4. {\it Jacobs N.\,T., Cortes D.\,H., Peloquin J.\,M., Vresilovic E.\,J., Elliott D.\,M.} Validation and application of an intervertebral disc finite element model utilizing independently constructed tissue-level constitutive formulations that are nonlinear, anisotropic, and time-dependent~// Journal of Biomechanics. 2014. Vol.~47. P.~2540--2546.

5. {\it Schmidt H., Bashkuev M., Galbusera F., Wilke H.-J., Shirazi-Adl A.} Finite element study of human lumbar disc nucleus replacements~// Computer Methods in Biomechanics and Biomedical Engineering. 2014. Vol. 17. Iss.~16. P.~1762--1776.

6. {\it Zanjani-Pour S., Winlove C.\,P., Smith C.\,W., Meakin J.\,R.} Image driven subject-specific finite element models of spinal biomechanics~// Journal of Biomechanics. 2016. Vol.~49. P.~919--925.

7. {\it Gohari E., Nikkhoo M., Haghpanahi M., Parnianpour M.} Analysis of different material theories used in a FE model of a lumbar segment motion~// Acta of Bioengineering and Biomechanics. 2013. Vol.~15. N~2. P.~33--41.

8. {\it Schmidt H., Heuer F., Simon U., Kettler A., Rohlmann A., Claes L., Wilke H.-J.} Application of a new calibration method for a three-dimensional finite element model of a~human lumbar annulus fibrosus~// Clinical Biomechanics. 2006. Vol.~21. P.~337--344.

9. {\it Мерои Е.\,А., Натали А.\,Н., Паван П.\,Г., Скарпа К.} Численный анализ механического поведения межпозвонкового диска с учетом структуры коллагеновых волокон~// Рос. журн. биомеханики.  2005. Т.~9. №~1~(33). С.~36--51.

10. {\it Жарнов А.\,М., Жарнова О.\,А.} Биомеханические процессы в межпозвонковом диске шейного отдела позвоночника при его движении~// Рос. журн. биомеханики. 2013. Т.~17. №~1~(59). С.~32--40.

11. {\it  Хорошев Д.~В., Ильялов О.~Р., Устюжанцев Н.~Е., Няшин Ю.~И.} Биомеханическое моделирование межпозвоночного диска поясничного отдела человека --- современное состояние проблемы~// Рос. журн. биомеханики. 2019. Т.~23. №~3. С.~411--422.

\vskip 2.5mm%1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 19 июля 2021~г.

Cтатья принята к~печати 13 октября 2021~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Чубаров Дмитрий Александрович} --- студент; st050417@student.spbu.ru

\vskip2mm \textit{Трегубов Владимир Петрович} --- д-р физ.-мат. наук, проф.; v.tregubov@spbu.ru


\vskip2mm \textit{Егорова Надежда Константиновна} --- аспирант; nadezhda\_ego@mail.ru


}
