

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



%\bibitem{Conf-PQCrypto-2019}
1.\,\,Post-quantum cryptography. {\it 10th International conference}. Chongqing, China, May 8--10, 2019 (PQCrypto 2019). {\it Proceedings.  Lecture Notes in Computer Science Series}.
Berlin, Springer Publ., 2019, vol.~11505, pp.~1--421.

%\bibitem{Alamelou}
2.\,\,Alamelou Q., Blazy O., Cauchie S., Gaborit Ph.
A code-based group signature scheme. {\it Designs, codes and cryptography}, 2017, vol.~82, no.~1--2, pp.~469--493.

%\bibitem{Kuzmin}
3.\,\,Kuzmin A. S., Markov V. T., Mikhalev A. A., Mikhalev A. V., Ne\-chaev~A.~A. Cryptographic algorithms on groups and algebras.
{\it Journal of Mathematical Sciences}, 2017, vol.~223, no.~5, pp.~629--641.

%\bibitem{SUSU}
4.\,\,Moldovyan N.~A., Moldovyan A.~A. Finite non-commutative associative algebras as car\-riers of hidden discrete logarithm problem. {\it Bulletin of the South Ural State University. Series Ma\-the\-ma\-ti\-cal Modelling, Programming $\&$ Computer Software}, 2019, vol.~12, no.~1, pp.~66--81.\\ https://doi.org/10.14529/mmp190106

%\bibitem{Vestnik2020}
5.\,\,Moldovyan N. A., Moldovyan A. A. Candidate for practical post-quantum signature scheme.
{\it Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2020, vol.~16, iss.~4, pp.~455--461. https://doi.org/10.21638/11701/spbu10.2020.410

%\bibitem{QRS-NA}
6.\,\,Moldovyan N.~A. A unified method for setting finite non-commutative associative algebras and their properties. {\it Quasigroups and Related Systems}, 2018, vol.~26, no.~2, pp.~263--270.

%\bibitem{Buletin2020-DN}
7.\,\,Moldovyan D. N. New form of the hidden logarithm problem and its algebraic support. {\it  Bulletin of Academy of Sciences of Moldova. Mathematics}, 2020, no.~2~(93),
pp.~3--10.

%\bibitem{Buletin2020-NA}
8.\,\,Moldovyan N. A. Signature schemes on algebras,
satisfying enhanced criterion of post-quantum security. {\it Bulletin of Academy of Sciences of Moldova. Mathematics}, 2020, no.~2~(93),
pp.~62--67.

%\bibitem{QRS-2009}
9.\,\,Moldovyan N.~A., Moldovyan P.~A. New primitives for digital signature algorithms. {\it Quasigroups and Related Systems}, 2009, vol.~17, no.~2, pp.~271--282.

%\bibitem{Chaum}
10.\,\,Chaum D. Security without identification. Transaction
systems to make big brother obsolete. {\it Communications of the AMS}, 1985, vol.~28, no.~10, pp.~1030--1044.

%\bibitem{Blind}
11.\,\,Camenisch J. L., Piveteau J.-M., Stadler M. A. Blind signatures based on the discrete logarithm problem. {\it Advances in Cryptology (EUROCRYPT'94). Proceedings. Lecture Notes in Computer Science}. Berlin, Springer Verlang Publ., 1995, vol.~950, pp.~428--432.

%\bibitem{Shor}
12.\,\,Shor P. W. Polynomial-time algorithms for prime factorization and discrete logarithms on quantum computer. \textit{SIAM Journal of Computing}, 1997, vol.~26, pp.~1484--1509.

%\bibitem{Jozsa}
13.\,\,Jozsa R. Quantum algorithms and the fourier transform. \textit{Proceedings of the Royal Society of  London. Series A}, 1998, vol.~454, pp.~323--337.

%\bibitem{Yan-2}
14.\,\,Yan S. Y. \textit{Quantum attacks on public-key cryptosystems}. Boston, Springer Publ., 2013, 207~p.

%\bibitem{CSJM2020}
15.\,\,Moldovyan D.~N., Moldovyan A.~A., Moldovyan N.~A. Digital signature scheme with doubled verification equation. {\it Computer Science Journal of Moldova}, 2020, vol.~28, no.~1~(82), pp.~80--103.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 18, 2020.

Accepted: June 04, 2021.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Nikolay A. Moldovyan} ---  Dr. Sci. in Technics, Professor, Chief Researcher; nmold@mail.ru

\vskip 2mm \textit{Alexandr A. Moldovyan} ---  Dr. Sci. in Technics, Professor, Chief Researcher; maa1305@yandex.ru \par%
%
%
}
