
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

1. {\it  Губанов Д. А., Новиков Д. А., Чхартишвили А. Г.}
Социальные сети:  модели информационного влияния, управления и
противоборства.  М.: Физматлит, 2010. 228~с.

2. {\it Belen S., Kropat E.,   Weber G.-W.}    On the classical
Maki---Thompson rumour model  in continuous time // Central
European Journal of Operations Researches. 2011. Vol.~19.
P.~1--17.

3. {\it Rosnow  R. L.}  Psychology of rumor reconsidered //
Psychol. Bull. 1980. Vol.~87, N~3. P.~578--591.

4. {\it Rosnow  R. L. }Inside rumor: a personal journey // Amer.
Psychol. 1991.   Vol.~46, N~5. P.~484--496.

5. {\it Difonzo  N.,  Bordia  P.}  Rumor and prediction:  making
sense (but losing dollars) in the stock market~// Organ. Behav.
Hum. Decis. Process. 1997. Vol.~71, N~3. P.~329--353.

6. {\it Maki D. P., Thompson M.} Mathematical models and
applications. Prentice-Hall: Englewood Cliffs, 1973. 274~p.

7. {\it Daley  D. J., Kendall D. G.} Stochastic rumours // J.
Inst. Math. Appl.  1965. Vol.~1. P.~42--55.

8. {\it Karelin V. V., Bure V. M., Polyakova L. N., Elfimov A. N.}
Control problem of a deterministic queuing system // Applied
Mathematical Sciences. 2016. Vol.~10, N~21--24. P.~1023--1030.

9. {\it Bure V.~M., Karelin ~V.~V.,  Polyakova L. N.}
Probabilistic model of terminal services // Applied Mathematical
Sciences. 2016. Vol.~10,  N~39. P.~1945--1952.

10. {\it Bure V.~M., Karelin V.~V., Polyakova L. N.} The problem
of resource allocation between the protection system and
constructing redundant components //  Applied Mathematical
Sciences. 2015.  Vol.~9, N~93--96. P.~4771--4779.

11. {\it Yakushev V.~P., ~Karelin V.~V., ~Bure V.~M., Parilina
E.~M.}  Soil acidity adaptive control problem // Stochastic
enviromental research and risk assessment. 2015. Vol.~29, N~6.
P.~1671--1677 (see also URL:
http://dx.doi.org/10.1007/s00477-014-0965-5, дата обращения:
15.10.2016).

12. {\it    Bure V., Parilina E., Sedakov A.}  Consensus in social
networks with heterogeneous agents and two centers   of influence
// Intern. conference   ``Stability and control processes'' in
memory of V. I. Zubov (SCP) joined with 21st Intern. workshop on
beam dynamics and optimization (BDO). Saint Petersburg, 05--09
Oct. 2015. Saint Petersburg, 2015. P.~233--235.

13. {\it Kamke E.} Differentialgleichungen: Losungsmethoden und
Losungen, I, Gewohnliche Differen-\linebreak tialgleichungen.
Leipzig: Teubner, 1959. 668~p.



\vskip 2mm

{\bf Для цитирования:} Карелин  В. В., Буре В. М., Свиркин М. В.
Обобщенная модель распространения   информации в непрерывном
времени // Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07



}
