

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1. Gubanov D. A. ,  Novikov D. A.,  Chkhartishvili A. G. {\it
Socialnye seti: modeli informacionnogo vliyaniya upravleniya i
protivoborstva} [{\it Social networks: models of informational
influence, control and confrontation}]. Moscow, Fizmatlit Publ.,
2010, 228~p. (In Russian)

2. Belen S., Kropat E.,   Weber G.-W.    On the classical
Maki---Thompson rumour model  in continuous time. {\it  Central
European Journal of Operations Researches}, 2011, vol.~19,
pp.~1--17.

3. Rosnow  R. L.  Psychology of rumor reconsidered. {\it Psychol.
Bull.}, 1980, vol.~87, no.~3, pp.~578--591.

4. Rosnow  R. L. Inside rumor: a personal journey. {\it Amer.
Psychol.}, 1991,   vol.~46, no.~5, pp.~484--496.

5. Difonzo  N.,  Bordia  P.  Rumor and prediction:  making sense
(but losing dollars) in the stock market. {\it Organ. Behav. Hum.
Decis. Process}, 1997, vol.~71, no.~3, pp.~329--353.

6. Maki D. P., Thompson M. {\it  Mathematical models and
applications}. Prentice-Hall, Englewood Cliffs, 1973, 274~p.

7. Daley  D. J., Kendall D. G. Stochastic rumours. {\it J. Inst.
Math. Appl.},  1965, vol.~1, pp.~42--55.

8. Karelin V. V., Bure V. M., Polyakova L. N., Elfimov A. N.
Control problem of a deterministic queuing system. {\it Applied
Mathematical Sciences}, 2016, vol.~10, no.~21--24, pp.~1023--1030.

9. Bure V.~M., Karelin~V.~V.,  Polyakova L. N. Probabilistic model
of terminal services. {\it Applied Mathematical Sciences}, 2016,
vol.~10,  no.~39, pp.~1945--1952.

10. Bure V.~M., Karelin V.~V., Polyakova L. N. The problem of
resource allocation between the protection system and constructing
redundant components. {\it  Applied Mathematical Sciences}, 2015,
vol.~9, no.~93--96, pp.~4771--4779.

11. Yakushev V.~P., Karelin V.~V., Bure V.~M., Parilina E.~M. Soil
acidity adaptive control problem. {\it Stochastic enviromental
research and risk assessment}, 2015, vol.~29, no.~6,
pp.~1671--1677. Available at:
http://dx.doi.org/10.1007/s00477-014-0965-5 (accessed:
15.10.2016).

12.    Bure V., Parilina E., Sedakov A.  Consensus in social
networks with heterogeneous agents and two centers   of influence.
{\it Intern. conference  ``Stability and control processes'' in
memory of V. I. Zubov} (SCP) {\it joined with 21st intern.
workshop on beam dynamics and optimization} (BDO), Saint
Petersburg (2015/05--09/10). Saint Petersburg, 2015, pp.~233--235.
(In Germany)

13. Kamke E. {\it Differentialgleichungen: Losungsmethoden und
Losungen, I, Gewohnliche Differen-\linebreak tialgleichungen}.
Leipzig, Teubner Publ., 1959, 668~p.




\vskip 2mm

{\bf For citation:} Karelin V. V., Bure V. M., Svirkin M. V.
Generalized model of information spreading in continuous time.
{\it Vestnik of Saint Petersburg University. Applied mathematics.
Computer science. Control processes}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p7}--\pageref{p7e}.
\doivyp/spbu10.\issueyear.\issuenum07


}
