
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. \textit{Leemann~S.~C., Wurtz~W.~A.} Pushing the MAX-IV 3 GeV
storage ring brightness and coherence towards the limit of its
magnetic lattice // Proc. of 8th Intern. Particle Accelerator
Conference, IPAC’17. 2017. P.~2557--2560.

 2. \textit{Liu~L., Westfahl-Jr.~H.} Towards diffraction
limited storage ring based light sources // Proc. of 8th Intern.
Particle Accelerator Conference, IPAC’17. 2017. P.~1203--1208.

 3. \textit{Jiao~Y., Cui~X., Duan~Z., Guo~Y.~Y., Ji~D.,
Li~J.~Y., Li~X.~Y., Peng~Y.~M., Qin~Q., Tian~S.~K., Wang~J.~Q.,
Wang~N., Wei~Y., Xu~G., Xu~H.~S., Yan~F., Yu~C.~H., Zhao~Y.~L.}
Progress of the lattice design and physics studies on the high
energy photon source // Proc. of 8th Intern. Particle Accelerator
Conference, IPAC’17. 2017. P.~2697--2699.

 4. \textit{Krinsky~S., Bengtsson~J., Kramer~S.~L.}
Consideration of a double bend achromatic lattice for NSLS-II //
Proc. of XVI European Particle Accelerator Conference, EPAC’06.
2006. P.~3487--3489.

 5. \textit{Borland~M., Berenc~T.~G., Lindberg~R.~R.,
Sajaev~V., Sun~Y.~P.} Lower emittance lattice for the Advanced
Photon Source upgrade using reverse bending magnets // Proc. of
North American Particle Accelerator Conference, NAPAC’16. 2016.
P.~877--880.

 6. \textit{Keil~J.} PETRA-IV lattice studies //
Abstracts of 2nd Workshop on Low Emittance Ring Lattice Design.
2016. P.~10.

 7. \textit{Revol~J.-L., Berkvens~P., Biasci~J.~C.,
Bouteille~J.-F.~B., Carmignani~N., Ewald~F., Farvacque~L.,
Franchi~A., Goirand~L., Hahn~M., Hardy~L., Jacob~J., Koch~J.~M.,
Lebec~G., Liuzzo~S.~M., Nash~B., Perron~T.~P., Plouviez~E.,
Raimondi~P., Scheidt~K.~B., Serriere~V.} ESRF upgrade Phase II //
Proc. of 4th Intern. Particle Accelerator Conference, IPAC’13.
2013. P.~1140--1142.

 8. \textit{Raimondi~P.} The ESRF low-emittance upgrade
// Proc. of 7th Intern. Particle Accelerator Conference, IPAC’16.
2016. P.~2023-2027.

 9. \textit{Tanaka~H., Ishikawa~T., Goto~S., Takano~S.,
Watanabe~T., Yabashi~M.} Spring-8 upgrade project // Proc. of 7th
Intern. Particle Accelerator Conference, IPAC’16. 2016.
P.~2867--2870.

 10. \textit{Ашанин~И.~А., Башмаков~Ю.~А., Будкин~В.~А.,
Валентинов~А.~Г., Гусарова~М.~А., Данилова~Д.~К., Дементьев~А.~А.,
Дмитриева~В.~В., Дудина~Н.~С., Дюбков~В.~С., Ключевская~Ю.~Д.,
Корчуганов~В.~Н., Лалаян~М.~В., Лозеев~Ю.~Ю., Лозеева~Т.~А.,
Махоро~А.~А., Механикова~В.~Ю., Мосолова~О.~А., Полозов~С.~М.,
Проников~А.~И., Ращиков~В.~И., Савченко~А.~А., Самошин~А.~В.,
Смыгачева~А.~С., Ушаков~В.~А., Фещенко~А.~М., Фомин~Е.~А.,
Шатохин~В.~Л., Biasci~J.-C., Liuzzo~S., Raimondi~P., Revol~J.-L.,
Farvaque~L., White~S.} Разработка концепции Российского
Спе\-циа\-лизированного источника синхротронного излучения 4-го
поколения ИССИ-4 НИЦ «Курчатовский институт» // Ядерная физика и
инжиниринг. 2018. Т.~9, №~2. С.~192--199.

 11. \textit{Satoh~M., Akemoto~M., Arakawa~D.~A.,
Arakida~Y., Enomoto~A., Enomoto~Y., Fukuda~S., Funakoshi~Y.,
Furukawa~K., Higo~T., Honma~H., Iida~N., Ikeda~M., Iwase~H.,
Kaji~H., Kakihara~K., Kamitani~T., Katagiri~H., Kazama~S.,
Kikuchi~M., Koiso~H.,  Matsumoto~S., Matsumoto~T., Matsushita~H.,
Michizono~S., Mikawa~K., Mimashi~T., Miura~T., Miyahara~F.,
Mori~T., Morita~A., Nakajima~H., Nakao~K., Natsui~T., Ogawa~Y.,
Ohnishi~Y., Ohsawa~S., Qiu~F., Satake~I., Satoh~D., Seimiya~Y.,
Shidara~T., Shirakawa~A., Suetake~M., Sugimoto~H., Suwada~T.,
Tanaka~M., Tawada~M., Yano~Y., Yokoyama~K., Yoshida~M., Zhang~R.,
Zhou~X.} Commissioning status of SuperKEKB injector linac // Proc.
of 7th Intern. Particle Accelerator Conference, IPAC’16. 2016.
P.~4152--4154.

 12. \textit{Benedikt~M., Zimmermann~F.} Status of the
Future Circular Collider study // Proc. of XXV~Rus\-sian Particle
Accelerator Conference, RuPAC’16. 2016. P.~34--38.

 13. \textit{Masunov~E.~S., Polozov~S.~M.} High
intensity ion beams in rf undulator linac // Phys. Rev. ST AB.
2008. Vol.~11. P.~074201.

 14. \textit{Masunov~E.~S., Polozov~S.~M.} The new
version of BEAMDULAC code for high intensity ion beam dynamics //
Problems of Atomic Science and Technology. Series Nuclear Physics
Investigations. 2006. Vol.~3 (47). P.~119--121.

 15. \textit{Masunov~E.~S., Polozov~S.~M.} BEAMDULAC
code for numerical simulation of 3D beam dynamics in a
high-intensity undulator linac // Nuclear Instruments and Methods
in Physics Research A. 2006. Vol.~558. P.~184--187.

 16. \textit{Воронков~А.~В., Масунов~Э.~С.,
Полозов~С.~М., Ращиков~В.~И.} Расчет динамики пучка в~ускорителях,
работающих на~бегущей волне, с~учетом эффекта нагрузки током //
Атомная Энергия. 2010. Т.~109, вып.~2. С.~84--89.

 17.  \textit{Masunov~E.~S., Polozov~S.~M.,
Rashchikov~V.~I., Voronkov~A.~V.} Stationary and transient beam
dynamics simulation results comparison for traveling wave electron
linac with beam loading // Problems of Atomic Science and
Technology. Series Nuclear Physics Investigations. 2012. Vol.~4
(80). P.~96--99.

 18. \textit{Масунов~Э.~С.} Эффекты нагрузки током
в~ускорителях заряженных частиц. М.: Изд-во МИФИ, 1999. 112~с.

 19. \textit{Klucheskaia~Yu.~D., Polozov~S.~M.} Optimal
RF-photogun parameters for the compact XFEL based on the new
linac-injector prototype // Abstracts of Channeling--2018. 2018.
P.~30.

 20. \textit{Demsky~M.~I., Polozov~S.~M.,
Rashchikov~V.~I.} Beam dynamics in new 10~MeV high-power electron
linac for industrial application // Proc. of XXV Russian Particle
Accelerator Conference, RuPAC’2016. 2016. P.~493--495.

 21. \textit{Polozov~S.~M., Bazyl~D.~S.,
Bondarenko~T.~V., Gusarova~M.~A.,  Kliuchevskaia~Yu.~D.,
Lalayan~M.~V., Rashchikov~V.~I., Savin~E.~A., Demsky~M.~I.,
Eliseev~A.~A., Krotov~V.~V., Trifonov~D.~E., Han~B.~S.,
Kang~W.~G., Park~H.~G.} New 10 MeV high-power electron linac for
industrial application // Proc. of 7th Intern. Particle
Accelerator Conference, IPAC’2016. 2016. P.~1794--1796.

 22. \textit{Polozov~S.~M., Bazyl~D.~S.,
Bondarenko~T.~V., Gusarova~M.~A.,  Kliuchevskaia~Yu.~D.,
Lalayan~M.~V., Rashchikov~V.~I., Savin~E.~A., Demsky~M.~I.,
Eliseev~A.~A., Krotov~V.~V., Trifonov~D.~E.} Commissioning and
first tests of the new standing wave 10~MeV electron accelerator
// Proc. of XXV Russian Particle Accelerator Conference,
RuPAC’2016. 2016. P.~173--176.


\vskip 1.5mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 7 декабря 2018 г.

Cтатья принята к~печати 18 декабря 2018~г.

\vskip4mm%6mm
К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

%\vskip1.8mm%2mm
%\textit{Буре Наталья Анатольевна}~--- канд. филол. наук,
%доц.;  nataly.bure@gmail.com


\vskip2mm\textit{Ашанин Илья Андреевич} --- ilya.ashanin@mail.ru

\vskip2mm\textit{Ключевская Юлия Денисовна} ---
kluchevskaia@mail.ru

\vskip2mm\textit{Махоро Алексей Алексеевич} --- ma\_horo@mail.ru

\vskip2mm\textit{Механикова Валерия Юрьевна} ---
mek-lera@yandex.ru

\vskip2mm\textit{Мосолова Ольга Анатольевна} ---
olechka\_1104@mail.ru

\vskip2mm\textit{Полозов Сергей Маркович} --- smpolozov@mephi.ru

\vskip2mm\textit{Проников Алексей Игоревич} ---
pronikovalexey@mail.ru

\vskip2mm\textit{Ращиков Владимир Иванович} ---
virashchikov@mephi.ru

}
