
{\normalsize

\vskip 6mm

\noindent{\bf Beam dynamics simulation in the linear accelerator
used as an injector\\ for the 4th generation Specialized
Synchrotron Radiation Source SSRS-4$\,^*$}

}

\vskip 2mm

{\small

\noindent{\it I. A. Ashanin$^{\,1,2}$, Yu. D.
Kluchevskaia$^{\,1,2}$, A. A. Makhoro$^{\,1,2}$,
V.~Yu.~Mechanikova$^{\,1,2}$,\\ O.~A.~Mo\-solova$^{\,1,2}$,
S.~M.~Polozov$^{\,1,2}$, A.~I.~Pronikov$^{\,1,2}$,
V.~I.~Rashchikov$^{\,1,2}$%
%, I.~Î. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work is supported by the Ministry of
Science and Higher Education of the Russian Federation in the
framework of Federal Targeted Program ``Research and Development
in the Priority Directions of Development of the Scientific and
Technological Complex of Russia for 2014--2020'' (agreement on
December 24, 2017, N~14.616.21.0086, ID RFMEFI61617X0086).\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%óíèâåðñèòåò, \issueyear%
%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
$^1$~%
National Research Nuclear University ``MEPhI'', 31, Kashirskoe
sh., Moscow,

\noindent%
\hskip2.45mm%
115409, Russian Federation

\noindent%
$^2$~%
National Research Center ``Kurchatov Institute'', 1, Akademika
Kurchatova pl., Moscow,

\noindent%
\hskip2.45mm%
123182, Russian Federation

%\noindent%
%$^2$~%
%St.\,Petersburg State University, 7--9, Universitetskaya nab.,
%St.\,Petersburg,

%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip3mm

\noindent \textbf{For citation:}   Ashanin~I.~A.,
Kluchevskaia~Yu.~D., Makhoro~A.~A., Mechanikova~V.~Yu.,
Mosolova~O.~A., Polozov~S.~Ì., Pronikov~A.~I., Rashchikov~V.~I.
Beam dynamics simulation in the linear accelerator used as an
injector for the 4th generation Specialized Synchrotron
Radia\-tion Source SSRS-4. {\it Vestnik of Saint~Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~15, iss.~\issuenum,
pp.~\pageref{p10}--\pageref{p10e}.
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum10  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent Development of the several new synchrotron
radiation sources has begun in Russia at the moment. The 4th
generation Specialized Synchrotron Radiation Source SSRS-4 is the
mega-science project being developed at National Research Center
``Kurchatov Institute''. The project is being realized in
collaboration with the European synchrotron radiation source
(European Synchrotron Radiation Facility, ESRF, Grenoble, France).
It is assumed that the radiation source will include both storage
synchrotron with energy near to 6 GeV and free electron laser. To
achieve a design transverse emittance of 70--100 pm$\, \cdot
\,$rad it was proposed to use a multiple-band-achromat magnetic
lattice. The length of the main storage ring will be about 1300 m,
it will consist of 40 superperiods. Each period will include two
antisymmetric magnetic arches and a free gap with length near
about 5 m to accommodate embedded devices there between. It is
proposed to use one linear accelerator with beam energy equal to 6
GeV with two RF-guns: a photo gun for free electron laser and
RF-gun with thermocathode for injection to the storage ring. Beam
dynamics simulation
results in such linear accelerator are discussed in this article.\\[1mm]
\textit{Keywords}: synchrotron light source, free electron laser,
injection linac, beam dynamics.
\par}

\vskip 5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Leemann~S.~C., Wurtz~W.~A. Pushing the MAX-IV 3 GeV storage
ring brightness and coherence towards the limit of its magnetic
lattice.  \textit{Proc. of 8th Intern. Particle Accelerator
Conference, IPAC’17}, 2017, pp.~2557--2560.

2. Liu~L., Westfahl Jr.~H. Towards diffraction limited storage
ring based light sources. \textit{Proc. of 8th~Intern. Particle
Accelerator Conference, IPAC’17}, 2017, pp.~1203--1208.

3. Jiao~Y., Cui~X., Duan~Z., Guo~Y.~Y., Ji~D., Li~J.~Y., Li~X.~Y.,
Peng~Y.~M., Qin~Q., Tian~S.~K., Wang~J.~Q., Wang~N., Wei~Y.,
Xu~G., Xu~H.~S., Yan~F., Yu~C.~H., Zhao~Y.~L. Progress of the
lattice design and physics studies on the high energy photon
source. \textit{Proc. of 8th Intern. Particle Accelerator
Conference, IPAC’17}, 2017, pp.~2697--2699.

4. Krinsky~S., Bengtsson~J., Kramer~S.~L. Consideration of a
double bend achromatic lattice for NSLS-II. \textit{Proc. of XVI
European Particle Accelerator Conference, EPAC’06}, 2006,
pp.~3487--3489.

5. Borland~M., Berenc~T.~G., Lindberg~R.~R., Sajaev~V., Sun~Y.~P.
Lower emittance lattice for the Advanced Photon Source upgrade
using reverse bending magnets. \textit{Proc. of North American
Particle Accelerator Conference, NAPAC’16}, 2016, pp.~877--880.

6. Keil~J. PETRA-IV lattice studies. \textit{Abstracts of 2nd
Workshop on Low Emittance Ring Lattice Design}, 2016, p.~10.

7. Revol~J.-L., Berkvens~P., Biasci~J.~C., Bouteille~J.-F.~B.,
Carmignani~N., Ewald~F., Farvacque~L., Franchi~A., Goirand~L.,
Hahn~M., Hardy~L., Jacob~J., Koch~J.~M., Lebec~G., Liuzzo~S.~M.,
Nash~B., Perron~T.~P., Plouviez~E., Raimondi~P., Scheidt~K.~B.,
Serriere~V. ESRF upgrade Phase II. \textit{Proc. of 4th~Intern.
Particle Accelerator Conference, IPAC’13}, 2013, pp.~1140--1142.

8. Raimondi~P. The ESRF low-emittance upgrade. \textit{Proc. of
7th Intern. Particle Accelerator Conference, IPAC’16}, 2016,
pp.~2023--2027.

9. Tanaka~H., Ishikawa~T., Goto~S., Takano~S., Watanabe~T.,
Yabashi~M. Spring-8 upgrade project. \textit{Proc. of 7th Intern.
Particle Accelerator Conference, IPAC’16}, 2016, pp.~2867--2870.

10. Ashanin~I.~A., Bashmakov~Yu.~A., Budkin~V.~A.,
Valentinov~A.~G., Gusarova~M.~A., Danilova~D.~K., Dementiev~A.~A.,
Dmitriyeva~V.~V., Dudina~N.~S., Dyubkov~V.~S.,
Klyuchevskaia~Yu.~D., Korchuganov~V.~N., Lalayan~M.~V.,
Lozeev~Yu.~Yu., Lozeeva~T.~A., Makhoro~A.~A., Mekhanikova~V.~Yu.,
Mosolova~O.~A., Polozov~S.~M., Pronikov~A.~I., Rashchikov~V.~I.,
Savchenko~A.~A., Samoshin~A.~V., Smygachova~A.~S., Ushakov~V.~A.,
Feshchenko~A.~M., Fomin~E.~A., Shatokhin~V.~L., Biasci~J.-C.,
Liuzzo~S., Raimondi~P., Revol~J.-L., Farvaque~L., White~S.
Razrabotkà kontseptsii Rossiyskogo Spetsializirovannogo istochnika
sinhronnogo izluchenia  4-gî pokolenia ISSI-4 NITS ``Kurchatovskiy
institut'' [Conceptual design of a dedicated fourth-generation
Specialized Synchrotron radiation Source (SSRS-4) at the Kurchatov
Institute]. \textit{Physics of Atomic Nuclei}, 2018, vol.~9,
no.~2, pp.~192--199. (In Russian)

11. Satoh~M., Akemoto~M., Arakawa~D.~A., Arakida~Y., Enomoto~A.,
Enomoto~Y., Fukuda~S., Funakoshi~Y., Furukawa~K., Higo~T.,
Honma~H., Iida~N., Ikeda~M., Iwase~H., Kaji~H., Kakihara~K.,
Kamitani~T., Katagiri~H., Kazama~S., Kikuchi~M., Koiso~H.,
Matsumoto~S., Matsumoto~T., Matsushita~H., Michizono~S.,
Mikawa~K., Mimashi~T., Miura~T., Miyahara~F., Mori~T., Morita~A.,
Nakajima~H., Nakao~K., Natsui~T., Ogawa~Y., Ohnishi~Y., Ohsawa~S.,
Qiu~F., Satake~I., Satoh~D., Seimiya~Y., Shidara~T., Shirakawa~A,
Suetake~M., Sugimoto~H., Suwada~T., Tanaka~M., Tawada~M., Yano~Y.,
Yokoyama~K., Yoshida~M., Zhang~R., Zhou~X. Commissioning status of
SuperKEKB injector linac. \textit{Proc. of 7th Intern. Particle
Accelerator Conference, IPAC’16}, 2016, pp.~4152--4154.

12. Benedikt~M., Zimmermann~F. Status of the Future Circular
Collider study. \textit{Proc. of XXV Russian Particle Accelerator
Conference, RuPAC’16}, 2016, pp.~34--38.

13. Masunov~E.~S., Polozov~S.~M. High intensity ion beams in rf
undulator linac. \textit{Phys. Rev. ST AB}, 2008, vol.~11,
pp.~074201.

14. Masunov~E.~S., Polozov~S.~M. The new version of BEAMDULAC code
for high intensity ion beam dynamics. \textit{Problems of Atomic
Science and Technology. Series Nuclear Physics Investigations},
2006, vol.~3 (47), pp.~119--121.

15. Masunov~E.~S., Polozov~S.~M. BEAMDULAC code for numerical
simulation of 3D beam dynamics in a high-intensity undulator
linac. \textit{Nuclear Instruments and Methods in Physics Research
A}, 2006, vol.~558, pp.~184--187.

16. Masunov~E.~S., Polozov~S.~M., Rashchikov~V.~I., Voronkov~A.~V.
Raschet dinamiki puchka v uskoriteliah, rabotauschih na beguschey
volne, s uchetom effecta nagruzki tokom [Calculation of beam
dynamics in traveling-wave accelerators taking account of the
current load]. \textit{Atomic Energy}, 2010, vol.~109 (2),
pp.~106--112.  (In Russian)

17.  Masunov~E.~S., Polozov~S.~M.,  Rashchikov~V.~I.,
Voronkov~A.~V. Stationary and transient beam dynamics simulation
results comparison for traveling wave electron linac with beam
loading. \textit{Problems of Atomic Science and Technology. Series
Nuclear Physics Investigations}, 2012, vol.~4 (80), pp.~96--99.

18. Masunov~E.~S. {\it Effecty nagruzki tokom v uskoriteliah
zariazhennyh chastits}  [\textit{Beam loading effects in charged
particles accelerators}]. Moscow, MEPhI Publ., 1999, 112~p. (In
Russian)

19. Klucheskaia~Yu.~D., Polozov~S.~M. Optimal RF-photogun
parameters for the compact XFEL based on the new linac-injector
prototype. \textit{Abstracts of Channeling--2018}, 2018, p.~30.

20. Demsky~M.~I., Polozov~S.~M., Rashchikov~V.~I. Beam dynamics in
new 10~MeV high-power electron linac for industrial application.
\textit{Proc. of XXV Russian Particle Accelerator Conference,
RuPAC’2016}, 2016, pp.~493--495.\newpage

21. Polozov~S.~M., Bazyl~D.~S., Bondarenko~T.~V., Gusarova~M.~A.,
Kliuchevskaia~Yu.~D., Lalayan~M.~V., Rashchikov~V.~I.,
Savin~E.~A., Demsky~M.~I.,  Eliseev~A.~A., Krotov~V.~V.,
Trifonov~D.~E., Han~B.~S., Kang~W.~G., Park~H.~G. New 10 MeV
high-power electron linac for industrial application.
\textit{Proc. of 7th Intern. Particle Accelerator Conference,
IPAC’2016}, 2016, pp.~1794--1796.

22. Polozov~S.~M., Bazyl~D.~S., Bondarenko~T.~V., Gusarova~M.~A.,
Kliuchevskaia~Yu.~D., La\-layan~M.~V., Rashchikov~V.~I.,
Savin~E.~A., Demsky~M.~I.,  Eliseev~A.~A., Krotov~V.~V.,
Trifonov~D.~E. Commissioning and first tests of the new standing
wave 10~MeV electron accelerator. \textit{Proc. of XXV~Rus\-sian
Particle Accelerator Conference, RuPAC’2016}, 2016, pp.~173--176.


\vskip 1.5mm

Received:  December 7, 2018.

Accepted: December 18, 2018.


\vskip4mm%5mm
A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip1.5mm \textit{Ilya A. Ashanin}  --- ilya.ashanin@mail.ru

\vskip1.5mm \textit{Yulia D. Kluchevskaia} ---
kluchevskaia@mail.ru

\vskip1.5mm \textit{Aleksey A. Makhoro} --- ma\_horo@mail.ru

\vskip1.5mm \textit{Valeria Yu. Mechanikova} ---
mek-lera@yandex.ru

\vskip1.5mm \textit{Olga A. Mosolova} --- olechka\_1104@mail.ru

\vskip1.5mm \textit{Sergey M. Polozov} --- smpolozov@mephi.ru

\vskip1.5mm \textit{Alexey I. Pronikov} --- pronikovalexey@mail.ru

\vskip1.5mm \textit{Vladimir I. Rashchikov} ---
virashchikov@mephi.ru\par
%
}
