

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Provotorov V.~V.,  Gnilitskaya Yu.~A. Granichnoe upravlenie
volnovoi sistemoi v prostranstve obobshennyh reshenii na grafe
[Boundary control of a wave systems in the space of the
generalized solutions]. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2013, iss.~3, pp.~112--120. (In Russian)

2. Podvalny S.~L., Provotorov V.~V. Startovoe upravlenie
parabolicheskoj sistemoj s raspredelennymi parametrami na grafe
[Starting control of a parabolic system with distributed
parameters on a graph]. \textit{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2015, iss.~3, pp.~126--142. (In Russian)

3. Provotorov V.~V. Boundary control of a parabolic system with
distributed parameters on a graph in the class of summable
functions. \emph{Automation and Remote Control}, 2015, vol.~76.
iss.~2, pp.~318--322.

4. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredelennymi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \textit{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224.
https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)

5. Zhabko A.~P., Tikhomirov O.~G., Chizhova O.~N. On stabilization
of a class of systems with time proportional delay.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2018, vol.~14,
iss.~2, pp.~165--172.
https://doi.org/10.21638/11702/spbu10.2018.209

6. Alexandrova I.~V., Zhabko A.~P.  A new LKF approach to
stability analysis of linear systems with uncertain delays.
\emph{Automatica}, 2018, vol. 91, pp.~173--178.

7. Provotorov V.~V. Boundary control of a parabolic system with
delay and distributed parameters on the graph. \emph{International
Conference ``Stability and Control Processes'' in memory of V.~I.
Zubov} (\emph{SCP}). Saint Petersburg, 2015, pp.~126--128.

8. Podvalny S.~L., Provotorov V.~V. The questions of
controllability of a parabolic systems with distributed parameters
on the graph. \emph{International Conference ``Stability and
Control Processes'' in memory of V.~I. Zubov} (\emph{SCP}). Saint
Petersburg, 2015, pp.~117--119.

9. Provotorov V.~V., Volkova A.~S.  \textit{Nachal'no-kraevie
zadachi s raspredelennimi parametrami na grafe} [\textit{Initial
boundary value problems with distributed parameters on the
graph}]. Voronezh, Nauchnay kniga Publ.,  2014,  188~p. (In
Russian)

10. Provotorov V.~V.  Sobstvennye funkcii zadachi
Shturma---Liuvillja na grafe-zvezde [Eigenfunctions of the
Sturm---Liouville problem on astar graph]. \emph{Mathematics},
2008, vol.~199, iss.~10, pp.~105--126.    (In Russian)

11. Provotorov V.~V. Razlozenie po sobstvennym funkciyam zadachi
Shturma---Liuvillya na grafe-puchke [Expansion  of eigenfunctions
of Sturm---Liouville problem on bundle graph]. \emph{Russian
Mathematics}, 2008, vol.~3, pp.~50--62. (In Russian)

12. Ladyzhenskaya O.~A. \textit{Kraevye zadachi matematicheskoi
fiziki} [\textit{Boundary value problems of mathematical
physics}]. Moscow, Nauka Publ., 1973, 407~p. (In Russian)

13. Lions J.-L. \textit{Quelques methodes de resolution des
problems aux limites non lineaire}. Paris, Dunod Gauther-Villars
Press, 1969, 598~p. (Russ. ed.: Lions J.-L. \textit{Nekotorye
metody resheniya nelineinykh kraevykh zadach} [\textit{Some
methods of solving non-linear boundary value problems}]. Moscow,
Mir Publ., 1972, 587~p.)

14. Provotorov V.~V.,  Ryazhskikh V.~I., Gnilitskaya Yu.~A. Unique
weak solvability of a nonlinear initial boundary value problem
with distributed parameters in a netlike region. \textit{Vestnik
of Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2017, vol.~13, iss.~3, pp.~264--277.
https://doi.org/10.21638/11701/spbu10.2017.304

15. Provotorov V.~V., Provotorova E.~N.  Optimal control of the
linearized Navier---Stokes system in a netlike domain.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~4, pp.~428--441.
https://doi.org/10.21638/11701/spbu10.2017.409

16. Artemov M.~A.,  Baranovskii E.~S.,  Zhabko A.~P.,  Provotorov
V.~V. On a 3D model of non-isothermal flows in a pipeline network.
\emph{Journal of Physics. Conference Series}, 2019, vol. 1203,
Article ID 012094. https://doi.org/10.1088/1742-6596/1203/1/012094

17. Aleksandrov A.~Yu., Zhabko A.~P. O stabilizacii recheniya
odnogo klassa nelineinyh differencial'nyh sistem [On stability of
solutions to one class of nonlinear difference systems].
\emph{Siberian Mathematical Journal}, 2003, vol. 44, no. 6, pp.
951--958. (In Russian)

18. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \emph{WSEAS Transactions on Systems and Control},
2014, vol.~9, pp.~388--397.

19. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions of solutions for nonlinear multiconnected
time-delay systems. \emph{Circuits  Systems and Signal
Processing}, 2016, vol.~35, no.~10, pp.~3531--3554.

20. Karelin V.~V.  Shtrafnye funkcii v zadache upravleniya
processom nabludeniya [Penalty functions in the control problem of
an observation process]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss. 4, pp. 109--114. (In Russian)

21. Karelin V.~V., Bure V.~M., Svirkin M.~V. Obobchennaja model
rasprostranenija informacii v neprerivnom vremeni [The generalized
model of information dissemination in continuous time].
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2017, vol.~13,
iss.~1, pp.~74--80. https://doi.org/10.21638/11701/spbu
10.2017.107 (In Russian)

22. Kamachkin A.~M., Yevstafyeva V.~V.   Oscillations in a relay
control system at an external disturbance.  \emph{Control
Applications of Optimization 2000}. \emph{Proceedings of the 11th
IFAC Workshop}, 2000, vol.~2, pp.~459--462.

23. Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze
prognoza s ustoichivym lineinym priblizheniem [Plasma
stabilization by prediction with stable linear approximation].
\emph{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2011, iss.~1,
pp.~116--133. (In Russian)

24. Aliseiko A.~N. Matricy Lyapunova dlya klassa sistem s
eksponencial'nym yadrom [Lyapunov matrices for a class of systems
with an exponential core]. \textit{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~3, pp.~228--240.
https://doi.org/10.21638/11701/spbu 10.2017.301 (In Russian)

25. Ponomarev A.~A. Approksimaciya obratnoi svyazi v regulyatore
``predictor-corrector'' yavnoi funkcii [Approximation of feedback
in the ``predictor-corrector'' regulator by an explicit function].
\textit{Vestnik\linebreak\newpage\noindent of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~193--208.
https://doi.org/10.21638/11701/spbu 10.2017.206  (In Russian)

26. Kuptsova S.~E., Kuptsov S.~Yu., Stepenko N.~A. On the limiting
behavior of a time-delay system's solution. \textit{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2018, vol. 14, iss. 2, pp. 173--182.
https://doi.org/10.21638/11702/spbu10.2018.2010

27. Krasnov S.~V., Sergeev S.~M., Mukhanova N.~V., Grushkin A.~N.
Methodical forming business competencies for private label.
\emph{6th International Conference on Reliability, Infocom
Technologies and Optimization (Trends and Future Directions),
ICRITO}, 2017, pp. 569--574.

28. Provotorov V.~V., Sergeev S.~M., Part A.~A. Solvability of
hyperbolic systems with distributed parameters on the graph in the
weak formulation. \textit{Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019,
vol. 15, iss. 1, pp. 107--117.
https://doi.org/10.21638/11702/spbu10.2019.2003



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  August 15, 2019.

Accepted: November 07, 2019.

\vskip 6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Aleksei P. Zhabko} --- Dr. Sci. in  Physics and
Mathematics, Professor; zhabko.apmath.spbu@mail.ru

\vskip 2mm \textit{Andrey I. Shindyapin} --- Dr. Sci.  in  Physics
and Mathematics, Professor; shindyapin.andrey@gmail.com

\vskip 2mm \textit{Vyacheslav V. Provotorov} --- Dr. Sci. in
Physics and Mathematics, Professor; wwprov@mail.ru

}
