
{\normalsize

%\vskip 6mm
\newpage

\noindent{\bf Beam dynamics of the project DARIA RFQ$^{*}$
 }

}

\vskip 2.5%3
mm

{\small

\noindent{\it G. N.~Kropachev$^{1,2}$, T. V.~Kulevoy$^{1}$, A. L.~Sitnikov$^{1}$, E. R.~Khabibullina$^{1}$, S. V.~Vinogradov$^{3}$%
%, I.~ќ. Famylia%$~^2$%

 }

\vskip 2.5%3
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent~$^{*}$ This work was financially supported by Ministry of Science and Higher Education of the Russian Federation in framework of Agreement N~075-15-2022-830 from  May 27, 2022 (Prolongation of Agreement N~075-15-2021-1358 from  October 12, 2021).\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} —анкт-ѕетербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize



\noindent%
$^1$~%
National Research Centre ``Kurchatov InstituteТТ, 1, pl. Kurchatova, Moscow,

\noindent%
\hskip2.45mm%
117218, Russian Federation


\noindent%
$^2$~%
Joint Institute for Nuclear Research, 6, ul. Joliot-Curie,  Dubna, Moscow Region,

\noindent%
\hskip2.45mm%
141980, Russian Federation


\noindent%
$^3$~%
Moscow Institute of Physics and Technology, 9, Institutskiy per.,  Dolgoprudny, Moscow Region,

\noindent%
\hskip2.45mm%
141701, Russian Federation



%\noindent%
%%$^2$~%
%St~Petersburg State University, 7--9, Universitetskaya nab., %St~Petersburg,
%
%\noindent%
%\hskip2.45mm%
%199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 2.5%3
mm


\noindent \textbf{For citation:}  Kropachev~G.~N., Kulevoy~T.~V., Sitnikov~A.~L., Khabibullina~E.~R., Vi\-no\-gradov~S.~V. Beam dynamics of the project DARIA RFQ. {\it Vest\-nik of Saint Pe\-ters\-burg Uni\-ver\-si\-ty. Ap\-plied Mathe\-ma\-tics. Com\-pu\-ter
Scien\-ce. Cont\-rol Pro\-cesses}, %~
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p11}--\pageref{p11e}.  \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum11 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent The project DARIA (neutron source dedicated to applied research and industrial applications) directed to the development of compact neutron generators for universities, scientific centers and industry. In framework of the DARIA project, the 3~MeV, 162.5~MHz and 100~mA pulse proton Radio Frequency Quadrupole (RFQ) is under development at National Research Centre ``Kurchatov InstituteТТ. In this article the main aspects of the beam dynamics design of this RFQ are described, namely the choice of RFQ parameters, the optimization of the transport and the transmission. Results of beam dynamic simulation in RFQ are presented.
\\[1mm]
\textit{Keywords}: dynamic simulation, RFQ, transport, transmission.\par}

\vskip4.5%6
mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Grigoriev S., Iashina E., Pavlov K.
Spin-echo small angle neutron scattering for a compact neutron source DARIA.
{\it Journal of Synch. Investigation,}
2019, vol.~13, pp.~1132--1134. \\	
 https://doi.org/10.1134/S1027451019060314

2. Skalyga V., Izotov I., Razin S.
High current proton beams production at simple mirror ion source 37.
{\it Review of Scientific Instrumentsl,}
2014, vol.~85~(2), pp.~02A702-1Ц02A702-3.	\\
 https://doi.org/10.1063/1.4825074

3. Barabin S.~V., Kropachev G.~N., Lukashin A.~Yu., Kulevoy~T.~V., Vybin~S.~S.,  Golubev~S.~V., Izotov~I.~V., Kiseleva~E.~M., Skalyga~V.~A., Grigoriev~S.~V., Kovalenko~N.~A.
Izmereniya emittansa gazodinamicheskogo elektronno-tsiklotronnogo rezonansnogo istochnika ionov  [Measurements of the emittance of a gas-dynamic electron-cyclotron resonant ion source].
{\it Letters to the Journal of Technical Physics},
2021, vol.~47~(10), pp. 7--10.
 https://doi.org/10.21883/PJTF.2021.10.50964.18628 (In Russian)

4. Kapchinsky I.~M.
About approximations of Kilpatrick criterion.
{\it PTE,}
1986, no.~1, pp.~33--35.	

% пример ссылки на переводную книгу
5. Kapchinsky I.~M.
{\it Dinamika chastits v lineynykh rezonansnykh uskoritelyakh $[$Particle dynamics in linear resonant accelerators$]$}.
Moscow, Atomizdat Publ.,
1966, 247~p. (In Russian)

6. Wadlinger E.~A.
Scaling laws for RFQ design procedures.
{\it IEEE Transactions on Nuclear Science,}
1985, vol.~32~(5), pp.~2596--2598.	
 https://doi.org/10.1109/TNS.1985.4333992

7. Kropachev G., Kulevoy T., Sitnikov A.
Proton linac for compact neutron source Daria.
{\it Journal of Surface Investigation: $X$-ray, Synchrotron and Neutron Techniques},
2019, vol.~13~(6), pp. 1126--1131.	 https://doi.org/10.1134/S1027451019060399

% пример ссылки на статью в материалах конференции
8. Kulevoy T., Fatkullin R., Kozlov A., Kropachev G., Selesnev D., Semennikov A., Sitnikov~A.
Compact multipurpose facility --- BELA.
{\it Proceedings of 29$^{th}$ Linear Accelerator Conference},
2018, pp.~349--351.
 https://doi.org/10.18429/JACoW-LINAC2018-TUPO012

9. Balabanov M.~Yu., Mizintseva M.~A., Ovsyannikov D.~A.
Beam dynamics optimization in a linear accelerator.
{\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes},
2018, vol.~14, iss.~1, pp.~4--13.	
 https://doi.org/10.21638/11701/spbu10.2018.101

10. Antropov I.~V., Ovsyannikov A.~D.
Modelirovaniye i optimizatsiya dinamiki chastits v us\-ko\-ri\-tele s prostranstvenno-odnorodnoy kvadrupol'noy fokusirovkoy [Simulation and optimization of particle dynamics in accelerator with spatially uniform quadrupole focusing]. {\it Vestnik of Saint Petersburg University. Series 10. Applied Mathematics. Computer Science. Control Processes},
2009, iss.~4, pp.~3--24.	(In Russian)

11. Balabin ј.~I., Lipkin I.~M., Ugarov S.~B.
O vybore formy elektrodov v lineynom uskoritele s prostranstvenno-odnorodnoy kvadrupol'noy fokusirovkoy [On choosing the electrodes from in linear accelerator with spatially uniform quadrupole focusing].
{\it VANT. Series Technique of physical experiment},
1988, vol.~1~(36), pp.~20--22. (In Russian)	

% пример ссылки на переводную книгу
12. Kapchinsky I.~M.
{\it Teoriya lineynykh rezonansnykh uskoriteley $[$Theory of linear resonance accelerators$]$}.
Moscow,  Energoizdat Publ.,
1982, 241~p. (In Russian)

% пример ссылки на статью в материалах конференции
13. Uriot D.
Status of TraceWin Code.
{\it Proceeding of IPAC},
2015, pp.~92--94. \\
 https://doi.org/10.18429/JACoW-IPAC2015-MOPWA008

% пример ссылки на статью в материалах конференции
14. Bondarev B.~I., Durkin A.~P., Murin B.~P., Nikolaishvili G.~T., Shlygin O.~Yu.
LIDOS --- unconventional helper for linac beam designing.
{\it AIP Conference Proceedings,}
1993, vol.~297, pp.~377--384.
 https://doi.org/10.1063/1.45334

% пример ссылки на электронный ресурс
15.	{\it DACM Software.}
Available at: http://irfu.cea.fr/Sacm/logiciels/ (accessed: June 14, 2022).


\vskip1.5mm Received:  August 19, 2022.

Accepted: September 01, 2022.

\vskip6mm
A~u~t~h~o~r~s' ~ i~n~f~o~r~m~a~t~i~o~n:%
%
\vskip2mm \textit{Gennady N. Kropachev} --- PhD in Physics and Mathematics;  kropachev@itep.ru

\vskip2mm \textit{Timur V. Kulevoy} --- Dr. Sci. in Technics;  kulevoy@itep.ru

\vskip2mm \textit{Alexei L. Sitnikov} --- PhD in Physics and Mathematics;  aleksey.sitnikov@itep.ru

\vskip2mm \textit{Ekaterina R. Khabibullina} ---   Ekaterina.Khabibullina@itep.ru

\vskip2mm \textit{Stanislav V. Vinogradov} --- PhD in Physics and Mathematics; s.vinogradov@gmail.com

 \par
%
%
}
