

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. {Hairer E., N\o{}rsett S.\,P., Wanner G.} \emph{Solving ordinary differential equations~I: Nonstiff prob\-lems}. $2^{\rm nd}$~ed., $3^{\rm rd}$~corr. print. Heidelberg, Berlin, Springer-Verlag Publ., 2008, 528~p.

2. {Butcher J.\,C.} \emph{Numerical methods for ordinary differential equations}. $3^{\rm rd}$~ed. Chichester, UK, John Wiley \& Sons Publ., 2016, 513~p.

3. {Hairer E., Wanner G.} \emph{Solving ordinary differential equations II: Stiff and
differential-algebraic problems}. $2^{\rm nd}$~ed., $2^{\rm rd}$~corr. print. Heidelberg, Berlin, Springer-Verlag Publ., 2002, 614~p.

4. Hofer E. A partially implicit method for large stiff systems of ODEs with
only few equations introducing small time-constants. \emph{SIAM Journal Numerical Analytics}, 1976, vol.~13, iss.~5, pp.~645--663.

5. Kalogiratou Z., Monovasilis T., Simos T.\,E. Symplectic partitioned Runge\,---\,Kutta methods for the numerical integration of periodic and oscillatory
problems. \emph{Recent Advances in Com\-puta\-ti\-onal and
Applied Mathematics}. Dordrecht, Springer Netherlands Publ., 2011, pp.~169--208.

6. Monovasilis T. Symplectic partitioned Runge\,---\,Kutta methods with the
phase-lag property. \emph{Applied Mathematics Comput.}, 2012, vol.~218, iss.~18, pp.~9075--9084.

7. McLachlan R., Ryland B., Sun Y. High order multisymplectic Runge\,---\,Kutta methods. \emph{SIAM Journal Sciences Comput.}, 2014, vol.~36, iss.~5, pp.~A2199--A2226.

8. Shome S.\,S., Haug E.\,J., Jay L.\,O. Dual-rate integration using partitioned
Runge\,---\,Kutta methods for mechanical systems with interacting subsystems. \emph{Mechanics Based Design of Structures and Machines}, 2004, vol.~32, iss.~3, pp.~253--282.

9. Sandu A., G\"unther M. Multirate generalized additive Runge\,---\,Kutta methods. \emph{Numerische Mathematik}, 2016, vol.~133, iss.~3, pp.~497–524.

10. Sandu A. A class of multirate infinitesimal GARK methods. \emph{SIAM Journal Numerical Analytics}, 2019, vol.~57, iss.~5, pp.~2300--2327.

11. Koto T. IMEX Runge\,---\,Kutta schemes for reaction\,---\,diffusion equations. \emph{J. Comput. Appl. Math.}, 2008, vol.~215, iss.~1, pp.~182--195.

12. Ketcheson D.\,I., MacDonald C., Ruuth S.\,J. Spatially partitioned embedded Runge\,---\,Kutta methods. \emph{SIAM Journal Numerical Analytics}, 2013, vol.~51, iss.~5, pp.~2887--2910.

13. Olemskoy I.\,V. Fifth-order four-stage method for numerical integration of
special systems. \emph{Computational Mathematics and Mathematical Physics}, 2002, vol.~42, iss.~8, pp.~1135--1145.

14. Olemskoy I.\,V., Eremin A.\,S., Ivanov A.\,P. Sixth order method with six stages for integrating special systems of ordinary differential equations.
\emph{Proceedings of 2015 Intern. Conference ``Stability and Control Processes'' in
memory of V.\,I. Zubov (SCP)}. St. Petersburg, St. Petersburg University Press, 2015, pp.~110--113.

15. Eremin A.\,S., Kovrizhnykh N.\,A., Olemskoy I.\,V. An explicit one-step multischeme sixth order method for systems of special structure. \emph{Applied Mathematics Computational}, 2019, vol.~347, pp.~853--864.

16. Olemskoy I.\,V. A fifth-order five-stage embedded method of the Dormand\,---\,Prince type. \emph{Computational Mathematics and Mathematical Physics}, 2005, vol.~45, iss.~7, pp.~1140--1150.

17. Olemskoy I.\,V. \emph{Metody integrirovaniya system strukturno razdelyonnykh
differentsialnykh uravnenii} [\emph{Integration of structurally partitioned systems
of ordinary differential equations}]. St. Pe\-ters\-burg, St. Petersburg University Press, 2009, 179~p. (In Russian).

18. Olemskoy I.\,V., Eremin A.\,S. An embedded method for integrating systems of structurally separated ordinary differential equations. \emph{Computational Mathematics and Mathematical Physics}, 2010, vol.~50, iss.~3, pp.~414--427.

19. Eremin A.\,S., Kovrizhnykh N.\,A., Olemskoy I.\,V. Economical sixth order Runge\,---\,Kutta method for systems of ordinary differential equations. \emph{Computational Science and its Applica\-ti\-ons}~--- ICCSA 2019, vol. 11619 of LNCS Springer Series. Cham, Springer Publ., 2019, pp.~89--102.

20. Butcher J.\,C. On Runge\,---\,Kutta processes of high order. \emph{Journal Australian Mathematics Soc.}, 1964, vol.~4, iss.~2, pp.~179--194.

21. Olemskoy I.\,V., Kovrizhnykh N.\,A. A family of sixth-order methods
with six stages. \emph{Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2018, vol.~14, iss.~3, pp.~215--229.

22. Olemskoy I.\,V., Eremin A.\,S. An embedded fourth order method for solving structurally partitioned systems of ordinary differential equations. \emph{Applied Mathematical Sciences}, 2015, vol.~9, iss.~97--100, pp.~4843--4852.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  July 1, 2020.

Accepted: October 13, 2021.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Igor V. Olemskoy} --- Dr.\,Sci. in Physics and Mathematics, Professor; i.olemskoj@spbu.ru \par%

\vskip 2mm \textit{Alexey S. Eremin} --- PhD in Physics and Mathematics, Associate Professor; a.eremin@spbu.ru \par%
%
%
}
