
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Impact of collisions on the dynamics of waves of finite amplitude in a plasma$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it A. R. Karimov$^{1,2,3}$,
V. K. Bogdanov$^{1,2}$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm \indent~$^{*}$ This work was financially supported by the Ministry of Science and Higher Education of the Russian Federation (contract N~075-15-2021-1361 dated October 07, 2021), and within the framework of the grant ``Regulation of structure formation processes in macromolecular compounds under non-equilibrium conditions’’ of the G.~V.~Plekhanov Russian Economic University (order N 657 of June 07, 2021).\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


%\noindent%
%%$^2$~%
%St\,Petersburg State University, 7--9, Universitetskaya nab., %St\,Petersburg,
%
%\noindent%
%%\hskip2.45mm%
%199034, Russian Federation


\noindent%
$^1$~%
National Research Nuclear University ``MEPhI’’, 31, Kashirskoe sh., Moscow,

\noindent%
\hskip2.45mm%
115409, Russian Federation


\noindent%
$^2$~%
G. V. Plekhanov Russian Economic University, 36, Stremyanny per., Moscow,

\noindent%
\hskip2.45mm%
117997, Russian Federation


\noindent%
$^3$~%
Joint Institute for High Temperatures of the Russian Academy of Sciences, 13/19, Izhorskaya ul.,

\noindent%
\hskip2.45mm%
Moscow, 117997, Russian Federation


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:} Karimov A. R.,
Bogdanov V. K. Impact of collisions on the dynamics of waves of finite amplitude in a plasma. {\it Vest\-nik of Saint Pe\-ters\-burg
University. Applied Mathe\-ma\-tics. Com\-pu\-ter
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear,
vol.~18, iss.~\issuenum, pp.~\pageref{p4}--\pageref{p4e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum04 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent The problem of determining wave dynamics, considering the evolution of nonlinear waves of finite amplitude in a weakly collisional, Maxwellian plasma, is the focus of this article. Considering this medium with a certain interaction potential associated with a certain limited core of pairwise interaction, the dynamics of the distribution function was studied using the Vlasov equation. Collisions of electrons with neutral particles are described using the collision integral in the Bhatnagar\,---\,Gross\,---\,Krook form. Having constructed its particular solution and the equilibrium distribution function in the form of a series, an equation was obtained that makes it possible to determine the potential function. Considering the case of a Maxwellian plasma, an integral potential equation was obtained. Based on it, an equation was constructed that determines the perturbation of the potential relative to the spatially homogeneous one. At the same time, this perturbation appears due to the existence of some spatial-temporal stable structure. Based on this, a dispersion relation was obtained, which makes it possible to estimate the spatial scales of the coherent structure.\\[1mm]
\textit{Keywords}: nonideal plasma, weak collisions, coherent structures, waves of finite amplitude.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. Fainberg Ja. B. Uskorenie chastits v plasme [Acceleration of particles in plasma.] \textit{Atomic Energy}, 1959, vol.~6, iss.~4, pp.~431--446. (In Russian)

2. Ashanin~I.~A., Klyuchevskaya~Yu.~D., Makhoro~A.~A., Mekhanikova~V.~Yu., Mosolova~O.~A., Polozov~S.~M., Pronikov~A.~I., Rashchikov~V.~I. Dinamika puchka v lineinom uskoritele-inzhektore Spetsializirovannogo istochnika sinkhrotronnogo izlucheniia 4-go pokoleniia ISSI-4 [Beam dynamics in the linear accelerator-injector of the Specialized source of synchrotron radiation of the $4^{\rm th}$ generation ISSI-4]. \textit{Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathe\-ma\-tics. Computer Science. Cont\-rol Pro\-cesses}, 2019, vol.~15, no.~1, pp.~126--139. %\\
https://doi.org/10.21638/11701/spbu10.2019.110 (In Russian)

3. Kadomtsev B. B. Zatukhanie Landau i echo v plasme [Landau damping and echo in plasma.] \textit{Usp. phys. nauk} [\textit{Successes of Physical Sciences}], 1968, vol.~95, iss.~1, pp.~111--129. (In Russian)

4. Schamel H. Hole equilibria in Vlasov\,---\,Poisson systems: A challenge to wave theories of ideal plasmas. \textit{Phys. Plasmas}, 2000, vol.~7, iss.~12, pp.~4831--4844.

5. Ovsyannikov D. A., Drivotin O. I. \textit{Modelirovanie intensivnykh puchkov zariazhennykh chastits} [\textit{Simulation of intense beams of charged particles}]. St~Pe\-ters\-burg, St~Pe\-ters\-burg State University Press, 2003, 176~p. (In Russian)

6. Diamond P. H., Itoh S.-I., Itoh K.,  Hahm T. S. Zonal flows in plasma~--- a review. \textit{Plasma Phys. Control. Fusion}, 2005, vol.~47, iss.~5, pp.~R35--R161.

7. Rowlands G., Dieckmann M. E., Shukla P. K. The plasma filamentation instability in one di\-men\-sion: nonlinear evolution. \textit{New J. Phys.}, 2007,  vol.~9, iss.~8, no.~247.

8. Polozov S. M. A possible scheme of electron beam bunching in laser plasma accelerators. \textit{NIM A}, 2013, vol.~729, iss.~11, pp.~517--521.

9. Roudskoy I., Kulevoy T. V., Petrenko S. V., Kuibeda R. P., Seleznev~D.~N., Pershin~V.~I., Hershcovitch~A., Johnson~B.~M., Gushenets~V.~I., Oks~E.~M., Poole~H.~P. Bernas ion source discharge simulation.  \textit{Review of Scientific Instruments}, 2008,  vol.~79, iss.~2, p. 02B313.

10. Potanin E. P. Nagrev ionov gadolinievoi plazmy metodom ionnogo tsiklotronnogo rezonansa [Heating of gadolinium plasma ions by the ion cyclotron resonance method]. \textit{Journal of Technical Physics}, 2006, vol.~76, iss.~12, pp.~47--51. (In Russian)

11. Van Kampen N. G. On the theory of stationary waves in plasmas. {\it Physica}, 1955,  vol.~21, pp.~949--963.

12. Case K. M. Plasma oscillations. \textit{Ann. Phys.}, 1959, vol.~7, iss.~3, pp.~349--364.

13. Bernstein I. B., Greene J. M., Kruskal M. D. Exact nonlinear plasma oscillations. {\it Phys. Rev.}, 1957,  vol.~108, iss.~3, pp.~546--549.

14. Villani C. Particle systems and nonlinear Landau damping. \textit {Phys. Plasmas}, 2014, vol.~21, iss.~3, p.~030901.

15. Kaganovich I. D. Effects of collisions and particle trapping on collisionless heating. \textit{Phys. Rev.}, 1999,  vol.~88, iss.~2, pp.~327--330.

16. Zheng J., Qin H. On the singularity of the Vlasov\,---\,Poisson system. \textit{Phys. Plasmas}, 2013, vol.~20, iss.~9, p.~092114.

17. Karimov A. R., Lewis H. R.  Nonlinear solutions of the Vlasov\,---\,Poisson equations. \textit{Phys. Plasmas}, 1999, vol.~6, iss.~3, pp.~759--761.

18. Karimov A. R. Nonlinear solutions of a Maxwellian type for the Vlasov\,---\,Poisson equations. \textit{Phys. Plasmas}, 2001, vol.~8, iss.~5, pp.~1533--1537.

19. Karimov A. R., Bogdanov V. K. Formation of kinetics coherent structures in weakly collisional media. \textit{Plasma}, 2021, vol.~4, iss.~2, pp.~359--365.

20. Vlasov A. A. \textit{Nelokal'naia statisticheskaia mekhanika} [\textit{Nonlocal statistical mechanics}]. Moscow, Nauka Publ., 1978, 264~p. (In Russian)


\vskip1.5mm Received:  April 11, 2022.

Accepted: May 05, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Alexander R. Karimov} --- Dr. Sci. in Physics and Mathematics, Professor; arkarimov@mephi.ru \par
%
\vskip2mm \textit{Vladislav K. Bogdanov} --- bogdanov.starscream@mail.ru \par
%
%
}
