

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Brunner  H. {\it Collocation methods for Volterra integral and
related functional equations}. Cambridge, Cambridge University
Press, 2004, 597~p.

2. Brunner H. {\it Volterra integral equations: An introduction to
theory and  applications}. Cambridge, Cambridge University Press,
2017, 402~p.

3. Brunner H., Van der Houwen P. J. {\it The numerical solution of
Volterra equations}. Amsterdam, Elsevier Science Ltd. Publ.,
1986, 604~p.

4. Linz  P.  {\it Analytical and numerical methods for Volterra
equations}. Philadelphia, SIAM Publ.,  1985, 240~p.

5. Apartsyn A. S.  {\it Nonclassical linear Volterra equations of
the first kind}. Utrecht, VSP Publ., 2003, 168~p.

6. Brunner  H.  1896--1996: One hundred years of Volterra integral
equations of the first kind. {\it Applied Numerical Mathematics},
1997, vol.~24, pp.~83--93.

7. Lamm P. K. A survey of regularization methods for first-kind
Volterra equations.  {\it Surveys on Solution Methods for Inverse
Problems}. Eds by D.~Colton, H.~W.~Engl, H.~K.~Louis,
J.~R.~McLaughlin, W.~Rundell. Vienna, Springer Press, 2000,
pp.~53--82.

8. Ten Men Yan. {\it Priblizhennoe reshenie linejnyh uravnenij
Vol'terra pervogo roda} [{\it Approximate solution of linear
volterra equations of the first kind}]. PhD Thesis. Irkutsk,
V.~M.~Matrosov Institute for System Dynamics and Control Theory of
Siberian Branch of Russian Academy of Sciences Publ., 1985, 97~p.
(In Russian)

9. Von Wolfersdorf L. On identification of memory kernels in
linear theory of heat conduction. {\it Mathematical Methods in
Applied Sciences}, 1994, vol.~17~(12), pp.~919--932.

10. Jumarhon B., Lamb W., McKee S., Tang T. A Volterra integral
type method for solving a class of nonlinear initial-boundary
value problems. {\it Numerical Methods in Partial Differential
Equations}, 1996, vol.~12~(7), pp.~265--281.

11. Gomilko A. A Dirichlet problem for the biharmonic equation in
a semi-infinite strip. {\it Journal of Engineering Mathematics},
2003, vol.~46~(4), pp.~253--268.

12. Liang H., Brunner H. Integral-algebraic equations: theory of
collocation methods, I. {\it SIAM Journal on Numerical Analysis},
2013, vol.~51~(4), pp.~2238--2259.

13.  Zenchuk A. I. Combination of inverse spectral transform
method and method of characteristics: deformed Pohlmeyer equation.
{\it Journal of Nonlinear Mathematical Physics}, 2008, vol.~15,
pp.~437--448.

14. Chistyakov V. F. O vyrozhdennyh sistemah obyknovennyh
differencial'nyh uravnenij i ih integral'nyh analogah [On singular
systems of ordinary differential equations and their integrals
analogues]. {\it Lyapunov Functions and Applications}.
Novosibirsk, Nauka Publ., 1987, pp.~231--239. (In Russian)

15. Gear C. W.  Differential algebraic equations, indices, and
integral algebraic equations. {\it SIAM Journal on Numerical
Analysis}, 1990, vol.~27~(6), pp.~1527--1534.

16. Kauthen J. P. The numerical solution of integral-algebraic
equations of index 1 by polynomial spline collocation methods.
{\it Mathematics of Computation}, 2001, vol.~70~(236),
pp.~1503--1514.

17. Hadizadeh M., Ghoreishi F., Pishbin S.  Jacobi spectral
solution for integral algebraic equations of index-2.  {\it
Applied Numerical Mathemathics}, 2011, vol.~61~(1), pp.~131--148.

18. Pishbin S., Ghoreishi F., Hadizadeh M. A posteriori error
estimation for the Legendre collocation method applied to
integral-algebraic Volterra equations. {\it Electronic
Transactions on Numerical Analysis}, 2011, vol.~38, pp.~327--346.

19. Pishbin S., Ghoreishi F.,  Hadizadeh M. The semi-explicit
Volterra integral algebraic equations with weakly singular
kernels: the numerical treatments. {\it Journal of Computational
and Applied Mathematics}, 2013, vol.~245, pp.~121--132.

20. Budnikova O. S., Bulatov M. V.  Numerical solution of
integral-algebraic equations of  multi\-step methods. {\it Journal
of Computational Mathematics and Mathematical  Physics}, 2012,
vol.~52~(5),\linebreak pp.~691--701.

21. Balakumar V., Murugesan K. Numerical solution of Volterra
integral-algebraic equations using block pulse functions. {\it
Applied Mathematics and Computation}, 2015, vol.~265,
pp.~165--170.

22. Bulatov M. V.  Regularization of singular systems of Volterra
integral equations. {\it Journal of Computational Mathematics and
Mathematical  Physics}, 2002, vol.~42~(3), pp.~315--320.

23. Liang H., Brunner H. Integral-algebraic equations: theory of
collocation methods, II.  {\it SIAM  Journal on Numerical
Analysis}, 2016, vol.~54~(4), pp.~2640--2663.

24. Chistyakov V. F. {\it Algebro-differencial'nye operatory s
konechnomernym yadrom} [{\it Al\-ge\-braic-differential operators
with a finite-dimensional kernel}]. Novosibirsk, Nauka Publ.,
1996, 278~p. (In Russian)

25. Bulatov M. V., Chistyakov V. F. {\it The properties of
differential-algebraic systems and their integral analogues}.
Preprint. Newfoundland,  Memorial University of Newfoundland
Press, 1997, 80~p.

26. Mehrmann V.  Index concepts for differential-algebraic
equations. {\it Encyclopedia of Applied and Computational
Mathematics}. Ed. by B.~Engquist. Berlin, Springer Press, 2012,
p.~21.

27. Gantmacher  F. R. {\it The theory of matrices}. Vol.~I. New
York, Chelsea Publ. Company, 1960, 277~p.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  May 06, 2019.

Accepted: June 06, 2019.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 1.5mm%2mm
\textit{Mikhail V. Bulatov} --- Dr. Sci. in Physics
and Mathematics, Professor; mvbul@icc.ru

\vskip 1.5mm%2mm
\textit{Mahmoud Hadizadeh} --- PhD in Physics and Mathematics,
Associate Professor; hadizadeh@kntu.ac.ir

\vskip 1.5mm%2mm
\textit{Elena V. Chistyakova} --- PhD in Physics and Mathematics,
Fellow Researcher; chistyak@gmail.com

}
