
{\small

\vskip6mm \noindent \textbf{Литература}

}

\vskip3mm

{\footnotesize

1. \textit{Евтушенко Ю. Г., Посыпкин М. А.} Варианты метода
неравномерных покрытий для глобальной оптимизации
частично-целочисленных нелинейных задач // Докл. Академии наук.
2011. Т.~437. № 2. С.~168--172.

2. \textit{Karnopp D. C.} Random search techniques for
optimization problems // Automatica. 1963. Vol.~1.  N 2--3.
P.~111--121.

3.  \textit{Solis F. J., Wets R. J.-B.} Minimization by random
search techniques // Mathematics of operations research. 1981.
Vol. 6. N 1. P.~19--30.

4. \textit{Pag\`{e}s G.} The Quasi-Monte Carlo Method // Numerical
Probability.  Cham: Springer, 2018.\linebreak P.~95--132.

5. \textit{Owen A. B., Glynn P. W.} Monte Carlo and Quasi-Monte
Carlo methods. California: Springer, 2016. P.~1--478.

6. \textit{Bousquet O., Gelly S., Kurach K.} et al. Critical
hyper-parameters: No random, no cry. arXiv Preprint arXiv:
1706.03200.  2017. URL: \url{https://arxiv.org/abs/1706.03200}
(дата обращения: 15.05.2019~г.).

7. \textit{Halton J. H.} Algorithm 247: Radical-inverse
quasi-random point sequence  // CACM. 1964. Vol.~7. N~12.
P.~701--702.

8. \textit{Muniraju G., Kailkhura B., Thiagarajan J., Bremer P.
T.} Controlled random search improves sample mining and
hyper-parameter optimization. arXiv Preprint arXiv: 1809.01712v1.
2018. URL: \url{https://arxiv.org/abs/1706.03200} (дата обращения:
15.05.2019~г.).

9. \textit{Gerstner T., Griebel M.} Sparse grids // Encyclopedia
of Quantitative Finance. 2010. P.~1--6. URL:
\url{https://doi.org/10.1002/9780470061602.eqf12011} (дата
обращения:  21.05.2019~г.).

10. \textit{Sobol I. M., Asotsky D., Kreinin A., Kucherenko K.}
Construction and comparison of high-dimensional Sobol' generators
// Wilmott. 2011. Vol.~2011. N~56. P.~64--79.

11. \textit{Соболь И. М.} Точки, равномерно заполняющие
многомерный куб. М.: Знание, 1985. 125~с.

12. \textit{Hickernell F. J., Yuan Y.} A simple multistart
algorithm for global optimization // CiteSeerX Рreprint. 1997.
URL:
\url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.46.1346}
(дата обращения: 10.05.2019~г.).

13. \textit{Mart\'{i} R., Lozano J. A., Mendiburu A., Hernando L.}
Multi-start methods // Handbook of Heuristics. Cham: Springer,
2016. P.~1--21.

14. \textit{Mart\'{i} R., Moreno-Vega J. M., Duarte A.} Advanced
multi-start methods // Handbook of Metaheuristics.  Boston:
Springer, 2010. P.~265--281.

15. \textit{Mart\'{i} R., Aceves R., Leonet M. T.}  et al.
Intelligent multi-start methods
// Handbook of Metaheuristics. Cham: Springer, 2019. P.~221--243.

16. \textit{Горчаков А. Ю., Посыпкин М. А.} Эффективность методов
локального поиска в~задаче минимизации энергии плоского кристалла
// Современные информационные технологии и~ИТ-образование. 2017.
Т.~13. №~2. C.~97--102.

17. \textit{McKay M. D., Beckman R. J., Conover W. J.} Comparison
of three methods for selecting values of input variables in the
analysis of output from a computer code // Technometrics. 1979.
Vol.~21. N~2. P.~239--245.

18. \textit{Hofer R., Ktitzer P., Larcher G., Pillichshammer F.}
Distribution properties of generalized van der Corput---Halton
sequences and their subsequences
// International Journal of Number Theory. 2009. Vol.~5. N~4.
P.~719--746.

\sloppy 19. \textit{Lambert J. P.} Quasi-Monte Carlo, low
discrepancy sequences, and ergodic transformations // Journal of
Computational and Applied Mathematics. 1985. Vol.~12. P.~419--423.

20. \textit{Faure H.} Discr\'{e}pance de suites associ\'{e}es
\`{a} un syst\`{e}me de num\'{e}ration (en dimensions) // Acta
arithmetica. 1982. Vol.~41. N~4. P.~337--351.

21. \textit{Niederreiter H.} Random number generation and
quasi-Monte Carlo methods. Philadelphia: Siam, 1992. Vol.~63.
242~p.

22. \textit{Лурье С. А., Соляев Ю. О., Посыпкин М. А.} Метод
идентификации масштабных параметров градиентной теории упругости
на основе численных экспериментов для плоских композитных структур
// International Journal of Open Information Technologies. 2015.
Vol.~3. N~6. P.~1--5.

23. \textit{Евтушенко Ю. Г., Лурье С. А., Посыпкин М. А.}
Применение методов оптимизации для поис\-ка равновесных состояний
двумерных кристаллов
// Журн. вычисл. математики и~матем. физики. 2016. Т.~56. №~12.
С.~2032--2041.

24. \textit{Амирханова Г. А., Горчаков А. Ю., Дуйсенбаева А. Ж.,
Посыпкин М. А.} Применение метода точных штрафных функций к~задаче
минимизации энергии плоского кристалла // XIV Междунар. Азиатская
школа-семинар «Проблемы оптимизации сложных систем», 20--31 июля
2018 г., Кыргызская Республика, оз. Иссык-Куль. Алматы: Ин-т
информ. и~вычисл. технологий МОН РК,  2018. С.~107--113.

25. \textit{Амирханова Г. А., Горчаков А. Ю., Дуйсенбаева А. Ж.}
Гибридизация методов Монте-Карло, имитации отжига и~локального
поиска // III Междунар. науч. конференция «Информатика
и~прикладная математика», 26--29  сентября 2018 г. Алматы,
Казахстан. 2018. С.~266--274.

26. \textit{Amirkhanova G., Gorchakov A., Duysenbaeva A.} The
application of the methodology of fast automatic differentiation
to calculate the gradient of the potential REBO (LAMMPS) //
DEStech Transactions on Computer Science and Engineering. 2018. N.
optim. P.~103--113.

27. \textit{Plimpton S.} Fast parallel algorithms for short-range
molecular dynamics // Journal of Computational Physics. 1995. Vol.
117. N~1. P.~1--19.

28. \textit{Plimpton S., Crozier P., Thompson A.}
Lammps-large-scale atomic/molecular massively parallel simulator
// Sandia National Laboratories. 2007. Vol.~18. P.~43.

29. \textit{Wright S. J.} Coordinate descent algorithms //
Mathematical Programming. 2015. Vol.~151. N~1. P.~3--34.

30. \textit{Khamisov O. V., Posypkin M.} Univariate global
optimization with point-dependent Lipschitz constants // AIP
Conference Proceedings / AIP Publishing. 2019. Vol.~2070. P.~1--4.

31. \textit{Khamisov O., Posypkin M., Usov A.} Piecewise linear
bounding functions for univariate global optimization //
International Conference on Optimization and Applications. Cham:
Springer, 2018.\linebreak P.~170--185.

32. \textit{Piyavskii S. A.} An algorithm for finding the absolute
extremum of a function // USSR Computational Mathematics and
Mathematical Physics. 1972. Vol.~12. N~4. P.~57--67.

33. \textit{Hansen P., Jaumard B., Lu Shi-Hui.} Global
optimization of univariate lipschitz functions:~I. Survey and
properties // Mathematical Programming. 1992. Vol.~55. N~1--3.
P.~251--272.

34. \textit{Tersoff J.} Modeling solid-state chemistry:
Interatomic potentials for  multicomponent systems // Physical
Review. B. 1989. Vol.~39. N~8. P.~55--66.

35. \textit{Evtushenko Y. G., Posypkin M. A., Sigal I.} A
framework for parallel large-scale global optimization // Computer
Science-Research and Development. 2009. Vol. 23. N~3--4.
P.~211--215.

36. \textit{Bychkov I. V., Manzyuk M. O., Semenov A. A.} et al.
Technology for integrating idle computing cluster resources into
volunteer computing projects
// 2015 5th International Workshop on Computer Science and
Engineering: Information Processing and Control Engineering, WCSE
2015--IPCE. 2015. P.~109--114.

37. \textit{Posypkin M., Usov A.} Implementation and verification
of global optimization benchmark problems // Open Engineering.
2017. Vol.~7. N~1. P.~470--478.



\pagebreak
%\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. Л. А. Петросяном.
%
%\vskip 1.5mm

Статья поступила в~редакцию 31 мая 2019~г.

Cтатья принята к~печати 28 мая 2020~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Амирханова Гульшат Аманжоловна} --- %
канд. физ.-мат. наук, ст. науч. сотр.;\\ gulshat.aa@gmail.com

\vskip2mm \textit{Горчаков Андрей Юрьевич}~--- канд. физ.-мат. наук, ст. науч. сотр.;
andrgor12@gmail.com

\vskip2mm \textit{Дуйсенбаева Айгерим Жанболатовна} --- %
%канд. физ.-мат. наук;
aigerim.95.05@mail.ru

\vskip2mm \textit{Посыпкин Михаил Анатольевич}~--- д-р физ.-мат. наук, гл. науч. сотр.;
mposypkin@gmail.com

}
