
{\small

\vskip6 mm \noindent \textbf{Литература}

}

\vskip2 mm

{\footnotesize

1. {\it Fominyh A. V.} Open-loop control of a plant described by a
system with nonsmooth right-hand side~// Computational Mathematics and Mathematical Physics. 2019. Vol.~59. Iss.~10. P.~1639--1648.

2. {\it Frankowska H.} The first order necessary conditions
for nonsmooth variational and control problems~// SIAM J. Control Optim. 1984.
Vol.~22. N~1. P.~1--12.

3.  {\it Ioffe A. D.} Necessary conditions in nonsmooth optimization~// Mathematics of Operations Research. 1984. Vol.~9. N~2. P.~159--189.

4. {\it Mordukhovich B.} Necessary conditions for optimality in
nonsmooth control problems with nonfixed time~// Differential Equations.
1989. Vol.~25. N~1. P.~290--299.

5.  {\it Shvartsman I. A.} New approximation method in the proof
of the maximum principle for nonsmooth optimal control problems with state constraints~// Journal of Mathematical Analysis and Applications. 2007. Vol.~326. N~2. P.~974--1000.

6. {\it Vinter R. B., Cheng H.} Necessary conditions for optimal
control problems with state constraints~// Transactions of the American Mathematical Society.
1998. Vol.~350. N~3. P.~1181--1204.

7. {\it Vinter R. B.} Minimax optimal control~//
SIAM J. Control Optim. 2005. Vol.~44. N~3. P.~939--968.


8.  {\it Gorelik V. A., Tarakanov A. F.} Penalty method and
maximum principle for nonsmooth variable-structure control
problems~// Cybernetics and Systems Analysis. 1992. Vol.~28.
Iss.~3. P.~432--437.

9.  {\it Gorelik V. A., Tarakanov A. F.} Penalty method for
nonsmooth minimax control problems with interdependent
variables~// Cybernetics. 1989. Vol.~25. Iss.~4.
P.~483--488.\pagebreak

10.  {\it Моржин О. В.} Об аппроксимации субдифференциала негладкого штрафного функционала в задачах оптимального управления~// Автоматика и телемеханика. 2009. №~5. С.~24--34.

11. {\it Demyanov V. F., Nikulina V. N., Shablinskaya I. R.}
Quasidifferentiable functions in optimal control~// Mathematical Programming Study.
1986. Vol.~29. P.~160--175.

12. {\it Демьянов В. Ф., Рубинов А. М.}
Основы негладкого анализа и квазидифференциальное исчисление. М.: Наука, 1990. 432~с.

13. {\it Demyanov V. F., Tamasyan G. Sh.} Direct methods in the parametric
 moving boundary
varia\-tional problem~// Numerical Functional Analysis and
Optimization. 2014. Vol.~35. Iss.~7--9. P.~932--961.

14. {\it Fominyh A. V., Karelin V. V., Polyakova L. N.}
Application of the hypodifferential descent method to the problem of
constructing an optimal control~// Optimization Letters. 2018. Vol.~12. N~8. P.~1825--1839.

15. {\it Fominyh A. V.} Methods of subdifferential and
hypodifferential descent in the problem of constructing an integrally
constrained program control~// Automation and Remote Control. 2017. Vol.~78. Iss.~4. P.~608--617.

16. {\it Polyakova  L. N.} On global unconstrained minimization of the difference of polyhedral functions~//
Journal of Global Optimization. 2011. Vol.~50. P.~179--195.

17. {\it Demyanov V. F., Bagirov A. M., Rubinov A. M.} A method of
truncated codifferential with ap\-pli\-cations to some problems of
cluster analysis~// Journal of Global Optimization. 2002. Vol.~23.
P.~63--80.

18.  {\it Dolgopolik M. V.} The method of codifferential descent for
convex and global piecewise affine optimization~//
Optimization Methods and Software. 2020. Vol.~35. Iss.~6. P.~1191--1222.

19. {\it Loxton R. C., Teo K. L., Rehbocka V., Yiu K. F. C.}
Optimal control problems with a continuous inequality constraint on the state and the control~// Automatica. 2009. Vol.~45. P.~2250--2257.

20. {\it Teo K. L., Goh C. J., Wong K. H.} A unified computational
 approach to optimal control problems. New York: Longman Scientific and Technical, 1991. 356~p. (Pitman Monographs and Surveys in Pure and Applied Mathematics)

21. {\it Васильев Ф. П.} Методы оптимизации. М.: Факториал,
2002. 824~с.

22. {\it Filippov A. F.} On certain questions in the theory of optimal control~//
J. SIAM Control. Ser.~A~1. 1962. P.~76--84.

23. {\it Gorokhovik V. V., Zorko O. I.} Piecewise affine functions
and polyhedral sets~// Optimization. 1994. Vol.~31. P.~209--221.

24. {\it Dolgopolik M. V.} A unifying theory of exactness of linear
penalty functions~// Optimization. 2015. Vol.~65. N~6. P.~1167--1202.

25. {\it Dolgopolik M. V.} Exact penalty functions
for optimal control problems. II. Exact penalization of terminal and pointwise
state constraints~// Optimal Control Applications and Methods. 2020. Vol.~41. Iss.~3. P.~898--947.

26. {\it Алексеев В. М., Тихомиров В. М., Фомин С. В.}
Оптимальное управление. М.:~Наука, 1979. 432~с.


\vskip 1.3mm

% Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 15 августа 2020~г.

Cтатья принята к~печати 15 января 2021~г.

\vskip4.2mm К~о~н~т~а~к~т~н~а~я \ и~н~ф~о~р~м~а~ц~и~я:

%\vskip1.8mm%2mm

\vskip2mm\textit{Фоминых Александр Владимирович}  --- канд. физ.-мат. наук, доц.; alexfomster@mail.ru

\vskip2mm\textit{Карелин Владимир Витальевич}  --- канд. физ.-мат. наук, доц.; vlkarelin@mail.ru

\vskip2mm\textit{Полякова Людмила Николаевна}  --- д-р физ.-мат. наук, проф.; lnpol07@mail.ru

\vskip2mm\textit{Мышков Станислав Константинович}  --- канд. физ.-мат. наук, доц.; skmyshkov@mail.ru

\vskip2mm\textit{Трегубов Владимир Петрович}  --- д-р физ.-мат. наук, проф.; v.tregubov@spbu.ru\par
%
}
