
{\normalsize

\vskip 6mm

\noindent{\bf The codifferential descent method in the problem of finding the global\\ minimum of a piecewise affine objective functional in linear control systems$^*$%
}

}

\vskip 3%2
mm

{\small

\noindent{\it A. V. Fominyh, V. V. Karelin, L. N. Polyakova, S. K. Myshkov,  V. P. Tregubov%$^{1,4}$%
%, I.~О. Famylia%$~^2$%

 }

\vskip 3%2
mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
%\vspace{-3mm}%
\parindent=7mm
%%
%\vskip 0.0mm
\hskip 4mm$^{*}$ This work was supported by the Russian Science Foundation (project N 20-71-10032).%\par
%%
%%\vskip 2.0mm
%%
%\indent{\copyright} Санкт-Петербургский государственный
%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St.~Petersburg State University, 7--9, Universitetskaya nab.,
St.~Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip2.0mm%3mm

\noindent \textbf{For citation:} Fominyh A. V., Karelin V. V., Polyakova L. N., Myshkov S. K., Tregubov V. P.  The codifferential descent method in the problem of finding the global minimum of a piecewise affine objective functional in linear control systems. {\it Vestnik of Saint~Peters\-burg Uni\-versity.
Applied Mathematics. Computer Science. Control Processes},
\issueyear,
vol.~17, iss.~\issuenum, pp.~\pageref{p5}--\pageref{p5e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05  (In Russian)

\vskip2.0%3
mm

{\leftskip=7mm\noindent The article considers the problem of optimal control of an object described by a linear nonstationary system and with a piecewise affine quality functional. The problem is examined in Mayer’s form with both free and partially fixed right endpoints. Piecewise continuous and bounded controls that lie in some parallelepiped at each moment of time are admissible. The standard discretization of the original system and the control parametrization are used, some convergence theorems of the discrete problem solution to the continuous problem solution are presented. Further, for the obtained discrete system, the necessary and sufficient minimum conditions are written out in terms of the codifferential, the method of the modified codifferential descent is applied to it, which guarantees to find the global minimum of this problem in a finite number of steps. The proposed algorithm is illustrated with examples.\\[1mm]
\textit{Keywords}: nonsmooth optimal control problem, piecewise affine function, codifferential, parametrization of control, method of codifferential descent method.
\par}

\vskip 6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize

1.  Fominyh A. V. Open-loop control of a plant described by a
system with nonsmooth right-hand side. {\it Computational Mathematics and Mathematical Physics}, 2019, vol.~59, iss.~10, pp.~1639--1648.

2. Frankowska H. The first order necessary conditions for nonsmooth variational and control problems. {\it SIAM J. Control Optim.}, 1984, vol.~22, no.~1, pp.~1--12.

3. Ioffe A. D. Necessary conditions in nonsmooth optimization. {\it Mathematics of Operations Research}, 1984, vol.~9, no.~2, pp.~159--189.

4. Mordukhovich B. Necessary conditions for optimality in nonsmooth control problems with nonfixed time. {\it Differential Equations}, 1989, vol.~25, no.~1, pp.~290--299.

5.  Shvartsman I. A. New approximation method in the proof of the maximum principle for nonsmooth optimal control problems with state constraints. {\it Journal of Mathematical Analysis and Applications}, 2007, vol.~326, no.~2, pp.~974--1000.

6. Vinter R. B., Cheng H. Necessary conditions for optimal control problems with state constraints. {\it Transactions of the American Mathematical Society}, 1998, vol.~350, no.~3, pp.~1181--1204.

7. Vinter R. B. Minimax optimal control. {\it SIAM J. Control Optim.}, 2005, vol.~44, no.~3, pp.~939--968.

8.  Gorelik V. A., Tarakanov A. F. Penalty method and maximum principle for nonsmooth variable-structure control problems. {\it Cybernetics and Systems Analysis}, 1992, vol.~28, iss.~3, pp.~432--437.

9. Gorelik V. A., Tarakanov A. F. Penalty method for nonsmooth minimax control problems with interdependent variables. {\it Cybernetics}, 1989, vol.~25, iss.~4, p.~483--488.


10. Morzhin O. V. Ob approksimatsii subdifferentsiala negladkogo
shtrafnogo funktsionala v zadachakh optimal'nogo upravleniia [On
approximation of the subdifferential of the nonsmooth penalty
functional in the problems of optimal control]. {\it Avtomatika i
telemekhanika} {\it $[$Automation  and Tele\-mecha\-nics}], 2009,
no.~5, pp.~24--34. (In Russian)

11. Demyanov V. F., Nikulina V. N., Shablinskaya I. R. Quasidifferentiable functions in optimal control. {\it Mathematical Programming Study}, 1986, vol.~29, pp.~160--175.

12. Demyanov V. F., Rubinov A. M. {\it Osnovy negladkogo analiza i kvazidifferentsial'noe ischislenie} [{\it Foundations of nonsmooth analysis and quasidifferential calculus}]. Moscow, Nauka Publ., 1990, 432~p. (In Russian)

13. Demyanov V. F., Tamasyan G. Sh. Direct methods in the parametric
 moving boundary
variational problem. {\it Numerical Functional Analysis and Optimization}, 2014, vol.~35, iss.~7--9, pp.~932--961.

14. Fominyh A. V., Karelin V. V., Polyakova L. N. Application of the hypodifferential descent method to the problem of
constructing an optimal control. {\it Optimization Letters}, 2018, vol.~12, no.~8, pp.~1825--1839.

15. Fominyh A. V. Methods of subdifferential and hypodifferential descent in the problem of constructing an integrally
constrained program control. {\it Automation and Remote Control}, 2017, vol.~78, iss.~4, pp.~608--617.

16. Polyakova  L. N. On global unconstrained minimization of the difference of polyhedral functions.
{\it Journal of Global Optimization}, 2011, vol.~50, pp.~179--195.


17. Demyanov V. F., Bagirov A. M., Rubinov A. M. A method of
truncated codifferential with ap\-pli\-cations to some problems of
cluster analysis. {\it Journal of Global Optimization}, 2002,
vol.~23, pp.~63--80.

18. Dolgopolik M. V. The method of codifferential descent for
convex and global piecewise affine optimization. {\it
Optimization Methods and Software}, 2020, vol.~35, iss.~6, pp.~1191--1222.

19. Loxton R. C., Teo K. L., Rehbocka V., Yiu K. F. C. Optimal control problems with a continuous inequality constraint on the state and the control. {\it Automatica}, 2009, vol.~45, pp.~2250--2257.

20. Teo K. L., Goh C. J., Wong K. H. {\it A unified computational
 approach to optimal control problems}. New York, Longman Scientific and Technical Publ., 1991. 356~p. (Pitman Monographs and Surveys in Pure and Applied Mathematics)

21. Vasil'ev F. P. {\it Metody optimizatsii}  [{\it Optimization methods}]. Moscow, Factorial Publ., 2002. 824~p. (In Russian)

22. Filippov A. F. On certain questions in the theory of optimal
control. {\it  J. SIAM Control, Ser.~A~1}, 1962, pp.~76--84.

23. Gorokhovik V. V., Zorko O. I. Piecewise affine functions
and polyhedral sets.  {\it Optimization}, 1994, vol.~31, pp.~209--221.

24. Dolgopolik M. V. A unifying theory of exactness of linear
penalty functions. {\it Optimization}, 2015, vol.~65, no.~6, pp.~1167--1202.

25. Dolgopolik M. V. Exact penalty functions
for optimal control problems. II. Exact penalization of terminal and pointwise
state constraints. {\it Optimal Control Applications and Methods}, 2020, vol.~41, iss.~3, pp.~898--947.

26. Alekseev V. M., Tikhomirov V. M., Fomin S. V. {\it Optimal'noe upravlenie} [{\it Optimal control}]. Moscow, Nauka Publ., 1979, 432~p. (In Russian)



\vskip 1.5mm

Received:  August 15, 2020.

Accepted: January 15, 2021.


\vskip6 mm A~u~t~h~o~r~s' \ i~n~f~o~r~m~a~t~i~o~n:


\vskip2 mm \textit{Alexander V. Fominyh}  --- PhD in Physics and
Mathematics, Associate Professor; alexfomster@mail.ru

\vskip2 mm \textit{Vladimir V. Karelin}  ---  PhD in Physics and
Mathematics, Associate Professor; vlkarelin@mail.ru

\vskip2 mm \textit{Lyudmila N. Polyakova}  --- Dr. Sci. in Physics
and Mathematics, Professor; lnpol07@mail.ru

\vskip2 mm \textit{Stanislav K. Myshkov}  ---  PhD in Physics and
Mathematics, Associate Professor; skmyshkov@mail.ru

\vskip2 mm \textit{Vladimir P. Tregubov}  ---  Dr. Sci.  in Physics and
Mathematics, Professor; v.tregubov@spbu.ru\par
%
}
