

{\small



\vskip6 mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



%{Kras}
1. Krasovskii N. N. {\it Nekotorye zadachi teorii ustoichivosti dvizheniya} [{\it Some problems in the theory of motion stability}]. Moscow, Fizmatlit Publ., 1959, 211~p. (In Russian)

2. Alexandrova I. V., Zhabko A. P. Funkcionaly Lyapunova\,---\,Krasovskogo dlya odnorodnyh sistem s neskol'kimi zapazdyvaniyami [Lyapunov\,---\,Krasovskii functionals for homogeneous systems with multiple delays]. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~2, pp.~183--195. %\\
https://doi.org/10.21638/11701/spbu10.2021.208 (In Russian)

%{Ras}
3. Razumikhin B. S. On stability of delayed systems. {\it J. Appl. Math. Mech.}, 1956, vol.~56, no.~2, pp.~500--512.

%{Ras1}
4. Razumikhin B. S. The application of Lyapunov’s method to problems in the stability of systems with delay. {\it Autom. Remote Control}, 1960, vol.~21, no.~6, pp.~740--748.

%{AJ2015}
5. Medvedeva I. V., Zhabko A. P. Synthesis of Razumikhin and Lyapunov\,---\,Krasovskii approaches to stability analysis of time-delay systems. {\it Automatica}, 2015, vol.~51, no.~1, pp.~372--377.

%{AJ2018}
6. Alexandrova I. V., Zhabko A. P. At the junction of Lyapunov\,---\,Krasovskii and Razumikhin approaches. {\it 15 Jul. 2018 IFAC-PapersOnLine}, 2018. %\\
https://doi.org/10.1016/j.ifacol.2018.07.214

%{AJ2019}
7. Alexandrova I. V., Zhabko A. P. Lyapunov direct method for homogeneous time delay systems. {\it 15 Dec. 2019 IFAC-PapersOnLine}, 2019. %\\
https://doi.org/10.1016/j.ifacol.2019.12.210

%{Zub}
8. Zubov V. I. {\it Kolebaniya i volny} [{\it Oscillations and waves}]. Leningrad, Leningrad State University Press, 1989, 416~p. (In Russian)

%{Kup}
9. Kuptsova S. E. Asimptoticheskie invariantnye mnozhestva [Asymptotically invariant sets]. {\it Trudy 37~Mezh\-du\-na\-rod\-noi konferencii ``Protsessy upravleniya i ustoichivosti’’} [{\it Proceedings 37$^{th}$~Intern. Con\-fe\-ren\-ce ``Control Processes and Stability’’}], 2006, pp.~50--56. (In Russian)

%{Kup1}
10. Kuptsova S. E. On asymptotic behavior of the solutions of systems of nonlinear time-varying differential equations. {\it Middle Volga Mathematical Society Journal}, 2006, vol.~8, no.~1, pp.~235--243.

%{ZTCh}
11. Zhabko A. P., Tikhomirov O. G., Chizhova O. N. Ustoichivost' asimptoticheskogo polozheniya pokoya vozmushchyonnyh odnorodnyh nestatsionarnyh sistem [Stability of asym\-p\-totic equilibrium of perturbed homogeneous time-varying systems]. {\it Middle Volga Mathematical Society Journal}, 2018, vol.~20, no.~1, pp.~13--22. (In Russian)

%{KKS2018}
12. Kuptsova S. E., Kuptsov S. Yu., Stepenko N. A. O predel'nom povedenii reshenii sistem dif\-fe\-ren\-tsial'nykh urav\-ne\-nii s zapazdyvaiushchim argumentom [On the limiting behavior of the solutions of sys\-tems of dif\-fe\-ren\-tial equations with delayed argument].{\it Vestnik of Saint Petersburg University. Applied Ma\-the\-ma\-tics. Com\-pu\-ter Science. Control Processes}, 2018, vol.~14, iss.~2, pp.~173--182. \\
https://doi.org/10.21638/11701/spbu10.2018.205 (In Russian)

%{ZKS2018}
13. Zaranik U. P., Kuptsova S. E., Stepenko N. A. Dostatochnye usloviya sushchestvovaniya asimp\-to\-ti\-cheskogo polozheniya pokoya v sistemah s zapazdyvaniem [Sufficient conditions for the existence of an asymp\-to\-tic quies\-cent position in time-delay systems]. {\it Middle Volga Mathematical Society Journal}, 2018, vol.~20, no.~2, pp.~175--186. (In Russian)

%{KKS2019}
14. Kuptsova S. E., Stepenko N. A., Kuptsov S. Yu. Sufficient conditions for the existence of asymp\-to\-tic quiescent position for one class of differential-difference systems. {\it Automation and Remote Cont\-rol}, 2019, vol.~80, pp.~1016--1025. %\\
https://doi.org/10.1134/S000511791906002X

15. Kharitonov V. L. Time-delay systems: Lyapunov functionals and matrices. Basel, Birkh\"{a}user, 2013, 322~p.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  November 19, 2021.

Accepted: May 05, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:


\vskip 2mm \textit{Svetlana E. Kuptsova} --- PhD in Physics and
Mathematics, Associate Professor; sekuptsova@yandex.ru \par

\vskip 2mm \textit{Sergey Yu. Kuptsov} --- PhD in Physics and Mathematics, Mathematician-Programmer;\\ srgkuptsov@yandex.ru \par
%
}
