{\footnotesize

\vskip 4mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 3mm


1. Zyryanov~V.~V., Kocherga~V.~G., Pozdnyakov~M.~N. Sovremennye
podhody k razrabotke kompleksnyh skhem organizacii dorozhnogo
dvizheniya [Modern approaches to development of complex traffic
management schemes]. {\em Transport of Russian Federation}, 2011,
no.~1(32), pp.~54--59. (In Russian)

2. Farahani~R.~Z., Miandoabchi~E., Szeto~W.~Y., Rashidi~H. A
review of urban transportation network design problems. {\em
European Journal of Operational Research}, 2013, no.~229,
pp.~281--302.

3. Wardrop~J.~G. Some theoretical aspects of road traffic
research. {\em Proc. Institution of Civil Engineers}, 1952,
vol.~2, pp.~325--378.

4. Beckmann~M.~J., McGuire~C.~B., Winsten~~C.~B. {\em Studies in
the economics of transportation}. New Haven, CT, Yale University
Press, 1956, 359~p.

5. Sheffi~Y. {\em Urban transportation networks: equilibrium
analysis with mathematical programming methods}. New Jersey,
Prentice-Hall Inc., Englewood Cliffs Publ., 1985, 416~p.

6. Yang~H., Huang~H.-J. The multi-class, multi-criteria traffic
network equilibrium and systems optimum problem. {\em
Transportation Research. Pt B}, 2004, vol.~38, pp.~1--15.

7. {\em Vvedenie v matematicheskoe modelirovanie transportnyh
potokov $[$Introduction to mathematical modelling of traffic
flows}]. Pod red. V.~A.~Druzhininoj, I. A.~Volkovoj. Moscow,
Moscow phys. and techn. University Publ., 2010, 360~p. (In
Russian)

8. Krylatov~A.~Yu. Optimalnye strategii upravleniya transportnymi
potokami na seti iz parallelnyh kanalov [Optimal strategies for
traffic flow management on the transportation network of parallel
links]. {\em Vestnik of Saint Petersburg State University.
Series~10. Applied Mathematics. Computer Sciences. Control
Processes}, 2014, iss.~2, pp.~121--130. (In Russian)



\vskip 2mm

{\bf For citation:}  Krylatov A.~Yu. Optimal strategies for road
network's capacity allocation. {\it Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p5}--\pageref{p5e}.
\doivyp/spbu10.\issueyear.\issuenum05


}
