

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {Duan H.\,L., Weissm\"{u}ller J.,  Wang Y.}
Instabilities of core-shell heterostructured cylinders due to diffusion and epitaxy: spheroidization and blossom of nanowires.
{\it Journal of the Mechanics and Physics of Solids}, 2008, vol.~56, pp.~1831--1851.

2. {Erd\'{e}lyi Z., Beke D.\,L., Langer G.}
Interface kinetics and morphology on the nanoscale.
{\it Vacuum}, 2010, vol.~84, pp.~26--31.

3. {Romanova V.\,A., Balokhonov R.\,R.}
Numerical analysis of mesoscale surface roughening in a coated plate.
{\it Computational Materials Science}, 2012, vol.~61, pp.~71--75.

4. {Huang Y., Chen H., Wu J., Feng X.}
Controllable wrinkle configurations by soft micro-patterns to enhance the stretchability of Si ribbons.
{\it Soft Matter}, 2014, vol.~10, pp.~2559--2566.

5. {Kim H.\,K., Lee S.\,H., Yao Z., Wang C., Kim N.\,Y.}
Suppression of interface roughness between BaTiO$_3$ film and substrate by Si$_3$N$_4$ buffer layer regarding aerosol deposition process.
{\it Journal of Alloys and Compounds}, 2015, vol.~653, pp.~69--76.

6. {Bashkankova E.\,A., Vakaeva A.\,B., Grekov M. A.}
Perturbation method in the problem on a nearly circular hole in an elastic plane.
{\it Mechanics of Solids}, 2015, vol.~50, pp.~198--207.

7. {Gao H.}
A boundary perturbation analysis for elastic inclusions and interfaces.
{\it International Journal of Solids and Structures}, 1991, vol.~28, pp.~703--725.

8. {Gao H.}
Stress concentration at slightly undulating surfaces.
{\it Journal of the Mechanics and Physics of Solids}, 1991, vol.~39, pp.~443--458.

9. {Grekov M.\,A.}
The perturbation approach for a two-component composite with a slightly curved interface.
{\it Vestnik of Saint Petersburg University. Series 1. Mathematics. Mechanics. Astronomy}, 2004, iss.~1, pp.~81--88. (In Russian)

10. {Grekov M.\,A., Kostyrko S.\,A.}
A film coating on a rough surface of an elastic body.
{\it Journal of Applied Mathematics and Mechanics}, 2013, vol.~77, N~1, pp.~79--90.

11. {Grekov M.\,A., Kostyrko S.\,A.}
A multilayer film coating with slightly curved boundary.
{\it International Journal of Engineering Science}, 2015, vol.~89, pp.~61--74.

12. {Kainuma S., Jeong Y.\,S., Ahn J.\,H.}
Investigation on the stress concentration effect at the corroded surface achieved by atmospheric exposure test.
{\it Materials Science and Engineering, A}, 2014, vol.~602, pp.~89--97.

13. {Medina H.}
A stress-concentration-formula generating equation for arbitrary shallow surfaces.
{\it International Journal of Solids and Structures}, 2015,  pp.~86--93.

14. {Vikulina Y.\,I., Grekov M.\,A., Kostyrko S.\,A.}
Model of film coating with weakly curved surface.
{\it Mechanics of Solids}, 2010, vol.~45, pp.~778--788.

15. {Cammarata R.\,C., Sieradzki K.}
Effects of surface stress on the elastic moduli of thin films and superlattices.
{\it Physical Review Letters}, 1989, vol.~62, pp.~2005--2008.

16. {Fartash A., Fullerton E.\,E., Schuller I.\,K.}
Evidence for the supermodulus effect and enhanced hardness in metallic superlattices.
{\it Physical Review, B, Condensed Matter}, 1991, vol.~44, pp.~13760--13763.

17. {Sun C.\,T., Zhang H.\,T.}
Size-dependent elastic moduli of platelike nanomaterials.
{\it Journal of Applied Physics}, 2003, vol.~93, pp.~1212--1218.

18. {Gurtin M.\,E., Murdoch A.\,I.}
A continuum theory of elastic material surfaces.
{\it Archive for Rational Mechanics and Analysis}, 1975, vol.~57, pp.~291--323.

19. {Gurtin M.\,E., Murdoch A.\,I.}
Surface stress in solids.
{\it International Journal of Solids and Structures}, 1978, vol.~14, pp.~431--440.

20. {Goldstein R.\,V.,  Gorodtsov V.\,A., Ustinov K.\,V.}
Effect of residual stress and surface elasticity on deformation of nanometer spherical inclusions in an elastic matrix.
{\it Physical Mesomechanics}, 2010, vol.~13, pp.~318--328.

21. {Altenbach H., Eremeyev V.\,A., Morozov N.\,F.}
Surface viscoelasticity and effective properties of thin-walled structures at the nanoscale.
{\it International Journal of Engineering Science}, 2012, vol.~53, pp.~83--89.

22. {Eremeyev V.\,A.}
On effective properties of materials at the nano- and microscales considering surface effect.
{\it Acta Mechanica}, 2016, vol.~227(1), pp.~29--42.

23. {Dai M., Li M., Schiavone P.}
Plane deformations of an inhomogeneity --- matrix system incorporating a compressible liquid inhomogeneity and complete Gurtin---Murdoch interface model.
{\it Journal of Applied Mechanics}, 2018, vol.~85, p.~121010.

24. {Dai M., Wang Y.\,J., Schiavone P.}
Integral-type stress boundary condition in the complete Gurtin---Murdoch surface model with accompanying complex variable representation.
{\it Journal of Elasticity}, 2019, vol.~134, pp.~235--241.

25. {Iovane G.,  Nasedkin A.\,V.}
Numerical modelling of two-phase piezocomposites with interface mechanical anisotropic effects.
{\it Advanced Structured Materials}, 2019, vol.~103, pp.~293--304.

26. {Song K.,  Song H.\,P., Schiavone P., Gao C.\,F.}
The effects of surface elasticity on the thermal stress around a circular nano-hole in a thermoelectric material.
{\it Mathematics and Mechanics of Solids}, 2019, vol.~24(10), pp.~3156--3166.

27. {Nazarenko L., Bargmann S., Stolarski H.}
Closed-form formulas for the effective properties of random particulate nanocomposites with complete
Gurtin---Murdoch model of material surfaces.
{\it Continuum Mechanics and Thermodynamics}, 2017, vol.~29, pp.~77--96.

28. {Nazarenko L., Stolarski H., Altenbach H.}
Effective properties of short-fiber composites with Gurtin---Murdoch model of interphase.
{\it International Journal of Solids and Structures}, 2016, vol.~97, pp.~75--88.

29. {Altenbach H., Eremeyev V.\,A., Lebedev L.\,P.}
On the existence of solution in the linear elasticity with surface stresses.
{\it ZAMM Journal of Applied Mathematics and Mechanics: Zeitschrift fur angewandte Mathematik und Mechanik}, 2010, vol.~90, pp.~231--240.

30. {Steigmann D.\,J., Ogden R.\,W.}
Plane deformations of elastic solids with intrinsic boundary elasticity.
{\it Proceedings of the Royal Society, A}, 1997, vol.~453, pp.~853--877.

31. {Steigmann D.\,J., Ogden R.\,W.}
Elastic surface-substrate interactions.
{\it Proceedings of the Royal Society, A}, 1997, vol.~455, pp.~437--474.

32. {Zemlyanova A.\,Y., Mogilevskaya S.\,G.}
Circular inhomogeneity with Steigmann---Ogden interface: local fields, neutrality, and maxwell’s type approximation formula.
{\it International Journal of Solids and Structures}, 2018, vol.~135, pp.~85--98.

33. {Zemlyanova A.\,Y., Mogilevskaya S.\,G.}
On spherical inhomogeneity with Steigmann---Ogden interface.
{\it Journal of Applied Mechanics}, 2018, vol.~85, p.~121009.

34. {Benveniste Y., Miloh T.}
Imperfect soft and stiff interfaces in two-dimensional elasticity.
{\it Mechanics of Materials}, 2001, vol.~33, pp.~309--323.

35. {Lurie S., Belov P.}
Gradient effects in fracture mechanics for nano-structured materials.
{\it Engineering Fracture Mechanics}, 2014, vol.~130, pp.~3--11.

36. {Mohammadi P., Liu L.\,P., Sharma P., Kukta R.\,V.}
Surface energy, elasticity and the homogenization of rough surfaces.
{\it Journal of the Mechanics and Physics of Solids}, 2013, vol.~61, pp.~325--340.

37. {Wang Y., Weissm\"{u}ller J., Duan H.\,L.}
Mechanics of corrugated surfaces.
{\it Journal of the Mechanics and Physics of Solids}, 2010, vol.~58, pp.~1552--1566.

38. {Weissm\"{u}ller J., Duan H.\,L.}
Cantilever bending with rough surfaces.
{\it Physical Review Letters}, 2008, vol.~101,  p.~146102.

39. {Grekov M.\,A., Kostyrko S.\,A.}
Surface effects in an elastic solid with nanosized surface asperities.
{\it International Journal of Solids and Structures}, 2016, vol.~96, pp.~153--161.

40. {Kostyrko S.\,A., Grekov M.\,A.}
Elastic field at a rugous interface of a bimaterial with surface effects.
{\it Engineering Fracture Mechanics},  2019, vol.~216, p.~106507.

41. {Kostyrko S.\,A., Grekov M.\,A., Altenbach\,H.}
Stress concentration analysis of nanosized thin-film coating with rough interface.
{\it Continuum Mechanics and Thermodynamics}, 2019,  vol.~31, pp.~1863--1871.

42. {Vakaeva A.\,B., Shuvalov G.\,M., Kostyrko S.\,A.}
Interfacial stresses in bimaterial composites with nanosized interface relief.
{\it Proceedings of the 8th International Conference on Coupled Problems in Science and Engineering. Coupled Problems}, 2019, pp.~679--688.

43. {Vikulina Y.\,I., Grekov M.\,A.}
The stress state of planar surface of a nanometer-sized elastic body under periodic loading. {\it Vestnik of Saint Petersburg University. Mathematics}, 2012, vol.~45, pp.~174--180.

44. {Tian L., Rajapakse R.\,K.\,N.\,D.}
Finite element modeling of nanoscale inhomogeneities in an elastic matrix.
{\it Computational Materials Science}, 2007, vol.~41, pp.~44--53.

45. {Miller R.\,E.,  Shenoy V.\,B.}
Size-dependent elastic properties of nanosized structural elements.
{\it Nanotechnology}, 2000, vol.~11, pp.~139--147.



\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  April 27, 2020.

Accepted: May 28, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm
\textit{Gleb M. Shuvalov} ---  Postgraduate Student, Assistant; g.shuvalov@spbu.ru


\vskip 2mm
\textit{Alexandra B. Vakaeva} --- PhD in Physics and Mathematics, Senior Lecturer; a.vakaeva@spbu.ru

\vskip 2mm
\textit{Denis A. Shamsutdinov} ---  Master Student; st070089@student.spbu.ru


\vskip 2mm
\textit{Sergey A. Kostyrko} --- PhD in Physics and Mathematics, Associate Professor; s.kostyrko@spbu.ru

}
