{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Tikhonov A.~N. O priblizhennyh sistemah linejnyh
algebraicheskih uravnenij [About approximate systems of linear
algebraic equations]. \textit{USSR Computational Mathematics and
Mathematical Physics}, 1980, vol. 20, no. 6, pp. 1373--1383. (In
Russian)

%1. Tikhonov A.~N.
%Approximate systems of linear algebraic equations.
%\textit{USSR Computational Mathematics and Mathematical Physics},
%1980, vol. 20, no. 6, pp. 10--22.

%02
%\bibitem{Tihonov_AN_1980}
2. Tikhonov A.~N. O normalnyh resheniyah priblizhennyh sistem
linejnyh algebraicheskih uravnenij $[$About normal solutions of
approximate systems of linear algebraic equations$]$.
\textit{Doklady Akademii Nauk SSSR $[$Papers of Academy of
sciences of USSR$]$}, 1980, vol. 254, no. 3, pp. 549--554. (In
Russian)

%03
%\bibitem{Tihonov_VAN_1983}
3. Tikhonov A.~N. O metodah avtomatizacii obrabotki nablyudenij
[About methods of automation of processing observations].
\textit{Vestnik Akademii Nauk SSSR $[$Vestnik of Academy of
sciences of USSR$]$}, 1983, no. 1, pp. 14--25. (In Russian)

%04
%\bibitem{Tihonov_Arsenin}
4. Tikhonov A.~N., Arsenin V.~Ya. \textit{Metody resheniya
nekorrektnyh zadach} [\textit{Methods of solving incorrect
problems}]. Moscow, Nauka Publ., 1986, 288 p. (In Russian)

%05
%\bibitem{Ivanov_Vasin_Tanana}
5. Ivanov~V.~K., Vasin~V.~V., Tanana~V.~P. \textit{Teoriya
linejnyh nekorrektnyh zadach i ee prilozheniya} [\textit{Theory of
linear incorrect problems and it’s applications}]. Moscow, Nauka
Publ., 1978, 206 p. (In Russian)

%06
%\bibitem{Tihonov_Goncharsky}
6. Tikhonov~A.~N., Goncharsky~A.~V., Stepanov~V.~V., Yagola~A.~G.
\textit{Chislennye metody resheniya nekorrektnyh zadach}
[\textit{Numerical methods of solving incorrect problems}].
Moscow, Nauka Publ., 1990, 229~p. (In Russian)

%07
%\bibitem{Voevodin_Kuznecov}
7. Voevodin~V.~V., Kuznetcov~Yu.~A. \textit{Matricy i
vychisleniya} [\textit{Matrices and calculations}]. Moscow, Nauka
Publ., 1984, 320 p. (In Russian)

%08
%\bibitem{Volkov_Erohin_GVM_2010}
8. Volkov~V.~V., Erokhin~V.~I. Tikhonov solutions of approximately
given systems of linear algebraic equations under finite
pertuberations of their matrices. \textit{Computational
Mathematics and Mathematical Physics}, 2010, vol. 50, no.~4, pp.
589--605. (Original Russian text  \copyright\ V.~V.~Volkov,
V.~I.~Erokhin, 2010, published in \textit{Zhurnal Vychidlitel'noi
Matematiki i Matematicheskoi Fiziki}, 2010, vol. 50, no. 4, pp.
618--635.) (In Russian)


%8. Volkov~V.~V., Erokhin~V.~I.
%Tikhonov solutions of approximately given systems of linear algebraic equations under finite perturbations of their matrices.
%\textit{Computational Mathematics and Mathematical Physics}, 2010, vol. 50, no. 4, pp. 589--605.

%09
%\bibitem{Lowson_Henson}
9. Lawson~Ch., Hanson~R.~J. \textit{Solving least squares
problems}. New Jork, Englewood Cliffs, 1985, 374~p. (Russ. ed.:
Lawson C., Hanson R. \textit{Chislennoe reshenie zadach metoda
naimenshih kvadratov}. Moscow, Nauka Publ., 1986, 232~p.)

%10
10. Volkov~V.~V. \textit{Vosstanovlenie linejnyh zavisimostej po
netochnoj informacii} [\textit{Recovering linear dependencies on
inaccurate information}]. PhD dissertation. Moscow, Moscow State
University of Education, 2011, 135 p. (In Russian)

% 11 - äîáàâëåí
11. Horn~R.~A., Johnson~Ch.~R. \textit{Matrix analysis}.
Cambridge, Cambridge University Press, 1985, 561~p. (Russ. ed.:
Horn~R., Johnson~ C. \textit{Matrichnyj analiz}. Moscow, Mir
Publ., 1989, 655~p.)

%11->12
%\bibitem{Golub_Hansen_OLeary}
12. Golub~G.~H., Hansen~P.~C., O'Leary~D.~P. Tikhonov
regularization and total least squares. \textit{SIAM J. on Matrix
Analysis and Applications}, 1999, vol. 21, no. 1, pp. 185--194.

%12->13
%\bibitem{ZHdanov_2012}
13. Zhdanov~A.~I. The method of augmented regularized normal
equations. \textit{Computational Mathematics and Mathematical
Physics}, 2012, vol.~52, no.~2, pp.~194--197. (Original Russian
text\linebreak \copyright\ A.~I.~Zhdanov, 2012, published in
\textit{Zhurnal Vychidlitel'noi Matematiki i Matematicheskoi
Fiziki}, 2012, vol.~52, no.~2, pp.~205--208.) (In Russian)

%13->14
%\bibitem{GE2004}
14. Gorelik~V.~A., Erokhin~V.~I. \textit{Optimalnaya matrichnaya
korrekciya nesovmestnyh sistem linejnyh algebraicheskih uravnenij
po minimumu evklidovoj normy} [\textit{Optimal matrix correction
of inconsistent systems of linear algebraic equations by minimum
of euclidean norm}]. Moscow, VC RAN, 2004, 194~p. (In Russian)

%14->15
%\bibitem{EVB_ISTI_2014}
15. Erokhin~V.~I., Volkov~V.~V., Budaev~A.~A. O primenenii
otricatelnogo parametra regulyarizacii v regulyarizovannom metode
naimenshih kvadratov A. N. Tihonova [Using negative regularization
parameter in Tikhonov's regularized least squares method].
\textit{Izvestija Sankt Peterburgskogo Gosudarstvennogo
Technologicheskogo Instituta $($Technicheskogo Universiteta$)$}
[Proceedings of Saint Petersburg State Technological Institute
(Technical University)], 2014, no. 24(50), pp. 86--92. (In
Russian)

%15->16
%\bibitem{Sizikov}
16. Sizikov~V.~S. \textit{Obratnye prikladnye zadachi i Matlab}
[\textit{Inverse applied problems and Matlab}]. Saint Petersburg,
Lan’ Publ., 2011, 256 p. (In Russian)

%16->17
%\bibitem{Voskoboinikov_Litasov}
17. Voskoboinikov~Yu.~E., Litasov~V.~A. Ustojchivyj algoritm
vosstanovleniya izobrazheniya pri netochno zadannoj apparatnoj
funkcii [A stable image reconstruction algorithm for inexact
point-spread function]. \textit{Avtometrija $[$Optoelectronics,
Instrumentation and Data Processing$]$}, 2006, no. 42(6), pp.
3--15. (In Russian)


%17->18
18. Erokhin V.~I., Volkov V.~V. Recovering images, registered by
device with inexact point-spread function, using tikhonov’s
regularized least squares method. \textit{International Journal of
Artificial Intelligence}, 2015, vol. 13, no. 1, 12 p. Available
at: http://www.ceser.in/ceserp/index.php/ijai/article/ view/3531
(accessed: 01.06.2016).

\vskip 2mm

{\bf For citation:} Erokhin~V.~I., Volkov~V.~V.  About
A.~N.~Tikhonov's regularized least squares method. {\it Vestnik of
Saint Petersburg University. Applied mathematics. Computer
science. Control processes}, \issueyear, volume~13,
issue~\issuenum, pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
