
{\normalsize

\vskip 4.5mm%6mm

\noindent{\bf Methods of tropical optimization in multicriteria
problems of raiting\\ alternatives from pairwise comparisons$^{*}$%

}

}

\vskip 1.8mm%2mm

{\small

\noindent{\it N.~K.~Krivulin%$\,^1$%
, V.~A.~Ageev%$^1$%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 1.8mm%2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\efootnote{
%%
\vspace{-3mm}\parindent=7mm
%%
\vskip 0.1mm $^{*}$ This work was supported by the Russian
Foundation for Basic Reaserch (grant N18-010-00723).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize

\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab.,


\noindent%
%\hskip2.45mm%
St.\,Petersburg, 199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip1.8mm%3mm


\noindent \textbf{For citation:}  Krivulin~N.~K., Ageev~V.~A.
Methods of tropical optimization in multi\-criteria problems of
raiting alternatives from pairwise comparisons. {\it Vestnik of
Saint~Pe\-tersburg University. Applied Mathematics. Computer
Science. Control Processes},\,\issueyear,
vol.~15, %~
iss.~\issuenum,~pp.~\pageref{p5}--\pageref{p5e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum05  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The paper deals with the application of
methods and results of tropical mathematics, which focuses on the
theory and applications of algebraic systems with idempotent
operations, to the development of a multicriteria decision-making
procedure. A problem is considered to evaluate ratings of
alternatives from pairwise comparisons of the alternatives under
several criteria, and from pairwise comparisons of the criteria.
To solve the problem, a decision-making procedure is proposed
based on the Chebyshev approximation, in logarithmic scale, of
pairwise comparison matrices by reciprocally symmetrical matrices
of unit rank (consistent matrices), which determine the elements
in the vectors of weights of criteria and ratings of alternatives.
First, the approximation problem for the matrix of pairwise
comparison of criteria is solved to find the weights of criteria.
Then, the weighted pairwise comparison matrices of alternatives
are approximated by a common consistent matrix, which gives the
required vector of ratings of alternatives. If the result is not
unique (up to a positive factor), an additional problem of
analyzing the solutions is solved to find vectors that can be
considered, in a sense, as the worst and best solutions. In the
framework of the proposed procedure, the problems of approximation
and analysis of solutions are formulated as tropical optimization
problems, which have direct analytical solutions in a compact
vector form. An example of the application of the procedure to
solve the known problem by T.~Saaty on selecting a school is given.\\[1mm]
\textit{Keywords}: idempotent semifield, tropical optimization,
pairwise comparison matrix, matrix approximation, log-Chebyshev
metric, multicretiria decision making problem.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1.~Ehrgott~M. \textit{Multicriteria optimization.} 2nd~ed. Berlin,
Springer Press, 2005, 323~p. \\
https://doi.org/10.1007/3-540-27659-9

%2.~\textit{Ногин~В.~Д.}
%Принятие решений в многокритериальной среде. 2-е изд., испр. и доп.
%М.: Физматлит, 2005.
%176~с.
2.~Nogin~V.~D. \textit{Prinyatie reshenij v mnogokriterial'noj
srede} [\textit{Decision-making in multicriteria framework}]. 2nd
ed., rev. and enl. Moscow, Fizmatlit Publ., 1994, 176~p. (In
Russian)

3.~Thurstone~L.~L. A law of comparative judgment.
\textit{Psychological Review}, 1927, vol.~34, no.~4, pp.~273--286.
https://doi.org/10.1037/h0070288

%4.~\textit{Саати~Т.}
%Принятие решений. Метод анализа иерархий / пер. с англ. Р.~Г.~Вачнадзе.
%М.: Радио и связь, 1993. 315~с.
%(Saaty~T.~L. The analytic hierarchy process: planning, priority setting, resource allocation. New York: McGraw-Hill, 1980. 281~p.)
4.~Saaty~T.~L. \textit{The analytic hierarchy process: planning,
priority setting, resource allocation.} New York, McGraw-Hill,
1980, 281~p. (Russ. ed.: Saaty~T. \textit{Prinyatie reshenij.
Metod analiza ierarkhij.} Moscow, Radio i svyaz’ Publ., 1993,
315~p.)

5.~Saaty~T.~L., Vargas~L.~G. Comparison of eigenvalue, logarithmic
least squares and least squares methods in estimating ratios.
\textit{Math. Modelling.} 1984, vol.~5, no.~5, pp.~309--324. \\
https://doi.org/10.1016/0270-0255(84)90008-3


6.~Koczkodaj~W.~W., Or{\l}owski~M. Computing a consistent
approximation to a generalized pairwise comparisons matrix.
\textit{Comput. Math. Appl.}, 1999, vol.~37, no.~3, pp.~79--85. \\
https://doi.org/10.1016/S0898-1221(99)00048-6

7.~Gonz\'{a}lez-Pach\'{o}n~J., Rodr\'{\i}guez-Galiano~M.~I.,
Romero~C. Transitive approximation to pairwise comparison matrices
by using interval goal programming. \textit{J. Oper. Res. Soc.},
2003, vol.~54, no.~5, pp.~532--538.
https://doi.org/10.1057/palgrave.jors.2601542

8.~Dahl~G. A method for approximating symmetrically reciprocal
matrices by transitive matrices. \textit{Linear Algebra Appl.},
2005, vol.~403, pp.~207--215.
https://doi.org/10.1016/j.laa.2005.02.002

9.~Gavalec~M., Ram\'{\i}k~J., Zimmermann~K. \textit{Decision
making and optimization.} Cham, Springer Press, 2015, 225~p.
(Vol.~677 of Lecture Notes in Economics and Mathematical Systems)
 \\ https://doi.org/10.1007/978-3-319-08323-0

%10.~\textit{Маслов~В.~П., Колокольцов~В.~Н.}
%Идемпотентный анализ и его применение в оптимальном управлении.
%М.: Физматлит, 1994. 144~с.
10.~Maslov~V.~P., Kolokol’tsov~V.~N. \textit{Idempotentnyj analiz
i ego primenenie v optimal’nom upravlenii} [\textit{Idempotent
analysis and its applications in optimal control}]. Moscow,
Fizmatlit Publ., 1994, 144~p. (In Russian)

11.~Golan~J.~S. \textit{Semirings and affine equations over them.}
New York, Springer Press, 2003, 256~p. (Vol.~556 of Mathematics
and its Applications)

12.~Heidergott~B., Olsder~G.~J., van der Woude~J. \textit{Max Plus
at work.} Princeton, Princeton University Press, 2006, 226~p.
(Princeton Series in Applied Mathematics)

%13.~\textit{Кривулин~Н.~К.}
%Методы идемпотентной алгебры в задачах моделирования и анализа сложных систем.
%СПб.: Изд-во С.-Петерб. ун-та, 2009. 256~с.
13.~Krivulin~N.~K. \textit{Metody idempotentnoj algebry v
zadachakh modelirovaniya i analiza slozhnykh sistem}
[\textit{Methods of idempotent algebra for problems in modeling
and analysis of complex systems}]. St.~Petersburg, St.~Petersburg
University Publ., 2009, 256~p. (In Russian)

14.~Butkovi\v{c}~P. \textit{Max-linear systems.} London, Springer
Press, 2010, 274~p. (Springer Monographs in Mathematics)
https://doi.org/10.1007/978-1-84996-299-5

%15.~\textit{Кривулин~Н.~К., Гладких~И.~В.}
%Построение согласованной матрицы парных сравнений в маркетинговых исследованиях на основе методов тропической математики
%// Вестн. С.-Петерб. ун-та. Сер.~10. Менеджмент. 2015.
%Вып.~1. P.~3--43.
15.~Krivulin~N.~K., Gladkikh~I.~V. Postroenie soglasovannoj
matritsy parnykh sravnenij v marketingovykh issledovaniyakh na
osnove metodov tropicheskoj matematiki [Computation of the
consistent pairwise comparison matrix in marketing research by
using methods of tropical mathematics]. \textit{Vestnik of
Saint~Petersburg University. Series~8. Management}, 2015, iss.~1,
pp.~3--43. (In Russian)


16.~Krivulin~N. Rating alternatives from pairwise comparisons by
solving tropical optimization problems.
\textit{2015 12th International Conference on Fuzzy Systems and Knowledge Discovery (FSKD),} %/ ed. by Z.~Tang, and J.~Du, S.~Yin, L.~He, R.~Li.
IEEE, 2015, pp.~162--167.
https://doi.org/10.1109/FSKD.2015.7381933

17.~Krivulin~N. Using tropical optimization techniques to evaluate
alternatives via pairwise comparisons.
\textit{2016 Proceedings 7th SIAM Workshop on Combinatorial Scientific Computing.} %/ ed. by A.~H.~Gebremedhin, E.~G.~Boman, B.~Ucar.
SIAM, 2016, pp.~62--72.
https://doi.org/10.1137/1.9781611974690.ch7

%18.~\textit{Кривулин~Н.~К., Агеев~В.~А., Гладких~И.~В.}
%Применение методов тропической оптимизации для оценки альтернатив на основе парных сравнений
%// Вестн. С.-Петерб. ун-та. Прикл. мат. 2017.
%Т.~13, №1. P.~27--41.
18.~Krivulin~N.~K., Ageev~V.~A., Gladkikh~I.~V. Primenenie metodov
tropicheskoi optimizatsii dlya otsenki al'ternativ na osnove
parnyh sravneniy  [Application of methods of tropical optimization
for evaluating alternatives based on pairwise comparisons].
\textit{Vestnik of Saint~Pe\-ters\-burg University. Applied
Mathematics. Informatics. Control Processes}, 2017, vol.~13,
iss.~1, pp.~27--41. (In Russian)


19.~van Laarhoven~P.~J.~M., Pedrycz~W. A fuzzy extension of
{S}aaty's priority theory. \textit{Fuzzy Sets and Systems}, 1983,
vol.~11, no.~1--3, pp.~229--241.
https://doi.org/10.1016/S0165-0114(83)80082-7

%20.~\textit{Ногин~В.~Д.}
%Упрощенный вариант метода анализа иерархий на основе нелинейной свертки критериев
%// Ж. выч. мат. мат. физ. 2004.
%Т.~44, №7. С.~1261--1270.
20.~Nogin~V.~D. Uproshhennyj variant metoda analiza ierarkhij na
osnove nelinejnoj svertki kriteriev [A simplified variant of a
method for the analysis of hierarchies, based on a nonlinear
convolution of criteria]. \textit{Zhurnal vychislitel’noi
matematiki i matematicheskoi fiziki} [\textit{Journal of
Computational Mathematics and Mathematical Physics}], 2004,
vol.~44, no.~7, pp.~1261–1270. (In Russian)

21.~Kubler~S., Robert~J., Derigent~W., Voisin~A., Le Traon~Y. A
state-of the-art survey and testbed of fuzzy AHP (FAHP)
applications. \textit{Expert Syst. Appl.}, 2016, vol.~65,
pp.~398--422. https://doi.org/10.1016/j.eswa.2016.08.064

22.~Ahn~B.~S. The analytic hierarchy process with interval
preference statements. \textit{Omega}, 2017, vol.~67,
pp.~177--185. https://doi.org/10.1016/j.omega.2016.05.004

23.~Podinovski~V.~V. Interval articulation of superiority and
precise elicitation of priorities. \textit{European J. Oper.
Res.}, 2007, vol.~180, no.~1, pp.~406--417.
https://doi.org/10.1016/j.ejor.2006.01.046

24.~Krivulin~N., Sergeev~S. Tropical optimization techniques in
multicriteria decision making with analytical hierarchy process.
\textit{UKSim-AMSS 11th European Modelling Symposium on Computer Modelling and Simulation (EMS 2017),} %/ ed. by D.~Al-Dabass, Z.~Xie, A.~Orsoni, A.~Pantelous.
IEEE, 2017, pp.~38--43. https://doi.org/10.1109/EMS.2017.18

25.~Krivulin~N. Methods of tropical optimization in rating
alternatives based on pairwise comparisons.
\textit{Operations Research Proceedings 2016.} %/ ed. by A.~Fink, A.~F\"{u}genschuh, M.~J.~Geiger.
Cham, Springer Press, 2018, pp.~85--91. \\
https://doi.org/10.1007/978-3-319-55702-1\_13

26.~Krivulin~N., Sergeev~S. Tropical implementation of the
analytical hierarchy process decision method. \textit{Fuzzy Sets
and Systems}, 2019, vol.~377, pp.~31--51.
https://doi.org/10.1016/j.fss.2018.10.013

27.~Krivulin~N. Tropical optimization problems.
\textit{Advances in Economics and Optimization.} %/ ed. by L.~A.~Petrosyan, J.~V.~Romanovsky, D.~W.~K.~Yeung.
New York, Nova Sci. Publ., 2014, pp.~195--214. (Economic Issues,
Problems and Perspectives)


\vskip1.5mm Received:  November 21, 2018.

Accepted: November 07, 2019.


\vskip6mm A\,u\,t\,h\,o\,r's \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip1.5mm%2mm
\textit{Nikolai K. Krivulin} -- Dr. Sci. in Physics and
Mathematics, Professor; nkk@math.spbu.ru

\vskip1.5mm%2mm
\textit{Vladimir A. Ageev} -- Student; vladimir.ageev@me.com

}
