
{\footnotesize


\vskip3mm \noindent {\small\textbf{Литература} }

\vskip2mm

1. {\em Lau J. H., Collier N., Baldwin T.} {On-line trend analysis
with topic models: twitter trends detection topic model online~//
Proceedings of COLING: technical papers. Mumbai, 2012.
P.~1519--1534. }

2. {\em Ahmed A., Xing E. P.} {Timeline: A dynamic hierarchical
dirichlet process model for recovering birth/death and evolution
of topics in text stream~// Proceedings of the Twenty-Sixth
Conference. Conference on Uncertainty in Artificial Intelligence.
2010. Vol.~20.  P.~29.}

3. {\em Schubert E., Weiler M., Kriegel H.-P.} {Signitrend:
scalable detection of emerging topics in textual streams by hashed
significance thresholds~// Proceedings of the 20th ACM SIGKDD
International conference on Knowledge discovery and data mining.
2014.  P.~871--880.}

4. {\em Cvijikj I. P., Michahelles F.} {Monitoring trends on
facebook~// Dependable, Autonomic and Secure Computing (DASC),
2011. IEEE Ninth Intern. Conference on. 2011.  P.~895--902.}

5. {\em Finch T.} {Incremental calculation of weighted mean and
variance: technical report. Cambridge, 2009. Vol.~4.}

6. {\em Ester M., Kriegel H.-P., Sander J., Xu X.}{ A
density-based algorithm for discovering clusters in large spatial
databases with noise~// Kdd. 1996. Vol.~96, N~34. P.~226--231.}

7. Open-source library for language detection. URL:
\url{https://github.com/optimaize/language-detector} (accessed:
26.02.2017).

8. Additional language profile for CIS-languages. URL:
\url{https://github.com/denniean/language\_ profiles} (accessed:
26.02.2017).

9. \textit{Jeffrey D., Ullman Anand Rajaraman, Jure Leskovec}.
Mining of massive datasets, 2013. URL:
\url{http://infolab.stanford.edu/\~{}ullman/mmds.html} (accessed:
26.02.2017).

10. Open-source library for data analysis. URL:
\url{https://elki-project.github.io/} (accessed: 26.02.2017).

11. Scalable stream processing platform. URL:
\url{https://kafka.apache.org/} (accessed: 26.02.2017).

12. Apache Samza: distributed stream processing framework. URL:
\url{http://samza.apache.org/} (accessed: 26.02.2017).

13. Apache Zeppelin: web-dashboard for interactive data analysis.
 URL: \url{https://zeppelin.apache.org/} (accessed:
26.02.2017).




\vskip 2mm

{\bf Для цитирования:} {\it Малютин Е.~А.,~Бугайченко
Д.~Ю.,~Мишенин} А.~Н. Выделение текстовых трендов в~социальной
сети OK~// Вестник Санкт-Петербургского университета. Прикладная
математика. Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08



}
