

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm

1. {Lau J. H., Collier N., Baldwin T.} {On-line trend analysis
with topic models: twitter trends detection topic model online.
\textit{Proceedings of COLING}: Technical Papers. Mumbai, 2012,
pp.~1519--1534. }

2. { Ahmed A., Xing E. P.} {Timeline: A dynamic hierarchical
dirichlet process model for recovering birth/death and evolution
of topics in text stream. \textit{Proceedings of the Twenty-Sixth
Conference. Conference on Uncertainty in Artificial Intelligence},
2010, iss.~20, p.~29.}

3. { Schubert E., Weiler M., Kriegel H.-P.} {Signitrend: scalable
detection of emerging topics in textual streams by hashed
significance thresholds. \textit{Proceedings of the 20th ACM
SIGKDD International conference on Knowledge discovery and data
mining}, 2014, pp.~871--880.}

4. {Cvijikj I. P., Michahelles F.} {Monitoring trends on facebook.
\textit{Dependable, Autonomic and Secure Computing $($DASC$)$,
IEEE Ninth International Conference on.}, 2011, pp.~895--902.}

5.{ Finch T.} { \textit{Incremental calculation of weighted mean
and variance}. Technical report. Cambridge, 2009,  vol.~4.}

6. {Ester M., Kriegel H.-P., Sander J., Xu X.}{ A density-based
algorithm for discovering clusters in large spatial databases with
noise. \textit{Kdd}, 1996, vol.~96, no.~34, pp.~226--231.}

7. \textit{Open-source library for language detection}. Available
at: \url{https://github.com/optimaize/language-detector}
(accessed: 26.02.2017).

8. \textit{Additional language profile for CIS-languages}.
Available at: \url{https://github.com/denniean/
language\_profiles} (accessed: 26.02.2017).

9. Jeffrey D., Ullman Anand Rajaraman, Jure Leskovec.
\textit{Mining of massive datasets, 2013.} Available at:
\url{http://infolab.stanford.edu/\~{}ullman/mmds.html} (accessed:
26.02.2017).

10. \textit{Open-source library for data analysis.} Available at:
\url{https://elki-project.github.io/} (accessed: 26.02.2017).

11. \textit{Scalable stream processing platform.} Available at:
\url{https://kafka.apache.org/} (accessed:  26.02.2017).

12. \textit{Apache Samza: distributed stream processing
framework.} Available at: \url{http://samza.apache.org/}
(accessed: 26.02.2017).

13. \textit{Apache Zeppelin: web-dashboard for interactive data
analysis.} Available at: \url{https:// zeppelin.apache.org/}
(accessed: 26.02.2017).




\vskip 2mm

{\bf For citation:}  Malyutin E.~A.,~Bugaichenko D.~Y.,~Mishenin
A.~N. Textual trends detection at OK. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p8}--\pageref{p8e}.
\doivyp/spbu10.\issueyear.\issuenum08


}
