

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize


1. Provotorov V.~V., Podvalny S.~L. Opredelenie startovoi funkcii
v zadache nabludeniy pa\-ra\-bo\-liches\-koi sistemi na grafe
[Determining the starting function in the task of observing the
parabolic system with distributed parameters on the graph].
\emph{Vestnik of Voronezh State Technical University}, 2014, vol.
10, no.~6, pp. 29--35. (In Russian)


2. Zhabko A.~P., Nurtazina K.~B., Provotorov V.~V. About one
approach to solving the inverse problem for parabolic equation.
\emph{Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, 2019, vol. 15, iss. 3,
pp.~322--335.\\ https://doi.org/10.21638/11701/spbu10.2019.303


3. Avdonin S., Murzabekova G., Nurtazina K. Source identification
for the differential equation with memory. \textit{Trends in
Mathematics. Research Perspective}. Switzerland, Birkh$\ddot{\rm
a}$euser Springer International Publishing,  2017, pp.~111--120.


4. Avdonin S., Bell J., Nurtazina K. Determining distributed
parameters in a neuronal cable model on a tree graph.
\textit{Mathematic Methods in the Applied Sciences}, 2017,
vol.~40, iss.~11, pp.~3973--3991.


5. Podvalny S.~L., Provotorov V.~V., Podvalny E.~S. The
controllability of parabolic systems with delay and distributed
parameters on the graph. \emph{Procedia Computer Sciense. Series
``12th  International Symposium Intelligent Systems, INTELS
2016''},  2017, pp. 324--330.


6. Karelin V.~V.  Shtrafnye funkcii v zadache upravleniya
processom nabludeniya [Penalty functions in the control problem of
an observation process]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss. 4, pp. 109--114. (In Russian)


7. Avdonin S., Kurasov P. Inverse problems for quantum trees.
\textit{Inverse Problems Imag.}, 2008, vol.~2, iss.~1,
pp.~3973--3991.


8. Yurko V.~A. \emph{Vvedenie v teoriyu obratnih spektral'nih
zadach} [\textit{Introduction to the theory of inverse spectral
problems}]. Moscow, Fizmatlit Publ., 2007, 384~p. (In Russian)


9. Provotorov V.~V. Eigenfunctions of  the Sturm---Liouville problem
on astar graph. \emph{Mathematics}, 2008, vol.~199, no.~10,
pp.~1523--1545.


10. Provotorov V.~V. Modelirovanie kolebatelnih processov
``machta-rastjagki'' [Modeling of vibrating processes of
``mast-stretching'']. \emph{Systems of Control and Information
Technologies}, 2008,  no.~1.2(31), pp.~272--277. (In Russian)


11. Provotorov V.~V. Razlozenie po sobstvennym funkciyam zadachi
Shturma---Liuvillya na grafe-puchke [Expansion  of eigenfunctions
of Sturm---Liouville problem on astar graph]. \emph{Russian
Mathematics}, 2008, vol.~3, pp.~50--62. (In Russian)


12. Provotorov V.~V.  Sobstvennye funkcii zadachi
Shturma---Liuvillja na grafe-zvezde [Eigenfunctions of the
Sturm---Liouville problem astar graph]. \emph{Mathematics}, 2008,
vol.~199, iss.~10, pp.~105--126.    (In Russian)


13.  Provotorov V.~V. Metod momentov v zadache gasheniy kolebanii
differecialnoi sistemi na grafe [The method of moments in the
problem of extinguishing the oscillations of the differential
system on the graph]. \emph{Vestnik of Saint Petersburg
University. Series 10. Applied Mathematics. Computer Science.
Control Processes}, 2010, iss. 2, pp. 60--69.  (In Russian)


14. Provotorov V.~V., Provotorova E.~N. Sintez optimal'nogo
granichnogo upravlenija parabolicheskoi sistemy s zapazdyvaniem i
raspredelennymi parametrami na grafe [Synthesis of optimal
boundary control of parabolic systems with delay and distributed
parameters on the graph]. \textit{Vestnik of Saint Petersburg
University. Applied Mathematics. Computer Science. Control
Processes}, 2017, vol.~13, iss.~2, pp.~209--224.
https://doi.org/10.21638/11701/spbu10.2017.207 (In Russian)


15. Provotorov V.~V., Ryazhskikh V.~I., Gnilitskaya Yu.~A. Unique
weak solvability of nonlinear initial boundary value problem with
distributed parameters in the netlike domain. \emph{Vestnik of
Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, 2017, vol. 13, iss. 3, pp. 264--277.
https://doi.org/10.21638/11701/spbu10.2017.304


16. Provotorov V.~V. Boundary control of a parabolic system with
delay and distributed parameters on the graph. \emph{International
Conference ``Stability and Control Processes’’ in memory of V. I.
Zubov (SCP)}. Saint Petersburg, Russia, 2015, pp. 126--128.


17. Provotorov V.~V., Sergeev S.~M., Part A.~A. Solvability of
hyperbolic systems with distributed parameters on the graph in the
weak formulation. \textit{Vestnik of Saint Petersburg University.
Applied Mathematics. Computer Science. Control Processes}, 2019,
vol. 14, iss. 1, pp. 107--117.\\
https://doi.org/10.21638/11701/spbu10.2019.2003


18. Provotorov V. V., Provotorova E. N. Optimal control of the linearized %
Navier---Stokes system in a netlike domain. \emph{Vestnik of
Saint Petersburg University.  Applied Mathematics. Computer
Science. Control Processes}, 2017, vol. 13, iss. 4, pp.
428--441. %\\
https://doi.org/10.21638/11701/spbu10.2017.409


19. Artemov M. A.,  Baranovskii E. S., Zhabko A. P., Provotorov V.
V.  On a 3D model of non-isothermal flows in a pipeline network.
\emph{Journal of Physics. Conference Series}, 2019, vol. 1203,
Article ID 012094. https://doi.org/10.1088/1742-6596/1203/1/012094


20. Zhabko A.~P.,  Provotorov V.~V., Balaban O.~R.   Stabilization
of weak solutions of pa\-rabolic systems with distributed parameters
on the graph. \emph{Vestnik of Saint Petersburg University.
App\-lied Mathematics. Computer Science. Control Processes}, 2019,
vol. 15, iss. 2, pp. 187--198.\\
https://doi.org/10.21638/11701/spbu10.2019.203


21. Zhabko A.~P., Tikhomirov O.~G., Chizhova O.~N. On
stabilization of a class of systems with time proportional delay.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2018, vol.~14,
iss.~2, pp.~165--172.
https://doi.org/10.21638/11701/spbu10.2018.209


22. Alexandrova  I.~V., Zhabko A.~P.  A new LKF approach to
stability analysis of linear systems with uncertain delays.
\emph{Automatica}, 2018, vol.~91, pp.~173--178.


23. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions for certain classes of mechanical systems
with time delay. \emph{WSEAS Transactions on Systems and Control},
2014, vol.~9, pp.~388--397.


24. Aleksandrov A., Aleksandrova E., Zhabko A. Asymptotic
stability conditions of solutions for nonlinear multiconnected
time-delay systems. \emph{Circuits  Systems and Signal
Processing}, 2016, vol.~35, no.~10, pp.~3531--3554.


25. Zhabko A.~P., Tikhomirov O.~G., Chizhova O.~N. On
stabilization of a class of systems with time proportional delay.
\textit{Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, 2018, vol.~14,
iss.~2, pp.~165--172.
https://doi.org/10.21638/11701/spbu10.2018.209


26. Veremey E.~I., Sotnikova M.~V. Stabilizaciya plazmy na baze
prognoza s ustoichivym lineinym priblizheniem [Plasma
stabilization by prediction with stable linear approximation].
\emph{Vestnik of Saint Petersburg University. Series 10. Applied
Mathematics. Computer Science. Control Processes}, 2011, iss.~1,
pp.~116--133. (In Russian)


27. Kamachkin A.~M., Yevstafyeva V.~V.   Oscillations in a relay
control system at an external disturbance.  \emph{Control
Applications of Optimization 2000}: \emph{Proceedings of the 11th
IFAC Workshop}, 2000, vol.~2, pp.~459--462.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  January 01, 2020.

Accepted: May 28, 2020.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm
\textit{Aleksei P. Zhabko} --- Dr. Sci. in Physics and Mathematics, Professor;
 zhabko.apmath.spbu@mail.ru

\vskip 2mm
\textit{Karlygash B. Nurtazina} ---  PhD Sci. in  Physics and Mathematics;   knurtazina@mail.ru

\vskip 2mm
\textit{Vyacheslav V. Provotorov} --- Dr. Sci. in Physics and Mathematics, Professor;  wwprov@mail.ru

}
