
{\footnotesize


\vskip4mm \noindent {\small\textbf{Литература} }

\vskip3mm

1. \textit{Severy~D. M., Mathewson~ L. H., Bechtol~C. O.}
Controlled automobile rear-end collisions --- an investigation of
related engineering and medical phenomena // Proc. of the Montreal
conference on medical aspects of traffic accidents. 1955.
P.~152--184.

2. \textit{Davidson~J., Deutscher~C., Hell~W., Linder~A.,
Lovsund~P., Svensson~M. Y.} Human volunteer kinematics in rear-end
sled collisions~// Proc. of Intern. Council on biomechanics of
impact. Goteborg, Sweden, 1998. P.~289--301.

3. \textit{Yamazaki~K., Ono~ K., Kaneoka~K.} A simulation analysis
of human cervical motion during low speed rear-end impacts~//
Proc. of Society of Automotive Engineers World Congress. Detroit,
USA, 2000. P.~186--192.

4. \textit{Tencer~A. F., Mirza~S. K., Bensel~K.} The response of
human volunteers to rear-end impacts: the effect of head restraint
properties // Spine. 2001. N~26. P.~2432--2440.

5. \textit{Martinez~J. L., Garcia~D. J.} A model for whiplash
//  Journal of Biomechanics. 1965. N~1. P.~23--32.

6. \textit{McHenry~R. R., Naab~K. N.} Computer simulation of the
automobile crash victim in a frontal collision: A validation study
report N~YB-2126-V-1. New York: Cornell Aeronautical Laboratory,
1966. 86~p.

7. \textit{Трегубов~В. П.} Анализ поведения тела человека при
горизонтальном импульсном воздействии~// Физическая механика. Л.:
Изд-во Ленингр. ун-та, 1976. Bып.~2. C.~140--154.

8. \textit{Tregubov~V. P., Klikunova~K. A., Asanchevsky~V. V.}
Some peculiarities of the skeletal muscle modeling // Acta of
Bioengineering and Biomechanics. 2008. Vol.~10, suppl.~1.
P.~30--36.

9. \textit{Orne~D., King Y. Liu}. A mathematical model of spinal
response to impact // Journal of Biomechanics. 1971. Vol.~4, N~1.
P.~49--71.

10. \textit{Mc\,Kenzie~J. A., Williams~J. F.} Dynamics of cervical
spine during whiplash // Journal of Biomechanics.  1971. Vol.~4,
N~6. P.~477--491.

11. \textit{Panjubi~M., Brand~ R., White~A.} Tree dimensional
flexibility and stiffness properties of human thoracic spine //
Journal of Biomechanics. 1976. Vol.~9. P.~185--192.

12. \textit{Maroney~S., Schultz~A., Miller~J., Anderson~G.}
Load-displacement properties of lower cervical spine motion
segments // Journal of Biomechanics. 1988. Vol.~21. P.~769--779.

13. \textit{Shea~M., Edwards~W. T., White~A. A., Hayes~W.}
Variations of stiffness and strength along the human cervical
spine // Journal of Biomechanics. 1991. Vol.~2. P.~95--107.

14. \textit{Sobczak~P., Golinski~W. Z., Gentle~R. C.}
Biomechanical evaluation of anterior cervical spine stabilization
using the finite element approach // Acta of Bioengineering and
Biomechanics.  1999. Vol.~1, N~1. P.~95--100.

15. \textit{Pintar~F. A., Miclebust~J., Sances A.,~Jr.,
Yoganandan~N.} Biomechanical properties of human intervertebral
disk in tension
// Proc. ASMEF Advances in Bioegineering (New York, USA). 1986.
P.~38--39.

16. \textit{Ciach~M., Awrejcewicz~J., Maciejczak~A., Radek~M.}
Experimental and numerical investigations of C5--C6 cervical
spinal segment before and after discectomy using the Cloward
operation technique // Acta of Bioengineering and Biomechanics.
1999. Vol.~1, N~1. P.~101--105.

17. \textit{Yoganandan~N., Kumaresan~S., Pintar~F. A.} Geometrical
and mechanical properties of human cervical spine ligaments //
Journal of Biomech. Engineering. 2000. Vol.~22. P.~623--629.

18. \textit{Deng~D. C., Goldsmith~W.} Response of a human
head/neck/upper-torso replica to dynamic loading. II.
Analytical-numerical model // Journal of Biomechanics. 1987.
Vol.~20, N~5. P.~487--497.

19. \textit{Skrzupiec~D. M., Pollintine~P., Przybyla~A., Dolan~P.,
Adams~M. A.} The internal mechanical properties of cervical
intervertebral discs as revealed by stress profilometry //
European Spine Journal. 2007. Vol.~6, N~10. P.~1701--1709.

20. \textit{Ступаков~Г. П., Козловский~А. П., Казейкин~В. С.}
Биомеханика позвоночника при ударных перегрузках в~практике
авиационных и~космических полетов. Л.: Наука, 1987. 240~с.

21. \textit{Stemper~B. D., Yoganandan~N., Pinter~F. A.} Validation
of a head--neck computer model for whiplash simulation // Medical
\& Biological Engineering \& Computing. 2004. N~42. P.~333--338.

22. \textit{Takeshima~T., Omokawa~S., Takaoka~T., Araki~M.,
Ueda~Y., Takakura~Y.} Sagittal alignment of cervical flexion and
expencion // Spine. 2002. Vol.~22. P.~2432--2442.

23. \textit{Хилл~А. В.} Механика мышечного сокращения. Старые
и~новые опыты / пер. с~англ. Ю.~А.~Шаронова; под ред.
Г.~М.~Франка. М.: Мир, 1972. 184~с.





}
