
{\small

\vskip4mm \noindent \textbf{Литература}

}

\vskip2mm

{\footnotesize

1. {\em Абанькин~А.~Е.} {Безусловная минимизация
$H$-гипердифференцируемых функций~// Журн. вычисл. математики
и~матем. физики. 1998. Т.~38(9). С.~1500--1508.}

2. {\em  Demyanov~V.~F.} Exhausters and convexificators --- New
tools in nonsmooth analysis~// Quasi-differentiability and related
topics / eds by V.~Demyanov, A.~Rubinov. Dordrecht: Kluwer
Academic Publ., 2000. P.~85--137.

3. {\em Abbasov~M.~E., Demyanov~V.~F.} {Extremum conditions for a
nonsmooth function in terms of exhausters and coexhausters~//
Proceedings of the Steklov Institute of Mathematics. 2010.
Vol.~269(1). P.~6--15.}

4. {\em Abbasov~M.~E., Demyanov~V.~F.} Adjoint coexhausters in
nonsmooth analysis and extremality conditions~// Journal of
Optimization Theory and Applications. 2013. Vol.~156(3).
P.~535--553.

5. {\em Dolgopolik~M.~V.} {Inhomogeneous convex approximations of
nonsmooth functions~// Russian Mathematics. 2012. Vol.~56(12).
P.~28--42.}

6. {\em Abbasov~M.~E.} {Second-order minimization method for
nonsmooth functions allowing convex quadratic approximations of
the augment~// Journal of Optimization Theory and Applications.
2016. Vol.~171(2). P.~666--674.}

\vskip 1.5mm

%\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

%\vskip 1.5mm

Статья поступила в~редакцию 23 марта 2018 г.

Cтатья принята к~печати 25 сентября 2018~г.

\vskip6mm К\,о\,н\,т\,а\,к\,т\,н\,а\,я \
и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я:

\vskip2mm \textit{Аббасов Меджид Эльхан оглы}~--- канд. физ.-мат.
наук, доц.; m.abbasov@spbu.ru

}
