
%\begin{center}
%{\footnotesize
%\begin{tabular}{lcr}
%$\issueyear$   & ВЕСТНИК\,САНКТ-ПЕТЕРБУРГСКОГО\,УНИВЕРСИТЕТА  &  Том\,13.\,\,Вып.\,$\issuenum$ \\
%\multicolumn{3}{c}{ПРИКЛАДНАЯ МАТЕМАТИКА.
%ИНФОРМАТИКА. ПРОЦЕССЫ УПРАВЛЕНИЯ}\\
%\end{tabular}
%\end{center}
%}
{\footnotesize \noindent$\issueyear$\mbox{~~~~~~~~~~}
ВЕСТНИК\,САНКТ-ПЕТЕРБУРГСКОГО\,УНИВЕРСИТЕТА
Т.\,13.\,\,Вып.\,$\issuenum$\linebreak %
\mbox{~~~~~~~~~~}ПРИКЛАДНАЯ МАТЕМАТИКА. ИНФОРМАТИКА. ПРОЦЕССЫ
УПРАВЛЕНИЯ %
}

%\ \\ \vskip 0.8mm\hrule \\ \hrule \\ \ \\

\vskip 0.5mm

\hline\vskip .5mm

\hline

\vspace{1.2cm} \noindent {\large ПРОЦЕССЫ УПРАВЛЕНИЯ}
\vspace{1.0cm}

\noindent{\footnotesize UDC 517.929}

\vskip3mm

\noindent{\it M.~Gomez $^1$, A.~V.~Egorov $^2$, S.~Mondi\'e $^1$}

\vskip3mm

\noindent{\bf A LYAPUNOV MATRIX BASED STABILITY CRITERION\\ FOR A
CLASS OF TIME-DELAY SYSTEMS$^*$}

\efootnote{

\vspace{-3mm}\parindent=7mm


%{\copyright} Н. А. Валиотти, 2014

\textit{Gomez Marco} --- postgraduate student;
mgomez@ctrl.cinvestav.mx

\textit{Egorov Alexey Valerievich} --- PhD of physical and
mathematical sciences, associate professor; alexey.egorov@spbu.ru

\textit{Mondi\'e Sabine} --- PhD of physical and mathematical
sciences, professor; smondie@ctrl.cinvestav.mx

\vskip 3.0mm


{\it Гомез Марко} --- аспирант; mgomez@ctrl.cinvestav.mx

{\it Егоров Алексей Валерьевич} --- кандидат физико-математических
наук, доцент;\\ alexey.egorov@spbu.ru

{\it Мондьё Сабин} --- кандидат физико-математических наук,
профессор; smondie@ctrl.cinvestav.mx


\vskip 3.0mm


$^{*}$ This work was supported by Project CONACYT N 180725 and by
Russian Foundation for Basic Research (RFBR), research project
N~16-31-00436 мол\_a (Работа выполнена при финансовой поддержке
CONACYT (проект №~180725) и~Российского фонда фундаментальных
исследований (проект №~16-31-00436 мол\_a)).

{\copyright} Санкт-Петербургский государственный университет,
\issueyear%
%
}

\vskip3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp09 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum07 } }\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp09 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum07}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\footnotesize


\noindent $^1$ CINVESTAV-IPN, 2508, Av. Instituto Polit\'ecnico
Nacional, Mexico city,

\noindent\hskip2.45mm 07360, United Mexican States


\noindent $^2$ St.~Petersburg State University, 7--9,
Universitetskaya nab., St.~Petersburg,

\noindent\hskip2.45mm 199034, Russian Federation


\vskip3mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item This paper is devoted to the stability analysis of linear
time-invariant systems with multiple delays. First, we recover
some basic elements of our research. Namely, we introduce the
complete type functionals, the delay Lyapunov matrix, and a space
of special functions that allow to present a family of necessary
stability conditions. Then, we prove a sufficient stability
condition (instability condition) in terms of a quadratic
Lyapunov---Krasovskii functional. Summarizing these results, we
finally obtain an exponential stability criterion for a class of
linear time-delay systems. The criterion requires only a finite
number of mathematical operations to be tested and depends
uniquely on the delay Lyapunov matrix. Refs~15.

\textit{Keywords}: time-delay system, Lyapunov matrix, stability
criterion.


\end{list}

}


%\newpage
\vskip4mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}



\noindent{\it М.~Гомез $^1$, А.~В.~Егоров $^2$, С.~Мондьё $^1$}

\vskip3mm\noindent{\bf КРИТЕРИЙ УСТОЙЧИВОСТИ ДЛЯ ОДНОГО\\ КЛАССА
СИСТЕМ С~ЗАПАЗДЫВАНИЕМ,\\ ОСНОВАННЫЙ НА МАТРИЦЕ ЛЯПУНОВА$^*$}

\vskip3mm


{\footnotesize


\noindent $^1$~CINVESTAV-IPN, Мексиканские Соединенные Штаты,

\noindent\hskip2.45mm 07360, Мехико, Проспект Национального
Политехнического института, 2508

\noindent $^2$~Санкт-Петербургский государственный университет,
Российская Федерация,

\noindent\hskip2.45mm 199034, Санкт-Петербург, Университетская
наб., 7--9


\vskip3mm


\item Статья посвящена анализу устойчивости линейных стационарных систем
с несколькими запаздываниями. Сначала мы вводим известные
элементы, на~которых базируется наше исследование, а~именно:
квадратичные функционалы Ляпунова---Красовского полного типа,
матрицу Ляпунова для систем с~запаздыванием и~пространство
некоторых функций, которые позволяют получить семейство
необходимых условий устойчивости. Эти функции строятся на~основе
значений фундаментальной матрицы на~некотором конечном отрезке.
Затем доказываем достаточное условие устойчивости (условие
неустойчивости), выраженное через специальный квадратичный
функционал Ляпунова---Красовского: показываем, что для
неустойчивой системы найдeтся точка из~некоторого компактного
бесконечномерного множества, значение функционала в~которой
отрицательно. Суммируя данные результаты, в~итоге получаем
критерий экспоненциальной устойчивости для некоторого класса
линейных систем с~запаздыванием. Проверка критерия требует лишь
конечного числа математических операций, а~проверяемые условия
зависят только от~матрицы Ляпунова для систем с~запаздыванием.
Библиогр. 15 назв.

{\it Ключевые слова}: система с~запаздыванием, матрица Ляпунова,
критерий устойчи\-вости.

}

\end{list}





\vskip 4mm



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{1. Introduction.} The importance of the
Lyapunov---Krasovskii functionals~[1] in the stability analysis of
time-delay systems is well known. The main ideas in the
construction of this class of functionals lies in the early
contributions by~[2--4]. A decisive impulse was given in the past
decade in~[5], where the so-called Lyapunov---Krasovskii
functionals of complete type were introduced. The main
characteristics of this class of functionals is that they have a
quadratic lower bound, and they are determined by the delay
Lyapunov matrix, solution of the dynamic, symmetry and algebraic
properties. For a deeper study on functionals of complete type and
the delay Lyapunov matrix, the reader is referred to the book~[6].

The availability of the analogous of the Lyapunov matrix  for
time-delay systems has allowed the extension of  well-known
results  for delay free systems to the time-delay case (see,
Section 2.12 in~[6]). One of the most interesting problems is the
extension of the stability criterion for linear systems, which
depends on the positivity of the Lyapunov matrix $V$, solution of
the Lyapunov equation $A^TV+VA=-W$. The extension of this result
to the time-delay case has been object of study in numerous
contributions in the last years. See, for instance, the necessary
stability conditions depending on the delay Lyapunov matrix
introduced in~[7] for systems with pointwise delays, in~[8] for
distributed delays and in~[9] for the neutral-type case, also the
stability criteria in~[10, 11], for retarded and neutral type
scalar equations, respectively.

A first criterion depending uniquely on the delay Lyapunov matrix
systems with multiple pointwise delays was presented in~[12] (see
also~[13]). However, the sufficiency part is only theoretical, as
one has to make an infinite number of mathematical operations in
order to check the stability condition (in this case, adopting the
terminology used in~[14], we say that the stability criterion is
\emph{infinite}). A first attempt to overcome this problem was
recently reported in~[14]. There, a new stability criterion
depending on the delay Lyapunov matrix and the fundamental matrix
of the system is introduced. The main distinctive feature of this
criterion is that it is \emph{finite}, i.~e. a finite number of
mathematical operations is required to test the stability
condition.  Nonetheless, the introduction of the fundamental
matrix  demands a greater computational effort in the test of the
conditions.

Inspired by the results in~[14], we present a new finite necessary
and sufficient stability conditions for a class of retarded type
systems depending uniquely on the delay Lyapunov matrix. The new
criterion is constrained to systems with sufficiently small
parameter values and delays. However, despite such restriction, it
differs from the previously mentioned results in two aspects: (i)
in contrast with~[12], the stability criterion presented in this
contribution is finite and (ii) unlike~[14], it does not require
the computation of the fundamental matrix, as it only depends on
the delay Lyapunov matrix.

The rest of the contribution is organized as follows. The
Lyapunov---Krasovskii framework and some basic definitions are
introduced in the next section. In Section~3 the problem
formulation is presented. Some auxiliary results concerning
instability conditions are pro\-vided in Section~4. In Section~5
the main result of the contribution is presented:  necessary and
sufficient stability condition for a class of retarded type
systems.  Finally we conclude with some remarks and future work.

Throughout the paper,
$\mathbb{PC}\left([-H,0],\mathbf{R}^n\right)$ and
$\mathbb{C}^{(1)}\left([-H,0],\mathbf{R}^n\right)$  denotes the
space of piecewise continuous  and continuously differentiable
vector functions defined on the interval $[-H,0]$, respectively.
The maximum and minimum eigenvalues of a matrix $Q$ are
represented by $\lambda_{\mathrm{max}}(Q)$ and
$\lambda_{\mathrm{min}}(Q)$, respectively. The notation $Q>0$
means that the matrix $Q$ is positive definite and $\|\cdot\|$
stands for the standard Euclidian vector norm. The square  block
matrix with $i$-th row and $j$-th column element $Q_{ij}$ is
represented by $\left[Q_{ij}\right]_{i,j=1}^r$.


\textbf{2. Preliminary results.} Consider the retarded type system
\begin{equation}
\label{ec:sys} \dot{x}(t)=\sum_{i=0}^{m}A_ix(t-h_i),
\end{equation}
where $0=h_0<h_1<\hdots <h_m=H$ and $A_i\in \mathbf{R}^{n\times
n}$. The initial function $\varphi$ belongs to the space
$\mathbb{PC}\left([-H,0],\mathbf{R}^n\right)$. The restriction of
the solution $x(t,\varphi)$, $t\>-H$, of system \eqref{ec:sys}
(such that $x(\theta,\varphi)=\varphi(\theta)$, $\theta\in[-H,0]$)
on the interval $[t-H,t]$, $t\>0$, is represented by
$$
x_t(\varphi):\theta \rightarrow x(t+\theta,\varphi),\;\; \theta\in
[-H,0].
$$
We equip the set of piecewise continuous initial functions with
the norm
$$
\|\varphi\|_H=\sup_{\theta\in [-H,0]}\|\varphi(\theta)\|.
$$

\textbf{Definition 1.} System \eqref{ec:sys} is exponentially
stable if there exist constants $\mu>0$ and $\sigma>0$ such that
$$
\|x(t,\varphi)\|\< \mu e^{-\sigma t}\|\varphi\|_H,\;\;~ t\> 0.
$$


The fundamental matrix of system \eqref{ec:sys}, denoted by $K$,
satisfies the  equation
$$
\dot K(t)=\sum_{i=0}^{m}A_i K(t-h_i),~ \;\; t>0,
$$
with the initial conditions $K(0)=I$ and $K(\theta)=0$ for
$\theta<0$.

Let us introduce the delay Lyapunov matrix.

\textbf{Definition 2.} The delay Lyapunov matrix $U(\tau)$,
$\tau\in[-H,H]$, associated with a symmetric matrix $W$ is a
continuous matrix function that satisfies the following equations:
$$
U'(\tau)=\sum_{i=0}^{m}U(\tau-h_i)A_i,\;\;\tau\in(0,H),
$$
$$
U^T(\tau)=U(-\tau),\;\;\tau\in[-H,H],
$$
$$
U'(+0)-U'(-0)=-W,
$$
called the dynamic, symmetry and algebraic properties,
respectively. Here $U'(+0)$ and $U'(-0)$ denote the corresponding
one-sided limits.


The existence and uniqueness of matrix $U$ depends on the Lyapunov
condition. This result is recalled in the next theorem (see [6]).

\begin{theoreng}
The delay Lyapunov matrix {\it U} associated with a matrix {\it W}
exists and is unique if and only if the Lyapunov condition holds,
i.~e. if the spectrum of system \eqref{ec:sys}
$$
\Lambda=\left\lbrace
s\left|\det\left(sI-\sum_{i=0}^{m}A_ie^{-sh_i}\right)=0
\right.\right\rbrace
$$
does not contain a root $\widehat s$ such that $-\widehat s$ also
belongs to the spectrum.
\end{theoreng}

In~[5] a functional, such that
\begin{equation}
\label{ec:derivative_functional}
\dfrac{d}{dt}v_0(x_t(\varphi))=-x^T(t,\varphi)Wx(t,\varphi),\;\;~
W>0, ~\;\;\varphi\in \mathbb{PC}([-H,0],\mathbf{R}^n),
\end{equation}
is introduced and is determined by the delay Lyapunov matrix as
follows:
\begin{gather*}
v_0(\varphi)=\varphi^T(0)U(0)\varphi(0) +2\varphi^T(0)\sum_{i=1}^{m}\int\limits_{-h_i}^{0}U(-h_i-\theta) A_i\varphi(\theta)d\theta ~+\\
+~ \sum_{i=1}^{m}\sum_{j=1}^{m}\int\limits_{-h_i}^{0}\int\limits_{-h_j}^{0} \varphi^T(\theta_1)A_i^TU(\theta_1-\theta_2+h_i-h_j) A_j\varphi(\theta_2) d\theta_2 d\theta_1,\\
\varphi\in \mathbb{PC}\left([-H,0],\mathbf{R}^n\right).
\end{gather*}
A functional based on $v_0$ that plays a key role for obtaining
necessary and sufficient stability condition depending on the
delay Lyapunov matrix  is presented next~[7, 12]:
\begin{equation}
\label{ec:functional_v1}
v_1(\varphi)=v_0(\varphi)+\int\limits_{-H}^{0}\varphi^T(\theta)W\varphi(\theta)d\theta,
\;\;~ \varphi\in \mathbb{PC}\left([-H,0],\mathbf{R}^n\right).
\end{equation}
Its derivative along the solutions of system \eqref{ec:sys}
satisfies
$$
\dfrac{d}{dt}v(x_t(\varphi))=-x^T(t-H,\varphi)Wx(t-H,\varphi),~\;\;
\varphi\in \mathbb{PC}([-H,0],\mathbf{R}^n).
$$
We introduce now the following bilinear functional:
\begin{gather*}
z(\varphi_1,\varphi_2)=\varphi_1^T(0)U(0)\varphi_2(0)~ +\\
+~ \varphi_1^T(0)\sum_{i=1}^{m}\int\limits_{-h_i}^{0}U(-h_i-\theta) A_i\varphi_2(\theta)d\theta +\sum_{i=1}^{m}\int\limits_{-h_i}^{0} \varphi^T_1(\theta)A_i^TU(h_i+\theta)d\theta\varphi_2(0)~ +\\
+~ \sum_{i=1}^{m}\sum_{j=1}^{m}\int\limits_{-h_i}^{0}\int\limits_{-h_j}^{0} \varphi_1^T(\theta_1)A_i^TU(\theta_1-\theta_2+h_i-h_j) A_j\varphi_2(\theta_2) d\theta_2 d\theta_1~ +\\
+~
\int\limits_{-H}^{0}\varphi_1^T(\theta)W\varphi_2(\theta)d\theta,\;\;~
\varphi_1,\varphi_2\in
\mathbb{PC}\left([-H,0],\mathbf{R}^n\right).
\end{gather*}
Notice that this bilinear functional is related to the functional
$v_1$ by the equality $v_1(\varphi)=z(\varphi,\varphi)$. In the
next lemma (see [14]) we recall some results concerning the
quadratic upper bounds of the functional $v_1$ and the bilinear
functional $z$.
\begin{lemmaeng}
\label{lem:upper_bound} There exists a positive number $\beta$
such that
$$
v_1(\varphi)\< \beta\|\varphi\|^2_H,\;\;~ \varphi\in
\mathbb{PC}\left([-H,0],\mathbf{R}^n\right),
$$
$$
|z(\varphi_1,\varphi_2)|\<
\beta\|\varphi_1\|_H\|\varphi_2\|_H,\;\;~ \varphi_1,\varphi_2\in
\mathbb{PC}\left([-H,0],\mathbf{R}^n\right).
$$
\end{lemmaeng}


\textbf{3. Problem statement.} Consider the following function
that depends on the funda\-mental matrix:
\begin{equation}
\label{ec:function_psi}
\psi_r(\theta)=\sum_{i=1}^{r}K(\tau_i+\theta)\gamma_i,~ \;\;
\theta\in [-H,0],
\end{equation}
where $\gamma_i\in\mathbf{R}^n$,~ $\tau_i\in[0,H]$,~
$i=\overline{1,r}$.

Based on new properties that connect the fundamental matrix $K$
with the delay Lyapu\-nov matrix $U$, and the introduction of the
functional $z(\cdot,\cdot)$, the next equality has been provided
in~[7]:
\begin{equation}
\label{ec:functional_matLyap}
v_1(\psi_r)=\gamma^T\left[U(\tau_j-\tau_i)\right]_{i,j=1}^r\gamma
\end{equation}
with $\gamma=\begin{pmatrix} \gamma_1^T & \hdots & \gamma_r^T
\end{pmatrix}^T$.

Take equidistant points from the segment $[0,H]$:
$$
\tau_i=\dfrac{i-1}{r-1}H,~ \;\;i=\overline{1,r}.
$$
For these points introduce block-matrix
$$
\mathcal{K}_r=\left[U(\tau_j-\tau_i)\right]_{i,j=1}^r
=\left[U\left(\dfrac{j-i}{r-1}H\right)\right]_{i,j=1}^r
$$
for $r\>2$ and separately $\mathcal{K}_1=U(0)$. To make the
notation more clear, we present three particular cases:
$$
\mathcal{K}_2=
\begin{pmatrix}
U\left(\vphantom{h}0\right) & U\left(H\right)\\
\ast & U\left(\vphantom{h}0\right)
\end{pmatrix},
$$
$$
\mathcal{K}_3=
\begin{pmatrix}
U(0) & U(H/2) & U(H) \\
\ast & U(0) & U(H/2)\\
\ast & \ast & U(0)
\end{pmatrix},
$$
$$
\mathcal{K}_4=
\begin{pmatrix}
U(0) & U(H/3) & U(2H/3) & U(H) \\
\ast & U(0) & U(H/3) & U(2H/3)\\
\ast & \ast & U(0) & U(H/3)\\
\ast & \ast & \ast & U(0)
\end{pmatrix}.
$$
Stars here denote the blocks, which are obvious, as we deal with
the symmetric matrices.

In~[12] an infinite stability criterion for system \eqref{ec:sys}
is introduced.
\begin{theoreng}
\label{teo:criterion} Assume that the Lyapunov condition holds.
System \eqref{ec:sys} is exponentially stable if and only if for
every natural number $r$, the following holds$:$
\begin{equation}
\label{ec:criterion} \mathcal{K}_r>0.
\end{equation}
\end{theoreng}
The result is based on the fact that one can make an arbitrarily
close approximation of any continuous function by the function
$\psi_r$ given by \eqref{ec:function_psi} for sufficiently large
$r$. This criterion can be successfully used as a necessary
stability condition to discard unstable systems, but checking of
the stability requires an infinite number of mathematical
operations, which leads us to formulate the problem addressed in
this contribution.

\begin{probleng}
\label{prob:problem} Find an estimate of the number $r$ for which
condition \eqref{ec:criterion} of Theorem 2 is necessary and
sufficient for the stability of system \eqref{ec:sys}.
\end{probleng}


\textbf{4. Auxiliary results.} Consider the compact set~[14]
$$
\mathcal{S}=\bigg\{\vphom \varphi\in
\mathbb{C}^{(1)}\left([-H,0],\mathbf{R}^n\right)\:
\right|\left.\:\vphom\|\varphi\|_H=\|\varphi(0)\|=1,~\;\;\|\varphi'(\theta)\|\<
M,~ \;\;\theta\in[-H,0]\bigg\},
$$
where $M=\displaystyle\sum_{i=0}^{m}\|A_i\|$. We introduce some
instrumental results that allow us to obtain the main contribution
of the paper. The first one concerns the approximation of a
function $\varphi$ of the compact set $\mathcal{S}$ by the
function $\psi_r$ given by \eqref{ec:function_psi}. This
approximation  has been introduced in~[14] and is included here
for the sake of completeness. The second one is inspired by~[15]
and corresponds to an instability condition of system
\eqref{ec:sys} based on the functional $v_1$.


\textit{\textbf{4.1. Approximation of the set $\mathcal{S}$.}}
Consider an arbitrary initial function $\varphi$ from the set
$\mathcal{S}$ and the function $\psi_r$ of the form
\eqref{ec:function_psi}, which satisfies the following equalities:
$$
\psi_r(-\tau_i)=\varphi(-\tau_i),\;\;i=\overline{1,r},
$$
with $\tau_i=(i-1)H/(r-1)$, $i=\overline{1,r}$. Such function
always exists~[14], and vectors $\gamma_i$, $i=\overline{1,r}$,
can be computed iteratively. The next lemma (see [14]) gives an
estimate of the approximation error between
$\varphi\in\mathcal{S}$ and $\psi_r$, denoted by
$R_r=\varphi-\psi_r$.

\begin{lemmaeng}
\label{lem:approximation_initialcond} For every
$\varphi\in\mathcal{S}$,
$$
\|R_r\|_H=\|\varphi-\psi_r\|_H\<\varepsilon_r,
$$
where
$$
\varepsilon_r=\dfrac{(M+L)e^{LH}}{1/\delta_r+L}.
$$
Here $\delta_r=\dfrac{H}{r-1}$ and $L$ is the Lipschitz constant
for the fundamental matrix on $[0,H]$, i.~e. it is such that
$\|K'(t)\|\< L$ on $[0,H]$ almost everywhere.
\end{lemmaeng}


\textit{\textbf{4.2. Instability condition.}} The next lemma is
useful for proving the main result of this section.
\begin{lemmaeng}
\label{lem:eigenvectors} Let $P$ and $Q$ be real matrices. If
$\det(P+iQ)=0$, then there exist two vectors $C_1$ and $C_2$ such
that
%\begin{enumerate}

$1)$ $(P+iQ)(C_1+iC_2)=0;$

$2)$ $\|C_1\|=1;$

$3)$ $\|C_2\|\< 1;$

$4)$ $C_1^{T}C_2=0$.
%\end{enumerate}
Here $i$ is the imaginary unit.
\end{lemmaeng}
%\begin{proof}


P r o o f. Since $\det(P+iQ)=0$, there exists a complex vector
$\xi_1+i\xi_2\neq 0$, such that
$$
\left(P+iQ\right)\left(\xi_1+i\xi_2\right)=0.
$$
Let us introduce now the following vectors:
$$
\widehat C_1=\xi_1+b\xi_2,
$$
$$
\widehat C_2=-b\xi_1+\xi_2,
$$
where $b$ is a real number, and observe that
$$
\left(P+iQ\right)\left(\widehat C_1+i\widehat C_2\right)=0.
$$
Consider the product
$$
\widehat C_1^T\widehat
C_2=(1-b^2)\xi_1^T\xi_2-b\left(\|\xi_1\|^2-\|\xi_2\|^2\right).
$$
We need to choose $b$ to guarantee that $\widehat C_1^T\widehat
C_2=0$. If $\xi_1^T\xi_2=0$ one can take $b=0$, otherwise, one can
take any real solution of the quadratic equation, which always has
two:
$$
b^2+b\dfrac{\|\xi_1\|^2-\|\xi_2\|^2}{\xi_1^T\xi_2}-1=0.
$$

Now, at least one of the vectors $\widehat C_1$ and $\widehat C_2$
is nonzero and the desired vectors $C_1$ and $C_2$ can be
constructed as follows: if $\|\widehat C_1\|\> \|\widehat C_2\|$,
we have
$$
C_1=\dfrac{\widehat C_1}{\|\widehat C_1\|},~ \;\;
C_2=\dfrac{\widehat C_2}{\|\widehat C_1\|},
$$
and if $\|\widehat C_1\|<\|\widehat C_2\|$,
$$
C_1=\dfrac{\widehat C_2}{\|\widehat C_2\|},\;\;~
C_2=-\dfrac{\widehat C_1}{\|\widehat C_2\|}.
$$ \hfill\square
%\end{proof}

We provide an instability condition for system \eqref{ec:sys}
depending on the functional $v_1$. The result is based on~[15],
where the condition is obtained for the functional $v_0$.









\begin{lemmaeng}
\label{lem:instability} Assume that system \eqref{ec:sys} is such
that
\begin{equation}
\label{ass:sys} \dfrac{\lambda_{\min}(W)}{\lambda_{\max}(W)}> 4MH,
\end{equation}
where the matrix $W$ is the one to which the delay Lyapunov matrix
is associated. If system \eqref{ec:sys} is unstable, there exists
$\varphi\in \mathcal{S}$, such that
$$
v_1(\varphi)\< -\alpha_1,
$$
here
$\alpha_1=\dfrac{\lambda_{\min}(W)}{4M}-\lambda_{\max}(W)H>0$.
\end{lemmaeng}
%\begin{proof}

P r o o f.  As system \eqref{ec:sys} is unstable,  there exist an
eigenvalue $\lambda=\alpha+i\beta$ with $\alpha>0$, and two
vectors $C_1,\:C_2\in\mathbf{R}^n$ that satisfy the conditions of
Lemma 3 such that the following expression is a solution of system
\eqref{ec:sys}:
$$
x(t,\varphi)=e^{\alpha t}\phi(t),~ \;\;\phi(t)=\cos\beta t
C_1-\sin \beta t C_2,~ \;\;t\in (-\infty,\infty),
$$
which corresponds to the initial function
$$
\varphi(\theta)=x(\theta,\varphi),~ \;\;\theta\in [-H,0].
$$
We prove first that $\varphi\in \mathcal{S}$. By Lemma 3, it is
easy to see that $\left\|\varphi(0)\right\|=1$ and
$$
\max\limits_{t\in\mathbf{R}}\|\phi(t)\|=1.
$$
Indeed, $\|\phi(t)\|^2=\|C_1\|^2+(\|C_2\|^2-\|C_1\|^2)\sin^2 \beta
t\<1$.

Thus,
$$
\left\|x(\theta)\right\|=e^{\alpha\theta}\left\|\phi(\theta)\right\|\<
1,~ \;\;\theta\<0.
$$
Finally, since $x(t,\varphi)$ is a solution of system
\eqref{ec:sys}, we get
$$
\|\varphi'(t)\|=\|\dot{x}(t)\|\<\sum_{i=0}^m\|A_i\|\|x(t-h_i)\|\<
M \|\varphi(0)\|=M,~ \;\;t\in [-H,0].
$$

We focus next on the functional $v_0$. Let us set $T=2\pi/\beta$
for $\beta\neq 0$ and $T=1$ for $\beta=0$. It is easy to see that
$T$ is a period of $\phi(t)$. By equation
\eqref{ec:derivative_functional},
$$
\dfrac{d}{dt}v_0(x_t(\varphi))=-x^T(t,\varphi)Wx(t,\varphi),~ \;\;
t\> 0,
$$
which implies that
$$
v_0(\varphi)=v_0(x_T)+\int\limits_{0}^{T}
x^T(t,\varphi)Wx(t,\varphi)dt.
$$
As $x(T+\theta)=e^{\alpha T}\varphi(\theta)$,
$$
v_0( x_T(\varphi))=e^{2\alpha T}v_0(\varphi),
$$
hence,
$$
v_0(\varphi)=-\dfrac{1}{e^{2\alpha T}-1}\int\limits_{0}^{T}
x^T(t,\varphi)W x(t,\varphi)dt\<
-\dfrac{\lambda_{\min}(W)}{(e^{2\alpha
T}-1)}\int\limits_{0}^{T}\|x(t)\|^2dt.
$$
By Lemma 3,
$$
\int\limits_{0}^{T}\|x(t)\|^2dt=\left(\int\limits_{0}^{T}e^{2\alpha
t}\left(\cos^2(\beta t)\|C_1\|^2+\sin^2(\beta
t)\|C_2\|^2\right)dt\right) \>\int\limits_{0}^{T}e^{2\alpha t}
\cos^2(\beta t)dt.
$$
Solving the right hand side integral, we obtain
\begin{gather*}
\int\limits_{0}^{T}e^{2\alpha t} \cos^2(\beta t)dt=\dfrac{1}{4\alpha}(e^{2\alpha T}-1) +\dfrac{1}{4(\alpha^2+\beta^2)}\left(e^{2\alpha T}(\alpha \cos (2\beta T)+\beta \sin (2\beta T))-\alpha\right)=\\
=\dfrac{(2\alpha^2+\beta^2)\left(e^{2\alpha T}-1\right)}{4\alpha
(\alpha^2+\beta^2)}\>\dfrac{e^{2\alpha T}-1}{4\alpha}.
\end{gather*}
Taking into account that the spectral abscissa can be estimated by
$M=\sum_{i=0}^{m}\|A_i\|$, we arrive at
$$
v_0(\varphi)\<-\dfrac{\lambda_{\min}(W)}{4\alpha}\<
-\dfrac{\lambda_{\min}(W)}{4M}.
$$
Finally, from  expression \eqref{ec:functional_v1} for the
functional $v_1$,  it follows that
$$
v_1(\varphi)\<-\dfrac{\lambda_{\min}(W)}{4M}+\lambda_{\max}(W)H=-\alpha_1.
$$  \hfill\square
%\end{proof}


\textbf{5. Necessary and sufficient conditions.} We provide the
main result of the contribu\-tion, namely, finite necessary and
sufficient stability conditions for the system of the form
\eqref{ec:sys} that satisfies inequality \eqref{ass:sys}.
\begin{theoreng}
\label{teo:finite_criterion} Assume that the Lyapunov condition
holds and  system \eqref{ec:sys} satisfies  \eqref{ass:sys}.
System \eqref{ec:sys} is exponentially stable if and only if
$$
\mathcal{K}_r>0
$$
for
\begin{equation}
\label{ec:number_r}
r=1+H\left(e^{LH}(M+L)\left(\alpha+\sqrt{\alpha(\alpha+1)}\right)-L\right),
\end{equation}
where $\alpha=\beta/\alpha_1$.
\end{theoreng}
%\begin{proof}

P r o o f. The necessity directly follows from Theorem 2. In order
to prove the sufficiency, we assume by contradiction that system
\eqref{ec:sys} is unstable but the Lyapunov condition and the
conditions of the theorem hold. Consider $\varphi\in \mathcal{S}$
and notice that
$$
v_1(\varphi)=v_1(R_r+\psi_r)=v_1(\psi_r)+2z(\varphi,
R_r)-v_1(R_r).
$$
By Lemmas~1 and 4,
$$
v_1(\psi_r)\< -\alpha_1 +2\beta\|R_r\|_H+\beta\|R_r\|_H^2.
$$
By using Lemma 2 and considering $r$ given by
\eqref{ec:number_r}, we have that
$$
\|R_r\|_H\< \dfrac{(M+L)e^{LH}}{1/\delta_r+L}\<
\dfrac{\alpha_1}{\sqrt{\beta(\beta+ \alpha_1)}+\beta},
$$
which implies that
$$
-\alpha_1+2\beta\|R_r\|_H+ \beta\|R_r\|_H^2\< 0.
$$
Finally, from the previous inequality and equation
\eqref{ec:functional_matLyap}, we get
$$
v_1(\psi_r)=\gamma^T\mathcal{K}_r\gamma\< 0.
$$
The obtained contradiction finishes the proof. \hfill\square
%\end{proof}

\textbf{Remark.} {\it The number $r$ given by \eqref{ec:number_r}
has the same form as the estimate obtained in~$\mathrm{[14]}$. The
only difference lies in the computation of $\alpha$ as in this
case $\alpha_1$ does not come from the quadratic lower bound of
the functional $v_1$, but from the instability result given in
Lemma~4}.
%\end{obs}

Although Theorem 3 partially solves Problem 1 by giving a finite
stability criterion, it only works for a constrained class of
systems of the form \eqref{ec:sys}. However, in contrast with the
finite stability criterion introduced in~[14], here one does not
need the computation of the fundamental matrix, which increases
the computational effort and seems not to be a trivial task in the
non-commensurate delays case. Obviously, the constraints
introduced by inequality \eqref{ass:sys} can be relaxed if one
considers a positive definite matrix $W$ such that
$\lambda_{\mathrm{min}}(W)=\lambda_{\mathrm{max}}(W)$, or uses
less conservative estimate on $\alpha_1$ in the proof of Lemma~4.


\textbf{6. Conclusions.} A new stability criterion for a class of
time delay systems is introduced in the framework of the
Lyapunov---Krasovskii functionals. The main characteristic of this
criterion is that it depends exclusively on the delay Lyapunov
matrix and only requires a finite number of mathematical
operations to be checked. Future research directions include the
generalization to systems without restrictions in the parameter
values and the extension to the neutral-type case.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%\input{06/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{07/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize



\vskip 3mm

%\thispagestyle{empty}



\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~13.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. А. П. Жабко.

\vskip 1mm

\noindent Статья поступила в~редакцию 2 сентября 2017~г.

\vskip 1mm

\noindent Статья принята к~печати 12 октября 2017~г.


}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vskip 5mm

%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak \vskip 3mm

%{\it Балонин Николай Алексеевич}~-- доктор технических наук,
%профессор; e-mail: korbendfs@mail.ru

%{\it Сергеев Михаил Борисович}~-- доктор технических наук,
%профессор,  директор; e-mail: mbse@mail.ru

%\vskip 2mm

%\emph{Balonin Nikolaj Alekseevich}~-- doctor of technical
%sciences, professor; e-mail: korbendfs@mail.ru


%\emph{Sergeev Mikhail Borisovich}~-- doctor of technical sciences,
%director; e-mail: mbse@mail.ru


%}


%\thispagestyle{empty}
