

{\footnotesize

\vskip 4mm
%\newpage

\noindent {\small\textbf{References} }

\vskip 4mm





1. Krasovskii N. N. O primenenii vtorogo metoda Lyapunova dlya
uravnenij s zapazdyvaniyami vremeni [On the application of the
second method of Lyapunov for equations with time delays].
\textit{Prikladnaya Matematika i Mekhanika} [\textit{Applied
Mathematics and Mechanics}], 1956, vol.~20, pp.~315--327. (In
Russian)

2. Datko R. An algorithm for computing Lyapunov functionals for
some differential difference equations. \textit{Ordinary
Differential Equations}. Ed. by L. Weiss. New York, Academic
Press, 1972, pp.~387--398.

3. Infante E. F., Castelan W. B. A Liapunov functional for a
matrix difference-differential equation. \textit{Journal of
Differential Equations}, 1978, vol.~29, pp.~439--451.

4. Huang W. Generalization of Liapunov’s theorem in a linear delay
systems. \textit{Journal of Mathematical Analysis and
Applications}, 1989, vol.~142, pp.~83--94.

5. Kharitonov V. L., Zhabko A. P. Lyapunov---Krasovskii approach
to the robust stability analysis of time-delay systems.
\textit{Automatica}, 2003, vol.~39(1), pp.~15–20.

6. Kharitonov~V.~L. \textit{Time-delay systems. Lyapunov
functionals and matrices}. Basel, Birkh\"auser Press, 2013, 311~p.

7. Egorov A. V., Mondi\'e S. Necessary stability conditions for
linear delay systems. \textit{Automatica}, 2014, vol.~50(12),
pp.~3204--3208.

8. Cuvas C., Mondi\'e S. Necessary stability conditions for delay
systems with multiple pointwise and distributed delays.
\textit{IEEE Transactions on Automatic Control}, 2016, vol.~61(7),
pp.~1987--1994.

9. Gomez M. A., Egorov A. V., Mondi\'e S. Necessary stability
conditions for neutral type systems with a single delay.
\textit{IEEE Transactions on Automatic Control}, 2016, vol.~62(9),
pp.~4691--4697.

10. Mondi\'e S. Assessing the exact stability region of the
single-delay scalar equation via its Lyapunov function.
\textit{IMA Journal of Mathematical Control and Information},
2012, vol.~29(4), pp.~459--470.

11. Egorov A. V. A stability criterion for the neutral type
time-delay equation. \textit{2016 Intern. Conference on
``Stability and Oscillations of Nonlinear Control Systems''}.
Moscow, Russia, V.~A.~Trapeznikov Institute of Control Sciences,
2016, pp.~1--4.

12. Egorov A. V. A new necessary and sufficient stability
condition for linear time-delay systems. \textit{19th IFAC
Workshop on Time Delay Systems}. Cape Town, South Africa, 2014,
pp.~11018--11023.

13. Egorov A. V., Cuvas C., Mondi\'e S. Necessary and sufficient
stability conditions for linear systems with pointwise and
distributed delays. \textit{Automatica}, 2017, vol.~80,
pp.~218--224.

14. Egorov A. V. A finite necessary and sufficient stability
condition for linear retarded type systems. \textit{Conference on
Decision and Control}. Las Vegas, USA, 2016, pp.~3155--3160.

15. Medvedeva I. V., Zhabko A. P. Synthesis of Razumikhin and
Lyapunov---Krasovskii approac\-hes to stability analysis of
time-delay systems. \textit{Automatica}, 2015, vol.~51,
pp.~372--377.%\pubdata




\vskip 2mm

{\bf For citation:}   Gomez~M., Egorov~A.~V., Mondi\'e~S. A
Lyapunov matrix based stability criterion for a class of
time-delay systems. {\it Vestnik of Saint Petersburg University.
Applied Mathematics. Com-\linebreak puter Science. Control
Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p7}--\pageref{p7e}. \doivyp/
spbu10.\issueyear.\issuenum07


}
