
{\normalsize

\vskip 6mm
%\newpage

\noindent{\bf Families of embedded methods of order six %$^{*}$
 }

}

\vskip 3mm

{\small

\noindent{\it I.~V.~Olemskoy,~O.~S.~Firuylina,~O.~A.~Tumka%
%, I.~О. Famylia%$\,^2$%

 }

\vskip 3mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm \indent~$^{*}$ Работа выполнена в рамках государственного %
%задания по теме N 0827-2018-0003 «Фундаментальные исследования %
%океанологических процессов, определяющих состояние и эволюцию морской %
%среды под влиянием естественных и антропогенных факторов, на основе %
%методов наблюдения и моделирования».\par%
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Санкт-Петербургский государственный
%%университет, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^2$~%
St\,Petersburg State University, 7--9, Universitetskaya nab., St\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 3%
mm


\noindent \textbf{For citation:}  Olemskoy~I.~V.,~Firyulina~O.~S., Tumka~O.~A. Families of embedded methods of order six. {\it Vest\-nik of Saint Pe\-ters\-burg University. Applied Mathe\-ma\-tics. Computer
Science. Cont\-rol Pro\-cesses}, %\,
\issueyear, vol.~18, iss.~\issuenum, pp.~\pageref{p9}--\pageref{p9e}. \\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum09 (In Russian)

\vskip2.2mm

\begin{hyphenrules}{english}

%\pagebreak

{\leftskip=7mm\noindent In the paper embedded methods of order six, with seven stages for solving systems of ordinary differential equations, are derived. A family of Runge\,---\,Kutta methods, of order six with seven stages and having three free parameters, is presented. This family is extended in two different ways with embedded methods to form families of embedded method pairs. Numerical comparison is given for certain examples of the embedded pairs from the constructed families.
\\[1mm]
\textit{Keywords}: Cauchy problem, embedded methods, error control, order, stage, order conditions, simplifying conditions.\par}

\vskip6mm

\end{hyphenrules}
%\pagebreak

\noindent \textbf{References} }

\vskip 2.0mm

{\footnotesize

1. {\rm Arushanyan~O.~B., Zaletkin~S.~F.} {\it Chislennoe reshenie obyknovennykh differentsial'nykh uravnenii na Fortrane} [{\it Numerical solution of ordinary differential equations on
Fortran}]. Moscow, Moscow University Press, 1990, 336~p. (In Russian)

2. {\rm Hairer~E., Nersett~S.~P., Wanner~G.} {\it Reshenie
obyknovennykh differentsial’nykh urav\-ne\-nii.~I.~Nezhestkie
zadachi} [{\it Solving ordinary differential equation.~I. Nonstiff
problems}]. Ed. 3. Berlin, Heidelberg, Springer-Verlag Publ.,
2008, 528~p. (Rus. ed.: Hairer~E., Nersett~S., Wanner~G. {\it
Reshenie obyknovennykh differentsial’nykh uravnenii.~I. Nezhestkie
zadachi.} Mos\-cow, Mir Publ., 1990, 512~p.)


3. {\rm Fehlberg~E.} Classical fifth-, sixth-, seventh- and
eighth order Runge\,---\,Kutta formulas with step  size
control. NASA Technical Report, 1968, no.~287. {\it
Computing}, 1969, vol.~4, pp.~93--106.

4. {\rm Butcher~J.~C.} Coefficients for the study of
Runge\,---\,Kutta integration processes. {\it Journal of the
Australian Mathematical Society}, 1963, vol.~3, pp.~185--201.

5. {\rm Butcher~J.~C.} On Runge\,---\,Kutta processes of high
order. {\it Journal of the Australian Mathematical Society}, 1964,
vol.~4, pp.~179--194.

6. {\rm Dormand~J.~R., Prince~P.~J.}~ A family of embedded
Runge\,---\,Kutta formulae. {\it Journal of Com\-pu\-ta\-tio\-nal and
Applied Mathematics}, 1980, vol.~6, iss.~1, pp.~19--26.

7. {\rm Dormand~J.~R., Prince~P.~J.} High order embedded
Runge\,---\,Kutta formulae. {\it Journal of Com\-pu\-ta\-tional and Applied
Mathematics}, 1981, vol.~7, iss.~1, pp.~67--75.

8. {\rm Olemskoy~I.~V., Eremin~A.~S.} Algorithm of
construction of effective explicit methods for structurally
partitioned systems of ordinary differential equations. {\it
Vestnik of Saint Petersburg Universitety. Applied Mathematics.
Computer Sciences. Control Processes}, 2021, vol.~17, iss.~4,
pp.~353--369. \\https://doi.org/10.21638/11701/spbu10.2021.404

9. {\rm Eremin~A.~S., Kovrizhnykh~N. A., Olemskoy~I.~V.} An
explicit one-step multischeme sixth order me\-thod for systems of
special structure. {\it Applied Mathematics and
Computation}, 2019, vol.~347, pp.~853--864.

10.{ \rm Olemskoy~I.~V., Kovrizhnykh~N.~A.}  Semeystvo
shestietapnykh metodov shestogo poryadka [A~fa\-mi\-ly of sixth-order methods  with six stages]. {\it Vestnik of Saint Petersburg University. Applied Ma\-the\-ma\-tics. Computer Sciences. Control Processes}, 2018, vol.~14, iss.~3, pp.~215--229.
\\https://doi.org/10.21638/11701/spbu10.2018.303 (In
Russian)

11. {\rm Olemskoy~I.~V., Kovrizhnykh~N.~A., Firyulina~O. S.}
Dvukhparametricheskoye semeystvo metodov shestogo poryadka
integrirovaniya sistem obyknovennykh differentsialnykh
uravneniy [Two-parametric family of sixth order numerical
methods for solving systems of ordinary differential equations].
{\it Vestnik of Saint Petersburg University. Applied
Mathematics. Computer Sciences. Control Processes}, 2019, vol.~15,
iss.~4, pp.~502--517. %\\
https://doi.org/10.21638/11702/spbu10.2019.407 (In Russian)


\vskip1.5mm Received:  January 12, 2022.

Accepted: May 05, 2022.

\vskip6mm
A\,u\,t\,h\,o\,r\,s' \, i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%
%
\vskip2mm \textit{Igor V. Olemskoy} --- Dr.~Sci.~in Physics and Mathematics, Professor; i.olemskoj@spbu.ru \par
%
\vskip2mm \textit{Oxana S. Firyulina} --- PhD in Physics and Mathematics, Senior Lecturer; firyulina.oxana@mail.ru \par
%
\vskip2mm \textit{Oleg A. Tumka} ---  Senior Lecturer;
tumka.oleg@rambler.ru \par
%
%
}
