


\zageng{519.213}{A.~A.~Rogov$^1$, ~A.~G.~Varfolomeyev$^1$,
~A.~O.~Timonin$^1$, ~K.~A.~Proen\c{c}a$^2$}{A PROBABILISTIC
APPROACH TO COMPARING THE DISTANCES\\ BETWEEN PARTITIONS OF A
SET$^{*}$}{



\vspace{-3mm}\parindent=7mm



%{\copyright} А.~В.~Буре, 2014




\emph{Rogov Aleksandr Aleksandrovisch} --- doctor of technical
sciences, professor,\\ head of department; rogov@psu.karelia.ru


\emph{Varfolomeyev Aleksey Gennadievich} --- PhD of physical and
mathematical sciences, associate\\ professor; avarf@petrsu.ru



\emph{Timonin Artem Olegovich} --- postgraduate student;
timonin.artem@gmail.com


\emph{Proen\c{c}a Kseniya Aleksandrovna} --- data scientist;
kseniya.proenca@gmail.com



\vskip 1.5mm


\emph{Рогов Александр Александрович} --- доктор технических наук,
профессор, заведующий каферой; rogov@psu.karelia.ru


\emph{Варфоломеев Алексей Геннадьевич} --- кандидат
физико-математических наук, доцент;\\ avarf@petrsu.ru


\emph{Тимонин Артем Олегович} --- аспирант;
timonin.artem@gmail.com


\emph{Проенца Ксения Александровна} --- cпециалист по~обработке
и~анализу данных;\\ kseniya.proenca@gmail.com



\vskip 1.5mm



$^{*}$ The work was supported by the Program of Strategic
Development of Retrozavodsk State University within the framework
of the implementation of a set of activities for the development
of research activities for 2012--2016.

Работа выполнена при поддержке Программы стратегического развития
Петрозаводского государственного университета в~рамках реализации
комплекса мероприятий по~развитию научно-ис\-следовательской
деятельности на~2012--2016~гг.

{\copyright} Санкт-Петербургский государственный университет,
\issueyear%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
%\fancyfoot[LO]{{\footnotesize\emph{\doivyp07 } }\hfill\thepage}%
\fancyfoot[LO]{{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum02 } }\hfill\thepage}%
%\fancyfoot[RE]{\thepage\hfill{\footnotesize\emph{\doivyp07 } } }%
\fancyfoot[RE]{\thepage\hfill{\footnotesize\rm{\doivyp/spbu10.\issueyear.\issuenum02}}}%
%\fancyfoot[LO]{\hfill{\fontsize{10.5}{10.5}\selectfont \thepage}}%
%\fancyfoot[RE]{{\fontsize{10.5}{10.5}\selectfont \thepage}\hfill}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize


\noindent $^1$~Petrozavodsk State University, 33, Lenin pr.,
Petrozavodsk,

\noindent\hskip2.45mm 185910, Russian Federation


\noindent $^2$~Feedzai, Avenida D. Joao II, Lote 1.16.01 Piso 11,
Lisbon, 1990-083, Portugal





\vskip1.8mm


\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}


\item This article describes and compares a number of classical metrics
to compare different approaches to partition a given set, such as
the Rand index, the Larsen and Aone coefficient, among others. We
developed a probabilistic framework to compare these metrics and
unified representation  of distances that uses a common set of
parameters. This is done by taking all possible values of
similarity measurements between different possible partitions and
graduating them by using quantiles of a distribution function. Let
${\lambda }_{\alpha }$ be a quantile with $\alpha $ level for
distribution function $F_{\rho }\left(t\right)=P\left(\rho
<t\right)$. Then if the proximity measurement $\rho $ is not less
than ${\lambda }_{\alpha }$, we can conclude that $\alpha \cdot
100\%$ of randomly chosen pairs of partitions have a proximity
measurement less than $\rho $. This means that these partitions
can neither be considered close nor similar. This paper identifies
the general case of distribution functions that describe
similarity measurements, with a special focus on uniform
distributions. The comparison results are presented in tables for
quantiles of probability distributions, using computer simulations
over our selected set of similarity metrics. Refs~9. Table~1.

{\it Keywords}: distance between partitions of a set,
probabilistic approach, comparing the distances.

\end{list}

}

\vskip2mm

\begin{list}{}{\leftmargin=7mm \rightmargin=7mm \listparindent=5mm}

\noindent{\it А.~А. Рогов$^1$, А.~Г. Варфоломеев$^1$, А.~О.
Тимонин$^1$, К.~А. Проенца$^2$}

\vskip1.8mm \noindent{\bf ВЕРОЯТНОСТНЫЙ ПОДХОД К~СРАВНЕНИЮ МЕР\\
БЛИЗОСТИ МЕЖДУ РАЗБИЕНИЯМИ МНОЖЕСТВА}

\vskip1.8mm


{\footnotesize



\noindent $^1$ Петрозаводский государственный университет,
Российская Федерация,

\noindent\hskip2.45mm 185910, Петрозаводск, проспект Ленина, 33



\noindent $^2$ Фидзаи (Feedzai), Португалия, 1990-083, Лиссабон,


\noindent\hskip2.45mm проспект Д. Жуана II, 1.16.01, 11





\vskip3.0mm


\item В~статье рассматривается  ряд классических метрик (индекс сходства
разбиений, предложенный Рандом; коэффициент Ларсена---Аоне и~др.)
между разбиениями одного множества. Унифицированы формулы для их
вычисления на~основании одинаковых параметров. Разработан
вероятностный подход к~сравнению приведенных мер близости
(сходства). Для этого требуется градуировка интервала возможных
значений мер близости между возможными разбиениями с~помощью
квантилей функции распределения. Пусть ${\lambda }_{\alpha }$ ---
квантиль уровня $\alpha $ для функции распределения $F_{\rho
}\left(t\right)=P\left(\rho <t\right)$. Тогда, если мера близости
$\rho $ оказывается не~меньше, чем ${\lambda }_{\alpha }$, можно
сделать вывод, что $\alpha \cdot 100\%$ случайно выбранных пар
разбиений имеют между собой меру близости меньше, чем $\rho $.
Следовательно, их нельзя считать близкими или похожими. Получен
общий вид функции распределения для приведенных мер близости.
Подробно изучен случай равномерного распределения элемента
разбиения в~любой группе. Для ряда мер близости приведены таблицы
квантилей функции распределения, которые были построены с~помощью
компьютерного моделирования. Библиогр. 9 назв. Табл. 1.

\textit{Ключевые слова}: меры близости между разбиениями множеств,
вероятностный подход, сравнение мер близости.


}

\end{list}


\vskip4mm

\textbf{Introduction.} The numerical comparison of disjoint set
partitions, which we call clusters, is a well studied subject in
the literature [1--5]. We consider three types of similarity
measurements between clusters, following Meil\u{a}~[1]:
%\begin{enumerate}



  1)~~by checking if a given object belongs or not to each known cluster~[2, 3];

  2)~~by comparing clusters regarded as sets~[4, 5];

  3)~~by calculating the delta produced from moving an object between two partitions~[1].
%\end{enumerate}

There is, however, no approach to precisely compare these
similarity measurements, since each of them has its own advantages
and disadvantages [6]. This paper takes a step forward in this
direction, comparing and relating different similarity
measurements.

\textbf{Similarity measurements of set partitions.} Assuming we
have a set with $n$ elements and two disjoin non-empty partitions
(clusters) of this set. Let's call $m_{jl}$ a frequency of
elements to belong to clusters with numbers $j$ and $l$ in the
first and second partitions. The paper [1] proposes to express all
measurements that compare such kind of subsets through these
frequencies $m_{jl}$. Let's call $m_{j*}$ and $m_{*l}$ as marginal
frequencies. Their values will be equal to the number of elements
in the clusters with numbers $j$ and $l$ mentioned above with
numbers $j$ and $l$. The following relations stay for the
frequencies introduced above:
\[\sum_{j,l}{m_{jl}=n}, \quad \sum_l{m_{jl}=m_{j*}}, \quad \sum_j{m_{jl}=m_{*l}}.\]

Calling matrix M a matrix consisting of the elements $m_{jl}$.
Then for two identical partitions in each row $j$ and in each
column $l$ of the matrix M will be only one non-zero element on
the main diagonal. When using additional values
\[T=\sum_{j,l}{m^2_{jl}}-n, \quad S=\sum_j{m^2_{j*}}-n, \quad Q=\sum_l{m^2_{*l}}-n\]
then, in these terms, a partition similarity index, proposed by
Rand [2], will be equal to
\begin{equation} \label{GrindEQ__1_}
R=1-\frac{S+Q-2T}{n(n-1)}
\end{equation}
and the proximity factor introduced in [3] appears as
\begin{equation*}
F=\frac{T}{\sqrt{SQ}}.
\end{equation*}

Let ${\mu }_i$ be some proximity measurement between two clusters
from different partitions that contain the $i$-th element of the
set. We call ${\rho }_k$ the mean of proximity measurements
between two partitions of a set splitter into $k$ non-empty
subsets, which is calculated by formula
\begin{equation} \label{GrindEQ__3_}
{\rho }_k=\frac{\sum^n_{i=1}{{\mu }_i}}{n}.
\end{equation}
The coefficient ${\rho }_k$ is calculated in the following way:
each pair of clusters $j$ and $l$ from the first and second
partitions is being compared as many times as the pair has common
elements.

Introducing the notation $\mu \left(j,l\right)$ for the proximity
coefficient between clusters $j$ and $l$ allow us to write the
proximity coefficient \eqref{GrindEQ__3_} as
\begin{equation*}
{\rho }_k=\frac{1}{n}\sum_{j,l}{m_{jl}\cdot \mu \left(j,l\right)}.
\end{equation*}

Any of the proximity coefficient can be used as a measurement $\mu
\left(j,l\right)$ between two sets [7], or, what is the same, two
(0,1) vectors [8]. For example:
\begin{equation*}
{\mu }^1\left(j,l\right)=\frac{m_{jl}}{m_{j*}+m_{*l}-m_{jl}},
\end{equation*}
\begin{equation} \label{GrindEQ__7_}
{\mu }^2\left(j,l\right)=\frac{m_{jl}}{{\mathrm{max}
\left(m_{j*}+m_{*l}\right)\ }},
\end{equation}
\begin{equation*}
{\mu }^3\left(j,l\right)=\frac{2m_{jl}}{m_{j*}+m_{*l}}.
\end{equation*}

Obviously, $\mu \left(j,l\right)$ takes values from 0 to 1. The
more matching elements are in sets, the closer these coefficients
are to 1. Look like:
\begin{equation} \label{GrindEQ__8_}
{\rho
}^1_k=\frac{1}{n}\sum_{j,l}{\frac{m^2_{jl}}{m_{j*}+m_{*l}-m_{jl}}}\
,
\end{equation}
\begin{equation} \label{GrindEQ__9_}
{\rho }^2_k=\frac{1}{n}\sum_{j,l}{\frac{m^2_{jl}}{{\mathrm{max}
\left(m_{j*}+m_{*l}\right)\ }}} ,
\end{equation}
\begin{equation} \label{GrindEQ__10_}
{\rho
}^2_k=\frac{1}{n}\sum_{j,l}{\frac{{2m}^2_{jl}}{m_{j*}+m_{*l}}}.
\end{equation}

The proposed similarity coefficient is the proximity measurement
of weighted sum between all clusters from the first and second
partitions. The corresponding intersection cardinalities are used
as weights. The coefficients from the papers [4, 5] are the most
similar to the proposed measurement. They are also calculated
using a pairwise comparison of clusters, but the summation is
unweighted and is not performed for all pairs of clusters. For
example, the Larsen---Aone coefficient [5] is
\begin{equation*} \label{GrindEQ__11_}
L=\sum_j{{\mathop{\mathrm{max}}_{l} {\mu }^3\left(j,l\right) }}.
\end{equation*}

\textbf{Proximity measurements comparison.} Regardless of which
proximity measu-\linebreak rements are used, the problem arises
when determining which measurements values can be considered large
(close to 1) and which ones should be considered small. The
solution to this problem will answer the question if the
difference between the partitions is significant or appeared to be
random. This article develops an approach relaying on a
probabilistic model for generating partitions and is based in the
previously described work from  [7, 9]. This approach allows us to
set a specific value --- threshold to determine ``big'' and
``small'' values of the similarity measurement. If the value of
the proximity measurements seldom appears to be the same or higher
then it is considered ``large''. The opposite is also true: if
values occur frequently, it is considered to be ``small''. The
paper proposes a method for constructing quantitative estimates
for the concepts ``rarely'' and ``often'' based on the probability
distribution of the proximity measurements values.

We perform a random experiment that generates a pair of
partitions. We also introduce a probability measurement for the
set of outcomes of the experiment. Like this we obtain a
probability distribution of the proximity measurements values.
This lets us to perform a calibration of the possible values range
using quantiles of the proximity measurements distribution
function. Let ${\lambda }_{\alpha }$ be a quantile with $\alpha $
level for distribution function $F_{\rho
}\left(t\right)=P\left(\rho <t\right)$. Then if the proximity
measurement $\rho $ is not less than ${\lambda }_{\alpha }$, we
can conclude that $\alpha \cdot 100\%$ of randomly chosen pairs of
partitions have a proximity measurement less than $\rho $. A
similar approach was considered in the paper [9] when comparing
distances between subsets, and in the paper [7] when comparing
dendrograms.

\textbf{The distance probability distribution in a general case.}
Let $U=\left\{u_1, \right.$ $\left. u_2,\dots ,u_n\right\}$ be a
set of $n$ elements. $X$ and $Y$ are the two of its partitions,
both consisting of $k$ groups. We represent the partitions $X$ and
$Y$ in the form of vectors $x$ and $y$ of dimension $n$. $X$ is
constructed according to the principle: $x_i=j$ if and only if
$u_i$ belongs to the $j$th group. $Y$ is being built in the same
way. We name $p^i_j,\ i=1,\dots ,n,\ j=1,\dots ,k$, the
probability of appearance of the element $u_i$ in the $j$-th
group. Then we can consider a random experiment that consists of
$n$ independent tests and in each test the element $u_i$ can
appear in any partition group. It appears that each test can have
$k^2$ species $A^{ijl}=\left\{x_i=j,y_i=l \right\}$, where $i$ is
the test number. Let $I\left(A\right)$ be the indicator of the
event $A$. Then $m_{jl}=\sum^n_{i=1}{I\left(A^{ijl}\right)}$,
$m_{j*}=\sum^k_{l=1}{\sum^n_{i=1}{I\left(A^{ijl}\right)}}$,
$m_{*l}=\sum^k_{j=1}{\sum^n_{i=1}{I\left(A^{ijl}\right)}}$.

We construct the set of events $B=\left(A^{111},A^{112},\dots
,A^{nkk}\right)$, taking into account the condition that empty
groups are not allowed. Each element can be exactly in one group
in each of the two partitions. Then for each $i\in 1,\dots ,n$ the
condition $\sum^k_{j=1}{\sum^k_{l=1}{I\left(A^{ijl}\right)}}=1$ is
right, and the condition
$\sum^n_{i=1}{\sum^k_{j=1}{\sum^k_{l=1}{I\left(A^{ijl}\right)}}}=n$
is true.

If $I\left(A^{irt}\right)=1$ is true, then for any $j\neq r,\
l\neq t$ appears $I\left(A^{ijl}\right)=0$. There are $(k-1)^2$ of
such pairs of $j$ and $l$, therefore $\forall i\in 1,\dots ,n:
\sum^k_{j=1}{\sum^k_{l=1}{\left(1-I\left(A^{ijl}\right)\right)=}(k-1)^2}$.

To guarantee the absence of empty groups, we introduce the
conditions $\forall
j:\sum^n_{i=1}{\sum^k_{l=1}{I\left(A^{ijl}\right)\ge 1}}$, \
$\forall l:\sum^n_{i=1}{\sum^k_{j=1}{I\left(A^{ijl}\right)\ge
1}}$. Thus, the set $B$ of outcomes follows the conditions:
\[B=\left\{ \begin{array}{c}
\left(A^{111},A^{112},\dots ,A^{nkk}\right) \\
\sum^k_{j=1}{\sum^k_{l=1}{I\left(A^{ijl}\right)}}=1 \\
\sum^k_{j=1}{\sum^k_{l=1}{\left(1-I\left(A^{ijl}\right)\right)=}(k-1)^2} \\
\forall j:\sum^n_{i=1}{\sum^k_{l=1}{I\left(A^{ijl}\right)\ge 1}},
\quad \forall l:\sum^n_{i=1}{\sum^k_{j=1}{I\left(A^{ijl}\right)\ge
1}}\ \  \end{array} \right\}.\]

As it was shown in the previous sections, different similarity
coefficients between two set partitions are described as functions
of $m_{jl}$, i.~e. $p\left(X,Y\right)=h\left(m_{jl}\right)$. To
calculate the distribution function of the random variable
$p\left(X,Y\right)$, we can use the formula for conditional
probabilities. We call $H$ the event that the partition does not
contain empty groups. Then

\[P\left(p\left(X,Y\right)<t\mathrel{\left|\vphantom{p\left(X,Y\right)<t H}\right.\kern-\nulldelimiterspace}H\right)=\frac{P\left(\left\{p\left(X,Y\right)<t\right\} \cdot H\right)}{P\left(H\right)},\]
\[P\left(\left\{p\left(X,Y\right)<t\right\} \cdot H\right)=\sum_{m_{jl}\in C}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in B}{\prod^k_{j=1}{\prod^k_{l=1}{\prod^n_{i=1}{{\left(p^i_jp^i_l\right)}^{I\left(A^{ijl}\right)}}}}}},\]
where $$C=\left\{m_{jl}\in Z:m_{jl}\ge 0,\ \
\sum^n_{i=1}{\sum^k_{j=1}{\sum^k_{l=1}{m_{jl}}}}=n,h\left(m_{jl}\right)<t\right\};$$
\[P\left(H\right)=\ P\left(\left\{p\left(X,Y\right)<\infty \right\} \cdot H\right).\]

Then the distribution function of the random variable
$p\left(X,Y\right)$ can be written in the following form:

\begin{equation} \label{GrindEQ__12_}
F\left(t\right)=P\left(\left\{p\left(X,Y\right)<t\right\} \cdot
H\right)=\frac{1}{P\left(H\right)}\sum_{m_{jl}\in
C}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in
B}{\prod^k_{j=1}{\prod^k_{l=1}{\prod^n_{i=1}{{\left(p^i_jp^i_l\right)}^{I\left(A^{ijl}\right)}}}}}}.
\end{equation}

Let us consider a special case.

\textbf{A special case. Uniform distribution.} Let's call
$p^i_j=\frac{1}{k}$. Then the formula~\eqref{GrindEQ__12_} takes
the form

\begin{equation*}
\begin{split}
F_p\left(t\right)=\frac{1}{P\left(H\right)}\sum_{m_{jl}\in
C}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in
B}{\prod^k_{j=1}{\prod^k_{l=1}{\prod^n_{i=1}{{\left(\frac{1}{k}\right)}^{2I\left(A^{ijl}\right)}}}}}}=
\\ =\frac{1}{P\left(H\right)}\sum_{m_{jl}\in
C}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in
B}{\prod^n_{i=1}{{\left(\frac{1}{k}\right)}^2=\frac{1}{P\left(H\right)}\sum_{m_{jl}\in
C}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in
B}{{\left(\frac{1}{k}\right)}^{2n}}}}}},
\end{split}
\end{equation*}

\[P\left(H\right)=\sum_{m_{jl}\in C_1}{\sum_{\left(A^{111},\dots ,A^{nkk}\right)\in B}{{\left(\frac{1}{k}\right)}^{2n}}} ,\]

\noindent where

\[C_1=\left\{m_{jl}\in Z:m_{jl}\ge 0,\ \ \sum^n_{i=1}{\sum^k_{j=1}{\sum^k_{l=1}{m_{jl}}}}=n\right\}.\]

We developed the program  to calculate the quantiles of the
proximity measurement distributions using the formulas
\eqref{GrindEQ__7_}--\eqref{GrindEQ__9_}. The calculation we done
using simulation modelling. The table presents the calculated
quantile values of some values $n$ and $k$ with different
$\alpha$. In a rectangle corresponding to the same values of $n$
and $k$, the measurements were calculated with formulas
\eqref{GrindEQ__1_}, \eqref{GrindEQ__8_}--\eqref{GrindEQ__10_}.
The upper left corner values were calculated using the formula
\eqref{GrindEQ__8_}; the upper right corner --- the formula
\eqref{GrindEQ__9_}; the lower-left corner --- formula
\eqref{GrindEQ__10_} and the lower right corner was computed using
the formula \eqref{GrindEQ__1_}. The number of experiments was 10
000.

\newpage


\vskip 2mm
\begin{center}
{\small

{\bf\emph{Table.} Proximity measurements quantities for different
$\alpha$}

}

\vskip 3mm

{\footnotesize


\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
$\alpha$ & $k${\textbackslash}$n$ & \multicolumn{2}{|c|}{5} &
\multicolumn{2}{|c|}{10} & \multicolumn{2}{|c|}{30} \\ \hline

\multirow{6}{*}{0.2} & \multirow{2}{*}{3} &  0.307 & 0.333 & 0.229
& 0.313 & 0.208 & 0.299  \\ \cline{3-8}
                     &                    & 0.467 & 0.400 & 0.370 & 0.422 & 0.343 & 0.508  \\ \cline{2-8}
                     & \multirow{2}{*}{5} &  0.0 & 0.0 & 0.252 & 0.298 & 0.146 & 0.215  \\ \cline{3-8}
                     &                    & 0.0 & 0.0 & 0.397 & 0.600 & 0.252 & 0.623  \\ \cline{2-8}
                     & \multirow{2}{*}{7} &  0.0 & 0.0 & 0.442 & 0.450 & 0.146 & 0.205  \\ \cline{3-8}
                     &                    &  0.0 & 0.0 & 0.582 & 0.778 & 0.250 & 0.703  \\ \hline

\multirow{6}{*}{0.1} & \multirow{2}{*}{3} &  0.307 & 0.333 & 0.229
& 0.313 & 0.209 & 0.300  \\ \cline{3-8}
                     &                    & 0.467 & 0.400 & 0.370 & 0.422 & 0.343 & 0.508  \\ \cline{2-8}
                     & \multirow{2}{*}{5} &  0.0 & 0.0 & 0.254 & 0.292 & 0.147 & 0.216  \\ \cline{3-8}
                     &                    & 0.0 & 0.0 & 0.402 & 0.600 & 0.253 & 0.621  \\ \cline{2-8}
                     & \multirow{2}{*}{7} &  0.0 & 0.0 & 0.442 & 0.450 & 0.146 & 0.206  \\ \cline{3-8}
                     &                    &  0.0 & 0.0 & 0.583 & 0.778 & 0.252 & 0.706  \\ \hline

\multirow{6}{*}{0.05} & \multirow{2}{*}{3} & 0.307 & 0.333 & 0.229
& 0.313 & 0.209 & 0.300  \\ \cline{3-8}
                     &                    & 0.467 & 0.400 & 0.370 & 0.422 & 0.344 & 0.508  \\ \cline{2-8}
                     & \multirow{2}{*}{5} &  0.0 & 0.0 & 0.257 & 0.292 & 0.148 & 0.216  \\ \cline{3-8}
                     &                    & 0.0 & 0.0 & 0.399 & 0.600 & 0.252 & 0.623  \\ \cline{2-8}
                     & \multirow{2}{*}{7} &  0.0 & 0.0 & 0.433 & 0.450 & 0.146 & 0.206  \\ \cline{3-8}
                     &                    &  0.0 & 0.0 & 0.582 & 0.778 & 0.252 & 0.706  \\ \hline
\end{tabular}


}
\end{center}



\textbf{Conclusions.} The introduced proximity measurements
estimation allows us to evaluate values obtained on different sets
and using different proximity measurements. For example, we assume
that the similarity measurements ${\rho }^1\left(X,Y\right)$ and
${\rho }^2\left(A,B\right)$ are statistically close with precision
$\varepsilon >0$ if the inequality $\left|F^1_{\rho }\left({\rho
}^1\left(X,Y\right)\right)-F^2_{\rho }\left({\rho
}^2\left(A,B\right)\right)\right|\le \varepsilon $ is true.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
%%%\input{02/lit-ra}

%%%%%N DOI в~ссылке!!!!!!!!!!

\input{02/ref-s}

%%%%%N DOI в~ссылке!!!!!!!!!!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\footnotesize




%\thispagestyle{empty}

\vskip 2mm

%\thispagestyle{empty}


\thispagestyle{empty} %очищаем стиль страницы
\thispagestyle{fancy} %включаем пользовательский стиль
\renewcommand{\headrulewidth}{0pt}%
\fancyhead[LO]{}%
\fancyhead[RE]{}%
\fancyfoot[LO]{\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~14.~Вып.~\issuenum}}
\hfill}%
\fancyfoot[RE]{\hfill\footnotesize{\rm{Вестник~СПбГУ.~Прикладная~математика.~Информатика...~\issueyear.~Т.~14.~Вып.~\issuenum}}}%
%\lhead{} %верхний колонтитул слева
%%\rhead{} % верхний колонтитул справа
% для оформления нижнего колонтитула
\cfoot{} %
%\lfoot{} %
%\rfoot{\thepage} %


\noindent Статья рекомендована к~печати проф. А.~П. Жабко.

\vskip 1mm

\noindent Статья поступила в~редакцию 7 октября 2017~г.

\vskip 1mm

\noindent Статья принята к~печати 11 января 2018~г.

}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vskip 5mm


%{\footnotesize

%\noindent К\,о\,н\,т\,а\,к\,т\,н\,а\,я\,
%и\,н\,ф\,о\,р\,м\,а\,ц\,и\,я \nopagebreak

%\vskip 3mm

%\textit{Буре Артем Владимирович}~--- аспирант; e-mail:
%bure.artem@gmail.com

%\vskip 2mm

%\emph{Bure Artem Vladimirovich}~--- post-graduate student; e-mail:
%bure.artem@gmail.com

%}
