

{\footnotesize

\vskip 2mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 1.5mm

1. Meil\u{a} M. Comparing clusterings by the variation of
information. {\it Learning Theory and Kernel Machines. Lecture
Notes in Computer Science} (Springer), 2003, vol.~2777,
pp.~173--187.

2. Rand W. M. Objective criteria for the evaluation of clustering
methods. {\it Journal of the American Statistical Association},
1971, vol.~66, pp.~846--850.

3. Fowlkes E. B., Mallows C. L. A Method for comparing two
Hierarchical Clusterings. {\it Journal of the American Statistical
Association}, 1983, vol.~78, pp.~553--569.

4. Meil\u{a} M., Heckerman D. An experimental comparison of
model-based clustering methods. {\it Machine Learning}, 2001,
vol.~42, pp.~9--29.

5. Larsen B., Aone C. Fast and effective text mining using linear
time Document Clustering. {\it Proceedings of the Conference on
Knowledge Discovery and Data Mining}, 1999, pp.~16--22.

6. Steel M. A., Penny D. Distributions of tree comparison metrics
--- Some new results. {\it Systematic Biology}, 1993, vol.~42,
pp.~126--141.

7. Sidorov~Y.~V., Kirikov~P.~V., Rogov~A.~A. Sravnenie dendrogramm
s ravnyim chislom vershin [Dendrograms comparison with an equal
vertices number].  {\it Scientific notes of Petrozavodsk State
University. Series Natural and Technical Sciences.} Petrozavodsk,
Petrozavodsk State University Publ., 2011, no.~8, pp.~108--110.
(In Russian)

8. Warrens M. J. On Robinsonian dissimilarities, the consecutive
ones property and latent variable models. {\it Advances in Data
Analysis and Classification}, 2009, vol.~3, pp.~169--184.

9. Varfolomeyev~A.~A., Kirikov~P.~V., Rogov~A.~A. Veroyatnostnyiy
podhod k sravneniyu rasstoyaniy mezhdu podmnozhestvami konechnogo
mnozhestva [Probabilistic approach to distances comparison between
subsets of a finite set]. {\it Scientific notes of Petrozavodsk
State University.} Petrozavodsk, Petrozavodsk State University
Publ., 2010, no.~8, pp.~83--88. (In Russian)



\vskip 1.2mm

{\bf For citation:}  Rogov A.~A.,~Varfolomeyev~A.~G.,
Timonin~A.~O.,~Proen\c{c}a~K.~A. A probabilistic approach to
comparing the distances between partitions of a set. {\it Vestnik
of Saint Petersburg University. Applied Mathematics. Computer
Science. Control Processes}, \issueyear, vol.~14, iss.~\issuenum,
pp.~\pageref{p2}--\pageref{p2e}. \doivyp/
spbu10.\issueyear.\issuenum02



}
