
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm


1.   \textit{Красовский~Н.~Н.} Некоторые задачи теории
устойчивости движения. М.: Физматгиз, 1959. 211 с.

2. \textit{Repin~Iu.~M.} Quadratic Liapunov functionals for
systems with delay~// Journal of Applied Mathematics and
Mechanics. 1965. Vol.~29, N~3. P.~669--672.

3. \textit{Infante~E.~F., Castelan~W.~B.} A Liapunov functional
for a matrix difference-differential equation~// Journal of
Differential Equations. 1978. Vol.~29, N~3. P.~439--451.

4. \textit{Huang~W.} Generalization of Liapunov’s theorem in a
linear delay system~// Journal of Mathematical Analysis and
Applications. 1989. Vol.~142, N~1. P.~83--94.

5. \textit{Kharitonov~V.~L., Zhabko~A.~P.} Lyapunov---Krasovskii
approach to the robust stability analysis of time-delay systems~//
Automatica. 2003. Vol.~39, N~1. P.~15--20.

6. \textit{Kharitonov~V.~L.} On the uniqueness of Lyapunov
matrices for a time-delay system~// Systems \& Control Letters.
2012. Vol.~61, N~3. P.~397--402.

7. \textit{Kharitonov~V.~L.} Time-delay systems: Lyapunov
functionals and matrices. Basel: Birkh{\"a}user, 2013. 311 p.

8. \textit{Kharitonov~V.~L., Plischke~E.} Lyapunov matrices for
time-delay systems~// Systems \& Control Letters. 2006. Vol.~55,
N~9. P.~697--706.

9. \textit{Garcia-Lozano~H., Kharitonov~V.~L.} Lyapunov matrices
for time delay systems with commensurate delays~// 2nd IFAC
Symposium on System, Structure and Control / ed. S.~Mondi{\'e}.
Oaxaca, Mexico: IFAC, 2004. Vol.~1. P.~102--106.

10. \textit{Алисейко~А.~Н.} Матрицы Ляпунова для класса уравнений
с распределенным запаздыва\-нием~// Процессы управления
и~устойчивость. 2016. Т.~3(19), №~1. С.~68--74.

11. \textit{Kharitonov~V.~L.} Lyapunov matrices for a class of
time delay systems~// Systems \& Control Letters. 2006. Vol.~55,
N~7. P.~610--617.

12. \textit{Bellman~R., Cooke~K.~L.} Differential-difference
equations. New York: Academic Press, 1963. 482~p.

\vskip 2mm

{\bf Для цитирования:}  {\it Алисейко А.~Н.} Матрицы Ляпунова для
класса систем с~экспоненциальным ядром~// Вестник
Санкт-Петербургского университета. Прикладная математика.
Информатика. Процессы управления. \issueyear. Т.~13.
Вып.~\issuenum. С.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01




}
