{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm


1. Krasovskii~N.~N. \textit{Nekotorye zadachi teorii ustojchivosti
dvizheniya} [\textit{Some problems of the stability of motion}].
Moscow, Fizmatgiz Publ., 1959, 211 p. (In Russian)

2. Repin~Iu.~M. Quadratic Liapunov functionals for systems with
delay. \textit{Journal of Applied Mathematics and Mechanics},
1965, vol.~29, no.~3, pp.~669--672.

3. Infante~E.~F., Castelan~W.~B. A Liapunov functional for a
matrix difference-differential equation. \textit{Journal of
Differential Equations}, 1978, vol.~29, no.~3, pp.~439--451.

4. Huang~W. Generalization of Liapunov’s theorem in a linear delay
system. \textit{Journal of Mathematical Analysis and
Applications}, 1989, vol.~142, no.~1, pp.~83--94.

5. Kharitonov~V.~L., Zhabko~A.~P. Lyapunov---Krasovskii approach
to the robust stability analysis of time-delay systems.
\textit{Automatica}, 2003, vol.~39, no.~1, pp.~15--20.

6. Kharitonov~V.~L. On the uniqueness of Lyapunov matrices for a
time-delay system. \textit{Systems {\normalfont\&} Control
Letters}, 2012, vol.~61, no.~3, pp.~397--402.

7. Kharitonov~V.~L. \textit{Time-delay systems: Lyapunov
functionals and matrices}. Basel, Birkh{\"a}user Publ., 2013,
311~p.

8. Kharitonov~V.~L., Plischke~E. Lyapunov matrices for time-delay
systems. \textit{Systems {\normalfont\&} Control Letters}, 2006,
vol.~55, no.~9, pp.~697--706.

9. Garcia-Lozano~H., Kharitonov~V.~L. Lyapunov matrices for time
delay systems with commensurate delays. \textit{2nd IFAC Symposium
on System, Structure and Control}. Ed. by S.~Mondi{\'e}. Oaxaca,
Mexico, IFAC, 2004, vol.~1, pp.~102--106.

10. Aliseyko~A.~N. Matritsy Lyapunova dlya klassa uravnenij s
raspredelyonnym zapazdyvaniem [Lyapunov matrices for a class of
equations with distributed delay]. \textit{Processy upravleniya i
ustojchivost’} [\textit{Control Processes and Stability}], 2016,
vol.~3(19), no.~1, pp.~68--74. (In Russian)

11. Kharitonov~V.~L. Lyapunov matrices for a class of time delay
systems. \textit{Systems {\normalfont\&} Control Letters}, 2006,
vol.~55, no.~7, pp.~610--617.

12. Bellman~R., Cooke~K.~L. \textit{Differential-difference
equations}. New York, Academic Press, 1963, 482~p.



\vskip 2mm

{\bf For citation:}  Aliseyko A.~N.  Lyapunov matrices for a class
of systems with exponential kernel. {\it Vestnik of Saint
Petersburg University. Applied Mathematics. Computer Science.
Control Processes}, \issueyear, vol.~13, iss.~\issuenum,
pp.~\pageref{p1}--\pageref{p1e}.
\doivyp/spbu10.\issueyear.\issuenum01


}
