
{\footnotesize


\vskip3mm \noindent {\small \textbf{Литература} }

\vskip2mm



1. \textit{Berlekamp E., Welch L.} Error correction of algebraic
block codes. Patent USA 4633470. 1986.

2. \textit{Beckermann B., Labahn G.} Fraction-free computation of
matrix rational interpolants and matrix GCD's~// SIAM J. Matrix
anal. appl. 2000. Vol.~22, N~1. P.~114--144.

3. \textit{Berrut J.-P., Baltensperger R., Mittelmann H.~D.}
Recent developments in barycentric rational interpolation~//
Intern. Series of numerical mathematics. Basel: Birkh\"auser,
2005. Vol.~151. P.~27--51.

4. \textit{von zur Gathen J., Gerhard J.} Modern computer algebra.
2nd ed. Cambridge: Cambridge University Press, 2003. 785~p.

5. \textit{Jacobi C.~G.~J.} \"Uber die Darstellung einer Reihe
gegebner Werthe durch eine gebrochne rationale Function~//
J.~reine angew. Math. 1846. Vol.~30. P.~127--156.

6. \textit{Jacobi C.~G.~J.} De eliminatione variabilis e duabus
aequationibus algebraicis~// J.~reine angew. Math. 1836. Vol.~15.
P.~101--124.

7. \textit{Joachimsthal F.} Bemerkungen \"uber den Sturm'schen
Satz~// J.~reine angew. Math. 1854. Vol.~48. P.~386--416.

8. \textit{Uteshev A.~Yu., Baravy I.} Solution of interpolation
problems via the Hankel polynomial construction. arXiv:
cs.SC/1603.08752. 2016. 56~p.

9. \textit{Henrici P.} Applied and computational complex analysis.
Vol.~1. Power series, integration, conformal mapping, location of
zeros. New York; London: Wiley and Sons, Inc., 1974. 700~p.

10. \textit{Фаддеев Д. К.} Лекции по~алгебре. М.: Наука, 1984.
416~с.

11. \textit{Блейхут Р. E.} Быстрые алгоритмы цифровой обработки
сигналов. / пер. с~англ. И.~И.~Грушко.  М.: Мир, 1989. 448~с.
(\textit{Blahut R. E.} Fast algorithms for signal processing.)

12. \textit{Иохвидов И. С.} Ганкелевы и~теплицевы матрицы и~формы.
М.: Наука, 1974. 263~с. (\textit{Iohvidov~I.~S.} Hankel and
Toeplitz matrices and forms: Algebraic theory.)



\vskip 2mm

{\bf Для цитирования:} Утешев А.\,Ю., Боровой И.\,И. Решение
задачи рациональной интерполяции с~использованием ганкелевых
полиномов // Вестник Санкт-Петербургского университета. Сер.~10.
Прикладная математика. Информатика. Процессы управления.
\issueyear. Вып.~\issuenum. С.~\pageref{p3}--\pageref{p3e}.
\doivyp/ spbu10.\issueyear.\issuenum03




}
