

{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2mm

1. Berlekamp E., Welch L. \textit{Error correction of algebraic
block codes.} Patent US~4633470, 1986.

2. Beckermann B., Labahn G. Fraction-free computation of matrix
rational interpolants and matrix GCD's. \textit{SIAM J. Matrix
Anal. Appl.} 2000, vol.~22, no.~1, pp.~114--144.

3. Berrut J.-P., Baltensperger R., Mittelmann H.~D. Recent
developments in barycentric rational interpolation.
\textit{Intern. Series of numerical mathematics.} Basel,
Birkh\"auser Press, 2005, vol.~151,\linebreak pp.~27--51.

4. von zur Gathen J., Gerhard J. \textit{Modern Computer Algebra.}
2nd ed. Cambridge, Cambridge University Press, 2013, 785~p.

5. Jacobi C.~G.~J. \"Uber die Darstellung einer Reihe gegebner
Werthe durch eine gebrochne rationale Function [On the
representation of the set of given values via the rational
function]. \textit{J.~reine angew. Math.} [{\it Journal of Pure
and Applied Mathematics}], 1846, vol.~30, pp.~127--156.

6. Jacobi C.~G.~J. De eliminatione variabilis e duabus
aequationibus algebraicis [On the elimination of variable from two
algebraic equations]. \textit{J.~reine angew. Math.} [{\it Journal
of Pure and Applied Mathematics}], 1836, vol.~15, pp.~101--124.

7. Joachimsthal F. Bemerkungen \"uber den Sturm'schen Satz [A note
of Sturm's theorem]. \textit{J.~reine angew. Math.}  [{\it Journal
of Pure and Applied Mathematics}], 1854, vol.~48, pp.~386--416.

8. Uteshev A.~Yu., Baravy I. Solution of interpolation problems
via the Hankel polynomial construction. \emph{arXiv:
cs.SC/1603.08752}, 2016, 56~p.

9. Henrici P. \textit{Applied and computational complex analysis.
Vol.~1. Power series, integration, conformal mapping, location of
zeros}. New York, London, Wiley and Sons Inc. Publ., 1974, 700~p.

10. Faddeev D.~K. \emph{Lekcii po~algebre} [\emph{Lectures in
Algebra}]. Moscow, Nauka Publ., 1984, 416~p. (In Russian).

11. Blahut R.~E. \textit{Fast algorithms for digital signal
processing.} New York, Cambridge University Press, 1985, 485~p.
(Russ. ed.: Blahut~R. \emph{Bystrye algoritmy cifrovoj obrabotki
signalov}. Moscow, Mir Publ., 1989, 448~p.)

12. Iohvidov I.~S. \emph{Hankel and Toeplitz matrices and forms:
algebraic theory}. Boston, Birkh\"auser Press, 1972, 260~p. (Russ.
ed.: Iohvidov~I.\,S. \emph{Gankelevy i~teplicevy matricy i~formy}.
Moscow, Nauka Publ., 1974, 263~p.)



\vskip 2mm

{\bf For citation:} Uteshev A.\,Yu., Baravy I.\,I. Solution of
rational interpolation problem  via the Hankel polynomial
construction. {\it Vestnik of Saint Petersburg University.
Series~10. Applied mathematics. Computer science. Control
processes}, \issueyear, issue~\issuenum,
pp.~\pageref{p3}--\pageref{p3e}.\doivyp/
spbu10.\issueyear.\issuenum03



}
