
{\normalsize

\vskip 4.5mm%6mm

\noindent{\bf The stability of differential-dif\-fe\-ren\-ce
equations with proportional time delay. I. Linear controlled
system %$^{*}$
}

}

\vskip 2mm

{\small

\noindent{\it A.~V.~Ekimov, A.~P.~Zhabko, P.~V.~Yakovlev %$\,^1$%
%, I.~Î. Famylia%$\,^2$%

 }

\vskip 2mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\efootnote{
%%
%\vspace{-3mm}\parindent=7mm
%%
%\vskip 0.1mm $^{*}$ This work is supported by Russian Science
%Foundation (project N~18-71-00006 ).\par
%%
%%\vskip 2.0mm
%%
%%\indent{\copyright} Ñàíêò-Ïåòåðáóðãñêèé ãîñóäàðñòâåííûé
%%óíèâåðñèòåò, \issueyear%
%%
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\footnotesize


\noindent%
%$^1$~%
St.\,Petersburg State University, 7--9, Universitetskaya nab., St.\,Petersburg,

\noindent%
%\hskip2.45mm%
199034, Russian Federation

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip1.8mm%3mm


\noindent \textbf{For citation:}  Ekimov~A.~V., Zhabko~A.~P.,
Yakovlev~P.~V. The stability of
dif\-fe\-ren\-tial-dif\-fe\-ren\-ce equations with proportional
time delay. I. Linear controlled system. {\it Vest\-nik of Saint
Pe-\linebreak tersburg University. Applied Mathe\-ma\-tics.
Computer
Science. Control Pro\-cesses}, %\,
\issueyear,
vol.~16, iss.~\issuenum,~pp.~\pageref{p8}--\pageref{p8e}. %\\
\doivyp/\enskip%
\!\!\!spbu10.\issueyear.\issuenum08  (In Russian)

\vskip3mm

{\leftskip=7mm\noindent The article considers a controlled system
of linear differential-difference equations with a linearly
increasing delay. Sufficient conditions for the asymptotic
stability of such systems are known; however, general conditions
for the stabilizability of controlled systems and constructive
algorithms for constructing stabilizing controls have not yet been
obtained. For a linear differential-difference equation of delayed
type with linearly increasing delay, the canonical Zubov
transformation is applied and conditions for the stabilization of
such systems by static control are derived. An algorithm for
checking the conditions for the existence of a stabilizing control
and for its constructing is formulated. New theorems on stability
analysis of systems of linear differential-difference equations
with linearly increasing delay are proven. The results obtained
can be applied to the case of systems with several proportional
delays.
\\[1mm]
\textit{Keywords}: system of linear differential-difference
equations, linearly increasing time delay, asymptotic stability,
stabilizing control, asymptotic evaluation system.\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. {\textnormal  Bellman~R., Cooke~K.~L.} {\itshape
Differential-difference equations.} London, United Kingdom,
Academic Press, 1963, 461~p. (Russ. ed.: Bellman R., Cooke K. L.
{\it Differencial’no-raznostnye uravnenija}. Moscow, Mir~Publ.,
1967, 548~p.)

2. {\textnormal Zhabko~A.~P., Chizhova~O.~N.} Analiz ustojchivosti
odnorodnogo differencial’no-raznostnogo uravnenija s linejnym
zapazdyvaniem [Stability analysis of homogeneous
differential-difference equation with linear delay]. {\itshape
Vestnik of Saint Petersburg University.} {\itshape Applied
Mathematics. Computer Sciences. Cont\-rol Processes}, 2015,
iss.~3, pp.~105--115. (In Russian)

3. {\textnormal Ekimov~A.~V., Chizhova~O.~N., Zaranik~U.~P.}
Ustoichivost odnorodnykh nestatsionarnykh system
differentsial'no-raznostnykh uravnenij s linejno vozrastajushim
zapazdyvaniem [Stability of homogeneous nonstationary systems of
differential-difference equations with linearly time delay].
{\itshape Vestnik of Saint Petersburg University.} {\itshape
Applied Mathematics. Computer Sciences. Control Processes}, 2019,
vol.~15, iss.~4, pp.~415--424. (In Russian)

4. {\textnormal Laktionov~A.~A., Zhabko~A.~P.} Method of
differential transformations for differential systems with linear
time-delay. {\itshape Proceedings of the First IFAC Conference
LTDS--98}. France, 1998, pp.~201--205.

5. {\textnormal Grebenshhikov~B.~G.} Metody issledovanija
ustojchivosti sistem s linejnym zapazdyvaniem [Methods for
investigating the stability of systems with linear delay].
{\itshape Siberian Mathe\-ma\-ti\-cal Journal}, 2001, vol.~42,
no.~1, pp.~41--51. (In Russian)

6. {\textnormal Grebenshhikov~B.~G., Lozhnikov~A.~B.} O
stabilizacii odnoj sistemy s posledejstviem [On stabilization of
one system with aftereffect]. {\itshape Automation and Remote
Control}, 2011, no.~1, pp.~13--26. (In Russian)

7. {\textnormal Zhabko~A.~P., Chizhova~O.~N.} On stabilization of
systems of linear equations with linear increasing time-delay by
observations. {\itshape Proceedings of RuPAC2016}. St.~Petersburg,
Russia, 2016, pp.~261--263.

8. {\textnormal Zhabko~A.~P., Tikhomirov~O.~G., Chizhova~O.~N.} O
stabilizatsii klassa system s proportsionalnym zapazdyvaniem [On
stabilization of a class of systems with time proportional delay].
{\itshape Vestnik of Saint Petersburg University.} {\itshape
Applied Mathematics. Computer Sciences. Control Processes}, 2018,
vol.~14, iss.~2, pp.~165--172. (In Russian)

9. {\textnormal Zubov~V.~I.} {\itshape Lektsii po teorii
upravleniya} [{\itshape Lectures on control theory}]. Moscow,
Nauka~Publ., 1975, 496~p. (In Russian)

10. {\textnormal Zhabko~A., Chizhova~O., Zaranik~U.} Stability
analysis of the linear time delay systems with linearly increasing
delay. {\itshape Cybernetics and Physics}, 2016, vol.~5, no.~2,
pp.~67--72.


\vskip1.5mm Received:  May 24, 2020.

Accepted: August 13, 2020.

\vskip6mm A\,u\,t\,h\,o\,r'\,s \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:%

\vskip2mm \textit{Alexander V. Ekimov} --- PhD in Physics and
Mathematics, Associate Professor; a.ekimov@spbu.ru

\vskip2mm \textit{Aleksei P.~Zhabko}  --- Dr. Sci. in Physics and
Mathematics, Professor; zhabko.apmath.spbu@mail.ru

\vskip2mm \textit{Pavel V. Yakovlev} --- PhD in Physics and
Mathematics; w330433@gmail.com


}
