

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2 mm

{\footnotesize



1.{ Nassiri M., Elahi T. M., Ghovvati S. }
Evaluation of different statistical methods using SAS software: an in silico approach for analysis of real-time PCR. {\it Journal of Applied Statistics}, 2018, vol.~45, iss.~2, pp.~306--319.

2. {Bure V. M., Petrushin A. F., Mitrofanov E. P., Mitrofanova O. A., Denisov V.}
Experience with the use of mathematical statistics methods for assessment of agricultural plants status. {\it Sel'sko\-kho\-zyaist\-vennaya Biologiya} [{\it Agricultural Biology}], 2019, vol.~54, iss.~1, pp.~84--90. \\ https://doi.org/10.15389/agrobiology.2019.1.84eng

3. {Iakushev V. P., Bure V. M., Mitrofanova O. A., Mitrofanov E. P.}
 Theoretical foundations of probabilistic and statistical forecasting of agrometeorological risks. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2021, vol.~17, iss.~2, pp.~174--182. https://doi.org/10.21638/11701/spbu10.2021.207

4. {Iakushev V. P., Bure V. M., Mitrofanova O. A., Mitrofanov E. P.}
 On the issue of se\-mi\-variograms constructing automation for precision agriculture problems. {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes}, 2020, vol.~16, iss.~2, pp.~177--185. \\
 https://doi.org/10.21638/11701/spbu10.2020.209


5. {Ghani I. M., Ahmad S.} Stepwise multiple regression method to forecast fish landing. {\it Procedia-Social and Behavioral Sciences}, 2010, vol.~8, pp.~549--554.

6. {Bure V. M., Parilina E. M., Sedakov A. A.}
Metody prikladnoi statistiki v R i Excel. 3-izd. [Applied statistics methods in R and Excel]. 3rd ed. St Petersburg, Lan’ Publ.,  2019, 196~p. (In Russian)


7. {Qi D.}  Study of the investment attractiveness of China's regions. {\it Management Processes and Sustainability}, 2020, vol.~7, iss.~1, pp.~423--427.


8. {Karim S. A., Kamsani N. F.} Water quality index prediction using multiple linear fuzzy regression model: Case study in Perak River, Malaysia. {\it Springer Nature}, 2020, pp.~31--35.



9. {Adrain R.} Research concerning the probabilities of the errors which happen in making observations. {\it  George Long}, 1814, vol.~1, no.~4, pp.~93--107.


10. {Merriman M.} On the history of the method of least squares. {\it The Analyst}, 1877, vol.~4, iss.~2, pp.~33--36.

11.  {Zyskind G., Martin F. B.}
On best linear estimation and general Gauss\,---\,Markov theorem in linear models with arbitrary nonnegative covariance structure. {\it SIAM Journal on Applied Mathematics}, 1969, vol.~17(6), pp.~1190--1202.

12. {Quandt R. E.}
Tests of the hypothesis that a linear regression system obeys two separate regimes. {\it Journal of the American Statistical Association}, 1960, vol.~55, iss.~290, pp.~324--330.

13. {Pope P. T., Webster J. T.} The use of an $F$-statistic in stepwise regression procedures. {\it Technometrics}, 1972, vol.~14, iss.~2, pp.~327--340.

14. {Bure V. M., Parilina E. M.} {\it Teoriia veroiatnosti i matematicheskaia statistika $[$Probability theory and mathematical statistics$]$}. 1$^{\rm st}$ ed., St Petersburg, Lan’ Publ., 2013, 416~p. (In Russian)

15. {Royston P.} Approximating the Shapiro\,---\,Wilk test for non-normality. {\it Statistics and Computing}, 1992, vol.~2, iss.~3, pp.~117--119.

16. {Wilford L. L., Taylor D.} The power of four tests of autocorrelation in the linear regression model. {\it  Journal of Econometrics}, 1975, vol.~3, iss.~1, pp.~1--21.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  March 19, 2022.

Accepted: September 01, 2022.

\vskip 6mm

%\pagebreak

A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm
 \textit{Yang He}  --- Postgraduate Student; hy1186867324@outlook.com \par

\vskip 2mm
 \textit{Dongfang Qi}  --- Postgraduate Student; st073409@student.spbu.ru \par


\vskip 2mm
 \textit{Vladimir M. Bure}  --- Dr. Sci. in Engineering, Professor; vlb310154@gmail.com
 \par
%
%
}
