
{\footnotesize


\vskip4mm \noindent {\small \textbf{Литература} }

\vskip3mm


1. {\it Brucker P.}  Scheduling algorithms. Heidelberg: Springer,
2007. 378~p.

2. {\it Graham R. L., Lawner E. L., Kan R.} Optimization and
approximation in deterministic sequencing and scheduling: A survey
//  Ann. of Disc. Math. 1979. Vol.~5, N~10. P.~287--326.




3. {\it Lenstra J. A., Kan R., Brucker P.} Complexity of machine
scheduling problems // Ann. of Disc. Math. 1977. Vol.~1.
P.~343--362.

4. {\it Brucker P, Garey M. R., Johnson D. S.} Scheduling
equal-length tasks under tree-like precendence constraints to
minimize maximum lateness // Matematics of Operations Research.
1977. N~2. P.~275--284.

5. {\it Zinder Y., Singh G.} Preemptive scheduling on parallel
processors with due dates // Asia Pacific Journal of Operational
Research. 2005. N~22. P.~445--462.


6. {\it Baker K. R. }Introduction to Sequencing and Scheduling.
New York: John Wiley \& Son,  1974. 318~p.

7. {\it Kanet J. J., Sridharan V.} Scheduling with inserted idle
time: problem taxonomy and literature review // Operations
Research. 2000. Vol.~48, N~1. P.~99--100.


8. {\it Carlier J.} The one-machine sequencing problem // European
J. Oper. Res. 1982. N~11. P.~42--47.

9. {\it Григорьева Н. С.} Алгоритм ветвей и~границ для задачи
составления расписаний на~параллельных процессорах // Вестн.
С.-Петерб. ун-та. Сер.~10. Прикладная~математика. Информатика.
Процессы управления. 2009. Вып.~1. С.~44--55.


10. {\it Grigoreva N. S. } Multiprocessor scheduling with inserted
idle time to minimize the maximum lateness // Proceedings of the
7th Multidisciplinary Intern. Conference of Scheduling: Theory and
Applications. Prague: MISTA, 2015. P.~814--816.

11. {\it Gusfield D.} Bounds for naive multiple machine scheduling
with release times and deadlines // Journal of Algorithms. 1984.
Vol.~5. P.~1--6.


12. {\it Романовский И. В., Христова Н. П.} Решение минимаксных
задач методом дихотомии // Журн. вычисл. математики и матем.
физики. 1973. Т.~13, №~5. С.~200--209.

13. {\it Mastrolilli M.} Efficient approximation schemes for
scheduling problems with release dates and delivery times
// Journal of Scheduling. 2003. Vol.~6. P.~521--531.


14. {\it Fernandez E., Bussell B.} Bounds the number of processors
and time for multiprocessor optimal schedules // IEEE Trans. on
Computers. 1973. Vol.~4, N~11. P.~745--751.



\vskip 2mm

{\bf Для цитирования:} Григорьева Н.~С. Задача минимизации
максимального временного смещения для параллельных процессоров
// Вестник Санкт-Петербургского университета. Сер.~10. Прикладная
математика. Информатика. Процессы управления. \issueyear.
Вып.~\issuenum. С.~\pageref{p5}--\pageref{p5e}. \doivyp/
spbu10.\issueyear.\issuenum05



}
