

{\small



\vskip6mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize



1. Asaro R.\,J., Tiller W.\,A. 
Interface morphology development during stress-corrosion cracking. Pt~I. Via surface diffusion. 
{\it Metallurgical and Materials Transactions}, 1972,  vol.~3, pp.~1789--1796.

2. Grinfeld M.\,A. 
The stress driven instabilities in elastic crystals: mathematical models and physical manifestation.  {\it Journal of Nonlinear Science}, 1993, vol.~3, no.~1, pp.~35--83.

3. Colin J., Grilhe J., Junqua N. 
Morphological instabilities of a stressed pore channel. 
{\it Acta Materialia}, 1997, vol.~45, pp.~3835--3841.

4. Kim J.\,H., Vlassak J.\,J. 
Perturbation analysis of an undulating free surface in a multilayered structure. 
{\it International Journal of Solids and Structures},   2007, vol.~44, pp.~7924--7937.

5. Shuvalov G., Kostyrko S.
Surface self-organization in multilayer film coatings. 
{\it AIP Conference Proceedings}, 2017, vol.~1909, pp.~020196.

6. Gurtin M.\,E., Murdoch A.\,I. 
A continuum theory of elastic material surfaces. 
{\it Archive for Rational Mechanics and Analysis},  1975,  vol.~57, pp.~291--323.

7. Gurtin M.\,E., Murdoch A.\,I. 
Surface stress in solids. 
{\it International Journal of Solids and Structures},  1978, vol.~14, pp.~431--440.

8. Grekov M.\,A., Kostyrko S.\,A. 
Surface effects in an elastic solid with nanosized surface asperities. 
{\it International Journal of Solids and Structures}, 2016, vol.~96, pp.~153--161.

9. Klinger L., Levin L., Srolovitz D. 
Morphological stability of a heterophase interface under electromigration conditions. 
{\it Journal of Applied Physics},  1996, vol.~79, pp.~6834--6839.

10. Freund L.\,B. 
Evolution of waviness on the surface of a strained elastic solid due to stress-driven diffusion. 
{\it International Journal of Solids and Structures}, 1995,  vol.~28, pp.~911--923.

11. Pronina Y. 
An analytical solution for the mechanochemical growth of an elliptical hole in an elastic plane under a uniform remote load. 
{\it European Journal of Mechanics, A/Solids},  2017, vol.~61, pp.~357--363.

12. Pronina Y., Sedova O., Grekov M., Sergeeva T. 
On corrosion of a thin-walled spherical vessel under pressure. 
{\it International Journal of Engineering Science},  2018, vol.~130, pp.~115--128.

13. Goldstein R.\,V., Makhviladze T.\,M., Sarychev M.\,E. 
Instability of the interface between joint conducting materials under electrical current. 
{\it Materials Letters}, 2016, vol.~6, pp.~98--101.

14. Kostyrko S.\,A., Grekov M.\,A. 
Elastic field at a rugous interface of a bimaterial with surface effects. 
{\it Engineering Fracture Mechanics},  2019, vol.~216, pp.~106507.

15. Kostyrko S., Shuvalov G. 
Surface elasticity effect on diffusional growth of surface defects in strained solids. 
{\it Continuum Mechanics and Thermodynamics},   2019, vol.~31, pp.~1795--1803.


\vskip 1.5mm

%\noindent Recommendation: prof. L. A. Petrosyan.
%
%\vskip 1.5mm

%\noindent

Received:  November 11, 2020.

Accepted: January 15, 2021.

\vskip 4.5mm%6mm
A\,u\,t\,h\,o\,r\,s' \ i\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:

\vskip 2mm \textit{Gleb M. Shuvalov} ---  Postgraduate Student, Assistant; g.shuvalov@spbu.ru 

\vskip 2mm \textit{Sergey A. Kostyrko} --- PhD in Physics and Mathematics, Associate Professor; s.kostyrko@spbu.ru 


}
