{\footnotesize

\vskip 3mm
%\newpage

\noindent{\small \textbf{References} }

\vskip 2.5mm
%%%%%%%%%%%в транслит





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

1. {John F.} Plane strain problems for a perfectly elastic
material of harmonic type. {\it Commun. Pure and Appl. Math.},
1960, vol.~13. no.~2, pp.~239--296.

2. {Varley E., Cumberbatch E}. Finite deformation of elastic
materials surrounding cylindrical holes. {\it Journal of
Elasticity}, 1980, vol.~10, no.~4, pp.~341--405.

3. {Ru C.\,Q}. On complex-variable formulation for finite plane
elastostatics of harmonic materials. {\it Acta Mechanica}, 2002,
vol.~156, no.~3--4, pp.~219--234.

4. {Malkov V.\,M., Malkova Yu.\,V.} Ploskaya zadacha nelineynoy
uprugosti dlya garmonicheskogo materiala [Plane problem of
non-linear elasticity for harmonic material]. {\it Vestnik of
Saint Petersburg State University. Series 1. Mathematics.
Mechanics. Astronomy}, 2008, iss.~3, pp.~114--126. (In Russian)

5. {Ru C.\,Q., Schiavone P., Sudak L.\,J., Mioduchowski A.}
Uniformity of stresses inside an elliptic inclusion in finite
plane elastostatics. {\it Intern. Journal of Non-linear
mechanics}, 2005, vol.~38, no.~2--3, pp.~281--287.

6. {Malkov V.\,M., Malkova Yu.\,V.} Modelirovanie nelineinoy
deormacii ploskosti s ellipticheskim otverstiem ili vklucheniem
garmonicheskim materialom Djona [Modeling nonlinear deformation of
a plane with an elliptic inclusion by John's harmonic material].
{\it Vestnik of Saint Petersburg State Uni-\linebreak versity.
Mathematics. Mechanics. Astronomy}, 2017, vol. 4 (62), iss.~1,
pp.~121--130. (In Russian) DOI: 10.21638/11701/ spbu01.2017.114

7. { Mal'kov V.\,M.,  Mal'kova Yu.\,V.} Modeling Nonlinear
Deformation of a Plate with an Elliptic Inclusion by John's
Harmonic Material. {\it Vestnik of Saint Petersburg University.
Mathematics}, 2017, vol.~50, iss.~1, pp.~74--81. DOI:
10.3103/S1063454117010095

8. {Malkov V.\,M., Malkova Yu.\,V., Stepanova V.\,A.}
Dvuhkomponentnaya ploskost is materiala Dzhona s mezhfaznoy
treshinoy, nagruzhennoy davleniem [Bi-material plane of John's
material with interface crack loaded by pressure]. {\it Vestnik of
Saint Petersburg State University. Series 1. Mathematics.
Mechanics. Astronomy}, 2013, iss.~3, pp.~113--125. (In Russian)

9. {Malkov V.\,M., Malkova Yu.\,V., Domanskaya T.\,O.} Analiz
napryazheniy dvuhkomponentnoy ploskosti i poluploskosti pri
deystvii sosredotochennoy sily dlya dvuh modeley garmonicheskogo
materiala [Analysis of stresses of bi-material plane and
half-plane at action of a point force for two models of harmonic
materials]. {\it Vestnik of Saint Petersburg State University.
Series 10. Applied Mathematics. Computer Science. Control
Processes}, 2016, iss.~1, pp.~38--52. (In Russian)%\newpage

10. { Domanskaia T., Malkov V., Malkova Yu}. Bi-material plane of
John's harmonic material with %\linebreak\newpage\noindent
a point
force at interface. {\it XXIV Intern. Congress of Theor. and Appl.
Mech. (ICTAM)}, 21--26 August 2016. Montreal,  Canada, 2016,
pp.~1958--1959.

11. {Domanskaya T.\,O., Malkov V.\,M., Malkova Yu.\,V.}
Nelineinaya zadacha dlya compozitnoy plastinu s mejfaznoy
trechinoy dlya garmonicheskogo materiala Djona [Nonlinear problem
for bi-material plate with interface crack for harmonic John's
material].  {\it  2nd Intern. Conference ``Deformation and Failure
of Composite Materials and Structures''.} (DFCMS--2016). October
2016. Moscow, Institute of Engineering RAS Publ., 2016,
pp.~33--35.  (In Russian)

12. {Malkov V.\,M., Malkova Yu.\,V.} Issledovanie nelineynoy
zadachi Flamana [Investigation of non-linear Flamant's problem].
{\it Izv. RAS. Mechanics of solids}, 2006, no.~5, pp.~68--78. (In
Russian)

13. {Malkov V.\,M., Malkova Yu.\,V.} Analiz singulyarnosti
napryazheniy v nelineynoy zadache Flamana dlya nekotoryih modeley
materiala [Analysis of singularity of stresses in non-linear
Flamant's problem for some material models]. {\it Applied
Mathematics and Mechanics}, 2008, vol.~72, no.~3, pp.~453--462.
(In Russian)

14. {Malkov V.\,M.} {\it Vvedenie v nelineynuyu uprugost} [{\it
Introduction to non-linear elasticity}]. Saint Petersburg, Saint
Petersburg State University Publ., 2010, 276~p. (In Russian)

15. {Muskhelishvili N.\,I.} {\it Nekotorye osnovnye zadachi
matematicheskoy teorii uprugosti} [{\it Some basic problems of
mathematical theory of elasticity}].
 Moscow, Nauka Publ., 1966, 708~p. (In Russian)

16. {Malkova Yu.\,V.} {\it Nekotorye zadachi dlya dvuhkomponentnoy
ploskosti s krivolineynyimi treshinami} [{\it Some problems for
bi-material plane with curvilinear cracks}]. Saint Petersburg,
Saint Petersburg State University Publ., 2008, 160~p. (In Russian)




\vskip 2mm

{\bf For citation:}  Domanskaya T.\,O., Malkov V.\,M.,
Malkova~Yu.\,V. Mathematical modeling of the deformation of
composite plane with interface crack for John's harmonic material.
{\it Vestnik of Saint Petersburg University. Applied Mathematics.
Computer Science. Control Processes}, \issueyear, vol.~13,
iss.~\issuenum, pp.~\pageref{p4}--\pageref{p4e}.
\doivyp/spbu10.\issueyear.\issuenum04


}
