
{\normalsize

\vskip 6mm

\noindent{\bf On the limiting behavior of a time-delay system's
solutions}

}

\vskip 1.5mm

{\small

\noindent{\it S.~E.~Kuptsova$^1$, S.~Yu.~Kuptsov$^2$,
N.~A.~Stepenko$^1$}

\vskip 1.5mm


{\footnotesize

\noindent $^1$~St.\,Petersburg State University, 7--9,
Universitetskaya nab., St.\,Petersburg, 199034, Russian Federation

\noindent $^2$~OOO ``OGS Russia'', 21a, Gakkelevskaya str.,
St.\,Petersburg, 197227, Russian Federation

}

\vskip3mm

\noindent \textbf{For citation:}  Kuptsova S. E., Kuptsov S. Yu.,
Stepenko N. A. On the limiting behavior of a time-delay system's
solutions. {\it Vestnik of Saint~Petersburg University. Applied
Mathematics. Computer Science. Control Processes}, \issueyear,
vol.~14, iss.~\issuenum, pp.~\pageref{p10}--\pageref{p10e}.
\doivyp/ spbu10.\issueyear.\issuenum10

\vskip3mm

{\leftskip=7mm\noindent In the present paper, we study motions of
time-delay systems that have limiting behavior for an unbounded
increase in time in the case when the limit sets might not be
invariant with respect to initial differential-difference
equations. The concept of an asymptotic quiescent position for the
trajectories of time-delay systems is introduced. By the use of
the Lyapunov functionals method, sufficient conditions for the
existence of an asymptotic quiescent position for systems of
differential-difference equations were obtained. In the case when
a general system has a trivial solution, new sufficient conditions
for its asymptotic stability are obtained. Namely, the condition
of the negativity of the time-derivative
of Krasovskii functionals is weakened.\\[1mm]
\textit{Keywords}: Time-delay systems, asymptotic stability,
asymptotic quiescent position, Lyapu-\linebreak nov functions.
\par}

\vskip5mm

\noindent \textbf{References} }

\vskip 2mm

{\footnotesize

1. Krasovskii~N.~N. {\it Nekotorye zadachi teorii ustoichivosti
dvizhenia $[$Some problems of the theory of stability of
motions$]$.} Ìoscow, State Publ. of Phys. and Math. Literature,
1959, 211~p. (In Russian)

2. Bellman~R., Cooke~K.~L. {\it Differencial-difference
equations.} New York, Academic Press, 1963, 482~p. (Russ. ed.:
Bellman~R., Cooke~K.~L. {\it Differentsial'no-raznostnye
uravneniia.} Moscow, Mir Publ., 1967, 548~p.)

3. Hale~J. {\it Theory of functional differential equations.} New
York, Springer Press, 1977, 365~p. (Russ. ed.: Hale J. {\it Teoria
functsional'no-differentsial'nyh uravnenii.} Moscow, Mir Publ.,
1984, 421~p.)

4. Zubov~V.~I. {\it Lektsii po teorii upravlenia $[$Lectures on
theory of control$]$.} Moscow, Nauka Publ., 1975, 496~p.

5. Zubov~V.~I. K teorii lineinyh statsionarnyh sistem s
zapazdyvayuschim argumentom [To the theory of linear time-delay
systems]. {\it Izvestiia visshikh uchebnih zavedenii. Matematika
$[$Proc. of Higher Educational Institutions. Mathematics$]$},
1958, no.~6, pp.~86--95. (In Russian)

6. Zubov~V.~I. {\it Kolebania i volny $[$Oscillations and
waves$]$.} Leningrad, Leningr. State University Publ., 1989,
416~p. (In Russian)

7. Kuptsova~S.~E. Asimptoticheski invariantnye mnojestva [An
asymptotically invariant sets]. {\it Control Processes and
Stability $($CPS$)$.} Saint Petersburg, Saint Petersburg
Uni\-ver\-sity Publ., 2006, pp.~50--56. (In Russian)

8. Zubov~S.~V. O raschotnoi ustoichivosty odnogo klassa nelineinyh
sistem [On the rated stability of a class of nonlinear systems].
{\it Control Processes and Stability (CPS).} Saint Petersburg,
Saint Petersburg University Publ., 2006, pp.~29--33. (In Russian)

9. Tikhomirov~O.~G., Temkina~E.~V. Asimptoticheskoe polojenie
pokoia dlia sistem odnorodnyh nestatsyonarnyh differentialnyh
uravnenii [Asymptotic quiescent position for systems of
homogeneous non-autonomous differential equations]. {\it Vestnik
of Saint Petersburg University. Series~10. Applied Mathematics.
Computer Science. Control Processes}, 2014. iss.~2, pp.~58--65.
(In Russian)

10. Ekimov~A.~V., Svirkin~M.~V. Analysis of asymptotic equilibrium
state of differential systems using Lyapunov function method. {\it
2015 Intern. conference ``Stability and control processes'' in
memory of V.~I.~Zubov $($SCP$)$.}  Saint Petersburg, IEEE, 2015,
pp.~45--47.

11. Kuptsova~S.~E. Asimptoticheskie polojenia pokoia v sistemah
raznostnyh uravnenii [The asymptotic rest positions  in the
systems of difference equations]. {\it Sistemy uprav\-leniia i
informatsionnye tekhnologii $[$Control Systems and Information
Technology$]$}, 2014, vol.~56, no.~2, pp.~67--71. (In Russian)

12. Kuptsov~S.~Yu., Kuptsova~S.~E., Zaranik~U.~P. On asymptotic
quiescent position of nonlinear difference systems with
perturbations. {\it 2015 Intern. conference ``Stability and
control processes'' in memory of V.~I.~Zubov $($SCP$)$.} Saint
Petersburg, IEEE, 2015, pp.~20--22.

13. Kharitonov~V.~L. {\it Time-delay systems: Lyapunov functionals
and matrices}. Basel, Birkh\"{a}user Press,  2013, 311~p.

14. Kudryavtsev~L.~D.  {\it Kurs matematicheskogo analiza $[$A
course in mathematical analy\-sis$]$.} In~3~vol. Moscow, Vysshaya
shkola Publ., 1988, vol.~1, 712~p. (in Russian)



\vskip5mm A\,u\,t\,h\,o\,r's \ I\,n\,f\,o\,r\,m\,a\,t\,i\,o\,n:
\vskip1.5mm \textit{Kuptsova Svetlana E.}~--- PhD Sci. in physics
and mathematics, associate professor;\\ sekuptsova@yandex.ru

\textit{Kuptsov Sergey Yu.} --- PhD Sci. in physics and
mathematics; srgkuptsov@yandex.ru

\textit{Stepenko Nikolai A.} --- PhD Sci. in physics and
mathematics, associate professor; nick\_st@mail.ru


}
